### 2011-04-07 extended_catalog/paper/paper.tex
more paper

\documentclass[12pt]{article}

\title{Search for Spatially Extended Sources Using Two Years of Flight
Data}

\usepackage{amsmath}

\begin{document}

\maketitle

\abstract{
We present a new method for analyzing spatially 
extended sources with the Fermi Large Area
Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.
We provide a series of Monte Carlo studies
that were done to validate this tool.
We then apply this tool to test all sources in
the 2FGL Two Year Catalog for extension
and report on the discovery of new extended sources.\cite{2FGL}
}

\section{Introduction}

% * Resolving spatially extended Fermi sources is important for 
%    * studying supernova remnants, 
%    * pulsar wind nebulae, 
%    * galaxies,  
%    * potentially dark matter or new physics.
% * We searched all 2FGL catalog sources
% * Systematic test for a certain kind of (~ small) regularly shaped extended

\section{Analysis Method}

%   * Difficulty of studying spatially extended sources
%   * Pointlike, great features
%   * modifying it to fit spatially extended sources.
%      * semi-analytic convolution formula
%   * importance of fitting position + extension + spectrum simultaneously to apply statistical significance
%   * Monte Carlo Validation
%

Performing morphological studies of sources in the GeV energy range using
the Fermi LAT is challenging primarily because of the significantly energy
dependent point spread function and because of systematic errors in the
galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
at 100MeV to $XXXXX^\circ$ at 100GeV and so the higher energy photons are
significantly more important for studying the shape of sources. One could
ideally look just at the highest energy photons, but the trade off is that
for typical sources many more source events are expected at low energy.
For this reason, it is especially important to use as much of the data
as possible.

The second primary difficult in studying spatially extended sources is
systematic uncertainties in the diffuse emission. Systematic errors are
notoriously difficult and will be discussed more later, but the important
point to make here is that one of the most important diagnostic tools for
studying systematic errors is being able to iterate the analysis while
varying different parameters such as what goes into the diffuse model.

A new analysis tool has been developed to address these unique
requirements for studying spatially extended sources with the Fermi
LAT. The overall approach for this analysis is to perform a maximum
likelihood analysis where the Poisson likelihood for observing the
measured counts is computed given an assumed sky model. The parameters
of the sky model are then fit by maximizing the log of the likelihood.
To study the extension of a source, one can assume a particular shape
for an extended source (e.g. a disk or Gaussian), and fit the spatial
parameters of that source.

In principle, the entire task can be done using the standard science
tools package {\em gtlike}\cite{Science-Tools-gtlike}. But {\em gtlike} is
only able to fit the spectral parameters of the source, so the extension
fitting would have to be done as an external loop. Typically, the run time
for a binned source analysis using {\em gtlike} is several hours so this loop
would be especially time consuming. In principle, parallel computing could
ease this burdon, but parallel fitting algorithms are rather untested
and complex. Furthermore, the machinery required to do something like
this would necessarily be rather complex. What has typically been done by
the Fermi team to study extended sources is to fix the assumed position
of the extended source, either by our knowledge of a source from other
wavelenghts, or by fitting it as a point source. Then, a profile of the
likelihood as a function of extension is developed using {\em gtlike}
and the maximum of this profile. This approach is not optimal because it
needs not be the case that the best fit position of a point source would
be the same as the best fit position of an extended source. Furthermore,
by not fully maximizing the likelihood, this method is not as significant to
extension, especially of faint sources. And finally, since this approach
is so computationally intensive, no large scale Monte Carlo effort has been
launched to validate the method.

Instead, an alternate approach was developed for performing
a morphological analysis. An alternate maximum likelihood fitting
package called {\em pointlike} has been developed by the Fermi
collaboration and we have expanded its functionality to fully support
analyzing spatially extended sources. {\em pointlike} is most thoroughly
described in Matthew Kerr's Ph.D Thesis\cite{Matthew_kerr_phd_thesis}
but the important aspects will be summarized below. What differentiates
{\em pointlike} most significantly from {\em gtlike} is its emphasis
on speed by introducing approximations into the calculation of the
likelihood function while at the same time trying to reduce any
numerical errors that may be introduced.  Like binned {\em gtlike},
{\em pointlike} bins the sky both in position and energy.  Unlike {\em
gtlike}, pointlike relies on the {\em healpix} representation of spatial
bins\cite{healpix_paper} and scales the size of each spatial bin to be
smaller than the point spread function. This is convenient because it no
significant information is lost due to binning at all energies and it is
always a good approximation that the model predicted counts are uniform
across a spatial bin. Furthermore, {\em pointlike} uses a sparse matrix
representation of the spatial bins where only the bins with counts in
them are looped over. The only downside to this is that the integral of
the model predicted counts must be independently calculated.  Effectivly,
{\em pointlike} efficiently interpolates from a totally binned analysis
at low energy (where the resolution is poor and there are many counts)
to an unbinned analysis at high energy (where the resolution is very good
but there are few counts). This approach provides significant savings
in time without introducing large numerical error.

% PseudoHypothesis

\section{Validation}

One can define a parameter $\text{TS}_\text{ext}$ as twice the increase
in log likelihood going from fitting a source with a point hypothesis to fitting
it as an extended hypothesis. So $\text{TS}_\text{ext}=2\times(LL_\text{ext}-LL_\text{ps})$.
In going from fitting a point source to fitting a simple extended source such as
a disk, one degree of freedom, the source width, is added. According to
Wilk's Theorem, the distribution of $\text{TS}_\text{ext}$ for no signal (a true
point source) should follow a $\chi^2$ distribution with one degree of freedom\cite{Wilks_Theorem}.
On the other hand, since the null hypothesis exists on the edge of parameter space,
and so so Wilk's Theorem does not hold\cite{Warnings about Wilk's Thorem}.
One might expect the actual distribution to be a half $\chi^2$ distribution with a delta
function at 0. This was the distribution found to be true for source finding of
gamma ray sources.\cite{Mattox_et_All_Paper}. A Monte Carlo study has been performed to
show how well we can believe the statistical significance.

\section{Extension search method}

% * Plots we make ...

\section{Results}

\section{Interpretation}

\end{document}

### 2011-04-11 extended_catalog/paper/extended_catalog.tex
adding new figure

--- 2011-04-07 extended_catalog/paper/paper.tex
@@
 \documentclass[12pt]{article}
+\usepackage{fullpage}
 
@@
 \abstract{
-We present a new method for analyzing spatially 
-extended sources with the Fermi Large Area
-Telescope (LAT), the primary science instrument
-on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.
-We provide a series of Monte Carlo studies
-that were done to validate this tool.
-We then apply this tool to test all sources in
-the 2FGL Two Year Catalog for extension
-and report on the discovery of new extended sources.\cite{2FGL}
+We present a new method for analyzing spatially extended sources with
+the Fermi Large Area Telescope (LAT), the primary science instrument
+on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
+series of Monte Carlo studies that were done to validate this tool.
+We then apply this tool to test all sources in the 2FGL Two Year Catalog
+for extension.\cite{2FGL} We then report on the discovery of XXX new
+extended sources.
 }
@@
 % * Systematic test for a certain kind of (~ small) regularly shaped extended
+
+The Large Area Telescope (LAT) on the Fermi Gamma-Ray Space Telescope
+has been surveying the Gamma-ray sky since August 2008. The LAT has been
+been essential in studying a variety of astrophysical sources including
+Active Galactic Nuclie, Pulsars, Supernova Remnants. 
+One of the important data productes
+
+Using 11 months of data, the LAT produced the best-resolved survey of the sky
+in the 100 MeV to 100 GeV energy range\cite{2FGL Paper}. The
 
@@
 the Fermi LAT is challenging primarily because of the significantly energy
-dependent point spread function and because of systematic errors in the
+dependent point spread function (PSF) and because of systematic errors in the
 galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
@@
 bins\cite{healpix_paper} and scales the size of each spatial bin to be
-smaller than the point spread function. This is convenient because it no
+smaller than the PSF. This is convenient because it no
 significant information is lost due to binning at all energies and it is
@@
 across a spatial bin. Furthermore, {\em pointlike} uses a sparse matrix
-representation of the spatial bins where only the bins with counts in
-them are looped over. The only downside to this is that the integral of
-the model predicted counts must be independently calculated.  Effectivly,
+representation of the spatial bins where only the bins with counts in them
+are looped over. The only downside to this is that the integral of the
+model predicted counts must be independently calculated.  Effectively,
 {\em pointlike} efficiently interpolates from a totally binned analysis
 at low energy (where the resolution is poor and there are many counts)
-to an unbinned analysis at high energy (where the resolution is very good
-but there are few counts). This approach provides significant savings
-in time without introducing large numerical error.
+to an unbinned analysis at high energy (where the resolution is very
+good but there are few counts). This approach provides a significant
+savings in time while introducing only small numerical error.
 
-% PseudoHypothesis
+We have modified {\em pointlike} to support fitting spatially extended
+sources.  To do this, we introduced a new class of diffuse sources where
+the spatial and spectral information completely decouple and where
+the spatial shape is parameters by simple objects (Disks, Gaussian).
+The code consistently convolves the extended source shape with the point
+spread function (as a function of energy) and integrates the spectrum over energy
+to computed model predicted counts.
 
-\section{Validation}
+Finally, {\em pointlike} allows the spatial parameters of an extended
+source to be simulataneoulsy fit. {\em pointlike} uses the Minuit fitting
+library to perform the maximum likelihood maximization of the position
+and extension of an extended source\cite{Minuit reference}.  At each
+step in the fit of the shape, the spectral parameters of the entire sky
+model are reoptimized. To avoid projection effects, what is directly
+fit is not the longitude and latitude of the source but instead
+the displacement in a rotated reference frame. The covariance matrix is
+then computed and inverted to estimate the statistical errors on the
+position and extension.
+
+{\em pointlike} optimizes the analysis of extended sources in two ways.
+First, for extended sources which are radially symmetric, the convolution
+of the source shape with our parameterization of the PSF can be performed
+semi-analytically. Generally, at a given energy the observed 
+photon distribution is
+\begin{equation}
+  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') d A' 
+\end{equation}
+where $I_\text{src}$ is the extended soruce shape and the PSF is parameterized by
+\begin{equation}
+  \text{PSF}(\vec r) = 
+  \frac{1}{2\pi\sigma^2}
+  \left(1-\frac{1}{\gamma}\right)
+  \left(1+\frac{u}{\gamma}\right)^{-\gamma}
+\end{equation}
+Here, $\sigma$ and $\gamma$ are parameterize the $PSF$.
+If the extended source is radially symmetric, then
+$I_\text{src} (\vec r') = I_\text{src} (r')$ and the angular part of the
+integral can be done analytically, leaving a simpler one dimensional
+integral:
+\begin{equation}
+  \text{PDF}(u)= \int_0^\infty dv
+  I_\text{src}(v) 
+  \left(\frac{\gamma-1}{\gamma}\right)
+  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma
+  ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right)
+\end{equation}
+Not only is this convolution formula faster, but it has the advantage
+that it more accurately reduces to the actual PSF shape as the source's
+size decreases.  Decreasing the numerical difference between a small extended
+source and the PSF is important when searching for smaller extended sources
+and when determining the statistical significance of a detection.
+
+There is one final approximation which speeds up the convolution.
+Generally, the PSF is a function of the angle $\theta$ of the incident
+event measured relative to the normal to the LAT. To avoid repeatedly
+convolving the source shape with the PSF at a series of $\theta$ angles,
+an effective PSF is fit to the weighted sum of the PSF times the exposure
+at different $\theta$ angles.  Since the source convolution has to be
+done at each fit iteration, these optimization were essential for making
+this tool fast enough for the following analysis. Typically, the entire
+process of fitting the extension and estimating the errors for a source
+would run on the order of an hour.
+
+\section{Monte Carlo Validation}
 
@@
 it as an extended hypothesis. So $\text{TS}_\text{ext}=2\times(LL_\text{ext}-LL_\text{ps})$.
+Note that Wilk's Theorem only holds when the likelihood is maximized simultaneoulsy
+fitting all of the parameters of model. It is for this reason why {\em pointlike}
+goes through such great effort to simultaneously fit the position and extension of
+a source.
 In going from fitting a point source to fitting a simple extended source such as
@@
 On the other hand, since the null hypothesis exists on the edge of parameter space,
-and so so Wilk's Theorem does not hold\cite{Warnings about Wilk's Thorem}.
+and so so Wilk's Theorem does not hold\cite{Warnings about Wilk's Theorem Paper}.
 One might expect the actual distribution to be a half $\chi^2$ distribution with a delta
@@
 
+One issue that we found when testing this analysis method is that
+despite our best efforts, there was always a small discrepancy between
+the likelihood value when fitting the source as a point source and when
+fitting it as an extended source with a small extension.  This is to be
+expected due to numerical innacuracies introduced by the convolution.
+For most cases, this error is insignificant. It would not significanlty
+bias any of the fit values or errors. But it would bias the distribution
+of $\text{TS}_\text{ext}$ in the null hypothesis. To correct for this,
+instead of computing the likelihood in the null hypothesis by fitting
+a point source, a new source model was introduced which is an extended
+source with its extension fixed to a very small value. $LL_\text{ps}$
+is then calculated by refitting this source using the same extended
+source fitting code. It was only after introducing this change that we
+were able to get broad agreement between simulations and Wilk's theorem.
+
+\includegraphics{k
+
 \section{Extension search method}
@@
 
-\section{Results}
+\section{Test of 1LAC Sources}
+
+\section{Validation of Known Extended Sources}
+
+\section{New Extended Sources}
 

### 2011-04-12 extended_catalog/paper/extended_catalog.tex
Working on paper

@@
 \usepackage{fullpage}
+\usepackage{graphicx}
 
@@
 
-One can define a parameter $\text{TS}_\text{ext}$ as twice the increase
-in log likelihood going from fitting a source with a point hypothesis to fitting
-it as an extended hypothesis. So $\text{TS}_\text{ext}=2\times(LL_\text{ext}-LL_\text{ps})$.
-Note that Wilk's Theorem only holds when the likelihood is maximized simultaneoulsy
+To calculate the statistical significance of the extension of a source,
+one can define a parameter $\text{TS}_\text{ext}$ as twice the increase
+in log likelihood between fitting a source with a
+spatially extended hypothesis and a point hypothesis. 
+So $\text{TS}_\text{ext}=2\times(LL_\text{ext}-LL_\text{ps})$.
+
+In going from fitting a point source to fitting a simple extended source such as
+a disk, the source's width is the only degree of freedom added to the model. According to
+Wilk's Theorem, the distribution of $\text{TS}_\text{ext}$ for no signal (when there is a true
+point source) should follow a $\chi^2$ distribution with one degree of freedom\cite{Wilks_Theorem}.
+Wilk's Theorem only holds when the likelihood is maximized simultaneoulsy
 fitting all of the parameters of model. It is for this reason why {\em pointlike}
-goes through such great effort to simultaneously fit the position and extension of
-a source.
-In going from fitting a point source to fitting a simple extended source such as
-a disk, one degree of freedom, the source width, is added. According to
-Wilk's Theorem, the distribution of $\text{TS}_\text{ext}$ for no signal (a true
-point source) should follow a $\chi^2$ distribution with one degree of freedom\cite{Wilks_Theorem}.
-On the other hand, since the null hypothesis exists on the edge of parameter space,
-and so so Wilk's Theorem does not hold\cite{Warnings about Wilk's Theorem Paper}.
-One might expect the actual distribution to be a half $\chi^2$ distribution with a delta
-function at 0. This was the distribution found to be true for source finding of
-gamma ray sources.\cite{Mattox_et_All_Paper}. A Monte Carlo study has been performed to
-show how well we can believe the statistical significance.
+goes through such great effort to simultaneously fit the position, extension,
+and spectral paramters of a source.
+
+On the other hand, since the null hypothesis rests on the edge of
+parameter space, when the extension is fixed to 0, Wilk's Theorem does
+not formally hold\cite{Warnings about Wilk's Theorem Paper}.  One might
+expect the actual distribution to be a half $\chi^2_1$ distribution with
+one degree of freedom plus half of a delta function at 0:
+\begin{equation}
+  P(\text{TS})=\tfrac{1}{2}(\chi^2_1(\text{TS})+\delta(\text{TS})).
+\end{equation}
+The false detection probability can be estimated by integrating this function 
+from an observed test statistic value to infinity. It is for this
+particular distribution that the often quoted result holds that
+$\sqrt{TS}$ is a measure of the number of $\sigma$ of the detection.
+
+The half $\chi^2_1$ distribution was found by a monte carlo study
+to hold for the special case of source finding of EGRET sources using the
+maximum likelihood technique.  They were comparing the hypothesis of a
+source to the hypothesis of just a background\cite{Mattox_et_All_Paper}.
+Their argument for why this null hypothesis distribution was reasonable
+was that half of the time, statistical underfluctuations would cause
+there to be fewer fewer photons then expected where the sources is being
+tested. Since the maximim likelihood machinery cannot fit negative
+sources (which would lead to negative model predicted for which the
+poisson likelihood is undefined), half of the tests would not have the
+likelihood improved by adding a source to the model and $\text{TS}=0$.
+It is for the case that the null distribution has
+
+It seems plausable that a similar situation could happen for when 
+testing a source for extension. Half of the time, statistical flucutations
+might make the observed counts narrower thant the point spread function
+and the likelhood would not improve by fitting the source with an extended
+hypothesis. We tested this hypothesis using a dedicated monte carlo study.
+
+\begin{figure}
+\includegraphics{mc_plots/ts_ext_emin_1000.pdf}
+% this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
+% using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
+\caption{Lalla}
+\end{figure}
 
@@
 
-\includegraphics{k
+\section{Extended Source Sensitivity}
 

### 2011-04-20 extended_catalog/paper/extended_catalog.tex
Adding more plots

@@
-\documentclass[12pt]{article}
+\documentclass{emulateapj}
+
 \usepackage{fullpage}
@@
 
-\title{Search for Spatially Extended Sources Using Two Years of Flight
-Data}
+\shorttitle{Search for Extended LAT Sources}
 
@@
 
-\maketitle
+\title{Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight
+Data}
 
-\abstract{
+\author{
+J.~Lande\altaffilmark{3}, 
+\altaffiltext{3}{W.
+W.
+Hansen Experimental Physics Laboratory, Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics and SLAC National Accelerator Laboratory, Stanford University, Stanford, CA 94305, USA}
+}
+
+\begin{abstract}
 We present a new method for analyzing spatially extended sources with
@@
 extended sources.
-}
+\end{abstract}
 
@@
 % * Systematic test for a certain kind of (~ small) regularly shaped extended
+
+The Large Area Telescope (LAT) is a pair conversion telescope on the
+Fermi Gamma-Ray Space Telescope that has been surveying the gamma ray
+sky since June 2008.  Fermi is particuarly well suited for surveying
+the entire Gamma-ray sky since it has a broad energy coverage (20MeV
+and 300GeV), a wide field of view (~2.4 sr) and large effective area
+($\approx 8000 \text{cm}^2$ at > 1GeV).
+
+The LAT has been essential in understanding a variety of astrophysical
+sources including Active Galactic Nuclei, Pulsars, and Supernova Remnants.
+Many of the astrophysical sources seen by the Fermi LAT, espeically
+galactic Supernova Remnants and Pulsar Wind Nebulae, can be resolved at
+other wavelengths and could potentially be resolved by the LAT.
+
+Resolving spatially extended GeV sources is important for studying a
+variety of science topics. The most important use of spatial morphology
+is in source identification. Many of the sources found in GeV sources
+
+Nevertheless, morphological studies of sources in the GeV energy range using
+the Fermi LAT is challenging primarily because of the significantly energy
+dependent PSF and because of systematic errors in the
+galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
+at 100MeV to $XXXXX^\circ$ at 100GeV and so the higher energy photons are
+
+studying supernova remnants, 
+pulsar wind nebulae, 
+ * galaxies,  
+ * potentially dark matter or new physics.
 
@@
 the Fermi LAT is challenging primarily because of the significantly energy
-dependent point spread function (PSF) and because of systematic errors in the
+dependent PSF and because of systematic errors in the
 galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
@@
 integral:
-\begin{equation}
+\begin{multline}
   \text{PDF}(u)= \int_0^\infty dv
@@
   \left(\frac{\gamma-1}{\gamma}\right)
-  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma
-  ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right)
-\end{equation}
+  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma \\
+  \times ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right)
+\end{multline}
 Not only is this convolution formula faster, but it has the advantage
@@
 
-\section{Monte Carlo Validation}
-
 To calculate the statistical significance of the extension of a source,
@@
 Wilk's Theorem, the distribution of $\text{TS}_\text{ext}$ for no signal (when there is a true
-point source) should follow a $\chi^2$ distribution with one degree of freedom\cite{Wilks_Theorem}.
+point source) should follow a $\chi^2_1$ distribution with one degree of freedom\cite{Wilks_Theorem}.
 Wilk's Theorem only holds when the likelihood is maximized simultaneoulsy
@@
 
-It seems plausable that a similar situation could happen for when 
-testing a source for extension. Half of the time, statistical flucutations
-might make the observed counts narrower thant the point spread function
-and the likelhood would not improve by fitting the source with an extended
-hypothesis. We tested this hypothesis using a dedicated monte carlo study.
-
-\begin{figure}
-\includegraphics{mc_plots/ts_ext_emin_1000.pdf}
-% this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
-% using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
-\caption{Lalla}
-\end{figure}
+It seems plausable that a similar situation could happen for when testing
+a source for extension. Half of the time, statistical flucutations might
+make the observed counts narrower thant the point spread function and
+the likelhood would not improve by fitting the source with an extended
+hypothesis. We tested this hypothesis below using a dedicated monte
+carlo study.
 
@@
 
+\section{Monte Carlo Validation}
+
+We performed a dedicated monte carlo study to validate pointlike for
+studying spatially extended sources and also to demonstrate that we can
+use $\text{TS}_\text{ext}$ as a test of the statistical significance
+of a source's extension.  The monte carlo study involved simulating point
+sources of varying spectral models on top of a simulated background. The
+simulated point source was then fit using pointlike as both an extended
+source and a point source and $\text{TS}_\text{ext}$ was calculated.
+
+Fermi LAT data was simulated using the publically avaliabable Science
+Tools package {\em gtobssim}\cite{GTOBSSIM_CITATION}. The sources were
+simulated with a powerlaw spectral model with 6 Were given 6 $>100\text{MeV}$
+fluxes ranging from $3\times 10^{-9} ph/cm^2/s$ to $10^{-6} ph/cm^2/s$.
+The sources were then simulated with spectral index ($\gamma$) values of
+1.5, 2, 2.5, and 3.  These values were picked to probe a representative
+range measurable values.  For particular spectral indices, only the
+fluxes which would create a statistically significant source detection
+($\text{TS}>25$) where selected, since we are only interested in
+testing for extension sources with a significant extent. The sources were
+simulated on top of an isotropic powerlaw background with a Sreekumar-like
+spectrum ($>\text{100MeV}$ flux of 1.5e-5 and spectral index 2.1).\cite{Sreekumar
+et al. ApJ 494 pag 523 1998}
+
+The monte carlo simulation was perforormed over a one year time interval using
+a default rocking profile and an assumed livetime fraction of 0.8.
+The reconstruction was perfromed with events from an energy range of
+1GeV to 100GeV using 4 energy bins per decade and using the Pass 7 Version 6
+source IRFs to be consistent with the following analysis.
+
+For most of the spectral models, over 10,000 statistically independent simulations were performed.
+For fainter sources, some of the simulated sources, statistical flucatuations
+caused the source to be not significant and they were excluded from the following analysis.
+Table~\ref{ts_ext_num_sims} shows the parametesr used in the simualtion,
+the number of simulations perfromed, and the average test statistic value.
+
+\begin{table}
+  \begin{centering}
+\begin{tabular}{ | r | r | r | r | }
+\hline
+$\gamma$ & flux ($ph/cm^2/s$) & $N_\text{sims}$ & $<\text{TS}>$ \\
+\hline
+  1.5 &          $10^{-6}$ &           11405 &  90861 \\
+      &  $3\times 10^{-7}$ &           11490 &  21922 \\
+      &          $10^{-7}$ &           11101 &   5765 \\
+      &  $3\times 10^{-8}$ &           10269 &   1262 \\
+      &          $10^{-8}$ &            9941 &    306 \\
+      &  $3\times 10^{-9}$ &           10427 &     61 \\
+\hline
+    2 &          $10^{-6}$ &           11632 &  22025 \\
+      &  $3\times 10^{-7}$ &           11622 &   4886 \\
+      &           $1^{-7}$ &           11115 &   1159 \\
+      &  $3\times 10^{-8}$ &           10503 &    222 \\
+      &           $1^{-8}$ &            9893 &     50 \\
+\hline
+  2.5 &          $10^{-6}$ &           11522 &   4722 \\
+      &  $3\times 10^{-7}$ &           11445 &    948 \\
+      &           $1^{-7}$ &           10966 &    202 \\
+      &  $3\times 10^{-8}$ &            8227 &     41 \\
+\hline                                                
+    3 &          $10^{-6}$ &           11264 &    949 \\
+      &  $3\times 10^{-7}$ &           10986 &    172 \\
+      &           $1^{-7}$ &            7855 &     40 \\
+\hline
+\end{tabular}
+\caption{List of the spectral models used to the monte carlo simulation of
+{\em pointlike}.$N_\text{sims}$ is the number of monte carlo simluations
+which produce a significant source detection.The final column is the
+average test statistic that was found during the monte carlo fit of
+the source. Only simluations which were deemed significant ($\text{TS}>25$)
+were kept.}
+\label{ts_ext_num_sims}
+  \end{centering}
+\end{table}
+
+The results of the monte carlo simulation are shown in
+figure~\ref{ts_ext}.  The cumulative density function (CDF) is plotted
+against $\text{TS}_\text{ext}$ For reference, the CDF for $\chi^2_1/2$,
+suggested by Wilk's Theorem, is also plotted for comparison. Overall,
+there is good agreement between Wilk's theorem, although the agreement
+is not perfect.  Possible reasons for departure from Wilk's theorem may
+include pointlike ignoring energy dispersion, which would generally change
+the shape as a function of energy, numerical innacuracies in evaluating
+the convolution algorithm, or possibly problems with the fitting algorithm
+getting stuck in false minimum. It is important to emphasize that if
+our emperical curve lies to the left of the curve we assume to estimate
+significance, we would underestimate the statistical significance of
+our result. Since this is the case for most of our simluations, we are
+reasonable confident that $\sqrt{\text{TS}_\text{ext}}$ can be safely
+used as a measure of the statistical significance of a source's extension.
+
 \section{Extended Source Sensitivity}
+
+We use another monte carlo study to determine the Fermi LAT's sensitivity to
+spatially extended sources.
 
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
+    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
+    \end{center}
+    \caption{Lalla}\label{ts_ext}
+  \end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics{mc_plots/sensitivity.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v8/merged_plot.py
+    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/sensitivity/v7/merged.hdf5 (>1GeV)
+    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/sensitivity/v8/merged.hdf5 (>100MeV)
+    \end{center}
+    \caption{Lalla}\label{sensitivity_ext}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1628.6-2419c}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J1628.6-2419c/v2/source_1FGL_J1628.6-2419c.pdf
+    \caption{Lalla}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1554.0-5345c}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J1554.0-5345c/v2/source_1FGL_J1554.0-5345c.pdf
+    \caption{Lalla}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
+    \caption{Lalla}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J2020.0+4049}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J2020.0+4049/v2/source_1FGL_J2020.0+4049.pdf
+    \caption{Lalla}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_MRFH0254}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/MRFH0254/v2/source_MRFH0254.pdf
+    \caption{Lalla}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1837.5-0659c}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J1837.5-0659c/v2/source_1FGL_J1837.5-0659c.pdf
+    \caption{1FGL J1837.5-0659c}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1636.4-4737c}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J1636.4-4737c/v2/source_1FGL_J1636.4-4737c.pdf
+    \caption{1FGL J1636.4-4737c}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1613.6-5100c}
+    \end{center}
+    % this plot came from 
+    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
+    \caption{Lalla}
+  \end{figure}
+
   \end{document}

### 2011-04-26 extended_catalog/paper/extended_catalog.tex
Modifications

@@
 
-We use another monte carlo study to determine the Fermi LAT's sensitivity to
-spatially extended sources.
+We performed another monte carlo study to determine the Fermi LAT's
+sensitivity to spatially extended sources. The sensitivity to extension
+is defined as the flux at which $\text{TS}_\text{ext}$ for a source is on
+average equal to 25 (for a given spectral model). We emphasize that this
+is not the sensitivity to detect a source, but instead the sensitivity
+to detecting a source as being extended.  One would expect that we would
+become very insensitive to detecting the extension of very small sources
+that look just like the PSF. Similarly, we would be very insensitive to
+very large sources which would get lost in the background. Furtheremore,
+one expects our sensitivity to be greater for harder sources since our
+angular resolution improves with energy.
+
+To calculate the LAT's sensitivity to spatially extended sources,
+we simulated sources with a disk morphology on top of a powerlaw
+Sreekumar-like spectrum.\cite{Sreekumar et al. ApJ 494 pag 523 1998}.
+We calculated the sensitivity for sources of a spectral index $\gamma$
+of 1.5, 2, 2.5, and 3 and for sources of 20 extensions varying
+from $0.1^\circ$ to $2.0^\circ$ To calculate the sensitivity, we
+found a flux for which $\text{TS}_\text{ext}<25$ and a flux for which
+$\text{TS}_\text{ext}>25$ and then multiple simulations
+of fluxes in the range were run. A line was fit to the 
+flux vs $\text{TS}_\text{ext}$ data to determine the average
+flux for which $\text{TS}_\text{ext}=25$.
+
+The resulting Fermi sensitivity to extension is shown in figure~\ref{sensitivity_ext}.
 
@@
 
-% * Plots we make ...
+\section{Validation of Known Extended Sources}
 
 \section{Test of 1LAC Sources}
-
-\section{Validation of Known Extended Sources}
 

### 2011-05-21 extended_catalog/paper/extended_catalog.tex
better discussion

--- 2011-04-20 extended_catalog/paper/extended_catalog.tex
@@
-\documentclass{emulateapj}
+\documentclass[preprint]{aastex}
 
-\usepackage{fullpage}
+\usepackage{rotating}
+\usepackage{amsmath}
 \usepackage{graphicx}
 
+\newcommand{\mev}{\text{MeV}}
+\newcommand{\gev}{\text{GeV}}
+\newcommand{\sr}{\text{sr}}
+\newcommand{\cm}{\text{cm}}
+\newcommand{\tsext}{\ensuremath{\text{TS}_\text{ext}}}
+\newcommand{\ts}{\text{TS}}
+\newcommand{\pointlike}{{\em pointlike}}
+\newcommand{\gtlike}{{\em gtlike}}
+
 \shorttitle{Search for Extended LAT Sources}
-
-\usepackage{amsmath}
 
@@
 series of Monte Carlo studies that were done to validate this tool.
+We then calculate the Fermi LAT's sensitivity to spatially exnteded
+sources.
 We then apply this tool to test all sources in the 2FGL Two Year Catalog
@@
 sky since June 2008.  Fermi is particuarly well suited for surveying
-the entire Gamma-ray sky since it has a broad energy coverage (20MeV
-and 300GeV), a wide field of view (~2.4 sr) and large effective area
-($\approx 8000 \text{cm}^2$ at > 1GeV).
+the entire Gamma-ray sky since it has a broad energy coverage ($20\mev$
+and $300\gev$), a wide field of view ($\sim 2.4 \sr$) and large effective area
+($\sim 8000 \cm^2$ at $>1\gev$).
 
@@
 
-Resolving spatially extended GeV sources is important for studying a
+studying supernova remnants, 
+pulsar wind nebulae, 
+galaxies,  galaxy clusters, and potentially dark matter and new physics.
+
+Resolving spatially extended $\gev$ sources is important for studying a
 variety of science topics. The most important use of spatial morphology
-is in source identification. Many of the sources found in GeV sources
+is in source identification. Many of the sources found in $\gev$ sources
 
-Nevertheless, morphological studies of sources in the GeV energy range using
+Nevertheless, morphological studies of sources in the $\gev$ energy range using
 the Fermi LAT is challenging primarily because of the significantly energy
@@
 galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
-at 100MeV to $XXXXX^\circ$ at 100GeV and so the higher energy photons are
-
-studying supernova remnants, 
-pulsar wind nebulae, 
- * galaxies,  
- * potentially dark matter or new physics.
+at $100\mev$ to $XXXXX^\circ$ at $100\gev$ and so the higher energy photons are
 
@@
 Using 11 months of data, the LAT produced the best-resolved survey of the sky
-in the 100 MeV to 100 GeV energy range\cite{2FGL Paper}. The
+in the $100\mev$ to $100\gev$ energy range\cite{2FGL Paper}. The
 
@@
 
-Performing morphological studies of sources in the GeV energy range using
+Performing morphological studies of sources in the $\gev$ energy range using
 the Fermi LAT is challenging primarily because of the significantly energy
@@
 galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
-at 100MeV to $XXXXX^\circ$ at 100GeV and so the higher energy photons are
+at $100\mev$ to $XXXXX^\circ$ at $100\gev$ and so the higher energy photons are
 significantly more important for studying the shape of sources. One could
@@
 In principle, the entire task can be done using the standard science
-tools package {\em gtlike}\cite{Science-Tools-gtlike}. But {\em gtlike} is
+tools package \gtlike\cite{Science-Tools-gtlike}. But \gtlike is
 only able to fit the spectral parameters of the source, so the extension
 fitting would have to be done as an external loop. Typically, the run time
-for a binned source analysis using {\em gtlike} is several hours so this loop
+for a binned source analysis using \gtlike is several hours so this loop
 would be especially time consuming. In principle, parallel computing could
@@
 wavelenghts, or by fitting it as a point source. Then, a profile of the
-likelihood as a function of extension is developed using {\em gtlike}
+likelihood as a function of extension is developed using \gtlike
 and the maximum of this profile. This approach is not optimal because it
@@
 a morphological analysis. An alternate maximum likelihood fitting
-package called {\em pointlike} has been developed by the Fermi
+package called \pointlike has been developed by the Fermi
 collaboration and we have expanded its functionality to fully support
-analyzing spatially extended sources. {\em pointlike} is most thoroughly
+analyzing spatially extended sources. \pointlike is most thoroughly
 described in Matthew Kerr's Ph.D Thesis\cite{Matthew_kerr_phd_thesis}
 but the important aspects will be summarized below. What differentiates
-{\em pointlike} most significantly from {\em gtlike} is its emphasis
+\pointlike most significantly from \gtlike is its emphasis
 on speed by introducing approximations into the calculation of the
 likelihood function while at the same time trying to reduce any
-numerical errors that may be introduced.  Like binned {\em gtlike},
-{\em pointlike} bins the sky both in position and energy.  Unlike {\em
-gtlike}, pointlike relies on the {\em healpix} representation of spatial
+numerical errors that may be introduced.  Like binned \gtlike,
+\pointlike bins the sky both in position and energy.  Unlike 
+\gtlike, \pointlike relies on the {\em healpix} representation of spatial
 bins\cite{healpix_paper} and scales the size of each spatial bin to be
@@
 always a good approximation that the model predicted counts are uniform
-across a spatial bin. Furthermore, {\em pointlike} uses a sparse matrix
+across a spatial bin. 
+\pointlike additionaly bins the Fermi Gamma-rays by their conversion type,
+which corresponds to whether the photon converted in the front or back
+part of the detector. Since the PSF is smaller for front entering events,
+one would expect binning each conversion type independently to improve
+our sensitivity.
+Furthermore, \pointlike uses a sparse matrix
 representation of the spatial bins where only the bins with counts in them
@@
 model predicted counts must be independently calculated.  Effectively,
-{\em pointlike} efficiently interpolates from a totally binned analysis
+\pointlike efficiently interpolates from a totally binned analysis
 at low energy (where the resolution is poor and there are many counts)
@@
 
-We have modified {\em pointlike} to support fitting spatially extended
+We have modified \pointlike to support fitting spatially extended
 sources.  To do this, we introduced a new class of diffuse sources where
@@
 
-Finally, {\em pointlike} allows the spatial parameters of an extended
-source to be simulataneoulsy fit. {\em pointlike} uses the Minuit fitting
+Finally, \pointlike allows the spatial parameters of an extended
+source to be simulataneoulsy fit. \pointlike uses the Minuit fitting
 library to perform the maximum likelihood maximization of the position
@@
 
-{\em pointlike} optimizes the analysis of extended sources in two ways.
+\pointlike optimizes the analysis of extended sources in two ways.
 First, for extended sources which are radially symmetric, the convolution
@@
 integral:
-\begin{multline}
+\begin{equation}
   \text{PDF}(u)= \int_0^\infty dv
@@
   \left(\frac{\gamma-1}{\gamma}\right)
-  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma \\
+  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
   \times ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right)
-\end{multline}
+\end{equation}
 Not only is this convolution formula faster, but it has the advantage
@@
 To calculate the statistical significance of the extension of a source,
-one can define a parameter $\text{TS}_\text{ext}$ as twice the increase
+one can define a parameter $\tsext$ as twice the increase
 in log likelihood between fitting a source with a
 spatially extended hypothesis and a point hypothesis. 
-So $\text{TS}_\text{ext}=2\times(LL_\text{ext}-LL_\text{ps})$.
+So $\tsext=2\times(LL_\text{ext}-LL_\text{ps})$.
 
@@
 a disk, the source's width is the only degree of freedom added to the model. According to
-Wilk's Theorem, the distribution of $\text{TS}_\text{ext}$ for no signal (when there is a true
+Wilk's Theorem, the distribution of $\tsext$ for no signal (when there is a true
 point source) should follow a $\chi^2_1$ distribution with one degree of freedom\cite{Wilks_Theorem}.
 Wilk's Theorem only holds when the likelihood is maximized simultaneoulsy
-fitting all of the parameters of model. It is for this reason why {\em pointlike}
+fitting all of the parameters of model. It is for this reason why 
+\pointlike
 goes through such great effort to simultaneously fit the position, extension,
@@
 \begin{equation}
-  P(\text{TS})=\tfrac{1}{2}(\chi^2_1(\text{TS})+\delta(\text{TS})).
+  P(\ts)=\tfrac{1}{2}(\chi^2_1(\text{TS})+\delta(\text{TS})).
 \end{equation}
@@
 particular distribution that the often quoted result holds that
-$\sqrt{TS}$ is a measure of the number of $\sigma$ of the detection.
+$\sqrt{\ts}$ is a measure of the number of $\sigma$ of the detection.
 
@@
 poisson likelihood is undefined), half of the tests would not have the
-likelihood improved by adding a source to the model and $\text{TS}=0$.
+likelihood improved by adding a source to the model and $\ts=0$.
 It is for the case that the null distribution has
@@
 bias any of the fit values or errors. But it would bias the distribution
-of $\text{TS}_\text{ext}$ in the null hypothesis. To correct for this,
+of $\tsext$ in the null hypothesis. To correct for this,
 instead of computing the likelihood in the null hypothesis by fitting
@@
 
-We performed a dedicated monte carlo study to validate pointlike for
+We performed a dedicated monte carlo study to validate \pointlike for
 studying spatially extended sources and also to demonstrate that we can
-use $\text{TS}_\text{ext}$ as a test of the statistical significance
+use $\tsext$ as a test of the statistical significance
 of a source's extension.  The monte carlo study involved simulating point
 sources of varying spectral models on top of a simulated background. The
-simulated point source was then fit using pointlike as both an extended
-source and a point source and $\text{TS}_\text{ext}$ was calculated.
+simulated point source was then fit using \pointlike as both an extended
+source and a point source and $\tsext$ was calculated.
 
@@
 Tools package {\em gtobssim}\cite{GTOBSSIM_CITATION}. The sources were
-simulated with a powerlaw spectral model with 6 Were given 6 $>100\text{MeV}$
-fluxes ranging from $3\times 10^{-9} ph/cm^2/s$ to $10^{-6} ph/cm^2/s$.
+simulated with a powerlaw spectral model with 6 Were given 6 $>100\mev$
+fluxes ranging from $3\times 10^{-9} \text{ph}/\text{cm}^2/\text{s}$ to 
+$10^{-6} \text{ph}/\text{cm}^2/\text{s}$.
 The sources were then simulated with spectral index ($\gamma$) values of
@@
 fluxes which would create a statistically significant source detection
-($\text{TS}>25$) where selected, since we are only interested in
+($\ts>25$) where selected, since we are only interested in
 testing for extension sources with a significant extent. The sources were
 simulated on top of an isotropic powerlaw background with a Sreekumar-like
-spectrum ($>\text{100MeV}$ flux of 1.5e-5 and spectral index 2.1).\cite{Sreekumar
+spectrum ($>100\mev$ flux of 1.5e-5 and spectral index 2.1).\cite{Sreekumar
 et al. ApJ 494 pag 523 1998}
@@
 The reconstruction was perfromed with events from an energy range of
-1GeV to 100GeV using 4 energy bins per decade and using the Pass 7 Version 6
+$1\gev$ to $100\gev$ using 4 energy bins per decade and using the Pass 7 Version 6
 source IRFs to be consistent with the following analysis.
@@
 
+The results of the monte carlo simulation are shown in
+figure~\ref{ts_ext_mc}.  The cumulative density function (CDF) is plotted
+against $\tsext$ For reference, the CDF for $\chi^2_1/2$,
+suggested by Wilk's Theorem, is also plotted for comparison. Overall,
+there is good agreement between Wilk's theorem, although the agreement
+is not perfect.  Possible reasons for departure from Wilk's theorem may
+include \pointlike ignoring energy dispersion, which would generally change
+the shape as a function of energy, numerical innacuracies in evaluating
+the convolution algorithm, or possibly problems with the fitting algorithm
+getting stuck in false minimum. It is important to emphasize that if
+our emperical curve lies to the left of the curve we assume to estimate
+significance, we would underestimate the statistical significance of
+our result. Since this is the case for most of our simluations, we are
+reasonable confident that $\sqrt{\tsext}$ can be safely
+used as a measure of the statistical significance of a source's extension.
+
+\section{Extended Source Sensitivity}
+
+We performed another monte carlo study to determine the Fermi LAT's
+sensitivity to spatially extended sources. The sensitivity to extension
+is defined as the flux at which 
+the average value of $\tsext$ for a source is 
+e equal to 25 (for a given spectral model). This correseoncs
+to an average extension significance of $5\sigma$.  This is not the
+sensitivity to detect an extended source but instead the sensitivity to
+resolve an already detected source as being extended.
+
+One would intuitivly expect that we would be less sensitivie to resolving
+small extended sources since they would be lost in the PSF.  Similarly,
+we would be less sensitive to very large extended sources which would
+get completely lost in the background. Furtheremore, one expects our
+sensitivity to be greater for harder sources since our angular resolution
+improves significantly with energy.
+
+To calculate the LAT's sensitivity to spatially extended sources,
+we simulated sources with a uniform radially symmetric
+disk morphology on top of a powerlaw
+Sreekumar-like isotropic spectrum.\cite{Sreekumar et al. ApJ 494 pag
+523 1998}.  For a given extension and spectral index, we calculated the
+sensitivity by varying the flux of a source until we found 
+when $\tsext=25$. In particular, we hand picked a flux range
+where $\tsext<25$ and $\tsext>25$ and simulated 10 points with
+a log uniform distribution in this range and performed an extension
+test for each of these fluxes. Since the measured signifciance is
+a statistical which will vary from realization to realization,
+we then repeated this procedure >15 times for each realization.
+By fitting a line to the flux vs $\tsext$ data, we were able to
+estimage the flux at which $\tsext=25$.
+
+Our first result is the extension sensitivity for sources of varying
+spectral indices. The result is shown in figure~\ref{index_sensitivity}.
+We computed the sensitivty for sources with a spectral index of 1.5,
+2, 2.5, and 3 and for sources of 20 extensions varying from $0.1^\circ$
+to $2.0^\circ$. The $y$ axis is the $100\mev$ to $100\gev$ flux of the
+source and the $x$ axis is the monte carlo extension. The curves then
+represent the division in this extension and flux space where one gets
+on average $\tsext=25$.
+The solid lines of the plot are the sensitivity computed when using
+with all events from $100\mev$ to $100\gev$. The dashed lines is the
+same sensitivity but only using events from from $1\gev$ to $100\gev$.
+
+This results shows that our extension sensitivity is
+significantly better for harder sources where there are more high
+energy events. Furthermore, our sensitivity is best for sources with an
+extension around $0.5^\circ$.  our sensitivity gets significantly worse
+for very small sources and gets slightly worse for very large sources.
+
+Futheremore, we note that except for the hardest or largest sources,
+our sensitivity is almost entirly whether or not we use events from
+$100\mev$ to $1\gev$. On the other hand, other systematic errors become
+increasingly important at low energy so for our extension search we will
+not use the events in this energy range.
+
+We performed a second computation to see how the LAT's extension
+sensitivity varied with increasing background, as is at lower latitude
+in the galactic plane. To do so, we computed the sensitivity using the
+extragalactic barground as well as 10 and 100 times the extragalactic
+background. The latter result approximatly represents the intensity of
+the galactic diffuse emission near the galactic center. The results are
+shown in figure~\ref{diff_factor_sensitivity}. Two plots are presented,
+one fitting only in the energy range between $1\gev$ and $100\gev$ and
+one fitting only in the energy range between $10\gev$ and $100\gev$. For
+each plot, the $y$ axis quotes the flux in the fit energy range and the
+simulation was done only for a representivite spectral index 2 source.
+
+These plots show that we are much less sensitivie to extended sources in
+a higher background region. By comparing the two plots, we also see that
+we would be more sensitive to an extended source if it had the same
+integral flux, but only over a higher energy range. This is 
+consistent with the improved angular resolution at higher energy.
+
+\section{Extension search method}
+
+The LAT two year catalog presented a search for all
+statistically significant sources that are detected in the $\gev$
+sky\cite{2FGL_catalog}.  The catalog group's source finding method assumes
+that the emission originated as point sources and what was presented was
+a list of all sources fit assuming a point source spatial hyopthesis. All
+published extended sources were modeled by the catalog group as extended
+sources, but no attempt was made to test if other sources in the catalog
+could be spatially resolved.
+
+We performed a search of all Fermi sources found in the second Fermi LAT
+catalog for extension.  We performed the extension fit using \pointlike.
+To perform this search, we built a model of the sky consistent with
+the two year catalog's model.   We used the same two year data set and
+the same pass 7 instrument response function We used the same galactic
+diffuse, isotropic diffuse, and earth limb emission model. The spectrum
+of the galactic and isotropic diffuse models were refit during the
+analysis. The earth limb emission was fixed to predicted value.
+
+For each source, we used a circular $10^\circ$ region of interest centered
+on our source. We performed a fully binned analysis.  The spatial bin
+size was scaled with energy as was described above and we uniformly
+binned in log energy, using 4 binned per logarithmic decade of of energy.
+We included all background catalog sources within $15^\circ$ of the source
+of interest and refit the spectral parameters of sources within $2^\circ$
+of our source.
+
+As was shown, we gain very little in sensitivity using events with energy
+below $1\gev$. On the other hand, the large PSF at low energy makes us
+more succeptable to systmetic errors arising from source confusion and
+from out modeling of the galactic diffuse emission.  For that reason,
+we performed our search using events between $1\gev$ and $100\gev$.
+
+We also performed a search for extended sources using events only between
+$10\gev$ and $100\gev$. Even though we are testing the same sources,
+this approach is complimentary because there are regions in the galactic
+plane where at lower energies the diffuse emission dominates and is
+likely not perfectly modeled. On the other hand, at the highest energies
+accessible by the LAT, the galactic diffuse emission will be smaller and
+we might expect to detect significantly harder soruces. This approach
+of using only events above $10\gev$ was succesfully used to detecting
+HESS J1825-137 with the Fermi LAT~\cite{HESS J1825 paper}.
+
+For each source we were testing, we modified the source to have a
+uniform radially symmetric disk spatial shape and then used \pointlike to
+simultenously fit the position and extension of the source. As described
+above, we additionally modified the source to be a extended source with
+it's extension fixed to $10^{-10\circ}$ and fit this position of this
+pseudo source. For each source, we then computed the increase in log
+likelihood fitting with the extended hypothesis and looked at all of
+the sources with $\tsext>16$ corresponding to a $4\sigma$ statistical
+significance of extension.
+
+We expect most extended sources to be galactic sources since
+extragalacitc sources are typically too far away to be spatially
+resolved. Unfortuantly, the galactic plane is the most difficult place
+to find sources since they must be found for on top of the anisotropic
+galactic diffuse emission.  Modeling the galactic diffuse emision is
+very difficult~\ref{first_diffuse_paper}.  And finding sources in the
+galactic plane is notoriusly difficult, as was discussed in the Fermi
+catalog~\ref{1FGL}. One would expect extended sources to be even more
+difficult to detect since diffuse emission residuals are expected
+to be large compared to the PSF. Furthermore, the galacitc plane
+is very crowded and there is a degenecy between an extended source
+and multiple point sources. So finding a source with
+$\tsext>16$ is not sufficint for detecting an extended.
+
+For each of the extended source candidates for which either the analysis
+using events above $1\gev$ or $10\gev$ found $\tsext>16$
+and performed several followup analyses to substantiate our analysis.
+
+First, we took the spatial and spectral model found using \pointlike
+and performed a crosscheck by refitting the spectral parameters using 
+\gtlike.
+We used a square ROI $10^\circ$ in diamater, the same 4 degrees
+per decade, and $0.125^\circ$ energy binning.
+The \gtlike analysis provided a second estimate of the spectral
+paramters of the extended source as well as a second calculation of
+$\text{TS}_\text{disk}$, $\text{TS}_\text{point}$, and 
+$\tsext$. We only looked for extended sources which 
+both \pointlike and \gtlike considered significantly extended.
+
+Additionaly, we generated for each 
+extended source candidate residual test statistic maps. 
+The residual TS Map
+
+Large
+TS values in test
+
+We generated a residual test statistic maps to look for
+, which is a map of the test
+statistic adding new points
+Figure~\ref{res_tsmaps} shows an example residual TS map.
+
+\section{Validation of Known Extended Sources}
+\label{validate_known}
+
+We validated our method by testing for extension all of the sources
+which the Fermi Collaboration had previously published on.  We applied
+no special method to test these sources but used the same pipeline which
+was used to test all other catalog sources.  The results are published
+in table~\ref{known_extended_sources}.  Using events with energies
+greater than $1\gev$, our analysis succesfully fit the extension of the
+the two galaxies the Large Magalengic Cloud and the Small Magalenic
+Cloud.~\cite{SMC & LMC Paper}.  Our tool also successfully detected the
+extension of hte supernova remenants IC443, W28, W30, W44, and W51C.
+
+Using events above $10\gev$, we were able to succesffuly fit the extesion
+of HESS J1825-137\cite{HESS 1825 paper}. Our analysis of MSH 15-52 using
+events above $10\gev$ found an extension consistent with the publisehed
+result, but with $\tsext=11.2$.\cite{MSH 15-52 Paper}. This
+is most likely because the published analysis used events above $6\gev$.
+
+Our analysis failed to detect the extension of Vela X. Vela X can only be
+successfully analyzed after applying a phase cut to removed the heavily
+dominant emission from the pular.
+
+Our analysis also failed to detect a significant extension for the
+Centaurus A Lobes.\cite{CenA paper}. This is most likely because the
+discoverd emission was significantly more complicted then a uniform
+radially symmetric Disk.  Furthermore, our analysis failed to correctly
+fit the extension of the Cygnus Loop\cite{Cygnus Loop Paper}.  This is
+most likely because Cygnus Loop is rather large and its shell type
+morphology is not well represented by a uniform disk. The source is
+also rather soft so the publisehd results used a larger energy range
+then our search.
+
+The difficulty our analysis analysis had fitting the extension of several
+of the already published extended sources should be used to emphasize
+the difficultly with which
+
+\section{Test of 1LAC Sources}
+
+A furthere test we did to validate our analysis was to test all of the
+
+\section{New Extended Sources}
+
+\section{Interpretation}
+
+\appendix
+
 \begin{table}
@@
 \hline
-$\gamma$ & flux ($ph/cm^2/s$) & $N_\text{sims}$ & $<\text{TS}>$ \\
+$\gamma$ & flux ($\text{ph}/\text{cm}^2/\text{s}$) & $N_\text{sims}$ & $<\text{TS}>$ \\
 \hline
@@
       &  $3\times 10^{-7}$ &           11622 &   4886 \\
-      &           $1^{-7}$ &           11115 &   1159 \\
+      &          $10^{-7}$ &           11115 &   1159 \\
       &  $3\times 10^{-8}$ &           10503 &    222 \\
-      &           $1^{-8}$ &            9893 &     50 \\
+      &          $10^{-8}$ &            9893 &     50 \\
 \hline
@@
       &  $3\times 10^{-7}$ &           11445 &    948 \\
-      &           $1^{-7}$ &           10966 &    202 \\
+      &          $10^{-7}$ &           10966 &    202 \\
       &  $3\times 10^{-8}$ &            8227 &     41 \\
@@
       &  $3\times 10^{-7}$ &           10986 &    172 \\
-      &           $1^{-7}$ &            7855 &     40 \\
+      &          $10^{-7}$ &            7855 &     40 \\
 \hline
 \end{tabular}
-\caption{List of the spectral models used to the monte carlo simulation of
-{\em pointlike}.$N_\text{sims}$ is the number of monte carlo simluations
+\caption{List of the spectral models used in the monte carlo simulation of
+\pointlike. $N_\text{sims}$ is the number of monte carlo simluations
 which produce a significant source detection.The final column is the
@@
 
-The results of the monte carlo simulation are shown in
-figure~\ref{ts_ext}.  The cumulative density function (CDF) is plotted
-against $\text{TS}_\text{ext}$ For reference, the CDF for $\chi^2_1/2$,
-suggested by Wilk's Theorem, is also plotted for comparison. Overall,
-there is good agreement between Wilk's theorem, although the agreement
-is not perfect.  Possible reasons for departure from Wilk's theorem may
-include pointlike ignoring energy dispersion, which would generally change
-the shape as a function of energy, numerical innacuracies in evaluating
-the convolution algorithm, or possibly problems with the fitting algorithm
-getting stuck in false minimum. It is important to emphasize that if
-our emperical curve lies to the left of the curve we assume to estimate
-significance, we would underestimate the statistical significance of
-our result. Since this is the case for most of our simluations, we are
-reasonable confident that $\sqrt{\text{TS}_\text{ext}}$ can be safely
-used as a measure of the statistical significance of a source's extension.
+\clearpage
 
-\section{Extended Source Sensitivity}
-
-We use another monte carlo study to determine the Fermi LAT's sensitivity to
-spatially extended sources.
-
-\section{Extension search method}
-
-% * Plots we make ...
-
-\section{Test of 1LAC Sources}
-
-\section{Validation of Known Extended Sources}
-
-\section{New Extended Sources}
-
-\section{Interpretation}
-
+\clearpage
 \begin{figure}
@@
     \end{center}
-    \caption{Lalla}\label{ts_ext}
+    \caption{Lalla}\label{ts_ext_mc}
+  \end{figure}
+
+\clearpage
+
+\begin{figure}
+  \begin{center}
+    \includegraphics{mc_plots/index_sensitivity.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
+    \end{center}
+    \caption{Lalla}\label{index_sensitivity}
+  \end{figure}
+
+\clearpage
+
+\begin{figure}
+  \begin{center}
+    \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_diff_factor.py
+    \end{center}
+    \caption{Lalla}\label{diff_factor_sensitivity}
   \end{figure}
@@
   \begin{center}
-    \includegraphics{mc_plots/sensitivity.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v8/merged_plot.py
-    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/sensitivity/v7/merged.hdf5 (>1GeV)
-    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/sensitivity/v8/merged.hdf5 (>100MeV)
+    \includegraphics{source_plots/agn.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v2/agn.py
     \end{center}
-    \caption{Lalla}\label{sensitivity_ext}
+    \caption{Lalla}\label{agn_ts_ext}
   \end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics{ic443_plots/res_tsmap_ic443.pdf}
+  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1
+
+  \caption{An example residual test statistic map generated for the
+  supernova rememnant IC443 using events between $1\gev$ and
+  $100\gev$.  The top plot is the residual TS map fitting IC443
+  as a point source and the bottom plot is the residual TS map fitting
+  IC443 as an extended source. The crosses in the plot represent all of
+  the sources fit in the region. Since there is a residual TS greater
+  than 160 fitting with the point hypothesis, it is clear that a point
+  source is not a good fit to the region. On the other hand,
+  the residual TS fitting as an extended source is much lower, showing
+  that IC443 is better fit by an extended source. These plots were generated
+  for all extended source candidates to help validate the analysis.}
+  \label{res_tsmaps}
+  \end{center}
+\end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/ic443_ts_ext_vs_energy.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
+    \caption{\tsext vs log(energy)}
+    \label{counts_slice}
+  \end{center}
+\end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/ic443_counts_slice.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/counts_slice_ic443/v1/ic443_counts_slice.pdf
+    \caption{Counts slice}
+    \label{counts_slice}
+  \end{center}
+\end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/ic443_radial_integral.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/radial_integral_ic443/v1/ic443_radial_integral.pdf
+    \caption{The radial integral of the counts and the model predicted counts.}
+    \label{radial_profile}
+  \end{center}
+\end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/ic443_smoothed_counts.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/smoothed_counts_ic443/v1
+    \caption{Smoothed counts}
+    \label{smoothed_counts}
+  \end{center}
+\end{figure}
+
+\clearpage
+\begin{sidewaystable}
+    \begin{centering}
+      \begin{tabular}{rrrrrrrrrrr}
+        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\text{TS}_\text{ext}$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
+        \hline
+        \multicolumn{11}{l}{$E > 1\gev$} \\
+        \hline
+        SMC            & 302.87  &  -44.65 &    $1.59\pm0.15$ &    93.1 &                   51.2 & 0.173 & 0.129 &  41.9 &   $3.0\pm0.4$    & $2.42\pm0.16$ \\
+        LMC            & 278.58  &  -32.82 &    $2.26\pm0.09$ &   384.2 &                304.374 & 0.096 & 0.071 & -35.5 &  $12.9\pm0.7$    & $2.42\pm0.08$ \\
+        IC443          & 189.05  &  3.04   &    $0.35\pm0.01$ & 10765.3 &                535.282 & 0.006 & 0.006 &  84.0 &  $65.2\pm1.2$    & $2.23\pm0.02$ \\
+        W28            & 6.51    &  -0.29  &    $0.39\pm0.02$ &  1231.3 &                   92.1 & 0.014 & 0.013 &  30.4 &  $55.9\pm1.8$    & $2.65\pm0.03$ \\
+        W30            & 8.61    &  -0.20  &    $0.36\pm0.04$ &   458.1 &                  66.0  & 0.020 & 0.018 &  14.1 &  $30.0\pm1.8$    & $2.58\pm0.06$ \\
+        W44            & 34.68   &  -0.42  &    $0.34\pm0.02$ &  1387.6 &                  111.3 & 0.009 & 0.009 & -39.4 &  $74.7\pm1.0$    & $2.67\pm0.01$ \\
+        W51C           & 49.12   &  -0.44  &    $0.28\pm0.02$ &  2174.7 &                   87.6 & 0.010 & 0.010 &  59.4 &  $41.6\pm1.3$    & $2.38\pm0.04$ \\
+        \hline
+        \multicolumn{11}{l}{$E > 10\gev$} \\
+        \hline
+        HESS J1825-137 &   17.58 &   -0.46 &    $0.64\pm0.08$ &    85.6 &                   62.5 & 0.050 & 0.045 & 33.6  &     $19.4\pm1.4$ & $2.27\pm0.07$ \\
+        MSH 15-52      &  320.39 &   -1.22 &    $0.20\pm0.06$ &    73.7 &                    9.5 & 0.033 & 0.032 & 3.9   &      $4.7\pm0.7$ & $1.88\pm0.12$ \\
+      \label{known_extended_sources}
+      \end{tabular}
+      \caption{The fit results for the known extended sources that
+      were found by our analysis. The top results were found using
+      an energy range between $1\gev$ and $100\gev$.
+      The quoted flux is in units of $10^{-9}\text{ph}/\text{cm}^2/\text{s}$ and 
+      is the flux in the fit energy range.
+      The lower analysis was done using events between
+      $10\gev$ and $100\gev$ and the quoted flux
+      values are in the fit energy range. All sources were
+      fit using a disk morphology. The localiztaion and extension
+      were found using \pointlike while the TS and spectral
+      values were calculated using \gtlike.
+      The TS value was computed using 
+      the assumed disk morphology. The Centaurus A Lobes,
+      the Cygnus Loop, and Vela X were not found to be extended by
+      this too. The reasons for this are discussed in~\ref{validate_known}.
+      }
+    \end{centering}
+\end{sidewaystable}
+
+\clearpage
+
+\begin{sidewaystable}
+    \begin{centering}
+      \begin{tabular}{rrrrrrrrrrr}
+        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\text{TS}_\text{ext}$ & Major & Minor & Ang & Flux ($10^{-9}$) & Index \\
+        \hline
+        \multicolumn{11}{l}{$E > 1\gev$} \\
+        \hline
+        1FGL J1628.6-2419c \\
+        1FGL J1554.0-5345c \\
+        1FGL J0823.3-4248 \\
+        \hline
+        \multicolumn{11}{l}{$E > 10\gev$} \\
+        \hline
+        1FGL J2020.0+4049 \\
+        1FGL J1837.5-0659c \\
+        1FGL J1632.9-4802c \\
+        1FGL J1613.6-5100c \\
+        \hline
+      \label{new_ext_srcs}
+      \end{tabular}
+      \caption{}
+    \end{centering}
+\end{sidewaystable}
 
@@
     % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J1628.6-2419c/v2/source_1FGL_J1628.6-2419c.pdf
-    \caption{Lalla}
+    \caption{1FGL J1628.6-2419c}
   \end{figure}
@@
     % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J1554.0-5345c/v2/source_1FGL_J1554.0-5345c.pdf
-    \caption{Lalla}
+    \caption{1FGL J1554.0-5345c}
   \end{figure}
@@
     % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-    \caption{Lalla}
+    \caption{1FGL J0823.3-4248}
   \end{figure}
@@
     % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J2020.0+4049/v2/source_1FGL_J2020.0+4049.pdf
-    \caption{Lalla}
+    \caption{
+    1FGL J2020.0+4049
+    }
   \end{figure}
@@
     % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
-    \caption{Lalla}
+    \caption{
+    1FGL J1613.6-5100c }
   \end{figure}

### 2011-05-24 extended_catalog/paper/extended_catalog.tex
modifying plots & fixing legend

@@
 \usepackage{graphicx}
+\usepackage{xspace}
 
-\newcommand{\mev}{\text{MeV}}
-\newcommand{\gev}{\text{GeV}}
-\newcommand{\sr}{\text{sr}}
-\newcommand{\cm}{\text{cm}}
-\newcommand{\tsext}{\ensuremath{\text{TS}_\text{ext}}}
-\newcommand{\ts}{\text{TS}}
-\newcommand{\pointlike}{{\em pointlike}}
-\newcommand{\gtlike}{{\em gtlike}}
+\newcommand{\mev}{\text{MeV}\xspace}
+\newcommand{\gev}{\text{GeV}\xspace}
+\newcommand{\sr}{\text{sr}\xspace}
+\newcommand{\s}{\text{s}\xspace}
+\newcommand{\ph}{\text{ph}\xspace}
+\newcommand{\cm}{\text{cm}\xspace}
+\newcommand{\tsext}{\ensuremath{\text{TS}_\text{ext}}\xspace}
+\newcommand{\ts}{\text{TS}\xspace}
+\newcommand{\pointlike}{{\em pointlike}\xspace}
+\newcommand{\gtlike}{{\em gtlike}\xspace}
 
@@
 \begin{equation}
-  P(\ts)=\tfrac{1}{2}(\chi^2_1(\text{TS})+\delta(\text{TS})).
+  P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
 \end{equation}
@@
 
-\section{Monte Carlo Validation}
+\section{Monte Carlo Validation}\label{monte_carlo_validation}
 
@@
 simulated with a powerlaw spectral model with 6 Were given 6 $>100\mev$
-fluxes ranging from $3\times 10^{-9} \text{ph}/\text{cm}^2/\text{s}$ to 
-$10^{-6} \text{ph}/\text{cm}^2/\text{s}$.
+fluxes ranging from $3\times 10^{-9} \ph/\cm^2/s$ to 
+$10^{-6} \ph/\cm^2/s$.
 The sources were then simulated with spectral index ($\gamma$) values of
@@
 $1\gev$ to $100\gev$ using 4 energy bins per decade and using the Pass 7 Version 6
-source IRFs to be consistent with the following analysis.
+source instrument response function (IRFs) to be consistent with the following analysis.
 
@@
 a statistical which will vary from realization to realization,
-we then repeated this procedure >15 times for each realization.
+we then repeated this procedure $>15$ times for each spectral
+and spatial model.
 By fitting a line to the flux vs $\tsext$ data, we were able to
@@
 paramters of the extended source as well as a second calculation of
-$\text{TS}_\text{disk}$, $\text{TS}_\text{point}$, and 
+$\ts_\text{disk}$, $\ts_\text{point}$, and 
 $\tsext$. We only looked for extended sources which 
@@
 
-A furthere test we did to validate our analysis was to test all of the
+To validate our method and assess systematic issues with our
+analysis, we used \pointlike to test known active galaxies (AGN) for extension.
+\gev emission from AGN is believed to comes from the
+core of supermassive blackholes. Since this happens in a very small region
+in the core of very distant galaxies,
+
+AGN are not expected to be spatially resolvable and therefore
+provide a good calibration source to demonstrate the efficacy of our
+tool. Nevertheless, it would be very interesting if AGN could be
+spatially resolved AGN and there are theories that predict
+this\cite{pair_halo_paper, http://adsabs.harvard.edu/doi/10.1086/187222}.
+
+Following the Fermi-LAT one year catalog, the Fermi collaboration
+published a list of the Fermi catalog sources that had a high probability
+association with AGN. The first year catalog had 709 AGN associated with
+671 distinct 1FGL sources at high latitude ($|b|>10^\circ$).  For our
+study, we are looking to assess systematics with extension fitting so
+it is important to avoid any possible issues with AGN associations.
+For that reason, we select only the 599 AGN which make it into the
+``clean'' AGN sample. An AGN association is only considered ``clean''
+if it has a high probability of association $P\ge 80\%$, if it is the
+only AGN associated with the 1FGL source, and if there are no flags
+on the source which shed doubt on the source\cite{1FGL}. These last two
+conditions are especially important for our analysis. One might expect
+source confusion between two AGN look like a spatially extended source.
+Testing only unflagged sources is also important because it removes
+any catalog sources coincident with structures in the diffuse emission.
+It is possible that these flagged catalog sources which are really poorly
+modeled diffuse emission might also look extended.
+
+Of the 599 ``clean'' AGN, we select 556 of these 1FGL sources which
+we uniquely associate with a 2 year catalog source. And we furthermore
+restrict our select to 515 of these AGN for which we fit $\ts>25$ using
+\pointlike.  Our intention here is not to find the largest sample of
+AGN and this will be the scope of a follow up AGN association paper. Our
+purpose is simply to find a good sample of AGN which can be used to
+test the systematics of our tool.
+
+Using the same extension fitting procedure as described above, we test
+these 515 AGN for extension. A histogram of the fit \tsext values is
+shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again
+a $\chi^2/2$ distribution suggested by Wilk's Theorem.
+This plot shows a worse agreement with the theoretical distribution
+then was found by our monte carlo study in figure~\ref{ts_ext_mc}.
+
+Several possible systematics could cause this discrepancy. The first
+is that in our analysis we fit each source with a powerlaw index.
+AGN tend to have curved spectral and fitting with a wrong spectral
+model might effect the value of \tsext. Nevertheless, since we use only
+events with $E>1\gev$, this would effect is not expected to be large.
+Another possible source for the discrepancy is that pointlike performs a
+likelihood analysis without modeling the energy dispersion of our source.
+But energy dispersion is expected to be more significant at low
+energy and furthermore if this was a signifciant effect the same results
+would have showed up with the monte carlo simultions which included the
+effects of energy dispersion.
+
+The third possible effect causing this discrepancy is an
+imperfect modeling of the PSF of the LAT.  Before launch,
+the LAT PSF was determined using a Monte Carlo simulation of
+the detector.  After launch, a discrepancy was found using flight
+data above a few \gev in the PSF measured using very bright AGN.
+This result was presented in conference and a publication is in preparation.
+Subsequently, the PSF was fit empirically to these bright AGN and
+this empirical parameterization is used in the Pass 7 Version 6 IRFs.\cite{
+https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
+}. But our current parameterization is not perfect. There are 
+especially lingering issues because there is not good enough statistics
+at high energy to validate the PSF as a function of the incident $\theta$
+angle of a photon. It is likely that these issues could cause this 
+systematic in the fit value of \tsext for point sources. We should
+furtheremore note that since the PSF was
+
+with only 2 AGN having $\tsext>10$ and the maximum having $\tsext=13.7$
 
@@
 \hline
-$\gamma$ & flux ($\text{ph}/\text{cm}^2/\text{s}$) & $N_\text{sims}$ & $<\text{TS}>$ \\
+$\gamma$ & flux ($\ph/\cm^2/\s$) & $N_\text{sims}$ & $<\ts>$ \\
 \hline
@@
 \end{tabular}
-\caption{List of the spectral models used in the monte carlo simulation of
-\pointlike. $N_\text{sims}$ is the number of monte carlo simluations
-which produce a significant source detection.The final column is the
-average test statistic that was found during the monte carlo fit of
-the source. Only simluations which were deemed significant ($\text{TS}>25$)
-were kept.}
+\caption{
+This table presents a list of the spectral models (flux and spectral index)
+used in the monte carlo study of 
+\pointlike described in section~\ref{monte_carlo_validation}.
+For each spectral model, the number of statistically indepdent simulations
+and the average test statistic found for that given spectral model
+($<\ts>$) is tabulated. 
+The important feature to see in this table is that the monte carlo simulation
+probes most of the sources parameters that could be detected by the LAT.
+The simulation probles a wide range of spectral indices (from index 1.5 to 3) and
+a wide range of the fluxes (varying
+from a close to $5\sigma$ source detection to a $>10\sigma$ source detection).
+Only simluations which produced statistically
+significant detections ($\ts>25$) were kept. 
+What is quoted is the $>100\mev$ integral flux in measured in units of $\ph/\cm^2/\s$.
+}
 \label{ts_ext_num_sims}
@@
     \end{center}
-    \caption{Lalla}\label{ts_ext_mc}
+    \caption{
+    The results of the monte carlo simulation described in section
+    \ref{monte_carlo_validation} testing the null distribution of
+    the likelihood ratio test for extension.  The $x$ axis of this
+    plot is \tsext and the $y$ axis is the cumulative density for
+    \tsext that was found by testing simulated point sources of
+    various spectral models for extension. The four plots represent
+    different spectral indices (for $\gamma$ of 1, 2, 2.5, and 3).
+    And the different colors lines represent different fluxes chosen
+    to span a representative range of Overlayed on the plot in dashed
+    red is the cumulative density function of $\chi^2(\ts)/2$ which is
+    suggested by Wilk's theorem as the theoretical distribution these
+    curves should should follow.  Overall, it should be noted that there
+    is a surprisingly good agreement between the monte carlo study and
+    the theoeretical distribution. And for most spectral parameters, the
+    Monte Carlo curve lies to the left of the theoretical curve, which
+    would imply that using Wilk's Theorem as the null distribution would
+    conservativly underestimate the signifcance of a source detection. In
+    the rest of the paper, we use this theoretical curve to estimate
+    the significance of our source detections.  What is quoted is the
+    $>100\mev$ integral flux in measured in units of $\ph/\cm^2/\s$.
+    For each spectral model, more information about the simulations is
+    summarized in table~\ref{ts_ext_num_sims}.
+    }\label{ts_ext_mc}
   \end{figure}
@@
       \begin{tabular}{rrrrrrrrrrr}
-        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\text{TS}_\text{ext}$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
+        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &     \ts & $\tsext$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
         \hline
@@
       an energy range between $1\gev$ and $100\gev$.
-      The quoted flux is in units of $10^{-9}\text{ph}/\text{cm}^2/\text{s}$ and 
+      The quoted flux is in units of $10^{-9}\ph/\cm^2/\s$ and 
       is the flux in the fit energy range.
@@
       \begin{tabular}{rrrrrrrrrrr}
-        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\text{TS}_\text{ext}$ & Major & Minor & Ang & Flux ($10^{-9}$) & Index \\
+        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\tsext$ & Major & Minor & Ang & Flux ($10^{-9}$) & Index \\
         \hline

### 2011-06-01 extended_catalog/paper/extended_catalog.tex
More to the draft

@@
 
+% some units
 \newcommand{\mev}{\text{MeV}\xspace}
@@
 \newcommand{\tsext}{\ensuremath{\text{TS}_\text{ext}}\xspace}
+\newcommand{\tsinc}{\ensuremath{\text{TS}_\text{inc}}\xspace}
 \newcommand{\ts}{\text{TS}\xspace}
+
+\renewcommand{\deg}{\ensuremath{^\circ}\xspace}
+
+% the program names
 \newcommand{\pointlike}{{\em pointlike}\xspace}
 \newcommand{\gtlike}{{\em gtlike}\xspace}
+\newcommand{\gtobssim}{{\em gtobssim}\xspace}
 
@@
 We then apply this tool to test all sources in the 2FGL Two Year Catalog
-for extension.\cite{2FGL} We then report on the discovery of XXX new
+for extension.\cite{2FGL} We then report on the discovery of XXXXXXXXXXXXXX new
 extended sources.
@@
 dependent PSF and because of systematic errors in the
-galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
-at $100\mev$ to $XXXXX^\circ$ at $100\gev$ and so the higher energy photons are
+galactic diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXX\deg$
+at $100\mev$ to $XXXXXXXXXXXXXXXX\deg$ at $100\gev$ and so the higher energy photons are
 
@@
 dependent PSF and because of systematic errors in the
-galactic diffuse emission. The Fermi PSF varies from over $XXXXX^\circ$
-at $100\mev$ to $XXXXX^\circ$ at $100\gev$ and so the higher energy photons are
+galactic diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXXX\deg$
+at $100\mev$ to $XXXXXXXXXXXXXXXX\deg$ at $100\gev$ and so the higher energy photons are
 significantly more important for studying the shape of sources. One could
@@
 varying different parameters such as what goes into the diffuse model.
+
+\subsection{\pointlike}
 
@@
 
+% XXXXXXXXXXXX describe how \pointlike calculates extension errors and how localization errors are calculated.
+
+% XXXXXXXXXXXX note about how \pointlike is written in python = more flexible
+
+\subsection{Extension Fitting}
+
 We have modified \pointlike to support fitting spatially extended
@@
 spatially extended hypothesis and a point hypothesis. 
-So $\tsext=2\times(LL_\text{ext}-LL_\text{ps})$.
+So 
+\begin{equation}
+  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
+\end{equation}
 
@@
 
+% XXXXXXXXXXXXXXXXXXX NOTE ABOUT gtlike crosscheck
+
+\subsection{Dual Localization}
+
+There is a degeneracy in the signal expected from spatially extended
+sources and multiple point sources.  To assess the possibility of source
+confusion, we developed a function in pointlike for simulatenously fitting
+two point sources so that the likelihood fitting two point sources
+could be compared to the likelihood fitting one extended source.
+
+The algorithm works by first dividing the selected point source into
+two separate sources. Then, the position of the two sources 
+are fit simultanously. To avoid projection effects, the fit is
+done in a coordiante system rotated to the celestial equator.
+In this rotated coordiante system, space can be well approximated
+as being flat and we are interested in fitting the 
+rotated coordiante $(x_1',y_1')$ and $(x_2',y_2')$
+We decided not to directly fit the positions of the two sources 
+but instead the fit sum and difference of the rotated coordiantes
+$S_x=(x_2'+x_1')/2$, $S_x=(y_2'+y_1')/2$, $D_x=(x_2'-x_1')/2$, and $D_y=(y_2'-y_1')/2$.
+We believe that fitting the average of position and the difference
+independently would cause less degeneracy in the fit and help the fitter
+find the best position.
+
+For a particular value of $S_x$, $S_y$, $D_x$, and $D_y$, the Poisson
+likelihood is computed by converting the sum and difference coordaintes
+into the rotated coordiantes, unrotating the coordiantes, moving the
+two sources in the \pointlike to the new positions, and performing a new
+spectral analysis at the modified position.  The function then maximizes
+The Poission likelihood $L(S_x,S_y,D_x,D_y)$ as a function of the sum
+and difference of the rotated coordaintes using the Minuit to fit the
+sum and differenc coordiantes\cite{Minuit reference}.
+
+After the minimization converges, we can define the 
+parameter $\tsext$ as twice the 
+increase
+in log likelihood between fitting the region with
+two point sources and fitting the region with one point source
+\begin{equation}
+  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
+\end{equation}
+Generally, \tsinc can also
+
+% XXXXXXXXXXXXXXX \tsinc vs \tsext NOT A CALIBRATED TEST
+% but still suggestive in the cases \tsinc \ll \tsext and
+% \tsinc \gg \tsext.
+
+Because of \pointlike's computational efficiency, this algorithm
+runs in a reasonable amount of time.
+
+After
+% XXXXXXXXXXXXXXXXXXX NOTE ABOUT gtlike crosscheck
+
+\subsection{Comparing Source Sizes}
+
+Description of comparing r68, sigma for disk, gaussian, etc.
+why the plots don't look correct.
+
 \section{Monte Carlo Validation}\label{monte_carlo_validation}
+
+% XXXXXXXXXXXXXXXX better description of how TSext is always > 0
+% but wilk's thorem says that it won't be must better if the source
+% is a point source
 
@@
 Fermi LAT data was simulated using the publically avaliabable Science
-Tools package {\em gtobssim}\cite{GTOBSSIM_CITATION}. The sources were
+Tools package \gtobssim\cite{GTOBSSIM_CITATION}. The sources were
 simulated with a powerlaw spectral model with 6 Were given 6 $>100\mev$
@@
 suggested by Wilk's Theorem, is also plotted for comparison. Overall,
-there is good agreement between Wilk's theorem, although the agreement
-is not perfect.  Possible reasons for departure from Wilk's theorem may
-include \pointlike ignoring energy dispersion, which would generally change
-the shape as a function of energy, numerical innacuracies in evaluating
-the convolution algorithm, or possibly problems with the fitting algorithm
-getting stuck in false minimum. It is important to emphasize that if
+there is good agreement between Wilk's theorem, although the agreement is
+not perfect.  It should be noted that the discrepancy seems to be worst
+for bright sources which seems to imply that numerical errors in the
+way \pointlike models the PSF and performs the convolution become more
+apparent for sufficiently bright sources.  Other possible reasons for
+departure from Wilk's theorem might include \pointlike ignoring energy
+dispersion. Energy dispersion will change the shape as a function of
+energy. \pointlike may also run into possibly problems with the fitting
+algorithm getting stuck in false minimum. It is important to emphasize
+that if
 our emperical curve lies to the left of the curve we assume to estimate
@@
 We computed the sensitivty for sources with a spectral index of 1.5,
-2, 2.5, and 3 and for sources of 20 extensions varying from $0.1^\circ$
-to $2.0^\circ$. The $y$ axis is the $100\mev$ to $100\gev$ flux of the
+2, 2.5, and 3 and for sources of 20 extensions varying from $0.1\deg$
+to $2.0\deg$. The $y$ axis is the $100\mev$ to $100\gev$ flux of the
 source and the $x$ axis is the monte carlo extension. The curves then
@@
 energy events. Furthermore, our sensitivity is best for sources with an
-extension around $0.5^\circ$.  our sensitivity gets significantly worse
+extension around $0.5\deg$.  our sensitivity gets significantly worse
 for very small sources and gets slightly worse for very large sources.
@@
 
-For each source, we used a circular $10^\circ$ region of interest centered
+For each source, we used a circular $10\deg$ region of interest centered
 on our source. We performed a fully binned analysis.  The spatial bin
@@
 binned in log energy, using 4 binned per logarithmic decade of of energy.
-We included all background catalog sources within $15^\circ$ of the source
-of interest and refit the spectral parameters of sources within $2^\circ$
+We included all background catalog sources within $15\deg$ of the source
+of interest and refit the spectral parameters of sources within $2\deg$
 of our source.
@@
 \gtlike.
-We used a square ROI $10^\circ$ in diamater, the same 4 degrees
-per decade, and $0.125^\circ$ energy binning.
+We used a square ROI $10\deg$ in diamater, the same 4 degrees
+per decade, and $0.125\deg$ energy binning.
 The \gtlike analysis provided a second estimate of the spectral
@@
 association with AGN. The first year catalog had 709 AGN associated with
-671 distinct 1FGL sources at high latitude ($|b|>10^\circ$).  For our
+671 distinct 1FGL sources at high latitude ($|b|>10\deg$).  For our
 study, we are looking to assess systematics with extension fitting so
@@
 
-Using the same extension fitting procedure as described above, we test
-these 515 AGN for extension. A histogram of the fit \tsext values is
-shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again
-a $\chi^2/2$ distribution suggested by Wilk's Theorem.
-This plot shows a worse agreement with the theoretical distribution
-then was found by our monte carlo study in figure~\ref{ts_ext_mc}.
+Using the same extension fitting procedure as described above, we
+test these 515 AGN for extension. A histogram of the fit \tsext values
+is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again a
+$\chi^2/2$ distribution suggested by Wilk's Theorem.  This plot shows
+a worse agreement with the theoretical distribution then was found
+by our monte carlo study in figure~\ref{ts_ext_mc}.  But overall, the
+distribution is good. No AGN get fit with a particularly significant
+value of $\tsext$. Almost all of the AGN get fit with $\tsext<1$ and
+there are very few AGN fit with large values of \tsext.  There where
+only 2 AGN having $\tsext>10$.  The maximum fit $\tsext=13.7$ whereas the
+maximum value expected theoeritcally for the $\chi^2/2$ distribution is
+8.3. This result therefore shows that there is some systematic on our
+analysis but that we understand it and that it will not significantly
+cast into doubt our subsequent results.
+% 8.3 number gotten from mathematica:
+% PDF[ChiSquareDistribution[1], x]
+% N[Solve[(1/2)*
+%     Integrate[1/(E^(x/2)*(Sqrt[2*Pi]*Sqrt[x])), {x, TS, Infinity}] &=&  
+%        1/515, TS]]
 
@@
 
-The third possible effect causing this discrepancy is an
-imperfect modeling of the PSF of the LAT.  Before launch,
-the LAT PSF was determined using a Monte Carlo simulation of
-the detector.  After launch, a discrepancy was found using flight
-data above a few \gev in the PSF measured using very bright AGN.
-This result was presented in conference and a publication is in preparation.
-Subsequently, the PSF was fit empirically to these bright AGN and
-this empirical parameterization is used in the Pass 7 Version 6 IRFs.\cite{
+Another possible systematic may be due to remaning issues with our
+background model. Due to chance coincidence, a catalog source might
+lie very close to nearby source. If the two sources were near enough,
+they would be unresolvable by the catalog and the catalog would simply
+fit them both together.  This could easily lead to an anomolously high
+value of \tsext for a paritcular point source. Issues could also arise
+from farther away but fainter sources which did not make the catalog's
+significance cut, but nonetheless would pull the fitter away from the
+point hyoptehsis.  Finally, it is possible that there are lingering
+residuals in the diffuse emission in parts of the high latitude sky
+which would cause the fitter to prefer a slightly extneded hypotehsis
+that could fill in parts of the unmodeled diffuse emission.
+
+The final possible effect causing this discrepancy is an imperfect
+modeling of the PSF of the LAT.  Before launch, the LAT PSF
+was determined using a Monte Carlo simulation of the detector.
+After launch, a discrepancy was found using flight data above a
+few \gev in the PSF measured using very bright AGN.  This result
+was presented in conference and a publication is in preparation.
+Subsequently, the PSF was fit empirically to these bright AGN and this
+empirical parameterization is used in the Pass 7 Version 6 IRFs.\cite{
 https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
-}. But our current parameterization is not perfect. There are 
-especially lingering issues because there is not good enough statistics
-at high energy to validate the PSF as a function of the incident $\theta$
-angle of a photon. It is likely that these issues could cause this 
-systematic in the fit value of \tsext for point sources. We should
-furtheremore note that since the PSF was
-
-with only 2 AGN having $\tsext>10$ and the maximum having $\tsext=13.7$
+}. But our current parameterization is not perfect. There are especially
+lingering issues due to lackign the statistics at high energy to
+validate the PSF as a function of the incident $\theta$ angle of a
+photon. Since the distribution of $\theta$ angles for observing any
+sources is different, the PSF for every source should be different.
+It is likely that these issues could cause this systematic in the fit
+value of \tsext for AGN.
+
+We should furtheremore note that since the PSF was found empirically in
+the first place by fitting the shape of brigh AGN, finding that the AGN we
+test are not significantly extended is not surprising.  We hope to note
+that because of the difficulties in validating the PSF, we are strictly
+searching for sources that are significantly extended when compared to
+bright AGN measured by the LAT. Trying to look for the extension of these
+AGN, or more realistically trying to put an upper limit on thier size,
+would require its own dedicated analysis.
 
@@
 
-\section{Interpretation}
+\begin{itemize}
+  \item Results summarized in table~\ref{new_ext_srcs}.
+  \item Add extra stuff to this section, $\tsinc$.
+  \item Disribe what had to be done to modify regionregion.
+    What sources had to be deleted (or moved).
+%  \item XXXXXXXXXXXXXXXXXXXXXXXXXX Say that errors are just statistical (or have a descritpion of errors).
+
+\end{itemize}
+
+\subsection{1FGL J1628.6-2419c}
+
+The two year catalog source P72Y2516 was found at ($l,b)=(353.09\deg, 16.79\deg)$
+with a best fit extension of $0.40\pm0.05$ and an extension significance of
+$\tsext=26.3$.
+
+In the ophiucus region=most likely a molecular cloud
+
+\subsection{1FGL J1554.0-5345c}
+Unidentified source likely diffuse emission
+
+\subsection{1FGL J0823.3-4248}
+Coincident with Puppis A SNR
+
+\subsection{1FGL J1613.6-5100c}
+Near HESS Source XXXXXXXXXXXXXX
+
+\subsection{1FGL J1632.9-4802c}
+Near HESS Source XXXXXXXXXXXXXX
+
+\subsection{1FGL J2020.0+4049}
+Gamam Cygni SNR. Upcomming publication.
+
+\subsection{1FGL J1837.5-0659c}
+Near HESS source HESS J1837. Upcomming publication???
+
+\subsection{P72Y1287}
+
+Vela Jr. Upcomming publication.
+
+\section{Conclusion}
 
@@
 \hline
-  1.5 &          $10^{-6}$ &           11405 &  90861 \\
-      &  $3\times 10^{-7}$ &           11490 &  21922 \\
-      &          $10^{-7}$ &           11101 &   5765 \\
-      &  $3\times 10^{-8}$ &           10269 &   1262 \\
-      &          $10^{-8}$ &            9941 &    306 \\
-      &  $3\times 10^{-9}$ &           10427 &     61 \\
-\hline
-    2 &          $10^{-6}$ &           11632 &  22025 \\
-      &  $3\times 10^{-7}$ &           11622 &   4886 \\
-      &          $10^{-7}$ &           11115 &   1159 \\
-      &  $3\times 10^{-8}$ &           10503 &    222 \\
-      &          $10^{-8}$ &            9893 &     50 \\
-\hline
-  2.5 &          $10^{-6}$ &           11522 &   4722 \\
-      &  $3\times 10^{-7}$ &           11445 &    948 \\
-      &          $10^{-7}$ &           10966 &    202 \\
-      &  $3\times 10^{-8}$ &            8227 &     41 \\
-\hline                                                
-    3 &          $10^{-6}$ &           11264 &    949 \\
-      &  $3\times 10^{-7}$ &           10986 &    172 \\
-      &          $10^{-7}$ &            7855 &     40 \\
+  1.5 &          $10^{-6}$ &           31952 &  92862 \\
+      &  $3\times 10^{-7}$ &           31962 &  22169 \\
+      &          $10^{-7}$ &           31977 &   5806 \\
+      &  $3\times 10^{-8}$ &           31991 &   1270 \\
+      &          $10^{-8}$ &           31940 &    301 \\
+      &  $3\times 10^{-9}$ &           30324 &     62 \\
+\hline
+    2 &          $10^{-6}$ &           31872 &  22067 \\
+      &  $3\times 10^{-7}$ &           31890 &   4898 \\
+      &          $10^{-7}$ &           31858 &   1097 \\
+      &  $3\times 10^{-8}$ &           31632 &    236 \\
+      &          $10^{-8}$ &           27491 &    103 \\
+\hline
+  2.5 &          $10^{-6}$ &           31822 &   4706 \\
+      &  $3\times 10^{-7}$ &           31822 &    889 \\
+      &          $10^{-7}$ &           31169 &    176 \\
+      &  $3\times 10^{-8}$ &           21591 &     41 \\
+\hline                                                
+    3 &          $10^{-6}$ &           31763 &    929 \\
+      &  $3\times 10^{-7}$ &           31665 &    161 \\
+      &          $10^{-7}$ &           19271 &     40 \\
 \hline
@@
 \caption{
-This table presents a list of the spectral models (flux and spectral index)
-used in the monte carlo study of 
-\pointlike described in section~\ref{monte_carlo_validation}.
-For each spectral model, the number of statistically indepdent simulations
-and the average test statistic found for that given spectral model
-($<\ts>$) is tabulated. 
-The important feature to see in this table is that the monte carlo simulation
-probes most of the sources parameters that could be detected by the LAT.
-The simulation probles a wide range of spectral indices (from index 1.5 to 3) and
-a wide range of the fluxes (varying
-from a close to $5\sigma$ source detection to a $>10\sigma$ source detection).
-Only simluations which produced statistically
-significant detections ($\ts>25$) were kept. 
-What is quoted is the $>100\mev$ integral flux in measured in units of $\ph/\cm^2/\s$.
+This table presents a list of the spectral models (flux and spectral
+index) used in the monte carlo study of \pointlike described in
+section~\ref{monte_carlo_validation}.  For each spectral model, the
+number of statistically indepdent simulations and the average test
+statistic found for that given spectral model ($<\ts>$) is tabulated.
+The important feature to see in this table is that the monte carlo
+simulation probes most of the sources parameters that could be detected
+by the LAT.  The simulation probles a wide range of spectral indices
+(from spectral index $\gamma$ of 1.5 to 3) and a wide range of the fluxes
+(varying from a close to $5\sigma$ source detection to a $>10\sigma$
+source detection).  Only simluations which produced statistically
+significant detections ($\ts>25$) were kept.  What is quoted is the
+$>100\mev$ integral flux measured in units of $\ph/\cm^2/\s$.
 }
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
-    \caption{\tsext vs log(energy)}
+    \caption{A plot of \tsext vs log(energy)
+    for the SNR IC443, which has a typical spectral model.}
     \label{counts_slice}
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/smoothed_counts_ic443/v1
-    \caption{Smoothed counts}
+    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.}
     \label{smoothed_counts}
@@
       \begin{tabular}{rrrrrrrrrrr}
-        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &     \ts & $\tsext$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
+        Name           &    GLON &    GLAT & $\sigma(\deg)$ &     \ts & $\tsext$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
         \hline
@@
       \caption{The fit results for the known extended sources that
-      were found by our analysis. The top results were found using
-      an energy range between $1\gev$ and $100\gev$.
-      The quoted flux is in units of $10^{-9}\ph/\cm^2/\s$ and 
-      is the flux in the fit energy range.
-      The lower analysis was done using events between
-      $10\gev$ and $100\gev$ and the quoted flux
-      values are in the fit energy range. All sources were
-      fit using a disk morphology. The localiztaion and extension
-      were found using \pointlike while the TS and spectral
-      values were calculated using \gtlike.
-      The TS value was computed using 
-      the assumed disk morphology. The Centaurus A Lobes,
-      the Cygnus Loop, and Vela X were not found to be extended by
-      this too. The reasons for this are discussed in~\ref{validate_known}.
+      were found by our analysis. The top results were found using an
+      energy range between $1\gev$ and $100\gev$.  The lower analysis
+      was done using events between $10\gev$ and $100\gev$.  The quoted
+      flux is in units of $10^{-9}\ph/\cm^2/\s$ and is the flux in the
+      fit energy range (either 1\gev to 100\gev or 10\gev to 100\gev).
+      All sources were fit using a uniform disk spatial template. The
+      localiztaion and extension were found using \pointlike while the TS
+      and spectral values were calculated using \gtlike.  The TS value was
+      computed using the assumed disk morphology. The Centaurus A Lobes,
+      the Cygnus Loop, and Vela X were not found to be extended by this
+      too. The reasons for this are discussed in~\ref{validate_known}.
       }
@@
       \begin{tabular}{rrrrrrrrrrr}
-        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\tsext$ & Major & Minor & Ang & Flux ($10^{-9}$) & Index \\
+        Name               &        GLON &        GLAT  &                $\sigma$ &       TS &   $\tsext$ &  Major &  Minor &    Ang &       Flux ($10^{-9}$) &      Index \\
         \hline
@@
         \hline
-        1FGL J1628.6-2419c \\
-        1FGL J1554.0-5345c \\
-        1FGL J0823.3-4248 \\
+        1FGL J1628.6-2419c &   353.09\deg&    16.79\deg & $  0.40\deg\pm0.05\deg$ &    140.3 &       26.3 &  0.042 &  0.036 &   54.4 & $    6.3\pm0.6$ &$   2.50\pm0.14$ \\
+        1FGL J1554.0-5345c &   328.12\deg&     0.26\deg & $  0.49\deg\pm0.04\deg$ &    148.6 &       80.9 &  0.046 &  0.041 &   55.4 & $   16.3\pm1.5$ &$   2.31\pm0.11$ \\
+        1FGL J0823.3-4248  &   260.32\deg&    -3.28\deg & $  0.37\deg\pm0.03\deg$ &    306.1 &       47.8 &  0.026 &  0.023 &    4.4 & $    8.2\pm0.6$ &$   2.19\pm0.06$ \\
         \hline
@@
         \hline
-        1FGL J2020.0+4049 \\
-        1FGL J1837.5-0659c \\
-        1FGL J1632.9-4802c \\
-        1FGL J1613.6-5100c \\
+        1FGL J1613.6-5100c &   331.74\deg&    -0.58\deg & $  0.52\deg\pm0.04\deg$ &     73.3 &       39.9 &  0.071 &  0.049 &  -21.7 & $    1.3\pm0.2$ &$   1.76\pm0.25$ \\
+        1FGL J1632.9-4802c &   336.52\deg&     0.05\deg & $  0.66\deg\pm0.03\deg$ &    175.1 &       92.9 &  0.040 &  0.037 &    6.2 & $    2.9\pm0.3$ &$   2.27\pm0.17$ \\
+        1FGL J2020.0+4049  &    78.32\deg&     2.21\deg & $  0.70\deg\pm0.04\deg$ &    245.4 &      141.0 &  0.048 &  0.039 &    4.4 & $    2.1\pm0.2$ &$   2.36\pm0.18$ \\
+        1FGL J1837.5-0659c &    25.04\deg&     0.26\deg & $  0.61\deg\pm0.04\deg$ &    115.4 &       50.4 &  0.064 &  0.051 &   19.7 & $    2.2\pm0.3$ &$   2.09\pm0.20$ \\
+        P72Y1287           &   266.41\deg&    -0.75\deg & $  1.41\deg\pm0.06\deg$ &    128.8 &       99.4 &  0.097 &  0.087 &   19.3 & $    1.7\pm0.2$ &$   1.96\pm0.20$ \\
         \hline
@@
       \end{tabular}
-      \caption{}
+      \caption{New extended soruce candidates}
     \end{centering}
@@
 
+\clearpage
+\begin{sidewaystable}
+    \begin{centering}
+      \begin{tabular}{rrrrrrrrrrr}
+        Name               &        GLON &        GLAT  &                $\sigma$ &       TS &   $\tsext$ &  Major &  Minor &    Ang &       Flux ($10^{-9}$) &      Index \\
+        \hline
+        \multicolumn{11}{l}{$E > 1\gev$} \\
+        \hline
+        1FGL J1628.6-2419c &   353.09\deg&    16.79\deg & $  0.40\deg\pm0.05\deg$ &    140.3 &       26.3 &  0.042 &  0.036 &   54.4 & $    6.3\pm0.6$ &$   2.50\pm0.14$ \\
+        1FGL J1554.0-5345c &   328.12\deg&     0.26\deg & $  0.49\deg\pm0.04\deg$ &    148.6 &       80.9 &  0.046 &  0.041 &   55.4 & $   16.3\pm1.5$ &$   2.31\pm0.11$ \\
+        1FGL J0823.3-4248  &   260.32\deg&    -3.28\deg & $  0.37\deg\pm0.03\deg$ &    306.1 &       47.8 &  0.026 &  0.023 &    4.4 & $    8.2\pm0.6$ &$   2.19\pm0.06$ \\
+        \hline
+        \multicolumn{11}{l}{$E > 10\gev$} \\
+        \hline
+        1FGL J1613.6-5100c &   331.74\deg&    -0.58\deg & $  0.52\deg\pm0.04\deg$ &     73.3 &       39.9 &  0.071 &  0.049 &  -21.7 & $    1.3\pm0.2$ &$   1.76\pm0.25$ \\
+        1FGL J1632.9-4802c &   336.52\deg&     0.05\deg & $  0.66\deg\pm0.03\deg$ &    175.1 &       92.9 &  0.040 &  0.037 &    6.2 & $    2.9\pm0.3$ &$   2.27\pm0.17$ \\
+        1FGL J2020.0+4049  &    78.32\deg&     2.21\deg & $  0.70\deg\pm0.04\deg$ &    245.4 &      141.0 &  0.048 &  0.039 &    4.4 & $    2.1\pm0.2$ &$   2.36\pm0.18$ \\
+        1FGL J1837.5-0659c &    25.04\deg&     0.26\deg & $  0.61\deg\pm0.04\deg$ &    115.4 &       50.4 &  0.064 &  0.051 &   19.7 & $    2.2\pm0.3$ &$   2.09\pm0.20$ \\
+        P72Y1287           &   266.41\deg&    -0.75\deg & $  1.41\deg\pm0.06\deg$ &    128.8 &       99.4 &  0.097 &  0.087 &   19.3 & $    1.7\pm0.2$ &$   1.96\pm0.20$ \\
+        \hline
+      \label{new_ext_srcs}
+      \end{tabular}
+      \caption{New extended soruce candidates}
+    \end{centering}
+\end{sidewaystable}
+
+\clearpage
+\begin{sidewaystable}
+    \begin{centering}
+      \begin{tabular}{rrrrrrrrrr}
+        Name               & $\text{GLON}_1$ & $\text{GLAT}_1$ & $\text{GLON}_2$ & $\text{GLAT}_2$ & $\text{Flux}_1$ & $\text{Flux}_2$ & $\text{Index}_1$ & $\text{Index}_2$ & \tsinc \\
+        \hline
+        \multicolumn{6}{l}{$E > 1\gev$} \\
+        \hline
+        1FGL J1628.6-2419c &&&&& \\
+        1FGL J1554.0-5345c &&&&& \\
+        1FGL J0823.3-4248  &&&&& \\
+        \hline
+        \multicolumn{6}{l}{$E > 10\gev$} \\
+        \hline
+        1FGL J1613.6-5100c &&&&& \\
+        1FGL J1632.9-4802c &&&&& \\
+        1FGL J2020.0+4049  &&&&& \\
+        1FGL J1837.5-0659c &&&&& \\
+        P72Y1287           &&&&& \\
+        \hline
+      \label{new_ext_srcs}
+      \end{tabular}
+      \caption{Dual localization results for new extended sources.
+      \tsinc is the increase in TS compared to fitting a single point source. 
+      }
+    \end{centering}
+\end{sidewaystable}
+
   \begin{figure}
@@
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J1628.6-2419c/v2/source_1FGL_J1628.6-2419c.pdf
-    \caption{1FGL J1628.6-2419c}
+     % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v2/run.py
+    \caption{1FGL J1628.6-2419c. In the opiucus region=most likeliy a molecular cloud.
+    P72Y2516.
+    Note that unlike other plots, that this plot has the nearby sources subtracted.
+    This was done to remove the very bright, $\ts=460$, source P72Y2510 % XXXXXXXXXXXXXXXXXXXX what is this source
+    which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
+    }
   \end{figure}
@@
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J1554.0-5345c/v2/source_1FGL_J1554.0-5345c.pdf
-    \caption{1FGL J1554.0-5345c}
+     % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1554.0-5345c/v2/source_1FGL_J1554.0-5345c.pdf
+    \caption{1FGL J1554.0-5345c. P72Y2405. Unidentified source likely diffuse emission.}
   \end{figure}
@@
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_1000_v1/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-    \caption{1FGL J0823.3-4248}
-  \end{figure}
-
-  \begin{figure}
-    \begin{center}
-      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J2020.0+4049}
+     % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
+    \caption{1FGL J0823.3-4248. P72Y1212. Coincident with Puppis A SNR.
+    P72Y1212.
+    Note that unlike most other plots, this plot has the nearby sources subtracted.
+    This was done to remove the very bright source Vela which,
+    at position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
+    would otherwise spill over into the top left of the image.
+    }
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Gamma_Cygni}
     \end{center}
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J2020.0+4049/v2/source_1FGL_J2020.0+4049.pdf
+    % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
     \caption{
-    1FGL J2020.0+4049
+    Gamma Cygni. P72Y3281
     }
@@
     \begin{center}
-      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_MRFH0254}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
     \end{center}
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/MRFH0254/v2/source_MRFH0254.pdf
-    \caption{Lalla}
+    % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
+    \caption{Vela Jr. P72Y1287. Using $E>10\gev$. Here, the image is
+      convovled with a $0.25\deg$ gaussian. }
   \end{figure}
@@
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J1837.5-0659c/v2/source_1FGL_J1837.5-0659c.pdf
-    \caption{1FGL J1837.5-0659c}
-  \end{figure}
-
-  \begin{figure}
-    \begin{center}
-      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1636.4-4737c}
+    % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v2/source_1FGL_J1837.5-0659c.pdf
+    \caption{1FGL J1837.5-0659c. P72Y2974}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1632.9-4802c}
     \end{center}
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J1636.4-4737c/v2/source_1FGL_J1636.4-4737c.pdf
-    \caption{1FGL J1636.4-4737c}
+    % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
+    \caption{1FGL J1632.9-4802c. P72Y2540}
   \end{figure}
@@
     % this plot came from 
-    % /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v10/spectral_emin_10000_v1/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
+    % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
     \caption{
-    1FGL J1613.6-5100c }
+    1FGL J1613.6-5100c . P72Y2473}
   \end{figure}

### 2011-06-16 extended_catalog/paper/extended_catalog.tex
Adding bibliography

@@
 \documentclass[preprint]{aastex}
+
+% TODO:
+%   Add contours to images.
 
@@
 \newcommand{\gev}{\text{GeV}\xspace}
+\newcommand{\tev}{\text{TeV}\xspace}
 \newcommand{\sr}{\text{sr}\xspace}
@@
 \newcommand{\cm}{\text{cm}\xspace}
-\newcommand{\tsext}{\ensuremath{\text{TS}_\text{ext}}\xspace}
+\newcommand{\tsext}{{\ensuremath{\text{TS}_\text{ext}}}\xspace}
 \newcommand{\tsinc}{\ensuremath{\text{TS}_\text{inc}}\xspace}
+
+\newcommand{\rsixeight}{{\ensuremath{\text{r}_{68}}}\xspace}
+
+\newcommand{\tsextpointlike}{\ensuremath{\tsext_{,\pointlike}}}
+\newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}}
+\newcommand{\tsextalt}{\ensuremath{\tsext_{,\alt}}}
+
 \newcommand{\ts}{\text{TS}\xspace}
+\newcommand{\glon}{\text{GLON}\xspace}
+\newcommand{\glat}{\text{GLAT}\xspace}
+\newcommand{\alt}{\text{alt}\xspace}
 
@@
 % the program names
-\newcommand{\pointlike}{{\em pointlike}\xspace}
-\newcommand{\gtlike}{{\em gtlike}\xspace}
-\newcommand{\gtobssim}{{\em gtobssim}\xspace}
+\newcommand{\pointlike}{\text{\em pointlike}\xspace}
+\newcommand{\python}{\text{\em python}\xspace}
+\newcommand{\gtlike}{\text{\em gtlike}\xspace}
+\newcommand{\gtobssim}{\text{\em gtobssim}\xspace}
+\newcommand{\minuit}{\text{\em Minuit}\xspace}
 
@@
 The Large Area Telescope (LAT) is a pair conversion telescope on the
-Fermi Gamma-Ray Space Telescope that has been surveying the gamma ray
-sky since June 2008.  Fermi is particuarly well suited for surveying
-the entire Gamma-ray sky since it has a broad energy coverage ($20\mev$
-and $300\gev$), a wide field of view ($\sim 2.4 \sr$) and large effective area
-($\sim 8000 \cm^2$ at $>1\gev$).
-
-The LAT has been essential in understanding a variety of astrophysical
-sources including Active Galactic Nuclei, Pulsars, and Supernova Remnants.
-Many of the astrophysical sources seen by the Fermi LAT, espeically
-galactic Supernova Remnants and Pulsar Wind Nebulae, can be resolved at
-other wavelengths and could potentially be resolved by the LAT.
-
-studying supernova remnants, 
-pulsar wind nebulae, 
-galaxies,  galaxy clusters, and potentially dark matter and new physics.
-
-Resolving spatially extended $\gev$ sources is important for studying a
-variety of science topics. The most important use of spatial morphology
-is in source identification. Many of the sources found in $\gev$ sources
+Fermi Gamma-Ray Space Telescope. It has been surveying the Gamma-ray
+sky since June 2008.  Fermi is particularly well suited as a survey
+instrument because of its to survey the broad energy coverage ($20\mev$
+to $>300\gev$), a wide field of view ($\sim 2.4 \sr$) and large effective
+area ($\sim 8000 \cm^2$ at $>1\gev$).
+
+Using one year of all sky monitoring, the LAT published a catalog of
+source that were significantly resolved.  Many of these sources could
+be be associated with a variety of source classes including active
+galactic nuclei, pulsars, galaxies, and supernova remenants.  Many of
+these source classes can be spatially resolved when observed at other
+frequencies and could possibly be spatially resolvable by the LAT.
+
+In particular, the LAT has discovered a variety of spatially extended
+supernova remnants including IC443 and W51C (\cite{IC443,W51C}) and pulsar
+wind nebulae (\cite{MSH15-52,VelaX}). And there are other source classes
+which could possibly be spatially resolved by the LAT including galaxy
+clusters, dark matter, and possibly new physics.
+
+Furthermore, a variety of spatially extended but otherwise unassociated
+sources have been detected in the galacitc plane at \tev energies using
+Air Cherenkov detectors. Most prominent was a survey of the galaictc
+plane using H.E.S.S which discovered XXXXXXXXX spatially extended
+sources\cite{HESS_plane_survey}.
+
+Being able to spatially resolve a fermi source is important for several
+reasons. Most importantly, the spatial morphology can be used to help
+identify a Fermi source. Because of the large point spread function (PSF),
+for any source there are often several counterparts which it could be
+associated with. Finding a matching morphology can uniquly identify the
+source emitting the Gamma-rays.
+
+Because of the largely varying PSF of the LAT, the
+spatial and spectral model of a source do not nicely decouple and
+spatially resolving a Fermi source is also important for obtaining an
+unbiased spectral model of the source.  Furthermore, using this extension
+information is important for improved the overall model of the sky which
+is important for obtaining a better fit of nearby sources and removing
+spurious point sources which we might otherwise think we detect.
 
 Nevertheless, morphological studies of sources in the $\gev$ energy range using
-the Fermi LAT is challenging primarily because of the significantly energy
+the Fermi LAT is challenging because of the significantly energy
 dependent PSF and because of systematic errors in the
 galactic diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXX\deg$
-at $100\mev$ to $XXXXXXXXXXXXXXXX\deg$ at $100\gev$ and so the higher energy photons are
-
-The Large Area Telescope (LAT) on the Fermi Gamma-Ray Space Telescope
-has been surveying the Gamma-ray sky since August 2008. The LAT has been
-been essential in studying a variety of astrophysical sources including
-Active Galactic Nuclie, Pulsars, Supernova Remnants. 
-One of the important data productes
-
-Using 11 months of data, the LAT produced the best-resolved survey of the sky
-in the $100\mev$ to $100\gev$ energy range\cite{2FGL Paper}. The
+at $100\mev$ to $XXXXXXXXXXXXXXXX\deg$ at $100\gev$ so the higher energy photons 
+are significantly more important for resolving a source. On the other hand, 
+we tend to run out of photons at higher energies so a detailed statistical 
+test must be used to maximize our sensitivity.
 
@@
 significantly more important for studying the shape of sources. One could
-ideally look just at the highest energy photons, but the trade off is that
+ideally look at just the highest energy photons, but the trade off is that
 for typical sources many more source events are expected at low energy.
@@
 
-\subsection{\pointlike}
+\subsection{The \pointlike Package}
 
@@
 analyzing spatially extended sources. \pointlike is most thoroughly
-described in Matthew Kerr's Ph.D Thesis\cite{Matthew_kerr_phd_thesis}
+described in Matthew Kerr's Ph.D Thesis\cite{matthew_kerr_phd_thesis}
 but the important aspects will be summarized below. What differentiates
@@
 across a spatial bin.
-\pointlike additionaly bins the Fermi Gamma-rays by their conversion type,
-which corresponds to whether the photon converted in the front or back
-part of the detector. Since the PSF is smaller for front entering events,
-one would expect binning each conversion type independently to improve
-our sensitivity.
-Furthermore, \pointlike uses a sparse matrix
-representation of the spatial bins where only the bins with counts in them
-are looped over. The only downside to this is that the integral of the
-model predicted counts must be independently calculated.  Effectively,
-\pointlike efficiently interpolates from a totally binned analysis
-at low energy (where the resolution is poor and there are many counts)
-to an unbinned analysis at high energy (where the resolution is very
-good but there are few counts). This approach provides a significant
-savings in time while introducing only small numerical error.
-
-% XXXXXXXXXXXX describe how \pointlike calculates extension errors and how localization errors are calculated.
-
-% XXXXXXXXXXXX note about how \pointlike is written in python = more flexible
+
+\pointlike additionaly bins the Fermi Gamma-rays by their conversion
+type, which corresponds to whether the photon converted in the front or
+back part of the detector. Since the PSF is smaller for front entering
+events, one would expect binning each conversion type independently to
+improve our sensitivity.
+
+Furthermore, \pointlike uses a sparse matrix representation of the spatial
+bins where only the bins with counts in them are looped over. The only
+downside to this is that the integral of the model predicted counts
+must be independently calculated.  Effectively, \pointlike efficiently
+interpolates from a totally binned analysis at low energy (where the
+resolution is poor and there are many counts) to an unbinned analysis
+at high energy (where the resolution is very good but there are few
+counts). This approach provides a significant savings in time while
+introducing only small numerical error.
+
+Finally, \pointlike is written mostly in the \python programming language
+using numpy and scipy to vectorize most of the computations. This provides
+a reasonable tradeoff between computational efficiency and quickness
+of development time. And by leaving the interface to use \pointlike as a
+series of \python modules, advanced functions including extension fittion
+described in section~\ref{extesion_fitting} and the dual localization
+procedure described in section~\ref{dual_localization_method} could
+quickly be build on top of the core modules.
 
 \subsection{Extension Fitting}
+\label{extension_fitting}
 
@@
 the spatial and spectral information completely decouple and where
-the spatial shape is parameters by simple objects (Disks, Gaussian).
+the spatial shape is parameters by simple shapes.
 The code consistently convolves the extended source shape with the point
@@
 Finally, \pointlike allows the spatial parameters of an extended
-source to be simulataneoulsy fit. \pointlike uses the Minuit fitting
+source to be simulataneoulsy fit. \pointlike uses the \minuit fitting
 library to perform the maximum likelihood maximization of the position
-and extension of an extended source\cite{Minuit reference}.  At each
+and extension of an extended source (\cite{minuit_documentation}).  At each
 step in the fit of the shape, the spectral parameters of the entire sky
@@
 fit is not the longitude and latitude of the source but instead
-the displacement in a rotated reference frame. The covariance matrix is
-then computed and inverted to estimate the statistical errors on the
-position and extension.
+the displacement in a rotated reference frame.
 
@@
 
-To calculate the statistical significance of the extension of a source,
-one can define a parameter $\tsext$ as twice the increase
-in log likelihood between fitting a source with a
-spatially extended hypothesis and a point hypothesis. 
-So 
+\subsection{Extension Errors}
+
+Errors on fit parameters are typically calculated in one of two ways. The
+first method requires explicilty varying one paramter until the log of
+the likelihood has fallen by a value 1/2 while simulatenously optimizing
+the other fit parmaeters.  \minuit provides the {\em Simplex} function to
+calculate errors this way.\cite{minuit documentation and UP parameter}
+The second method involves estimating the likelihood function as being
+a multivariate gaussian and calcluating the curvature of the log of
+the likelihood at the peak to estimate when the function will fall by
+a value 1/2. \minuit provides the {\em HESSE} algorithm to calcualte
+errors this way.  The {\em HESSE} are significantly faster but make the
+approximation that the log of the likelihood is perfectly gaussian.
+
+We found that although much faster, the {\em HESSE} algorithm would
+somtimes grosely understimate the errors on the localization and extension
+of the source.  On the other hand, we found the {\em Simplex} algorithm
+was computationally very slow and would often run into convergence
+problems and fail to get reasonable errors.
+
+As a compromise, we employed a hybrid approach to calculate
+the localization and extension errors in \pointlike by making the
+approximation that the covariance between the extension and location of
+the source was small. On the other hand, we do not necessarily expect the
+likelihood profile to be Gaussian when varying the source's extension.
+So we calculate the error on the extension by fixing the position of the
+source and then explicitly using {\em Simplex} to vary the extension of
+the source until the log of the likelihood has fallen by 1/2.
+
+Then, the extended source's position error is calculated using the
+same code employed to calculate position errors of point sources. This
+code is used to calculate the localization error of all point sources
+in the catalog\cite{2FGL paper}. It works by fitting an ellipse to the
+likelihood surface near the maximum and using this fit ellipse to estimate
+an elliptical localization errors. By reporting two localization errors
+as well as a localization error angle, this method explicitly takes care
+of covariance between the two position coordinates.
+
+% Make an extension profile plot.
+% show it in figures an ddescirbeit.
+
+\subsection{Gtlike Crosscheck}
+
+Because of its computational speed, \pointlike is especially well
+optimized for analysis that requires many iterations. This include
+source localization, extension fitting, source finding, building test
+statistic maps, and model comparison. On the other hand, \pointlike's
+efficiency has to entail some loss of precision and so it is generally
+expected that \gtlike will produce a more precise result.  Furthermore,
+because it is the standard likelihood analysis package, \gtlike has been
+more extensively validated and is very well trusted.
+
+For that reason, we take our best fit source model obtained by
+\pointlike with the best fit positions and extensions and refit the
+spectral parameters of the model using \gtlike.  \gtlike provides a
+second calculation of the likelihood which can then be used to obtain
+for any source a second measure of \ts and \tsext.
+
+We find very good agreement between the two methods. For the new extended
+source candidates, Table \ref{alt_diff_model_results} shows a comparison
+of \ts and \tsext computed using \pointlike and \gtlike. For the rest
+of this paper, unless otherwise mentioned all \ts, \tsext, flux, and
+spectral index values were obtained using \gtlike with the localization
+results found by \pointlike.
+
+\subsection{Dual Localization}
+\label{dual_localization_method}
+
+There is a degeneracy in the signal expected from spatially extended
+sources and multiple point sources.  To assess the possibility of source
+confusion, we developed a function in pointlike for simulatenously fitting
+two point sources so that the likelihood fitting two point sources
+could be compared to the likelihood fitting one extended source.
+
+The algorithm works by first dividing the selected point source into
+two separate sources. Then, the position of the two sources 
+are fit simultanously. To avoid projection effects, the fit is
+done in a coordiante system rotated to the celestial equator.
+In this rotated coordiante system, space can be well approximated
+as being flat and we are interested in fitting the 
+rotated coordiante $(x_1',y_1')$ and $(x_2',y_2')$
+We decided not to directly fit the positions of the two sources 
+but instead the fit sum and difference of the rotated coordiantes
+$S_x=(x_2'+x_1')/2$, $S_x=(y_2'+y_1')/2$, $D_x=(x_2'-x_1')/2$, and $D_y=(y_2'-y_1')/2$.
+We believe that fitting the average of position and the difference
+independently would cause less degeneracy in the fit and help the fitter
+find the best position.
+
+For a particular value of $S_x$, $S_y$, $D_x$, and $D_y$, the Poisson
+likelihood is computed by converting the sum and difference coordinates
+into the rotated coordiantes, unrotating the coordiantes, moving the
+two sources in the \pointlike to the new positions, and performing a new
+spectral analysis at the modified position.  The function then maximizes
+The Poission likelihood $L(S_x,S_y,D_x,D_y)$ as a function of the sum
+and difference of the rotated coordaintes using the Minuit to fit the
+sum and differenc coordiantes (\cite{minuit_documentation}).
+
+After the minimization converges, we can define the parameter $\tsext$
+as twice the increase in log likelihood between fitting the region with
+two point sources and fitting the region with one point source
 \begin{equation}
@@
 \end{equation}
-
-In going from fitting a point source to fitting a simple extended source such as
-a disk, the source's width is the only degree of freedom added to the model. According to
-Wilk's Theorem, the distribution of $\tsext$ for no signal (when there is a true
-point source) should follow a $\chi^2_1$ distribution with one degree of freedom\cite{Wilks_Theorem}.
-Wilk's Theorem only holds when the likelihood is maximized simultaneoulsy
-fitting all of the parameters of model. It is for this reason why 
-\pointlike
-goes through such great effort to simultaneously fit the position, extension,
-and spectral paramters of a source.
+Generally, \tsinc can be directly compared to \tsext to see wheter two
+point sources are prefered over one extended source. Unfortunatly,
+performing a likelihood ratio test between two unnested models
+is not a calibrated test and so there is no straightforward way
+to convert the change in likelihood into a significance~\ref{
+http://arxiv.org/abs/astro-ph/0201547 }. Nevertheless, we find this
+ratio, at least in the extreme case where $\tsinc \ll \tsext$ or
+$\tsinc\gg\tsext$ to be suggestive. For all the spatally extended
+candidates found, we computed both \tsext and \tsinc.
+
+Because of \pointlike's computational efficiency, this algorithm
+runs in a reasonable amount of time.
+
+\subsection{Comparing Source Sizes}
+
+% XXXXXXXXXXXXXXX This section needs work
+
+When running \pointlike, we have to pick a spatial model for an extended
+source. Our spatial model is then convolved with the PSF to create the
+probability density function (PDF) that is is fit to the obersved counts.
+Possible choices for spatial models include a Two dimensional gaussian
+source (defined as a Gaussian in $x$ times a Gaussian in $y$):
+\begin{equation}
+  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
+\end{equation}
+or a uniform disk:
+\begin{equation}
+  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(\sqrt{x^2+y^2}<\sigma\right).
+\end{equation}
+
+Although these shapes look significantly different from eachother, the
+convolution of these spatial models of typtical sizes 
+with the PSF will produce PDFs that are very similar.
+
+This is demonstrated in figure~\ref{compare_disk_gauss}.  The plot shows
+(in black) the PSF that would be observed for a source of spectral index
+2. The dashed red (blue) line shows the probabability density function
+for a Gaussian (uniform disk) of width $0.5\deg$.  The solid red (blue)
+line shows the probability density function for the same Gaussian (uniform
+disk) convolved with the PSF of an index 2 source.  
+figure~\ref{compare_disk_gauss} shows the analysis using an energy range
+of 1\gev to 100\gev whereas the right plot shows an analysis using an
+energy range from 10\gev to 100\gev.
+
+This plot shows that significantly different extended source shapes
+look very similar after smearing with the PSF. The convolved shape of
+the disk and Gaussian admittedly do look more different when restrict
+ourselves to higher energy where the PSF is narrower, but we do not
+excpet to have much luch learning about the exact nature of the
+extended source shape. For that reason, in this paper we always use
+the uniform disk spatial model to emphaizie our ignorance to the true
+shape of the extended sources we are studying.
+
+To get the convolved disk and Gaussian models looked so similar in
+figure~\ref{compare_disk_gauss}, we had to pick the extension of the two
+sources so that they each predicted a 68\% containment radius of 0.5\deg.
+
+The 68\% containment radius for a spatial model is
+the radius at which 68\% of the intensity is enclosed.
+It can be computed by a straightforward integral and we
+find that $\rsixeight_\text{,disk}=0.82\sigma$ whereas
+the $\rsixeight_\text{,Gaussian}=1.51\sigma$. Therefore, in
+figure~\ref{compare_disk_gauss} the uniform disk has an extension
+of $\sigma=0.41\deg$ whereas the Gaussian has an extension of
+$\sigma=0.75\deg$. Even though these sources have quite different
+values of the extension $\sigma$, they look almost identical when convolved
+with the PSF.
+
+Finally, we note that comparing observed morphologies to 
+counts maps can be misleading.  This effect can best be seen
+in figure~\ref{compare_r68} where we have simulted a
+extended source with 
+a spatial model that is a uniform disk of extension 0.5\deg,
+integral flux between 1\gev and 100\gev of $3e-8\ph/\cm^2/s$,
+and a spectral index of 2.
+
+To reduce Poisson noise, figure~\ref{compare_r68} shows a counts map of
+this simulated source smoothed with a 0.1\deg Gaussain kernel.  Overlaied
+on the plot is the results of fitting this simulated source with a uniform
+disk and a Gaussian spatial model.  The solid white line represents the
+fit extension $\sigma_\text{disk}=0.496$ for the disk which was found to
+be in very good agreemen with the simulated value.  The solid black line
+represenst the fit extension $\sigma$ for the Gaussian which was found to
+be $\sigma_\text{Gaussian}=0.2627$.  The white dashed line is the 68\%
+containment radius of the fit Disk shape and the black dashed line is
+the 68\% containment radius of the fit Gaussian shape.  Even though the
+fit $\sigma$ for the disk and uniform Gaussian are different, the fit
+68\% continment radius are very similar ($\rsixeight_\text{,disk}=0.41$
+whereas $\rsixeight_\text{,Gaussian}=0.40$).
+
+There are three important conclusions to take from this. The first is
+that depending upon what spatial model you pick and what parameter you
+choose to overlay on the smoothed counts ($\sigma$ or $rsixeight$),
+you will get very different looking shapes even though the all lead
+to a PDF which is very similar. And since we are not very sensitive
+to the particular morphology of extended sources that we are seeing,
+there is no correct choice for which shape to use. For the following
+analysis, we always use a uniform disk as our spatial model because
+of its conceptual simplicity and to emphasize our ignorance to the
+true morphology. And for subsequent smoothed counts maps, we overlay
+the $\sigma$ because that shows directly the edge of the shape we fit.
+But due to smearing of the PSF, it has the unfotunatly concequence that
+the extended source shape always (including in the simulated image)
+looks larger than in the counts map.
+
+The second conclusion we make is that because a counts map is smeared
+out by the PSF and depends strongly on the particular color bar used, it
+is very difficult to determine directly from a counts map a reasonable
+spatial model that fits the data.  It is much better to obtain the
+spatial model by a direct fit of a spatial parameters of a selected
+model to the data.  The third conclusion we make is that when comparing
+fit extensions to those at other wavelenghts (espeically in \tev), it is
+important to compare fits of consistent spatial models. If this is not
+possible, it is impotant to at least compare indirectly the $rsixeight$
+for the different spatial models.
+
+\section{LAT Extended Source Validation}
+
+\subsection{Significance of Extension}
+
+To calculate the statistical significance of the extension of a source,
+one can define a parameter $\tsext$ as twice the increase in log
+likelihood between fitting a source with a spatially extended hypothesis
+and a point hypothesis:
+\begin{equation}
+  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
+\end{equation}
+Of course, these are nested hypotehsis since a point sources is just an
+extended source in the limit that the extension goes to 0. So since we
+are just adding a paramter, it should always be true that $\tsext > 0$
+We would expect that if we were really testing a point source that
+\tsext would not be very large since a point model would fit about
+as good as anytthing else. Therefore, we can consider a source to be
+extended (and reject the null hyopthesis) if \tsext is large enough.
+Since going from fitting a point soue to fitting a simple extended
+source introduces only one degree of freedom (the source's extension)
+Wilks' Theorem says that the distribution of $\tsext$ wen testin
+point sources should follow a $\chi^2_1$ distribution with one degree
+of freedom (\cite{wilks_theorem}).
 
 On the other hand, since the null hypothesis rests on the edge of
-parameter space, when the extension is fixed to 0, Wilk's Theorem does
-not formally hold\cite{Warnings about Wilk's Theorem Paper}.  One might
+parameter space, when the extension is fixed to 0, Wilks' Theorem does
+not formally hold (\cite{warn_wilks_theorem}).  One might
 expect the actual distribution to be a half $\chi^2_1$ distribution with
@@
 \end{equation}
+Chernoff proved that given certain assumtipons, this is
+the ditribution that would hold when the null hypothesis
+lies on the edge of parameter space for a particular parameter~\ref{chernof}.
 The false detection probability can be estimated by integrating this function 
@@
 $\sqrt{\ts}$ is a measure of the number of $\sigma$ of the detection.
+
+It should be noted that Wilks' Theorem only holds when the likelihood
+is maximized simultaneoulsy fitting all of the parameters of model. It
+is for this reason why \pointlike goes through such great effort to
+simultaneously fit the position, extension, and spectral paramters of
+a source.
 
@@
 
-It seems plausable that a similar situation could happen for when testing
+It seems plausable that a similar situation could happen when testing
 a source for extension. Half of the time, statistical flucutations might
@@
 source fitting code. It was only after introducing this change that we
-were able to get broad agreement between simulations and Wilk's theorem.
-
-% XXXXXXXXXXXXXXXXXXX NOTE ABOUT gtlike crosscheck
-
-\subsection{Dual Localization}
-
-There is a degeneracy in the signal expected from spatially extended
-sources and multiple point sources.  To assess the possibility of source
-confusion, we developed a function in pointlike for simulatenously fitting
-two point sources so that the likelihood fitting two point sources
-could be compared to the likelihood fitting one extended source.
-
-The algorithm works by first dividing the selected point source into
-two separate sources. Then, the position of the two sources 
-are fit simultanously. To avoid projection effects, the fit is
-done in a coordiante system rotated to the celestial equator.
-In this rotated coordiante system, space can be well approximated
-as being flat and we are interested in fitting the 
-rotated coordiante $(x_1',y_1')$ and $(x_2',y_2')$
-We decided not to directly fit the positions of the two sources 
-but instead the fit sum and difference of the rotated coordiantes
-$S_x=(x_2'+x_1')/2$, $S_x=(y_2'+y_1')/2$, $D_x=(x_2'-x_1')/2$, and $D_y=(y_2'-y_1')/2$.
-We believe that fitting the average of position and the difference
-independently would cause less degeneracy in the fit and help the fitter
-find the best position.
-
-For a particular value of $S_x$, $S_y$, $D_x$, and $D_y$, the Poisson
-likelihood is computed by converting the sum and difference coordaintes
-into the rotated coordiantes, unrotating the coordiantes, moving the
-two sources in the \pointlike to the new positions, and performing a new
-spectral analysis at the modified position.  The function then maximizes
-The Poission likelihood $L(S_x,S_y,D_x,D_y)$ as a function of the sum
-and difference of the rotated coordaintes using the Minuit to fit the
-sum and differenc coordiantes\cite{Minuit reference}.
-
-After the minimization converges, we can define the 
-parameter $\tsext$ as twice the 
-increase
-in log likelihood between fitting the region with
-two point sources and fitting the region with one point source
-\begin{equation}
-  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
-\end{equation}
-Generally, \tsinc can also
-
-% XXXXXXXXXXXXXXX \tsinc vs \tsext NOT A CALIBRATED TEST
-% but still suggestive in the cases \tsinc \ll \tsext and
-% \tsinc \gg \tsext.
-
-Because of \pointlike's computational efficiency, this algorithm
-runs in a reasonable amount of time.
-
-After
-% XXXXXXXXXXXXXXXXXXX NOTE ABOUT gtlike crosscheck
-
-\subsection{Comparing Source Sizes}
-
-Description of comparing r68, sigma for disk, gaussian, etc.
-why the plots don't look correct.
-
-\section{Monte Carlo Validation}\label{monte_carlo_validation}
-
-% XXXXXXXXXXXXXXXX better description of how TSext is always > 0
-% but wilk's thorem says that it won't be must better if the source
-% is a point source
+were able to get broad agreement between simulations and Wilks' theorem.
+
+\subsection{Monte Carlo Validation} \label{monte_carlo_validation}
 
@@
 The monte carlo simulation was perforormed over a one year time interval using
-a default rocking profile and an assumed livetime fraction of 0.8.
+a default rocking profile and an assumed a represntative
+livetime fraction of 0.8.
 The reconstruction was perfromed with events from an energy range of
@@
 against $\tsext$ For reference, the CDF for $\chi^2_1/2$,
-suggested by Wilk's Theorem, is also plotted for comparison. Overall,
-there is good agreement between Wilk's theorem, although the agreement is
+suggested by Wilks' Theorem, is also plotted for comparison. Overall,
+there is good agreement between Wilks' theorem, although the agreement is
 not perfect.  It should be noted that the discrepancy seems to be worst
@@
 apparent for sufficiently bright sources.  Other possible reasons for
-departure from Wilk's theorem might include \pointlike ignoring energy
+departure from Wilks' theorem might include \pointlike ignoring energy
 dispersion. Energy dispersion will change the shape as a function of
@@
 
-\section{Extended Source Sensitivity}
+\section{Extended Source Sensitivity}\label{extension_sensitivity}
 
@@
 we simulated sources with a uniform radially symmetric
-disk morphology on top of a powerlaw
-Sreekumar-like isotropic spectrum.\cite{Sreekumar et al. ApJ 494 pag
-523 1998}.  For a given extension and spectral index, we calculated the
+disk morphology on top of a powerlaw Sreekumar-like isotropic
+spectrum.\cite{Sreekumar et al. ApJ 494 pag 523 1998}.  The monte carlo
+simulation was perforormed over a one year time interval using a default
+rocking profile and an assumed a represntative livetime fraction of 0.8.
+For a given extension and spectral index, we calculated the
 sensitivity by varying the flux of a source until we found 
@@
 that the emission originated as point sources and what was presented was
-a list of all sources fit assuming a point source spatial hyopthesis. All
-published extended sources were modeled by the catalog group as extended
-sources, but no attempt was made to test if other sources in the catalog
+a list of all sources fit assuming a point source spatial hypothesis. 
+Published extended sources were modeled by the catalog group as 
+being extended, but no attempt was made to test if other sources in the catalog
 could be spatially resolved.
@@
 We performed a search of all Fermi sources found in the second Fermi LAT
-catalog for extension.  We performed the extension fit using \pointlike.
-To perform this search, we built a model of the sky consistent with
-the two year catalog's model.   We used the same two year data set and
-the same pass 7 instrument response function We used the same galactic
-diffuse, isotropic diffuse, and earth limb emission model. The spectrum
-of the galactic and isotropic diffuse models were refit during the
-analysis. The earth limb emission was fixed to predicted value.
-
-For each source, we used a circular $10\deg$ region of interest centered
-on our source. We performed a fully binned analysis.  The spatial bin
-size was scaled with energy as was described above and we uniformly
-binned in log energy, using 4 binned per logarithmic decade of of energy.
-We included all background catalog sources within $15\deg$ of the source
-of interest and refit the spectral parameters of sources within $2\deg$
-of our source.
+catalog for extension.  To perform this search, we built a model of the
+sky consistent with the two year catalog's model.   We used the same two
+year data set running from XXXXXXXXXXX MET to XXXXXXXXXXX MET and we used
+the same pass 7 instrument response function.  We used the same galactic
+diffuse, isotropic diffuse, and earth limb emission model. The spectrum of
+the galactic and isotropic diffuse models were refit during the analysis
+while the earth limb emission was fixed to it's predicted value.
+
+We performed the extension fit using \pointlike.  For each source, we
+used a circular $10\deg$ region of interest centered on our source and
+using 4 bins uniformly in each logarithm of energy.  We included all
+background catalog sources within $15\deg$ of the source of interest
+and refit the spectral parameters of sources within $2\deg$ of our source.
 
@@
 below $1\gev$. On the other hand, the large PSF at low energy makes us
-more succeptable to systmetic errors arising from source confusion and
-from out modeling of the galactic diffuse emission.  For that reason,
-we performed our search using events between $1\gev$ and $100\gev$.
+more succeptable to systmetic errors arising from source confusion due
+to multiple point soruces and succeptable to incorrect modeling of the
+galactic diffuse emission.  For that reason, we performed our search
+using events only between $1\gev$ and $100\gev$.
 
 We also performed a search for extended sources using events only between
-$10\gev$ and $100\gev$. Even though we are testing the same sources,
-this approach is complimentary because there are regions in the galactic
+10\gev and 100\gev. Even though we are testing the same sources, this
+approach is complimentary because there are regions in the galactic
 plane where at lower energies the diffuse emission dominates and is
@@
 accessible by the LAT, the galactic diffuse emission will be smaller and
-we might expect to detect significantly harder soruces. This approach
+we might expect to detect significantly harder sources. This approach is
+also beneficial because harder sources with nearby neighbors that are
+softer may end up being incorrectly fit at lower energies but correctly
+found looking only at the high energy.  This is also beneficial in the
+galactic plane looking for possible extended sources near pulsars which
+are very bright at lower energy but cutoff before 10\gev.  This approach
 of using only events above $10\gev$ was succesfully used to detecting
@@
 
-For each source we were testing, we modified the source to have a
-uniform radially symmetric disk spatial shape and then used \pointlike to
-simultenously fit the position and extension of the source. As described
-above, we additionally modified the source to be a extended source with
-it's extension fixed to $10^{-10\circ}$ and fit this position of this
-pseudo source. For each source, we then computed the increase in log
-likelihood fitting with the extended hypothesis and looked at all of
-the sources with $\tsext>16$ corresponding to a $4\sigma$ statistical
-significance of extension.
-
-We expect most extended sources to be galactic sources since
-extragalacitc sources are typically too far away to be spatially
-resolved. Unfortuantly, the galactic plane is the most difficult place
-to find sources since they must be found for on top of the anisotropic
-galactic diffuse emission.  Modeling the galactic diffuse emision is
-very difficult~\ref{first_diffuse_paper}.  And finding sources in the
-galactic plane is notoriusly difficult, as was discussed in the Fermi
-catalog~\ref{1FGL}. One would expect extended sources to be even more
-difficult to detect since diffuse emission residuals are expected
-to be large compared to the PSF. Furthermore, the galacitc plane
-is very crowded and there is a degenecy between an extended source
-and multiple point sources. So finding a source with
-$\tsext>16$ is not sufficint for detecting an extended.
-
-For each of the extended source candidates for which either the analysis
-using events above $1\gev$ or $10\gev$ found $\tsext>16$
-and performed several followup analyses to substantiate our analysis.
+For each catalog source, we modified the source to have a uniform radially
+symmetric disk spatial shape and used \pointlike to simultaneously fit
+the position and extension of the source.  We then selected the sources
+for which \pointlike found $\tsext>16$ and refit their spectral parameters
+using \gtlike.
+
+% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+% NOTE ABOUT PRUNE aridus
+
+\subsection{Additional Analysis}
+
+We expect most extended sources to be galactic sources since extragalactic
+sources are typically too far away to be resolvable. Unfortunately,
+the \gev emission in the galactic plane is dominated by anisotropic
+galactic diffuse emission.  Modeling the galactic diffuse emission is
+very difficult~\ref{first_diffuse_paper}  and finding sources on top of
+this emission is notoriously difficult. This issue has been discussed
+in the Fermi catalog~\ref{1FGL,2FGL}. Furthermore, the galactic plane
+is very crowded and there is a degeneracy between an extended source
+and multiple point sources. So it is often difficult to ensure you have
+a good model for the region around a source .  Finding a source with
+$\tsext>16$ is not sufficient for detecting an extended and we had to
+perform many crosschecks to make sure we had a good fit to our region.
+
+% XXXXXXXXXXXXXXXXXXXXX
+% LIST OF All extended source candidates and how many of them are clearly bad.
+% best we can do is sort through them.
+
+% XXXXXXXXXXXXXXXXXXXXXXXXXXX
+% Put example of poorly fit region and how it is difficult to know what
+% is going on.
+
+For each of the extended source candidates where $\tsext>16$,
+we performed several additional analyses to determine whether
+our model for the region was believable and that we could therefore
+find out source to be extended.
+We did so for all sources found either at events above 1\gev or above 10\gev
 
@@
 \gtlike.
-We used a square ROI $10\deg$ in diamater, the same 4 degrees
-per decade, and $0.125\deg$ energy binning.
+We used a square ROI $14.1\deg$ in diamater with $1/16\deg$ pixels
+and the same energy binning.
+% XXXXXXXXXXXXXX put note about how this binning was necessary for morphological analysis and how any smaller is no good.
+% using gtlike. But how pointlike handles this automatically
 The \gtlike analysis provided a second estimate of the spectral
-paramters of the extended source as well as a second calculation of
+parameters of the extended source as well as a second calculation of
 $\ts_\text{disk}$, $\ts_\text{point}$, and 
@@
 
+% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+% Note about how it is helfpul to look at high energy
+% to avoid source confusion and even though a source
+% might show up above 1GeV, it might be hard to realize
+% wheter it is source confusion/diffuse emission, etc.
+% but at high energy, less diffuse emission + better PSF
+% = easier to find extended sources.
+
+% Also note about how softer other sources nearby 
+% might go away at higher energy
+
+% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+% NOTE about pointlike TS_ext generally being larger then
+% gtlike TS_ext and why this may be (binning front/back evnets
+% seperatly, using too large an energy bin, etc).
+% 
+% This is no longer true with better binning 1/16 instead of 1/8 degree binning.
+
 Additionaly, we generated for each 
@@
 TS values in test
+
+% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+% Note about dual localization
 
@@
 Figure~\ref{res_tsmaps} shows an example residual TS map.
+
+% XXXXXXXXXXXXXXX add now about using powerlaw models for our source +
+% setting e0 in geometric range of energy bin.
+
+% XXXXXXXXXXXXXXXXXXXXX
+% Discussion of how 
+% counts slices are best for
+% looking at overall diffuse emission.
+
+% XXXXXXXXXXXXXX discussion of complicated regions having to simulatenously refit
+% backgorund sources. Relocalizing sources.
+% bg sources are obtained by catalog w/ > 100MeV analysis may
+% not be idea for >1GeV & >10GeV analysis. Also, may require moving b/c
+% extension will effect their extension.
+
+\subsection{Alternate Diffuse Model Crosscheck}
+\label{alt_diff_model_description}
+% XXXXXXXXXXX All about using alternate diffuse model
 
@@
 Cloud.~\cite{SMC & LMC Paper}.  Our tool also successfully detected the
-extension of hte supernova remenants IC443, W28, W30, W44, and W51C.
+extension of the supernova remenants IC443, W28, W30, W44, and W51C.
 
@@
 is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again a
-$\chi^2/2$ distribution suggested by Wilk's Theorem.  This plot shows
+$\chi^2/2$ distribution suggested by Wilks' Theorem.  This plot shows
 a worse agreement with the theoretical distribution then was found
@@
 
+% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+% Note about how TSext for AGN calculated with pointlike
+
 \section{New Extended Sources}
@@
 \subsection{1FGL J1554.0-5345c}
-Unidentified source likely diffuse emission
+Unidentified source likely diffuse emission.
+See figure \ref{1FGL_J1554.0-5345c}.
 
 \subsection{1FGL J0823.3-4248}
-Coincident with Puppis A SNR
+Coincident with Puppis A SNR.
+See figure~\ref{1FGL_J0823.3-4248}.
 
 \subsection{1FGL J1613.6-5100c}
-Near HESS Source XXXXXXXXXXXXXX
+Near HESS Source XXXXXXXXXXXXXX.
+See figure~\ref{1FGL_J1613.6-5100c}.
 
 \subsection{1FGL J1632.9-4802c}
-Near HESS Source XXXXXXXXXXXXXX
+Near HESS Source XXXXXXXXXXXXXX.
+See figure~\ref{1FGL_J1632.9-4802c}.
+
+% XXXXXXXXXXXXXXXXXXXXXXXXXXX
+% Note about uncertainty about background sources. 
+% We model the northwestern source separatly
+% but not the southeastern 'possible source'.
 
@@
 Gamam Cygni SNR. Upcomming publication. 
+% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
+See figure~\ref{1FGL_J2020.0+4049}.
 
@@
 Near HESS source HESS J1837. Upcomming publication???
+% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
+See figure~\ref{1FGL_J1837.5-0659c}.
 
@@
 Vela Jr. Upcomming publication.
+% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
+See figure~\ref{Vela_Jr}.
 
 \section{Conclusion}
+
+We make some conclusions about finding extended
+sources with the Fermi LAT.
+
+Many extended sources. Especially instructive to
+use events with $E>10\gev$ where we don't have
+to worry about diffuse background as much.
+
+Make some conclusion about how the LAT will eventually collect a factor
+of 5 more data! Pointlike will be necessary to improve the model of the
+high energy sky.
+
+\bibliographystyle{apj}
+\bibliography{extended_catalog}
 
@@
   \begin{centering}
-\begin{tabular}{ | r | r | r | r | }
-\hline
-$\gamma$ & flux ($\ph/\cm^2/\s$) & $N_\text{sims}$ & $<\ts>$ \\
+    \begin{tabular}{ r | r | r | r }
+      \hline
+      \hline
+      $\gamma$ & flux ($\ph/\cm^2/\s$) & $N_\text{sims}$ & $\langle\ts\rangle$ \\
       \hline
@@
     number of statistically indepdent simulations and the average test
-statistic found for that given spectral model ($<\ts>$) is tabulated.
+    statistic found for that given spectral model ($\langle\ts\rangle$) is tabulated.
     The important feature to see in this table is that the monte carlo
@@
     $>100\mev$ integral flux measured in units of $\ph/\cm^2/\s$.
+    More information about this monte carlo analysis is presented in
+    section~\ref{monte_carlo_validation}
     }
@@
     red is the cumulative density function of $\chi^2(\ts)/2$ which is
-    suggested by Wilk's theorem as the theoretical distribution these
+    suggested by Wilks' theorem as the theoretical distribution these
     curves should should follow.  Overall, it should be noted that there
@@
     Monte Carlo curve lies to the left of the theoretical curve, which
-    would imply that using Wilk's Theorem as the null distribution would
+    would imply that using Wilks' Theorem as the null distribution would
     conservativly underestimate the signifcance of a source detection. In
@@
     For each spectral model, more information about the simulations is
-    summarized in table~\ref{ts_ext_num_sims}.
+    summarized in table~\ref{ts_ext_num_sims}. More
+    information about this monte carlo analysis is presented in
+    section~\ref{monte_carlo_validation}
     }\label{ts_ext_mc}
@@
     \end{center}
-    \caption{Lalla}\label{index_sensitivity}
+    \caption{This is the Fermi LAT's sensitivity to spatially
+    extended sources. The $x$ axis is Monte Carlo extension of a
+    simulated uniform disk source and the $y$ axis is the simulated
+    source's $100\mev$ to $100\gev$ photon flux. Each curve represents
+    the detection threshold for being able to spatially resolve an
+    extended source (when $\langle\tsext\rangle=25$ averaged over
+    multiple simulations).  
+    All sources have an assumed powerlaw spectrum and the different
+    colors are for sources of different simulated spectral indices.
+    The dashed line shows simulations using events with energy between 
+    $100\mev$ and $100\gev$ while the solid lien shows simulations
+    using events with energy between $1\gev$ and $100\gev$.
+    The sensitivity is for a one year simulation against a Sreekumar-like
+    isotropic background\cite{Sreekumar et al. ApJ 494 pag 523 1998}.
+    This plot shows that our sensitivity is best for sources that are
+    about $1\deg$ large. It also shows that for sources That are neither
+    very large nor very soft, our sensitivity is not significantly
+    improved using events between $100\mev$ and $1\gev$.  More information
+    about this plot is presented in section~\ref{extension_sensitivity}.
+    }\label{index_sensitivity}
   \end{figure}
@@
     \begin{center}
+      \includegraphics{mc_plots/compare_disk_gauss.pdf}
+      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
+    \end{center}
+    \caption{Comparison of Disk and Gauss.
+    % XXXXXXXXXXXXXXXXXXXXX
+    % the overall point here is that disk looks like gauss once convolved with the psf.
+    }\label{compare_disk_gauss}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics{mc_plots/compare_r68.pdf}
+      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_r68/v2/plot.py
+    \end{center}
+    \caption{Comparison of r68 for disk and gauss. This is a simulated disk source.
+    % XXXXXXXXXXXXXXXXXXXXX
+    % Add more to caption about htis plot.
+    }\label{compare_r68}
+  \end{figure}
+
+\begin{figure}
+  \begin{center}
     \includegraphics{source_plots/agn.pdf}
@@
     \end{center}
-    \caption{Lalla}\label{agn_ts_ext}
+    \caption{Lalla
+% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+% Note about how TSext for AGN calculated with pointlike
+    }\label{agn_ts_ext}
   \end{figure}
@@
     for the SNR IC443, which has a typical spectral model.}
-    \label{counts_slice}
+    \label{ts_ext_vs_energy}
   \end{center}
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/counts_slice_ic443/v1/ic443_counts_slice.pdf
-    \caption{Counts slice}
+    \caption{
+    % XXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+    % best for lookign at overall diffuse emission and visually assesing quality of the fit.
+    }
     \label{counts_slice}
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/smoothed_counts_ic443/v1
-    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.}
+    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.
+    % XXXXXXXXXXXXXXXXXXXXXXXXXXX 
+    % describe that this is IC443 using (front? or back? or both?) events.
+    }
     \label{smoothed_counts}
@@
 \end{figure}
+
+% XXXXXXXXXXXXXXXXXXXXXXXX
+% Make IC443 extension profile
+% good for looking for
+% how peaky likelihood is and
+% wheter or not there is one unique
+% extension maximum (Often times
+% double peaked or does not fall
+% at low/high energies.
+% 
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/profile_ic443.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_profile_ic443/v1/profile_ic443.pdf
+    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.
+    % XXXXXXXXXXXXXXXXXXXXXXXXXXX 
+    % describe that this is IC443 using (front? or back? or both?) events.
+    }
+    \label{extension_profile}
+  \end{center}
+\end{figure}
+
+% XXXXXXXXXXXXXXXXXXXXXXX
+% example bad fit
+% P72Y3047
 
@@
     \begin{centering}
-      \begin{tabular}{rrrrrrrrrrr}
-        Name           &    GLON &    GLAT & $\sigma(\deg)$ &     \ts & $\tsext$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
-        \hline
-        \multicolumn{11}{l}{$E > 1\gev$} \\
-        \hline
-        SMC            & 302.87  &  -44.65 &    $1.59\pm0.15$ &    93.1 &                   51.2 & 0.173 & 0.129 &  41.9 &   $3.0\pm0.4$    & $2.42\pm0.16$ \\
-        LMC            & 278.58  &  -32.82 &    $2.26\pm0.09$ &   384.2 &                304.374 & 0.096 & 0.071 & -35.5 &  $12.9\pm0.7$    & $2.42\pm0.08$ \\
-        IC443          & 189.05  &  3.04   &    $0.35\pm0.01$ & 10765.3 &                535.282 & 0.006 & 0.006 &  84.0 &  $65.2\pm1.2$    & $2.23\pm0.02$ \\
-        W28            & 6.51    &  -0.29  &    $0.39\pm0.02$ &  1231.3 &                   92.1 & 0.014 & 0.013 &  30.4 &  $55.9\pm1.8$    & $2.65\pm0.03$ \\
-        W30            & 8.61    &  -0.20  &    $0.36\pm0.04$ &   458.1 &                  66.0  & 0.020 & 0.018 &  14.1 &  $30.0\pm1.8$    & $2.58\pm0.06$ \\
-        W44            & 34.68   &  -0.42  &    $0.34\pm0.02$ &  1387.6 &                  111.3 & 0.009 & 0.009 & -39.4 &  $74.7\pm1.0$    & $2.67\pm0.01$ \\
-        W51C           & 49.12   &  -0.44  &    $0.28\pm0.02$ &  2174.7 &                   87.6 & 0.010 & 0.010 &  59.4 &  $41.6\pm1.3$    & $2.38\pm0.04$ \\
-        \hline
-        \multicolumn{11}{l}{$E > 10\gev$} \\
-        \hline
-        HESS J1825-137 &   17.58 &   -0.46 &    $0.64\pm0.08$ &    85.6 &                   62.5 & 0.050 & 0.045 & 33.6  &     $19.4\pm1.4$ & $2.27\pm0.07$ \\
-        MSH 15-52      &  320.39 &   -1.22 &    $0.20\pm0.06$ &    73.7 &                    9.5 & 0.033 & 0.032 & 3.9   &      $4.7\pm0.7$ & $1.88\pm0.12$ \\
-      \label{known_extended_sources}
+      \begin{tabular}{r|rrrrrrrrrr}
+        \hline
+        \hline
+        Name                 &          \glon &          \glat &                    $\sigma$ &       TS &   $\tsext$ &      Major &      Minor &    Pos Ang &      Flux ($10^{-9}$) &                 Index \\
+        \hline
+        \multicolumn{11}{c}{$E > 1\gev$} \\
+        \hline
+        SMC                  &     302.87\deg &     -44.65\deg & $  1.59\deg \pm   0.15\deg$ &     93.1 &       51.2 &  0.173\deg &  0.129\deg &   41.9\deg & $    3.0 \pm     0.4$ & $   2.42 \pm    0.16$ \\
+        LMC                  &     278.58\deg &     -32.82\deg & $  2.26\deg \pm   0.09\deg$ &    384.2 &      304.4 &  0.096\deg &  0.071\deg &  -35.5\deg & $   12.9 \pm     0.7$ & $   2.42 \pm    0.08$ \\
+        IC443                &     189.05\deg &       3.04\deg & $  0.35\deg \pm   0.01\deg$ &  10765.3 &      535.3 &  0.006\deg &  0.006\deg &   84.0\deg & $   65.2 \pm     1.2$ & $   2.23 \pm    0.02$ \\
+        W28                  &       6.51\deg &      -0.29\deg & $  0.39\deg \pm   0.02\deg$ &   1231.3 &       92.1 &  0.014\deg &  0.013\deg &   30.4\deg & $   55.9 \pm     1.8$ & $   2.65 \pm    0.03$ \\
+        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.04\deg$ &    458.1 &       66.0 &  0.020\deg &  0.018\deg &   14.1\deg & $   30.0 \pm     1.8$ & $   2.58 \pm    0.06$ \\
+        W44                  &      34.68\deg &      -0.42\deg & $  0.34\deg \pm   0.02\deg$ &   1387.6 &      111.3 &  0.009\deg &  0.009\deg &  -39.4\deg & $   74.7 \pm     1.0$ & $   2.67 \pm    0.01$ \\
+        W51C                 &      49.12\deg &      -0.44\deg & $  0.28\deg \pm   0.02\deg$ &   2174.7 &       87.6 &  0.010\deg &  0.010\deg &   59.4\deg & $   41.6 \pm     1.3$ & $   2.38 \pm    0.04$ \\
+        \hline
+        \multicolumn{11}{c}{$E > 10\gev$} \\
+        \hline
+        HESS J1825-137       &      17.58\deg &      -0.46\deg & $  0.64\deg \pm   0.08\deg$ &     85.6 &       62.5 &  0.050\deg &  0.045\deg &   33.6\deg & $    1.8 \pm     0.3$ & $   1.75 \pm    0.20$ \\
+        MSH 15-52            &     320.39\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &     73.7 &        9.5 &  0.033\deg &  0.032\deg &    3.9\deg & $    0.6 \pm     0.1$ & $   2.32 \pm    0.23$ \\
+
       \end{tabular}
-      \caption{The fit results for the known extended sources that
+      \caption{The fit results for the already known extended sources that
       were found by our analysis. The top results were found using an
@@
       All sources were fit using a uniform disk spatial template. The
-      localiztaion and extension were found using \pointlike while the TS
-      and spectral values were calculated using \gtlike.  The TS value was
-      computed using the assumed disk morphology. The Centaurus A Lobes,
-      the Cygnus Loop, and Vela X were not found to be extended by this
-      too. The reasons for this are discussed in~\ref{validate_known}.
+      localization and extension were found using \pointlike while the
+      TS and spectral values were calculated using \gtlike.  The TS value
+      was computed using the assumed disk morphology and \tsext compares
+      is the increase in \ts fitting the source with an extended spatial
+      model instead of a point model.  \glon and \glat are respectivly
+      the galactic longitute and galactic latitude of the source and
+      $\sigma$ is the edge of the uniform disk spatial model that was fit
+      to the source.  The Centaurus A Lobes, the Cygnus Loop, and Vela
+      X were not found to be extended by this too. The
+      reasons for this are discussed in section~\ref{validate_known}.
+      }
+      \label{known_extended_sources}
+    \end{centering}
+\end{sidewaystable}
+
+\clearpage
+
+\begin{sidewaystable}
+  \begin{centering}
+    \begin{tabular}{r|rrrrrrrrrr}
+      \hline
+      \hline
+      Name                 &          \glon &          \glat &                    $\sigma$ &       TS &   $\tsext$ &      Major &      Minor &    Pos Ang &      Flux ($10^{-9}$) &                 Index \\
+      \hline
+      \multicolumn{11}{c}{$E > 1\gev$} \\
+      \hline
+      P72Y2516             &     353.08\deg &      16.80\deg & $  0.41\deg \pm   0.05\deg$ &    139.2 &       28.9 &  0.042\deg &  0.036\deg &   54.4\deg & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ \\
+      P72Y2405             &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
+      P72Y1212             &     260.31\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &    314.6 &       49.2 &  0.026\deg &  0.023\deg &    5.0\deg & $    8.3 \pm     0.3$ & $   2.18 \pm    0.02$ \\
+      \hline
+      \multicolumn{11}{c}{$E > 10\gev$} \\
+      \hline
+      P72Y2473             &     331.74\deg &      -0.58\deg & $  0.52\deg \pm   0.04\deg$ &     75.3 &       45.2 &  0.071\deg &  0.049\deg &  -21.9\deg & $    1.3 \pm     0.2$ & $   1.75 \pm    0.25$ \\
+      P72Y2540             &     336.52\deg &       0.06\deg & $  0.65\deg \pm   0.03\deg$ &    173.0 &       95.3 &  0.041\deg &  0.037\deg &    5.3\deg & $    2.9 \pm     0.2$ & $   2.28 \pm    0.08$ \\
+      P72Y3281             &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
+      P72Y2979             &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
+      P72Y1287             &     266.29\deg &      -1.43\deg & $  1.15\deg \pm   0.08\deg$ &    119.6 &       90.9 &  0.080\deg &  0.065\deg &   54.6\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.18$ \\
+      \hline
+    \end{tabular}
+    \caption{This table presents the new extended soruce candidates found with
+    this search. 3 new extended sources were found searching above 1\gev and
+    5 new candidates were found looking above 10\gev.
+    The columns in this table have the same defintion as table~\ref{known_extended_sources}.}
+    \label{new_ext_srcs}
+  \end{centering}
+\end{sidewaystable}
+
+\clearpage
+\begin{sidewaystable}
+    \begin{centering}
+      \begin{tabular}{r|rr|rrrr|rrrr}
+        \hline
+        \hline
+        Name                 &     \tsinc &     \tsext &      $\glon_1$ &      $\glat_1$ & $\text{Flux}_1$ ($10^{-9}$) &   $\text{Index}_1$ &      $\glon_2$ &      $\glat_2$ & $\text{Flux}_1$ ($10^{-9}$) &  $\text{Index}_2$ \\
+        \hline
+        \multicolumn{11}{c}{$E > 1\gev$} \\
+        \hline
+        P72Y2516             &       23.8 &       28.9 &     353.04\deg &      16.96\deg & $       3.5 \pm        0.6$ & $  2.7 \pm   0.3$  &     353.14\deg &      16.50\deg & $       2.0 \pm        0.5$ & $  2.4 \pm   0.3$ \\
+        P72Y2405             &       48.6 &       77.6 &     328.31\deg &       0.31\deg & $      10.0 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.28\deg &      -0.06\deg & $       1.0 \pm        0.7$ & $  1.6 \pm   0.4$ \\
+        P72Y1212             &       22.2 &       49.2 &     260.59\deg &      -3.26\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
+        \hline
+        \multicolumn{11}{c}{$E > 10\gev$} \\
+        \hline
+        P72Y2473             &       34.3 &       45.2 &     331.77\deg &      -0.35\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.5$  &     331.51\deg &      -0.83\deg & $       0.4 \pm        0.1$ & $  2.1 \pm   0.5$ \\
+        P72Y2540             &       24.8 &       95.3 &     336.16\deg &       0.34\deg & $       0.7 \pm        0.1$ & $  2.0 \pm   0.4$  &     336.72\deg &      -0.06\deg & $       0.7 \pm        0.1$ & $  3.1 \pm   0.5$ \\
+        P72Y3281             &       34.5 &      151.7 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.45\deg &       2.54\deg & $       0.5 \pm        0.1$ & $  1.9 \pm   0.4$ \\
+        P72Y2979             &       15.4 &       20.6 &      25.06\deg &       0.24\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.6$  &      25.08\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.6$ \\
+        P72Y1287             &       32.5 &       90.9 &     267.16\deg &      -1.60\deg & $       0.2 \pm        0.1$ & $  1.9 \pm   0.4$  &     266.43\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.5$ \\
+        \hline
+      \end{tabular}
+      \label{dual_localization_results}
+      \caption{For the new extended source candidates in
+      figure~\ref{new_ext_srcs}, we describe the results
+      of the dual localization procedure described in
+      section~\ref{dual_localization_method}. Here, the extended
+      source candidate is not fit as an extended source but instead
+      fit as two point sources.  The dual localization is performed
+      with \pointlike and results in the best fit position of the two
+      sources $(\glon_1,\glat_1)$ and $(\glon_2,\glat_2)$.  The change in
+      likelihood and spectral values are then computed using \gtlike with
+      the best fit positions found by \pointlike.  \tsinc is the increase
+      in TS fitting the region as two sources compared to fitting compared
+      to fitting a single point source and is computed using \gtlike with
+      the best fit positions taken from \pointlike.  It can be directly
+      compared to \tsext, which is taken from table \ref{new_ext_srcs}.
+      For all of our candiates, $\tsext > \tsinc$ which shows that an
+      extended source fits the source better than two point sources.
+      As in table~\ref{known_extended_sources}, flux is measured in
+      units of $10^{-9}\ph/\cm^2/\s$ and is the integral flux between
+      1\gev (10\gev) and 100\gev for the sources found using events above 1\gev (10\gev).
       }
@@
   \clearpage
-
   \begin{sidewaystable}
     \begin{centering}
-      \begin{tabular}{rrrrrrrrrrr}
-        Name               &        GLON &        GLAT  &                $\sigma$ &       TS &   $\tsext$ &  Major &  Minor &    Ang &       Flux ($10^{-9}$) &      Index \\
-        \hline
-        \multicolumn{11}{l}{$E > 1\gev$} \\
-        \hline
-        1FGL J1628.6-2419c &   353.09\deg&    16.79\deg & $  0.40\deg\pm0.05\deg$ &    140.3 &       26.3 &  0.042 &  0.036 &   54.4 & $    6.3\pm0.6$ &$   2.50\pm0.14$ \\
-        1FGL J1554.0-5345c &   328.12\deg&     0.26\deg & $  0.49\deg\pm0.04\deg$ &    148.6 &       80.9 &  0.046 &  0.041 &   55.4 & $   16.3\pm1.5$ &$   2.31\pm0.11$ \\
-        1FGL J0823.3-4248  &   260.32\deg&    -3.28\deg & $  0.37\deg\pm0.03\deg$ &    306.1 &       47.8 &  0.026 &  0.023 &    4.4 & $    8.2\pm0.6$ &$   2.19\pm0.06$ \\
-        \hline
-        \multicolumn{11}{l}{$E > 10\gev$} \\
-        \hline
-        1FGL J1613.6-5100c &   331.74\deg&    -0.58\deg & $  0.52\deg\pm0.04\deg$ &     73.3 &       39.9 &  0.071 &  0.049 &  -21.7 & $    1.3\pm0.2$ &$   1.76\pm0.25$ \\
-        1FGL J1632.9-4802c &   336.52\deg&     0.05\deg & $  0.66\deg\pm0.03\deg$ &    175.1 &       92.9 &  0.040 &  0.037 &    6.2 & $    2.9\pm0.3$ &$   2.27\pm0.17$ \\
-        1FGL J2020.0+4049  &    78.32\deg&     2.21\deg & $  0.70\deg\pm0.04\deg$ &    245.4 &      141.0 &  0.048 &  0.039 &    4.4 & $    2.1\pm0.2$ &$   2.36\pm0.18$ \\
-        1FGL J1837.5-0659c &    25.04\deg&     0.26\deg & $  0.61\deg\pm0.04\deg$ &    115.4 &       50.4 &  0.064 &  0.051 &   19.7 & $    2.2\pm0.3$ &$   2.09\pm0.20$ \\
-        P72Y1287           &   266.41\deg&    -0.75\deg & $  1.41\deg\pm0.06\deg$ &    128.8 &       99.4 &  0.097 &  0.087 &   19.3 & $    1.7\pm0.2$ &$   1.96\pm0.20$ \\
-        \hline
-      \label{new_ext_srcs}
+      \begin{tabular}{r|rrrrrrrr}
+        \hline
+        \hline
+        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
+        \hline
+        \multicolumn{9}{c}{$E > 1\gev$} \\
+        \hline
+        P72Y2516             &                155.0 &                139.2 &                103.8 &                     38.5 &                   28.9 &                 22.5 & $  0.41\deg \pm   0.05\deg$ & $  0.38\deg \pm   0.04\deg$ \\
+        P72Y2405             &                108.4 &                148.8 &                138.4 &                     25.7 &                   77.6 &                 40.6 & $  0.49\deg \pm   0.04\deg$ & $  0.51\deg \pm   0.04\deg$ \\
+        P72Y1212             &                329.5 &                314.6 &                345.6 &                     60.4 &                   49.2 &                 51.5 & $  0.37\deg \pm   0.03\deg$ & $  0.38\deg \pm   0.03\deg$ \\
+        \hline
+        \multicolumn{9}{c}{$E > 10\gev$} \\
+        \hline
+        P72Y2473             &                 74.7 &                 75.3 &                 88.7 &                     43.7 &                   45.2 &                 50.0 & $  0.52\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
+        P72Y2540             &                173.9 &                173.0 &                157.7 &                     97.9 &                   95.3 &                 93.6 & $  0.65\deg \pm   0.03\deg$ & $  0.66\deg \pm   0.03\deg$ \\
+        P72Y3281             &                244.9 &                245.7 &                264.3 &                    152.8 &                  151.7 &                162.9 & $  0.71\deg \pm   0.04\deg$ & $  0.71\deg \pm   0.03\deg$ \\
+        P72Y2979             &                 43.4 &                 47.3 &                 39.0 &                     17.4 &                   20.6 &                 17.7 & $  0.35\deg \pm   0.07\deg$ & $  0.34\deg \pm   0.06\deg$ \\
+        P72Y1287             &                117.1 &                119.6 &                124.7 &                     86.1 &                   90.9 &                 95.0 & $  1.15\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
+        \hline
       \end{tabular}
-      \caption{New extended soruce candidates}
-    \end{centering}
-\end{sidewaystable}
-
-\clearpage
-\begin{sidewaystable}
-    \begin{centering}
-      \begin{tabular}{rrrrrrrrrrr}
-        Name               &        GLON &        GLAT  &                $\sigma$ &       TS &   $\tsext$ &  Major &  Minor &    Ang &       Flux ($10^{-9}$) &      Index \\
-        \hline
-        \multicolumn{11}{l}{$E > 1\gev$} \\
-        \hline
-        1FGL J1628.6-2419c &   353.09\deg&    16.79\deg & $  0.40\deg\pm0.05\deg$ &    140.3 &       26.3 &  0.042 &  0.036 &   54.4 & $    6.3\pm0.6$ &$   2.50\pm0.14$ \\
-        1FGL J1554.0-5345c &   328.12\deg&     0.26\deg & $  0.49\deg\pm0.04\deg$ &    148.6 &       80.9 &  0.046 &  0.041 &   55.4 & $   16.3\pm1.5$ &$   2.31\pm0.11$ \\
-        1FGL J0823.3-4248  &   260.32\deg&    -3.28\deg & $  0.37\deg\pm0.03\deg$ &    306.1 &       47.8 &  0.026 &  0.023 &    4.4 & $    8.2\pm0.6$ &$   2.19\pm0.06$ \\
-        \hline
-        \multicolumn{11}{l}{$E > 10\gev$} \\
-        \hline
-        1FGL J1613.6-5100c &   331.74\deg&    -0.58\deg & $  0.52\deg\pm0.04\deg$ &     73.3 &       39.9 &  0.071 &  0.049 &  -21.7 & $    1.3\pm0.2$ &$   1.76\pm0.25$ \\
-        1FGL J1632.9-4802c &   336.52\deg&     0.05\deg & $  0.66\deg\pm0.03\deg$ &    175.1 &       92.9 &  0.040 &  0.037 &    6.2 & $    2.9\pm0.3$ &$   2.27\pm0.17$ \\
-        1FGL J2020.0+4049  &    78.32\deg&     2.21\deg & $  0.70\deg\pm0.04\deg$ &    245.4 &      141.0 &  0.048 &  0.039 &    4.4 & $    2.1\pm0.2$ &$   2.36\pm0.18$ \\
-        1FGL J1837.5-0659c &    25.04\deg&     0.26\deg & $  0.61\deg\pm0.04\deg$ &    115.4 &       50.4 &  0.064 &  0.051 &   19.7 & $    2.2\pm0.3$ &$   2.09\pm0.20$ \\
-        P72Y1287           &   266.41\deg&    -0.75\deg & $  1.41\deg\pm0.06\deg$ &    128.8 &       99.4 &  0.097 &  0.087 &   19.3 & $    1.7\pm0.2$ &$   1.96\pm0.20$ \\
-        \hline
-      \label{new_ext_srcs}
-      \end{tabular}
-      \caption{New extended soruce candidates}
-    \end{centering}
-\end{sidewaystable}
-
-\clearpage
-\begin{sidewaystable}
-    \begin{centering}
-      \begin{tabular}{rrrrrrrrrr}
-        Name               & $\text{GLON}_1$ & $\text{GLAT}_1$ & $\text{GLON}_2$ & $\text{GLAT}_2$ & $\text{Flux}_1$ & $\text{Flux}_2$ & $\text{Index}_1$ & $\text{Index}_2$ & \tsinc \\
-        \hline
-        \multicolumn{6}{l}{$E > 1\gev$} \\
-        \hline
-        1FGL J1628.6-2419c &&&&& \\
-        1FGL J1554.0-5345c &&&&& \\
-        1FGL J0823.3-4248  &&&&& \\
-        \hline
-        \multicolumn{6}{l}{$E > 10\gev$} \\
-        \hline
-        1FGL J1613.6-5100c &&&&& \\
-        1FGL J1632.9-4802c &&&&& \\
-        1FGL J2020.0+4049  &&&&& \\
-        1FGL J1837.5-0659c &&&&& \\
-        P72Y1287           &&&&& \\
-        \hline
-      \label{new_ext_srcs}
-      \end{tabular}
-      \caption{Dual localization results for new extended sources.
-      \tsinc is the increase in TS compared to fitting a single point source. 
+      \label{alt_diff_model_results}
+      \caption{
+      This table shows a comparison of the \ts values gotten using \gtlike and \pointlike.
+      It also compares the fit values using the standard diffuse model and using the alternate
+      diffuse model described in section~\ref{alt_diff_model_description}.
+      $\ts_\pointlike$ is the \ts of the source fit with the extended hypothesis using \pointlike
+      whereas $\ts_\gtlike$ is the same quantity using the same model but fitting with \gtlike.
+      There is very good agreement between the two methods.
+%&        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
       }
@@
   which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
-    }
+  }\label{1FGL_J1628.6-2419c}
 \end{figure}
@@
   \caption{1FGL J1554.0-5345c. P72Y2405. Unidentified source likely diffuse emission.}
+  \label{1FGL_J1554.0-5345c}
 \end{figure}
@@
   would otherwise spill over into the top left of the image.
-    }
+  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  }\label{1FGL_J0823.3-4248}
 \end{figure}
@@
   Gamma Cygni. P72Y3281
-    }
+  }\label{Gamma_Cygni}
 \end{figure}
@@
   \caption{Vela Jr. P72Y1287. Using $E>10\gev$. Here, the image is
-      convovled with a $0.25\deg$ gaussian. }
+  convovled with a $0.25\deg$ gaussian.
+  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  }\label{Vela_Jr}
 \end{figure}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v2/source_1FGL_J1837.5-0659c.pdf
-    \caption{1FGL J1837.5-0659c. P72Y2974}
+  \caption{1FGL J1837.5-0659c. P72Y2974
+  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  }\label{1FGL_J1837.5-0659c}
 \end{figure}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
-    \caption{1FGL J1632.9-4802c. P72Y2540}
+  \caption{1FGL J1632.9-4802c. P72Y2540
+  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  }\label{1FGL_J1632.9-4802c}
 \end{figure}
@@
   \caption{
-    1FGL J1613.6-5100c . P72Y2473}
+  1FGL J1613.6-5100c . P72Y2473
+  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  }\label{1FGL_J1613.6-5100c}
 \end{figure}

### 2011-06-16 extended_catalog/paper/extended_catalog.tex
Improved bibliography

@@
 \usepackage{xspace}
+\usepackage{url}
 
@@
 We then calculate the Fermi LAT's sensitivity to spatially exnteded
-sources.
-We then apply this tool to test all sources in the 2FGL Two Year Catalog
-for extension.\cite{2FGL} We then report on the discovery of XXXXXXXXXXXXXX new
-extended sources.
+sources.  We then apply this tool to test all sources in the 2FGL Two
+Year Catalog for extension.\cite{2fgl} We then report on the discovery
+of XXXXXXXXXXXXXX new extended sources.
 \end{abstract}
@@
 In particular, the LAT has discovered a variety of spatially extended
-supernova remnants including IC443 and W51C (\cite{IC443,W51C}) and pulsar
-wind nebulae (\cite{MSH15-52,VelaX}). And there are other source classes
+supernova remnants including IC443 and W51C (\cite{ic443,w51c}) and pulsar
+wind nebulae (\cite{msh1552,velax}). And there are other source classes
 which could possibly be spatially resolved by the LAT including galaxy
@@
 
-In principle, the entire task can be done using the standard science
-tools package \gtlike\cite{Science-Tools-gtlike}. But \gtlike is
+In principle, the entire task can be done using the 
+official maximum likelihood tool \gtlike which is 
+distributed publically by the Fermi Science Support Center\cite{fssc}. 
+But \gtlike is
 only able to fit the spectral parameters of the source, so the extension
@@
 analyzing spatially extended sources. \pointlike is most thoroughly
-described in Matthew Kerr's Ph.D Thesis\cite{matthew_kerr_phd_thesis}
-but the important aspects will be summarized below. What differentiates
+described in Matthew Kerr's Ph.D Thesis but the important aspects will
+be summarized below (\cite{matthew_kerr_thesis}) . What differentiates
 \pointlike most significantly from \gtlike is its emphasis
@@
 \gtlike, \pointlike relies on the {\em healpix} representation of spatial
-bins\cite{healpix_paper} and scales the size of each spatial bin to be
+bins\cite{healpix} and scales the size of each spatial bin to be
 smaller than the PSF. This is convenient because it no
@@
 the other fit parmaeters.  \minuit provides the {\em Simplex} function to
-calculate errors this way.\cite{minuit documentation and UP parameter}
+calculate errors this way (\cite{minuit_documentation}).
 The second method involves estimating the likelihood function as being
@@
 code is used to calculate the localization error of all point sources
-in the catalog\cite{2FGL paper}. It works by fitting an ellipse to the
+kn the catalog\cite{2fgl}. It works by fitting an ellipse to the
 likelihood surface near the maximum and using this fit ellipse to estimate
@@
 maximum likelihood technique.  They were comparing the hypothesis of a
-source to the hypothesis of just a background\cite{Mattox_et_All_Paper}.
+source to the hypothesis of just a background\cite{mattox_egret}.
 Their argument for why this null hypothesis distribution was reasonable
@@
 
-Fermi LAT data was simulated using the publically avaliabable Science
-Tools package \gtobssim\cite{GTOBSSIM_CITATION}. The sources were
-simulated with a powerlaw spectral model with 6 Were given 6 $>100\mev$
-fluxes ranging from $3\times 10^{-9} \ph/\cm^2/s$ to 
-$10^{-6} \ph/\cm^2/s$.
-The sources were then simulated with spectral index ($\gamma$) values of
-1.5, 2, 2.5, and 3.  These values were picked to probe a representative
-range measurable values.  For particular spectral indices, only the
-fluxes which would create a statistically significant source detection
-($\ts>25$) where selected, since we are only interested in
-testing for extension sources with a significant extent. The sources were
-simulated on top of an isotropic powerlaw background with a Sreekumar-like
-spectrum ($>100\mev$ flux of 1.5e-5 and spectral index 2.1).\cite{Sreekumar
-et al. ApJ 494 pag 523 1998}
+Fermi LAT data was simulated using program \gtobssim which is
+distributed publically by the Fermi Science Support Center
+(\cite{fssc}).  The sources were simulated with a powerlaw spectral
+model with 6 Were given 6 $>100\mev$ fluxes ranging from $3\times 10^{-9}
+\ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.  The sources were then simulated
+with spectral index ($\gamma$) values of 1.5, 2, 2.5, and 3.  These
+values were picked to probe a representative range measurable values.
+For particular spectral indices, only the fluxes which would create a
+statistically significant source detection ($\ts>25$) where selected,
+since we are only interested in testing for extension sources with a
+significant extent. The sources were simulated on top of an isotropic
+powerlaw background with a Sreekumar-like spectrum ($>100\mev$ flux
+of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).
 
@@
 disk morphology on top of a powerlaw Sreekumar-like isotropic
-spectrum.\cite{Sreekumar et al. ApJ 494 pag 523 1998}.  The monte carlo
+spectrum (\cite{sreekumar_isotropic}).  The monte carlo
 simulation was perforormed over a one year time interval using a default
@@
 statistically significant sources that are detected in the $\gev$
-sky\cite{2FGL_catalog}.  The catalog group's source finding method assumes
+sky\cite{2fgl}.  The catalog group's source finding method assumes
 that the emission originated as point sources and what was presented was
@@
 of using only events above $10\gev$ was succesfully used to detecting
-HESS J1825-137 with the Fermi LAT~\cite{HESS J1825 paper}.
+HESS J1825-137 with the Fermi LAT~\cite{fermi_hess_j1825}.
 
@@
 this emission is notoriously difficult. This issue has been discussed
-in the Fermi catalog~\ref{1FGL,2FGL}. Furthermore, the galactic plane
+in the Fermi catalog~\ref{first_cat,2fgl}. Furthermore, the galactic plane
 is very crowded and there is a degeneracy between an extended source
@@
 % is going on.
+Example Bad fit~\ref{example_bad_fit}
 
@@
 Using events above $10\gev$, we were able to succesffuly fit the extesion
-of HESS J1825-137\cite{HESS 1825 paper}. Our analysis of MSH 15-52 using
+of HESS J1825-137\cite{fermi_hess_j1825}. Our analysis of MSH 15-52 using
 events above $10\gev$ found an extension consistent with the publisehed
-result, but with $\tsext=11.2$.\cite{MSH 15-52 Paper}. This
+result, but with $\tsext=11.2$.\cite{msh1552}. This
 is most likely because the published analysis used events above $6\gev$.
@@
 spatially resolved AGN and there are theories that predict
-this\cite{pair_halo_paper, http://adsabs.harvard.edu/doi/10.1086/187222}.
+this\cite{pair_halo_paper}.
 
@@
 only AGN associated with the 1FGL source, and if there are no flags
-on the source which shed doubt on the source\cite{1FGL}. These last two
+on the source which shed doubt on the source\cite{first_cat}. These last two
 conditions are especially important for our analysis. One might expect
@@
     The sensitivity is for a one year simulation against a Sreekumar-like
-    isotropic background\cite{Sreekumar et al. ApJ 494 pag 523 1998}.
+    isotropic background (\cite{sreekumar_isotropic}).
     This plot shows that our sensitivity is best for sources that are
@@
 
-% XXXXXXXXXXXXXXXXXXXXXXX
-% example bad fit
-% P72Y3047
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{source_plots/example_bad_fit.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v2
+    \caption{Example bad Fit: P72Y3047}
+    \label{example_bad_fit}
+  \end{center}
+\end{figure}
 
@@
   P72Y2516.
-  Note that unlike other plots, that this plot has the nearby sources subtracted.
-  This was done to remove the very bright, $\ts=460$, source P72Y2510 % XXXXXXXXXXXXXXXXXXXX what is this source
-  which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %Note that unlike other plots, that this plot has the nearby sources subtracted.
+  %This was done to remove the very bright, $\ts=460$, source P72Y2510 % XXXXXXXXXXXXXXXXXXXX what is this source
+  %which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   }\label{1FGL_J1628.6-2419c}
@@
   P72Y1212.
-  Note that unlike most other plots, this plot has the nearby sources subtracted.
-  This was done to remove the very bright source Vela which,
-  at position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
-  would otherwise spill over into the top left of the image.
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %Note that unlike most other plots, this plot has the nearby sources subtracted.
+  %This was done to remove the very bright source Vela which,
+  %at position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
+  %would otherwise spill over into the top left of the image.
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour

### 2011-06-22 extended_catalog/paper/extended_catalog.tex
Imporved draft + plots

@@
 %   Add contours to images.
+%   What other citations to add?
 
@@
 sources.  We then apply this tool to test all sources in the 2FGL Two
-Year Catalog for extension.\cite{2fgl} We then report on the discovery
+Year Catalog for extension.\cite{second_cat} We then report on the discovery
 of XXXXXXXXXXXXXX new extended sources.
@@
 The Large Area Telescope (LAT) is a pair conversion telescope on the
-Fermi Gamma-Ray Space Telescope. It has been surveying the Gamma-ray
+Fermi Gamma-Ray Space Telescope. It has been surveying the $\gamma$-ray
 sky since June 2008.  Fermi is particularly well suited as a survey
-instrument because of its to survey the broad energy coverage ($20\mev$
-to $>300\gev$), a wide field of view ($\sim 2.4 \sr$) and large effective
-area ($\sim 8000 \cm^2$ at $>1\gev$).
+instrument because of its to survey the broad energy coverage (20 \mev
+to >300 \gev), a wide field of view ($\sim 2.4 \sr$) and large effective
+area ($\sim 8000 \cm^2$ at $>1 \gev$).
 
@@
 associated with. Finding a matching morphology can uniquly identify the
-source emitting the Gamma-rays.
-
-Because of the largely varying PSF of the LAT, the
-spatial and spectral model of a source do not nicely decouple and
-spatially resolving a Fermi source is also important for obtaining an
-unbiased spectral model of the source.  Furthermore, using this extension
-information is important for improved the overall model of the sky which
-is important for obtaining a better fit of nearby sources and removing
-spurious point sources which we might otherwise think we detect.
-
-Nevertheless, morphological studies of sources in the $\gev$ energy range using
-the Fermi LAT is challenging because of the significantly energy
-dependent PSF and because of systematic errors in the
-galactic diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXX\deg$
-at $100\mev$ to $XXXXXXXXXXXXXXXX\deg$ at $100\gev$ so the higher energy photons 
-are significantly more important for resolving a source. On the other hand, 
-we tend to run out of photons at higher energies so a detailed statistical 
-test must be used to maximize our sensitivity.
+source emitting the $\gamma$-rays.
+
+Because of the largely varying PSF of the LAT, the spatial and spectral
+model of a source do not nicely decouple and spatially resolving a Fermi
+source is also important for obtaining an unbiased spectral model of
+the source.  Furthermore, using this extension information is important
+for improved the overall model of the sky which is important for obtaining
+a better fit of nearby sources and removing spurious point sources which
+we might otherwise think we detect.
+
+Nevertheless, morphological studies of sources in the $\gev$ energy
+range using the Fermi LAT is challenging because of the significantly
+energy dependent PSF and because of systematic errors in the galactic
+diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXX\deg$
+at 100 \mev to $XXXXXXXXXXXXXXXX\deg$ at $100 \gev$ so the higher energy
+photons are significantly more important for resolving a source. On
+the other hand, we tend to run out of photons at higher energies so a
+detailed statistical test must be used to maximize our sensitivity.
 
 \section{Analysis Method}
-
-%   * Difficulty of studying spatially extended sources
-%   * Pointlike, great features
-%   * modifying it to fit spatially extended sources.
-%      * semi-analytic convolution formula
-%   * importance of fitting position + extension + spectrum simultaneously to apply statistical significance
-%   * Monte Carlo Validation
-%
 
@@
 galactic diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXXX\deg$
-at $100\mev$ to $XXXXXXXXXXXXXXXX\deg$ at $100\gev$ and so the higher energy photons are
+at 100 \mev to $XXXXXXXXXXXXXXXX\deg$ at $100 \gev$ and so the higher energy photons are
 significantly more important for studying the shape of sources. One could
 ideally look at just the highest energy photons, but the trade off is that
-for typical sources many more source events are expected at low energy.
+for typical sources many more source photons are expected at low energy.
 For this reason, it is especially important to use as much of the data
@@
 
-\pointlike additionaly bins the Fermi Gamma-rays by their conversion
+\pointlike additionaly bins the Fermi $\gamma$-rays by their conversion
 type, which corresponds to whether the photon converted in the front or
 back part of the detector. Since the PSF is smaller for front entering
-events, one would expect binning each conversion type independently to
+photons, one would expect binning each conversion type independently to
 improve our sensitivity.
@@
 code is used to calculate the localization error of all point sources
-kn the catalog\cite{2fgl}. It works by fitting an ellipse to the
+kn the catalog\cite{second_cat}. It works by fitting an ellipse to the
 likelihood surface near the maximum and using this fit ellipse to estimate
@@
 % Make an extension profile plot.
-% show it in figures an ddescirbeit.
+% show it in figures and describe it.
 
@@
 Although these shapes look significantly different from eachother, the
-convolution of these spatial models of typtical sizes 
-with the PSF will produce PDFs that are very similar.
+convolution of these spatial models of typtical sizes with the PSF will
+produce PDFs that are very similar.
 
 This is demonstrated in figure~\ref{compare_disk_gauss}.  The plot shows
-(in black) the PSF that would be observed for a source of spectral index
-2. The dashed red (blue) line shows the probabability density function
-for a Gaussian (uniform disk) of width $0.5\deg$.  The solid red (blue)
-line shows the probability density function for the same Gaussian (uniform
-disk) convolved with the PSF of an index 2 source.  
+(in black) the PSF that would be observed for a source of spectral
+index 2. The dashed red (blue) line shows the probabability density
+function for a Gaussian (uniform disk) of width $0.5\deg$.  The solid
+red (blue) line shows the probability density function for the same
+Gaussian (uniform disk) convolved with the PSF of an index 2 source.
 figure~\ref{compare_disk_gauss} shows the analysis using an energy range
-of 1\gev to 100\gev whereas the right plot shows an analysis using an
-energy range from 10\gev to 100\gev.
+betewen 1 \gev and 100 \gev whereas the right plot shows an analysis using an
+energy range from 10 \gev to 100 \gev.
 
@@
 a spatial model that is a uniform disk of extension 0.5\deg,
-integral flux between 1\gev and 100\gev of $3e-8\ph/\cm^2/s$,
+integral flux between 1 \gev and 100 \gev of $3e-8\ph/\cm^2/s$,
 and a spectral index of 2.
@@
 \section{LAT Extended Source Validation}
+
+We validated \pointlike for extended source
+analysis using a series of Monte Carlo studies.
 
@@
 
-The half $\chi^2_1$ distribution was found by a monte carlo study
+The half $\chi^2_1$ distribution was found by a Monte Carlo study
 to hold for the special case of source finding of EGRET sources using the
@@
 
-We performed a dedicated monte carlo study to validate \pointlike for
+We performed a dedicated Monte Carlo study to validate \pointlike for
 studying spatially extended sources and also to demonstrate that we can
 use $\tsext$ as a test of the statistical significance
-of a source's extension.  The monte carlo study involved simulating point
+of a source's extension.  The Monte Carlo study involved simulating point
 sources of varying spectral models on top of a simulated background. The
@@
 (\cite{fssc}).  The sources were simulated with a powerlaw spectral
-model with 6 Were given 6 $>100\mev$ fluxes ranging from $3\times 10^{-9}
+model with 6 Were given 6 $>100$ \mev fluxes ranging from $3\times 10^{-9}
 \ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.  The sources were then simulated
@@
 significant extent. The sources were simulated on top of an isotropic
-powerlaw background with a Sreekumar-like spectrum ($>100\mev$ flux
+powerlaw background with a Sreekumar-like spectrum ($>100$ \mev flux
 of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).
 
-The monte carlo simulation was perforormed over a one year time interval using
+The Monte Carlo simulation was perforormed over a one year time interval using
 a default rocking profile and an assumed a represntative
 livetime fraction of 0.8.
-The reconstruction was perfromed with events from an energy range of
-$1\gev$ to $100\gev$ using 4 energy bins per decade and using the Pass 7 Version 6
+The reconstruction was performed with photons from an energy range of
+1 \gev to 100 \gev using 4 energy bins per decade and using the Pass 7 Version 6
 source instrument response function (IRFs) to be consistent with the following analysis.
@@
 
-The results of the monte carlo simulation are shown in
+The results of the Monte Carlo simulation are shown in
 figure~\ref{ts_ext_mc}.  The cumulative density function (CDF) is plotted
@@
 
-We performed another monte carlo study to determine the Fermi LAT's
+We performed another Monte Carlo study to determine the Fermi LAT's
 sensitivity to spatially extended sources. The sensitivity to extension
@@
 disk morphology on top of a powerlaw Sreekumar-like isotropic
-spectrum (\cite{sreekumar_isotropic}).  The monte carlo
+spectrum (\cite{sreekumar_isotropic}).  The Monte Carlo
 simulation was perforormed over a one year time interval using a default
@@
 and spatial model.
-By fitting a line to the flux vs $\tsext$ data, we were able to
+By fitting a line to the flux vs $\tsext$, we were able to
 estimage the flux at which $\tsext=25$.
@@
 2, 2.5, and 3 and for sources of 20 extensions varying from $0.1\deg$
-to $2.0\deg$. The $y$ axis is the $100\mev$ to $100\gev$ flux of the
-source and the $x$ axis is the monte carlo extension. The curves then
+to $2.0\deg$. The $y$ axis is the 100 \mev to 100 \gev flux of the
+source and the $x$ axis is the Monte Carlo extension. The curves then
 represent the division in this extension and flux space where one gets
@@
 The solid lines of the plot are the sensitivity computed when using
-with all events from $100\mev$ to $100\gev$. The dashed lines is the
-same sensitivity but only using events from from $1\gev$ to $100\gev$.
+with all photons with energry between 100 \mev and 100 \gev. The dashed lines is the
+same sensitivity but only using photons with energy from 1 \gev to 100 \gev.
 
@@
 significantly better for harder sources where there are more high
-energy events. Furthermore, our sensitivity is best for sources with an
+energy photons. Furthermore, our sensitivity is best for sources with an
 extension around $0.5\deg$.  our sensitivity gets significantly worse
@@
 Futheremore, we note that except for the hardest or largest sources,
-our sensitivity is almost entirly whether or not we use events from
-$100\mev$ to $1\gev$. On the other hand, other systematic errors become
+our sensitivity is almost entirly whether or not we use photons 
+with energy from
+100 \mev to 1 \gev. On the other hand, other systematic errors become
 increasingly important at low energy so for our extension search we will
-not use the events in this energy range.
+not use the photons in this energy range.
 
@@
 shown in figure~\ref{diff_factor_sensitivity}. Two plots are presented,
-one fitting only in the energy range between $1\gev$ and $100\gev$ and
-one fitting only in the energy range between $10\gev$ and $100\gev$. For
+one fitting only in the energy range between 1 \gev and 100 \gev and
+one fitting only in the energy range between 10 \gev and 100 \gev. For
 each plot, the $y$ axis quotes the flux in the fit energy range and the
@@
 The LAT two year catalog presented a search for all
-statistically significant sources that are detected in the $\gev$
-sky\cite{2fgl}.  The catalog group's source finding method assumes
+statistically significant sources that are detected in the \gev
+sky\cite{second_cat}.  The catalog group's source finding method assumes
 that the emission originated as point sources and what was presented was
@@
 
-As was shown, we gain very little in sensitivity using events with energy
-below $1\gev$. On the other hand, the large PSF at low energy makes us
+As was shown, we gain very little in sensitivity using photons with energy
+below 1 \gev. On the other hand, the large PSF at low energy makes us
 more succeptable to systmetic errors arising from source confusion due
@@
 galactic diffuse emission.  For that reason, we performed our search
-using events only between $1\gev$ and $100\gev$.
-
-We also performed a search for extended sources using events only between
-10\gev and 100\gev. Even though we are testing the same sources, this
+using photons only between 1 \gev and 100 \gev.
+
+We also performed a search for extended sources using photons only between
+10 \gev and 100 \gev. Even though we are testing the same sources, this
 approach is complimentary because there are regions in the galactic
@@
 galactic plane looking for possible extended sources near pulsars which
-are very bright at lower energy but cutoff before 10\gev.  This approach
-of using only events above $10\gev$ was succesfully used to detecting
+are very bright at lower energy but cutoff before 10 \gev.  This approach
+of using only photons with energy above 10 \gev was succesfully used to detecting
 HESS J1825-137 with the Fermi LAT~\cite{fermi_hess_j1825}.
+
+For each catalog source, we modified the spectral index of the source
+to be a powerlaw. We did this for two reasons. The first is that for a
+source to be significantly extended, we would expect it to be reasonably
+hard and therefore be fit reasonably well by a powerlaw.  The seond reason
+is that since we begin our analysis at either 1 \gev or 10 \gev, we didn't
+expect there to be significant curvature over this smaller energy range.
+This method has the advantange that for the following analysis, we can
+simply quote the fit powerlaw spectral index.
+
+Finally, when analyzing our region, we automatically removed all other
+catalog sources which were within 0.5\deg. This was done because of
+a concern that truly extended sources might end up in the catalog as
+multiple point sources. These spurious nearby catalogs sources might then
+distort our fit enough that it no longer would show up as being extended.
+Nevertheless, we investiated for each of our extended candidates if
+if we seemed to be legitimatly removing real backgorund sources. And
+we employed a dual localiation procedure (described above) to test
+all of our candidates for source confusion.
 
@@
 symmetric disk spatial shape and used \pointlike to simultaneously fit
-the position and extension of the source.  We then selected the sources
-for which \pointlike found $\tsext>16$ and refit their spectral parameters
-using \gtlike.
-
-% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-% NOTE ABOUT PRUNE aridus
+the position and extension of the source.  We then selected all of the
+sources for which \pointlike found $\tsext>16$.
 
@@
 
-We expect most extended sources to be galactic sources since extragalactic
-sources are typically too far away to be resolvable. Unfortunately,
-the \gev emission in the galactic plane is dominated by anisotropic
-galactic diffuse emission.  Modeling the galactic diffuse emission is
-very difficult~\ref{first_diffuse_paper}  and finding sources on top of
-this emission is notoriously difficult. This issue has been discussed
-in the Fermi catalog~\ref{first_cat,2fgl}. Furthermore, the galactic plane
-is very crowded and there is a degeneracy between an extended source
-and multiple point sources. So it is often difficult to ensure you have
-a good model for the region around a source .  Finding a source with
-$\tsext>16$ is not sufficient for detecting an extended and we had to
-perform many crosschecks to make sure we had a good fit to our region.
-
-% XXXXXXXXXXXXXXXXXXXXX
-% LIST OF All extended source candidates and how many of them are clearly bad.
-% best we can do is sort through them.
-
-% XXXXXXXXXXXXXXXXXXXXXXXXXXX
-% Put example of poorly fit region and how it is difficult to know what
-% is going on.
-Example Bad fit~\ref{example_bad_fit}
-
-For each of the extended source candidates where $\tsext>16$,
-we performed several additional analyses to determine whether
-our model for the region was believable and that we could therefore
-find out source to be extended.
-We did so for all sources found either at events above 1\gev or above 10\gev
+We expect most extended sources to be inside teh galactic plane
+since extragalactic sources are typically too far away to be
+resolvable. Unfortunately, the \gev emission in the galactic plane
+is dominated by anisotropic galactic diffuse emission.  Modeling the
+galactic diffuse emission and finding sources on top of this emission is
+difficult~\ref{first_diffuse_paper}. This issue has been discussed in the
+Fermi catalog~\ref{first_cat,second_cat}. Furthermore, the galactic plane is
+very crowded and so it is offent difficult to get a good model for the
+region around a catalog source.  Because of this, finding a source with
+$\tsext>16$ is not a sufficient test and we perform several crosschecks
+to ensure our overal region is well modeled.
+
+As an example of why this issue, we describe our test of P72Y3047 for
+extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
+using photons with energy above 1 \gev. In the map, the galacitc and isotropic diffuse
+emission subtracted.  A two year catalog source P72Y3047 was found at the
+position $(l,b)=(37.79\deg,1.14\deg)$.  By looking at the smoothed map,
+we see that there appears to be overall some large scale residaul in the
+diffuse emission along the galactic plane. Furthermore, it appears that
+we don't have a great model of the nearby catalog sources. As a result,
+P72Y3047 fits to a very large extension of 1.37\deg and the result is
+statistically significant with \tsext=51.6.  By looking at the residuals,
+it is clear that this complicated region is not well fit even though
+the source's extension is statistically significant. For this reason,
+we have to perform a series of followup analysis for all of the soruces
+that are found with \tsext=16.
+% information came from
+% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
 
@@
 and performed a crosscheck by refitting the spectral parameters using
-\gtlike.
-We used a square ROI $14.1\deg$ in diamater with $1/16\deg$ pixels
-and the same energy binning.
-% XXXXXXXXXXXXXX put note about how this binning was necessary for morphological analysis and how any smaller is no good.
-% using gtlike. But how pointlike handles this automatically
-The \gtlike analysis provided a second estimate of the spectral
-parameters of the extended source as well as a second calculation of
-$\ts_\text{disk}$, $\ts_\text{point}$, and 
-$\tsext$. We only looked for extended sources which 
-both \pointlike and \gtlike considered significantly extended.
-
-% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-% Note about how it is helfpul to look at high energy
-% to avoid source confusion and even though a source
-% might show up above 1GeV, it might be hard to realize
-% wheter it is source confusion/diffuse emission, etc.
-% but at high energy, less diffuse emission + better PSF
-% = easier to find extended sources.
-
-% Also note about how softer other sources nearby 
-% might go away at higher energy
-
-% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-% NOTE about pointlike TS_ext generally being larger then
-% gtlike TS_ext and why this may be (binning front/back evnets
-% seperatly, using too large an energy bin, etc).
-% 
-% This is no longer true with better binning 1/16 instead of 1/8 degree binning.
-
-Additionaly, we generated for each 
-extended source candidate residual test statistic maps. 
-The residual TS Map
-
-Large
-TS values in test
-
-% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-% Note about dual localization
-
-We generated a residual test statistic maps to look for
-, which is a map of the test
-statistic adding new points
-Figure~\ref{res_tsmaps} shows an example residual TS map.
-
-% XXXXXXXXXXXXXXX add now about using powerlaw models for our source +
-% setting e0 in geometric range of energy bin.
-
-% XXXXXXXXXXXXXXXXXXXXX
-% Discussion of how 
-% counts slices are best for
-% looking at overall diffuse emission.
-
-% XXXXXXXXXXXXXX discussion of complicated regions having to simulatenously refit
-% backgorund sources. Relocalizing sources.
-% bg sources are obtained by catalog w/ > 100MeV analysis may
-% not be idea for >1GeV & >10GeV analysis. Also, may require moving b/c
-% extension will effect their extension.
+\gtlike.  We used a square ROI $14.1\deg$ in diamater with $1/16\deg$
+pixels and the same energy binning. We found that $1/16\deg$ bins were
+fine enough for \gtlike to get an extension significances consistent
+with \pointlike.  Using \gtlike, we found a second measure of \tsext and
+we only considered a source to be significanlty extended if \pointlike
+and \gtlike both agreed.  For the new extended source candidates, with
+table~\ref{alt_diff_model_results} shows a comparison of their the value
+of \tsext found by \gtlike and \pointlike.  Everywhere else, the values
+from \gtlike are used.
+
+Additionaly, we generated for each extended source candidate residual
+test statistic (\ts) maps.  The residual \ts map is a map of the \ts
+value evalualted at each point by adding onto the map at that position
+a new source of spectral index 2 and finding the increase in lieklihood
+when fitting its flux. \ts maps are especially useful as looking for
+new sources or other residual featuers that are not included in the
+model. They also have the advantagous feature that the aboslute scale
+can be used to clearly look for when the residual is signifciant.
+The downside is they are biased to look for residual features
+that look like the PSF and so are not as sensitive to diffuse residual
+features. Furthermore, since by defintion \ts>0, \ts maps can only show
+positive fluctuations. Nevertheless, \ts maps were useful for
+assessing the overal quality of the fit. Figure~\ref{res_tsmap}
+shows an exmaple residual \ts map for the extended source IC443.
+
+For each candidate, we also generated counts slices. A counts slice
+plots the sum of all counts in the longitudinal direction within 2\deg in
+the latitudinal direction.  The same plot is also shown integrating in
+the longitudinal direction.  On top of the plot is overlayed the model
+predicted counts assuming the source has a disk spatial model, assuming
+the source is a point source, and fitting just the diffuse emission in
+the region.  An example counts slice is shows for the extended source
+IC443 in figure~\ref{counts_slice}. Counts slices were especially useful
+for looking at how well the overal diffuse emisison model fits the region
+near the sources.
+
+For each candidate, we also made was a radial integral of the data. This
+plot shows the sum of all counts within a given distance from the
+source's center. The plot is binned uniformly in $\Delta \theta^2$ so
+that an isotropic background will be flat in the plot. On top of this
+plot is overlayed the model predicted counts assuming the source has a
+disk spatial model, assumgng the source is a point source, and fitting
+just the diffuse emisison in the region. An example radial integral
+is shown for the extended source IC443 in figure~\ref{radial_profile}.
+This plot is best for comparing the observed counts to the PSF.
+
+Finally, for each source, we performed the dual localization method
+described in section~\ref{dual_localization_method}.  We 
+did so by replacing the source with two sources each containing
+half of the original flux and then using \pointlike to
+simulatnoulsy fit the postion and spectrum of these sources.
+We then used \gtlike to refit the spectrum of these
+sources using the best fit positions. For the
+new extended sources found, we summarize the results of
+this dual localization test and compare the values of \tsext
+to \tsinc in table~\ref{dual_localization_results}.
+
+for sources that seemed promising, we performed in a case
+by case basis a refit of the region where we would move or delete
+background catalog sources until it was clear that we had obtained on
+a case by case a good overal fit of the region. This was necessary in
+many situations whrere the position of background sources in the catalog
+was not consistent and when the offet of the background sources biased
+the fit extension of our source. This was likey the case because the
+catalog positions of the backgorund sources came usign all photons above
+100 \mev and the low energy localization disagreed with the higher energy
+localization we found. This also happened in certain situations because
+the localization of a backgorund source dependend upon correctly modeling
+the extended source as being extended and so once we fit our source for
+extension, we had to relcoalizae the backgorund source.  For each source,
+we descirbe in a case by case basis any modifications which were required
+to obtain a good fit of our source and the surrounding region.
 
@@
 We validated our method by testing for extension all of the sources
-which the Fermi Collaboration had previously published on.  We applied
-no special method to test these sources but used the same pipeline which
-was used to test all other catalog sources.  The results are published
-in table~\ref{known_extended_sources}.  Using events with energies
-greater than $1\gev$, our analysis succesfully fit the extension of the
-the two galaxies the Large Magalengic Cloud and the Small Magalenic
-Cloud.~\cite{SMC & LMC Paper}.  Our tool also successfully detected the
-extension of the supernova remenants IC443, W28, W30, W44, and W51C.
-
-Using events above $10\gev$, we were able to succesffuly fit the extesion
-of HESS J1825-137\cite{fermi_hess_j1825}. Our analysis of MSH 15-52 using
-events above $10\gev$ found an extension consistent with the publisehed
-result, but with $\tsext=11.2$.\cite{msh1552}. This
-is most likely because the published analysis used events above $6\gev$.
+which the Fermi Collaboration had previously published on.  
+This list includes the extended sources where were modeled
+in the 2FGL catalog\cite{second_cat}.
+This list contains the Large Magelenic Cloud and the Small Magilenic Cloud
+which were first published in \cite{LMC,SMC}.
+We also included the Supernova rememants IC443, W28, W30,
+W44, W51C, and the Cygnus Loop which were 
+first published in \cite{ic443,w28,w30,w44,w51c,cygnus_loop}.
+We include the Pulsar Wind Nebulae Vela X, MSH 15-52, and 
+HESS J1825-137\cite{velax,msh1552,fermi_hess_j1825}.
+In addition to those sources included by the catalog, we include in
+this list the supernova rememnat RX J1713.7-3946 which was recently
+published (\cite{RXJ1713}).
+
+Since these sources are all included in the 2 year catalog,
+we applied no special method to test these sources but used the same
+pipeline that tested all other catalog sources for extension.  The results
+are summarized in table~\ref{known_extended_sources}.  
+%XXXXXXXXXXXXX DISCUSSION OF WHAT IS IN THE ABLE
+Using photons with
+energies greater than 1 \gev, our analysis succesfully fit the extension
+of the LMC, SMC, IC443, W28, W30, W44, and W51C.  Using photons with 
+energy above 10
+\gev, we were able to succesffuly fit the extesion of HESS J1825-137.
+
+Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
+consistent with the publisehed result, but with $\tsext=11.2$. This is
+most likely because the published analysis used a larger energy range,
+considering all evnets above 6\gev. Looking at all photons with
+energy above 1\gev 
+is problematic because of background source confusion whereas using photons
+with energy above 10\gev does not have the statistics for a significant dection.
 
@@
 successfully analyzed after applying a phase cut to removed the heavily
-dominant emission from the pular.
+dominant pular emission. It is beyond the scope of the paper to perform
+such specialized analysis.
 
@@
 The difficulty our analysis analysis had fitting the extension of several
-of the already published extended sources should be used to emphasize
-the difficultly with which
+of the already published extended sources should be used to emphasize the
+overal difficultly in studying spatially extendee sources with the Fermi
+LAT, especially in the crowded galactic plane. For particular sources,
+it is often necessary to perform careful and specalized analysis to
+correctly find and model the sources we see. We can not claim our method
+is very complete, only that it is systematic and statistically rigorous.
 
@@
 a worse agreement with the theoretical distribution then was found
-by our monte carlo study in figure~\ref{ts_ext_mc}.  But overall, the
+by our Monte Carlo study in figure~\ref{ts_ext_mc}.  But overall, the
 distribution is good. No AGN get fit with a particularly significant
@@
 model might effect the value of \tsext. Nevertheless, since we use only
-events with $E>1\gev$, this would effect is not expected to be large.
+photons with energy above 1 \gev, this would effect is not expected to be large.
 Another possible source for the discrepancy is that pointlike performs a
@@
 energy and furthermore if this was a signifciant effect the same results
-would have showed up with the monte carlo simultions which included the
+would have showed up with the Monte Carlo simultions which included the
 effects of energy dispersion.
@@
 
-\begin{itemize}
-  \item Results summarized in table~\ref{new_ext_srcs}.
-  \item Add extra stuff to this section, $\tsinc$.
-  \item Disribe what had to be done to modify regionregion.
-    What sources had to be deleted (or moved).
-%  \item XXXXXXXXXXXXXXXXXXXXXXXXXX Say that errors are just statistical (or have a descritpion of errors).
-
-\end{itemize}
+For all extended sources, the results of our fit are summarized in
+table~\ref{new_ext_srcs}. The table includes the best fit position
+and extension of the source. It also includes the source's significance
+and significance of extension.
 
@@
 
-The two year catalog source P72Y2516 was found at ($l,b)=(353.09\deg, 16.79\deg)$
-with a best fit extension of $0.40\pm0.05$ and an extension significance of
-$\tsext=26.3$.
-
-In the ophiucus region=most likely a molecular cloud
+A catalog source P72Y2516 located at $(l,b)=(353.09\deg, 16.79\deg)$
+was found to be significantly extended when using photons between
+1 \gev and 100 \gev.  The best fit extension was
+$0.41\deg\pm0.05\deg$ and the extension significance was $\tsext=28.9$.
+A smoothed counts map showing this source is seen in figure
+\ref{1FGL_J1628.6-2419c}.
+
+This source is in a region of remarkably complicated diffuse emission.
+Even though it is 16\deg from the Galactic plane,
+the source is right on top of the core of the Ophiuchus molecular cloud,
+which contains massive star-forming regions that are very bright
+in the infrared.  The region has abundant molecular and atomic gas
+traced by CO and HI but also plenty of dark gas, the kind that
+we find only by its association with dust emission.
+% XXXXXXXXXXXXXXXXXXXXXXXX
+% Citation needed
+Embedded star-forming regions make it even more challenging to measure
+the column density of dust.
+% XXXXXXXXXXXXXXXXXXXXXXXX
+% Citation needed
+% XXXXXXXXXXXXXXXXXXXXXXXX
+% Note about spectral index being typical of difuse emission
+Although this region is significantly extended, we conclude that what we
+are seeing is most likely an inadequacy in the diffuse $\gamma$-ray emission
 
 \subsection{1FGL J1554.0-5345c}
+
+Using photons with energy between 1 \gev and 100 \gev
+
 Unidentified source likely diffuse emission.
 See figure \ref{1FGL_J1554.0-5345c}.
+
+To get a good fit of the source, we had to delete the nearby catalog sources P72Y2416 and P72Y2422
 
@@
 Many extended sources. Especially instructive to
-use events with $E>10\gev$ where we don't have
+use photons with energy above 10 \gev where we don't have
 to worry about diffuse background as much.
@@
 Make some conclusion about how the LAT will eventually collect a factor
-of 5 more data! Pointlike will be necessary to improve the model of the
+of five more data! Pointlike will be necessary to improve the model of the
 high energy sky.
@@
     This table presents a list of the spectral models (flux and spectral
-    index) used in the monte carlo study of \pointlike described in
+    index) used in the Monte Carlo study of \pointlike described in
     section~\ref{monte_carlo_validation}.  For each spectral model, the
@@
     statistic found for that given spectral model ($\langle\ts\rangle$) is tabulated.
-    The important feature to see in this table is that the monte carlo
+    The important feature to see in this table is that the Monte Carlo
     simulation probes most of the sources parameters that could be detected
@@
     significant detections ($\ts>25$) were kept.  What is quoted is the
-    $>100\mev$ integral flux measured in units of $\ph/\cm^2/\s$.
-    More information about this monte carlo analysis is presented in
+    $>100$ \mev integral flux measured in units of $\ph/\cm^2/\s$.
+    More information about this Monte Carlo analysis is presented in
     section~\ref{monte_carlo_validation}
@@
     \caption{
-    The results of the monte carlo simulation described in section
+    The results of the Monte Carlo simulation described in section
     \ref{monte_carlo_validation} testing the null distribution of
@@
     curves should should follow.  Overall, it should be noted that there
-    is a surprisingly good agreement between the monte carlo study and
+    is a surprisingly good agreement between the Monte Carlo study and
     the theoeretical distribution. And for most spectral parameters, the
@@
     the significance of our source detections.  What is quoted is the
-    $>100\mev$ integral flux in measured in units of $\ph/\cm^2/\s$.
+    $>100$ \mev integral flux in measured in units of $\ph/\cm^2/\s$.
     For each spectral model, more information about the simulations is
     summarized in table~\ref{ts_ext_num_sims}. More
-    information about this monte carlo analysis is presented in
+    information about this Monte Carlo analysis is presented in
     section~\ref{monte_carlo_validation}
@@
     simulated uniform disk source and the $y$ axis is the simulated
-    source's $100\mev$ to $100\gev$ photon flux. Each curve represents
+    source's 100 \mev to 100 \gev photon flux. Each curve represents
     the detection threshold for being able to spatially resolve an
@@
     colors are for sources of different simulated spectral indices.
-    The dashed line shows simulations using events with energy between 
-    $100\mev$ and $100\gev$ while the solid lien shows simulations
-    using events with energy between $1\gev$ and $100\gev$.
+    The dashed line shows simulations using photons with energy between 
+    100 \mev and 100 \gev while the solid lien shows simulations
+    using photons with energy between 1 \gev and 100 \gev.
     The sensitivity is for a one year simulation against a Sreekumar-like
@@
     very large nor very soft, our sensitivity is not significantly
-    improved using events between $100\mev$ and $1\gev$.  More information
+    improved using photons with energy between 100 \mev and 1 \gev.  More information
     about this plot is presented in section~\ref{extension_sensitivity}.
@@
   \begin{center}
-    \includegraphics{source_plots/agn.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v2/agn.py
-    \end{center}
-    \caption{Lalla
-% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-% Note about how TSext for AGN calculated with pointlike
-    }\label{agn_ts_ext}
-  \end{figure}
-
-\begin{figure}
-  \begin{center}
   \includegraphics{ic443_plots/res_tsmap_ic443.pdf}
@@
   \caption{An example residual test statistic map generated for the
-  supernova rememnant IC443 using events between $1\gev$ and
-  $100\gev$.  The top plot is the residual TS map fitting IC443
+  supernova rememnant IC443 using photons with energy between 1 \gev and
+  100 \gev.  The top plot is the residual TS map fitting IC443
   as a point source and the bottom plot is the residual TS map fitting
@@
     % XXXXXXXXXXXXXXXXXXXXXXXXXXX 
-    % describe that this is IC443 using (front? or back? or both?) events.
+    % describe that this is IC443 using (front? or back? or both?) photons.
     }
@@
 
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/profile_ic443.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_profile_ic443/v1/profile_ic443.pdf
+    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.
+    % XXXXXXXXXXXXXXXXXXXXXXXXXXX 
+    % describe that this is IC443 using (front? or back? or both?) photons.
 % XXXXXXXXXXXXXXXXXXXXXXXX
@@
 % 
-\clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{ic443_plots/profile_ic443.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_profile_ic443/v1/profile_ic443.pdf
-    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.
-    % XXXXXXXXXXXXXXXXXXXXXXXXXXX 
-    % describe that this is IC443 using (front? or back? or both?) events.
     }
@@
       were found by our analysis. The top results were found using an
-      energy range between $1\gev$ and $100\gev$.  The lower analysis
-      was done using events between $10\gev$ and $100\gev$.  The quoted
+      energy range between 1 \gev and 100 \gev.  The lower analysis
+      was done using photons between 10 \gev and 100 \gev.  The quoted
       flux is in units of $10^{-9}\ph/\cm^2/\s$ and is the flux in the
-      fit energy range (either 1\gev to 100\gev or 10\gev to 100\gev).
+      fit energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
       All sources were fit using a uniform disk spatial template. The
@@
 \clearpage
-
+\begin{figure}
+  \begin{center}
+    \includegraphics{source_plots/agn.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v2/agn.py
+    \end{center}
+    \caption{Lalla
+% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+% Note about how TSext for AGN calculated with pointlike
+    }\label{agn_ts_ext}
+  \end{figure}
+
+\clearpage
 \begin{sidewaystable}
@@
     \caption{This table presents the new extended soruce candidates found with
-    this search. 3 new extended sources were found searching above 1\gev and
-    5 new candidates were found looking above 10\gev.
+    this search. 3 new extended sources were found searching above 1 \gev and
+    5 new candidates were found looking above 10 \gev.
     The columns in this table have the same defintion as table~\ref{known_extended_sources}.}
@@
       units of $10^{-9}\ph/\cm^2/\s$ and is the integral flux between
-      1\gev (10\gev) and 100\gev for the sources found using events above 1\gev (10\gev).
+      1 \gev (10 \gev) and 100 \gev for the sources found using photonons above 1 \gev (10 \gev).
       }

### 2011-06-25 extended_catalog/paper/extended_catalog.tex
lots of improvements

@@
-\documentclass[preprint]{aastex}
-
-% TODO:
-%   Add contours to images.
-%   What other citations to add?
+\documentclass[12pt,preprint]{aastex}
+%\documentclass[preprint]{aastex}
+
+\usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
+
+%#For adding line numbers:
+\usepackage{lineno}
+\linenumbers
 
@@
 
-\newcommand{\tsextpointlike}{\ensuremath{\tsext_{,\pointlike}}}
-\newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}}
-\newcommand{\tsextalt}{\ensuremath{\tsext_{,\alt}}}
+\newcommand{\tsextpointlike}{\ensuremath{\tsext_{,\pointlike}}\xspace}
+\newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}\xspace}
+\newcommand{\tsextalt}{\ensuremath{\tsext_{,\alt}}\xspace}
 
@@
 sources.  We then apply this tool to test all sources in the 2FGL Two
-Year Catalog for extension.\cite{second_cat} We then report on the discovery
-of XXXXXXXXXXXXXX new extended sources.
+Year Catalog for extension. We then report on the discovery
+of XXXXXX\todo{What number should be put
+here???} new extended sources.
 \end{abstract}
@@
 Air Cherenkov detectors. Most prominent was a survey of the galaictc
-plane using H.E.S.S which discovered XXXXXXXXX spatially extended
-sources\cite{HESS_plane_survey}.
+plane using H.E.S.S which discovered 14 spatially extended sources
+(\cite{HESS_plane_survey}).
 
@@
 
-Nevertheless, morphological studies of sources in the $\gev$ energy
-range using the Fermi LAT is challenging because of the significantly
-energy dependent PSF and because of systematic errors in the galactic
-diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXX\deg$
-at 100 \mev to $XXXXXXXXXXXXXXXX\deg$ at $100 \gev$ so the higher energy
-photons are significantly more important for resolving a source. On
-the other hand, we tend to run out of photons at higher energies so a
-detailed statistical test must be used to maximize our sensitivity.
+Nevertheless, morphological studies of sources in the \gev energy range
+using the Fermi LAT is challenging because of the significantly energy
+dependent PSF and because of systematic errors in the galactic diffuse
+emission.  The Fermi PSF is determinted at lower energies by multiple
+scatteering in the tracker The 68\% containment radius of the PSF is
+approximatly 5.1\deg at 100 \mev  when averaged over instrumetn acceptance
+and including photons which convert in either the thick or thin layers of
+the tracker.  The PSF approaches a limit given by the granularity of the
+tracker channeles and is 0.14\deg at 10 \gev (\cite{on_orbit_calibration}).
+Therefore, the higher energy photons are significantly more important for
+resolving a source but there are typically fewere of them.  So a detailed
+maximum likelihood analysis must be used to maximize our sensitivity.
 
@@
 
-Performing morphological studies of sources in the $\gev$ energy range using
-the Fermi LAT is challenging primarily because of the significantly energy
-dependent PSF and because of systematic errors in the
-galactic diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXXX\deg$
-at 100 \mev to $XXXXXXXXXXXXXXXX\deg$ at $100 \gev$ and so the higher energy photons are
-significantly more important for studying the shape of sources. One could
-ideally look at just the highest energy photons, but the trade off is that
-for typical sources many more source photons are expected at low energy.
-For this reason, it is especially important to use as much of the data
-as possible.
-
-The second primary difficult in studying spatially extended sources is
-systematic uncertainties in the diffuse emission. Systematic errors are
-notoriously difficult and will be discussed more later, but the important
-point to make here is that one of the most important diagnostic tools for
-studying systematic errors is being able to iterate the analysis while
-varying different parameters such as what goes into the diffuse model.
-
 \subsection{The \pointlike Package}
 
-A new analysis tool has been developed to address these unique
-requirements for studying spatially extended sources with the Fermi
-LAT. The overall approach for this analysis is to perform a maximum
-likelihood analysis where the Poisson likelihood for observing the
-measured counts is computed given an assumed sky model. The parameters
-of the sky model are then fit by maximizing the log of the likelihood.
-To study the extension of a source, one can assume a particular shape
-for an extended source (e.g. a disk or Gaussian), and fit the spatial
-parameters of that source.
-
-In principle, the entire task can be done using the 
-official maximum likelihood tool \gtlike which is 
-distributed publically by the Fermi Science Support Center\cite{fssc}. 
-But \gtlike is
-only able to fit the spectral parameters of the source, so the extension
-fitting would have to be done as an external loop. Typically, the run time
-for a binned source analysis using \gtlike is several hours so this loop
-would be especially time consuming. In principle, parallel computing could
-ease this burdon, but parallel fitting algorithms are rather untested
-and complex. Furthermore, the machinery required to do something like
-this would necessarily be rather complex. What has typically been done by
+A new analysis tool has been developed to address the unique requirements
+for studying spatially extended sources with the Fermi LAT. The tool
+implements a maximum likelihood analysis where the Poisson likelihood
+for observing the measured counts is computed for a particular sky
+model. The parameters of the sky model are then fit by maximizing the log
+of the likelihood.  To study the extension of a source, one can assume
+a particular shape for an extended source (e.g. a disk or Gaussian),
+and fit the spatial parameters of that source.
+
+In principle, the entire task can be done using the official maximum
+likelihood tool \gtlike which is distributed publically by the Fermi
+Science Support Center\cite{fssc}.  But \gtlike is only able to fit the
+spectral parameters of the source, so the extension fitting would have
+to be done as an external loop. Typically, the run time for a binned
+source analysis using \gtlike is several hours so this loop would be
+especially time consuming. In principle, parallel computing could ease
+this burdon, but parallel fitting algorithms are rather untested and
+complex. Furthermore, the machinery required to do something like this
+would necessarily be rather complex. What has typically been done by
 the Fermi team to study extended sources is to fix the assumed position
@@
 wavelenghts, or by fitting it as a point source. Then, a profile of the
-likelihood as a function of extension is developed using \gtlike
-and the maximum of this profile. This approach is not optimal because it
-needs not be the case that the best fit position of a point source would
-be the same as the best fit position of an extended source. Furthermore,
-by not fully maximizing the likelihood, this method is not as significant to
+likelihood as a function of extension is developed using \gtlike and the
+maximum of this profile. This approach is not optimal because it needs
+not be the case that the best fit position of a point source would be
+the same as the best fit position of an extended source. Furthermore, by
+not fully maximizing the likelihood, this method is not as significant to
 extension, especially of faint sources. And finally, since this approach
-is so computationally intensive, no large scale Monte Carlo effort has been
-launched to validate the method.
-
-Instead, an alternate approach was developed for performing
-a morphological analysis. An alternate maximum likelihood fitting
-package called \pointlike has been developed by the Fermi
-collaboration and we have expanded its functionality to fully support
-analyzing spatially extended sources. \pointlike is most thoroughly
-described in Matthew Kerr's Ph.D Thesis but the important aspects will
-be summarized below (\cite{matthew_kerr_thesis}) . What differentiates
-\pointlike most significantly from \gtlike is its emphasis
-on speed by introducing approximations into the calculation of the
-likelihood function while at the same time trying to reduce any
-numerical errors that may be introduced.  Like binned \gtlike,
-\pointlike bins the sky both in position and energy.  Unlike 
-\gtlike, \pointlike relies on the {\em healpix} representation of spatial
-bins\cite{healpix} and scales the size of each spatial bin to be
-smaller than the PSF. This is convenient because it no
-significant information is lost due to binning at all energies and it is
-always a good approximation that the model predicted counts are uniform
-across a spatial bin.
+is so computationally intensive, no large scale Monte Carlo effort has
+been launched to validate the method.
+
+Instead, an alternate approach was developed for performing a
+morphological analysis. An alternate maximum likelihood fitting package
+called \pointlike has been developed by the Fermi collaboration and we
+have expanded its functionality to fully support analyzing spatially
+extended sources. \pointlike is most thoroughly described in Matthew
+Kerr's Ph.D Thesis but the important aspects will be summarized below
+(\cite{matthew_kerr_thesis}) . What differentiates \pointlike most
+significantly from \gtlike is its emphasis on speed by introducing
+approximations into the calculation of the likelihood function while
+at the same time trying to reduce any numerical errors that may
+be introduced.  Like binned \gtlike, \pointlike bins the sky both in
+position and energy.  Unlike \gtlike, \pointlike relies on the {\em
+healpix} representation of spatial bins\cite{healpix} and scales the
+size of each spatial bin to be smaller than the PSF. This is convenient
+because it no significant information is lost due to binning at all
+energies and it is always a good approximation that the model predicted
+counts are uniform across a spatial bin.
 
@@
 using numpy and scipy to vectorize most of the computations. This provides
-a reasonable tradeoff between computational efficiency and quickness
-of development time. And by leaving the interface to use \pointlike as a
+a reasonable tradeoff between computational efficiency and quickness of
+development time. And by leaving the interface to use \pointlike as a
 series of \python modules, advanced functions including extension fittion
@@
 
-We have modified \pointlike to support fitting spatially extended
-sources.  To do this, we introduced a new class of diffuse sources where
-the spatial and spectral information completely decouple and where
-the spatial shape is parameters by simple shapes.
-The code consistently convolves the extended source shape with the point
-spread function (as a function of energy) and integrates the spectrum over energy
-to computed model predicted counts.
-
-Finally, \pointlike allows the spatial parameters of an extended
-source to be simulataneoulsy fit. \pointlike uses the \minuit fitting
-library to perform the maximum likelihood maximization of the position
-and extension of an extended source (\cite{minuit_documentation}).  At each
-step in the fit of the shape, the spectral parameters of the entire sky
-model are reoptimized. To avoid projection effects, what is directly
-fit is not the longitude and latitude of the source but instead
-the displacement in a rotated reference frame.
-
-\pointlike optimizes the analysis of extended sources in two ways.
-First, for extended sources which are radially symmetric, the convolution
-of the source shape with our parameterization of the PSF can be performed
-semi-analytically. Generally, at a given energy the observed 
-photon distribution is
+We have modified \pointlike to support fitting spatially extended sources.
+To do this, we introduced a new class of diffuse sources where the spatial
+and spectral information completely decouple and where the spatial shape
+is parameters by simple shapes.  The code consistently convolves the
+extended source shape with the point spread function (as a function
+of energy) and integrates the spectrum over energy to computed model
+predicted counts.
+
+Finally, \pointlike allows the spatial parameters of an extended source
+to be simulataneoulsy fit. \pointlike uses the \minuit fitting library to
+perform the maximum likelihood maximization of the position and extension
+of an extended source (\cite{minuit_documentation}).  At each step in
+the fit of the shape, the spectral parameters of the entire sky model
+are reoptimized. To avoid projection effects, what is directly fit is
+not the longitude and latitude of the source but instead the displacement
+in a rotated reference frame.
+
+\pointlike optimizes the analysis of extended sources in two ways.  First,
+for extended sources which are radially symmetric, the convolution of
+the source shape with our parameterization of the PSF can be performed
+semi-analytically. Generally, at a given energy the observed photon
+distribution is
 \begin{equation}
@@
 \end{equation}
-Here, $\sigma$ and $\gamma$ are parameterize the $PSF$.
-If the extended source is radially symmetric, then
-$I_\text{src} (\vec r') = I_\text{src} (r')$ and the angular part of the
-integral can be done analytically, leaving a simpler one dimensional
-integral:
+Here, $\sigma$ and $\gamma$ are parameterize the $PSF$.  If the extended
+source is radially symmetric, then $I_\text{src} (\vec r') = I_\text{src}
+(r')$ and the angular part of the integral can be done analytically,
+leaving a simpler one dimensional integral:
 \begin{equation}
@@
 \end{equation}
-Not only is this convolution formula faster, but it has the advantage
-that it more accurately reduces to the actual PSF shape as the source's
-size decreases.  Decreasing the numerical difference between a small extended
-source and the PSF is important when searching for smaller extended sources
-and when determining the statistical significance of a detection.
+Not only is this convolution formula faster, but it has the advantage that
+it more accurately reduces to the actual PSF shape as the source's size
+decreases.  Decreasing the numerical difference between a small extended
+source and the PSF is important when searching for smaller extended
+sources and when determining the statistical significance of a detection.
 
@@
 
-Errors on fit parameters are typically calculated in one of two ways. The
-first method requires explicilty varying one paramter until the log of
-the likelihood has fallen by a value 1/2 while simulatenously optimizing
-the other fit parmaeters.  \minuit provides the {\em Simplex} function to
-calculate errors this way (\cite{minuit_documentation}).
+Errors on fit parameters are typically calculated in one of two
+ways. The first method requires explicilty varying one paramter until
+the log of the likelihood has fallen by a value 1/2 while simulatenously
+optimizing the other fit parmaeters.  \minuit provides the {\em Simplex}
+function to calculate errors this way (\cite{minuit_documentation}).
 The second method involves estimating the likelihood function as being
@@
 
-% Make an extension profile plot.
-% show it in figures and describe it.
+\todo[inline]{Document the extension profile
+shown in figure~\ref{extension_profile}.
+Make an extension profile plot.
+show it in figures and describe it.
+}
 
@@
 
-% XXXXXXXXXXXXXXX This section needs work
+\todo{This Section Needs Work}
 
@@
 we then repeated this procedure $>15$ times for each spectral
-and spatial model.
-By fitting a line to the flux vs $\tsext$, we were able to
-estimage the flux at which $\tsext=25$.
+and spatial model.  By fitting a line to the flux vs $\tsext$, we were
+able to estimage the flux at which $\tsext=25$.
 
@@
 sky consistent with the two year catalog's model.   We used the same two
-year data set running from XXXXXXXXXXX MET to XXXXXXXXXXX MET and we used
-the same pass 7 instrument response function.  We used the same galactic
-diffuse, isotropic diffuse, and earth limb emission model. The spectrum of
-the galactic and isotropic diffuse models were refit during the analysis
+years of data from August 4, 2008 to August 1, 2010 and we used the same
+pass 7 instrument response function.  We used the same galactic diffuse,
+isotropic diffuse, and earth limb emission model. The spectrum of the
+galactic and isotropic diffuse models were refit during the analysis
 while the earth limb emission was fixed to it's predicted value.
@@
 \label{alt_diff_model_description}
-% XXXXXXXXXXX All about using alternate diffuse model
+
+To estimate systematic errors due to uncertaintly in our diffuse
+emission background model, we performed an additional analysis
+of our extended source candidates using an alternate diffuse
+model. Our alterate model was based on the GALPROP\footnote{GALPROP
+is a software package for calculating the dise Galactic $\gamma$-ray
+emission based on a model of cosmic-ray propagation in the Galaxy. See
+\url{http://galprop.stanford.edu/} for details and references} code
+used in the Fermi LAT analysis of the isotropic diffuse emission
+(\cite{isotropic_lat}).  In addition to using an alternate model, we
+freeded additional compoents of this model and fit them simulatentously
+with our source during the likelihood analysis. In particular,
+we independently fit 7 HI rings, 7 HII rings, the inverse compoton,
+and the E(B-V) residual component, and the isotropic and earth albedo
+template. All told, there were 18 individual tempaltes where were all
+simulatenously optimized during this analysis.
+
+We do not expect that locally fitting tehse diffuse components would
+produce a more physical model of the didffuse emission in the region.
+But we do believe a source which does away when adding additional
+degrees of freedom to the background model is likely spurious and so
+this provides an important test of the valididity of our source.
+The results of this fit for the new extended source candidates are
+shown in table~\ref{alt_diff_model_results}. There is overal
+good agreement between the \ts using the standard and alternate diffuse
+models ($\ts_\gtlike$ and $\ts_\alt$ respectivly) and the \tsext values
+(\tsextgtlike and \tsextalt respectivly).
 
@@
 
-Since these sources are all included in the 2 year catalog,
-we applied no special method to test these sources but used the same
-pipeline that tested all other catalog sources for extension.  The results
-are summarized in table~\ref{known_extended_sources}.  
-%XXXXXXXXXXXXX DISCUSSION OF WHAT IS IN THE ABLE
-Using photons with
-energies greater than 1 \gev, our analysis succesfully fit the extension
-of the LMC, SMC, IC443, W28, W30, W44, and W51C.  Using photons with 
-energy above 10
-\gev, we were able to succesffuly fit the extesion of HESS J1825-137.
-
+Since these sources are all included in the 2 year catalog, we applied
+no special method to test these sources but used the same pipeline
+that tested all other catalog sources for extension.  The results are
+summarized in table~\ref{known_extended_sources}.  This table includes
+the best fit position and extension. It also includes the source's
+significance \ts and extension significance \tsext and the localization
+error ellipse. The table also includes the best fit powerlaw spectral
+model.
+
+Using photons with energies greater than 1 \gev, our analysis succesfully
+fit the extension of the LMC, SMC, IC443, W28, W30, W44, and W51C.
+Using photons with energy above 10 \gev, we were able to succesffuly
+fit the extesion of HESS J1825-137.
 Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
@@
 correctly find and model the sources we see. We can not claim our method
-is very complete, only that it is systematic and statistically rigorous.
+is complete.
 
@@
 Using the same extension fitting procedure as described above, we
-test these 515 AGN for extension. A histogram of the fit \tsext values
+test these 515 AGN for extension. A histogram of the \tsext values
+computed with \pointlike
 is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again a
@@
 Subsequently, the PSF was fit empirically to these bright AGN and this
-empirical parameterization is used in the Pass 7 Version 6 IRFs.\cite{
-https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
+empirical parameterization is used in the Pass 7 Version 6 IRFs.\footnote{
+LAT Collaboraiton publication pending.
+%https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
 }. But our current parameterization is not perfect. There are especially
@@
 
-% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-% Note about how TSext for AGN calculated with pointlike
-
 \section{New Extended Sources}
+
+% Notes about extended Catalog sources
+% Catalog used for analysis is P72Y_uw23.fits
+% Compare to final catalog gll_pscP72Y_v4r2_v5r7p3_flags
+%          1FGL Name - Preliminary 2FGL - 2FGL Name
+% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425
+% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333
+% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
+% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
+% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753
+% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
+% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705
+% N/A                - P72Y1287         - 2FGL J0851.7-4635
 
@@
 
-\subsection{1FGL J1628.6-2419c}
-
-A catalog source P72Y2516 located at $(l,b)=(353.09\deg, 16.79\deg)$
-was found to be significantly extended when using photons between
-1 \gev and 100 \gev.  The best fit extension was
-$0.41\deg\pm0.05\deg$ and the extension significance was $\tsext=28.9$.
-A smoothed counts map showing this source is seen in figure
-\ref{1FGL_J1628.6-2419c}.
+\subsection{2FGL J1627.0-2425}
+
+% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425
+% No modifications to background were needed
+
+The two year catalog source 2FGL J1627.0-2425 was found to be significantly
+extended when using photons between 1 \gev and 100 \gev.  The best
+fit extension was $0.41\deg\pm0.05\deg$ and the best fit position is
+$(l,b)=(353.09\deg, 16.79\deg)$ The source also appeared in the first
+fermi catalog as 1FGL J1628.6-2419c.  and the extension significance
+was $\tsext=28.9$.  A smoothed counts map showing this source is seen
+in figure \ref{1FGL_J1628.6-2419c}.
 
@@
 traced by CO and HI but also plenty of dark gas, the kind that
-we find only by its association with dust emission.
-% XXXXXXXXXXXXXXXXXXXXXXXX
-% Citation needed
+we find only by its association with dust emission.\todo{Citation Needed}
 Embedded star-forming regions make it even more challenging to measure
-the column density of dust.
-% XXXXXXXXXXXXXXXXXXXXXXXX
-% Citation needed
-% XXXXXXXXXXXXXXXXXXXXXXXX
-% Note about spectral index being typical of difuse emission
+the column density of dust.\todo{Citation Needed}
+\todo[inline]{Note about spectral index being typical of difuse emission}
 Although this region is significantly extended, we conclude that what we
@@
 
-\subsection{1FGL J1554.0-5345c}
-
-Using photons with energy between 1 \gev and 100 \gev
-
-Unidentified source likely diffuse emission.
-See figure \ref{1FGL_J1554.0-5345c}.
-
-To get a good fit of the source, we had to delete the nearby catalog sources P72Y2416 and P72Y2422
-
-\subsection{1FGL J0823.3-4248}
-Coincident with Puppis A SNR.
-See figure~\ref{1FGL_J0823.3-4248}.
-
-\subsection{1FGL J1613.6-5100c}
-Near HESS Source XXXXXXXXXXXXXX.
+\subsection{2FGL J1551.3-5333}
+
+% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333
+% Sources that had to be deleted
+%   * P72Y2416 - 2FGL J1554.4-5317
+%   * P72Y2422 - Not in 2FGL source
+
+The two year catalog source 2FGL J1551.3-5333 was found to be
+extended using photons with energy between 1 \gev and 100 \gev.
+We found an extension of $0.49\deg\pm 0.04\deg$ and an extension significance of
+$\tsext=77.6$ at a position $(l,b)=(328.1387\deg,0.26\deg)$.  Figure
+\ref{1FGL_J1554.0-5345c} shows a smoothed counts map of this source.
+
+It was found in the one year catalog under the name 1FGL J1554.0-5345c.
+To get a good fit of the source, we had to remove the nearby catalog
+sources 2FGL J1554.4-5317 which we believed to be suprious. By looking at
+the counts map, we saw no differentation in the source at the location
+of the two catalog sources. We tested this region for source confusion
+by comparing the increase in log likelihood fitting the region as an
+extended source (\tsext=77.6) to the increase in log likelihood fitting
+the region as two point sources (\tsinc=48.6).  Since the extended
+hypothesis is a has a higher likelihood, we conclude that the source is
+spatially extended More
+information about the dual localization results for this source are
+shown in table \ref{dual_localization_results}.
+
+There are no obvious counterparts to this source. Furthermore, this
+source is relativly soft with a spectral index of $2.31$ and
+very close to the galacitc plane in a region of large diffuse emission.
+We conclude that although this region is significantly extended, it most
+likely represents unmodeled diffuse emission.
+\todo[inline]{this needs more quantification/description}
+\todo[inline]{Improve note about spectral check and lack of hardness}
+
+\subsection{2FGL J0823.0-4246}
+
+% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
+% Deleted 
+%  * P72Y1214 - 2FGL J0823.4-4305
+%  * P72Y1210 - 2FGL J0821.0-4254
+
+The two year catalog source 2FGL J0823.0-4246 was found to be
+extended using photons with energy between 1 \gev and 100 \gev.
+We found an extension of $0.37\deg$ and an extension
+significance of $\tsext=49.2$.  The source was fit to a position of
+$(l,b)=(260.31\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
+a smoothed counts map of this source.
+
+This soruce is coincident with the one year catalog source named 1FGL J0823.3-4248.
+To get a good fit of the source, we had to remove the nearby catalog
+sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254.  We tested the 
+region for source confusion by fitting the region instead as two point
+sources and obtained $\tsinc=22.2$ which is smaller then \tsext.
+
+\todo[inline]{Describe how this source is Coincident with Puppis A SNR
+and give some interpretation of it.}
+
+\subsection{2FGL J1615.2-5138}
+
+% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
+% Deleted
+%  *P72Y2490 - 2FGL J1520.6-5111
+%  *P72Y2487 - 2FGL J1619.7-5040
+%  *P72Y2496 - 2FGL J1622.8-5006
+% Modify 
+%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.410,-0.293,SkyDir.GALACTIC)
+
+The two year catalog source 2FGL J1615.2-5138 was found to be extended
+using photons with energies between 10 \gev and 100 \gev. We foudn an
+extension of $0.52\deg$ with an extension significance of \tsext=75.3.
+The source was fit to a position of $(l,b)=(331.74\deg,-0.58\deg)$.
+Figure~\ref{1FGL_1613.6-5100c} shows a smoothed counts map of this source.
+
+This source is coincident with the one year catalog source named 1FGL
+J1613.6-5100c. To get a good fit for the region, we had to remove from our
+model the nearby catalog sources 2FGL J1520.6-5111, 2FGL J1619.7-5040,
+and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
+iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
+position and extension of 2FGL J1615.2-5138.  We ended up with a best
+fit position of the nearby source 2FGL J1615.0-5051 having moved from
+$(l,b)=(332.2684,0.043)$ to $(l,b)=(332.41,-0.29)$. This was necessary
+because the initial localization of this source was done assumign that
+2FGL J1615.2-5138 was modeled as several point sources.  To address
+the possibility of source confusion, to compare the overal change in
+likelihood fitting 2FGL J1615.2-5138 as two point sources and find
+\tsinc=34.3 which is smaller then \tsext.
+
+\todo[inline]{Interpret source as being coincident with HESS JXXX
+and what the possible emission mechanism could be.}
+
 See figure~\ref{1FGL_J1613.6-5100c}.
 
-\subsection{1FGL J1632.9-4802c}
-Near HESS Source XXXXXXXXXXXXXX.
+\todo[inline]{Describe What this source is/What HESS Source this is near}
+
+\subsection{2FGL J1632.4-4753}
+
+% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753
+% Deleted
+% * P72Y2535 - 2FGL J1631.7-4720
+% * P72Y2550 - 2FGL J1636.3-4740
+% * P72Y2556 - 2FGL J1638.0-4703
+% * P72Y2528 - 2FGL J1630.2-4752
+% * P72Y2543 - 2FGL J1634.4-4743
+% * P72Y2539 - 2FGL J1632.4-4820
+% * P72Y2521 - 2FGL J1628.1-4857
+% * P72Y2527 - 2FGL J1630.1-4615
+% * P72Y2562 - 2FGL J1639.8-4921
+% Modify
+% * P72Y2547 - 2FGL J1635.4-4717 - SkyDir(337.230,0.346,SkyDir.GALACTIC) 
+%              (initial Position - SkyDir(337.1396,0.1433)
+\todo[inline]{Describe how ROI was modified.
+Note about uncertainty about background sources. 
+We model the northwestern source separatly
+but not the southeastern 'possible source'.}
+
 See figure~\ref{1FGL_J1632.9-4802c}.
 
-% XXXXXXXXXXXXXXXXXXXXXXXXXXX
-% Note about uncertainty about background sources. 
-% We model the northwestern source separatly
-% but not the southeastern 'possible source'.
-
-\subsection{1FGL J2020.0+4049}
-Gamam Cygni SNR. Upcomming publication. 
-% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
+\todo[inline]{Describe What this source is/What HESS Source it is near}
+
+\subsection{2FGL J2019.1+4040}
+
+Gamam Cygni SNR.
+
+% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
+% Delete:
+% * P72Y3287
+% * P72Y3262
+% * P72Y3282
+% * P72Y3260
+\todo[inline]{Describe how ROI was modified}
+
+\todo[inline]{
+Describe how this source is analyzed more carefully in the paper
+``A cocoon of freshly accelerated cosmic rays detected by Fermi
+in the Cygnus superbubble''}
+
 See figure~\ref{1FGL_J2020.0+4049}.
 
-\subsection{1FGL J1837.5-0659c}
+\todo[inline]{explain upcomming publication}
+
+\subsection{2FGL J1834.7-0705}
+
+% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705
+% Delete:
+% * P72Y2982
+% * P72Y2986
+% * P72Y2994
+% * P72Y2993
+% Modify:
+% * P72Y2985 - SkyDir(25.574,0.320,SkyDir.GALACTIC)
+%              (initial Position - SkyDir(,)
+% * P72Y2974 - SkyDir(24.716,0.500,SkyDir.GALACTIC)
+%              (initial Position - SkyDir(,)
+
 Near HESS source HESS J1837. Upcomming publication???
-% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
+\todo[inline]{Describe how ROI was modified}
+\todo[inline]{Discuss the upcomming publication}
 See figure~\ref{1FGL_J1837.5-0659c}.
 
-\subsection{P72Y1287}
+\subsection{2FGL J0851.7-4635}
+
+% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
+
+% Delete:
+% * P72Y1291 - 2FGL J0853.5-4711
+% * P72Y1296 - 2FGL J0855.4-4625
+% * P72Y1274 - 2FGL J0848.5-4535
+% * P72Y1259 - 2FGL J0842.9-4721
+% * P72Y1310 - 2FGL J0901.7-4655
+% * P72Y1300 - 2FGL J0858.0-4815
+% Modify:
+%  * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.232,0.517,SkyDir.GALACTIC))
+%              (initial Position - SkyDir(265.5705,-0.0099)
+
+\todo[inline]{Describe how ROI was modified}
 
 Vela Jr. Upcomming publication.
-% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
+\todo[inline]{explain that Vela Jr will be described better in upcomming publication}
 See figure~\ref{Vela_Jr}.
@@
 
-We make some conclusions about finding extended
-sources with the Fermi LAT.
+\todo[inline]{This conclusion needs to be written}
 
@@
     \caption{
+\todo[inline]{Shorted this caption}
     The results of the Monte Carlo simulation described in section
@@
     information about this Monte Carlo analysis is presented in
-    section~\ref{monte_carlo_validation}
+    section~\ref{monte_carlo_validation}.
     }\label{ts_ext_mc}
@@
     \end{center}
-    \caption{Lalla}\label{diff_factor_sensitivity}
+    \caption{
+    \todo[inline]{Add Caption}
+    }\label{diff_factor_sensitivity}
   \end{figure}
@@
     \caption{Comparison of Disk and Gauss.
-    % XXXXXXXXXXXXXXXXXXXXX
-    % the overall point here is that disk looks like gauss once convolved with the psf.
+    \todo[inline]{Add Caption.
+    the overall point here is that disk looks like gauss once convolved with the psf.
+    }
     }\label{compare_disk_gauss}
@@
     \caption{Comparison of r68 for disk and gauss. This is a simulated disk source.
-    % XXXXXXXXXXXXXXXXXXXXX
-    % Add more to caption about htis plot.
+    \todo[inline]{Add more to caption about this plot.}
     }\label{compare_r68}
@@
     \caption{A plot of \tsext vs log(energy)
-    for the SNR IC443, which has a typical spectral model.}
+    for the SNR IC443, which has a typical spectral model.
+    \todo[inline]{Add more caption}
+    }
     \label{ts_ext_vs_energy}
@@
     \caption{
-    % XXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-    % best for lookign at overall diffuse emission and visually assesing quality of the fit.
+    \todo[inline]{Describe that best for lookign at overall diffuse emission and visually assesing quality of the fit.}
     }
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/radial_integral_ic443/v1/ic443_radial_integral.pdf
-    \caption{The radial integral of the counts and the model predicted counts.}
+    \caption{The radial integral of the counts and the model predicted counts.
+    \todo[inline]{Add more text about why this is useful}
+    }
     \label{radial_profile}
@@
     \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.
-    % XXXXXXXXXXXXXXXXXXXXXXXXXXX 
-    % describe that this is IC443 using (front? or back? or both?) photons.
+    \todo[inline]{describe that this is IC443 using (front? or back? or both?) photons.}
     }
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_profile_ic443/v1/profile_ic443.pdf
-    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.
-    % XXXXXXXXXXXXXXXXXXXXXXXXXXX 
-    % describe that this is IC443 using (front? or back? or both?) photons.
-% XXXXXXXXXXXXXXXXXXXXXXXX
-% Make IC443 extension profile
-% good for looking for
-% how peaky likelihood is and
-% wheter or not there is one unique
-% extension maximum (Often times
-% double peaked or does not fall
-% at low/high energies.
-% 
+    \caption{
+    \todo[inline]{
+    Describe that this is IC443 using (front? or back? or both?) photons.
+    Describe that the extension profile is good for looking for how peaky
+    likelihood is and whether or not there is one unique extension maximum
+    (Often times double peaked or does not fall at low/high energies.
+    }
     }
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v2
-    \caption{Example bad Fit: P72Y3047}
+    \caption{Example bad Fit: P72Y3047
+    \todo[inline]{Describe how this is a bad fit}
+    }
     \label{example_bad_fit}
@@
     \end{center}
-    \caption{Lalla
-% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
-% Note about how TSext for AGN calculated with pointlike
+    \caption{
+    \todo[inline]{Add Caption.
+    Note about how \tsext for AGN calculated with pointlike}
     }\label{agn_ts_ext}
@@
   \caption{1FGL J1628.6-2419c. In the opiucus region=most likeliy a molecular cloud.
-  P72Y2516.
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  %Note that unlike other plots, that this plot has the nearby sources subtracted.
-  %This was done to remove the very bright, $\ts=460$, source P72Y2510 % XXXXXXXXXXXXXXXXXXXX what is this source
-  %which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %P72Y2516.
+  \todo[inline]{Add description of this source.
+  Note the bright nearby source
+  which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
+  $\ts=460$, source is P72Y2510. What is this source?}
   }\label{1FGL_J1628.6-2419c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1554.0-5345c/v2/source_1FGL_J1554.0-5345c.pdf
-  \caption{1FGL J1554.0-5345c. P72Y2405. Unidentified source likely diffuse emission.}
+  \caption{1FGL J1554.0-5345c. 
+  %P72Y2405. 
+  \todo[inline]{Describe this source/the fit.Unidentified source likely diffuse emission.}
+  }
   \label{1FGL_J1554.0-5345c}
@@
   \caption{1FGL J0823.3-4248. P72Y1212. Coincident with Puppis A SNR.
-  P72Y1212.
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  %Note that unlike most other plots, this plot has the nearby sources subtracted.
-  %This was done to remove the very bright source Vela which,
-  %at position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
-  %would otherwise spill over into the top left of the image.
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  %P72Y1212.
+  \todo[inline]{
+  Describe this soruce better.
+  Describe nearby source Vela.
+  At position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
+  Spills into the image at left.}
+  \todo[inline]{Describe this source better. Add in Contour}
   }\label{1FGL_J0823.3-4248}
@@
   Gamma Cygni. P72Y3281
+  \todo[inline]{Describe this source better. Add in Contour}
   }\label{Gamma_Cygni}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
-  \caption{Vela Jr. P72Y1287. Using $E>10\gev$. Here, the image is
-  convovled with a $0.25\deg$ gaussian.
-  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  \caption{Vela Jr. P72Y1287. Using $E>10\gev$. 
+  \todo[inline]{Note that sourceis con with a $0.25\deg$ gaussian which is different than other plots.}
+  \todo[inline]{Describe this source better. Add in Contour}
   }\label{Vela_Jr}
@@
   \caption{1FGL J1837.5-0659c. P72Y2974
-  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  \todo[inline]{Describe this source better. Add in Contour}
   }\label{1FGL_J1837.5-0659c}
@@
   \caption{1FGL J1632.9-4802c. P72Y2540
-  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  \todo[inline]{Describe this source better. Add in Contour}
   }\label{1FGL_J1632.9-4802c}
@@
   1FGL J1613.6-5100c . P72Y2473
-  % XXXXXXXXXXXXXXXXXXXXXXXXXXX add in contour
+  \todo[inline]{Describe this source better. Add in Contour}
   }\label{1FGL_J1613.6-5100c}

### 2011-06-29 extended_catalog/paper/extended_catalog.tex
typos and stuff

@@
 \usepackage{url}
+
+% Note, hyperref has to come after other packages!
+\usepackage{hyperref}
 
@@
 on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
-series of Monte Carlo studies that were done to validate this tool.
-We then calculate the Fermi LAT's sensitivity to spatially exnteded
-sources.  We then apply this tool to test all sources in the 2FGL Two
-Year Catalog for extension. We then report on the discovery
+series of Monte Carlo studies that validate this tool.
+We then calculate the Fermi LAT's sensitivity to spatially extended
+sources.  We then use this tool to test all sources in the two
+year source catalog for extension and report on the discovery
 of XXXXXX\todo{What number should be put
@@
 Fermi Gamma-Ray Space Telescope. It has been surveying the $\gamma$-ray
-sky since June 2008.  Fermi is particularly well suited as a survey
-instrument because of its to survey the broad energy coverage (20 \mev
-to >300 \gev), a wide field of view ($\sim 2.4 \sr$) and large effective
+sky since June 2008.  Fermi is well suited as a survey
+instrument because of its broad energy coverage (20 \mev
+to $>300$ \gev), wide field of view ($\sim 2.4 \sr$) and large effective
 area ($\sim 8000 \cm^2$ at $>1 \gev$).
 
-Using one year of all sky monitoring, the LAT published a catalog of
-source that were significantly resolved.  Many of these sources could
-be be associated with a variety of source classes including active
-galactic nuclei, pulsars, galaxies, and supernova remenants.  Many of
-these source classes can be spatially resolved when observed at other
-frequencies and could possibly be spatially resolvable by the LAT.
-
-In particular, the LAT has discovered a variety of spatially extended
-supernova remnants including IC443 and W51C (\cite{ic443,w51c}) and pulsar
-wind nebulae (\cite{msh1552,velax}). And there are other source classes
-which could possibly be spatially resolved by the LAT including galaxy
-clusters, dark matter, and possibly new physics.
+Using one year of all sky surveying data, the LAT published a catalog of
+source that were significantly detected.  Many of these were associated
+with a variety of source classes including active galactic nuclei,
+pulsars, galaxies, and supernova remnants.  Many of these classes can be
+spatially resolved when observed at other frequencies and could possibly
+be spatially resolvable in \gev by the LAT.
+
+The LAT collaboration has previously reported on the discovered
+a variety of spatially extended supernova remnants (SNRs)
+IC443 and W51C, pulsar wind nebulae (PWNe) MSH 15-52 and Vela X
+(\cite{ic443,w51c,msh1552,velax}), and galaxies the Large Magellanic
+Cloud and the Small Magalenic Cloud (\cite{lmc,smc}.  There are other
+source classes which could possibly be spatially resolved by the LAT
+including galaxy clusters, dark matter, and possibly new physics.
 
 Furthermore, a variety of spatially extended but otherwise unassociated
-sources have been detected in the galacitc plane at \tev energies using
-Air Cherenkov detectors. Most prominent was a survey of the galaictc
-plane using H.E.S.S which discovered 14 spatially extended sources
-(\cite{HESS_plane_survey}).
-
-Being able to spatially resolve a fermi source is important for several
-reasons. Most importantly, the spatial morphology can be used to help
-identify a Fermi source. Because of the large point spread function (PSF),
-for any source there are often several counterparts which it could be
-associated with. Finding a matching morphology can uniquly identify the
-source emitting the $\gamma$-rays.
+sources have been detected in the galactic plane at \tev energies using
+Air Cherenkov detectors. Most prominent was a survey of the galactic plane
+using the High Energy Stereoscopic System (H.E.S.S) which discovered 14
+spatially extended sources (\cite{HESS_plane_survey}).
+
+Being able to spatially resolve a LAT source is important for several
+reasons. Most importantly, the spatial morphology can be used to
+help identify the source at other wavelengths. Because of the large
+point spread function (PSF), there are often several possible source
+counterparts.  Finding a matching morphology can uniquely identify
+the source.
 
 Because of the largely varying PSF of the LAT, the spatial and spectral
-model of a source do not nicely decouple and spatially resolving a Fermi
-source is also important for obtaining an unbiased spectral model of
-the source.  Furthermore, using this extension information is important
-for improved the overall model of the sky which is important for obtaining
-a better fit of nearby sources and removing spurious point sources which
-we might otherwise think we detect.
-
-Nevertheless, morphological studies of sources in the \gev energy range
-using the Fermi LAT is challenging because of the significantly energy
+model of a source do not nicely decouple. Therefore, spatially resolving
+a LAT source is also important for obtaining an unbiased spectrum.
+Furthermore, correctly modeling a source's extension is important for
+improved the overall model of the sky and removing excess residuals.
+These residuals around catalog sources can lead to finding spurious nearby
+point sources. This was found to be the case with the one year catalog
+in the region surrounding the Large Magellanic Cloud (\cite{first_cat}).
+
+\section{Analysis Method}
+
+Morphological studies of sources in the \gev energy range
+using the Fermi LAT are challenging because of the significantly energy
 dependent PSF and because of systematic errors in the galactic diffuse
-emission.  The Fermi PSF is determinted at lower energies by multiple
-scatteering in the tracker The 68\% containment radius of the PSF is
-approximatly 5.1\deg at 100 \mev  when averaged over instrumetn acceptance
+emission.  The LAT's PSF is determined at lower energies by multiple
+scattering in the tracker and the 68\% containment radius of the PSF is
+approximately 5.1\deg at 100 \mev  when averaged over instrument acceptance
 and including photons which convert in either the thick or thin layers of
 the tracker. The PSF approaches a limit given by the granularity of the
-tracker channeles and is 0.14\deg at 10 \gev (\cite{on_orbit_calibration}).
+tracker channels and is 0.14\deg at 10 \gev (\cite{on_orbit_calibration}).
 Therefore, the higher energy photons are significantly more important for
-resolving a source but there are typically fewere of them.  So a detailed
-maximum likelihood analysis must be used to maximize our sensitivity.
-
-\section{Analysis Method}
+resolving a source but are limited by statistics. Therefore,
+a detailed analysis procedure mused be used to maximize our
+sensitivity.
 
@@
 for studying spatially extended sources with the Fermi LAT. The tool
-implements a maximum likelihood analysis where the Poisson likelihood
-for observing the measured counts is computed for a particular sky
-model. The parameters of the sky model are then fit by maximizing the log
-of the likelihood.  To study the extension of a source, one can assume
-a particular shape for an extended source (e.g. a disk or Gaussian),
-and fit the spatial parameters of that source.
-
-In principle, the entire task can be done using the official maximum
-likelihood tool \gtlike which is distributed publically by the Fermi
-Science Support Center\cite{fssc}.  But \gtlike is only able to fit the
-spectral parameters of the source, so the extension fitting would have
-to be done as an external loop. Typically, the run time for a binned
-source analysis using \gtlike is several hours so this loop would be
-especially time consuming. In principle, parallel computing could ease
-this burdon, but parallel fitting algorithms are rather untested and
-complex. Furthermore, the machinery required to do something like this
-would necessarily be rather complex. What has typically been done by
-the Fermi team to study extended sources is to fix the assumed position
-of the extended source, either by our knowledge of a source from other
-wavelenghts, or by fitting it as a point source. Then, a profile of the
-likelihood as a function of extension is developed using \gtlike and the
-maximum of this profile. This approach is not optimal because it needs
-not be the case that the best fit position of a point source would be
-the same as the best fit position of an extended source. Furthermore, by
-not fully maximizing the likelihood, this method is not as significant to
-extension, especially of faint sources. And finally, since this approach
-is so computationally intensive, no large scale Monte Carlo effort has
-been launched to validate the method.
-
-Instead, an alternate approach was developed for performing a
-morphological analysis. An alternate maximum likelihood fitting package
-called \pointlike has been developed by the Fermi collaboration and we
-have expanded its functionality to fully support analyzing spatially
-extended sources. \pointlike is most thoroughly described in Matthew
-Kerr's Ph.D Thesis but the important aspects will be summarized below
-(\cite{matthew_kerr_thesis}) . What differentiates \pointlike most
-significantly from \gtlike is its emphasis on speed by introducing
-approximations into the calculation of the likelihood function while
-at the same time trying to reduce any numerical errors that may
-be introduced.  Like binned \gtlike, \pointlike bins the sky both in
-position and energy.  Unlike \gtlike, \pointlike relies on the {\em
-healpix} representation of spatial bins\cite{healpix} and scales the
-size of each spatial bin to be smaller than the PSF. This is convenient
-because it no significant information is lost due to binning at all
-energies and it is always a good approximation that the model predicted
-counts are uniform across a spatial bin.
-
-\pointlike additionaly bins the Fermi $\gamma$-rays by their conversion
-type, which corresponds to whether the photon converted in the front or
-back part of the detector. Since the PSF is smaller for front entering
-photons, one would expect binning each conversion type independently to
-improve our sensitivity.
-
+provides a maximum likelihood analysis where the Poisson likelihood
+for observing the measured counts is computed is maximized by fitting
+parameters of the model.  The extension of a source can be modeled by a
+geometric shape (e.g. a disk or Gaussian) and the source's position
+and extension can simultaneously fit by maximizing the likelihood.
+
+This analysis is not very feasible using the official LAT likelihood
+analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
+Fermi Science Support Center\cite{fssc}} because \gtlike is only able to
+fit the spectral parameters of the source. The extension fitting would
+have to be done as an external loop outside of the code. Typically, the
+run time for a binned source analysis using \gtlike is several hours
+so this loop would be especially time consuming. What has typically
+been done to study an extended sources is to fix the position of the
+extended source and then develop a profile of the likelihood as a
+function of the extension.  This approach is not optimal because the
+position and extension of the source should be simultaneously maximized
+to find the best fit parameters.  Furthermore since this approach is
+very computationally intensive, no large scale Monte Carlo effort can
+be launched to validate it.
+
+An alternate approach was developed for fitting spatially extended
+sources.  An alternate maximum likelihood fitting package called
+\pointlike has been developed by the Fermi collaboration and we have
+added to it the ability to analyze spatially extended sources. \pointlike
+is described in the one year catalog and in Matthew Kerr's Ph.D thesis
+(\cite{first_cat,matthew_kerr_thesis}).
+
+What differentiates \pointlike most significantly from \gtlike is its
+emphasis on speed by introducing approximations into the calculation
+of the likelihood function.  This is done while at the same time
+trying to minimized the introduced numerical errors.  Like the binned
+version of \gtlike, \pointlike bins the sky both in position and energy.
+Unlike \gtlike, \pointlike relies on the {\em healpix} representation of
+spatial bins (\cite{healpix}). Since the PSF changes significantly with
+energy, the spatial size of each bin for a given energy is calculated
+to be smaller than than the PSF. This ensures that little information
+is lost at each energy level while minimizing the overall number of bins.
+
+\pointlike also bins $\gamma$-rays depending upon whether they
+convert in the front or back parts of the detector. Since the PSF
+is smaller for front entering photons, binning each conversion type
+independently improves the tool's sensitivity.
 Furthermore, \pointlike uses a sparse matrix representation of the spatial
-bins where only the bins with counts in them are looped over. The only
-downside to this is that the integral of the model predicted counts
-must be independently calculated.  Effectively, \pointlike efficiently
-interpolates from a totally binned analysis at low energy (where the
-resolution is poor and there are many counts) to an unbinned analysis
-at high energy (where the resolution is very good but there are few
-counts). This approach provides a significant savings in time while
-introducing only small numerical error.
-
-Finally, \pointlike is written mostly in the \python programming language
-using numpy and scipy to vectorize most of the computations. This provides
-a reasonable tradeoff between computational efficiency and quickness of
-development time. And by leaving the interface to use \pointlike as a
-series of \python modules, advanced functions including extension fittion
-described in section~\ref{extesion_fitting} and the dual localization
-procedure described in section~\ref{dual_localization_method} could
-quickly be build on top of the core modules.
+bins where only the bins with counts in them are used. \pointlike
+then independently integrates the overall model predicted counts in the region.
+
+The intelligent binning and sparse matrix representation of the data
+effectively interpolates between a binned analysis at low energy (where
+the resolution is poor and there are many counts) and an unbinned
+analysis at high energy (where the resolution is good but there are
+few counts). This approach provides a significant savings in time while
+introducing small numerical error.
+
+Finally, \pointlike is written mostly in the \python programming
+language and uses {\em numpy} and {\em scipy} to vectorize most of the
+calculations. This provides a reasonable trade off between computational
+efficiency and ease of development. By leaving the interface as a series
+of \python modules, advanced functions including extension fitting
+(described in section~\ref{extesion_fitting}) and a dual localization
+(described in section~\ref{dual_localization_method}) could be quickly
+added on top of the core functionality.
 
@@
 
-We have modified \pointlike to support fitting spatially extended sources.
-To do this, we introduced a new class of diffuse sources where the spatial
-and spectral information completely decouple and where the spatial shape
-is parameters by simple shapes.  The code consistently convolves the
-extended source shape with the point spread function (as a function
-of energy) and integrates the spectrum over energy to computed model
-predicted counts.
-
-Finally, \pointlike allows the spatial parameters of an extended source
-to be simulataneoulsy fit. \pointlike uses the \minuit fitting library to
-perform the maximum likelihood maximization of the position and extension
-of an extended source (\cite{minuit_documentation}).  At each step in
-the fit of the shape, the spectral parameters of the entire sky model
-are reoptimized. To avoid projection effects, what is directly fit is
-not the longitude and latitude of the source but instead the displacement
-in a rotated reference frame.
-
-\pointlike optimizes the analysis of extended sources in two ways.  First,
-for extended sources which are radially symmetric, the convolution of
-the source shape with our parameterization of the PSF can be performed
-semi-analytically. Generally, at a given energy the observed photon
-distribution is
+We modified \pointlike to allow modeling the spatial extension of
+of a source. It is assumed that the spatial and spectral information
+completely decouple and that the spatial shape can be represented by a
+simple geometric function.  The code consistently convolves the extended
+source shape with the PSF (as a function of energy) when computing the
+model predicted counts in a bin.
+
+\pointlike uses the \minuit fitting library to simultaneously maximize
+the likelihood by fitting the position and extension of an extended
+source (\cite{minuit_documentation}).  For each position and extension,
+the spectral parameters of the sky model are refit. To avoid projection
+effects, what is directly fit is not the longitude and latitude of
+the source but instead the displacement in a rotated reference frame.
+The significance of the extension of a source can be calculated from
+\tsext, which is defined as twice the increase in log likelihood between
+the extended source model at its best fit values and the
+point source model at its best fit values:
 \begin{equation}
-  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') d A' 
+  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
 \end{equation}
-where $I_\text{src}$ is the extended soruce shape and the PSF is parameterized by
+The interpretation of \tsext in terms of a statistical significance is
+discussed in section~\ref{significance_of_extension}.
+
+The extended source code is speed up in two ways. First, the convolution
+of the spatial shape of a radially symmetric extended source with the PSF is
+done semi-analytically. The observed photon
+distribution can be written as the convolution of the source shape ($I_\text{src}$)
+with the psf
+\begin{equation}
+  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') d A'.
+\end{equation}
+The PSF is parameterized by
 \begin{equation}
@@
   \left(1-\frac{1}{\gamma}\right)
-  \left(1+\frac{u}{\gamma}\right)^{-\gamma}
+  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
 \end{equation}
-Here, $\sigma$ and $\gamma$ are parameterize the $PSF$.  If the extended
-source is radially symmetric, then $I_\text{src} (\vec r') = I_\text{src}
-(r')$ and the angular part of the integral can be done analytically,
-leaving a simpler one dimensional integral:
+where $\sigma$ and $\gamma$ have been found empirically as a function
+of energy.  For radially symmetric
+extended sources, the angular part of the integral can be done analytically
+leaving a easier one dimensional integral:
 \begin{equation}
@@
   \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
-  \times ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right)
+  \times ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
 \end{equation}
-Not only is this convolution formula faster, but it has the advantage that
-it more accurately reduces to the actual PSF shape as the source's size
-decreases.  Decreasing the numerical difference between a small extended
-source and the PSF is important when searching for smaller extended
-sources and when determining the statistical significance of a detection.
-
-There is one final approximation which speeds up the convolution.
-Generally, the PSF is a function of the angle $\theta$ of the incident
-event measured relative to the normal to the LAT. To avoid repeatedly
-convolving the source shape with the PSF at a series of $\theta$ angles,
-an effective PSF is fit to the weighted sum of the PSF times the exposure
-at different $\theta$ angles.  Since the source convolution has to be
-done at each fit iteration, these optimization were essential for making
-this tool fast enough for the following analysis. Typically, the entire
-process of fitting the extension and estimating the errors for a source
-would run on the order of an hour.
+This convolution formula is faster and more closely reduces to the PSF
+when the source's size is very small. Decreasing this the numerical
+error is important when evaluating the statistical significance of a
+source's extension.
+
+The other approximation is to ignore the dependence of the PSF on the
+incident angle of a $\gamma$-ray.  Generally, the PSF is a function
+of the incident angle of a photon measured with respect to the LAT.
+To avoid multiple convolutions of the source shape with the PSF, an
+effective PSF is calculated by weighted the PSF for different incident
+angles.  Since the convolution has to be done at each iteration of the
+extension fit, these approximations were necessary to make the tool run
+in a reasonable amount of time.
 
 \subsection{Extension Errors}
+\label{extension_error}
 
 Errors on fit parameters are typically calculated in one of two
-ways. The first method requires explicilty varying one paramter until
-the log of the likelihood has fallen by a value 1/2 while simulatenously
-optimizing the other fit parmaeters.  \minuit provides the {\em Simplex}
+ways. The first method requires explicitly varying one parameter until
+the log of the likelihood has fallen by a particular value while 
+simultaneously
+optimizing the other fit parameters. The
+\minuit fitting package provides the {\em Simplex}
 function to calculate errors this way (\cite{minuit_documentation}).
 The second method involves estimating the likelihood function as being
-a multivariate gaussian and calcluating the curvature of the log of
-the likelihood at the peak to estimate when the function will fall by
-a value 1/2. \minuit provides the {\em HESSE} algorithm to calcualte
-errors this way.  The {\em HESSE} are significantly faster but make the
-approximation that the log of the likelihood is perfectly gaussian.
-
-We found that although much faster, the {\em HESSE} algorithm would
-somtimes grosely understimate the errors on the localization and extension
-of the source.  On the other hand, we found the {\em Simplex} algorithm
-was computationally very slow and would often run into convergence
-problems and fail to get reasonable errors.
-
-As a compromise, we employed a hybrid approach to calculate
-the localization and extension errors in \pointlike by making the
-approximation that the covariance between the extension and location of
-the source was small. On the other hand, we do not necessarily expect the
-likelihood profile to be Gaussian when varying the source's extension.
-So we calculate the error on the extension by fixing the position of the
-source and then explicitly using {\em Simplex} to vary the extension of
-the source until the log of the likelihood has fallen by 1/2.
-
-Then, the extended source's position error is calculated using the
-same code employed to calculate position errors of point sources. This
-code is used to calculate the localization error of all point sources
-kn the catalog\cite{second_cat}. It works by fitting an ellipse to the
-likelihood surface near the maximum and using this fit ellipse to estimate
-an elliptical localization errors. By reporting two localization errors
-as well as a localization error angle, this method explicitly takes care
-of covariance between the two position coordinates.
-
-\todo[inline]{Document the extension profile
-shown in figure~\ref{extension_profile}.
-Make an extension profile plot.
-show it in figures and describe it.
-}
+a multivariate Gaussian and calculating the curvature of the log of
+the likelihood at the peak to estimate when the function will fall 
+by the same value. \minuit provides the {\em HESSE} algorithm to calculate
+errors this way.  The {\em HESSE} errors are significantly faster but 
+are only approximately true.
+
+We found that the {\em HESSE} algorithm would sometimes badly
+underestimate the errors on the extension of the source.  On the other
+hand, the {\em Simplex} algorithm was prohibitively slow and would often
+fail to convergence. \pointlike's approach to calculating extension errors
+is to fixing all the spatial parameters and varying just the extension
+until the likelihood has fallen by the desired amount.  This approach
+makes the approximation that the covariance between each spatial parameter
+is small but not that the likelihood is Gaussian. This method 
+is shown schematically in figure~\ref{extension_profile} which shows
+the change in log likelihood when varying the fit extension of
+the SNR IC443.
+
+The localization error is then calculated by fixing the extension to the
+best fit value and fitting an ellipse to the likelihood as a function of
+the spatial parameters.  This fit can be used to calculate an elliptical
+localization error which correctly accounts for covariance between the
+two position coordinates.  This same method is used to calculate the
+localization error of all point sources in the LAT catalog
+(\cite{first_cat}).
 
 \subsection{Gtlike Crosscheck}
-
-Because of its computational speed, \pointlike is especially well
-optimized for analysis that requires many iterations. This include
-source localization, extension fitting, source finding, building test
-statistic maps, and model comparison. On the other hand, \pointlike's
-efficiency has to entail some loss of precision and so it is generally
-expected that \gtlike will produce a more precise result.  Furthermore,
-because it is the standard likelihood analysis package, \gtlike has been
-more extensively validated and is very well trusted.
-
-For that reason, we take our best fit source model obtained by
-\pointlike with the best fit positions and extensions and refit the
-spectral parameters of the model using \gtlike.  \gtlike provides a
-second calculation of the likelihood which can then be used to obtain
-for any source a second measure of \ts and \tsext.
-
-We find very good agreement between the two methods. For the new extended
-source candidates, Table \ref{alt_diff_model_results} shows a comparison
-of \ts and \tsext computed using \pointlike and \gtlike. For the rest
-of this paper, unless otherwise mentioned all \ts, \tsext, flux, and
-spectral index values were obtained using \gtlike with the localization
-results found by \pointlike.
+\label{gtlike_crosscheck}
+
+Because of its computational speed, \pointlike is important for analysis
+that require many iterations such as source localization and extension
+fitting.  On the other hand, we expect \gtlike to get a slightly
+more precise answer for fitting the spectral parameters of a source.
+Furthermore, because \gtlike is the standard likelihood analysis package,
+it has been more extensively validated for spectral analysis.
+
+For that reason, in the following analysis we took the best fit
+positions and extensions of the source model fit by \pointlike but
+refit the spectral spectral parameters of the model using \gtlike.
+\gtlike provides a second calculation of the likelihood which gives a
+second measure of \ts and \tsext.
+
+We found very good agreement between the two methods. For the new
+extended source candidates, table~\ref{alt_diff_model_results} shows a
+comparison of \ts and \tsext computed using \pointlike and \gtlike. For
+the rest of this paper, unless otherwise stated all \ts, \tsext, and
+fit spectral parameters were found using \gtlike with the localization
+results computed by \pointlike.
 
@@
 
-There is a degeneracy in the signal expected from spatially extended
-sources and multiple point sources.  To assess the possibility of source
-confusion, we developed a function in pointlike for simulatenously fitting
-two point sources so that the likelihood fitting two point sources
-could be compared to the likelihood fitting one extended source.
-
-The algorithm works by first dividing the selected point source into
-two separate sources. Then, the position of the two sources 
-are fit simultanously. To avoid projection effects, the fit is
-done in a coordiante system rotated to the celestial equator.
-In this rotated coordiante system, space can be well approximated
-as being flat and we are interested in fitting the 
-rotated coordiante $(x_1',y_1')$ and $(x_2',y_2')$
-We decided not to directly fit the positions of the two sources 
-but instead the fit sum and difference of the rotated coordiantes
-$S_x=(x_2'+x_1')/2$, $S_x=(y_2'+y_1')/2$, $D_x=(x_2'-x_1')/2$, and $D_y=(y_2'-y_1')/2$.
-We believe that fitting the average of position and the difference
-independently would cause less degeneracy in the fit and help the fitter
-find the best position.
-
-For a particular value of $S_x$, $S_y$, $D_x$, and $D_y$, the Poisson
-likelihood is computed by converting the sum and difference coordinates
-into the rotated coordiantes, unrotating the coordiantes, moving the
-two sources in the \pointlike to the new positions, and performing a new
-spectral analysis at the modified position.  The function then maximizes
-The Poission likelihood $L(S_x,S_y,D_x,D_y)$ as a function of the sum
-and difference of the rotated coordaintes using the Minuit to fit the
-sum and differenc coordiantes (\cite{minuit_documentation}).
-
-After the minimization converges, we can define the parameter $\tsext$
-as twice the increase in log likelihood between fitting the region with
-two point sources and fitting the region with one point source
+There is a degeneracy between a spatially extended source and multiple
+point sources.  To assess the possibility of source confusion,
+we developed a function in \pointlike to simultaneously fit two point
+sources and compare the likelihood of two point sources to the likelihood
+of one extended source.
+
+The code uses \minuit to simultaneously fit the position of the two point
+sources.  To avoid projection effects, the fit is done in a coordinate
+system rotated to the celestial equator.  Instead of directly fitting
+the rotated coordinates $x_1$ and $x_2$, we decided there would be less
+covariance by fitting instead the sum and difference of the rotated
+coordinates $S=(x_1+x_2)/2$ and $D=(x_2-x_1)/2$.  The log likelihood
+$L(S,D)$ is maximized by fitting the sum and difference of the two point
+sources.  Because of \pointlike's computational efficiency, this algorithm
+runs in a reasonable amount of time. Similar to extension described in
+section~\ref{gtlike_crosscheck}, the spectrum of can be refit using \gtlike
+at the best fit positions.
+
+We can define the parameter \tsinc as twice the increase in log likelihood
+fitting the region with two point sources compared to fitting the region
+with one point source:
 \begin{equation}
-  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
+  \tsinc=2\times(LL_\text{2pts}-LL_\text{ps}).
 \end{equation}
-Generally, \tsinc can be directly compared to \tsext to see wheter two
-point sources are prefered over one extended source. Unfortunatly,
-performing a likelihood ratio test between two unnested models
-is not a calibrated test and so there is no straightforward way
-to convert the change in likelihood into a significance~\ref{
-http://arxiv.org/abs/astro-ph/0201547 }. Nevertheless, we find this
-ratio, at least in the extreme case where $\tsinc \ll \tsext$ or
-$\tsinc\gg\tsext$ to be suggestive. For all the spatally extended
-candidates found, we computed both \tsext and \tsinc.
-
-Because of \pointlike's computational efficiency, this algorithm
-runs in a reasonable amount of time.
+A straightforward likelihood ratio test between the two point source
+model and the extended source model because the models are note nested.
+
+\tsinc can not be directly compared to \tsext to see whether two
+point sources are preferred over one extended source. Unfortunately,
+performing a likelihood ratio test between two models that are not nested
+(\cite{statistics_with_care}). So the comparison of \tsext with \tsinc is
+not a calibrated test.  Nevertheless, we find the extreme cases where
+$\tsinc \ll \tsext$ or $\tsinc\gg\tsext$ to be suggestive and use this
+as a test for source confusion. For the spatially extended candidates
+found, we computed both \tsext and \tsinc.  The results are presented
+in table~\ref{dual_localization_results}
 
@@
 
-When running \pointlike, we have to pick a spatial model for an extended
-source. Our spatial model is then convolved with the PSF to create the
-probability density function (PDF) that is is fit to the obersved counts.
-Possible choices for spatial models include a Two dimensional gaussian
-source (defined as a Gaussian in $x$ times a Gaussian in $y$):
+An extended source must be modeled by an assumed spatial shape and
+the convolution of that shape with the PSF is fit to the data.
+Possible choices for spatial models include a two dimensional Gaussian
 \begin{equation}
@@
 \end{equation}
-
-Although these shapes look significantly different from eachother, the
-convolution of these spatial models of typtical sizes with the PSF will
+Although these shapes are significantly different from each other, the
+convolution of these spatial models of typical sizes with the PSF will
 produce PDFs that are very similar.
@@
 (in black) the PSF that would be observed for a source of spectral
-index 2. The dashed red (blue) line shows the probabability density
+index 2. The dashed red (blue) line shows the probability density
 function for a Gaussian (uniform disk) of width $0.5\deg$.  The solid
@@
 Gaussian (uniform disk) convolved with the PSF of an index 2 source.
-figure~\ref{compare_disk_gauss} shows the analysis using an energy range
-betewen 1 \gev and 100 \gev whereas the right plot shows an analysis using an
+Figure~\ref{compare_disk_gauss} shows the analysis using an energy range
+between 1 \gev and 100 \gev whereas the right plot shows an analysis using an
 energy range from 10 \gev to 100 \gev.
@@
 ourselves to higher energy where the PSF is narrower, but we do not
-excpet to have much luch learning about the exact nature of the
+except to have much luck learning about the exact nature of the
 extended source shape. For that reason, in this paper we always use
-the uniform disk spatial model to emphaizie our ignorance to the true
+the uniform disk spatial model to emphasize our ignorance to the true
 shape of the extended sources we are studying.
@@
 counts maps can be misleading.  This effect can best be seen
-in figure~\ref{compare_r68} where we have simulted a
+in figure~\ref{compare_r68} where we have simulated a
 extended source with 
@@
 To reduce Poisson noise, figure~\ref{compare_r68} shows a counts map of
-this simulated source smoothed with a 0.1\deg Gaussain kernel.  Overlaied
+this simulated source smoothed with a 0.1\deg Gaussian kernel. Overlaid
 on the plot is the results of fitting this simulated source with a uniform
@@
 fit extension $\sigma_\text{disk}=0.496$ for the disk which was found to
-be in very good agreemen with the simulated value.  The solid black line
-represenst the fit extension $\sigma$ for the Gaussian which was found to
+be in very good agreement with the simulated value.  The solid black line
+represents the fit extension $\sigma$ for the Gaussian which was found to
 be $\sigma_\text{Gaussian}=0.2627$.  The white dashed line is the 68\%
@@
 fit $\sigma$ for the disk and uniform Gaussian are different, the fit
-68\% continment radius are very similar ($\rsixeight_\text{,disk}=0.41$
+68\% containment radius are very similar ($\rsixeight_\text{,disk}=0.41$
 whereas $\rsixeight_\text{,Gaussian}=0.40$).
@@
 model to the data.  The third conclusion we make is that when comparing
-fit extensions to those at other wavelenghts (espeically in \tev), it is
+fit extensions to those at other wavelenghts (especially in \tev), it is
 important to compare fits of consistent spatial models. If this is not
@@
 \subsection{Significance of Extension}
-
-To calculate the statistical significance of the extension of a source,
-one can define a parameter $\tsext$ as twice the increase in log
-likelihood between fitting a source with a spatially extended hypothesis
-and a point hypothesis:
-\begin{equation}
-  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
-\end{equation}
-Of course, these are nested hypotehsis since a point sources is just an
-extended source in the limit that the extension goes to 0. So since we
-are just adding a paramter, it should always be true that $\tsext > 0$
+\label{significance_of_extension}
+
+The value of \tsext, the increase in likelihood fitting the source
+with an extended spatial model, can be used to calculate
+the statistical significance of the source's extension.
+Since the point and extended models are nested hypothesis,
+we would always expect $\tsext>0$.
+
 We would expect that if we were really testing a point source that
@@
 maximum likelihood technique.  They were comparing the hypothesis of a
-source to the hypothesis of just a background\cite{mattox_egret}.
+source to the hypothesis of just a background (\cite{mattox_egret}).
 Their argument for why this null hypothesis distribution was reasonable
@@
 
-Fermi LAT data was simulated using program \gtobssim which is
-distributed publically by the Fermi Science Support Center
-(\cite{fssc}).  The sources were simulated with a powerlaw spectral
+Fermi LAT data was simulated using program 
+\gtobssim\footnote{\gtobssim is distributed by and supported 
+by the Fermi Science Support Center
+(\cite{fssc}).}  The sources were simulated with a powerlaw spectral
 model with 6 Were given 6 $>100$ \mev fluxes ranging from $3\times 10^{-9}
@@
 
-The Monte Carlo simulation was perforormed over a one year time interval using
-a default rocking profile and an assumed a represntative
+The Monte Carlo simulation was performed over a one year time interval using
+a default rocking profile and a representative
 livetime fraction of 0.8.
@@
 For most of the spectral models, over 10,000 statistically independent simulations were performed.
-For fainter sources, some of the simulated sources, statistical flucatuations
+For fainter sources, some of the simulated sources, statistical fluctuations
 caused the source to be not significant and they were excluded from the following analysis.
-Table~\ref{ts_ext_num_sims} shows the parametesr used in the simualtion,
-the number of simulations perfromed, and the average test statistic value.
+Table~\ref{ts_ext_num_sims} shows the parameters used in the simulation,
+the number of simulations performed, and the average test statistic value.
 
@@
 
+\todo[inline]{Note about \ref{extension_profile}}
+
 \section{Validation of Known Extended Sources}
@@
 This list contains the Large Magelenic Cloud and the Small Magilenic Cloud
-which were first published in \cite{LMC,SMC}.
+which were first published in \cite{lmc,smc}.
 We also included the Supernova rememants IC443, W28, W30,
@@
     simulation probes most of the sources parameters that could be detected
-    by the LAT.  The simulation probles a wide range of spectral indices
+    by the LAT.  The simulation probes a wide range of spectral indices
     (from spectral index $\gamma$ of 1.5 to 3) and a wide range of the fluxes
     (varying from a close to $5\sigma$ source detection to a $>10\sigma$
-    source detection).  Only simluations which produced statistically
+    source detection).  Only simulations which produced statistically
     significant detections ($\ts>25$) were kept.  What is quoted is the
@@
     \caption{
-\todo[inline]{Shorted this caption}
+\todo[inline]{Shorten this caption}
     The results of the Monte Carlo simulation described in section
@@
     different spectral indices (for $\gamma$ of 1, 2, 2.5, and 3).
-    And the different colors lines represent different fluxes chosen
-    to span a representative range of Overlayed on the plot in dashed
-    red is the cumulative density function of $\chi^2(\ts)/2$ which is
+    The different colored lines represent different fluxes which were
+    chosen to span a representative range of values. The dashed
+    red line is the cumulative density function of $\chi^2(\ts)/2$ which is
     suggested by Wilks' theorem as the theoretical distribution these
@@
     \caption{
-    \todo[inline]{
-    Describe that this is IC443 using (front? or back? or both?) photons.
-    Describe that the extension profile is good for looking for how peaky
-    likelihood is and whether or not there is one unique extension maximum
-    (Often times double peaked or does not fall at low/high energies.
-    }
+    A plot of the overall change in Test Statistic when varying the
+    extension of the extended SNR IC443.  As is discussed in section
+    \ref{extension_error}, the error on the extension of a source is
+    calculated by varying the extension away from its best fit value until
+    the log likelihood has changed by an amount 1/2.  These profiles are
+    generated for all extended source candidates. They plot is useful
+    to make sure the fitter is not stuck in a local minimum and to make
+    sure the profile is reasonably parabolic.
     }
@@
       compared to \tsext, which is taken from table \ref{new_ext_srcs}.
-      For all of our candiates, $\tsext > \tsinc$ which shows that an
+      For all of our candidates, $\tsext > \tsinc$ which shows that an
       extended source fits the source better than two point sources.
@@
       units of $10^{-9}\ph/\cm^2/\s$ and is the integral flux between
-      1 \gev (10 \gev) and 100 \gev for the sources found using photonons above 1 \gev (10 \gev).
+      1 \gev (10 \gev) and 100 \gev for the sources found using photons above 1 \gev (10 \gev).
       }

### 2011-07-01 extended_catalog/paper/extended_catalog.tex
typos

@@
 \usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
+
+% TODO:
+%  how to format powerlaw, power-law, power law?
 
@@
 the likelihood by fitting the position and extension of an extended
-source (\cite{minuit_documentation}).  For each position and extension,
+source (\cite{minuit_documentation}).  As will be described in
+section~\ref{monte_carlo_validation}, the statistical significance
+of the detection of an extended source can only be correctly calculated
+when all of the parameters of a model are simultaneously fit
+
+For each position and extension,
 the spectral parameters of the sky model are refit. To avoid projection
@@
 \begin{equation}
-  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
+  \tsext=2\log(LL_\text{ext}/LL_\text{ps}).
 \end{equation}
 The interpretation of \tsext in terms of a statistical significance is
-discussed in section~\ref{significance_of_extension}.
+discussed in section~\ref{monte_carlo_validation}.
 
@@
 
-An extended source must be modeled by an assumed spatial shape and
-the convolution of that shape with the PSF is fit to the data.
+An extended source must be modeled with a spatial shape.
+The convolution of that shape with the PSF is fit to the data.
 Possible choices for spatial models include a two dimensional Gaussian
@@
 \end{equation}
-or a uniform disk:
+or a uniform disk
 \begin{equation}
-  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(\sqrt{x^2+y^2}<\sigma\right).
+  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
 \end{equation}
-Although these shapes are significantly different from each other, the
-convolution of these spatial models of typical sizes with the PSF will
-produce PDFs that are very similar.
-
-This is demonstrated in figure~\ref{compare_disk_gauss}.  The plot shows
-(in black) the PSF that would be observed for a source of spectral
-index 2. The dashed red (blue) line shows the probability density
-function for a Gaussian (uniform disk) of width $0.5\deg$.  The solid
-red (blue) line shows the probability density function for the same
-Gaussian (uniform disk) convolved with the PSF of an index 2 source.
-Figure~\ref{compare_disk_gauss} shows the analysis using an energy range
-between 1 \gev and 100 \gev whereas the right plot shows an analysis using an
-energy range from 10 \gev to 100 \gev.
-
-This plot shows that significantly different extended source shapes
-look very similar after smearing with the PSF. The convolved shape of
-the disk and Gaussian admittedly do look more different when restrict
-ourselves to higher energy where the PSF is narrower, but we do not
-except to have much luck learning about the exact nature of the
-extended source shape. For that reason, in this paper we always use
-the uniform disk spatial model to emphasize our ignorance to the true
-shape of the extended sources we are studying.
-
-To get the convolved disk and Gaussian models looked so similar in
-figure~\ref{compare_disk_gauss}, we had to pick the extension of the two
-sources so that they each predicted a 68\% containment radius of 0.5\deg.
-
-The 68\% containment radius for a spatial model is
-the radius at which 68\% of the intensity is enclosed.
-It can be computed by a straightforward integral and we
-find that $\rsixeight_\text{,disk}=0.82\sigma$ whereas
-the $\rsixeight_\text{,Gaussian}=1.51\sigma$. Therefore, in
-figure~\ref{compare_disk_gauss} the uniform disk has an extension
-of $\sigma=0.41\deg$ whereas the Gaussian has an extension of
-$\sigma=0.75\deg$. Even though these sources have quite different
-values of the extension $\sigma$, they look almost identical when convolved
-with the PSF.
-
-Finally, we note that comparing observed morphologies to 
-counts maps can be misleading.  This effect can best be seen
-in figure~\ref{compare_r68} where we have simulated a
-extended source with 
-a spatial model that is a uniform disk of extension 0.5\deg,
-integral flux between 1 \gev and 100 \gev of $3e-8\ph/\cm^2/s$,
-and a spectral index of 2.
-
-To reduce Poisson noise, figure~\ref{compare_r68} shows a counts map of
-this simulated source smoothed with a 0.1\deg Gaussian kernel. Overlaid
-on the plot is the results of fitting this simulated source with a uniform
-disk and a Gaussian spatial model.  The solid white line represents the
-fit extension $\sigma_\text{disk}=0.496$ for the disk which was found to
-be in very good agreement with the simulated value.  The solid black line
-represents the fit extension $\sigma$ for the Gaussian which was found to
-be $\sigma_\text{Gaussian}=0.2627$.  The white dashed line is the 68\%
-containment radius of the fit Disk shape and the black dashed line is
-the 68\% containment radius of the fit Gaussian shape.  Even though the
-fit $\sigma$ for the disk and uniform Gaussian are different, the fit
-68\% containment radius are very similar ($\rsixeight_\text{,disk}=0.41$
-whereas $\rsixeight_\text{,Gaussian}=0.40$).
-
-There are three important conclusions to take from this. The first is
-that depending upon what spatial model you pick and what parameter you
-choose to overlay on the smoothed counts ($\sigma$ or $rsixeight$),
-you will get very different looking shapes even though the all lead
-to a PDF which is very similar. And since we are not very sensitive
-to the particular morphology of extended sources that we are seeing,
-there is no correct choice for which shape to use. For the following
-analysis, we always use a uniform disk as our spatial model because
-of its conceptual simplicity and to emphasize our ignorance to the
-true morphology. And for subsequent smoothed counts maps, we overlay
-the $\sigma$ because that shows directly the edge of the shape we fit.
-But due to smearing of the PSF, it has the unfotunatly concequence that
-the extended source shape always (including in the simulated image)
-looks larger than in the counts map.
+Although these shapes are significantly different, the
+convolution of them with the PSF for typical sizes look very
+similar.
+
+This is demonstrated in figure~\ref{compare_disk_gauss}.  It shows the
+PSF that would be observed for a powerlaw source of spectral index two,
+the probability density function for a Gaussian and uniform disk of width
+$0.5\deg$, and the probability density function for the same Gaussian
+and uniform disk convolved with the PSF.  The figure shows the analysis
+using an energy range between 1 \gev and 100 \gev and using an energy
+range between 10 \gev and 100 \gev.  The convolved shape of the disk and
+Gaussian do separate better at higher energy where the PSF is narrower.
+This plot shows that the LAT is not very sensitive to probing different
+kinds of extended sources.  In this paper we always fit with uniform disk
+spatial models.
+
+To get the convolved disk and Gaussian shapes to match in
+figure~\ref{compare_disk_gauss}, we had to set them to predict
+a 68\% containment radius of 0.5\deg.  The 68\% containment
+radius for a spatial model is the radius at which 68\% of the
+intensity is enclosed.  It can be computed by a straightforward
+integral and we find that $\rsixeight_\text{,disk}=0.82\sigma$
+whereas the $\rsixeight_\text{,Gaussian}=1.51\sigma$. Therefore, in
+figure~\ref{compare_disk_gauss} the uniform disk has
+$\sigma=0.41\deg$ whereas the Gaussian has 
+$\sigma=0.75\deg$.
+
+Finally, we note that comparing fit sizes to counts maps can look
+misleading.  This effect can best be seen in figure~\ref{compare_r68}
+which shows a simulated a extended source with a uniform disk spatial
+model with $\sigma=0.5\deg$. The simulated source has integral flux
+between 1 \gev and 100 \gev of $3\times 10^{-8}\ph/\cm^2/s$, and a
+spectral index of 2.  To reduce Poisson noise, figure~\ref{compare_r68}
+shows a counts map of this source smoothed with by a 0.1\deg Gaussian
+kernel. Overlaid on the plot is the results of fitting this simulated
+source with a uniform disk and a Gaussian spatial model.  The solid white
+line represents the best fit disk extension $\sigma_\text{disk}=0.496$
+The solid black line represents the fit extension $\sigma$ for the
+Gaussian which was found to be $\sigma_\text{Gaussian}=0.2627$.
+The white and black dashed lines are the 68\% containment radius of
+the fit Disk and Gaussian respectivly.  Even though the fit $\sigma$
+for the disk and uniform Gaussian seem very different, the fit 68\%
+containment radius are very similar ($\rsixeight_\text{,disk}=0.41$
+whereas $\rsixeight_\text{,Gaussian}=0.40$) and the results are in
+agreement.
+
+This study shows that depending upon what spatial model you pick and
+what parameter you choose to overlay on the smoothed counts ($\sigma$ or
+$rsixeight$), you will get shapes that look very different but predict
+very similar counts distributions.  Since we are not very sensitive to
+the particular morphology of an extended source, there is no correct
+choice for which shape to use. For the following analysis, we always use
+a uniform disk as our spatial model because of its conceptual simplicity
+and to emphasize our ignorance to the true morphology. And for subsequent
+smoothed counts maps, we overlay the $\sigma$ because that shows directly
+the edge of the shape we fit.  But due to smearing of the PSF, it has the
+unfortunate consequence that the extended source shape always (including
+in the simulated image) looks larger than in the counts map.
 
@@
 important to compare fits of consistent spatial models. If this is not
-possible, it is impotant to at least compare indirectly the $rsixeight$
+possible, it is important to at least compare indirectly the $rsixeight$
 for the different spatial models.
@@
 
-We validated \pointlike for extended source
-analysis using a series of Monte Carlo studies.
+We validated \pointlike for extended source analysis using a series of
+Monte Carlo studies.
 
 \subsection{Significance of Extension}
-\label{significance_of_extension}
-
-The value of \tsext, the increase in likelihood fitting the source
-with an extended spatial model, can be used to calculate
-the statistical significance of the source's extension.
-Since the point and extended models are nested hypothesis,
-we would always expect $\tsext>0$.
-
-We would expect that if we were really testing a point source that
-\tsext would not be very large since a point model would fit about
-as good as anytthing else. Therefore, we can consider a source to be
-extended (and reject the null hyopthesis) if \tsext is large enough.
-Since going from fitting a point soue to fitting a simple extended
-source introduces only one degree of freedom (the source's extension)
-Wilks' Theorem says that the distribution of $\tsext$ wen testin
-point sources should follow a $\chi^2_1$ distribution with one degree
-of freedom (\cite{wilks_theorem}).
+\label{monte_carlo_validation}
+
+\tsext can be used to calculate the statistical significance
+of the source's extension.  Since the point and extended models are
+nested, we would always expect $\tsext>0$.  On the other hand,
+we would not expect the likelihood to change very much unless the source
+was significantly extended.  Since an extended source has one additional
+degree of freedom, Wilks' Theorem says that the distribution
+of $\tsext$ when testing a point source for extension should follow a
+$\chi^2_1$ distribution (\cite{wilks_theorem}).
 
 On the other hand, since the null hypothesis rests on the edge of
-parameter space, when the extension is fixed to 0, Wilks' Theorem does
-not formally hold (\cite{warn_wilks_theorem}).  One might
-expect the actual distribution to be a half $\chi^2_1$ distribution with
-one degree of freedom plus half of a delta function at 0:
+parameter space when the extension is 0, Wilks' Theorem does not hold
+(\cite{warn_wilks_theorem}).  One might expect the actual distribution
+to be a half $\chi^2_1$ distribution with one degree of freedom plus
+half a delta function at 0:
 \begin{equation}
@@
 \end{equation}
-Chernoff proved that given certain assumtipons, this is
-the ditribution that would hold when the null hypothesis
-lies on the edge of parameter space for a particular parameter~\ref{chernof}.
-The false detection probability can be estimated by integrating this function 
-from an observed test statistic value to infinity. It is for this
-particular distribution that the often quoted result holds that
-$\sqrt{\ts}$ is a measure of the number of $\sigma$ of the detection.
-
-It should be noted that Wilks' Theorem only holds when the likelihood
-is maximized simultaneoulsy fitting all of the parameters of model. It
-is for this reason why \pointlike goes through such great effort to
-simultaneously fit the position, extension, and spectral paramters of
-a source.
-
-The half $\chi^2_1$ distribution was found by a Monte Carlo study
-to hold for the special case of source finding of EGRET sources using the
-maximum likelihood technique.  They were comparing the hypothesis of a
-source to the hypothesis of just a background (\cite{mattox_egret}).
-Their argument for why this null hypothesis distribution was reasonable
-was that half of the time, statistical underfluctuations would cause
-there to be fewer fewer photons then expected where the sources is being
-tested. Since the maximim likelihood machinery cannot fit negative
-sources (which would lead to negative model predicted for which the
-poisson likelihood is undefined), half of the tests would not have the
-likelihood improved by adding a source to the model and $\ts=0$.
-It is for the case that the null distribution has
-
-It seems plausable that a similar situation could happen when testing
-a source for extension. Half of the time, statistical flucutations might
-make the observed counts narrower thant the point spread function and
-the likelhood would not improve by fitting the source with an extended
-hypothesis. We tested this hypothesis below using a dedicated monte
-carlo study.
-
-One issue that we found when testing this analysis method is that
-despite our best efforts, there was always a small discrepancy between
-the likelihood value when fitting the source as a point source and when
-fitting it as an extended source with a small extension.  This is to be
-expected due to numerical innacuracies introduced by the convolution.
-For most cases, this error is insignificant. It would not significanlty
-bias any of the fit values or errors. But it would bias the distribution
-of $\tsext$ in the null hypothesis. To correct for this,
+Chernoff proved that under certain assumptions, this is the distribution
+that would hold when the null hypothesis lies on the edge of parameter
+space (\cite{chernof}).  The false detection
+probability can be estimated by integrating this function from an observed
+test statistic value to infinity. It is for this particular distribution
+that the often quoted result holds that $\sqrt{\ts}$ is a measure of
+the number of $\sigma$ of the detection (\cite{mattox_egret}).
+
+The half $\chi^2_1$ distribution was found by a Monte Carlo study to hold
+for the special case of source finding of EGRET sources using a maximum
+likelihood analysis (\cite{mattox_egret}).  For half of the tests of a
+point source, statistical fluctuations would make the observed counts look
+narrower than the point spread function leading to $\tsext=0$. So it is
+reasonable to expect that a similar half $\chi^2_1$ would be appropriate
+for extension testing. We tested this hypothesis using a dedicated Monte
+Carlo study.
+
+Before we show the Monte Carlo simulations, we have to bring up one issue
+we found with these tests.  Despite our best efforts, there was always
+a small numerical discrepancy between the likelihood when fitting the
+source as the PSF and when fitting it as a very small extended source
+with This is due to numerical error introduced by the convolution.
+In most situations, this error would be insignificant. But it does bias the
+distribution of \tsext in the null hypothesis. To correct for this,
 instead of computing the likelihood in the null hypothesis by fitting
-a point source, a new source model was introduced which is an extended
-source with its extension fixed to a very small value. $LL_\text{ps}$
-is then calculated by refitting this source using the same extended
-source fitting code. It was only after introducing this change that we
-were able to get broad agreement between simulations and Wilks' theorem.
-
-\subsection{Monte Carlo Validation} \label{monte_carlo_validation}
-
-We performed a dedicated Monte Carlo study to validate \pointlike for
-studying spatially extended sources and also to demonstrate that we can
-use $\tsext$ as a test of the statistical significance
-of a source's extension.  The Monte Carlo study involved simulating point
-sources of varying spectral models on top of a simulated background. The
-simulated point source was then fit using \pointlike as both an extended
-source and a point source and $\tsext$ was calculated.
-
-Fermi LAT data was simulated using program 
-\gtobssim\footnote{\gtobssim is distributed by and supported 
-by the Fermi Science Support Center
-(\cite{fssc}).}  The sources were simulated with a powerlaw spectral
-model with 6 Were given 6 $>100$ \mev fluxes ranging from $3\times 10^{-9}
-\ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.  The sources were then simulated
-with spectral index ($\gamma$) values of 1.5, 2, 2.5, and 3.  These
-values were picked to probe a representative range measurable values.
-For particular spectral indices, only the fluxes which would create a
-statistically significant source detection ($\ts>25$) where selected,
-since we are only interested in testing for extension sources with a
-significant extent. The sources were simulated on top of an isotropic
-powerlaw background with a Sreekumar-like spectrum ($>100$ \mev flux
-of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).
-
-The Monte Carlo simulation was performed over a one year time interval using
-a default rocking profile and a representative
-livetime fraction of 0.8.
-The reconstruction was performed with photons from an energy range of
-1 \gev to 100 \gev using 4 energy bins per decade and using the Pass 7 Version 6
-source instrument response function (IRFs) to be consistent with the following analysis.
-
-For most of the spectral models, over 10,000 statistically independent simulations were performed.
-For fainter sources, some of the simulated sources, statistical fluctuations
-caused the source to be not significant and they were excluded from the following analysis.
-Table~\ref{ts_ext_num_sims} shows the parameters used in the simulation,
-the number of simulations performed, and the average test statistic value.
-
-The results of the Monte Carlo simulation are shown in
-figure~\ref{ts_ext_mc}.  The cumulative density function (CDF) is plotted
-against $\tsext$ For reference, the CDF for $\chi^2_1/2$,
-suggested by Wilks' Theorem, is also plotted for comparison. Overall,
-there is good agreement between Wilks' theorem, although the agreement is
-not perfect.  It should be noted that the discrepancy seems to be worst
-for bright sources which seems to imply that numerical errors in the
-way \pointlike models the PSF and performs the convolution become more
-apparent for sufficiently bright sources.  Other possible reasons for
-departure from Wilks' theorem might include \pointlike ignoring energy
-dispersion. Energy dispersion will change the shape as a function of
-energy. \pointlike may also run into possibly problems with the fitting
-algorithm getting stuck in false minimum. It is important to emphasize
-that if
-our emperical curve lies to the left of the curve we assume to estimate
-significance, we would underestimate the statistical significance of
-our result. Since this is the case for most of our simluations, we are
-reasonable confident that $\sqrt{\tsext}$ can be safely
-used as a measure of the statistical significance of a source's extension.
+the PSF, we instead fit the null hypothesis as an extended source with
+the extension fixed to be very small.
+
+The Monte Carlo study involved simulating point sources of varying
+spectral models and fitting them using \pointlike as both point
+and extended sources.  Fermi LAT data was simulated using program
+\gtobssim\footnote{\gtobssim is distributed by and supported by the
+Fermi Science Support Center (\cite{fssc}).}  The sources were simulated
+with a powerlaw spectral model with 6 Were given 6 $>100$ \mev fluxes
+ranging from $3\times 10^{-9} \ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.
+The sources were then simulated with spectral index ($\gamma$) values of
+1.5, 2, 2.5, and 3.  These values were picked to probe a representative
+range measurable values.  For particular spectral indices, only the fluxes
+which would create a statistically significant source detection ($\ts>25$)
+where selected, since we are only interested in testing for extension
+sources with a significant extent. The sources were simulated on top of
+an isotropic powerlaw background with a Sreekumar-like spectrum ($>100$
+\mev flux of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).
+
+The Monte Carlo simulation was performed over a one year time interval
+using a default rocking profile and a representative livetime fraction
+of 0.8.  The reconstruction was performed with photons from an energy
+range of 1 \gev to 100 \gev using 4 energy bins per decade and using
+the Pass 7 Version 6 source instrument response function (IRFs) to be
+consistent with the following analysis.
+
+For most of the spectral models, over 10,000 statistically independent
+simulations were performed.  For fainter sources, some of the
+simulated sources, statistical fluctuations caused the source
+to be not significant and they were excluded from the following
+analysis.  Table~\ref{ts_ext_num_sims} shows the parameters used in
+the simulation, the number of simulations performed, and the average
+test statistic value.  The results of the Monte Carlo simulation are
+shown in figure~\ref{ts_ext_mc}.  The cumulative density function (CDF)
+is plotted against $\tsext$ For reference, the CDF for $\chi^2_1/2$,
+suggested by Wilks' Theorem, is also plotted for comparison.
+
+Our Monte Carlo study showed broad agreement between simulations and
+Wilks' theorem and that we can use \tsext as a test of the statistical
+significance of a source's extension.  Nevertheless, the agreement
+is not perfect.  It should be noted that the discrepancy seems to be
+worst for bright sources. This seems to imply that numerical errors in
+the convolution become more apparent for sufficiently bright sources.
+Other possible reasons for departure from Wilks' theorem might include
+\pointlike ignoring energy dispersion. Energy dispersion will change
+the shape as a function of energy. \pointlike may also run into possibly
+problems with the fitting algorithm getting stuck in false minimum. It
+is important to emphasize that if our emperical curve lies to the left of
+the curve we assume to estimate significance, we would underestimate the
+statistical significance of our result. Since this is the case for most
+of our simluations, we are reasonable confident that $\sqrt{\tsext}$
+can be safely used as a measure of the statistical significance of a
+source's extension.
 
@@
 We validated our method by testing for extension all of the sources
-which the Fermi Collaboration had previously published on.  
-This list includes the extended sources where were modeled
-in the 2FGL catalog\cite{second_cat}.
-This list contains the Large Magelenic Cloud and the Small Magilenic Cloud
-which were first published in \cite{lmc,smc}.
-We also included the Supernova rememants IC443, W28, W30,
-W44, W51C, and the Cygnus Loop which were 
-first published in \cite{ic443,w28,w30,w44,w51c,cygnus_loop}.
-We include the Pulsar Wind Nebulae Vela X, MSH 15-52, and 
-HESS J1825-137\cite{velax,msh1552,fermi_hess_j1825}.
-In addition to those sources included by the catalog, we include in
-this list the supernova rememnat RX J1713.7-3946 which was recently
-published (\cite{RXJ1713}).
+which the Fermi Collaboration had previously published on.  This list
+includes the extended sources where were modeled in the two year catalog
+(\cite{second_cat}).  This list contains the Large Magalenic Cloud
+and the Small Magalenic Cloud which were previously published by the
+LAT collaboration (\cite{lmc,smc}).  We also included the SNRs IC443, W28, W30, W44, W51C, and the Cygnus Loop which
+were first published in \cite{ic443,w28,w30,w44,w51c,cygnus_loop}.
+We include the Pulsar Wind Nebulae Vela X, MSH 15-52, and HESS
+J1825-137\cite{velax,msh1552,fermi_hess_j1825}.  In addition to those
+sources included by the catalog, we include in this list the SNR RX J1713.7-3946 which was recently published (\cite{RXJ1713}).
 
@@
     \end{center}
-    \caption{Comparison of Disk and Gauss.
-    \todo[inline]{Add Caption.
-    the overall point here is that disk looks like gauss once convolved with the psf.
-    }
+    \caption{
+    This plot demonstrates that different spatial models when smoothed
+    out by the PSF look very similar.  The $y$ axis is the log of the
+    intensity and the $x$ axis is $\theta^2$.  The black line are PSF that
+    would be observed for a powerlaw source of spectral index two. The
+    dashed red line is the probability density of a Gaussian of width
+    $\rsixeight=0.5\deg$, which is a straight line in this log intensity
+    vs $\theta^2$ plot.  The dashed blue line is the probability density
+    for a uniform disk of $\rsixeight=0.5\deg$.  Finally, the solid red
+    and blue lines show the convolution of the Gaussian and uniform disk
+    with the PSF.  The left plot shows the analysis with an energy range
+    from 1 \gev to 100 \gev whereas the right plot shows the analysis
+    with an energy range from 10 \gev to 100 \gev.
     }\label{compare_disk_gauss}

### 2011-07-08 extended_catalog/paper/extended_catalog.tex
adding green catalog

@@
 % TODO:
-%  how to format powerlaw, power-law, power law?
+%  how to format power-law, power-law, power law?
 
@@
 \newcommand{\cm}{\text{cm}\xspace}
+\renewcommand{\sec}{\text{s}\xspace}
 \newcommand{\tsext}{{\ensuremath{\text{TS}_\text{ext}}}\xspace}
@@
 
-% * Resolving spatially extended Fermi sources is important for 
-%    * studying supernova remnants, 
-%    * pulsar wind nebulae, 
-%    * galaxies,  
-%    * potentially dark matter or new physics.
-% * We searched all 2FGL catalog sources
-% * Systematic test for a certain kind of (~ small) regularly shaped extended
-
 The Large Area Telescope (LAT) is a pair conversion telescope on the
@@
 Morphological studies of sources in the \gev energy range
-using the Fermi LAT are challenging because of the significantly energy
+using the LAT are challenging because of the significantly energy
 dependent PSF and because of systematic errors in the galactic diffuse
@@
 A new analysis tool has been developed to address the unique requirements
-for studying spatially extended sources with the Fermi LAT. The tool
+for studying spatially extended sources with the LAT. The tool
 provides a maximum likelihood analysis where the Poisson likelihood
@@
 Errors on fit parameters are typically calculated in one of two
-ways. The first method requires explicitly varying one parameter until
-the log of the likelihood has fallen by a particular value while 
-simultaneously
-optimizing the other fit parameters. The
-\minuit fitting package provides the {\em Simplex}
-function to calculate errors this way (\cite{minuit_documentation}).
-The second method involves estimating the likelihood function as being
-a multivariate Gaussian and calculating the curvature of the log of
-the likelihood at the peak to estimate when the function will fall 
-by the same value. \minuit provides the {\em HESSE} algorithm to calculate
-errors this way.  The {\em HESSE} errors are significantly faster but 
-are only approximately true.
+ways. The first method requires explicitly varying one parameter
+until the log of the likelihood has fallen by a particular value while
+simultaneously optimizing the other fit parameters. The \minuit fitting
+package provides the {\em Simplex} function to calculate errors this way
+(\cite{minuit_documentation}).  The second method involves estimating the
+likelihood function as being a multivariate Gaussian and calculating the
+curvature of the log of the likelihood at the peak to estimate when the
+function will fall by the same value. \minuit provides the {\em HESSE}
+algorithm to calculate errors this way.  The {\em HESSE} errors are
+significantly faster but are only approximately true.
 
@@
 The localization error is then calculated by fixing the extension to the
-best fit value and fitting an ellipse to the likelihood as a function of
-the spatial parameters.  This fit can be used to calculate an elliptical
-localization error which correctly accounts for covariance between the
-two position coordinates.  This same method is used to calculate the
-localization error of all point sources in the LAT catalog
+best fit value and fitting an ellipse to the likelihood as a function
+of the spatial parameters.  This fit can be used to calculate an
+elliptical localization error which correctly accounts for covariance
+between the two position coordinates.  This same method is used to
+calculate the localization error of all point sources in the LAT catalog
 (\cite{first_cat}).
@@
 
-\tsinc can not be directly compared to \tsext to see whether two
-point sources are preferred over one extended source. Unfortunately,
-performing a likelihood ratio test between two models that are not nested
-(\cite{statistics_with_care}). So the comparison of \tsext with \tsinc is
-not a calibrated test.  Nevertheless, we find the extreme cases where
-$\tsinc \ll \tsext$ or $\tsinc\gg\tsext$ to be suggestive and use this
-as a test for source confusion. For the spatially extended candidates
-found, we computed both \tsext and \tsinc.  The results are presented
-in table~\ref{dual_localization_results}
+\tsinc can not be directly compared to \tsext to see which model is better
+because the models are not nested (\cite{statistics_with_care}). Even
+though the comparison of \tsext with \tsinc is not a calibrated test,
+we find the extreme cases where $\tsinc \ll \tsext$ or $\tsinc\gg\tsext$
+to be suggestive and use this as a test for source confusion. For the
+spatially extended candidates found, we computed both \tsext and \tsinc.
+The results are presented in table~\ref{dual_localization_results}
 
@@
 
-\todo{This Section Needs Work}
+\label{compare_source_size}
 
@@
 This is demonstrated in figure~\ref{compare_disk_gauss}.  It shows the
-PSF that would be observed for a powerlaw source of spectral index two,
-the probability density function for a Gaussian and uniform disk of width
-$0.5\deg$, and the probability density function for the same Gaussian
+PSF that would be observed for a power-law source of spectral index two,
+the probability density function (PDF) for a Gaussian and uniform disk of width
+$0.5\deg$, and the PDF for the same Gaussian
 and uniform disk convolved with the PSF.  The figure shows the analysis
@@
 
-Finally, we note that comparing fit sizes to counts maps can look
-misleading.  This effect can best be seen in figure~\ref{compare_r68}
-which shows a simulated a extended source with a uniform disk spatial
-model with $\sigma=0.5\deg$. The simulated source has integral flux
-between 1 \gev and 100 \gev of $3\times 10^{-8}\ph/\cm^2/s$, and a
-spectral index of 2.  To reduce Poisson noise, figure~\ref{compare_r68}
-shows a counts map of this source smoothed with by a 0.1\deg Gaussian
-kernel. Overlaid on the plot is the results of fitting this simulated
-source with a uniform disk and a Gaussian spatial model.  The solid white
+Overlaying fit sizes on top of counts maps can be misleading.
+This effect can best be seen in figure~\ref{compare_r68} which shows
+an extended source simulated in the energy range from 1 \gev to 100
+\gev with a uniform disk spatial model. The simulated source has a size
+$\sigma=0.5\deg$, an integral flux between 1 \gev and 100 \gev of $3\times
+10^{-8}\ph/\cm^2/\sec$, and a spectral index 2.  To reduce Poisson noise,
+the counts map in figure~\ref{compare_r68} is smoothed by a 0.1\deg
+Gaussian kernel. Overlaid on the plot is the fit extension assuming the
+source has a uniform disk and a Gaussian spatial model.  The solid white
 line represents the best fit disk extension $\sigma_\text{disk}=0.496$
-The solid black line represents the fit extension $\sigma$ for the
-Gaussian which was found to be $\sigma_\text{Gaussian}=0.2627$.
+The solid black line represents the best fit extension $\sigma$ for
+the Gaussian which was found to be $\sigma_\text{Gaussian}=0.2627$.
 The white and black dashed lines are the 68\% containment radius of
-the fit Disk and Gaussian respectivly.  Even though the fit $\sigma$
-for the disk and uniform Gaussian seem very different, the fit 68\%
+the fit Disk and Gaussian respectively.  Even though the fit $\sigma$
+for the disk and uniform Gaussian seem very different, their 68\%
 containment radius are very similar ($\rsixeight_\text{,disk}=0.41$
-whereas $\rsixeight_\text{,Gaussian}=0.40$) and the results are in
-agreement.
-
-This study shows that depending upon what spatial model you pick and
-what parameter you choose to overlay on the smoothed counts ($\sigma$ or
-$rsixeight$), you will get shapes that look very different but predict
-very similar counts distributions.  Since we are not very sensitive to
-the particular morphology of an extended source, there is no correct
-choice for which shape to use. For the following analysis, we always use
-a uniform disk as our spatial model because of its conceptual simplicity
-and to emphasize our ignorance to the true morphology. And for subsequent
-smoothed counts maps, we overlay the $\sigma$ because that shows directly
-the edge of the shape we fit.  But due to smearing of the PSF, it has the
-unfortunate consequence that the extended source shape always (including
-in the simulated image) looks larger than in the counts map.
-
-The second conclusion we make is that because a counts map is smeared
-out by the PSF and depends strongly on the particular color bar used, it
-is very difficult to determine directly from a counts map a reasonable
-spatial model that fits the data.  It is much better to obtain the
-spatial model by a direct fit of a spatial parameters of a selected
-model to the data.  The third conclusion we make is that when comparing
-fit extensions to those at other wavelenghts (especially in \tev), it is
-important to compare fits of consistent spatial models. If this is not
-possible, it is important to at least compare indirectly the $rsixeight$
-for the different spatial models.
+and $\rsixeight_\text{,Gaussian}=0.40$).
+
+This study shows that the extension $\sigma$ for different spatial
+models can be very different even when predicting almost the same PDF.
+Since we are not very sensitive to the particular morphology of an
+extended source, there is no correct choice for which shape to plot. For
+the following analysis, we use a uniform disk as our spatial model
+and overlay the disk's edge $\sigma$.  But due to smearing of the PSF,
+$\sigma$ typically looks larger than the observed counts distribution.
+When comparing the fit extensions with other wavelengths (especially \tev
+measurements of galactic sources), it is important to compare consistent
+values. If the assumed shapes are different, it is best to indirectly
+compare $rsixeight$.
 
@@
 
-\tsext can be used to calculate the statistical significance
-of the source's extension.  Since the point and extended models are
-nested, we would always expect $\tsext>0$.  On the other hand,
-we would not expect the likelihood to change very much unless the source
-was significantly extended.  Since an extended source has one additional
-degree of freedom, Wilks' Theorem says that the distribution
-of $\tsext$ when testing a point source for extension should follow a
-$\chi^2_1$ distribution (\cite{wilks_theorem}).
+\tsext can be used to calculate the statistical significance of the
+source's extension.  Since the point and extended models are nested, we
+would always expect $\tsext>0$.  On the other hand, we would not expect
+the likelihood to change very much unless the source was significantly
+extended.  Since an extended source has one additional degree of freedom,
+Wilks' Theorem says that the distribution of $\tsext$ when testing
+a point source for extension should follow a $\chi^2_1$ distribution
+(\cite{wilks_theorem}).
 
@@
 that would hold when the null hypothesis lies on the edge of parameter
-space (\cite{chernof}).  The false detection
+space (\cite{chernoff}).  The false detection
 probability can be estimated by integrating this function from an observed
@@
 spectral models and fitting them using \pointlike as both point
-and extended sources.  Fermi LAT data was simulated using program
+and extended sources.  LAT data was simulated using program
 \gtobssim\footnote{\gtobssim is distributed by and supported by the
 Fermi Science Support Center (\cite{fssc}).}  The sources were simulated
-with a powerlaw spectral model with 6 Were given 6 $>100$ \mev fluxes
-ranging from $3\times 10^{-9} \ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.
+with a power-law spectral model with 6 Were given 6 $>100$ \mev fluxes
+ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to $10^{-6} \ph/\cm^2/\sec$.
 The sources were then simulated with spectral index ($\gamma$) values of
@@
 sources with a significant extent. The sources were simulated on top of
-an isotropic powerlaw background with a Sreekumar-like spectrum ($>100$
+an isotropic power-law background with a Sreekumar-like spectrum ($>100$
 \mev flux of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).
@@
 problems with the fitting algorithm getting stuck in false minimum. It
-is important to emphasize that if our emperical curve lies to the left of
+is important to emphasize that if our empirical curve lies to the left of
 the curve we assume to estimate significance, we would underestimate the
 statistical significance of our result. Since this is the case for most
-of our simluations, we are reasonable confident that $\sqrt{\tsext}$
+of our simulations, we are reasonable confident that $\sqrt{\tsext}$
 can be safely used as a measure of the statistical significance of a
@@
 
-We performed another Monte Carlo study to determine the Fermi LAT's
-sensitivity to spatially extended sources. The sensitivity to extension
-is defined as the flux at which 
-the average value of $\tsext$ for a source is 
-e equal to 25 (for a given spectral model). This correseoncs
-to an average extension significance of $5\sigma$.  This is not the
-sensitivity to detect an extended source but instead the sensitivity to
-resolve an already detected source as being extended.
-
-One would intuitivly expect that we would be less sensitivie to resolving
-small extended sources since they would be lost in the PSF.  Similarly,
-we would be less sensitive to very large extended sources which would
-get completely lost in the background. Furtheremore, one expects our
-sensitivity to be greater for harder sources since our angular resolution
-improves significantly with energy.
+We performed a second study to determine the LAT's sensitivity
+to spatially extended sources. The sensitivity to extension
+is defined as the flux at which the average value of
+$\tsext$ is equal to $\langle\ts\rangle=25$. As was seen in
+section~\ref{monte_carlo_validation}, this corresponds to an average
+extension significance of $5\sigma$.
+Qualitatively, we expect that the LAT would not be sensitive to
+extended sources much smaller than the PSF. Similarly,
+we expect that the LAT would not be sensitive to sources
+much larger than the PSF since they would get lost in the
+background.
 
 To calculate the LAT's sensitivity to spatially extended sources,
-we simulated sources with a uniform radially symmetric
-disk morphology on top of a powerlaw Sreekumar-like isotropic
-spectrum (\cite{sreekumar_isotropic}).  The Monte Carlo
-simulation was perforormed over a one year time interval using a default
-rocking profile and an assumed a represntative livetime fraction of 0.8.
-For a given extension and spectral index, we calculated the
-sensitivity by varying the flux of a source until we found 
-when $\tsext=25$. In particular, we hand picked a flux range
-where $\tsext<25$ and $\tsext>25$ and simulated 10 points with
-a log uniform distribution in this range and performed an extension
-test for each of these fluxes. Since the measured signifciance is
-a statistical which will vary from realization to realization,
-we then repeated this procedure $>15$ times for each spectral
-and spatial model.  By fitting a line to the flux vs $\tsext$, we were
-able to estimage the flux at which $\tsext=25$.
-
-Our first result is the extension sensitivity for sources of varying
-spectral indices. The result is shown in figure~\ref{index_sensitivity}.
-We computed the sensitivty for sources with a spectral index of 1.5,
-2, 2.5, and 3 and for sources of 20 extensions varying from $0.1\deg$
-to $2.0\deg$. The $y$ axis is the 100 \mev to 100 \gev flux of the
-source and the $x$ axis is the Monte Carlo extension. The curves then
-represent the division in this extension and flux space where one gets
-on average $\tsext=25$.
-The solid lines of the plot are the sensitivity computed when using
-with all photons with energry between 100 \mev and 100 \gev. The dashed lines is the
-same sensitivity but only using photons with energy from 1 \gev to 100 \gev.
-
-This results shows that our extension sensitivity is
-significantly better for harder sources where there are more high
-energy photons. Furthermore, our sensitivity is best for sources with an
-extension around $0.5\deg$.  our sensitivity gets significantly worse
-for very small sources and gets slightly worse for very large sources.
-
-Futheremore, we note that except for the hardest or largest sources,
-our sensitivity is almost entirly whether or not we use photons 
-with energy from
-100 \mev to 1 \gev. On the other hand, other systematic errors become
-increasingly important at low energy so for our extension search we will
-not use the photons in this energy range.
-
-We performed a second computation to see how the LAT's extension
-sensitivity varied with increasing background, as is at lower latitude
-in the galactic plane. To do so, we computed the sensitivity using the
-extragalactic barground as well as 10 and 100 times the extragalactic
-background. The latter result approximatly represents the intensity of
-the galactic diffuse emission near the galactic center. The results are
-shown in figure~\ref{diff_factor_sensitivity}. Two plots are presented,
-one fitting only in the energy range between 1 \gev and 100 \gev and
-one fitting only in the energy range between 10 \gev and 100 \gev. For
-each plot, the $y$ axis quotes the flux in the fit energy range and the
-simulation was done only for a representivite spectral index 2 source.
-
-These plots show that we are much less sensitivie to extended sources in
-a higher background region. By comparing the two plots, we also see that
-we would be more sensitive to an extended source if it had the same
-integral flux, but only over a higher energy range. This is 
-consistent with the improved angular resolution at higher energy.
+we simulated sources with a uniform radially symmetric disk
+morphology on top of a power-law Sreekumar-like isotropic spectrum
+(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was performed
+over a one year time interval using a default rocking profile and a
+livetime fraction of 0.8.  For a given extension and spectral index, we
+first hand picked a flux range such that $\tsext<25$ and $\tsext>25$. We
+then picked 10 flux points in this range and performed an extension test
+for each of these fluxes. We repeated this procedure $>15$ times for each
+spectral and spatial model.  By fitting a line to the flux vs $\tsext$,
+we estimated when $\langle\tsext\rangle=25$.
+
+Figure~\ref{index_sensitivity} shows the extension sensitivity for
+sources of different spectral indices and extensions.  We selected
+spectral indices 1.5, 2, 2.5, and 3 and 
+extensions from $\sigma=0.1\deg$ to $2.0\deg$.  The curves
+on the plot represent the division in extension and flux space where
+$\langle\tsext=25\rangle$.  The plot shows by the sensitivity using all
+photons with energy between 100 \mev and 100 \gev and the sensitivity
+using only photons with energy between 1 \gev and 100 \gev.  This results
+shows that the LAT's sensitivity to extension is better for harder sources
+with more high energy photons. The sensitivity is best for sources with
+an extension around $0.5\deg$ and is worse for small and large sources.
+
+Except for the hardest and largest sources, our sensitivity is almost
+unchanged when using events between 100 \mev and 1 \gev.  This is also
+demonstrated in figure~\ref{ts_ext_vs_energy} which shows the \tsext for
+the SNR IC443 in 12 energy bins between 100 \mev and 100 \gev. For IC443,
+which has a spectral index ~2.4, almost the entire increase in \ts comes
+from energies above 1 \gev.  On the other hand, other systematic errors
+become increasingly important at low energy. For our extension search,
+we include only photons above 1 \gev.
+
+Figure~\ref{diff_factor_sensitivity} shows how the LAT's
+sensitivity varies with increasing background, typical of sources
+at lower galactic latitude. We compute the sensitivity for spectral
+index 2 sources using 10 and 100 times the
+extragalactic background. The latter result approximately represents the intensity of
+the galactic diffuse emission near the galactic center. 
+The figure shows two plots, the first showing the sensitivity looking only between 
+1 \gev and 100 \gev and the second showing the sensitivity looking only
+between 10 \gev and 100 \gev.
+For each plot, the $y$ axis quotes the flux in the selected energy range
+which weaken the dependence of the sensitivity on spectral index.
+This shows that we are less sensitive to extended sources in
+a higher background region and that if the flux is constant,
+we are more sensitive if the source is harder (has more high energy
+photons).
 
@@
 
-As was shown, we gain very little in sensitivity using photons with energy
+As was shown, we gain very little in sensitivity using photons with energies
 below 1 \gev. On the other hand, the large PSF at low energy makes us
-more succeptable to systmetic errors arising from source confusion due
-to multiple point soruces and succeptable to incorrect modeling of the
+more susceptible to systematic errors arising from source confusion due
+to multiple point sources and susceptible to incorrect modeling of the
 galactic diffuse emission.  For that reason, we performed our search
@@
 are very bright at lower energy but cutoff before 10 \gev.  This approach
-of using only photons with energy above 10 \gev was succesfully used to detecting
-HESS J1825-137 with the Fermi LAT~\cite{fermi_hess_j1825}.
+of using only photons with energy above 10 \gev was successfully used
+to detecting HESS J1825-137 with the LAT (\cite{fermi_hess_j1825}).
 
 For each catalog source, we modified the spectral index of the source
-to be a powerlaw. We did this for two reasons. The first is that for a
+to be a power-law. We did this for two reasons. The first is that for a
 source to be significantly extended, we would expect it to be reasonably
-hard and therefore be fit reasonably well by a powerlaw.  The seond reason
+hard and therefore be fit reasonably well by a power-law.  The second reason
 is that since we begin our analysis at either 1 \gev or 10 \gev, we didn't
 expect there to be significant curvature over this smaller energy range.
-This method has the advantange that for the following analysis, we can
-simply quote the fit powerlaw spectral index.
+This method has the advantage that for the following analysis, we can
+simply quote the fit power-law spectral index.
 
@@
 distort our fit enough that it no longer would show up as being extended.
-Nevertheless, we investiated for each of our extended candidates if
-if we seemed to be legitimatly removing real backgorund sources. And
-we employed a dual localiation procedure (described above) to test
+Nevertheless, we investigated for each of our extended candidates if
+if we seemed to be legitimately removing real background sources. And
+we employed a dual localization procedure (described above) to test
 all of our candidates for source confusion.
@@
 
-We expect most extended sources to be inside teh galactic plane
+We expect most extended sources to be inside the galactic plane
 since extragalactic sources are typically too far away to be
@@
 Fermi catalog~\ref{first_cat,second_cat}. Furthermore, the galactic plane is
-very crowded and so it is offent difficult to get a good model for the
+very crowded and so it is often difficult to get a good model for the
 region around a catalog source.  Because of this, finding a source with
 $\tsext>16$ is not a sufficient test and we perform several crosschecks
-to ensure our overal region is well modeled.
+to ensure our overall region is well modeled.
 
@@
 extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
-using photons with energy above 1 \gev. In the map, the galacitc and isotropic diffuse
+using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
 emission subtracted.  A two year catalog source P72Y3047 was found at the
-position $(l,b)=(37.79\deg,1.14\deg)$.  By looking at the smoothed map,
-we see that there appears to be overall some large scale residaul in the
+position $(l,b)=(37.79\deg,1.14\deg)$.  
+We find that there appears to be overall some large scale residual in the
 diffuse emission along the galactic plane. Furthermore, it appears that
@@
 the source's extension is statistically significant. For this reason,
-we have to perform a series of followup analysis for all of the soruces
+we have to perform a series of followup analysis for all of the sources
 that are found with \tsext=16.
@@
 and performed a crosscheck by refitting the spectral parameters using
-\gtlike.  We used a square ROI $14.1\deg$ in diamater with $1/16\deg$
+\gtlike.  We used a square ROI $14.1\deg$ in diameter with $1/16\deg$
 pixels and the same energy binning. We found that $1/16\deg$ bins were
@@
 with \pointlike.  Using \gtlike, we found a second measure of \tsext and
-we only considered a source to be significanlty extended if \pointlike
+we only considered a source to be significantly extended if \pointlike
 and \gtlike both agreed.  For the new extended source candidates, with
@@
 
-Additionaly, we generated for each extended source candidate residual
+Additionally,
+we generated for each extended source candidate residual
 test statistic (\ts) maps.  The residual \ts map is a map of the \ts
-value evalualted at each point by adding onto the map at that position
-a new source of spectral index 2 and finding the increase in lieklihood
+value evaluated at each point by adding onto the map at that position
+a new source of spectral index 2 and finding the increase in likelihood
 when fitting its flux. \ts maps are especially useful as looking for
-new sources or other residual featuers that are not included in the
-model. They also have the advantagous feature that the aboslute scale
-can be used to clearly look for when the residual is signifciant.
+new sources or other residual features that are not included in the
+model. They also have the advantageous feature that the absolute scale
+can be used to clearly look for when the residual is significant.
 The downside is they are biased to look for residual features
 that look like the PSF and so are not as sensitive to diffuse residual
-features. Furthermore, since by defintion \ts>0, \ts maps can only show
+features. Furthermore, since by definition \ts>0, \ts maps can only show
 positive fluctuations. Nevertheless, \ts maps were useful for
-assessing the overal quality of the fit. Figure~\ref{res_tsmap}
-shows an exmaple residual \ts map for the extended source IC443.
+assessing the overall quality of the fit. Figure~\ref{res_tsmap}
+shows an example residual \ts map for the extended source IC443.
 
@@
 the latitudinal direction.  The same plot is also shown integrating in
-the longitudinal direction.  On top of the plot is overlayed the model
+the longitudinal direction.  On top of the plot is overlaid the model
 predicted counts assuming the source has a disk spatial model, assuming
@@
 IC443 in figure~\ref{counts_slice}. Counts slices were especially useful
-for looking at how well the overal diffuse emisison model fits the region
+for looking at how well the overall diffuse emission model fits the region
 near the sources.
@@
 that an isotropic background will be flat in the plot. On top of this
-plot is overlayed the model predicted counts assuming the source has a
-disk spatial model, assumgng the source is a point source, and fitting
-just the diffuse emisison in the region. An example radial integral
+plot is overlaid the model predicted counts assuming the source has a
+disk spatial model, assuming the source is a point source, and fitting
+just the diffuse emission in the region. An example radial integral
 is shown for the extended source IC443 in figure~\ref{radial_profile}.
@@
 half of the original flux and then using \pointlike to
-simulatnoulsy fit the postion and spectrum of these sources.
+simultaneously fit the position and spectrum of these sources.
 We then used \gtlike to refit the spectrum of these
@@
 \url{http://galprop.stanford.edu/} for details and references} code
-used in the Fermi LAT analysis of the isotropic diffuse emission
+used in the LAT analysis of the isotropic diffuse emission
 (\cite{isotropic_lat}).  In addition to using an alternate model, we
@@
 significance \ts and extension significance \tsext and the localization
-error ellipse. The table also includes the best fit powerlaw spectral
+error ellipse. The table also includes the best fit power-law spectral
 model.
@@
 
-To validate our method and assess systematic issues with our
-analysis, we used \pointlike to test known active galaxies (AGN) for extension.
-\gev emission from AGN is believed to comes from the
-core of supermassive blackholes. Since this happens in a very small region
-in the core of very distant galaxies,
-
-AGN are not expected to be spatially resolvable and therefore
-provide a good calibration source to demonstrate the efficacy of our
-tool. Nevertheless, it would be very interesting if AGN could be
-spatially resolved AGN and there are theories that predict
-this\cite{pair_halo_paper}.
-
-Following the Fermi-LAT one year catalog, the Fermi collaboration
-published a list of the Fermi catalog sources that had a high probability
-association with AGN. The first year catalog had 709 AGN associated with
-671 distinct 1FGL sources at high latitude ($|b|>10\deg$).  For our
-study, we are looking to assess systematics with extension fitting so
-it is important to avoid any possible issues with AGN associations.
-For that reason, we select only the 599 AGN which make it into the
-``clean'' AGN sample. An AGN association is only considered ``clean''
-if it has a high probability of association $P\ge 80\%$, if it is the
-only AGN associated with the 1FGL source, and if there are no flags
-on the source which shed doubt on the source\cite{first_cat}. These last two
-conditions are especially important for our analysis. One might expect
-source confusion between two AGN look like a spatially extended source.
-Testing only unflagged sources is also important because it removes
-any catalog sources coincident with structures in the diffuse emission.
-It is possible that these flagged catalog sources which are really poorly
-modeled diffuse emission might also look extended.
+To validate our method and assess systematic issues with our analysis,
+we used \pointlike to test known active galaxies (AGN) for extension.
+\gev emission from AGN is believed to comes from the core of supermassive
+blackholes in small regions in the core of distant galaxies.  AGN are
+not expected to be spatially resolvable and therefore provide a good
+calibration source to demonstrate the efficacy of our tool. Nevertheless,
+it would be very interesting if AGN could be spatially resolved and
+there are theories that predict this (\cite{pair_halo_paper}).
+
+Following the LAT's one year catalog, the LAT collaboration published
+a list of catalog sources that had a high probability association with
+AGN. The first year catalog had 709 AGN associated with 671 distinct
+1FGL sources at high latitude ($|b|>10\deg$).  To avoid systematic
+problems with AGN classification, we used only the 599 AGN which made
+it into the clean AGN sample.  An AGN association is only considered
+clean if it has a high probability of association $P\ge 80\%$, if it is
+the only AGN associated with the 1FGL source, and if there are no flags
+on the catalog source (\cite{first_cat}). These last two conditions are
+especially important for our analysis.  Source confusion may look like
+a spatially extended source and flagged catalog sources may correlate
+with unmodeled structure in the diffuse emission.
 
 Of the 599 ``clean'' AGN, we select 556 of these 1FGL sources which
-we uniquely associate with a 2 year catalog source. And we furthermore
-restrict our select to 515 of these AGN for which we fit $\ts>25$ using
-\pointlike.  Our intention here is not to find the largest sample of
-AGN and this will be the scope of a follow up AGN association paper. Our
-purpose is simply to find a good sample of AGN which can be used to
-test the systematics of our tool.
-
-Using the same extension fitting procedure as described above, we
-test these 515 AGN for extension. A histogram of the \tsext values
-computed with \pointlike
-is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again a
-$\chi^2/2$ distribution suggested by Wilks' Theorem.  This plot shows
-a worse agreement with the theoretical distribution then was found
-by our Monte Carlo study in figure~\ref{ts_ext_mc}.  But overall, the
+we uniquely associate with a 2 year catalog source. We furthermore
+restrict our select to the 515 of these AGN for which we fit $\ts>25$
+using \pointlike and photons with energy above 1 \gev.  Our intention
+here is not to find the largest sample of AGN but simply
+to find a goog sample to test the systematics of our extended source
+search.
+
+Using the same extension fitting procedure as described above, we tested
+these 515 AGN for extension. A histogram of the \tsext values computed
+with \pointlike is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot
+is a $\chi^2/2$ distribution suggested by Wilks' Theorem.  This plot
+shows a worse agreement with the theoretical distribution and
+a discrepancy with 
+our Monte Carlo study in figure~\ref{ts_ext_mc}.  But overall, the
 distribution is good. No AGN get fit with a particularly significant
-value of $\tsext$. Almost all of the AGN get fit with $\tsext<1$ and
-there are very few AGN fit with large values of \tsext.  There where
-only 2 AGN having $\tsext>10$.  The maximum fit $\tsext=13.7$ whereas the
-maximum value expected theoeritcally for the $\chi^2/2$ distribution is
-8.3. This result therefore shows that there is some systematic on our
-analysis but that we understand it and that it will not significantly
-cast into doubt our subsequent results.
+value of $\tsext$ and almost all of the AGN get fit with $\tsext<1$.
+There where only two AGN with $\tsext>10$. The maximum had $\tsext=13.7$
+whereas the maximum value expected theoretically by the $\chi^2/2$ distribution is
+8.3. This result shows that there is some systematic with our
+analysis but that it will not significantly affect our analysis.
 % 8.3 number gotten from mathematica:
@@
 
-Several possible systematics could cause this discrepancy. The first
-is that in our analysis we fit each source with a powerlaw index.
-AGN tend to have curved spectral and fitting with a wrong spectral
+Several possible systematics could cause this discrepancy. The first is
+that in our analysis we fit each source with a power-law spectral model.
+AGN tend to have curved spectral and fitting with the wrong spectral
 model might effect the value of \tsext. Nevertheless, since we use only
-photons with energy above 1 \gev, this would effect is not expected to be large.
-Another possible source for the discrepancy is that pointlike performs a
-likelihood analysis without modeling the energy dispersion of our source.
-But energy dispersion is expected to be more significant at low
-energy and furthermore if this was a signifciant effect the same results
-would have showed up with the Monte Carlo simultions which included the
-effects of energy dispersion.
-
-Another possible systematic may be due to remaning issues with our
-background model. Due to chance coincidence, a catalog source might
-lie very close to nearby source. If the two sources were near enough,
-they would be unresolvable by the catalog and the catalog would simply
-fit them both together.  This could easily lead to an anomolously high
-value of \tsext for a paritcular point source. Issues could also arise
-from farther away but fainter sources which did not make the catalog's
-significance cut, but nonetheless would pull the fitter away from the
-point hyoptehsis.  Finally, it is possible that there are lingering
-residuals in the diffuse emission in parts of the high latitude sky
-which would cause the fitter to prefer a slightly extneded hypotehsis
-that could fill in parts of the unmodeled diffuse emission.
-
-The final possible effect causing this discrepancy is an imperfect
-modeling of the PSF of the LAT.  Before launch, the LAT PSF
-was determined using a Monte Carlo simulation of the detector.
+photons with energy above 1 \gev, this effect is not expected to be large.
+Another possible source for the discrepancy is that \pointlike performs
+a likelihood analysis without modeling the energy dispersion of the LAT.
+This probably is not the cause because energy dispersion is expected to
+be more significant at low energy and it would have also showed up with
+the Monte Carlo simulations.
+
+Another possible systematic may be due to source confusion to problems
+with the background model. If the two sources were close,
+they may be unresolvable and get fit as a more significant extended source.
+It is also possible that there are lingering
+residuals in the diffuse emission. Unmodeled parts of the diffuse
+emission could be filled in by modeling point sources as being slightly extended.
+
+The final effect that could cause this discrepancy is an imperfect
+modeling of the PSF.  Before launch, the PSF
+was determined by a Monte Carlo simulation of the detector.
 After launch, a discrepancy was found using flight data above a
@@
 was presented in conference and a publication is in preparation.
-Subsequently, the PSF was fit empirically to these bright AGN and this
-empirical parameterization is used in the Pass 7 Version 6 IRFs.\footnote{
-LAT Collaboraiton publication pending.
+Subsequently, the PSF was fit empirically to bright AGN and this
+empirical parameterization was used in our instrument
+response function.
+%\footnote{
+%LAT Collaboraiton publication pending.
 %https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
-}. But our current parameterization is not perfect. There are especially
-lingering issues due to lackign the statistics at high energy to
-validate the PSF as a function of the incident $\theta$ angle of a
-photon. Since the distribution of $\theta$ angles for observing any
-sources is different, the PSF for every source should be different.
-It is likely that these issues could cause this systematic in the fit
-value of \tsext for AGN.
-
-We should furtheremore note that since the PSF was found empirically in
-the first place by fitting the shape of brigh AGN, finding that the AGN we
-test are not significantly extended is not surprising.  We hope to note
-that because of the difficulties in validating the PSF, we are strictly
-searching for sources that are significantly extended when compared to
-bright AGN measured by the LAT. Trying to look for the extension of these
-AGN, or more realistically trying to put an upper limit on thier size,
-would require its own dedicated analysis.
+%}. 
+But our current parameterization is not perfect. There are lingering
+issues due to a lack of statistics at high energy which makes it hard to
+validate the PSF as a function of the incident angle of the photon. Since
+the distribution of incident angles varies from source to source, an
+average PSF may make some of the sources look more and less extended
+than the PSF.
+
+We should finally clarify that since the PSF was found empirically
+from the shape of bright AGN, finding that the AGN we test are not
+significantly extended is not surprising.  All this analysis shows
+is that the we can significantly find sources larger than bright AGN
+found by the LAT.  Trying to look for the extension of these AGN as a
+population would require a more specialized analysis.
 
 \section{New Extended Sources}
+\label{new_ext_srcs_section}
 
@@
 % Catalog used for analysis is P72Y_uw23.fits
-% Compare to final catalog gll_pscP72Y_v4r2_v5r7p3_flags
+% Compare to final catalog gll_psc_v04.fit
 %          1FGL Name - Preliminary 2FGL - 2FGL Name
-% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425
-% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333
+% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
+% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
 % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
 % 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
-% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753
+% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
 % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
-% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705
+% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
 % N/A                - P72Y1287         - 2FGL J0851.7-4635
 
-For all extended sources, the results of our fit are summarized in
-table~\ref{new_ext_srcs}. The table includes the best fit position
-and extension of the source. It also includes the source's significance
-and significance of extension.
-
-\subsection{2FGL J1627.0-2425}
-
-% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425
+Eight new extended sources not included in the two year catalog were
+found using this search. Three were found in our search using events
+above 1 \gev and five were found in the search using events
+above 10 \gev.
+For all the extended sources, the results of our fit are summarized in
+table~\ref{new_ext_srcs_table}. The table includes the best fit position and
+extension of the source. It also includes the source's significance and
+significance of extension.
+
+\subsection{2FGL J1627.0-2425c}
+
+% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
 % No modifications to background were needed
 
-The two year catalog source 2FGL J1627.0-2425 was found to be significantly
+The two year catalog source 2FGL J1627.0-2425c was found to be significantly
 extended when using photons between 1 \gev and 100 \gev.  The best
@@
 
-\subsection{2FGL J1551.3-5333}
-
-% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333
+\subsection{2FGL J1551.3-5333c}
+
+% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
 % Sources that had to be deleted
-%   * P72Y2416 - 2FGL J1554.4-5317
-%   * P72Y2422 - Not in 2FGL source
-
-The two year catalog source 2FGL J1551.3-5333 was found to be
+%   * P72Y2416 - 2FGL J1554.4-5317c
+%   * P72Y2422 - Not a 2FGL source
+
+The two year catalog source 2FGL J1551.3-5333c was found to be
 extended using photons with energy between 1 \gev and 100 \gev.
@@
 To get a good fit of the source, we had to remove the nearby catalog
-sources 2FGL J1554.4-5317 which we believed to be suprious. By looking at
+sources 2FGL J1554.4-5317c which we believed to be suprious. By looking at
 the counts map, we saw no differentation in the source at the location
@@
 There are no obvious counterparts to this source. Furthermore, this
-source is relativly soft with a spectral index of $2.31$ and
+source is relativly soft with a spectral index 2.31 and
 very close to the galacitc plane in a region of large diffuse emission.
@@
 % Deleted
-%  *P72Y2490 - 2FGL J1520.6-5111
-%  *P72Y2487 - 2FGL J1619.7-5040
+%  *P72Y2490 - 2FGL J1520.6-5111c
+%  *P72Y2487 - 2FGL J1619.7-5040c
 %  *P72Y2496 - 2FGL J1622.8-5006
@@
 
-The two year catalog source 2FGL J1615.2-5138 was found to be extended
-using photons with energies between 10 \gev and 100 \gev. We foudn an
-extension of $0.52\deg$ with an extension significance of \tsext=75.3.
-The source was fit to a position of $(l,b)=(331.74\deg,-0.58\deg)$.
-Figure~\ref{1FGL_1613.6-5100c} shows a smoothed counts map of this source.
-
+The two year catalog source 2FGL J1615.2-5138 was found to be
+extended using photons with energies between 10 \gev and 100 \gev.
 This source is coincident with the one year catalog source named 1FGL
-J1613.6-5100c. To get a good fit for the region, we had to remove from our
-model the nearby catalog sources 2FGL J1520.6-5111, 2FGL J1619.7-5040,
+J1613.6-5100c.  We found an extension of $0.52\deg$ with an extension
+significance of \tsext=75.3.  The source was fit to a position of
+$(l,b)=(331.74\deg,-0.58\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
+a smoothed counts map of this source.
+
+ To get a good fit for the region, we had to remove from our
+model the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
 and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
@@
 
-\todo[inline]{Interpret source as being coincident with HESS JXXX
+\todo[inline]{Interpret source as being coincident with HESS JXXXX
 and what the possible emission mechanism could be.}
@@
 
-\subsection{2FGL J1632.4-4753}
-
-% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753
+\subsection{2FGL J1632.4-4753c}
+
+% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
 % Deleted
-% * P72Y2535 - 2FGL J1631.7-4720
-% * P72Y2550 - 2FGL J1636.3-4740
-% * P72Y2556 - 2FGL J1638.0-4703
+% * P72Y2535 - 2FGL J1631.7-4720c
+% * P72Y2550 - 2FGL J1636.3-4740c
+% * P72Y2556 - 2FGL J1638.0-4703c
 % * P72Y2528 - 2FGL J1630.2-4752
-% * P72Y2543 - 2FGL J1634.4-4743
-% * P72Y2539 - 2FGL J1632.4-4820
-% * P72Y2521 - 2FGL J1628.1-4857
+% * P72Y2543 - 2FGL J1634.4-4743c
+% * P72Y2539 - 2FGL J1632.4-4820c
+% * P72Y2521 - 2FGL J1628.1-4857c
 % * P72Y2527 - 2FGL J1630.1-4615
-% * P72Y2562 - 2FGL J1639.8-4921
+% * P72Y2562 - 2FGL J1639.8-4921c
 % Modify
-% * P72Y2547 - 2FGL J1635.4-4717 - SkyDir(337.230,0.346,SkyDir.GALACTIC) 
+% * P72Y2547 - 2FGL J1635.4-4717c - SkyDir(337.230,0.346,SkyDir.GALACTIC) 
 %              (initial Position  - SkyDir(337.1396,0.1433)
+
+The two year catalog source 2FGL J1632.4-4753c was found to be extended
+using photons with energies between 10 \gev and 100 \gev.  This source
+was found to be consistent with 1FGL J1632.9-4802c.  We fit an
+extension of 0.65\deg with an extension significance of \tsext=95.3.
+The source was fit to a position of $(l,b)=(336.52\deg,0.06\deg)$.
+Figure~\ref{1FGL_J1632.9-4802c}.  shows a smoothed counts map of this
+source. The figure shows as a red star the catalog position
+of this source.
+
+To get a good fit of the region, had to remove from our model the 5
+catalog sources 2FGL J1631.7-4720c, 2FGL J1636.3-4740c, 2FGL J1630.2-4752,
+2FGL J1634.4-4743c, and 2FGL J1632.4-4820c. These sources all are on top
+of this extended source but there is no indication that the emission of
+these sources separates.  These sources are indicated as green stars in
+figure~\ref{1FGL_J1632.9-4802c}.
+
+In addition we removed from our region the 4 nearby catalog sources
+2FGL J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL
+J1639.8-4921c because they were not significant above 10 \gev. Finally,
+we had to move the source 2FGL J1635.4-4717c to a better fit position
+$(l,b)=(337.230,0.346)$ to get a good fit of it and our extended source in
+the $>10$ \gev energy range. The initial position of this source is shown
+in the figure as a blue star and its best fit position is also indicated.
+
+To test for source confusion, we compared the likelihood fitting this
+region as one extended source to the likelihood fitting this region as
+two point sources. We found $\tsinc=24.8\ll\tsext$ which indicates that
+this is extended emission and not source confusion.
+
 \todo[inline]{Describe how ROI was modified.
@@
 
-See figure~\ref{1FGL_J1632.9-4802c}.
-
 \todo[inline]{Describe What this source is/What HESS Source it is near}
@@
 % Delete:
-% * P72Y3287
-% * P72Y3262
-% * P72Y3282
-% * P72Y3260
+% * P72Y3287 - 2FGL J2021.5+4026
+% * P72Y3262 - 2FGL J2013.8+4115c
+% * P72Y3282 - 2FGL J2020.0+4159
+% * P72Y3260 - 2FGL J2012.4+3955c
 \todo[inline]{Describe how ROI was modified}
@@
 
-\subsection{2FGL J1834.7-0705}
-
-% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705
+\subsection{2FGL J1834.7-0705c}
+
+% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
 % Delete:
-% * P72Y2982
-% * P72Y2986
-% * P72Y2994
-% * P72Y2993
+% * P72Y2982 - Not a 2FGL source
+% * P72Y2986 - 2FGL J1837.3-0700c
+% * P72Y2994 - 2FGL J1839.3-0558c
+% * P72Y2993 - 2FGL J1839.0-0539
 % Modify:
-% * P72Y2985 - SkyDir(25.574,0.320,SkyDir.GALACTIC)
+% * P72Y2985 - 2FGL J1836.8-0623c - SkyDir(25.574,0.320,SkyDir.GALACTIC)
 %              (initial Position - SkyDir(,)
-% * P72Y2974 - SkyDir(24.716,0.500,SkyDir.GALACTIC)
+% * P72Y2974 - 2FGL J1834.7-0705c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
 %              (initial Position - SkyDir(,)
@@
       \hline
-      $\gamma$ & flux ($\ph/\cm^2/\s$) & $N_\text{sims}$ & $\langle\ts\rangle$ \\
+      $\gamma$ & flux ($\ph/\cm^2/\sec$) & $N_\text{sims}$ & $\langle\ts\rangle$ \\
       \hline
@@
     section~\ref{monte_carlo_validation}.  For each spectral model, the
-    number of statistically indepdent simulations and the average test
+    number of statistically independent simulations and the average test
     statistic found for that given spectral model ($\langle\ts\rangle$) is tabulated.
-    The important feature to see in this table is that the Monte Carlo
+    The important feature in this table is that the Monte Carlo
     simulation probes most of the sources parameters that could be detected
@@
     significant detections ($\ts>25$) were kept.  What is quoted is the
-    $>100$ \mev integral flux measured in units of $\ph/\cm^2/\s$.
+    $>100$ \mev integral flux measured in units of $\ph/\cm^2/\sec$.
     More information about this Monte Carlo analysis is presented in
@@
     the significance of our source detections.  What is quoted is the
-    $>100$ \mev integral flux in measured in units of $\ph/\cm^2/\s$.
+    $>100$ \mev integral flux in measured in units of $\ph/\cm^2/\sec$.
     For each spectral model, more information about the simulations is
@@
     \end{center}
-    \caption{This is the Fermi LAT's sensitivity to spatially
+    \caption{This is the LAT's sensitivity to spatially
     extended sources. The $x$ axis is Monte Carlo extension of a
@@
     the detection threshold for being able to spatially resolve an
-    extended source (when $\langle\tsext\rangle=25$ averaged over
-    multiple simulations).  
-    All sources have an assumed powerlaw spectrum and the different
+    extended source (when $\langle\tsext\rangle=25$).  
+    All sources have an assumed power-law spectrum and the different
     colors are for sources of different simulated spectral indices.
@@
     out by the PSF look very similar.  The $y$ axis is the log of the
-    intensity and the $x$ axis is $\theta^2$.  The black line are PSF that
-    would be observed for a powerlaw source of spectral index two. The
-    dashed red line is the probability density of a Gaussian of width
-    $\rsixeight=0.5\deg$, which is a straight line in this log intensity
-    vs $\theta^2$ plot.  The dashed blue line is the probability density
-    for a uniform disk of $\rsixeight=0.5\deg$.  Finally, the solid red
-    and blue lines show the convolution of the Gaussian and uniform disk
-    with the PSF.  The left plot shows the analysis with an energy range
-    from 1 \gev to 100 \gev whereas the right plot shows the analysis
-    with an energy range from 10 \gev to 100 \gev.
+    intensity and the $x$ axis is $\theta^2$.  The black line is the
+    PSF that would be observed for a power-law source of spectral index
+    two. The dashed red line is the probability density of a Gaussian
+    of width $\rsixeight=0.5\deg$. A Gaussian on this plot is just a
+    straight line.  The dashed blue line is the probability density for
+    a uniform disk of width $\rsixeight=0.5\deg$.  Finally, the solid
+    red and blue lines show the convolution of the Gaussian and uniform
+    disk respectively with the PSF.  The left plot shows the analysis
+    with an energy range from 1 \gev to 100 \gev whereas the right plot
+    shows the analysis with an energy range from 10 \gev to 100 \gev.
     }\label{compare_disk_gauss}
@@
       \end{center}
-    \caption{Comparison of r68 for disk and gauss. This is a simulated disk source.
-    \todo[inline]{Add more to caption about this plot.}
+      \caption{A plot of the smoothed counts for a simulated uniform
+        disk extended source in the energy range from 1 \gev to 100 \gev.
+        The source has a size $\sigma=0.5\deg$, an integral flux between
+        1 \gev and 100 \gev of $3\times 10^{-8}\ph/\cm^2/\sec$, and
+        a spectral index 2.  The smoothed counts from a point source
+        with the same spectrum are shown in the bottom right inset.
+        This source was fit with both a uniform disk and a Gaussian
+        spatial model.  The white circle represents the fit size $\sigma$
+        fitting with the disk hypothesis.  The black circle is the fit
+        $\sigma$ fitting with the Gaussian hypothesis.  The dashed white
+        and black circles are the fit \rsixeight defined in section
+        \ref{compare_source_size} for the disk and Gaussian hypothesis
+        respectively.  This plot shows that fitting the same source with
+        different spatial shapes can lead to very different values of
+        $\sigma$. On the other hand, the different shapes have a good
+        agreement about the 68\% containment radius \rsixeight.
       }\label{compare_r68}
@@
   \caption{An example residual test statistic map generated for the
-  supernova rememnant IC443 using photons with energy between 1 \gev and
+  supernova remnant IC443 using photons with energy between 1 \gev and
   100 \gev.  The top plot is the residual TS map fitting IC443
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
-    \caption{A plot of \tsext vs log(energy)
-    for the SNR IC443, which has a typical spectral model.
-    \todo[inline]{Add more caption}
+    \caption{
+    The plot shows \tsext for 12 uniform log(energy) bins between 100
+    \mev and 100 \gev for the SNR IC443. IC443 has a spectral index
+    ~2.4 (table~\ref{known_extended_sources}) which is typical of
+    extended sources.  This plot shows that there is little gain in
+    sensitivity in the data with energy below 1 \gev.  For this reason,
+    this paper restricts its analysis to energies above 1 \gev.
     }
@@
     \caption{
-    \todo[inline]{Describe that best for lookign at overall diffuse emission and visually assesing quality of the fit.}
+    \todo[inline]{Describe that best for looking at overall diffuse emission and visually assesing quality of the fit.}
     }
@@
       was done using photons between 10 \gev and 100 \gev.  The quoted
-      flux is in units of $10^{-9}\ph/\cm^2/\s$ and is the flux in the
+      flux is in units of $10^{-9}\ph/\cm^2/\sec$ and is the flux in the
       fit energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
@@
       is the increase in \ts fitting the source with an extended spatial
-      model instead of a point model.  \glon and \glat are respectivly
-      the galactic longitute and galactic latitude of the source and
+      model instead of a point model.  \glon and \glat are respectively
+      the galactic longitude and galactic latitude of the source and
       $\sigma$ is the edge of the uniform disk spatial model that was fit
@@
 
+  % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
+  % 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
+  % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
+  % 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
+  % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
+  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
+  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
+  % N/A                - P72Y1287         - 2FGL J0851.7-4635
+
 \clearpage
@@
       \hline
-      P72Y2516             &     353.08\deg &      16.80\deg & $  0.41\deg \pm   0.05\deg$ &    139.2 &       28.9 &  0.042\deg &  0.036\deg &   54.4\deg & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ \\
-      P72Y2405             &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
-      P72Y1212             &     260.31\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &    314.6 &       49.2 &  0.026\deg &  0.023\deg &    5.0\deg & $    8.3 \pm     0.3$ & $   2.18 \pm    0.02$ \\
+      2FGL J1627.0-2425c   &     353.08\deg &      16.80\deg & $  0.41\deg \pm   0.05\deg$ &    139.2 &       28.9 &  0.042\deg &  0.036\deg &   54.4\deg & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ \\
+      2FGL J1551.3-5333c   &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
+      2FGL J0823.0-4246    &     260.31\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &    314.6 &       49.2 &  0.026\deg &  0.023\deg &    5.0\deg & $    8.3 \pm     0.3$ & $   2.18 \pm    0.02$ \\
       \hline
@@
       \hline
-      P72Y2473             &     331.74\deg &      -0.58\deg & $  0.52\deg \pm   0.04\deg$ &     75.3 &       45.2 &  0.071\deg &  0.049\deg &  -21.9\deg & $    1.3 \pm     0.2$ & $   1.75 \pm    0.25$ \\
-      P72Y2540             &     336.52\deg &       0.06\deg & $  0.65\deg \pm   0.03\deg$ &    173.0 &       95.3 &  0.041\deg &  0.037\deg &    5.3\deg & $    2.9 \pm     0.2$ & $   2.28 \pm    0.08$ \\
-      P72Y3281             &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
-      P72Y2979             &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
-      P72Y1287             &     266.29\deg &      -1.43\deg & $  1.15\deg \pm   0.08\deg$ &    119.6 &       90.9 &  0.080\deg &  0.065\deg &   54.6\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.18$ \\
+      2FGL J1615.2-5138          &     331.74\deg &      -0.58\deg & $  0.52\deg \pm   0.04\deg$ &     75.3 &       45.2 &  0.071\deg &  0.049\deg &  -21.9\deg & $    1.3 \pm     0.2$ & $   1.75 \pm    0.25$ \\
+      2FGL J1632.4-4753c         &     336.52\deg &       0.06\deg & $  0.65\deg \pm   0.03\deg$ &    173.0 &       95.3 &  0.041\deg &  0.037\deg &    5.3\deg & $    2.9 \pm     0.2$ & $   2.28 \pm    0.08$ \\
+      2FGL J2019.1+4040          &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
+      2FGL J1834.7-0705c         &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
+      2FGL J0851.7-4635          &     266.29\deg &      -1.43\deg & $  1.15\deg \pm   0.08\deg$ &    119.6 &       90.9 &  0.080\deg &  0.065\deg &   54.6\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.18$ \\
       \hline
     \end{tabular}
-    \caption{This table presents the new extended soruce candidates found with
-    this search. 3 new extended sources were found searching above 1 \gev and
-    5 new candidates were found looking above 10 \gev.
-    The columns in this table have the same defintion as table~\ref{known_extended_sources}.}
-    \label{new_ext_srcs}
+    \caption{The 8 new source candidates found by the
+    extended source search. 3 new extended sources were found searching looking at photons with energies 1 \gev and
+    5 new candidates were found looking at photons with energies above 10 \gev.
+    The columns in this table have the same definition as table~\ref{known_extended_sources}.
+    More information about these sources can be found in section~\ref{new_ext_srcs_section}
+    }
+    \label{new_ext_srcs_table}
   \end{centering}
@@
         \hline
-        P72Y2516             &       23.8 &       28.9 &     353.04\deg &      16.96\deg & $       3.5 \pm        0.6$ & $  2.7 \pm   0.3$  &     353.14\deg &      16.50\deg & $       2.0 \pm        0.5$ & $  2.4 \pm   0.3$ \\
-        P72Y2405             &       48.6 &       77.6 &     328.31\deg &       0.31\deg & $      10.0 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.28\deg &      -0.06\deg & $       1.0 \pm        0.7$ & $  1.6 \pm   0.4$ \\
-        P72Y1212             &       22.2 &       49.2 &     260.59\deg &      -3.26\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
+        2FGL J1627.0-2425c   &       23.8 &       28.9 &     353.04\deg &      16.96\deg & $       3.5 \pm        0.6$ & $  2.7 \pm   0.3$  &     353.14\deg &      16.50\deg & $       2.0 \pm        0.5$ & $  2.4 \pm   0.3$ \\
+        2FGL J1551.3-5333c   &       48.6 &       77.6 &     328.31\deg &       0.31\deg & $      10.0 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.28\deg &      -0.06\deg & $       1.0 \pm        0.7$ & $  1.6 \pm   0.4$ \\
+        2FGL J0823.0-4246    &       22.2 &       49.2 &     260.59\deg &      -3.26\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
         \hline
@@
         \hline
-        P72Y2473             &       34.3 &       45.2 &     331.77\deg &      -0.35\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.5$  &     331.51\deg &      -0.83\deg & $       0.4 \pm        0.1$ & $  2.1 \pm   0.5$ \\
-        P72Y2540             &       24.8 &       95.3 &     336.16\deg &       0.34\deg & $       0.7 \pm        0.1$ & $  2.0 \pm   0.4$  &     336.72\deg &      -0.06\deg & $       0.7 \pm        0.1$ & $  3.1 \pm   0.5$ \\
-        P72Y3281             &       34.5 &      151.7 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.45\deg &       2.54\deg & $       0.5 \pm        0.1$ & $  1.9 \pm   0.4$ \\
-        P72Y2979             &       15.4 &       20.6 &      25.06\deg &       0.24\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.6$  &      25.08\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.6$ \\
-        P72Y1287             &       32.5 &       90.9 &     267.16\deg &      -1.60\deg & $       0.2 \pm        0.1$ & $  1.9 \pm   0.4$  &     266.43\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.5$ \\
+        2FGL J1615.2-5138    &       34.3 &       45.2 &     331.77\deg &      -0.35\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.5$  &     331.51\deg &      -0.83\deg & $       0.4 \pm        0.1$ & $  2.1 \pm   0.5$ \\
+        2FGL J1632.4-4753c   &       24.8 &       95.3 &     336.16\deg &       0.34\deg & $       0.7 \pm        0.1$ & $  2.0 \pm   0.4$  &     336.72\deg &      -0.06\deg & $       0.7 \pm        0.1$ & $  3.1 \pm   0.5$ \\
+        2FGL J2019.1+4040    &       34.5 &      151.7 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.45\deg &       2.54\deg & $       0.5 \pm        0.1$ & $  1.9 \pm   0.4$ \\
+        2FGL J1834.7-0705c   &       15.4 &       20.6 &      25.06\deg &       0.24\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.6$  &      25.08\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.6$ \\
+        2FGL J0851.7-4635    &       32.5 &       90.9 &     267.16\deg &      -1.60\deg & $       0.2 \pm        0.1$ & $  1.9 \pm   0.4$  &     266.43\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.5$ \\
         \hline
@@
       \caption{For the new extended source candidates in
-      figure~\ref{new_ext_srcs}, we describe the results
+      table~\ref{new_ext_srcs_table}, we describe the results
       of the dual localization procedure described in
@@
       with \pointlike and results in the best fit position of the two
-      sources $(\glon_1,\glat_1)$ and $(\glon_2,\glat_2)$.  The change in
-      likelihood and spectral values are then computed using \gtlike with
-      the best fit positions found by \pointlike.  \tsinc is the increase
-      in TS fitting the region as two sources compared to fitting compared
-      to fitting a single point source and is computed using \gtlike with
-      the best fit positions taken from \pointlike.  It can be directly
-      compared to \tsext, which is taken from table \ref{new_ext_srcs}.
-      For all of our candidates, $\tsext > \tsinc$ which shows that an
-      extended source fits the source better than two point sources.
-      As in table~\ref{known_extended_sources}, flux is measured in
-      units of $10^{-9}\ph/\cm^2/\s$ and is the integral flux between
-      1 \gev (10 \gev) and 100 \gev for the sources found using photons above 1 \gev (10 \gev).
-      }
+      sources $(\glon_1,\glat_1)$ and $(\glon_2,\glat_2)$.  The change
+      in likelihood and spectral values are then computed using \gtlike
+      with the best fit positions found by \pointlike.  \tsinc is the
+      increase in TS fitting the region as two sources compared to
+      fitting compared to fitting a single point source and is computed
+      using \gtlike with the best fit positions taken from \pointlike.
+      It can be directly compared to \tsext, which is taken from table~\ref{new_ext_srcs_table}.  For all of our candidates, $\tsext > \tsinc$
+      which shows that an extended source fits the source better than two
+      point sources.  As in table~\ref{known_extended_sources}, flux is
+      measured in units of $10^{-9}\ph/\cm^2/\sec$ and is the integral
+      flux between 1 \gev (10 \gev) and 100 \gev for the sources found
+      using photons above 1 \gev (10 \gev).}
     \end{centering}
@@
         \hline
-        P72Y2516             &                155.0 &                139.2 &                103.8 &                     38.5 &                   28.9 &                 22.5 & $  0.41\deg \pm   0.05\deg$ & $  0.38\deg \pm   0.04\deg$ \\
-        P72Y2405             &                108.4 &                148.8 &                138.4 &                     25.7 &                   77.6 &                 40.6 & $  0.49\deg \pm   0.04\deg$ & $  0.51\deg \pm   0.04\deg$ \\
-        P72Y1212             &                329.5 &                314.6 &                345.6 &                     60.4 &                   49.2 &                 51.5 & $  0.37\deg \pm   0.03\deg$ & $  0.38\deg \pm   0.03\deg$ \\
+        2FGL J1627.0-2425c   &                155.0 &                139.2 &                103.8 &                     38.5 &                   28.9 &                 22.5 & $  0.41\deg \pm   0.05\deg$ & $  0.38\deg \pm   0.04\deg$ \\
+        2FGL J1551.3-5333c   &                108.4 &                148.8 &                138.4 &                     25.7 &                   77.6 &                 40.6 & $  0.49\deg \pm   0.04\deg$ & $  0.51\deg \pm   0.04\deg$ \\
+        2FGL J0823.0-4246    &                329.5 &                314.6 &                345.6 &                     60.4 &                   49.2 &                 51.5 & $  0.37\deg \pm   0.03\deg$ & $  0.38\deg \pm   0.03\deg$ \\
         \hline
@@
         \hline
-        P72Y2473             &                 74.7 &                 75.3 &                 88.7 &                     43.7 &                   45.2 &                 50.0 & $  0.52\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
-        P72Y2540             &                173.9 &                173.0 &                157.7 &                     97.9 &                   95.3 &                 93.6 & $  0.65\deg \pm   0.03\deg$ & $  0.66\deg \pm   0.03\deg$ \\
-        P72Y3281             &                244.9 &                245.7 &                264.3 &                    152.8 &                  151.7 &                162.9 & $  0.71\deg \pm   0.04\deg$ & $  0.71\deg \pm   0.03\deg$ \\
-        P72Y2979             &                 43.4 &                 47.3 &                 39.0 &                     17.4 &                   20.6 &                 17.7 & $  0.35\deg \pm   0.07\deg$ & $  0.34\deg \pm   0.06\deg$ \\
-        P72Y1287             &                117.1 &                119.6 &                124.7 &                     86.1 &                   90.9 &                 95.0 & $  1.15\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
+        2FGL J1615.2-5138    &                 74.7 &                 75.3 &                 88.7 &                     43.7 &                   45.2 &                 50.0 & $  0.52\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
+        2FGL J1632.4-4753c   &                173.9 &                173.0 &                157.7 &                     97.9 &                   95.3 &                 93.6 & $  0.65\deg \pm   0.03\deg$ & $  0.66\deg \pm   0.03\deg$ \\
+        2FGL J2019.1+4040    &                244.9 &                245.7 &                264.3 &                    152.8 &                  151.7 &                162.9 & $  0.71\deg \pm   0.04\deg$ & $  0.71\deg \pm   0.03\deg$ \\
+        2FGL J1834.7-0705c   &                 43.4 &                 47.3 &                 39.0 &                     17.4 &                   20.6 &                 17.7 & $  0.35\deg \pm   0.07\deg$ & $  0.34\deg \pm   0.06\deg$ \\
+        2FGL J0851.7-4635    &                117.1 &                119.6 &                124.7 &                     86.1 &                   90.9 &                 95.0 & $  1.15\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
         \hline
@@
       There is very good agreement between the two methods.
-%&        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
       }

### 2011-07-10 extended_catalog/paper/extended_catalog.tex
better plots

@@
 \usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
-
-% TODO:
-%  how to format power-law, power-law, power law?
 
@@
 We present a new method for analyzing spatially extended sources with
-the Fermi Large Area Telescope (LAT), the primary science instrument
+the Large Area Telescope (LAT), the primary science instrument
 on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
-series of Monte Carlo studies that validate this tool.
-We then calculate the Fermi LAT's sensitivity to spatially extended
+series of Monte Carlo studies that validate this tool
+and calculate the LAT's detection threshold to spatially extended
 sources.  We then use this tool to test all sources in the two
@@
 \section{Analysis Method}
+
+\todo[inline]{Add note about how we had to delete nearby sources
+which were not hard above 10GeV for analysis to converge.}
 
@@
 
-\section{Extended Source Sensitivity}\label{extension_sensitivity}
-
-We performed a second study to determine the LAT's sensitivity
-to spatially extended sources. The sensitivity to extension
+\section{Extended Source Detection Threshold}\label{extension_sensitivity}
+
+We performed a second study to determine the LAT's detection threshold
+to spatially extended sources. The detection threshold to extension
 is defined as the flux at which the average value of
@@
 
-To calculate the LAT's sensitivity to spatially extended sources,
+To calculate the LAT's detection threshold to spatially extended sources,
 we simulated sources with a uniform radially symmetric disk
@@
 
-Figure~\ref{index_sensitivity} shows the extension sensitivity for
+Figure~\ref{index_sensitivity} shows the threshold for
 sources of different spectral indices and extensions.  We selected
@@
 on the plot represent the division in extension and flux space where
-$\langle\tsext=25\rangle$.  The plot shows by the sensitivity using all
-photons with energy between 100 \mev and 100 \gev and the sensitivity
+$\langle\tsext=25\rangle$.  The plot shows the threshold using all
+photons with energy between 100 \mev and 100 \gev and the threshold
 using only photons with energy between 1 \gev and 100 \gev.  This results
-shows that the LAT's sensitivity to extension is better for harder sources
-with more high energy photons. The sensitivity is best for sources with
+shows that the LAT's threshold to extension is better for harder sources
+with more high energy photons. The threshold is best for sources with
 an extension around $0.5\deg$ and is worse for small and large sources.
 
-Except for the hardest and largest sources, our sensitivity is almost
+Except for the hardest and largest sources, our detection threshold is almost
 unchanged when using events between 100 \mev and 1 \gev.  This is also
@@
 Figure~\ref{diff_factor_sensitivity} shows how the LAT's
-sensitivity varies with increasing background, typical of sources
-at lower galactic latitude. We compute the sensitivity for spectral
+detection threshold varies with increasing background, typical of sources
+at lower galactic latitude. We compute it for spectral
 index 2 sources using 10 and 100 times the
@@
 the galactic diffuse emission near the galactic center. 
-The figure shows two plots, the first showing the sensitivity looking only between 
-1 \gev and 100 \gev and the second showing the sensitivity looking only
+The figure shows two plots, the first showing the threshold looking only between 
+1 \gev and 100 \gev and the second showing the threshold looking only
 between 10 \gev and 100 \gev.
 For each plot, the $y$ axis quotes the flux in the selected energy range
-which weaken the dependence of the sensitivity on spectral index.
+which weaken the dependence of the detection threshold on spectral index.
 This shows that we are less sensitive to extended sources in
@@
 statistically significant sources that are detected in the \gev
-sky\cite{second_cat}.  The catalog group's source finding method assumes
+sky (\cite{second_cat}).  The catalog group's source finding method assumes
 that the emission originated as point sources and what was presented was
@@
 % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
+% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
 % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
@@
 % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
-% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
+% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
+% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
 % N/A                - P72Y1287         - 2FGL J0851.7-4635
@@
 
-\subsection{2FGL J1551.3-5333c}
-
-% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
+\subsection{2FGL J1554.4-5317c}
+
+% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
 % Sources that had to be deleted
-%   * P72Y2416 - 2FGL J1554.4-5317c
+%   * P72Y2416 - 2FGL J1551.3-5333c
 %   * P72Y2422 - Not a 2FGL source
 
-The two year catalog source 2FGL J1551.3-5333c was found to be
+The two year catalog source 2FGL J1554.4-5317c was found to be
 extended using photons with energy between 1 \gev and 100 \gev.
@@
 To get a good fit of the source, we had to remove the nearby catalog
-sources 2FGL J1554.4-5317c which we believed to be suprious. By looking at
+source 2FGL J1551.3-5333c
+which we believed to be suprious. By looking at
 the counts map, we saw no differentation in the source at the location
@@
 % Deleted
-%  *P72Y2490 - 2FGL J1520.6-5111c
+%  *P72Y2490 - 2FGL J1620.6-5111c
 %  *P72Y2487 - 2FGL J1619.7-5040c
@@
 
-\subsection{2FGL J2019.1+4040}
+\subsection{2FGL J2021.5+4026}
 
@@
 
-% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
+% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
 % Delete:
-% * P72Y3287 - 2FGL J2021.5+4026
+% * P72Y3282 - 2FGL J2019.1+4040
+% * P72Y3287 - 2FGL J2020.0+4159
 % * P72Y3262 - 2FGL J2013.8+4115c
-% * P72Y3282 - 2FGL J2020.0+4159
 % * P72Y3260 - 2FGL J2012.4+3955c
@@
 Describe how this source is analyzed more carefully in the paper
-``A cocoon of freshly accelerated cosmic rays detected by Fermi
-in the Cygnus superbubble''}
+\cite{A cocoon of freshly accelerated cosmic rays detected by Fermi
+in the Cygnus superbubble}
+}
 
@@
 
-\subsection{2FGL J1834.7-0705c}
-
-% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
+\subsection{2FGL J1837.3-0700c}
+
+% 1FGL J1837.5-0659c - P72Y2986 - 2FGL J1837.3-0700c
+
 % Delete:
-% * P72Y2982 - Not a 2FGL source
-% * P72Y2986 - 2FGL J1837.3-0700c
+% * P72Y2979 - 2FGL J1835.5-0649
 % * P72Y2994 - 2FGL J1839.3-0558c
 % * P72Y2993 - 2FGL J1839.0-0539
+
 % Modify:
@@
 %              (initial Position - SkyDir(,)
-% * P72Y2974 - 2FGL J1834.7-0705c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
+% * P72Y2974 - 2FGL J1837.3-0700c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
 %              (initial Position - SkyDir(,)
@@
 % (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
-
 % Delete:
@@
     \end{center}
-    \caption{This is the LAT's sensitivity to spatially
+    \caption{This is the LAT's detection threshold to spatially
     extended sources. The $x$ axis is Monte Carlo extension of a
@@
     using photons with energy between 1 \gev and 100 \gev.
-    The sensitivity is for a one year simulation against a Sreekumar-like
+    The detection threshold is for a one year simulation against a Sreekumar-like
     isotropic background (\cite{sreekumar_isotropic}).
-    This plot shows that our sensitivity is best for sources that are
-    about $1\deg$ large. It also shows that for sources That are neither
+    This plot shows that our threshold is best for sources that are
+    about $1\deg$ large. It also shows that for sources that are neither
     very large nor very soft, our sensitivity is not significantly
@@
   % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-  % 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333c
+  % 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
   % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
@@
   % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
-  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705c
+  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
+  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
   % N/A                - P72Y1287         - 2FGL J0851.7-4635
@@
       2FGL J1627.0-2425c   &     353.08\deg &      16.80\deg & $  0.41\deg \pm   0.05\deg$ &    139.2 &       28.9 &  0.042\deg &  0.036\deg &   54.4\deg & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ \\
-      2FGL J1551.3-5333c   &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
+      2FGL J1554.4-5317c   &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
       2FGL J0823.0-4246    &     260.31\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &    314.6 &       49.2 &  0.026\deg &  0.023\deg &    5.0\deg & $    8.3 \pm     0.3$ & $   2.18 \pm    0.02$ \\
@@
       2FGL J1632.4-4753c         &     336.52\deg &       0.06\deg & $  0.65\deg \pm   0.03\deg$ &    173.0 &       95.3 &  0.041\deg &  0.037\deg &    5.3\deg & $    2.9 \pm     0.2$ & $   2.28 \pm    0.08$ \\
-      2FGL J2019.1+4040          &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
-      2FGL J1834.7-0705c         &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
+      2FGL J2021.5+4026          &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
+      2FGL J1837.3-0700c         &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
       2FGL J0851.7-4635          &     266.29\deg &      -1.43\deg & $  1.15\deg \pm   0.08\deg$ &    119.6 &       90.9 &  0.080\deg &  0.065\deg &   54.6\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.18$ \\
@@
         2FGL J1627.0-2425c   &       23.8 &       28.9 &     353.04\deg &      16.96\deg & $       3.5 \pm        0.6$ & $  2.7 \pm   0.3$  &     353.14\deg &      16.50\deg & $       2.0 \pm        0.5$ & $  2.4 \pm   0.3$ \\
-        2FGL J1551.3-5333c   &       48.6 &       77.6 &     328.31\deg &       0.31\deg & $      10.0 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.28\deg &      -0.06\deg & $       1.0 \pm        0.7$ & $  1.6 \pm   0.4$ \\
+        2FGL J1554.4-5317c   &       48.6 &       77.6 &     328.31\deg &       0.31\deg & $      10.0 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.28\deg &      -0.06\deg & $       1.0 \pm        0.7$ & $  1.6 \pm   0.4$ \\
         2FGL J0823.0-4246    &       22.2 &       49.2 &     260.59\deg &      -3.26\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
@@
         2FGL J1632.4-4753c   &       24.8 &       95.3 &     336.16\deg &       0.34\deg & $       0.7 \pm        0.1$ & $  2.0 \pm   0.4$  &     336.72\deg &      -0.06\deg & $       0.7 \pm        0.1$ & $  3.1 \pm   0.5$ \\
-        2FGL J2019.1+4040    &       34.5 &      151.7 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.45\deg &       2.54\deg & $       0.5 \pm        0.1$ & $  1.9 \pm   0.4$ \\
-        2FGL J1834.7-0705c   &       15.4 &       20.6 &      25.06\deg &       0.24\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.6$  &      25.08\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.6$ \\
+        2FGL J2021.5+4026    &       34.5 &      151.7 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.45\deg &       2.54\deg & $       0.5 \pm        0.1$ & $  1.9 \pm   0.4$ \\
+        2FGL J1837.3-0700c   &       15.4 &       20.6 &      25.06\deg &       0.24\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.6$  &      25.08\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.6$ \\
         2FGL J0851.7-4635    &       32.5 &       90.9 &     267.16\deg &      -1.60\deg & $       0.2 \pm        0.1$ & $  1.9 \pm   0.4$  &     266.43\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.5$ \\
@@
         2FGL J1627.0-2425c   &                155.0 &                139.2 &                103.8 &                     38.5 &                   28.9 &                 22.5 & $  0.41\deg \pm   0.05\deg$ & $  0.38\deg \pm   0.04\deg$ \\
-        2FGL J1551.3-5333c   &                108.4 &                148.8 &                138.4 &                     25.7 &                   77.6 &                 40.6 & $  0.49\deg \pm   0.04\deg$ & $  0.51\deg \pm   0.04\deg$ \\
+        2FGL J1554.4-5317c   &                108.4 &                148.8 &                138.4 &                     25.7 &                   77.6 &                 40.6 & $  0.49\deg \pm   0.04\deg$ & $  0.51\deg \pm   0.04\deg$ \\
         2FGL J0823.0-4246    &                329.5 &                314.6 &                345.6 &                     60.4 &                   49.2 &                 51.5 & $  0.37\deg \pm   0.03\deg$ & $  0.38\deg \pm   0.03\deg$ \\
@@
         2FGL J1632.4-4753c   &                173.9 &                173.0 &                157.7 &                     97.9 &                   95.3 &                 93.6 & $  0.65\deg \pm   0.03\deg$ & $  0.66\deg \pm   0.03\deg$ \\
-        2FGL J2019.1+4040    &                244.9 &                245.7 &                264.3 &                    152.8 &                  151.7 &                162.9 & $  0.71\deg \pm   0.04\deg$ & $  0.71\deg \pm   0.03\deg$ \\
-        2FGL J1834.7-0705c   &                 43.4 &                 47.3 &                 39.0 &                     17.4 &                   20.6 &                 17.7 & $  0.35\deg \pm   0.07\deg$ & $  0.34\deg \pm   0.06\deg$ \\
+        2FGL J2021.5+4026    &                244.9 &                245.7 &                264.3 &                    152.8 &                  151.7 &                162.9 & $  0.71\deg \pm   0.04\deg$ & $  0.71\deg \pm   0.03\deg$ \\
+        2FGL J1837.3-0700c   &                 43.4 &                 47.3 &                 39.0 &                     17.4 &                   20.6 &                 17.7 & $  0.35\deg \pm   0.07\deg$ & $  0.34\deg \pm   0.06\deg$ \\
         2FGL J0851.7-4635    &                117.1 &                119.6 &                124.7 &                     86.1 &                   90.9 &                 95.0 & $  1.15\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
@@
   \todo[inline]{Describe this source better. Add in Contour}
+  \todo[inline]{Note about why the top right source was not found to
+  be extended b/c the scale is cut.}
   }\label{1FGL_J1837.5-0659c}

### 2011-07-10 extended_catalog/paper/extended_catalog.tex
Typos

@@
 on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
-series of Monte Carlo studies that validate this tool
+series of Monte Carlo studies to validate this tool
 and calculate the LAT's detection threshold to spatially extended
-sources.  We then use this tool to test all sources in the two
+sources.  We then apply this tool to test all sources in the two
 year source catalog for extension and report on the discovery
@@
 instrument because of its broad energy coverage (20 \mev
-to $>300$ \gev), wide field of view ($\sim 2.4 \sr$) and large effective
+to $>300$ \gev), wide field of view ($\sim 2.4 \sr$), and large effective
 area ($\sim 8000 \cm^2$ at $>1 \gev$).
@@
 The LAT collaboration has previously reported on the discovered
-a variety of spatially extended supernova remnants (SNRs)
-IC443 and W51C, pulsar wind nebulae (PWNe) MSH 15-52 and Vela X
-(\cite{ic443,w51c,msh1552,velax}), and galaxies the Large Magellanic
-Cloud and the Small Magalenic Cloud (\cite{lmc,smc}.  There are other
+a variety of spatially extended including the supernova remnants (SNRs)
+IC443 and W51C (\cite{ic443,w51c}),
+the pulsar wind nebulae (PWNe) MSH 15-52 and Vela X
+(\cite{msh1552,velax}), and the Large Magellanic
+and the Small Magalenic Cloud (\cite{lmc,smc}).  There are other
 source classes which could possibly be spatially resolved by the LAT
@@
 
-Being able to spatially resolve a LAT source is important for several
-reasons. Most importantly, the spatial morphology can be used to
-help identify the source at other wavelengths. Because of the large
-point spread function (PSF), there are often several possible source
-counterparts.  Finding a matching morphology can uniquely identify
-the source.
-
+Being able to spatially resolve the \gev emission from a source is
+important for several reasons. Because of the large point spread
+function (PSF), there are often several possible source counterparts.
+Finding a matching morphology can be used to uniquely identify the source.
 Because of the largely varying PSF of the LAT, the spatial and spectral
-model of a source do not nicely decouple. Therefore, spatially resolving
-a LAT source is also important for obtaining an unbiased spectrum.
-Furthermore, correctly modeling a source's extension is important for
-improved the overall model of the sky and removing excess residuals.
-These residuals around catalog sources can lead to finding spurious nearby
-point sources. This was found to be the case with the one year catalog
-in the region surrounding the Large Magellanic Cloud (\cite{first_cat}).
-
-\section{Analysis Method}
-
-\todo[inline]{Add note about how we had to delete nearby sources
-which were not hard above 10GeV for analysis to converge.}
+information about a source do not nicely decouple. Therefore, a biased
+spatial model will bias the spectral model of the source and studyign
+the extension of the source can correct for htis.  Furthermore, correctly
+modeling a source's extension is important for improving the overall model
+of the sky and removing excess residuals.  These residuals manifested
+themseleves in the one year catalog as spurious point sources in the
+region region surrounding the Large Magellanic Cloud (\cite{first_cat}).
+
+\section{Analysis Methods}
 
@@
 Therefore, the higher energy photons are significantly more important for
-resolving a source but are limited by statistics. Therefore,
-a detailed analysis procedure mused be used to maximize our
-sensitivity.
+resolving a source but are typically limited by statistics. 
+A detailed analysis procedure must be used to maximize our
+sensitivity over all energies.
 
@@
 provides a maximum likelihood analysis where the Poisson likelihood
-for observing the measured counts is computed is maximized by fitting
+for observing the measured counts is maximized by fitting
 parameters of the model.  The extension of a source can be modeled by a
 geometric shape (e.g. a disk or Gaussian) and the source's position
-and extension can simultaneously fit by maximizing the likelihood.
-
-This analysis is not very feasible using the official LAT likelihood
+and extension can be simultaneously fit.
+
+This analysis is not feasible using the official LAT likelihood
 analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
-Fermi Science Support Center\cite{fssc}} because \gtlike is only able to
-fit the spectral parameters of the source. The extension fitting would
-have to be done as an external loop outside of the code. Typically, the
+Fermi Science Support Center (\cite{fssc})} because \gtlike can only 
+fit the spectral parameters of the model. The extension fitting would
+have to be done as an external loop. Typically, the
 run time for a binned source analysis using \gtlike is several hours
@@
 been done to study an extended sources is to fix the position of the
-extended source and then develop a profile of the likelihood as a
-function of the extension.  This approach is not optimal because the
+source and develop a profile of the likelihood as a
+function of extension.  This approach is not optimal because the
 position and extension of the source should be simultaneously maximized
-to find the best fit parameters.  Furthermore since this approach is
-very computationally intensive, no large scale Monte Carlo effort can
-be launched to validate it.
-
-An alternate approach was developed for fitting spatially extended
-sources.  An alternate maximum likelihood fitting package called
-\pointlike has been developed by the Fermi collaboration and we have
+to find the best fit parameters and to correctly compute the statistical
+significance of the detection.  Furthermore since this approach is
+computationally intensive, no large scale Monte Carlo effort can
+be run to validate it.
+
+We developed an alternate approach to fit spatially extended
+sources. A separate maximum likelihood fitting package called
+\pointlike has been developed by the LAT collaboration and we have
 added to it the ability to analyze spatially extended sources. \pointlike
-is described in the one year catalog and in Matthew Kerr's Ph.D thesis
+is described in the one year catalog paper and in Matthew Kerr's Ph.D thesis
 (\cite{first_cat,matthew_kerr_thesis}).
@@
 emphasis on speed by introducing approximations into the calculation
-of the likelihood function.  This is done while at the same time
-trying to minimized the introduced numerical errors.  Like the binned
-version of \gtlike, \pointlike bins the sky both in position and energy.
-Unlike \gtlike, \pointlike relies on the {\em healpix} representation of
-spatial bins (\cite{healpix}). Since the PSF changes significantly with
-energy, the spatial size of each bin for a given energy is calculated
-to be smaller than than the PSF. This ensures that little information
-is lost at each energy level while minimizing the overall number of bins.
+of the likelihood function while trying to minimized the introduced
+numerical errors.  Like the binned version of \gtlike, \pointlike bins
+the sky in both position and energy.  Unlike \gtlike, \pointlike relies on
+the {\em healpix} representation of spatial bins (\cite{healpix}). Since
+the PSF changes significantly with energy, the spatial size of each bin
+is calculated to be smaller than than the PSF. By changing the spatial
+bin size with energy, \pointlike ensures that little information is lost
+at each energy while minimizing the required number of bins.
 
@@
 
+\todo[inline]{Add note about how we had to delete nearby sources
+which were not hard above 10GeV for analysis to converge.}
+
 The LAT two year catalog presented a search for all

### 2011-07-13 extended_catalog/paper/extended_catalog.tex
more revisions

@@
 
-\pointlike also bins $\gamma$-rays depending upon whether they
-convert in the front or back parts of the detector. Since the PSF
-is smaller for front entering photons, binning each conversion type
-independently improves the tool's sensitivity.
-Furthermore, \pointlike uses a sparse matrix representation of the spatial
-bins where only the bins with counts in them are used. \pointlike
-then independently integrates the overall model predicted counts in the region.
-
-The intelligent binning and sparse matrix representation of the data
+\pointlike also bins $\gamma$-rays depending upon whether they convert
+in the thin or thick layers of the tracker. Since the PSF is smaller for
+front entering photons, by binning each conversion type independently,
+\pointlike improves the overall sensitivity.  Furthermore, \pointlike
+uses a sparse matrix representation of the spatial bins where only the
+bins with counts in them are used. To evaluate the likelihood, \pointlike
+then independently integrates the model predicted counts in the region.
+
+Intelligent binning and a sparse matrix representation of the data
 effectively interpolates between a binned analysis at low energy (where
@@
 analysis at high energy (where the resolution is good but there are
-few counts). This approach provides a significant savings in time while
-introducing small numerical error.
+few counts). This approach provides significant savings in time while
+introducing only small numerical error.
 
@@
 of \python modules, advanced functions including extension fitting
-(described in section~\ref{extesion_fitting}) and a dual localization
-(described in section~\ref{dual_localization_method}) could be quickly
-added on top of the core functionality.
+(section~\ref{extension_fitting}) and dual localization
+(section~\ref{dual_localization_method}) could be quickly
+built on top of the core functionality.
 
@@
 
-We modified \pointlike to allow modeling the spatial extension of
+We modified \pointlike to allow modeling the spatial extension 
 of a source. It is assumed that the spatial and spectral information
@@
 source shape with the PSF (as a function of energy) when computing the
-model predicted counts in a bin.
-
-\pointlike uses the \minuit fitting library to simultaneously maximize
-the likelihood by fitting the position and extension of an extended
+model predicted counts.
+
+\pointlike uses the \minuit fitting library to maximize the likelihood
+by simultaneously fitting the position and extension of an extended
 source (\cite{minuit_documentation}).  As will be described in
-section~\ref{monte_carlo_validation}, the statistical significance
-of the detection of an extended source can only be correctly calculated
-when all of the parameters of a model are simultaneously fit
-
+section~\ref{monte_carlo_validation}, this simultaneous fitting
+is necessary to correctly calculating the statistical significance
+of the detection of extension.
 For each position and extension,
@@
 the source but instead the displacement in a rotated reference frame.
+
 The significance of the extension of a source can be calculated from
 \tsext, which is defined as twice the increase in log likelihood between
-the extended source model at its best fit values and the
-point source model at its best fit values:
+the extended source model at its best fit values and the point source
+model at its best fit values:
 \begin{equation}
@@
 \end{equation}
-The interpretation of \tsext in terms of a statistical significance is
-discussed in section~\ref{monte_carlo_validation}.
-
-The extended source code is speed up in two ways. First, the convolution
-of the spatial shape of a radially symmetric extended source with the PSF is
-done semi-analytically. The observed photon
-distribution can be written as the convolution of the source shape ($I_\text{src}$)
+\pointlike calculates \tsext by fitting a source first with a spatially
+extended model and then as a point source.  The interpretation
+of \tsext in terms of a statistical significance is discussed in
+section~\ref{monte_carlo_validation}.
+
+The convolution of radially symmetric extended sources is optimized by
+using a semi-analytic calculation.  The observed photon distribution
+can be written as the convolution of the source shape ($I_\text{src}$)
 with the psf
@@
 \end{equation}
-The PSF is parameterized by
+For the LAT, the PSF is parameterized as
 \begin{equation}
@@
 \end{equation}
-where $\sigma$ and $\gamma$ have been found empirically as a function
-of energy.  For radially symmetric
+where $\sigma$ and $\gamma$ are free parameters.  For radially symmetric
 extended sources, the angular part of the integral can be done analytically
-leaving a easier one dimensional integral:
 \begin{equation}
@@
 \end{equation}
-This convolution formula is faster and more closely reduces to the PSF
-when the source's size is very small. Decreasing this the numerical
-error is important when evaluating the statistical significance of a
-source's extension.
-
-The other approximation is to ignore the dependence of the PSF on the
-incident angle of a $\gamma$-ray.  Generally, the PSF is a function
-of the incident angle of a photon measured with respect to the LAT.
-To avoid multiple convolutions of the source shape with the PSF, an
-effective PSF is calculated by weighted the PSF for different incident
-angles.  Since the convolution has to be done at each iteration of the
-extension fit, these approximations were necessary to make the tool run
-in a reasonable amount of time.
+This convolution formula is used by \pointlike because it is faster
+and more closely reduces to the PSF when the source's size is 
+small.
 
@@
 Errors on fit parameters are typically calculated in one of two
-ways. The first method requires explicitly varying one parameter
-until the log of the likelihood has fallen by a particular value while
-simultaneously optimizing the other fit parameters. The \minuit fitting
+ways. The first method requires explicitly varying a parameter
+while simultaneously optimizing the other parameters.
+until the log of the likelihood has fallen by a particular value.
+The \minuit fitting
 package provides the {\em Simplex} function to calculate errors this way
@@
 curvature of the log of the likelihood at the peak to estimate when the
-function will fall by the same value. \minuit provides the {\em HESSE}
-algorithm to calculate errors this way.  The {\em HESSE} errors are
-significantly faster but are only approximately true.
-
-We found that the {\em HESSE} algorithm would sometimes badly
-underestimate the errors on the extension of the source.  On the other
+function will decrease by the desired value. \minuit provides the {\em HESSE}
+algorithm to calculate errors this way.  {\em HESSE} errors 
+can be calculated significantly faster.
+
+We found that the {\em HESSE} errors on the extension of a source
+were sometimes badly estimated.  On the other
 hand, the {\em Simplex} algorithm was prohibitively slow and would often
-fail to convergence. \pointlike's approach to calculating extension errors
-is to fixing all the spatial parameters and varying just the extension
-until the likelihood has fallen by the desired amount.  This approach
+fail to convergence. Our approach to calculating extension errors
+is to fix the position of the source and varying just the extension
+using the {\em Simplex} algorithm.  This approach
 makes the approximation that the covariance between each spatial parameter
@@
 is shown schematically in figure~\ref{extension_profile} which shows
-the change in log likelihood when varying the fit extension of
+the change in log likelihood when varying the extension of
 the SNR IC443.
-
-The localization error is then calculated by fixing the extension to the
+The localization error separately calculated by fixing the extension to the
 best fit value and fitting an ellipse to the likelihood as a function
-of the spatial parameters.  This fit can be used to calculate an
-elliptical localization error which correctly accounts for covariance
-between the two position coordinates.  This same method is used to
-calculate the localization error of all point sources in the LAT catalog
+of the spatial parameters. This
+elliptical localization error correctly accounts for the covariance
+in the position of the source and this same me method is used to
+calculate the localization error of all point sources in the first LAT catalog
 (\cite{first_cat}).
@@
 
-Because of its computational speed, \pointlike is important for analysis
+\pointlike is important for LAT analysis
 that require many iterations such as source localization and extension
-fitting.  On the other hand, we expect \gtlike to get a slightly
-more precise answer for fitting the spectral parameters of a source.
+fitting.  On the other hand, we expect that the spectral paramaters
+fit by \gtlike to be slightly more precise.
 Furthermore, because \gtlike is the standard likelihood analysis package,
 it has been more extensively validated for spectral analysis.
-
 For that reason, in the following analysis we took the best fit
-positions and extensions of the source model fit by \pointlike but
-refit the spectral spectral parameters of the model using \gtlike.
-\gtlike provides a second calculation of the likelihood which gives a
-second measure of \ts and \tsext.
+position and extension found by \pointlike and
+refit the spectral spectral parameters using \gtlike.
+\gtlike also provides a second calculation of the likelihood which gives a
+second measure of \ts and \tsext. We do not consider a source to be
+significant unless there is agreement between the two methods.
 
 We found very good agreement between the two methods. For the new
-extended source candidates, table~\ref{alt_diff_model_results} shows a
-comparison of \ts and \tsext computed using \pointlike and \gtlike. For
-the rest of this paper, unless otherwise stated all \ts, \tsext, and
-fit spectral parameters were found using \gtlike with the localization
-results computed by \pointlike.
+extended source candidates, table~\ref{alt_diff_model_results} shows
+a comparison of \ts and \tsext computed using \pointlike and \gtlike.
+Unless explicitly mentioned, all \ts, \tsext, and spectral parameters
+were calculated using \gtlike using \pointlike's positions and extensions.
 
@@
 point sources.  To assess the possibility of source confusion,
-we developed a function in \pointlike to simultaneously fit two point
-sources and compare the likelihood of two point sources to the likelihood
-of one extended source.
-
-The code uses \minuit to simultaneously fit the position of the two point
-sources.  To avoid projection effects, the fit is done in a coordinate
-system rotated to the celestial equator.  Instead of directly fitting
-the rotated coordinates $x_1$ and $x_2$, we decided there would be less
-covariance by fitting instead the sum and difference of the rotated
+we developed a function in \pointlike to simultaneously fit 
+the position of two point sources.
+The code uses \minuit to fit the position of the two point
+sources.  To avoid projection effects, the fit is done in a rotated coordinate
+system.  To improve the robustness of the fit, Instead of directly fitting
+the rotated coordinates $x_1$ and $x_2$ we instead
+fit the sum and difference of the rotated
 coordinates $S=(x_1+x_2)/2$ and $D=(x_2-x_1)/2$.  The log likelihood
-$L(S,D)$ is maximized by fitting the sum and difference of the two point
+is then maximized by fitting the sum and difference of the 
 sources.  Because of \pointlike's computational efficiency, this algorithm
-runs in a reasonable amount of time. Similar to extension described in
-section~\ref{gtlike_crosscheck}, the spectrum of can be refit using \gtlike
-at the best fit positions.
-
-We can define the parameter \tsinc as twice the increase in log likelihood
-fitting the region with two point sources compared to fitting the region
-with one point source:
+runs in a reasonable amount of time.
+
+We define \tsinc as twice the increase in log likelihood
+fitting the region as two point sources compared to fitting the region
+as one point source:
 \begin{equation}
@@
 \end{equation}
-A straightforward likelihood ratio test between the two point source
-model and the extended source model because the models are note nested.
-
-\tsinc can not be directly compared to \tsext to see which model is better
+\tsinc can not be directly compared to \tsext to see which model is 
+more significant
 because the models are not nested (\cite{statistics_with_care}). Even
 though the comparison of \tsext with \tsinc is not a calibrated test,
-we find the extreme cases where $\tsinc \ll \tsext$ or $\tsinc\gg\tsext$
-to be suggestive and use this as a test for source confusion. For the
-spatially extended candidates found, we computed both \tsext and \tsinc.
-The results are presented in table~\ref{dual_localization_results}
+we find the extreme cases $\tsinc \ll \tsext$ or $\tsinc\gg\tsext$
+to be suggestive and we only consider a source to be extended if
+$\tsext>\tsinc$.
+
+Like extended sources described in section~\ref{gtlike_crosscheck},
+the spectrum of the two point sources can be refit using \gtlike. we quote
+the spectral values obtained from \gtlike using the best fit positions
+found using \pointlike.  For the extended candidates found by our search,
+we computed both \tsext and \tsinc.  The results are presented in
+table~\ref{dual_localization_results}.
 
@@
 
-An extended source must be modeled with a spatial shape.
-The convolution of that shape with the PSF is fit to the data.
-Possible choices for spatial models include a two dimensional Gaussian
+The spatial shape of extended soruces can e modeled
+as a two dimensional Gaussian
 \begin{equation}
@@
 \end{equation}
-Although these shapes are significantly different, the
-convolution of them with the PSF for typical sizes look very
-similar.
-
-This is demonstrated in figure~\ref{compare_disk_gauss}.  It shows the
-PSF that would be observed for a power-law source of spectral index two,
-the probability density function (PDF) for a Gaussian and uniform disk of width
-$0.5\deg$, and the PDF for the same Gaussian
-and uniform disk convolved with the PSF.  The figure shows the analysis
-using an energy range between 1 \gev and 100 \gev and using an energy
-range between 10 \gev and 100 \gev.  The convolved shape of the disk and
-Gaussian do separate better at higher energy where the PSF is narrower.
-This plot shows that the LAT is not very sensitive to probing different
-kinds of extended sources.  In this paper we always fit with uniform disk
-spatial models.
-
-To get the convolved disk and Gaussian shapes to match in
-figure~\ref{compare_disk_gauss}, we had to set them to predict
-a 68\% containment radius of 0.5\deg.  The 68\% containment
-radius for a spatial model is the radius at which 68\% of the
-intensity is enclosed.  It can be computed by a straightforward
-integral and we find that $\rsixeight_\text{,disk}=0.82\sigma$
-whereas the $\rsixeight_\text{,Gaussian}=1.51\sigma$. Therefore, in
-figure~\ref{compare_disk_gauss} the uniform disk has
-$\sigma=0.41\deg$ whereas the Gaussian has 
+Although these shapes are significantly different, the convolution
+of them with the PSF for typical sizes look very similar.  Even
+though these shapes are significantly different, we demonstrate in
+figure~\ref{compare_disk_gauss} that the convolution of shows the
+PSF that would be observed for a power-law source of spectral index
+2, the probability density function (PDF) for a Gaussian and uniform
+disk of width $0.5\deg$, and the convolution of this PDF with the PSF.
+The figure shows the convolution for the PSF in the energy range between
+1 \gev and and 100 \gev and also in the energy range between 10 \gev and
+100 \gev.  The convolved shapesdo separate better at higher energy, but
+nevertheless this plot shows that we are not very sensitive to probing
+the exact structure of an extended source.  In this paper we always
+assume a uniform disk spatial model.
+
+To get the convolved shapes to match in figure~\ref{compare_disk_gauss},
+we had to set them to predict the same 68\% containment radius of 0.5\deg.  The
+68\% containment radius for a spatial model is the radius at which 68\%
+of the intensity is enclosed.  It can be computed by a straightforward
+integral and we find that $\rsixeight_\text{,disk}=0.82\sigma$ whereas the
+$\rsixeight_\text{,Gaussian}=1.51\sigma$.  Since $\rsixeight=0.5\deg$,
+the uniform disk has $\sigma=0.41\deg$ whereas the Gaussian has
 $\sigma=0.75\deg$.
 
-Overlaying fit sizes on top of counts maps can be misleading.
-This effect can best be seen in figure~\ref{compare_r68} which shows
-an extended source simulated in the energy range from 1 \gev to 100
-\gev with a uniform disk spatial model. The simulated source has a size
-$\sigma=0.5\deg$, an integral flux between 1 \gev and 100 \gev of $3\times
-10^{-8}\ph/\cm^2/\sec$, and a spectral index 2.  To reduce Poisson noise,
-the counts map in figure~\ref{compare_r68} is smoothed by a 0.1\deg
-Gaussian kernel. Overlaid on the plot is the fit extension assuming the
-source has a uniform disk and a Gaussian spatial model.  The solid white
-line represents the best fit disk extension $\sigma_\text{disk}=0.496$
-The solid black line represents the best fit extension $\sigma$ for
-the Gaussian which was found to be $\sigma_\text{Gaussian}=0.2627$.
-The white and black dashed lines are the 68\% containment radius of
-the fit Disk and Gaussian respectively.  Even though the fit $\sigma$
-for the disk and uniform Gaussian seem very different, their 68\%
-containment radius are very similar ($\rsixeight_\text{,disk}=0.41$
-and $\rsixeight_\text{,Gaussian}=0.40$).
-
-This study shows that the extension $\sigma$ for different spatial
-models can be very different even when predicting almost the same PDF.
+This is important when comparing morphologies to other wavelengths
+because the quoted size can vary significantly depending on which quanity
+is reported.  This effect can be best seen in figure~\ref{compare_r68}
+which a counts map of an extended source simulated in the energy
+range from 1 \gev to 100 \gev with a uniform disk spatial model and
+$\sigma=05$. Overlaid on the plot is the fit extension assuming the
+source has a uniform disk and a Gaussian spatial model. The plot overlays
+both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly larger for
+the disk spatial hypothesis compared to the Gaussian spatial model. On
+the other hand, the disk and Gaussian's 68\% containment radius are
+very similar.
+
 Since we are not very sensitive to the particular morphology of an
-extended source, there is no correct choice for which shape to plot. For
-the following analysis, we use a uniform disk as our spatial model
-and overlay the disk's edge $\sigma$.  But due to smearing of the PSF,
+extended source, there is no correct choice for which size to quote
+or which shape to overlay. For the following analysis, we quite the
+disk's edge and overlay this size.  But due to smearing of the PSF,
 $\sigma$ typically looks larger than the observed counts distribution.
-When comparing the fit extensions with other wavelengths (especially \tev
-measurements of galactic sources), it is important to compare consistent
-values. If the assumed shapes are different, it is best to indirectly
-compare $rsixeight$.
+When comparing the fit extensions with other wavelengths, it is important
+to compare consistent quantities.
 
 \section{LAT Extended Source Validation}
-
-We validated \pointlike for extended source analysis using a series of
-Monte Carlo studies.
 
@@
 
-\tsext can be used to calculate the statistical significance of the
-source's extension.  Since the point and extended models are nested, we
-would always expect $\tsext>0$.  On the other hand, we would not expect
-the likelihood to change very much unless the source was significantly
-extended.  Since an extended source has one additional degree of freedom,
-Wilks' Theorem says that the distribution of $\tsext$ when testing
-a point source for extension should follow a $\chi^2_1$ distribution
-(\cite{wilks_theorem}).
+We validated \pointlike's extension fitting code with a Monte Carlo
+study. \tsext (defined in section~\ref{extension_fitting}) can be used to calculate the statistical significance
+of the extension of a source.  Since the point source and extended source models are
+nested, an extended source must always fit as well as a point source.  On the other hand, we would
+not expect the likelihood to change very much unless the source was
+significantly extended.  Since an extended source has one additional
+degree of freedom, Wilks' Theorem says that the distribution of $\tsext$
+when testing a point source for extension should follow a $\chi^2_1$
+distribution (\cite{wilks_theorem}).
 
@@
 \end{equation}
-Chernoff proved that under certain assumptions, this is the distribution
-that would hold when the null hypothesis lies on the edge of parameter
+Chernoff proved that under certain assumptions this is the correct distribution
+when the null hypothesis is on the edge of parameter
 space (\cite{chernoff}).  The false detection
@@
 
-The half $\chi^2_1$ distribution was found by a Monte Carlo study to hold
-for the special case of source finding of EGRET sources using a maximum
-likelihood analysis (\cite{mattox_egret}).  For half of the tests of a
-point source, statistical fluctuations would make the observed counts look
-narrower than the point spread function leading to $\tsext=0$. So it is
-reasonable to expect that a similar half $\chi^2_1$ would be appropriate
-for extension testing. We tested this hypothesis using a dedicated Monte
+The half $\chi^2_1$ distribution was found to hold for the special case
+of source finding using EGRET (\cite{mattox_egret}). This distribution
+is also plausable when testing point sources for extension. Due to
+statistical flucuations, half of the point sources might look narrower
+than the PSF leading to $\tsext=0$. The other half of the time, we would
+get a distribution consistent with Wilk's theorem. We used a Monte Carlo
+study to demonstrat that this is the observed distribution.
+ We tested this hypothesis using a dedicated Monte
 Carlo study.
-
-Before we show the Monte Carlo simulations, we have to bring up one issue
-we found with these tests.  Despite our best efforts, there was always
-a small numerical discrepancy between the likelihood when fitting the
-source as the PSF and when fitting it as a very small extended source
-with This is due to numerical error introduced by the convolution.
-In most situations, this error would be insignificant. But it does bias the
-distribution of \tsext in the null hypothesis. To correct for this,
-instead of computing the likelihood in the null hypothesis by fitting
-the PSF, we instead fit the null hypothesis as an extended source with
-the extension fixed to be very small.
 
@@
 consistent with the following analysis.
+
+Before we present the results of the Monte Carlo simulations, we have to
+bring up one issue we found with these tests.  Despite our best efforts,
+there was always a small numerical discrepancy between the likelihood when
+fitting the source as the PSF and when fitting it as a very small extended
+source with This is due to numerical error introduced by the convolution.
+In most situations, this error would be insignificant. But it does bias
+the distribution of \tsext in the null hypothesis. To correct for this,
+instead of computing the likelihood in the null hypothesis by fitting
+the PSF, we instead fit the null hypothesis as an extended source with
+the extension fixed to be very small.
 
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics{mc_plots/compare_disk_gauss.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
+    \end{center}
+    \caption{
+    This plot demonstrates that different spatial models when smoothed
+    by the PSF look very similar.  The $y$ axis is the log of the
+    intensity and the $x$ axis is $\theta^2$.  The black line is the
+    PSF that would be observed for a power-law source of spectral index
+    2. The dashed red line is the probability density of a Gaussian with
+    $\rsixeight=0.5\deg$, which is just a straight line on this plot
+    The dashed blue line is the probability density for a uniform disk
+    with $\rsixeight=0.5\deg$.  Finally, the solid red and blue lines
+    show the convolution of the Gaussian and uniform disk with the PSF.
+    The left plot shows the analysis with an energy range from 1 \gev to
+    100 \gev whereas the right plot shows the analysis with an energy
+    range from 10 \gev to 100 \gev.  This plot is discussed futher in
+    section~\ref{compare_source_size}
+    }\label{compare_disk_gauss}
+  \end{figure}
+
+  \begin{figure}
+    \begin{center}
+      \includegraphics{mc_plots/compare_r68.pdf}
+      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_r68/v2/plot.py
+      \end{center}
+      \caption{
+      This plot shows that fitting the same source with different spatial
+      shapes can lead to very different values of $\sigma$. On the other
+      hand, the different shapes have a good agreement about the 68\%
+      containment radius \rsixeight.  It shows counts map for a simulated
+      uniform disk extended source in the energy range from 1 \gev to
+      100 \gev.  The source has a size $\sigma=0.5\deg$, an integral flux
+      between 1 \gev and 100 \gev of $3\times 10^{-8}\ph/\cm^2/\sec$, and
+      a spectral index 2.  The smoothed counts from a point source with
+      the same spectrum are shown in the bottom right inset.  This source
+      was fit with both a uniform disk and a Gaussian spatial model.
+      The white circle represents the fit size $\sigma$ modeling the
+      source with a uniform disk spatial model.  The black circle is
+      the fit $\sigma$ modeling the source with a Gaussian hypothesis.
+      The dashed white and black circles are the fit \rsixeight for the
+      disk and Gaussian hypothesis. This plot is discussed furhter in
+      section~\ref{compare_source_size}
+      }\label{compare_r68}
+    \end{figure}
+
     \begin{table}
@@
     \caption{
-    This table presents a list of the spectral models (flux and spectral
-    index) used in the Monte Carlo study of \pointlike described in
-    section~\ref{monte_carlo_validation}.  For each spectral model, the
-    number of statistically independent simulations and the average test
-    statistic found for that given spectral model ($\langle\ts\rangle$) is tabulated.
-    The important feature in this table is that the Monte Carlo
-    simulation probes most of the sources parameters that could be detected
-    by the LAT.  The simulation probes a wide range of spectral indices
-    (from spectral index $\gamma$ of 1.5 to 3) and a wide range of the fluxes
-    (varying from a close to $5\sigma$ source detection to a $>10\sigma$
-    source detection).  Only simulations which produced statistically
-    significant detections ($\ts>25$) were kept.  What is quoted is the
-    $>100$ \mev integral flux measured in units of $\ph/\cm^2/\sec$.
-    More information about this Monte Carlo analysis is presented in
-    section~\ref{monte_carlo_validation}
+    This table presents a list of the spectral models (flux and
+    spectral index) used in the Monte Carlo study of \pointlike
+    described in section~\ref{monte_carlo_validation} and presented
+    in figure~\ref{ts_ext_mc}.  For each spectral model, the number of
+    statistically independent simulations and the average value of \ts
+    value ($\langle\ts\rangle$) is tabulated.  The Monte Carlo simulation
+    spans parameters representative of sources that could be detected
+    by the LAT.  The simulation is of spectral indices $\gamma$ of 1.5,
+    2, 2.5, and 3.  The simulation is of fluxes varying from a $5\sigma$
+    source detection to a $>10\sigma$ source detection.  Only simulations
+    which produced statistically significant detections ($\ts>25$)
+    were kept.  What is quoted is the $>100$ \mev integral flux measured
+    in units of $\ph/\cm^2/\sec$.  More information about this Monte
+    Carlo analysis is presented in section~\ref{monte_carlo_validation}.
     }
@@
     \caption{
-    \todo[inline]{Shorten this caption}
-    The results of the Monte Carlo simulation described in section
-    \ref{monte_carlo_validation} testing the null distribution of
-    the likelihood ratio test for extension.  The $x$ axis of this
-    plot is \tsext and the $y$ axis is the cumulative density for
-    \tsext that was found by testing simulated point sources of
-    various spectral models for extension. The four plots represent
-    different spectral indices (for $\gamma$ of 1, 2, 2.5, and 3).
-    The different colored lines represent different fluxes which were
-    chosen to span a representative range of values. The dashed
-    red line is the cumulative density function of $\chi^2(\ts)/2$ which is
-    suggested by Wilks' theorem as the theoretical distribution these
-    curves should should follow.  Overall, it should be noted that there
-    is a surprisingly good agreement between the Monte Carlo study and
-    the theoeretical distribution. And for most spectral parameters, the
-    Monte Carlo curve lies to the left of the theoretical curve, which
-    would imply that using Wilks' Theorem as the null distribution would
-    conservativly underestimate the signifcance of a source detection. In
-    the rest of the paper, we use this theoretical curve to estimate
-    the significance of our source detections.  What is quoted is the
-    $>100$ \mev integral flux in measured in units of $\ph/\cm^2/\sec$.
-    For each spectral model, more information about the simulations is
-    summarized in table~\ref{ts_ext_num_sims}. More
-    information about this Monte Carlo analysis is presented in
-    section~\ref{monte_carlo_validation}.
+    The results of the Monte Carlo simulation described
+    in section \ref{monte_carlo_validation} and detailed in
+    table~\ref{ts_ext_num_sims}. The plot shows the null distribution of
+    the likelihood ratio test when fitting a point source for extension.
+    The $x$ axis is \tsext and the $y$ axis is the cumulative density
+    for \tsext of simulated point sources. The four plots represent
+    different spectral indices and the different colors represent
+    different flxues.  The dashed red line is the cumulative density
+    function of $\chi^2(\ts)/2$ which is suggested by Wilks' theorem
+    as the distribution these curves should should follow.  There is
+    a surprisingly good agreement between the Monte Carlo results and
+    the theoeretical distribution. For most spectral parameters, the
+    Monte Carlo curve lies to the left of the theoretical curve which
+    would make the theoretical distribution more conservative.  In this
+    paper, we use this theoretical curve to estimate the significance of
+    our source detections. This plot cuts off three simulations of the
+    source with flux $3\times10^{-8}\ph/\cm^2/\sec$ and spectral index
+    2.5 which had \tsext of 26.1, 28.9, and 38.1.
     }\label{ts_ext_mc}
@@
     }\label{diff_factor_sensitivity}
-  \end{figure}
-
-  \begin{figure}
-    \begin{center}
-      \includegraphics{mc_plots/compare_disk_gauss.pdf}
-      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
-    \end{center}
-    \caption{
-    This plot demonstrates that different spatial models when smoothed
-    out by the PSF look very similar.  The $y$ axis is the log of the
-    intensity and the $x$ axis is $\theta^2$.  The black line is the
-    PSF that would be observed for a power-law source of spectral index
-    two. The dashed red line is the probability density of a Gaussian
-    of width $\rsixeight=0.5\deg$. A Gaussian on this plot is just a
-    straight line.  The dashed blue line is the probability density for
-    a uniform disk of width $\rsixeight=0.5\deg$.  Finally, the solid
-    red and blue lines show the convolution of the Gaussian and uniform
-    disk respectively with the PSF.  The left plot shows the analysis
-    with an energy range from 1 \gev to 100 \gev whereas the right plot
-    shows the analysis with an energy range from 10 \gev to 100 \gev.
-    }\label{compare_disk_gauss}
-  \end{figure}
-
-  \begin{figure}
-    \begin{center}
-      \includegraphics{mc_plots/compare_r68.pdf}
-      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_r68/v2/plot.py
-      \end{center}
-      \caption{A plot of the smoothed counts for a simulated uniform
-        disk extended source in the energy range from 1 \gev to 100 \gev.
-        The source has a size $\sigma=0.5\deg$, an integral flux between
-        1 \gev and 100 \gev of $3\times 10^{-8}\ph/\cm^2/\sec$, and
-        a spectral index 2.  The smoothed counts from a point source
-        with the same spectrum are shown in the bottom right inset.
-        This source was fit with both a uniform disk and a Gaussian
-        spatial model.  The white circle represents the fit size $\sigma$
-        fitting with the disk hypothesis.  The black circle is the fit
-        $\sigma$ fitting with the Gaussian hypothesis.  The dashed white
-        and black circles are the fit \rsixeight defined in section
-        \ref{compare_source_size} for the disk and Gaussian hypothesis
-        respectively.  This plot shows that fitting the same source with
-        different spatial shapes can lead to very different values of
-        $\sigma$. On the other hand, the different shapes have a good
-        agreement about the 68\% containment radius \rsixeight.
-      }\label{compare_r68}
   \end{figure}

### 2011-07-14 extended_catalog/paper/extended_catalog.tex
mroe chnages

@@
 of the sky and removing excess residuals.  These residuals manifested
-themseleves in the one year catalog as spurious point sources in the
+themselves in the one year catalog as spurious point sources in the
 region region surrounding the Large Magellanic Cloud (\cite{first_cat}).
@@
 ways. The first method requires explicitly varying a parameter
-while simultaneously optimizing the other parameters.
+while simultaneously optimizing the other parameters
 until the log of the likelihood has fallen by a particular value.
@@
 The figure shows the convolution for the PSF in the energy range between
-1 \gev and and 100 \gev and also in the energy range between 10 \gev and
-100 \gev.  The convolved shapesdo separate better at higher energy, but
+1 \gev and 100 \gev and also in the energy range between 10 \gev and
+100 \gev.  The convolved shapes do separate better at higher energy, but
 nevertheless this plot shows that we are not very sensitive to probing
@@
 of source finding using EGRET (\cite{mattox_egret}). This distribution
-is also plausable when testing point sources for extension. Due to
-statistical flucuations, half of the point sources might look narrower
+is also plausible when testing point sources for extension. Due to
+statistical fluctuations, half of the point sources might look narrower
 than the PSF leading to $\tsext=0$. The other half of the time, we would
-get a distribution consistent with Wilk's theorem. We used a Monte Carlo
-study to demonstrat that this is the observed distribution.
- We tested this hypothesis using a dedicated Monte
-Carlo study.
-
-The Monte Carlo study involved simulating point sources of varying
-spectral models and fitting them using \pointlike as both point
-and extended sources.  LAT data was simulated using program
-\gtobssim\footnote{\gtobssim is distributed by and supported by the
-Fermi Science Support Center (\cite{fssc}).}  The sources were simulated
-with a power-law spectral model with 6 Were given 6 $>100$ \mev fluxes
-ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to $10^{-6} \ph/\cm^2/\sec$.
-The sources were then simulated with spectral index ($\gamma$) values of
-1.5, 2, 2.5, and 3.  These values were picked to probe a representative
-range measurable values.  For particular spectral indices, only the fluxes
-which would create a statistically significant source detection ($\ts>25$)
-where selected, since we are only interested in testing for extension
-sources with a significant extent. The sources were simulated on top of
-an isotropic power-law background with a Sreekumar-like spectrum ($>100$
-\mev flux of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).
-
-The Monte Carlo simulation was performed over a one year time interval
-using a default rocking profile and a representative livetime fraction
-of 0.8.  The reconstruction was performed with photons from an energy
-range of 1 \gev to 100 \gev using 4 energy bins per decade and using
-the Pass 7 Version 6 source instrument response function (IRFs) to be
-consistent with the following analysis.
-
-Before we present the results of the Monte Carlo simulations, we have to
-bring up one issue we found with these tests.  Despite our best efforts,
-there was always a small numerical discrepancy between the likelihood when
-fitting the source as the PSF and when fitting it as a very small extended
-source with This is due to numerical error introduced by the convolution.
-In most situations, this error would be insignificant. But it does bias
-the distribution of \tsext in the null hypothesis. To correct for this,
-instead of computing the likelihood in the null hypothesis by fitting
-the PSF, we instead fit the null hypothesis as an extended source with
-the extension fixed to be very small.
-
-For most of the spectral models, over 10,000 statistically independent
-simulations were performed.  For fainter sources, some of the
-simulated sources, statistical fluctuations caused the source
-to be not significant and they were excluded from the following
-analysis.  Table~\ref{ts_ext_num_sims} shows the parameters used in
-the simulation, the number of simulations performed, and the average
-test statistic value.  The results of the Monte Carlo simulation are
-shown in figure~\ref{ts_ext_mc}.  The cumulative density function (CDF)
-is plotted against $\tsext$ For reference, the CDF for $\chi^2_1/2$,
-suggested by Wilks' Theorem, is also plotted for comparison.
-
-Our Monte Carlo study showed broad agreement between simulations and
-Wilks' theorem and that we can use \tsext as a test of the statistical
-significance of a source's extension.  Nevertheless, the agreement
-is not perfect.  It should be noted that the discrepancy seems to be
-worst for bright sources. This seems to imply that numerical errors in
-the convolution become more apparent for sufficiently bright sources.
-Other possible reasons for departure from Wilks' theorem might include
-\pointlike ignoring energy dispersion. Energy dispersion will change
-the shape as a function of energy. \pointlike may also run into possibly
-problems with the fitting algorithm getting stuck in false minimum. It
-is important to emphasize that if our empirical curve lies to the left of
-the curve we assume to estimate significance, we would underestimate the
-statistical significance of our result. Since this is the case for most
-of our simulations, we are reasonable confident that $\sqrt{\tsext}$
-can be safely used as a measure of the statistical significance of a
-source's extension.
+get a distribution consistent with Wilk's theorem. We will present a
+Monte Carlo study that shows an empirical distribution of \tsext in the
+null hypothesis and compares it to this distribution.
+
+We simulated point sources of varying spectral models and fit them
+them using \pointlike as both point and extended sources. The data was
+simulated using \gtobssim\footnote{The \gtobssim program is distributed
+and supported by the Fermi Science Support Center (\cite{fssc}).}
+The point sources were simulated with a power-law spectral model with
+six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
+$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
+indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
+to represent the types of sources detectable by the LAT.  The point
+sources were simulated on top of an isotropic power-law background
+with a Sreekumar-like spectrum ($>100$ \mev flux of 1.5e-5 and spectral
+index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
+performed over a one year time interval using a default rocking profile
+and a representative livetime fraction of 0.8.  The reconstruction was
+performed with photons from an energy range of 1 \gev to 100 \gev using 4
+energy bins per decade and using the Pass 7 Version 6 Source instrument
+response function (IRFs).  For each point source, we used \pointlike
+to fit it as both a point and extended source and calculate \tsext and
+we only dept the sources which had a significant point source detection
+($\ts>25$).
+
+Before we present the results of the Monte Carlo simulations, we note
+that despite out best efforts, there was always a small numerical
+discrepancy between the likelihood when fitting the source as the PSF
+and when fitting it as a very small extended source. This is due to
+numerical error introduced by the convolution.  In most situations, this
+error would be insignificant. But when testing a source for extension,
+this offset significantly bias the distribution of \tsext in the null
+hypothesis. To correct for this, instead of computing the likelihood in
+the null hypothesis by fitting the PSF, we instead calculated \tsext by
+fitting the sources as an extended source and as an extended source with
+its extension fixed to ${10^{-10}}\deg$.
+
+For most of the spectral models, ~30,000 statistically independent
+simulations were performed. For the dimmer spectral models, many of the
+simulations had $\ts<25$ and were discarded.  Table~\ref{ts_ext_num_sims}
+shows the different spectral models used in our study as well as the
+number of simulations.  The cumulative density of \tsext is plotted in
+figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution suggested by Wilks'
+Theorem is overlaid for comparison.
+
+Our Monte Carlo study shows broad agreement between simulations and Wilks'
+theorem. Nevertheless, the agreement is not perfect.  It should be noted
+that the discrepancy seems to be worst for bright sources which seems to
+imply that numerical errors in the convolution become more apparent for
+sufficiently bright sources.  Other possible reasons for departure from
+Wilks' theorem might include \pointlike ignoring energy dispersion which
+would change the PSF's shape as a function of energy. But we emphasize
+that most of the time, our empirical curve lies to the left of the
+theoretical curve so using the theoretical distribution would lead to an
+underestimate of the statistical significance of a detection. Therefore,
+we are confident that $\sqrt{\tsext}$ can be used as a measure of the
+statistical significance of a source's extension and use it in the
+following analysis.
 
@@
 
-We performed a second study to determine the LAT's detection threshold
-to spatially extended sources. The detection threshold to extension
-is defined as the flux at which the average value of
-$\tsext$ is equal to $\langle\ts\rangle=25$. As was seen in
-section~\ref{monte_carlo_validation}, this corresponds to an average
-extension significance of $5\sigma$.
-Qualitatively, we expect that the LAT would not be sensitive to
-extended sources much smaller than the PSF. Similarly,
-we expect that the LAT would not be sensitive to sources
-much larger than the PSF since they would get lost in the
-background.
-
-To calculate the LAT's detection threshold to spatially extended sources,
-we simulated sources with a uniform radially symmetric disk
-morphology on top of a power-law Sreekumar-like isotropic spectrum
+We performed a second study to determine the LAT's detection
+threshold to spatially extended sources. The detection threshold
+to extension is defined as the flux at which the average
+value of $\tsext$ is $\langle\ts\rangle=25$. As was seen in
+section~\ref{monte_carlo_validation}, this corresponds to an extension
+significance of $5\sigma$.  Qualitatively, we expect the LAT would not
+be sensitive to sources much smaller than the PSF or much larger than
+the PSF.  Small sources would look too much like the PSF and larger
+sources would get lost in the background.
+
+To calculate the LAT's detection threshold to spatially extended
+sources, we simulated sources with a uniform radially symmetric disk
+spatial model on top of a power-law Sreekumar-like isotropic spectrum
 (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was performed
-over a one year time interval using a default rocking profile and a
-livetime fraction of 0.8.  For a given extension and spectral index, we
-first hand picked a flux range such that $\tsext<25$ and $\tsext>25$. We
-then picked 10 flux points in this range and performed an extension test
-for each of these fluxes. We repeated this procedure $>15$ times for each
-spectral and spatial model.  By fitting a line to the flux vs $\tsext$,
-we estimated when $\langle\tsext\rangle=25$.
-
-Figure~\ref{index_sensitivity} shows the threshold for
-sources of different spectral indices and extensions.  We selected
-spectral indices 1.5, 2, 2.5, and 3 and 
-extensions from $\sigma=0.1\deg$ to $2.0\deg$.  The curves
-on the plot represent the division in extension and flux space where
-$\langle\tsext=25\rangle$.  The plot shows the threshold using all
-photons with energy between 100 \mev and 100 \gev and the threshold
-using only photons with energy between 1 \gev and 100 \gev.  This results
-shows that the LAT's threshold to extension is better for harder sources
-with more high energy photons. The threshold is best for sources with
-an extension around $0.5\deg$ and is worse for small and large sources.
-
-Except for the hardest and largest sources, our detection threshold is almost
-unchanged when using events between 100 \mev and 1 \gev.  This is also
-demonstrated in figure~\ref{ts_ext_vs_energy} which shows the \tsext for
-the SNR IC443 in 12 energy bins between 100 \mev and 100 \gev. For IC443,
-which has a spectral index ~2.4, almost the entire increase in \ts comes
-from energies above 1 \gev.  On the other hand, other systematic errors
-become increasingly important at low energy. For our extension search,
-we include only photons above 1 \gev.
-
-Figure~\ref{diff_factor_sensitivity} shows how the LAT's
-detection threshold varies with increasing background, typical of sources
-at lower galactic latitude. We compute it for spectral
-index 2 sources using 10 and 100 times the
-extragalactic background. The latter result approximately represents the intensity of
-the galactic diffuse emission near the galactic center. 
-The figure shows two plots, the first showing the threshold looking only between 
-1 \gev and 100 \gev and the second showing the threshold looking only
-between 10 \gev and 100 \gev.
-For each plot, the $y$ axis quotes the flux in the selected energy range
-which weaken the dependence of the detection threshold on spectral index.
-This shows that we are less sensitive to extended sources in
-a higher background region and that if the flux is constant,
-we are more sensitive if the source is harder (has more high energy
-photons).
-
-\section{Extension search method}
-
-\todo[inline]{Add note about how we had to delete nearby sources
-which were not hard above 10GeV for analysis to converge.}
-
-The LAT two year catalog presented a search for all
-statistically significant sources that are detected in the \gev
-sky (\cite{second_cat}).  The catalog group's source finding method assumes
-that the emission originated as point sources and what was presented was
-a list of all sources fit assuming a point source spatial hypothesis. 
-Published extended sources were modeled by the catalog group as 
-being extended, but no attempt was made to test if other sources in the catalog
-could be spatially resolved.
+using the same one year time interval as in section~\ref{monte_carlo_validation}.
+For each extension and spectral index, we
+first picked a flux range which bracketed $\tsext=25$. We then picked
+ten flux points in this range and repeatedly simulated and performed
+extension tests of the extended sources.  For each flux, we performed
+$>15$ independent simulations and extension fits.  We calculated
+$\langle\tsext\rangle=25$ by fitting a line to all the flux and
+$\tsext$ values and estimating the flux when $\tsext=25$.
+
+Figure~\ref{index_sensitivity} shows the threshold for sources of four
+spectral indices from 1.5 to 3 and extension varying from $\sigma=0.1\deg$
+to $2.0\deg$.  The curves on the plot represent the flux for a given
+extension where $\langle\tsext=25\rangle$.  The plot shows the threshold
+using photons with energies between 100 \mev and 100 \gev and the
+threshold using only photons with energies between 1 \gev and 100 \gev.
+This results shows that the LAT's threshold to extension is better for
+harder sources with more high energy photons. This result also shows
+that the threshold is best for sources with an extension of $~0.5\deg$
+and is significantly worse for very small extended small.
+
+Except for the hardest and largest sources, our detection threshold
+is almost unchanged when using events between 100 \mev and 1 \gev.
+This is also demonstrated in figure~\ref{ts_ext_vs_energy} which shows
+the \tsext for the SNR IC443 computed independently in 12 energy bins between 100 \mev and
+100 \gev. For IC443, which has a spectral index ~2.4, almost the entire
+increase in \ts comes from energies above 1 \gev.  On the other hand,
+other systematic errors become increasingly important at low energy. For
+our extension search, we use only only photons with energy above 1 \gev.
+
+Figure~\ref{diff_factor_sensitivity} shows how the LAT's detection
+threshold varies with increasing diffuse background. We compute the
+sensitivity for a power-law source of spectral index 2 using 1, 10, and
+100 times the extragalactic background. The latter factor approximately
+represents the intensity of the galactic diffuse emission near the
+galactic center.  The figure shows two plots, the first showing the
+threshold using only photons with energies between 1 \gev and 100 \gev and
+the second showing the threshold using only photons with energies between
+10 \gev and 100 \gev. This plot demonstrates that we are less sensitive
+to extended sources in a higher background region and that if the flux of
+a source is constant (same number of photons), we would be more sensitive
+to the extension of that source if those photons had a higher energy.
+
+\section{Extended Source Search Method}
+
+\todo[inline]{Add note about how we had to delete nearby sources which
+were not hard above 10 \gev for analysis to converge.}
+
+The LAT two year catalog presented a search for all statistically
+significant sources that are detected in the \gev sky (\cite{second_cat}).
+The catalog group's source finding method assumes that the emission
+originated as point sources and what was presented was a list of all
+sources fit assuming a point source spatial hypothesis.  Published
+extended sources were modeled by the catalog group as being extended,
+but no attempt was made to test if other sources in the catalog could
+be spatially resolved.
 
@@
 years of data from August 4, 2008 to August 1, 2010 and we used the same
-pass 7 instrument response function.  We used the same galactic diffuse,
+pass 7 Version 6 Source IRFs.  We used the same galactic diffuse,
 isotropic diffuse, and earth limb emission model. The spectrum of the
@@
 % Modify 
-%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.410,-0.293,SkyDir.GALACTIC)
+%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.365,0.005,SkyDir.GALACTIC)
+% New source
+%  * SkyDir(332.426,-0.331,SkyDir.GALACTIC
 
@@
 model the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
-and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
-iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
-position and extension of 2FGL J1615.2-5138.  We ended up with a best
-fit position of the nearby source 2FGL J1615.0-5051 having moved from
-$(l,b)=(332.2684,0.043)$ to $(l,b)=(332.41,-0.29)$. This was necessary
-because the initial localization of this source was done assumign that
-2FGL J1615.2-5138 was modeled as several point sources.  To address
-the possibility of source confusion, to compare the overal change in
-likelihood fitting 2FGL J1615.2-5138 as two point sources and find
-\tsinc=34.3 which is smaller then \tsext.
+and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region
+we iterativly relocalized the source 2FGL J1615.0-5051 while fitting
+the position and extension of 2FGL J1615.2-5138.  We ended up with
+a best fit position of the nearby source 2FGL J1615.0-5051 having
+moved from $(l,b)=(332.2684,0.043)$ to $(l,b)=(332.365,0.005)$.
+In addition,we had to add a new source not in the catalog at the position
+of $(l,b)=(332.426,-0.331)$. The moved and now source are shown in
+figure~\ref{1FGL_J1613.6-5100c} are shown as the blue and XXXXXXXXXX\todo{what color} crosses
+respectivly.  The location of these sources was found by iterativly
+fitting the position of these sources as well as the extension of 2FGL
+J1615.2-5138 until a stable fit was found.  It is unclear of this new seed
+is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
+2FGL J1615.0-5051 was not found to be significantly extended using two
+years of data but the fit of 2FGL J1615.2-5138 was clearly growing
+too large to obsorb residual in the direction of 
+J1615.2-5138 until we added the additional point source.
+
+To address the possibility of source confusion, we compared the likelihood 
+fitting 2FGL J1615.2-5138 as two point sources to one source.
+We found that \tsinc=34.3 which is smaller then \tsext so we believe
+that this is extended emission.
 
@@
 
-See figure~\ref{1FGL_J1613.6-5100c}.
-
 \todo[inline]{Describe What this source is/What HESS Source this is near}
@@
 % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
+% Kept:
+% * P72Y2539 - 2FGL J1632.4-4820c
 % Deleted
 % * P72Y2535 - 2FGL J1631.7-4720c
-% * P72Y2550 - 2FGL J1636.3-4740c
 % * P72Y2556 - 2FGL J1638.0-4703c
@@
 % * P72Y2543 - 2FGL J1634.4-4743c
-% * P72Y2539 - 2FGL J1632.4-4820c
 % * P72Y2521 - 2FGL J1628.1-4857c
@@
 %              (initial Position  - SkyDir(337.1396,0.1433)
+% * P72Y2550 - 2FGL J1636.3-4740c - SkyDir(336.968,-0.066,SkyDir.GALACTIC))
+%              (initial Position  - SkyDir(336.9639,-0.236)
 
@@
 
-To get a good fit of the region, had to remove from our model the 5
-catalog sources 2FGL J1631.7-4720c, 2FGL J1636.3-4740c, 2FGL J1630.2-4752,
-2FGL J1634.4-4743c, and 2FGL J1632.4-4820c. These sources all are on top
+To get a good fit of the region, had to remove from our model the four
+catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
+2FGL J1634.4-4743c.4-4820c. These sources all are on top
 of this extended source but there is no indication that the emission of
@@
 
-In addition we removed from our region the 4 nearby catalog sources
-2FGL J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL
-J1639.8-4921c because they were not significant above 10 \gev. Finally,
-we had to move the source 2FGL J1635.4-4717c to a better fit position
-$(l,b)=(337.230,0.346)$ to get a good fit of it and our extended source in
-the $>10$ \gev energy range. The initial position of this source is shown
-in the figure as a blue star and its best fit position is also indicated.
+In addition we removed from our region the 4 nearby catalog sources 2FGL
+J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL J1639.8-4921c
+because they were not significant above 10 \gev.  Finally, we had to
+relocalized the source 2FGL J1635.4-4717c to a better fit position
+$(l,b)=(337.230,0.346)$ and the position of 2FGL J1636.3-4740c to the
+better fit position $(l,b)=(336.968,-0.066)$ to get a good overall fit
+of our source.
 
@@
 
-Gamam Cygni SNR.
+Gamma Cygni SNR.
 
@@
 % Delete:
+% * P72Y3292 - 2FGL J2022.8+3843c
 % * P72Y3282 - 2FGL J2019.1+4040
@@
 % * P72Y3260 - 2FGL J2012.4+3955c
+% New source
+%  * SkyDir(78.854,2.670,SkyDir.GALACTIC)
+
 \todo[inline]{Describe how ROI was modified}
@@
 % Delete:
+% * P72Y2982 - Not in 2FGL
 % * P72Y2979 - 2FGL J1835.5-0649
-% * P72Y2994 - 2FGL J1839.3-0558c
 % * P72Y2993 - 2FGL J1839.0-0539
@@
 % * P72Y2985 - 2FGL J1836.8-0623c - SkyDir(25.574,0.320,SkyDir.GALACTIC)
-%              (initial Position - SkyDir(,)
+%              (initial Position - SkyDir(25.5925,0.3103)
 % * P72Y2974 - 2FGL J1837.3-0700c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
-%              (initial Position - SkyDir(,)
+%              (initial Position - SkyDir(25.0953,-0.0887)
+% * P72Y2994 - 2FGL J1839.3-0558c - SkyDir(26.080,0.229,SkyDir.GALACTIC)
+%              (initial Position - SkyDir(26.2301,-0.0394)
 
@@
 % * P72Y1259 - 2FGL J0842.9-4721
-% * P72Y1310 - 2FGL J0901.7-4655
 % * P72Y1300 - 2FGL J0858.0-4815
@@
 %              (initial Position - SkyDir(265.5705,-0.0099)
+% * P72Y1310 - 2FGL J0901.7-4655 - SkyDir(267.311,-0.190,SkyDir.GALACTIC)
+%              (initial Position - SkyDir(267.79,-0.3339)
 
@@
     range from 10 \gev to 100 \gev.  This plot is discussed futher in
-    section~\ref{compare_source_size}
+    section~\ref{compare_source_size}.
     }\label{compare_disk_gauss}
@@
       disk and Gaussian hypothesis. This plot is discussed furhter in
-      section~\ref{compare_source_size}
+      section~\ref{compare_source_size}.
       }\label{compare_r68}
@@
     Carlo analysis is presented in section~\ref{monte_carlo_validation}.
-    }
-    \label{ts_ext_num_sims}
+    }\label{ts_ext_num_sims}
   \end{centering}
@@
     different spectral indices and the different colors represent
-    different flxues.  The dashed red line is the cumulative density
+    different fluxes.  The dashed red line is the cumulative density
     function of $\chi^2(\ts)/2$ which is suggested by Wilks' theorem
@@
     a surprisingly good agreement between the Monte Carlo results and
-    the theoeretical distribution. For most spectral parameters, the
+    the theoretical distribution. For most spectral parameters, the
     Monte Carlo curve lies to the left of the theoretical curve which
@@
     \end{center}
-    \caption{This is the LAT's detection threshold to spatially
-    extended sources. The $x$ axis is Monte Carlo extension of a
-    simulated uniform disk source and the $y$ axis is the simulated
-    source's 100 \mev to 100 \gev photon flux. Each curve represents
-    the detection threshold for being able to spatially resolve an
-    extended source (when $\langle\tsext\rangle=25$).  
-    All sources have an assumed power-law spectrum and the different
-    colors are for sources of different simulated spectral indices.
-    The dashed line shows simulations using photons with energy between 
-    100 \mev and 100 \gev while the solid lien shows simulations
-    using photons with energy between 1 \gev and 100 \gev.
-    The detection threshold is for a one year simulation against a Sreekumar-like
-    isotropic background (\cite{sreekumar_isotropic}).
-    This plot shows that our threshold is best for sources that are
-    about $1\deg$ large. It also shows that for sources that are neither
-    very large nor very soft, our sensitivity is not significantly
-    improved using photons with energy between 100 \mev and 1 \gev.  More information
-    about this plot is presented in section~\ref{extension_sensitivity}.
+    \caption{
+    This plot shows that our threshold to detecting the extension of
+    a soruce is best for sources with size $~0.5\deg$. It also shows
+    that for sources neither very large nor soft, our sensitivity is
+    not significantly improved using photons with energy between 100
+    \mev and 1 \gev.  The $x$ axis is extension of a simulated uniform
+    disk extended source and the $y$ axis is the simulated source's 100
+    \mev to 100 \gev photon flux. The curves represent the detection
+    threshold to an extended source which is defiend as the flux when
+    $\langle\tsext\rangle=25$ for a particular extension.  All sources
+    have an assumed power-law spectrum and the different colors are
+    for sources of different simulated spectral indices.  The dashed
+    line shows simulations using photons with energy between 100 \mev
+    and 100 \gev while the solid lien shows simulations using photons
+    with energy between 1 \gev and 100 \gev.  The detection threshold
+    is for a one year simulation against a Sreekumar-like isotropic
+    background.  More information about this plot is presented in
+    section~\ref{extension_sensitivity}.
     }\label{index_sensitivity}
@@
     \caption{
-    \todo[inline]{Add Caption}
+    This plot shows that we are less sensitive to extended sources in
+    regions with higher background and (given the same number of photons)
+    more sensitive to harder soruces.  The plot has the same meaning as
+    in figure~\ref{index_sensitivity} and the simulations occur over
+    the same time range.  These plots presents the sensitivity over
+    for varying background levels and two energy ranges.  The blue dash
+    dotted plot is the sensitivity against a Sreekumar-like isotropic
+    background. The green dashed curve shows the sensitivity against 10
+    times that isotropic background and the solid red curve shows the
+    sensitivity against 100 times that isotropic background.  The latter
+    factor approximately represents the intensity of the galactic
+    diffuse emission near the galactic center.  The left plot presents
+    the sensitivity when usings only photons with energies between 1 \gev
+    and 100 \gev while the plot on the right presents the sensitivity only
+    when using photons with energies between 10 \gev and 100 \gev. Unlike
+    figure~\ref{index_sensitivity}, the sensitivity was calculated only
+    for a power-law source of spectral index 2. Similarly, the flux is
+    quoted only in the selected energy range which weakens the dependence
+    of the detection threshold on spectral index.  More information
+    about this plot is presented in section~\ref{extension_sensitivity}.
     }\label{diff_factor_sensitivity}
@@
     \caption{
-    The plot shows \tsext for 12 uniform log(energy) bins between 100
-    \mev and 100 \gev for the SNR IC443. IC443 has a spectral index
-    ~2.4 (table~\ref{known_extended_sources}) which is typical of
-    extended sources.  This plot shows that there is little gain in
-    sensitivity in the data with energy below 1 \gev.  For this reason,
-    this paper restricts its analysis to energies above 1 \gev.
+    The plot shows \tsext for 12 uniform log(energy) bins between 100 \mev
+    and 100 \gev for the SNR IC443. IC443 has a spectral index $~2.4$
+    (table~\ref{known_extended_sources}) which is typical of extended
+    sources.  This plot shows that there is little gain in sensitivity to
+    the extension of a source using photons with energies below 1 \gev.
+    For this reason, this paper restricts its analysis to energies above
+    1 \gev.
     }
@@
     \caption{
-    \todo[inline]{Describe that best for looking at overall diffuse emission and visually assesing quality of the fit.}
+    The upper plot is the sum of the counts binned in galactic longitudinal
+    summed within 2\deg in galactic latitude centered on the SNR
+    IC443. The lower plot shows the same image but instead integrated
+    in galactic longitude.  Overlaid on the plot is the model predicted
+    counts assuming that IC443 is a point source, an extended source,
+    and that there is just the diffuse background. These counts slices
+    are especially useful for visually assessing the quality of
+    the diffuse emission model in the region surrounding an
+    extended source candidate.
+    \label{counts_slice}
     }
-    \label{counts_slice}
   \end{center}
@@
     \caption{
-    A plot of the overall change in Test Statistic when varying the
+    A plot of the overall change in \ts when varying the
     extension of the extended SNR IC443.  As is discussed in section
@@
     \end{tabular}
-    \caption{The 8 new source candidates found by the
-    extended source search. 3 new extended sources were found searching looking at photons with energies 1 \gev and
-    5 new candidates were found looking at photons with energies above 10 \gev.
-    The columns in this table have the same definition as table~\ref{known_extended_sources}.
-    More information about these sources can be found in section~\ref{new_ext_srcs_section}
+    \caption{The 8 new source candidates found by the extended source
+    search. Three new extended sources were found using photons with
+    energies above 1 \gev and five new candidates were found using photons
+    with energies above 10 \gev.  The columns in this table have the same
+    meaning as in table~\ref{known_extended_sources}.  More information
+    about these sources can be found in section~\ref{new_ext_srcs_section}.
     }
@@
       \caption{
-      This table shows a comparison of the \ts values gotten using \gtlike and \pointlike.
-      It also compares the fit values using the standard diffuse model and using the alternate
-      diffuse model described in section~\ref{alt_diff_model_description}.
-      $\ts_\pointlike$ is the \ts of the source fit with the extended hypothesis using \pointlike
-      whereas $\ts_\gtlike$ is the same quantity using the same model but fitting with \gtlike.
-      There is very good agreement between the two methods.
+      This table shows a comparison of the \ts values gotten using \gtlike
+      and \pointlike.  It also compares the fit values using the standard
+      diffuse model and using the alternate diffuse model described
+      in section~\ref{alt_diff_model_description}.  $\ts_\pointlike$
+      is the \ts of the source fit with the extended hypothesis using
+      \pointlike whereas $\ts_\gtlike$ is the same quantity using the
+      same model but fitting with \gtlike.  There is very good agreement
+      between the two methods.
       }
@@
   Spills into the image at left.}
-  \todo[inline]{Describe this source better. Add in Contour}
+  \todo[inline]{Describe this source better. Describe the Contour}
   }\label{1FGL_J0823.3-4248}
@@
   Gamma Cygni. P72Y3281
-  \todo[inline]{Describe this source better. Add in Contour}
+  \todo[inline]{Describe this source better. Describe the Contour}
   }\label{Gamma_Cygni}
@@
   \todo[inline]{Note that sourceis con with a $0.25\deg$ gaussian which is different than other plots.}
-  \todo[inline]{Describe this source better. Add in Contour}
+  \todo[inline]{Describe this source better. Describe the Contour}
   }\label{Vela_Jr}
@@
   \caption{1FGL J1837.5-0659c. P72Y2974
-  \todo[inline]{Describe this source better. Add in Contour}
+  \todo[inline]{Describe this source better. Describe the Contour}
   \todo[inline]{Note about why the top right source was not found to
@@
   \caption{1FGL J1632.9-4802c. P72Y2540
-  \todo[inline]{Describe this source better. Add in Contour}
+  \todo[inline]{Describe this source better. Describe the Contour}
   }\label{1FGL_J1632.9-4802c}
@@
   1FGL J1613.6-5100c . P72Y2473
-  \todo[inline]{Describe this source better. Add in Contour}
+  \todo[inline]{Describe this source better. Describe the Contour}
   }\label{1FGL_J1613.6-5100c}

### 2011-07-15 extended_catalog/paper/extended_catalog.tex
more changes

@@
 of XXXXXX\todo{What number should be put
-here???} new extended sources.
+here. Should we report the total number of extended sources instead of the
+number of new sources???} new extended sources.
 \end{abstract}
@@
 
-The spatial shape of extended soruces can e modeled
+The spatial shape of extended sources can e modeled
 as a two dimensional Gaussian
@@
 them using \pointlike as both point and extended sources. The data was
-simulated using \gtobssim\footnote{The \gtobssim program is distributed
-and supported by the Fermi Science Support Center (\cite{fssc}).}
+simulated using \gtobssim\footnote{\gtobssim is distributed
+by the Fermi Science Support Center (\cite{fssc}).}
 The point sources were simulated with a power-law spectral model with
@@
 
-As an example of why this issue, we describe our test of P72Y3047 for
+% 2FGL J1856.2+0450c = P72Y3047 for
+As an example of why this issue, we describe our test of 
+2FGL J1856.2+0450c for
 extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
 using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
-emission subtracted.  A two year catalog source P72Y3047 was found at the
+emission subtracted.  A two year catalog source 
+2FGL J1856.2+0450c was found at the
 position $(l,b)=(37.79\deg,1.14\deg)$.  
@@
 we don't have a great model of the nearby catalog sources. As a result,
-P72Y3047 fits to a very large extension of 1.37\deg and the result is
+2FGL J1856.2+0450c fits to a very large extension of 1.37\deg and the result is
 statistically significant with \tsext=51.6.  By looking at the residuals,
@@
 \section{Test of 1LAC Sources}
+\label{test_1lac_sources}
 
@@
 a list of catalog sources that had a high probability association with
-AGN. The first year catalog had 709 AGN associated with 671 distinct
+AGN (\cite{first_agn_cat}).
+The first year catalog had 709 AGN associated with 671 distinct
 1FGL sources at high latitude ($|b|>10\deg$).  To avoid systematic
@@
 \subsection{2FGL J1627.0-2425c}
+\label{section_ophiuchus}
 
@@
 
-The two year catalog source 2FGL J1627.0-2425c was found to be significantly
-extended when using photons between 1 \gev and 100 \gev.  The best
-fit extension was $0.41\deg\pm0.05\deg$ and the best fit position is
-$(l,b)=(353.09\deg, 16.79\deg)$ The source also appeared in the first
+The two year catalog source 2FGL J1627.0-2425c was found to be
+significantly extended when using photons between 1 \gev and 100 \gev.
+The best fit extension was $0.53\deg\pm0.06\deg$ and the best fit position
+is $(l,b)=(352.87\deg, 16.79\deg)$ The source also appeared in the first
 fermi catalog as 1FGL J1628.6-2419c.  and the extension significance
-was $\tsext=28.9$.  A smoothed counts map showing this source is seen
-in figure \ref{1FGL_J1628.6-2419c}.
+was $\tsext=21.1$.  A counts map showing this source is seen in
+figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion, we also
+fit this region as two point sources. Since $\tsinc=16.6$ is smaller
+than \tsext, the emission is more likeliy to come from an extended source.
 
 This source is in a region of remarkably complicated diffuse emission.
-Even though it is 16\deg from the Galactic plane,
-the source is right on top of the core of the Ophiuchus molecular cloud,
-which contains massive star-forming regions that are very bright
-in the infrared.  The region has abundant molecular and atomic gas
-traced by CO and HI but also plenty of dark gas, the kind that
-we find only by its association with dust emission.\todo{Citation Needed}
-Embedded star-forming regions make it even more challenging to measure
-the column density of dust.\todo{Citation Needed}
-\todo[inline]{Note about spectral index being typical of difuse emission}
-Although this region is significantly extended, we conclude that what we
-are seeing is most likely an inadequacy in the diffuse $\gamma$-ray emission
+Even though it is 16\deg from the Galactic plane, the source is on top
+of the core of the Ophiuchus molecular cloud which contains massive
+star-forming regions that are very bright in the infrared.  We have
+overlaid on the plot of figure~\ref{1FGL_J1628.6-2419c} a 100 micrometer
+infared image of this region as seen by IRAS and there is good spatial
+overlap between with the \gev observed emission
+(\cite{iras_rho_ophiuci}).
+
+The region has abundant molecular and atomic gas traced by CO and HI but
+also plenty of dark gas, the kind that we find only by its association
+with dust emission. Embedded star-forming regions make it even more
+challenging to measure the column density of dust.
+Although this region is significantly extended, we conclude that what
+we are seeing is most likely an inadequacy in the diffuse $\gamma$-ray
+emission model.
+
+\todo[inline]{Can we get another citation about dark gas
+and stuff?
+Better note about spectral index being typical of difuse emission.
+Also does this description make sense? Also, is 
+citation about IRAS good?}
 
@@
 
-The two year catalog source 2FGL J1554.4-5317c was found to be
-extended using photons with energy between 1 \gev and 100 \gev.
-We found an extension of $0.49\deg\pm 0.04\deg$ and an extension significance of
-$\tsext=77.6$ at a position $(l,b)=(328.1387\deg,0.26\deg)$.  Figure
-\ref{1FGL_J1554.0-5345c} shows a smoothed counts map of this source.
+The two year catalog source 2FGL J1554.4-5317c was found to be extended
+using photons with energy between 1 \gev and 100 \gev.  We found an
+extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
+$\tsext=39.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
+\ref{1FGL_J1554.0-5345c} shows a counts map of this source.
 
@@
 To get a good fit of the source, we had to remove the nearby catalog
-source 2FGL J1551.3-5333c
-which we believed to be suprious. By looking at
+source 2FGL J1551.3-5333c which we believed to be suprious. By looking at
 the counts map, we saw no differentation in the source at the location
-of the two catalog sources. We tested this region for source confusion
+of the two catalog sources. 
+These soruce modifications are further described
+in the caption to figure~\ref{1FGL_J1554.0-5345c}.
+
+We tested this region for source confusion
 by comparing the increase in log likelihood fitting the region as an
-extended source (\tsext=77.6) to the increase in log likelihood fitting
-the region as two point sources (\tsinc=48.6).  Since the extended
-hypothesis is a has a higher likelihood, we conclude that the source is
-spatially extended More
-information about the dual localization results for this source are
-shown in table \ref{dual_localization_results}.
+extended source to the increase in log likelihood fitting the region
+as two point sources. Since $\tsinc=10.2$ is smaller than \tsext, we
+conclude that the source is spatially extended and not multiple point
+sources. More information about the dual localization results for this
+source are shown in table \ref{dual_localization_results}.
 
 There are no obvious counterparts to this source. Furthermore, this
-source is relativly soft with a spectral index 2.31 and
-very close to the galacitc plane in a region of large diffuse emission.
-We conclude that although this region is significantly extended, it most
-likely represents unmodeled diffuse emission.
-\todo[inline]{this needs more quantification/description}
-\todo[inline]{Improve note about spectral check and lack of hardness}
+source is relativly soft with a spectral index 2.31 and very close to
+the galacitc plane in a region of large diffuse emission.  We conclude
+that although this region is significantly extended, it most likely
+represents unmodeled diffuse emission.
+\todo[inline]{this needs more quantification/description.
+Improve the point about how since the source is soft, it
+is more consistent with diffuse emission.
+}
 
 \subsection{2FGL J0823.0-4246}
+\label{section_puppis_a}
 
@@
 extended using photons with energy between 1 \gev and 100 \gev.
-We found an extension of $0.37\deg$ and an extension
+We found an extension of $0.37\deg\pm0.03\deg$ and an extension
 significance of $\tsext=49.2$.  The source was fit to a position of
-$(l,b)=(260.31\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
-a smoothed counts map of this source.
-
-This soruce is coincident with the one year catalog source named 1FGL J0823.3-4248.
-To get a good fit of the source, we had to remove the nearby catalog
-sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254.  We tested the 
-region for source confusion by fitting the region instead as two point
-sources and obtained $\tsinc=22.2$ which is smaller then \tsext.
-
-\todo[inline]{Describe how this source is Coincident with Puppis A SNR
-and give some interpretation of it.}
+$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
+a counts map of this source.
+
+This source is coincident with the one year catalog source named 1FGL
+J0823.3-4248.  To get a good fit of the source, we had to remove the
+nearby catalog sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which
+are part of the extended emission.  We tested the source for spatial
+confusion by fitting it as two point sources. Because $\tsinc=22.3$ is
+smaller then \tsext, we believe that this source is spatially extended.
+These removed catalog soruces are shown in figure~\ref{1FGL_J0823.3-4248}.
+
+This extended source is spatially coincident with the SNR Puppis A.
+Overlaid on figure~\ref{1FGL_J0823.3-4248} are ROSAT contours of
+Puppis A (\cite{rosat_puppis_a}). There is good agreement
+between the measured radius of $\sigma=0.37$ degrees in \gev and 
+the X-ray contours of the source.
+
+\todo[inline]{Give some additional interpretation of the Puppis A SNR.}
 
@@
 
-The two year catalog source 2FGL J1615.2-5138 was found to be
-extended using photons with energies between 10 \gev and 100 \gev.
-This source is coincident with the one year catalog source named 1FGL
-J1613.6-5100c.  We found an extension of $0.52\deg$ with an extension
-significance of \tsext=75.3.  The source was fit to a position of
-$(l,b)=(331.74\deg,-0.58\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
-a smoothed counts map of this source.
-
- To get a good fit for the region, we had to remove from our
-model the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
-and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region
-we iterativly relocalized the source 2FGL J1615.0-5051 while fitting
-the position and extension of 2FGL J1615.2-5138.  We ended up with
-a best fit position of the nearby source 2FGL J1615.0-5051 having
-moved from $(l,b)=(332.2684,0.043)$ to $(l,b)=(332.365,0.005)$.
-In addition,we had to add a new source not in the catalog at the position
-of $(l,b)=(332.426,-0.331)$. The moved and now source are shown in
-figure~\ref{1FGL_J1613.6-5100c} are shown as the blue and XXXXXXXXXX\todo{what color} crosses
-respectivly.  The location of these sources was found by iterativly
+The two year catalog source 2FGL J1615.2-5138 was found to be extended
+using photons with energies between 10 \gev and 100 \gev.  This source
+is coincident with the one year catalog source 1FGL J1613.6-5100c.
+We found an extension of $0.43\deg\pm0.04\deg$ with an extension
+significance of \tsext=45.3.  The source was fit to a position of
+$(l,b)=(331.67\deg,-0.66\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
+a counts map of this source.
+
+To get a good fit for the region, we had to remove from our model
+the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
+and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
+iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
+position and extension of 2FGL J1615.2-5138.  We ended up with a best
+fit position of the nearby source 2FGL J1615.0-5051 having moved from
+$(l,b)=(332.2684\deg,0.043\deg)$ to $(l,b)=(332.365\deg,0.005\deg)$.  In addition,we
+had to add a new source not in the catalog at the position of
+$(l,b)=(332.426\deg,-0.331\deg)$.  The location of these sources was found by iterativly
 fitting the position of these sources as well as the extension of 2FGL
@@
 2FGL J1615.0-5051 was not found to be significantly extended using two
-years of data but the fit of 2FGL J1615.2-5138 was clearly growing
-too large to obsorb residual in the direction of 
-J1615.2-5138 until we added the additional point source.
+years of data but the fit of 2FGL J1615.2-5138 was clearly growing too
+large to obsorb residual in the direction of J1615.2-5138 until we added
+the additional point source.
+These modifications are further described in the caption to 
+figure~\ref{1FGL_J1613.6-5100c}.
 
 To address the possibility of source confusion, we compared the likelihood
-fitting 2FGL J1615.2-5138 as two point sources to one source.
-We found that \tsinc=34.3 which is smaller then \tsext so we believe
-that this is extended emission.
+fitting 2FGL J1615.2-5138 as two point sources to one source.  We found
+that \tsinc=30.1 which is smaller then \tsext so we believe that this
+is extended emission.
 
@@
 \todo[inline]{Describe What this source is/What HESS Source this is near}
+\todo[inline]{Describe contours overlaied on source}
 
@@
 using photons with energies between 10 \gev and 100 \gev.  This source
-was found to be consistent with 1FGL J1632.9-4802c.  We fit an
-extension of 0.65\deg with an extension significance of \tsext=95.3.
-The source was fit to a position of $(l,b)=(336.52\deg,0.06\deg)$.
-Figure~\ref{1FGL_J1632.9-4802c}.  shows a smoothed counts map of this
-source. The figure shows as a red star the catalog position
-of this source.
-
-To get a good fit of the region, had to remove from our model the four
-catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
-2FGL J1634.4-4743c.4-4820c. These sources all are on top
-of this extended source but there is no indication that the emission of
-these sources separates.  These sources are indicated as green stars in
+is coincident with the one year catalog source 1FGL J1632.9-4802c.
+We fit an extension of $0.44\deg\pm0.04\deg$ with an extension
+significance of \tsext=62.2.  The source was fit to a position
+of $(l,b)=(336.52\deg,0.06\deg)$.  Figure~\ref{1FGL_J1632.9-4802c}.
+shows a counts map of this source.
+
+To get a good fit of the region, we had to remove from our model
+the four catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
+2FGL J1634.4-4743c.4-4820c. These sources all are on top of this
+extended source but there is no indication that the emission of these
+sources separates.  Finally, we relocalized the
+source 2FGL J1635.4-4717c to a better fit position $(l,b)=(337.230\deg,0.346\deg)$
+and the position of 2FGL J1636.3-4740c to the better fit position
+$(l,b)=(336.968\deg,-0.066\deg)$ to get a good overall fit of our source.
+These modifications are further described in the caption to 
 figure~\ref{1FGL_J1632.9-4802c}.
 
-In addition we removed from our region the 4 nearby catalog sources 2FGL
-J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL J1639.8-4921c
-because they were not significant above 10 \gev.  Finally, we had to
-relocalized the source 2FGL J1635.4-4717c to a better fit position
-$(l,b)=(337.230,0.346)$ and the position of 2FGL J1636.3-4740c to the
-better fit position $(l,b)=(336.968,-0.066)$ to get a good overall fit
-of our source.
+In addition we removed from our region four farther away two year
+catalog sources J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615,
+2FGL J1639.8-4921c because they were not significant above 10 \gev.
 
@@
 region as one extended source to the likelihood fitting this region as
-two point sources. We found $\tsinc=24.8\ll\tsext$ which indicates that
+two point sources. We found $\tsinc=38.5\ll\tsext$ which indicates that
 this is extended emission and not source confusion.
 
-\todo[inline]{Describe how ROI was modified.
-Note about uncertainty about background sources. 
-We model the northwestern source separatly
-but not the southeastern 'possible source'.}
-
 \todo[inline]{Describe What this source is/What HESS Source it is near}
+\todo[inline]{Describe contours overlaid on source}
 
 \subsection{2FGL J2021.5+4026}
-
-Gamma Cygni SNR.
 
@@
 % Delete:
+% * P72Y3282 - 2FGL J2019.1+4040
 % * P72Y3292 - 2FGL J2022.8+3843c
-% * P72Y3282 - 2FGL J2019.1+4040
 % * P72Y3287 - 2FGL J2020.0+4159
@@
 
-\todo[inline]{Describe how ROI was modified}
+The two year catalog source 2FGL J2021.5+4026 was found to be extended
+using photons with energies between 10 \gev and 100 \gev. This source
+is coincident with the one year catalog source 1FGL J2020.0+4049. We
+fit an extension of $0.59\deg\pm0.03\deg$ with an extension
+significance of $\tsext=140.6$.  The source was fit to a position of
+$(l,b)=(78.17\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
+counts map of this source.
+
+To get a good fit of the region, we had to remove the nearby catalog
+source 2FGL J2019.1+4040 which were part of the extended source.
+Further, we found it necessary to add an additional point source not in
+the two year catalog into our background model.  The new source is was
+localized to a position of $(l,b)=(78.854,2.670)$ and had $\ts\approx 16$
+(using \pointlike).  Although the source is not very significant, not
+including it into the background model appeared visually to significantly
+throw off the fit of the region.  In addition, we removed the four
+further away catalog sources 2FGL J2022.8+3843c, 2FGL J2020.0+4159,
+2FGL J2013.8+4115c, and 2FGL J2012.4+3955c from our region becuase they
+were not signifcant above 10\gev.  After modifying the region, we found
+that \tsinc=34.7 which is less than \tsext, so we believe that source
+source is spatially extended.  These modifications are further described
+in the caption to figure~\ref{1FGL_J2020.0+4049}.
 
 \todo[inline]{
+This source is the Gamma Cygni SNR!
+
 Describe how this source is analyzed more carefully in the paper
@@
 }
-
-See figure~\ref{1FGL_J2020.0+4049}.
-
-\todo[inline]{explain upcomming publication}
+\todo[inline]{Describe contours overlaid on source}
 
@@
 % * P72Y2982 - Not in 2FGL
-% * P72Y2979 - 2FGL J1835.5-0649
-% * P72Y2993 - 2FGL J1839.0-0539
+% * P72Y2979 - 2FGL J1835.5-0649 - SkyDir(25.0503,0.3894)
+% * P72Y2993 - 2FGL J1839.0-0539 - SkyDir(26.4904,0.1632)
 
@@
 
-Near HESS source HESS J1837. Upcomming publication???
-\todo[inline]{Describe how ROI was modified}
-\todo[inline]{Discuss the upcomming publication}
-See figure~\ref{1FGL_J1837.5-0659c}.
+The two year catalog source 2FGL J1837.3-0700c was found to be extended
+using photons with energies between 10 \gev and 100 \gev. This source
+is coincident with the one year catalog source 1FGL J1837.5-0659c. We
+fit an extension of $0.35\deg\pm0.08\deg$ with an extension
+significance of $\tsext=20.9$.  The source was fit to a position of
+$(l,b)=(25.08\deg,0.13\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
+counts map of this source.
+
+This source is in a very complicated region. There are two very nearby
+catalog sources 2FGL J1836.8-0623c and 2FGL J1837.3-0700c which are
+about $~0.5\deg$ away from our source. To get a good fit of the region,
+we slightly relocalize these sources so that 2FGL J1836.8-0623c is at
+a postiion of $(l,b)=(25.574\deg,0.320\deg)$ and 2FGL J1837.3-0700c is
+at a position of $(l,b)=(24.716\deg,0.500\deg)$.  We also relocalized
+the source 2FGL J1839.3-0558c which is about $~1\deg$ away from our
+source to a better position of $(l,b)=(26.080\deg,0.229\deg)$ Finally,
+we had to remove the nearby catalog source 2FGL J1835.5-0649 which we
+believed to be part of our extended source. We also removed the farther
+away catalog source 2FGL J1839.0-0539 because it was not significant
+above 10 \gev.  After modifying the region, we found that \tsinc=15.4
+which is less than \tsext, so we believe that the emission from this
+soruce spatially extended.  These modifications are further described
+in the caption to figure~\ref{1FGL_J2020.0+4049}.
+
+\todo[inline]{
+Near HESS source HESS J1837. 
+Discuss the upcomming publication???
+Describe contours overlaied on source}
 
@@
 
-\todo[inline]{Describe how ROI was modified}
-
-Vela Jr. Upcomming publication.
-\todo[inline]{explain that Vela Jr will be described better in upcomming publication}
-See figure~\ref{Vela_Jr}.
+The two year catalog source 2FGL J0851.7-4635 was found to be extended
+using photons with energies between 10 \gev and 100 \gev. This source has
+no counterparts in the first year LAT catalog.  We fit an extension of
+$1.12\deg\pm0.07\deg$ with an extension significance of $\tsext=90.9$.
+The source was fit to a position of $(l,b)=(266.29\deg,-1.41\deg)$.
+Figure~\ref{Vela_Jr} shows a counts map of this source.
+
+To get a good fit of the region, we had to remove three nearby catalog
+sources 2FGL J0848.5-4535, 2FGL J0855.4-4625, and 2FGL J0853.5-4711 which
+were part of the extended source.  In addition, we had to relocalize
+the position of two nearby catalog sources to better fit their position
+at high energies.  We localized 2FGL J0854.7-4501 to a position of
+$(l,b)=(266.232\deg,0.517\deg)$ and 2FGL J0901.7-4655 to a position of
+$(l,b)=(267.311\deg,-0.190\deg)$. In addition, we removed the further
+away catalog source 2FGL J0858.0-4815 beacuse it was not significant
+above 10 \gev.  After modifying the region, we found that \tsinc=17.2
+which is less than \tsext, so we believe that this region is not source
+confusion but is instead a spatially extended source.  These modifications
+are further described in the caption to figure~\ref{Vela_Jr}.
+
+\todo[inline]{explain that Vela Jr will be described better in upcoming publication}
+\todo[inline]{Describe contours overlaid on source}
 
@@
     This plot shows that our threshold to detecting the extension of
-    a soruce is best for sources with size $~0.5\deg$. It also shows
+    a source is best for sources with size $~0.5\deg$. It also shows
     that for sources neither very large nor soft, our sensitivity is
@@
     \mev to 100 \gev photon flux. The curves represent the detection
-    threshold to an extended source which is defiend as the flux when
+    threshold to an extended source which is defined as the flux when
     $\langle\tsext\rangle=25$ for a particular extension.  All sources
@@
     regions with higher background and (given the same number of photons)
-    more sensitive to harder soruces.  The plot has the same meaning as
+    more sensitive to harder sources.  The plot has the same meaning as
     in figure~\ref{index_sensitivity} and the simulations occur over
@@
     diffuse emission near the galactic center.  The left plot presents
-    the sensitivity when usings only photons with energies between 1 \gev
+    the sensitivity when using only photons with energies between 1 \gev
     and 100 \gev while the plot on the right presents the sensitivity only
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/counts_slice_ic443/v1/ic443_counts_slice.pdf
-    \caption{
-    The upper plot is the sum of the counts binned in galactic longitudinal
-    summed within 2\deg in galactic latitude centered on the SNR
-    IC443. The lower plot shows the same image but instead integrated
+    \caption{ The upper plot is the sum of the counts binned in galactic
+    longitudinal summed within 2\deg in galactic latitude centered on the
+    SNR IC443. The lower plot shows the same image but instead integrated
     in galactic longitude.  Overlaid on the plot is the model predicted
-    counts assuming that IC443 is a point source, an extended source,
-    and that there is just the diffuse background. These counts slices
-    are especially useful for visually assessing the quality of
-    the diffuse emission model in the region surrounding an
-    extended source candidate.
-    \label{counts_slice}
-    }
+    counts assuming that IC443 is a point source, an extended source, and
+    that there is just the diffuse background.  These plots were generated
+    for all extended source candidates.  They are especially useful for
+    visually assessing the quality of the diffuse emission model in the
+    region surrounding an extended source candidate.} \label{counts_slice}
   \end{center}
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/radial_integral_ic443/v1/ic443_radial_integral.pdf
-    \caption{The radial integral of the counts and the model predicted counts.
-    \todo[inline]{Add more text about why this is useful}
-    }
+    \caption{The sum of all counts within a given radial distance from
+    the SNR IC443's best fit position.  This plot is binned uniformly
+    in $\theta^2$ to correct for solid angle so that an isotropic
+    distribution is flat. Overlaid on the counts distribution is the
+    model predicted counts assuming the IC4343 is a point source, an
+    extended source, and that there is just the diffuse background.
+    These plots were generated for all extended source candidates.
+    These radial integral plots are useful for visually comparing the
+    observed counts to the PSF.}
     \label{radial_profile}
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/smoothed_counts_ic443/v1
-    \caption{Smoothed counts. Galactic and isotoropic as well as earth albedo background were subtracted.
-    \todo[inline]{describe that this is IC443 using (front? or back? or both?) photons.}
-    }
+    \caption{A map of the observed photons in the region around the SNR
+    IC443 with energies between 1 \gev and 100 \gev.  This plot has the
+    galactic and isotropic diffuse emission subtracted and is smoothed
+    by a $0.1\deg$ Gaussain kernel.  The overlaid box is the PSF for
+    a source of the same spectrum as IC443 normalized to have the same
+    intensity as IC443.  This PSF is smoothed by the same Gaussian kernel
+    and so represents the model of what IC443 would look like if it was
+    a point source. Since the observed counts are wider than the PSF,
+    we can see visually that IC443 is an extended source.  The black
+    cross is IC443's best fit center when fitting it with a uniform
+    disk spatial model. The
+    black crosses are all of the catalog sources in
+    the region and the white circle is the edge of the best fit
+    uniform disk which was fit to IC443 using \pointlike.  These plots
+    were generated for all extended source candidates.  They are useful
+    for assessing the overall quality of the source model and for looking
+    for nearby background sources which are not correctly modeled.}
     \label{smoothed_counts}
@@
     calculated by varying the extension away from its best fit value until
-    the log likelihood has changed by an amount 1/2.  These profiles are
-    generated for all extended source candidates. They plot is useful
-    to make sure the fitter is not stuck in a local minimum and to make
-    sure the profile is reasonably parabolic.
+    the log likelihood has changed by a particular amount.  These profiles are
+    generated for all extended source candidates. They are useful
+    to make sure the fitter find a global minimum and that
+    the likelihood function is not unphysically double peaked.
     }
@@
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v2
-    \caption{Example bad Fit: P72Y3047
-    \todo[inline]{Describe how this is a bad fit}
+    \caption{
+    The observed 1 \gev to 100 \gev photons for the
+    two year catalog source 2FGL J1856.2+0450c. This map is smoothed by
+    a 0.1\deg Gaussian kernel and the large white circle is the edge of
+    the fit uniform disk spatial model.  2FGL J1856.2+0450c fits to an
+    extension of 1.37\deg and the result is statistically significant
+    with \tsext=51.6. On the other hand, the extension encompasses many
+    catalog sources and the emission does not look to be uniform. Instead,
+    this source is fitting large scale residual. Although the fit is 
+    statistically significant, it is not physical and we discard sources
+    that look like this.
     }
@@
         \hline
-        Name                 &          \glon &          \glat &                    $\sigma$ &       TS &   $\tsext$ &      Major &      Minor &    Pos Ang &      Flux ($10^{-9}$) &                 Index \\
+        Name                 &          \glon &          \glat &                    $\sigma$ &       TS &   $\tsext$ &      Major &      Minor &        Ang &      Flux ($10^{-9}$) &                 Index \\
         \hline
@@
     \end{center}
-    \caption{
-    \todo[inline]{Add Caption.
-    Note about how \tsext for AGN calculated with pointlike}
+    \caption{The cumulative distribution of \tsext for 515 AGN associated
+    in the first LAT AGN catalog using photons with energies between 1
+    \gev and 100 \gev.  The method for selecting these AGN is described in
+    section~\ref{test_1lac_sources}.  AGN are expected to be unresolvable
+    so overlaid on this plot is a $\chi^2/2$ distribution suggested by
+    Wilk's theorem.  The motivation for this distribution to hold is
+    discussed in section~\ref{monte_carlo_validation}.  Overall, there
+    is very good agreement between this the fit values of \tsext and the
+    $\chi^2/2$ distribution.  Possible reasons for the discrepancy between
+    the distrubtions are discussed in section~\ref{test_1lac_sources}
+    but this plot demonstrates that any systematics in our extension
+    test are small compared to the signals we are looking for.
     }\label{agn_ts_ext}
@@
       \hline
-      Name                 &          \glon &          \glat &                    $\sigma$ &       TS &   $\tsext$ &      Major &      Minor &    Pos Ang &      Flux ($10^{-9}$) &                 Index \\
+      Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &      Major &      Minor &        Ang &      Flux ($10^{-9}$) &                 Index \\
       \hline
@@
       \hline
-      2FGL J1627.0-2425c   &     353.08\deg &      16.80\deg & $  0.41\deg \pm   0.05\deg$ &    139.2 &       28.9 &  0.042\deg &  0.036\deg &   54.4\deg & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ \\
-      2FGL J1554.4-5317c   &     328.13\deg &       0.26\deg & $  0.49\deg \pm   0.04\deg$ &    148.8 &       77.6 &  0.046\deg &  0.041\deg &   55.3\deg & $   16.2 \pm     1.5$ & $   2.31 \pm    0.11$ \\
-      2FGL J0823.0-4246    &     260.31\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &    314.6 &       49.2 &  0.026\deg &  0.023\deg &    5.0\deg & $    8.3 \pm     0.3$ & $   2.18 \pm    0.02$ \\
+      2FGL J1627.0-2425c   &     352.87\deg &      16.79\deg & $  0.53\deg \pm   0.06\deg$ &      131.0 &       21.1 &  0.060\deg &  0.047\deg &   39.8\deg & $    6.8 \pm     0.7$ & $   2.49 \pm    0.14$ \\
+      2FGL J1554.4-5317c   &     328.12\deg &       0.26\deg & $  0.52\deg \pm   0.04\deg$ &      149.0 &       39.6 &  0.044\deg &  0.039\deg &   55.5\deg & $   16.6 \pm     1.5$ & $   2.30 \pm    0.11$ \\
+      2FGL J0823.0-4246    &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      314.5 &       49.2 &  0.026\deg &  0.023\deg &    5.3\deg & $    8.3 \pm     0.6$ & $   2.18 \pm    0.07$ \\
       \hline
@@
       \hline
-      2FGL J1615.2-5138          &     331.74\deg &      -0.58\deg & $  0.52\deg \pm   0.04\deg$ &     75.3 &       45.2 &  0.071\deg &  0.049\deg &  -21.9\deg & $    1.3 \pm     0.2$ & $   1.75 \pm    0.25$ \\
-      2FGL J1632.4-4753c         &     336.52\deg &       0.06\deg & $  0.65\deg \pm   0.03\deg$ &    173.0 &       95.3 &  0.041\deg &  0.037\deg &    5.3\deg & $    2.9 \pm     0.2$ & $   2.28 \pm    0.08$ \\
-      2FGL J2021.5+4026          &      78.33\deg &       2.22\deg & $  0.71\deg \pm   0.04\deg$ &    245.7 &      151.7 &  0.047\deg &  0.038\deg &    4.3\deg & $    2.1 \pm     0.2$ & $   2.36 \pm    0.18$ \\
-      2FGL J1837.3-0700c         &      25.09\deg &       0.13\deg & $  0.35\deg \pm   0.07\deg$ &     47.3 &       20.6 &  0.076\deg &  0.063\deg &   -7.7\deg & $    1.0 \pm     0.2$ & $   1.59 \pm    0.30$ \\
-      2FGL J0851.7-4635          &     266.29\deg &      -1.43\deg & $  1.15\deg \pm   0.08\deg$ &    119.6 &       90.9 &  0.080\deg &  0.065\deg &   54.6\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.18$ \\
+      2FGL J1615.2-5138    &     331.67\deg &      -0.66\deg & $  0.43\deg \pm   0.04\deg$ &       77.6 &       45.3 &  0.058\deg &  0.047\deg &   20.4\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.26$ \\
+      2FGL J1632.4-4753c   &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      126.4 &       62.2 &  0.042\deg &  0.036\deg &  -16.1\deg & $    1.9 \pm     0.2$ & $   2.30 \pm    0.22$ \\
+      2FGL J2021.5+4026    &      78.17\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      221.2 &      140.6 &  0.044\deg &  0.030\deg &   51.1\deg & $    1.8 \pm     0.2$ & $   2.32 \pm    0.19$ \\
+      2FGL J1837.3-0700c   &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       48.0 &       20.9 &  0.075\deg &  0.064\deg &  -12.4\deg & $    1.1 \pm     0.1$ & $   1.60 \pm    0.17$ \\
+      2FGL J0851.7-4635    &     266.29\deg &      -1.41\deg & $  1.12\deg \pm   0.07\deg$ &      119.7 &       90.9 &  0.090\deg &  0.064\deg &   63.8\deg & $    1.3 \pm     0.1$ & $   1.74 \pm    0.12$ \\
       \hline
@@
         \hline
-        Name                 &     \tsinc &     \tsext &      $\glon_1$ &      $\glat_1$ & $\text{Flux}_1$ ($10^{-9}$) &   $\text{Index}_1$ &      $\glon_2$ &      $\glat_2$ & $\text{Flux}_1$ ($10^{-9}$) &  $\text{Index}_2$ \\
+        Name                 &     \tsinc &     \tsext &      $\glon_1$ &      $\glat_1$ & $\text{Flux}_1$             &   $\text{Index}_1$ &      $\glon_2$ &      $\glat_2$ & $\text{Flux}_2$             &  $\text{Index}_2$ \\
         \hline
@@
         \hline
-        2FGL J1627.0-2425c   &       23.8 &       28.9 &     353.04\deg &      16.96\deg & $       3.5 \pm        0.6$ & $  2.7 \pm   0.3$  &     353.14\deg &      16.50\deg & $       2.0 \pm        0.5$ & $  2.4 \pm   0.3$ \\
-        2FGL J1554.4-5317c   &       48.6 &       77.6 &     328.31\deg &       0.31\deg & $      10.0 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.28\deg &      -0.06\deg & $       1.0 \pm        0.7$ & $  1.6 \pm   0.4$ \\
-        2FGL J0823.0-4246    &       22.2 &       49.2 &     260.59\deg &      -3.26\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
+        2FGL J1627.0-2425c   &       16.6 &       21.1 &     353.00\deg &      16.97\deg & $       2.9 \pm        0.6$ & $  2.6 \pm   0.3$  &     353.26\deg &      16.67\deg & $       2.5 \pm        0.6$ & $  2.6 \pm   0.4$ \\
+        2FGL J1554.4-5317c   &       10.2 &       39.6 &     328.30\deg &       0.31\deg & $      10.1 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.27\deg &      -0.07\deg & $       0.9 \pm        0.7$ & $  1.5 \pm   0.4$ \\
+        2FGL J0823.0-4246    &       22.3 &       49.2 &     260.59\deg &      -3.27\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
         \hline
@@
         \hline
-        2FGL J1615.2-5138    &       34.3 &       45.2 &     331.77\deg &      -0.35\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.5$  &     331.51\deg &      -0.83\deg & $       0.4 \pm        0.1$ & $  2.1 \pm   0.5$ \\
-        2FGL J1632.4-4753c   &       24.8 &       95.3 &     336.16\deg &       0.34\deg & $       0.7 \pm        0.1$ & $  2.0 \pm   0.4$  &     336.72\deg &      -0.06\deg & $       0.7 \pm        0.1$ & $  3.1 \pm   0.5$ \\
-        2FGL J2021.5+4026    &       34.5 &      151.7 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.45\deg &       2.54\deg & $       0.5 \pm        0.1$ & $  1.9 \pm   0.4$ \\
-        2FGL J1837.3-0700c   &       15.4 &       20.6 &      25.06\deg &       0.24\deg & $       0.3 \pm        0.1$ & $  1.1 \pm   0.6$  &      25.08\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.6$ \\
-        2FGL J0851.7-4635    &       32.5 &       90.9 &     267.16\deg &      -1.60\deg & $       0.2 \pm        0.1$ & $  1.9 \pm   0.4$  &     266.43\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.5$ \\
+        2FGL J1615.2-5138    &       30.1 &       45.3 &     331.75\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.2 \pm   0.5$  &     331.46\deg &      -0.79\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
+        2FGL J1632.4-4753c   &       38.5 &       62.2 &     336.52\deg &       0.18\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
+        2FGL J2021.5+4026    &       34.7 &      140.6 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.43\deg &       2.55\deg & $       0.4 \pm        0.1$ & $  1.8 \pm   0.4$ \\
+        2FGL J1837.3-0700c   &       15.4 &       20.9 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.6$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.5$ \\
+        2FGL J0851.7-4635    &       17.2 &       90.9 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.38\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
         \hline
@@
       \label{dual_localization_results}
-      \caption{For the new extended source candidates in
-      table~\ref{new_ext_srcs_table}, we describe the results
-      of the dual localization procedure described in
+      \caption{For the new extended source candidates
+      in table~\ref{new_ext_srcs_table}, we describe the
+      results of the dual localization procedure described in
       section~\ref{dual_localization_method}. Here, the extended
@@
       using \gtlike with the best fit positions taken from \pointlike.
-      It can be directly compared to \tsext, which is taken from table~\ref{new_ext_srcs_table}.  For all of our candidates, $\tsext > \tsinc$
-      which shows that an extended source fits the source better than two
-      point sources.  As in table~\ref{known_extended_sources}, flux is
-      measured in units of $10^{-9}\ph/\cm^2/\sec$ and is the integral
-      flux between 1 \gev (10 \gev) and 100 \gev for the sources found
-      using photons above 1 \gev (10 \gev).}
+      It can be directly compared to \tsext, which is taken from
+      table~\ref{new_ext_srcs_table}.  For all of our candidates, $\tsext
+      > \tsinc$ which shows that an extended source fits the source better
+      than two point sources.  As in table~\ref{known_extended_sources},
+      flux is measured in units of $10^{-9}\ph/\cm^2/\sec$ and is the
+      integral flux between 1 \gev (10 \gev) and 100 \gev for the sources
+      found using photons above 1 \gev (10 \gev).}
     \end{centering}
@@
         \hline
-        2FGL J1627.0-2425c   &                155.0 &                139.2 &                103.8 &                     38.5 &                   28.9 &                 22.5 & $  0.41\deg \pm   0.05\deg$ & $  0.38\deg \pm   0.04\deg$ \\
-        2FGL J1554.4-5317c   &                108.4 &                148.8 &                138.4 &                     25.7 &                   77.6 &                 40.6 & $  0.49\deg \pm   0.04\deg$ & $  0.51\deg \pm   0.04\deg$ \\
-        2FGL J0823.0-4246    &                329.5 &                314.6 &                345.6 &                     60.4 &                   49.2 &                 51.5 & $  0.37\deg \pm   0.03\deg$ & $  0.38\deg \pm   0.03\deg$ \\
+        2FGL J1627.0-2425c   &                154.9 &                131.0 &                102.4 &                     32.6 &                   21.1 &                 23.3 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
+        2FGL J1554.4-5317c   &                134.8 &                149.0 &                137.6 &                     39.4 &                   39.6 &                 39.8 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
+        2FGL J0823.0-4246    &                347.3 &                314.5 &                343.6 &                     66.1 &                   49.2 &                 56.6 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
         \hline
@@
         \hline
-        2FGL J1615.2-5138    &                 74.7 &                 75.3 &                 88.7 &                     43.7 &                   45.2 &                 50.0 & $  0.52\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
-        2FGL J1632.4-4753c   &                173.9 &                173.0 &                157.7 &                     97.9 &                   95.3 &                 93.6 & $  0.65\deg \pm   0.03\deg$ & $  0.66\deg \pm   0.03\deg$ \\
-        2FGL J2021.5+4026    &                244.9 &                245.7 &                264.3 &                    152.8 &                  151.7 &                162.9 & $  0.71\deg \pm   0.04\deg$ & $  0.71\deg \pm   0.03\deg$ \\
-        2FGL J1837.3-0700c   &                 43.4 &                 47.3 &                 39.0 &                     17.4 &                   20.6 &                 17.7 & $  0.35\deg \pm   0.07\deg$ & $  0.34\deg \pm   0.06\deg$ \\
-        2FGL J0851.7-4635    &                117.1 &                119.6 &                124.7 &                     86.1 &                   90.9 &                 95.0 & $  1.15\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
+        2FGL J1615.2-5138    &                 78.2 &                 77.6 &                 88.2 &                     46.4 &                   45.3 &                 53.7 & $  0.43\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
+        2FGL J1632.4-4753c   &                126.9 &                126.4 &                158.1 &                     64.0 &                   62.2 &                 94.1 & $  0.44\deg \pm   0.04\deg$ & $  0.67\deg \pm   0.03\deg$ \\
+        2FGL J2021.5+4026    &                236.5 &                221.2 &                265.8 &                    156.0 &                  140.6 &                162.6 & $  0.59\deg \pm   0.03\deg$ & $  0.72\deg \pm   0.03\deg$ \\
+        2FGL J1837.3-0700c   &                 45.5 &                 48.0 &                 39.2 &                     18.6 &                   20.9 &                 18.8 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
+        2FGL J0851.7-4635    &                120.2 &                119.7 &                125.9 &                     90.1 &                   90.9 &                 94.7 & $  1.12\deg \pm   0.07\deg$ & $  1.16\deg \pm   0.08\deg$ \\
         \hline
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v2/run.py
-  \caption{1FGL J1628.6-2419c. In the opiucus region=most likeliy a molecular cloud.
-  %P72Y2516.
-  \todo[inline]{Add description of this source.
-  Note the bright nearby source
-  which would be in the lower right of the image at $l,b=352.14\deg,16.34\deg$.
-  $\ts=460$, source is P72Y2510. What is this source?}
+  \caption{
+  A diffuse subtracted 1 \gev to 100 \gev counts map of the region around
+  2FGL J1627.0-2425 smoothed by a 0.1\deg Gaussian kernel.  The red star
+  is the second LAT catalog's best fit position of 2FGL J1627.0-2425 and
+  the black cross is the background source 2FGL J1625.7-2526.  The red
+  cross and white circle represent the best position and extension of
+  2FGL J1627.0-2425 when fit assuming a uniform disk spatial model.
+  Overlaid on the plot are contours of a 100 micrometer infrared
+  image of the region as seen by IRAS (\cite{iras_rho_ophiuci}). This
+  source is in the Ophiuchus region and is most likely unaccounted for
+  diffuse emission.  More information about this source is presented
+  in section~\ref{section_ophiuchus}.
   }\label{1FGL_J1628.6-2419c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1554.0-5345c/v2/source_1FGL_J1554.0-5345c.pdf
-  \caption{1FGL J1554.0-5345c. 
+  \caption{
+2FGL J1554.4-5317c
+1FGL J1554.0-5345c
   %P72Y2405.
+  Using $E>1\gev$. 
   \todo[inline]{Describe this source/the fit.Unidentified source likely diffuse emission.}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-  \caption{1FGL J0823.3-4248. P72Y1212. Coincident with Puppis A SNR.
-  %P72Y1212.
-  \todo[inline]{
-  Describe this soruce better.
-  Describe nearby source Vela.
-  At position $l,b=263.55\deg,-2.79\deg$ is over 3 degrees away,
-  Spills into the image at left.}
+  \caption{A diffuse subtracted 1 \gev to 100 \gev counts map of the
+  region around 2FGL J0823.0-4246. The red star is the second LAT
+  catalog's best fit position of 2FGL J0823.0-4246.  The red cross
+  and white circle are the best fit position and extension of this
+  source assuming a uniform disk spatial model.  The two green stars
+  are the positions of two nearby catalog source 2FGL J0823.4-4305 and
+  2FGL J0821.0-4254 that we removed from our region. This source is
+  spatially coincident with the Puppis A SNR. Overlaid on the figure are
+  ROSAT contours of Puppis A SNR (\cite{rosat_puppis_a}). There is good
+  agreement between the LAT and X-ray emission.  More information about
+  this source is shown in section~\ref{section_puppis_a}.  The emission
+  on the top left comes from the very bright Vela Pulsar. Even though
+  Vela is over 3 degrees away from this source at a position of
+  $l,b=263.55\deg,-2.79\deg$, it can be seen because it is so bright.
+  \todo[inline]{This figure could better explain the source}
+  }\label{1FGL_J0823.3-4248}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1613.6-5100c}
+  \end{center}
+  % this plot came from 
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
+  \caption{
+2FGL J1615.2-5138
+1FGL J1613.6-5100c
+%P72Y2473
   \todo[inline]{Describe this source better. Describe the Contour}
-  }\label{1FGL_J0823.3-4248}
+  }\label{1FGL_J1613.6-5100c}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1632.9-4802c}
+  \end{center}
+  % this plot came from 
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
+  \caption{
+2FGL J1632.4-4753c
+1FGL J1632.9-4802c. 
+% P72Y2540
+  \todo[inline]{Describe this source better. Describe the Contour}
+  }\label{1FGL_J1632.9-4802c}
 \end{figure}
@@
   \caption{
-  Gamma Cygni. P72Y3281
+  2FGL J2021.5+4026
+  1FGL J2020.0+4049
+  P72Y3281
+  Using $E>10\gev$. 
   \todo[inline]{Describe this source better. Describe the Contour}
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
-  \end{center}
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
-  \caption{Vela Jr. P72Y1287. Using $E>10\gev$. 
-  \todo[inline]{Note that sourceis con with a $0.25\deg$ gaussian which is different than other plots.}
-  \todo[inline]{Describe this source better. Describe the Contour}
-  }\label{Vela_Jr}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
     \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1837.5-0659c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v2/source_1FGL_J1837.5-0659c.pdf
-  \caption{1FGL J1837.5-0659c. P72Y2974
+  \caption{
+2FGL J1837.3-0700c
+1FGL J1837.5-0659c. 
+%P72Y2974
   \todo[inline]{Describe this source better. Describe the Contour}
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1632.9-4802c}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
-  \caption{1FGL J1632.9-4802c. P72Y2540
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
+  \caption{
+2FGL J0851.7-4635
+  Vela Jr. 
+  P72Y1287. 
+  Using $E>10\gev$. 
+  \todo[inline]{Note that source is convolved with a $0.25\deg$ gaussian
+  which is different than other plots.}
   \todo[inline]{Describe this source better. Describe the Contour}
-  }\label{1FGL_J1632.9-4802c}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1613.6-5100c}
-  \end{center}
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
-  \caption{
-  1FGL J1613.6-5100c . P72Y2473
-  \todo[inline]{Describe this source better. Describe the Contour}
-  }\label{1FGL_J1613.6-5100c}
+  }\label{Vela_Jr}
 \end{figure}

### 2011-07-17 extended_catalog/paper/extended_catalog.tex
improvements

@@
 \section{Introduction}
+
+\todo[inline]{Add note about how difficult lat analysis in
+the galactic plane is because of large PSF, low statistics,
+and high source density. Describe how it requires a certain amount
+of iterative, by eye modifying of the sky model. Not
+adequate to simply use 2FGL}
 
@@
 
-We found very good agreement between the two methods. For the new
+We found good agreement between the two methods. For the new
 extended source candidates, table~\ref{alt_diff_model_results} shows
@@
 Although these shapes are significantly different, the convolution
-of them with the PSF for typical sizes look very similar.  Even
+of them with the PSF for typical sizes look similar.  Even
 though these shapes are significantly different, we demonstrate in
@@
 the other hand, the disk and Gaussian's 68\% containment radius are
-very similar.
+similar.
 
@@
 
-As was shown, we gain very little in sensitivity using photons with energies
+As was shown, we gain little in sensitivity using photons with energies
 below 1 \gev. On the other hand, the large PSF at low energy makes us
@@
 galactic plane looking for possible extended sources near pulsars which
-are very bright at lower energy but cutoff before 10 \gev.  This approach
+are bright at lower energy but cutoff before 10 \gev.  This approach
 of using only photons with energy above 10 \gev was successfully used
@@
 Fermi catalog~\ref{first_cat,second_cat}. Furthermore, the galactic plane is
-very crowded and so it is often difficult to get a good model for the
+crowded and so it is often difficult to get a good model for the
 region around a catalog source.  Because of this, finding a source with
@@
 we don't have a great model of the nearby catalog sources. As a result,
-2FGL J1856.2+0450c fits to a very large extension of 1.37\deg and the result is
+2FGL J1856.2+0450c fits to a large extension of 1.37\deg and the result is
 statistically significant with \tsext=51.6.  By looking at the residuals,
@@
 considering all evnets above 6\gev. Looking at all photons with
-energy above 1\gev 
+energy above 1 \gev 
 is problematic because of background source confusion whereas using photons
-with energy above 10\gev does not have the statistics for a significant dection.
+with energy above 10 \gev does not have the statistics for a significant dection.
 
@@
 calibration source to demonstrate the efficacy of our tool. Nevertheless,
-it would be very interesting if AGN could be spatially resolved and
+it would be interesting if AGN could be spatially resolved and
 there are theories that predict this (\cite{pair_halo_paper}).
@@
 After launch, a discrepancy was found using flight data above a
-few \gev in the PSF measured using very bright AGN.  This result
+few \gev in the PSF measured using bright AGN.  This result
 was presented in conference and a publication is in preparation.
@@
 % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
+% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 
+% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
 % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
@@
 
-Eight new extended sources not included in the two year catalog were
-found using this search. Three were found in our search using events
-above 1 \gev and five were found in the search using events
-above 10 \gev.
-For all the extended sources, the results of our fit are summarized in
-table~\ref{new_ext_srcs_table}. The table includes the best fit position and
-extension of the source. It also includes the source's significance and
-significance of extension.
+Eight new extended sources not included in the two year catalog
+were found using this search. Three were found in our search using
+events above 1 \gev and five were found in the search using events
+above 10 \gev.  For all the extended sources, the results of our
+fit are summarized in table~\ref{new_ext_srcs_table}. The table
+includes for each source the best fit position, extension, spectrum,
+source significance, and significance of extension.
+
+For all the extended sources, table~\ref{dual_localization_results}
+presents information about the of source confusion by fitting the same
+region as two point sources using the dual localization method described
+in section~\ref{dual_localization_method}. The table compares \tsext
+to \tsinc and summarized the positions and spectra of the two sources.
+Finally, table~\ref{alt_diff_model_results} summarized the results of
+a crosscheck of the source fitting the region with an alternate diffuse
+model described in section~\ref{alt_diff_model_description}.  These tables
+show that our extended sources are not likely the result of source confusion
+and that they are robust to changing the diffuse emission model.
+
+\subsection{2FGL J0823.0-4246}
+\label{section_2FGL_J0823.0-4246}
+
+% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
+% Deleted 
+%  * P72Y1214 - 2FGL J0823.4-4305
+%  * P72Y1210 - 2FGL J0821.0-4254
+
+The two year catalog source 2FGL J0823.0-4246 was found to be
+extended using photons with energy between 1 \gev and 100 \gev.
+We found an extension of $0.37\deg\pm0.03\deg$ and an extension
+significance of $\tsext=46.1$.  The source was fit to a position of
+$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
+counts map of this source.  This source is coincident with the one year
+catalog source 1FGL J0823.3-4248.
+
+To get a good fit of the region we had to remove the nearby catalog
+sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
+extended emission.  We tested the source for source confusion by fitting
+it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
+we conclude that this is an extended source.  The removed catalog sources
+are shown in figure~\ref{1FGL_J0823.3-4248}.
+
+This extended source is spatially coincident with the SNR Puppis A.
+Overlaid on figure~\ref{1FGL_J0823.3-4248} are ROSAT contours of Puppis
+A (\cite{rosat_puppis_a}). There is good agreement between of the X-ray
+shape with the fit size in \gev.
+
+\todo[inline]{Give some additional interpretation of the Puppis A SNR.}
 
 \subsection{2FGL J1627.0-2425c}
-\label{section_ophiuchus}
+\label{section_2FGL_J1627.0-2425c}
 
@@
 The two year catalog source 2FGL J1627.0-2425c was found to be
-significantly extended when using photons between 1 \gev and 100 \gev.
-The best fit extension was $0.53\deg\pm0.06\deg$ and the best fit position
-is $(l,b)=(352.87\deg, 16.79\deg)$ The source also appeared in the first
-fermi catalog as 1FGL J1628.6-2419c.  and the extension significance
-was $\tsext=21.1$.  A counts map showing this source is seen in
-figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion, we also
-fit this region as two point sources. Since $\tsinc=16.6$ is smaller
-than \tsext, the emission is more likeliy to come from an extended source.
+significantly extended when using photons with energies between 1 \gev
+and 100 \gev.  The best fit extension was $0.53\deg\pm0.06\deg$ and the
+best fit position is $(l,b)=(352.87\deg, 16.79\deg)$ The source also
+appeared in the first LAT catalog as 1FGL J1628.6-2419c.  The extension
+significance was $\tsext=20.3$.  A counts map showing this source is
+seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
+we also fit the source instead as two point sources. Since $\tsinc=19.3$
+is smaller than \tsext, we conclude that this is an extended source.
 
@@
 of the core of the Ophiuchus molecular cloud which contains massive
-star-forming regions that are very bright in the infrared.  We have
-overlaid on the plot of figure~\ref{1FGL_J1628.6-2419c} a 100 micrometer
-infared image of this region as seen by IRAS and there is good spatial
-overlap between with the \gev observed emission
-(\cite{iras_rho_ophiuci}).
-
-The region has abundant molecular and atomic gas traced by CO and HI but
-also plenty of dark gas, the kind that we find only by its association
-with dust emission. Embedded star-forming regions make it even more
-challenging to measure the column density of dust.
-Although this region is significantly extended, we conclude that what
-we are seeing is most likely an inadequacy in the diffuse $\gamma$-ray
-emission model.
-
-\todo[inline]{Can we get another citation about dark gas
-and stuff?
+star-forming regions that are bright in the infrared.  We have overlaid
+on figure~\ref{1FGL_J1628.6-2419c} contours of the 100 micrometer infared
+image of this region measured by IRAS. There is good spatial overlap
+with the \gev emission (\cite{iras_rho_ophiuci}).
+
+The region also has abundant molecular and atomic gas traced by CO
+and HI but also plenty of dark gas, the kind that we find only by its
+association with dust emission. Embedded star-forming regions make it even
+more challenging to measure the column density of dust.  Although this
+region is significantly extended, we conclude that this source most
+likely represents inadequacy in the diffuse $\gamma$-ray emission model.
+
+\todo[inline]{Can we get another citation about dark gas and stuff?
 Better note about spectral index being typical of difuse emission.
-Also does this description make sense? Also, is 
-citation about IRAS good?}
+Also does this description make sense?}
 
 \subsection{2FGL J1554.4-5317c}
+\label{section_2FGL_J1554.4-5317c}
 
@@
 The two year catalog source 2FGL J1554.4-5317c was found to be extended
-using photons with energy between 1 \gev and 100 \gev.  We found an
+using photons with energies between 1 \gev and 100 \gev.  We found an
 extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
-$\tsext=39.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
+$\tsext=37.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
 \ref{1FGL_J1554.0-5345c} shows a counts map of this source.
-
-It was found in the one year catalog under the name 1FGL J1554.0-5345c.
-To get a good fit of the source, we had to remove the nearby catalog
-source 2FGL J1551.3-5333c which we believed to be suprious. By looking at
-the counts map, we saw no differentation in the source at the location
-of the two catalog sources. 
-These soruce modifications are further described
-in the caption to figure~\ref{1FGL_J1554.0-5345c}.
-
-We tested this region for source confusion
-by comparing the increase in log likelihood fitting the region as an
-extended source to the increase in log likelihood fitting the region
-as two point sources. Since $\tsinc=10.2$ is smaller than \tsext, we
-conclude that the source is spatially extended and not multiple point
-sources. More information about the dual localization results for this
-source are shown in table \ref{dual_localization_results}.
-
-There are no obvious counterparts to this source. Furthermore, this
-source is relativly soft with a spectral index 2.31 and very close to
-the galacitc plane in a region of large diffuse emission.  We conclude
-that although this region is significantly extended, it most likely
-represents unmodeled diffuse emission.
-\todo[inline]{this needs more quantification/description.
-Improve the point about how since the source is soft, it
-is more consistent with diffuse emission.
+This source was found in the one year catalog with the name 1FGL J1554.0-5345c.
+
+To get a good fit of the source, we removed the nearby catalog source
+2FGL J1551.3-5333c which is contained within the extended source.
+We tested this source for source confusion by fitting it instead
+as two point sources.  Since $\tsinc=9.2$ is less than \tsext,
+we conclude that the source is spatially extended. The region is further described in
+the caption to figure~\ref{1FGL_J1554.0-5345c}.
+
+There are no obvious counterparts to this source at other
+wavelengths. Furthermore, this source is relativly soft with a spectral
+index 2.31 and is close to the galacitc plane in a region of large
+diffuse emission.  We conclude that although this region is significantly
+extended, it is most likely unmodeled diffuse emission.
+
+\todo[inline]{this needs more quantification/description.  Improve the
+point about how since the source is soft, it is more consistent with
+diffuse emission.}
+
+\subsection{2FGL J0851.7-4635}
+\label{section_2FGL_J0851.7-4635}
+
+% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
+% Delete:
+% * P72Y1291 - 2FGL J0853.5-4711
+% * P72Y1296 - 2FGL J0855.4-4625
+% * P72Y1274 - 2FGL J0848.5-4535
+% * P72Y1259 - 2FGL J0842.9-4721
+% * P72Y1300 - 2FGL J0858.0-4815
+% Modify:
+% * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.232,0.517,SkyDir.GALACTIC))
+%              (initial Position - SkyDir(265.5705,-0.0099)
+% * P72Y1310 - 2FGL J0901.7-4655 - SkyDir(267.311,-0.190,SkyDir.GALACTIC)
+%              (initial Position - SkyDir(267.79,-0.3339)
+
+The two year catalog source 2FGL J0851.7-4635 was found to be
+extended using photons with energies between 10 \gev and 100
+\gev. We fit an extension of $1.12\deg\pm0.07\deg$ with an extension
+significance of $\tsext=76.7$.  The source was fit to a position of
+$(l,b)=(266.29\deg,-1.41\deg)$.  Figure~\ref{Vela_Jr} shows a counts
+map of this source.  This source has no counterparts in the first year
+LAT catalog.
+
+To get a good fit of the region, we had to remove three nearby catalog
+sources 2FGL J0848.5-4535, 2FGL J0855.4-4625, and 2FGL J0853.5-4711
+which are part of the extended emission.  In addition, we relocalized
+the position of two nearby catalog sources 2FGL J0854.7-4501 and 2FGL
+J0901.7-4655 to better fit their position at high energies in the presence
+of an extended source.  This localization was done iterativly alterantly
+fitting the position of these two point sources and the extension of
+2FGL J0851.7-4635 until the fit globally converged.  2FGL J0854.7-4501
+moved to $(l,b)=(266.232\deg,0.517\deg)$ and 2FGL J0901.7-4655 moved to
+$(l,b)=(267.311\deg,-0.190\deg)$. In addition, we removed the further away
+catalog source 2FGL J0858.0-4815 beacuse it was not significant above 10
+\gev.  After modifying the region, we found that \tsinc=16.2 which is less
+than \tsext so we conclude that the source is extended These modifications
+are further described in the caption to figure~\ref{Vela_Jr}.
+
+2FGL J0851.7-4635 is spatially coincident with the SNR Vela Jr.  Overlaid
+on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in \tev by
+H.E.S.S (\cite{vela_jr_hess}).  The \gev and \tev morphology match well.
+
+\todo[inline]{
+Add a better interpreation.
+Explain that Vela Jr will be described better in upcoming publication???
 }
 
-\subsection{2FGL J0823.0-4246}
-\label{section_puppis_a}
-
-% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-% Deleted 
-%  * P72Y1214 - 2FGL J0823.4-4305
-%  * P72Y1210 - 2FGL J0821.0-4254
-
-The two year catalog source 2FGL J0823.0-4246 was found to be
-extended using photons with energy between 1 \gev and 100 \gev.
-We found an extension of $0.37\deg\pm0.03\deg$ and an extension
-significance of $\tsext=49.2$.  The source was fit to a position of
-$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
-a counts map of this source.
-
-This source is coincident with the one year catalog source named 1FGL
-J0823.3-4248.  To get a good fit of the source, we had to remove the
-nearby catalog sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which
-are part of the extended emission.  We tested the source for spatial
-confusion by fitting it as two point sources. Because $\tsinc=22.3$ is
-smaller then \tsext, we believe that this source is spatially extended.
-These removed catalog soruces are shown in figure~\ref{1FGL_J0823.3-4248}.
-
-This extended source is spatially coincident with the SNR Puppis A.
-Overlaid on figure~\ref{1FGL_J0823.3-4248} are ROSAT contours of
-Puppis A (\cite{rosat_puppis_a}). There is good agreement
-between the measured radius of $\sigma=0.37$ degrees in \gev and 
-the X-ray contours of the source.
-
-\todo[inline]{Give some additional interpretation of the Puppis A SNR.}
-
-\subsection{2FGL J1615.2-5138}
-
-% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
+\subsection{2FGL J1615.0-5051}
+\label{section_2FGL_J1615.0-5051}
+
+% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138 % extended source
+% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 % extended source
 % Deleted
@@
 %  *P72Y2496 - 2FGL J1622.8-5006
-% Modify 
-%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.365,0.005,SkyDir.GALACTIC)
-% New source
-%  * SkyDir(332.426,-0.331,SkyDir.GALACTIC
-
-The two year catalog source 2FGL J1615.2-5138 was found to be extended
-using photons with energies between 10 \gev and 100 \gev.  This source
-is coincident with the one year catalog source 1FGL J1613.6-5100c.
-We found an extension of $0.43\deg\pm0.04\deg$ with an extension
-significance of \tsext=45.3.  The source was fit to a position of
-$(l,b)=(331.67\deg,-0.66\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
-a counts map of this source.
-
-To get a good fit for the region, we had to remove from our model
-the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
-and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
-iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
-position and extension of 2FGL J1615.2-5138.  We ended up with a best
-fit position of the nearby source 2FGL J1615.0-5051 having moved from
-$(l,b)=(332.2684\deg,0.043\deg)$ to $(l,b)=(332.365\deg,0.005\deg)$.  In addition,we
-had to add a new source not in the catalog at the position of
-$(l,b)=(332.426\deg,-0.331\deg)$.  The location of these sources was found by iterativly
-fitting the position of these sources as well as the extension of 2FGL
-J1615.2-5138 until a stable fit was found.  It is unclear of this new seed
-is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
-2FGL J1615.0-5051 was not found to be significantly extended using two
-years of data but the fit of 2FGL J1615.2-5138 was clearly growing too
-large to obsorb residual in the direction of J1615.2-5138 until we added
-the additional point source.
-These modifications are further described in the caption to 
-figure~\ref{1FGL_J1613.6-5100c}.
-
-To address the possibility of source confusion, we compared the likelihood
-fitting 2FGL J1615.2-5138 as two point sources to one source.  We found
-that \tsinc=30.1 which is smaller then \tsext so we believe that this
-is extended emission.
+
+\subsection{2FGL J1615.2-5138}
+\label{section_2FGL_J1615.2-5138}
+
+% Same modifications as 2FGL J1615.0-5051.
+
+%The two year catalog source 2FGL J1615.2-5138 was found to be extended
+%using photons with energies between 10 \gev and 100 \gev.  This source
+%is coincident with the one year catalog source 1FGL J1614.7-5138c.
+%We found an extension of $0.43\deg\pm0.04\deg$ with an extension
+%significance of \tsext=45.3.  The source was fit to a position of
+%$(l,b)=(331.67\deg,-0.66\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
+%a counts map of this source.
+
+%To get a good fit for the region, we had to remove from our model
+%the nearby catalog sources 2FGL J1620.6-5111c, 2FGL J1619.7-5040c,
+%and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
+%iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
+%position and extension of 2FGL J1615.2-5138.  We ended up with a best
+%fit position of the nearby source 2FGL J1615.0-5051 having moved from
+%$(l,b)=(332.2684\deg,0.043\deg)$ to $(l,b)=(332.365\deg,0.005\deg)$.  In addition,we
+%had to add a new source not in the catalog at the position of
+%$(l,b)=(332.426\deg,-0.331\deg)$.  The location of these sources was found by iterativly
+%fitting the position of these sources as well as the extension of 2FGL
+%J1615.2-5138 until a stable fit was found.  
+%These modifications are further described in the caption to 
+%figure~\ref{1FGL_J1613.6-5100c}.
+
+%To address the possibility of source confusion, we compared the likelihood
+%fitting 2FGL J1615.2-5138 as two point sources to one source.  We found
+%that \tsinc=30.1 which is smaller then \tsext so we believe that this
+%is extended emission.
+
+\todo[inline]{This section needs to be rewritten}
+
+%This extended source is spatially coincident with the extended source
+%HESS J1614-518 which was reported in the H.E.S.S. survey of the Inner
+%Galaxy (\cite{HESS_plane_survey}). Overlaid on figure~\ref{1FGL_J1613.6-5100c} are the H.E.S.S
+%contours of this source and it can be seen that there is good spatial
+%overlap between the LAT and H.E.S.S. emission.
+%
+%It is unclear if our model around the nearby souce 2FGL J1615.0-5051
+%is good. 2FGL J1615.0-5051 is spatially coincident with the extended H.E.S.S.
+%source HESS J1616-508 but was not found to be significantly extended
+%with our extended source search.
+%
+%It is unclear if this new source is physically real.
+%2FGL J1615.0-5051 fit $\ts=28$ and the added source had $\ts=12$
+%which is not extended.
+%2FGL J1615.0-5051 was not found to be significantly extended.
+%$\ts=12$ which is not significant. 
+%
+%It is unclear of this new seed
+%is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
+%2FGL J1615.0-5051 was not found to be significantly extended using two
+%years of data but the fit of 2FGL J1615.2-5138 was clearly growing too
+%large to obsorb residual in the direction of J1615.2-5138 until we added
+%the additional point source.
+%
+%
+%HESS J1616-508
 
@@
 \subsection{2FGL J1632.4-4753c}
+\label{section_2FGL_J1632.4-4753c}
 
@@
 To get a good fit of the region, we had to remove from our model
-the four catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
+the three catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
 2FGL J1634.4-4743c.4-4820c. These sources all are on top of this
@@
 In addition we removed from our region four farther away two year
-catalog sources J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615,
+catalog sources 2FGL J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615,
 2FGL J1639.8-4921c because they were not significant above 10 \gev.
@@
 
-\todo[inline]{Describe What this source is/What HESS Source it is near}
-\todo[inline]{Describe contours overlaid on source}
-
-\subsection{2FGL J2021.5+4026}
-
-% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-% Delete:
-% * P72Y3282 - 2FGL J2019.1+4040
-% * P72Y3292 - 2FGL J2022.8+3843c
-% * P72Y3287 - 2FGL J2020.0+4159
-% * P72Y3262 - 2FGL J2013.8+4115c
-% * P72Y3260 - 2FGL J2012.4+3955c
-% New source
-%  * SkyDir(78.854,2.670,SkyDir.GALACTIC)
-
-The two year catalog source 2FGL J2021.5+4026 was found to be extended
-using photons with energies between 10 \gev and 100 \gev. This source
-is coincident with the one year catalog source 1FGL J2020.0+4049. We
-fit an extension of $0.59\deg\pm0.03\deg$ with an extension
-significance of $\tsext=140.6$.  The source was fit to a position of
-$(l,b)=(78.17\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
-counts map of this source.
-
-To get a good fit of the region, we had to remove the nearby catalog
-source 2FGL J2019.1+4040 which were part of the extended source.
-Further, we found it necessary to add an additional point source not in
-the two year catalog into our background model.  The new source is was
-localized to a position of $(l,b)=(78.854,2.670)$ and had $\ts\approx 16$
-(using \pointlike).  Although the source is not very significant, not
-including it into the background model appeared visually to significantly
-throw off the fit of the region.  In addition, we removed the four
-further away catalog sources 2FGL J2022.8+3843c, 2FGL J2020.0+4159,
-2FGL J2013.8+4115c, and 2FGL J2012.4+3955c from our region becuase they
-were not signifcant above 10\gev.  After modifying the region, we found
-that \tsinc=34.7 which is less than \tsext, so we believe that source
-source is spatially extended.  These modifications are further described
-in the caption to figure~\ref{1FGL_J2020.0+4049}.
-
-\todo[inline]{
-This source is the Gamma Cygni SNR!
-
-Describe how this source is analyzed more carefully in the paper
-\cite{A cocoon of freshly accelerated cosmic rays detected by Fermi
-in the Cygnus superbubble}
-}
-\todo[inline]{Describe contours overlaid on source}
+This extended source is spatially coincident with
+the \tev source HESS J1634-472.  Overlaid on the counts map are the
+contours of the region as seen in \tev (\cite{HESS_plane_survey})
+and we see that there is good spatial overlap of these sources.
+
+\todo[inline]{Describe the interpretation of this source}
 
 \subsection{2FGL J1837.3-0700c}
+\label{section_2FGL_J1837.3-0700c}
 
@@
 
-This source is in a very complicated region. There are two very nearby
+This source is in a complicated region. There are two nearby
 catalog sources 2FGL J1836.8-0623c and 2FGL J1837.3-0700c which are
@@
 which is less than \tsext, so we believe that the emission from this
-soruce spatially extended.  These modifications are further described
+source spatially extended.  These modifications are further described
 in the caption to figure~\ref{1FGL_J2020.0+4049}.
+
+This source is spatially coincident with the \tev source HESS J1837-069.
+Overlaid on the figure~\ref{1FGL_J2020.0+4049} are H.E.S.S contours of
+HESS J1837-069 (\cite{HESS_plane_survey}). There is a reasonable spatial
+overlap of these sources.
 
@@
 Near HESS source HESS J1837. 
-Discuss the upcomming publication???
-Describe contours overlaied on source}
-
-\subsection{2FGL J0851.7-4635}
-
-% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
+Discuss the upcomming publication???}
+
+\subsection{2FGL J2021.5+4026}
+\label{section_2FGL J2021.5+4026}
+
+% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
 % Delete:
-% * P72Y1291 - 2FGL J0853.5-4711
-% * P72Y1296 - 2FGL J0855.4-4625
-% * P72Y1274 - 2FGL J0848.5-4535
-% * P72Y1259 - 2FGL J0842.9-4721
-% * P72Y1300 - 2FGL J0858.0-4815
-% Modify:
-% * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.232,0.517,SkyDir.GALACTIC))
-%              (initial Position - SkyDir(265.5705,-0.0099)
-% * P72Y1310 - 2FGL J0901.7-4655 - SkyDir(267.311,-0.190,SkyDir.GALACTIC)
-%              (initial Position - SkyDir(267.79,-0.3339)
-
-The two year catalog source 2FGL J0851.7-4635 was found to be extended
-using photons with energies between 10 \gev and 100 \gev. This source has
-no counterparts in the first year LAT catalog.  We fit an extension of
-$1.12\deg\pm0.07\deg$ with an extension significance of $\tsext=90.9$.
-The source was fit to a position of $(l,b)=(266.29\deg,-1.41\deg)$.
-Figure~\ref{Vela_Jr} shows a counts map of this source.
-
-To get a good fit of the region, we had to remove three nearby catalog
-sources 2FGL J0848.5-4535, 2FGL J0855.4-4625, and 2FGL J0853.5-4711 which
-were part of the extended source.  In addition, we had to relocalize
-the position of two nearby catalog sources to better fit their position
-at high energies.  We localized 2FGL J0854.7-4501 to a position of
-$(l,b)=(266.232\deg,0.517\deg)$ and 2FGL J0901.7-4655 to a position of
-$(l,b)=(267.311\deg,-0.190\deg)$. In addition, we removed the further
-away catalog source 2FGL J0858.0-4815 beacuse it was not significant
-above 10 \gev.  After modifying the region, we found that \tsinc=17.2
-which is less than \tsext, so we believe that this region is not source
-confusion but is instead a spatially extended source.  These modifications
-are further described in the caption to figure~\ref{Vela_Jr}.
-
-\todo[inline]{explain that Vela Jr will be described better in upcoming publication}
-\todo[inline]{Describe contours overlaid on source}
+% * P72Y3282 - 2FGL J2019.1+4040
+% * P72Y3292 - 2FGL J2022.8+3843c
+% * P72Y3287 - 2FGL J2020.0+4159
+% * P72Y3262 - 2FGL J2013.8+4115c
+% * P72Y3260 - 2FGL J2012.4+3955c
+% New source
+%  * SkyDir(78.854,2.670,SkyDir.GALACTIC)
+
+The two year catalog source 2FGL J2021.5+4026 was found to be extended
+using photons with energies between 10 \gev and 100 \gev. This source
+is coincident with the one year catalog source 1FGL J2020.0+4049. We
+fit an extension of $0.59\deg\pm0.03\deg$ with an extension
+significance of $\tsext=140.6$.  The source was fit to a position of
+$(l,b)=(78.17\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
+counts map of this source.
+
+To get a good fit of the region, we had to remove the nearby catalog
+source 2FGL J2019.1+4040 which were part of the extended source.
+Further, we found it necessary to add an additional point source not in
+the two year catalog into our background model.  The new source is was
+localized to a position of $(l,b)=(78.854,2.670)$ and had $\ts\approx 16$
+(using \pointlike).  Although the source is not very significant, not
+including it into the background model appeared visually to significantly
+throw off the fit of the region.  In addition, we removed the four
+further away catalog sources 2FGL J2022.8+3843c, 2FGL J2020.0+4159,
+2FGL J2013.8+4115c, and 2FGL J2012.4+3955c from our region becuase they
+were not significant above 10 \gev.  After modifying the region, we found
+that \tsinc=34.7 which is less than \tsext, so we believe that this
+source is spatially extended.  These modifications are further described
+in the caption to figure~\ref{1FGL_J2020.0+4049}.
+
+This source is spatially coincident with the Gamma Cygni SNR.  Contours of
+Gamma Cygni at 408MHz from the Canadian Galactic Plane Survey are overlaid
+on figure~\ref{1FGL_J2020.0+4049} and there is good spatial agreement
+with the LAT emission (\cite{canadian_galactic_plane_survey}).
+
+\todo[inline]{
+Add more interpreation about this source. Describe how this source
+will be more carefully analyzed in the paper
+``A cocoon of freshly accelerated cosmic rays detected by Fermi
+in the Cygnus superbubble''}
 
@@
     This plot demonstrates that different spatial models when smoothed
-    by the PSF look very similar.  The $y$ axis is the log of the
+    by the PSF look similar.  The $y$ axis is the log of the
     intensity and the $x$ axis is $\theta^2$.  The black line is the
@@
       This plot shows that fitting the same source with different spatial
-      shapes can lead to very different values of $\sigma$. On the other
+      shapes can lead to different values of $\sigma$. On the other
       hand, the different shapes have a good agreement about the 68\%
@@
     a source is best for sources with size $~0.5\deg$. It also shows
-    that for sources neither very large nor soft, our sensitivity is
+    that for sources neither too large nor soft, our sensitivity is
     not significantly improved using photons with energy between 100
@@
     \begin{centering}
-      \begin{tabular}{r|rrrrrrrrrr}
+      \begin{tabular}{l|rrrrrrrrrr}
         \hline
@@
         \hline
-        \multicolumn{11}{c}{$E > 1\gev$} \\
+        \multicolumn{11}{c}{$E > 1 \gev$} \\
         \hline
@@
         \hline
-        \multicolumn{11}{c}{$E > 10\gev$} \\
-        \hline
+        \multicolumn{11}{c}{$E > 10 \gev$} \\
+        \hline
+        MSH 15-52            &     320.39\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &       73.7 &        9.5 &  0.033\deg &  0.032\deg &    3.9\deg & $    0.6 \pm     0.1$ & $   2.32 \pm    0.23$ \\
         HESS J1825-137       &      17.58\deg &      -0.46\deg & $  0.64\deg \pm   0.08\deg$ &       85.6 &       62.5 &  0.050\deg &  0.045\deg &   33.6\deg & $    1.8 \pm     0.3$ & $   1.75 \pm    0.20$ \\
-        MSH 15-52            &     320.39\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &     73.7 &        9.5 &  0.033\deg &  0.032\deg &    3.9\deg & $    0.6 \pm     0.1$ & $   2.32 \pm    0.23$ \\
-
       \end{tabular}
@@
     discussed in section~\ref{monte_carlo_validation}.  Overall, there
-    is very good agreement between this the fit values of \tsext and the
+    is good agreement between this the fit values of \tsext and the
     $\chi^2/2$ distribution.  Possible reasons for the discrepancy between
@@
   % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-  % 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
+  % 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
   % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
@@
   \begin{centering}
-    \begin{tabular}{r|rrrrrrrrrr}
+    \begin{tabular}{l|rrrrrrrrrr}
       \hline
@@
       \hline
-      \multicolumn{11}{c}{$E > 1\gev$} \\
-      \hline
-      2FGL J1627.0-2425c   &     352.87\deg &      16.79\deg & $  0.53\deg \pm   0.06\deg$ &      131.0 &       21.1 &  0.060\deg &  0.047\deg &   39.8\deg & $    6.8 \pm     0.7$ & $   2.49 \pm    0.14$ \\
-      2FGL J1554.4-5317c   &     328.12\deg &       0.26\deg & $  0.52\deg \pm   0.04\deg$ &      149.0 &       39.6 &  0.044\deg &  0.039\deg &   55.5\deg & $   16.6 \pm     1.5$ & $   2.30 \pm    0.11$ \\
-      2FGL J0823.0-4246    &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      314.5 &       49.2 &  0.026\deg &  0.023\deg &    5.3\deg & $    8.3 \pm     0.6$ & $   2.18 \pm    0.07$ \\
-      \hline
-      \multicolumn{11}{c}{$E > 10\gev$} \\
-      \hline
-      2FGL J1615.2-5138    &     331.67\deg &      -0.66\deg & $  0.43\deg \pm   0.04\deg$ &       77.6 &       45.3 &  0.058\deg &  0.047\deg &   20.4\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.26$ \\
-      2FGL J1632.4-4753c   &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      126.4 &       62.2 &  0.042\deg &  0.036\deg &  -16.1\deg & $    1.9 \pm     0.2$ & $   2.30 \pm    0.22$ \\
-      2FGL J2021.5+4026    &      78.17\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      221.2 &      140.6 &  0.044\deg &  0.030\deg &   51.1\deg & $    1.8 \pm     0.2$ & $   2.32 \pm    0.19$ \\
-      2FGL J1837.3-0700c   &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       48.0 &       20.9 &  0.075\deg &  0.064\deg &  -12.4\deg & $    1.1 \pm     0.1$ & $   1.60 \pm    0.17$ \\
-      2FGL J0851.7-4635    &     266.29\deg &      -1.41\deg & $  1.12\deg \pm   0.07\deg$ &      119.7 &       90.9 &  0.090\deg &  0.064\deg &   63.8\deg & $    1.3 \pm     0.1$ & $   1.74 \pm    0.12$ \\
+      \multicolumn{11}{c}{$E > 1 \gev$} \\
+      \hline
+      2FGL J0823.0-4246    &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      314.7 &       46.1 &  0.026\deg &  0.023\deg &    5.3\deg & $    8.3 \pm     0.6$ & $   2.18 \pm    0.07$ \\
+      2FGL J1627.0-2425c   &     352.87\deg &      16.79\deg & $  0.53\deg \pm   0.06\deg$ &      130.3 &       20.3 &  0.060\deg &  0.047\deg &   39.8\deg & $    6.7 \pm     0.7$ & $   2.48 \pm    0.15$ \\
+      2FGL J1554.4-5317c   &     328.12\deg &       0.26\deg & $  0.52\deg \pm   0.04\deg$ &      150.8 &       37.6 &  0.044\deg &  0.039\deg &   55.5\deg & $   16.7 \pm     1.5$ & $   2.30 \pm    0.11$ \\
+      \hline
+      \multicolumn{11}{c}{$E > 10 \gev$} \\
+      \hline
+      2FGL J0851.7-4635    &     266.29\deg &      -1.41\deg & $  1.12\deg \pm   0.07\deg$ &      120.0 &       76.7 &  0.090\deg &  0.064\deg &   63.8\deg & $    1.3 \pm     0.1$ & $   1.75 \pm    0.08$ \\
+      2FGL J1615.0-5051    &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg$ &       54.0 &       16.6 &  0.049\deg &  0.040\deg &    1.7\deg & $    1.1 \pm     0.2$ & $   2.25 \pm    0.28$ \\
+      2FGL J1615.2-5138    &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg$ &       75.9 &       47.6 &  0.048\deg &  0.044\deg &   31.1\deg & $    1.1 \pm     0.2$ & $   1.77 \pm    0.26$ \\
+      2FGL J1632.4-4753c   &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      128.3 &       64.8 &  0.042\deg &  0.036\deg &  -16.1\deg & $    2.0 \pm     0.2$ & $   2.29 \pm    0.22$ \\
+      2FGL J1837.3-0700c   &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       47.0 &       20.2 &  0.075\deg &  0.064\deg &  -12.4\deg & $    1.1 \pm     0.2$ & $   1.65 \pm    0.21$ \\
+      2FGL J2021.5+4026    &      78.17\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      225.3 &      139.4 &  0.044\deg &  0.030\deg &   51.1\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ \\
       \hline
@@
     \begin{centering}
-      \begin{tabular}{r|rr|rrrr|rrrr}
+      \begin{tabular}{l|rr|rrrr|rrrr}
         \hline
@@
         \hline
-        \multicolumn{11}{c}{$E > 1\gev$} \\
-        \hline
-        2FGL J1627.0-2425c   &       16.6 &       21.1 &     353.00\deg &      16.97\deg & $       2.9 \pm        0.6$ & $  2.6 \pm   0.3$  &     353.26\deg &      16.67\deg & $       2.5 \pm        0.6$ & $  2.6 \pm   0.4$ \\
-        2FGL J1554.4-5317c   &       10.2 &       39.6 &     328.30\deg &       0.31\deg & $      10.1 \pm        1.2$ & $  2.7 \pm   0.2$  &     328.27\deg &      -0.07\deg & $       0.9 \pm        0.7$ & $  1.5 \pm   0.4$ \\
-        2FGL J0823.0-4246    &       22.3 &       49.2 &     260.59\deg &      -3.27\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
-        \hline
-        \multicolumn{11}{c}{$E > 10\gev$} \\
-        \hline
-        2FGL J1615.2-5138    &       30.1 &       45.3 &     331.75\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.2 \pm   0.5$  &     331.46\deg &      -0.79\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
-        2FGL J1632.4-4753c   &       38.5 &       62.2 &     336.52\deg &       0.18\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
-        2FGL J2021.5+4026    &       34.7 &      140.6 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.43\deg &       2.55\deg & $       0.4 \pm        0.1$ & $  1.8 \pm   0.4$ \\
-        2FGL J1837.3-0700c   &       15.4 &       20.9 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.6$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  1.9 \pm   0.5$ \\
-        2FGL J0851.7-4635    &       17.2 &       90.9 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.38\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
+        \multicolumn{11}{c}{$E > 1 \gev$} \\
+        \hline
+        2FGL J0823.0-4246    &       21.9 &       46.1 &     260.59\deg &      -3.27\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
+        2FGL J1627.0-2425c   &       19.1 &       20.3 &     353.00\deg &      16.97\deg & $       3.0 \pm        0.6$ & $  2.6 \pm   0.4$  &     353.26\deg &      16.67\deg & $       2.4 \pm        0.6$ & $  2.5 \pm   0.5$ \\
+        2FGL J1554.4-5317c   &        9.2 &       37.6 &     328.30\deg &       0.31\deg & $      10.3 \pm        1.2$ & $  2.7 \pm   0.5$  &     328.27\deg &      -0.07\deg & $       0.9 \pm        0.6$ & $  1.6 \pm   0.4$ \\
+        \hline
+        \multicolumn{11}{c}{$E > 10 \gev$} \\
+        \hline
+        2FGL J0851.7-4635    &       16.1 &       76.7 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.38\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
+        2FGL J1615.0-5051    &       12.2 &       16.6 &     332.39\deg &      -0.07\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.6$  &     332.43\deg &      -0.36\deg & $       0.4 \pm        0.1$ & $  2.4 \pm   0.5$ \\
+        2FGL J1615.2-5138    &       37.6 &       47.6 &     331.75\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.3 \pm   0.5$  &     331.46\deg &      -0.79\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
+        2FGL J1632.4-4753c   &       40.9 &       64.8 &     336.52\deg &       0.18\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
+        2FGL J1837.3-0700c   &       12.3 &       20.2 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.6$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.6$ \\
+        2FGL J2021.5+4026    &       29.7 &      139.4 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.43\deg &       2.55\deg & $       0.5 \pm        0.1$ & $  1.8 \pm   0.4$ \\
         \hline
@@
     \begin{centering}
-      \begin{tabular}{r|rrrrrrrr}
-        \hline
-        \hline
-        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
-        \hline
-        \multicolumn{9}{c}{$E > 1\gev$} \\
-        \hline
-        2FGL J1627.0-2425c   &                154.9 &                131.0 &                102.4 &                     32.6 &                   21.1 &                 23.3 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
-        2FGL J1554.4-5317c   &                134.8 &                149.0 &                137.6 &                     39.4 &                   39.6 &                 39.8 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
-        2FGL J0823.0-4246    &                347.3 &                314.5 &                343.6 &                     66.1 &                   49.2 &                 56.6 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
-        \hline
-        \multicolumn{9}{c}{$E > 10\gev$} \\
-        \hline
-        2FGL J1615.2-5138    &                 78.2 &                 77.6 &                 88.2 &                     46.4 &                   45.3 &                 53.7 & $  0.43\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
-        2FGL J1632.4-4753c   &                126.9 &                126.4 &                158.1 &                     64.0 &                   62.2 &                 94.1 & $  0.44\deg \pm   0.04\deg$ & $  0.67\deg \pm   0.03\deg$ \\
-        2FGL J2021.5+4026    &                236.5 &                221.2 &                265.8 &                    156.0 &                  140.6 &                162.6 & $  0.59\deg \pm   0.03\deg$ & $  0.72\deg \pm   0.03\deg$ \\
-        2FGL J1837.3-0700c   &                 45.5 &                 48.0 &                 39.2 &                     18.6 &                   20.9 &                 18.8 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
-        2FGL J0851.7-4635    &                120.2 &                119.7 &                125.9 &                     90.1 &                   90.9 &                 94.7 & $  1.12\deg \pm   0.07\deg$ & $  1.16\deg \pm   0.08\deg$ \\
-        \hline
+      \begin{tabular}{l|rrrrrrrr}
+%        \hline
+%        \hline
+%        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
+%        \hline
+%        \multicolumn{9}{c}{$E > 1 \gev$} \\
+%        \hline
+%        2FGL J1627.0-2425c   &                154.9 &                131.0 &                102.4 &                     32.6 &                   21.1 &                 23.3 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
+%        2FGL J1554.4-5317c   &                134.8 &                149.0 &                137.6 &                     39.4 &                   39.6 &                 39.8 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
+%        2FGL J0823.0-4246    &                347.3 &                314.5 &                343.6 &                     66.1 &                   49.2 &                 56.6 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
+%        \hline
+%        \multicolumn{9}{c}{$E > 10 \gev$} \\
+%        \hline
+%        2FGL J1615.2-5138    &                 78.2 &                 77.6 &                 88.2 &                     46.4 &                   45.3 &                 53.7 & $  0.43\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
+%        2FGL J1632.4-4753c   &                126.9 &                126.4 &                158.1 &                     64.0 &                   62.2 &                 94.1 & $  0.44\deg \pm   0.04\deg$ & $  0.67\deg \pm   0.03\deg$ \\
+%        2FGL J2021.5+4026    &                236.5 &                221.2 &                265.8 &                    156.0 &                  140.6 &                162.6 & $  0.59\deg \pm   0.03\deg$ & $  0.72\deg \pm   0.03\deg$ \\
+%        2FGL J1837.3-0700c   &                 45.5 &                 48.0 &                 39.2 &                     18.6 &                   20.9 &                 18.8 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
+%        2FGL J0851.7-4635    &                120.2 &                119.7 &                125.9 &                     90.1 &                   90.9 &                 94.7 & $  1.12\deg \pm   0.07\deg$ & $  1.16\deg \pm   0.08\deg$ \\
+%        \hline
       \end{tabular}
@@
       \pointlike whereas $\ts_\gtlike$ is the same quantity using the
-      same model but fitting with \gtlike.  There is very good agreement
+      same model but fitting with \gtlike.  There is good agreement
       between the two methods.
@@
   \caption{
-  A diffuse subtracted 1 \gev to 100 \gev counts map of the region around
+  A galactic and isotropic diffuse subtracted 1 \gev to 100 \gev counts map of the region around
   2FGL J1627.0-2425 smoothed by a 0.1\deg Gaussian kernel.  The red star
@@
   diffuse emission.  More information about this source is presented
-  in section~\ref{section_ophiuchus}.
+  in section~\ref{section_2FGL_J1627.0-2425c}.
   }\label{1FGL_J1628.6-2419c}
@@
   \caption{
-2FGL J1554.4-5317c
-1FGL J1554.0-5345c
-  %P72Y2405.
-  Using $E>1\gev$. 
-  \todo[inline]{Describe this source/the fit.Unidentified source likely diffuse emission.}
+  A galactic and isotropic diffuse subtracted 1 \gev to 100 \gev
+  counts map of the region around 2FGL J1554.4-5317c smoothed by a
+  0.1\deg Gaussian kernel.  The red star is the catalog position of
+  2FGL J1554.4-5317c.  The red cross and white circle are the best
+  fit position and extension of this source assuming a uniform disk
+  spatial model.  The green star represents the catalog source 2FGL
+  J1551.3-5333c which was removed from the region because it was part of
+  the extended source.  Because the source has no obviosu counterpart and
+  is in a region of large diffuse emission, the source is most likely
+  unmodeled diffuse emission.  More information about this source is
+  presented in section~\ref{section_2FGL_J1554.4-5317c}.
   }
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-  \caption{A diffuse subtracted 1 \gev to 100 \gev counts map of the
-  region around 2FGL J0823.0-4246. The red star is the second LAT
-  catalog's best fit position of 2FGL J0823.0-4246.  The red cross
-  and white circle are the best fit position and extension of this
-  source assuming a uniform disk spatial model.  The two green stars
-  are the positions of two nearby catalog source 2FGL J0823.4-4305 and
-  2FGL J0821.0-4254 that we removed from our region. This source is
-  spatially coincident with the Puppis A SNR. Overlaid on the figure are
-  ROSAT contours of Puppis A SNR (\cite{rosat_puppis_a}). There is good
-  agreement between the LAT and X-ray emission.  More information about
-  this source is shown in section~\ref{section_puppis_a}.  The emission
-  on the top left comes from the very bright Vela Pulsar. Even though
-  Vela is over 3 degrees away from this source at a position of
-  $l,b=263.55\deg,-2.79\deg$, it can be seen because it is so bright.
+  \caption{A galactic and isotropic diffuse subtracted 1 \gev to 100
+  \gev counts map of the region around 2FGL J0823.0-4246 smoothed by
+  a 0.1\deg Gaussian kernel.  The red star is the catalog position
+  of 2FGL J0823.0-4246.  The red cross and white circle are the best
+  fit position and extension of this source assuming a uniform disk
+  spatial model.  The two green stars are the positions of two nearby
+  catalog source 2FGL J0823.4-4305 and 2FGL J0821.0-4254 that we removed
+  from our region. This source is spatially coincident with the Puppis
+  A SNR. Overlaid on the figure are ROSAT contours of Puppis A SNR
+  (\cite{rosat_puppis_a}). There is good spatial overlap between the
+  LAT and X-ray emission.  The emission on the upper east comes from the
+  bright Vela Pulsar. Even though Vela is over 3 degrees away from
+  this source at a position of $l,b=(263.55\deg,-2.79\deg)$, it can be
+  seen because it is so bright. More information about this source is
+  presented in section~\ref{section_2FGL_J0823.0-4246}.
   \todo[inline]{This figure could better explain the source}
@@
   \caption{
-2FGL J1615.2-5138
-1FGL J1613.6-5100c
-%P72Y2473
-  \todo[inline]{Describe this source better. Describe the Contour}
+\todo[inline]{This section needs to be rewritten}
+%A galactic and isotropic diffuse subtracted 10 \gev to 100 \gev counts map of the region
+%around 2FGL J1615.2-5138. The red star is the catalog position of 2FGL
+%J1615.2-5138 and the red cross and the white circle are the best fit
+%position and extension of this source assuming a uniform disk spatial
+%model.  Overlaid on this plot are contours of this region as seen in \tev
+%by H.E.S.S. This source spatially overlaps the extended H.E.S.S. source
+%HESS J1614-518 (\cite{HESS_plane_survey}).  To fit this region, we had to
+%relocalize the source 2FGL J1615.0-5051 from its catalog position (blue
+%star) to its best fit position (blue cross) and add an additional source
+%into the region at the position of the grey cross.  It is unclear of this
+%is a physically new source or if 2FGL J1615.0-5051 is spatially extended.
+%2FGL J1615.0-5051 is spatially coincident with the extended H.E.S.S.
+%source HESS J1616-508 but was not found to be significantly extended
+%using two years of data. Nevertheless, adding this addtional source
+%was necessary to stop 2FGL J1615.2-5138's extension from growing too
+%large and fitting both sources. To fit this region, we had to remove three catalog
+%sources 2FGL J1619.7-5040c, 2FGL J1620.6-5111c, and 2FGL J1622.8-5006
+%from the region because they were not significant. Two are shown as green
+%stars and one is outside of the plot region.
+  \todo[inline]{Describe this source better.}
   }\label{1FGL_J1613.6-5100c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
-  \caption{
-2FGL J1632.4-4753c
-1FGL J1632.9-4802c. 
-% P72Y2540
-  \todo[inline]{Describe this source better. Describe the Contour}
+  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
+  \gev counts map of the region around 2FGL J1632.4-4753c smoothed by
+  a 0.1\deg Gaussian kernel.  This source is in a crowded region.
+  The red star is the catalog position of 2FGL J1632.4-4753c.  The red
+  cross and white circle are the best fit position and extension 2FGL
+  J1632.4-4753c assuming a uniform disk spatial model.  The three
+  green crosses inside the extension circle are the sources 2FGL
+  J1631.7-4720c, 2FGL J1630.2-4752, and 2FGL J1634.4-4743c.4-4820c
+  which were removed from the region when fitting 2FGL J1632.4-4753c
+  for extension.  The blue stars and crosses are the catalog
+  positions and the relocalized positions of (from east to west)
+  2FGL J1636.3-4740c and 2FGL J1635.4-4717c.  The farther away green
+  stars represent other catalog sources which were not significant
+  above 10 \gev.  This extended source is spatially coincident
+  with the extended H.E.S.S source HESS J1634-472.  Overlaid on
+  the counts map are the contours of the region as seen in \tev
+  (\cite{HESS_plane_survey}). More information about this source is
+  presented in section~\ref{section_2FGL_J1632.4-4753c}.
+  \todo[inline]{Describe the interpreation.}
   }\label{1FGL_J1632.9-4802c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
-  \caption{
-  2FGL J2021.5+4026
-  1FGL J2020.0+4049
-  P72Y3281
-  Using $E>10\gev$. 
-  \todo[inline]{Describe this source better. Describe the Contour}
-  }\label{Gamma_Cygni}
+  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
+  \gev counts map of the region around 2FGL J2021.5+4026 smoothed by
+  a 0.1\deg Gaussian kernel. The red star is the catalog position of
+  2FGL J2021.5+4026.  The red cross and white circle are the best fit
+  position and extension 2FGL J2021.5+4026 assuming a uniform disk
+  spatial model.  The green cross inside of the extension is a nearby
+  catalog source 2FGL J2019.1+4040 which was removed from our region
+  when fitting this source for extension.  The further away green stars
+  represent other catalog sources which were removed from the analysis
+  because they were not significant above 10 \gev.  The grey cross is
+  the position a source not in the two year LAT catalog which was added
+  to the region to get a better fit of 2FGL J2021.5+4026.  This source
+  is spatially coincident with the Gamma Cygni SNR.  Contours of
+  Gamma Cygni at 408MHz from the Canadian Galactic Plane Survey are
+  overlaid and there is good spatial agreement with the LAT emission
+  (\cite{canadian_galactic_plane_survey}).  More information about this
+  source is presented in section~\ref{section_2FGL J2021.5+4026}.
+  \todo[inline]{Describe the interpreation better.}
+  }\label{1FGL_J2020.0+4049}
 \end{figure}
@@
   \caption{
-2FGL J1837.3-0700c
-1FGL J1837.5-0659c. 
-%P72Y2974
-  \todo[inline]{Describe this source better. Describe the Contour}
-  \todo[inline]{Note about why the top right source was not found to
-  be extended b/c the scale is cut.}
+  A galactic and isotropic diffuse subtracted 10 \gev to 100 \gev
+  counts map of the region around 2FGL J1837.3-0700c smoothed by a
+  0.1\deg Gaussian kernel.  The red star is the catalog position of
+  2FGL J1837.3-0700c. The red cross and white circle are the best fit
+  position and extension  of 2FGL J1837.3-0700c assuming a uniform disk
+  spatial model.  The blue stars and crosses are the catalog position and
+  the relocalized poistion of (from east to west) 2FGL J1837.3-0700c,
+  2FGL J1836.8-0623c, and 2FGL J1839.3-0558c.  The green cross inside
+  of the extension is a nearby catalog source 2FGL J1835.5-0649 which
+  was removed from the region.  The further away green star is 2FGL
+  J1839.0-0539 which was removed from the analysis because it was not
+  significant above 10 \gev.  
+  This source is spatially coincident with the \tev source HESS J1837-069.
+  Overlaid on the figure~\ref{1FGL_J2020.0+4049} are H.E.S.S contours of
+  HESS J1837-069 (\cite{HESS_plane_survey}).  
+  \todo[inline]{Describe the interpreation
+  better.} \todo[inline]{Note about why the top right source was not
+  found to be extended b/c the scale is cut.}
   }\label{1FGL_J1837.5-0659c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
-  \caption{
-2FGL J0851.7-4635
-  Vela Jr. 
-  P72Y1287. 
-  Using $E>10\gev$. 
-  \todo[inline]{Note that source is convolved with a $0.25\deg$ gaussian
-  which is different than other plots.}
-  \todo[inline]{Describe this source better. Describe the Contour}
+  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
+  \gev counts map of the region around 2FGL J0851.7-4635 smoothed by a
+  0.25\deg Gaussian kernel. The red star is the catalog position of 2FGL
+  J0851.7-4635.  The red cross and white circle are the best fit position
+  and extension 2FGL J0851.7-4635 assuming a uniform disk spatial model.
+  The green cross inside of the extension is a nearby catalog source
+  2FGL J2019.1+4040 which was removed from our region when fitting this
+  source for extension.  Three nearby catalog sources 2FGL J0848.5-4535,
+  2FGL J0855.4-4625, and 2FGL J0853.5-4711 were removed from the region
+  because they are inside of this extended source.  The further away
+  green star is 2FGL J0858.0-4815 which was removed from the anlaysis
+  because it was not significant above 10 \gev.  The blue stars and
+  crosses are the catalog position and the relocalized poistion of (from
+  east to west) 2FGL J0854.7-4501 and 2FGL J0901.7-4655.   The extended
+  source 2FGL J0851.7-4635 is spatially coincident with the SNR Vela Jr.
+  Overlaid on figure are contours of Vela Jr. as  seen in \tev by H.E.S.S
+  (\cite{vela_jr_hess}).  More information about this source is presented
+  in section~\ref{section_2FGL_J0851.7-4635}.
+  \todo[inline]{Describe interpreation better.} 
   }\label{Vela_Jr}

### 2011-07-19 extended_catalog/paper/extended_catalog.tex
new plot

@@
 sources.  We then apply this tool to test all sources in the two
-year source catalog for extension and report on the discovery
-of XXXXXX\todo{What number should be put
-here. Should we report the total number of extended sources instead of the
-number of new sources???} new extended sources.
+year source catalog for extension. We present on the detection of
+ten spatially extended sources in addition to the twelve spatially
+extended sources reported in the second Fermi LAT Catalog.
 \end{abstract}
 
+\listoftodos
+
 \section{Introduction}
-
-\todo[inline]{Add note about how difficult lat analysis in
-the galactic plane is because of large PSF, low statistics,
-and high source density. Describe how it requires a certain amount
-of iterative, by eye modifying of the sky model. Not
-adequate to simply use 2FGL}
 
@@
 information about a source do not nicely decouple. Therefore, a biased
-spatial model will bias the spectral model of the source and studyign
-the extension of the source can correct for htis.  Furthermore, correctly
+spatial model will bias the spectral model of the source and studying
+the extension of the source can correct for this.  Furthermore, correctly
 modeling a source's extension is important for improving the overall model
@@
 that require many iterations such as source localization and extension
-fitting.  On the other hand, we expect that the spectral paramaters
+fitting.  On the other hand, we expect that the spectral parameters
 fit by \gtlike to be slightly more precise.
@@
 Like extended sources described in section~\ref{gtlike_crosscheck},
-the spectrum of the two point sources can be refit using \gtlike. we quote
-the spectral values obtained from \gtlike using the best fit positions
+the spectrum of the two point sources can be refit using \gtlike. 
+we quote the spectral values obtained from \gtlike using the best fit positions
 found using \pointlike.  For the extended candidates found by our search,
@@
 This is important when comparing morphologies to other wavelengths
-because the quoted size can vary significantly depending on which quanity
+because the quoted size can vary significantly depending on which quantity
 is reported.  This effect can be best seen in figure~\ref{compare_r68}
@@
 performed with photons from an energy range of 1 \gev to 100 \gev using 4
-energy bins per decade and using the Pass 7 Version 6 Source instrument
-response function (IRFs).  For each point source, we used \pointlike
+energy bins per decade and using the 
+Pass 7\_V6 (P7\_V6) Source Instrument
+Response Function (IRFs).  For each point source, we used \pointlike
 to fit it as both a point and extended source and calculate \tsext and
@@
 
-\todo[inline]{Add note about how we had to delete nearby sources which
-were not hard above 10 \gev for analysis to converge.}
-
-The LAT two year catalog presented a search for all statistically
-significant sources that are detected in the \gev sky (\cite{second_cat}).
-The catalog group's source finding method assumes that the emission
-originated as point sources and what was presented was a list of all
-sources fit assuming a point source spatial hypothesis.  Published
-extended sources were modeled by the catalog group as being extended,
-but no attempt was made to test if other sources in the catalog could
-be spatially resolved.
-
-We performed a search of all Fermi sources found in the second Fermi LAT
-catalog for extension.  To perform this search, we built a model of the
-sky consistent with the two year catalog's model.   We used the same two
+The first and second LAT catalog produced a list of all significant point
+sources seen by the LAT.  (\cite{first_cat,second_cat}).  The first LAT
+catalog's source finding method assumes that all sources were consistent
+with the PSF. The second LAT catalog modeled previously published
+spatially extended sources with an extended spatial model but did not
+attempt to resolve new spatially extended sources. In this paper,
+we took the sources from the second Fermi LAT catalog and perform
+a search to attempt to spatially resolve new sources.
+
+For this search, we build a model of the
+sky consistent with the second catalog.   We used the same two
 years of data from August 4, 2008 to August 1, 2010 and we used the same
-pass 7 Version 6 Source IRFs.  We used the same galactic diffuse,
+Pass 7\_V6 (P7\_V6) Source class event selections and 
+Instrument Response Functions (IRFs, \cite{lat_on_orbit_psf}).  We used the same galactic diffuse,
 isotropic diffuse, and earth limb emission model. The spectrum of the
@@
 while the earth limb emission was fixed to it's predicted value.
-
-We performed the extension fit using \pointlike.  For each source, we
-used a circular $10\deg$ region of interest centered on our source and
-using 4 bins uniformly in each logarithm of energy.  We included all
-background catalog sources within $15\deg$ of the source of interest
-and refit the spectral parameters of sources within $2\deg$ of our source.
 
@@
 using photons only between 1 \gev and 100 \gev.
+We used 4 energy bins per each logarithmic decade in energy.
 
@@
 approach is complimentary because there are regions in the galactic
-plane where at lower energies the diffuse emission dominates and is
-likely not perfectly modeled. On the other hand, at the highest energies
-accessible by the LAT, the galactic diffuse emission will be smaller and
-we might expect to detect significantly harder sources. This approach is
-also beneficial because harder sources with nearby neighbors that are
-softer may end up being incorrectly fit at lower energies but correctly
-found looking only at the high energy.  This is also beneficial in the
-galactic plane looking for possible extended sources near pulsars which
-are bright at lower energy but cutoff before 10 \gev.  This approach
-of using only photons with energy above 10 \gev was successfully used
-to detecting HESS J1825-137 with the LAT (\cite{fermi_hess_j1825}).
-
-For each catalog source, we modified the spectral index of the source
-to be a power-law. We did this for two reasons. The first is that for a
-source to be significantly extended, we would expect it to be reasonably
-hard and therefore be fit reasonably well by a power-law.  The second reason
-is that since we begin our analysis at either 1 \gev or 10 \gev, we didn't
-expect there to be significant curvature over this smaller energy range.
-This method has the advantage that for the following analysis, we can
-simply quote the fit power-law spectral index.
-
-Finally, when analyzing our region, we automatically removed all other
-catalog sources which were within 0.5\deg. This was done because of
-a concern that truly extended sources might end up in the catalog as
-multiple point sources. These spurious nearby catalogs sources might then
-distort our fit enough that it no longer would show up as being extended.
-Nevertheless, we investigated for each of our extended candidates if
-if we seemed to be legitimately removing real background sources. And
-we employed a dual localization procedure (described above) to test
-all of our candidates for source confusion.
-
-For each catalog source, we modified the source to have a uniform radially
-symmetric disk spatial shape and used \pointlike to simultaneously fit
-the position and extension of the source.  We then selected all of the
+plane where at lower energies the diffuse emission dominates and the
+analysis is challenged by the difficulty in modeling this emission.
+The analysis is also challenged by source confusion in crowded regions.
+On the other hand, at the highest energies accessible by the LAT, the
+galactic diffuse emission is less dominant and nearby sources might
+be expected to be softer.  Using higher energies, we might expect
+to detect harder sources in more complicated regions. This approach
+is This is especially beneficial for regions near pulsars which
+cutoff before 10 \gev.  This approach of using high energies was was
+successfully used to detecting HESS J1825-137 and MSH 15-52 with the LAT
+(\cite{msh1552,fermi_hess_j1825}).
+
+For each catalog source, we tested it for extension using \pointlike
+assuming the source had a uniform radially symmetric disk spatial model.
+we used a circular $10\deg$ region of interest centered on our source and
+included all catalog sources within $15\deg$ of the source of interest.
+We refit the spectral parameters of sources within $2\deg$ of our source.
+We modified the spectral index of each source we were testing to be a
+power-law. This was reasonable because for a source to be significantly
+extended, it would have to be fairly hard and fit reasonably well by
+a power-law. Second, since we began our analysis at either 1 \gev or
+10 \gev, we didn't expect there to be significant curvature over this
+smaller energy range.
+
+Finally, when analyzing our region, we automatically removed other
+catalog sources which were within 0.5\deg of the source of interest. This was done because of
+a concern that extended sources would end up in the catalog as
+multiple point sources. These spurious catalogs sources would then
+distort the extension fit.
+For each extended candidate, we performed a dual localization procedure
+(described in section~\ref{dual_localization_method} to test if the
+source was extended multiple point sources.
+
+\subsection{Additional Analysis}
+
+We then selected all of the
 sources for which \pointlike found $\tsext>16$.
-
-\subsection{Additional Analysis}
 
@@
 galactic diffuse emission and finding sources on top of this emission is
-difficult~\ref{first_diffuse_paper}. This issue has been discussed in the
-Fermi catalog~\ref{first_cat,second_cat}. Furthermore, the galactic plane is
+difficult (\cite{first_diffuse_paper}). This issue has been discussed in the
+Fermi catalog (\cite{first_cat,second_cat}). Furthermore, the galactic plane is
 crowded and so it is often difficult to get a good model for the
@@
 % 2FGL J1856.2+0450c = P72Y3047 for
-As an example of why this issue, we describe our test of 
-2FGL J1856.2+0450c for
-extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
-using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
-emission subtracted.  A two year catalog source 
-2FGL J1856.2+0450c was found at the
-position $(l,b)=(37.79\deg,1.14\deg)$.  
-We find that there appears to be overall some large scale residual in the
-diffuse emission along the galactic plane. Furthermore, it appears that
-we don't have a great model of the nearby catalog sources. As a result,
-2FGL J1856.2+0450c fits to a large extension of 1.37\deg and the result is
-statistically significant with \tsext=51.6.  By looking at the residuals,
-it is clear that this complicated region is not well fit even though
-the source's extension is statistically significant. For this reason,
-we have to perform a series of followup analysis for all of the sources
-that are found with \tsext=16.
+As an example of why this issue, we describe our test of 2FGL
+J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
+a smoothed counts map using photons with energy above 1 \gev. In
+the map, the galactic and isotropic diffuse emission subtracted.
+A two year catalog source 2FGL J1856.2+0450c was found at the position
+$(l,b)=(37.79\deg,1.14\deg)$.  We find that there appears to be overall
+some large scale residual in the diffuse emission along the galactic
+plane. Furthermore, it appears that we don't have a great model of
+the nearby catalog sources. As a result, 2FGL J1856.2+0450c fits to a
+large extension of 1.37\deg and the result is statistically significant
+with \tsext=51.6.  By looking at the residuals, it is clear that this
+complicated region is not well fit even though the source's extension is
+statistically significant. For this reason, we have to perform a series
+of further analysis for all of the sources that are found with \tsext=16.
 % information came from
@@
 
-Additionally,
-we generated for each extended source candidate residual
+Additionally, we generated for each extended source candidate residual
 test statistic (\ts) maps.  The residual \ts map is a map of the \ts
-value evaluated at each point by adding onto the map at that position
-a new source of spectral index 2 and finding the increase in likelihood
+value evaluated at each point by adding onto the map at that position a
+new source of spectral index 2 and finding the increase in likelihood
 when fitting its flux. \ts maps are especially useful as looking for
@@
 can be used to clearly look for when the residual is significant.
-The downside is they are biased to look for residual features
-that look like the PSF and so are not as sensitive to diffuse residual
+The downside is they are biased to look for residual features that
+look like the PSF and so are not as sensitive to diffuse residual
 features. Furthermore, since by definition \ts>0, \ts maps can only show
-positive fluctuations. Nevertheless, \ts maps were useful for
-assessing the overall quality of the fit. Figure~\ref{res_tsmap}
-shows an example residual \ts map for the extended source IC443.
+positive fluctuations. Nevertheless, \ts maps were useful for assessing
+the overall quality of the fit. Figure~\ref{res_tsmaps} shows an example
+residual \ts map for the extended source IC443.
 
 For each candidate, we also generated counts slices. A counts slice
-plots the sum of all counts in the longitudinal direction within 2\deg in
-the latitudinal direction.  The same plot is also shown integrating in
-the longitudinal direction.  On top of the plot is overlaid the model
+plots the sum of all counts in the longitudinal direction within 2\deg
+in the latitudinal direction.  The same plot is also shown integrating
+in the longitudinal direction.  On top of the plot is overlaid the model
 predicted counts assuming the source has a disk spatial model, assuming
@@
 IC443 in figure~\ref{counts_slice}. Counts slices were especially useful
-for looking at how well the overall diffuse emission model fits the region
-near the sources.
+for looking at how well the overall diffuse emission model fits the
+region near the sources.
 
@@
 
+For each source, we computed an extension profile.  An example
+extension profile for the extended source IC443 is shown in
+figure~\ref{extension_profile}.
+
 Finally, for each source, we performed the dual localization method
-described in section~\ref{dual_localization_method}.  We 
-did so by replacing the source with two sources each containing
-half of the original flux and then using \pointlike to
-simultaneously fit the position and spectrum of these sources.
-We then used \gtlike to refit the spectrum of these
-sources using the best fit positions. For the
-new extended sources found, we summarize the results of
-this dual localization test and compare the values of \tsext
-to \tsinc in table~\ref{dual_localization_results}.
-
-for sources that seemed promising, we performed in a case
-by case basis a refit of the region where we would move or delete
-background catalog sources until it was clear that we had obtained on
-a case by case a good overal fit of the region. This was necessary in
-many situations whrere the position of background sources in the catalog
-was not consistent and when the offet of the background sources biased
-the fit extension of our source. This was likey the case because the
-catalog positions of the backgorund sources came usign all photons above
-100 \mev and the low energy localization disagreed with the higher energy
-localization we found. This also happened in certain situations because
-the localization of a backgorund source dependend upon correctly modeling
-the extended source as being extended and so once we fit our source for
-extension, we had to relcoalizae the backgorund source.  For each source,
-we descirbe in a case by case basis any modifications which were required
-to obtain a good fit of our source and the surrounding region.
+described in section~\ref{dual_localization_method}.  We did so by
+replacing the source with two sources each containing half of the original
+flux and then using \pointlike to simultaneously fit the position and
+spectrum of these sources.  We then used \gtlike to refit the spectrum of
+these sources using the best fit positions. For the new extended sources
+found, we summarize the results of this dual localization test and compare
+the values of \tsext to \tsinc in table~\ref{dual_localization_results}.
+
+Because of the high source density in the galactic plane for promising
+extended source candidates we often had to iteratively improve our model
+of background sources to obtain a good fit of the extended source.
+Often, several catalog sources would fill in the emission of one
+extended source and all but one of them would have to be removed from
+the model. Similarly, the position of background sources would often
+have to be refit once the extended source's extension was correctly
+fit. Similarly, background sources were insignificant in the fit energy
+range and had to be removed.  When the localization of background
+sources and the extension of our catalog source coupled, we iteratively
+fit the position and extended of the nearby sources in the region until
+the fitter stabilized on the overall best fit positions and extensions.
+For each extended source, we describe what modifications were required
+to the sky model to obtain a good fit of the region.
 
@@
 
-To estimate systematic errors due to uncertaintly in our diffuse
-emission background model, we performed an additional analysis
-of our extended source candidates using an alternate diffuse
-model. Our alterate model was based on the GALPROP\footnote{GALPROP
-is a software package for calculating the dise Galactic $\gamma$-ray
+To estimate systematic errors due to uncertainty in our diffuse
+emission background model, we performed a second
+extension test of our candidates using
+an alternate diffuse
+model. Our alternate model was based on the GALPROP\footnote{GALPROP
+is a software package for calculating the Galactic $\gamma$-ray
 emission based on a model of cosmic-ray propagation in the Galaxy. See
@@
 used in the LAT analysis of the isotropic diffuse emission
-(\cite{isotropic_lat}).  In addition to using an alternate model, we
-freeded additional compoents of this model and fit them simulatentously
-with our source during the likelihood analysis. In particular,
-we independently fit 7 HI rings, 7 HII rings, the inverse compoton,
-and the E(B-V) residual component, and the isotropic and earth albedo
-template. All told, there were 18 individual tempaltes where were all
-simulatenously optimized during this analysis.
-
-We do not expect that locally fitting tehse diffuse components would
-produce a more physical model of the didffuse emission in the region.
-But we do believe a source which does away when adding additional
-degrees of freedom to the background model is likely spurious and so
-this provides an important test of the valididity of our source.
-The results of this fit for the new extended source candidates are
-shown in table~\ref{alt_diff_model_results}. There is overal
-good agreement between the \ts using the standard and alternate diffuse
-models ($\ts_\gtlike$ and $\ts_\alt$ respectivly) and the \tsext values
-(\tsextgtlike and \tsextalt respectivly).
-
-\todo[inline]{Note about \ref{extension_profile}}
+(\cite{isotropic_lat}).  
+With this model,
+we independently fit in the nearby region 
+7 HI rings, 7 HII rings, the inverse component,
+the E(B-V) residual, and the isotropic component of
+the background ration.
+All told, we fit in or region 18 individual templates along
+with all source parameters during the analysis.
+
+It is not expected that this diffuse model is more physical.
+But adding degrees of freedom to the background model is a good
+way to remove additional degrees of freedom to the background
+model is likely spurious sources which correlate to features in
+the diffuse emission.  Therefore, this tests systematics that may
+be due to incorrect modeling of the diffuse emission in the region.
+The results of this fit for the new extended source candidates are shown
+in table~\ref{alt_diff_model_results}. Overall, there is good agreement
+between the \ts using the standard and alternate diffuse models.
 
@@
 
-We validated our method by testing for extension all of the sources
-which the Fermi Collaboration had previously published on.  This list
-includes the extended sources where were modeled in the two year catalog
-(\cite{second_cat}).  This list contains the Large Magalenic Cloud
-and the Small Magalenic Cloud which were previously published by the
-LAT collaboration (\cite{lmc,smc}).  We also included the SNRs IC443, W28, W30, W44, W51C, and the Cygnus Loop which
-were first published in \cite{ic443,w28,w30,w44,w51c,cygnus_loop}.
-We include the Pulsar Wind Nebulae Vela X, MSH 15-52, and HESS
-J1825-137\cite{velax,msh1552,fermi_hess_j1825}.  In addition to those
-sources included by the catalog, we include in this list the SNR RX J1713.7-3946 which was recently published (\cite{RXJ1713}).
-
-Since these sources are all included in the 2 year catalog, we applied
-no special method to test these sources but used the same pipeline
-that tested all other catalog sources for extension.  The results are
-summarized in table~\ref{known_extended_sources}.  This table includes
-the best fit position and extension. It also includes the source's
-significance \ts and extension significance \tsext and the localization
-error ellipse. The table also includes the best fit power-law spectral
-model.
-
-Using photons with energies greater than 1 \gev, our analysis succesfully
-fit the extension of the LMC, SMC, IC443, W28, W30, W44, and W51C.
-Using photons with energy above 10 \gev, we were able to succesffuly
-fit the extesion of HESS J1825-137.
+We first present on our analysis of the twelve extended sources
+previously published and include in the second catalog's sky model.
+(\cite{second_cat}).
+
+% 6 SNRs
+The largest population of extended source are SNRs. The six extended SNRs
+included in the catalog are IC443, W28, W30, W44, W51C, and the Cygnus
+Loop. These sources were first reported in (\cite{ic443,w28,w44,w51c}).
+Detailed papers reporting on W30 and the Cygnus Loop are still in
+preparation.  Using photons with energies greater than 1 \gev, our
+analysis significantly detected the extension of the SNRs IC443, W28,
+W30, W44, and W51C.
+
+Our analysis failed to correctly fit the extension of the Cygnus Loop.
+Publications describing the detailed analysis for the Cygnus Loop are
+still in preparation.  This is most likely because Cygnus Loop is rather
+large and its shell type morphology is not well represented by a uniform
+disk. The source is also rather soft so the published results used a
+larger energy range then our search.
+
+% 2 galaxies
+
+Two galaxies the Large Magalenic Cloud and the Small Magalenic Cloud 
+were included in the second catalog (\cite{lmc,smc}).
+
+% 3 PWN
+Three pulsar wind nebula Vela X, MSH 15-52, and HESS J1825-137 
+were included in the second catalog (\cite{velax,msh1552,fermi_hess_j1825}).
+
+Our analysis failed to detect the extension of Vela X. Vela X can only be
+successfully analyzed after applying a phase cut to removed the heavily
+dominant pulsar emission. It is beyond the scope of the paper to perform
+such specialized analysis.
+
+Using photons with energy above 10 \gev, we significantly detected
+the extension of HESS J1825-137.
 Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
-consistent with the publisehed result, but with $\tsext=11.2$. This is
+consistent with the published result, but with $\tsext=11.2$. This is
 most likely because the published analysis used a larger energy range,
-considering all evnets above 6\gev. Looking at all photons with
+considering all events above 6 \gev. Looking at all photons with
 energy above 1 \gev 
 is problematic because of background source confusion whereas using photons
-with energy above 10 \gev does not have the statistics for a significant dection.
-
-Our analysis failed to detect the extension of Vela X. Vela X can only be
-successfully analyzed after applying a phase cut to removed the heavily
-dominant pular emission. It is beyond the scope of the paper to perform
-such specialized analysis.
+with energy above 10 \gev does not have the statistics for a significant detection.
+
+\todo[inline]{note about how MSH 15-52 and Vela X were hard
+to analysze without phase cuts.}
+
+% 1 radio galaxy
+Centarus A.
 
 Our analysis also failed to detect a significant extension for the
-Centaurus A Lobes.\cite{CenA paper}. This is most likely because the
-discoverd emission was significantly more complicted then a uniform
-radially symmetric Disk.  Furthermore, our analysis failed to correctly
-fit the extension of the Cygnus Loop\cite{Cygnus Loop Paper}.  This is
-most likely because Cygnus Loop is rather large and its shell type
-morphology is not well represented by a uniform disk. The source is
-also rather soft so the publisehd results used a larger energy range
-then our search.
-
+Centaurus A Lobes (\cite{cen_a_lat}). This is most likely because the
+discovered emission was significantly more complicated then a uniform
+radially symmetric Disk.
+
+The results are summarized in table~\ref{known_extended_sources}.
+This table includes the best fit position and extension of these
+sources when fitting them with a radially symmetric uniform disk spatial
+model.  It also includes the best fit spectral model of each source.
 The difficulty our analysis analysis had fitting the extension of several
-of the already published extended sources should be used to emphasize the
-overal difficultly in studying spatially extendee sources with the Fermi
-LAT, especially in the crowded galactic plane. For particular sources,
-it is often necessary to perform careful and specalized analysis to
-correctly find and model the sources we see. We can not claim our method
-is complete.
+of the already published extended sources should be used to emphasize
+the overall difficultly in studying spatially extended sources in crowded
+regions of the sky.
 
@@
 Another possible systematic may be due to source confusion to problems
-with the background model. If the two sources were close,
-they may be unresolvable and get fit as a more significant extended source.
-It is also possible that there are lingering
-residuals in the diffuse emission. Unmodeled parts of the diffuse
-emission could be filled in by modeling point sources as being slightly extended.
+with the background model. If the two sources were close, they may
+be unresolvable and get fit as a more significant extended source.
+It is also possible that there are lingering residuals in the diffuse
+emission. Unmodeled parts of the diffuse emission could be filled in by
+modeling point sources as being slightly extended.
 
@@
 empirical parameterization was used in our instrument
-response function.
-%\footnote{
-%LAT Collaboraiton publication pending.
-%https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
-%}. 
+response function (\cite{lat_on_orbit_psf}).
 But our current parameterization is not perfect. There are lingering
@@
 % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
+% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
 % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
@@
 
-Eight new extended sources not included in the two year catalog
-were found using this search. Three were found in our search using
-events above 1 \gev and five were found in the search using events
-above 10 \gev.  For all the extended sources, the results of our
-fit are summarized in table~\ref{new_ext_srcs_table}. The table
-includes for each source the best fit position, extension, spectrum,
-source significance, and significance of extension.
+Ten extended sources not include in the second LAT catalog were found
+using this search.  Four were found in our search using only photons
+with energies above 1 \gev and six were found only using photones with
+energies above 10 \gev.  The fit properties of these ten sources is
+summarized in table~\ref{new_ext_srcs_table}.  The table includes for each
+source the best fit position, extension, spectrum, source significance,
+and significance of extension.  Figure~\ref{allsky_extended_sources}
+shows a skymap of the position of the twelve sources included in the
+second catalog and the ten sources analysis in this paper.
 
@@
 
-To get a good fit of the region we had to remove the nearby catalog
+To get a good fit of the source, we had to remove the nearby catalog
 sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
@@
 it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
-we conclude that this is an extended source.  The removed catalog sources
-are shown in figure~\ref{1FGL_J0823.3-4248}.
+we conclude that this is an extended source.  
+These modifications are shown in
+figure~\ref{1FGL_J0823.3-4248}.
 
@@
 
-\todo[inline]{Give some additional interpretation of the Puppis A SNR.}
+\todo[inline]{Add interpretations of Puppis A}
 
@@
 and 100 \gev.  The best fit extension was $0.53\deg\pm0.06\deg$ and the
-best fit position is $(l,b)=(352.87\deg, 16.79\deg)$ The source also
-appeared in the first LAT catalog as 1FGL J1628.6-2419c.  The extension
-significance was $\tsext=20.3$.  A counts map showing this source is
+best fit position is $(l,b)=(352.87\deg, 16.79\deg)$.
+The extension significance was $\tsext=20.3$. 
+This source is coincident with the one year catalog source 1FGL J1628.6-2419c.
+A counts map showing this source is
 seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
@@
 \todo[inline]{Can we get another citation about dark gas and stuff?
-Better note about spectral index being typical of difuse emission.
-Also does this description make sense?}
+And a better description of spectral index being typical of diffuse emission.}
 
@@
 extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
-$\tsext=37.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
-\ref{1FGL_J1554.0-5345c} shows a counts map of this source.
-This source was found in the one year catalog with the name 1FGL J1554.0-5345c.
+$\tsext=37.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  
+This source is coincident with the one year catalog source 1FGL J1554.0-5345c.
+Figure \ref{1FGL_J1554.0-5345c} shows a counts map of this source.
 
@@
 2FGL J1551.3-5333c which is contained within the extended source.
-We tested this source for source confusion by fitting it instead
-as two point sources.  Since $\tsinc=9.2$ is less than \tsext,
-we conclude that the source is spatially extended. The region is further described in
-the caption to figure~\ref{1FGL_J1554.0-5345c}.
+We tested this source for source confusion by fitting it instead as
+two point sources.  Since $\tsinc=9.2$ is less than \tsext, we conclude
+that the source is spatially extended. The region is further described
+in the caption to figure~\ref{1FGL_J1554.0-5345c}.
 
 There are no obvious counterparts to this source at other
-wavelengths. Furthermore, this source is relativly soft with a spectral
-index 2.31 and is close to the galacitc plane in a region of large
+wavelengths. Furthermore, this source is relatively soft with a spectral
+index 2.31 and is close to the galactic plane in a region of large
 diffuse emission.  We conclude that although this region is significantly
@@
 
-\todo[inline]{this needs more quantification/description.  Improve the
-point about how since the source is soft, it is more consistent with
-diffuse emission.}
+\todo[inline]{This needs more quantification/description.  
+Can we improve the argument about spectral index}
 
@@
 significance of $\tsext=76.7$.  The source was fit to a position of
-$(l,b)=(266.29\deg,-1.41\deg)$.  Figure~\ref{Vela_Jr} shows a counts
-map of this source.  This source has no counterparts in the first year
-LAT catalog.
-
-To get a good fit of the region, we had to remove three nearby catalog
+$(l,b)=(266.29\deg,-1.41\deg)$.  
+This source has no counterparts in the first year LAT catalog.
+Figure~\ref{Vela_Jr} shows a counts map of this source.
+
+To get a good fit of the source, we had to remove three nearby catalog
 sources 2FGL J0848.5-4535, 2FGL J0855.4-4625, and 2FGL J0853.5-4711
@@
 J0901.7-4655 to better fit their position at high energies in the presence
-of an extended source.  This localization was done iterativly alterantly
+of an extended source.  This localization was done iteratively alternately 
 fitting the position of these two point sources and the extension of
@@
 $(l,b)=(267.311\deg,-0.190\deg)$. In addition, we removed the further away
-catalog source 2FGL J0858.0-4815 beacuse it was not significant above 10
+catalog source 2FGL J0858.0-4815 because it was not significant above 10
 \gev.  After modifying the region, we found that \tsinc=16.2 which is less
-than \tsext so we conclude that the source is extended These modifications
-are further described in the caption to figure~\ref{Vela_Jr}.
+than \tsext so we conclude that the source is extended 
+These modifications are shown in
+figure~\ref{Vela_Jr}.
 
@@
 
-\todo[inline]{
-Add a better interpreation.
-Explain that Vela Jr will be described better in upcoming publication???
-}
+\todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming publication?}
 
@@
 
-% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138 % extended source
-% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 % extended source
+% For both 2FGL J1615.0-5051 and 2FGL J1615.2-5138 
+% Extended Sources:
+%   * 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 % extended source
+%   * 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138 % extended source
 % Deleted
@@
 
+The two year catalog source 2FGL J1615.0-5051 was found to be
+extended using photons with energies between 10 \gev and 100 \gev.
+We found an extension of $0.33\deg\pm0.04\deg$ with an extension
+significance of \tsext=16.6.  The source was fit to a position of
+$(l,b)=(332.38\deg,-0.14\deg)$.  This source is coincident with the one
+year catalog source 1FGL J1613.6-5100c.  Figure~\ref{1FGL_J1613.6-5100c}
+shows a counts map of this source.
+
+This source is less than 1\deg away from 2FGL J1615.0-5051 which is
+also spatially extended (see section~\ref{section_2FGL_J1615.2-5138}).
+To get a good fit of both sources, we had to model both sources as being
+spatially extended and iteratively fit the position and extension of each
+source until obtaining a global best fit.  Before doing this, We removed
+from our model the three nearby catalog sources 2FGL J1620.6-5111c, 2FGL
+J1619.7-5040c, and 2FGL J1622.8-5006 2FGL J1615.0-5051 because they were
+not significant above 10 \gev.  These modifications are further described
+in the caption to figure~\ref{1FGL_J1613.6-5100c}.  After modifying
+the region, we found that \tsinc=12.2 which is less than \tsext so we
+conclude that the source is extended.
+
+This source is spatially coincident with the extended \tev source HESS
+J1616-508 (\cite{HESS_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
+contours of HESS J1616-508 are overlaid on 2FGL J1615.0-5051.  The
+H.E.S.S. experiment measured an extension $\sigma$ of $0.23\pm0.02$ and
+$0.15\pm0.02$ along the semi-major and semi-minor axes respectively when
+fitting the source with an elliptical Gaussian spatial model.  This size
+corresponds to a 68\% source containment radius of $\rsixeight\sim0.22\deg$
+to $0.34\deg$. This size matches very well with the LAT size
+$\rsixeight=0.27\deg\pm0.03$ (see section~\ref{compare_source_size}).
+
+\todo[inline]{Add interpretations of HESS J1616-508.}
+
 \subsection{2FGL J1615.2-5138}
@@
 
-% Same modifications as 2FGL J1615.0-5051.
-
-%The two year catalog source 2FGL J1615.2-5138 was found to be extended
-%using photons with energies between 10 \gev and 100 \gev.  This source
-%is coincident with the one year catalog source 1FGL J1614.7-5138c.
-%We found an extension of $0.43\deg\pm0.04\deg$ with an extension
-%significance of \tsext=45.3.  The source was fit to a position of
-%$(l,b)=(331.67\deg,-0.66\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
-%a counts map of this source.
-
-%To get a good fit for the region, we had to remove from our model
-%the nearby catalog sources 2FGL J1620.6-5111c, 2FGL J1619.7-5040c,
-%and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
-%iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
-%position and extension of 2FGL J1615.2-5138.  We ended up with a best
-%fit position of the nearby source 2FGL J1615.0-5051 having moved from
-%$(l,b)=(332.2684\deg,0.043\deg)$ to $(l,b)=(332.365\deg,0.005\deg)$.  In addition,we
-%had to add a new source not in the catalog at the position of
-%$(l,b)=(332.426\deg,-0.331\deg)$.  The location of these sources was found by iterativly
-%fitting the position of these sources as well as the extension of 2FGL
-%J1615.2-5138 until a stable fit was found.  
-%These modifications are further described in the caption to 
-%figure~\ref{1FGL_J1613.6-5100c}.
-
-%To address the possibility of source confusion, we compared the likelihood
-%fitting 2FGL J1615.2-5138 as two point sources to one source.  We found
-%that \tsinc=30.1 which is smaller then \tsext so we believe that this
-%is extended emission.
-
-\todo[inline]{This section needs to be rewritten}
-
-%This extended source is spatially coincident with the extended source
-%HESS J1614-518 which was reported in the H.E.S.S. survey of the Inner
-%Galaxy (\cite{HESS_plane_survey}). Overlaid on figure~\ref{1FGL_J1613.6-5100c} are the H.E.S.S
-%contours of this source and it can be seen that there is good spatial
-%overlap between the LAT and H.E.S.S. emission.
-%
-%It is unclear if our model around the nearby souce 2FGL J1615.0-5051
-%is good. 2FGL J1615.0-5051 is spatially coincident with the extended H.E.S.S.
-%source HESS J1616-508 but was not found to be significantly extended
-%with our extended source search.
-%
-%It is unclear if this new source is physically real.
-%2FGL J1615.0-5051 fit $\ts=28$ and the added source had $\ts=12$
-%which is not extended.
-%2FGL J1615.0-5051 was not found to be significantly extended.
-%$\ts=12$ which is not significant. 
-%
-%It is unclear of this new seed
-%is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
-%2FGL J1615.0-5051 was not found to be significantly extended using two
-%years of data but the fit of 2FGL J1615.2-5138 was clearly growing too
-%large to obsorb residual in the direction of J1615.2-5138 until we added
-%the additional point source.
-%
-%
-%HESS J1616-508
-
-\todo[inline]{Interpret source as being coincident with HESS JXXXX
-and what the possible emission mechanism could be.}
-
-\todo[inline]{Describe What this source is/What HESS Source this is near}
-\todo[inline]{Describe contours overlaied on source}
+The two year catalog source 2FGL J1615.2-5138 was found to be
+extended using photons with energies between 10 \gev and 100 \gev.
+We found an extension of $0.42\deg\pm0.03\deg$ with an extension
+significance of \tsext=47.6.  The source was fit to a position
+of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
+with the one year catalog source 1FGL J1614.7-5138c.  Because 2FGL
+J1615.2-5138 is close to 2FGL J1615.0-5051, the same model described
+in section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
+sources. Both sources can be seen in figure~\ref{1FGL_J1613.6-5100c}.
+For 2FGL J1615.2-5138, \tsinc=37.6 which is less than \tsext so we
+conclude that the source is extended.
+
+This source is spatially coincident with the extended \tev source
+HESS J1614-518 (\cite{HESS_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
+contours of HESS J1614-518 are overlaid on 2FGL J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian extension of
+$\sigma=0.156\deg\pm0.008\deg$. This size corresponds to a 68\% source
+containment radius of $\rsixeight\sim0.33\pm0.01\deg$.  This size matches
+very well with the LAT size of $\rsixeight\sim0.34\pm0.02$.
+
+\todo[inline]{Add interpretations of HESS J16154-518.}
 
@@
 
-The two year catalog source 2FGL J1632.4-4753c was found to be extended
-using photons with energies between 10 \gev and 100 \gev.  This source
-is coincident with the one year catalog source 1FGL J1632.9-4802c.
+The two year catalog source 2FGL J1632.4-4753c was found to be
+extended using photons with energies between 10 \gev and 100 \gev.
 We fit an extension of $0.44\deg\pm0.04\deg$ with an extension
-significance of \tsext=62.2.  The source was fit to a position
-of $(l,b)=(336.52\deg,0.06\deg)$.  Figure~\ref{1FGL_J1632.9-4802c}.
+significance of \tsext=64.8.  The source was fit to a position of
+$(l,b)=(336.41\deg,0.22\deg)$.  This source is coincident with the one
+year catalog source 1FGL J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
 shows a counts map of this source.
 
-To get a good fit of the region, we had to remove from our model
-the three catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
-2FGL J1634.4-4743c.4-4820c. These sources all are on top of this
-extended source but there is no indication that the emission of these
-sources separates.  Finally, we relocalized the
-source 2FGL J1635.4-4717c to a better fit position $(l,b)=(337.230\deg,0.346\deg)$
-and the position of 2FGL J1636.3-4740c to the better fit position
-$(l,b)=(336.968\deg,-0.066\deg)$ to get a good overall fit of our source.
-These modifications are further described in the caption to 
+To get a good fit of the source, we had to remove from our model
+three catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752, 2FGL
+J1634.4-4743c.4-4820c that were part of the extended source..
+We then iterativly relocalized the source 2FGL J1635.4-4717c
+to $(l,b)=(337.230\deg,0.346\deg)$ and 2FGL J1636.3-4740c to
+$(l,b)=(336.968\deg,-0.066\deg)$ while fitting the extension of
+2FGL J1632.4-4753c.  In addition we removed from our model four
+farther away two year catalog sources 2FGL J1638.0-4703c, 2FGL
+J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL J1639.8-4921c because they
+were not significant above 10 \gev.  These modifications are shown in
 figure~\ref{1FGL_J1632.9-4802c}.
-
-In addition we removed from our region four farther away two year
-catalog sources 2FGL J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615,
-2FGL J1639.8-4921c because they were not significant above 10 \gev.
 
@@
 region as one extended source to the likelihood fitting this region as
-two point sources. We found $\tsinc=38.5\ll\tsext$ which indicates that
-this is extended emission and not source confusion.
-
-This extended source is spatially coincident with
-the \tev source HESS J1634-472.  Overlaid on the counts map are the
-contours of the region as seen in \tev (\cite{HESS_plane_survey})
-and we see that there is good spatial overlap of these sources.
-
-\todo[inline]{Describe the interpretation of this source}
+two point sources. We found $\tsinc=40.9\ll\tsext$ which is less than \tsext
+so we conclude that this is an extended source.
+
+This extended source is spatially coincident with the extended \tev source HESS
+J1632-478 (\cite{HESS_plane_survey}).  In figure~\ref{1FGL_J1632.9-4802c},
+contours of  HESS J1632-478 are overlaid on 2FGL J1635.4-4717c.
+H.E.S.S measured an extension of $\sigma=0.21\pm0.05$ and
+$0.06\pm0.04$ along the semi-major and semi-minor axes when fitting the source
+with an elliptical Gaussian spatial model.  This corresponds to a 68\%
+containment size of $\rsixeight=0.31\pm0.08$ and $0.09\pm0.06$ along the
+semi-major and semi-minor axis. This size is consistent with the LAT size of
+$\rsixeight=0.36\pm0.03$.
+
+\todo[inline]{Add interpretation of HESS J1632-478.}
 
@@
 % Modify:
+% * P72Y2974 - 2FGL J1834.7-0705c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
+%              (initial Position  - SkyDir(25.0953,-0.0887)
 % * P72Y2985 - 2FGL J1836.8-0623c - SkyDir(25.574,0.320,SkyDir.GALACTIC)
 %              (initial Position  - SkyDir(25.5925,0.3103)
-% * P72Y2974 - 2FGL J1837.3-0700c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
-%              (initial Position - SkyDir(25.0953,-0.0887)
 % * P72Y2994 - 2FGL J1839.3-0558c - SkyDir(26.080,0.229,SkyDir.GALACTIC)
@@
 
-The two year catalog source 2FGL J1837.3-0700c was found to be extended
-using photons with energies between 10 \gev and 100 \gev. This source
-is coincident with the one year catalog source 1FGL J1837.5-0659c. We
-fit an extension of $0.35\deg\pm0.08\deg$ with an extension
-significance of $\tsext=20.9$.  The source was fit to a position of
-$(l,b)=(25.08\deg,0.13\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
-counts map of this source.
-
-This source is in a complicated region. There are two nearby
-catalog sources 2FGL J1836.8-0623c and 2FGL J1837.3-0700c which are
-about $~0.5\deg$ away from our source. To get a good fit of the region,
-we slightly relocalize these sources so that 2FGL J1836.8-0623c is at
-a postiion of $(l,b)=(25.574\deg,0.320\deg)$ and 2FGL J1837.3-0700c is
-at a position of $(l,b)=(24.716\deg,0.500\deg)$.  We also relocalized
-the source 2FGL J1839.3-0558c which is about $~1\deg$ away from our
-source to a better position of $(l,b)=(26.080\deg,0.229\deg)$ Finally,
-we had to remove the nearby catalog source 2FGL J1835.5-0649 which we
-believed to be part of our extended source. We also removed the farther
-away catalog source 2FGL J1839.0-0539 because it was not significant
-above 10 \gev.  After modifying the region, we found that \tsinc=15.4
-which is less than \tsext, so we believe that the emission from this
-source spatially extended.  These modifications are further described
-in the caption to figure~\ref{1FGL_J2020.0+4049}.
-
-This source is spatially coincident with the \tev source HESS J1837-069.
-Overlaid on the figure~\ref{1FGL_J2020.0+4049} are H.E.S.S contours of
-HESS J1837-069 (\cite{HESS_plane_survey}). There is a reasonable spatial
-overlap of these sources.
-
-\todo[inline]{
-Near HESS source HESS J1837. 
-Discuss the upcomming publication???}
+The two year catalog source 2FGL J1837.3-0700c was found to be
+extended using photons with energies between 10 \gev and 100 \gev.
+We fit an extension of $0.35\deg\pm0.08\deg$ with an extension
+significance of $\tsext=20.2$.  The source was fit to a position of
+$(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
+year catalog source 1FGL J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
+shows a counts map of this source.
+
+This source is in a complicated region. There are three nearby catalog
+sources 
+2FGL J1834.7-0705c, 2FGL J1836.8-0623c, and 2FGL J1839.3-0558c.
+To get a good fit of 2FGL J1837.3-0700c,
+we relocalized 
+2FGL J1834.7-0705c to $(l,b)=(24.77\deg,0.50\deg)$.  
+2FGL J1836.8-0623c moved to $(l,b)=(25.57\deg,0.32\deg)$, and 
+2FGL J1839.3-0558c to $(l,b)=(26.08\deg,0.23\deg)$.  
+We removed the nearby catalog source 2FGL J1835.5-0649 which is part
+of the extended emission and the farther away catalog
+source 2FGL J1839.0-0539 because it was not significant above 10 \gev.
+After modifying the region, we found that \tsinc=12.3 which is less
+than \tsext, so we conclude that the source is spatially extended. These
+modifications are shown in figure~\ref{1FGL_J1837.5-0659c}.
+
+This source is spatially coincident with the \tev source HESS J1837-069 (\cite{HESS_plane_survey}).
+In figure~\ref{1FGL_J1837.5-0659c}, contours of 
+are H.E.S.S J1837-069 are overlaid on 
+2FGL J1837.3-0700c. H.E.S.S. measured an extension of
+$\sigma=0.12\pm0.02$ and $0.05\pm0.02$ along the semi-major and 
+semi-minor axis when fitting the source
+with an elliptical Gaussian spatial model.
+This corresponds to a 68\% containment radius of $\rsixeight=0.18\pm0.03$ and $0.08\pm0.03$ 
+along the semi-major and semi-minor axis. The size is comparable to LAT 
+which fit a 68\% containment radius of
+$\rsixeight=0.29\pm0.07$.
+The LAT size is larger than the H.E.S.S. size but the sizes are almost almost within
+the $1\sigma$ errors. It is possible that the morphologies are different but
+this is not very significant.
+A possible reason is confusion could be that the LAT source may be partially
+fitting other sources in the region.
+
+\todo[inline]{Add interpretation of HESS J1837-069.}
+
+\subsection{2FGL J1712.4-3941}
+\label{section_2FGL_J1712.4-3941}
+
+% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
+% New Source:
+%  * SkyDir(346.85102135118683,0.24359779858357899,SkyDir.GALACTIC),
+% Delete:
+%  * P72Y2685 - Not in 2FGL
+%  * P72Y2680 - Not in 2FGL
+%  * P72Y2689 - Not in 2FGL
+
+This is RX J1713.7-2946. This analysis not finished.
+
+Recent LAT publication: \cite{rx_j1713_lat}.
+
+Contours taken from HESS Paper: \cite{rx_j1713_hess}
+
+The Figure is \ref{2FGL_J1712.4-3941}
 
@@
 fit an extension of $0.59\deg\pm0.03\deg$ with an extension
-significance of $\tsext=140.6$.  The source was fit to a position of
+significance of $\tsext=139.4$.  The source was fit to a position of
 $(l,b)=(78.17\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
@@
 
-To get a good fit of the region, we had to remove the nearby catalog
+To get a good fit of the source, we had to remove the nearby catalog
 source 2FGL J2019.1+4040 which were part of the extended source.
@@
 the two year catalog into our background model.  The new source is was
-localized to a position of $(l,b)=(78.854,2.670)$ and had $\ts\approx 16$
+localized to a position of $(l,b)=(78.85,2.67)$ and had $\ts\approx 16$
 (using \pointlike).  Although the source is not very significant, not
@@
 were not significant above 10 \gev.  After modifying the region, we found
-that \tsinc=34.7 which is less than \tsext, so we believe that this
+that \tsinc=29.7 which is less than \tsext, so we believe that this
 source is spatially extended.  These modifications are further described
@@
 \todo[inline]{
-Add more interpreation about this source. Describe how this source
-will be more carefully analyzed in the paper
-``A cocoon of freshly accelerated cosmic rays detected by Fermi
-in the Cygnus superbubble''}
+Add interpretations paragraph.  Describe how this source will be more
+carefully analyzed in ``A cocoon of freshly accelerated cosmic rays
+detected by Fermi in the Cygnus superbubble''}
 
@@
 
-\todo[inline]{This conclusion needs to be written}
+\todo[inline]{This conclusion needs to be written.}
 
@@
 of five more data! Pointlike will be necessary to improve the model of the
-high energy sky.
+high energy sky. Hard to do a blind analysis of LAT data.
 
@@
     100 \gev whereas the right plot shows the analysis with an energy
-    range from 10 \gev to 100 \gev.  This plot is discussed futher in
+    range from 10 \gev to 100 \gev.  This plot is discussed further in
     section~\ref{compare_source_size}.
@@
       was fit with both a uniform disk and a Gaussian spatial model.
-      The white circle represents the fit size $\sigma$ modeling the
+      The red circle represents the fit size $\sigma$ modeling the
       source with a uniform disk spatial model.  The black circle is
       the fit $\sigma$ modeling the source with a Gaussian hypothesis.
-      The dashed white and black circles are the fit \rsixeight for the
-      disk and Gaussian hypothesis. This plot is discussed furhter in
+      The dashed white and black circle are the fit \rsixeight for the
+      disk and Gaussian hypothesis. This plot is discussed further in
       section~\ref{compare_source_size}.
@@
     black crosses are all of the catalog sources in
-    the region and the white circle is the edge of the best fit
+    the region and the red circle is the edge of the best fit
     uniform disk which was fit to IC443 using \pointlike.  These plots
@@
     two year catalog source 2FGL J1856.2+0450c. This map is smoothed by
-    a 0.1\deg Gaussian kernel and the large white circle is the edge of
+    a 0.1\deg Gaussian kernel and the red circle is the edge of
     the fit uniform disk spatial model.  2FGL J1856.2+0450c fits to an
@@
     $\chi^2/2$ distribution.  Possible reasons for the discrepancy between
-    the distrubtions are discussed in section~\ref{test_1lac_sources}
+    the distributions are discussed in section~\ref{test_1lac_sources}
     but this plot demonstrates that any systematics in our extension
@@
 \end{sidewaystable}
+
+\clearpage
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics{source_plots/allsky_extended_sources.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v1/run.py
+    \end{center}
+    \caption{A plot of all \gev extended sources detected by the LAT
+    with two years of data.  The twelve extended sources included in
+    the second LAT catalog are the red markers and the ten additional
+    extended sources analyzed in this paper are the green markers. The
+    extended sources are overlaid on an Aitoff projection Galactic
+    coordinate map of all 100 \mev to 100 \gev photons measured by the
+    LAT in the two year time interval of this analysis.}\label{allsky_extended_sources}
+  \end{sidewaysfigure}
 
@@
     \begin{centering}
-      \begin{tabular}{l|rrrrrrrr}
+%      \begin{tabular}{l|rrrrrrrr}
 %        \hline
@@
 %        \hline
-      \end{tabular}
+%      \end{tabular}
+      \missingfigure{This analysis is still running\ldots}
       \label{alt_diff_model_results}
@@
   \begin{center}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
+  \end{center}
+  % this plot came from 
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
+  \caption{A galactic and isotropic diffuse subtracted 1 \gev to 100
+  \gev counts map of the region around 2FGL J0823.0-4246 smoothed by a
+  0.1\deg Gaussian kernel.  The red star is the catalog position of this source.  
+  The red cross and circle are the best fit position
+  and extension of this source assuming a uniform disk spatial model.
+  The two green stars are the positions of the sources 2FGL J0823.4-4305
+  and 2FGL J0821.0-4254 which were removed because they are part of the
+  extended source.  This source is spatially coincident with the Puppis
+  A SNR. The green contours are an X-ray image of Puppis A observed by
+  ROSAT (\cite{rosat_puppis_a}). There is good spatial overlap between
+  the LAT and X-ray emission.  Even though the Vela pulsar is over 3
+  degrees away from the source, because it is so bright it can be seen
+  on the top left.  More information about this source can be found in 
+  section~\ref{section_2FGL_J0823.0-4246}.
+  }\label{1FGL_J0823.3-4248}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
     \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1628.6-2419c}
@@
   \caption{
-  A galactic and isotropic diffuse subtracted 1 \gev to 100 \gev counts map of the region around
-  2FGL J1627.0-2425 smoothed by a 0.1\deg Gaussian kernel.  The red star
-  is the second LAT catalog's best fit position of 2FGL J1627.0-2425 and
-  the black cross is the background source 2FGL J1625.7-2526.  The red
-  cross and white circle represent the best position and extension of
-  2FGL J1627.0-2425 when fit assuming a uniform disk spatial model.
-  Overlaid on the plot are contours of a 100 micrometer infrared
+  A galactic and isotropic diffuse subtracted 1 \gev to 100 \gev counts
+  map of the region around 2FGL J1627.0-2425 smoothed by a 0.1\deg
+  Gaussian kernel.  The red star is the catalog's position of
+  this source.  The red cross and circle are
+  the best position and extension of this source assuming a
+  uniform disk spatial model.  The black cross is the background source
+  2FGL J1625.7-2526.  The green contours are a 100 micrometer infrared
   image of the region as seen by IRAS (\cite{iras_rho_ophiuci}). This
-  source is in the Ophiuchus region and is most likely unaccounted for
-  diffuse emission.  More information about this source is presented
+  source is in the Ophiuchus region and most likely represents 
+  unmodeled diffuse emission.  More information about this source can be found
   in section~\ref{section_2FGL_J1627.0-2425c}.
@@
   0.1\deg Gaussian kernel.  The red star is the catalog position of
-  2FGL J1554.4-5317c.  The red cross and white circle are the best
+  2FGL J1554.4-5317c.  The red cross and circle are the best
   fit position and extension of this source assuming a uniform disk
   spatial model.  The green star represents the catalog source 2FGL
-  J1551.3-5333c which was removed from the region because it was part of
-  the extended source.  Because the source has no obviosu counterpart and
+  J1551.3-5333c which was removed because it was part of
+  the extended source.  Because the source has no obvious counterpart and
   is in a region of large diffuse emission, the source is most likely
-  unmodeled diffuse emission.  More information about this source is
-  presented in section~\ref{section_2FGL_J1554.4-5317c}.
+  unmodeled diffuse emission.  More information about this source can be
+  found in section~\ref{section_2FGL_J1554.4-5317c}.
   }
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-  \caption{A galactic and isotropic diffuse subtracted 1 \gev to 100
-  \gev counts map of the region around 2FGL J0823.0-4246 smoothed by
-  a 0.1\deg Gaussian kernel.  The red star is the catalog position
-  of 2FGL J0823.0-4246.  The red cross and white circle are the best
-  fit position and extension of this source assuming a uniform disk
-  spatial model.  The two green stars are the positions of two nearby
-  catalog source 2FGL J0823.4-4305 and 2FGL J0821.0-4254 that we removed
-  from our region. This source is spatially coincident with the Puppis
-  A SNR. Overlaid on the figure are ROSAT contours of Puppis A SNR
-  (\cite{rosat_puppis_a}). There is good spatial overlap between the
-  LAT and X-ray emission.  The emission on the upper east comes from the
-  bright Vela Pulsar. Even though Vela is over 3 degrees away from
-  this source at a position of $l,b=(263.55\deg,-2.79\deg)$, it can be
-  seen because it is so bright. More information about this source is
-  presented in section~\ref{section_2FGL_J0823.0-4246}.
-  \todo[inline]{This figure could better explain the source}
-  }\label{1FGL_J0823.3-4248}
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
+  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
+  \gev counts map of the region around 2FGL J0851.7-4635 smoothed by
+  a 0.25\deg Gaussian kernel. This image is smoothed by a larger
+  kernel because it is significantly larger than the other sources.
+  The red star is the catalog position of
+  this source.  The red cross and circle are the best fit position
+  and extension of the source assuming a uniform disk spatial model.
+  Three nearby catalog sources 2FGL J0848.5-4535,
+  2FGL J0855.4-4625, and 2FGL J0853.5-4711 were removed 
+  because they are part of the extended source.  The farther away
+  green star is 2FGL J0858.0-4815 which was removed 
+  because it was not significant above 10 \gev.  The blue stars and
+  crosses are the catalog positions and the relocalized positions of (from
+  left to right) 2FGL J0901.7-4655 and 2FGL J0854.7-4501.  This
+  extended source is spatially coincident with the Vela Jr SNR.
+  The green contours are the \tev emission of Vela Jr. observed by
+  H.E.S.S (\cite{vela_jr_hess}).  More information about this source 
+  can be found in section~\ref{section_2FGL_J0851.7-4635}.
+  }\label{Vela_Jr}
 \end{figure}
@@
   \caption{
-\todo[inline]{This section needs to be rewritten}
-%A galactic and isotropic diffuse subtracted 10 \gev to 100 \gev counts map of the region
-%around 2FGL J1615.2-5138. The red star is the catalog position of 2FGL
-%J1615.2-5138 and the red cross and the white circle are the best fit
-%position and extension of this source assuming a uniform disk spatial
-%model.  Overlaid on this plot are contours of this region as seen in \tev
-%by H.E.S.S. This source spatially overlaps the extended H.E.S.S. source
-%HESS J1614-518 (\cite{HESS_plane_survey}).  To fit this region, we had to
-%relocalize the source 2FGL J1615.0-5051 from its catalog position (blue
-%star) to its best fit position (blue cross) and add an additional source
-%into the region at the position of the grey cross.  It is unclear of this
-%is a physically new source or if 2FGL J1615.0-5051 is spatially extended.
-%2FGL J1615.0-5051 is spatially coincident with the extended H.E.S.S.
-%source HESS J1616-508 but was not found to be significantly extended
-%using two years of data. Nevertheless, adding this addtional source
-%was necessary to stop 2FGL J1615.2-5138's extension from growing too
-%large and fitting both sources. To fit this region, we had to remove three catalog
-%sources 2FGL J1619.7-5040c, 2FGL J1620.6-5111c, and 2FGL J1622.8-5006
-%from the region because they were not significant. Two are shown as green
-%stars and one is outside of the plot region.
-  \todo[inline]{Describe this source better.}
+    A galactic and isotropic diffuse subtracted 10 \gev to 100 \gev counts
+    map of the region around 2FGL J1615.0-5051 and 2FGL J1615.2-5138
+    smoothed by a 0.1\deg Gaussian kernel. The upper left source is
+    2FGL J1615.0-5051 and the lower right source is 2FGL J1615.2-5138.
+    The red stars are the catalog positions of these sources.  The red
+    stars and circles are the best fit positions and extensions
+    of these sources assuming uniform disk spatial model.  To fit these
+    sources, we had to remove 
+    the sources 2FGL J1619.7-5040c, 2FGL J1620.6-5111c, and 2FGL
+    J1622.8-5006 because they were not significant above 10\gev. Two
+    of these sources are on the left side of the plot and one is
+    outside the region.  The green contours are the \tev emission of
+    the extended source HESS J1614-518 and the extended source HESS
+    J1616-508 measured by H.E.S.S.(\cite{HESS_plane_survey}). 2FGL
+    J1615.0-5051 is spatially
+    consistent with HESS J1616-508 and 2FGL J1615.2-5138 is spatially
+    consistent with HESS J1614-518.  More information about 2FGL
+    J1615.0-5051 can be found in section~\ref{section_2FGL_J1615.0-5051} and
+    2FGL J1615.2-5138 in section~\ref{section_2FGL_J1615.2-5138}.
   }\label{1FGL_J1613.6-5100c}
@@
   a 0.1\deg Gaussian kernel.  This source is in a crowded region.
-  The red star is the catalog position of 2FGL J1632.4-4753c.  The red
-  cross and white circle are the best fit position and extension 2FGL
+  The red star is the catalog position of this source.  The red
+  cross and circle are the best fit position and extension 2FGL
   J1632.4-4753c assuming a uniform disk spatial model.  The three
-  green crosses inside the extension circle are the sources 2FGL
+  green crosses inside the extension are 2FGL
   J1631.7-4720c, 2FGL J1630.2-4752, and 2FGL J1634.4-4743c.4-4820c
-  which were removed from the region when fitting 2FGL J1632.4-4753c
-  for extension.  The blue stars and crosses are the catalog
-  positions and the relocalized positions of (from east to west)
-  2FGL J1636.3-4740c and 2FGL J1635.4-4717c.  The farther away green
-  stars represent other catalog sources which were not significant
+  which were removed because they are part
+  of the extended source.  The blue stars and crosses are the catalog
+  positions and the relocalized positions of (from left to right)
+  2FGL J1635.4-4717c and 2FGL J1636.3-4740c.  The farther away green
+  stars are other catalog sources which were removed 
+  because they are not significant
   above 10 \gev.  This extended source is spatially coincident
-  with the extended H.E.S.S source HESS J1634-472.  Overlaid on
-  the counts map are the contours of the region as seen in \tev
-  (\cite{HESS_plane_survey}). More information about this source is
-  presented in section~\ref{section_2FGL_J1632.4-4753c}.
-  \todo[inline]{Describe the interpreation.}
+  with the extended H.E.S.S source HESS J1634-472.  The green
+  contours are the \tev emission seen by H.E.S.S. 
+  (\cite{HESS_plane_survey}). More information about this source 
+  can be found in section~\ref{section_2FGL_J1632.4-4753c}.
   }\label{1FGL_J1632.9-4802c}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Gamma_Cygni}
-  \end{center}
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
-  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
-  \gev counts map of the region around 2FGL J2021.5+4026 smoothed by
-  a 0.1\deg Gaussian kernel. The red star is the catalog position of
-  2FGL J2021.5+4026.  The red cross and white circle are the best fit
-  position and extension 2FGL J2021.5+4026 assuming a uniform disk
-  spatial model.  The green cross inside of the extension is a nearby
-  catalog source 2FGL J2019.1+4040 which was removed from our region
-  when fitting this source for extension.  The further away green stars
-  represent other catalog sources which were removed from the analysis
-  because they were not significant above 10 \gev.  The grey cross is
-  the position a source not in the two year LAT catalog which was added
-  to the region to get a better fit of 2FGL J2021.5+4026.  This source
-  is spatially coincident with the Gamma Cygni SNR.  Contours of
-  Gamma Cygni at 408MHz from the Canadian Galactic Plane Survey are
-  overlaid and there is good spatial agreement with the LAT emission
-  (\cite{canadian_galactic_plane_survey}).  More information about this
-  source is presented in section~\ref{section_2FGL J2021.5+4026}.
-  \todo[inline]{Describe the interpreation better.}
-  }\label{1FGL_J2020.0+4049}
 \end{figure}
@@
   0.1\deg Gaussian kernel.  The red star is the catalog position of
-  2FGL J1837.3-0700c. The red cross and white circle are the best fit
-  position and extension  of 2FGL J1837.3-0700c assuming a uniform disk
-  spatial model.  The blue stars and crosses are the catalog position and
-  the relocalized poistion of (from east to west) 2FGL J1837.3-0700c,
-  2FGL J1836.8-0623c, and 2FGL J1839.3-0558c.  The green cross inside
-  of the extension is a nearby catalog source 2FGL J1835.5-0649 which
-  was removed from the region.  The further away green star is 2FGL
-  J1839.0-0539 which was removed from the analysis because it was not
-  significant above 10 \gev.  
-  This source is spatially coincident with the \tev source HESS J1837-069.
-  Overlaid on the figure~\ref{1FGL_J2020.0+4049} are H.E.S.S contours of
-  HESS J1837-069 (\cite{HESS_plane_survey}).  
-  \todo[inline]{Describe the interpreation
-  better.} \todo[inline]{Note about why the top right source was not
-  found to be extended b/c the scale is cut.}
+  this source. The red cross and circle are the best fit position and
+  extension  of 2FGL J1837.3-0700c assuming a uniform disk spatial model.
+  The blue stars and crosses are the catalog position and the relocalized
+  position of (from left to right) 2FGL J1839.3-0558c, 2FGL J1836.8-0623c,
+  and 2FGL J1834.7-0705c.  The green cross inside the extension is 
+  2FGL J1835.5-0649 which was removed because it
+  is part of the extended source.  The farther away green star is 2FGL
+  J1839.0-0539 which was removed because it is not significant above
+  10 \gev.  This source is spatially coincident with the \tev source HESS
+  J1837-069.  The green contours are the \tev emission of HESS J1837-069
+  observed by H.E.S.S (\cite{HESS_plane_survey}).  More information about
+  this source can be found in section~\ref{section_2FGL_J1837.3-0700c}.
   }\label{1FGL_J1837.5-0659c}
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
+    %\includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946.pdf}
+    \missingfigure{This analysis is not finished}
+  \end{center}
+  \caption{
+  This is RX J1713.7-2946. This analysis not finished.
+  The 2FGL source is 2FGL J1712.4-3941.
+  More information about this source can be found in section~\ref{section_2FGL_J1712.4-3941}.
+Contours taken from HESS Paper: \cite{rx_j1713_hess}
+  }\label{2FGL_J1712.4-3941}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Gamma_Cygni}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
   \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
-  \gev counts map of the region around 2FGL J0851.7-4635 smoothed by a
-  0.25\deg Gaussian kernel. The red star is the catalog position of 2FGL
-  J0851.7-4635.  The red cross and white circle are the best fit position
-  and extension 2FGL J0851.7-4635 assuming a uniform disk spatial model.
-  The green cross inside of the extension is a nearby catalog source
-  2FGL J2019.1+4040 which was removed from our region when fitting this
-  source for extension.  Three nearby catalog sources 2FGL J0848.5-4535,
-  2FGL J0855.4-4625, and 2FGL J0853.5-4711 were removed from the region
-  because they are inside of this extended source.  The further away
-  green star is 2FGL J0858.0-4815 which was removed from the anlaysis
-  because it was not significant above 10 \gev.  The blue stars and
-  crosses are the catalog position and the relocalized poistion of (from
-  east to west) 2FGL J0854.7-4501 and 2FGL J0901.7-4655.   The extended
-  source 2FGL J0851.7-4635 is spatially coincident with the SNR Vela Jr.
-  Overlaid on figure are contours of Vela Jr. as  seen in \tev by H.E.S.S
-  (\cite{vela_jr_hess}).  More information about this source is presented
-  in section~\ref{section_2FGL_J0851.7-4635}.
-  \todo[inline]{Describe interpreation better.} 
-  }\label{Vela_Jr}
+  \gev counts map of the region around 2FGL J2021.5+4026 smoothed by a
+  0.1\deg Gaussian kernel. The red star is the catalog position of 2FGL
+  J2021.5+4026.  The red cross and circle are the best fit position and
+  extension 2FGL J2021.5+4026 assuming a uniform disk spatial model.
+  The green cross inside the extension is 2FGL J2019.1+4040 which
+  was removed because it is part of the extended source.  The farther
+  away green stars represent other catalog sources which were removed
+  because they were not significant above 10 \gev.  The grey cross is
+  the position a source not in the two year catalog which was added
+  to the region. 2FGL J2021.5+4026 is spatially coincident with the
+  Gamma Cygni SNR.  The green contours are a 408MHz image of Gamma Cygni
+  observed by the Canadian Galactic Plane Survey.  More information about
+  this source can be found in section~\ref{section_2FGL J2021.5+4026}.
+  }\label{1FGL_J2020.0+4049}
 \end{figure}

### 2011-07-19 extended_catalog/paper/extended_catalog.tex
new plots

@@
 sources were simulated on top of an isotropic power-law background
-with a Sreekumar-like spectrum ($>100$ \mev flux of 1.5e-5 and spectral
+with a Sreekumar-like spectrum ($>100$ \mev flux of $1.5\times 10^{-5}$ and spectral
 index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
@@
     \begin{centering}
-%      \begin{tabular}{l|rrrrrrrr}
-%        \hline
-%        \hline
-%        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
-%        \hline
-%        \multicolumn{9}{c}{$E > 1 \gev$} \\
-%        \hline
-%        2FGL J1627.0-2425c   &                154.9 &                131.0 &                102.4 &                     32.6 &                   21.1 &                 23.3 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
-%        2FGL J1554.4-5317c   &                134.8 &                149.0 &                137.6 &                     39.4 &                   39.6 &                 39.8 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
-%        2FGL J0823.0-4246    &                347.3 &                314.5 &                343.6 &                     66.1 &                   49.2 &                 56.6 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
-%        \hline
-%        \multicolumn{9}{c}{$E > 10 \gev$} \\
-%        \hline
-%        2FGL J1615.2-5138    &                 78.2 &                 77.6 &                 88.2 &                     46.4 &                   45.3 &                 53.7 & $  0.43\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
-%        2FGL J1632.4-4753c   &                126.9 &                126.4 &                158.1 &                     64.0 &                   62.2 &                 94.1 & $  0.44\deg \pm   0.04\deg$ & $  0.67\deg \pm   0.03\deg$ \\
-%        2FGL J2021.5+4026    &                236.5 &                221.2 &                265.8 &                    156.0 &                  140.6 &                162.6 & $  0.59\deg \pm   0.03\deg$ & $  0.72\deg \pm   0.03\deg$ \\
-%        2FGL J1837.3-0700c   &                 45.5 &                 48.0 &                 39.2 &                     18.6 &                   20.9 &                 18.8 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
-%        2FGL J0851.7-4635    &                120.2 &                119.7 &                125.9 &                     90.1 &                   90.9 &                 94.7 & $  1.12\deg \pm   0.07\deg$ & $  1.16\deg \pm   0.08\deg$ \\
-%        \hline
-%      \end{tabular}
-      \missingfigure{This analysis is still running\ldots}
+      \begin{tabular}{l|rrrrrrrr}
+        \hline
+        \hline
+        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
+        \hline
+        \multicolumn{9}{c}{$E > 1 \gev$} \\
+        \hline
+        2FGL J0823.0-4246    &                347.3 &                314.7 &                343.9 &                     66.1 &                   46.1 &                 53.4 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
+        2FGL J1627.0-2425c   &                154.9 &                130.3 &                102.4 &                     32.6 &                   20.3 &                 23.8 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
+        2FGL J1554.4-5317c   &                134.8 &                150.8 &                139.4 &                     39.4 &                   37.6 &                 38.0 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
+        \hline
+        \multicolumn{9}{c}{$E > 10 \gev$} \\
+        \hline
+        2FGL J0851.7-4635    &                120.2 &                120.0 &                126.1 &                     90.1 &                   76.7 &                 82.9 & $  1.12\deg \pm   0.07\deg$ & $  1.12\deg \pm   0.08\deg$ \\
+        2FGL J1615.0-5051    &                 52.5 &                 54.0 &                 57.4 &                     17.5 &                   16.6 &                 12.4 & $  0.33\deg \pm   0.04\deg$ & $  0.33\deg \pm   0.04\deg$ \\
+        2FGL J1615.2-5138    &                 76.2 &                 75.9 &                 89.4 &                     44.3 &                   47.6 &                 55.9 & $  0.42\deg \pm   0.03\deg$ & $  0.43\deg \pm   0.03\deg$ \\
+        2FGL J1632.4-4753c   &                126.9 &                128.3 &                120.4 &                     64.0 &                   64.8 &                 63.7 & $  0.44\deg \pm   0.04\deg$ & $  0.44\deg \pm   0.04\deg$ \\
+        2FGL J1837.3-0700c   &                 45.5 &                 47.0 &                 39.0 &                     18.6 &                   20.2 &                 16.6 & $  0.35\deg \pm   0.08\deg$ & $  0.35\deg \pm   0.07\deg$ \\
+        2FGL J2021.5+4026    &                236.5 &                225.3 &                240.5 &                    156.0 &                  139.4 &                148.8 & $  0.59\deg \pm   0.03\deg$ & $  0.60\deg \pm   0.03\deg$ \\
+      \end{tabular}
       \label{alt_diff_model_results}

### 2011-07-24 extended_catalog/paper/extended_catalog.tex
adding stefan's revisions

@@
 \newcommand{\tsinc}{\ensuremath{\text{TS}_\text{inc}}\xspace}
+\newcommand{\loglikelihood}{\ensuremath{LL}\xspace}
 
@@
 We present a new method for analyzing spatially extended sources with
-the Large Area Telescope (LAT), the primary science instrument
-on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
-series of Monte Carlo studies to validate this tool
-and calculate the LAT's detection threshold to spatially extended
-sources.  We then apply this tool to test all sources in the two
-year source catalog for extension. We present on the detection of
-ten spatially extended sources in addition to the twelve spatially
-extended sources reported in the second Fermi LAT Catalog.
+the Large Area Telescope (LAT), the primary science instrument on the
+{\em Fermi Gamma-ray Space Telescope (Fermi)}. Measuring the extension
+of a LAT source is important for uniquely identifying it.  We provide
+a series of Monte Carlo studies to validate this tool and calculate
+the LAT's detection threshold to spatially extended sources.  We then
+apply this tool to test all sources in the two year source catalog for
+extension. We present on the detection of ten spatially extended sources
+in addition to the twelve spatially extended sources reported in the
+second Fermi LAT Catalog.
 \end{abstract}
@@
 The Large Area Telescope (LAT) is a pair conversion telescope on the
-Fermi Gamma-Ray Space Telescope. It has been surveying the $\gamma$-ray
+Fermi Gamma-Ray Space Telescope (Fermi). It has been surveying the $\gamma$-ray
 sky since June 2008.  Fermi is well suited as a survey
@@
 Morphological studies of sources in the \gev energy range
-using the LAT are challenging because of the significantly energy
-dependent PSF and because of systematic errors in the galactic diffuse
+using the LAT are challenging because of the significantly 
+energy-dependent PSF and because of systematic errors in the galactic diffuse
 emission.  The LAT's PSF is determined at lower energies by multiple
@@
 fit the spectral parameters of the model. The extension fitting would
-have to be done as an external loop. Typically, the
-run time for a binned source analysis using \gtlike is several hours
-so this loop would be especially time consuming. What has typically
+have to be done as an external loop which would typically be
+too time consuming. What has typically
 been done to study an extended sources is to fix the position of the
@@
 the PSF changes significantly with energy, the spatial size of each bin
-is calculated to be smaller than than the PSF. By changing the spatial
+is chosen to be smaller than the PSF. By changing the spatial
 bin size with energy, \pointlike ensures that little information is lost
@@
 in the thin or thick layers of the tracker. Since the PSF is smaller for
-front entering photons, by binning each conversion type independently,
-\pointlike improves the overall sensitivity.  Furthermore, \pointlike
+photons which convert in the thin layers of the tracker,
+photons are also binned depending upon where they 
+convert in the tracker.
+Furthermore, \pointlike
 uses a sparse matrix representation of the spatial bins where only the
@@
 
-Finally, \pointlike is written mostly in the \python programming
-language and uses {\em numpy} and {\em scipy} to vectorize most of the
-calculations. This provides a reasonable trade off between computational
-efficiency and ease of development. By leaving the interface as a series
-of \python modules, advanced functions including extension fitting
-(section~\ref{extension_fitting}) and dual localization
-(section~\ref{dual_localization_method}) could be quickly
-built on top of the core functionality.
-
 \subsection{Extension Fitting}
@@
 
-We modified \pointlike to allow modeling the spatial extension 
-of a source. It is assumed that the spatial and spectral information
-completely decouple and that the spatial shape can be represented by a
-simple geometric function.  The code consistently convolves the extended
-source shape with the PSF (as a function of energy) when computing the
-model predicted counts.
-
-\pointlike uses the \minuit fitting library to maximize the likelihood
-by simultaneously fitting the position and extension of an extended
-source (\cite{minuit_documentation}).  As will be described in
-section~\ref{monte_carlo_validation}, this simultaneous fitting
-is necessary to correctly calculating the statistical significance
-of the detection of extension.
-For each position and extension,
-the spectral parameters of the sky model are refit. To avoid projection
-effects, what is directly fit is not the longitude and latitude of
-the source but instead the displacement in a rotated reference frame.
+In \pointlike, it is assumed that the spatial and spectral model
+of an extended source decouple and that the spatial shape can be
+represented by a two dimensional function.  To fit the extended source,
+\pointlike convolves the extended source shape with the PSF (as a
+function of energy) and uses the \minuit fitting library to maximize
+the likelihood by simultaneously fitting the position and extension
+of the source (\cite{minuit_documentation}).  As will be described in
+section~\ref{monte_carlo_validation}, simultaneously fitting the position
+and extension is necessary to correctly calculate the statistical
+significance of the detection of extension.  For each position and
+extension, the spectral parameters of the sky model are refit. To avoid
+projection effects, what is directly fit is not the longitude and latitude
+but instead the source's displacement in a rotated reference frame.
 
 The significance of the extension of a source can be calculated from
-\tsext, which is defined as twice the increase in log likelihood between
+\tsext, which is defined as twice the increase in log likelihood (\loglikelihood)
+between
 the extended source model at its best fit values and the point source
@@
 \begin{equation}
-  \tsext=2\log(LL_\text{ext}/LL_\text{ps}).
+  \tsext=2\log(\loglikelihood_\text{ext}/\loglikelihood_\text{ps}).
 \end{equation}
@@
 is shown schematically in figure~\ref{extension_profile} which shows
-the change in log likelihood when varying the extension of
+the change in \loglikelihood when varying the extension of
 the SNR IC443.
@@
 fit the sum and difference of the rotated
-coordinates $S=(x_1+x_2)/2$ and $D=(x_2-x_1)/2$.  The log likelihood
+coordinates $S=(x_1+x_2)/2$ and $D=(x_2-x_1)/2$.  The \loglikelihood
 is then maximized by fitting the sum and difference of the 
@@
 
-We define \tsinc as twice the increase in log likelihood
+We define \tsinc as twice the increase in \loglikelihood
 fitting the region as two point sources compared to fitting the region
@@
 \begin{equation}
-  \tsinc=2\times(LL_\text{2pts}-LL_\text{ps}).
+  \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
 \end{equation}
@@
 though the comparison of \tsext with \tsinc is not a calibrated test,
-we find the extreme cases $\tsinc \ll \tsext$ or $\tsinc\gg\tsext$
+we find the extreme cases $\tsinc \loglikelihood \tsext$ or $\tsinc\gg\tsext$
 to be suggestive and we only consider a source to be extended if
@@
 % 6 SNRs
-The largest population of extended source are SNRs. The six extended SNRs
-included in the catalog are IC443, W28, W30, W44, W51C, and the Cygnus
-Loop. These sources were first reported in (\cite{ic443,w28,w44,w51c}).
-Detailed papers reporting on W30 and the Cygnus Loop are still in
-preparation.  Using photons with energies greater than 1 \gev, our
-analysis significantly detected the extension of the SNRs IC443, W28,
-W30, W44, and W51C.
-
-Our analysis failed to correctly fit the extension of the Cygnus Loop.
-Publications describing the detailed analysis for the Cygnus Loop are
-still in preparation.  This is most likely because Cygnus Loop is rather
-large and its shell type morphology is not well represented by a uniform
-disk. The source is also rather soft so the published results used a
-larger energy range then our search.
+The largest population of extended source are SNRs. The six
+extended SNRs included in the second catalog are IC443, W28, W30,
+W44, W51C, and the Cygnus Loop. These sources were first reported in
+(\cite{ic443,w28,w44,w51c}).  Detailed papers studying W30 and the Cygnus
+Loop are still in preparation.  Using photons with energies between 1
+\gev and 100 \gev, our analysis significantly detected the extension
+of all six SNRs. Table~\ref{known_extended_sources} shows the best fit
+positions and extensions of these sources.
 
@@
 % 3 PWN
-Three pulsar wind nebula Vela X, MSH 15-52, and HESS J1825-137 
-were included in the second catalog (\cite{velax,msh1552,fermi_hess_j1825}).
-
-Our analysis failed to detect the extension of Vela X. Vela X can only be
-successfully analyzed after applying a phase cut to removed the heavily
-dominant pulsar emission. It is beyond the scope of the paper to perform
-such specialized analysis.
-
-Using photons with energy above 10 \gev, we significantly detected
-the extension of HESS J1825-137.
-Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
-consistent with the published result, but with $\tsext=11.2$. This is
-most likely because the published analysis used a larger energy range,
-considering all events above 6 \gev. Looking at all photons with
-energy above 1 \gev 
-is problematic because of background source confusion whereas using photons
-with energy above 10 \gev does not have the statistics for a significant detection.
-
-\todo[inline]{note about how MSH 15-52 and Vela X were hard
-to analysze without phase cuts.}
+Three pulsar wind nebula Vela X, MSH 15-52, and HESS J1825-137 were
+included in the second catalog (\cite{velax,msh1552,fermi_hess_j1825}).
+Using photons with energy above 10 \gev, we significantly detected the
+extension of HESS J1825-137.  To improve our model of this source, we
+removed the nearby catalog source 2FGL J1823.1-1338c which is part of the
+extended emission of HESS J1825-137.  Using photons with energies above
+10 \gev, we fit the extension of MSH 15-52 consistent with the published
+result at an extension significance of \tsext=9.5.  Our analysis was
+unable to resolve Vela X. An analysis of this source requires removing on
+pulse events from the Vela pulsar and is beyond the scope of this paper.
+
+\todo[inline]{note about how MSH 15-52 can't go lower in
+energy because of nearby pulsar.}
 
@@
 % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
+% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
+
 % 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 
@@
 % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
 % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
@@
 % Modify:
-% * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.232,0.517,SkyDir.GALACTIC))
+% * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.235,0.493,SkyDir.GALACTIC))
 %              (initial Position - SkyDir(265.5705,-0.0099)
-% * P72Y1310 - 2FGL J0901.7-4655 - SkyDir(267.311,-0.190,SkyDir.GALACTIC)
+% * P72Y1310 - 2FGL J0901.7-4655 - SkyDir(267.575,-0.191,SkyDir.GALACTIC)
 %              (initial Position - SkyDir(267.79,-0.3339)
@@
 2FGL J0851.7-4635 until the fit globally converged.  2FGL J0854.7-4501
-moved to $(l,b)=(266.232\deg,0.517\deg)$ and 2FGL J0901.7-4655 moved to
-$(l,b)=(267.311\deg,-0.190\deg)$. In addition, we removed the further away
+moved to $(l,b)=(266.24\deg,0.49\deg)$ and 2FGL J0901.7-4655 moved to
+$(l,b)=(267.58\deg,-0.19\deg)$. In addition, we removed the further away
 catalog source 2FGL J0858.0-4815 because it was not significant above 10
@@
 
-This source is less than 1\deg away from 2FGL J1615.0-5051 which is
+This source is less than 1\deg away from 2FGL J1615.2-5138 which is
 also spatially extended (see section~\ref{section_2FGL_J1615.2-5138}).
-To get a good fit of both sources, we had to model both sources as being
-spatially extended and iteratively fit the position and extension of each
-source until obtaining a global best fit.  Before doing this, We removed
-from our model the three nearby catalog sources 2FGL J1620.6-5111c, 2FGL
-J1619.7-5040c, and 2FGL J1622.8-5006 2FGL J1615.0-5051 because they were
-not significant above 10 \gev.  These modifications are further described
-in the caption to figure~\ref{1FGL_J1613.6-5100c}.  After modifying
-the region, we found that \tsinc=12.2 which is less than \tsext so we
-conclude that the source is extended.
+To get a good fit of both sources, we had to model both sources as
+being spatially extended and iteratively fit the position and extension
+of each source until obtaining a global best fit.  Before doing this,
+We removed from our model the source 2FGL J1614.9-5212 because it is
+part of 2FGL J1615.2-5138's extended emission. Furthermore, we removed
+the nearby catalog sources 2FGL J1619.7-5040c and 2FGL J1620.6-5111c
+because they were not significant above 10 \gev.  These modifications
+are further described in the caption to figure~\ref{1FGL_J1613.6-5100c}.
+After modifying the region, we found that \tsinc=12.2 which is less than
+\tsext so we conclude that the source is extended.
 
@@
 J1616-508 (\cite{HESS_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
-contours of HESS J1616-508 are overlaid on 2FGL J1615.0-5051.  The
-H.E.S.S. experiment measured an extension $\sigma$ of $0.23\pm0.02$ and
-$0.15\pm0.02$ along the semi-major and semi-minor axes respectively when
-fitting the source with an elliptical Gaussian spatial model.  This size
-corresponds to a 68\% source containment radius of $\rsixeight\sim0.22\deg$
-to $0.34\deg$. This size matches very well with the LAT size
+contours of HESS J1616-508 are overlaid on 2FGL J1615.0-5051.
+The H.E.S.S. experiment measured an extension $0.136\pm 0.008$
+when fitting the source with an elliptical Gaussian spatial model.
+This size corresponds to a 68\% source containment radius of
+$\rsixeight\sim0.21\deg\pm0.01$. This size is comparable to the LAT size
 $\rsixeight=0.27\deg\pm0.03$ (see section~\ref{compare_source_size}).
@@
 
-This source is spatially coincident with the extended \tev source
-HESS J1614-518 (\cite{HESS_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
-contours of HESS J1614-518 are overlaid on 2FGL J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian extension of
-$\sigma=0.156\deg\pm0.008\deg$. This size corresponds to a 68\% source
-containment radius of $\rsixeight\sim0.33\pm0.01\deg$.  This size matches
-very well with the LAT size of $\rsixeight\sim0.34\pm0.02$.
+This source is spatially coincident with the extended \tev source HESS
+J1614-518 (\cite{HESS_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
+contours of HESS J1614-518 are overlaid on 2FGL J1615.2-5138.
+The H.E.S.S. experiment measured a Gaussian extension of
+$\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$ in the semi-major
+and semi-minor axis. This size corresponds to a 68\% containment size
+of $\rsixeight=0.35\pm0.03\deg$ and $0.23\pm0.03$.  This elliptical size
+matches well the LAT size of $\rsixeight\sim0.34\pm0.02$.
 
@@
 region as one extended source to the likelihood fitting this region as
-two point sources. We found $\tsinc=40.9\ll\tsext$ which is less than \tsext
+two point sources. We found $\tsinc=40.9\loglikelihood\tsext$ which is less than \tsext
 so we conclude that this is an extended source.
@@
 
-This source is spatially coincident with the \tev source HESS J1837-069 (\cite{HESS_plane_survey}).
-In figure~\ref{1FGL_J1837.5-0659c}, contours of 
-are H.E.S.S J1837-069 are overlaid on 
-2FGL J1837.3-0700c. H.E.S.S. measured an extension of
-$\sigma=0.12\pm0.02$ and $0.05\pm0.02$ along the semi-major and 
-semi-minor axis when fitting the source
-with an elliptical Gaussian spatial model.
-This corresponds to a 68\% containment radius of $\rsixeight=0.18\pm0.03$ and $0.08\pm0.03$ 
-along the semi-major and semi-minor axis. The size is comparable to LAT 
-which fit a 68\% containment radius of
-$\rsixeight=0.29\pm0.07$.
-The LAT size is larger than the H.E.S.S. size but the sizes are almost almost within
-the $1\sigma$ errors. It is possible that the morphologies are different but
-this is not very significant.
-A possible reason is confusion could be that the LAT source may be partially
-fitting other sources in the region.
+This source is spatially coincident with the \tev source HESS J1837-069
+(\cite{HESS_plane_survey}).  In figure~\ref{1FGL_J1837.5-0659c},
+contours of are H.E.S.S J1837-069 are overlaid on 2FGL
+J1837.3-0700c. H.E.S.S. measured an extension of $\sigma=0.12\pm0.02$
+and $0.05\pm0.02$ along the semi-major and semi-minor axis when fitting
+the source with an elliptical Gaussian spatial model.  This corresponds to
+a 68\% containment radius of $\rsixeight=0.18\pm0.03$ and $0.08\pm0.03$
+along the semi-major and semi-minor axis. The size is comparable to
+LAT which fit a 68\% containment radius of $\rsixeight=0.29\pm0.07$.
+The LAT size is larger than the H.E.S.S. size but the sizes are almost
+almost within the $1\sigma$ errors. It is possible that the morphologies
+are different but this is not very significant.  A possible reason is
+confusion could be that the LAT source may be partially fitting other
+sources in the region.
 
@@
 
-This is RX J1713.7-2946. This analysis not finished.
-
-Recent LAT publication: \cite{rx_j1713_lat}.
-
-Contours taken from HESS Paper: \cite{rx_j1713_hess}
-
-The Figure is \ref{2FGL_J1712.4-3941}
+The two year catalog source 2FGL J1712.4-3941 was found to be
+spatially extended using photons with energies between 10 \gev and
+100 \gev. The source is coincident with the one year catalog source
+1FGL J1711.7-3944c. We fit an extension of $0.56\deg\pm0\pm04$ with an
+extension significance of $\tsext=41.2$. This source was fit to a position
+of $(l,b)=(347.25\deg,-0.54\deg)$. Figure \ref{2FGL_J1712.4-3941} shows
+a smoothed counts map of this source.
+
+This source is spatially conincident with the SNR RX J1713.7-2946 and was
+recently reported by (\cite{rx_j1713_lat}).  To analyze this source,
+we used the same background model as the recent LAT publication.
+2FGL J1715.4-4024c is spatially coincident with Source A and was
+moved to the published location of $(ra,dec)=(258.84,-40.46)$. Source
+B was added at $(ra,dec)=(258.71,-38.70)$ and Source C was added at
+$(ra,dec)=(257.47,-39.75)$.  Figure \ref{2FGL_J1712.4-3941} shows
+the position of these nearby sources on top of a contour of SNR RX
+J1713.7-2946 seen in \tev by H.E.S.S (\cite{rx_j1713_hess}).
 
@@
 high energy sky. Hard to do a blind analysis of LAT data.
+
+\todo[inline]{Describe comparison of \gev and \tev extensions from figure~\ref{gev_vs_tev_histogram}}
 
@@
     calculated by varying the extension away from its best fit value until
-    the log likelihood has changed by a particular amount.  These profiles are
+    the \loglikelihood has changed by a particular amount.  These profiles are
     generated for all extended source candidates. They are useful
@@
         W51C                 &      49.12\deg &      -0.44\deg & $  0.28\deg \pm   0.02\deg$ &     2174.7 &       87.6 &  0.010\deg &  0.010\deg &   59.4\deg & $   41.6 \pm     1.3$ & $   2.38 \pm    0.04$ \\
+        Cygnus Loop          &      74.20\deg &      -8.51\deg & $  1.74\deg \pm   0.06\deg$ &      206.2 &      164.1 &  0.096\deg &  0.063\deg &  -69.0\deg & $    8.7 \pm     0.7$ & $   2.55 \pm    0.15$ \\
         \hline
@@
       \end{tabular}
-      \caption{The fit results for the already known extended sources that
-      were found by our analysis. The top results were found using an
-      energy range between 1 \gev and 100 \gev.  The lower analysis
-      was done using photons between 10 \gev and 100 \gev.  The quoted
-      flux is in units of $10^{-9}\ph/\cm^2/\sec$ and is the flux in the
-      fit energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
-      All sources were fit using a uniform disk spatial template. The
-      localization and extension were found using \pointlike while the
-      TS and spectral values were calculated using \gtlike.  The TS value
-      was computed using the assumed disk morphology and \tsext compares
-      is the increase in \ts fitting the source with an extended spatial
-      model instead of a point model.  \glon and \glat are respectively
+      \caption{The fit for ten of the twelve extended sources included
+      in the second LAT catalog.  The top list are the extended sources
+      analyzed using photons with energies between 1 \gev and 100 \gev.
+      The lower table are the sources analyzed using photons with energies
+      between 10 \gev and 100 \gev.  The quoted flux is in units of
+      $10^{-9}\ph/\cm^2/\sec$ and is the flux in the fit energy range
+      (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).  All sources
+      were fit using a uniform disk spatial template. The localization
+      and extension were found using \pointlike while the TS and spectral
+      values were calculated using \gtlike.  The TS value was computed
+      assumgni the best fit uniform disk spatial model and \tsext
+      compares the increase in \ts fitting the source with an extended
+      spatial model to point model.  \glon and \glat are respectively
       the galactic longitude and galactic latitude of the source and
-      $\sigma$ is the edge of the uniform disk spatial model that was fit
-      to the source.  The Centaurus A Lobes, the Cygnus Loop, and Vela
-      X were not found to be extended by this too. The
-      reasons for this are discussed in section~\ref{validate_known}.
+      $\sigma$ is the edge of the best fit uniform disk spatial model.
+      The extended PWN Vela X is not include in this list because a phase
+      cut would be required to remove the Vela pulsar (\cite{velax}).
+      The extended Centaurus A lobes are not included because a radially
+      symmetric uniform disk spatial model is a bad match to the observed
+      emission (\cite{cen_a_lat}).  More information about these sources is
+      in section~\ref{validate_known}.
       }
@@
       2FGL J1554.4-5317c   &     328.12\deg &       0.26\deg & $  0.52\deg \pm   0.04\deg$ &      150.8 &       37.6 &  0.044\deg &  0.039\deg &   55.5\deg & $   16.7 \pm     1.5$ & $   2.30 \pm    0.11$ \\
+      2FGL J1712.4-3941    &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg$ &       77.6 &       41.2 &  0.055\deg &  0.043\deg &  -14.8\deg & $    4.3 \pm     0.9$ & $   1.48 \pm    0.12$ \\
       \hline
@@
   \begin{center}
-    \includegraphics{source_plots/allsky_extended_sources.pdf}
+    \includegraphics{summary_plots/allsky_extended_sources.pdf}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v1/run.py
@@
 \clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{summary_plots/gev_vs_tev_histogram.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v1/extension_histogram.py
+    \end{center}
+    \caption{
+    A comparison of the size of detected \tev and \gev sources.
+    The extension of the 22 extended LAT sources comes from
+    table~\ref{known_extended_sources}, table~\ref{new_ext_srcs_table},
+    and the LAT extension of Vela X is taken from (\cite{velax}). The
+    Centarus A lobes, which have an extension $~10\deg$, are not
+    included in the plot (\cite{cen_a_lat}).  The \tev extension of
+    the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
+    Catalog (\cite{hesscat}).  Because the \gev sources were fit
+    with a uniform disk spatial model whereas the \tev sources were
+    fit with a Gaussian spatial model, the histogram is of \rsixeight
+    (see section~\ref{compare_source_size}).  On the other hand, because
+    of their size, the \tev size of RX J1713.7-2946 and Vela Jr. were
+    obtained by a fit of a Gaussian spatial model so the \gev and \tev
+    sizes of these sources were not converted.
+    }\label{gev_vs_tev_histogram}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{summary_plots/gev_vs_tev_plot.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v1/run.py
+    \end{center}
+    \caption{
+    }\label{gev_vs_tev_plot}
+  \end{figure}
+
+\clearpage
 \begin{sidewaystable}
@@
         2FGL J1554.4-5317c   &        9.2 &       37.6 &     328.30\deg &       0.31\deg & $      10.3 \pm        1.2$ & $  2.7 \pm   0.5$  &     328.27\deg &      -0.07\deg & $       0.9 \pm        0.6$ & $  1.6 \pm   0.4$ \\
+        2FGL J1712.4-3941    &        6.6 &       41.2 &     347.28\deg &      -0.07\deg & $       0.2 \pm        0.1$ & $  0.6 \pm   0.5$  &     347.22\deg &      -0.26\deg & $       2.5 \pm        0.7$ & $  1.9 \pm   0.2$ \\
         \hline
@@
   extended source.  This source is spatially coincident with the Puppis
-  A SNR. The green contours are an X-ray image of Puppis A observed by
+  A SNR. The light blue contours are an X-ray image of Puppis A observed by
   ROSAT (\cite{rosat_puppis_a}). There is good spatial overlap between
@@
   uniform disk spatial model.  The black cross is the background source
-  2FGL J1625.7-2526.  The green contours are a 100 micrometer infrared
+  2FGL J1625.7-2526.  The light blue contours are a 100 micrometer infrared
   image of the region as seen by IRAS (\cite{iras_rho_ophiuci}). This
@@
   extended source is spatially coincident with the Vela Jr SNR.
-  The green contours are the \tev emission of Vela Jr. observed by
+  The light blue contours are the \tev emission of Vela Jr. observed by
   H.E.S.S (\cite{vela_jr_hess}).  More information about this source 
@@
     stars and circles are the best fit positions and extensions
-    of these sources assuming uniform disk spatial model.  To fit these
-    sources, we had to remove 
-    the sources 2FGL J1619.7-5040c, 2FGL J1620.6-5111c, and 2FGL
-    J1622.8-5006 because they were not significant above 10\gev. Two
-    of these sources are on the left side of the plot and one is
-    outside the region.  The green contours are the \tev emission of
+    of these sources assuming uniform disk spatial model.  The green star
+    inside of the extension of 2FGL J1615.2-5138  is 2FGL J1614.9-5212
+    which was removed because it is part of the extended emission.
+    The greeen stars to the left are 2FGL J1619.7-5040c and 2FGL
+    J1620.6-5111c which were removed because they were not significant
+    above 10\gev. These are shown as green stars.  The light blue contours
+    are the \tev emission of
     the extended source HESS J1614-518 and the extended source HESS
@@
   above 10 \gev.  This extended source is spatially coincident
-  with the extended H.E.S.S source HESS J1634-472.  The green
+  with the extended H.E.S.S source HESS J1634-472.  The light blue
   contours are the \tev emission seen by H.E.S.S. 
@@
   10 \gev.  This source is spatially coincident with the \tev source HESS
-  J1837-069.  The green contours are the \tev emission of HESS J1837-069
+  J1837-069.  The light blue contours are the \tev emission of HESS J1837-069
   observed by H.E.S.S (\cite{HESS_plane_survey}).  More information about
@@
   \begin{center}
-    %\includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946.pdf}
-    \missingfigure{This analysis is not finished}
-  \end{center}
-  \caption{
-  This is RX J1713.7-2946. This analysis not finished.
-  The 2FGL source is 2FGL J1712.4-3941.
-  More information about this source can be found in section~\ref{section_2FGL_J1712.4-3941}.
-Contours taken from HESS Paper: \cite{rx_j1713_hess}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946}
+    % this plot came from
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
+  \end{center}
+  \caption{A galactic and isotropic diffuse subtracted 1 \gev to 100
+  \gev counts map of the region around 2FGL J1712.4-3941 smoothed by a
+  0.25\deg Gaussian kernel.  This source is spatially coincident with
+  RX J1713.7-2946 was was recently reported by (\cite{rx_j1713_lat}).
+  The light blue contours are the \tev emission reported by
+  H.E.S.S. (\cite{rx_j1713_hess}).  The region was analyzed with the
+  same background model as (\cite{rx_j1713_lat}).  Source A (blue cross)
+  is spatially coincident with 2FGL J1715.4-4024c (blue star) so 2FGL
+  J1715.4-4024c was moved to the position of source A.  The grey crosses
+  represent from left to right the position of source B and C which were
+  added to the background model. Plot (a) has the diffuse emisission model
+  subtracted and plot (b) has the diffuse emission and all background
+  sources also subtracted.
   }\label{2FGL_J1712.4-3941}
@@
   to the region. 2FGL J2021.5+4026 is spatially coincident with the
-  Gamma Cygni SNR.  The green contours are a 408MHz image of Gamma Cygni
+  Gamma Cygni SNR.  The light blue contours are a 408MHz image of Gamma Cygni
   observed by the Canadian Galactic Plane Survey.  More information about

### 2011-07-25 extended_catalog/paper/extended_catalog.tex
lots of improvements

@@
 apply this tool to test all sources in the two year source catalog for
-extension. We present on the detection of ten spatially extended sources
+extension. We present on the detection of nine spatially extended sources
 in addition to the twelve spatially extended sources reported in the
-second Fermi LAT Catalog.
+second Fermi LAT Catalog (2FGL).
 \end{abstract}
@@
 
-Using one year of all sky surveying data, the LAT published a catalog of
-source that were significantly detected.  Many of these were associated
-with a variety of source classes including active galactic nuclei,
+Using two years of all sky surveying data, the LAT Collaboration
+published a catalog of 1873 \gev sources.
+Many of these were associated
+with a variety of source classes including Active Galactic Nuclei (AGN),
 pulsars, galaxies, and supernova remnants.  Many of these classes can be
@@
 
-The LAT collaboration has previously reported on the discovered
-a variety of spatially extended including the supernova remnants (SNRs)
-IC443 and W51C (\cite{ic443,w51c}),
-the pulsar wind nebulae (PWNe) MSH 15-52 and Vela X
-(\cite{msh1552,velax}), and the Large Magellanic
-and the Small Magalenic Cloud (\cite{lmc,smc}).  There are other
-source classes which could possibly be spatially resolved by the LAT
-including galaxy clusters, dark matter, and possibly new physics.
+The LAT collaboration has previously reported on the discovered of
+five spatially extended supernova remnants (SNRs) IC443, W28, W44,
+W51C, and RX J1713.7-2946 (\cite{ic443,w28,w44,w51c,rx_j1713_lat}).
+The LAT Collaboration has reported on the detection of three extended
+pulsar wind nebulae (PWNe) MSH 15-52 and Vela X, and HESS J1825-137
+(\cite{msh1552,velax,fermi_hess_j1825}), the Large Magellanic
+and Small Magalenic Cloud (\cite{lmc,smc}), and the radio galaxy
+Centarus A (\cite{cen_a_lat}) .  There are other source classes which
+could possibly be spatially resolved by the LAT including galaxy clusters
+and dark matter satellite galaxies.
 
 Furthermore, a variety of spatially extended but otherwise unassociated
-sources have been detected in the galactic plane at \tev energies using
-Air Cherenkov detectors. Most prominent was a survey of the galactic plane
-using the High Energy Stereoscopic System (H.E.S.S) which discovered 14
-spatially extended sources (\cite{HESS_plane_survey}).
+sources have been detected in the Galactic plane at \tev energies using
+Air Cherenkov detectors. Most prominent was a survey of the Galactic
+plane using the High Energy Stereoscopic System (H.E.S.S) which presented
+14 spatially extended sources (\cite{hess_plane_survey}) sources with
+extensions varying from $~0.1\deg$ to $~0.25\deg$. Most \tev sources
+in the galaxy are spatially extended and it is expected that these same
+sources would have have extended \gev emission.
 
@@
 of the sky and removing excess residuals.  These residuals manifested
-themselves in the one year catalog as spurious point sources in the
-region region surrounding the Large Magellanic Cloud (\cite{first_cat}).
+themselves in 1FGL as spurious point sources in the region region
+surrounding the Large Magellanic Cloud (\cite{first_cat}).  For this
+reason, we are motivated to take the 1873 sources that were detected in
+2FGL and apply a search for those sources which are spatially extended.
 
@@
 using the LAT are challenging because of the significantly 
-energy-dependent PSF and because of systematic errors in the galactic diffuse
+energy-dependent PSF and because of systematic errors in the Galactic diffuse
 emission.  The LAT's PSF is determined at lower energies by multiple
@@
 significance of the detection.  Furthermore since this approach is
-computationally intensive, no large scale Monte Carlo effort can
+computationally intensive, no large-scale Monte Carlo effort can
 be run to validate it.
 
-We developed an alternate approach to fit spatially extended
+We developed an alternative approach to fit spatially extended
 sources. A separate maximum likelihood fitting package called
@@
 added to it the ability to analyze spatially extended sources. \pointlike
-is described in the one year catalog paper and in Matthew Kerr's Ph.D thesis
+is described in 1FGL and in Matthew Kerr's Ph.D thesis
 (\cite{first_cat,matthew_kerr_thesis}).
@@
 \end{equation}
-For the LAT, the PSF is parameterized as
+For the LAT, the PSF is parameterized by a {\em King function}
 \begin{equation}
@@
 \end{equation}
-where $\sigma$ and $\gamma$ are free parameters.  For radially symmetric
-extended sources, the angular part of the integral can be done analytically
+where $\sigma$ and $\gamma$ are free parameters
+(\cite{matthew_kerr_thesis}).  For radially symmetric extended sources,
+the angular part of the integral can be done analytically
 \begin{equation}
@@
 small.
+
+There will always be a small numerical discrepancy between the PSF and
+a very small extended source due to numerical error in the convolution.
+In most situations, this error would be insignificant. But when testing
+a source for extension, this offset can significantly bias the estimate
+of the significance of the extension of a source.  To correct for this,
+when testing a source for extension we compare the likelihood fitting
+the source with an extended shape to the likelihood fitting it with its
+extension fixed to ${10^{-10}}\deg$.
 
@@
 We found that the {\em HESSE} errors on the extension of a source
-were sometimes badly estimated.  On the other
-hand, the {\em Simplex} algorithm was prohibitively slow and would often
-fail to convergence. Our approach to calculating extension errors
-is to fix the position of the source and varying just the extension
-using the {\em Simplex} algorithm.  This approach
-makes the approximation that the covariance between each spatial parameter
-is small but not that the likelihood is Gaussian. This method 
-is shown schematically in figure~\ref{extension_profile} which shows
-the change in \loglikelihood when varying the extension of
-the SNR IC443.
-The localization error separately calculated by fixing the extension to the
-best fit value and fitting an ellipse to the likelihood as a function
-of the spatial parameters. This
-elliptical localization error correctly accounts for the covariance
-in the position of the source and this same me method is used to
-calculate the localization error of all point sources in the first LAT catalog
-(\cite{first_cat}).
-
-\subsection{Gtlike Crosscheck}
+were sometimes badly estimated.  On the other hand, the {\em Simplex}
+algorithm was prohibitively slow and would often fail to convergence. Our
+approach to calculating extension errors is to fix the position of the
+source and varying just the extension using the {\em Simplex} algorithm.
+This approach makes the approximation that the covariance between each
+spatial parameter is small but not that the likelihood is Gaussian. This
+method is shown schematically in figure~\ref{extension_profile} which
+shows the change in \loglikelihood when varying the extension of the
+SNR IC443.  The localization error is separately calculated by fixing
+the extension and spectrum of the source and fitting a parabola to the
+likelihood as a function of position.
+
+\subsection{\gtlike Crosscheck}
 \label{gtlike_crosscheck}
 
-\pointlike is important for LAT analysis
-that require many iterations such as source localization and extension
-fitting.  On the other hand, we expect that the spectral parameters
-fit by \gtlike to be slightly more precise.
-Furthermore, because \gtlike is the standard likelihood analysis package,
-it has been more extensively validated for spectral analysis.
-For that reason, in the following analysis we took the best fit
-position and extension found by \pointlike and
-refit the spectral spectral parameters using \gtlike.
-\gtlike also provides a second calculation of the likelihood which gives a
-second measure of \ts and \tsext. We do not consider a source to be
-significant unless there is agreement between the two methods.
-
-We found good agreement between the two methods. For the new
-extended source candidates, table~\ref{alt_diff_model_results} shows
-a comparison of \ts and \tsext computed using \pointlike and \gtlike.
+\pointlike is important for LAT analysis that require many iterations
+such as source localization and extension fitting.  On the other hand,
+because of the fewer approximations used in calculating the likelihood
+we expect that the spectral parameters fit by \gtlike to be slightly
+more precise.  Furthermore, because \gtlike is the standard likelihood
+analysis package, it has been more extensively validated for spectral
+analysis.  For that reason, in the following analysis  we use \pointlike
+to determinate the position and extension of a source and then determine
+the spectrum using \gtlike. Both \gtlike and \pointlike can estimate
+the statistical significance of the extension of a source and we require
+that both methods agree to claim a detection.
+
+We found good agreement between the two methods. For the new extended
+source candidates, table~\ref{alt_diff_model_results} will shows a
+comparison of \ts and \tsext computed using \pointlike and \gtlike.
 Unless explicitly mentioned, all \ts, \tsext, and spectral parameters
@@
 point sources.  To assess the possibility of source confusion,
-we developed a function in \pointlike to simultaneously fit 
-the position of two point sources.
-The code uses \minuit to fit the position of the two point
-sources.  To avoid projection effects, the fit is done in a rotated coordinate
-system.  To improve the robustness of the fit, Instead of directly fitting
-the rotated coordinates $x_1$ and $x_2$ we instead
-fit the sum and difference of the rotated
-coordinates $S=(x_1+x_2)/2$ and $D=(x_2-x_1)/2$.  The \loglikelihood
-is then maximized by fitting the sum and difference of the 
-sources.  Because of \pointlike's computational efficiency, this algorithm
-runs in a reasonable amount of time.
-
-We define \tsinc as twice the increase in \loglikelihood
-fitting the region as two point sources compared to fitting the region
-as one point source:
-\begin{equation}
+we developed a function in \pointlike to simultaneously fit the position
+of two point sources.  To improve the robustness of the fit, the sum and
+difference of the positions of the two sources are fit in a coordinates
+rotated to the equator.  The \loglikelihood is then maximized by fitting
+the sum and difference of the positions.
+
+We define \tsinc as twice the increase in \loglikelihood fitting the
+region as two point sources compared to fitting the region as one point
+source: \begin{equation}
   \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
-\end{equation}
-\tsinc can not be directly compared to \tsext to see which model is 
-more significant
-because the models are not nested (\cite{statistics_with_care}). Even
-though the comparison of \tsext with \tsinc is not a calibrated test,
-we find the extreme cases $\tsinc \loglikelihood \tsext$ or $\tsinc\gg\tsext$
-to be suggestive and we only consider a source to be extended if
-$\tsext>\tsinc$.
+\end{equation} \tsinc can not be directly compared to \tsext to see
+which model is more significant because the models are not nested
+(\cite{statistics_with_care}). Even though the comparison of \tsext
+with \tsinc is not a calibrated test, we find the extreme cases $\tsinc
+\loglikelihood \tsext$ or $\tsinc\gg\tsext$ to be suggestive and we only
+consider a source to be extended if $\tsext>\tsinc$.
 
@@
 the spectrum of the two point sources can be refit using \gtlike.
-we quote the spectral values obtained from \gtlike using the best fit positions
-found using \pointlike.  For the extended candidates found by our search,
-we computed both \tsext and \tsinc.  The results are presented in
-table~\ref{dual_localization_results}.
+we quote the spectral values obtained from \gtlike using the best fit
+positions found using \pointlike.  For the extended candidates found
+by our search, we computed both \tsext and \tsinc.  The results will be
+presented in table~\ref{dual_localization_results}.
 
@@
 
-The spatial shape of extended sources can e modeled
+The spatial shape of extended sources can be modeled
 as a two dimensional Gaussian
-\begin{equation}
+\begin{equation}\label{gauss_pdf}
   \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
@@
 or a uniform disk
-\begin{equation}
+\begin{equation}\label{disk_pdf}
   \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
 \end{equation}
-Although these shapes are significantly different, the convolution
-of them with the PSF for typical sizes look similar.  Even
-though these shapes are significantly different, we demonstrate in
-figure~\ref{compare_disk_gauss} that the convolution of shows the
-PSF that would be observed for a power-law source of spectral index
-2, the probability density function (PDF) for a Gaussian and uniform
-disk of width $0.5\deg$, and the convolution of this PDF with the PSF.
-The figure shows the convolution for the PSF in the energy range between
-1 \gev and 100 \gev and also in the energy range between 10 \gev and
-100 \gev.  The convolved shapes do separate better at higher energy, but
-nevertheless this plot shows that we are not very sensitive to probing
-the exact structure of an extended source.  In this paper we always
-assume a uniform disk spatial model.
+Although these shapes are significantly different, the convolution of them
+with the PSF look similar.  Figure~\ref{compare_disk_gauss} demonstrates
+this by showing the PSF, PDF, and convolution of the PDF with the PSF
+for a uniform disk and Gaussian spatial model of size 0.5\deg.  This plot
+shows that we are not very sensitive to probing the exact structure of an
+extended source.  In the following we assume a uniform disk spatial model.
 
 To get the convolved shapes to match in figure~\ref{compare_disk_gauss},
-we had to set them to predict the same 68\% containment radius of 0.5\deg.  The
-68\% containment radius for a spatial model is the radius at which 68\%
-of the intensity is enclosed.  It can be computed by a straightforward
-integral and we find that $\rsixeight_\text{,disk}=0.82\sigma$ whereas the
-$\rsixeight_\text{,Gaussian}=1.51\sigma$.  Since $\rsixeight=0.5\deg$,
-the uniform disk has $\sigma=0.41\deg$ whereas the Gaussian has
+we had to set them to predict the same 68\% containment
+radius of 0.5\deg.  The 68\% containment radius for a
+spatial model is the radius at which 68\% of the intensity is
+enclosed.  It can be computed by a straightforward integral
+and we find that $\rsixeight_\text{,Gaussian}=1.51\sigma$
+whereas $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
+is defined in equation~\ref{disk_pdf} for the Gaussian source and
+equation~\ref{gauss_pdf} for the disk source.  Since $\rsixeight=0.5\deg$,
+the uniform disk has $\sigma=0.41\deg$ and the Gaussian has
 $\sigma=0.75\deg$.
@@
 which a counts map of an extended source simulated in the energy
-range from 1 \gev to 100 \gev with a uniform disk spatial model and
-$\sigma=05$. Overlaid on the plot is the fit extension assuming the
-source has a uniform disk and a Gaussian spatial model. The plot overlays
-both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly larger for
-the disk spatial hypothesis compared to the Gaussian spatial model. On
-the other hand, the disk and Gaussian's 68\% containment radius are
-similar.
+range from 1 \gev to 100 \gev with a uniform disk spatial model with
+an extension $\sigma$ of 0.5. Overlaid on the plot is the fit extension
+assuming the source has a uniform disk and a Gaussian spatial model. The
+plot overlays both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly
+larger for the disk spatial hypothesis compared to the Gaussian spatial
+model. On the other hand, the disk and Gaussian's 68\% containment radius
+are similar.
 
@@
 extended source, there is no correct choice for which size to quote
-or which shape to overlay. For the following analysis, we quite the
+or which shape to overlay. For the following analysis, we quote the
 disk's edge and overlay this size.  But due to smearing of the PSF,
@@
 significantly extended.  Since an extended source has one additional
-degree of freedom, Wilks' Theorem says that the distribution of $\tsext$
+degree of freedom, Wilks' Theorem predicts that the distribution of $\tsext$
 when testing a point source for extension should follow a $\chi^2_1$
@@
 
-On the other hand, since the null hypothesis rests on the edge of
+However, since the null hypothesis rests on the edge of
 parameter space when the extension is 0, Wilks' Theorem does not hold
@@
 indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
-to represent the types of sources detectable by the LAT.  The point
+to represent typical source paramters in LAT-detected sources. The point
 sources were simulated on top of an isotropic power-law background
@@
 to fit it as both a point and extended source and calculate \tsext and
-we only dept the sources which had a significant point source detection
+we only kept the sources which had a significant point source detection
 ($\ts>25$).
-
-Before we present the results of the Monte Carlo simulations, we note
-that despite out best efforts, there was always a small numerical
-discrepancy between the likelihood when fitting the source as the PSF
-and when fitting it as a very small extended source. This is due to
-numerical error introduced by the convolution.  In most situations, this
-error would be insignificant. But when testing a source for extension,
-this offset significantly bias the distribution of \tsext in the null
-hypothesis. To correct for this, instead of computing the likelihood in
-the null hypothesis by fitting the PSF, we instead calculated \tsext by
-fitting the sources as an extended source and as an extended source with
-its extension fixed to ${10^{-10}}\deg$.
 
@@
 to extension is defined as the flux at which the average
-value of $\tsext$ is $\langle\ts\rangle=25$. As was seen in
+value of $\tsext$ is $\langle\tsext\rangle=25$. As was seen in
 section~\ref{monte_carlo_validation}, this corresponds to an extension
@@
 the PSF.  Small sources would look too much like the PSF and larger
-sources would get lost in the background.
+sources would get lost in the background due to low surface brightness.
 
@@
 to $2.0\deg$.  The curves on the plot represent the flux for a given
-extension where $\langle\tsext=25\rangle$.  The plot shows the threshold
-using photons with energies between 100 \mev and 100 \gev and the
-threshold using only photons with energies between 1 \gev and 100 \gev.
+extension where $\langle\tsext\rangle=25$. 
 This results shows that the LAT's threshold to extension is better for
@@
 
-Except for the hardest and largest sources, our detection threshold
-is almost unchanged when using events between 100 \mev and 1 \gev.
-This is also demonstrated in figure~\ref{ts_ext_vs_energy} which shows
-the \tsext for the SNR IC443 computed independently in 12 energy bins between 100 \mev and
+Figure~\ref{index_sensitivity} shows the threshold using photons with
+energies between 100 \mev and 100 \gev and also only using photons
+with energies between 1 \gev and 100 \gev.  Except for the hardest
+and largest sources, our detection threshold is almost unchanged when
+including photons with energies between 100 \mev and 1 \gev.  This is also
+demonstrated in figure~\ref{ts_ext_vs_energy} which shows \tsext for the
+SNR IC443 computed independently in twelve energy bins between 100 \mev and
 100 \gev. For IC443, which has a spectral index ~2.4, almost the entire
@@
 100 times the extragalactic background. The latter factor approximately
-represents the intensity of the galactic diffuse emission near the
-galactic center.  The figure shows two plots, the first showing the
+represents the intensity of the Galactic diffuse emission near the
+Galactic center.  The figure shows two plots, the first showing the
 threshold using only photons with energies between 1 \gev and 100 \gev and
@@
 
-The first and second LAT catalog produced a list of all significant point
-sources seen by the LAT.  (\cite{first_cat,second_cat}).  The first LAT
-catalog's source finding method assumes that all sources were consistent
-with the PSF. The second LAT catalog modeled previously published
-spatially extended sources with an extended spatial model but did not
-attempt to resolve new spatially extended sources. In this paper,
-we took the sources from the second Fermi LAT catalog and perform
-a search to attempt to spatially resolve new sources.
+2FGL is a list of 1873 \gev sources detected by the LAT.  2FGL included
+twelve previously published spatially extended sources but did not
+attempt to fit the extension of these sources. Other than these sources,
+all 2FGL sources were modeled as point sources and 2FGL did not attempt to
+resolve the extension of new sources.  In this paper, we tested all 2FGL
+sources for extension to search for new spatially extended \gev sources.
 
 For this search, we build a model of the
-sky consistent with the second catalog.   We used the same two
+sky consistent with 2FGL.   We used the same two
 years of data from August 4, 2008 to August 1, 2010 and we used the same
 Pass 7\_V6 (P7\_V6) Source class event selections and 
-Instrument Response Functions (IRFs, \cite{lat_on_orbit_psf}).  We used the same galactic diffuse,
+Instrument Response Functions (IRFs, \cite{lat_on_orbit_psf}).  We used the same Galactic diffuse,
 isotropic diffuse, and earth limb emission model. The spectrum of the
-galactic and isotropic diffuse models were refit during the analysis
+Galactic and isotropic diffuse models were refit during the analysis
 while the earth limb emission was fixed to it's predicted value.
@@
 to multiple point sources and susceptible to incorrect modeling of the
-galactic diffuse emission.  For that reason, we performed our search
-using photons only between 1 \gev and 100 \gev.
-We used 4 energy bins per each logarithmic decade in energy.
+Galactic diffuse emission. In addition, the Galactic diffuse emission
+is more pronounced at lower energies due to its steep energy spectrum.
+For that reason, we performed our search using photons only between 1
+\gev and 100 \gev.  We used 4 energy bins per each logarithmic decade
+in energy.
 
@@
 10 \gev and 100 \gev. Even though we are testing the same sources, this
-approach is complimentary because there are regions in the galactic
-plane where at lower energies the diffuse emission dominates and the
-analysis is challenged by the difficulty in modeling this emission.
-The analysis is also challenged by source confusion in crowded regions.
-On the other hand, at the highest energies accessible by the LAT, the
-galactic diffuse emission is less dominant and nearby sources might
-be expected to be softer.  Using higher energies, we might expect
-to detect harder sources in more complicated regions. This approach
-is This is especially beneficial for regions near pulsars which
-cutoff before 10 \gev.  This approach of using high energies was was
-successfully used to detecting HESS J1825-137 and MSH 15-52 with the LAT
-(\cite{msh1552,fermi_hess_j1825}).
+approach is complimentary because the Galactic diffuse emission is even
+less dominant above 10 \gev. Furthermore, source confusion becomes less of
+a problem since most LAT sources are not significant at energies above 10
+\gev.  Using higher energies, we might expect to detect harder sources in
+more complicated regions. This is especially beneficial
+for regions near pulsars which cutoff before 10 \gev
+and was successfully used in detecting HESS J1825-137
+and MSH 15-52 with the LAT (\cite{msh1552,fermi_hess_j1825}).
 
@@
 assuming the source had a uniform radially symmetric disk spatial model.
-we used a circular $10\deg$ region of interest centered on our source and
+We used a circular $10\deg$ region of interest centered on our source and
 included all catalog sources within $15\deg$ of the source of interest.
-We refit the spectral parameters of sources within $2\deg$ of our source.
-We modified the spectral index of each source we were testing to be a
-power-law. This was reasonable because for a source to be significantly
+We refit the spectral parameters of sources within $2\deg$ of the source.
+We modeled each source with a power-law spectral model. This was reasonable because for a source to be significantly
 extended, it would have to be fairly hard and fit reasonably well by
-a power-law. Second, since we began our analysis at either 1 \gev or
+a power-law. Second, since we began the analysis at either 1 \gev or
 10 \gev, we didn't expect there to be significant curvature over this
-smaller energy range.
-
-Finally, when analyzing our region, we automatically removed other
-catalog sources which were within 0.5\deg of the source of interest. This was done because of
-a concern that extended sources would end up in the catalog as
-multiple point sources. These spurious catalogs sources would then
+energy range.
+
+Finally, when analyzing the region, we automatically removed other
+2FGL sources which were within 0.5\deg of the source of interest. This was done because of
+a concern that extended sources would end up 2FGL as
+multiple point sources. These spurious sources would then
 distort the extension fit.
@@
 (described in section~\ref{dual_localization_method} to test if the
-source was extended multiple point sources.
+source is extended. We select the sources where $\tsext>16$.
 
@@
 
-We then selected all of the
-sources for which \pointlike found $\tsext>16$.
-
-We expect most extended sources to be inside the galactic plane
-since extragalactic sources are typically too far away to be
-resolvable. Unfortunately, the \gev emission in the galactic plane
-is dominated by anisotropic galactic diffuse emission.  Modeling the
-galactic diffuse emission and finding sources on top of this emission is
-difficult (\cite{first_diffuse_paper}). This issue has been discussed in the
-Fermi catalog (\cite{first_cat,second_cat}). Furthermore, the galactic plane is
-crowded and so it is often difficult to get a good model for the
-region around a catalog source.  Because of this, finding a source with
-$\tsext>16$ is not a sufficient test and we perform several crosschecks
-to ensure our overall region is well modeled.
+Since extragalactic sources are typically too far away to be resolvable,
+we expect most extended sources to be inside our Galaxy and most
+likely on the Galactic plane.  Unfortunately, the \gev emission
+in the Galactic plane is dominated by extremely structured Galactic
+diffuse emission.  Finding sources on top of this emission is difficult
+(\cite{first_diffuse_paper}) as has been discussed in 1FGL and 2FGL
+(\cite{first_cat,second_cat}).  Furthermore, the Galactic plane is crowded
+so it is often difficult to model nearby sources.  Because of this,
+finding a source with $\tsext>16$ is not a sufficient for finding
+an extended source and we have to perform several analysis crosschecks.
 
 % 2FGL J1856.2+0450c = P72Y3047 for
-As an example of why this issue, we describe our test of 2FGL
+As an example of why this is important, we describe the test of 2FGL
 J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
 a smoothed counts map using photons with energy above 1 \gev. In
-the map, the galactic and isotropic diffuse emission subtracted.
-A two year catalog source 2FGL J1856.2+0450c was found at the position
-$(l,b)=(37.79\deg,1.14\deg)$.  We find that there appears to be overall
-some large scale residual in the diffuse emission along the galactic
-plane. Furthermore, it appears that we don't have a great model of
-the nearby catalog sources. As a result, 2FGL J1856.2+0450c fits to a
-large extension of 1.37\deg and the result is statistically significant
-with \tsext=51.6.  By looking at the residuals, it is clear that this
+the map, the Galactic and isotropic diffuse emission are subtracted.
+A 2FGL source 2FGL J1856.2+0450c was found at the position
+$(l,b)=(37.25\deg,0.84\deg)$.  We find that there appears to be overall
+some large-scale residual in the diffuse emission along the Galactic
+plane. As a result, 2FGL J1856.2+0450c fits to a
+large extension of 1.83\deg and the result is statistically significant
+with \tsext=103.6 (using \pointlike).  By looking at the residuals, it is clear that this
 complicated region is not well fit even though the source's extension is
@@
 \gtlike.  We used a square ROI $14.1\deg$ in diameter with $1/16\deg$
-pixels and the same energy binning. We found that $1/16\deg$ bins were
-fine enough for \gtlike to get an extension significances consistent
-with \pointlike.  Using \gtlike, we found a second measure of \tsext and
-we only considered a source to be significantly extended if \pointlike
-and \gtlike both agreed.  For the new extended source candidates, with
+pixels and the same energy binning as \pointlike. Using \gtlike, we found a second measure of \tsext,
+this time not fitting the extension but using a fixed template
+with extension determined by \pointlike.
+We only considered a source to be significantly extended if \pointlike
+and \gtlike both agreed.  For the new extended source candidates, 
 table~\ref{alt_diff_model_results} shows a comparison of their the value
@@
 Additionally, we generated for each extended source candidate residual
-test statistic (\ts) maps.  The residual \ts map is a map of the \ts
-value evaluated at each point by adding onto the map at that position a
-new source of spectral index 2 and finding the increase in likelihood
-when fitting its flux. \ts maps are especially useful as looking for
-new sources or other residual features that are not included in the
-model. They also have the advantageous feature that the absolute scale
-can be used to clearly look for when the residual is significant.
-The downside is they are biased to look for residual features that
-look like the PSF and so are not as sensitive to diffuse residual
-features. Furthermore, since by definition \ts>0, \ts maps can only show
-positive fluctuations. Nevertheless, \ts maps were useful for assessing
-the overall quality of the fit. Figure~\ref{res_tsmaps} shows an example
+test statistic (\ts) maps.  The residual \ts map is the \ts value
+evaluated at each grid point by adding a new source of spectral index
+2 and finding the increase in likelihood when fitting its flux. \ts
+maps are especially useful when looking for new sources or other
+residual features that are not included in the model. The downside
+is they are biased to look for residual features that look like
+the PSF and so are not as sensitive to large-scale diffuse features.
+features. Furthermore, by definition $\ts>0$ so \ts maps only show
+positive fluctuations. Figure~\ref{res_tsmaps} shows an example
 residual \ts map for the extended source IC443.
@@
 in the latitudinal direction.  The same plot is also shown integrating
-in the longitudinal direction.  On top of the plot is overlaid the model
+in the longitudinal direction.   An example counts slice is shows for the extended source
+IC443 in figure~\ref{counts_slice}. 
+On top of the plot is overlaid the model
 predicted counts assuming the source has a disk spatial model, assuming
 the source is a point source, and fitting just the diffuse emission in
-the region.  An example counts slice is shows for the extended source
-IC443 in figure~\ref{counts_slice}. Counts slices were especially useful
+the region. 
+Counts slices were especially useful
 for looking at how well the overall diffuse emission model fits the
@@
 
-For each candidate, we also made was a radial integral of the data. This
+For each candidate, we also generated a radial integral of the data. This
 plot shows the sum of all counts within a given distance from the
@@
 
-For each source, we computed an extension profile.  An example
-extension profile for the extended source IC443 is shown in
-figure~\ref{extension_profile}.
+For each source, we make a Galactic and extragalactic diffuse emisison
+subtracted smoothed counts map. Figure~\ref{smoothed_counts} shows an
+example smoothed counts map for IC443. They are useful for qualitativly
+assesing the background model.
 
@@
 
-Because of the high source density in the galactic plane for promising
-extended source candidates we often had to iteratively improve our model
-of background sources to obtain a good fit of the extended source.
+Because of the high source density in the Galactic plane for promising
+extended source candidates we often had to iteratively improve the model
+of the background sources to obtain a good fit of the extended source.
 Often, several catalog sources would fill in the emission of one
@@
 have to be refit once the extended source's extension was correctly
-fit. Similarly, background sources were insignificant in the fit energy
-range and had to be removed.  When the localization of background
-sources and the extension of our catalog source coupled, we iteratively
-fit the position and extended of the nearby sources in the region until
-the fitter stabilized on the overall best fit positions and extensions.
-For each extended source, we describe what modifications were required
-to the sky model to obtain a good fit of the region.
-
-\subsection{Alternate Diffuse Model Crosscheck}
+fit. Similarly, background sources were insignificant in the fit
+energy range and had to be removed.  When the position and extension
+of the sources couples strongly with the bacground catalog sources, we
+iteratively fit the position and extended of all nearby sources until the
+fit stabilized.  For each extended source, we describe what modifications
+were required to the sky model to obtain a good fit of the region.
+
+\subsection{Alternative Diffuse Model Crosscheck}
 \label{alt_diff_model_description}
 
-To estimate systematic errors due to uncertainty in our diffuse
+To estimate systematic errors due to uncertainty in the diffuse
 emission background model, we performed a second
-extension test of our candidates using
-an alternate diffuse
-model. Our alternate model was based on the GALPROP\footnote{GALPROP
+extension test of the candidates using
+an alternative diffuse
+model. The alternative model was based on the GALPROP\footnote{GALPROP
 is a software package for calculating the Galactic $\gamma$-ray
@@
 the background ration.
-All told, we fit in or region 18 individual templates along
+All told, we fit in the region 18 individual templates along
 with all source parameters during the analysis.
@@
 But adding degrees of freedom to the background model is a good
-way to remove additional degrees of freedom to the background
-model is likely spurious sources which correlate to features in
+way to remove likely spurious sources which correlate with features in
 the diffuse emission.  Therefore, this tests systematics that may
@@
 in table~\ref{alt_diff_model_results}. Overall, there is good agreement
-between the \ts using the standard and alternate diffuse models.
+between the \ts using the standard and alternative diffuse models, 
+suggesting that the sources are robust against features in the
+diffuse model.
 
@@
 We first present on our analysis of the twelve extended sources
-previously published and include in the second catalog's sky model.
+included in 2FGL.
 (\cite{second_cat}).
 
-% 6 SNRs
-The largest population of extended source are SNRs. The six
-extended SNRs included in the second catalog are IC443, W28, W30,
-W44, W51C, and the Cygnus Loop. These sources were first reported in
-(\cite{ic443,w28,w44,w51c}).  Detailed papers studying W30 and the Cygnus
-Loop are still in preparation.  Using photons with energies between 1
-\gev and 100 \gev, our analysis significantly detected the extension
+% 6 SNRs The six extended SNRs IC443, W28, W30, W44, W51C, and the Cygnus
+Loop were included in 2FGL.  IC443, W28, W44, W51C were first reported in
+(\cite{ic443,w28,w44,w51c}).  Detailed papers by the LAT collaboration
+studying W30 and the Cygnus Loop are still in preparation.  \gev emission
+from W30 was also studied in (\cite{castro_and_slane_2010}).  Using photons
+with energies between 1 \gev and 100 \gev, our analysis significantly
+detected the extension
 of all six SNRs. Table~\ref{known_extended_sources} shows the best fit
-positions and extensions of these sources.
+positions and extensions of these SNRs.
 
@@
 
-Two galaxies the Large Magalenic Cloud and the Small Magalenic Cloud 
-were included in the second catalog (\cite{lmc,smc}).
+In addition, two nearby galaxies the Large Magalenic Cloud and the
+Small Magalenic Cloud were included in 2FGL (\cite{lmc,smc}).  They were
+significantly detected using photons with energies between 1 \gev and
+100 \gev. Our fit extension is comparable to the published result,
+but we note that previous publication used a more complicated double
+Gaussian spatial model when fitting the LMC.
 
@@
 Three pulsar wind nebula Vela X, MSH 15-52, and HESS J1825-137 were
-included in the second catalog (\cite{velax,msh1552,fermi_hess_j1825}).
-Using photons with energy above 10 \gev, we significantly detected the
-extension of HESS J1825-137.  To improve our model of this source, we
-removed the nearby catalog source 2FGL J1823.1-1338c which is part of the
-extended emission of HESS J1825-137.  Using photons with energies above
-10 \gev, we fit the extension of MSH 15-52 consistent with the published
-result at an extension significance of \tsext=9.5.  Our analysis was
-unable to resolve Vela X. An analysis of this source requires removing on
-pulse events from the Vela pulsar and is beyond the scope of this paper.
+included in 2FGL (\cite{velax,msh1552,fermi_hess_j1825}).  Using photons
+with energy above 10 \gev, we significantly detected the extension of
+HESS J1825-137.  To improve the model of this source, we removed the
+nearby catalog source 2FGL J1823.1-1338c which is part of the extended
+source.  To avoid the nearby pulsar PSR J1509-5850, MSH 15-52 must be
+analyzed at high energies.  Using photons with energies above 10 \gev,
+we fit the extension of MSH 15-52 to be consistent with the published
+size with an extension significance of \tsext=7.2.  Our analysis was
+unable to resolve Vela X which would have required removing the pulsed
+photons from the Vela pulsar. This is beyond the scope of this paper.
 
@@
 % 1 radio galaxy
-Centarus A.
-
 Our analysis also failed to detect a significant extension for the
 Centaurus A Lobes (\cite{cen_a_lat}). This is most likely because the
-discovered emission was significantly more complicated then a uniform
+discovered emission was significantly more complicated than a uniform
 radially symmetric Disk.
@@
 model.  It also includes the best fit spectral model of each source.
-The difficulty our analysis analysis had fitting the extension of several
+The difficulty that out analysis had fitting the extension of several
 of the already published extended sources should be used to emphasize
@@
 To validate our method and assess systematic issues with our analysis,
-we used \pointlike to test known active galaxies (AGN) for extension.
+we used \pointlike to test known AGN for extension.
 \gev emission from AGN is believed to comes from the core of supermassive
@@
 
-Following the LAT's one year catalog, the LAT collaboration published
-a list of catalog sources that had a high probability association with
+Following 1FGL, the LAT collaboration published
+a list of sources that had a high probability association with
 AGN (\cite{first_agn_cat}).
-The first year catalog had 709 AGN associated with 671 distinct
+1FGL had 709 AGN associated with 671 distinct
 1FGL sources at high latitude ($|b|>10\deg$).  To avoid systematic
@@
 Of the 599 ``clean'' AGN, we select 556 of these 1FGL sources which
-we uniquely associate with a 2 year catalog source. We furthermore
+we uniquely associate with a 2FGL source. We furthermore
 restrict our select to the 515 of these AGN for which we fit $\ts>25$
@@
 here is not to find the largest sample of AGN but simply
-to find a goog sample to test the systematics of our extended source
+to find a good sample to test the systematics of our extended source
 search.
@@
 Subsequently, the PSF was fit empirically to bright AGN and this
-empirical parameterization was used in our instrument
+empirical parameterization was used in the LAT's instrument
 response function (\cite{lat_on_orbit_psf}).
-But our current parameterization is not perfect. There are lingering
+But the current parameterization is not perfect. There are lingering
 issues due to a lack of statistics at high energy which makes it hard to
@@
 % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
 % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
@@
 
-Ten extended sources not include in the second LAT catalog were found
-using this search.  Four were found in our search using only photons
+Nine extended sources not include in 2FGL were found
+using this search.  Three were found in our search using only photons
 with energies above 1 \gev and six were found only using photones with
-energies above 10 \gev.  The fit properties of these ten sources is
+energies above 10 \gev.  The fit properties of these nine sources is
 summarized in table~\ref{new_ext_srcs_table}.  The table includes for each
@@
 and significance of extension.  Figure~\ref{allsky_extended_sources}
-shows a skymap of the position of the twelve sources included in the
-second catalog and the ten sources analysis in this paper.
-
-For all the extended sources, table~\ref{dual_localization_results}
-presents information about the of source confusion by fitting the same
-region as two point sources using the dual localization method described
-in section~\ref{dual_localization_method}. The table compares \tsext
-to \tsinc and summarized the positions and spectra of the two sources.
+shows a skymap of the position of the twelve sources included in 2FGL
+and the nine sources analysis in this paper.
+
+For the new extended sources, table~\ref{dual_localization_results}
+presents a test for source confusion by fitting the region
+as two point sources. The table compares \tsext
+to \tsinc and summarizes the positions and spectra of the two sources.
 Finally, table~\ref{alt_diff_model_results} summarized the results of
-a crosscheck of the source fitting the region with an alternate diffuse
+a crosscheck of the source fitting the region with an alternative diffuse
 model described in section~\ref{alt_diff_model_description}.  These tables
@@
 sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
-extended emission.  We tested the source for source confusion by fitting
+extended source.  We tested the source for source confusion by fitting
 it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
@@
 
-\todo[inline]{Add interpretations of Puppis A}
+\todo[inline]{Add interpretations of Puppis A. Stefan volunteered to write this}
 
@@
 \todo[inline]{Can we get another citation about dark gas and stuff?
-And a better description of spectral index being typical of diffuse emission.}
-
-\subsection{2FGL J1554.4-5317c}
-\label{section_2FGL_J1554.4-5317c}
-
-% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
-% Sources that had to be deleted
-%   * P72Y2416 - 2FGL J1551.3-5333c
-%   * P72Y2422 - Not a 2FGL source
-
-The two year catalog source 2FGL J1554.4-5317c was found to be extended
-using photons with energies between 1 \gev and 100 \gev.  We found an
-extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
-$\tsext=37.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  
-This source is coincident with the one year catalog source 1FGL J1554.0-5345c.
-Figure \ref{1FGL_J1554.0-5345c} shows a counts map of this source.
-
-To get a good fit of the source, we removed the nearby catalog source
-2FGL J1551.3-5333c which is contained within the extended source.
-We tested this source for source confusion by fitting it instead as
-two point sources.  Since $\tsinc=9.2$ is less than \tsext, we conclude
-that the source is spatially extended. The region is further described
-in the caption to figure~\ref{1FGL_J1554.0-5345c}.
-
-There are no obvious counterparts to this source at other
-wavelengths. Furthermore, this source is relatively soft with a spectral
-index 2.31 and is close to the galactic plane in a region of large
-diffuse emission.  We conclude that although this region is significantly
-extended, it is most likely unmodeled diffuse emission.
-
-\todo[inline]{This needs more quantification/description.  
-Can we improve the argument about spectral index}
+And a better description of spectral index being typical of diffuse emission.
+Stefan says that Markus should write this section.
+He also says we should cite (\cite{isabelle_dark_gass}).  
+}
 
@@
 % * P72Y1300 - 2FGL J0858.0-4815
+% * P72Y1310 - 2FGL J0901.7-4655 
 % Modify:
@@
 %              (initial Position - SkyDir(265.5705,-0.0099)
-% * P72Y1310 - 2FGL J0901.7-4655 - SkyDir(267.575,-0.191,SkyDir.GALACTIC)
-%              (initial Position - SkyDir(267.79,-0.3339)
 
@@
 significance of $\tsext=76.7$.  The source was fit to a position of
-$(l,b)=(266.29\deg,-1.41\deg)$.  
-This source has no counterparts in the first year LAT catalog.
-Figure~\ref{Vela_Jr} shows a counts map of this source.
-
-To get a good fit of the source, we had to remove three nearby catalog
-sources 2FGL J0848.5-4535, 2FGL J0855.4-4625, and 2FGL J0853.5-4711
-which are part of the extended emission.  In addition, we relocalized
-the position of two nearby catalog sources 2FGL J0854.7-4501 and 2FGL
-J0901.7-4655 to better fit their position at high energies in the presence
-of an extended source.  This localization was done iteratively alternately 
-fitting the position of these two point sources and the extension of
-2FGL J0851.7-4635 until the fit globally converged.  2FGL J0854.7-4501
-moved to $(l,b)=(266.24\deg,0.49\deg)$ and 2FGL J0901.7-4655 moved to
-$(l,b)=(267.58\deg,-0.19\deg)$. In addition, we removed the further away
-catalog source 2FGL J0858.0-4815 because it was not significant above 10
-\gev.  After modifying the region, we found that \tsinc=16.2 which is less
-than \tsext so we conclude that the source is extended 
-These modifications are shown in
-figure~\ref{Vela_Jr}.
+$(l,b)=(266.29\deg,-1.41\deg)$.  Figure~\ref{Vela_Jr} shows a counts
+map of this source.
 
@@
 
-\todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming publication?}
+\todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming
+publication? Stefan volunteered to write this.}
+
+To get a good fit of the source, we had to remove thee nearby catalog
+sources 2FGL J0853.5-4711, 2FGL J0848.5-4535, and 2FGL J0855.4-4625
+which are part of the extended source.  In addition, we relocalized
+the position of the nearby catalog source 2FGL J0854.7-4501 to
+$(l,b)=(266.24\deg,0.49\deg)$ to better fit its position at high energies
+in the presence of of the eextended source.  In addition, we removed the
+further away catalog sources 2FGL J0858.0-4815 and 2FGL J0901.7-4655
+because they were not significant above 10 \gev.  After modifying
+the region, we found that \tsinc=16.2 which is less than \tsext so we
+conclude that the source is extended These modifications are shown in
+figure~\ref{Vela_Jr}.
 
@@
 We removed from our model the source 2FGL J1614.9-5212 because it is
-part of 2FGL J1615.2-5138's extended emission. Furthermore, we removed
+part of 2FGL J1615.2-5138's. Furthermore, we removed
 the nearby catalog sources 2FGL J1619.7-5040c and 2FGL J1620.6-5111c
@@
 This source is spatially coincident with the extended \tev source HESS
-J1616-508 (\cite{HESS_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
+J1616-508 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
 contours of HESS J1616-508 are overlaid on 2FGL J1615.0-5051.
@@
 This source is spatially coincident with the extended \tev source HESS
-J1614-518 (\cite{HESS_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
+J1614-518 (\cite{hess_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
 contours of HESS J1614-518 are overlaid on 2FGL J1615.2-5138.
@@
 
-\todo[inline]{Add interpretations of HESS J16154-518.}
+\todo[inline]{Add interpretations of HESS J1614-518. Stefan says to
+use the Rowell et al, Suzaku observations.}
 
@@
 This extended source is spatially coincident with the extended \tev source HESS
-J1632-478 (\cite{HESS_plane_survey}).  In figure~\ref{1FGL_J1632.9-4802c},
+J1632-478 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1632.9-4802c},
 contours of  HESS J1632-478 are overlaid on 2FGL J1635.4-4717c.
@@
 We removed the nearby catalog source 2FGL J1835.5-0649 which is part
-of the extended emission and the farther away catalog
+of the extended source and the farther away catalog
 source 2FGL J1839.0-0539 because it was not significant above 10 \gev.
@@
 This source is spatially coincident with the \tev source HESS J1837-069
-(\cite{HESS_plane_survey}).  In figure~\ref{1FGL_J1837.5-0659c},
+(\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1837.5-0659c},
 contours of are H.E.S.S J1837-069 are overlaid on 2FGL
@@
 further away catalog sources 2FGL J2022.8+3843c, 2FGL J2020.0+4159,
-2FGL J2013.8+4115c, and 2FGL J2012.4+3955c from our region becuase they
+2FGL J2013.8+4115c, and 2FGL J2012.4+3955c from the region because they
 were not significant above 10 \gev.  After modifying the region, we found
@@
 
-\todo[inline]{Describe comparison of \gev and \tev extensions from figure~\ref{gev_vs_tev_histogram}}
+Figure~\ref{allsky_extended_sources} is an all sky map showing the
+location of all \gev extended sources. Note how most
+extended sources are in the Galactic plane.
+
+Figure~\ref{gev_vs_tev_histogram} is a histogram comparing the size of
+all extended sources seen in \gev by the LAT and in \tev by H.E.S.S..
+Note how H.E.S.S. can see smaller sources whereas the LAT
+can see bigger sources.
+
+For all extended sources seen both in \gev and \tev,
+figure~\ref{gev_vs_tev_plot} shows a comparision of their sizes.
+Note that there is pretty good agreement.
 
@@
 \appendix
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/profile_ic443.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_profile_ic443/v1/profile_ic443.pdf
+    \caption{
+    A plot of the overall change in \ts when varying the
+    extension of the extended SNR IC443.  As is discussed in section
+    \ref{extension_error}, the error on the extension of a source is
+    calculated by varying the extension away from its best fit value until
+    the \loglikelihood has changed by a particular amount.  These profiles are
+    generated for all extended source candidates. They are useful
+    to make sure the fitter find a global minimum and that
+    the likelihood function is not unphysically double peaked.
+    }
+    \label{extension_profile}
+  \end{center}
+\end{figure}
 
@@
       \caption{
-      This plot shows that fitting the same source with different spatial
-      shapes can lead to different values of $\sigma$. On the other
-      hand, the different shapes have a good agreement about the 68\%
-      containment radius \rsixeight.  It shows counts map for a simulated
-      uniform disk extended source in the energy range from 1 \gev to
-      100 \gev.  The source has a size $\sigma=0.5\deg$, an integral flux
-      between 1 \gev and 100 \gev of $3\times 10^{-8}\ph/\cm^2/\sec$, and
-      a spectral index 2.  The smoothed counts from a point source with
-      the same spectrum are shown in the bottom right inset.  This source
-      was fit with both a uniform disk and a Gaussian spatial model.
-      The red circle represents the fit size $\sigma$ modeling the
-      source with a uniform disk spatial model.  The black circle is
-      the fit $\sigma$ modeling the source with a Gaussian hypothesis.
-      The dashed white and black circle are the fit \rsixeight for the
-      disk and Gaussian hypothesis. This plot is discussed further in
-      section~\ref{compare_source_size}.
+      This plot shows that fitting the same source with different
+      spatial shapes can lead to different values of the fitted
+      extensions. On the other hand, the different shapes have a
+      good agreement about the 68\% containment radius \rsixeight.
+      It shows counts map for a simulated uniform disk extended source
+      in the energy range from 1 \gev to 100 \gev.  The source has a
+      size $\sigma=0.5\deg$, an integral flux between 1 \gev and 100
+      \gev of $3\times 10^{-8}\ph/\cm^2/\sec$, and a spectral index 2.
+      The smoothed counts from a point source with the same spectrum are
+      shown in the bottom right inset.  This source was fit with both
+      a uniform disk and a Gaussian spatial model.  The white circle
+      represents the edge of the best fit uniform disk spatial model.
+      The black circle is the fit $\sigma$ modeling the source with a
+      Gaussian hypothesis.  The dashed white and black circle are the
+      fit \rsixeight for the disk and Gaussian hypothesis. This plot is
+      discussed further in section~\ref{compare_source_size}.
       }\label{compare_r68}
@@
     \caption{
+    This plot shows the detection threshold to resolve an extended source.
+    It is defined as the flux where $\langle\tsext\rangle=25$ for a
+    given extension.  The $x$ axis is the extension of a uniform disk
+    extended source and the $y$ axis is the source's 100 \mev to 100
+    \gev photon flux.  All sources have an assumed power-law spectrum
+    and the different colors are for sources of different simulated
+    spectral indices.  The solid line is the detection threshold using
+    photons with energy between 100 \mev and 100 \gev while the dashed
+    line is the threshold using photons with energy between 1 \gev and
+    100 \gev.  The detection threshold is for a one year simulation
+    against a Sreekumar-like isotropic background.  More information
+    about this plot is presented in section~\ref{extension_sensitivity}.
     This plot shows that our threshold to detecting the extension of
-    a source is best for sources with size $~0.5\deg$. It also shows
-    that for sources neither too large nor soft, our sensitivity is
-    not significantly improved using photons with energy between 100
-    \mev and 1 \gev.  The $x$ axis is extension of a simulated uniform
-    disk extended source and the $y$ axis is the simulated source's 100
-    \mev to 100 \gev photon flux. The curves represent the detection
-    threshold to an extended source which is defined as the flux when
-    $\langle\tsext\rangle=25$ for a particular extension.  All sources
-    have an assumed power-law spectrum and the different colors are
-    for sources of different simulated spectral indices.  The dashed
-    line shows simulations using photons with energy between 100 \mev
-    and 100 \gev while the solid lien shows simulations using photons
-    with energy between 1 \gev and 100 \gev.  The detection threshold
-    is for a one year simulation against a Sreekumar-like isotropic
-    background.  More information about this plot is presented in
-    section~\ref{extension_sensitivity}.
+    a source is best for a source with size $~0.5\deg$. It also shows
+    that for sources neither too large nor soft, our sensitivity is not
+    significantly improved using photons with energy between 100 \mev
+    and 1 \gev.
+    \todo[inline]{Overlay on this plot the twelve extended sources}
     }\label{index_sensitivity}
@@
     \caption{
-    This plot shows that we are less sensitive to extended sources in
-    regions with higher background and (given the same number of photons)
-    more sensitive to harder sources.  The plot has the same meaning as
-    in figure~\ref{index_sensitivity} and the simulations occur over
-    the same time range.  These plots presents the sensitivity over
-    for varying background levels and two energy ranges.  The blue dash
-    dotted plot is the sensitivity against a Sreekumar-like isotropic
-    background. The green dashed curve shows the sensitivity against 10
-    times that isotropic background and the solid red curve shows the
-    sensitivity against 100 times that isotropic background.  The latter
-    factor approximately represents the intensity of the galactic
-    diffuse emission near the galactic center.  The left plot presents
-    the sensitivity when using only photons with energies between 1 \gev
-    and 100 \gev while the plot on the right presents the sensitivity only
-    when using photons with energies between 10 \gev and 100 \gev. Unlike
-    figure~\ref{index_sensitivity}, the sensitivity was calculated only
-    for a power-law source of spectral index 2. Similarly, the flux is
-    quoted only in the selected energy range which weakens the dependence
-    of the detection threshold on spectral index.  More information
-    about this plot is presented in section~\ref{extension_sensitivity}.
+    These plots presents the sensitivity for varying background
+    levels and energy ranges.  The plots have the same meaning as in
+    figure~\ref{index_sensitivity} and the simulations occur over the
+    same time range.  The blue dash dotted line is the sensitivity
+    against a Sreekumar-like isotropic background. The green dashed
+    curve is the sensitivity against 10 times the isotropic background
+    and the solid red curve is the sensitivity against 100 times the
+    isotropic background.  The latter factor approximately represents
+    the intensity of the Galactic diffuse emission near the Galactic
+    center.  The left plot is the sensitivity using photons with energies
+    between 1 \gev and 100 \gev while the right plot is the sensitivity
+    using photons with energies between 10 \gev and 100 \gev. Unlike
+    figure~\ref{index_sensitivity}, the sensitivity was calculated
+    only for a power-law source of spectral index 2. The flux is quoted
+    only in the selected energy range which weakens the dependence of
+    the detection threshold on spectral index.  These plots show that
+    we are less sensitive to extended sources in regions with higher
+    background and (given the same number of photons) more sensitive
+    to harder sources.  More information about this plot is presented
+    in section~\ref{extension_sensitivity}.
     }\label{diff_factor_sensitivity}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{ic443_plots/ic443_ts_ext_vs_energy.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
+    \caption{
+    The plot shows \tsext for twelve uniform log(energy) bins between 100 \mev
+    and 100 \gev for the SNR IC443. IC443 has a spectral index $~2.4$
+    (table~\ref{known_extended_sources}). This plot shows that there is
+    little gain in sensitivity to the extension of a source using photons
+    with energies below 1 \gev, even for a source with an index 2.4.
+    For this reason, this paper restricts its analysis to energies above
+    1 \gev.
+    }
+    \label{ts_ext_vs_energy}
+  \end{center}
+\end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{source_plots/example_bad_fit.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
+    \caption{
+    The observed 1 \gev to 100 \gev photons for the two year catalog
+    source 2FGL J1856.2+0450c. This map is smoothed by a 0.1\deg Gaussian
+    kernel and the red cross and circle are the center and size of the
+    best fit uniform disk spatial model. The result is statistically
+    significant, but the extension encompasses many catalog sources and
+    the emission does not look to be uniform. Instead, this source is
+    probably fitting large-scale diffuse residual features. Although the
+    fit is statistically significant, it is not physical and we manually
+    discard candidates that appear like this.
+    }
+    \label{example_bad_fit}
+  \end{center}
 \end{figure}
@@
   \begin{center}
-    \includegraphics{ic443_plots/ic443_ts_ext_vs_energy.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
-    \caption{
-    The plot shows \tsext for 12 uniform log(energy) bins between 100 \mev
-    and 100 \gev for the SNR IC443. IC443 has a spectral index $~2.4$
-    (table~\ref{known_extended_sources}) which is typical of extended
-    sources.  This plot shows that there is little gain in sensitivity to
-    the extension of a source using photons with energies below 1 \gev.
-    For this reason, this paper restricts its analysis to energies above
-    1 \gev.
-    }
-    \label{ts_ext_vs_energy}
-  \end{center}
-\end{figure}
-
-\clearpage
-\begin{figure}
-  \begin{center}
     \includegraphics{ic443_plots/ic443_counts_slice.pdf}
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/counts_slice_ic443/v1/ic443_counts_slice.pdf
-    \caption{ The upper plot is the sum of the counts binned in galactic
-    longitudinal summed within 2\deg in galactic latitude centered on the
+    \caption{ The upper plot is the sum of the counts binned in Galactic
+    longitudinal summed within 2\deg in Galactic latitude centered on the
     SNR IC443. The lower plot shows the same image but instead integrated
-    in galactic longitude.  Overlaid on the plot is the model predicted
+    in Galactic longitude.  Overlaid on the plot is the model predicted
     counts assuming that IC443 is a point source, an extended source, and
@@
     IC443 with energies between 1 \gev and 100 \gev.  This plot has the
-    galactic and isotropic diffuse emission subtracted and is smoothed
+    Galactic and isotropic diffuse emission subtracted and is smoothed
     by a $0.1\deg$ Gaussain kernel.  The overlaid box is the PSF for
@@
 \clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{ic443_plots/profile_ic443.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_profile_ic443/v1/profile_ic443.pdf
-    \caption{
-    A plot of the overall change in \ts when varying the
-    extension of the extended SNR IC443.  As is discussed in section
-    \ref{extension_error}, the error on the extension of a source is
-    calculated by varying the extension away from its best fit value until
-    the \loglikelihood has changed by a particular amount.  These profiles are
-    generated for all extended source candidates. They are useful
-    to make sure the fitter find a global minimum and that
-    the likelihood function is not unphysically double peaked.
-    }
-    \label{extension_profile}
-  \end{center}
-\end{figure}
-
-\clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{source_plots/example_bad_fit.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v2
-    \caption{
-    The observed 1 \gev to 100 \gev photons for the
-    two year catalog source 2FGL J1856.2+0450c. This map is smoothed by
-    a 0.1\deg Gaussian kernel and the red circle is the edge of
-    the fit uniform disk spatial model.  2FGL J1856.2+0450c fits to an
-    extension of 1.37\deg and the result is statistically significant
-    with \tsext=51.6. On the other hand, the extension encompasses many
-    catalog sources and the emission does not look to be uniform. Instead,
-    this source is fitting large scale residual. Although the fit is 
-    statistically significant, it is not physical and we discard sources
-    that look like this.
-    }
-    \label{example_bad_fit}
-  \end{center}
-\end{figure}
-
-\clearpage
 \begin{sidewaystable}
@@
         \hline
-        Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &      Major &      Minor &        Ang &      Flux ($10^{-9}$) &                 Index \\
-        \hline
-        \multicolumn{11}{c}{$E > 1 \gev$} \\
-        \hline
-        SMC                  &     302.87\deg &     -44.65\deg & $  1.59\deg \pm   0.15\deg$ &       93.1 &       51.2 &  0.173\deg &  0.129\deg &   41.9\deg & $    3.0 \pm     0.4$ & $   2.42 \pm    0.16$ \\
-        LMC                  &     278.58\deg &     -32.82\deg & $  2.26\deg \pm   0.09\deg$ &      384.2 &      304.4 &  0.096\deg &  0.071\deg &  -35.5\deg & $   12.9 \pm     0.7$ & $   2.42 \pm    0.08$ \\
-        IC443                &     189.05\deg &       3.04\deg & $  0.35\deg \pm   0.01\deg$ &    10765.3 &      535.3 &  0.006\deg &  0.006\deg &   84.0\deg & $   65.2 \pm     1.2$ & $   2.23 \pm    0.02$ \\
-        W28                  &       6.51\deg &      -0.29\deg & $  0.39\deg \pm   0.02\deg$ &     1231.3 &       92.1 &  0.014\deg &  0.013\deg &   30.4\deg & $   55.9 \pm     1.8$ & $   2.65 \pm    0.03$ \\
-        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.04\deg$ &      458.1 &       66.0 &  0.020\deg &  0.018\deg &   14.1\deg & $   30.0 \pm     1.8$ & $   2.58 \pm    0.06$ \\
-        W44                  &      34.68\deg &      -0.42\deg & $  0.34\deg \pm   0.02\deg$ &     1387.6 &      111.3 &  0.009\deg &  0.009\deg &  -39.4\deg & $   74.7 \pm     1.0$ & $   2.67 \pm    0.01$ \\
-        W51C                 &      49.12\deg &      -0.44\deg & $  0.28\deg \pm   0.02\deg$ &     2174.7 &       87.6 &  0.010\deg &  0.010\deg &   59.4\deg & $   41.6 \pm     1.3$ & $   2.38 \pm    0.04$ \\
-        Cygnus Loop          &      74.20\deg &      -8.51\deg & $  1.74\deg \pm   0.06\deg$ &      206.2 &      164.1 &  0.096\deg &  0.063\deg &  -69.0\deg & $    8.7 \pm     0.7$ & $   2.55 \pm    0.15$ \\
-        \hline
-        \multicolumn{11}{c}{$E > 10 \gev$} \\
-        \hline
-        MSH 15-52            &     320.39\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &       73.7 &        9.5 &  0.033\deg &  0.032\deg &    3.9\deg & $    0.6 \pm     0.1$ & $   2.32 \pm    0.23$ \\
-        HESS J1825-137       &      17.58\deg &      -0.46\deg & $  0.64\deg \pm   0.08\deg$ &       85.6 &       62.5 &  0.050\deg &  0.045\deg &   33.6\deg & $    1.8 \pm     0.3$ & $   1.75 \pm    0.20$ \\
+        Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &   Pos. Err &      Flux ($10^{-9}$) &                 Index \\
+        \hline
+        \multicolumn{9}{c}{$E > 1 \gev$} \\
+        \hline
+        SMC                  &     302.68\deg &     -44.81\deg & $  1.75\deg \pm   0.13\deg$ &       94.4 &       66.4 &  0.118\deg & $    3.3 \pm     0.4$ & $   2.40 \pm    0.17$ \\
+        LMC                  &     279.10\deg &     -32.61\deg & $  1.74\deg \pm   0.07\deg$ &     1102.4 &      861.9 &  0.052\deg & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$ \\
+        IC443                &     189.05\deg &       3.04\deg & $  0.36\deg \pm   0.01\deg$ &    10698.1 &      503.5 &  0.006\deg & $   64.9 \pm     1.2$ & $   2.23 \pm    0.02$ \\
+        W28                  &       6.50\deg &      -0.27\deg & $  0.43\deg \pm   0.02\deg$ &     1323.4 &      172.6 &  0.014\deg & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$ \\
+        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.04\deg$ &      468.6 &       77.2 &  0.019\deg & $   30.8 \pm     1.6$ & $   2.59 \pm    0.05$ \\
+        W44                  &      34.69\deg &      -0.38\deg & $  0.36\deg \pm   0.02\deg$ &     1910.4 &      222.4 &  0.010\deg & $   74.0 \pm     2.0$ & $   2.68 \pm    0.02$ \\
+        W51C                 &      49.13\deg &      -0.45\deg & $  0.28\deg \pm   0.02\deg$ &     1814.2 &      110.6 &  0.010\deg & $   39.2 \pm     1.3$ & $   2.35 \pm    0.03$ \\
+        CygnusLoop           &      74.22\deg &      -8.46\deg & $  1.72\deg \pm   0.05\deg$ &      356.5 &      356.5 &  0.060\deg & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$ \\
+        \hline
+        \multicolumn{9}{c}{$E > 10 \gev$} \\
+        \hline
+        MSH15-52             &     320.38\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &       75.2 &        7.2 &  0.032\deg & $    0.6 \pm     0.7$ & $   2.26 \pm    0.73$ \\
+        HESSJ1825-137        &      17.56\deg &      -0.46\deg & $  0.65\deg \pm   0.07\deg$ &       81.6 &       51.4 &  0.047\deg & $    1.8 \pm     0.1$ & $   1.74 \pm    0.06$ \\
       \end{tabular}
       \caption{The fit for ten of the twelve extended sources included
-      in the second LAT catalog.  The top list are the extended sources
+      in 2FGL.  The top list are the extended sources
       analyzed using photons with energies between 1 \gev and 100 \gev.
@@
       values were calculated using \gtlike.  The TS value was computed
-      assumgni the best fit uniform disk spatial model and \tsext
+      assuming the best fit uniform disk spatial model and \tsext
       compares the increase in \ts fitting the source with an extended
-      spatial model to point model.  \glon and \glat are respectively
-      the galactic longitude and galactic latitude of the source and
-      $\sigma$ is the edge of the best fit uniform disk spatial model.
-      The extended PWN Vela X is not include in this list because a phase
-      cut would be required to remove the Vela pulsar (\cite{velax}).
-      The extended Centaurus A lobes are not included because a radially
-      symmetric uniform disk spatial model is a bad match to the observed
-      emission (\cite{cen_a_lat}).  More information about these sources is
-      in section~\ref{validate_known}.
+      spatial model to point model.  \glon and \glat are respectively the
+      Galactic longitude and Galactic latitude of the source and $\sigma$
+      is the edge of the best fit uniform disk spatial model.  Pos. Err
+      is the error on the localization of the source.  The extended PWN
+      Vela X is not include in this list because a phase cut would be
+      required to remove the Vela pulsar (\cite{velax}).  The extended
+      Centaurus A lobes are not included because a radially symmetric
+      uniform disk spatial model is a very bad match to the observed
+      emission (\cite{cen_a_lat}).  More information about these sources
+      is in section~\ref{validate_known}.
       }
@@
   % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-  % 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
   % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
@@
       \hline
-      Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &      Major &      Minor &        Ang &      Flux ($10^{-9}$) &                 Index \\
-      \hline
-      \multicolumn{11}{c}{$E > 1 \gev$} \\
-      \hline
-      2FGL J0823.0-4246    &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      314.7 &       46.1 &  0.026\deg &  0.023\deg &    5.3\deg & $    8.3 \pm     0.6$ & $   2.18 \pm    0.07$ \\
-      2FGL J1627.0-2425c   &     352.87\deg &      16.79\deg & $  0.53\deg \pm   0.06\deg$ &      130.3 &       20.3 &  0.060\deg &  0.047\deg &   39.8\deg & $    6.7 \pm     0.7$ & $   2.48 \pm    0.15$ \\
-      2FGL J1554.4-5317c   &     328.12\deg &       0.26\deg & $  0.52\deg \pm   0.04\deg$ &      150.8 &       37.6 &  0.044\deg &  0.039\deg &   55.5\deg & $   16.7 \pm     1.5$ & $   2.30 \pm    0.11$ \\
-      2FGL J1712.4-3941    &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg$ &       77.6 &       41.2 &  0.055\deg &  0.043\deg &  -14.8\deg & $    4.3 \pm     0.9$ & $   1.48 \pm    0.12$ \\
-      \hline
-      \multicolumn{11}{c}{$E > 10 \gev$} \\
-      \hline
-      2FGL J0851.7-4635    &     266.29\deg &      -1.41\deg & $  1.12\deg \pm   0.07\deg$ &      120.0 &       76.7 &  0.090\deg &  0.064\deg &   63.8\deg & $    1.3 \pm     0.1$ & $   1.75 \pm    0.08$ \\
-      2FGL J1615.0-5051    &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg$ &       54.0 &       16.6 &  0.049\deg &  0.040\deg &    1.7\deg & $    1.1 \pm     0.2$ & $   2.25 \pm    0.28$ \\
-      2FGL J1615.2-5138    &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg$ &       75.9 &       47.6 &  0.048\deg &  0.044\deg &   31.1\deg & $    1.1 \pm     0.2$ & $   1.77 \pm    0.26$ \\
-      2FGL J1632.4-4753c   &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      128.3 &       64.8 &  0.042\deg &  0.036\deg &  -16.1\deg & $    2.0 \pm     0.2$ & $   2.29 \pm    0.22$ \\
-      2FGL J1837.3-0700c   &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       47.0 &       20.2 &  0.075\deg &  0.064\deg &  -12.4\deg & $    1.1 \pm     0.2$ & $   1.65 \pm    0.21$ \\
-      2FGL J2021.5+4026    &      78.17\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      225.3 &      139.4 &  0.044\deg &  0.030\deg &   51.1\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ \\
+      Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &   Pos. Err &      Flux ($10^{-9}$) &                 Index \\
+      \hline
+      \multicolumn{9}{c}{$E > 1 \gev$} \\
+      \hline
+      2FGL J0823.0-4246    &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      320.9 &       46.3 &  0.024\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ \\
+      2FGL J1627.0-2425c   &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg$ &      144.5 &       31.1 &  0.038\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ \\
+      2FGL J1712.4-3941    &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg$ &       75.0 &       39.6 &  0.049\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ \\
+      \hline
+      \multicolumn{9}{c}{$E > 10 \gev$} \\
+      \hline
+      2FGL J0851.7-4635    &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg$ &      116.1 &       87.2 &  0.074\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ \\
+      2FGL J1615.0-5051    &     332.38\deg &      -0.14\deg & $  0.32\deg \pm   0.04\deg$ &       54.3 &       16.7 &  0.043\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.25$ \\
+      2FGL J1615.2-5138    &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg$ &       76.6 &       48.0 &  0.045\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ \\
+      2FGL J1632.4-4753c   &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      127.8 &       64.5 &  0.039\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ \\
+      2FGL J1837.3-0700c   &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       46.2 &       18.8 &  0.069\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ \\
+      2FGL J2021.5+4026    &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      222.2 &      116.4 &  0.037\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ \\
       \hline
@@
 \clearpage
-\begin{sidewaysfigure}
-  \begin{center}
-    \includegraphics{summary_plots/allsky_extended_sources.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v1/run.py
-    \end{center}
-    \caption{A plot of all \gev extended sources detected by the LAT
-    with two years of data.  The twelve extended sources included in
-    the second LAT catalog are the red markers and the ten additional
-    extended sources analyzed in this paper are the green markers. The
-    extended sources are overlaid on an Aitoff projection Galactic
-    coordinate map of all 100 \mev to 100 \gev photons measured by the
-    LAT in the two year time interval of this analysis.}\label{allsky_extended_sources}
-  \end{sidewaysfigure}
-
-\clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{summary_plots/gev_vs_tev_histogram.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v1/extension_histogram.py
-    \end{center}
-    \caption{
-    A comparison of the size of detected \tev and \gev sources.
-    The extension of the 22 extended LAT sources comes from
-    table~\ref{known_extended_sources}, table~\ref{new_ext_srcs_table},
-    and the LAT extension of Vela X is taken from (\cite{velax}). The
-    Centarus A lobes, which have an extension $~10\deg$, are not
-    included in the plot (\cite{cen_a_lat}).  The \tev extension of
-    the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-    Catalog (\cite{hesscat}).  Because the \gev sources were fit
-    with a uniform disk spatial model whereas the \tev sources were
-    fit with a Gaussian spatial model, the histogram is of \rsixeight
-    (see section~\ref{compare_source_size}).  On the other hand, because
-    of their size, the \tev size of RX J1713.7-2946 and Vela Jr. were
-    obtained by a fit of a Gaussian spatial model so the \gev and \tev
-    sizes of these sources were not converted.
-    }\label{gev_vs_tev_histogram}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{summary_plots/gev_vs_tev_plot.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v1/run.py
-    \end{center}
-    \caption{
-    }\label{gev_vs_tev_plot}
-  \end{figure}
-
-\clearpage
 \begin{sidewaystable}
@@
         \hline
-        2FGL J0823.0-4246    &       21.9 &       46.1 &     260.59\deg &      -3.27\deg & $       2.0 \pm        0.5$ & $  1.9 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.3 \pm        0.6$ & $  2.4 \pm   0.1$ \\
-        2FGL J1627.0-2425c   &       19.1 &       20.3 &     353.00\deg &      16.97\deg & $       3.0 \pm        0.6$ & $  2.6 \pm   0.4$  &     353.26\deg &      16.67\deg & $       2.4 \pm        0.6$ & $  2.5 \pm   0.5$ \\
-        2FGL J1554.4-5317c   &        9.2 &       37.6 &     328.30\deg &       0.31\deg & $      10.3 \pm        1.2$ & $  2.7 \pm   0.5$  &     328.27\deg &      -0.07\deg & $       0.9 \pm        0.6$ & $  1.6 \pm   0.4$ \\
-        2FGL J1712.4-3941    &        6.6 &       41.2 &     347.28\deg &      -0.07\deg & $       0.2 \pm        0.1$ & $  0.6 \pm   0.5$  &     347.22\deg &      -0.26\deg & $       2.5 \pm        0.7$ & $  1.9 \pm   0.2$ \\
+        2FGL J0823.0-4246    &       22.1 &       46.3 &     260.59\deg &      -3.27\deg & $       2.1 \pm        0.6$ & $  2.0 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.4 \pm        0.7$ & $  2.4 \pm   0.2$ \\
+        2FGL J1627.0-2425c   &       20.0 &       31.1 &     353.01\deg &      16.98\deg & $       3.1 \pm        0.6$ & $  2.6 \pm   0.3$  &     353.24\deg &      16.66\deg & $       2.5 \pm        0.6$ & $  2.5 \pm   0.4$ \\
+        2FGL J1712.4-3941    &        6.4 &       39.6 &     347.28\deg &      -0.07\deg & $       0.2 \pm        0.1$ & $  0.6 \pm   0.5$  &     347.22\deg &      -0.27\deg & $       2.4 \pm        0.7$ & $  1.9 \pm   0.2$ \\
         \hline
@@
         \hline
-        2FGL J0851.7-4635    &       16.1 &       76.7 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.38\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
-        2FGL J1615.0-5051    &       12.2 &       16.6 &     332.39\deg &      -0.07\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.6$  &     332.43\deg &      -0.36\deg & $       0.4 \pm        0.1$ & $  2.4 \pm   0.5$ \\
-        2FGL J1615.2-5138    &       37.6 &       47.6 &     331.75\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.3 \pm   0.5$  &     331.46\deg &      -0.79\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
-        2FGL J1632.4-4753c   &       40.9 &       64.8 &     336.52\deg &       0.18\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
-        2FGL J1837.3-0700c   &       12.3 &       20.2 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.6$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.6$ \\
-        2FGL J2021.5+4026    &       29.7 &      139.4 &      78.08\deg &       2.53\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$  &      78.43\deg &       2.55\deg & $       0.5 \pm        0.1$ & $  1.8 \pm   0.4$ \\
+        2FGL J0851.7-4635    &       16.1 &       87.2 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
+        2FGL J1615.0-5051    &       12.2 &       16.7 &     332.39\deg &      -0.07\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.6$  &     332.43\deg &      -0.35\deg & $       0.4 \pm        0.1$ & $  2.4 \pm   0.5$ \\
+        2FGL J1615.2-5138    &       37.0 &       48.0 &     331.76\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.3 \pm   0.5$  &     331.47\deg &      -0.80\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.4$ \\
+        2FGL J1632.4-4753c   &       40.6 &       64.5 &     336.52\deg &       0.17\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
+        2FGL J1837.3-0700c   &       12.6 &       18.8 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.5$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
+        2FGL J2021.5+4026    &       24.3 &      116.4 &      78.28\deg &       1.95\deg & $       0.3 \pm        0.1$ & $  5.0 \pm   0.0$  &      78.15\deg &       2.20\deg & $       0.6 \pm        0.1$ & $  1.7 \pm   0.4$ \\
         \hline
@@
         \hline
-        2FGL J0823.0-4246    &                347.3 &                314.7 &                343.9 &                     66.1 &                   46.1 &                 53.4 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
-        2FGL J1627.0-2425c   &                154.9 &                130.3 &                102.4 &                     32.6 &                   20.3 &                 23.8 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
-        2FGL J1554.4-5317c   &                134.8 &                150.8 &                139.4 &                     39.4 &                   37.6 &                 38.0 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
+        2FGL J0823.0-4246    &                350.9 &                320.9 &                352.5 &                     66.0 &                   46.3 &                 53.6 & $  0.37\deg \pm   0.03\deg$ & $  0.39\deg \pm   0.03\deg$ \\
+        2FGL J1627.0-2425c   &                170.2 &                144.5 &                112.6 &                     43.9 &                   31.1 &                 23.9 & $  0.41\deg \pm   0.05\deg$ & $  0.40\deg \pm   0.04\deg$ \\
+        2FGL J1712.4-3941    &                 80.9 &                 75.0 &                 43.4 &                     47.4 &                   39.6 &                 22.2 & $  0.56\deg \pm   0.04\deg$ & $  0.56\deg \pm   0.04\deg$ \\
         \hline
@@
         \hline
-        2FGL J0851.7-4635    &                120.2 &                120.0 &                126.1 &                     90.1 &                   76.7 &                 82.9 & $  1.12\deg \pm   0.07\deg$ & $  1.12\deg \pm   0.08\deg$ \\
-        2FGL J1615.0-5051    &                 52.5 &                 54.0 &                 57.4 &                     17.5 &                   16.6 &                 12.4 & $  0.33\deg \pm   0.04\deg$ & $  0.33\deg \pm   0.04\deg$ \\
-        2FGL J1615.2-5138    &                 76.2 &                 75.9 &                 89.4 &                     44.3 &                   47.6 &                 55.9 & $  0.42\deg \pm   0.03\deg$ & $  0.43\deg \pm   0.03\deg$ \\
-        2FGL J1632.4-4753c   &                126.9 &                128.3 &                120.4 &                     64.0 &                   64.8 &                 63.7 & $  0.44\deg \pm   0.04\deg$ & $  0.44\deg \pm   0.04\deg$ \\
-        2FGL J1837.3-0700c   &                 45.5 &                 47.0 &                 39.0 &                     18.6 &                   20.2 &                 16.6 & $  0.35\deg \pm   0.08\deg$ & $  0.35\deg \pm   0.07\deg$ \\
-        2FGL J2021.5+4026    &                236.5 &                225.3 &                240.5 &                    156.0 &                  139.4 &                148.8 & $  0.59\deg \pm   0.03\deg$ & $  0.60\deg \pm   0.03\deg$ \\
+        2FGL J0851.7-4635    &                116.7 &                116.1 &                122.3 &                     87.1 &                   87.2 &                 90.4 & $  1.13\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
+        2FGL J1615.0-5051    &                 53.0 &                 54.3 &                 55.6 &                     18.1 &                   16.7 &                  3.4 & $  0.32\deg \pm   0.04\deg$ & $  0.32\deg \pm   0.04\deg$ \\
+        2FGL J1615.2-5138    &                 76.3 &                 76.6 &                 86.3 &                     44.0 &                   48.0 &                 52.6 & $  0.42\deg \pm   0.03\deg$ & $  0.43\deg \pm   0.03\deg$ \\
+        2FGL J1632.4-4753c   &                126.6 &                127.8 &                120.7 &                     63.9 &                   64.5 &                 64.1 & $  0.44\deg \pm   0.04\deg$ & $  0.44\deg \pm   0.04\deg$ \\
+        2FGL J1837.3-0700c   &                 45.4 &                 46.2 &                 39.0 &                     18.5 &                   18.8 &                 16.6 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
+        2FGL J2021.5+4026    &                234.3 &                222.2 &                235.6 &                    135.9 &                  116.4 &                121.4 & $  0.59\deg \pm   0.03\deg$ & $  0.60\deg \pm   0.03\deg$ \\
       \end{tabular}
@@
       and \pointlike.  It also compares the fit values using the standard
-      diffuse model and using the alternate diffuse model described
+      diffuse model and using the alternative diffuse model described
       in section~\ref{alt_diff_model_description}.  $\ts_\pointlike$
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-  \caption{A galactic and isotropic diffuse subtracted 1 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 1 \gev to 100
   \gev counts map of the region around 2FGL J0823.0-4246 smoothed by a
@@
   \caption{
-  A galactic and isotropic diffuse subtracted 1 \gev to 100 \gev counts
+  A Galactic and isotropic diffuse subtracted 1 \gev to 100 \gev counts
   map of the region around 2FGL J1627.0-2425 smoothed by a 0.1\deg
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1554.0-5345c}
-  \end{center}
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1554.0-5345c/v2/source_1FGL_J1554.0-5345c.pdf
-  \caption{
-  A galactic and isotropic diffuse subtracted 1 \gev to 100 \gev
-  counts map of the region around 2FGL J1554.4-5317c smoothed by a
-  0.1\deg Gaussian kernel.  The red star is the catalog position of
-  2FGL J1554.4-5317c.  The red cross and circle are the best
-  fit position and extension of this source assuming a uniform disk
-  spatial model.  The green star represents the catalog source 2FGL
-  J1551.3-5333c which was removed because it was part of
-  the extended source.  Because the source has no obvious counterpart and
-  is in a region of large diffuse emission, the source is most likely
-  unmodeled diffuse emission.  More information about this source can be
-  found in section~\ref{section_2FGL_J1554.4-5317c}.
-  }
-  \label{1FGL_J1554.0-5345c}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
     \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
-  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
   \gev counts map of the region around 2FGL J0851.7-4635 smoothed by
@@
   and extension of the source assuming a uniform disk spatial model.
-  Three nearby catalog sources 2FGL J0848.5-4535,
-  2FGL J0855.4-4625, and 2FGL J0853.5-4711 were removed 
+  The inner three green stars are (from left to right)
+  2FGL J0853.5-4711,
+  2FGL J0855.4-4625, and
+  2FGL J0848.5-4535 which were 
+  removed 
   because they are part of the extended source.  The farther away
-  green star is 2FGL J0858.0-4815 which was removed 
-  because it was not significant above 10 \gev.  The blue stars and
-  crosses are the catalog positions and the relocalized positions of (from
-  left to right) 2FGL J0901.7-4655 and 2FGL J0854.7-4501.  This
+  green stars are (from left to right) 
+  2FGL J0901.7-4655 and
+  2FGL J0858.0-4815 which were removed 
+  because they were not significant above 10 \gev.  The blue cross 
+  is the relocalized position of
+  2FGL J0854.7-4501.  This
   extended source is spatially coincident with the Vela Jr SNR.
@@
   \caption{
-    A galactic and isotropic diffuse subtracted 10 \gev to 100 \gev counts
+    A Galactic and isotropic diffuse subtracted 10 \gev to 100 \gev counts
     map of the region around 2FGL J1615.0-5051 and 2FGL J1615.2-5138
@@
     inside of the extension of 2FGL J1615.2-5138  is 2FGL J1614.9-5212
-    which was removed because it is part of the extended emission.
+    which was removed because it is part of the extended source.
     The greeen stars to the left are 2FGL J1619.7-5040c and 2FGL
@@
     the extended source HESS J1614-518 and the extended source HESS
-    J1616-508 measured by H.E.S.S.(\cite{HESS_plane_survey}). 2FGL
+    J1616-508 measured by H.E.S.S.(\cite{hess_plane_survey}). 2FGL
     J1615.0-5051 is spatially
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
-  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
   \gev counts map of the region around 2FGL J1632.4-4753c smoothed by
@@
   contours are the \tev emission seen by H.E.S.S. 
-  (\cite{HESS_plane_survey}). More information about this source 
+  (\cite{hess_plane_survey}). More information about this source 
   can be found in section~\ref{section_2FGL_J1632.4-4753c}.
@@
   \caption{
-  A galactic and isotropic diffuse subtracted 10 \gev to 100 \gev
+  A Galactic and isotropic diffuse subtracted 10 \gev to 100 \gev
   counts map of the region around 2FGL J1837.3-0700c smoothed by a
@@
   J1837-069.  The light blue contours are the \tev emission of HESS J1837-069
-  observed by H.E.S.S (\cite{HESS_plane_survey}).  More information about
+  observed by H.E.S.S (\cite{hess_plane_survey}).  More information about
   this source can be found in section~\ref{section_2FGL_J1837.3-0700c}.
@@
   \end{center}
-  \caption{A galactic and isotropic diffuse subtracted 1 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 1 \gev to 100
   \gev counts map of the region around 2FGL J1712.4-3941 smoothed by a
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
-  \caption{A galactic and isotropic diffuse subtracted 10 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
   \gev counts map of the region around 2FGL J2021.5+4026 smoothed by a
@@
 
+\clearpage
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics{summary_plots/allsky_extended_sources.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v1/run.py
+    \end{center}
+    \caption{A plot of all \gev extended sources detected by the LAT
+    with two years of data.  The twelve extended sources included in
+    2FGL are the red markers and the nine additional
+    extended sources analyzed in this paper are the orange markers. The
+    extended sources are overlaid on an Aitoff projection Galactic
+    coordinate map of all 100 \mev to 100 \gev photons measured by the
+    LAT in the two year time interval of this analysis.
+    }\label{allsky_extended_sources}
+  \end{sidewaysfigure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{summary_plots/gev_vs_tev_plot.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v1/run.py
+    \end{center}
+    \caption{
+    A comparison of the \gev and \tev sizes of LAT
+    extended sources detected by \tev instruments.  The \tev
+    extensions of W30, 2FGL J1837.3-0700c, 2FGL J1632.4-4753c,
+    2FGL J1615.0-5051, and 2FGL J1615.2-5138 are from the
+    H.E.S.S. Galactic plane survey (\cite{hess_plane_survey}).
+    The \tev extensions of MSH 15-52, HESS J1825-137, Vela X,
+    Vela Jr., RX J1713.7-2946 and W28 are respectively from H.E.S.S.
+    (\cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}).
+    The \tev extension of IC443 is from Veritas (\cite{ic443_veritas})
+    and W51c is from Magic (\cite{w51c_with_magic_at_fermi_symposium}).
+    The LAT extension of Vela X is from (\cite{velax}).  Except for RX
+    J1713.7-2946 Vela Jr., the \tev sources were fit with a Gaussian
+    spatial model so the plotted \gev and \tev extensions were first
+    converted to \rsixeight (see section~\ref{compare_source_size}).
+    Because of their large size, the RX J1713.7-2946 and Vela Jr.
+    were not directly fit in \tev and do not have errors associated with
+    their measurements. The \tev radius of RX J1713.7-2946 is taken to
+    be 0.5\deg and Vela Jr. is taken to be 1\deg. For these two sources,
+    the LAT size is not converted to \rsixeight but the disk extension
+    is directly compared.  This plot shows that there is good correlation
+    between the \gev and \tev sizes of sources.
+    }\label{gev_vs_tev_plot}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{summary_plots/gev_vs_tev_histogram.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v2/extension_histogram.py
+    \end{center}
+    \caption{
+    A comparison of the size of detected LAT and H.E.S.S sources.
+    The extension of the 22 extended LAT sources comes from
+    table~\ref{known_extended_sources}, table~\ref{new_ext_srcs_table},
+    and the LAT extension of Vela X is taken from (\cite{velax}). The
+    Centarus A lobes, which have an extension $~10\deg$, are not
+    included in the plot (\cite{cen_a_lat}).  The \tev extension of
+    the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
+    Catalog (\cite{hesscat}).  Except for RX J1713.7-2946 and Vela Jr.,
+    the H.E.S.S. sources were fit with a Gaussian spatial model and
+    so the LAT and H.E.S.S. sizes are first converted to \rsixeight.
+    (see section~\ref{compare_source_size}). Beacuse the spatial
+    morphology of RX J1713.7-2946 and Vela Jr. is poorly matched by a
+    gaussian, the \tev sizes are assuming a uniform disk spatial model
+    and so neither the \gev nor \tev sizes were converted.  This plot
+    shows that \tev experiments are sensitive to smaller extended sources.
+    }\label{gev_vs_tev_histogram}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{summary_plots/compare_index_2FGL.pdf}
+    \end{center}
+    \caption{
+    The distribution of spectral indices of all 1873 2FGL sources in
+    red and all spatially extended sources in blue.  in 2FGL. The
+    spectral indices of LAT extended sources are taken from
+    table~\ref{known_extended_sources} table~\ref{new_ext_srcs_table}.
+    The index of centarus A is taken to be 2.58 from the two year catalog
+    (\cite{second_cat}) and the the index of Vela X is taken to be 2.41
+    from (\cite{velax}). This plot shows that many of the LAT
+    extended sources have a very harder spectral index.
+    }\label{compare_index_2FGL}
+  \end{figure}
+
 \end{document}

### 2011-07-29 extended_catalog/paper/extended_catalog.tex
improvements
adding stefan's introduciton

@@
 The Large Area Telescope (LAT) is a pair conversion telescope on the
-Fermi Gamma-Ray Space Telescope (Fermi). It has been surveying the $\gamma$-ray
-sky since June 2008.  Fermi is well suited as a survey
-instrument because of its broad energy coverage (20 \mev
-to $>300$ \gev), wide field of view ($\sim 2.4 \sr$), and large effective
-area ($\sim 8000 \cm^2$ at $>1 \gev$).
+Fermi Gamma-Ray Space Telescope (Fermi). It has been surveying the
+$\gamma$-ray sky since June 2008.  Fermi is well suited as a survey
+instrument because of its broad energy coverage (20 \mev to $>300$
+\gev), wide field of view ($\sim 2.4 \sr$), and large effective area
+($\sim 8000 \cm^2$ at $>1 \gev$).
 
 Using two years of all sky surveying data, the LAT Collaboration
-published a catalog of 1873 \gev sources.
-Many of these were associated
-with a variety of source classes including Active Galactic Nuclei (AGN),
-pulsars, galaxies, and supernova remnants.  Many of these classes can be
-spatially resolved when observed at other frequencies and could possibly
-be spatially resolvable in \gev by the LAT.
-
-The LAT collaboration has previously reported on the discovered of
-five spatially extended supernova remnants (SNRs) IC443, W28, W44,
-W51C, and RX J1713.7-2946 (\cite{ic443,w28,w44,w51c,rx_j1713_lat}).
-The LAT Collaboration has reported on the detection of three extended
-pulsar wind nebulae (PWNe) MSH 15-52 and Vela X, and HESS J1825-137
-(\cite{msh1552,velax,fermi_hess_j1825}), the Large Magellanic
-and Small Magalenic Cloud (\cite{lmc,smc}), and the radio galaxy
-Centarus A (\cite{cen_a_lat}) .  There are other source classes which
-could possibly be spatially resolved by the LAT including galaxy clusters
-and dark matter satellite galaxies.
-
-Furthermore, a variety of spatially extended but otherwise unassociated
-sources have been detected in the Galactic plane at \tev energies using
-Air Cherenkov detectors. Most prominent was a survey of the Galactic
-plane using the High Energy Stereoscopic System (H.E.S.S) which presented
-14 spatially extended sources (\cite{hess_plane_survey}) sources with
-extensions varying from $~0.1\deg$ to $~0.25\deg$. Most \tev sources
-in the galaxy are spatially extended and it is expected that these same
-sources would have have extended \gev emission.
+published a catalog of 1873 \gev sources\cite{second_cat}. Many of these can
+be positionally associated with a variety of source classes including
+Active Galactic Nuclei (AGN), pulsars, galaxies, and supernova
+remnants (SNRs).  While many of these classes can be spatially
+resolved when observed at other frequencies, detection an extension at
+GeV energies by the LAT is complicated by the rather large
+point-spread function (PSF) of the instrument (the angular resolution
+for events converting in the front part of the detector, defined as
+the 68\% containment radius for a point source, is approximately
+$3.5^{\circ}$ at 100 MeV, improving to about 0.1$^{\circ}$ at 10 GeV).
+
+Several of these source classes are extended (and close) enough to
+potentially be extended. In particular supernova remnants, pulsar wind
+nebulae, molecular clouds, normal galaxies, galaxy clusters or dark
+matter satellites can (in favorable cases) be expected to be extended
+beyond the LAT's PSF. The LAT collaboration has previously reported on
+the discovered of five spatially extended supernova remnants, IC443,
+W28, W44, W51C, and RX J1713.7-3946
+(\cite{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended
+pulsar wind nebulae (PWNe) were detected: MSH 15-52, Vela~X, and
+HESS\,J1825-137 (\cite{msh1552,velax,fermi_hess_j1825}), as well as
+two close-by galaxies, the Large Magellanic and Small Magalenic Cloud
+(\cite{lmc,smc}), and finally the radio galaxy Centarus A
+(\cite{cen_a_lat}) .
+
+In addition to these GeV $\gamma$-ray detections, a variety of
+spatially extended sources have been detected in the Galactic plane at
+\tev energies using Air Cherenkov detectors. Most prominent was a
+survey of the Galactic plane using the High Energy Stereoscopic System
+(H.E.S.S) which presented 14 spatially extended sources
+(\cite{hess_plane_survey}) sources with extensions varying from
+$~0.1\deg$ to $~0.25\deg$. In fact, within our Galaxy only very few
+sources (most notably the $\gamma$-ray binaries
+LS\,5039\cite{HESSLS5039}, LS I+61-303\cite{MAGICLSI, VERITASLSI} and
+HESS\,J0632+057\cite{HESS0632} are amongst the few Galactic sources
+for which no significant extension was detected at \tev
+energies. Given these findings, it can be expected that if the source
+population at GeV energies has similar properties, that at least some
+of the Fermi-LAT sources in our Galaxy should be spatially extended at
+GeV energies.
 
 Being able to spatially resolve the \gev emission from a source is
-important for several reasons. Because of the large point spread
-function (PSF), there are often several possible source counterparts.
-Finding a matching morphology can be used to uniquely identify the source.
-Because of the largely varying PSF of the LAT, the spatial and spectral
-information about a source do not nicely decouple. Therefore, a biased
-spatial model will bias the spectral model of the source and studying
-the extension of the source can correct for this.  Furthermore, correctly
-modeling a source's extension is important for improving the overall model
-of the sky and removing excess residuals.  These residuals manifested
-themselves in 1FGL as spurious point sources in the region region
-surrounding the Large Magellanic Cloud (\cite{first_cat}).  For this
-reason, we are motivated to take the 1873 sources that were detected in
-2FGL and apply a search for those sources which are spatially extended.
+important for several reasons. Because of the large PSF and the large
+candidate source density in our Galaxy, source confusion is a severe
+problem for the Fermi-LAT. Finding a matching morphology can be used
+to uniquely identify the source.  Because of the strongly varying PSF
+of the LAT, the spatial and spectral information about a source do not
+simply decouple. Therefore, a biased spatial model will bias the
+spectral model of the source and studying the extension of the source
+can correct for this.  Furthermore, correctly modeling a source's
+extension is important for improving the overall model of the sky and
+removing excess residuals.  These residuals manifested themselves in
+1FGL as spurious point sources in the region region surrounding the
+Large Magellanic Cloud (\cite{first_cat}).  For this reason, we are
+motivated to take the 1873 sources that were detected in 2FGL and
+apply a search for those sources which are spatially extended.
 
@@
 
-\todo[inline]{note about how MSH 15-52 can't go lower in
-energy because of nearby pulsar.}
-
 % 1 radio galaxy
@@
 $\rsixeight=0.27\deg\pm0.03$ (see section~\ref{compare_source_size}).
+Figure~\ref{hess_seds} shows that the LAT spectrum of
+2FGL J1615.0-5051 connects smoothly to the 
+H.E.S.S spectrum of HESS J1616-508.
 
@@
 matches well the LAT size of $\rsixeight\sim0.34\pm0.02$.
+Figure~\ref{hess_seds} shows that the LAT spectrum of
+2FGL J1615.2-5138 connects smoothly to the 
+H.E.S.S spectrum of HESS J1614-518.
 
@@
 $\rsixeight=0.36\pm0.03$.
+Figure~\ref{hess_seds} shows that the LAT spectrum of
+2FGL J1635.4-4717c connects smoothly to the 
+H.E.S.S spectrum of HESS J1632-478.
 
@@
 confusion could be that the LAT source may be partially fitting other
-sources in the region.
+sources in the region.  Figure~\ref{hess_seds} shows that the LAT
+spectrum of 2FGL J1837.3-0700c connects smoothly to the H.E.S.S spectrum
+of HESS J1837-069.
 
@@
 
-This source is spatially conincident with the SNR RX J1713.7-2946 and was
+This source is spatially conincident with the SNR RX J1713.7-3946 and was
 recently reported by (\cite{rx_j1713_lat}).  To analyze this source,
@@
 the position of these nearby sources on top of a contour of SNR RX
-J1713.7-2946 seen in \tev by H.E.S.S (\cite{rx_j1713_hess}).
+J1713.7-3946 seen in \tev by H.E.S.S (\cite{rx_j1713_hess}).
 
@@
   0.25\deg Gaussian kernel.  This source is spatially coincident with
-  RX J1713.7-2946 was was recently reported by (\cite{rx_j1713_lat}).
+  RX J1713.7-3946 was was recently reported by (\cite{rx_j1713_lat}).
   The light blue contours are the \tev emission reported by
@@
 \clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{summary_plots/hess_seds.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v2/plot_seds/plot_seds.py
+    \end{center}
+    \caption{
+    }\label{hess_seds}
+  \end{figure}
+
+\clearpage
 \begin{sidewaysfigure}
@@
     The \tev extensions of MSH 15-52, HESS J1825-137, Vela X,
-    Vela Jr., RX J1713.7-2946 and W28 are respectively from H.E.S.S.
+    Vela Jr., RX J1713.7-3946 and W28 are respectively from H.E.S.S.
     (\cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}).
@@
     The LAT extension of Vela X is from (\cite{velax}).  Except for RX
-    J1713.7-2946 Vela Jr., the \tev sources were fit with a Gaussian
+    J1713.7-3946 Vela Jr., the \tev sources were fit with a Gaussian
     spatial model so the plotted \gev and \tev extensions were first
     converted to \rsixeight (see section~\ref{compare_source_size}).
-    Because of their large size, the RX J1713.7-2946 and Vela Jr.
+    Because of their large size, the RX J1713.7-3946 and Vela Jr.
     were not directly fit in \tev and do not have errors associated with
-    their measurements. The \tev radius of RX J1713.7-2946 is taken to
+    their measurements. The \tev radius of RX J1713.7-3946 is taken to
     be 0.5\deg and Vela Jr. is taken to be 1\deg. For these two sources,
@@
     the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-    Catalog (\cite{hesscat}).  Except for RX J1713.7-2946 and Vela Jr.,
+    Catalog (\cite{hesscat}).  Except for RX J1713.7-3946 and Vela Jr.,
     the H.E.S.S. sources were fit with a Gaussian spatial model and
@@
     (see section~\ref{compare_source_size}). Beacuse the spatial
-    morphology of RX J1713.7-2946 and Vela Jr. is poorly matched by a
+    morphology of RX J1713.7-3946 and Vela Jr. is poorly matched by a
     gaussian, the \tev sizes are assuming a uniform disk spatial model

### 2011-07-29 extended_catalog/paper/extended_catalog.tex
better legedn

@@
     \caption{
+    The spectral energy distribution of four the extended sources
+    associated with extended \tev sources.  The black points
+    with circular markers are the LAT data points. The red points
+    with dashed markers are H.E.S.S points of associated sources.
+    Figure~\ref{hess_seds}a shows the \gev SED of 2FGL J1615.0-5051
+    and \tev SED of HESS J1616-508.  Figure~\ref{hess_seds}b shows
+    the \gev SED of 2FGL J1615.2-5138 and \tev SED of HESS J1614-518
+    Figure~\ref{hess_seds}c shows the \gev SED of 2FGL J1632.4-4753c
+    and \tev SED of HESS J1634-472 Figure~\ref{hess_seds}d shows the
+    \gev SED of 2FGL J1837.3-0700c and \tev SED of HESS J1837-069.
+    The H.E.S.S. data points are from (\cite{hess_plane_survey}).
+    Both LAT and H.E.S.S. spectral errors are systematic only.
     }\label{hess_seds}

### 2011-07-29 extended_catalog/paper/extended_catalog.tex
draft improvements

@@
 sources (most notably the $\gamma$-ray binaries
-LS\,5039\cite{HESSLS5039}, LS I+61-303\cite{MAGICLSI, VERITASLSI} and
-HESS\,J0632+057\cite{HESS0632} are amongst the few Galactic sources
+LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI}) and
+HESS\,J0632+057 (\cite{HESS0632}) are amongst the few Galactic sources
 for which no significant extension was detected at \tev
@@
 for regions near pulsars which cutoff before 10 \gev
-and was successfully used in detecting HESS J1825-137
+and was successfully used in detecting HESS\,J1825-137
 and MSH 15-52 with the LAT (\cite{msh1552,fermi_hess_j1825}).
@@
 the map, the Galactic and isotropic diffuse emission are subtracted.
-A 2FGL source 2FGL J1856.2+0450c was found at the position
+A 2FGL source 2FGL\,J1856.2+0450c was found at the position
 $(l,b)=(37.25\deg,0.84\deg)$.  We find that there appears to be overall
 some large-scale residual in the diffuse emission along the Galactic
-plane. As a result, 2FGL J1856.2+0450c fits to a
+plane. As a result, 2FGL\,J1856.2+0450c fits to a
 large extension of 1.83\deg and the result is statistically significant
@@
 % 3 PWN
-Three pulsar wind nebula Vela X, MSH 15-52, and HESS J1825-137 were
+Three pulsar wind nebula Vela X, MSH 15-52, and HESS\,J1825-137 were
 included in 2FGL (\cite{velax,msh1552,fermi_hess_j1825}).  Using photons
 with energy above 10 \gev, we significantly detected the extension of
-HESS J1825-137.  To improve the model of this source, we removed the
-nearby catalog source 2FGL J1823.1-1338c which is part of the extended
+HESS\,J1825-137.  To improve the model of this source, we removed the
+nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
 source.  To avoid the nearby pulsar PSR J1509-5850, MSH 15-52 must be
@@
 This table includes the best fit position and extension of these
-sources when fitting them with a radially symmetric uniform disk spatial
+sources when fitting with a radially symmetric uniform disk spatial
 model.  It also includes the best fit spectral model of each source.
@@
 
-To validate our method and assess systematic issues with our analysis,
-we used \pointlike to test known AGN for extension.
-\gev emission from AGN is believed to comes from the core of supermassive
-blackholes in small regions in the core of distant galaxies.  AGN are
-not expected to be spatially resolvable and therefore provide a good
-calibration source to demonstrate the efficacy of our tool. Nevertheless,
-it would be interesting if AGN could be spatially resolved and
-there are theories that predict this (\cite{pair_halo_paper}).
-
-Following 1FGL, the LAT collaboration published
-a list of sources that had a high probability association with
-AGN (\cite{first_agn_cat}).
-1FGL had 709 AGN associated with 671 distinct
-1FGL sources at high latitude ($|b|>10\deg$).  To avoid systematic
-problems with AGN classification, we used only the 599 AGN which made
-it into the clean AGN sample.  An AGN association is only considered
-clean if it has a high probability of association $P\ge 80\%$, if it is
-the only AGN associated with the 1FGL source, and if there are no flags
-on the catalog source (\cite{first_cat}). These last two conditions are
-especially important for our analysis.  Source confusion may look like
-a spatially extended source and flagged catalog sources may correlate
-with unmodeled structure in the diffuse emission.
-
-Of the 599 ``clean'' AGN, we select 556 of these 1FGL sources which
-we uniquely associate with a 2FGL source. We furthermore
-restrict our select to the 515 of these AGN for which we fit $\ts>25$
-using \pointlike and photons with energy above 1 \gev.  Our intention
-here is not to find the largest sample of AGN but simply
-to find a good sample to test the systematics of our extended source
-search.
-
-Using the same extension fitting procedure as described above, we tested
-these 515 AGN for extension. A histogram of the \tsext values computed
-with \pointlike is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot
-is a $\chi^2/2$ distribution suggested by Wilks' Theorem.  This plot
-shows a worse agreement with the theoretical distribution and
-a discrepancy with 
-our Monte Carlo study in figure~\ref{ts_ext_mc}.  But overall, the
-distribution is good. No AGN get fit with a particularly significant
-value of $\tsext$ and almost all of the AGN get fit with $\tsext<1$.
-There where only two AGN with $\tsext>10$. The maximum had $\tsext=13.7$
-whereas the maximum value expected theoretically by the $\chi^2/2$ distribution is
-8.3. This result shows that there is some systematic with our
-analysis but that it will not significantly affect our analysis.
-% 8.3 number gotten from mathematica:
-% PDF[ChiSquareDistribution[1], x]
-% N[Solve[(1/2)*
-%     Integrate[1/(E^(x/2)*(Sqrt[2*Pi]*Sqrt[x])), {x, TS, Infinity}] &=&  
-%        1/515, TS]]
-
-Several possible systematics could cause this discrepancy. The first is
-that in our analysis we fit each source with a power-law spectral model.
-AGN tend to have curved spectral and fitting with the wrong spectral
-model might effect the value of \tsext. Nevertheless, since we use only
-photons with energy above 1 \gev, this effect is not expected to be large.
-Another possible source for the discrepancy is that \pointlike performs
-a likelihood analysis without modeling the energy dispersion of the LAT.
-This probably is not the cause because energy dispersion is expected to
-be more significant at low energy and it would have also showed up with
-the Monte Carlo simulations.
-
-Another possible systematic may be due to source confusion to problems
-with the background model. If the two sources were close, they may
-be unresolvable and get fit as a more significant extended source.
-It is also possible that there are lingering residuals in the diffuse
-emission. Unmodeled parts of the diffuse emission could be filled in by
-modeling point sources as being slightly extended.
+To validate our method, we test associated AGN for extension.  \gev
+emission from AGN is believed to comes from the core of supermassive
+blackholes in small regions in the core of distant galaxies. Therefore AGN
+are not expected to be spatially resolvable and provide a good calibration
+source to demonstrate the efficacy of our tool. Nevertheless, it would
+be interesting if AGN could be spatially resolved and there are theories
+that predict this (\cite{pair_halo_paper}).
+
+Following 1FGL, the LAT collaboration published a list of sources that
+had a high probability association with AGN (\cite{first_agn_cat}).
+1FGL had 709 1FGL sources associated with 671 distinct AGN at high
+latitude ($|b|>10\deg$).  An upcoming publication by the LAT collaboration
+using two years of data and the 2FGL catalog associates 1017 2FGL sources
+with AGN.  To avoid systematic problems with AGN classification, we
+selected the 815 AGN which made it into the clean AGN sample.  An AGN
+association is considered clean only if it has a high probability
+of association $P\ge 80\%$, if it is the only AGN associated with the
+catalog source, and if there are no flags on the source in 2FGL. These
+last two conditions are especially important for our analysis. Source
+confusion may look like a spatially extended source and flagged catalog
+sources may correlate with unmodeled structure in the diffuse emission.
+
+Of the 815 clean AGN, we select 775 of these 2FGL sources which
+are significant above 1 \gev and fit each of them for extnesion.
+A histogram of the \tsext values computed for these AGN is shown
+in figure~\ref{agn_ts_ext}. Overlaid on the plot is a $\chi^2/2$
+distribution suggested by Wilks' Theorem.  The \tsext distribution
+for AGN shows good agreement between the theoretical distribution.
+Two sources had $\tsext>9$.  One was due to incorrectly
+    pruning a nearby catalog sources and the other was due to failure
+    of convergence of the point hypothesis.
+This result demonstrates that we can use \tsext as a measure of the
+statistical significance of the detection of the extension of a source.
 
 The final effect that could cause this discrepancy is an imperfect
-modeling of the PSF.  Before launch, the PSF
-was determined by a Monte Carlo simulation of the detector.
-After launch, a discrepancy was found using flight data above a
-few \gev in the PSF measured using bright AGN.  This result
-was presented in conference and a publication is in preparation.
-Subsequently, the PSF was fit empirically to bright AGN and this
-empirical parameterization was used in the LAT's instrument
-response function (\cite{lat_on_orbit_psf}).
-But the current parameterization is not perfect. There are lingering
-issues due to a lack of statistics at high energy which makes it hard to
-validate the PSF as a function of the incident angle of the photon. Since
-the distribution of incident angles varies from source to source, an
-average PSF may make some of the sources look more and less extended
-than the PSF.
-
-We should finally clarify that since the PSF was found empirically
-from the shape of bright AGN, finding that the AGN we test are not
-significantly extended is not surprising.  All this analysis shows
-is that the we can significantly find sources larger than bright AGN
-found by the LAT.  Trying to look for the extension of these AGN as a
-population would require a more specialized analysis.
+modeling of the PSF.  Before launch, the PSF was determined by a Monte
+Carlo simulation of the detector.  After launch, a discrepancy was found
+using flight data above a few \gev in the PSF measured using bright
+AGN.  This result was presented in conference and a publication is in
+preparation.  Subsequently, the PSF was fit empirically to bright AGN and
+this empirical parameterization was used in the LAT's instrument response
+function (\cite{lat_on_orbit_psf}).  But the current parameterization
+is not perfect. There are lingering issues due to a lack of statistics
+at high energy which makes it hard to validate the PSF as a function of
+the incident angle of the photon. Since the distribution of incident
+angles varies from source to source, an average PSF may make some of
+the sources look more and less extended than the PSF.
+
+We should finally clarify that the LAT PSF used in this study was
+determined empirically by fitting the observed shape of bright AGN
+(\cite{lat_on_orbit_psf}).  Therefore, finding that the AGN we test are
+not extended is not surprising.  All this analysis shows is that the we
+can search for sources significantly brighter than AGN.  Trying to look
+for the extension of AGN would require a more specialized analysis.
 
@@
 
-\subsection{2FGL J0823.0-4246}
+\subsection{2FGL\,J0823.0-4246}
 \label{section_2FGL_J0823.0-4246}
@@
 
-The two year catalog source 2FGL J0823.0-4246 was found to be
+The two year catalog source 2FGL\,J0823.0-4246 was found to be
 extended using photons with energy between 1 \gev and 100 \gev.
 We found an extension of $0.37\deg\pm0.03\deg$ and an extension
-significance of $\tsext=46.1$.  The source was fit to a position of
+significance of $\tsext=46.3$.  The source was fit to a position of
 $(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
 counts map of this source.  This source is coincident with the one year
-catalog source 1FGL J0823.3-4248.
+catalog source 1FGL\,J0823.3-4248.
 
 To get a good fit of the source, we had to remove the nearby catalog
-sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
+sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which are part of the
 extended source.  We tested the source for source confusion by fitting
-it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
+it as two point sources. Because $\tsinc=22.1$ is smaller then \tsext,
 we conclude that this is an extended source.  
@@
 
-\todo[inline]{Add interpretations of Puppis A. Stefan volunteered to write this}
-
-\subsection{2FGL J1627.0-2425c}
+\todo[inline]{Add interpretations of Puppis A.}
+
+\subsection{2FGL\,J1627.0-2425c}
 \label{section_2FGL_J1627.0-2425c}
@@
 
-The two year catalog source 2FGL J1627.0-2425c was found to be
+The two year catalog source 2FGL\,J1627.0-2425c was found to be
 significantly extended when using photons with energies between 1 \gev
-and 100 \gev.  The best fit extension was $0.53\deg\pm0.06\deg$ and the
-best fit position is $(l,b)=(352.87\deg, 16.79\deg)$.
-The extension significance was $\tsext=20.3$. 
-This source is coincident with the one year catalog source 1FGL J1628.6-2419c.
+and 100 \gev.  The best fit extension was $0.41\deg\pm0.05\deg$ and the
+best fit position is $(l,b)=(353.08\deg, 16.78\deg)$.
+The extension significance was $\tsext=31.1$. 
+This source is coincident with the one year catalog source 1FGL\,J1628.6-2419c.
 A counts map showing this source is
 seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
-we also fit the source instead as two point sources. Since $\tsinc=19.3$
+we also fit the source instead as two point sources. Since $\tsinc=20.0$
 is smaller than \tsext, we conclude that this is an extended source.
@@
 
-\subsection{2FGL J0851.7-4635}
+\subsection{2FGL\,J1712.4-3941}
+\label{section_2FGL_J1712.4-3941}
+
+% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
+% New Source:
+%  * SkyDir(346.85102135118683,0.24359779858357899,SkyDir.GALACTIC),
+% Delete:
+%  * P72Y2685 - Not in 2FGL
+%  * P72Y2680 - Not in 2FGL
+%  * P72Y2689 - Not in 2FGL
+
+The two year catalog source 2FGL\,J1712.4-3941 was found to be
+spatially extended using photons with energies between 1 \gev and
+100 \gev. The source is coincident with the one year catalog source
+1FGL\,J1711.7-3944c. We fit an extension of $0.56\deg\pm0\pm04$ with an
+extension significance of $\tsext=39.6$. This source was fit to a position
+of $(l,b)=(347.25\deg,-0.54\deg)$. Figure \ref{2FGL_J1712.4-3941} shows
+a smoothed counts map of this source.
+
+This source is spatially conincident with the SNR RX J1713.7-3946 and was
+recently reported by (\cite{rx_j1713_lat}).  To analyze this source,
+we used the same background model as the recent LAT publication.
+2FGL\,J1715.4-4024c is spatially coincident with Source A and was
+moved to the published location of 
+$(\text{RA},\text{Dec})=(258.84,-40.46)$. Source
+B was added at 
+$(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
+$(\text{RA},\text{Dec})=(257.47,-39.75)$.  Figure \ref{2FGL_J1712.4-3941} shows
+the position of these nearby sources on top of a contour of SNR RX
+J1713.7-3946 seen in \tev by H.E.S.S (\cite{rx_j1713_hess}).
+
+\subsection{2FGL\,J0851.7-4635}
 \label{section_2FGL_J0851.7-4635}
@@
 
-The two year catalog source 2FGL J0851.7-4635 was found to be
+The two year catalog source 2FGL\,J0851.7-4635 was found to be
 extended using photons with energies between 10 \gev and 100
-\gev. We fit an extension of $1.12\deg\pm0.07\deg$ with an extension
-significance of $\tsext=76.7$.  The source was fit to a position of
-$(l,b)=(266.29\deg,-1.41\deg)$.  Figure~\ref{Vela_Jr} shows a counts
+\gev. We fit an extension of $1.13\deg\pm0.08\deg$ with an extension
+significance of $\tsext=87.2$.  The source was fit to a position of
+$(l,b)=(266.29\deg,-1.43\deg)$.  Figure~\ref{Vela_Jr} shows a counts
 map of this source.
 
-2FGL J0851.7-4635 is spatially coincident with the SNR Vela Jr.  Overlaid
+2FGL\,J0851.7-4635 is spatially coincident with the SNR Vela Jr.  Overlaid
 on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in \tev by
@@
 \todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming
-publication? Stefan volunteered to write this.}
+publication?}
 
 To get a good fit of the source, we had to remove thee nearby catalog
-sources 2FGL J0853.5-4711, 2FGL J0848.5-4535, and 2FGL J0855.4-4625
+sources 2FGL\,J0853.5-4711, 2FGL\,J0848.5-4535, and 2FGL\,J0855.4-4625
 which are part of the extended source.  In addition, we relocalized
-the position of the nearby catalog source 2FGL J0854.7-4501 to
+the position of the nearby catalog source 2FGL\,J0854.7-4501 to
 $(l,b)=(266.24\deg,0.49\deg)$ to better fit its position at high energies
-in the presence of of the eextended source.  In addition, we removed the
-further away catalog sources 2FGL J0858.0-4815 and 2FGL J0901.7-4655
+in the presence of of the extended source.  In addition, we removed the
+further away catalog sources 2FGL\,J0858.0-4815 and 2FGL\,J0901.7-4655
 because they were not significant above 10 \gev.  After modifying
-the region, we found that \tsinc=16.2 which is less than \tsext so we
+the region, we found that \tsinc=16.1 which is less than \tsext so we
 conclude that the source is extended These modifications are shown in
@@
 
-\subsection{2FGL J1615.0-5051}
+\subsection{2FGL\,J1615.0-5051}
 \label{section_2FGL_J1615.0-5051}
@@
 
-The two year catalog source 2FGL J1615.0-5051 was found to be
+The two year catalog source 2FGL\,J1615.0-5051 was found to be
 extended using photons with energies between 10 \gev and 100 \gev.
 We found an extension of $0.33\deg\pm0.04\deg$ with an extension
-significance of \tsext=16.6.  The source was fit to a position of
+significance of \tsext=16.3.  The source was fit to a position of
 $(l,b)=(332.38\deg,-0.14\deg)$.  This source is coincident with the one
-year catalog source 1FGL J1613.6-5100c.  Figure~\ref{1FGL_J1613.6-5100c}
+year catalog source 1FGL\,J1613.6-5100c.  Figure~\ref{1FGL_J1613.6-5100c}
 shows a counts map of this source.
 
-This source is less than 1\deg away from 2FGL J1615.2-5138 which is
+This source is less than 1\deg away from 2FGL\,J1615.2-5138 which is
 also spatially extended (see section~\ref{section_2FGL_J1615.2-5138}).
@@
 of each source until obtaining a global best fit.  Before doing this,
-We removed from our model the source 2FGL J1614.9-5212 because it is
-part of 2FGL J1615.2-5138's. Furthermore, we removed
-the nearby catalog sources 2FGL J1619.7-5040c and 2FGL J1620.6-5111c
+We removed from our model the source 2FGL\,J1614.9-5212 because it is
+part of 2FGL\,J1615.2-5138's. Furthermore, we removed
+the nearby catalog sources 2FGL\,J1619.7-5040c and 2FGL\,J1620.6-5111c
 because they were not significant above 10 \gev.  These modifications
 are further described in the caption to figure~\ref{1FGL_J1613.6-5100c}.
-After modifying the region, we found that \tsinc=12.2 which is less than
+After modifying the region, we found that \tsinc=11.9 which is less than
 \tsext so we conclude that the source is extended.
@@
 J1616-508 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
-contours of HESS J1616-508 are overlaid on 2FGL J1615.0-5051.
+contours of HESS\,J1616-508 are overlaid on 2FGL\,J1615.0-5051.
 The H.E.S.S. experiment measured an extension $0.136\pm 0.008$
@@
 This size corresponds to a 68\% source containment radius of
-$\rsixeight\sim0.21\deg\pm0.01$. This size is comparable to the LAT size
+$\rsixeight=0.21\deg\pm0.01$. This size is comparable to the LAT size
 $\rsixeight=0.27\deg\pm0.03$ (see section~\ref{compare_source_size}).
-Figure~\ref{hess_seds} shows that the LAT spectrum of
-2FGL J1615.0-5051 connects smoothly to the 
-H.E.S.S spectrum of HESS J1616-508.
-
-\todo[inline]{Add interpretations of HESS J1616-508.}
-
-\subsection{2FGL J1615.2-5138}
+Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
+connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.
+
+\todo[inline]{Add interpretations of HESS\,J1616-508.}
+
+\subsection{2FGL\,J1615.2-5138}
 \label{section_2FGL_J1615.2-5138}
 
-The two year catalog source 2FGL J1615.2-5138 was found to be
+The two year catalog source 2FGL\,J1615.2-5138 was found to be
 extended using photons with energies between 10 \gev and 100 \gev.
 We found an extension of $0.42\deg\pm0.03\deg$ with an extension
-significance of \tsext=47.6.  The source was fit to a position
+significance of \tsext=48.0.  The source was fit to a position
 of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
-with the one year catalog source 1FGL J1614.7-5138c.  Because 2FGL
-J1615.2-5138 is close to 2FGL J1615.0-5051, the same model described
+with the one year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
+J1615.2-5138 is close to 2FGL\,J1615.0-5051, the same model described
 in section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
 sources. Both sources can be seen in figure~\ref{1FGL_J1613.6-5100c}.
-For 2FGL J1615.2-5138, \tsinc=37.6 which is less than \tsext so we
+For 2FGL\,J1615.2-5138, \tsinc=37.0 which is less than \tsext so we
 conclude that the source is extended.
@@
 J1614-518 (\cite{hess_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
-contours of HESS J1614-518 are overlaid on 2FGL J1615.2-5138.
+contours of HESS\,J1614-518 are overlaid on 2FGL\,J1615.2-5138.
 The H.E.S.S. experiment measured a Gaussian extension of
@@
 of $\rsixeight=0.35\pm0.03\deg$ and $0.23\pm0.03$.  This elliptical size
-matches well the LAT size of $\rsixeight\sim0.34\pm0.02$.
+matches the LAT size $\rsixeight=0.34\pm0.02$.
 Figure~\ref{hess_seds} shows that the LAT spectrum of
-2FGL J1615.2-5138 connects smoothly to the 
-H.E.S.S spectrum of HESS J1614-518.
-
-\todo[inline]{Add interpretations of HESS J1614-518. Stefan says to
+2FGL\,J1615.2-5138 connects smoothly to the 
+H.E.S.S spectrum of HESS\,J1614-518.
+
+\todo[inline]{Add interpretations of HESS\,J1614-518. Stefan says to
 use the Rowell et al, Suzaku observations.}
 
-\subsection{2FGL J1632.4-4753c}
+\subsection{2FGL\,J1632.4-4753c}
 \label{section_2FGL_J1632.4-4753c}
@@
 
-The two year catalog source 2FGL J1632.4-4753c was found to be
+The two year catalog source 2FGL\,J1632.4-4753c was found to be
 extended using photons with energies between 10 \gev and 100 \gev.
 We fit an extension of $0.44\deg\pm0.04\deg$ with an extension
-significance of \tsext=64.8.  The source was fit to a position of
+significance of \tsext=64.5.  The source was fit to a position of
 $(l,b)=(336.41\deg,0.22\deg)$.  This source is coincident with the one
-year catalog source 1FGL J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
+year catalog source 1FGL\,J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
 shows a counts map of this source.
@@
 To get a good fit of the source, we had to remove from our model
-three catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752, 2FGL
-J1634.4-4743c.4-4820c that were part of the extended source..
-We then iterativly relocalized the source 2FGL J1635.4-4717c
-to $(l,b)=(337.230\deg,0.346\deg)$ and 2FGL J1636.3-4740c to
+three catalog sources 2FGL\,J1631.7-4720c, 2FGL\,J1630.2-4752,
+2FGL J1634.4-4743c.4-4820c that were part of the extended source..
+We then iterativly relocalized the source 2FGL\,J1635.4-4717c
+to $(l,b)=(337.230\deg,0.346\deg)$ and 2FGL\,J1636.3-4740c to
 $(l,b)=(336.968\deg,-0.066\deg)$ while fitting the extension of
-2FGL J1632.4-4753c.  In addition we removed from our model four
-farther away two year catalog sources 2FGL J1638.0-4703c, 2FGL
-J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL J1639.8-4921c because they
-were not significant above 10 \gev.  These modifications are shown in
-figure~\ref{1FGL_J1632.9-4802c}.
-
-To test for source confusion, we compared the likelihood fitting this
-region as one extended source to the likelihood fitting this region as
-two point sources. We found $\tsinc=40.9\loglikelihood\tsext$ which is less than \tsext
-so we conclude that this is an extended source.
-
-This extended source is spatially coincident with the extended \tev source HESS
-J1632-478 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1632.9-4802c},
-contours of  HESS J1632-478 are overlaid on 2FGL J1635.4-4717c.
-H.E.S.S measured an extension of $\sigma=0.21\pm0.05$ and
-$0.06\pm0.04$ along the semi-major and semi-minor axes when fitting the source
-with an elliptical Gaussian spatial model.  This corresponds to a 68\%
-containment size of $\rsixeight=0.31\pm0.08$ and $0.09\pm0.06$ along the
-semi-major and semi-minor axis. This size is consistent with the LAT size of
-$\rsixeight=0.36\pm0.03$.
-Figure~\ref{hess_seds} shows that the LAT spectrum of
-2FGL J1635.4-4717c connects smoothly to the 
-H.E.S.S spectrum of HESS J1632-478.
-
-\todo[inline]{Add interpretation of HESS J1632-478.}
-
-\subsection{2FGL J1837.3-0700c}
+2FGL\,J1632.4-4753c.  In addition we removed from our model four
+farther away two year catalog sources 2FGL\,J1638.0-4703c, 2FGL
+J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL\,J1639.8-4921c because they
+were not significant above 10 \gev.  These modifications are shown
+in figure~\ref{1FGL_J1632.9-4802c}.  To test for source confusion,
+we compared the likelihood fitting this region as one extended source
+to the likelihood fitting this region as two point sources. We found
+$\tsinc=40.6\loglikelihood\tsext$ which is less than \tsext so we conclude
+that this is an extended source.
+
+This extended source is spatially coincident with the extended
+\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).  In
+figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478 are
+overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured an extension of
+$\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
+axes when fitting the source with an elliptical Gaussian spatial model.
+This corresponds to a 68\% containment size $\rsixeight=0.31\pm0.08$
+and $0.09\pm0.06$ along the semi-major and semi-minor axis. This
+size is consistent with the LAT size $\rsixeight=0.36\pm0.03$.
+Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1635.4-4717c
+connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478.
+
+\todo[inline]{Add interpretation of HESS\,J1632-478.}
+
+\subsection{2FGL\,J1837.3-0700c}
 \label{section_2FGL_J1837.3-0700c}
@@
 
-The two year catalog source 2FGL J1837.3-0700c was found to be
+The two year catalog source 2FGL\,J1837.3-0700c was found to be
 extended using photons with energies between 10 \gev and 100 \gev.
 We fit an extension of $0.35\deg\pm0.08\deg$ with an extension
-significance of $\tsext=20.2$.  The source was fit to a position of
+significance of $\tsext=18.8$.  The source was fit to a position of
 $(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
-year catalog source 1FGL J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
+year catalog source 1FGL\,J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
 shows a counts map of this source.
 
-This source is in a complicated region. There are three nearby catalog
-sources 
-2FGL J1834.7-0705c, 2FGL J1836.8-0623c, and 2FGL J1839.3-0558c.
-To get a good fit of 2FGL J1837.3-0700c,
-we relocalized 
-2FGL J1834.7-0705c to $(l,b)=(24.77\deg,0.50\deg)$.  
-2FGL J1836.8-0623c moved to $(l,b)=(25.57\deg,0.32\deg)$, and 
-2FGL J1839.3-0558c to $(l,b)=(26.08\deg,0.23\deg)$.  
-We removed the nearby catalog source 2FGL J1835.5-0649 which is part
-of the extended source and the farther away catalog
-source 2FGL J1839.0-0539 because it was not significant above 10 \gev.
-After modifying the region, we found that \tsinc=12.3 which is less
-than \tsext, so we conclude that the source is spatially extended. These
-modifications are shown in figure~\ref{1FGL_J1837.5-0659c}.
-
-This source is spatially coincident with the \tev source HESS J1837-069
-(\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1837.5-0659c},
-contours of are H.E.S.S J1837-069 are overlaid on 2FGL
-J1837.3-0700c. H.E.S.S. measured an extension of $\sigma=0.12\pm0.02$
-and $0.05\pm0.02$ along the semi-major and semi-minor axis when fitting
-the source with an elliptical Gaussian spatial model.  This corresponds to
-a 68\% containment radius of $\rsixeight=0.18\pm0.03$ and $0.08\pm0.03$
-along the semi-major and semi-minor axis. The size is comparable to
-LAT which fit a 68\% containment radius of $\rsixeight=0.29\pm0.07$.
-The LAT size is larger than the H.E.S.S. size but the sizes are almost
-almost within the $1\sigma$ errors. It is possible that the morphologies
-are different but this is not very significant.  A possible reason is
-confusion could be that the LAT source may be partially fitting other
-sources in the region.  Figure~\ref{hess_seds} shows that the LAT
-spectrum of 2FGL J1837.3-0700c connects smoothly to the H.E.S.S spectrum
-of HESS J1837-069.
-
-\todo[inline]{Add interpretation of HESS J1837-069.}
-
-\subsection{2FGL J1712.4-3941}
-\label{section_2FGL_J1712.4-3941}
-
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
-% New Source:
-%  * SkyDir(346.85102135118683,0.24359779858357899,SkyDir.GALACTIC),
-% Delete:
-%  * P72Y2685 - Not in 2FGL
-%  * P72Y2680 - Not in 2FGL
-%  * P72Y2689 - Not in 2FGL
-
-The two year catalog source 2FGL J1712.4-3941 was found to be
-spatially extended using photons with energies between 10 \gev and
-100 \gev. The source is coincident with the one year catalog source
-1FGL J1711.7-3944c. We fit an extension of $0.56\deg\pm0\pm04$ with an
-extension significance of $\tsext=41.2$. This source was fit to a position
-of $(l,b)=(347.25\deg,-0.54\deg)$. Figure \ref{2FGL_J1712.4-3941} shows
-a smoothed counts map of this source.
-
-This source is spatially conincident with the SNR RX J1713.7-3946 and was
-recently reported by (\cite{rx_j1713_lat}).  To analyze this source,
-we used the same background model as the recent LAT publication.
-2FGL J1715.4-4024c is spatially coincident with Source A and was
-moved to the published location of $(ra,dec)=(258.84,-40.46)$. Source
-B was added at $(ra,dec)=(258.71,-38.70)$ and Source C was added at
-$(ra,dec)=(257.47,-39.75)$.  Figure \ref{2FGL_J1712.4-3941} shows
-the position of these nearby sources on top of a contour of SNR RX
-J1713.7-3946 seen in \tev by H.E.S.S (\cite{rx_j1713_hess}).
-
-\subsection{2FGL J2021.5+4026}
+This source is in a complicated region. There are three nearby
+catalog sources 2FGL\,J1834.7-0705c, 2FGL\,J1836.8-0623c, and
+2FGL\,J1839.3-0558c.  To get a good fit of 2FGL\,J1837.3-0700c, we
+relocalized 2FGL\,J1834.7-0705c to $(l,b)=(24.77\deg,0.50\deg)$,
+2FGL\,J1836.8-0623c to $(l,b)=(25.57\deg,0.32\deg)$, and
+2FGL\,J1839.3-0558c to $(l,b)=(26.08\deg,0.23\deg)$.  We removed the
+nearby catalog source 2FGL\,J1835.5-0649 which is part of the extended
+source and also the farther away catalog source 2FGL\,J1839.0-0539
+because it was not significant above 10 \gev. These modifications are
+shown in figure~\ref{1FGL_J1837.5-0659c}.  After modifying the region,
+we found that \tsinc=12.6 which is less than \tsext, so we conclude that
+the source is spatially extended.
+
+This source is spatially coincident with the \tev
+source HESS\,J1837-069 (\cite{hess_plane_survey}).  In
+figure~\ref{1FGL_J1837.5-0659c}, contours of are HESS\,J1837-069
+are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured an extension
+of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$ along the semi-major and
+semi-minor axis when fitting the source with an elliptical Gaussian
+spatial model.  This corresponds to a 68\% containment radius of
+$\rsixeight=0.18\pm0.03$ and $0.08\pm0.03$ along the semi-major
+and semi-minor axis. The size is comparable to LAT which fit a 68\%
+containment radius of $\rsixeight=0.29\pm0.07$.  The LAT size is larger
+than the H.E.S.S. size but the sizes are almost almost within the
+$1\sigma$ errors. Figure~\ref{hess_seds} shows that the LAT spectrum
+of 2FGL\,J1837.3-0700c connects smoothly to the H.E.S.S spectrum of
+HESS\,J1837-069.
+
+\todo[inline]{Add interpretation of HESS\,J1837-069.}
+
+\subsection{2FGL\,J2021.5+4026}
 \label{section_2FGL J2021.5+4026}
@@
 
-The two year catalog source 2FGL J2021.5+4026 was found to be extended
-using photons with energies between 10 \gev and 100 \gev. This source
-is coincident with the one year catalog source 1FGL J2020.0+4049. We
-fit an extension of $0.59\deg\pm0.03\deg$ with an extension
-significance of $\tsext=139.4$.  The source was fit to a position of
-$(l,b)=(78.17\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
-counts map of this source.
+The two year catalog source 2FGL\,J2021.5+4026 was found to be
+extended using photons with energies between 10 \gev and 100
+\gev. This source is coincident with the one year catalog source
+1FGL\,J2020.0+4049. We fit an extension of $0.59\deg\pm0.03\deg$ with
+an extension significance of $\tsext=116.4$.  The source was fit to a
+position of $(l,b)=(78.18\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049}
+shows a counts map of this source.
 
 To get a good fit of the source, we had to remove the nearby catalog
-source 2FGL J2019.1+4040 which were part of the extended source.
+source 2FGL\,J2019.1+4040 which were part of the extended source.
 Further, we found it necessary to add an additional point source not in
 the two year catalog into our background model.  The new source is was
-localized to a position of $(l,b)=(78.85,2.67)$ and had $\ts\approx 16$
-(using \pointlike).  Although the source is not very significant, not
-including it into the background model appeared visually to significantly
-throw off the fit of the region.  In addition, we removed the four
-further away catalog sources 2FGL J2022.8+3843c, 2FGL J2020.0+4159,
-2FGL J2013.8+4115c, and 2FGL J2012.4+3955c from the region because they
-were not significant above 10 \gev.  After modifying the region, we found
-that \tsinc=29.7 which is less than \tsext, so we believe that this
-source is spatially extended.  These modifications are further described
-in the caption to figure~\ref{1FGL_J2020.0+4049}.
+localized to a position of $(l,b)=(78.85,2.67)$ and had $\ts=13.5$ .
+Although the source is not very significant, not including it into the
+background model appeared visually to significantly throw off the fit
+of the region.  In addition, we removed the four further away catalog
+sources 2FGL\,J2022.8+3843c, 2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c,
+and 2FGL\,J2012.4+3955c from the region because they were not significant
+above 10 \gev.  After modifying the region, we found that \tsinc=24.3
+which is less than \tsext, so we believe that this source is spatially
+extended.  These modifications are further described in the caption to
+figure~\ref{1FGL_J2020.0+4049}.
 
@@
 
-Many extended sources. Especially instructive to
-use photons with energy above 10 \gev where we don't have
-to worry about diffuse background as much.
+Many extended sources. Especially instructive to use photons with energy
+above 10 \gev where we don't have to worry about diffuse background
+as much.
 
 Make some conclusion about how the LAT will eventually collect a factor
-of five more data! Pointlike will be necessary to improve the model of the
-high energy sky. Hard to do a blind analysis of LAT data.
+of five more data! Pointlike will be necessary to improve the model of
+the high energy sky. Hard to do a blind analysis of LAT data.
 
 Figure~\ref{allsky_extended_sources} is an all sky map showing the
-location of all \gev extended sources. Note how most
-extended sources are in the Galactic plane.
+location of all \gev extended sources. Note how most extended sources
+are in the Galactic plane.
 
@@
 all extended sources seen in \gev by the LAT and in \tev by H.E.S.S..
-Note how H.E.S.S. can see smaller sources whereas the LAT
-can see bigger sources.
+Note how H.E.S.S. can see smaller sources whereas the LAT can see
+bigger sources.
 
@@
     The observed 1 \gev to 100 \gev photons for the two year catalog
-    source 2FGL J1856.2+0450c. This map is smoothed by a 0.1\deg Gaussian
+    source 2FGL\,J1856.2+0450c. This map is smoothed by a 0.1\deg Gaussian
     kernel and the red cross and circle are the center and size of the
@@
         \hline
-        Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &   Pos. Err &      Flux ($10^{-9}$) &                 Index \\
-        \hline
-        \multicolumn{9}{c}{$E > 1 \gev$} \\
-        \hline
-        SMC                  &     302.68\deg &     -44.81\deg & $  1.75\deg \pm   0.13\deg$ &       94.4 &       66.4 &  0.118\deg & $    3.3 \pm     0.4$ & $   2.40 \pm    0.17$ \\
-        LMC                  &     279.10\deg &     -32.61\deg & $  1.74\deg \pm   0.07\deg$ &     1102.4 &      861.9 &  0.052\deg & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$ \\
-        IC443                &     189.05\deg &       3.04\deg & $  0.36\deg \pm   0.01\deg$ &    10698.1 &      503.5 &  0.006\deg & $   64.9 \pm     1.2$ & $   2.23 \pm    0.02$ \\
-        W28                  &       6.50\deg &      -0.27\deg & $  0.43\deg \pm   0.02\deg$ &     1323.4 &      172.6 &  0.014\deg & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$ \\
-        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.04\deg$ &      468.6 &       77.2 &  0.019\deg & $   30.8 \pm     1.6$ & $   2.59 \pm    0.05$ \\
-        W44                  &      34.69\deg &      -0.38\deg & $  0.36\deg \pm   0.02\deg$ &     1910.4 &      222.4 &  0.010\deg & $   74.0 \pm     2.0$ & $   2.68 \pm    0.02$ \\
-        W51C                 &      49.13\deg &      -0.45\deg & $  0.28\deg \pm   0.02\deg$ &     1814.2 &      110.6 &  0.010\deg & $   39.2 \pm     1.3$ & $   2.35 \pm    0.03$ \\
-        CygnusLoop           &      74.22\deg &      -8.46\deg & $  1.72\deg \pm   0.05\deg$ &      356.5 &      356.5 &  0.060\deg & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$ \\
-        \hline
-        \multicolumn{9}{c}{$E > 10 \gev$} \\
-        \hline
-        MSH15-52             &     320.38\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &       75.2 &        7.2 &  0.032\deg & $    0.6 \pm     0.7$ & $   2.26 \pm    0.73$ \\
-        HESSJ1825-137        &      17.56\deg &      -0.46\deg & $  0.65\deg \pm   0.07\deg$ &       81.6 &       51.4 &  0.047\deg & $    1.8 \pm     0.1$ & $   1.74 \pm    0.06$ \\
+        Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &     PosErr &                  Flux &                 Index &                      \\
+        \hline
+        \multicolumn{10}{c}{$E > 1 \gev$} \\
+        \hline
+        SMC                  &     302.68\deg &     -44.81\deg & $  1.75\deg \pm   0.13\deg$ &       94.4 &       66.4 &   0.12\deg & $    3.3 \pm     0.4$ & $   2.40 \pm    0.17$ &                      \\
+        LMC                  &     279.10\deg &     -32.61\deg & $  1.74\deg \pm   0.07\deg$ &     1102.4 &      861.9 &   0.05\deg & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$ &                      \\
+        IC443                &     189.05\deg &       3.04\deg & $  0.36\deg \pm   0.01\deg$ &    10698.1 &      503.5 &   0.01\deg & $   64.9 \pm     1.2$ & $   2.23 \pm    0.02$ &                      \\
+        W28                  &       6.50\deg &      -0.27\deg & $  0.43\deg \pm   0.02\deg$ &     1323.4 &      172.6 &   0.01\deg & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$ &                      \\
+        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.04\deg$ &      468.6 &       77.2 &   0.02\deg & $   30.8 \pm     1.6$ & $   2.59 \pm    0.05$ &                      \\
+        W44                  &      34.69\deg &      -0.38\deg & $  0.36\deg \pm   0.02\deg$ &     1910.4 &      222.4 &   0.01\deg & $   74.0 \pm     2.0$ & $   2.68 \pm    0.02$ &                      \\
+        W51C                 &      49.13\deg &      -0.45\deg & $  0.28\deg \pm   0.02\deg$ &     1814.2 &      110.6 &   0.01\deg & $   39.2 \pm     1.3$ & $   2.35 \pm    0.03$ &                      \\
+        Cygnus Loop          &      74.22\deg &      -8.46\deg & $  1.72\deg \pm   0.05\deg$ &      356.5 &      356.5 &   0.06\deg & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$ &                      \\
+        \hline
+        \multicolumn{10}{c}{$E > 10 \gev$} \\
+        \hline
+        MSH 15-52            &     320.38\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &       75.2 &        7.2 &   0.03\deg & $    0.6 \pm     0.7$ & $   2.26 \pm    0.73$ &                      \\
+        HESS J1825-137       &      17.56\deg &      -0.46\deg & $  0.65\deg \pm   0.07\deg$ &       81.6 &       51.4 &   0.05\deg & $    1.8 \pm     0.1$ & $   1.74 \pm    0.06$ &                      \\
       \end{tabular}
@@
       Galactic longitude and Galactic latitude of the source and $\sigma$
-      is the edge of the best fit uniform disk spatial model.  Pos. Err
+      is the edge of the best fit uniform disk spatial model.  PosErr
       is the error on the localization of the source.  The extended PWN
@@
     \end{center}
-    \caption{The cumulative distribution of \tsext for 515 AGN associated
-    in the first LAT AGN catalog using photons with energies between 1
-    \gev and 100 \gev.  The method for selecting these AGN is described in
-    section~\ref{test_1lac_sources}.  AGN are expected to be unresolvable
-    so overlaid on this plot is a $\chi^2/2$ distribution suggested by
-    Wilk's theorem.  The motivation for this distribution to hold is
-    discussed in section~\ref{monte_carlo_validation}.  Overall, there
-    is good agreement between this the fit values of \tsext and the
-    $\chi^2/2$ distribution.  Possible reasons for the discrepancy between
-    the distributions are discussed in section~\ref{test_1lac_sources}
-    but this plot demonstrates that any systematics in our extension
-    test are small compared to the signals we are looking for.
+    \caption{The cumulative density of \tsext for 775 of the
+    clean AGN in 2LAC which are significant above 1 \gev.
+    AGN are expected to be unresolvable so overlaid on this plot
+    is a $\chi^2/2$ distribution suggested by Wilk's theorem (see
+    section~\ref{monte_carlo_validation}).  The \tsext distribution
+    computed with \pointlike agrees with Wilk's theorem which confirms
+    that we can use \tsext as a calibrated test of extension. The
+    distribution computed by \gtlike is biased towards smaller values of
+    \tsext. This is because \tsext is optimized using \pointlike and minor
+    difference in the \pointlike and \gtlike likelihood function will
+    cause the best fit value between these two methods to differ. Because
+    \gtlike's curve lies to the left of the theoretical distribution,
+    requiring that \tsext is significant with both methods makes this
+    test for extension conservative.  Two sources had $\tsext>9$.  One was due to incorrectly
+    pruning a nearby catalog sources and the other was due to failure
+    of convergence of the point hypothesis.  More information about this
+    analysis is presented in section~\ref{test_1lac_sources}.
     }\label{agn_ts_ext}
@@
       \hline
-      Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &   Pos. Err &      Flux ($10^{-9}$) &                 Index \\
-      \hline
-      \multicolumn{9}{c}{$E > 1 \gev$} \\
-      \hline
-      2FGL J0823.0-4246    &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      320.9 &       46.3 &  0.024\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ \\
-      2FGL J1627.0-2425c   &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg$ &      144.5 &       31.1 &  0.038\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ \\
-      2FGL J1712.4-3941    &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg$ &       75.0 &       39.6 &  0.049\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ \\
-      \hline
-      \multicolumn{9}{c}{$E > 10 \gev$} \\
-      \hline
-      2FGL J0851.7-4635    &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg$ &      116.1 &       87.2 &  0.074\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ \\
-      2FGL J1615.0-5051    &     332.38\deg &      -0.14\deg & $  0.32\deg \pm   0.04\deg$ &       54.3 &       16.7 &  0.043\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.25$ \\
-      2FGL J1615.2-5138    &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg$ &       76.6 &       48.0 &  0.045\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ \\
-      2FGL J1632.4-4753c   &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      127.8 &       64.5 &  0.039\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ \\
-      2FGL J1837.3-0700c   &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       46.2 &       18.8 &  0.069\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ \\
-      2FGL J2021.5+4026    &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      222.2 &      116.4 &  0.037\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ \\
+      Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &     PosErr &                  Flux &                 Index &          Counterpart \\
+      \hline
+      \multicolumn{10}{c}{$E > 1 \gev$} \\
+      \hline
+      2FGL\,J0823.0-4246   &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      320.9 &       46.3 &   0.02\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
+      2FGL\,J1627.0-2425c  &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg$ &      144.5 &       31.1 &   0.04\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
+      2FGL\,J1712.4-3941   &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg$ &       75.0 &       39.6 &   0.05\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
+      \hline
+      \multicolumn{10}{c}{$E > 10 \gev$} \\
+      \hline
+      2FGL\,J0851.7-4635   &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg$ &      116.1 &       87.2 &   0.07\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr.
+\\
+      2FGL\,J1615.0-5051   &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg$ &       53.4 &       16.3 &   0.04\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
+      2FGL\,J1615.2-5138   &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg$ &       76.6 &       48.0 &   0.05\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
+      2FGL\,J1632.4-4753c  &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      127.8 &       64.5 &   0.04\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
+      2FGL\,J1837.3-0700c  &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       46.2 &       18.8 &   0.07\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
+      2FGL\,J2021.5+4026   &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      222.2 &      116.4 &   0.04\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &          Gamma Cygni \\
       \hline
@@
     search. Three new extended sources were found using photons with
-    energies above 1 \gev and five new candidates were found using photons
-    with energies above 10 \gev.  The columns in this table have the same
-    meaning as in table~\ref{known_extended_sources}.  More information
-    about these sources can be found in section~\ref{new_ext_srcs_section}.
+    energies above 1 \gev and five new candidates were found using
+    photons with energies above 10 \gev.  The columns in this table
+    have the same meaning as in table~\ref{known_extended_sources}.
+    The quoted flux is in units of
+      $10^{-9}\ph/\cm^2/\sec$ and is the flux in the fit energy range
+      (either 1 \gev to 100 \gev or 10 \gev to 100 \gev)
+    More information about these sources can be found in
+    section~\ref{new_ext_srcs_section}.
     }
@@
         \hline
-        2FGL J0823.0-4246    &       22.1 &       46.3 &     260.59\deg &      -3.27\deg & $       2.1 \pm        0.6$ & $  2.0 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.4 \pm        0.7$ & $  2.4 \pm   0.2$ \\
-        2FGL J1627.0-2425c   &       20.0 &       31.1 &     353.01\deg &      16.98\deg & $       3.1 \pm        0.6$ & $  2.6 \pm   0.3$  &     353.24\deg &      16.66\deg & $       2.5 \pm        0.6$ & $  2.5 \pm   0.4$ \\
-        2FGL J1712.4-3941    &        6.4 &       39.6 &     347.28\deg &      -0.07\deg & $       0.2 \pm        0.1$ & $  0.6 \pm   0.5$  &     347.22\deg &      -0.27\deg & $       2.4 \pm        0.7$ & $  1.9 \pm   0.2$ \\
+        2FGL\,J0823.0-4246   &       22.1 &       46.3 &     260.59\deg &      -3.27\deg & $       2.1 \pm        0.6$ & $  2.0 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.4 \pm        0.7$ & $  2.4 \pm   0.2$ \\
+        2FGL\,J1627.0-2425c  &       20.0 &       31.1 &     353.01\deg &      16.98\deg & $       3.1 \pm        0.6$ & $  2.6 \pm   0.3$  &     353.24\deg &      16.66\deg & $       2.5 \pm        0.6$ & $  2.5 \pm   0.4$ \\
+        2FGL\,J1712.4-3941   &        6.4 &       39.6 &     347.28\deg &      -0.07\deg & $       0.2 \pm        0.1$ & $  0.6 \pm   0.5$  &     347.22\deg &      -0.27\deg & $       2.4 \pm        0.7$ & $  1.9 \pm   0.2$ \\
         \hline
@@
         \hline
-        2FGL J0851.7-4635    &       16.1 &       87.2 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
-        2FGL J1615.0-5051    &       12.2 &       16.7 &     332.39\deg &      -0.07\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.6$  &     332.43\deg &      -0.35\deg & $       0.4 \pm        0.1$ & $  2.4 \pm   0.5$ \\
-        2FGL J1615.2-5138    &       37.0 &       48.0 &     331.76\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.3 \pm   0.5$  &     331.47\deg &      -0.80\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.4$ \\
-        2FGL J1632.4-4753c   &       40.6 &       64.5 &     336.52\deg &       0.17\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
-        2FGL J1837.3-0700c   &       12.6 &       18.8 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.5$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
-        2FGL J2021.5+4026    &       24.3 &      116.4 &      78.28\deg &       1.95\deg & $       0.3 \pm        0.1$ & $  5.0 \pm   0.0$  &      78.15\deg &       2.20\deg & $       0.6 \pm        0.1$ & $  1.7 \pm   0.4$ \\
+        2FGL\,J0851.7-4635   &       16.1 &       87.2 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
+        2FGL\,J1615.0-5051   &       11.9 &       16.3 &     332.39\deg &      -0.08\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.6$  &     332.43\deg &      -0.36\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.5$ \\
+        2FGL\,J1615.2-5138   &       37.0 &       48.0 &     331.76\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.3 \pm   0.5$  &     331.47\deg &      -0.80\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.4$ \\
+        2FGL\,J1632.4-4753c  &       40.6 &       64.5 &     336.52\deg &       0.17\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
+        2FGL\,J1837.3-0700c  &       12.6 &       18.8 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.5$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
+        2FGL\,J2021.5+4026   &       24.3 &      116.4 &      78.28\deg &       1.95\deg & $       0.3 \pm        0.1$ & $  5.0 \pm   0.0$  &      78.15\deg &       2.20\deg & $       0.6 \pm        0.1$ & $  1.7 \pm   0.4$ \\
         \hline
@@
         \hline
-        2FGL J0823.0-4246    &                350.9 &                320.9 &                352.5 &                     66.0 &                   46.3 &                 53.6 & $  0.37\deg \pm   0.03\deg$ & $  0.39\deg \pm   0.03\deg$ \\
-        2FGL J1627.0-2425c   &                170.2 &                144.5 &                112.6 &                     43.9 &                   31.1 &                 23.9 & $  0.41\deg \pm   0.05\deg$ & $  0.40\deg \pm   0.04\deg$ \\
-        2FGL J1712.4-3941    &                 80.9 &                 75.0 &                 43.4 &                     47.4 &                   39.6 &                 22.2 & $  0.56\deg \pm   0.04\deg$ & $  0.56\deg \pm   0.04\deg$ \\
+        2FGL\,J0823.0-4246   &                350.9 &                320.9 &                352.5 &                     66.0 &                   46.3 &                 53.6 & $  0.37\deg \pm   0.03\deg$ & $  0.39\deg \pm   0.03\deg$ \\
+        2FGL\,J1627.0-2425c  &                170.2 &                144.5 &                112.6 &                     43.9 &                   31.1 &                 23.9 & $  0.41\deg \pm   0.05\deg$ & $  0.40\deg \pm   0.04\deg$ \\
+        2FGL\,J1712.4-3941   &                 80.9 &                 75.0 &                 43.4 &                     47.4 &                   39.6 &                 22.2 & $  0.56\deg \pm   0.04\deg$ & $  0.56\deg \pm   0.04\deg$ \\
         \hline
@@
         \hline
-        2FGL J0851.7-4635    &                116.7 &                116.1 &                122.3 &                     87.1 &                   87.2 &                 90.4 & $  1.13\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
-        2FGL J1615.0-5051    &                 53.0 &                 54.3 &                 55.6 &                     18.1 &                   16.7 &                  3.4 & $  0.32\deg \pm   0.04\deg$ & $  0.32\deg \pm   0.04\deg$ \\
-        2FGL J1615.2-5138    &                 76.3 &                 76.6 &                 86.3 &                     44.0 &                   48.0 &                 52.6 & $  0.42\deg \pm   0.03\deg$ & $  0.43\deg \pm   0.03\deg$ \\
-        2FGL J1632.4-4753c   &                126.6 &                127.8 &                120.7 &                     63.9 &                   64.5 &                 64.1 & $  0.44\deg \pm   0.04\deg$ & $  0.44\deg \pm   0.04\deg$ \\
-        2FGL J1837.3-0700c   &                 45.4 &                 46.2 &                 39.0 &                     18.5 &                   18.8 &                 16.6 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
-        2FGL J2021.5+4026    &                234.3 &                222.2 &                235.6 &                    135.9 &                  116.4 &                121.4 & $  0.59\deg \pm   0.03\deg$ & $  0.60\deg \pm   0.03\deg$ \\
+        2FGL\,J0851.7-4635   &                116.7 &                116.1 &                122.3 &                     87.1 &                   87.2 &                 90.4 & $  1.13\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
+        2FGL\,J1615.0-5051   &                 52.4 &                 53.4 &                 55.6 &                     17.5 &                   16.3 &                 17.4 & $  0.33\deg \pm   0.04\deg$ & $  0.32\deg \pm   0.04\deg$ \\
+        2FGL\,J1615.2-5138   &                 76.3 &                 76.6 &                 86.3 &                     44.0 &                   48.0 &                 52.6 & $  0.42\deg \pm   0.03\deg$ & $  0.43\deg \pm   0.03\deg$ \\
+        2FGL\,J1632.4-4753c  &                126.6 &                127.8 &                120.7 &                     63.9 &                   64.5 &                 64.1 & $  0.44\deg \pm   0.04\deg$ & $  0.44\deg \pm   0.04\deg$ \\
+        2FGL\,J1837.3-0700c  &                 45.4 &                 46.2 &                 39.0 &                     18.5 &                   18.8 &                 16.6 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
+        2FGL\,J2021.5+4026   &                234.3 &                222.2 &                235.6 &                    135.9 &                  116.4 &                121.4 & $  0.59\deg \pm   0.03\deg$ & $  0.60\deg \pm   0.03\deg$ \\
       \end{tabular}
@@
   \caption{A Galactic and isotropic diffuse subtracted 1 \gev to 100
-  \gev counts map of the region around 2FGL J0823.0-4246 smoothed by a
+  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed by a
   0.1\deg Gaussian kernel.  The red star is the catalog position of this source.  
@@
   and extension of this source assuming a uniform disk spatial model.
-  The two green stars are the positions of the sources 2FGL J0823.4-4305
-  and 2FGL J0821.0-4254 which were removed because they are part of the
+  The two green stars are the positions of the sources 2FGL\,J0823.4-4305
+  and 2FGL\,J0821.0-4254 which were removed because they are part of the
   extended source.  This source is spatially coincident with the Puppis
@@
   A Galactic and isotropic diffuse subtracted 1 \gev to 100 \gev counts
-  map of the region around 2FGL J1627.0-2425 smoothed by a 0.1\deg
+  map of the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
   Gaussian kernel.  The red star is the catalog's position of
@@
   uniform disk spatial model.  The black cross is the background source
-  2FGL J1625.7-2526.  The light blue contours are a 100 micrometer infrared
+  2FGL\,J1625.7-2526.  The light blue contours are a 100 micrometer infrared
   image of the region as seen by IRAS (\cite{iras_rho_ophiuci}). This
@@
   \begin{center}
+    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946}
+    % this plot came from
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
+  \end{center}
+  \caption{A Galactic and isotropic diffuse subtracted 1 \gev to 100
+  \gev counts map of the region around 2FGL\,J1712.4-3941 smoothed by a
+  0.25\deg Gaussian kernel.  This source is spatially coincident with
+  RX J1713.7-3946 was was recently reported by (\cite{rx_j1713_lat}).
+  The light blue contours are the \tev emission reported by
+  H.E.S.S. (\cite{rx_j1713_hess}).  The region was analyzed with the
+  same background model as (\cite{rx_j1713_lat}).  Source A (blue cross)
+  is spatially coincident with 2FGL\,J1715.4-4024c (blue star).  The grey 
+  crosses
+  represent from left to right the position of source B and C which were
+  added to the background model. Plot (a) has the diffuse emisission model
+  subtracted and plot (b) has the diffuse emission and all background
+  sources also subtracted.
+  }\label{2FGL_J1712.4-3941}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
     \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
@@
   \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
-  \gev counts map of the region around 2FGL J0851.7-4635 smoothed by
-  a 0.25\deg Gaussian kernel. This image is smoothed by a larger
+  \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
+  by a 0.25\deg Gaussian kernel. This image is smoothed by a larger
   kernel because it is significantly larger than the other sources.
-  The red star is the catalog position of
-  this source.  The red cross and circle are the best fit position
-  and extension of the source assuming a uniform disk spatial model.
-  The inner three green stars are (from left to right)
-  2FGL J0853.5-4711,
-  2FGL J0855.4-4625, and
-  2FGL J0848.5-4535 which were 
-  removed 
-  because they are part of the extended source.  The farther away
-  green stars are (from left to right) 
-  2FGL J0901.7-4655 and
-  2FGL J0858.0-4815 which were removed 
+  The red star is the catalog position of this source.  The red cross
+  and circle are the best fit position and extension of the source
+  assuming a uniform disk spatial model.  The inner three green stars
+  are (from left to right) 2FGL\,J0853.5-4711, 2FGL\,J0855.4-4625,
+  and 2FGL\,J0848.5-4535 which were removed because they are part of
+  the extended source.  The farther away green stars are (from left to
+  right) 2FGL\,J0901.7-4655 and 2FGL\,J0858.0-4815 which were removed
   because they were not significant above 10 \gev.  The blue cross
-  is the relocalized position of
-  2FGL J0854.7-4501.  This
-  extended source is spatially coincident with the Vela Jr SNR.
-  The light blue contours are the \tev emission of Vela Jr. observed by
-  H.E.S.S (\cite{vela_jr_hess}).  More information about this source 
-  can be found in section~\ref{section_2FGL_J0851.7-4635}.
+  is the relocalized position of 2FGL\,J0854.7-4501.  This extended
+  source is spatially coincident with the Vela Jr SNR.  The light
+  blue contours are the \tev emission of Vela Jr. observed by H.E.S.S
+  (\cite{vela_jr_hess}).  More information about this source can be
+  found in section~\ref{section_2FGL_J0851.7-4635}.
   }\label{Vela_Jr}
@@
   \caption{
-    A Galactic and isotropic diffuse subtracted 10 \gev to 100 \gev counts
-    map of the region around 2FGL J1615.0-5051 and 2FGL J1615.2-5138
-    smoothed by a 0.1\deg Gaussian kernel. The upper left source is
-    2FGL J1615.0-5051 and the lower right source is 2FGL J1615.2-5138.
-    The red stars are the catalog positions of these sources.  The red
-    stars and circles are the best fit positions and extensions
-    of these sources assuming uniform disk spatial model.  The green star
-    inside of the extension of 2FGL J1615.2-5138  is 2FGL J1614.9-5212
-    which was removed because it is part of the extended source.
-    The greeen stars to the left are 2FGL J1619.7-5040c and 2FGL
-    J1620.6-5111c which were removed because they were not significant
-    above 10\gev. These are shown as green stars.  The light blue contours
-    are the \tev emission of
-    the extended source HESS J1614-518 and the extended source HESS
-    J1616-508 measured by H.E.S.S.(\cite{hess_plane_survey}). 2FGL
-    J1615.0-5051 is spatially
-    consistent with HESS J1616-508 and 2FGL J1615.2-5138 is spatially
-    consistent with HESS J1614-518.  More information about 2FGL
-    J1615.0-5051 can be found in section~\ref{section_2FGL_J1615.0-5051} and
-    2FGL J1615.2-5138 in section~\ref{section_2FGL_J1615.2-5138}.
+    A Galactic and isotropic diffuse subtracted 10 \gev to 100
+    \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
+    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0.1\deg
+    Gaussian kernel.  The red stars are the catalog positions of these
+    sources.  The red stars and circles are the best fit positions and
+    extensions of these sources assuming uniform disk spatial models.
+    The green star inside the extension of 2FGL\,J1615.2-5138  is
+    2FGL\,J1614.9-5212 which was removed because it is part of the
+    extended source.  The greeen stars to the left are 2FGL\,J1619.7-5040c
+    and 2FGL\,J1620.6-5111c which were removed because they were
+    not significant above 10\gev. These are shown as green stars.
+    The light blue contours are the \tev emission of the extended source
+    HESS\,J1616-508 (left) and the extended source HESS\,J1614-518
+    (right) measured by H.E.S.S.(\cite{hess_plane_survey}). 2FGL
+    J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
+    2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
+    Figure~\ref{hess_seds} (a) and (b) shows the \gev and \tev SEDs for
+    these sources.
+    More information about 2FGL J1615.0-5051 can be found in
+    section~\ref{section_2FGL_J1615.0-5051} and 2FGL\,J1615.2-5138 in
+    section~\ref{section_2FGL_J1615.2-5138}.
   }\label{1FGL_J1613.6-5100c}
@@
   \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
-  \gev counts map of the region around 2FGL J1632.4-4753c smoothed by
+  \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
   a 0.1\deg Gaussian kernel.  This source is in a crowded region.
@@
   green crosses inside the extension are 2FGL
-  J1631.7-4720c, 2FGL J1630.2-4752, and 2FGL J1634.4-4743c.4-4820c
+  J1631.7-4720c, 2FGL\,J1630.2-4752, and 2FGL\,J1634.4-4743c.4-4820c
   which were removed because they are part
@@
   positions and the relocalized positions of (from left to right)
-  2FGL J1635.4-4717c and 2FGL J1636.3-4740c.  The farther away green
-  stars are other catalog sources which were removed 
-  because they are not significant
-  above 10 \gev.  This extended source is spatially coincident
-  with the extended H.E.S.S source HESS J1634-472.  The light blue
-  contours are the \tev emission seen by H.E.S.S. 
-  (\cite{hess_plane_survey}). More information about this source 
-  can be found in section~\ref{section_2FGL_J1632.4-4753c}.
+  2FGL\,J1635.4-4717c and 2FGL\,J1636.3-4740c.  The farther away green
+  stars are other catalog sources which were removed because they are
+  not significant above 10 \gev.  This extended source is spatially
+  coincident with the extended H.E.S.S source HESS\,J1632-478.
+  The light blue contours are the \tev emission seen by H.E.S.S.
+  (\cite{hess_plane_survey}).  Figure~\ref{hess_seds} (c) shows the \gev and
+  \tev SED for this source.  More information about this source can be
+  found in section~\ref{section_2FGL_J1632.4-4753c}.
   }\label{1FGL_J1632.9-4802c}
@@
   A Galactic and isotropic diffuse subtracted 10 \gev to 100 \gev
-  counts map of the region around 2FGL J1837.3-0700c smoothed by a
+  counts map of the region around 2FGL\,J1837.3-0700c smoothed by a
   0.1\deg Gaussian kernel.  The red star is the catalog position of
   this source. The red cross and circle are the best fit position and
-  extension  of 2FGL J1837.3-0700c assuming a uniform disk spatial model.
+  extension  of 2FGL\,J1837.3-0700c assuming a uniform disk spatial model.
   The blue stars and crosses are the catalog position and the relocalized
-  position of (from left to right) 2FGL J1839.3-0558c, 2FGL J1836.8-0623c,
-  and 2FGL J1834.7-0705c.  The green cross inside the extension is 
-  2FGL J1835.5-0649 which was removed because it
+  position of (from left to right) 2FGL\,J1839.3-0558c, 2FGL\,J1836.8-0623c,
+  and 2FGL\,J1834.7-0705c.  The green cross inside the extension is 
+  2FGL\,J1835.5-0649 which was removed because it
   is part of the extended source.  The farther away green star is 2FGL
   J1839.0-0539 which was removed because it is not significant above
-  10 \gev.  This source is spatially coincident with the \tev source HESS
-  J1837-069.  The light blue contours are the \tev emission of HESS J1837-069
-  observed by H.E.S.S (\cite{hess_plane_survey}).  More information about
+  10 \gev.  This source is spatially coincident with the \tev source 
+  HESS\,J1837-069.  The light blue contours are the \tev emission of HESS\,J1837-069
+  observed by H.E.S.S (\cite{hess_plane_survey}).  
+  Figure~\ref{hess_seds} (d) shows the \gev and
+  \tev SED for this source. 
+  More information about
   this source can be found in section~\ref{section_2FGL_J1837.3-0700c}.
   }\label{1FGL_J1837.5-0659c}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946}
-    % this plot came from
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
-  \end{center}
-  \caption{A Galactic and isotropic diffuse subtracted 1 \gev to 100
-  \gev counts map of the region around 2FGL J1712.4-3941 smoothed by a
-  0.25\deg Gaussian kernel.  This source is spatially coincident with
-  RX J1713.7-3946 was was recently reported by (\cite{rx_j1713_lat}).
-  The light blue contours are the \tev emission reported by
-  H.E.S.S. (\cite{rx_j1713_hess}).  The region was analyzed with the
-  same background model as (\cite{rx_j1713_lat}).  Source A (blue cross)
-  is spatially coincident with 2FGL J1715.4-4024c (blue star) so 2FGL
-  J1715.4-4024c was moved to the position of source A.  The grey crosses
-  represent from left to right the position of source B and C which were
-  added to the background model. Plot (a) has the diffuse emisission model
-  subtracted and plot (b) has the diffuse emission and all background
-  sources also subtracted.
-  }\label{2FGL_J1712.4-3941}
 \end{figure}
@@
   \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
-  \gev counts map of the region around 2FGL J2021.5+4026 smoothed by a
+  \gev counts map of the region around 2FGL\,J2021.5+4026 smoothed by a
   0.1\deg Gaussian kernel. The red star is the catalog position of 2FGL
   J2021.5+4026.  The red cross and circle are the best fit position and
-  extension 2FGL J2021.5+4026 assuming a uniform disk spatial model.
-  The green cross inside the extension is 2FGL J2019.1+4040 which
+  extension 2FGL\,J2021.5+4026 assuming a uniform disk spatial model.
+  The green cross inside the extension is 2FGL\,J2019.1+4040 which
   was removed because it is part of the extended source.  The farther
@@
   the position a source not in the two year catalog which was added
-  to the region. 2FGL J2021.5+4026 is spatially coincident with the
+  to the region. 2FGL\,J2021.5+4026 is spatially coincident with the
   Gamma Cygni SNR.  The light blue contours are a 408MHz image of Gamma Cygni
@@
     with dashed markers are H.E.S.S points of associated sources.
-    Figure~\ref{hess_seds}a shows the \gev SED of 2FGL J1615.0-5051
-    and \tev SED of HESS J1616-508.  Figure~\ref{hess_seds}b shows
-    the \gev SED of 2FGL J1615.2-5138 and \tev SED of HESS J1614-518
-    Figure~\ref{hess_seds}c shows the \gev SED of 2FGL J1632.4-4753c
-    and \tev SED of HESS J1634-472 Figure~\ref{hess_seds}d shows the
-    \gev SED of 2FGL J1837.3-0700c and \tev SED of HESS J1837-069.
+    Plot (a) shows the \gev SED of 2FGL\,J1615.0-5051
+    and the \tev SED of HESS\,J1616-508.  Plot (b) shows
+    the \gev SED of 2FGL\,J1615.2-5138 and \tev the SED of HESS\,J1614-518
+    Plot (c) shows the \gev SED of 2FGL\,J1632.4-4753c
+    and the \tev SED of HESS\,J1632-478. Plot (d) shows the
+    \gev SED of 2FGL\,J1837.3-0700c and the \tev SED of HESS\,J1837-069.
     The H.E.S.S. data points are from (\cite{hess_plane_survey}).
@@
     \caption{
-    A comparison of the \gev and \tev sizes of LAT
-    extended sources detected by \tev instruments.  The \tev
-    extensions of W30, 2FGL J1837.3-0700c, 2FGL J1632.4-4753c,
-    2FGL J1615.0-5051, and 2FGL J1615.2-5138 are from the
+    A comparison of the \gev and \tev sizes of LAT extended
+    sources detected by \tev instruments.  The \tev extensions
+    of W30, 2FGL\,J1837.3-0700c, 2FGL\,J1632.4-4753c,
+    2FGL\,J1615.0-5051, and 2FGL\,J1615.2-5138 are from the
     H.E.S.S. Galactic plane survey (\cite{hess_plane_survey}).
-    The \tev extensions of MSH 15-52, HESS J1825-137, Vela X,
+    The \tev extensions of MSH 15-52, HESS\,J1825-137, Vela X,
     Vela Jr., RX J1713.7-3946 and W28 are respectively from H.E.S.S.
@@
     be 0.5\deg and Vela Jr. is taken to be 1\deg. For these two sources,
-    the LAT size is not converted to \rsixeight but the disk extension
-    is directly compared.  This plot shows that there is good correlation
-    between the \gev and \tev sizes of sources.
+    the LAT size is not converted to \rsixeight but the disk extension is
+    directly compared.  This plot shows that there is good correlation
+    between the \gev and \tev sizes of sources.  The \tev size of MSH
+    15-52, HESS J1614-518, HESS J1632-478, and HESS J1837-069 have only
+    been reported with an elliptical Gaussian fit and so the plotted size
+    of these sources is the average of the radius in the semi-major and
+    semi-minor axis.
     }\label{gev_vs_tev_plot}
@@
     from (\cite{velax}). This plot shows that many of the LAT
-    extended sources have a very harder spectral index.
+    extended sources have a hard ($<2$) spectral index.
     }\label{compare_index_2FGL}

### 2011-08-07 extended_catalog/paper/extended_catalog.tex
many improvements

@@
 \usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
+\usepackage[toc,page]{appendix}
 
@@
 % some units
+\newcommand{\kev}{\text{Kev}\xspace}
 \newcommand{\mev}{\text{MeV}\xspace}
@@
 \renewcommand{\sec}{\text{s}\xspace}
-\newcommand{\tsext}{{\ensuremath{\text{TS}_\text{ext}}}\xspace}
-\newcommand{\tsinc}{\ensuremath{\text{TS}_\text{inc}}\xspace}
+\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
+\newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{inc}}}\xspace}
 \newcommand{\loglikelihood}{\ensuremath{LL}\xspace}
@@
 \newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}\xspace}
-\newcommand{\tsextalt}{\ensuremath{\tsext_{,\alt}}\xspace}
 
@@
 \newcommand{\glat}{\text{GLAT}\xspace}
-\newcommand{\alt}{\text{alt}\xspace}
+\newcommand{\altdiff}{\text{alt,diff}\xspace}
+\newcommand{\altpsf}{\text{alt,psf}\xspace}
+\newcommand{\sys}{\text{sys}\xspace}
+\newcommand{\stat}{\text{stat}\xspace}
 
@@
 \newcommand{\minuit}{\text{\em Minuit}\xspace}
+\renewcommand{\approx}{\sim\!\xspace}
 
@@
 instrument because of its broad energy coverage (20 \mev to $>300$
-\gev), wide field of view ($\sim 2.4 \sr$), and large effective area
-($\sim 8000 \cm^2$ at $>1 \gev$).
+\gev), wide field of view ($\approx 2.4 \sr$), and large effective area
+($\approx 8000 \cm^2$ at $>1 \gev$).
 
@@
 resolved when observed at other frequencies, detection an extension at
-GeV energies by the LAT is complicated by the rather large
+\gev energies by the LAT is complicated by the rather large
 point-spread function (PSF) of the instrument (the angular resolution
@@
 the 68\% containment radius for a point source, is approximately
-$3.5^{\circ}$ at 100 MeV, improving to about 0.1$^{\circ}$ at 10 GeV).
+$3.5^{\circ}$ at 100 \mev, improving to about 0.1$^{\circ}$ at 10 \gev).
 
@@
 
-In addition to these GeV $\gamma$-ray detections, a variety of
+In addition to these \gev $\gamma$-ray detections, a variety of
 spatially extended sources have been detected in the Galactic plane at
@@
 energies. Given these findings, it can be expected that if the source
-population at GeV energies has similar properties, that at least some
+population at \gev energies has similar properties, that at least some
 of the Fermi-LAT sources in our Galaxy should be spatially extended at
-GeV energies.
+\gev energies.
 
@@
 can correct for this.  Furthermore, correctly modeling a source's
-extension is important for improving the overall model of the sky and
+extension is important for improving the model of the sky and
 removing excess residuals.  These residuals manifested themselves in
@@
 can be written as the convolution of the source shape ($I_\text{src}$)
-with the psf
+with the PSF
 \begin{equation}
@@
 spatial parameter is small but not that the likelihood is Gaussian. This
-method is shown schematically in figure~\ref{extension_profile} which
+method is shown schematically in figure~\ref{four_plots_ic443}(a) which
 shows the change in \loglikelihood when varying the extension of the
@@
 than the PSF leading to $\tsext=0$. The other half of the time, we would
-get a distribution consistent with Wilk's theorem. We will present a
+get a distribution consistent with Wilks' theorem. We will present a
 Monte Carlo study that shows an empirical distribution of \tsext in the
@@
 indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
-to represent typical source paramters in LAT-detected sources. The point
+to represent typical source parameters in LAT-detected sources. The point
 sources were simulated on top of an isotropic power-law background
@@
 
-We performed a second study to determine the LAT's detection
-threshold to spatially extended sources. The detection threshold
-to extension is defined as the flux at which the average
-value of $\tsext$ is $\langle\tsext\rangle=25$. As was seen in
-section~\ref{monte_carlo_validation}, this corresponds to an extension
-significance of $5\sigma$.  Qualitatively, we expect the LAT would not
-be sensitive to sources much smaller than the PSF or much larger than
-the PSF.  Small sources would look too much like the PSF and larger
+We calculated the LAT's detection threshold to spatially
+extended sources. The detection threshold to extension is
+defined as the flux at which the average value of $\tsext$ is
+$\langle\tsext\rangle=16$ corresponding to a $4\sigma$ detection (see
+section~\ref{monte_carlo_validation}).  Qualitatively, we expect the LAT
+would not be sensitive to sources much smaller than the PSF or much larger
+than the PSF.  Small sources would look too much like the PSF and larger
 sources would get lost in the background due to low surface brightness.
 
-To calculate the LAT's detection threshold to spatially extended
-sources, we simulated sources with a uniform radially symmetric disk
-spatial model on top of a power-law Sreekumar-like isotropic spectrum
-(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was performed
-using the same one year time interval as in section~\ref{monte_carlo_validation}.
-For each extension and spectral index, we
-first picked a flux range which bracketed $\tsext=25$. We then picked
-ten flux points in this range and repeatedly simulated and performed
-extension tests of the extended sources.  For each flux, we performed
-$>15$ independent simulations and extension fits.  We calculated
-$\langle\tsext\rangle=25$ by fitting a line to all the flux and
-$\tsext$ values and estimating the flux when $\tsext=25$.
+To calculate the LAT's detection threshold, we simulated sources with
+a uniform radially symmetric disk spatial model on top of a power-law
+Sreekumar-like isotropic spectrum (\cite{sreekumar_isotropic}).  The Monte
+Carlo simulation was performed using the same two year time range that
+was used in 2FGL.  For each extension and spectral index, we picked a
+flux range which bracketed $\tsext=16$. We then picked ten flux points in
+this range and repeatedly simulated and then performed extension tests of
+the simulated extended source.  We calculated $\langle\tsext\rangle=16$
+by fitting a line to the flux and $\tsext$ values.
 
@@
 spectral indices from 1.5 to 3 and extension varying from $\sigma=0.1\deg$
-to $2.0\deg$.  The curves on the plot represent the flux for a given
-extension where $\langle\tsext\rangle=25$. 
-This results shows that the LAT's threshold to extension is better for
-harder sources with more high energy photons. This result also shows
-that the threshold is best for sources with an extension of $~0.5\deg$
-and is significantly worse for very small extended small.
-
+to $2.0\deg$.  The LAT's threshold to extension
+is better for harder sources with more high energy photons and
+the threshold is best for sources with an extension 
+$\approx0.5\deg$ and is significantly worse for very small extended small.
 Figure~\ref{index_sensitivity} shows the threshold using photons with
-energies between 100 \mev and 100 \gev and also only using photons
+energies between 100 \mev and 100 \gev and also using only photons
 with energies between 1 \gev and 100 \gev.  Except for the hardest
@@
 including photons with energies between 100 \mev and 1 \gev.  This is also
-demonstrated in figure~\ref{ts_ext_vs_energy} which shows \tsext for the
+demonstrated in figure~\ref{four_plots_ic443}(b) which shows \tsext for the
 SNR IC443 computed independently in twelve energy bins between 100 \mev and
-100 \gev. For IC443, which has a spectral index ~2.4, almost the entire
+100 \gev. For IC443, which has a spectral index $\approx2.4$, almost the entire
 increase in \ts comes from energies above 1 \gev.  On the other hand,
@@
 Figure~\ref{diff_factor_sensitivity} shows how the LAT's detection
-threshold varies with increasing diffuse background. We compute the
-sensitivity for a power-law source of spectral index 2 using 1, 10, and
-100 times the extragalactic background. The latter factor approximately
-represents the intensity of the Galactic diffuse emission near the
-Galactic center.  The figure shows two plots, the first showing the
-threshold using only photons with energies between 1 \gev and 100 \gev and
-the second showing the threshold using only photons with energies between
-10 \gev and 100 \gev. This plot demonstrates that we are less sensitive
-to extended sources in a higher background region and that if the flux of
-a source is constant (same number of photons), we would be more sensitive
-to the extension of that source if those photons had a higher energy.
+threshold increases with increasing background. We compute the threshold
+using 1, 10, and 100 times the Sreekumar-like isotropic background. The
+latter factor approximately represents the intensity of the Galactic
+diffuse emission near the Galactic center.  The figure shows the threshold
+using only photons with energies between 1 \gev and 100 \gev and aldo
+when using only photons with energies between 10 \gev and 100 \gev. We
+are less sensitive to extended sources with higher background. Also,
+given the same flux we are more sensitive to the source if those
+photons have a higher energies.
+
+Overlaid on figure~\ref{diff_factor_sensitivity} are the LAT
+detected extended sources from table~\ref{known_extended_sources} and
+table~\ref{new_ext_srcs_table}.  The extended sources are color coded
+based upon whether the galactic diffuse and isotropic emission model is
+closer to 1, 10, or 100 times the Sreekumar-like isotropic spectrum.
+
+Finally, figure~\ref{all_sensitivity} shows the LAT's detection threshold
+for all four spectral indices (1.5, 2, 2.5, and 3) against all three
+background levels (1, 10, and 100 times the Sreekumar-like isotropic
+background).  For a fixed 1 \gev to 100 \gev or 10 \gev to 100 \gev
+flux, the LAT's detection threshold is only weakly depends upon the
+spectral index.  This effect is most pronounced when using only photons
+with energies above 10 \gev. The extension thresholds are tabulated in
+table~\ref{all_sensitivity_table}.
 
@@
 
-We also performed a search for extended sources using photons only between
-10 \gev and 100 \gev. Even though we are testing the same sources, this
-approach is complimentary because the Galactic diffuse emission is even
-less dominant above 10 \gev. Furthermore, source confusion becomes less of
-a problem since most LAT sources are not significant at energies above 10
-\gev.  Using higher energies, we might expect to detect harder sources in
-more complicated regions. This is especially beneficial
-for regions near pulsars which cutoff before 10 \gev
-and was successfully used in detecting HESS\,J1825-137
-and MSH 15-52 with the LAT (\cite{msh1552,fermi_hess_j1825}).
+We also performed a search for extended sources using photons only
+between 10 \gev and 100 \gev. Even though we are testing the same
+sources, this approach is complimentary because the Galactic diffuse
+emission is even less dominant above 10 \gev. Furthermore, source
+confusion becomes less of a problem since most LAT sources are not
+significant at energies above 10 \gev.  Using higher energies, we might
+expect to detect harder sources in more complicated regions. This is
+beneficial for regions near pulsars which cutoff before 10 \gev and was
+successfully used in detecting HESS\,J1825-137 and MSH 15-52 with the LAT
+(\cite{msh1552,fermi_hess_j1825}).
 
@@
 (\cite{first_cat,second_cat}).  Furthermore, the Galactic plane is crowded
-so it is often difficult to model nearby sources.  Because of this,
-finding a source with $\tsext>16$ is not a sufficient for finding
-an extended source and we have to perform several analysis crosschecks.
+and it is often difficult to correctly model nearby sources.  Because of this,
+finding a source with $\tsext>16$ is not a sufficient
+criteria for resolving a source. For each extended source,
+we perform several analysis crosschecks.
 
 % 2FGL J1856.2+0450c = P72Y3047 for
-As an example of why this is important, we describe the test of 2FGL
-J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
-a smoothed counts map using photons with energy above 1 \gev. In
-the map, the Galactic and isotropic diffuse emission are subtracted.
-A 2FGL source 2FGL\,J1856.2+0450c was found at the position
-$(l,b)=(37.25\deg,0.84\deg)$.  We find that there appears to be overall
-some large-scale residual in the diffuse emission along the Galactic
-plane. As a result, 2FGL\,J1856.2+0450c fits to a
-large extension of 1.83\deg and the result is statistically significant
-with \tsext=103.6 (using \pointlike).  By looking at the residuals, it is clear that this
-complicated region is not well fit even though the source's extension is
-statistically significant. For this reason, we have to perform a series
-of further analysis for all of the sources that are found with \tsext=16.
+As an example of why this is important, we describe the test of 
+2FGL\,J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
+a Galactic and isotropic diffuse emission subtracted
+smoothed counts map of this source using photons with energy 
+between 1 \gev and 100 \gev. 
+In this region along the Galactic plane, there appears to be 
+large-scale residual in the diffuse emission. As a result, 2FGL\,J1856.2+0450c 
+fit to an extension of 1.83\deg and the result is statistically significant
+with \tsext=45.4.  By looking at the residuals, it is clear that this
+complicated region is not fit well even though the source's extension is
+statistically significant. For this reason, we manually discard
+the extension of this and similar sources.
 % information came from
@@
 
-First, we took the spatial and spectral model found using \pointlike
-and performed a crosscheck by refitting the spectral parameters using
-\gtlike.  We used a square ROI $14.1\deg$ in diameter with $1/16\deg$
-pixels and the same energy binning as \pointlike. Using \gtlike, we found a second measure of \tsext,
-this time not fitting the extension but using a fixed template
-with extension determined by \pointlike.
+For each extended source candidate,
+we took the spatial and spectral model found using \pointlike and
+performed a crosscheck by refitting the spectral parameters using
+\gtlike.  We used a square ROI $14.1\deg$ in diameter with $1/32\deg$
+spatial bins and the same energy binning as \pointlike. Using \gtlike,
+we found a second measure of \tsext, this time not fitting the extension
+but using a fixed template with the extension determined by \pointlike.
 We only considered a source to be significantly extended if \pointlike
 and \gtlike both agreed.  For the new extended source candidates,
-table~\ref{alt_diff_model_results} shows a comparison of their the value
-of \tsext found by \gtlike and \pointlike.  Everywhere else, the values
-from \gtlike are used.
-
-Additionally, we generated for each extended source candidate residual
-test statistic (\ts) maps.  The residual \ts map is the \ts value
-evaluated at each grid point by adding a new source of spectral index
-2 and finding the increase in likelihood when fitting its flux. \ts
-maps are especially useful when looking for new sources or other
-residual features that are not included in the model. The downside
-is they are biased to look for residual features that look like
-the PSF and so are not as sensitive to large-scale diffuse features.
-features. Furthermore, by definition $\ts>0$ so \ts maps only show
-positive fluctuations. Figure~\ref{res_tsmaps} shows an example
-residual \ts map for the extended source IC443.
-
-For each candidate, we also generated counts slices. A counts slice
-plots the sum of all counts in the longitudinal direction within 2\deg
-in the latitudinal direction.  The same plot is also shown integrating
-in the longitudinal direction.   An example counts slice is shows for the extended source
-IC443 in figure~\ref{counts_slice}. 
-On top of the plot is overlaid the model
-predicted counts assuming the source has a disk spatial model, assuming
-the source is a point source, and fitting just the diffuse emission in
-the region. 
-Counts slices were especially useful
-for looking at how well the overall diffuse emission model fits the
-region near the sources.
-
-For each candidate, we also generated a radial integral of the data. This
-plot shows the sum of all counts within a given distance from the
-source's center. The plot is binned uniformly in $\Delta \theta^2$ so
-that an isotropic background will be flat in the plot. On top of this
-plot is overlaid the model predicted counts assuming the source has a
-disk spatial model, assuming the source is a point source, and fitting
-just the diffuse emission in the region. An example radial integral
-is shown for the extended source IC443 in figure~\ref{radial_profile}.
-This plot is best for comparing the observed counts to the PSF.
-
-For each source, we make a Galactic and extragalactic diffuse emisison
-subtracted smoothed counts map. Figure~\ref{smoothed_counts} shows an
-example smoothed counts map for IC443. They are useful for qualitativly
-assesing the background model.
-
-Finally, for each source, we performed the dual localization method
-described in section~\ref{dual_localization_method}.  We did so by
-replacing the source with two sources each containing half of the original
-flux and then using \pointlike to simultaneously fit the position and
-spectrum of these sources.  We then used \gtlike to refit the spectrum of
-these sources using the best fit positions. For the new extended sources
-found, we summarize the results of this dual localization test and compare
-the values of \tsext to \tsinc in table~\ref{dual_localization_results}.
-
-Because of the high source density in the Galactic plane for promising
-extended source candidates we often had to iteratively improve the model
-of the background sources to obtain a good fit of the extended source.
-Often, several catalog sources would fill in the emission of one
-extended source and all but one of them would have to be removed from
-the model. Similarly, the position of background sources would often
-have to be refit once the extended source's extension was correctly
-fit. Similarly, background sources were insignificant in the fit
-energy range and had to be removed.  When the position and extension
-of the sources couples strongly with the bacground catalog sources, we
-iteratively fit the position and extended of all nearby sources until the
-fit stabilized.  For each extended source, we describe what modifications
-were required to the sky model to obtain a good fit of the region.
-
-\subsection{Alternative Diffuse Model Crosscheck}
-\label{alt_diff_model_description}
-
-To estimate systematic errors due to uncertainty in the diffuse
-emission background model, we performed a second
-extension test of the candidates using
-an alternative diffuse
-model. The alternative model was based on the GALPROP\footnote{GALPROP
-is a software package for calculating the Galactic $\gamma$-ray
-emission based on a model of cosmic-ray propagation in the Galaxy. See
-\url{http://galprop.stanford.edu/} for details and references} code
-used in the LAT analysis of the isotropic diffuse emission
-(\cite{isotropic_lat}).  
-With this model,
-we independently fit in the nearby region 
-7 HI rings, 7 HII rings, the inverse component,
-the E(B-V) residual, and the isotropic component of
-the background ration.
-All told, we fit in the region 18 individual templates along
-with all source parameters during the analysis.
+table~\ref{alt_diff_model_results} will show a comparison of of \tsext for
+\gtlike and \pointlike.
+
+For each candidate, we generated a map of residual \ts
+by adding a new source of spectral index 2 into the region and finding
+the increase in likelihood when fitting its flux. \ts maps are useful
+to look for residual structure in the sky mode.  Figure~\ref{res_tsmaps}
+shows a residual \ts map for the extended source IC443.
+
+For each candidate, we generated plots of the sum of all counts
+within a given distance of the source and compared it to the model
+predictions of a point source.  The plots were binned uniformly
+in $\Delta \theta^2$ so that an isotropic background would be flat.
+An example radial integral plot is shown for the extended source IC443
+in figure~\ref{four_plots_ic443}(c).  For each source, we also made
+Galactic and extragalactic diffuse emission subtracted smoothed counts
+maps. Figure~\ref{four_plots_ic443}(d) shows an example for IC443.
+
+For each source, we tested to see if the region contained instead
+multiple point sources by replacing the extended source with
+two point sources and performed the dual localization procedure
+described in section~\ref{dual_localization_method}.  We only
+considered a source to be extended if $\tsext>\tsinc$.  For the new
+extended sources, we will show the results of this dual localization in
+table~\ref{dual_localization_results}.
+
+Because of the high source density in the Galactic plane, for promising
+candidates we often had to iteratively improve the model of our background
+sources to obtain a better fit of the sources.  Often, several catalog
+sources would fill in the emission of the extended source and would
+have to be removed from the region.  Similarly, background sources
+were often insignificant in the fit energy range and had to be removed.
+The position of background sources would often have to be refit once the
+extended source was fit.  When the model of the extended source coupled
+strongly with nearby sources, we iteratively fit the extended source and
+all nearby sources until the fit converged.  For each extended source,
+we describe the modification that were required.
+
+\subsection{Systematic Errors on Extension}
+\label{systematic_errors_on_extension}
+
+% Alternative PSF
+
+We estimate a systematic error on the extension of a source due to
+uncertainty in our knowledge of the angular resolution of the LAT.  Before
+launch, the LAT PSF was determined by a detector simulation which was
+verified in accelerator tests (\cite{atwood_LAT_mission}).  A discrepancy
+was found in flight data above a few \gev in the PSF compared to the
+shape of bright AGN.  A publication on this issue is in preparation
+(\cite{lat_on_orbit_psf}).  Subsequently, the PSF was fit empirically to
+bright AGN and this empirical parameterization is the default PSF used
+in the P7\_V6 IRFs.  To account for this uncertainty in our knowledge of
+the PSF, we refit our extended source candidates using the Monte Carlo
+representation of the PSF and consider the difference in extension found
+using the two PSFs as a systematic error on the extension of a source.
+Because the Monte Carlo representation of the PSF is smaller, it leads
+to unphysically higher \tsext values.  This same approach was used in
+(\cite{ic443}).  At high energies, we believe that our parameterization
+of the PSF from bright AGN is substantially better than the Monte Carlo
+representation of the PSF so this systematic errors is conservative.
+
+% Alternate Diffuse
+
+We estimate a second systematic error on the extension of a source
+due to uncertainty in the model of the Galactic diffuse emission by
+using an alternative diffuse model. The alternative model was based on
+the GALPROP\footnote{GALPROP is a software package for calculating the
+Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
+in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
+references} model used in the LAT analysis of the isotropic diffuse
+emission (\cite{isotropic_lat}).  With this model, we independently fit
+along with the point and diffuse sources in the region seven HI rings,
+seven HII rings, the inverse component, the E(B-V) residual, and the
+isotropic component of the background emission.  All told, we fit in
+the region 18 diffuse templates.  This same crosscheck was used in the
+LAT Collaboration's analysis of RX J1713.7-3946 (\cite{rx_j1713_lat}).
 
 It is not expected that this diffuse model is more physical.
-But adding degrees of freedom to the background model is a good
-way to remove likely spurious sources which correlate with features in
-the diffuse emission.  Therefore, this tests systematics that may
-be due to incorrect modeling of the diffuse emission in the region.
+But adding degrees of freedom to the background model can remove
+likely spurious sources that correlate with features in the Galactic
+diffuse emission.  Therefore, this tests systematics that may be
+due to incorrect modeling of the diffuse emission in the region.
 The results of this fit for the new extended source candidates are shown
-in table~\ref{alt_diff_model_results}. Overall, there is good agreement
-between the \ts using the standard and alternative diffuse models, 
-suggesting that the sources are robust against features in the
-diffuse model.
-
-\section{Validation of Known Extended Sources}
+in table~\ref{alt_diff_model_results}. There is good agreement between
+the \ts using the standard and alternative diffuse models, suggesting
+that the sources are robust against features in the diffuse model.
+
+We do not except the systematic error due to uncertainties in the PSF to
+be correlated to the systematic due to uncertainty in the Galactic diffuse
+emission so the total systematic error on the extension of a source so
+we obtain the total systematic error by adding them in quadrature.
+
+\section{Analysis of Extended Sources in 2FGL}
 \label{validate_known}
+
+% 6 SNRs
 
@@
 (\cite{second_cat}).
-
-% 6 SNRs The six extended SNRs IC443, W28, W30, W44, W51C, and the Cygnus
-Loop were included in 2FGL.  IC443, W28, W44, W51C were first reported in
-(\cite{ic443,w28,w44,w51c}).  Detailed papers by the LAT collaboration
-studying W30 and the Cygnus Loop are still in preparation.  \gev emission
-from W30 was also studied in (\cite{castro_and_slane_2010}).  Using photons
-with energies between 1 \gev and 100 \gev, our analysis significantly
-detected the extension
-of all six SNRs. Table~\ref{known_extended_sources} shows the best fit
-positions and extensions of these SNRs.
-
+The six extended SNRs IC443, W28, W30, W44, W51C, and the
+Cygnus Loop were included in 2FGL.  IC443, W28, W44, W51C were
+first reported in (\cite{ic443,w28,w44,w51c}).  Detailed papers
+by the LAT collaboration studying W30 and the Cygnus Loop are
+still in preparation.  \gev emission from W30 was also studied in
+(\cite{castro_and_slane_2010}).  Using photons with energies between
+1 \gev and 100 \gev, our analysis significantly detected the extension
+of all six SNRs. 
 % 2 galaxies
 
-In addition, two nearby galaxies the Large Magalenic Cloud and the
-Small Magalenic Cloud were included in 2FGL (\cite{lmc,smc}).  They were
-significantly detected using photons with energies between 1 \gev and
-100 \gev. Our fit extension is comparable to the published result,
-but we note that previous publication used a more complicated double
-Gaussian spatial model when fitting the LMC.
+Two nearby galaxies the Large Magalenic Cloud and the Small Magalenic
+Cloud were included in 2FGL (\cite{lmc,smc}).  They were significantly
+detected using photons with energies between 1 \gev and 100 \gev. Our
+fit extension is comparable to the published result, but we note that
+previous publication used a more complicated double Gaussian spatial
+model when fitting the LMC.
 
@@
 we fit the extension of MSH 15-52 to be consistent with the published
-size with an extension significance of \tsext=7.2.  Our analysis was
-unable to resolve Vela X which would have required removing the pulsed
-photons from the Vela pulsar. This is beyond the scope of this paper.
-
-% 1 radio galaxy
-Our analysis also failed to detect a significant extension for the
-Centaurus A Lobes (\cite{cen_a_lat}). This is most likely because the
-discovered emission was significantly more complicated than a uniform
+size with an extension significance of \tsext=6.5.
+
+% failed to detect vela x + cen a
+Our analysis was unable to resolve Vela X which would have required first
+removing the pulsed photons from the Vela pulsar. This is beyond the
+scope of this paper.  Our analysis also failed to detect a significant
+extension for the Centaurus A Lobes (\cite{cen_a_lat}). This is because
+the source's emission is significantly more complicated than a uniform
 radially symmetric Disk.
 
-The results are summarized in table~\ref{known_extended_sources}.
-This table includes the best fit position and extension of these
-sources when fitting with a radially symmetric uniform disk spatial
-model.  It also includes the best fit spectral model of each source.
-The difficulty that out analysis had fitting the extension of several
-of the already published extended sources should be used to emphasize
-the overall difficultly in studying spatially extended sources in crowded
-regions of the sky.
+Our analysis of these sources is summarized in
+table~\ref{known_extended_sources}.  This table includes the best fit
+position and extension of these sources when fitting them with a radially
+symmetric uniform disk spatial model.  It also includes the best fit
+spectral parameters for each source.  The position and extension of Vela
+X and the Centaurus A Lobes are included in this list for completeness.
 
@@
 catalog source, and if there are no flags on the source in 2FGL. These
-last two conditions are especially important for our analysis. Source
+last two conditions are important for our analysis. Source
 confusion may look like a spatially extended source and flagged catalog
@@
 Of the 815 clean AGN, we select 775 of these 2FGL sources which
-are significant above 1 \gev and fit each of them for extnesion.
-A histogram of the \tsext values computed for these AGN is shown
-in figure~\ref{agn_ts_ext}. Overlaid on the plot is a $\chi^2/2$
-distribution suggested by Wilks' Theorem.  The \tsext distribution
-for AGN shows good agreement between the theoretical distribution.
-Two sources had $\tsext>9$.  One was due to incorrectly
-    pruning a nearby catalog sources and the other was due to failure
-    of convergence of the point hypothesis.
+are significant above 1 \gev and fit each of them for extension.
+A histogram of the \tsext values computed for these AGN is shown in
+figure~\ref{agn_ts_ext}. Overlaid on the plot is a $\chi^2/2$ distribution
+suggested by Wilks' Theorem.  The \tsext distribution for AGN shows good
+agreement with the theoretical distribution.  Two sources had $\tsext>9$.
+One was due to incorrectly pruning a nearby catalog sources and the
+other was due to a failure of convergence of the point hypothesis.
 This result demonstrates that we can use \tsext as a measure of the
@@
 
-The final effect that could cause this discrepancy is an imperfect
-modeling of the PSF.  Before launch, the PSF was determined by a Monte
-Carlo simulation of the detector.  After launch, a discrepancy was found
-using flight data above a few \gev in the PSF measured using bright
-AGN.  This result was presented in conference and a publication is in
-preparation.  Subsequently, the PSF was fit empirically to bright AGN and
-this empirical parameterization was used in the LAT's instrument response
-function (\cite{lat_on_orbit_psf}).  But the current parameterization
-is not perfect. There are lingering issues due to a lack of statistics
-at high energy which makes it hard to validate the PSF as a function of
-the incident angle of the photon. Since the distribution of incident
-angles varies from source to source, an average PSF may make some of
-the sources look more and less extended than the PSF.
-
-We should finally clarify that the LAT PSF used in this study was
-determined empirically by fitting the observed shape of bright AGN
-(\cite{lat_on_orbit_psf}).  Therefore, finding that the AGN we test are
-not extended is not surprising.  All this analysis shows is that the we
-can search for sources significantly brighter than AGN.  Trying to look
-for the extension of AGN would require a more specialized analysis.
+We should clarify that the LAT PSF used in this study was determined
+empirically by fitting the observed shape of bright AGN (see
+section~\ref{systematic_errors_on_extension}). Finding that the AGN we
+test are not extended is not surprising. Trying to look for the extension
+of AGN would require a more specialized analysis.
 
@@
 
-Nine extended sources not include in 2FGL were found
-using this search.  Three were found in our search using only photons
-with energies above 1 \gev and six were found only using photones with
-energies above 10 \gev.  The fit properties of these nine sources is
-summarized in table~\ref{new_ext_srcs_table}.  The table includes for each
-source the best fit position, extension, spectrum, source significance,
-and significance of extension.  Figure~\ref{allsky_extended_sources}
-shows a skymap of the position of the twelve sources included in 2FGL
-and the nine sources analysis in this paper.
+Nine extended sources not include in 2FGL were found using this search.
+Three were found in our search using photons with energies between
+1 \gev and 100 \gev and six were found using photons with energies between
+10 \gev and 100 \gev.  The fit properties of these nine sources is summarized in
+table~\ref{new_ext_srcs_table}.  This table includes for each source
+the best fit position, extension, spectrum, source significance, and
+significance of extension.
 
@@
 presents a test for source confusion by fitting the region
-as two point sources. The table compares \tsext
-to \tsinc and summarizes the positions and spectra of the two sources.
-Finally, table~\ref{alt_diff_model_results} summarized the results of
-a crosscheck of the source fitting the region with an alternative diffuse
-model described in section~\ref{alt_diff_model_description}.  These tables
-show that our extended sources are not likely the result of source confusion
-and that they are robust to changing the diffuse emission model.
+as two point sources. The table compares \tsext to \tsinc and
+summarizes the positions and spectra of the two sources. 
+Table~\ref{alt_diff_model_results} contains the fit extensions
+using the alternate PSF and Galactic diffuse model described in
+section~\ref{systematic_errors_on_extension}.
 
@@
 
-The two year catalog source 2FGL\,J0823.0-4246 was found to be
-extended using photons with energy between 1 \gev and 100 \gev.
-We found an extension of $0.37\deg\pm0.03\deg$ and an extension
+The two year catalog source 2FGL\,J0823.0-4246 was found 
+using 1-100 \gev photons to have an 
+extension of $0.37\deg\pm0.03\deg\stat\pm0.02\deg\sys$ 
+with an extension
 significance of $\tsext=46.3$.  The source was fit to a position of
@@
 it as two point sources. Because $\tsinc=22.1$ is smaller then \tsext,
-we conclude that this is an extended source.  
-These modifications are shown in
-figure~\ref{1FGL_J0823.3-4248}.
+we conclude that this is an extended source.  These modifications are
+shown in figure~\ref{1FGL_J0823.3-4248}.
 
@@
 
-The two year catalog source 2FGL\,J1627.0-2425c was found to be
-significantly extended when using photons with energies between 1 \gev
-and 100 \gev.  The best fit extension was $0.41\deg\pm0.05\deg$ and the
-best fit position is $(l,b)=(353.08\deg, 16.78\deg)$.
-The extension significance was $\tsext=31.1$. 
+The two year catalog source 2FGL\,J1627.0-2425c was found 
+using 1-100 \gev photons to have an 
+extension of $0.41\deg\pm0.05\deg\stat\pm0.02\deg\sys$ 
+with an extension significance of $\tsext=31.1$. 
+The best fit position is $(l,b)=(353.08\deg, 16.78\deg)$.
 This source is coincident with the one year catalog source 1FGL\,J1628.6-2419c.
@@
 
-The two year catalog source 2FGL\,J1712.4-3941 was found to be
-spatially extended using photons with energies between 1 \gev and
-100 \gev. The source is coincident with the one year catalog source
-1FGL\,J1711.7-3944c. We fit an extension of $0.56\deg\pm0\pm04$ with an
-extension significance of $\tsext=39.6$. This source was fit to a position
-of $(l,b)=(347.25\deg,-0.54\deg)$. Figure \ref{2FGL_J1712.4-3941} shows
-a smoothed counts map of this source.
-
-This source is spatially conincident with the SNR RX J1713.7-3946 and was
+The two year catalog source 2FGL\,J1712.4-3941 was found using 1-100 \gev
+photons to have an extnesion $0.56\deg\pm0.04\deg\stat\pm0.02\deg\sys$
+with an extension significance of $\tsext=39.6$.  This source was
+fit to a position of $(l,b)=(347.25\deg,-0.54\deg)$.  The source
+is coincident with the one year catalog source 1FGL\,J1711.7-3944c.
+Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.
+
+This source is spatially coincident with the SNR RX J1713.7-3946 and was
 recently reported by (\cite{rx_j1713_lat}).  To analyze this source,
@@
 
-The two year catalog source 2FGL\,J0851.7-4635 was found to be
-extended using photons with energies between 10 \gev and 100
-\gev. We fit an extension of $1.13\deg\pm0.08\deg$ with an extension
+The two year catalog source 2FGL\,J0851.7-4635 was found 
+using 10-100 \gev photons to have an
+extension of $1.13\deg\pm0.08\deg\stat\pm0.05\deg\sys$ 
+with an extension
 significance of $\tsext=87.2$.  The source was fit to a position of
@@
 
-2FGL\,J0851.7-4635 is spatially coincident with the SNR Vela Jr.  Overlaid
-on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in \tev by
-H.E.S.S (\cite{vela_jr_hess}).  The \gev and \tev morphology match well.
-
-\todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming
-publication?}
+2FGL\,J0851.7-4635 is spatially coincident with the SNR Vela Jr.
+Overlaid on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
+\tev by H.E.S.S (\cite{vela_jr_hess}).  The \gev and \tev morphology
+match well.  A detailed papers by the LAT collaboration on Vela Jr. is
+in preparation.
 
@@
 
-The two year catalog source 2FGL\,J1615.0-5051 was found to be
-extended using photons with energies between 10 \gev and 100 \gev.
-We found an extension of $0.33\deg\pm0.04\deg$ with an extension
-significance of \tsext=16.3.  The source was fit to a position of
-$(l,b)=(332.38\deg,-0.14\deg)$.  This source is coincident with the one
-year catalog source 1FGL\,J1613.6-5100c.  Figure~\ref{1FGL_J1613.6-5100c}
-shows a counts map of this source.
+The two year catalog source 2FGL\,J1615.0-5051 was found using 10-100 \tev
+photons to have an extension of $0.33\deg\pm0.04\deg\stat\pm0.01\deg\sys$
+with an extension significance of \tsext=16.3.  The source
+was fit to a position of $(l,b)=(332.38\deg,-0.14\deg)$.
+This source is coincident with the one year catalog source
+1FGL\,J1613.6-5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
+of this source.
 
@@
 We removed from our model the source 2FGL\,J1614.9-5212 because it is
-part of 2FGL\,J1615.2-5138's. Furthermore, we removed
-the nearby catalog sources 2FGL\,J1619.7-5040c and 2FGL\,J1620.6-5111c
-because they were not significant above 10 \gev.  These modifications
-are further described in the caption to figure~\ref{1FGL_J1613.6-5100c}.
-After modifying the region, we found that \tsinc=11.9 which is less than
-\tsext so we conclude that the source is extended.
-
-This source is spatially coincident with the extended \tev source HESS
-J1616-508 (\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1613.6-5100c},
-contours of HESS\,J1616-508 are overlaid on 2FGL\,J1615.0-5051.
-The H.E.S.S. experiment measured an extension $0.136\pm 0.008$
-when fitting the source with an elliptical Gaussian spatial model.
-This size corresponds to a 68\% source containment radius of
-$\rsixeight=0.21\deg\pm0.01$. This size is comparable to the LAT size
-$\rsixeight=0.27\deg\pm0.03$ (see section~\ref{compare_source_size}).
+part of 2FGL\,J1615.2-5138's. Furthermore, we removed the nearby catalog
+sources 2FGL\,J1619.7-5040c and 2FGL\,J1620.6-5111c because they were not
+significant above 10 \gev.  These modifications are further described
+in the caption to figure~\ref{1FGL_J1613.6-5100c}.  After modifying
+the region, we found that \tsinc=11.9 which is less than \tsext so we
+conclude that the source is extended.
+
+2FGL\,J1615.2-5138 is spatially coincident with the extended
+\tev source HESS\,J1616-508 (\cite{hess_plane_survey}).  In
+figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
+on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured a Gaussian
+extension $0.136\pm 0.008$ when fitting the source with an elliptical
+Gaussian spatial model.  This size corresponds to a 68\% containment
+radius of $\rsixeight=0.21\deg\pm0.01\deg$. This size is comparable to the LAT
+size $\rsixeight=0.27\deg\pm0.03\deg$ (see section~\ref{compare_source_size}).
 Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
@@
 
-\todo[inline]{Add interpretations of HESS\,J1616-508.}
+HESS\,J1616-508 is located in the region of two SNRs, RCW103 (G332.4-04)
+and Kes 32 (G332.4+0.1) but is not spatially coincident with either
+of them.  HESS\,J1616-508 is near three pulsars near PSR J1614-5048,
+PSR J1616-5109, and PSR J1617-5055 but only PSR J1617-5055 only
+PSR J1617-5055 is energetically favored as being the \tev emitter
+(\cite{integral_HESS_J1616-508}).  \cite{hess_plane_survey}
+speculated that this young pulsar could be responsible for the
+emission of HESS\,J1616-508.  HESS\,J1616-508 is 9' away from PSR
+J1617-5055, which was discovered during ASCA observations of RCW 103
+(\cite{discovery_of_PSR_J1617-5055}). Using an outer gap magnetospheric
+pulsar model, it was previously predicted to be a \tev emitter
+(\cite{pulsar_tev_emission_predictions}).
+
+The pulsar's position is offset from the maximum of the H.E.S.S
+emission and would require an asymetric PWNe to power the \tev
+emission. Offset PWN are expected on theoretical grounds due
+to the PWNe being crushed by an asymmetric SNR reverse shock
+(\cite{offset_pwn_ahronian,offset_pwn_blondin}) but this makes a
+possible association more difficult.  For HESS\,J1825-137, the X-ray
+emission is directed along the \tev offset making this association more
+compelling.\cite{hess_j1825_hess}.
+
+In the region around HESS\,J1616-508, Suzaku found only an upper limit
+in the 2-10 \kev energy range and suggested this source as an example
+of a ``dark particle accelerator'' (\cite{suzakzu_HESS_J1616-508}).
+\cite{integral_HESS_J1616-508} found no evidence of hard X-ray emission
+in the region of HESS\,J1616-508 in the 20-100 \kev energy band with the
+IBIS/ISGRBI on board INTEGRAL. They also observed the field with the XRT
+on board {\em Swift} between 0.2-10 \kev and found no compelling source
+counterpart. Using archival XMM-Newton and BeppoSAX data, they found no
+plausible X-ray counterpart except for PSR J1617-5055.
+
+Finally, Chandra ACIS observations of PSR J1617-5055 revealed
+an underlomonous PWN $\approx1'$ in size around the pulsar
+(\cite{discovery_of_pwn_for_PSR_J1617-5055}). But the PWN is not
+assymetric towards HESS\,J1616-508 which casts doubt upon the association.
+
+Note about this this paper finds other stuff: (\cite{discovery_of_pwn_for_PSR_J1617-5055}).
+
+The \gev emission is suggested to be the same emission component as
+the \tev emission, but further observations of this source at other
+frequencies will likely be needed to firmly associated this source.
+
+\todo[inline]{Finish interpretations of HESS\,J1616-508.}
 
@@
 
-The two year catalog source 2FGL\,J1615.2-5138 was found to be
-extended using photons with energies between 10 \gev and 100 \gev.
-We found an extension of $0.42\deg\pm0.03\deg$ with an extension
+The two year catalog source 2FGL\,J1615.2-5138 was found 
+using 10-100 \gev photons to have
+an extension of $0.42\deg\pm0.03\deg\stat\pm0.01\sys$ 
+with an extension
 significance of \tsext=48.0.  The source was fit to a position
@@
 
-This source is spatially coincident with the extended \tev source HESS
-J1614-518 (\cite{hess_plane_survey}). In figure~\ref{1FGL_J1613.6-5100c},
-contours of HESS\,J1614-518 are overlaid on 2FGL\,J1615.2-5138.
-The H.E.S.S. experiment measured a Gaussian extension of
-$\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$ in the semi-major
-and semi-minor axis. This size corresponds to a 68\% containment size
-of $\rsixeight=0.35\pm0.03\deg$ and $0.23\pm0.03$.  This elliptical size
-matches the LAT size $\rsixeight=0.34\pm0.02$.
-Figure~\ref{hess_seds} shows that the LAT spectrum of
-2FGL\,J1615.2-5138 connects smoothly to the 
-H.E.S.S spectrum of HESS\,J1614-518.
+This source is spatially coincident with the extended
+\tev source HESS\,J1614-518 (\cite{hess_plane_survey}). In
+figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
+on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian
+extension of $\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$ in
+the semi-major and semi-minor axis. This size corresponds to a 68\%
+containment size of $\rsixeight=0.35\deg\pm0.03\deg$ and $0.23\pm0.03$.
+This elliptical size matches the LAT size $\rsixeight=0.35\deg\pm0.03\deg$.
+Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.2-5138
+connects smoothly to the H.E.S.S spectrum of HESS\,J1614-518.
 
@@
 
-The two year catalog source 2FGL\,J1632.4-4753c was found to be
-extended using photons with energies between 10 \gev and 100 \gev.
-We fit an extension of $0.44\deg\pm0.04\deg$ with an extension
+The two year catalog source 2FGL\,J1632.4-4753c was found 
+using 10-100 \gev photons to
+have an extension of $0.44\deg\pm0.04\deg\stat\pm0.03\deg\sys$ 
+with an extension
 significance of \tsext=64.5.  The source was fit to a position of
@@
 2FGL J1634.4-4743c.4-4820c that were part of the extended source..
-We then iterativly relocalized the source 2FGL\,J1635.4-4717c
+We then iteratively relocalized the source 2FGL\,J1635.4-4717c
 to $(l,b)=(337.230\deg,0.346\deg)$ and 2FGL\,J1636.3-4740c to
@@
 to the likelihood fitting this region as two point sources. We found
-$\tsinc=40.6\loglikelihood\tsext$ which is less than \tsext so we conclude
+$\tsinc=40.6$ which is less than \tsext so we conclude
 that this is an extended source.
@@
 figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478 are
-overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured an extension of
+overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a Gaussian extension of
 $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
 axes when fitting the source with an elliptical Gaussian spatial model.
-This corresponds to a 68\% containment size $\rsixeight=0.31\pm0.08$
+This corresponds to a 68\% containment size $\rsixeight=0.31\deg\pm0.08\deg$
 and $0.09\pm0.06$ along the semi-major and semi-minor axis. This
-size is consistent with the LAT size $\rsixeight=0.36\pm0.03$.
+size is consistent with the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.
 Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1635.4-4717c
-connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478.
-
-\todo[inline]{Add interpretation of HESS\,J1632-478.}
+connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478 and most
+likely corresponds to the same emission process
+
+\cite{hess_plane_survey} argued that this source is positionally
+coincident with the hard X-ray source IGR\,J1632-4751 discovered above
+15 \kev by the INTEGRAL satellite (\cite{Igr_J16320-4751_circ}).
+It was also observed by XMM-Newton between 2 and 10 \kev
+(\cite{xmm_newton_IGR_J16320-4751}) and ASCI between 0.7 and 10 \kev
+(\cite{asca_plane_survey}).  But this X-ray source is suspected to be
+an galactic X-Ray Binary so the \gev and \tev extension HESS\,J1632-478
+and 2FGL\,J1632.4-4753c disfavors the association.
+
+Further observations of the region around HESS\,J1632-478 by XMM-Newton
+reveal extended emission between 0.2 \kev and 15 \kev with an elliptical
+size of $\approx32''$ and $\approx15''$ in the semi-major and semi-minor
+axes and inside this extended emission was point-like emission
+(\cite{hess_j1632_478_xmm_newton}).  This x-ray source is positionally
+coincident with the \tev centroid of the H.E.S.S source.  In addition,
+they used data from MGPS-2, an 843 MHz survey of the galactic plane
+carried out with the Molonglo Observatory Synthesis Telescope (MOST)
+to detect an extended diffuse radio source whose size matches well the
+extended X-ray emission \cite{most_survey_galactic_plane}.
+
+They argued that the positional match between the radio and X-ray
+observations argues for a single synchrotron processes emitting from
+radio to X-ray.  This same source could be responsible for the \tev
+emission due to inverse Compton and this matches the expected emission
+from a typical PWNe.
+
+The increased \gev and \tev size compared to the X-ray size
+has previously been observed in several aging PWNe including 
+HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess} and HESS\,J1640-465
+(\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}) and can be explained
+by the electrons emitting syncrotron radiation having a shorter lifetime
+than the electrons emitting inverse Compton radiation.
+
+Because of the spectral and spatial match between the \gev and \tev
+emission, the LAT data naturally fits into this model as being the rising
+edge of the inverse Compton component of a PWN.
 
@@
 
-The two year catalog source 2FGL\,J1837.3-0700c was found to be
-extended using photons with energies between 10 \gev and 100 \gev.
-We fit an extension of $0.35\deg\pm0.08\deg$ with an extension
+The two year catalog source 2FGL\,J1837.3-0700c was found 
+with 10-100 \gev photons 
+to have an extension
+of $0.35\deg\pm0.08\deg\stat\pm0.03\deg\sys$ 
+with an extension
 significance of $\tsext=18.8$.  The source was fit to a position of
@@
 source HESS\,J1837-069 (\cite{hess_plane_survey}).  In
-figure~\ref{1FGL_J1837.5-0659c}, contours of are HESS\,J1837-069
-are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured an extension
+figure~\ref{1FGL_J1837.5-0659c}, contours of HESS\,J1837-069
+are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured a 
+Gaussian extension
 of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$ along the semi-major and
@@
 spatial model.  This corresponds to a 68\% containment radius of
-$\rsixeight=0.18\pm0.03$ and $0.08\pm0.03$ along the semi-major
+$\rsixeight=0.18\deg\pm0.03\deg$ and $0.08\deg\pm0.03\deg$ along the semi-major
 and semi-minor axis. The size is comparable to LAT which fit a 68\%
-containment radius of $\rsixeight=0.29\pm0.07$.  The LAT size is larger
+containment radius of $\rsixeight=0.29\deg\pm0.07\deg$.  The LAT size is larger
 than the H.E.S.S. size but the sizes are almost almost within the
@@
 
-The two year catalog source 2FGL\,J2021.5+4026 was found to be
-extended using photons with energies between 10 \gev and 100
-\gev. This source is coincident with the one year catalog source
-1FGL\,J2020.0+4049. We fit an extension of $0.59\deg\pm0.03\deg$ with
-an extension significance of $\tsext=116.4$.  The source was fit to a
-position of $(l,b)=(78.18\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049}
-shows a counts map of this source.
+The two year catalog source 2FGL\,J2021.5+4026 was found with 10-100 \gev
+photons to have an extension of $0.59\deg\pm0.03\deg\stat\pm0.02\deg\sys$
+with an extension significance of $\tsext=116.4$.  The source was
+fit to a position of $(l,b)=(78.18\deg,2.19\deg)$.  This source
+is coincident with the one year catalog source 1FGL\,J2020.0+4049.
+Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source.
 
@@
 the two year catalog into our background model.  The new source is was
-localized to a position of $(l,b)=(78.85,2.67)$ and had $\ts=13.5$ .
+localized to a position of $(l,b)=(78.85\deg,2.67\deg)$ and had $\ts=13.5$ .
 Although the source is not very significant, not including it into the
@@
 
-Many extended sources. Especially instructive to use photons with energy
+Many extended sources. Instructive to use photons with energy
 above 10 \gev where we don't have to worry about diffuse background
@@
 Make some conclusion about how the LAT will eventually collect a factor
-of five more data! Pointlike will be necessary to improve the model of
+of five more data! \pointlike will be necessary to improve the model of
 the high energy sky. Hard to do a blind analysis of LAT data.
@@
 For all extended sources seen both in \gev and \tev,
-figure~\ref{gev_vs_tev_plot} shows a comparision of their sizes.
+figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.
 Note that there is pretty good agreement.
+
+Note about how comparison of HESS and LAT sizes will require more accurate
+ellitpical gaussian fitting + using the same spatial model.  Interesting
+to see if there is a correlation for PWN between energy and source size!
+
+LAT has a planned lifetime of 5 years with (don't know how to phrase this) 
+hope to run for 10 years. Additonal data will allow us to perfrom
+more detailed morphological and spectral analysis of these sources.
+
+Improved diffuse model and better statisticsl will allow us to push
+our analysis to lower energies.
 
@@
 \bibliography{extended_catalog}
-
-\appendix
 
@@
   \begin{center}
-    \includegraphics{ic443_plots/profile_ic443.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_profile_ic443/v1/profile_ic443.pdf
+    \includegraphics{ic443_plots/four_plots_ic443.pdf}
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
     \caption{
-    A plot of the overall change in \ts when varying the
-    extension of the extended SNR IC443.  As is discussed in section
-    \ref{extension_error}, the error on the extension of a source is
-    calculated by varying the extension away from its best fit value until
-    the \loglikelihood has changed by a particular amount.  These profiles are
-    generated for all extended source candidates. They are useful
-    to make sure the fitter find a global minimum and that
-    the likelihood function is not unphysically double peaked.
+    All plots are for the SNR IC443 using two years of data.
+    % ts vs extension
+    Plot (a) is the change in \ts when varying the
+    extension of the source.  
+    % ts_ext vs energy
+    Plot (b) is \tsext in twelve energy bins. This plot shows that there is
+    little gain in sensitivity to the extension using photons
+    with energies below 1 \gev, even for a source with an index $\approx2.4$.
+    % radial integral
+    Plot (c) is the sum of all counts within a given radial distance
+    from the source binned uniformly in $\theta^2$. 
+    Overlaid on the plot is the model predicted counts assuming that
+    the source is both an extended source and a point source
+    % smoothed counts
+    Plot (d) is a counts map of the source with the Galactic and
+    isotropic diffuse emission subtracted and smoothed by a $0.1\deg$
+    Gaussian kernel.  The inset is the predicted emission from a point
+    source of the same spectrum and intensity.  The PSF is smoothed
+    by the same kernel.  Plots (a), (c), and (d) use only photons with
+    energies between 1 \gev and 100 \gev. Plots (c) and (d)
+    use only photons which converted in the front
+    part of the detector and have an improved angular resolution.
     }
-    \label{extension_profile}
+    \label{four_plots_ic443}
   \end{center}
@@
     \caption{
-    This plot demonstrates that different spatial models when smoothed
-    by the PSF look similar.  The $y$ axis is the log of the
-    intensity and the $x$ axis is $\theta^2$.  The black line is the
-    PSF that would be observed for a power-law source of spectral index
-    2. The dashed red line is the probability density of a Gaussian with
-    $\rsixeight=0.5\deg$, which is just a straight line on this plot
+    A comparison of the Gaussian and uniform disk PDFs before and
+    after convolving with the PSF.  The black line is the PSF that
+    would be observed for a power-law source of spectral index 2. The
+    dashed red line is the probability density of a Gaussian with
+    $\rsixeight=0.5\deg$, which is just a straight line on this plot.
     The dashed blue line is the probability density for a uniform disk
@@
     show the convolution of the Gaussian and uniform disk with the PSF.
-    The left plot shows the analysis with an energy range from 1 \gev to
-    100 \gev whereas the right plot shows the analysis with an energy
-    range from 10 \gev to 100 \gev.  This plot is discussed further in
-    section~\ref{compare_source_size}.
+    Plot (a) shows the analysis in the energy range from 1 \gev to 100
+    \gev while plot (b) shows the analysis only in the energy range
+    from 10 \gev to 100 \gev. This plot demonstrates that different
+    spatial models when smoothed by the PSF look similar.  The $y$
+    axis is the log of the intensity and the $x$ axis is $\theta^2$.
+    This plot is discussed further in section~\ref{compare_source_size}.
     }\label{compare_disk_gauss}
@@
     \caption{
-    The results of the Monte Carlo simulation described
-    in section \ref{monte_carlo_validation} and detailed in
-    table~\ref{ts_ext_num_sims}. The plot shows the null distribution of
+     The plot shows the null distribution of
     the likelihood ratio test when fitting a point source for extension.
@@
     as the distribution these curves should should follow.  There is
-    a surprisingly good agreement between the Monte Carlo results and
+    good agreement between the Monte Carlo results and
     the theoretical distribution. For most spectral parameters, the
@@
     paper, we use this theoretical curve to estimate the significance of
-    our source detections. This plot cuts off three simulations of the
-    source with flux $3\times10^{-8}\ph/\cm^2/\sec$ and spectral index
-    2.5 which had \tsext of 26.1, 28.9, and 38.1.
+    the detection of a source's extension. This plot cuts off 
+    three simulations with $\tsext>25$. They 
+    had a flux $3\times10^{-8}\ph/\cm^2/\sec$, spectral index
+    2.5, and \tsext of 26.1, 28.9, and 38.1.
+    The Monte Carlo simulation is described in 
+    section \ref{monte_carlo_validation} and 
+    the number of simulation for each spectral model 
+    are presented in table~\ref{ts_ext_num_sims}.
     }\label{ts_ext_mc}
@@
     \includegraphics{mc_plots/index_sensitivity.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
     \end{center}
     \caption{
-    This plot shows the detection threshold to resolve an extended source.
-    It is defined as the flux where $\langle\tsext\rangle=25$ for a
-    given extension.  The $x$ axis is the extension of a uniform disk
-    extended source and the $y$ axis is the source's 100 \mev to 100
-    \gev photon flux.  All sources have an assumed power-law spectrum
-    and the different colors are for sources of different simulated
-    spectral indices.  The solid line is the detection threshold using
-    photons with energy between 100 \mev and 100 \gev while the dashed
-    line is the threshold using photons with energy between 1 \gev and
-    100 \gev.  The detection threshold is for a one year simulation
-    against a Sreekumar-like isotropic background.  More information
+    This plot shows the detection threshold to resolve a uniform
+    disk extended source.  The detection threshold is defined as the flux where
+    $\langle\tsext\rangle=16$ for a given extension.  The $x$ axis is
+    the extension of a uniform disk extended source and the $y$ axis
+    is the source's 100 \mev to 100 \gev photon flux.  All sources have
+    an assumed power-law spectrum and the different colors are different
+    simulated spectral indices.  The solid line is the detection threshold
+    using photons with energy between 100 \mev and 100 \gev while the
+    dashed line is the threshold using photons with energy between 1 \gev
+    and 100 \gev.  The detection threshold is for the same two year time
+    range as was used in 2FGL and in the following extended source search.
+    The extended sources are simulated against
+  a Sreekumar-like isotropic background.  More information
     about this plot is presented in section~\ref{extension_sensitivity}.
@@
     significantly improved using photons with energy between 100 \mev
-    and 1 \gev.
-    \todo[inline]{Overlay on this plot the twelve extended sources}
+    and 1 \gev. More information about this plot is presented
+    in section~\ref{extension_sensitivity}.
     }\label{index_sensitivity}
@@
     \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_diff_factor.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_diff_factor.py
     \end{center}
     \caption{
-    These plots presents the sensitivity for varying background
-    levels and energy ranges.  The plots have the same meaning as in
+    This shows the detection threshold to a uniform disk extended
+    source for varying background levels
+    and energy ranges.  The plots have the same meaning as in
     figure~\ref{index_sensitivity} and the simulations occur over the
-    same time range.  The blue dash dotted line is the sensitivity
-    against a Sreekumar-like isotropic background. The green dashed
-    curve is the sensitivity against 10 times the isotropic background
-    and the solid red curve is the sensitivity against 100 times the
-    isotropic background.  The latter factor approximately represents
-    the intensity of the Galactic diffuse emission near the Galactic
-    center.  The left plot is the sensitivity using photons with energies
-    between 1 \gev and 100 \gev while the right plot is the sensitivity
-    using photons with energies between 10 \gev and 100 \gev. Unlike
-    figure~\ref{index_sensitivity}, the sensitivity was calculated
-    only for a power-law source of spectral index 2. The flux is quoted
-    only in the selected energy range which weakens the dependence of
-    the detection threshold on spectral index.  These plots show that
-    we are less sensitive to extended sources in regions with higher
-    background and (given the same number of photons) more sensitive
-    to harder sources.  More information about this plot is presented
+    same time range.  The solid blue line is the detection threshold against a
+    Sreekumar-like isotropic background. The green dashed curve is the
+    threshold against 10 times the isotropic background and the dash
+    dotted red curve is the threshold against 100 times the isotropic
+    background.  The latter factor approximately represents the intensity
+    of the Galactic diffuse emission near the Galactic center.  Plot (a)
+    is the threshold using photons with energies between 1 \gev and 100
+    \gev while plot (b) is the threshold using photons with energies
+    between 10 \gev and 100 \gev. Unlike figure~\ref{index_sensitivity},
+    the detection threshold was calculated only for a power-law source of spectral
+    index 2. The flux is quoted only in the selected energy range which
+    weakens the dependence of the detection threshold on spectral index.
+    These plots show that we are less sensitive to extended sources in
+    regions with higher background and (given the same number of photons)
+    more sensitive to harder sources.  Overlaid on this plot are the
+    extended sources found in this extended source search. The extended
+    sources are color coded based upon whether the integral galactic
+    diffuse and isotropic diffuse emission model is closer to 1x, 10x,
+    or 100x the Sreekumar-like isotropic spectrum.  The red point
+    in plot (a) below the red line is RX J1713.7-3946 which is harder
+    ($\gamma\approx1.5$) and has diffuse emission only 53 times larger
+    than the isotropic emission.  The green point in plot (b) below
+    the green line is MSH 15-52 which was found by our analysis to
+    have $\tsext=6.5$.  More information about this plot is presented
     in section~\ref{extension_sensitivity}.
     }\label{diff_factor_sensitivity}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{ic443_plots/ic443_ts_ext_vs_energy.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
-    \caption{
-    The plot shows \tsext for twelve uniform log(energy) bins between 100 \mev
-    and 100 \gev for the SNR IC443. IC443 has a spectral index $~2.4$
-    (table~\ref{known_extended_sources}). This plot shows that there is
-    little gain in sensitivity to the extension of a source using photons
-    with energies below 1 \gev, even for a source with an index 2.4.
-    For this reason, this paper restricts its analysis to energies above
-    1 \gev.
-    }
-    \label{ts_ext_vs_energy}
-  \end{center}
   \end{figure}
@@
   \caption{An example residual test statistic map generated for the
-  supernova remnant IC443 using photons with energy between 1 \gev and
-  100 \gev.  The top plot is the residual TS map fitting IC443
-  as a point source and the bottom plot is the residual TS map fitting
-  IC443 as an extended source. The crosses in the plot represent all of
-  the sources fit in the region. Since there is a residual TS greater
-  than 160 fitting with the point hypothesis, it is clear that a point
-  source is not a good fit to the region. On the other hand,
-  the residual TS fitting as an extended source is much lower, showing
-  that IC443 is better fit by an extended source. These plots were generated
-  for all extended source candidates to help validate the analysis.}
+  supernova remnant IC443 using photons with energy between 1 \gev
+  and 100 \gev. Plot (a) is the residual \ts fitting IC443 as a point
+  source and plot (b) is the residual TS fitting IC443 as an extended
+  source. The crosses in the plot represent all of the sources modeled
+  in the region. Since there is residual TS greater than 160 fitting
+  with the point hypothesis so it is not a good model of the source.
+  On the other hand, the residual fitting IC443 as an extended source
+  is much lower because IC443 is better fit by an extended source. These
+  plots were generated for all extended source candidates to help validate
+  the analysis.}
   \label{res_tsmaps}
@@
 \clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{ic443_plots/ic443_counts_slice.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/counts_slice_ic443/v1/ic443_counts_slice.pdf
-    \caption{ The upper plot is the sum of the counts binned in Galactic
-    longitudinal summed within 2\deg in Galactic latitude centered on the
-    SNR IC443. The lower plot shows the same image but instead integrated
-    in Galactic longitude.  Overlaid on the plot is the model predicted
-    counts assuming that IC443 is a point source, an extended source, and
-    that there is just the diffuse background.  These plots were generated
-    for all extended source candidates.  They are especially useful for
-    visually assessing the quality of the diffuse emission model in the
-    region surrounding an extended source candidate.} \label{counts_slice}
-  \end{center}
-\end{figure}
-
-\clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{ic443_plots/ic443_radial_integral.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/radial_integral_ic443/v1/ic443_radial_integral.pdf
-    \caption{The sum of all counts within a given radial distance from
-    the SNR IC443's best fit position.  This plot is binned uniformly
-    in $\theta^2$ to correct for solid angle so that an isotropic
-    distribution is flat. Overlaid on the counts distribution is the
-    model predicted counts assuming the IC4343 is a point source, an
-    extended source, and that there is just the diffuse background.
-    These plots were generated for all extended source candidates.
-    These radial integral plots are useful for visually comparing the
-    observed counts to the PSF.}
-    \label{radial_profile}
-  \end{center}
-\end{figure}
-
-\clearpage
-\begin{figure}
-  \begin{center}
-    \includegraphics{ic443_plots/ic443_smoothed_counts.pdf}
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/smoothed_counts_ic443/v1
-    \caption{A map of the observed photons in the region around the SNR
-    IC443 with energies between 1 \gev and 100 \gev.  This plot has the
-    Galactic and isotropic diffuse emission subtracted and is smoothed
-    by a $0.1\deg$ Gaussain kernel.  The overlaid box is the PSF for
-    a source of the same spectrum as IC443 normalized to have the same
-    intensity as IC443.  This PSF is smoothed by the same Gaussian kernel
-    and so represents the model of what IC443 would look like if it was
-    a point source. Since the observed counts are wider than the PSF,
-    we can see visually that IC443 is an extended source.  The black
-    cross is IC443's best fit center when fitting it with a uniform
-    disk spatial model. The
-    black crosses are all of the catalog sources in
-    the region and the red circle is the edge of the best fit
-    uniform disk which was fit to IC443 using \pointlike.  These plots
-    were generated for all extended source candidates.  They are useful
-    for assessing the overall quality of the source model and for looking
-    for nearby background sources which are not correctly modeled.}
-    \label{smoothed_counts}
-  \end{center}
-\end{figure}
-
-\clearpage
 \begin{sidewaystable}
     \begin{centering}
-      \begin{tabular}{l|rrrrrrrrrr}
-        \hline
-        \hline
-        Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &     PosErr &                  Flux &                 Index &                      \\
-        \hline
-        \multicolumn{10}{c}{$E > 1 \gev$} \\
-        \hline
-        SMC                  &     302.68\deg &     -44.81\deg & $  1.75\deg \pm   0.13\deg$ &       94.4 &       66.4 &   0.12\deg & $    3.3 \pm     0.4$ & $   2.40 \pm    0.17$ &                      \\
-        LMC                  &     279.10\deg &     -32.61\deg & $  1.74\deg \pm   0.07\deg$ &     1102.4 &      861.9 &   0.05\deg & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$ &                      \\
-        IC443                &     189.05\deg &       3.04\deg & $  0.36\deg \pm   0.01\deg$ &    10698.1 &      503.5 &   0.01\deg & $   64.9 \pm     1.2$ & $   2.23 \pm    0.02$ &                      \\
-        W28                  &       6.50\deg &      -0.27\deg & $  0.43\deg \pm   0.02\deg$ &     1323.4 &      172.6 &   0.01\deg & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$ &                      \\
-        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.04\deg$ &      468.6 &       77.2 &   0.02\deg & $   30.8 \pm     1.6$ & $   2.59 \pm    0.05$ &                      \\
-        W44                  &      34.69\deg &      -0.38\deg & $  0.36\deg \pm   0.02\deg$ &     1910.4 &      222.4 &   0.01\deg & $   74.0 \pm     2.0$ & $   2.68 \pm    0.02$ &                      \\
-        W51C                 &      49.13\deg &      -0.45\deg & $  0.28\deg \pm   0.02\deg$ &     1814.2 &      110.6 &   0.01\deg & $   39.2 \pm     1.3$ & $   2.35 \pm    0.03$ &                      \\
-        Cygnus Loop          &      74.22\deg &      -8.46\deg & $  1.72\deg \pm   0.05\deg$ &      356.5 &      356.5 &   0.06\deg & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$ &                      \\
-        \hline
-        \multicolumn{10}{c}{$E > 10 \gev$} \\
-        \hline
-        MSH 15-52            &     320.38\deg &      -1.22\deg & $  0.20\deg \pm   0.06\deg$ &       75.2 &        7.2 &   0.03\deg & $    0.6 \pm     0.7$ & $   2.26 \pm    0.73$ &                      \\
-        HESS J1825-137       &      17.56\deg &      -0.46\deg & $  0.65\deg \pm   0.07\deg$ &       81.6 &       51.4 &   0.05\deg & $    1.8 \pm     0.1$ & $   1.74 \pm    0.06$ &                      \\
+      \begin{tabular}{l|rrlrrrrrrr}
+        \hline
+        \hline
+        Name                 &          \glon &          \glat &                \multicolumn{1}{r}{$\sigma$} &         TS &   $\tsext$ &    Pos Err &                  Flux &                 Index  \\
+        \hline
+        \multicolumn{9}{c}{$E > 1 \gev$} \\
+        \hline
+        SMC                  &     302.68\deg &     -44.81\deg & $  1.75\deg \pm   0.07\deg \pm   0.02\deg $ &       94.8 &       67.4 &   0.12\deg & $    3.3 \pm     0.4$ & $   2.41 \pm    0.17$  \\
+        LMC                  &     279.10\deg &     -32.61\deg & $  1.74\deg \pm   0.05\deg \pm   0.13\deg $ &     1101.3 &      860.5 &   0.05\deg & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$  \\
+        IC443                &     189.05\deg &       3.04\deg & $  0.36\deg \pm   0.01\deg \pm   0.04\deg $ &    10719.8 &      510.4 &   0.01\deg & $   64.8 \pm     1.2$ & $   2.23 \pm    0.02$  \\
+        Vela X               &     263.34\deg &      -3.11\deg & $                                 0.88\deg$ &            &            &            &                       &                       \\
+        Centarus A           &     309.52\deg &      19.42\deg & $                            \approx10\deg$ &            &            &            &                       &                       \\
+        W28                  &       6.50\deg &      -0.27\deg & $  0.43\deg \pm   0.02\deg \pm   0.03\deg $ &     1324.8 &      177.4 &   0.01\deg & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$  \\
+        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.02\deg \pm   0.02\deg $ &      465.4 &       73.3 &   0.02\deg & $   30.7 \pm     1.6$ & $   2.59 \pm    0.04$  \\
+        W44                  &      34.69\deg &      -0.38\deg & $  0.36\deg \pm   0.01\deg \pm   0.02\deg $ &     1903.3 &      217.7 &   0.01\deg & $   73.6 \pm     1.8$ & $   2.68 \pm    0.02$  \\
+        W51C                 &      49.13\deg &      -0.45\deg & $  0.28\deg \pm   0.02\deg \pm   0.05\deg $ &     1819.5 &      115.7 &   0.01\deg & $   39.3 \pm     1.3$ & $   2.35 \pm    0.03$  \\
+        Cygnus Loop          &      74.22\deg &      -8.46\deg & $  1.72\deg \pm   0.05\deg \pm   0.07\deg $ &      356.5 &      356.5 &   0.06\deg & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$  \\
+        \hline
+        \multicolumn{9}{c}{$E > 10 \gev$} \\
+        \hline
+        MSH 15-52            &     320.38\deg &      -1.22\deg & $  0.20\deg \pm   0.04\deg \pm   0.03\deg $ &       76.2 &        6.5 &   0.03\deg & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
+        HESS J1825-137       &      17.56\deg &      -0.46\deg & $  0.65\deg \pm   0.03\deg \pm   0.01\deg $ &       83.6 &       55.9 &   0.05\deg & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
+        \hline
+        \hline
       \end{tabular}
-      \caption{The fit for ten of the twelve extended sources included
-      in 2FGL.  The top list are the extended sources
-      analyzed using photons with energies between 1 \gev and 100 \gev.
-      The lower table are the sources analyzed using photons with energies
-      between 10 \gev and 100 \gev.  The quoted flux is in units of
-      $10^{-9}\ph/\cm^2/\sec$ and is the flux in the fit energy range
-      (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).  All sources
-      were fit using a uniform disk spatial template. The localization
-      and extension were found using \pointlike while the TS and spectral
-      values were calculated using \gtlike.  The TS value was computed
-      assuming the best fit uniform disk spatial model and \tsext
-      compares the increase in \ts fitting the source with an extended
-      spatial model to point model.  \glon and \glat are respectively the
-      Galactic longitude and Galactic latitude of the source and $\sigma$
-      is the edge of the best fit uniform disk spatial model.  PosErr
-      is the error on the localization of the source.  The extended PWN
-      Vela X is not include in this list because a phase cut would be
-      required to remove the Vela pulsar (\cite{velax}).  The extended
-      Centaurus A lobes are not included because a radially symmetric
-      uniform disk spatial model is a very bad match to the observed
-      emission (\cite{cen_a_lat}).  More information about these sources
-      is in section~\ref{validate_known}.
+      \caption{The twelve extended sources included in 2FGL.  The top
+      list are the extended sources analyzed using photons with energies
+      between 1 \gev and 100 \gev.  The lower table are the sources
+      analyzed using photons with energies between 10 \gev and 100 \gev.
+      The quoted flux is in units of $10^{-9}\ph/\cm^2/\sec$ and is the
+      flux in the fit energy range (either 1-100 \gev or 10-100 \gev).
+      All sources were fit using a uniform disk spatial template. The
+      localization and extension were found using \pointlike while the
+      TS and spectral values were calculated using \gtlike.  \ts and
+      \tsext was computed with \gtlike assuming the best fit uniform
+      disk spatial model from \pointlike.  \glon and \glat are Galactic
+      longitude and latitude of the best fit extended source respectively.
+      $\sigma$ is the edge of the best fit uniform disk spatial model.
+      The first error on $\sigma$ is statistical and the second error
+      is systematic (see section~\ref{systematic_errors_on_extension}).
+      Pos Err is the error on the localization of the source.  Statistical
+      errors are at the $1\sigma$ level.  The Vela X and the Centarus A
+      Lobes were not fit by our anaysis but are include for completeness
+      (\cite{velax,cen_a_lat}). More information about these sources is
+      in section~\ref{validate_known}.
       }
@@
     \end{center}
-    \caption{The cumulative density of \tsext for 775 of the
-    clean AGN in 2LAC which are significant above 1 \gev.
+    \caption{The cumulative density of \tsext for 775 of
+    the clean AGN in 2LAC which are significant above 1 \gev.
     AGN are expected to be unresolvable so overlaid on this plot
-    is a $\chi^2/2$ distribution suggested by Wilk's theorem (see
+    is a $\chi^2/2$ distribution suggested by Wilks' theorem (see
     section~\ref{monte_carlo_validation}).  The \tsext distribution
-    computed with \pointlike agrees with Wilk's theorem which confirms
-    that we can use \tsext as a calibrated test of extension. The
-    distribution computed by \gtlike is biased towards smaller values of
-    \tsext. This is because \tsext is optimized using \pointlike and minor
-    difference in the \pointlike and \gtlike likelihood function will
-    cause the best fit value between these two methods to differ. Because
-    \gtlike's curve lies to the left of the theoretical distribution,
-    requiring that \tsext is significant with both methods makes this
-    test for extension conservative.  Two sources had $\tsext>9$.  One was due to incorrectly
-    pruning a nearby catalog sources and the other was due to failure
-    of convergence of the point hypothesis.  More information about this
-    analysis is presented in section~\ref{test_1lac_sources}.
+    computed with \pointlike agrees with Wilks' theorem and confirms
+    that we can use \tsext as a test of extension. The distribution
+    computed by \gtlike is biased towards smaller values of \tsext. This
+    is because \tsext is optimized using \pointlike and minor difference
+    in the \pointlike and \gtlike likelihood function will cause the
+    best fit model to be slightly different. Because \gtlike's curve
+    lies to the left of the theoretical distribution, this makes our
+    test conservative. More information about this analysis is presented
+    in section~\ref{test_1lac_sources}.
     }\label{agn_ts_ext}
@@
 \clearpage
+\thispagestyle{empty}
 \begin{sidewaystable}
   \begin{centering}
-    \begin{tabular}{l|rrrrrrrrrr}
-      \hline
-      \hline
-      Name                 &          \glon &          \glat &                    $\sigma$ &         TS &   $\tsext$ &     PosErr &                  Flux &                 Index &          Counterpart \\
+    \begin{tabular}{l|rrlrrrrrrr}
+      \hline
+      \hline
+      Name                 &          \glon &          \glat &                \multicolumn{1}{r}{$\sigma$} &         TS &   $\tsext$ &    Pos Err &                  Flux &                 Index &          Counterpart \\
       \hline
@@
       \hline
-      2FGL\,J0823.0-4246   &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg$ &      320.9 &       46.3 &   0.02\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
-      2FGL\,J1627.0-2425c  &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg$ &      144.5 &       31.1 &   0.04\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
-      2FGL\,J1712.4-3941   &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg$ &       75.0 &       39.6 &   0.05\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
+      2FGL\,J0823.0-4246   &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg \pm   0.02\deg $ &      320.9 &       46.3 &   0.02\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
+      2FGL\,J1627.0-2425c  &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg \pm   0.02\deg $ &      144.5 &       31.1 &   0.04\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
+      2FGL\,J1712.4-3941   &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg \pm   0.01\deg $ &       75.0 &       39.6 &   0.05\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
       \hline
@@
       \hline
-      2FGL\,J0851.7-4635   &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg$ &      116.1 &       87.2 &   0.07\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr.
+      2FGL\,J0851.7-4635   &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg \pm   0.05\deg $ &      116.1 &       87.2 &   0.07\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr.
 \\
-      2FGL\,J1615.0-5051   &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg$ &       53.4 &       16.3 &   0.04\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
-      2FGL\,J1615.2-5138   &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg$ &       76.6 &       48.0 &   0.05\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
-      2FGL\,J1632.4-4753c  &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg$ &      127.8 &       64.5 &   0.04\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
-      2FGL\,J1837.3-0700c  &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg$ &       46.2 &       18.8 &   0.07\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
-      2FGL\,J2021.5+4026   &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg$ &      222.2 &      116.4 &   0.04\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &          Gamma Cygni \\
+      2FGL\,J1615.0-5051   &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg \pm   0.01\deg $ &       53.4 &       16.3 &   0.04\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
+      2FGL\,J1615.2-5138   &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg \pm   0.01\deg $ &       76.6 &       48.0 &   0.05\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
+      2FGL\,J1632.4-4753c  &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg \pm   0.03\deg $ &      127.8 &       64.5 &   0.04\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
+      2FGL\,J1837.3-0700c  &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg \pm   0.03\deg $ &       46.2 &       18.8 &   0.07\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
+      2FGL\,J2021.5+4026   &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg \pm   0.02\deg $ &      222.2 &      116.4 &   0.04\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &          Gamma Cygni \\
       \hline
@@
     have the same meaning as in table~\ref{known_extended_sources}.
-    The quoted flux is in units of
-      $10^{-9}\ph/\cm^2/\sec$ and is the flux in the fit energy range
-      (either 1 \gev to 100 \gev or 10 \gev to 100 \gev)
     More information about these sources can be found in
@@
     \begin{centering}
-      \begin{tabular}{l|rrrrrrrr}
-        \hline
-        \hline
-        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
-        \hline
-        \multicolumn{9}{c}{$E > 1 \gev$} \\
-        \hline
-        2FGL\,J0823.0-4246   &                350.9 &                320.9 &                352.5 &                     66.0 &                   46.3 &                 53.6 & $  0.37\deg \pm   0.03\deg$ & $  0.39\deg \pm   0.03\deg$ \\
-        2FGL\,J1627.0-2425c  &                170.2 &                144.5 &                112.6 &                     43.9 &                   31.1 &                 23.9 & $  0.41\deg \pm   0.05\deg$ & $  0.40\deg \pm   0.04\deg$ \\
-        2FGL\,J1712.4-3941   &                 80.9 &                 75.0 &                 43.4 &                     47.4 &                   39.6 &                 22.2 & $  0.56\deg \pm   0.04\deg$ & $  0.56\deg \pm   0.04\deg$ \\
-        \hline
-        \multicolumn{9}{c}{$E > 10 \gev$} \\
-        \hline
-        2FGL\,J0851.7-4635   &                116.7 &                116.1 &                122.3 &                     87.1 &                   87.2 &                 90.4 & $  1.13\deg \pm   0.08\deg$ & $  1.16\deg \pm   0.08\deg$ \\
-        2FGL\,J1615.0-5051   &                 52.4 &                 53.4 &                 55.6 &                     17.5 &                   16.3 &                 17.4 & $  0.33\deg \pm   0.04\deg$ & $  0.32\deg \pm   0.04\deg$ \\
-        2FGL\,J1615.2-5138   &                 76.3 &                 76.6 &                 86.3 &                     44.0 &                   48.0 &                 52.6 & $  0.42\deg \pm   0.03\deg$ & $  0.43\deg \pm   0.03\deg$ \\
-        2FGL\,J1632.4-4753c  &                126.6 &                127.8 &                120.7 &                     63.9 &                   64.5 &                 64.1 & $  0.44\deg \pm   0.04\deg$ & $  0.44\deg \pm   0.04\deg$ \\
-        2FGL\,J1837.3-0700c  &                 45.4 &                 46.2 &                 39.0 &                     18.5 &                   18.8 &                 16.6 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
-        2FGL\,J2021.5+4026   &                234.3 &                222.2 &                235.6 &                    135.9 &                  116.4 &                121.4 & $  0.59\deg \pm   0.03\deg$ & $  0.60\deg \pm   0.03\deg$ \\
+      \begin{tabular}{l|rrr|rrr|rrr}
+        \hline
+        \hline
+        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &       $\ts_\altdiff$ &      $\tsext_\pointlike$ &       $\tsext_\gtlike$ &    $\tsext_\altdiff$ &                $\sigma$ &       $\sigma_\altdiff$ &        $\sigma_\altpsf$ \\
+        \hline
+        \multicolumn{10}{c}{$E > 1 \gev$} \\
+        \hline
+        2FGL\,J0823.0-4246   &                350.9 &                320.9 &                352.5 &                     66.0 &                   46.3 &                 53.6 & $             0.37\deg$ & $             0.39\deg$ & $             0.38\deg$ \\
+        2FGL\,J1627.0-2425c  &                170.2 &                144.5 &                112.6 &                     43.9 &                   31.1 &                 23.9 & $             0.41\deg$ & $             0.40\deg$ & $             0.39\deg$ \\
+        2FGL\,J1712.4-3941   &                 80.9 &                 75.0 &                 43.4 &                     47.4 &                   39.6 &                 22.2 & $             0.56\deg$ & $             0.56\deg$ & $             0.54\deg$ \\
+        \hline
+        \multicolumn{10}{c}{$E > 10 \gev$} \\
+        \hline
+        2FGL\,J0851.7-4635   &                116.7 &                116.1 &                122.3 &                     87.1 &                   87.2 &                 90.4 & $             1.13\deg$ & $             1.16\deg$ & $             1.17\deg$ \\
+        2FGL\,J1615.0-5051   &                 52.4 &                 53.4 &                 55.6 &                     17.5 &                   16.3 &                 17.4 & $             0.33\deg$ & $             0.32\deg$ & $             0.32\deg$ \\
+        2FGL\,J1615.2-5138   &                 76.3 &                 76.6 &                 86.3 &                     44.0 &                   48.0 &                 52.6 & $             0.42\deg$ & $             0.43\deg$ & $             0.43\deg$ \\
+        2FGL\,J1632.4-4753c  &                126.6 &                127.8 &                120.7 &                     63.9 &                   64.5 &                 64.1 & $             0.44\deg$ & $             0.44\deg$ & $             0.47\deg$ \\
+        2FGL\,J1837.3-0700c  &                 45.4 &                 46.2 &                 39.0 &                     18.5 &                   18.8 &                 16.6 & $             0.35\deg$ & $             0.34\deg$ & $             0.38\deg$ \\
+        2FGL\,J2021.5+4026   &                234.3 &                222.2 &                235.6 &                    135.9 &                  116.4 &                121.4 & $             0.59\deg$ & $             0.60\deg$ & $             0.60\deg$ \\
       \end{tabular}
-      \label{alt_diff_model_results}
       \caption{
-      This table shows a comparison of the \ts values gotten using \gtlike
-      and \pointlike.  It also compares the fit values using the standard
-      diffuse model and using the alternative diffuse model described
-      in section~\ref{alt_diff_model_description}.  $\ts_\pointlike$
-      is the \ts of the source fit with the extended hypothesis using
-      \pointlike whereas $\ts_\gtlike$ is the same quantity using the
-      same model but fitting with \gtlike.  There is good agreement
-      between the two methods.
-      }
+      For the new extended sources, this table shows the results of
+      fitting the new extended sources with an alternate diffuse model and
+      an alternate PSF (see section~\ref{systematic_errors_on_extension}).
+      It also compares the best fit results of \pointlike to \gtlike.
+      $\ts_\pointlike$ and $\ts_\gtlike$, and $\ts_\altdiff$ are the \ts
+      from \pointlike, \gtlike, and \gtlike with the alternate diffuse
+      model respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$, and
+      $\tsext_\altdiff$ are the \tsext from \pointlike, \gtlike, and
+      \gtlike with the alternate diffuse model respectively.  $\sigma$
+      is the best fit extension using \pointlike and the standard PSF and
+      diffuse model. $\sigma_\altdiff$ is the best fit extension using
+      the alternate diffuse model and $\sigma_\altpsf$ is the best fit
+      extension using the alternate PSF. The difference between
+      these extensions is used to compute the systematic error
+      on extension in table~\ref{known_extended_sources} and
+      table~\ref{new_ext_srcs_table}.
+      }\label{alt_diff_model_results}
     \end{centering}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 1 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 1-100
   \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed by a
@@
   \caption{
-  A Galactic and isotropic diffuse subtracted 1 \gev to 100 \gev counts
+  A Galactic and isotropic diffuse subtracted 1-100 \gev counts
   map of the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
-  Gaussian kernel.  The red star is the catalog's position of
-  this source.  The red cross and circle are
-  the best position and extension of this source assuming a
-  uniform disk spatial model.  The black cross is the background source
-  2FGL\,J1625.7-2526.  The light blue contours are a 100 micrometer infrared
-  image of the region as seen by IRAS (\cite{iras_rho_ophiuci}). This
-  source is in the Ophiuchus region and most likely represents 
-  unmodeled diffuse emission.  More information about this source can be found
-  in section~\ref{section_2FGL_J1627.0-2425c}.
+  Gaussian kernel.  Plot (a) has the diffuse emission model subtracted
+  and plot (b) has the diffuse emission and 
+  the background source 2FGL\,J1625.7-2526.  
+  subtracted.  The red star is the catalog's position of this source.
+  The red cross and circle are the best position and extension of
+  this source assuming a uniform disk spatial model.  The light
+  blue contours are from a 100 micrometer infrared image of the region
+  as seen by IRAS (\cite{iras_rho_ophiuci}). This source is in the
+  Ophiuchus region and most likely represents unmodeled diffuse
+  emission.  More information about this source can be found in
+  section~\ref{section_2FGL_J1627.0-2425c}.
   }\label{1FGL_J1628.6-2419c}
@@
   \end{center}
-  \caption{A Galactic and isotropic diffuse subtracted 1 \gev to 100
-  \gev counts map of the region around 2FGL\,J1712.4-3941 smoothed by a
-  0.25\deg Gaussian kernel.  This source is spatially coincident with
-  RX J1713.7-3946 was was recently reported by (\cite{rx_j1713_lat}).
-  The light blue contours are the \tev emission reported by
-  H.E.S.S. (\cite{rx_j1713_hess}).  The region was analyzed with the
-  same background model as (\cite{rx_j1713_lat}).  Source A (blue cross)
-  is spatially coincident with 2FGL\,J1715.4-4024c (blue star).  The grey 
-  crosses
-  represent from left to right the position of source B and C which were
-  added to the background model. Plot (a) has the diffuse emisission model
-  subtracted and plot (b) has the diffuse emission and all background
-  sources also subtracted.
+  \caption{A Galactic and isotropic diffuse subtracted 1-100 \gev
+  counts map of the region around 2FGL\,J1712.4-3941 smoothed by
+  a 0.25\deg Gaussian kernel.  Plot (a) has the diffuse emission
+  model subtracted and plot (b) has the diffuse emission and all
+  background sources subtracted.  This source is spatially
+  coincident with RX J1713.7-3946 was was recently reported by
+  (\cite{rx_j1713_lat}).  The light blue contours are from the \tev image
+  observed by H.E.S.S. (\cite{rx_j1713_hess}).  The region was analyzed
+  with the same background model as (\cite{rx_j1713_lat}).  Source A (blue
+  cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
+  The grey crosses represent from left to right the position of source B
+  and C which were added to the background model. More information about
+  this source can be found in section~\ref{section_2FGL_J1712.4-3941}.
   }\label{2FGL_J1712.4-3941}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 10-100
   \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
@@
   source is spatially coincident with the Vela Jr SNR.  The light
-  blue contours are the \tev emission of Vela Jr. observed by H.E.S.S
+  blue contours are from the \tev image of Vela Jr. observed by H.E.S.S
   (\cite{vela_jr_hess}).  More information about this source can be
@@
   \caption{
-    A Galactic and isotropic diffuse subtracted 10 \gev to 100
+    A Galactic and isotropic diffuse subtracted 10-100
     \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
@@
     2FGL\,J1614.9-5212 which was removed because it is part of the
-    extended source.  The greeen stars to the left are 2FGL\,J1619.7-5040c
+    extended source.  The green stars to the left are 2FGL\,J1619.7-5040c
     and 2FGL\,J1620.6-5111c which were removed because they were
     not significant above 10\gev. These are shown as green stars.
-    The light blue contours are the \tev emission of the extended source
+    The light blue
+    contours are from the \tev image 
+    of the extended sources
     HESS\,J1616-508 (left) and the extended source HESS\,J1614-518
-    (right) measured by H.E.S.S.(\cite{hess_plane_survey}). 2FGL
-    J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
+    (right)
+    observed by H.E.S.S
+    (\cite{hess_plane_survey})
+    2FGL\,J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
     2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 10-100
   \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
@@
   coincident with the extended H.E.S.S source HESS\,J1632-478.
-  The light blue contours are the \tev emission seen by H.E.S.S.
+  The light blue contours are from the \tev image observed by H.E.S.S.
   (\cite{hess_plane_survey}).  Figure~\ref{hess_seds} (c) shows the \gev and
@@
   \caption{
-  A Galactic and isotropic diffuse subtracted 10 \gev to 100 \gev
-  counts map of the region around 2FGL\,J1837.3-0700c smoothed by a
-  0.1\deg Gaussian kernel.  The red star is the catalog position of
-  this source. The red cross and circle are the best fit position and
-  extension  of 2FGL\,J1837.3-0700c assuming a uniform disk spatial model.
-  The blue stars and crosses are the catalog position and the relocalized
-  position of (from left to right) 2FGL\,J1839.3-0558c, 2FGL\,J1836.8-0623c,
-  and 2FGL\,J1834.7-0705c.  The green cross inside the extension is 
-  2FGL\,J1835.5-0649 which was removed because it
-  is part of the extended source.  The farther away green star is 2FGL
-  J1839.0-0539 which was removed because it is not significant above
-  10 \gev.  This source is spatially coincident with the \tev source 
-  HESS\,J1837-069.  The light blue contours are the \tev emission of HESS\,J1837-069
-  observed by H.E.S.S (\cite{hess_plane_survey}).  
-  Figure~\ref{hess_seds} (d) shows the \gev and
-  \tev SED for this source. 
-  More information about
-  this source can be found in section~\ref{section_2FGL_J1837.3-0700c}.
+  A Galactic and isotropic diffuse subtracted 10-100 \gev counts map of
+  the region around 2FGL\,J1837.3-0700c smoothed by a 0.1\deg Gaussian
+  kernel.  Plot (a) has the diffuse emission model subtracted and plot (b)
+  has the diffuse emission and all background sources subtracted.  The red
+  star is the catalog position of this source. The red cross and circle
+  are the best fit position and extension  of 2FGL\,J1837.3-0700c assuming
+  a uniform disk spatial model.  The blue stars and crosses are the
+  catalog position and the relocalized position of (from left to right)
+  2FGL\,J1839.3-0558c, 2FGL\,J1836.8-0623c, and 2FGL\,J1834.7-0705c.
+  The green cross inside the extension is 2FGL\,J1835.5-0649 which
+  was removed because it is part of the extended source.  The farther
+  away green star is 2FGL J1839.0-0539 which was removed because
+  it is not significant above 10 \gev.  This source is spatially
+  coincident with the \tev source HESS\,J1837-069.  The light blue contours are from the \tev image observed by H.E.S.S.
+  (\cite{hess_plane_survey}).  Figure~\ref{hess_seds} (d) shows the \gev
+  and \tev SED for this source.  More information about this source can
+  be found in section~\ref{section_2FGL_J1837.3-0700c}.
   }\label{1FGL_J1837.5-0659c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 10 \gev to 100
+  \caption{A Galactic and isotropic diffuse subtracted 10-100
   \gev counts map of the region around 2FGL\,J2021.5+4026 smoothed by a
@@
   to the region. 2FGL\,J2021.5+4026 is spatially coincident with the
-  Gamma Cygni SNR.  The light blue contours are a 408MHz image of Gamma Cygni
+  Gamma Cygni SNR.  The light blue contours are from a 408MHz image of Gamma Cygni
   observed by the Canadian Galactic Plane Survey.  More information about
@@
     The spectral energy distribution of four the extended sources
-    associated with extended \tev sources.  The black points
-    with circular markers are the LAT data points. The red points
-    with dashed markers are H.E.S.S points of associated sources.
-    Plot (a) shows the \gev SED of 2FGL\,J1615.0-5051
-    and the \tev SED of HESS\,J1616-508.  Plot (b) shows
-    the \gev SED of 2FGL\,J1615.2-5138 and \tev the SED of HESS\,J1614-518
-    Plot (c) shows the \gev SED of 2FGL\,J1632.4-4753c
-    and the \tev SED of HESS\,J1632-478. Plot (d) shows the
-    \gev SED of 2FGL\,J1837.3-0700c and the \tev SED of HESS\,J1837-069.
-    The H.E.S.S. data points are from (\cite{hess_plane_survey}).
-    Both LAT and H.E.S.S. spectral errors are systematic only.
+    associated with extended \tev sources.  The black points with circular
+    markers are the LAT data points. The red points with dashed markers
+    are H.E.S.S points of associated sources.  Plot (a) shows the \gev
+    SED of 2FGL\,J1615.0-5051 and the \tev SED of HESS\,J1616-508.
+    Plot (b) shows 2FGL\,J1615.2-5138 and HESS\,J1614-518 Plot (c)
+    shows 2FGL\,J1632.4-4753c and HESS\,J1632-478. Plot (d) shows
+    2FGL\,J1837.3-0700c and HESS\,J1837-069. The H.E.S.S. data points
+    are from (\cite{hess_plane_survey}) The LAT upper limits are at the
+    95\% confidence level.  Both LAT and H.E.S.S. spectral errors are
+    systematic only.
     }\label{hess_seds}
@@
     Because of their large size, the RX J1713.7-3946 and Vela Jr.
-    were not directly fit in \tev and do not have errors associated with
-    their measurements. The \tev radius of RX J1713.7-3946 is taken to
-    be 0.5\deg and Vela Jr. is taken to be 1\deg. For these two sources,
-    the LAT size is not converted to \rsixeight but the disk extension is
-    directly compared.  This plot shows that there is good correlation
-    between the \gev and \tev sizes of sources.  The \tev size of MSH
-    15-52, HESS J1614-518, HESS J1632-478, and HESS J1837-069 have only
-    been reported with an elliptical Gaussian fit and so the plotted size
-    of these sources is the average of the radius in the semi-major and
-    semi-minor axis.
+    were not directly fit in \tev. The \tev radius of RX J1713.7-3946
+    is taken to be 0.5\deg and Vela Jr. to be 1\deg and the LAT size
+    is not converted to \rsixeight. The LAT extension errors are
+    the statistical and systematic errors added in quadrature. This
+    plot shows that there is a correlation between the \gev and \tev
+    sizes of sources.  The \tev size of MSH 15-52, HESS\,J1614-518,
+    HESS\,J1632-478, and HESS\,J1837-069 have only been reported with
+    an elliptical Gaussian fit and so the plotted size is the average
+    of semi-major and semi-minor axis.
     }\label{gev_vs_tev_plot}
@@
     \includegraphics{summary_plots/gev_vs_tev_histogram.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v2/extension_histogram.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v4/extension_histogram.py
     \end{center}
@@
     the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-    Catalog (\cite{hesscat}).  Except for RX J1713.7-3946 and Vela Jr.,
+    Catalog\cite{hesscat}.
+    Except for RX J1713.7-3946 and Vela Jr.,
     the H.E.S.S. sources were fit with a Gaussian spatial model and
     so the LAT and H.E.S.S. sizes are first converted to \rsixeight.
-    (see section~\ref{compare_source_size}). Beacuse the spatial
+    (see section~\ref{compare_source_size}). Because the spatial
     morphology of RX J1713.7-3946 and Vela Jr. is poorly matched by a
-    gaussian, the \tev sizes are assuming a uniform disk spatial model
+    Gaussian, the \tev sizes are assuming a uniform disk spatial model
     and so neither the \gev nor \tev sizes were converted.  This plot
@@
     \includegraphics{summary_plots/compare_index_2FGL.pdf}
+    % plot taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_index_2fgl/v3/run.py
     \end{center}
@@
     table~\ref{known_extended_sources} table~\ref{new_ext_srcs_table}.
-    The index of centarus A is taken to be 2.58 from the two year catalog
-    (\cite{second_cat}) and the the index of Vela X is taken to be 2.41
+    The index of Centarus A is taken to be 2.58 from the two year catalog
+    (\cite{second_cat}) and the index of Vela X is taken to be 2.41
     from (\cite{velax}). This plot shows that many of the LAT
@@
 
+  \clearpage
+\begin{appendices}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics{mc_plots/all_sensitivity.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
+    \end{center}
+    \caption{These six plots condense the LAT detection threshold for
+    all four spectral indices shown in figure~\ref{index_sensitivity}
+    (1.5, 2, 2.5, and 3) and all three background levels shown
+    in~\ref{diff_factor_sensitivity}.  (1x, 10x, and 100x the
+    Sreekumar-like isotropic spectrum).  The plots have the same meaning
+    as in figure~\ref{index_sensitivity} The left plots are the detection
+    threshold when using the photons with energies between 1 \gev and
+    100 \gev and the right plots are the detection threshold when using
+    photons with energies between 10 \gev and 100 \gev.  This plot shows
+    that when using only high energy photons with an improved angular
+    resolution, our detection threshold is only weakly a function of
+    spectral index. The numeric values plotted here are tabulated
+    in table~\ref{all_sensitivity_table}. More information about this plot is presented
+    in section~\ref{extension_sensitivity}.
+    }\label{all_sensitivity} 
+  \end{figure}
+
+  \clearpage
+  \thispagestyle{empty}
+  \begin{sidewaystable}\scriptsize
+    \begin{centering}
+      \begin{tabular}{r|r|rrrrrrrrrrrrrrrrrrrr}
+        \hline
+        \hline
+        \multicolumn{22}{c}{$ 1 \gev < E < 100 \gev$} \\
+        \hline
+        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
+        \hline
+             1.5 &       x1 &      149.5 &       23.5 &       11.4 &        8.1 &        7.2 &        7.0 &        6.8 &        6.8 &        7.0 &        7.4 &        7.5 &        7.7 &        7.9 &        8.2 &        8.9 &        9.7 &        9.0 &        9.0 &        8.7 &       10.1 \\
+                 &      x10 &      145.7 &       28.9 &       18.3 &       15.1 &       15.4 &       15.0 &       16.1 &       15.8 &       16.6 &       17.6 &       18.5 &       19.9 &       21.5 &       23.6 &       25.2 &       25.2 &       21.4 &       23.0 &       23.6 &       23.8 \\
+                 &     x100 &      184.2 &       55.3 &       42.1 &       40.6 &       40.5 &       42.0 &       42.1 &       40.6 &       43.0 &       43.7 &       37.6 &       39.4 &       39.9 &       36.8 &       35.9 &       36.1 &       36.3 &       37.7 &       37.0 &       37.4 \\
+               2 &       x1 &      332.5 &       44.1 &       18.9 &       13.4 &       11.3 &       10.4 &       10.1 &       10.0 &       10.1 &       10.3 &       10.6 &       10.8 &       11.0 &       11.3 &       12.2 &       12.4 &       12.8 &       13.2 &       13.5 &       13.8 \\
+                 &      x10 &      337.9 &       55.6 &       32.4 &       27.2 &       26.4 &       25.4 &       25.6 &       26.0 &       27.8 &       28.2 &       29.2 &       29.2 &       31.1 &       30.8 &       31.5 &       32.8 &       32.1 &       34.5 &       34.8 &       36.6 \\
+                 &     x100 &      416.0 &      133.9 &       88.0 &       77.8 &       74.1 &       72.6 &       68.7 &       65.0 &       63.0 &       63.3 &       61.7 &       61.8 &       60.1 &       59.0 &       54.7 &       58.0 &       58.9 &       60.8 &       57.5 &       53.9 \\
+             2.5 &       x1 &      635.5 &       74.3 &       29.8 &       19.2 &       15.8 &       13.7 &       12.8 &       12.7 &       12.3 &       12.4 &       12.4 &       12.6 &       12.7 &       12.9 &       13.3 &       13.4 &       13.8 &       14.3 &       14.7 &       15.4 \\
+                 &      x10 &      640.0 &       97.6 &       51.7 &       39.3 &       34.6 &       33.0 &       32.7 &       32.6 &       33.0 &       33.5 &       34.6 &       35.2 &       34.7 &       36.0 &       37.3 &       37.3 &       35.7 &       36.4 &       37.5 &       38.1 \\
+                 &     x100 &      794.9 &      261.2 &      134.2 &      103.5 &       89.5 &       80.7 &       78.1 &       75.3 &       70.1 &       70.2 &       65.5 &       64.7 &       61.9 &       59.8 &       56.4 &       55.6 &       57.9 &       55.0 &       53.3 &       51.8 \\
+               3 &       x1 &      857.2 &      110.2 &       43.5 &       25.8 &       18.9 &       16.1 &       14.3 &       13.5 &       13.2 &       13.2 &       13.0 &       12.9 &       13.2 &       13.3 &       13.2 &       13.5 &       13.8 &       14.1 &       14.4 &       15.0 \\
+                 &      x10 &      931.1 &      155.1 &       70.4 &       48.3 &       40.9 &       37.3 &       35.6 &       35.0 &       35.5 &       35.8 &       36.0 &       34.9 &       35.1 &       35.1 &       37.0 &       37.7 &       35.4 &       35.8 &       36.6 &       37.8 \\
+                 &     x100 &     1119.8 &      295.6 &      180.9 &      119.4 &      101.0 &       92.0 &       86.4 &       78.5 &       73.5 &       69.9 &       66.7 &       64.9 &       63.3 &       61.2 &       57.3 &       56.7 &       56.7 &       55.0 &       50.7 &       50.4 \\
+        \hline
+        \multicolumn{22}{}{} \\
+        \multicolumn{22}{}{} \\
+        \hline
+        \hline
+        \multicolumn{22}{c}{$ 10 \gev < E < 100 \gev$} \\
+        \hline
+        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
+        \hline
+             1.5 &       x1 &       43.9 &        8.2 &        4.3 &        3.2 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.8 &        2.8 &        3.0 &        3.0 &        3.1 &        3.3 &        3.4 &        3.5 \\
+                 &      x10 &       44.6 &        9.1 &        5.8 &        5.0 &        5.0 &        5.1 &        5.0 &        5.4 &        5.3 &        5.7 &        6.0 &        6.3 &        6.7 &        6.5 &        7.1 &        7.7 &        7.8 &        8.2 &        8.4 &        8.7 \\
+                 &     x100 &       47.2 &       13.3 &       11.4 &       10.6 &       10.6 &       10.7 &       11.9 &       12.7 &       13.2 &       13.6 &       15.3 &       16.2 &       17.4 &       18.4 &       19.3 &       20.1 &       20.8 &       21.8 &       22.6 &       24.0 \\
+               2 &       x1 &       49.1 &        8.5 &        4.4 &        3.3 &        2.8 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.1 &        3.2 &        3.2 &        3.4 &        3.5 &        3.6 \\
+                 &      x10 &       48.3 &        9.6 &        6.0 &        5.2 &        5.2 &        5.3 &        5.3 &        5.6 &        5.5 &        5.9 &        6.4 &        6.7 &        7.0 &        7.2 &        7.7 &        8.0 &        8.3 &        8.6 &        9.0 &        9.3 \\
+                 &     x100 &       51.1 &       14.8 &       11.7 &       11.4 &       11.5 &       12.0 &       13.1 &       14.0 &       14.4 &       15.2 &       16.1 &       17.1 &       18.7 &       19.7 &       20.5 &       21.9 &       22.9 &       23.7 &       24.1 &       25.2 \\
+             2.5 &       x1 &       52.1 &        9.2 &        4.6 &        3.3 &        2.9 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.8 &        2.9 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 &        3.6 \\
+                 &      x10 &       53.0 &       10.5 &        6.2 &        5.4 &        5.2 &        5.2 &        5.4 &        5.6 &        5.8 &        6.1 &        6.4 &        6.6 &        6.9 &        7.3 &        7.5 &        8.2 &        8.4 &        8.7 &        8.9 &        9.3 \\
+                 &     x100 &       55.5 &       15.9 &       12.7 &       12.0 &       11.9 &       12.3 &       13.0 &       14.4 &       14.7 &       15.2 &       16.4 &       17.2 &       19.1 &       19.6 &       20.6 &       21.9 &       23.0 &       23.4 &       24.4 &       24.9 \\
+               3 &       x1 &       54.6 &        9.5 &        4.7 &        3.4 &        2.9 &        2.7 &        2.6 &        2.5 &        2.5 &        2.6 &        2.6 &        2.7 &        2.7 &        2.9 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 \\
+                 &      x10 &       55.1 &       10.5 &        6.2 &        5.3 &        5.2 &        5.3 &        5.2 &        5.4 &        5.5 &        5.7 &        6.0 &        6.4 &        6.6 &        7.0 &        7.3 &        7.9 &        8.1 &        8.5 &        8.7 &        8.9 \\
+                 &     x100 &       59.8 &       16.0 &       12.7 &       11.8 &       11.6 &       12.2 &       12.7 &       14.1 &       14.2 &       14.6 &       16.0 &       16.9 &       17.9 &       19.0 &       20.1 &       20.6 &       21.6 &       22.1 &       22.7 &       23.5 \\
+        \hline
+      \end{tabular}
+      \caption{The detection threshold to resolve a uniform disk spatially
+      extended sources using two years of data for sources of varying
+      spectral index and extension against varying background levels
+      with different energy ranges.  The upper table is the sensitivity
+      when using photons with energies from 1-100 \gev and the bottom
+      table is when using 10-100 \gev photons. The first column is
+      the extended source's spectral index.  The extended sources
+      were simulated against a Sreekumar-like isotropic spectrum and
+      the second column is the factor that the simulated background
+      was scaled by. The remaining columns are varying sizes of the
+      source's spatial model. The table quotes fluxes in units of
+      $10^{-10} \ph/\cm^2/\sec$.  These values are also plotted in
+      figure~\ref{all_sensitivity}.  More information about this
+      table is presented in section~\ref{extension_sensitivity}.
+      }\label{all_sensitivity_table}
+    \end{centering}
+  \end{sidewaystable}
+
+\end{appendices}
+
 \end{document}

### 2011-08-07 extended_catalog/paper/extended_catalog.tex
markus changes

@@
 \begin{abstract}
-We present a new method for analyzing spatially extended sources with
+We present a new method for analyzing 
+the spatial extension of sources with
 the Large Area Telescope (LAT), the primary science instrument on the
-{\em Fermi Gamma-ray Space Telescope (Fermi)}. Measuring the extension
-of a LAT source is important for uniquely identifying it.  We provide
+{\em Fermi Gamma-ray Space Telescope (Fermi)}. 
+The source extension is an important input to correctly 
+associate LAT sources with their counterparts at other
+wavelengths. We provide
 a series of Monte Carlo studies to validate this tool and calculate
@@
 in addition to the twelve spatially extended sources reported in the
-second Fermi LAT Catalog (2FGL).
+second Fermi-LAT Catalog (2FGL).
 \end{abstract}
@@
 
-The Large Area Telescope (LAT) is a pair conversion telescope on the
-Fermi Gamma-Ray Space Telescope (Fermi). It has been surveying the
-$\gamma$-ray sky since June 2008.  Fermi is well suited as a survey
-instrument because of its broad energy coverage (20 \mev to $>300$
+The Large Area Telescope (LAT) is a pair conversion telescope on the Fermi
+Gamma-Ray Space Telescope (FGST). It has been surveying the $\gamma$-ray
+sky since June 2008.  Fermi has a broad energy coverage (20 \mev to $>300$
 \gev), wide field of view ($\approx 2.4 \sr$), and large effective area
@@
 Active Galactic Nuclei (AGN), pulsars, galaxies, and supernova
-remnants (SNRs).  While many of these classes can be spatially
-resolved when observed at other frequencies, detection an extension at
+remnants (SNRs).  While many of the LAT sources can be
+spatially
+resolved when observed at other frequencies, detection of 
+an extension at
 \gev energies by the LAT is complicated by the rather large
-point-spread function (PSF) of the instrument (the angular resolution
+point-spread function (PSF) of the instrument. The angular resolution
 for events converting in the front part of the detector, defined as
 the 68\% containment radius for a point source, is approximately
-$3.5^{\circ}$ at 100 \mev, improving to about 0.1$^{\circ}$ at 10 \gev).
-
-Several of these source classes are extended (and close) enough to
-potentially be extended. In particular supernova remnants, pulsar wind
-nebulae, molecular clouds, normal galaxies, galaxy clusters or dark
-matter satellites can (in favorable cases) be expected to be extended
-beyond the LAT's PSF. The LAT collaboration has previously reported on
+$3.5^{\circ}$ at 100 \mev, improving to about 0.1$^{\circ}$ at 10 \gev.
+
+However, a number of sources positionally coincident
+with LAT sources exhibit extensiosn at other
+wavelengths which are larger or comparable to the LAT PSF.
+In particular certain SNRs, pulsar wind
+nebulae (PWNe), molecular clouds, normal galaxies, 
+galaxy clusters or dark
+matter satellites can therefore be expected
+to be observed as spatially extended sources in the LAT.
+The LAT collaboration has previously reported on
 the discovered of five spatially extended supernova remnants, IC443,
@@
 (\cite{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended
-pulsar wind nebulae (PWNe) were detected: MSH 15-52, Vela~X, and
+PWNe were detected: MSH 15-52, Vela~X, and
 HESS\,J1825-137 (\cite{msh1552,velax,fermi_hess_j1825}), as well as
@@
 
-In addition to these \gev $\gamma$-ray detections, a variety of
-spatially extended sources have been detected in the Galactic plane at
-\tev energies using Air Cherenkov detectors. Most prominent was a
-survey of the Galactic plane using the High Energy Stereoscopic System
-(H.E.S.S) which presented 14 spatially extended sources
-(\cite{hess_plane_survey}) sources with extensions varying from
-$~0.1\deg$ to $~0.25\deg$. In fact, within our Galaxy only very few
-sources (most notably the $\gamma$-ray binaries
-LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI}) and
-HESS\,J0632+057 (\cite{HESS0632}) are amongst the few Galactic sources
-for which no significant extension was detected at \tev
-energies. Given these findings, it can be expected that if the source
-population at \gev energies has similar properties, that at least some
-of the Fermi-LAT sources in our Galaxy should be spatially extended at
-\gev energies.
+For each of these sources, the extension was determined based on
+dedicated analysis of the particular source or region of interest
+instead of being the outcome of a systematic search of the LAT catalog.
+For the systematic scan of all LAT catalog sources presented here, we
+therefore expect to find additional spatially extended LAT sources, in
+particular since many extended sources in the Galactic plane have been
+detected at \tev energies using Air Cherenkov detectors and \tev and
+\gev emission often originates from the same population of high-energy
+particles.  A variety of spatially extended sources have been detected
+in the Galactic plane at \tev energies. Most prominent was a survey of
+the Galactic plane using the High Energy Stereoscopic System (H.E.S.S)
+which presented 14 spatially extended sources
+ with extensions varying from
+$~0.1\deg$ to $~0.25\deg$ (\cite{hess_plane_survey}). In fact, within
+our Galaxy only very few sources (most notably the $\gamma$-ray binaries
+LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI})
+and HESS\,J0632+057 (\cite{HESS0632}) are amongst the few Galactic sources
+for which no significant extension was detected at \tev energies. Given
+these findings, it can be expected that if the source population at \gev
+energies has similar properties, that at least some of the Fermi-LAT
+sources in our Galaxy should be spatially resolvable at \gev energies.
 
@@
 candidate source density in our Galaxy, source confusion is a severe
-problem for the Fermi-LAT. Finding a matching morphology can be used
-to uniquely identify the source.  Because of the strongly varying PSF
-of the LAT, the spatial and spectral information about a source do not
-simply decouple. Therefore, a biased spatial model will bias the
-spectral model of the source and studying the extension of the source
-can correct for this.  Furthermore, correctly modeling a source's
-extension is important for improving the model of the sky and
-removing excess residuals.  These residuals manifested themselves in
-1FGL as spurious point sources in the region region surrounding the
-Large Magellanic Cloud (\cite{first_cat}).  For this reason, we are
-motivated to take the 1873 sources that were detected in 2FGL and
-apply a search for those sources which are spatially extended.
+problem for the identification of LAT sources.  Finding a coherent
+source extension across different energy bands allows a firm association
+of a LAT source to an otherwise confused counterpart.  Because of the
+strongly varying PSF of the LAT, the spatial and spectral information
+about a source do not simply decouple. A biased spatial model will bias
+the spectral model of the source. In particular, performing a spectral
+analysis on a spatially extended source modeled as point-like will
+systematically shift the spectral index to be softer.  Furthermore,
+correctly modeling a source's extension is important for improving
+the model of the sky and removing excess residuals, for example in the
+region around surrounding the Large Magellanic Cloud (\cite{first_cat}).
+Additionally, such excess residuals potentially bias the significance
+and measured spectrum of neighboring sources in the densely populated
+Galactic plane.
 
@@
 
-Morphological studies of sources in the \gev energy range
-using the LAT are challenging because of the significantly 
-energy-dependent PSF and because of systematic errors in the Galactic diffuse
-emission.  The LAT's PSF is determined at lower energies by multiple
-scattering in the tracker and the 68\% containment radius of the PSF is
-approximately 5.1\deg at 100 \mev  when averaged over instrument acceptance
-and including photons which convert in either the thick or thin layers of
-the tracker. The PSF approaches a limit given by the granularity of the
-tracker channels and is 0.14\deg at 10 \gev (\cite{on_orbit_calibration}).
-Therefore, the higher energy photons are significantly more important for
-resolving a source but are typically limited by statistics. 
-A detailed analysis procedure must be used to maximize our
-sensitivity over all energies.
+Morphological studies of sources in the \gev energy range using the
+LAT are challenging because of the significantly energy-dependent PSF.
+Additional complications arise close to the Galactic plane due to
+systematic uncertainties in the Galactic diffuse emission.  The LAT's
+PSF is limited at lower energies by multiple scattering in the tracker
+and the 68\% containment radius of the PSF is approximately 5.1\deg
+at 100 \mev  when averaged over instrument acceptance and including
+photons which convert in either the thick or thin layers of the
+tracker. The PSF improves with energy and approaches a limit given
+by the granularity of the silicon strips and is 0.14\deg at 10 \gev
+(\cite{on_orbit_calibration}).  The high resolution of the higher
+energy photons in the LAT energy range however is offset by their low
+statistics. Therefore a detailed investigation has been performed in this
+work to determine the optimal energy range to measure source extension
+(see below).
 
@@
 provides a maximum likelihood analysis where the Poisson likelihood
-for observing the measured counts is maximized by fitting
-parameters of the model.  The extension of a source can be modeled by a
-geometric shape (e.g. a disk or Gaussian) and the source's position
-and extension can be simultaneously fit.
+for observing the measured counts is maximized,
+given a parametrized spatial and spectral model of 
+the source and its surrounding region.
+The extension of a source can be modeled by a
+geometric shape (e.g. a disk or Gaussian) and the source's position,
+extension, and spectrum can be simultaneously fit.
 

### 2011-08-07 extended_catalog/paper/extended_catalog.tex
markus comments

@@
 However, a number of sources positionally coincident
-with LAT sources exhibit extensiosn at other
+with LAT sources exhibit extension at other
 wavelengths which are larger or comparable to the LAT PSF.
@@
 
-This analysis is not feasible using the official LAT likelihood
+This analysis is not feasible using the standard LAT likelihood
 analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
 Fermi Science Support Center (\cite{fssc})} because \gtlike can only 
-fit the spectral parameters of the model. The extension fitting would
-have to be done as an external loop which would typically be
-too time consuming. What has typically
-been done to study an extended sources is to fix the position of the
-source and develop a profile of the likelihood as a
-function of extension.  This approach is not optimal because the
-position and extension of the source should be simultaneously maximized
-to find the best fit parameters and to correctly compute the statistical
-significance of the detection.  Furthermore since this approach is
-computationally intensive, no large-scale Monte Carlo effort can
-be run to validate it.
-
-We developed an alternative approach to fit spatially extended
-sources. A separate maximum likelihood fitting package called
-\pointlike has been developed by the LAT collaboration and we have
-added to it the ability to analyze spatially extended sources. \pointlike
-is described in 1FGL and in Matthew Kerr's Ph.D thesis
-(\cite{first_cat,matthew_kerr_thesis}).
-
-What differentiates \pointlike most significantly from \gtlike is its
-emphasis on speed by introducing approximations into the calculation
-of the likelihood function while trying to minimized the introduced
-numerical errors.  Like the binned version of \gtlike, \pointlike bins
-the sky in both position and energy.  Unlike \gtlike, \pointlike relies on
-the {\em healpix} representation of spatial bins (\cite{healpix}). Since
-the PSF changes significantly with energy, the spatial size of each bin
-is chosen to be smaller than the PSF. By changing the spatial
-bin size with energy, \pointlike ensures that little information is lost
-at each energy while minimizing the required number of bins.
-
-\pointlike also bins $\gamma$-rays depending upon whether they convert
-in the thin or thick layers of the tracker. Since the PSF is smaller for
-photons which convert in the thin layers of the tracker,
-photons are also binned depending upon where they 
-convert in the tracker.
-Furthermore, \pointlike
-uses a sparse matrix representation of the spatial bins where only the
-bins with counts in them are used. To evaluate the likelihood, \pointlike
-then independently integrates the model predicted counts in the region.
-
-Intelligent binning and a sparse matrix representation of the data
-effectively interpolates between a binned analysis at low energy (where
-the resolution is poor and there are many counts) and an unbinned
-analysis at high energy (where the resolution is good but there are
-few counts). This approach provides significant savings in time while
-introducing only small numerical error.
+fit the spectral parameters of the model.
+
+We note that \gtlike has been used in the past in several studies of
+source extension in the LAT collaboration (\cite{lmc,smc,w28,w51c}).
+Based upon a set of \gtlike maximum likelihood fits at fixed extensions,
+a profile of the likelihood as a function of the extension was calculated.
+This approach is not optimal because the position, extension, and
+spectrum of the source must be simultaneously fit to find the best fit
+parameters and to correctly compute the statistical significance of the
+detection.  Furthermore since the \gtlike likelihood profile approach
+is computationally intensive, no large-scale Monte Carlo effort can be
+run to validate it.
+
+The approach presented here is based on a second maximum likelihood
+fitting package developed in the LAT collaboration and called \pointlike
+(\cite{first_cat,matthew_kerr_thesis}).  We extended the code to allow
+a simultaneous fit of the source extension together with the position
+and the spectral parameters.
+
+The choice to base the spatial extension fitting on \pointlike
+rather than \gtlike was made on considerations of computing time.
+The \pointlike algorithm was optimized for speed to handle
+larger numbers of sources efficiently which is important for
+our catalog scan as well as the Monte Carlo validation of our method.
+Details on the \pointlike package can be found in (\cite{matthew_kerr_thesis}).
 

### 2011-08-08 extended_catalog/paper/extended_catalog.tex
work on the conclusion

@@
 
-Using two years of all sky surveying data, the LAT Collaboration
-published a catalog of 1873 \gev sources\cite{second_cat}. Many of these can
-be positionally associated with a variety of source classes including
-Active Galactic Nuclei (AGN), pulsars, galaxies, and supernova
-remnants (SNRs).  While many of the LAT sources can be
-spatially
-resolved when observed at other frequencies, detection of 
-an extension at
-\gev energies by the LAT is complicated by the rather large
-point-spread function (PSF) of the instrument. The angular resolution
-for events converting in the front part of the detector, defined as
-the 68\% containment radius for a point source, is approximately
-$3.5^{\circ}$ at 100 \mev, improving to about 0.1$^{\circ}$ at 10 \gev.
-
-However, a number of sources positionally coincident
-with LAT sources exhibit extension at other
-wavelengths which are larger or comparable to the LAT PSF.
-In particular certain SNRs, pulsar wind
-nebulae (PWNe), molecular clouds, normal galaxies, 
-galaxy clusters or dark
-matter satellites can therefore be expected
-to be observed as spatially extended sources in the LAT.
-The LAT collaboration has previously reported on
-the discovered of five spatially extended supernova remnants, IC443,
-W28, W44, W51C, and RX J1713.7-3946
-(\cite{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended
-PWNe were detected: MSH 15-52, Vela~X, and
-HESS\,J1825-137 (\cite{msh1552,velax,fermi_hess_j1825}), as well as
-two close-by galaxies, the Large Magellanic and Small Magalenic Cloud
-(\cite{lmc,smc}), and finally the radio galaxy Centarus A
+Using two years of all sky surveying data, the LAT Collaboration published
+a catalog of 1873 \gev sources\cite{second_cat}. Many of these can be
+positionally associated with a variety of source classes including Active
+Galactic Nuclei (AGN), pulsars, galaxies, and supernova remnants (SNRs).
+While many of the LAT sources can be spatially resolved when observed
+at other frequencies, detection of an extension at \gev energies by
+the LAT is complicated by the rather large point-spread function (PSF)
+of the instrument. The angular resolution for events converting in the
+front part of the detector, defined as the 68\% containment radius for
+a point source, is approximately $3.5^{\circ}$ at 100 \mev, improving
+to about 0.1$^{\circ}$ at 10 \gev.
+
+However, a number of sources positionally coincident with LAT sources
+exhibit extension at other wavelengths which are larger or comparable to
+the LAT PSF.  In particular certain SNRs, pulsar wind nebulae (PWNe),
+molecular clouds, normal galaxies, galaxy clusters or dark matter
+satellites can therefore be expected to be observed as spatially extended
+sources in the LAT.  The LAT collaboration has previously reported on the
+discovered of five spatially extended supernova remnants, IC443, W28, W44,
+W51C, and RX J1713.7-3946 (\cite{ic443,w28,w44,w51c,rx_j1713_lat}). In
+addition, three extended PWNe were detected: MSH 15-52, Vela~X,
+and HESS\,J1825-137 (\cite{msh1552,velax,fermi_hess_j1825}), as well
+as two close-by galaxies, the Large Magellanic and Small Magalenic
+Cloud (\cite{lmc,smc}), and finally the radio galaxy Centarus A
 (\cite{cen_a_lat}) .
@@
 
-In \pointlike, it is assumed that the spatial and spectral model
-of an extended source decouple and that the spatial shape can be
-represented by a two dimensional function.  To fit the extended source,
+In \pointlike, it is assumed that the spatial and spectral
+model of an extended source are separable, i.e. that the source
+model $M(l,b,E)=S(l,b)\times X(E)$.  To fit an extended source,
 \pointlike convolves the extended source shape with the PSF (as a
-function of energy) and uses the \minuit fitting library to maximize
-the likelihood by simultaneously fitting the position and extension
-of the source (\cite{minuit_documentation}).  As will be described in
+function of energy) and uses the \minuit library to maximize the
+likelihood by simultaneously varying the position and extension of
+the source (\cite{minuit_documentation}).  As will be described in
 section~\ref{monte_carlo_validation}, simultaneously fitting the position
@@
 extension, the spectral parameters of the sky model are refit.  To avoid
-projection effects, what is directly fit is not the longitude and latitude
-but instead the source's displacement in a rotated reference frame.
-
-The significance of the extension of a source can be calculated from
-\tsext, which is defined as twice the increase in log likelihood (\loglikelihood)
-between
-the extended source model at its best fit values and the point source
-model at its best fit values:
+projection effects, the fitted source position parameters are not the
+source's longitude and latitude but instead the source's displacement
+in a rotated reference frame.
+
+The significance of the extension of a source can be calculated
+from \tsext, which 
+is the test statistic of the likelihood ratio test of
+a model with a spatially extended source and a model
+with a point-like source and defined as
 \begin{equation}
@@
 \end{equation}
+where \loglikelihood is the log of the Poisson likelihood.
 \pointlike calculates \tsext by fitting a source first with a spatially
@@
 
-The convolution of radially symmetric extended sources is optimized by
-using a semi-analytic calculation.  The observed photon distribution
-can be written as the convolution of the source shape ($I_\text{src}$)
-with the PSF
+For extended sources with an assumed radially symmetric shape,
+we use a semi-analytic calculation to speed up the calculation of
+the expected photon distribution. The expected photon 
+distribution can be written as
 \begin{equation}
@@
 \end{equation}
-For the LAT, the PSF is parameterized by a {\em King function}
+For the LAT, the PSF can be parameterized by a {\em King function}
 \begin{equation}
@@
 the angular part of the integral can be done analytically
-\begin{equation}
-  \text{PDF}(u)= \int_0^\infty dv
+\begin{align}
+  \text{PDF}(u) & = \int_0^\infty \sigma^2 dv 
+  I_\text{src}(v) 
+  \int_0^{2\pi} d\phi' 
+  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
+  \\
+  & = \int_0^\infty dv
   I_\text{src}(v) 
@@
   \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
-  \times ~_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
-\end{equation}
-This convolution formula is used by \pointlike because it is faster
-and more closely reduces to the PSF when the source's size is 
-small.
-
-There will always be a small numerical discrepancy between the PSF and
-a very small extended source due to numerical error in the convolution.
-In most situations, this error would be insignificant. But when testing
-a source for extension, this offset can significantly bias the estimate
-of the significance of the extension of a source.  To correct for this,
-when testing a source for extension we compare the likelihood fitting
-the source with an extended shape to the likelihood fitting it with its
-extension fixed to ${10^{-10}}\deg$.
-
-\subsection{Extension Errors}
-\label{extension_error}
-
-Errors on fit parameters are typically calculated in one of two
-ways. The first method requires explicitly varying a parameter
-while simultaneously optimizing the other parameters
-until the log of the likelihood has fallen by a particular value.
-The \minuit fitting
-package provides the {\em Simplex} function to calculate errors this way
-(\cite{minuit_documentation}).  The second method involves estimating the
-likelihood function as being a multivariate Gaussian and calculating the
-curvature of the log of the likelihood at the peak to estimate when the
-function will decrease by the desired value. \minuit provides the {\em HESSE}
-algorithm to calculate errors this way.  {\em HESSE} errors 
-can be calculated significantly faster.
-
-We found that the {\em HESSE} errors on the extension of a source
-were sometimes badly estimated.  On the other hand, the {\em Simplex}
-algorithm was prohibitively slow and would often fail to convergence. Our
-approach to calculating extension errors is to fix the position of the
-source and varying just the extension using the {\em Simplex} algorithm.
-This approach makes the approximation that the covariance between each
-spatial parameter is small but not that the likelihood is Gaussian. This
-method is shown schematically in figure~\ref{four_plots_ic443}(a) which
-shows the change in \loglikelihood when varying the extension of the
-SNR IC443.  The localization error is separately calculated by fixing
-the extension and spectrum of the source and fitting a parabola to the
-likelihood as a function of position.
-
-\subsection{\gtlike Crosscheck}
+  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
+\end{align}
+where $u=(r/\sigma)^2/2$, $v=(r'/\sigma)^2/2$, and ${}_2F_1$ is the
+Gaussian hypergeometric function.  This convolution formula is used by
+\pointlike, reducing the calculation of the expected photon distribution
+to a single numerical integral.
+
+There will always be a small numerical discrepancy between the expected
+photon distribution derived from a true point source and a very small
+extended source due to numerical error in the convolution.  In most
+situations, this error would be insignificant.  But in particular for
+very bright sources, this numerical error has the potential to bias the
+test statistic for the extension test.  the source with an extended shape
+to the likelihood fitting it with its extension fixed to ${10^{-10}}\deg$.
+
+We estimate the errors on the extension
+by recalculating the likelihood for a set of extension values
+while keeping the position fixed.
+
+We estimate the error on the extension of a source by fixing the position
+of the source and varying the extension until the likelihood has fallen
+by $\tfrac{1}{2}$, corresponding to a $1\sigma$ error.  This method is
+shown schematically in figure~\ref{four_plots_ic443}(a) which shows the
+change in \loglikelihood when varying the extension of the SNR IC443.
+The localization error is calculated by fixing the extension and spectrum
+of the source and fitting a Gaussian to the likelihood as a function
+of position.
+
+\subsection{\gtlike Analysis Validation}
 \label{gtlike_crosscheck}
@@
 because of the fewer approximations used in calculating the likelihood
-we expect that the spectral parameters fit by \gtlike to be slightly
+we expect the spectral parameters found with \gtlike to be slightly
 more precise.  Furthermore, because \gtlike is the standard likelihood
@@
 to determinate the position and extension of a source and then determine
-the spectrum using \gtlike. Both \gtlike and \pointlike can estimate
+the spectrum using \gtlike. Both \gtlike and \pointlike can be 
+used to estimate
 the statistical significance of the extension of a source and we require
@@
 source candidates, table~\ref{alt_diff_model_results} will shows a
-comparison of \ts and \tsext computed using \pointlike and \gtlike.
-Unless explicitly mentioned, all \ts, \tsext, and spectral parameters
-were calculated using \gtlike using \pointlike's positions and extensions.
+comparison of the test statistic \ts and \tsext computed using \pointlike
+and \gtlike.  Unless explicitly mentioned, all \ts, \tsext, and spectral
+parameters were calculated using \gtlike using \pointlike's positions
+and extensions.
 
@@
 There is a degeneracy between a spatially extended source and multiple
-point sources.  To assess the possibility of source confusion,
-we developed a function in \pointlike to simultaneously fit the position
-of two point sources.  To improve the robustness of the fit, the sum and
-difference of the positions of the two sources are fit in a coordinates
-rotated to the equator.  The \loglikelihood is then maximized by fitting
-the sum and difference of the positions.
+point sources that are separated by angular distances comparable or
+smaller than the size of the LAT PSF.  To assess the possibility of source
+confusion, we developed a function in \pointlike to simultaneously fit
+the position of two point sources.
 
@@
 region as two point sources compared to fitting the region as one point
-source: \begin{equation}
+source: 
+\begin{equation}
   \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
-\end{equation} \tsinc can not be directly compared to \tsext to see
-which model is more significant because the models are not nested
-(\cite{statistics_with_care}). Even though the comparison of \tsext
-with \tsinc is not a calibrated test, we find the extreme cases $\tsinc
-\loglikelihood \tsext$ or $\tsinc\gg\tsext$ to be suggestive and we only
-consider a source to be extended if $\tsext>\tsinc$.
+\end{equation} 
+\tsinc can not be directly compared to \tsext to see which
+model is more significant because the models are not nested
+(\cite{statistics_with_care}). Even though the comparison of \tsext with
+\tsinc is not a calibrated test, we find the cases $\tsinc \ll \tsext$
+or $\tsinc\gg\tsext$ suggestive and we only consider a source to be
+extended if $\tsext>\tsinc$.
 
@@
 the spectrum of the two point sources can be refit using \gtlike.
-we quote the spectral values obtained from \gtlike using the best fit
+We quote the spectral values obtained from \gtlike using the best fit
 positions found using \pointlike.  For the extended candidates found
@@
 
-The spatial shape of extended sources can be modeled
-as a two dimensional Gaussian
+We tested two different models for the
+spatial shape, either a two dimensional Gaussian
 \begin{equation}\label{gauss_pdf}
-  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
+  I(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
 \end{equation}
@@
 \begin{equation}\label{disk_pdf}
-  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
+  I(x,y)=
+  \begin{cases}
+    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
+    0                      & x^2+y^2>\sigma^2
+  \end{cases}
 \end{equation}
-Although these shapes are significantly different, the convolution of them
-with the PSF look similar.  Figure~\ref{compare_disk_gauss} demonstrates
-this by showing the PSF, PDF, and convolution of the PDF with the PSF
-for a uniform disk and Gaussian spatial model of size 0.5\deg.  This plot
-shows that we are not very sensitive to probing the exact structure of an
-extended source.  In the following we assume a uniform disk spatial model.
-
-To get the convolved shapes to match in figure~\ref{compare_disk_gauss},
-we had to set them to predict the same 68\% containment
-radius of 0.5\deg.  The 68\% containment radius for a
-spatial model is the radius at which 68\% of the intensity is
-enclosed.  It can be computed by a straightforward integral
-and we find that $\rsixeight_\text{,Gaussian}=1.51\sigma$
-whereas $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
-is defined in equation~\ref{disk_pdf} for the Gaussian source and
-equation~\ref{gauss_pdf} for the disk source.  Since $\rsixeight=0.5\deg$,
-the uniform disk has $\sigma=0.41\deg$ and the Gaussian has
-$\sigma=0.75\deg$.
-
-This is important when comparing morphologies to other wavelengths
-because the quoted size can vary significantly depending on which quantity
-is reported.  This effect can be best seen in figure~\ref{compare_r68}
-which a counts map of an extended source simulated in the energy
-range from 1 \gev to 100 \gev with a uniform disk spatial model with
-an extension $\sigma$ of 0.5. Overlaid on the plot is the fit extension
-assuming the source has a uniform disk and a Gaussian spatial model. The
-plot overlays both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly
-larger for the disk spatial hypothesis compared to the Gaussian spatial
-model. On the other hand, the disk and Gaussian's 68\% containment radius
-are similar.
-
-Since we are not very sensitive to the particular morphology of an
-extended source, there is no correct choice for which size to quote
-or which shape to overlay. For the following analysis, we quote the
-disk's edge and overlay this size.  But due to smearing of the PSF,
-$\sigma$ typically looks larger than the observed counts distribution.
-When comparing the fit extensions with other wavelengths, it is important
-to compare consistent quantities.
-
-\section{LAT Extended Source Validation}
+Although these shapes are significantly different, the convolution
+of them with the PSF look similar.  Figure~\ref{compare_disk_gauss}
+demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
+a uniform disk and Gaussian spatial model of size 0.5\deg.\footnote{To
+allow a valid comparison between Gaussian and disk shaped morphologies,
+we define the source size for this test as the radius containing
+68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
+and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
+is defined in equation~\ref{gauss_pdf} and
+equation~\ref{disk_pdf} respectively.} This plot shows that we are
+not very sensitive to probing the exact structure of an extended source.
+In the search for extended sources, we therefore use only a uniform
+disk as our spatial extension shape. We then quote the radius of the
+disk edge as the size of the source.
+
+\section{Validation of Analysis Method}
 
@@
 
-We validated \pointlike's extension fitting code with a Monte Carlo
-study. \tsext (defined in section~\ref{extension_fitting}) can be used to calculate the statistical significance
-of the extension of a source.  Since the point source and extended source models are
-nested, an extended source must always fit as well as a point source.  On the other hand, we would
-not expect the likelihood to change very much unless the source was
-significantly extended.  Since an extended source has one additional
-degree of freedom, Wilks' Theorem predicts that the distribution of $\tsext$
-when testing a point source for extension should follow a $\chi^2_1$
-distribution (\cite{wilks_theorem}).
-
-However, since the null hypothesis rests on the edge of
-parameter space when the extension is 0, Wilks' Theorem does not hold
-(\cite{warn_wilks_theorem}).  One might expect the actual distribution
-to be a half $\chi^2_1$ distribution with one degree of freedom plus
-half a delta function at 0:
-\begin{equation}
+Mattox et al. discuss that the test statistic distribution
+for a likelihood ratio test on the existence of a source at
+a given position is \cite{mattox_egret}
+\begin{equation}\label{ts_ext_distribution}
   P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
 \end{equation}
-Chernoff proved that under certain assumptions this is the correct distribution
-when the null hypothesis is on the edge of parameter
-space (\cite{chernoff}).  The false detection
-probability can be estimated by integrating this function from an observed
-test statistic value to infinity. It is for this particular distribution
-that the often quoted result holds that $\sqrt{\ts}$ is a measure of
-the number of $\sigma$ of the detection (\cite{mattox_egret}).
-
-The half $\chi^2_1$ distribution was found to hold for the special case
-of source finding using EGRET (\cite{mattox_egret}). This distribution
-is also plausible when testing point sources for extension. Due to
-statistical fluctuations, half of the point sources might look narrower
-than the PSF leading to $\tsext=0$. The other half of the time, we would
-get a distribution consistent with Wilks' theorem. We will present a
-Monte Carlo study that shows an empirical distribution of \tsext in the
-null hypothesis and compares it to this distribution.
-
-We simulated point sources of varying spectral models and fit them
-them using \pointlike as both point and extended sources. The data was
-simulated using \gtobssim\footnote{\gtobssim is distributed
+The particular form of equation \ref{ts_ext_distribution} is
+due to the null hypothesis (source flux $\Phi=0$) residing
+on the edge of parameter space and the model hypothesis
+adding a single degree of freedom. It is plausible to
+expect a similar distribution of the test statistic
+in the test for source extension as the same conditions
+apply (with source flux $\Phi$ replaced by source radius $r$).
+To validate this claim, we performed a Monte Carlo
+study to calculate empirical distributions for $\tsext$ and
+compared them to equation~\ref{ts_ext_distribution}.
+
+We simulated point sources of varying spectral models using
+\gtobssim\footnote{\gtobssim is distributed
 by the Fermi Science Support Center (\cite{fssc}).}
-The point sources were simulated with a power-law spectral model with
-six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
-$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
-indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
+and fit them
+them using \pointlike as both point and extended sources. 
+The point sources were simulated with a power-law spectral model 
+with integrated fluxes above 100 \mev ranging from
+$3\times 10^{-9}$ to $10^{-6} \ph/\cm^2/\sec$ in
+six discrete steps and spectral
+indices ranging from 1.5 to 3 in four discrete steps.
+These values were picked to
 to represent typical source parameters in LAT-detected sources. The point
-sources were simulated on top of an isotropic power-law background
-with a Sreekumar-like spectrum ($>100$ \mev flux of $1.5\times 10^{-5}$ and spectral
-index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
-performed over a one year time interval using a default rocking profile
+sources were simulated on top of an isotropic 
+background with an integrated flux above 100 \mev of $1.5\times10^{-5}$
+(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
+performed over a one year observation period
+using a default rocking profile
 and a representative livetime fraction of 0.8.  The reconstruction was
-performed with photons from an energy range of 1 \gev to 100 \gev using 4
-energy bins per decade and using the 
+performed using 1-100 \gev photons 
+and the 
 Pass 7\_V6 (P7\_V6) Source Instrument
@@
 simulations were performed. For the dimmer spectral models, many of the
-simulations had $\ts<25$ and were discarded.  Table~\ref{ts_ext_num_sims}
+simulations left the source undetected ($\ts<25$)
+and were discarded.  Table~\ref{ts_ext_num_sims}
 shows the different spectral models used in our study as well as the
 number of simulations.  The cumulative density of \tsext is plotted in
-figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution suggested by Wilks'
-Theorem is overlaid for comparison.
-
-Our Monte Carlo study shows broad agreement between simulations and Wilks'
-theorem. Nevertheless, the agreement is not perfect.  It should be noted
-that the discrepancy seems to be worst for bright sources which seems to
-imply that numerical errors in the convolution become more apparent for
-sufficiently bright sources.  Other possible reasons for departure from
-Wilks' theorem might include \pointlike ignoring energy dispersion which
-would change the PSF's shape as a function of energy. But we emphasize
-that most of the time, our empirical curve lies to the left of the
-theoretical curve so using the theoretical distribution would lead to an
-underestimate of the statistical significance of a detection. Therefore,
-we are confident that $\sqrt{\tsext}$ can be used as a measure of the
-statistical significance of a source's extension and use it in the
-following analysis.
+figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution of
+equation~\ref{ts_ext_distribution} is overlaid for comparison.
+
+Our Monte Carlo study shows broad agreement between simulations and
+equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is not
+perfect.  It should be noted that the discrepancy seems to be worst for
+bright sources, a likely cause being numerical errors in the convolution
+becoming more apparent for sufficiently bright sources.  Other possible
+reasons for departure from equation~\ref{ts_ext_distribution} could
+be that \pointlike ignores energy dispersion which would change the
+PSF's shape as a function of energy. We emphasize that most of the
+time, our empirical curve lies to the left of the theoretical curve so
+using the theoretical distribution would lead to an underestimate of the
+statistical significance of a detection. Therefore, we are confident that
+$\sqrt{\tsext}$ can be used as a conservative measure of the statistical
+significance of a source's extension and use it in the following analysis.
 
@@
 
-We calculated the LAT's detection threshold to spatially
-extended sources. The detection threshold to extension is
-defined as the flux at which the average value of $\tsext$ is
-$\langle\tsext\rangle=16$ corresponding to a $4\sigma$ detection (see
-section~\ref{monte_carlo_validation}).  Qualitatively, we expect the LAT
-would not be sensitive to sources much smaller than the PSF or much larger
-than the PSF.  Small sources would look too much like the PSF and larger
-sources would get lost in the background due to low surface brightness.
-
-To calculate the LAT's detection threshold, we simulated sources with
-a uniform radially symmetric disk spatial model on top of a power-law
-Sreekumar-like isotropic spectrum (\cite{sreekumar_isotropic}).  The Monte
-Carlo simulation was performed using the same two year time range that
-was used in 2FGL.  For each extension and spectral index, we picked a
-flux range which bracketed $\tsext=16$. We then picked ten flux points in
-this range and repeatedly simulated and then performed extension tests of
-the simulated extended source.  We calculated $\langle\tsext\rangle=16$
-by fitting a line to the flux and $\tsext$ values.
+We calculated the LAT's detection threshold to spatially extended
+sources. We define the detection threshold as the flux at which the value
+of $\tsext$ averaged over many statistical representations of a source
+is $\langle\tsext\rangle=16$ corresponding to a $4\sigma$ detection
+(see section~\ref{monte_carlo_validation}).
+
+We used the simulation setup described in
+section~\ref{monte_carlo_validation}, but instead simulated extended
+sources with a uniform radially symmetric disk spatial model and
+instead over the actual two year time interval.  For each extension and
+spectral index, we picked a flux range which bracketed $\tsext=16$. We
+then picked ten flux points in this range and repeatedly simulated
+and then performed extension tests of the simulated extended source.
+We calculated $\langle\tsext\rangle=16$ by fitting a line to the flux
+and $\tsext$ values.
 
@@
 spectral indices from 1.5 to 3 and extension varying from $\sigma=0.1\deg$
-to $2.0\deg$.  The LAT's threshold to extension
-is better for harder sources with more high energy photons and
-the threshold is best for sources with an extension 
-$\approx0.5\deg$ and is significantly worse for very small extended small.
-Figure~\ref{index_sensitivity} shows the threshold using photons with
-energies between 100 \mev and 100 \gev and also using only photons
-with energies between 1 \gev and 100 \gev.  Except for the hardest
-and largest sources, our detection threshold is almost unchanged when
-including photons with energies between 100 \mev and 1 \gev.  This is also
-demonstrated in figure~\ref{four_plots_ic443}(b) which shows \tsext for the
-SNR IC443 computed independently in twelve energy bins between 100 \mev and
-100 \gev. For IC443, which has a spectral index $\approx2.4$, almost the entire
-increase in \ts comes from energies above 1 \gev.  On the other hand,
-other systematic errors become increasingly important at low energy. For
-our extension search, we use only only photons with energy above 1 \gev.
+to $2.0\deg$.  The LAT's threshold to extension is better for harder
+sources with more high energy photons and the threshold is best for
+sources with an extension $\approx0.5\deg$ and is significantly worse
+for very small extended small.  Figure~\ref{index_sensitivity} shows
+the threshold using photons with energies between 100 \mev and 100 \gev
+and also using only photons with energies between 1 \gev and 100 \gev.
+Except for the hardest and largest sources, our detection threshold is
+almost unchanged when including photons with energies between 100 \mev and
+1 \gev.  This is also demonstrated in figure~\ref{four_plots_ic443}(b)
+which shows \tsext for the SNR IC443 computed independently in twelve
+energy bins between 100 \mev and 100 \gev. For IC443, which has a
+spectral index $\approx2.4$, almost the entire increase in \ts comes
+from energies above 1 \gev.  On the other hand, other systematic errors
+become increasingly important at low energy. For our extension search,
+we use only only photons with energy above 1 \gev.
 
@@
 A histogram of the \tsext values computed for these AGN is shown in
-figure~\ref{agn_ts_ext}. Overlaid on the plot is a $\chi^2/2$ distribution
-suggested by Wilks' Theorem.  The \tsext distribution for AGN shows good
+figure~\ref{agn_ts_ext}. Overlaid on the plot is the $\chi^2/2$
+distribution of equation~\ref{ts_ext_distribution}.
+The \tsext distribution for AGN shows good
 agreement with the theoretical distribution.  Two sources had $\tsext>9$.
@@
 
+\todo[inline]{
+Note about how it is difficult to explain the TeV to X-ray emission
+ratio b/c of magnetic field. Refernece in page 7 of (sukazu paper on HESS J1614-518, but
+it also refers to (Matsumoto et. al 2007 and says this requires small b/field with strong
+cutoff in eletron energy). Also some not eabout different photon fields
+being possible.}
+
+\todo[inline]{
 Note about this this paper finds other stuff: (\cite{discovery_of_pwn_for_PSR_J1617-5055}).
-
+}
+
+\todo[inline]{
 The \gev emission is suggested to be the same emission component as
@@
 frequencies will likely be needed to firmly associated this source.
+}
 
@@
 
-The two year catalog source 2FGL\,J1615.2-5138 was found 
-using 10-100 \gev photons to have
-an extension of $0.42\deg\pm0.03\deg\stat\pm0.01\sys$ 
-with an extension
-significance of \tsext=48.0.  The source was fit to a position
-of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
+The two year catalog source 2FGL\,J1615.2-5138 was found using 10-100 \gev
+photons to have an extension of $0.42\deg\pm0.03\deg\stat\pm0.01\sys$
+with an extension significance of \tsext=48.0.  The source was fit to a
+position of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
 with the one year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
@@
 on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian
-extension of $\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$ in
-the semi-major and semi-minor axis. This size corresponds to a 68\%
-containment size of $\rsixeight=0.35\deg\pm0.03\deg$ and $0.23\pm0.03$.
-This elliptical size matches the LAT size $\rsixeight=0.35\deg\pm0.03\deg$.
-Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.2-5138
-connects smoothly to the H.E.S.S spectrum of HESS\,J1614-518.
+extension of $\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$
+in the semi-major and semi-minor axis. This size corresponds
+to a 68\% containment size of $\rsixeight=0.35\deg\pm0.03\deg$
+and $0.23\pm0.03$.  This elliptical size matches the LAT size
+$\rsixeight=0.35\deg\pm0.03\deg$.  Figure~\ref{hess_seds} shows that
+the LAT spectrum of 2FGL\,J1615.2-5138 connects smoothly to the H.E.S.S
+spectrum of HESS\,J1614-518.  Further data collected by H.E.S.S. in 2007
+helped to resolve a double peaked structure in the H.E.S.S. data but no
+spectral variation across the source, suggesting that the emission is
+not the confusion of physically separate sources (\cite{closer_look_hess_j1614-518}).
+The source was also detected by CANGAROO-III (\cite{cangaroo_j1614-518}).
+
+This source is currently unidentifed. There are five nearby pulsars,
+but they are not luminous enough to provide the required energy output
+to power the \tev emission (\cite{closer_look_hess_j1614-518}).
+
+\todo[inline]{Swift observations}
+
+Suzaku observations of the region around HESS\,J1614-518 reveale three
+X-ray sources in the region. Suzaku source A is a hard extended source
+spatially coincident with the peak of HESS\,J1614-518.
+
+Suzaku source B is
+in a relativly dim region in the middle of HESS\,J1614-518 and was not
+spatially resolvable. source B is spatially coincident with Pisim 22.
+
+Suzaku Source C is a foreground source.
+
+Swift observations the region and resolved six X-ray sources.\todo{citation}
+
+\todo[inline]{Emission due to SNR}
+
+\todo[inline]{Emission could be due to a PWN}
+
+\todo[inline]{Emission due to Massive Star}
 
 \todo[inline]{Add interpretations of HESS\,J1614-518. Stefan says to
-use the Rowell et al, Suzaku observations.}
+Suzaku observations.}
 
@@
 has previously been observed in several aging PWNe including 
-HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess} and HESS\,J1640-465
-(\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}) and can be explained
-by the electrons emitting syncrotron radiation having a shorter lifetime
-than the electrons emitting inverse Compton radiation.
-
+HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess}, HESS\,J1640-465
+(\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}),
+and Vela X (\cite{vela_x_rosat,vela_x_hess}). 
+This can be explained by a different synchrotron cooling
+time for the electroncs producing X-rays and \tev gamma rays.
 Because of the spectral and spatial match between the \gev and \tev
@@
 
-\section{Conclusion}
-
-\todo[inline]{This conclusion needs to be written.}
-
-Many extended sources. Instructive to use photons with energy
-above 10 \gev where we don't have to worry about diffuse background
-as much.
-
-Make some conclusion about how the LAT will eventually collect a factor
-of five more data! \pointlike will be necessary to improve the model of
-the high energy sky. Hard to do a blind analysis of LAT data.
-
-Figure~\ref{allsky_extended_sources} is an all sky map showing the
-location of all \gev extended sources. Note how most extended sources
-are in the Galactic plane.
-
-Figure~\ref{gev_vs_tev_histogram} is a histogram comparing the size of
-all extended sources seen in \gev by the LAT and in \tev by H.E.S.S..
-Note how H.E.S.S. can see smaller sources whereas the LAT can see
-bigger sources.
-
-For all extended sources seen both in \gev and \tev,
-figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.
-Note that there is pretty good agreement.
-
-Note about how comparison of HESS and LAT sizes will require more accurate
-ellitpical gaussian fitting + using the same spatial model.  Interesting
-to see if there is a correlation for PWN between energy and source size!
-
-LAT has a planned lifetime of 5 years with (don't know how to phrase this) 
-hope to run for 10 years. Additonal data will allow us to perfrom
-more detailed morphological and spectral analysis of these sources.
-
-Improved diffuse model and better statisticsl will allow us to push
-our analysis to lower energies.
+\section{Discussion}
+
+\todo[inline]{Finish the discussion.}
+
+2FGL reported on the detection of twelve spatially extended sources. Using
+two years of LAT data and a new analysis method, we present on 
+the detection of nine additional extended sources. We also reanalyze
+the spatial shape of the extended sources in 2FGL.  Finding a coherent
+source extension with different frequencies, especially at \tev energies,
+allows us to identify the LAT source. Even still, for many extended LAT
+sources the source class and emission process is still uncertain.
+
+The position of the 21 extended LAT sources is plotted in
+figure~\ref{allsky_extended_sources}.  Most of them lie along the galactic
+plane.  This is expected because extragalactic sources are typically too
+far away to be resolvable and most Galactic sources lie along the plane.
+
+Figure~\ref{compare_index_2FGL} shows a comparison of the spectral index
+of LAT detected extended sources and of all sources in 2FGL. This, and
+table~\label{known_extended_sources} and~\label{new_ext_srcs_table},
+show that the LAT observes a population of hard (index $<2$)
+extended sources above 10 \gev which connects to \tev sources.
+Figure~\ref{hess_seds} shows the LAT energy spectrum of four of the
+extended sources which were first discovered in the H.E.S.S. Galactic
+plane survey (\cite{hess_plane_survey}) and have a matching size to LAT
+extended sources.  The LAT energy spectrum connects smoothly to \tev.
+This is also true of HESS\,J1825-137 (\ref{fermi_hess_j1825}) and RX
+J1713.7-3946 (\cite{rx_j1713_lat}). We conclude that the \gev and \tev
+emission from these sources is coming from the same emission mechanism.
+
+For the LAT extended sources also seen in \tev,
+figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
+a good correlation between the \gev and \tev sizes of the sources. Even
+so, the size of PWNe are expected to vary across the \gev and \tev energy
+range and the size of HESS\,J1825-137 was seen by H.E.S.S. to vary
+between 200 \gev and 20 \tev (\cite{energy_dependent_hess_j1825}).
+HESS\,J1825-137 is significantly larger in \gev than \tev
+(\cite{fermi_hess_j1825}).  It is interesting to compare the \gev and
+\tev size of other PWN candidates, but definitively measuring this effect
+would require a more careful analysis of the LAT data using the same 
+elliptical spatial model.
+
+Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
+LAT sources to the 42 extended H.E.S.S. sources.  Because of the large
+field of view and all sky coverage, the LAT can more easily measure
+larger sources including the LMC and SMC.  On the other hand, the
+smaller angular resolution of Air Cherenkov detectors allows them to
+measure a population of extended sources below our sensitivity limit
+(currently at about $\approx0.2\deg$).  Fermi has a five year nominal
+livetime with a goal of ten years of operation. With increased exposure,
+the LAT will likely begin to resolving these smaller \tev sources.
+
+Furthermore, our sensitivity to these extended sources will likely improve
+faster than $\sqrt{t}$ because at the highest energies, our background is
+relatively small and we are in the Poisson instead of Gaussian limit.
+Future improvements in the diffuse emission model will improve our
+sensitivity by allowing this analysis to go to lower energies.
 
@@
     }\label{compare_disk_gauss}
-  \end{figure}
-
-  \begin{figure}
-    \begin{center}
-      \includegraphics{mc_plots/compare_r68.pdf}
-      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_r68/v2/plot.py
-      \end{center}
-      \caption{
-      This plot shows that fitting the same source with different
-      spatial shapes can lead to different values of the fitted
-      extensions. On the other hand, the different shapes have a
-      good agreement about the 68\% containment radius \rsixeight.
-      It shows counts map for a simulated uniform disk extended source
-      in the energy range from 1 \gev to 100 \gev.  The source has a
-      size $\sigma=0.5\deg$, an integral flux between 1 \gev and 100
-      \gev of $3\times 10^{-8}\ph/\cm^2/\sec$, and a spectral index 2.
-      The smoothed counts from a point source with the same spectrum are
-      shown in the bottom right inset.  This source was fit with both
-      a uniform disk and a Gaussian spatial model.  The white circle
-      represents the edge of the best fit uniform disk spatial model.
-      The black circle is the fit $\sigma$ modeling the source with a
-      Gaussian hypothesis.  The dashed white and black circle are the
-      fit \rsixeight for the disk and Gaussian hypothesis. This plot is
-      discussed further in section~\ref{compare_source_size}.
-      }\label{compare_r68}
   \end{figure}
@@
         \hline
-             1.5 &       x1 &      149.5 &       23.5 &       11.4 &        8.1 &        7.2 &        7.0 &        6.8 &        6.8 &        7.0 &        7.4 &        7.5 &        7.7 &        7.9 &        8.2 &        8.9 &        9.7 &        9.0 &        9.0 &        8.7 &       10.1 \\
-                 &      x10 &      145.7 &       28.9 &       18.3 &       15.1 &       15.4 &       15.0 &       16.1 &       15.8 &       16.6 &       17.6 &       18.5 &       19.9 &       21.5 &       23.6 &       25.2 &       25.2 &       21.4 &       23.0 &       23.6 &       23.8 \\
-                 &     x100 &      184.2 &       55.3 &       42.1 &       40.6 &       40.5 &       42.0 &       42.1 &       40.6 &       43.0 &       43.7 &       37.6 &       39.4 &       39.9 &       36.8 &       35.9 &       36.1 &       36.3 &       37.7 &       37.0 &       37.4 \\
-               2 &       x1 &      332.5 &       44.1 &       18.9 &       13.4 &       11.3 &       10.4 &       10.1 &       10.0 &       10.1 &       10.3 &       10.6 &       10.8 &       11.0 &       11.3 &       12.2 &       12.4 &       12.8 &       13.2 &       13.5 &       13.8 \\
-                 &      x10 &      337.9 &       55.6 &       32.4 &       27.2 &       26.4 &       25.4 &       25.6 &       26.0 &       27.8 &       28.2 &       29.2 &       29.2 &       31.1 &       30.8 &       31.5 &       32.8 &       32.1 &       34.5 &       34.8 &       36.6 \\
-                 &     x100 &      416.0 &      133.9 &       88.0 &       77.8 &       74.1 &       72.6 &       68.7 &       65.0 &       63.0 &       63.3 &       61.7 &       61.8 &       60.1 &       59.0 &       54.7 &       58.0 &       58.9 &       60.8 &       57.5 &       53.9 \\
-             2.5 &       x1 &      635.5 &       74.3 &       29.8 &       19.2 &       15.8 &       13.7 &       12.8 &       12.7 &       12.3 &       12.4 &       12.4 &       12.6 &       12.7 &       12.9 &       13.3 &       13.4 &       13.8 &       14.3 &       14.7 &       15.4 \\
-                 &      x10 &      640.0 &       97.6 &       51.7 &       39.3 &       34.6 &       33.0 &       32.7 &       32.6 &       33.0 &       33.5 &       34.6 &       35.2 &       34.7 &       36.0 &       37.3 &       37.3 &       35.7 &       36.4 &       37.5 &       38.1 \\
-                 &     x100 &      794.9 &      261.2 &      134.2 &      103.5 &       89.5 &       80.7 &       78.1 &       75.3 &       70.1 &       70.2 &       65.5 &       64.7 &       61.9 &       59.8 &       56.4 &       55.6 &       57.9 &       55.0 &       53.3 &       51.8 \\
-               3 &       x1 &      857.2 &      110.2 &       43.5 &       25.8 &       18.9 &       16.1 &       14.3 &       13.5 &       13.2 &       13.2 &       13.0 &       12.9 &       13.2 &       13.3 &       13.2 &       13.5 &       13.8 &       14.1 &       14.4 &       15.0 \\
-                 &      x10 &      931.1 &      155.1 &       70.4 &       48.3 &       40.9 &       37.3 &       35.6 &       35.0 &       35.5 &       35.8 &       36.0 &       34.9 &       35.1 &       35.1 &       37.0 &       37.7 &       35.4 &       35.8 &       36.6 &       37.8 \\
-                 &     x100 &     1119.8 &      295.6 &      180.9 &      119.4 &      101.0 &       92.0 &       86.4 &       78.5 &       73.5 &       69.9 &       66.7 &       64.9 &       63.3 &       61.2 &       57.3 &       56.7 &       56.7 &       55.0 &       50.7 &       50.4 \\
+             1.5 &       x1 &      148.3 &       23.2 &       11.2 &        8.0 &        7.1 &        6.9 &        6.8 &        6.8 &        7.0 &        7.3 &        7.5 &        7.7 &        8.0 &        8.3 &        9.1 &        9.8 &        9.0 &        9.1 &        8.8 &       10.2 \\
+                 &      x10 &      146.9 &       29.0 &       18.5 &       15.1 &       15.4 &       15.0 &       14.7 &       15.6 &       16.6 &       17.3 &       18.0 &       19.1 &       20.7 &       22.5 &       23.6 &       24.3 &       21.2 &       22.8 &       23.3 &       23.6 \\
+                 &     x100 &      184.3 &       55.1 &       43.0 &       41.0 &       40.7 &       41.7 &       40.3 &       40.8 &       43.0 &       43.6 &       38.3 &       39.5 &       40.1 &       38.5 &       36.5 &       35.8 &       36.5 &       38.1 &       36.6 &       37.1 \\
+               2 &       x1 &      327.5 &       43.1 &       18.7 &       13.3 &       11.2 &       10.4 &       10.1 &       10.1 &       10.2 &       10.4 &       10.6 &       10.9 &       11.1 &       11.5 &       12.3 &       12.6 &       13.0 &       13.4 &       13.8 &       14.2 \\
+                 &      x10 &      336.1 &       55.3 &       32.2 &       27.4 &       26.3 &       25.3 &       25.5 &       25.8 &       27.2 &       26.6 &       27.6 &       28.5 &       30.1 &       29.9 &       30.8 &       31.8 &       31.9 &       34.2 &       34.2 &       36.1 \\
+                 &     x100 &      409.6 &      128.1 &       88.6 &       76.2 &       72.7 &       71.4 &       67.8 &       65.2 &       63.6 &       63.7 &       62.0 &       63.1 &       62.4 &       61.1 &       56.0 &       58.4 &       60.1 &       62.1 &       59.5 &       55.9 \\
+             2.5 &       x1 &      622.9 &       75.0 &       29.6 &       19.0 &       15.5 &       13.6 &       12.8 &       12.7 &       12.4 &       12.5 &       12.6 &       12.9 &       12.8 &       13.1 &       13.4 &       13.7 &       14.1 &       14.6 &       15.0 &       15.7 \\
+                 &      x10 &      641.5 &       98.2 &       51.8 &       39.2 &       34.7 &       33.1 &       32.6 &       32.3 &       33.0 &       33.4 &       33.8 &       34.5 &       34.5 &       35.4 &       37.0 &       37.2 &       35.6 &       36.2 &       37.1 &       37.8 \\
+                 &     x100 &      789.7 &      260.3 &      136.9 &      102.7 &       90.1 &       80.8 &       77.2 &       74.9 &       69.1 &       70.8 &       65.8 &       64.5 &       64.3 &       62.3 &       57.1 &       57.1 &       58.8 &       57.3 &       55.6 &       54.2 \\
+               3 &       x1 &      842.0 &      109.6 &       42.9 &       25.4 &       18.7 &       15.9 &       14.3 &       13.5 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.5 &       13.5 &       13.6 &       14.1 &       14.3 &       14.7 &       15.3 \\
+                 &      x10 &      919.0 &      153.8 &       69.7 &       48.1 &       40.9 &       37.6 &       35.7 &       34.9 &       35.3 &       35.3 &       35.3 &       35.2 &       35.1 &       35.5 &       37.0 &       37.7 &       35.3 &       35.5 &       36.4 &       37.5 \\
+                 &     x100 &     1077.5 &      289.1 &      180.2 &      119.2 &      101.0 &       92.4 &       86.2 &       79.3 &       74.3 &       70.8 &       67.2 &       66.4 &       65.0 &       62.9 &       58.4 &       56.6 &       57.4 &       55.9 &       54.3 &       52.2 \\
         \hline
@@
         \hline
-             1.5 &       x1 &       43.9 &        8.2 &        4.3 &        3.2 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.8 &        2.8 &        3.0 &        3.0 &        3.1 &        3.3 &        3.4 &        3.5 \\
-                 &      x10 &       44.6 &        9.1 &        5.8 &        5.0 &        5.0 &        5.1 &        5.0 &        5.4 &        5.3 &        5.7 &        6.0 &        6.3 &        6.7 &        6.5 &        7.1 &        7.7 &        7.8 &        8.2 &        8.4 &        8.7 \\
-                 &     x100 &       47.2 &       13.3 &       11.4 &       10.6 &       10.6 &       10.7 &       11.9 &       12.7 &       13.2 &       13.6 &       15.3 &       16.2 &       17.4 &       18.4 &       19.3 &       20.1 &       20.8 &       21.8 &       22.6 &       24.0 \\
-               2 &       x1 &       49.1 &        8.5 &        4.4 &        3.3 &        2.8 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.1 &        3.2 &        3.2 &        3.4 &        3.5 &        3.6 \\
-                 &      x10 &       48.3 &        9.6 &        6.0 &        5.2 &        5.2 &        5.3 &        5.3 &        5.6 &        5.5 &        5.9 &        6.4 &        6.7 &        7.0 &        7.2 &        7.7 &        8.0 &        8.3 &        8.6 &        9.0 &        9.3 \\
-                 &     x100 &       51.1 &       14.8 &       11.7 &       11.4 &       11.5 &       12.0 &       13.1 &       14.0 &       14.4 &       15.2 &       16.1 &       17.1 &       18.7 &       19.7 &       20.5 &       21.9 &       22.9 &       23.7 &       24.1 &       25.2 \\
-             2.5 &       x1 &       52.1 &        9.2 &        4.6 &        3.3 &        2.9 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.7 &        2.8 &        2.9 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 &        3.6 \\
-                 &      x10 &       53.0 &       10.5 &        6.2 &        5.4 &        5.2 &        5.2 &        5.4 &        5.6 &        5.8 &        6.1 &        6.4 &        6.6 &        6.9 &        7.3 &        7.5 &        8.2 &        8.4 &        8.7 &        8.9 &        9.3 \\
-                 &     x100 &       55.5 &       15.9 &       12.7 &       12.0 &       11.9 &       12.3 &       13.0 &       14.4 &       14.7 &       15.2 &       16.4 &       17.2 &       19.1 &       19.6 &       20.6 &       21.9 &       23.0 &       23.4 &       24.4 &       24.9 \\
-               3 &       x1 &       54.6 &        9.5 &        4.7 &        3.4 &        2.9 &        2.7 &        2.6 &        2.5 &        2.5 &        2.6 &        2.6 &        2.7 &        2.7 &        2.9 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 \\
-                 &      x10 &       55.1 &       10.5 &        6.2 &        5.3 &        5.2 &        5.3 &        5.2 &        5.4 &        5.5 &        5.7 &        6.0 &        6.4 &        6.6 &        7.0 &        7.3 &        7.9 &        8.1 &        8.5 &        8.7 &        8.9 \\
-                 &     x100 &       59.8 &       16.0 &       12.7 &       11.8 &       11.6 &       12.2 &       12.7 &       14.1 &       14.2 &       14.6 &       16.0 &       16.9 &       17.9 &       19.0 &       20.1 &       20.6 &       21.6 &       22.1 &       22.7 &       23.5 \\
+             1.5 &       x1 &       44.4 &        8.1 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.4 &        2.5 &        2.6 &        2.7 &        2.7 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
+                 &      x10 &       45.2 &        9.3 &        5.9 &        5.0 &        4.9 &        5.1 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.2 &        6.6 &        6.5 &        7.0 &        7.7 &        7.8 &        8.2 &        8.4 &        8.8 \\
+                 &     x100 &       47.2 &       13.5 &       11.5 &       10.6 &       10.6 &       10.8 &       12.0 &       12.7 &       13.3 &       13.7 &       15.2 &       16.1 &       17.2 &       18.2 &       19.1 &       19.8 &       20.7 &       21.3 &       22.1 &       23.4 \\
+               2 &       x1 &       49.6 &        8.3 &        4.4 &        3.2 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
+                 &      x10 &       48.5 &        9.6 &        6.0 &        5.2 &        5.1 &        5.2 &        5.2 &        5.4 &        5.5 &        5.8 &        6.4 &        6.7 &        7.0 &        7.2 &        7.6 &        8.0 &        8.3 &        8.7 &        9.0 &        9.3 \\
+                 &     x100 &       51.5 &       14.8 &       11.8 &       11.5 &       11.5 &       12.0 &       13.1 &       14.0 &       14.4 &       15.3 &       16.1 &       16.8 &       18.5 &       19.3 &       20.1 &       21.3 &       22.3 &       23.1 &       23.4 &       24.5 \\
+             2.5 &       x1 &       53.0 &        9.2 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.8 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.4 &        3.5 &        3.6 \\
+                 &      x10 &       53.8 &       10.6 &        6.3 &        5.4 &        5.1 &        5.2 &        5.3 &        5.5 &        5.7 &        6.1 &        6.4 &        6.6 &        6.9 &        7.3 &        7.5 &        8.2 &        8.4 &        8.7 &        9.0 &        9.4 \\
+                 &     x100 &       56.6 &       15.8 &       12.9 &       11.9 &       11.9 &       12.4 &       13.1 &       14.3 &       14.7 &       15.2 &       16.3 &       17.0 &       18.9 &       19.3 &       20.1 &       21.2 &       22.2 &       22.7 &       23.6 &       24.1 \\
+               3 &       x1 &       55.1 &        9.3 &        4.7 &        3.3 &        2.9 &        2.6 &        2.5 &        2.5 &        2.5 &        2.5 &        2.6 &        2.6 &        2.7 &        2.8 &        2.9 &        3.0 &        3.0 &        3.2 &        3.4 &        3.4 \\
+                 &      x10 &       55.7 &       10.5 &        6.3 &        5.3 &        5.2 &        5.3 &        5.2 &        5.4 &        5.6 &        5.7 &        6.0 &        6.4 &        6.6 &        6.9 &        7.1 &        7.9 &        8.1 &        8.5 &        8.7 &        8.9 \\
+                 &     x100 &       60.1 &       16.0 &       12.8 &       11.7 &       11.7 &       12.3 &       12.7 &       14.0 &       14.1 &       14.6 &       15.8 &       16.5 &       17.6 &       18.6 &       19.5 &       19.9 &       21.0 &       21.3 &       22.0 &       22.9 \\
         \hline

### 2011-08-09 extended_catalog/paper/extended_catalog.tex
markus changes

@@
 very bright sources, this numerical error has the potential to bias the
-test statistic for the extension test.  the source with an extended shape
+test statistic for the extension test. The source with an extended shape
 to the likelihood fitting it with its extension fixed to ${10^{-10}}\deg$.
@@
 We found good agreement between the two methods. For the new extended
-source candidates, table~\ref{alt_diff_model_results} will shows a
+source candidates, table~\ref{alt_diff_model_results} shows a
 comparison of the test statistic \ts and \tsext computed using \pointlike
@@
 positions found using \pointlike.  For the extended candidates found
-by our search, we computed both \tsext and \tsinc.  The results will be
+by our search, we computed both \tsext and \tsinc.  The results are
 presented in table~\ref{dual_localization_results}.
@@
 spectral indices from 1.5 to 3 and extension varying from $\sigma=0.1\deg$
-to $2.0\deg$.  The LAT's threshold to extension is better for harder
-sources with more high energy photons and the threshold is best for
-sources with an extension $\approx0.5\deg$ and is significantly worse
-for very small extended small.  Figure~\ref{index_sensitivity} shows
+to $2.0\deg$.  The LAT's threshold for a significant detection
+of an extension of a LAT souce drops quickly with
+increasing source size and reaches a minimum around 0.5\deg. 
+Figure~\ref{index_sensitivity} shows
 the threshold using photons with energies between 100 \mev and 100 \gev
-and also using only photons with energies between 1 \gev and 100 \gev.
+and also using only 1-100\gev photons.
 Except for the hardest and largest sources, our detection threshold is
@@
 become increasingly important at low energy. For our extension search,
-we use only only photons with energy above 1 \gev.
+we use therefore only photons with energies above 1 \gev.
 
@@
 diffuse emission near the Galactic center.  The figure shows the threshold
-using only photons with energies between 1 \gev and 100 \gev and aldo
-when using only photons with energies between 10 \gev and 100 \gev. We
+using 1-100 \gev photons and also
+using only 10-100 \gev photons. We
 are less sensitive to extended sources with higher background. Also,
@@
 
-Finally, figure~\ref{all_sensitivity} shows the LAT's detection threshold
-for all four spectral indices (1.5, 2, 2.5, and 3) against all three
-background levels (1, 10, and 100 times the Sreekumar-like isotropic
-background).  For a fixed 1 \gev to 100 \gev or 10 \gev to 100 \gev
+Figure 7 shows the flux threshold as a function of source extension for
+different background levels (1x, 10x, and 100x the
+nominal background), different spectral indices, and two
+different energy bands (1-100 \gev and 10-100 \gev).
+For a fixed 1-100 \gev or 10-100 \gev
 flux, the LAT's detection threshold is only weakly depends upon the
@@
 
-2FGL is a list of 1873 \gev sources detected by the LAT.  2FGL included
+We test all sources in the 2FGL catalog for spatial extendedness.
+2FGL is a catalog of 1873 sources detected by the LAT.  It included
 twelve previously published spatially extended sources but did not
 attempt to fit the extension of these sources. Other than these sources,
-all 2FGL sources were modeled as point sources and 2FGL did not attempt to
-resolve the extension of new sources.  In this paper, we tested all 2FGL
-sources for extension to search for new spatially extended \gev sources.
-
-For this search, we build a model of the
-sky consistent with 2FGL.   We used the same two
-years of data from August 4, 2008 to August 1, 2010 and we used the same
-Pass 7\_V6 (P7\_V6) Source class event selections and 
-Instrument Response Functions (IRFs, \cite{lat_on_orbit_psf}).  We used the same Galactic diffuse,
-isotropic diffuse, and earth limb emission model. The spectrum of the
-Galactic and isotropic diffuse models were refit during the analysis
-while the earth limb emission was fixed to it's predicted value.
+all 2FGL sources were modeled as point sources and 2FGL did not attempt
+to resolve the extension of new sources.
+
+Our analysis setup is closely related to the setup used for the
+derivation of the catalog We used the same two years of data from August
+4, 2008 to August 1, 2010 and we used the same Pass 7\_V6 (P7\_V6)
+Source class event selection and Instrument Response Functions (IRFs,
+\cite{lat_on_orbit_psf}).  We used the same models to describe the
+background from Galactic diffuse, isotropic, and earth limb emission.
+The galactic diffuse emission was scaled by a power-law and the isotropic
+component's normalization was left free.
 
@@
 For that reason, we performed our search using photons only between 1
-\gev and 100 \gev.  We used 4 energy bins per each logarithmic decade
-in energy.
-
-We also performed a search for extended sources using photons only
-between 10 \gev and 100 \gev. Even though we are testing the same
+\gev and 100 \gev.
+
+We also performed a search for extended sources using only 10-100 \gev photons. 
+Even though we are testing the same
 sources, this approach is complimentary because the Galactic diffuse
@@
 
-For each catalog source, we tested it for extension using \pointlike
-assuming the source had a uniform radially symmetric disk spatial model.
+We tested each source for extension using
+\pointlike
+assuming the source had a uniform radially symmetric surface brightness.
 We used a circular $10\deg$ region of interest centered on our source and
-included all catalog sources within $15\deg$ of the source of interest.
-We refit the spectral parameters of sources within $2\deg$ of the source.
-We modeled each source with a power-law spectral model. This was reasonable because for a source to be significantly
-extended, it would have to be fairly hard and fit reasonably well by
-a power-law. Second, since we began the analysis at either 1 \gev or
-10 \gev, we didn't expect there to be significant curvature over this
-energy range.
-
-Finally, when analyzing the region, we automatically removed other
-2FGL sources which were within 0.5\deg of the source of interest. This was done because of
-a concern that extended sources would end up 2FGL as
-multiple point sources. These spurious sources would then
-distort the extension fit.
-For each extended candidate, we performed a dual localization procedure
-(described in section~\ref{dual_localization_method} to test if the
-source is extended. We select the sources where $\tsext>16$.
+included all catalog sources within $15\deg$ of the source of interest
+in our background model.
+We refit the spectral parameters of sources within $2\deg$ of the source
+to avoid potential biases of the extension parameters of the source of
+interest due to close-by background sources.
+We modeled each source with a power-law spectral model.
+
+Finally, when analyzing the region, we automatically removed other 2FGL
+sources which were within 0.5\deg of the source of interest. This was
+done to avoid a concern that extended sources would end up in 2FGL as
+multiple point sources. These spurious sources would then distort the
+extension fit.  Instead, when a source is found to be significantly
+extended (i.e. $\tsext>16$), we perform the dual localization procedure
+(described in section~\ref{dual_localization_method} to compare the
+extended source hypothesis to the hypothesis of two independent point
+sources. Only sources with $\tsext>\tsinc$ are considered as extended.
 
@@
 
-Since extragalactic sources are typically too far away to be resolvable,
-we expect most extended sources to be inside our Galaxy and most
-likely on the Galactic plane.  Unfortunately, the \gev emission
-in the Galactic plane is dominated by extremely structured Galactic
-diffuse emission.  Finding sources on top of this emission is difficult
+Based on size vs. distance considerations,
+we expect most extended sources to be inside our Galaxy.  Unfortunately, the \gev emission
+in the Galactic plane is dominated by extremely structured 
+diffuse emission from the interactions of cosmic rays with the
+intergalactic medium.  Finding sources on top of this emission is difficult
 (\cite{first_diffuse_paper}) as has been discussed in 1FGL and 2FGL
@@
 
-% 2FGL J1856.2+0450c = P72Y3047 for
-As an example of why this is important, we describe the test of 
-2FGL\,J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
-a Galactic and isotropic diffuse emission subtracted
-smoothed counts map of this source using photons with energy 
-between 1 \gev and 100 \gev. 
-In this region along the Galactic plane, there appears to be 
-large-scale residual in the diffuse emission. As a result, 2FGL\,J1856.2+0450c 
-fit to an extension of 1.83\deg and the result is statistically significant
-with \tsext=45.4.  By looking at the residuals, it is clear that this
-complicated region is not fit well even though the source's extension is
-statistically significant. For this reason, we manually discard
-the extension of this and similar sources.
-% information came from
-% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
-
-For each extended source candidate,
-we took the spatial and spectral model found using \pointlike and
-performed a crosscheck by refitting the spectral parameters using
-\gtlike.  We used a square ROI $14.1\deg$ in diameter with $1/32\deg$
-spatial bins and the same energy binning as \pointlike. Using \gtlike,
-we found a second measure of \tsext, this time not fitting the extension
-but using a fixed template with the extension determined by \pointlike.
-We only considered a source to be significantly extended if \pointlike
-and \gtlike both agreed.  For the new extended source candidates,
-table~\ref{alt_diff_model_results} will show a comparison of of \tsext for
-\gtlike and \pointlike.
-
-For each candidate, we generated a map of residual \ts
-by adding a new source of spectral index 2 into the region and finding
-the increase in likelihood when fitting its flux. \ts maps are useful
-to look for residual structure in the sky mode.  Figure~\ref{res_tsmaps}
-shows a residual \ts map for the extended source IC443.
-
-For each candidate, we generated plots of the sum of all counts
-within a given distance of the source and compared it to the model
-predictions of a point source.  The plots were binned uniformly
+For each candidate, we generated a map of residual \ts by adding a new
+source of spectral index 2 into the region and finding the increase in
+likelihood when fitting its flux. \ts maps are useful to look for residual
+structure in the sky mode.  Figure~\ref{res_tsmaps} shows a residual \ts
+map for the extended source IC443.  We also generated plots of the sum of
+all counts within a given distance of the source and compared it to the
+model predictions of a point source.  The plots were binned uniformly
 in $\Delta \theta^2$ so that an isotropic background would be flat.
@@
 
-For each source, we tested to see if the region contained instead
-multiple point sources by replacing the extended source with
-two point sources and performed the dual localization procedure
-described in section~\ref{dual_localization_method}.  We only
-considered a source to be extended if $\tsext>\tsinc$.  For the new
-extended sources, we will show the results of this dual localization in
-table~\ref{dual_localization_results}.
+% 2FGL J1856.2+0450c = P72Y3047 for
+We then inspected the residual \ts, smoothed counts maps, and radial
+integral distributions to identify cases in which the extension fit
+is clearly biased by large-scale residuals in the diffuse emission
+and hence the extension measurement unreliable.  An example of such a
+case is shown in figure~\ref{example_bad_fit}. It shows a Galactic and
+isotropic diffuse emission subtracted smoothed counts map of this source
+using 1-100 \gev photons.  In this region along the Galactic plane,
+there appears to be large-scale residual in the diffuse emission. As
+a result, 2FGL\,J1856.2+0450c fit to an extension of 1.83\deg and the
+result is statistically significant with \tsext=45.4.  By looking at
+the residuals, it is clear that this complicated region is not fit well
+even though the source's extension is statistically significant. We do
+not report sources as extended that fail this inspection.
+% information came from
+% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
+
+For the remaining candidates, 
+we took the spatial and spectral model found using \pointlike and
+redetermined the spectral 
+parameters using
+\gtlike.  We used 
+the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
+ROI with a pixel size of 0.03\deg.
+We obtained a second measure of \tsext from \gtlike for the extension
+and position of the source as determined by \pointlike.
+We only considered a source to be significantly extended if $\tsext>16$ with
+both \pointlike and \gtlike.  For the new extended source candidates,
+table~\ref{alt_diff_model_results} shows a comparison of of \tsext for
+\gtlike and \pointlike.
 
@@
 candidates we often had to iteratively improve the model of our background
-sources to obtain a better fit of the sources.  Often, several catalog
-sources would fill in the emission of the extended source and would
+sources to obtain a better fit of the sources.  Several catalog
+sources would often fill in the emission of the extended source and would
 have to be removed from the region.  Similarly, background sources
@@
 all nearby sources until the fit converged.  For each extended source,
-we describe the modification that were required.
+we describe the modifications of the background model compared to the model
+used in the creation of the 2FGL catalog that were required.
 
@@
 using the two PSFs as a systematic error on the extension of a source.
-Because the Monte Carlo representation of the PSF is smaller, it leads
-to unphysically higher \tsext values.  This same approach was used in
+The same approach was used in
 (\cite{ic443}).  At high energies, we believe that our parameterization
@@
 Cygnus Loop were included in 2FGL.  IC443, W28, W44, W51C were
-first reported in (\cite{ic443,w28,w44,w51c}).  Detailed papers
-by the LAT collaboration studying W30 and the Cygnus Loop are
-still in preparation.  \gev emission from W30 was also studied in
-(\cite{castro_and_slane_2010}).  Using photons with energies between
-1 \gev and 100 \gev, our analysis significantly detected the extension
-of all six SNRs. 
+first reported in (\cite{ic443,w28,w44,w51c}).  Detailed papers by the LAT
+collaboration studying W30 and the Cygnus Loop are still in preparation.
+\gev emission from W30 was also studied in (\cite{castro_and_slane_2010}).
+Using 1-100 \gev photons, our analysis significantly detected the
+extension of all six SNRs.
 % 2 galaxies
@@
 Cloud were included in 2FGL (\cite{lmc,smc}).  They were significantly
-detected using photons with energies between 1 \gev and 100 \gev. Our
+detected using 1-100 \gev photons. Our
 fit extension is comparable to the published result, but we note that
@@
 Nine extended sources not include in 2FGL were found using this search.
-Three were found in our search using photons with energies between
-1 \gev and 100 \gev and six were found using photons with energies between
-10 \gev and 100 \gev.  The fit properties of these nine sources is summarized in
+Three were found in our search using 1-100 \gev photons and 
+six were found in our search using 10-100 \gev photons.  
+The fit properties of these nine sources is summarized in
 table~\ref{new_ext_srcs_table}.  This table includes for each source
@@
 
-This source is spatially coincident with the SNR RX J1713.7-3946 and was
-recently reported by (\cite{rx_j1713_lat}).  To analyze this source,
+This source is spatially coincident with the SNR RX J1713.7-3946
+and was recently reported by (\cite{rx_j1713_lat}).  Figure
+\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR RX
+J1713.7-3946 from (\cite{rx_j1713_hess}).  To analyze this source,
 we used the same background model as the recent LAT publication.
 2FGL\,J1715.4-4024c is spatially coincident with Source A and was
-moved to the published location of 
-$(\text{RA},\text{Dec})=(258.84,-40.46)$. Source
-B was added at 
-$(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
-$(\text{RA},\text{Dec})=(257.47,-39.75)$.  Figure \ref{2FGL_J1712.4-3941} shows
-the position of these nearby sources on top of a contour of SNR RX
-J1713.7-3946 seen in \tev by H.E.S.S (\cite{rx_j1713_hess}).
+moved to $(\text{RA},\text{Dec})=(258.84,-40.46)$. Source B was added
+at $(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
+$(\text{RA},\text{Dec})=(257.47,-39.75)$.
 
@@
 This source is currently unidentifed. There are five nearby pulsars,
-but they are not luminous enough to provide the required energy output
+but note are luminous enough to provide the required energy output
 to power the \tev emission (\cite{closer_look_hess_j1614-518}).
+
+HESS J1614-518 is spatially coincident with a young open cluster Pismis
+22 (\cite{hess_1614_landi_atel,closer_look_hess_j1614-518}).
+\gev and \tev emission could arrise from
+hadronic acceleration in the winds of massive stars
+\cite{cosmic_rays_and_gamma-rays_from_ob_stars,gamma-ray_production_in_young_open_clusters}.
+Pisim 22 is at a distance $\approx1$ kpc and can energetically account
+for the \tev emission (\cite{closer_look_hess_j1614-518}), but
+it is difficult to explain the difference in size and positional offset
+between Pismis 22 and HESS\,J1614-518.
 
@@
 
-\todo[inline]{Finish the discussion.}
-
 2FGL reported on the detection of twelve spatially extended sources. Using
@@
 of LAT detected extended sources and of all sources in 2FGL. This, and
-table~\label{known_extended_sources} and~\label{new_ext_srcs_table},
+table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
 show that the LAT observes a population of hard (index $<2$)
@@
 the LAT will likely begin to resolving these smaller \tev sources.
-
-Furthermore, our sensitivity to these extended sources will likely improve
-faster than $\sqrt{t}$ because at the highest energies, our background is
-relatively small and we are in the Poisson instead of Gaussian limit.
-Future improvements in the diffuse emission model will improve our
-sensitivity by allowing this analysis to go to lower energies.
+As figure~\ref{time_sensitivity} showed, our sensitivity to these smaller
+sources will actually improve faster than $\sqrt{t}$.
 
@@
     source of the same spectrum and intensity.  The PSF is smoothed
-    by the same kernel.  Plots (a), (c), and (d) use only photons with
-    energies between 1 \gev and 100 \gev. Plots (c) and (d)
+    by the same kernel.  Plots (a), (c), and (d) use only 1-100 \gev photons. 
+    Plots (c) and (d)
     use only photons which converted in the front
@@
     show the convolution of the Gaussian and uniform disk with the PSF.
-    Plot (a) shows the analysis in the energy range from 1 \gev to 100
-    \gev while plot (b) shows the analysis only in the energy range
-    from 10 \gev to 100 \gev. This plot demonstrates that different
+    Plot (a) uses a 1-100 \gev energy range while plot (b)
+    uses a 10-100 \gev enregy range. This plot demonstrates that different
     spatial models when smoothed by the PSF look similar.  The $y$
@@
     using photons with energy between 100 \mev and 100 \gev while the
-    dashed line is the threshold using photons with energy between 1 \gev
-    and 100 \gev.  The detection threshold is for the same two year time
+    dashed line is the threshold using 1-100 \gev photons. The detection threshold is for the same two year time
     range as was used in 2FGL and in the following extended source search.
@@
     of the Galactic diffuse emission near the Galactic center.  Plot (a)
-    is the threshold using photons with energies between 1 \gev and 100
-    \gev while plot (b) is the threshold using photons with energies
-    between 10 \gev and 100 \gev. Unlike figure~\ref{index_sensitivity},
+    is the threshold using 1-100\gev photons while plot (b) is the threshold using
+    10-100\gev photons. Unlike figure~\ref{index_sensitivity},
     the detection threshold was calculated only for a power-law source of spectral
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics{mc_plots/time_sensitivity.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
+    \end{center}
+    \caption{
+    This plot shows our projected sensitivity to extension after 10 years
+    of operation for an assumed power-law source of spectral index
+    2 against a representative 10 times the isotropic background in the
+    energy range from 1-100 \gev (solid red) and 10-100 \gev (dashed
+    blue). Flux is quoted in this energy range and the gray region is
+    the projected sensitivity assuming that our sensitivity improves
+    with $\sqrt{\text{t}}$ (top edge) and linearly with time (bottom
+    edge). For small extended sources, our sensitivity to the extension
+    of a source actually improves better than $\sqrt{\text{t}}$
+    because at the highest energies, where we are most sensitive to the
+    extension of a source, the relevant background near the sources is in
+    the Poisson instead of Gaussian regime.  For large extended sources,
+    the relevant background is over a larger area and our gain
+    in sensitivity is closer to $\sqrt{\text{t}}$.  This effect is
+    even more pronounced for sources hard only above 10 \gev.
+    }\label{time_sensitivity}
+  \end{figure}
+
 \clearpage
@@
     \caption{
-    The observed 1 \gev to 100 \gev photons for the two year catalog
-    source 2FGL\,J1856.2+0450c. This map is smoothed by a 0.1\deg Gaussian
-    kernel and the red cross and circle are the center and size of the
+    A Galactic and isotropic diffuse subtracted 1-100 \gev counts map of
+    the region around 2FGL\,J1856.2+0450c smoothed by a 0.1\deg Gaussian
+    kernel. The red cross and circle are the center and size of the
     best fit uniform disk spatial model. The result is statistically
@@
   \caption{An example residual test statistic map generated for the
-  supernova remnant IC443 using photons with energy between 1 \gev
-  and 100 \gev. Plot (a) is the residual \ts fitting IC443 as a point
+  supernova remnant IC443 using 1-100 \gev photons. 
+  Plot (a) is the residual \ts fitting IC443 as a point
   source and plot (b) is the residual TS fitting IC443 as an extended
@@
       \caption{The twelve extended sources included in 2FGL.  The top
-      list are the extended sources analyzed using photons with energies
-      between 1 \gev and 100 \gev.  The lower table are the sources
-      analyzed using photons with energies between 10 \gev and 100 \gev.
+      list are the extended sources analyzed using 1-100 \gev photons.  
+      The lower table are the sources
+      analyzed using 10-100 \gev photons.
       The quoted flux is in units of $10^{-9}\ph/\cm^2/\sec$ and is the
@@
       than two point sources.  As in table~\ref{known_extended_sources},
-      flux is measured in units of $10^{-9}\ph/\cm^2/\sec$ and is the
-      integral flux between 1 \gev (10 \gev) and 100 \gev for the sources
-      found using photons above 1 \gev (10 \gev).}
+      flux is measured in units of $10^{-9}\ph/\cm^2/\sec$ and is either
+      the 1-100 \gev or 10-100 \gev photon flux.
+      }
     \end{centering}
@@
   cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
-  The grey crosses represent from left to right the position of source B
+  The gray crosses represent from left to right the position of source B
   and C which were added to the background model. More information about
@@
   away green stars represent other catalog sources which were removed
-  because they were not significant above 10 \gev.  The grey cross is
+  because they were not significant above 10 \gev.  The gray cross is
   the position a source not in the two year catalog which was added
@@
     as in figure~\ref{index_sensitivity} The left plots are the detection
-    threshold when using the photons with energies between 1 \gev and
-    100 \gev and the right plots are the detection threshold when using
-    photons with energies between 10 \gev and 100 \gev.  This plot shows
+    threshold when using 1-100 \gev photons and the right plots are the detection threshold when using
+    10-100 \gev photons.  This plot shows
     that when using only high energy photons with an improved angular

### 2011-08-11 extended_catalog/paper/extended_catalog.tex
stuff

@@
 \begin{equation}
-  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') d A'.
+  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r'^2 dr' d\phi'
 \end{equation}
@@
 \begin{equation}
-  \text{PSF}(\vec r) = 
+  \text{PSF}(r) = 
   \frac{1}{2\pi\sigma^2}
@@
 \end{equation}
-where $\sigma$ and $\gamma$ are free parameters
+where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
 (\cite{matthew_kerr_thesis}).  For radially symmetric extended sources,
@@
 \begin{align}
-  \text{PDF}(u) & = \int_0^\infty \sigma^2 dv 
+  \text{PDF}(u) & = \int_0^\infty r'^2 dr'
   I_\text{src}(v) 
@@
 \end{align}
-where $u=(r/\sigma)^2/2$, $v=(r'/\sigma)^2/2$, and ${}_2F_1$ is the
-Gaussian hypergeometric function.  This convolution formula is used by
-\pointlike, reducing the calculation of the expected photon distribution
-to a single numerical integral.
+where $v=(r'/\sigma)^2/2$ and ${}_2F_1$ is the Gaussian hypergeometric
+function.  This convolution formula reduces the expected photon
+distribution to a single numerical integral.
 
@@
 
-We found good agreement between the two methods. For the new extended
-source candidates, table~\ref{alt_diff_model_results} shows a
-comparison of the test statistic \ts and \tsext computed using \pointlike
-and \gtlike.  Unless explicitly mentioned, all \ts, \tsext, and spectral
+We found good agreement between the two methods.  
+Unless explicitly mentioned, all \ts, \tsext, and spectral
 parameters were calculated using \gtlike using \pointlike's positions
@@
 extended if $\tsext>\tsinc$.
-
 Like extended sources described in section~\ref{gtlike_crosscheck},
@@
 We quote the spectral values obtained from \gtlike using the best fit
-positions found using \pointlike.  For the extended candidates found
-by our search, we computed both \tsext and \tsinc.  The results are
-presented in table~\ref{dual_localization_results}.
+positions found using \pointlike.
 
@@
 demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
-a uniform disk and Gaussian spatial model of size 0.5\deg.\footnote{To
+a radially symmetric uniform and Gaussian surface brightness of size 0.5\deg.\footnote{To
 allow a valid comparison between Gaussian and disk shaped morphologies,
@@
 section~\ref{monte_carlo_validation}, but instead simulated extended
-sources with a uniform radially symmetric disk spatial model and
+sources with a radially symmetric uniform surface
+brightness and
 instead over the actual two year time interval.  For each extension and
@@
 \section{Extended Source Search Method}
+\label{extended_source_search_method}
 
@@
 We only considered a source to be significantly extended if $\tsext>16$ with
-both \pointlike and \gtlike.  For the new extended source candidates,
-table~\ref{alt_diff_model_results} shows a comparison of of \tsext for
-\gtlike and \pointlike.
+both \pointlike and \gtlike.
 
@@
 references} model used in the LAT analysis of the isotropic diffuse
-emission (\cite{isotropic_lat}).  With this model, we independently fit
-along with the point and diffuse sources in the region seven HI rings,
-seven HII rings, the inverse component, the E(B-V) residual, and the
-isotropic component of the background emission.  All told, we fit in
-the region 18 diffuse templates.  This same crosscheck was used in the
+emission (\cite{isotropic_lat}).  
+The intensities of various contributions to the galactic
+diffuse emission are then fitted individually using a spatial
+distribution of the intensities within the ROI 
+as predicted by the model.
+We distinguish contributions from CR interactions with
+the molecular hydrogen, the atomic+ionized hydrogen,
+residual gas traced by dust (\cite{isabelle_dark_gass}),
+and the interstellar radiation field. We further
+split the contributions from interactions with molecular
+and atomic hydrogen to the
+Galactic diffuse emission according
+to the distance from the Galactic center in
+which they are produced. Hence, we replace
+the standard diffuse emission model by 18
+individually fitted templates to describe individual
+components of the diffuse emission.
+A similar crosscheck was used in the
 LAT Collaboration's analysis of RX J1713.7-3946 (\cite{rx_j1713_lat}).
 
-It is not expected that this diffuse model is more physical.
-But adding degrees of freedom to the background model can remove
-likely spurious sources that correlate with features in the Galactic
-diffuse emission.  Therefore, this tests systematics that may be
-due to incorrect modeling of the diffuse emission in the region.
-The results of this fit for the new extended source candidates are shown
-in table~\ref{alt_diff_model_results}. There is good agreement between
-the \ts using the standard and alternative diffuse models, suggesting
-that the sources are robust against features in the diffuse model.
+It is not expected that this diffuse model is superior to the standard
+LAT model.  But adding degrees of freedom to the background model can
+remove likely spurious sources that correlate with features in the
+Galactic diffuse emission.  Therefore, this tests systematics that may
+be due to incorrect modeling of the diffuse emission in the region.
 
@@
 nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
-source.  To avoid the nearby pulsar PSR J1509-5850, MSH 15-52 must be
+source.  To avoid confusion with the nearby bright pulsar PSR J1509-5850, MSH 15-52 must be
 analyzed at high energies.  Using photons with energies above 10 \gev,
@@
 extension for the Centaurus A Lobes (\cite{cen_a_lat}). This is because
-the source's emission is significantly more complicated than a uniform
+the source's emission is significantly different from a uniform
 radially symmetric Disk.
@@
 table~\ref{known_extended_sources}.  This table includes the best fit
-position and extension of these sources when fitting them with a radially
-symmetric uniform disk spatial model.  It also includes the best fit
-spectral parameters for each source.  The position and extension of Vela
-X and the Centaurus A Lobes are included in this list for completeness.
-
-\section{Test of 1LAC Sources}
-\label{test_1lac_sources}
-
-To validate our method, we test associated AGN for extension.  \gev
-emission from AGN is believed to comes from the core of supermassive
-blackholes in small regions in the core of distant galaxies. Therefore AGN
-are not expected to be spatially resolvable and provide a good calibration
-source to demonstrate the efficacy of our tool. Nevertheless, it would
-be interesting if AGN could be spatially resolved and there are theories
-that predict this (\cite{pair_halo_paper}).
-
-Following 1FGL, the LAT collaboration published a list of sources that
+position and extension of these sources when fitting them as disk-shaped
+sources with a radially symmetric uniform surface brightness. It also
+includes the best fit spectral parameters for each source.  The position
+and extension of Vela X and the Centaurus A Lobes are included in this
+list for completeness.
+
+\section{Test of 2LAC Sources}
+\label{test_2lac_sources}
+
+To validate our method, we test LAT sources associated with AGN for
+extension.  \gev emission from AGN is believed to originate from the cores
+of kpc-scale jets of distant galaxies.  Therefore AGN are not expected
+to be spatially resolvable and provide a good calibration source to
+demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
+halos around AGNs have been hypothesized (\cite{pair_halo_paper}) which
+could be resolved by the LAT However, no such halo has been discovered
+in the LAT data so far.
+
+Following 1FGL, the LAT collaboration published a list called 1LAC
+of sources that
 had a high probability association with AGN (\cite{first_agn_cat}).
@@
 latitude ($|b|>10\deg$).  An upcoming publication by the LAT collaboration
-using two years of data and the 2FGL catalog associates 1017 2FGL sources
+will produce a second list 2LAC. 2LAC 
+uses the 2FGL catalog and associates 1017 2FGL sources
 with AGN.  To avoid systematic problems with AGN classification, we
-selected the 815 AGN which made it into the clean AGN sample.  An AGN
+selected 815 out of the 1017 AGN which made it into the clean AGN sub-sample.  An AGN
 association is considered clean only if it has a high probability
@@
 are significant above 1 \gev and fit each of them for extension.
-A histogram of the \tsext values computed for these AGN is shown in
-figure~\ref{agn_ts_ext}. Overlaid on the plot is the $\chi^2/2$
-distribution of equation~\ref{ts_ext_distribution}.
-The \tsext distribution for AGN shows good
-agreement with the theoretical distribution.  Two sources had $\tsext>9$.
-One was due to incorrectly pruning a nearby catalog sources and the
-other was due to a failure of convergence of the point hypothesis.
-This result demonstrates that we can use \tsext as a measure of the
-statistical significance of the detection of the extension of a source.
+A histogram of the \tsext values computed for these AGN is
+shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is the
+$\chi^2/2$ distribution of equation~\ref{ts_ext_distribution}.
+The \tsext distribution for AGN shows good agreement with the
+theoretical distribution.  Two sources had $\tsext>9$.  One was due
+to incorrectly automatically removing a nearby catalog sources (see
+section~\ref{extended_source_search_method}) and the other was due to a
+failure of convergence of the point hypothesis.  This result demonstrates
+that we can use \tsext as a measure of the statistical significance of
+the detection of the extension of a source.
 
@@
 section~\ref{systematic_errors_on_extension}). Finding that the AGN we
-test are not extended is not surprising. Trying to look for the extension
-of AGN would require a more specialized analysis.
+test are not extended is not surprising.  This validation analysis is
+not suitable to reject any hypotheses about the existence of mpc-scale
+halos around AGN.
 
@@
 
-Nine extended sources not include in 2FGL were found using this search.
-Three were found in our search using 1-100 \gev photons and 
-six were found in our search using 10-100 \gev photons.  
-The fit properties of these nine sources is summarized in
-table~\ref{new_ext_srcs_table}.  This table includes for each source
-the best fit position, extension, spectrum, source significance, and
-significance of extension.
-
-For the new extended sources, table~\ref{dual_localization_results}
-presents a test for source confusion by fitting the region
-as two point sources. The table compares \tsext to \tsinc and
-summarizes the positions and spectra of the two sources. 
-Table~\ref{alt_diff_model_results} contains the fit extensions
-using the alternate PSF and Galactic diffuse model described in
-section~\ref{systematic_errors_on_extension}.
+Nine extended sources not included in 2FGL were found using this search.
+Three were found in our search using 1-100 \gev photons and six were
+found in our search using 10-100 \gev photons.  The fit properties of
+these nine sources is summarized in table~\ref{new_ext_srcs_table}.
+This table includes for each source the best fit position, extension,
+spectrum, source significance, and significance of extension.
+
+The results of our investigation of systematic uncertainties of this
+measurement are presented in table~\ref{dual_localization_results}
+and~\ref{alt_diff_model_results}.  Table~\ref{dual_localization_results}
+shows a comparison between the fit with a single extended source
+hypothesis and the fit assuming the emission originates from two
+independent sources.  Table~\ref{alt_diff_model_results} shows the
+results of the extension fit using variations of the PSF and the galactic
+diffuse model described in section~\ref{systematic_errors_on_extension}.
+There is good agreement between \tsext and the fit size using
+the standard analysis, the alternative diffuse models, and the alternative PSF.
+This suggests that the sources are robust against features in the diffuse
+model and uncertainties in the angular resolution.
 
@@
 
-The two year catalog source 2FGL\,J0823.0-4246 was found 
+The source 2FGL\,J0823.0-4246 was found 
 using 1-100 \gev photons to have an 
-extension of $0.37\deg\pm0.03\deg\stat\pm0.02\deg\sys$ 
+extension of $0.37\deg\pm0.03\deg_\stat\pm0.02\deg_\sys$ 
 with an extension
@@
 
-The two year catalog source 2FGL\,J1627.0-2425c was found 
+The source 2FGL\,J1627.0-2425c was found 
 using 1-100 \gev photons to have an 
-extension of $0.41\deg\pm0.05\deg\stat\pm0.02\deg\sys$ 
+extension of $0.41\deg\pm0.05\deg_\stat\pm0.02\deg_\sys$ 
 with an extension significance of $\tsext=31.1$. 
@@
 
-The two year catalog source 2FGL\,J1712.4-3941 was found using 1-100 \gev
-photons to have an extnesion $0.56\deg\pm0.04\deg\stat\pm0.02\deg\sys$
+The source 2FGL\,J1712.4-3941 was found using 1-100 \gev
+photons to have an extension $0.56\deg\pm0.04\deg_\stat\pm0.02\deg_\sys$
 with an extension significance of $\tsext=39.6$.  This source was
@@
 
-The two year catalog source 2FGL\,J0851.7-4635 was found 
+The source 2FGL\,J0851.7-4635 was found 
 using 10-100 \gev photons to have an
-extension of $1.13\deg\pm0.08\deg\stat\pm0.05\deg\sys$ 
+extension of $1.13\deg\pm0.08\deg_\stat\pm0.05\deg_\sys$ 
 with an extension
@@
 the region, we found that \tsinc=16.1 which is less than \tsext so we
-conclude that the source is extended These modifications are shown in
-figure~\ref{Vela_Jr}.
+conclude that the source is extended.
 
@@
 
-The two year catalog source 2FGL\,J1615.0-5051 was found using 10-100 \tev
-photons to have an extension of $0.33\deg\pm0.04\deg\stat\pm0.01\deg\sys$
+The source 2FGL\,J1615.0-5051 was found using 10-100 \tev
+photons to have an extension of $0.33\deg\pm0.04\deg_\stat\pm0.01\deg_\sys$
 with an extension significance of \tsext=16.3.  The source
@@
 extension $0.136\pm 0.008$ when fitting the source with an elliptical
-Gaussian spatial model.  This size corresponds to a 68\% containment
+Gaussian surface brightness.  This size corresponds to a 68\% containment
 radius of $\rsixeight=0.21\deg\pm0.01\deg$. This size is comparable to the LAT
@@
 
-The two year catalog source 2FGL\,J1615.2-5138 was found using 10-100 \gev
-photons to have an extension of $0.42\deg\pm0.03\deg\stat\pm0.01\sys$
+The source 2FGL\,J1615.2-5138 was found using 10-100 \gev
+photons to have an extension of $0.42\deg\pm0.03\deg_\stat\pm0.01_\sys$
 with an extension significance of \tsext=48.0.  The source was fit to a
@@
 
-The two year catalog source 2FGL\,J1632.4-4753c was found 
+The source 2FGL\,J1632.4-4753c was found 
 using 10-100 \gev photons to
-have an extension of $0.44\deg\pm0.04\deg\stat\pm0.03\deg\sys$ 
+have an extension of $0.44\deg\pm0.04\deg_\stat\pm0.03\deg_\sys$ 
 with an extension
@@
 $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
-axes when fitting the source with an elliptical Gaussian spatial model.
+axes when fitting the source with an elliptical Gaussian surface 
+brightness.
 This corresponds to a 68\% containment size $\rsixeight=0.31\deg\pm0.08\deg$
@@
 connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478 and most
-likely corresponds to the same emission process
+likely corresponds to the same emission process.
 
@@
 
-The two year catalog source 2FGL\,J1837.3-0700c was found 
+The source 2FGL\,J1837.3-0700c was found 
 with 10-100 \gev photons 
 to have an extension
-of $0.35\deg\pm0.08\deg\stat\pm0.03\deg\sys$ 
+of $0.35\deg\pm0.08\deg_\stat\pm0.03\deg_\sys$ 
 with an extension
@@
 semi-minor axis when fitting the source with an elliptical Gaussian
-spatial model.  This corresponds to a 68\% containment radius of
+surface brightness.  This corresponds to a 68\% containment radius of
 $\rsixeight=0.18\deg\pm0.03\deg$ and $0.08\deg\pm0.03\deg$ along the semi-major
@@
 
-The two year catalog source 2FGL\,J2021.5+4026 was found with 10-100 \gev
-photons to have an extension of $0.59\deg\pm0.03\deg\stat\pm0.02\deg\sys$
+The source 2FGL\,J2021.5+4026 was found with 10-100 \gev
+photons to have an extension of $0.59\deg\pm0.03\deg_\stat\pm0.02\deg_\sys$
 with an extension significance of $\tsext=116.4$.  The source was
@@
 would require a more careful analysis of the LAT data using the same 
-elliptical spatial model.
+elliptical surface brightness model.
 
@@
     uses a 10-100 \gev enregy range. This plot demonstrates that different
-    spatial models when smoothed by the PSF look similar.  The $y$
+    surface brightness models when smoothed by the PSF look similar.  The $y$
     axis is the log of the intensity and the $x$ axis is $\theta^2$.
@@
     kernel. The red cross and circle are the center and size of the
-    best fit uniform disk spatial model. The result is statistically
+    best fit radially symmetric uniform surface brightness extension
+    model. The result is statistically
     significant, but the extension encompasses many catalog sources and
@@
       TS and spectral values were calculated using \gtlike.  \ts and
-      \tsext was computed with \gtlike assuming the best fit uniform
-      disk spatial model from \pointlike.  \glon and \glat are Galactic
+      \tsext was computed with \gtlike assuming the best fit radially
+      symmetric uniform surface brightness from \pointlike.  \glon and \glat are Galactic
       longitude and latitude of the best fit extended source respectively.
-      $\sigma$ is the edge of the best fit uniform disk spatial model.
+      $\sigma$ is the edge of the best fit radially
+      symmetric uniform surface brightness model.
       The first error on $\sigma$ is statistical and the second error
@@
       errors are at the $1\sigma$ level.  The Vela X and the Centarus A
-      Lobes were not fit by our anaysis but are include for completeness
+      Lobes were not fit by our analysis but are include for completeness
       (\cite{velax,cen_a_lat}). More information about these sources is
@@
     test conservative. More information about this analysis is presented
-    in section~\ref{test_1lac_sources}.
+    in section~\ref{test_2lac_sources}.
     }\label{agn_ts_ext}
@@
       \end{tabular}
-      \label{dual_localization_results}
       \caption{For the new extended source candidates
@@
       }
+      \label{dual_localization_results}
     \end{centering}
@@
   The red cross and circle are the best fit position
-  and extension of this source assuming a uniform disk spatial model.
+  and extension of this source assuming a radially
+  symmetric uniform surface brightness.
   The two green stars are the positions of the sources 2FGL\,J0823.4-4305
@@
   The red cross and circle are the best position and extension of
-  this source assuming a uniform disk spatial model.  The light
+  this source assuming a radially
+  symmetric uniform surface brightness.  The light
   blue contours are from a 100 micrometer infrared image of the region
@@
   and circle are the best fit position and extension of the source
-  assuming a uniform disk spatial model.  The inner three green stars
+  assuming a radially
+  symmetric uniform surface brightness.  The inner three green stars
   are (from left to right) 2FGL\,J0853.5-4711, 2FGL\,J0855.4-4625,
@@
     sources.  The red stars and circles are the best fit positions and
-    extensions of these sources assuming uniform disk spatial models.
+    extensions of these sources 
+    assuming a radially
+    symmetric uniform surface brightness.
     The green star inside the extension of 2FGL\,J1615.2-5138  is
@@
   The red star is the catalog position of this source.  The red
-  cross and circle are the best fit position and extension 2FGL
-  J1632.4-4753c assuming a uniform disk spatial model.  The three
+  cross and circle are the best fit position and extension 2FGL\,J1632.4-4753c 
+  assuming a radially
+  symmetric uniform surface brightness.
+  The three
   green crosses inside the extension are 2FGL
@@
   star is the catalog position of this source. The red cross and circle
-  are the best fit position and extension  of 2FGL\,J1837.3-0700c assuming
-  a uniform disk spatial model.  The blue stars and crosses are the
+  are the best fit position and extension  of 2FGL\,J1837.3-0700c 
+  assuming a radially
+  symmetric uniform surface brightness. The blue stars and crosses are the
   catalog position and the relocalized position of (from left to right)
@@
   J2021.5+4026.  The red cross and circle are the best fit position and
-  extension 2FGL\,J2021.5+4026 assuming a uniform disk spatial model.
+  extension 2FGL\,J2021.5+4026 
+  assuming a radially
+  symmetric uniform surface brightness. 
   The green cross inside the extension is 2FGL\,J2019.1+4040 which
@@
     The LAT extension of Vela X is from (\cite{velax}).  Except for RX
-    J1713.7-3946 Vela Jr., the \tev sources were fit with a Gaussian
-    spatial model so the plotted \gev and \tev extensions were first
+    J1713.7-3946 Vela Jr., the \tev sources were fit assuming a Gaussian
+    surface brightness so the plotted \gev and \tev extensions were first
     converted to \rsixeight (see section~\ref{compare_source_size}).
@@
     Except for RX J1713.7-3946 and Vela Jr.,
-    the H.E.S.S. sources were fit with a Gaussian spatial model and
+    the H.E.S.S. sources were fit with a Gaussian surface
+    brightness model and
     so the LAT and H.E.S.S. sizes are first converted to \rsixeight.
@@
     morphology of RX J1713.7-3946 and Vela Jr. is poorly matched by a
-    Gaussian, the \tev sizes are assuming a uniform disk spatial model
-    and so neither the \gev nor \tev sizes were converted.  This plot
+    Gaussian surface brightness model, so the \tev sizes 
+    were found assuming a uniform surface brightness. Here,
+    neither the \gev nor \tev sizes were converted.  This plot
     shows that \tev experiments are sensitive to smaller extended sources.
@@
     The distribution of spectral indices of all 1873 2FGL sources in
-    red and all spatially extended sources in blue.  in 2FGL. The
+    red and all spatially extended sources in blue. The
     spectral indices of LAT extended sources are taken from
@@
       was scaled by. The remaining columns are varying sizes of the
-      source's spatial model. The table quotes fluxes in units of
+      source assuming a uniform surface brightness. The table quotes fluxes in units of
       $10^{-10} \ph/\cm^2/\sec$.  These values are also plotted in

### 2011-08-12 extended_catalog/paper/extended_catalog.tex
better table

@@
 \newcommand{\loglikelihood}{\ensuremath{LL}\xspace}
+\newcommand{\chandra}{\text{{\em Chandra}}\xspace}
 
@@
 sources in our Galaxy should be spatially resolvable at \gev energies.
+
+\todo[inline]{add note about how high energy emission may be hadron,
+and the origin of cosmic rays}
 
@@
 We tested two different models for the
-spatial shape, either a two dimensional Gaussian
+surface brightness profile, either a two dimensional Gaussian
 \begin{equation}\label{gauss_pdf}
@@
 demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
-a radially symmetric uniform and Gaussian surface brightness of size 0.5\deg.\footnote{To
+a radially symmetric uniform brightness and the Gaussian surface brightness of size 0.5\deg.\footnote{To
 allow a valid comparison between Gaussian and disk shaped morphologies,
@@
 We simulated point sources of varying spectral models using
-\gtobssim\footnote{\gtobssim is distributed
-by the Fermi Science Support Center (\cite{fssc}).}
-and fit them
-them using \pointlike as both point and extended sources. 
-The point sources were simulated with a power-law spectral model 
-with integrated fluxes above 100 \mev ranging from
-$3\times 10^{-9}$ to $10^{-6} \ph/\cm^2/\sec$ in
-six discrete steps and spectral
-indices ranging from 1.5 to 3 in four discrete steps.
-These values were picked to
-to represent typical source parameters in LAT-detected sources. The point
-sources were simulated on top of an isotropic 
+\gtobssim\footnote{\gtobssim is distributed by the Fermi Science Support
+Center (\cite{fssc}).} and fit them them using \pointlike as both point
+and extended sources.  The point sources were simulated with a power-law
+spectral model with integrated fluxes above 100 \mev ranging from $3\times
+10^{-9}$ to $10^{-6} \ph/\cm^2/\sec$ in six discrete steps and spectral
+indices ranging from 1.5 to 3 in four discrete steps.  These values
+were picked to to represent typical source parameters in LAT-detected
+sources. The point sources were simulated on top of an isotropic
 background with an integrated flux above 100 \mev of $1.5\times10^{-5}$
-(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
-performed over a one year observation period
-using a default rocking profile
-and a representative livetime fraction of 0.8.  The reconstruction was
-performed using 1-100 \gev photons 
-and the 
-Pass 7\_V6 (P7\_V6) Source Instrument
+(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was performed
+over a one year observation period using a default rocking profile and a
+representative livetime fraction of 0.8.  The reconstruction was performed
+using 1-100 \gev photons and the Pass 7\_V6 (P7\_V6) Source Instrument
 Response Function (IRFs).  For each point source, we used \pointlike
@@
 fit extension is comparable to the published result, but we note that
-previous publication used a more complicated double Gaussian spatial
-model when fitting the LMC.
+previous publication used a more complicated two Gaussian surface
+brightness spatial model when fitting the LMC.
 
@@
 the source's emission is significantly different from a uniform
-radially symmetric Disk.
+radially symmetric surface brightness.
 
@@
 and HI but also plenty of dark gas, the kind that we find only by its
-association with dust emission. Embedded star-forming regions make it even
-more challenging to measure the column density of dust.  Although this
-region is significantly extended, we conclude that this source most
-likely represents inadequacy in the diffuse $\gamma$-ray emission model.
-
-\todo[inline]{Can we get another citation about dark gas and stuff?
-And a better description of spectral index being typical of diffuse emission.
-Stefan says that Markus should write this section.
-He also says we should cite (\cite{isabelle_dark_gass}).  
-}
+association with dust emission (\cite{isabelle_dark_gass}). Embedded
+star-forming regions make it even more challenging to measure the column
+density of dust.  Therefore this source might represent an inadequacy
+in the diffuse $\gamma$-ray model
 
@@
 figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
-on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured a Gaussian
+on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured an
 extension $0.136\pm 0.008$ when fitting the source with an elliptical
@@
 
-HESS\,J1616-508 is located in the region of two SNRs, RCW103 (G332.4-04)
-and Kes 32 (G332.4+0.1) but is not spatially coincident with either
-of them.  HESS\,J1616-508 is near three pulsars near PSR J1614-5048,
-PSR J1616-5109, and PSR J1617-5055 but only PSR J1617-5055 only
-PSR J1617-5055 is energetically favored as being the \tev emitter
-(\cite{integral_HESS_J1616-508}).  \cite{hess_plane_survey}
-speculated that this young pulsar could be responsible for the
-emission of HESS\,J1616-508.  HESS\,J1616-508 is 9' away from PSR
-J1617-5055, which was discovered during ASCA observations of RCW 103
-(\cite{discovery_of_PSR_J1617-5055}). Using an outer gap magnetospheric
-pulsar model, it was previously predicted to be a \tev emitter
-(\cite{pulsar_tev_emission_predictions}).
-
-The pulsar's position is offset from the maximum of the H.E.S.S
-emission and would require an asymetric PWNe to power the \tev
-emission. Offset PWN are expected on theoretical grounds due
-to the PWNe being crushed by an asymmetric SNR reverse shock
-(\cite{offset_pwn_ahronian,offset_pwn_blondin}) but this makes a
-possible association more difficult.  For HESS\,J1825-137, the X-ray
-emission is directed along the \tev offset making this association more
-compelling.\cite{hess_j1825_hess}.
-
-In the region around HESS\,J1616-508, Suzaku found only an upper limit
-in the 2-10 \kev energy range and suggested this source as an example
-of a ``dark particle accelerator'' (\cite{suzakzu_HESS_J1616-508}).
-\cite{integral_HESS_J1616-508} found no evidence of hard X-ray emission
-in the region of HESS\,J1616-508 in the 20-100 \kev energy band with the
-IBIS/ISGRBI on board INTEGRAL. They also observed the field with the XRT
-on board {\em Swift} between 0.2-10 \kev and found no compelling source
-counterpart. Using archival XMM-Newton and BeppoSAX data, they found no
-plausible X-ray counterpart except for PSR J1617-5055.
-
-Finally, Chandra ACIS observations of PSR J1617-5055 revealed
-an underlomonous PWN $\approx1'$ in size around the pulsar
-(\cite{discovery_of_pwn_for_PSR_J1617-5055}). But the PWN is not
-assymetric towards HESS\,J1616-508 which casts doubt upon the association.
-
-\todo[inline]{
-Note about how it is difficult to explain the TeV to X-ray emission
-ratio b/c of magnetic field. Refernece in page 7 of (sukazu paper on HESS J1614-518, but
-it also refers to (Matsumoto et. al 2007 and says this requires small b/field with strong
-cutoff in eletron energy). Also some not eabout different photon fields
-being possible.}
-
-\todo[inline]{
-Note about this this paper finds other stuff: (\cite{discovery_of_pwn_for_PSR_J1617-5055}).
-}
-
-\todo[inline]{
-The \gev emission is suggested to be the same emission component as
-the \tev emission, but further observations of this source at other
-frequencies will likely be needed to firmly associated this source.
-}
-
-\todo[inline]{Finish interpretations of HESS\,J1616-508.}
+HESS\,J1616-508 is located in the region of two SNRs, RCW103
+(G332.4-04) and Kes 32 (G332.4+0.1) but is not spatially coincident
+with either of them (\cite{hess_plane_survey}).  HESS\,J1616-508 is near
+three pulsars PSR J1614-5048, PSR J1616-5109, and PSR J1617-5055
+but only PSR J1617-5055 is energetically favored as being the \tev
+emitter (\cite{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}).
+\cite{hess_plane_survey} speculated that a PWN powered by this young
+pulsar could be responsible for the emission of HESS\,J1616-508.
+Because HESS\,J1616-508 is 9' away from PSR J1617-5055, this would
+require an assymetric X-ray PWNe to power the \tev emission. However,
+\chandra ACIS observations revealed only an underluminous PWN of
+about $\approx1'$ size around the pulsar which was not oriented
+towards the \tev emission, rendering this association as uncertain
+\cite{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
+counterparts were observed in observations of x-ray and soft gamma-ray
+emission by Suzaku (\cite{suzakzu_HESS_J1616-508}), Swift/XRT,
+IBIS/ISGRBI, BeppoSAX and XMM-Newton (\cite{integral_HESS_J1616-508}).
+Finally, \cite{discovery_of_pwn_for_PSR_J1617-5055} found diffuse
+emission towards the center of HESS\,J1616-508 using archival radio and
+infared observations.  Deeper observations will likely be necessary to
+understand this region.
 
@@
 and $0.23\pm0.03$.  This elliptical size matches the LAT size
-$\rsixeight=0.35\deg\pm0.03\deg$.  Figure~\ref{hess_seds} shows that
-the LAT spectrum of 2FGL\,J1615.2-5138 connects smoothly to the H.E.S.S
-spectrum of HESS\,J1614-518.  Further data collected by H.E.S.S. in 2007
-helped to resolve a double peaked structure in the H.E.S.S. data but no
-spectral variation across the source, suggesting that the emission is
-not the confusion of physically separate sources (\cite{closer_look_hess_j1614-518}).
-The source was also detected by CANGAROO-III (\cite{cangaroo_j1614-518}).
-
-This source is currently unidentifed. There are five nearby pulsars,
-but note are luminous enough to provide the required energy output
-to power the \tev emission (\cite{closer_look_hess_j1614-518}).
-
-HESS J1614-518 is spatially coincident with a young open cluster Pismis
+$\rsixeight=0.35\deg\pm0.03\deg$.  Figure~\ref{hess_seds} shows
+that the LAT spectrum of 2FGL\,J1615.2-5138 connects smoothly to
+the H.E.S.S spectrum of HESS\,J1614-518.  Further data collected by
+H.E.S.S. in 2007 helped to resolve a double peaked structure in the
+H.E.S.S. data but no spectral variation across the source, suggesting
+that the emission is not the confusion of physically separate sources
+(\cite{closer_look_hess_j1614-518}).  The source was also detected by
+CANGAROO-III (\cite{cangaroo_j1614-518}).
+
+There are five nearby pulsars, but none are luminous enough to
+provide the required energy output to power the \gev and \tev emission
+(\cite{closer_look_hess_j1614-518}).
+
+HESS\,J1614-518 is spatially coincident with a young open cluster Pismis
 22 (\cite{hess_1614_landi_atel,closer_look_hess_j1614-518}).
-\gev and \tev emission could arrise from
+\gev and \tev emission could arise from
 hadronic acceleration in the winds of massive stars
@@
 This extended source is spatially coincident with the extended
-\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).  In
-figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478 are
-overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a Gaussian extension of
-$\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
-axes when fitting the source with an elliptical Gaussian surface 
-brightness.
-This corresponds to a 68\% containment size $\rsixeight=0.31\deg\pm0.08\deg$
-and $0.09\pm0.06$ along the semi-major and semi-minor axis. This
-size is consistent with the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.
-Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1635.4-4717c
-connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478 and most
-likely corresponds to the same emission process.
-
-\cite{hess_plane_survey} argued that this source is positionally
-coincident with the hard X-ray source IGR\,J1632-4751 discovered above
-15 \kev by the INTEGRAL satellite (\cite{Igr_J16320-4751_circ}).
-It was also observed by XMM-Newton between 2 and 10 \kev
-(\cite{xmm_newton_IGR_J16320-4751}) and ASCI between 0.7 and 10 \kev
-(\cite{asca_plane_survey}).  But this X-ray source is suspected to be
-an galactic X-Ray Binary so the \gev and \tev extension HESS\,J1632-478
-and 2FGL\,J1632.4-4753c disfavors the association.
-
-Further observations of the region around HESS\,J1632-478 by XMM-Newton
-reveal extended emission between 0.2 \kev and 15 \kev with an elliptical
-size of $\approx32''$ and $\approx15''$ in the semi-major and semi-minor
-axes and inside this extended emission was point-like emission
-(\cite{hess_j1632_478_xmm_newton}).  This x-ray source is positionally
-coincident with the \tev centroid of the H.E.S.S source.  In addition,
-they used data from MGPS-2, an 843 MHz survey of the galactic plane
-carried out with the Molonglo Observatory Synthesis Telescope (MOST)
-to detect an extended diffuse radio source whose size matches well the
-extended X-ray emission \cite{most_survey_galactic_plane}.
-
-They argued that the positional match between the radio and X-ray
-observations argues for a single synchrotron processes emitting from
-radio to X-ray.  This same source could be responsible for the \tev
-emission due to inverse Compton and this matches the expected emission
-from a typical PWNe.
-
-The increased \gev and \tev size compared to the X-ray size
-has previously been observed in several aging PWNe including 
-HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess}, HESS\,J1640-465
-(\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}),
-and Vela X (\cite{vela_x_rosat,vela_x_hess}). 
-This can be explained by a different synchrotron cooling
-time for the electroncs producing X-rays and \tev gamma rays.
-Because of the spectral and spatial match between the \gev and \tev
-emission, the LAT data naturally fits into this model as being the rising
-edge of the inverse Compton component of a PWN.
+\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).
+In figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478
+are overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a 
+extension of $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the
+semi-major and semi-minor axes when fitting the source with an
+elliptical Gaussian surface brightness.  This corresponds to a 68\%
+containment size $\rsixeight=0.31\deg\pm0.08\deg$ and $0.09\pm0.06$
+along the semi-major and semi-minor axis. This size is consistent with
+the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.  Figure~\ref{hess_seds}
+shows that the LAT spectrum of 2FGL\,J1635.4-4717c connects smoothly to
+the H.E.S.S spectrum of HESS\,J1632-478.
+
+\cite{hess_plane_survey} argued that HESS\,J1632-478 is
+positionally coincident with the hard X-ray source IGR\,J1632-4751
+observed by INTEGRAL (\cite{Igr_J16320-4751_circ}), XMM-Newton
+(\cite{xmm_newton_IGR_J16320-4751}), and ASCI (\cite{asca_plane_survey}).
+But it is suspected to be an galactic X-Ray Binary so the \gev and \tev
+extension disfavors the association.
+
+Further observations by XMM-Newton reveal extended emission of size
+$\approx32''x\approx15''$ and inside point-like emission coincident with
+the peak H.E.S.S. emimssion (\cite{hess_j1632_478_xmm_newton}).  They
+found in archival MGPS-2 data a spatially coincident extended radio source
+\cite{most_survey_galactic_plane}.  The positional match argues for a
+single synchrotron processes producing X-ray and \gev and \tev radiation,
+likely due to a PWNe.  The increased \gev and \tev size compared
+to the X-ray size has previously been observed in several aging PWNe
+including HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess},
+HESS\,J1640-465 (\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}),
+and Vela X (\cite{vela_x_rosat,vela_x_hess}).  This can be explained by
+a different synchrotron cooling time for the electrons producing X-rays
+and \tev gamma rays.
 
@@
 
-The source 2FGL\,J1837.3-0700c was found 
-with 10-100 \gev photons 
-to have an extension
-of $0.35\deg\pm0.08\deg_\stat\pm0.03\deg_\sys$ 
-with an extension
-significance of $\tsext=18.8$.  The source was fit to a position of
-$(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
+The source 2FGL\,J1837.3-0700c was found with 10-100 \gev photons to
+have an extension of $0.35\deg\pm0.08\deg_\stat\pm0.03\deg_\sys$ with an
+extension significance of $\tsext=18.8$.  The source was fit to a position
+of $(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
 year catalog source 1FGL\,J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
@@
 
-This source is spatially coincident with the \tev
-source HESS\,J1837-069 (\cite{hess_plane_survey}).  In
-figure~\ref{1FGL_J1837.5-0659c}, contours of HESS\,J1837-069
-are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured a 
-Gaussian extension
-of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$ along the semi-major and
-semi-minor axis when fitting the source with an elliptical Gaussian
-surface brightness.  This corresponds to a 68\% containment radius of
-$\rsixeight=0.18\deg\pm0.03\deg$ and $0.08\deg\pm0.03\deg$ along the semi-major
-and semi-minor axis. The size is comparable to LAT which fit a 68\%
-containment radius of $\rsixeight=0.29\deg\pm0.07\deg$.  The LAT size is larger
-than the H.E.S.S. size but the sizes are almost almost within the
-$1\sigma$ errors. Figure~\ref{hess_seds} shows that the LAT spectrum
-of 2FGL\,J1837.3-0700c connects smoothly to the H.E.S.S spectrum of
-HESS\,J1837-069.
-
-\todo[inline]{Add interpretation of HESS\,J1837-069.}
+This source is spatially coincident with the \tev source HESS\,J1837-069
+(\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1837.5-0659c}, contours
+of HESS\,J1837-069 are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured
+an extension of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$
+along the semi-major and semi-minor axis when fitting the source
+with an elliptical Gaussian surface brightness.  This corresponds
+to a 68\% containment radius of $\rsixeight=0.18\deg\pm0.03\deg$ and
+$0.08\deg\pm0.03\deg$ along the semi-major and semi-minor axis. The
+size is comparable to LAT which fit a 68\% containment radius of
+$\rsixeight=0.29\deg\pm0.07\deg$.  the size difference is not significant
+(less than 2 sigma).  Figure~\ref{hess_seds} shows that the LAT spectrum
+connects smoothly to the H.E.S.S spectrum of HESS\,J1837-069.
+
+HESS\,J1837-069 is coincident with the hard
+and steady X-ray source AX J1838.0-0655
+(\cite{einstein_galactic_plane_survey,hard_x-ray_asca,integral_AX_J1838.0-0655,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}).
+This source was discovery by RXTE to 
+be a pulsar 
+sufficiently luminous to power the \tev emission.
+AX J1838.0-0655 was spatially resolved by \chandra to be a bright point source
+surrounded by a $\sim2'$ nebula (\cite{pulsations_HESS_J1837-069}).
+
+A second X-ray point source AX J1837.3-0652 is in the region of HESS\,J1837-069
+(\cite{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}).
+It was also resolved into point-like and diffuse component
+although no pulsations have yet been detected from it
+(\cite{pulsations_HESS_J1837-069}).  If AX J1838.0-0655 is a pulsar/PWN
+powering HESS\,J1837-069, some of the \tev emission
+may also be powered by AX J1837.3-0652.
 
@@
 extended sources.  The LAT energy spectrum connects smoothly to \tev.
-This is also true of HESS\,J1825-137 (\ref{fermi_hess_j1825}) and RX
-J1713.7-3946 (\cite{rx_j1713_lat}). We conclude that the \gev and \tev
-emission from these sources is coming from the same emission mechanism.
+This is also true of HESS\,J1825-137 (\cite{fermi_hess_j1825}) and RX
+J1713.7-3946 (\cite{rx_j1713_lat}).
 
@@
 (\cite{fermi_hess_j1825}).  It is interesting to compare the \gev and
-\tev size of other PWN candidates, but definitively measuring this effect
-would require a more careful analysis of the LAT data using the same 
+\tev size of other PWN candidates, but definitively measuring this 
+would require a more in-depth analysis of the LAT data using the same 
 elliptical surface brightness model.
@@
 field of view and all sky coverage, the LAT can more easily measure
-larger sources including the LMC and SMC.  On the other hand, the
-smaller angular resolution of Air Cherenkov detectors allows them to
-measure a population of extended sources below our sensitivity limit
-(currently at about $\approx0.2\deg$).  Fermi has a five year nominal
-livetime with a goal of ten years of operation. With increased exposure,
-the LAT will likely begin to resolving these smaller \tev sources.
-As figure~\ref{time_sensitivity} showed, our sensitivity to these smaller
-sources will actually improve faster than $\sqrt{t}$.
+larger sources including the LMC and SMC.  On the other hand, the smaller
+angular resolution of Air Cherenkov detectors allows them to measure a
+population of extended sources below our sensitivity limit (currently at
+about $\approx0.2\deg$).  Fermi has a five year nominal livetime with a
+goal of ten years of operation.  As figure~\ref{time_sensitivity} showes,
+our sensitivity to these smaller sources will improve by a factor greater
+than $\sqrt{t}$.  With increased exposure, the LAT will likely begin to
+resolve these smaller \tev sources.
 
@@
     \caption{
-    All plots are for the SNR IC443 using two years of data.
-    % ts vs extension
-    Plot (a) is the change in \ts when varying the
-    extension of the source.  
-    % ts_ext vs energy
-    Plot (b) is \tsext in twelve energy bins. This plot shows that there is
-    little gain in sensitivity to the extension using photons
-    with energies below 1 \gev, even for a source with an index $\approx2.4$.
-    % radial integral
-    Plot (c) is the sum of all counts within a given radial distance
-    from the source binned uniformly in $\theta^2$. 
-    Overlaid on the plot is the model predicted counts assuming that
-    the source is both an extended source and a point source
-    % smoothed counts
-    Plot (d) is a counts map of the source with the Galactic and
-    isotropic diffuse emission subtracted and smoothed by a $0.1\deg$
-    Gaussian kernel.  The inset is the predicted emission from a point
-    source of the same spectrum and intensity.  The PSF is smoothed
-    by the same kernel.  Plots (a), (c), and (d) use only 1-100 \gev photons. 
+    Counts and test statistic profiles for the SNR IC443. (a) \ts
+    vs. extension of the source. (b) \tsext for individual energy bands. (c)
+    observed radial profile of counts in comparison to the expected profiles
+    for a point source (blue) and a spatially extended source (red) . (d)
+    smoothed count map after subtraction of the diffuse emission compared
+    to the LAT PSF (inset).  Plots (a), (c), and (d) use only 1-100 \gev photons. 
     Plots (c) and (d)
@@
     \caption{
-    A comparison of the Gaussian and uniform disk PDFs before and
-    after convolving with the PSF.  The black line is the PSF that
-    would be observed for a power-law source of spectral index 2. The
-    dashed red line is the probability density of a Gaussian with
-    $\rsixeight=0.5\deg$, which is just a straight line on this plot.
-    The dashed blue line is the probability density for a uniform disk
-    with $\rsixeight=0.5\deg$.  Finally, the solid red and blue lines
-    show the convolution of the Gaussian and uniform disk with the PSF.
-    Plot (a) uses a 1-100 \gev energy range while plot (b)
-    uses a 10-100 \gev enregy range. This plot demonstrates that different
-    surface brightness models when smoothed by the PSF look similar.  The $y$
-    axis is the log of the intensity and the $x$ axis is $\theta^2$.
-    This plot is discussed further in section~\ref{compare_source_size}.
+    A comparison of a Gaussian and disk like surface brightness profile
+    of extended sources before and after convolving with the PSF for two
+    energy ranges.  The black line is the PSF that would be observed
+    for a power-law source of spectral index 2. The dashed red line
+    is the brightness profile of a Gaussian with $\rsixeight=0.5\deg$.
+    The dashed blue line is the brightness profile for a uniform disk
+    with $\rsixeight=0.5\deg$.  The solid red and blue lines show the
+    convolution of the Gaussian and uniform disk brightness profiles
+    with the LAT PSF.
     }\label{compare_disk_gauss}
@@
 
-    \begin{table}
-  \begin{centering}
-    \begin{tabular}{ r | r | r | r }
-      \hline
-      \hline
-      $\gamma$ & flux ($\ph/\cm^2/\sec$) & $N_\text{sims}$ & $\langle\ts\rangle$ \\
-      \hline
+\begin{deluxetable}{rrrr}
+\tabletypesize{\normalsize}
+\tablecaption{Monte Carlo Validation Parameters
+\label{ts_ext_num_sims}
+}
+\tablewidth{0pt}
+\tablehead{
+
+\colhead{Spectral Index}&
+\colhead{Flux\tablenotemark{a}}&
+\colhead{$N_\text{sims}$}&
+\colhead{$\langle\ts\rangle$}
+}
+
+\startdata
       1.5 &          $10^{-6}$ &           31952 &  92862 \\
@@
           &          $10^{-7}$ &           19271 &     40 \\
-      \hline
-    \end{tabular}
-    \caption{
-    This table presents a list of the spectral models (flux and
-    spectral index) used in the Monte Carlo study of \pointlike
-    described in section~\ref{monte_carlo_validation} and presented
-    in figure~\ref{ts_ext_mc}.  For each spectral model, the number of
-    statistically independent simulations and the average value of \ts
-    value ($\langle\ts\rangle$) is tabulated.  The Monte Carlo simulation
-    spans parameters representative of sources that could be detected
-    by the LAT.  The simulation is of spectral indices $\gamma$ of 1.5,
-    2, 2.5, and 3.  The simulation is of fluxes varying from a $5\sigma$
-    source detection to a $>10\sigma$ source detection.  Only simulations
-    which produced statistically significant detections ($\ts>25$)
-    were kept.  What is quoted is the $>100$ \mev integral flux measured
-    in units of $\ph/\cm^2/\sec$.  More information about this Monte
-    Carlo analysis is presented in section~\ref{monte_carlo_validation}.
-    }\label{ts_ext_num_sims}
-  \end{centering}
-\end{table}
+\enddata
+
+\tablenotetext{a}{Integral 1-100 \mev flux in units of $\ph/\cm^2/\sec$}
+
+\tablecomments{
+    the spectral models used in the Monte Carlo validation of \pointlike.
+    For each model, the number of statistically independent simulations
+    and the average value of \ts is tabulated.  The models spans
+    representative spectral parameters.
+}
+
+\end{deluxetable}
 
@@
     blue). Flux is quoted in this energy range and the gray region is
-    the projected sensitivity assuming that our sensitivity improves
+    the projected detection threshold to the extension
+  of a source assuming that it improves
+    from the 2 year threshold
     with $\sqrt{\text{t}}$ (top edge) and linearly with time (bottom
-    edge). For small extended sources, our sensitivity to the extension
+    edge). For small extended sources, our detection threshold to the extension
     of a source actually improves better than $\sqrt{\text{t}}$
@@
     the relevant background is over a larger area and our gain
-    in sensitivity is closer to $\sqrt{\text{t}}$.  This effect is
+    improvement is closer to $\sqrt{\text{t}}$.  This effect is
     even more pronounced for sources hard only above 10 \gev.
@@
   Gaussian kernel.  Plot (a) has the diffuse emission model subtracted
-  and plot (b) has the diffuse emission and 
-  the background source 2FGL\,J1625.7-2526.  
-  subtracted.  The red star is the catalog's position of this source.
-  The red cross and circle are the best position and extension of
-  this source assuming a radially
-  symmetric uniform surface brightness.  The light
-  blue contours are from a 100 micrometer infrared image of the region
-  as seen by IRAS (\cite{iras_rho_ophiuci}). This source is in the
-  Ophiuchus region and most likely represents unmodeled diffuse
-  emission.  More information about this source can be found in
+  and plot (b) has the diffuse emission and the background source
+  2FGL\,J1625.7-2526.  subtracted.  The red star is the catalog's
+  position of this source.  The red cross and circle are the best
+  position and extension of this source assuming a radially symmetric
+  uniform surface brightness.  This source is in the Ophiucus and might
+  represent an inadequacy in the diffuse $\gamma$-ray model . The left are
+  the IRAS 100 micrometer image (\cite{iras_rho_ophiuci}) and the right
+  contours are the CO (\cite{co_rho_ophiuci}).  This source is in the
+  Ophiuchus region and most likely represents unmodeled diffuse emission.
+  More information about this source can be found in
   section~\ref{section_2FGL_J1627.0-2425c}.

### 2011-08-14 extended_catalog/paper/extended_catalog.tex
lots of markus suggestions

@@
 \usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
-\usepackage[toc,page]{appendix}
 
@@
 \section{Introduction}
+
+\todo[inline]{Remove from all figures - "more infomration can be foudn in"}
 
@@
 LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI})
-and HESS\,J0632+057 (\cite{HESS0632}) are amongst the few Galactic sources
+HESS\,J0632+057 (\cite{HESS0632}), and the Crab nebula (\cite{crab_weekes})
+are amongst the few Galactic sources
 for which no significant extension was detected at \tev energies. Given
@@
 
+todo[inline]{This text needs to be fixed}
+
 Figure~\ref{diff_factor_sensitivity} shows how the LAT's detection
@@
 \todo[inline]{Add interpretations of Puppis A.}
+\todo[inline]{Markus says to add an SED.}
 
@@
 
-2FGL reported on the detection of twelve spatially extended sources. Using
+2FGL reported on the detection of twelve sources
+prviously known as extende. Using
 two years of LAT data and a new analysis method, we present on 
@@
 source extension with different frequencies, especially at \tev energies,
-allows us to identify the LAT source. Even still, for many extended LAT
-sources the source class and emission process is still uncertain.
-
-The position of the 21 extended LAT sources is plotted in
-figure~\ref{allsky_extended_sources}.  Most of them lie along the galactic
-plane.  This is expected because extragalactic sources are typically too
-far away to be resolvable and most Galactic sources lie along the plane.
+allows us to firmly associate the LAT source in many cases.
+
+The position of the 21 extended LAT sources are close to the Galactic
+plane and plotted in figure~\ref{allsky_extended_sources}.  Most of the
+extended sources are indeed expected to be of Galactic origin as the
+distance of extragalactic sources (with exception of the local group
+Galaxies) is typically too large to resolve them in gamma rays.
 
@@
     \caption{
-     The plot shows the null distribution of
-    the likelihood ratio test when fitting a point source for extension.
-    The $x$ axis is \tsext and the $y$ axis is the cumulative density
-    for \tsext of simulated point sources. The four plots represent
-    different spectral indices and the different colors represent
-    different fluxes.  The dashed red line is the cumulative density
-    function of $\chi^2(\ts)/2$ which is suggested by Wilks' theorem
-    as the distribution these curves should should follow.  There is
-    good agreement between the Monte Carlo results and
-    the theoretical distribution. For most spectral parameters, the
-    Monte Carlo curve lies to the left of the theoretical curve which
-    would make the theoretical distribution more conservative.  In this
-    paper, we use this theoretical curve to estimate the significance of
-    the detection of a source's extension. This plot cuts off 
-    three simulations with $\tsext>25$. They 
-    had a flux $3\times10^{-8}\ph/\cm^2/\sec$, spectral index
-    2.5, and \tsext of 26.1, 28.9, and 38.1.
-    The Monte Carlo simulation is described in 
-    section \ref{monte_carlo_validation} and 
-    the number of simulation for each spectral model 
-    are presented in table~\ref{ts_ext_num_sims}.
+    Distribution of the test statistic \tsext of a likelihood ratio
+    test when fitting the extension of a point source.  The four plots
+    represent simulated point sources of different spectral indices and
+    the different colors represent point sources with different 100 \mev
+    to 100 \gev integral fluxes.  The dashed red line is the cumulative
+    density function of equation~\ref{ts_ext_distribution}.
     }\label{ts_ext_mc}
@@
     \caption{
-    This plot shows the detection threshold to resolve a uniform
-    disk extended source.  The detection threshold is defined as the flux where
-    $\langle\tsext\rangle=16$ for a given extension.  The $x$ axis is
-    the extension of a uniform disk extended source and the $y$ axis
-    is the source's 100 \mev to 100 \gev photon flux.  All sources have
-    an assumed power-law spectrum and the different colors are different
-    simulated spectral indices.  The solid line is the detection threshold
-    using photons with energy between 100 \mev and 100 \gev while the
-    dashed line is the threshold using 1-100 \gev photons. The detection threshold is for the same two year time
-    range as was used in 2FGL and in the following extended source search.
-    The extended sources are simulated against
-  a Sreekumar-like isotropic background.  More information
-    about this plot is presented in section~\ref{extension_sensitivity}.
-    This plot shows that our threshold to detecting the extension of
-    a source is best for a source with size $~0.5\deg$. It also shows
-    that for sources neither too large nor soft, our sensitivity is not
-    significantly improved using photons with energy between 100 \mev
-    and 1 \gev. More information about this plot is presented
-    in section~\ref{extension_sensitivity}.
+    The detection threshold ($\langle\tsext\rangle=16$) to resolve a
+    uniform disk extended source for a two-year exposure.  All sources
+    have an assumed power-law spectrum and the different colors correspond
+    to different simulated spectral indices.  The solid line is the
+    detection threshold using photons with energy between 100 \mev and 100
+    \gev while the dashed line is the threshold using 1-100 \gev photons.
     }\label{index_sensitivity}
@@
 
+% \begin{figure}
+%   \begin{center}
+%     \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
+%     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_diff_factor.py
+%     \end{center}
+%     \caption{
+%     This shows the detection threshold to a uniform disk extended
+%     source for varying background levels
+%     and energy ranges.  The plots have the same meaning as in
+%     figure~\ref{index_sensitivity} and the simulations occur over the
+%     same time range.  The solid blue line is the detection threshold against a
+%     Sreekumar-like isotropic background. The green dashed curve is the
+%     threshold against 10 times the isotropic background and the dash
+%     dotted red curve is the threshold against 100 times the isotropic
+%     background.  The latter factor approximately represents the intensity
+%     of the Galactic diffuse emission near the Galactic center.  Plot (a)
+%     is the threshold using 1-100\gev photons while plot (b) is the threshold using
+%     10-100\gev photons. Unlike figure~\ref{index_sensitivity},
+%     the detection threshold was calculated only for a power-law source of spectral
+%     index 2. The flux is quoted only in the selected energy range which
+%     weakens the dependence of the detection threshold on spectral index.
+%     These plots show that we are less sensitive to extended sources in
+%     regions with higher background and (given the same number of photons)
+%     more sensitive to harder sources.  Overlaid on this plot are the
+%     extended sources found in this extended source search. The extended
+%     sources are color coded based upon whether the integral galactic
+%     diffuse and isotropic diffuse emission model is closer to 1x, 10x,
+%     or 100x the Sreekumar-like isotropic spectrum.  The red point
+%     in plot (a) below the red line is RX J1713.7-3946 which is harder
+%     ($\gamma\approx1.5$) and has diffuse emission only 53 times larger
+%     than the isotropic emission.  The green point in plot (b) below
+%     the green line is MSH 15-52 which was found by our analysis to
+%     have $\tsext=6.5$.  More information about this plot is presented
+%     in section~\ref{extension_sensitivity}.
+%     }\label{diff_factor_sensitivity}
+%   \end{figure}
+
 \begin{figure}
   \begin{center}
-    \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_diff_factor.py
+    \includegraphics{mc_plots/all_sensitivity.pdf}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
     \end{center}
-    \caption{
-    This shows the detection threshold to a uniform disk extended
-    source for varying background levels
-    and energy ranges.  The plots have the same meaning as in
-    figure~\ref{index_sensitivity} and the simulations occur over the
-    same time range.  The solid blue line is the detection threshold against a
-    Sreekumar-like isotropic background. The green dashed curve is the
-    threshold against 10 times the isotropic background and the dash
-    dotted red curve is the threshold against 100 times the isotropic
-    background.  The latter factor approximately represents the intensity
-    of the Galactic diffuse emission near the Galactic center.  Plot (a)
-    is the threshold using 1-100\gev photons while plot (b) is the threshold using
-    10-100\gev photons. Unlike figure~\ref{index_sensitivity},
-    the detection threshold was calculated only for a power-law source of spectral
-    index 2. The flux is quoted only in the selected energy range which
-    weakens the dependence of the detection threshold on spectral index.
-    These plots show that we are less sensitive to extended sources in
-    regions with higher background and (given the same number of photons)
-    more sensitive to harder sources.  Overlaid on this plot are the
-    extended sources found in this extended source search. The extended
-    sources are color coded based upon whether the integral galactic
-    diffuse and isotropic diffuse emission model is closer to 1x, 10x,
-    or 100x the Sreekumar-like isotropic spectrum.  The red point
-    in plot (a) below the red line is RX J1713.7-3946 which is harder
-    ($\gamma\approx1.5$) and has diffuse emission only 53 times larger
-    than the isotropic emission.  The green point in plot (b) below
-    the green line is MSH 15-52 which was found by our analysis to
-    have $\tsext=6.5$.  More information about this plot is presented
-    in section~\ref{extension_sensitivity}.
-    }\label{diff_factor_sensitivity}
+    \caption{the LAT detection threshold for four spectral indices and
+    three background (1x, 10x, and 100x the Sreekumar-like isotropic
+    spectrum) for a two-year exposure. The left plots are the detection
+    threshold when using 1-100 \gev photons and the right plots are
+    the detection threshold when using 10-100 \gev photons.  The flux
+    is integrated only in the selected energy range.  Overlaid on this
+    plot are the LAT detected extended sources placed by the nearby
+    Galactic diffuse emission and color coded by their spectral idnex.
+    The black point in plot (d) below the green line is MSH 15-52 which
+    was found by our analysis to have $\tsext=6.5$.  
+    }\label{all_sensitivity} 
   \end{figure}
+
+  \clearpage
+  \thispagestyle{empty}
+  \begin{sidewaystable}\scriptsize
+    \begin{centering}
+      \begin{tabular}{r|r|rrrrrrrrrrrrrrrrrrrr}
+        \hline
+        \hline
+        \multicolumn{22}{c}{$ 1 \gev < E < 100 \gev$} \\
+        \hline
+        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
+        \hline
+             1.5 &       x1 &      148.3 &       23.2 &       11.2 &        8.0 &        7.1 &        6.9 &        6.8 &        6.8 &        7.0 &        7.3 &        7.5 &        7.7 &        8.0 &        8.3 &        9.1 &        9.8 &        9.0 &        9.1 &        8.8 &       10.2 \\
+                 &      x10 &      146.9 &       29.0 &       18.5 &       15.1 &       15.4 &       15.0 &       14.7 &       15.6 &       16.6 &       17.3 &       18.0 &       19.1 &       20.7 &       22.5 &       23.6 &       24.3 &       21.2 &       22.8 &       23.3 &       23.6 \\
+                 &     x100 &      184.3 &       55.1 &       43.0 &       41.0 &       40.7 &       41.7 &       40.3 &       40.8 &       43.0 &       43.6 &       38.3 &       39.5 &       40.1 &       38.5 &       36.5 &       35.8 &       36.5 &       38.1 &       36.6 &       37.1 \\
+               2 &       x1 &      327.5 &       43.1 &       18.7 &       13.3 &       11.2 &       10.4 &       10.1 &       10.1 &       10.2 &       10.4 &       10.6 &       10.9 &       11.1 &       11.5 &       12.3 &       12.6 &       13.0 &       13.4 &       13.8 &       14.2 \\
+                 &      x10 &      336.1 &       55.3 &       32.2 &       27.4 &       26.3 &       25.3 &       25.5 &       25.8 &       27.2 &       26.6 &       27.6 &       28.5 &       30.1 &       29.9 &       30.8 &       31.8 &       31.9 &       34.2 &       34.2 &       36.1 \\
+                 &     x100 &      409.6 &      128.1 &       88.6 &       76.2 &       72.7 &       71.4 &       67.8 &       65.2 &       63.6 &       63.7 &       62.0 &       63.1 &       62.4 &       61.1 &       56.0 &       58.4 &       60.1 &       62.1 &       59.5 &       55.9 \\
+             2.5 &       x1 &      622.9 &       75.0 &       29.6 &       19.0 &       15.5 &       13.6 &       12.8 &       12.7 &       12.4 &       12.5 &       12.6 &       12.9 &       12.8 &       13.1 &       13.4 &       13.7 &       14.1 &       14.6 &       15.0 &       15.7 \\
+                 &      x10 &      641.5 &       98.2 &       51.8 &       39.2 &       34.7 &       33.1 &       32.6 &       32.3 &       33.0 &       33.4 &       33.8 &       34.5 &       34.5 &       35.4 &       37.0 &       37.2 &       35.6 &       36.2 &       37.1 &       37.8 \\
+                 &     x100 &      789.7 &      260.3 &      136.9 &      102.7 &       90.1 &       80.8 &       77.2 &       74.9 &       69.1 &       70.8 &       65.8 &       64.5 &       64.3 &       62.3 &       57.1 &       57.1 &       58.8 &       57.3 &       55.6 &       54.2 \\
+               3 &       x1 &      842.0 &      109.6 &       42.9 &       25.4 &       18.7 &       15.9 &       14.3 &       13.5 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.5 &       13.5 &       13.6 &       14.1 &       14.3 &       14.7 &       15.3 \\
+                 &      x10 &      919.0 &      153.8 &       69.7 &       48.1 &       40.9 &       37.6 &       35.7 &       34.9 &       35.3 &       35.3 &       35.3 &       35.2 &       35.1 &       35.5 &       37.0 &       37.7 &       35.3 &       35.5 &       36.4 &       37.5 \\
+                 &     x100 &     1077.5 &      289.1 &      180.2 &      119.2 &      101.0 &       92.4 &       86.2 &       79.3 &       74.3 &       70.8 &       67.2 &       66.4 &       65.0 &       62.9 &       58.4 &       56.6 &       57.4 &       55.9 &       54.3 &       52.2 \\
+        \hline
+        \multicolumn{22}{}{} \\
+        \multicolumn{22}{}{} \\
+        \hline
+        \hline
+        \multicolumn{22}{c}{$ 10 \gev < E < 100 \gev$} \\
+        \hline
+        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
+        \hline
+             1.5 &       x1 &       44.4 &        8.1 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.4 &        2.5 &        2.6 &        2.7 &        2.7 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
+                 &      x10 &       45.2 &        9.3 &        5.9 &        5.0 &        4.9 &        5.1 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.2 &        6.6 &        6.5 &        7.0 &        7.7 &        7.8 &        8.2 &        8.4 &        8.8 \\
+                 &     x100 &       47.2 &       13.5 &       11.5 &       10.6 &       10.6 &       10.8 &       12.0 &       12.7 &       13.3 &       13.7 &       15.2 &       16.1 &       17.2 &       18.2 &       19.1 &       19.8 &       20.7 &       21.3 &       22.1 &       23.4 \\
+               2 &       x1 &       49.6 &        8.3 &        4.4 &        3.2 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
+                 &      x10 &       48.5 &        9.6 &        6.0 &        5.2 &        5.1 &        5.2 &        5.2 &        5.4 &        5.5 &        5.8 &        6.4 &        6.7 &        7.0 &        7.2 &        7.6 &        8.0 &        8.3 &        8.7 &        9.0 &        9.3 \\
+                 &     x100 &       51.5 &       14.8 &       11.8 &       11.5 &       11.5 &       12.0 &       13.1 &       14.0 &       14.4 &       15.3 &       16.1 &       16.8 &       18.5 &       19.3 &       20.1 &       21.3 &       22.3 &       23.1 &       23.4 &       24.5 \\
+             2.5 &       x1 &       53.0 &        9.2 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.8 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.4 &        3.5 &        3.6 \\
+                 &      x10 &       53.8 &       10.6 &        6.3 &        5.4 &        5.1 &        5.2 &        5.3 &        5.5 &        5.7 &        6.1 &        6.4 &        6.6 &        6.9 &        7.3 &        7.5 &        8.2 &        8.4 &        8.7 &        9.0 &        9.4 \\
+                 &     x100 &       56.6 &       15.8 &       12.9 &       11.9 &       11.9 &       12.4 &       13.1 &       14.3 &       14.7 &       15.2 &       16.3 &       17.0 &       18.9 &       19.3 &       20.1 &       21.2 &       22.2 &       22.7 &       23.6 &       24.1 \\
+               3 &       x1 &       55.1 &        9.3 &        4.7 &        3.3 &        2.9 &        2.6 &        2.5 &        2.5 &        2.5 &        2.5 &        2.6 &        2.6 &        2.7 &        2.8 &        2.9 &        3.0 &        3.0 &        3.2 &        3.4 &        3.4 \\
+                 &      x10 &       55.7 &       10.5 &        6.3 &        5.3 &        5.2 &        5.3 &        5.2 &        5.4 &        5.6 &        5.7 &        6.0 &        6.4 &        6.6 &        6.9 &        7.1 &        7.9 &        8.1 &        8.5 &        8.7 &        8.9 \\
+                 &     x100 &       60.1 &       16.0 &       12.8 &       11.7 &       11.7 &       12.3 &       12.7 &       14.0 &       14.1 &       14.6 &       15.8 &       16.5 &       17.6 &       18.6 &       19.5 &       19.9 &       21.0 &       21.3 &       22.0 &       22.9 \\
+        \hline
+      \end{tabular}
+      \caption{The detection threshold to resolve a uniform disk spatially
+      extended sources using two years of data for sources of varying
+      spectral index and extension against varying background levels
+      with different energy ranges.  The upper table is the sensitivity
+      when using photons with energies from 1-100 \gev and the bottom
+      table when using 10-100 \gev photons. The first column is
+      the extended source's spectral index.  The extended sources
+      were simulated against a Sreekumar-like isotropic spectrum and
+      the second column is the factor that the simulated background
+      was scaled by. The remaining columns are varying sizes of the
+      source assuming a uniform surface brightness. The table quotes integral
+      fluxes in the analyzed energy range in units of
+      $10^{-10} \ph/\cm^2/\sec$.  
+      }\label{all_sensitivity_table}
+    \end{centering}
+  \end{sidewaystable}
 
@@
     \caption{
-    This plot shows our projected sensitivity to extension after 10 years
-    of operation for an assumed power-law source of spectral index
-    2 against a representative 10 times the isotropic background in the
-    energy range from 1-100 \gev (solid red) and 10-100 \gev (dashed
-    blue). Flux is quoted in this energy range and the gray region is
-    the projected detection threshold to the extension
-  of a source assuming that it improves
-    from the 2 year threshold
-    with $\sqrt{\text{t}}$ (top edge) and linearly with time (bottom
-    edge). For small extended sources, our detection threshold to the extension
-    of a source actually improves better than $\sqrt{\text{t}}$
-    because at the highest energies, where we are most sensitive to the
-    extension of a source, the relevant background near the sources is in
-    the Poisson instead of Gaussian regime.  For large extended sources,
-    the relevant background is over a larger area and our gain
-    improvement is closer to $\sqrt{\text{t}}$.  This effect is
-    even more pronounced for sources hard only above 10 \gev.
+    Our projected sensitivity to extension after 10 years for a power-law
+    source of spectral index 2 against 10 times the isotropic background
+    in the energy range from 1-100 \gev (solid red) and 10-100 \gev
+    (dashed blue). This background is representative of the background
+    near the Galactic plane.  The solid gray region is the projected
+    detection threshold assuming the sensitivity improves from the 2
+    year threshold by $\sqrt{\text{t}}$ (top edge) and linearly with
+    time (bottom edge).  The lower plot shows the factor increase in
+    sensitivity.  For small extended sources, our detection threshold
+    improves better than $\sqrt{\text{t}}$ because at high energies where
+    we are most sensitive to extension, the background levels are in the
+    Poisson instead of Gaussian regime.  For large extended sources,
+    the relevant background is larger and the improvement is closer
+    to $\sqrt{\text{t}}$.
     }\label{time_sensitivity}
@@
   \end{tabular}
-    \caption{The 8 new source candidates found by the extended source
+    \caption{The 9 new source candidates found by the extended source
     search. Three new extended sources were found using photons with
@@
 
-  \clearpage
-\begin{appendices}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics{mc_plots/all_sensitivity.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
-    \end{center}
-    \caption{These six plots condense the LAT detection threshold for
-    all four spectral indices shown in figure~\ref{index_sensitivity}
-    (1.5, 2, 2.5, and 3) and all three background levels shown
-    in~\ref{diff_factor_sensitivity}.  (1x, 10x, and 100x the
-    Sreekumar-like isotropic spectrum).  The plots have the same meaning
-    as in figure~\ref{index_sensitivity} The left plots are the detection
-    threshold when using 1-100 \gev photons and the right plots are the detection threshold when using
-    10-100 \gev photons.  This plot shows
-    that when using only high energy photons with an improved angular
-    resolution, our detection threshold is only weakly a function of
-    spectral index. The numeric values plotted here are tabulated
-    in table~\ref{all_sensitivity_table}. More information about this plot is presented
-    in section~\ref{extension_sensitivity}.
-    }\label{all_sensitivity} 
-  \end{figure}
-
-  \clearpage
-  \thispagestyle{empty}
-  \begin{sidewaystable}\scriptsize
-    \begin{centering}
-      \begin{tabular}{r|r|rrrrrrrrrrrrrrrrrrrr}
-        \hline
-        \hline
-        \multicolumn{22}{c}{$ 1 \gev < E < 100 \gev$} \\
-        \hline
-        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
-        \hline
-             1.5 &       x1 &      148.3 &       23.2 &       11.2 &        8.0 &        7.1 &        6.9 &        6.8 &        6.8 &        7.0 &        7.3 &        7.5 &        7.7 &        8.0 &        8.3 &        9.1 &        9.8 &        9.0 &        9.1 &        8.8 &       10.2 \\
-                 &      x10 &      146.9 &       29.0 &       18.5 &       15.1 &       15.4 &       15.0 &       14.7 &       15.6 &       16.6 &       17.3 &       18.0 &       19.1 &       20.7 &       22.5 &       23.6 &       24.3 &       21.2 &       22.8 &       23.3 &       23.6 \\
-                 &     x100 &      184.3 &       55.1 &       43.0 &       41.0 &       40.7 &       41.7 &       40.3 &       40.8 &       43.0 &       43.6 &       38.3 &       39.5 &       40.1 &       38.5 &       36.5 &       35.8 &       36.5 &       38.1 &       36.6 &       37.1 \\
-               2 &       x1 &      327.5 &       43.1 &       18.7 &       13.3 &       11.2 &       10.4 &       10.1 &       10.1 &       10.2 &       10.4 &       10.6 &       10.9 &       11.1 &       11.5 &       12.3 &       12.6 &       13.0 &       13.4 &       13.8 &       14.2 \\
-                 &      x10 &      336.1 &       55.3 &       32.2 &       27.4 &       26.3 &       25.3 &       25.5 &       25.8 &       27.2 &       26.6 &       27.6 &       28.5 &       30.1 &       29.9 &       30.8 &       31.8 &       31.9 &       34.2 &       34.2 &       36.1 \\
-                 &     x100 &      409.6 &      128.1 &       88.6 &       76.2 &       72.7 &       71.4 &       67.8 &       65.2 &       63.6 &       63.7 &       62.0 &       63.1 &       62.4 &       61.1 &       56.0 &       58.4 &       60.1 &       62.1 &       59.5 &       55.9 \\
-             2.5 &       x1 &      622.9 &       75.0 &       29.6 &       19.0 &       15.5 &       13.6 &       12.8 &       12.7 &       12.4 &       12.5 &       12.6 &       12.9 &       12.8 &       13.1 &       13.4 &       13.7 &       14.1 &       14.6 &       15.0 &       15.7 \\
-                 &      x10 &      641.5 &       98.2 &       51.8 &       39.2 &       34.7 &       33.1 &       32.6 &       32.3 &       33.0 &       33.4 &       33.8 &       34.5 &       34.5 &       35.4 &       37.0 &       37.2 &       35.6 &       36.2 &       37.1 &       37.8 \\
-                 &     x100 &      789.7 &      260.3 &      136.9 &      102.7 &       90.1 &       80.8 &       77.2 &       74.9 &       69.1 &       70.8 &       65.8 &       64.5 &       64.3 &       62.3 &       57.1 &       57.1 &       58.8 &       57.3 &       55.6 &       54.2 \\
-               3 &       x1 &      842.0 &      109.6 &       42.9 &       25.4 &       18.7 &       15.9 &       14.3 &       13.5 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.5 &       13.5 &       13.6 &       14.1 &       14.3 &       14.7 &       15.3 \\
-                 &      x10 &      919.0 &      153.8 &       69.7 &       48.1 &       40.9 &       37.6 &       35.7 &       34.9 &       35.3 &       35.3 &       35.3 &       35.2 &       35.1 &       35.5 &       37.0 &       37.7 &       35.3 &       35.5 &       36.4 &       37.5 \\
-                 &     x100 &     1077.5 &      289.1 &      180.2 &      119.2 &      101.0 &       92.4 &       86.2 &       79.3 &       74.3 &       70.8 &       67.2 &       66.4 &       65.0 &       62.9 &       58.4 &       56.6 &       57.4 &       55.9 &       54.3 &       52.2 \\
-        \hline
-        \multicolumn{22}{}{} \\
-        \multicolumn{22}{}{} \\
-        \hline
-        \hline
-        \multicolumn{22}{c}{$ 10 \gev < E < 100 \gev$} \\
-        \hline
-        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
-        \hline
-             1.5 &       x1 &       44.4 &        8.1 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.4 &        2.5 &        2.6 &        2.7 &        2.7 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
-                 &      x10 &       45.2 &        9.3 &        5.9 &        5.0 &        4.9 &        5.1 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.2 &        6.6 &        6.5 &        7.0 &        7.7 &        7.8 &        8.2 &        8.4 &        8.8 \\
-                 &     x100 &       47.2 &       13.5 &       11.5 &       10.6 &       10.6 &       10.8 &       12.0 &       12.7 &       13.3 &       13.7 &       15.2 &       16.1 &       17.2 &       18.2 &       19.1 &       19.8 &       20.7 &       21.3 &       22.1 &       23.4 \\
-               2 &       x1 &       49.6 &        8.3 &        4.4 &        3.2 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
-                 &      x10 &       48.5 &        9.6 &        6.0 &        5.2 &        5.1 &        5.2 &        5.2 &        5.4 &        5.5 &        5.8 &        6.4 &        6.7 &        7.0 &        7.2 &        7.6 &        8.0 &        8.3 &        8.7 &        9.0 &        9.3 \\
-                 &     x100 &       51.5 &       14.8 &       11.8 &       11.5 &       11.5 &       12.0 &       13.1 &       14.0 &       14.4 &       15.3 &       16.1 &       16.8 &       18.5 &       19.3 &       20.1 &       21.3 &       22.3 &       23.1 &       23.4 &       24.5 \\
-             2.5 &       x1 &       53.0 &        9.2 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.8 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.4 &        3.5 &        3.6 \\
-                 &      x10 &       53.8 &       10.6 &        6.3 &        5.4 &        5.1 &        5.2 &        5.3 &        5.5 &        5.7 &        6.1 &        6.4 &        6.6 &        6.9 &        7.3 &        7.5 &        8.2 &        8.4 &        8.7 &        9.0 &        9.4 \\
-                 &     x100 &       56.6 &       15.8 &       12.9 &       11.9 &       11.9 &       12.4 &       13.1 &       14.3 &       14.7 &       15.2 &       16.3 &       17.0 &       18.9 &       19.3 &       20.1 &       21.2 &       22.2 &       22.7 &       23.6 &       24.1 \\
-               3 &       x1 &       55.1 &        9.3 &        4.7 &        3.3 &        2.9 &        2.6 &        2.5 &        2.5 &        2.5 &        2.5 &        2.6 &        2.6 &        2.7 &        2.8 &        2.9 &        3.0 &        3.0 &        3.2 &        3.4 &        3.4 \\
-                 &      x10 &       55.7 &       10.5 &        6.3 &        5.3 &        5.2 &        5.3 &        5.2 &        5.4 &        5.6 &        5.7 &        6.0 &        6.4 &        6.6 &        6.9 &        7.1 &        7.9 &        8.1 &        8.5 &        8.7 &        8.9 \\
-                 &     x100 &       60.1 &       16.0 &       12.8 &       11.7 &       11.7 &       12.3 &       12.7 &       14.0 &       14.1 &       14.6 &       15.8 &       16.5 &       17.6 &       18.6 &       19.5 &       19.9 &       21.0 &       21.3 &       22.0 &       22.9 \\
-        \hline
-      \end{tabular}
-      \caption{The detection threshold to resolve a uniform disk spatially
-      extended sources using two years of data for sources of varying
-      spectral index and extension against varying background levels
-      with different energy ranges.  The upper table is the sensitivity
-      when using photons with energies from 1-100 \gev and the bottom
-      table is when using 10-100 \gev photons. The first column is
-      the extended source's spectral index.  The extended sources
-      were simulated against a Sreekumar-like isotropic spectrum and
-      the second column is the factor that the simulated background
-      was scaled by. The remaining columns are varying sizes of the
-      source assuming a uniform surface brightness. The table quotes fluxes in units of
-      $10^{-10} \ph/\cm^2/\sec$.  These values are also plotted in
-      figure~\ref{all_sensitivity}.  More information about this
-      table is presented in section~\ref{extension_sensitivity}.
-      }\label{all_sensitivity_table}
-    \end{centering}
-  \end{sidewaystable}
-
-\end{appendices}
-
 \end{document}

### 2011-08-15 extended_catalog/paper/extended_catalog.tex
working on interpretation

@@
 
-\usepackage{rotating}
+%\usepackage{rotating}
 \usepackage{amsmath}
@@
 \newcommand{\chandra}{\text{{\em Chandra}}\xspace}
+\newcommand{\rosat}{\text{{\em ROSAT}}\xspace}
+\newcommand{\asca}{\text{{\em ASCA}}\xspace}
+\newcommand{\einstein}{\text{{\em Einstein}}\xspace}
+\newcommand{\xmmnewton}{\text{{\em XMM-Newton}}\xspace}
 
@@
 \section{Introduction}
-
-\todo[inline]{Remove from all figures - "more infomration can be foudn in"}
 
@@
 sources in our Galaxy should be spatially resolvable at \gev energies.
+
+\todo[inline]{Ask Stefan/Markus if they think we should get rid of
+this note about what point soruces in the plane.}
 
@@
 
-todo[inline]{This text needs to be fixed}
-
-Figure~\ref{diff_factor_sensitivity} shows how the LAT's detection
-threshold increases with increasing background. We compute the threshold
-using 1, 10, and 100 times the Sreekumar-like isotropic background. The
-latter factor approximately represents the intensity of the Galactic
-diffuse emission near the Galactic center.  The figure shows the threshold
-using 1-100 \gev photons and also
-using only 10-100 \gev photons. We
-are less sensitive to extended sources with higher background. Also,
-given the same flux we are more sensitive to the source if those
-photons have a higher energies.
-
-Overlaid on figure~\ref{diff_factor_sensitivity} are the LAT
-detected extended sources from table~\ref{known_extended_sources} and
-table~\ref{new_ext_srcs_table}.  The extended sources are color coded
-based upon whether the galactic diffuse and isotropic emission model is
-closer to 1, 10, or 100 times the Sreekumar-like isotropic spectrum.
-
-Figure 7 shows the flux threshold as a function of source extension for
+Figure~\ref{all_sensitivity}
+shows the flux threshold as a function of source extension for
 different background levels (1x, 10x, and 100x the
@@
 different energy bands (1-100 \gev and 10-100 \gev).
+The detection threshold is higher for sources in regions
+of higher background.
 For a fixed 1-100 \gev or 10-100 \gev
 flux, the LAT's detection threshold is only weakly depends upon the
-spectral index.  This effect is most pronounced when using only photons
+spectral index.  
+Overlaid on figure~\ref{all_sensitivity} are the LAT
+detected extended sources from table~\ref{known_extended_sources} and
+table~\ref{new_ext_srcs_table}.  
+This effect is most pronounced when using only photons
 with energies above 10 \gev. The extension thresholds are tabulated in
 table~\ref{all_sensitivity_table}.
+
+Finally, figure~\ref{time_sensitivity} shows the LAT's projected detection
+threshold to extension after 10 years against 10 times the isotropic
+background. This background is representative of the background near
+the Galactic plane.  For small extended sources, our detection threshold
+improves better than $\sqrt{\text{t}}$ because at high energies, where we
+are most sensitive to extension, the background levels are in the Poisson
+instead of Gaussian regime.  For large extended sources, the relevant
+background is larger and the improvement is closer to $\sqrt{\text{t}}$.
 
@@
 The six extended SNRs IC443, W28, W30, W44, W51C, and the
-Cygnus Loop were included in 2FGL.  IC443, W28, W44, W51C were
-first reported in (\cite{ic443,w28,w44,w51c}).  Detailed papers by the LAT
-collaboration studying W30 and the Cygnus Loop are still in preparation.
+Cygnus Loop were included in 2FGL.  IC443, W28, W44, W51C, and the
+Cygnus Loop were
+first reported in (\cite{ic443,w28,w44,w51c,cygnus_loop_lat}).  A
+detailed publication by the LAT
+collaboration about W30 is still in preparation.
 \gev emission from W30 was also studied in (\cite{castro_and_slane_2010}).
@@
 1FGL had 709 1FGL sources associated with 671 distinct AGN at high
-latitude ($|b|>10\deg$).  An upcoming publication by the LAT collaboration
-will produce a second list 2LAC. 2LAC 
-uses the 2FGL catalog and associates 1017 2FGL sources
-with AGN.  To avoid systematic problems with AGN classification, we
-selected 815 out of the 1017 AGN which made it into the clean AGN sub-sample.  An AGN
+latitude ($|b|>10\deg$).  
+Using two years of data and 2FGL, the LAT collaboraiton
+associated 1016 2FGL sources
+with AGN (\cite{second_agn_cat}).  
+To avoid systematic problems with AGN classification, we
+selected 885 out of the 1016 AGN which made it into the clean AGN sub-sample.  An AGN
 association is considered clean only if it has a high probability
@@
 
-Of the 815 clean AGN, we select 775 of these 2FGL sources which
+Of the 885 clean AGN, we select 783 of these 2FGL sources which
 are significant above 1 \gev and fit each of them for extension.
@@
 The \tsext distribution for AGN shows good agreement with the
-theoretical distribution.  Two sources had $\tsext>9$.  One was due
+theoretical distribution.  Two sources had $\tsext>10$.  One was due
 to incorrectly automatically removing a nearby catalog sources (see
@@
 The results of our investigation of systematic uncertainties of this
-measurement are presented in table~\ref{dual_localization_results}
-and~\ref{alt_diff_model_results}.  Table~\ref{dual_localization_results}
+measurement are presented in 
+table~\ref{alt_diff_model_results}.  It
 shows a comparison between the fit with a single extended source
 hypothesis and the fit assuming the emission originates from two
-independent sources.  Table~\ref{alt_diff_model_results} shows the
+independent sources and  the
 results of the extension fit using variations of the PSF and the galactic
@@
 
-This extended source is spatially coincident with the SNR Puppis A.
-Overlaid on figure~\ref{1FGL_J0823.3-4248} are ROSAT contours of Puppis
-A (\cite{rosat_puppis_a}). There is good agreement between of the X-ray
-shape with the fit size in \gev.
-
-\todo[inline]{Add interpretations of Puppis A.}
-\todo[inline]{Markus says to add an SED.}
+This extended source is spatially coincident with the middle-aged
+SNR Puppis A.  Puppis A has been studied in detail in radio
+(\cite{puppis_a_vla}, and references therein).  X-ray observations
+have been performed by a variety of instruments 
+(\cite{einstein_puppis_a,rosat_puppis_a,chandra_puppis_a,xmm_newton_puppis_a,suzaku_puppis_a})
+The highest resolution image of the entire source was obtained
+by \rosat and contours corresponding to this
+image are overlaid on figure~\ref{1FGL_J0823.3-4248} and match the
+inferred \gev size (\cite{rosat_puppis_a}).
+
+Puppis A's age was estimated to be $\approx3700$ years (\cite{winkler_1988}) and
+its distance was estimated at 2.2 kpc (\cite{ reynoso_1995,reynoso_2003}).
+Assuming this distance, the \gev luminosity of Puppis A between 1 and
+100 \gev is $\approx 3\times 10^{34}$ ergs/\s.
+
+Molecular clouds have not been detected ajacent to Puppis A (\cite{puppis_a_co})
+Similarly, the luminsoity is lower than that of other LAT
+detected SNRs interacting with molecular clouds (\cite{\dots}),.
+The LAT emission could therefore be explained by the interaciton of acclerated
+particles by interstellar matter or fields in the regions, similar
+to what was suggested for the Cygnus Loop SNR (\cite{cygnus_loop_lat}).
+
+Puppis A has not been observed to direct
+% 1 - 100 GeV
+%      Norm      
+%      Index     
+% Flux = PowerLaw(norm=6.21e-14,index=2.22,e0=10000).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
+%      = 4.7804242225163421e-11 ergs/cm^2/s
+% Luminosity =  Flux * 4*pi*r^2 = 4.78e-11 ergs/cm^2/s * 4*pi * (2.2 kpc )**2 in ergs/s
+%            = 2.8e34 ergs/s from 1-100 gev
+
+\todo[inline]{Make point about how this source
+is like Cygnus Loop. Discuss with Yasunobu.  Main points about CO
+Emission / moelcular cloud interactions (\cite{co_eastern_puppis_a}).
+Can we say anything about emission could be hadronic or leptonic models?
+Markus says to add SEDs. Should we?
+}
 
@@
 
-The source 2FGL\,J1627.0-2425c was found 
-using 1-100 \gev photons to have an 
-extension of $0.41\deg\pm0.05\deg_\stat\pm0.02\deg_\sys$ 
-with an extension significance of $\tsext=31.1$. 
-The best fit position is $(l,b)=(353.08\deg, 16.78\deg)$.
-This source is coincident with the one year catalog source 1FGL\,J1628.6-2419c.
-A counts map showing this source is
-seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
+The source 2FGL\,J1627.0-2425c was found using 1-100 \gev photons to
+have an extension of $0.41\deg\pm0.05\deg_\stat\pm0.02\deg_\sys$ with
+an extension significance of $\tsext=31.1$.  The best fit position is
+$(l,b)=(353.08\deg, 16.78\deg)$.  This source is coincident with the one
+year catalog source 1FGL\,J1628.6-2419c.  A counts map showing this source
+is seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
 we also fit the source instead as two point sources. Since $\tsinc=20.0$
@@
 This source is in a region of remarkably complicated diffuse emission.
-Even though it is 16\deg from the Galactic plane, the source is on top
-of the core of the Ophiuchus molecular cloud which contains massive
-star-forming regions that are bright in the infrared.  We have overlaid
-on figure~\ref{1FGL_J1628.6-2419c} contours of the 100 micrometer infared
-image of this region measured by IRAS. There is good spatial overlap
-with the \gev emission (\cite{iras_rho_ophiuci}).
-
-The region also has abundant molecular and atomic gas traced by CO
-and HI but also plenty of dark gas, the kind that we find only by its
-association with dust emission (\cite{isabelle_dark_gass}). Embedded
-star-forming regions make it even more challenging to measure the column
-density of dust.  Therefore this source might represent an inadequacy
-in the diffuse $\gamma$-ray model
+Even though it is 16\deg from the Galactic plane, the source is on
+top of the core of the Ophiuchus molecular cloud which contains massive
+star-forming regions that are bright in the infrared.  The region also has
+abundant molecular and atomic gas traced by CO and HI but also plenty of
+dark gas, the kind that we find only by its association with dust emission
+(\cite{isabelle_dark_gass}). Embedded star-forming regions make it even
+more challenging to measure the column density of dust.  Infared and CO
+contours are overlaid on figure~\ref{1FGL_J1628.6-2419c} and there is good
+spatial correlation with the \gev emission (\cite{iras_rho_ophiuci}).
+Therefore this source might represent an inadequacy in the diffuse
+$\gamma$-ray model
 
@@
 emission by Suzaku (\cite{suzakzu_HESS_J1616-508}), Swift/XRT,
-IBIS/ISGRBI, BeppoSAX and XMM-Newton (\cite{integral_HESS_J1616-508}).
+IBIS/ISGRBI, BeppoSAX and \xmmnewton (\cite{integral_HESS_J1616-508}).
 Finally, \cite{discovery_of_pwn_for_PSR_J1617-5055} found diffuse
@@
 
-\todo[inline]{Swift observations}
-
 Suzaku observations of the region around HESS\,J1614-518 reveale three
@@
 
-Swift observations the region and resolved six X-ray sources.\todo{citation}
-
-\todo[inline]{Emission due to SNR}
-
-\todo[inline]{Emission could be due to a PWN}
-
-\todo[inline]{Emission due to Massive Star}
-
-\todo[inline]{Add interpretations of HESS\,J1614-518. Stefan says to
-Suzaku observations.}
+Swift observations the region and resolved six X-ray sources.
+
+\todo[inline]{Emission due to SNR, PWN, Massive Star. Stefan
+says to add Suzaku observations. Add note about SWIFT observations + citation.}
 
@@
 positionally coincident with the hard X-ray source IGR\,J1632-4751
-observed by INTEGRAL (\cite{Igr_J16320-4751_circ}), XMM-Newton
-(\cite{xmm_newton_IGR_J16320-4751}), and ASCI (\cite{asca_plane_survey}).
+observed by INTEGRAL (\cite{Igr_J16320-4751_circ}), \xmmnewton
+(\cite{xmm_newton_IGR_J16320-4751}), and \asca (\cite{asca_plane_survey}).
 But it is suspected to be an galactic X-Ray Binary so the \gev and \tev
@@
 
-Further observations by XMM-Newton reveal extended emission of size
+Further observations by \xmmnewton reveal extended emission of size
 $\approx32''x\approx15''$ and inside point-like emission coincident with
@@
 
-This source is spatially coincident with the Gamma Cygni SNR.  Contours of
-Gamma Cygni at 408MHz from the Canadian Galactic Plane Survey are overlaid
+This source is spatially coincident with the $\gamma$ Cygni SNR.  Contours of
+$\gamma$ Cygni at 408MHz from the Canadian Galactic Plane Survey are overlaid
 on figure~\ref{1FGL_J2020.0+4049} and there is good spatial agreement
@@
 
-\todo[inline]{
-Add interpretations paragraph.  Describe how this source will be more
-carefully analyzed in ``A cocoon of freshly accelerated cosmic rays
-detected by Fermi in the Cygnus superbubble''}
+\todo[inline]{Add some more information about $\gamma$ cygni.}
 
@@
 about $\approx0.2\deg$).  Fermi has a five year nominal livetime with a
-goal of ten years of operation.  As figure~\ref{time_sensitivity} showes,
+goal of ten years of operation.  As figure~\ref{time_sensitivity} shows,
 our sensitivity to these smaller sources will improve by a factor greater
@@
 
+\clearpage
 \begin{figure}
@@
 
+\clearpage
 \begin{deluxetable}{rrrr}
@@
 }
-
 \end{deluxetable}
-
-\clearpage
 
@@
 \clearpage
-
-% \begin{figure}
-%   \begin{center}
-%     \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
-%     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_diff_factor.py
-%     \end{center}
-%     \caption{
-%     This shows the detection threshold to a uniform disk extended
-%     source for varying background levels
-%     and energy ranges.  The plots have the same meaning as in
-%     figure~\ref{index_sensitivity} and the simulations occur over the
-%     same time range.  The solid blue line is the detection threshold against a
-%     Sreekumar-like isotropic background. The green dashed curve is the
-%     threshold against 10 times the isotropic background and the dash
-%     dotted red curve is the threshold against 100 times the isotropic
-%     background.  The latter factor approximately represents the intensity
-%     of the Galactic diffuse emission near the Galactic center.  Plot (a)
-%     is the threshold using 1-100\gev photons while plot (b) is the threshold using
-%     10-100\gev photons. Unlike figure~\ref{index_sensitivity},
-%     the detection threshold was calculated only for a power-law source of spectral
-%     index 2. The flux is quoted only in the selected energy range which
-%     weakens the dependence of the detection threshold on spectral index.
-%     These plots show that we are less sensitive to extended sources in
-%     regions with higher background and (given the same number of photons)
-%     more sensitive to harder sources.  Overlaid on this plot are the
-%     extended sources found in this extended source search. The extended
-%     sources are color coded based upon whether the integral galactic
-%     diffuse and isotropic diffuse emission model is closer to 1x, 10x,
-%     or 100x the Sreekumar-like isotropic spectrum.  The red point
-%     in plot (a) below the red line is RX J1713.7-3946 which is harder
-%     ($\gamma\approx1.5$) and has diffuse emission only 53 times larger
-%     than the isotropic emission.  The green point in plot (b) below
-%     the green line is MSH 15-52 which was found by our analysis to
-%     have $\tsext=6.5$.  More information about this plot is presented
-%     in section~\ref{extension_sensitivity}.
-%     }\label{diff_factor_sensitivity}
-%   \end{figure}
-
 \begin{figure}
@@
     is integrated only in the selected energy range.  Overlaid on this
-    plot are the LAT detected extended sources placed by the nearby
-    Galactic diffuse emission and color coded by their spectral idnex.
+    plot are the LAT detected extended sources placed by their nearby
+    Galactic diffuse emission and color coded by their spectral index.
     The black point in plot (d) below the green line is MSH 15-52 which
@@
   \thispagestyle{empty}
-  \begin{sidewaystable}\scriptsize
-    \begin{centering}
-      \begin{tabular}{r|r|rrrrrrrrrrrrrrrrrrrr}
+\begin{deluxetable}{rrrrrrrrrrrrrrrrrrrrrrr}
+\tabletypesize{\scriptsize}
+\rotate
+\tablewidth{0pt}
+\tablecaption{Extension Detection Threshold
+\label{all_sensitivity_table}
+}
+\tablehead{
+\colhead{$\gamma$}&       
+\colhead{BG}&
+\colhead{$0.1$}&
+\colhead{$0.2$}&
+\colhead{$0.3$}&
+\colhead{$0.4$}&
+\colhead{$0.5$}&
+\colhead{$0.6$}&
+\colhead{$0.7$}&
+\colhead{$0.8$}&
+\colhead{$0.9$}&
+\colhead{$1.0$}&
+\colhead{$1.1$}&
+\colhead{$1.2$}&
+\colhead{$1.3$}&
+\colhead{$1.4$}&
+\colhead{$1.5$}&
+\colhead{$1.6$}&
+\colhead{$1.7$}&
+\colhead{$1.8$}&
+\colhead{$1.9$}&
+\colhead{$2.0$}
+}
+\startdata
+\multicolumn{22}{c}{E$>$1 \gev} \\
 \hline
-        \hline
-        \multicolumn{22}{c}{$ 1 \gev < E < 100 \gev$} \\
-        \hline
-        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
-        \hline
-             1.5 &       x1 &      148.3 &       23.2 &       11.2 &        8.0 &        7.1 &        6.9 &        6.8 &        6.8 &        7.0 &        7.3 &        7.5 &        7.7 &        8.0 &        8.3 &        9.1 &        9.8 &        9.0 &        9.1 &        8.8 &       10.2 \\
-                 &      x10 &      146.9 &       29.0 &       18.5 &       15.1 &       15.4 &       15.0 &       14.7 &       15.6 &       16.6 &       17.3 &       18.0 &       19.1 &       20.7 &       22.5 &       23.6 &       24.3 &       21.2 &       22.8 &       23.3 &       23.6 \\
-                 &     x100 &      184.3 &       55.1 &       43.0 &       41.0 &       40.7 &       41.7 &       40.3 &       40.8 &       43.0 &       43.6 &       38.3 &       39.5 &       40.1 &       38.5 &       36.5 &       35.8 &       36.5 &       38.1 &       36.6 &       37.1 \\
-               2 &       x1 &      327.5 &       43.1 &       18.7 &       13.3 &       11.2 &       10.4 &       10.1 &       10.1 &       10.2 &       10.4 &       10.6 &       10.9 &       11.1 &       11.5 &       12.3 &       12.6 &       13.0 &       13.4 &       13.8 &       14.2 \\
-                 &      x10 &      336.1 &       55.3 &       32.2 &       27.4 &       26.3 &       25.3 &       25.5 &       25.8 &       27.2 &       26.6 &       27.6 &       28.5 &       30.1 &       29.9 &       30.8 &       31.8 &       31.9 &       34.2 &       34.2 &       36.1 \\
-                 &     x100 &      409.6 &      128.1 &       88.6 &       76.2 &       72.7 &       71.4 &       67.8 &       65.2 &       63.6 &       63.7 &       62.0 &       63.1 &       62.4 &       61.1 &       56.0 &       58.4 &       60.1 &       62.1 &       59.5 &       55.9 \\
-             2.5 &       x1 &      622.9 &       75.0 &       29.6 &       19.0 &       15.5 &       13.6 &       12.8 &       12.7 &       12.4 &       12.5 &       12.6 &       12.9 &       12.8 &       13.1 &       13.4 &       13.7 &       14.1 &       14.6 &       15.0 &       15.7 \\
-                 &      x10 &      641.5 &       98.2 &       51.8 &       39.2 &       34.7 &       33.1 &       32.6 &       32.3 &       33.0 &       33.4 &       33.8 &       34.5 &       34.5 &       35.4 &       37.0 &       37.2 &       35.6 &       36.2 &       37.1 &       37.8 \\
-                 &     x100 &      789.7 &      260.3 &      136.9 &      102.7 &       90.1 &       80.8 &       77.2 &       74.9 &       69.1 &       70.8 &       65.8 &       64.5 &       64.3 &       62.3 &       57.1 &       57.1 &       58.8 &       57.3 &       55.6 &       54.2 \\
-               3 &       x1 &      842.0 &      109.6 &       42.9 &       25.4 &       18.7 &       15.9 &       14.3 &       13.5 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.5 &       13.5 &       13.6 &       14.1 &       14.3 &       14.7 &       15.3 \\
-                 &      x10 &      919.0 &      153.8 &       69.7 &       48.1 &       40.9 &       37.6 &       35.7 &       34.9 &       35.3 &       35.3 &       35.3 &       35.2 &       35.1 &       35.5 &       37.0 &       37.7 &       35.3 &       35.5 &       36.4 &       37.5 \\
-                 &     x100 &     1077.5 &      289.1 &      180.2 &      119.2 &      101.0 &       92.4 &       86.2 &       79.3 &       74.3 &       70.8 &       67.2 &       66.4 &       65.0 &       62.9 &       58.4 &       56.6 &       57.4 &       55.9 &       54.3 &       52.2 \\
-        \hline
-        \multicolumn{22}{}{} \\
-        \multicolumn{22}{}{} \\
-        \hline
-        \hline
-        \multicolumn{22}{c}{$ 10 \gev < E < 100 \gev$} \\
-        \hline
-        $\gamma$ &       BG &  $0.1\deg$ &  $0.2\deg$ &  $0.3\deg$ &  $0.4\deg$ &  $0.5\deg$ &  $0.6\deg$ &  $0.7\deg$ &  $0.8\deg$ &  $0.9\deg$ &    $1\deg$ &  $1.1\deg$ &  $1.2\deg$ &  $1.3\deg$ &  $1.4\deg$ &  $1.5\deg$ &  $1.6\deg$ &  $1.7\deg$ &  $1.8\deg$ &  $1.9\deg$ &    $2\deg$ \\
-        \hline
-             1.5 &       x1 &       44.4 &        8.1 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.4 &        2.5 &        2.6 &        2.7 &        2.7 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
-                 &      x10 &       45.2 &        9.3 &        5.9 &        5.0 &        4.9 &        5.1 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.2 &        6.6 &        6.5 &        7.0 &        7.7 &        7.8 &        8.2 &        8.4 &        8.8 \\
-                 &     x100 &       47.2 &       13.5 &       11.5 &       10.6 &       10.6 &       10.8 &       12.0 &       12.7 &       13.3 &       13.7 &       15.2 &       16.1 &       17.2 &       18.2 &       19.1 &       19.8 &       20.7 &       21.3 &       22.1 &       23.4 \\
-               2 &       x1 &       49.6 &        8.3 &        4.4 &        3.2 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
-                 &      x10 &       48.5 &        9.6 &        6.0 &        5.2 &        5.1 &        5.2 &        5.2 &        5.4 &        5.5 &        5.8 &        6.4 &        6.7 &        7.0 &        7.2 &        7.6 &        8.0 &        8.3 &        8.7 &        9.0 &        9.3 \\
-                 &     x100 &       51.5 &       14.8 &       11.8 &       11.5 &       11.5 &       12.0 &       13.1 &       14.0 &       14.4 &       15.3 &       16.1 &       16.8 &       18.5 &       19.3 &       20.1 &       21.3 &       22.3 &       23.1 &       23.4 &       24.5 \\
-             2.5 &       x1 &       53.0 &        9.2 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.8 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.4 &        3.5 &        3.6 \\
-                 &      x10 &       53.8 &       10.6 &        6.3 &        5.4 &        5.1 &        5.2 &        5.3 &        5.5 &        5.7 &        6.1 &        6.4 &        6.6 &        6.9 &        7.3 &        7.5 &        8.2 &        8.4 &        8.7 &        9.0 &        9.4 \\
-                 &     x100 &       56.6 &       15.8 &       12.9 &       11.9 &       11.9 &       12.4 &       13.1 &       14.3 &       14.7 &       15.2 &       16.3 &       17.0 &       18.9 &       19.3 &       20.1 &       21.2 &       22.2 &       22.7 &       23.6 &       24.1 \\
-               3 &       x1 &       55.1 &        9.3 &        4.7 &        3.3 &        2.9 &        2.6 &        2.5 &        2.5 &        2.5 &        2.5 &        2.6 &        2.6 &        2.7 &        2.8 &        2.9 &        3.0 &        3.0 &        3.2 &        3.4 &        3.4 \\
-                 &      x10 &       55.7 &       10.5 &        6.3 &        5.3 &        5.2 &        5.3 &        5.2 &        5.4 &        5.6 &        5.7 &        6.0 &        6.4 &        6.6 &        6.9 &        7.1 &        7.9 &        8.1 &        8.5 &        8.7 &        8.9 \\
-                 &     x100 &       60.1 &       16.0 &       12.8 &       11.7 &       11.7 &       12.3 &       12.7 &       14.0 &       14.1 &       14.6 &       15.8 &       16.5 &       17.6 &       18.6 &       19.5 &       19.9 &       21.0 &       21.3 &       22.0 &       22.9 \\
-        \hline
-      \end{tabular}
-      \caption{The detection threshold to resolve a uniform disk spatially
-      extended sources using two years of data for sources of varying
-      spectral index and extension against varying background levels
-      with different energy ranges.  The upper table is the sensitivity
-      when using photons with energies from 1-100 \gev and the bottom
-      table when using 10-100 \gev photons. The first column is
-      the extended source's spectral index.  The extended sources
-      were simulated against a Sreekumar-like isotropic spectrum and
-      the second column is the factor that the simulated background
-      was scaled by. The remaining columns are varying sizes of the
-      source assuming a uniform surface brightness. The table quotes integral
-      fluxes in the analyzed energy range in units of
-      $10^{-10} \ph/\cm^2/\sec$.  
-      }\label{all_sensitivity_table}
-    \end{centering}
-  \end{sidewaystable}
+     1.5 &       x1 &      148.1 &       23.3 &       11.3 &        8.0 &        7.2 &        6.9 &        6.7 &        6.8 &        7.1 &        7.4 &        7.6 &        7.9 &        8.1 &        8.5 &        9.2 &        9.9 &        9.1 &        9.2 &        9.0 &       10.3 \\
+         &      x10 &      148.4 &       29.0 &       18.7 &       15.2 &       15.4 &       15.0 &       16.1 &       16.0 &       16.8 &       17.7 &       18.2 &       19.3 &       20.9 &       22.5 &       23.8 &       24.8 &       21.3 &       22.8 &       23.4 &       23.7 \\
+         &     x100 &      186.8 &       55.0 &       43.4 &       40.7 &       41.0 &       41.8 &       40.9 &       40.9 &       42.7 &       43.6 &       38.4 &       39.9 &       40.6 &       38.4 &       36.9 &       36.3 &       37.1 &       38.8 &       37.2 &       37.6 \\
+       2 &       x1 &      328.4 &       43.4 &       18.9 &       13.4 &       11.2 &       10.4 &       10.2 &       10.2 &       10.2 &       10.4 &       10.7 &       10.9 &       11.2 &       11.5 &       12.4 &       12.6 &       13.0 &       13.4 &       14.0 &       14.4 \\
+         &      x10 &      341.0 &       55.9 &       32.3 &       27.6 &       26.5 &       25.4 &       25.6 &       25.9 &       27.4 &       26.8 &       27.8 &       28.7 &       29.8 &       30.1 &       31.0 &       31.5 &       31.7 &       34.0 &       34.3 &       35.9 \\
+         &     x100 &      420.5 &      128.3 &       90.2 &       77.3 &       73.3 &       70.8 &       67.5 &       64.3 &       64.2 &       64.1 &       62.8 &       63.6 &       61.7 &       61.9 &       58.4 &       59.0 &       61.4 &       63.3 &       60.1 &       58.1 \\
+     2.5 &       x1 &      627.1 &       75.6 &       29.8 &       19.3 &       15.5 &       13.5 &       12.8 &       12.6 &       12.5 &       12.5 &       12.6 &       12.9 &       12.9 &       13.1 &       13.5 &       13.7 &       14.3 &       14.8 &       15.2 &       15.8 \\
+         &      x10 &      638.9 &       99.1 &       52.1 &       39.1 &       34.6 &       33.0 &       32.5 &       32.5 &       32.8 &       33.2 &       34.1 &       34.3 &       34.5 &       35.1 &       36.6 &       36.9 &       35.5 &       36.0 &       36.5 &       37.3 \\
+         &     x100 &      795.0 &      262.1 &      140.9 &      104.3 &       90.4 &       81.2 &       77.2 &       75.1 &       69.7 &       70.9 &       66.5 &       65.6 &       64.9 &       64.0 &       58.9 &       58.1 &       60.2 &       58.4 &       57.5 &       55.8 \\
+       3 &       x1 &      841.5 &      110.6 &       43.2 &       25.5 &       18.7 &       16.1 &       14.4 &       13.6 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.6 &       13.5 &       13.8 &       14.2 &       14.4 &       14.8 &       15.4 \\
+         &      x10 &      921.6 &      151.3 &       69.1 &       47.8 &       40.7 &       37.1 &       35.5 &       34.5 &       35.1 &       35.5 &       35.3 &       35.3 &       35.4 &       35.5 &       36.8 &       37.6 &       35.3 &       35.4 &       36.3 &       36.6 \\
+         &     x100 &     1124.1 &      282.9 &      181.1 &      119.8 &      100.7 &       91.1 &       84.3 &       77.9 &       73.3 &       71.8 &       67.6 &       66.4 &       65.5 &       63.9 &       59.0 &       58.6 &       58.8 &       57.5 &       55.4 &       54.4 \\
+\cutinhead{E$>$10 \gev}
+     1.5 &       x1 &       44.6 &        8.0 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.5 &        2.5 &        2.6 &        2.7 &        2.8 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
+         &      x10 &       45.2 &        9.2 &        5.8 &        5.0 &        4.9 &        4.9 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.3 &        6.6 &        6.5 &        6.8 &        7.6 &        7.8 &        8.2 &        8.5 &        8.7 \\
+         &     x100 &       47.3 &       13.4 &       11.6 &       10.6 &       10.8 &       10.8 &       12.0 &       12.7 &       13.2 &       13.7 &       15.3 &       16.1 &       17.2 &       18.2 &       18.9 &       19.5 &       20.4 &       21.0 &       21.7 &       22.9 \\
+       2 &       x1 &       49.7 &        8.4 &        4.4 &        3.3 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
+         &      x10 &       48.6 &        9.5 &        6.0 &        5.2 &        5.0 &        5.2 &        5.2 &        5.3 &        5.4 &        5.8 &        6.4 &        6.6 &        7.0 &        7.1 &        7.5 &        8.0 &        8.3 &        8.6 &        9.0 &        9.2 \\
+         &     x100 &       51.8 &       14.7 &       11.8 &       11.5 &       11.5 &       11.9 &       13.2 &       14.0 &       14.3 &       15.3 &       16.2 &       16.9 &       18.4 &       19.2 &       19.8 &       21.0 &       22.0 &       22.8 &       23.2 &       24.3 \\
+     2.5 &       x1 &       53.1 &        9.1 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.8 &        2.9 &        3.1 &        3.2 &        3.3 &        3.5 &        3.6 \\
+         &      x10 &       53.7 &       10.5 &        6.3 &        5.4 &        5.1 &        5.1 &        5.3 &        5.4 &        5.7 &        6.0 &        6.3 &        6.6 &        6.8 &        6.9 &        7.5 &        8.1 &        8.3 &        8.6 &        8.9 &        9.2 \\
+         &     x100 &       57.0 &       15.6 &       12.7 &       11.9 &       11.8 &       12.2 &       13.1 &       14.3 &       14.6 &       15.2 &       16.3 &       17.0 &       18.8 &       19.2 &       19.9 &       21.0 &       21.9 &       22.3 &       23.3 &       23.7 \\
+       3 &       x1 &       55.5 &        9.4 &        4.8 &        3.4 &        2.9 &        2.7 &        2.6 &        2.5 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 \\
+         &      x10 &       56.0 &       10.5 &        6.2 &        5.3 &        5.1 &        5.1 &        5.1 &        5.3 &        5.5 &        5.7 &        5.9 &        6.4 &        6.4 &        6.6 &        7.0 &        7.8 &        8.0 &        8.3 &        8.6 &        8.9 \\
+         &     x100 &       60.3 &       16.2 &       12.7 &       11.7 &       11.8 &       12.2 &       12.6 &       13.8 &       14.2 &       14.6 &       15.8 &       16.5 &       17.6 &       18.5 &       19.4 &       19.8 &       20.7 &       21.0 &       21.8 &       22.5 \\
+\enddata
+\tablecomments{
+      The detection threshold to resolve a uniform disk spatially extended
+      sources using two years of data for sources of varying energy
+      ranges, spectral indices, and background levels.  The extended
+      sources were simulated against a Sreekumar-like isotropic spectrum
+      and the second column is the factor that the simulated background
+      was scaled by. The remaining columns are varying sizes of the source
+      in degrees assuming a uniform surface brightness. The table quotes
+      integral fluxes in the analyzed energy range (1-100 \gev or 10-100
+      \gev) in units of $10^{-10}\ph/\cm^2/\sec$.
+      }
+\end{deluxetable}
 
@@
     \caption{
-    Our projected sensitivity to extension after 10 years for a power-law
+    The LAT's projected detection theshold to extension after 10 years for a power-law
     source of spectral index 2 against 10 times the isotropic background
     in the energy range from 1-100 \gev (solid red) and 10-100 \gev
-    (dashed blue). This background is representative of the background
-    near the Galactic plane.  The solid gray region is the projected
+    (dashed blue). The solid gray region is the 
     detection threshold assuming the sensitivity improves from the 2
@@
     sensitivity.  For small extended sources, our detection threshold
-    improves better than $\sqrt{\text{t}}$ because at high energies where
-    we are most sensitive to extension, the background levels are in the
-    Poisson instead of Gaussian regime.  For large extended sources,
-    the relevant background is larger and the improvement is closer
-    to $\sqrt{\text{t}}$.
+    improves by a factor better than $\sqrt{\text{t}}$. 
     }\label{time_sensitivity}
@@
     \caption{
-    A Galactic and isotropic diffuse subtracted 1-100 \gev counts map of
-    the region around 2FGL\,J1856.2+0450c smoothed by a 0.1\deg Gaussian
-    kernel. The red cross and circle are the center and size of the
-    best fit radially symmetric uniform surface brightness extension
-    model. The result is statistically
-    significant, but the extension encompasses many catalog sources and
-    the emission does not look to be uniform. Instead, this source is
-    probably fitting large-scale diffuse residual features. Although the
-    fit is statistically significant, it is not physical and we manually
-    discard candidates that appear like this.
+    A Diffuse emission subtracted 1-100 \gev counts map of the region
+    around 2FGL\,J1856.2+0450c smoothed by a 0.1\deg Gaussian kernel. The
+    red cross and circle are the center and size of the best fit radially
+    symmetric source with a uniform intensity profile. The result is
+    statistically significant, but the extension encompasses many catalog
+    sources and the emission does not look to be uniform. Instead,
+    this source is probably fitting large-scale diffuse residual
+    features. Although the fit is statistically significant, it likely
+    corresponds to residual features of inaccurately modeled diffuse
+    emission picked up by the fit.  We manually discard candidates that
+    appear like this.
     }
@@
 
-  \caption{An example residual test statistic map generated for the
-  supernova remnant IC443 using 1-100 \gev photons. 
-  Plot (a) is the residual \ts fitting IC443 as a point
-  source and plot (b) is the residual TS fitting IC443 as an extended
-  source. The crosses in the plot represent all of the sources modeled
-  in the region. Since there is residual TS greater than 160 fitting
-  with the point hypothesis so it is not a good model of the source.
-  On the other hand, the residual fitting IC443 as an extended source
-  is much lower because IC443 is better fit by an extended source. These
-  plots were generated for all extended source candidates to help validate
-  the analysis.}
+  \caption{
+  A test statistic map generated for the region around supernova
+  remnant IC443 using 1-100 \gev photons.  (a) test statistic map after
+  subtracting IC443 modeled as a point source. (b) same as (a), but
+  IC443 modeled as extended source. Crosses represent sources included
+  in the model of the region.  Such maps were generated for all extended
+  source candidates.}
   \label{res_tsmaps}
@@
 
-\clearpage
-\begin{sidewaystable}
-    \begin{centering}
-      \begin{tabular}{l|rrlrrrrrrr}
+\begin{deluxetable}{lrrrrrrrr}
+\rotate
+\tabletypesize{\footnotesize}
+\tablewidth{0pt}
+\tablecaption{Extension fit for the twelve extended sources included in 2FGL
+\label{known_extended_sources}
+}
+\tablehead{
+\colhead{Name}&
+\colhead{\glon\tablenotemark{a}}&
+\colhead{\glat\tablenotemark{a}}&
+\colhead{$\sigma$\tablenotemark{a}}&
+\colhead{\ts}&
+\colhead{\tsext}&
+\colhead{Pos Err\tablenotemark{a}}&
+\colhead{Flux\tablenotemark{b}}&
+\colhead{Index}
+}
+
+\startdata
+\multicolumn{9}{c}{E$>$1 \gev} \\
 \hline
-        \hline
-        Name                 &          \glon &          \glat &                \multicolumn{1}{r}{$\sigma$} &         TS &   $\tsext$ &    Pos Err &                  Flux &                 Index  \\
-        \hline
-        \multicolumn{9}{c}{$E > 1 \gev$} \\
-        \hline
-        SMC                  &     302.68\deg &     -44.81\deg & $  1.75\deg \pm   0.07\deg \pm   0.02\deg $ &       94.8 &       67.4 &   0.12\deg & $    3.3 \pm     0.4$ & $   2.41 \pm    0.17$  \\
-        LMC                  &     279.10\deg &     -32.61\deg & $  1.74\deg \pm   0.05\deg \pm   0.13\deg $ &     1101.3 &      860.5 &   0.05\deg & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$  \\
-        IC443                &     189.05\deg &       3.04\deg & $  0.36\deg \pm   0.01\deg \pm   0.04\deg $ &    10719.8 &      510.4 &   0.01\deg & $   64.8 \pm     1.2$ & $   2.23 \pm    0.02$  \\
-        Vela X               &     263.34\deg &      -3.11\deg & $                                 0.88\deg$ &            &            &            &                       &                       \\
-        Centarus A           &     309.52\deg &      19.42\deg & $                            \approx10\deg$ &            &            &            &                       &                       \\
-        W28                  &       6.50\deg &      -0.27\deg & $  0.43\deg \pm   0.02\deg \pm   0.03\deg $ &     1324.8 &      177.4 &   0.01\deg & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$  \\
-        W30                  &       8.61\deg &      -0.20\deg & $  0.36\deg \pm   0.02\deg \pm   0.02\deg $ &      465.4 &       73.3 &   0.02\deg & $   30.7 \pm     1.6$ & $   2.59 \pm    0.04$  \\
-        W44                  &      34.69\deg &      -0.38\deg & $  0.36\deg \pm   0.01\deg \pm   0.02\deg $ &     1903.3 &      217.7 &   0.01\deg & $   73.6 \pm     1.8$ & $   2.68 \pm    0.02$  \\
-        W51C                 &      49.13\deg &      -0.45\deg & $  0.28\deg \pm   0.02\deg \pm   0.05\deg $ &     1819.5 &      115.7 &   0.01\deg & $   39.3 \pm     1.3$ & $   2.35 \pm    0.03$  \\
-        Cygnus Loop          &      74.22\deg &      -8.46\deg & $  1.72\deg \pm   0.05\deg \pm   0.07\deg $ &      356.5 &      356.5 &   0.06\deg & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$  \\
-        \hline
-        \multicolumn{9}{c}{$E > 10 \gev$} \\
-        \hline
-        MSH 15-52            &     320.38\deg &      -1.22\deg & $  0.20\deg \pm   0.04\deg \pm   0.03\deg $ &       76.2 &        6.5 &   0.03\deg & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
-        HESS J1825-137       &      17.56\deg &      -0.46\deg & $  0.65\deg \pm   0.03\deg \pm   0.01\deg $ &       83.6 &       55.9 &   0.05\deg & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
-        \hline
-        \hline
-      \end{tabular}
-      \caption{The twelve extended sources included in 2FGL.  The top
-      list are the extended sources analyzed using 1-100 \gev photons.  
-      The lower table are the sources
-      analyzed using 10-100 \gev photons.
-      The quoted flux is in units of $10^{-9}\ph/\cm^2/\sec$ and is the
-      flux in the fit energy range (either 1-100 \gev or 10-100 \gev).
-      All sources were fit using a uniform disk spatial template. The
-      localization and extension were found using \pointlike while the
-      TS and spectral values were calculated using \gtlike.  \ts and
-      \tsext was computed with \gtlike assuming the best fit radially
-      symmetric uniform surface brightness from \pointlike.  \glon and \glat are Galactic
-      longitude and latitude of the best fit extended source respectively.
-      $\sigma$ is the edge of the best fit radially
-      symmetric uniform surface brightness model.
-      The first error on $\sigma$ is statistical and the second error
-      is systematic (see section~\ref{systematic_errors_on_extension}).
-      Pos Err is the error on the localization of the source.  Statistical
-      errors are at the $1\sigma$ level.  The Vela X and the Centarus A
-      Lobes were not fit by our analysis but are include for completeness
-      (\cite{velax,cen_a_lat}). More information about these sources is
-      in section~\ref{validate_known}.
-      }
-      \label{known_extended_sources}
-    \end{centering}
-\end{sidewaystable}
+SMC                  &     302.68 &     -44.81 & $  1.75 \pm   0.07 \pm   0.02 $ &       94.8 &       67.4 &   0.12 & $    3.3 \pm     0.4$ & $   2.41 \pm    0.17$  \\
+LMC                  &     279.10 &     -32.61 & $  1.74 \pm   0.05 \pm   0.13 $ &     1101.3 &      860.5 &   0.05 & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$  \\
+IC443                &     189.05 &       3.04 & $  0.36 \pm   0.01 \pm   0.04 $ &    10719.8 &      510.4 &   0.01 & $   64.8 \pm     1.2$ & $   2.23 \pm    0.02$  \\
+Vela X               &     263.34 &      -3.11 & $                         0.88$ &            &            &        &                       &                        \\
+Centarus A           &     309.52 &      19.42 &                     $\approx10$ &            &            &        &                       &                        \\
+W28                  &       6.50 &      -0.27 & $  0.43 \pm   0.02 \pm   0.03 $ &     1324.8 &      177.4 &   0.01 & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$  \\
+W30                  &       8.61 &      -0.20 & $  0.36 \pm   0.02 \pm   0.02 $ &      465.4 &       73.3 &   0.02 & $   30.7 \pm     1.6$ & $   2.59 \pm    0.04$  \\
+W44                  &      34.69 &      -0.38 & $  0.36 \pm   0.01 \pm   0.02 $ &     1903.3 &      217.7 &   0.01 & $   73.6 \pm     1.8$ & $   2.68 \pm    0.02$  \\
+W51C                 &      49.13 &      -0.45 & $  0.28 \pm   0.02 \pm   0.05 $ &     1819.5 &      115.7 &   0.01 & $   39.3 \pm     1.3$ & $   2.35 \pm    0.03$  \\
+Cygnus Loop          &      74.22 &      -8.46 & $  1.72 \pm   0.05 \pm   0.07 $ &      356.5 &      356.5 &   0.06 & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$  \\
+\cutinhead{E$>$10 \gev}
+MSH 15-52            &     320.38 &      -1.22 & $  0.20 \pm   0.04 \pm   0.03 $ &       76.2 &        6.5 &   0.03 & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
+HESS J1825-137       &      17.56 &      -0.46 & $  0.65 \pm   0.03 \pm   0.01 $ &       83.6 &       55.9 &   0.05 & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
+\enddata
+
+\tablenotetext{a}{in degrees.}
+\tablenotetext{b}{
+integrated in the fit energy range (either 1-100 \gev or 10-100 \gev)
+in units of $10^{-9}\ph/\cm^2/\sec$.
+}
+
+\tablecomments{
+All sources were fit using a spatial model assuming a uniform radially
+symmetric intensity distribution. \glon and \glat are Galactic longitude
+and latitude of the best fit extended source respectively.  The first
+error on $\sigma$ is statistical and the second is systematic (see
+section~\ref{systematic_errors_on_extension}).  Pos Err is the error on
+the position of the source.  Vela X and the Centarus A Lobes were
+not fit by our analysis but are include for completeness.
+}
+\end{deluxetable}
 
@@
     \end{center}
-    \caption{The cumulative density of \tsext for 775 of
-    the clean AGN in 2LAC which are significant above 1 \gev.
-    AGN are expected to be unresolvable so overlaid on this plot
-    is a $\chi^2/2$ distribution suggested by Wilks' theorem (see
-    section~\ref{monte_carlo_validation}).  The \tsext distribution
-    computed with \pointlike agrees with Wilks' theorem and confirms
-    that we can use \tsext as a test of extension. The distribution
-    computed by \gtlike is biased towards smaller values of \tsext. This
-    is because \tsext is optimized using \pointlike and minor difference
-    in the \pointlike and \gtlike likelihood function will cause the
-    best fit model to be slightly different. Because \gtlike's curve
-    lies to the left of the theoretical distribution, this makes our
-    test conservative. More information about this analysis is presented
-    in section~\ref{test_2lac_sources}.
+    \caption{The cumulative density of \tsext for 783 of the clean
+    AGN in 2LAC which are significant above 1 \gev.  AGNs are too far
+    and too small to be resolved by the LAT. Therefore, the cumulative
+    density of $\tsext$ is expected to follow a $\chi^2/2$ distribution
+    (equation~\ref{ts_ext_distribution}).     
     }\label{agn_ts_ext}
@@
 \thispagestyle{empty}
-\begin{sidewaystable}
-  \begin{centering}
-    \begin{tabular}{l|rrlrrrrrrr}
+\begin{deluxetable}{lrrrrrrrrr}
+\tabletypesize{\small}
+\rotate
+\tablewidth{0pt}
+\tablecaption{Extension fit for the nine new extended sources
+\label{new_ext_srcs_table}
+}
+\tablehead{
+\colhead{Name}&
+\colhead{\glon}&
+\colhead{\glat}&
+\colhead{$\sigma$}&
+\colhead{\ts}&
+\colhead{\tsext}&
+\colhead{Pos Err}&
+\colhead{Flux}&
+\colhead{Index}&
+\colhead{Counterpart}
+}
+
+\startdata
+\multicolumn{10}{c}{E$>$1 \gev} \\
 \hline
+2FGL\,J0823.0-4246   &     260.32 &      -3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      320.9 &       46.3 &   0.02 & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
+2FGL\,J1627.0-2425c  &     353.08 &      16.78 & $  0.41 \pm   0.05 \pm   0.02 $ &      144.5 &       31.1 &   0.04 & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
+2FGL\,J1712.4-3941   &     347.25 &      -0.54 & $  0.56 \pm   0.04 \pm   0.01 $ &       75.0 &       39.6 &   0.05 & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
+\cutinhead{E$>$10 \gev}
+2FGL\,J0851.7-4635   &     266.29 &      -1.43 & $  1.13 \pm   0.08 \pm   0.05 $ &      116.1 &       87.2 &   0.07 & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr. \\
+2FGL\,J1615.0-5051   &     332.38 &      -0.14 & $  0.33 \pm   0.04 \pm   0.01 $ &       53.4 &       16.3 &   0.04 & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
+2FGL\,J1615.2-5138   &     331.66 &      -0.66 & $  0.42 \pm   0.03 \pm   0.01 $ &       76.6 &       48.0 &   0.05 & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
+2FGL\,J1632.4-4753c  &     336.41 &       0.22 & $  0.44 \pm   0.04 \pm   0.03 $ &      127.8 &       64.5 &   0.04 & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
+2FGL\,J1837.3-0700c  &      25.08 &       0.13 & $  0.35 \pm   0.08 \pm   0.03 $ &       46.2 &       18.8 &   0.07 & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
+2FGL\,J2021.5+4026   &      78.18 &       2.19 & $  0.59 \pm   0.03 \pm   0.02 $ &      222.2 &      116.4 &   0.04 & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &       $\gamma$ Cygni \\
+\enddata
+
+\tablecomments{
+    The columns in this table
+    are equivalent to the columns in table~\ref{known_extended_sources}.
+}
+\end{deluxetable}
+
+\clearpage
+\thispagestyle{empty}
+\begin{deluxetable}{lrrrrrrrrrr}
+  \rotate
+  \tablewidth{0pt}
+  \tablecaption{Dual localization, alternative PSF, and alternative diffuse results
+  \label{alt_diff_model_results}
+  }
+  \tablehead{
+  \colhead{Name}&
+  \colhead{$\ts_\pointlike$}&
+  \colhead{$\ts_\gtlike$}&
+  \colhead{$\ts_\altdiff$}&
+  \colhead{$\tsext_\pointlike$}&
+  \colhead{$\tsext_\gtlike$}&
+  \colhead{$\tsext_\altdiff$}&
+  \colhead{$\sigma$\tablenotemark{a}}&
+  \colhead{$\sigma_\altdiff$\tablenotemark{a}}&
+  \colhead{$\sigma_\altpsf$\tablenotemark{a}}&
+  \colhead{$\tsinc$}
+  }
+  \startdata
+  \multicolumn{11}{c}{E$>$1 \gev} \\
   \hline
-      Name                 &          \glon &          \glat &                \multicolumn{1}{r}{$\sigma$} &         TS &   $\tsext$ &    Pos Err &                  Flux &                 Index &          Counterpart \\
-      \hline
-      \multicolumn{10}{c}{$E > 1 \gev$} \\
-      \hline
-      2FGL\,J0823.0-4246   &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg \pm   0.02\deg $ &      320.9 &       46.3 &   0.02\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
-      2FGL\,J1627.0-2425c  &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg \pm   0.02\deg $ &      144.5 &       31.1 &   0.04\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
-      2FGL\,J1712.4-3941   &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg \pm   0.01\deg $ &       75.0 &       39.6 &   0.05\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
-      \hline
-      \multicolumn{10}{c}{$E > 10 \gev$} \\
-      \hline
-      2FGL\,J0851.7-4635   &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg \pm   0.05\deg $ &      116.1 &       87.2 &   0.07\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr.
-\\
-      2FGL\,J1615.0-5051   &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg \pm   0.01\deg $ &       53.4 &       16.3 &   0.04\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
-      2FGL\,J1615.2-5138   &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg \pm   0.01\deg $ &       76.6 &       48.0 &   0.05\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
-      2FGL\,J1632.4-4753c  &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg \pm   0.03\deg $ &      127.8 &       64.5 &   0.04\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
-      2FGL\,J1837.3-0700c  &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg \pm   0.03\deg $ &       46.2 &       18.8 &   0.07\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
-      2FGL\,J2021.5+4026   &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg \pm   0.02\deg $ &      222.2 &      116.4 &   0.04\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &          Gamma Cygni \\
-      \hline
-  \end{tabular}
-    \caption{The 9 new source candidates found by the extended source
-    search. Three new extended sources were found using photons with
-    energies above 1 \gev and five new candidates were found using
-    photons with energies above 10 \gev.  The columns in this table
-    have the same meaning as in table~\ref{known_extended_sources}.
-    More information about these sources can be found in
-    section~\ref{new_ext_srcs_section}.
-    }
-    \label{new_ext_srcs_table}
-  \end{centering}
-\end{sidewaystable}
-
-\clearpage
-\begin{sidewaystable}
-    \begin{centering}
-      \begin{tabular}{l|rr|rrrr|rrrr}
-        \hline
-        \hline
-        Name                 &     \tsinc &     \tsext &      $\glon_1$ &      $\glat_1$ &   $\text{Flux}_1$ &   $\text{Index}_1$ &      $\glon_2$ &      $\glat_2$ &   $\text{Flux}_2$ &  $\text{Index}_2$ \\
-        \hline
-        \multicolumn{11}{c}{$E > 1 \gev$} \\
-        \hline
-        2FGL\,J0823.0-4246   &       22.1 &       46.3 &     260.59\deg &      -3.27\deg & $       2.1 \pm        0.6$ & $  2.0 \pm   0.2$  &     260.24\deg &      -3.20\deg & $       5.4 \pm        0.7$ & $  2.4 \pm   0.2$ \\
-        2FGL\,J1627.0-2425c  &       20.0 &       31.1 &     353.01\deg &      16.98\deg & $       3.1 \pm        0.6$ & $  2.6 \pm   0.3$  &     353.24\deg &      16.66\deg & $       2.5 \pm        0.6$ & $  2.5 \pm   0.4$ \\
-        2FGL\,J1712.4-3941   &        6.4 &       39.6 &     347.28\deg &      -0.07\deg & $       0.2 \pm        0.1$ & $  0.6 \pm   0.5$  &     347.22\deg &      -0.27\deg & $       2.4 \pm        0.7$ & $  1.9 \pm   0.2$ \\
-        \hline
-        \multicolumn{11}{c}{$E > 10 \gev$} \\
-        \hline
-        2FGL\,J0851.7-4635   &       16.1 &       87.2 &     266.79\deg &      -1.32\deg & $       0.2 \pm        0.1$ & $  1.8 \pm   0.5$  &     266.41\deg &      -1.39\deg & $       0.2 \pm        0.1$ & $  1.5 \pm   0.6$ \\
-        2FGL\,J1615.0-5051   &       11.9 &       16.3 &     332.39\deg &      -0.08\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.6$  &     332.43\deg &      -0.36\deg & $       0.4 \pm        0.1$ & $  2.3 \pm   0.5$ \\
-        2FGL\,J1615.2-5138   &       37.0 &       48.0 &     331.76\deg &      -0.37\deg & $       0.4 \pm        0.1$ & $  1.3 \pm   0.5$  &     331.47\deg &      -0.80\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.4$ \\
-        2FGL\,J1632.4-4753c  &       40.6 &       64.5 &     336.52\deg &       0.17\deg & $       0.7 \pm        0.2$ & $  2.8 \pm   0.5$  &     336.13\deg &       0.37\deg & $       0.5 \pm        0.1$ & $  1.7 \pm   0.4$ \\
-        2FGL\,J1837.3-0700c  &       12.6 &       18.8 &      25.04\deg &       0.26\deg & $       0.3 \pm        0.1$ & $  1.2 \pm   0.5$  &      25.10\deg &      -0.05\deg & $       0.4 \pm        0.1$ & $  2.0 \pm   0.5$ \\
-        2FGL\,J2021.5+4026   &       24.3 &      116.4 &      78.28\deg &       1.95\deg & $       0.3 \pm        0.1$ & $  5.0 \pm   0.0$  &      78.15\deg &       2.20\deg & $       0.6 \pm        0.1$ & $  1.7 \pm   0.4$ \\
-        \hline
-      \end{tabular}
-      \caption{For the new extended source candidates
-      in table~\ref{new_ext_srcs_table}, we describe the
-      results of the dual localization procedure described in
-      section~\ref{dual_localization_method}. Here, the extended
-      source candidate is not fit as an extended source but instead
-      fit as two point sources.  The dual localization is performed
-      with \pointlike and results in the best fit position of the two
-      sources $(\glon_1,\glat_1)$ and $(\glon_2,\glat_2)$.  The change
-      in likelihood and spectral values are then computed using \gtlike
-      with the best fit positions found by \pointlike.  \tsinc is the
-      increase in TS fitting the region as two sources compared to
-      fitting compared to fitting a single point source and is computed
-      using \gtlike with the best fit positions taken from \pointlike.
-      It can be directly compared to \tsext, which is taken from
-      table~\ref{new_ext_srcs_table}.  For all of our candidates, $\tsext
-      > \tsinc$ which shows that an extended source fits the source better
-      than two point sources.  As in table~\ref{known_extended_sources},
-      flux is measured in units of $10^{-9}\ph/\cm^2/\sec$ and is either
-      the 1-100 \gev or 10-100 \gev photon flux.
-      }
-      \label{dual_localization_results}
-    \end{centering}
-  \end{sidewaystable}
-
-  \clearpage
-  \begin{sidewaystable}
-    \begin{centering}
-      \begin{tabular}{l|rrr|rrr|rrr}
-        \hline
-        \hline
-        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &       $\ts_\altdiff$ &      $\tsext_\pointlike$ &       $\tsext_\gtlike$ &    $\tsext_\altdiff$ &                $\sigma$ &       $\sigma_\altdiff$ &        $\sigma_\altpsf$ \\
-        \hline
-        \multicolumn{10}{c}{$E > 1 \gev$} \\
-        \hline
-        2FGL\,J0823.0-4246   &                350.9 &                320.9 &                352.5 &                     66.0 &                   46.3 &                 53.6 & $             0.37\deg$ & $             0.39\deg$ & $             0.38\deg$ \\
-        2FGL\,J1627.0-2425c  &                170.2 &                144.5 &                112.6 &                     43.9 &                   31.1 &                 23.9 & $             0.41\deg$ & $             0.40\deg$ & $             0.39\deg$ \\
-        2FGL\,J1712.4-3941   &                 80.9 &                 75.0 &                 43.4 &                     47.4 &                   39.6 &                 22.2 & $             0.56\deg$ & $             0.56\deg$ & $             0.54\deg$ \\
-        \hline
-        \multicolumn{10}{c}{$E > 10 \gev$} \\
-        \hline
-        2FGL\,J0851.7-4635   &                116.7 &                116.1 &                122.3 &                     87.1 &                   87.2 &                 90.4 & $             1.13\deg$ & $             1.16\deg$ & $             1.17\deg$ \\
-        2FGL\,J1615.0-5051   &                 52.4 &                 53.4 &                 55.6 &                     17.5 &                   16.3 &                 17.4 & $             0.33\deg$ & $             0.32\deg$ & $             0.32\deg$ \\
-        2FGL\,J1615.2-5138   &                 76.3 &                 76.6 &                 86.3 &                     44.0 &                   48.0 &                 52.6 & $             0.42\deg$ & $             0.43\deg$ & $             0.43\deg$ \\
-        2FGL\,J1632.4-4753c  &                126.6 &                127.8 &                120.7 &                     63.9 &                   64.5 &                 64.1 & $             0.44\deg$ & $             0.44\deg$ & $             0.47\deg$ \\
-        2FGL\,J1837.3-0700c  &                 45.4 &                 46.2 &                 39.0 &                     18.5 &                   18.8 &                 16.6 & $             0.35\deg$ & $             0.34\deg$ & $             0.38\deg$ \\
-        2FGL\,J2021.5+4026   &                234.3 &                222.2 &                235.6 &                    135.9 &                  116.4 &                121.4 & $             0.59\deg$ & $             0.60\deg$ & $             0.60\deg$ \\
-      \end{tabular}
-      \caption{
-      For the new extended sources, this table shows the results of
-      fitting the new extended sources with an alternate diffuse model and
-      an alternate PSF (see section~\ref{systematic_errors_on_extension}).
-      It also compares the best fit results of \pointlike to \gtlike.
-      $\ts_\pointlike$ and $\ts_\gtlike$, and $\ts_\altdiff$ are the \ts
-      from \pointlike, \gtlike, and \gtlike with the alternate diffuse
-      model respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$, and
-      $\tsext_\altdiff$ are the \tsext from \pointlike, \gtlike, and
-      \gtlike with the alternate diffuse model respectively.  $\sigma$
-      is the best fit extension using \pointlike and the standard PSF and
-      diffuse model. $\sigma_\altdiff$ is the best fit extension using
-      the alternate diffuse model and $\sigma_\altpsf$ is the best fit
-      extension using the alternate PSF. The difference between
-      these extensions is used to compute the systematic error
-      on extension in table~\ref{known_extended_sources} and
-      table~\ref{new_ext_srcs_table}.
-      }\label{alt_diff_model_results}
-    \end{centering}
-  \end{sidewaystable}
+  2FGL\,J0823.0-4246   &                350.9 &                320.9 &                352.5 &                 66.0 &                 46.3 &                 53.6 &                 0.37 &                 0.39 &                 0.38 &                 22.1 \\
+  2FGL\,J1627.0-2425c  &                170.2 &                144.5 &                112.6 &                 43.9 &                 31.1 &                 23.9 &                 0.41 &                 0.40 &                 0.39 &                 20.0 \\
+  2FGL\,J1712.4-3941   &                 80.9 &                 75.0 &                 43.4 &                 47.4 &                 39.6 &                 22.2 &                 0.56 &                 0.56 &                 0.54 &                  6.4 \\
+  \cutinhead{E$>$10 \gev}
+  2FGL\,J0851.7-4635   &                116.7 &                116.1 &                122.3 &                 87.1 &                 87.2 &                 90.4 &                 1.13 &                 1.16 &                 1.17 &                 16.1 \\
+  2FGL\,J1615.0-5051   &                 52.4 &                 53.4 &                 55.6 &                 17.5 &                 16.3 &                 17.4 &                 0.33 &                 0.32 &                 0.32 &                 11.9 \\
+  2FGL\,J1615.2-5138   &                 76.3 &                 76.6 &                 86.3 &                 44.0 &                 48.0 &                 52.6 &                 0.42 &                 0.43 &                 0.43 &                 37.0 \\
+  2FGL\,J1632.4-4753c  &                126.6 &                127.8 &                120.7 &                 63.9 &                 64.5 &                 64.1 &                 0.44 &                 0.44 &                 0.47 &                 40.6 \\
+  2FGL\,J1837.3-0700c  &                 45.4 &                 46.2 &                 39.0 &                 18.5 &                 18.8 &                 16.6 &                 0.35 &                 0.34 &                 0.38 &                 12.6 \\
+  2FGL\,J2021.5+4026   &                234.3 &                222.2 &                235.6 &                135.9 &                116.4 &                121.4 &                 0.59 &                 0.60 &                 0.60 &                 24.3 \\
+  \enddata
+
+\tablenotetext{a}{in degrees.}
+
+\tablecomments{
+$\ts_\pointlike$, $\ts_\gtlike$, and $\ts_\altdiff$ are the test
+statistic values from \pointlike, \gtlike, and with the alternate
+diffuse model respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$,
+and $\tsext_\altdiff$ are the test statistic values of the extension
+test from \pointlike, \gtlike, and with the alternate diffuse
+model respectively.  $\sigma$, $\sigma_\altdiff$, and $\sigma_\altpsf$
+are the fit extension with the standard analysis,
+alternate diffuse model, and alternate PSF respectively.  \tsinc is
+the test statistic for the two point source test.
+}
+\end{deluxetable}
 
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 1-100
-  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed by a
-  0.1\deg Gaussian kernel.  The red star is the catalog position of this source.  
-  The red cross and circle are the best fit position
-  and extension of this source assuming a radially
-  symmetric uniform surface brightness.
-  The two green stars are the positions of the sources 2FGL\,J0823.4-4305
-  and 2FGL\,J0821.0-4254 which were removed because they are part of the
-  extended source.  This source is spatially coincident with the Puppis
-  A SNR. The light blue contours are an X-ray image of Puppis A observed by
-  ROSAT (\cite{rosat_puppis_a}). There is good spatial overlap between
-  the LAT and X-ray emission.  Even though the Vela pulsar is over 3
-  degrees away from the source, because it is so bright it can be seen
-  on the top left.  More information about this source can be found in 
-  section~\ref{section_2FGL_J0823.0-4246}.
+  \caption{A Diffuse emission subtracted 1-100
+  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
+  by a 0.1\deg Gaussian kernel.  The red star is the catalog position
+  of this source.  The red cross and circle are the best fit position
+  and extension of this source assuming a radially symmetric uniform
+  surface brightness.  The two green stars are the positions of the
+  sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which were removed
+  because they are part of the extended source.  The lower right inset
+  is the model predicted emission from a point source with the same
+  spectrum as 2FGL\,J0823.4-4305 smoothed by the same Gaussian kernel.
+  This source is spatially coincident with the Puppis A SNR. The
+  light blue contours correspond to the X-ray image of Puppis A observed by 
+  \rosat
+  (\cite{rosat_puppis_a}). 
   }\label{1FGL_J0823.3-4248}
@@
   \caption{
-  A Galactic and isotropic diffuse subtracted 1-100 \gev counts
-  map of the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
-  Gaussian kernel.  Plot (a) has the diffuse emission model subtracted
-  and plot (b) has the diffuse emission and the background source
-  2FGL\,J1625.7-2526.  subtracted.  The red star is the catalog's
+  A Diffuse emission subtracted 1-100 \gev counts
+  map of (a) the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
+  Gaussian kernel (b) also the emission from the background source 
+  2FGL\,J1625.7-2526 subtracted.  The red star is the catalog's
   position of this source.  The red cross and circle are the best
   position and extension of this source assuming a radially symmetric
-  uniform surface brightness.  This source is in the Ophiucus and might
-  represent an inadequacy in the diffuse $\gamma$-ray model . The left are
-  the IRAS 100 micrometer image (\cite{iras_rho_ophiuci}) and the right
-  contours are the CO (\cite{co_rho_ophiuci}).  This source is in the
-  Ophiuchus region and most likely represents unmodeled diffuse emission.
-  More information about this source can be found in
-  section~\ref{section_2FGL_J1627.0-2425c}.
+  uniform surface brightness.  The left contours correspond to the
+  100 micrometer image observed by IRAS (\cite{iras_rho_ophiuci}) and the right
+  contours correspond to CO emission (\cite{co_rho_ophiuci}).
+  \todo[inline]{Rewrite CO contours based upon descritipon
+  of CO contours in Cygnus Loop paper
+  http://arxiv.org/pdf/1108.1833v2
+  }
+  \todo[inline]{Ask markus if this description of ophicucus is good}
   }\label{1FGL_J1628.6-2419c}
@@
   \end{center}
-  \caption{A Galactic and isotropic diffuse subtracted 1-100 \gev
-  counts map of the region around 2FGL\,J1712.4-3941 smoothed by
-  a 0.25\deg Gaussian kernel.  Plot (a) has the diffuse emission
-  model subtracted and plot (b) has the diffuse emission and all
-  background sources subtracted.  This source is spatially
+  \caption{A Diffuse emission subtracted 1-100 \gev
+  counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
+  a 0.25\deg Gaussian kernel and (b) also the emission 
+  from the background sources subtracted.
+  This source is spatially
   coincident with RX J1713.7-3946 was was recently reported by
-  (\cite{rx_j1713_lat}).  The light blue contours are from the \tev image
+  (\cite{rx_j1713_lat}).  The light blue contours correspond to the \tev image
   observed by H.E.S.S. (\cite{rx_j1713_hess}).  The region was analyzed
@@
   The gray crosses represent from left to right the position of source B
-  and C which were added to the background model. More information about
-  this source can be found in section~\ref{section_2FGL_J1712.4-3941}.
+  and C which were added to the background model. 
   }\label{2FGL_J1712.4-3941}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 10-100
+  \caption{A Diffuse emission subtracted 10-100
   \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
-  by a 0.25\deg Gaussian kernel. This image is smoothed by a larger
-  kernel because it is significantly larger than the other sources.
-  The red star is the catalog position of this source.  The red cross
+  by a 0.25\deg Gaussian kernel. The red star is the catalog position of this source.  The red cross
   and circle are the best fit position and extension of the source
@@
   source is spatially coincident with the Vela Jr SNR.  The light
-  blue contours are from the \tev image of Vela Jr. observed by H.E.S.S
-  (\cite{vela_jr_hess}).  More information about this source can be
-  found in section~\ref{section_2FGL_J0851.7-4635}.
+  blue contours correspond to the \tev image of Vela Jr. observed by H.E.S.S
+  (\cite{vela_jr_hess}).  
   }\label{Vela_Jr}
@@
   \caption{
-    A Galactic and isotropic diffuse subtracted 10-100
+    A Diffuse emission subtracted 10-100
     \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
@@
     The light blue
-    contours are from the \tev image 
+    contours correspond to the \tev image 
     of the extended sources
@@
     2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
-    Figure~\ref{hess_seds} (a) and (b) shows the \gev and \tev SEDs for
-    these sources.
-    More information about 2FGL J1615.0-5051 can be found in
-    section~\ref{section_2FGL_J1615.0-5051} and 2FGL\,J1615.2-5138 in
-    section~\ref{section_2FGL_J1615.2-5138}.
   }\label{1FGL_J1613.6-5100c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 10-100
+  \caption{A Diffuse emission subtracted 10-100
   \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
@@
   coincident with the extended H.E.S.S source HESS\,J1632-478.
-  The light blue contours are from the \tev image observed by H.E.S.S.
-  (\cite{hess_plane_survey}).  Figure~\ref{hess_seds} (c) shows the \gev and
-  \tev SED for this source.  More information about this source can be
-  found in section~\ref{section_2FGL_J1632.4-4753c}.
+  The light blue contours correspond to the \tev image observed by H.E.S.S.
+  (\cite{hess_plane_survey}).  
   }\label{1FGL_J1632.9-4802c}
@@
   \caption{
-  A Galactic and isotropic diffuse subtracted 10-100 \gev counts map of
+  A Diffuse emission subtracted 10-100 \gev counts map of
+  (a)
   the region around 2FGL\,J1837.3-0700c smoothed by a 0.1\deg Gaussian
-  kernel.  Plot (a) has the diffuse emission model subtracted and plot (b)
-  has the diffuse emission and all background sources subtracted.  The red
+  kernel and (b) also the emission from the background 
+  sources subtracted.  The red
   star is the catalog position of this source. The red cross and circle
@@
   it is not significant above 10 \gev.  This source is spatially
-  coincident with the \tev source HESS\,J1837-069.  The light blue contours are from the \tev image observed by H.E.S.S.
-  (\cite{hess_plane_survey}).  Figure~\ref{hess_seds} (d) shows the \gev
-  and \tev SED for this source.  More information about this source can
-  be found in section~\ref{section_2FGL_J1837.3-0700c}.
-  }\label{1FGL_J1837.5-0659c}
+  coincident with the \tev source HESS\,J1837-069.  The light blue
+  contours correspond to the \tev image observed by H.E.S.S.
+  (\cite{hess_plane_survey}).  }\label{1FGL_J1837.5-0659c}
 \end{figure}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
-  \caption{A Galactic and isotropic diffuse subtracted 10-100
-  \gev counts map of the region around 2FGL\,J2021.5+4026 smoothed by a
-  0.1\deg Gaussian kernel. The red star is the catalog position of 2FGL
-  J2021.5+4026.  The red cross and circle are the best fit position and
-  extension 2FGL\,J2021.5+4026 
-  assuming a radially
-  symmetric uniform surface brightness. 
-  The green cross inside the extension is 2FGL\,J2019.1+4040 which
-  was removed because it is part of the extended source.  The farther
-  away green stars represent other catalog sources which were removed
-  because they were not significant above 10 \gev.  The gray cross is
-  the position a source not in the two year catalog which was added
-  to the region. 2FGL\,J2021.5+4026 is spatially coincident with the
-  Gamma Cygni SNR.  The light blue contours are from a 408MHz image of Gamma Cygni
-  observed by the Canadian Galactic Plane Survey.  More information about
-  this source can be found in section~\ref{section_2FGL J2021.5+4026}.
+  \caption{A Diffuse subtracted 10-100 \gev counts map of the region
+  around 2FGL\,J2021.5+4026 smoothed by a 0.1\deg Gaussian kernel. The
+  red star is the catalog position of 2FGL J2021.5+4026.  The red cross
+  and circle are the best fit position and extension 2FGL\,J2021.5+4026
+  assuming a radially symmetric uniform surface brightness.  The green
+  cross inside the extension is 2FGL\,J2019.1+4040 which was removed
+  because it is part of the extended source.  The farther away green
+  stars represent other catalog sources which were removed because
+  they were not significant above 10 \gev.  The gray cross is the
+  position a source not in the two year catalog which was added to the
+  region. 2FGL\,J2021.5+4026 is spatially coincident with the $\gamma$
+  Cygni SNR.  The light blue contours correspond to the 408MHz image of
+  $\gamma$ Cygni observed by the Canadian Galactic Plane Survey.
   }\label{1FGL_J2020.0+4049}
@@
     are H.E.S.S points of associated sources.  Plot (a) shows the \gev
-    SED of 2FGL\,J1615.0-5051 and the \tev SED of HESS\,J1616-508.
+    SED of 2FGL\,J1615.0-5051 together with the \tev SED of HESS\,J1616-508.
     Plot (b) shows 2FGL\,J1615.2-5138 and HESS\,J1614-518 Plot (c)
@@
     systematic only.
-    }\label{hess_seds}
+    \todo[inline]{Investigate quality of upper limits. Markus wants SEDs
+    for other sources. Ask Stefan if he thinks we should add SEDs for
+    more sources}
+    }
+    \label{hess_seds}
   \end{figure}
@@
 \clearpage
-\begin{sidewaysfigure}
+{\rotate
+\begin{figure}
   \begin{center}
@@
     2FGL are the red markers and the nine additional
-    extended sources analyzed in this paper are the orange markers. The
-    extended sources are overlaid on an Aitoff projection Galactic
-    coordinate map of all 100 \mev to 100 \gev photons measured by the
-    LAT in the two year time interval of this analysis.
+    extended sources analyzed in this paper are the orange markers. 
     }\label{allsky_extended_sources}
-  \end{sidewaysfigure}
+  \end{figure}
+  }
 
@@
     of W30, 2FGL\,J1837.3-0700c, 2FGL\,J1632.4-4753c,
-    2FGL\,J1615.0-5051, and 2FGL\,J1615.2-5138 are from the
-    H.E.S.S. Galactic plane survey (\cite{hess_plane_survey}).
+    2FGL\,J1615.0-5051, and 2FGL\,J1615.2-5138 (\cite{hess_plane_survey}).
     The \tev extensions of MSH 15-52, HESS\,J1825-137, Vela X,
-    Vela Jr., RX J1713.7-3946 and W28 are respectively from H.E.S.S.
+    Vela Jr., RX J1713.7-3946 and W28 are from 
     (\cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}).
-    The \tev extension of IC443 is from Veritas (\cite{ic443_veritas})
-    and W51c is from Magic (\cite{w51c_with_magic_at_fermi_symposium}).
+    The \tev extension of IC443 is from (\cite{ic443_veritas})
+    and W51c is from (\cite{w51c_with_magic_at_fermi_symposium}).
     The LAT extension of Vela X is from (\cite{velax}).  Except for RX
@@
     converted to \rsixeight (see section~\ref{compare_source_size}).
-    Because of their large size, the RX J1713.7-3946 and Vela Jr.
-    were not directly fit in \tev. The \tev radius of RX J1713.7-3946
-    is taken to be 0.5\deg and Vela Jr. to be 1\deg and the LAT size
-    is not converted to \rsixeight. The LAT extension errors are
-    the statistical and systematic errors added in quadrature. This
-    plot shows that there is a correlation between the \gev and \tev
-    sizes of sources.  The \tev size of MSH 15-52, HESS\,J1614-518,
+    Because of their large size, the shape of RX J1713.7-3946 and Vela Jr.
+    were not directly fit in \tev. Here, we take their
+    sizes to be the same as the LAT size and 
+    do not converted it to \rsixeight. The LAT extension errors are
+    the statistical and systematic errors added in quadrature. The \tev size of MSH 15-52, HESS\,J1614-518,
     HESS\,J1632-478, and HESS\,J1837-069 have only been reported with
@@
     and the LAT extension of Vela X is taken from (\cite{velax}). The
-    Centarus A lobes, which have an extension $~10\deg$, are not
-    included in the plot (\cite{cen_a_lat}).  The \tev extension of
+    The \tev extension of
     the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
@@
     morphology of RX J1713.7-3946 and Vela Jr. is poorly matched by a
-    Gaussian surface brightness model, so the \tev sizes 
-    were found assuming a uniform surface brightness. Here,
-    neither the \gev nor \tev sizes were converted.  This plot
-    shows that \tev experiments are sensitive to smaller extended sources.
+    Gaussian surface brightness model, the \gev and
+    \tev extensions are assuming a uniform surface brightness.
     }\label{gev_vs_tev_histogram}
@@
     (\cite{second_cat}) and the index of Vela X is taken to be 2.41
-    from (\cite{velax}). This plot shows that many of the LAT
-    extended sources have a hard ($<2$) spectral index.
-    }\label{compare_index_2FGL}
+    from (\cite{velax}). }\label{compare_index_2FGL}
   \end{figure}

### 2011-08-16 extended_catalog/paper/extended_catalog.tex
before (most of) keiths changes

@@
 
+\bibliographystyle{apj}
+\newcommand{\etal}{et al.}
+
 \usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
+
+% for highlighting text
+\usepackage{framed}
+\colorlet{shadecolor}{yellow}
 
@@
 \newcommand{\chandra}{\text{{\em Chandra}}\xspace}
+\newcommand{\swiftxrt}{\text{{\em Swift}/XRT}\xspace}
 \newcommand{\rosat}{\text{{\em ROSAT}}\xspace}
+\newcommand{\suzaku}{\text{{\em Suzaku}}\xspace}
 \newcommand{\asca}{\text{{\em ASCA}}\xspace}
@@
 Using two years of all sky surveying data, the LAT Collaboration published
-a catalog of 1873 \gev sources\cite{second_cat}. Many of these can be
+a catalog of 1873 \gev sources \citep{second_cat}. Many of these can be
 positionally associated with a variety of source classes including Active
@@
 discovered of five spatially extended supernova remnants, IC443, W28, W44,
-W51C, and RX J1713.7-3946 (\cite{ic443,w28,w44,w51c,rx_j1713_lat}). In
+W51C, and RX J1713.7-3946 \citep{ic443,w28,w44,w51c,rx_j1713_lat}. In
 addition, three extended PWNe were detected: MSH 15-52, Vela~X,
-and HESS\,J1825-137 (\cite{msh1552,velax,fermi_hess_j1825}), as well
+and HESS\,J1825-137 \citep{msh1552,velax,fermi_hess_j1825}, as well
 as two close-by galaxies, the Large Magellanic and Small Magalenic
-Cloud (\cite{lmc,smc}), and finally the radio galaxy Centarus A
-(\cite{cen_a_lat}) .
+Cloud \citep{lmc,smc}, and finally the radio galaxy Centarus A
+\citep{cen_a_lat}.
 
@@
  with extensions varying from
-$~0.1\deg$ to $~0.25\deg$ (\cite{hess_plane_survey}). In fact, within
+$~0.1\deg$ to $~0.25\deg$ \citep{hess_plane_survey}.
+In fact, within
 our Galaxy only very few sources (most notably the $\gamma$-ray binaries
-LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI})
-HESS\,J0632+057 (\cite{HESS0632}), and the Crab nebula (\cite{crab_weekes})
+LS\,5039 \citep{HESSLS5039}, LS I+61-303 \citep{MAGICLSI, VERITASLSI}
+HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes}
 are amongst the few Galactic sources
@@
 
-\todo[inline]{Ask Stefan/Markus if they think we should get rid of
-this note about what point soruces in the plane.}
-
-\todo[inline]{add note about how high energy emission may be hadron,
-and the origin of cosmic rays}
+\begin{shaded} 
+High energy $\gamma$-rays are produced by the decay of $\pi^0$s produced
+by hadronic interactions with interstellar matter and by relativistic
+electrons due to Inverse Compton (IC) scattering and Bremsstrahlung
+radiation.  Many of these spatially extended \tev sources in the
+Galactic plane are unidentified. Some of these sources could produce
+hadronic cosmic rays up to $\approx 10^{15}$ eV and subsequently radiate
+$\gamma$-rays through $\pi^0$ decay \citep{blandford_and_eichler_1987}.
+Studying the spectra of these \tev sources at \gev energies may help to
+determine the emission mechanisms of these high energy sources.
+\end{shaded}
 
@@
 the model of the sky and removing excess residuals, for example in the
-region around surrounding the Large Magellanic Cloud (\cite{first_cat}).
+region around surrounding the Large Magellanic Cloud \citep{first_cat}.
 Additionally, such excess residuals potentially bias the significance
@@
 Morphological studies of sources in the \gev energy range using the
-LAT are challenging because of the significantly energy-dependent PSF.
-Additional complications arise close to the Galactic plane due to
+LAT are challenging because of the strongly energy-dependent PSF.
+Additional complications arise for sources along the Galactic plane due to
 systematic uncertainties in the Galactic diffuse emission.  The LAT's
@@
 by the granularity of the silicon strips and is 0.14\deg at 10 \gev
-(\cite{on_orbit_calibration}).  The high resolution of the higher
-energy photons in the LAT energy range however is offset by their low
+\citep{on_orbit_calibration}.  However, since most high energy
+astrophysical sources have power-law spectra, the better resolution of the higher
+energy photons is offset by their low
 statistics. Therefore a detailed investigation has been performed in this
@@
 analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
-Fermi Science Support Center (\cite{fssc})} because \gtlike can only 
+Fermi Science Support Center \citep{fssc}} because \gtlike can only 
 fit the spectral parameters of the model.
@@
 We note that \gtlike has been used in the past in several studies of
-source extension in the LAT collaboration (\cite{lmc,smc,w28,w51c}).
+source extension in the LAT collaboration \citep{lmc,smc,w28,w51c}.
 Based upon a set of \gtlike maximum likelihood fits at fixed extensions,
@@
 fitting package developed in the LAT collaboration and called \pointlike
-(\cite{first_cat,matthew_kerr_thesis}).  We extended the code to allow
+\citep{first_cat,matthew_kerr_thesis}.  We extended the code to allow
 a simultaneous fit of the source extension together with the position
@@
 our catalog scan as well as the Monte Carlo validation of our method.
-Details on the \pointlike package can be found in (\cite{matthew_kerr_thesis}).
+Details on the \pointlike package can be found in \citep{matthew_kerr_thesis}.
 
@@
 likelihood by simultaneously varying the position and extension of
-the source (\cite{minuit_documentation}).  As will be described in
+the source \citep{minuit_documentation}.  As will be described in
 section~\ref{monte_carlo_validation}, simultaneously fitting the position
@@
 where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
-(\cite{matthew_kerr_thesis}).  For radially symmetric extended sources,
+\citep{matthew_kerr_thesis}.  For radially symmetric extended sources,
 the angular part of the integral can be done analytically
@@
 model is more significant because the models are not nested
-(\cite{statistics_with_care}). Even though the comparison of \tsext with
+\citep{statistics_with_care}. Even though the comparison of \tsext with
 \tsinc is not a calibrated test, we find the cases $\tsinc \ll \tsext$
@@
 
-Mattox et al. discuss that the test statistic distribution
+\cite{mattox_egret} discuss that the test statistic distribution
 for a likelihood ratio test on the existence of a source at
-a given position is \cite{mattox_egret}
+a given position is 
 \begin{equation}\label{ts_ext_distribution}
@@
 \gtobssim\footnote{\gtobssim is distributed by the Fermi Science Support
-Center (\cite{fssc}).} and fit them them using \pointlike as both point
+Center \citep{fssc}.} and fit them them using \pointlike as both point
 and extended sources.  The point sources were simulated with a power-law
@@
 background with an integrated flux above 100 \mev of $1.5\times10^{-5}$
-(\cite{sreekumar_isotropic}).  The Monte Carlo simulation was performed
+\citep{sreekumar_isotropic}.  The Monte Carlo simulation was performed
 over a one year observation period using a default rocking profile and a
@@
 
-Figure~\ref{all_sensitivity}
-shows the flux threshold as a function of source extension for
-different background levels (1x, 10x, and 100x the
-nominal background), different spectral indices, and two
-different energy bands (1-100 \gev and 10-100 \gev).
-The detection threshold is higher for sources in regions
-of higher background.
-For a fixed 1-100 \gev or 10-100 \gev
-flux, the LAT's detection threshold is only weakly depends upon the
-spectral index.  
-Overlaid on figure~\ref{all_sensitivity} are the LAT
-detected extended sources from table~\ref{known_extended_sources} and
-table~\ref{new_ext_srcs_table}.  
-This effect is most pronounced when using only photons
-with energies above 10 \gev. The extension thresholds are tabulated in
-table~\ref{all_sensitivity_table}.
+\begin{shaded}
+Figure~\ref{all_sensitivity} shows the flux threshold as a function of
+source extension for different background levels (1x, 10x, and 100x the
+nominal background), different spectral indices, and two different energy
+bands (1-100 \gev and 10-100 \gev).  The detection threshold is higher
+for sources in regions of higher background.  For a fixed 1-100 \gev or
+10-100 \gev flux, the LAT's detection threshold is only weakly depends
+upon the spectral index.  Overlaid on figure~\ref{all_sensitivity} are
+the LAT detected extended sources from table~\ref{known_extended_sources}
+and table~\ref{new_ext_srcs_table}.  This effect is most pronounced when
+using only photons with energies above 10 \gev. The extension thresholds
+are tabulated in table~\ref{all_sensitivity_table}.
 
@@
 background is larger and the improvement is closer to $\sqrt{\text{t}}$.
+\end{shaded}
 
@@
 4, 2008 to August 1, 2010 and we used the same Pass 7\_V6 (P7\_V6)
-Source class event selection and Instrument Response Functions (IRFs,
-\cite{lat_on_orbit_psf}).  We used the same models to describe the
+Source class event selection and IRFs \citep{lat_on_orbit_psf}.  We used the same models to describe the
 background from Galactic diffuse, isotropic, and earth limb emission.
@@
 successfully used in detecting HESS\,J1825-137 and MSH 15-52 with the LAT
-(\cite{msh1552,fermi_hess_j1825}).
+\citep{msh1552,fermi_hess_j1825}.
 
@@
 intergalactic medium.  Finding sources on top of this emission is difficult
-(\cite{first_diffuse_paper}) as has been discussed in 1FGL and 2FGL
-(\cite{first_cat,second_cat}).  Furthermore, the Galactic plane is crowded
+\citep{first_diffuse_paper} as has been discussed in 1FGL and 2FGL
+\citep{first_cat,second_cat}.  Furthermore, the Galactic plane is crowded
 and it is often difficult to correctly model nearby sources.  Because of this,
@@
 launch, the LAT PSF was determined by a detector simulation which was
-verified in accelerator tests (\cite{atwood_LAT_mission}).  A discrepancy
+verified in accelerator tests \citep{atwood_LAT_mission}.  A discrepancy
 was found in flight data above a few \gev in the PSF compared to the
 shape of bright AGN.  A publication on this issue is in preparation
-(\cite{lat_on_orbit_psf}).  Subsequently, the PSF was fit empirically to
+\citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit empirically to
 bright AGN and this empirical parameterization is the default PSF used
@@
 The same approach was used in
-(\cite{ic443}).  At high energies, we believe that our parameterization
+\citep{ic443}.  At high energies, we believe that our parameterization
 of the PSF from bright AGN is substantially better than the Monte Carlo
@@
 references} model used in the LAT analysis of the isotropic diffuse
-emission (\cite{isotropic_lat}).  
+emission \citep{isotropic_lat}.  
 The intensities of various contributions to the galactic
@@
 the molecular hydrogen, the atomic+ionized hydrogen,
-residual gas traced by dust (\cite{isabelle_dark_gass}),
+residual gas traced by dust \citep{isabelle_dark_gass},
 and the interstellar radiation field. We further
@@
 A similar crosscheck was used in the
-LAT Collaboration's analysis of RX J1713.7-3946 (\cite{rx_j1713_lat}).
+LAT Collaboration's analysis of RX J1713.7-3946 \citep{rx_j1713_lat}.
 
@@
 included in 2FGL.
-(\cite{second_cat}).
+\citep{second_cat}.
 The six extended SNRs IC443, W28, W30, W44, W51C, and the
@@
 Cygnus Loop were
-first reported in (\cite{ic443,w28,w44,w51c,cygnus_loop_lat}).  A
+first reported in \citep{ic443,w28,w44,w51c,cygnus_loop_lat}.  A
 detailed publication by the LAT
 collaboration about W30 is still in preparation.
-\gev emission from W30 was also studied in (\cite{castro_and_slane_2010}).
+\gev emission from W30 was also studied in \citep{castro_and_slane_2010}.
 Using 1-100 \gev photons, our analysis significantly detected the
@@
 Two nearby galaxies the Large Magalenic Cloud and the Small Magalenic
-Cloud were included in 2FGL (\cite{lmc,smc}).  They were significantly
+Cloud were included in 2FGL \citep{lmc,smc}.  They were significantly
 detected using 1-100 \gev photons. Our
@@
 Three pulsar wind nebula Vela X, MSH 15-52, and HESS\,J1825-137 were
-included in 2FGL (\cite{velax,msh1552,fermi_hess_j1825}).  Using photons
+included in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  Using photons
 with energy above 10 \gev, we significantly detected the extension of
@@
 scope of this paper.  Our analysis also failed to detect a significant
-extension for the Centaurus A Lobes (\cite{cen_a_lat}). This is because
+extension for the Centaurus A Lobes \citep{cen_a_lat}. This is because
 the source's emission is significantly different from a uniform
@@
 demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
-halos around AGNs have been hypothesized (\cite{pair_halo_paper}) which
+halos around AGNs have been hypothesized \citep{pair_halo_paper} which
 could be resolved by the LAT However, no such halo has been discovered
@@
 of sources that
-had a high probability association with AGN (\cite{first_agn_cat}).
+had a high probability association with AGN \citep{first_agn_cat}.
 1FGL had 709 1FGL sources associated with 671 distinct AGN at high
@@
 associated 1016 2FGL sources
-with AGN (\cite{second_agn_cat}).  
+with AGN \citep{second_agn_cat}.
 To avoid systematic problems with AGN classification, we
@@
 
+\begin{shaded}
 This extended source is spatially coincident with the middle-aged
 SNR Puppis A.  Puppis A has been studied in detail in radio
-(\cite{puppis_a_vla}, and references therein).  X-ray observations
-have been performed by a variety of instruments 
-(\cite{einstein_puppis_a,rosat_puppis_a,chandra_puppis_a,xmm_newton_puppis_a,suzaku_puppis_a})
+(\cite{puppis_a_vla}, and references therein) and  X-ray 
+(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
 The highest resolution image of the entire source was obtained
@@
 image are overlaid on figure~\ref{1FGL_J0823.3-4248} and match the
-inferred \gev size (\cite{rosat_puppis_a}).
-
-Puppis A's age was estimated to be $\approx3700$ years (\cite{winkler_1988}) and
-its distance was estimated at 2.2 kpc (\cite{ reynoso_1995,reynoso_2003}).
-Assuming this distance, the \gev luminosity of Puppis A between 1 and
-100 \gev is $\approx 3\times 10^{34}$ ergs/\s.
-
-Molecular clouds have not been detected ajacent to Puppis A (\cite{puppis_a_co})
-Similarly, the luminsoity is lower than that of other LAT
-detected SNRs interacting with molecular clouds (\cite{\dots}),.
-The LAT emission could therefore be explained by the interaciton of acclerated
-particles by interstellar matter or fields in the regions, similar
-to what was suggested for the Cygnus Loop SNR (\cite{cygnus_loop_lat}).
-
-Puppis A has not been observed to direct
-% 1 - 100 GeV
-%      Norm      
-%      Index     
+inferred \gev size \citep{rosat_puppis_a}.
+Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
+which leads to a 1-100 \gev luminosity of $\approx 3\times 10^{34}$ ergs/\s.
+
+No molecular clouds have been observed directly ajacent to Puppis A 
+\citep{co_eastern_puppis_a}.
+This is similar to the the LAT detected SNR the Cyngus Loop \citep{cygnus_loop_lat}.
+The luminolsity of Puppis A is also smaller than that of 
+other SNRs believed to interact with molecular clouds
+\citep{w51c,ic443,w44,w28,w49b_lat}.
+The \gev emission could therefore be explained by the interaction
+of accelerated particles by interstellar matter or fields, similar
+to the emission mechanism suggested for the Cygnus Loop SNR
+\citep{cygnus_loop_lat}.
+\end{shaded}
+
+% Puppis A:
 %   Flux = PowerLaw(norm=6.21e-14,index=2.22,e0=10000).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
@@
 %   Luminosity =  Flux * 4*pi*r^2 = 4.78e-11 ergs/cm^2/s * 4*pi * (2.2 kpc )**2 in ergs/s
-%            = 2.8e34 ergs/s from 1-100 gev
-
-\todo[inline]{Make point about how this source
-is like Cygnus Loop. Discuss with Yasunobu.  Main points about CO
-Emission / moelcular cloud interactions (\cite{co_eastern_puppis_a}).
-Can we say anything about emission could be hadronic or leptonic models?
-Markus says to add SEDs. Should we?
-}
+%              = 2.8e34 ergs/s from 1.0-100 gev
+%              = 5.6e34 ergs/s from 0.1-100 gev
+%   Luminosities
+%   Cygnus Loop:
+%     L = 10^33 ergs/s between 1-100 \gev
+%   W51C : 
+%     http://arxiv.org/pdf/0910.0908
+%     L > 1 x 10^36 ergs/s (0.2-50GeV) - 
+%   IC443:
+%     http://arxiv.org/pdf/1002.2198v1
+%     L = 1.2e35 ergs/s (from 0.2-50 gev)
+%     d = 1.5 kpc
+%     From my (possibly incorrect) powerlaw analysis 
+%       In [30]: PowerLaw(norm=4.69e-13,index=2.21,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
+%       Out[30]: 3.5968626651391638e-10 ergs/cm^2/s
+%       L = 3.5968626651391638e-10/cm^2 * 4*pi*(1.5kpc)**2 = 1e35 (1-100gev)
+%   W44:
+%     http://www.sciencemag.org/content/327/5969/1103.full.pdf
+%     From my (possibly incorrect) powerlaw analysis 
+%       PowerLaw(norm=2.7e-13,index=2.63,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
+%       Out[27]: 2.7681360351439016e-10 ergs/cm^2/s
+%     Distance = 3kpc
+%     L = 3e35 ergs/s (1-100 gev)
+%   W28
+%     http://iopscience.iop.org/0004-637X/718/1/348/
+%     From my (possibly incorrect) powerlaw analysis 
+%       In [28]: PowerLaw(norm=2.23e-13,index=2.6,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
+%       Out[28]: 2.221059203350944e-10 ergs/cm^2/s
+%     Distance = 2kpc
+%     L = 1e35 ergs/s (1-100 gev)
+%   W49B
+%     http://iopscience.iop.org/0004-637X/722/2/1303
+%     L = 10^36 erg/s (0.2 - 200 gev)
+%
 
@@
 
+\begin{shaded}
 This source is in a region of remarkably complicated diffuse emission.
@@
 dark gas, the kind that we find only by its association with dust emission
-(\cite{isabelle_dark_gass}). Embedded star-forming regions make it even
+\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
 more challenging to measure the column density of dust.  Infared and CO
 contours are overlaid on figure~\ref{1FGL_J1628.6-2419c} and there is good
-spatial correlation with the \gev emission (\cite{iras_rho_ophiuci}).
+spatial correlation with the \gev emission \citep{iras_rho_ophiuci}.
 Therefore this source might represent an inadequacy in the diffuse
 $\gamma$-ray model
+\end{shaded}
 
@@
 This source is spatially coincident with the SNR RX J1713.7-3946
-and was recently reported by (\cite{rx_j1713_lat}).  Figure
+and was recently reported by \citep{rx_j1713_lat}.  Figure
 \ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR RX
-J1713.7-3946 from (\cite{rx_j1713_hess}).  To analyze this source,
+J1713.7-3946 from \citep{rx_j1713_hess}.  To analyze this source,
 we used the same background model as the recent LAT publication.
@@
 Overlaid on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
-\tev by H.E.S.S (\cite{vela_jr_hess}).  The \gev and \tev morphology
+\tev by H.E.S.S \citep{vela_jr_hess}.  The \gev and \tev morphology
 match well.  A detailed papers by the LAT collaboration on Vela Jr. is
@@
 2FGL\,J1615.2-5138 is spatially coincident with the extended
-\tev source HESS\,J1616-508 (\cite{hess_plane_survey}).  In
+\tev source HESS\,J1616-508 \citep{hess_plane_survey}.  In
 figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
@@
 
+\begin{shaded}
 HESS\,J1616-508 is located in the region of two SNRs, RCW103
 (G332.4-04) and Kes 32 (G332.4+0.1) but is not spatially coincident
-with either of them (\cite{hess_plane_survey}).  HESS\,J1616-508 is near
+with either of them \citep{hess_plane_survey}.  HESS\,J1616-508 is near
 three pulsars PSR J1614-5048, PSR J1616-5109, and PSR J1617-5055
 but only PSR J1617-5055 is energetically favored as being the \tev
-emitter (\cite{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}).
+emitter \citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.
 \cite{hess_plane_survey} speculated that a PWN powered by this young
@@
 towards the \tev emission, rendering this association as uncertain
-\cite{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
+\citep{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
 counterparts were observed in observations of x-ray and soft gamma-ray
-emission by Suzaku (\cite{suzakzu_HESS_J1616-508}), Swift/XRT,
-IBIS/ISGRBI, BeppoSAX and \xmmnewton (\cite{integral_HESS_J1616-508}).
+emission by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
+IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
 Finally, \cite{discovery_of_pwn_for_PSR_J1617-5055} found diffuse
@@
 understand this region.
+\end{shaded}
 
@@
 This source is spatially coincident with the extended
-\tev source HESS\,J1614-518 (\cite{hess_plane_survey}). In
+\tev source HESS\,J1614-518 \citep{hess_plane_survey}. In
 figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
@@
 that the emission is not the confusion of physically separate sources
-(\cite{closer_look_hess_j1614-518}).  The source was also detected by
-CANGAROO-III (\cite{cangaroo_j1614-518}).
-
+\citep{closer_look_hess_j1614-518}.  The source was also detected by
+CANGAROO-III \citep{cangaroo_j1614-518}.
+
+\begin{shaded}
 There are five nearby pulsars, but none are luminous enough to
-provide the required energy output to power the \gev and \tev emission
-(\cite{closer_look_hess_j1614-518}).
-
-HESS\,J1614-518 is spatially coincident with a young open cluster Pismis
-22 (\cite{hess_1614_landi_atel,closer_look_hess_j1614-518}).
-\gev and \tev emission could arise from
-hadronic acceleration in the winds of massive stars
-\cite{cosmic_rays_and_gamma-rays_from_ob_stars,gamma-ray_production_in_young_open_clusters}.
-Pisim 22 is at a distance $\approx1$ kpc and can energetically account
-for the \tev emission (\cite{closer_look_hess_j1614-518}), but
-it is difficult to explain the difference in size and positional offset
-between Pismis 22 and HESS\,J1614-518.
-
-Suzaku observations of the region around HESS\,J1614-518 reveale three
-X-ray sources in the region. Suzaku source A is a hard extended source
-spatially coincident with the peak of HESS\,J1614-518.
-
-Suzaku source B is
-in a relativly dim region in the middle of HESS\,J1614-518 and was not
-spatially resolvable. source B is spatially coincident with Pisim 22.
-
-Suzaku Source C is a foreground source.
-
-Swift observations the region and resolved six X-ray sources.
-
-\todo[inline]{Emission due to SNR, PWN, Massive Star. Stefan
-says to add Suzaku observations. Add note about SWIFT observations + citation.}
+provide the required energy output required to power the $\tev$ 
+emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614-518
+is spatially coincident with a young open cluster Pismis 22
+\citep{hess_1614_landi_atel,closer_look_hess_j1614-518}.
+\suzaku detected two
+promising x-ray candidates. Source A is an extended source consistent
+with the peak of HESS\,J1614-518 and source B coincident with Pismis 22
+and towards the center but in a relatively dim region of HESS\,J1614-518
+\citep{suazku_hess_j1614_518}.  Three hypothesis have been presented to
+explain this emission; either source A is an SNR powering the $\gamma$-ray
+emission, source A is a PWN powered by an undiscovered pulsar in either
+source A or B, and finally that the emission may arise from hadronic 
+acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
+\end{shaded}
 
@@
 This extended source is spatially coincident with the extended
-\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).
+\tev source HESS\,J1632-478 \citep{hess_plane_survey}.
 In figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478
@@
 
-\cite{hess_plane_survey} argued that HESS\,J1632-478 is
-positionally coincident with the hard X-ray source IGR\,J1632-4751
-observed by INTEGRAL (\cite{Igr_J16320-4751_circ}), \xmmnewton
-(\cite{xmm_newton_IGR_J16320-4751}), and \asca (\cite{asca_plane_survey}).
-But it is suspected to be an galactic X-Ray Binary so the \gev and \tev
-extension disfavors the association.
-
-Further observations by \xmmnewton reveal extended emission of size
-$\approx32''x\approx15''$ and inside point-like emission coincident with
-the peak H.E.S.S. emimssion (\cite{hess_j1632_478_xmm_newton}).  They
-found in archival MGPS-2 data a spatially coincident extended radio source
-\cite{most_survey_galactic_plane}.  The positional match argues for a
+\begin{shaded}
+\cite{hess_plane_survey} argued that HESS\,J1632-478
+is positionally coincident with the hard X-ray source
+IGR\,J1632-4751 observed by INTEGRAL, \xmmnewton, and \asca
+\citep{Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751,asca_plane_survey},
+but this source is suspected to be an galactic X-Ray Binary so the $\gamma$-ray
+extension disfavors the association.  Further observations by
+\xmmnewton reveal extended emission of size $\approx32''\times15''$
+and inside point-like emission coincident with the peak
+H.E.S.S. emission \citep{hess_j1632_478_xmm_newton}.  They found
+in archival MGPS-2 data a spatially coincident extended radio source
+\citep{most_survey_galactic_plane}.  The positional match argues for a
 single synchrotron processes producing X-ray and \gev and \tev radiation,
@@
 to the X-ray size has previously been observed in several aging PWNe
-including HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess},
-HESS\,J1640-465 (\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}),
-and Vela X (\cite{vela_x_rosat,vela_x_hess}).  This can be explained by
+including HESS\,J1825-137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
+HESS\,J1640-465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
+and Vela X \citep{vela_x_rosat,vela_x_hess}.  This can be explained by
 a different synchrotron cooling time for the electrons producing X-rays
 and \tev gamma rays.
+\end{shaded}
 
@@
 This source is spatially coincident with the \tev source HESS\,J1837-069
-(\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1837.5-0659c}, contours
+\citep{hess_plane_survey}.  In figure~\ref{1FGL_J1837.5-0659c}, contours
 of HESS\,J1837-069 are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured
@@
 
-HESS\,J1837-069 is coincident with the hard
-and steady X-ray source AX J1838.0-0655
-(\cite{einstein_galactic_plane_survey,hard_x-ray_asca,integral_AX_J1838.0-0655,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}).
-This source was discovery by RXTE to 
-be a pulsar 
-sufficiently luminous to power the \tev emission.
-AX J1838.0-0655 was spatially resolved by \chandra to be a bright point source
-surrounded by a $\sim2'$ nebula (\cite{pulsations_HESS_J1837-069}).
-
-A second X-ray point source AX J1837.3-0652 is in the region of HESS\,J1837-069
-(\cite{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}).
+\begin{shaded}
+HESS\,J1837-069 is coincident
+with the hard and steady X-ray source AX J1838.0-0655
+\citep{einstein_galactic_plane_survey,hard_x-ray_asca,integral_AX_J1838.0-0655,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
+This source was discovery by RXTE to be a pulsar sufficiently
+luminous to power the \tev emission.  AX J1838.0-0655 was spatially
+resolved by \chandra to be a bright point source surrounded by
+a $\sim2'$ nebula \citep{pulsations_HESS_J1837-069} and so the
+$\gamma$-ray emission may be powered by this pulsar.  A second
+X-ray point source AX J1837.3-0652 is in the region of HESS\,J1837-069
+\citep{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
 It was also resolved into point-like and diffuse component
 although no pulsations have yet been detected from it
-(\cite{pulsations_HESS_J1837-069}).  If AX J1838.0-0655 is a pulsar/PWN
-powering HESS\,J1837-069, some of the \tev emission
-may also be powered by AX J1837.3-0652.
+\citep{pulsations_HESS_J1837-069}.  If AX J1838.0-0655 is a pulsar/PWN
+powering HESS\,J1837-069, some of the \tev emission may also come from
+AX J1837.3-0652.
+\end{shaded}
 
@@
 on figure~\ref{1FGL_J2020.0+4049} and there is good spatial agreement
-with the LAT emission (\cite{canadian_galactic_plane_survey}).
+with the LAT emission \citep{canadian_galactic_plane_survey}.
+
+% Radio observations
+% ...
+
+% X-ray observations
+% ...
+
+% Age
+% ...
+
+% Distance
+%   1.5 kpc Landecker et al 1980 (from integral paper)
+
+% Optical (Mavromatakis 2003 (from integral paper)
+
+% EGRET observations
+%   3EG J2020+4027
+%   ...
+
+% LAT Pulsar detected
+%   PSR J2021+4026
+%   Prestended at scineghe2010.
+%     http://scineghe2010.ts.infn.it/allegati/talks/ThursdaySept9/13_Razzano.pdf
+%   Presented at Fermi Symposium 2011:
+%     https://confluence.slac.stanford.edu/download/attachments/98831433/2011_3FermiSymp_CygPsr_ver2.pdf
+%     "PSR J2021+4026 is a 265 ms pulsar found by Fermi LAT using"
+%     "This discovery help to better clarify the nature of the
+%      unidentified source 3EG J2020+4027, thought to be associated
+%      with SNR 78.2+2.1, a.k.a. the Gamma Cygni SNR.
+%      Unfortunately, so far this pulsar lacks a radio counterpart, and
+%      observations with Chandra and XMM show a potential X-ray
+%      counterpart [8,9,15], but no pulsations have been detected so
+%      far."
+
+% Milagro analysis
+% http://arxiv.org/abs/astro-ph/0611691
+% Milagro $4.2\sigma$ excess.
+
+% Veritas observations of Gamma Cygni: 
+%   http://arxiv.org/pdf/0912.4492v1
+%   extended: VER J019+407
+% 
+%     Veritas observations of $\gamm$-Cygni veritas_gamma_cygni,
+
+\begin{shaded}
+Interpreation...
+\end{shaded}
 
@@
 2FGL reported on the detection of twelve sources
-prviously known as extende. Using
+prviously known as extended. Using
 two years of LAT data and a new analysis method, we present on 
@@
 extended sources which were first discovered in the H.E.S.S. Galactic
-plane survey (\cite{hess_plane_survey}) and have a matching size to LAT
+plane survey \citep{hess_plane_survey} and have a matching size to LAT
 extended sources.  The LAT energy spectrum connects smoothly to \tev.
-This is also true of HESS\,J1825-137 (\cite{fermi_hess_j1825}) and RX
-J1713.7-3946 (\cite{rx_j1713_lat}).
+This is also true of HESS\,J1825-137 \citep{fermi_hess_j1825} and RX
+J1713.7-3946 \citep{rx_j1713_lat}.
 
@@
 range and the size of HESS\,J1825-137 was seen by H.E.S.S. to vary
-between 200 \gev and 20 \tev (\cite{energy_dependent_hess_j1825}).
+between 200 \gev and 20 \tev \citep{energy_dependent_hess_j1825}.
 HESS\,J1825-137 is significantly larger in \gev than \tev
-(\cite{fermi_hess_j1825}).  It is interesting to compare the \gev and
+\citep{fermi_hess_j1825}.  It is interesting to compare the \gev and
 \tev size of other PWN candidates, but definitively measuring this 
@@
 
-\bibliographystyle{apj}
 \bibliography{extended_catalog}
@@
   \rosat
-  (\cite{rosat_puppis_a}). 
+  \citep{rosat_puppis_a}. 
   }\label{1FGL_J0823.3-4248}
@@
   uniform surface brightness.  The left contours correspond to the
-  100 micrometer image observed by IRAS (\cite{iras_rho_ophiuci}) and the right
-  contours correspond to CO emission (\cite{co_rho_ophiuci}).
+  100 micrometer image observed by IRAS \citep{iras_rho_ophiuci} and the right
+  contours correspond to CO emission \citep{co_rho_ophiuci}.
   \todo[inline]{Rewrite CO contours based upon descritipon
@@
   }
-  \todo[inline]{Ask markus if this description of ophicucus is good}
   }\label{1FGL_J1628.6-2419c}
@@
   coincident with RX J1713.7-3946 was was recently reported by
-  (\cite{rx_j1713_lat}).  The light blue contours correspond to the \tev image
-  observed by H.E.S.S. (\cite{rx_j1713_hess}).  The region was analyzed
-  with the same background model as (\cite{rx_j1713_lat}).  Source A (blue
+  \citep{rx_j1713_lat}.  The light blue contours correspond to the \tev image
+  observed by H.E.S.S. \citep{rx_j1713_hess}.  The region was analyzed
+  with the same background model as \citep{rx_j1713_lat}.  Source A (blue
   cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
@@
   blue contours correspond to the \tev image of Vela Jr. observed by H.E.S.S
-  (\cite{vela_jr_hess}).  
+  \citep{vela_jr_hess}.
   }\label{Vela_Jr}
@@
     observed by H.E.S.S
-    (\cite{hess_plane_survey})
+    \citep{hess_plane_survey}
     2FGL\,J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
@@
   The light blue contours correspond to the \tev image observed by H.E.S.S.
-  (\cite{hess_plane_survey}).  
+  \citep{hess_plane_survey}.
   }\label{1FGL_J1632.9-4802c}
@@
   contours correspond to the \tev image observed by H.E.S.S.
-  (\cite{hess_plane_survey}).  }\label{1FGL_J1837.5-0659c}
+  \citep{hess_plane_survey}.}\label{1FGL_J1837.5-0659c}
 \end{figure}
@@
     \includegraphics{summary_plots/hess_seds.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v2/plot_seds/plot_seds.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_seds.py
     \end{center}
@@
     2FGL\,J1837.3-0700c and HESS\,J1837-069. The H.E.S.S. data points
-    are from (\cite{hess_plane_survey}) The LAT upper limits are at the
+    are from \citep{hess_plane_survey} The LAT upper limits are at the
     95\% confidence level.  Both LAT and H.E.S.S. spectral errors are
-    systematic only.
-    \todo[inline]{Investigate quality of upper limits. Markus wants SEDs
-    for other sources. Ask Stefan if he thinks we should add SEDs for
-    more sources}
-    }
+    systematic only.}
     \label{hess_seds}
@@
     of W30, 2FGL\,J1837.3-0700c, 2FGL\,J1632.4-4753c,
-    2FGL\,J1615.0-5051, and 2FGL\,J1615.2-5138 (\cite{hess_plane_survey}).
+    2FGL\,J1615.0-5051, and 2FGL\,J1615.2-5138 \citep{hess_plane_survey}.
     The \tev extensions of MSH 15-52, HESS\,J1825-137, Vela X,
     Vela Jr., RX J1713.7-3946 and W28 are from 
-    (\cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}).
-    The \tev extension of IC443 is from (\cite{ic443_veritas})
-    and W51c is from (\cite{w51c_with_magic_at_fermi_symposium}).
-    The LAT extension of Vela X is from (\cite{velax}).  Except for RX
+    \citep{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
+    The \tev extension of IC443 is from \citep{ic443_veritas}
+    and W51c is from \citep{w51c_with_magic_at_fermi_symposium}.
+    The LAT extension of Vela X is from \citep{velax}.  Except for RX
     J1713.7-3946 Vela Jr., the \tev sources were fit assuming a Gaussian
@@
     table~\ref{known_extended_sources}, table~\ref{new_ext_srcs_table},
-    and the LAT extension of Vela X is taken from (\cite{velax}). The
+    and the LAT extension of Vela X is taken from \citep{velax}. The
     The \tev extension of
     the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-    Catalog\cite{hesscat}.
+    Catalog \citep{hesscat}.
     Except for RX J1713.7-3946 and Vela Jr.,
@@
     table~\ref{known_extended_sources} table~\ref{new_ext_srcs_table}.
-    The index of Centarus A is taken to be 2.58 from the two year catalog
-    (\cite{second_cat}) and the index of Vela X is taken to be 2.41
-    from (\cite{velax}). }\label{compare_index_2FGL}
+    The index of Centarus A is taken to be 2.58 from 
+    \cite{second_cat} and the index of Vela X is taken to be 2.41
+    from \cite{velax}. }\label{compare_index_2FGL}
   \end{figure}

### 2011-08-16 extended_catalog/paper/extended_catalog.tex
lots of keiths changes

@@
 \renewcommand{\sec}{\text{s}\xspace}
+\newcommand{\phflux}{\ensuremath{\ph\ \cm^{-2}\s^{-1}}\xspace}
 \newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
@@
 \newcommand{\loglikelihood}{\ensuremath{LL}\xspace}
+\newcommand{\likelihood}{\ensuremath{L}\xspace}
 \newcommand{\chandra}{\text{{\em Chandra}}\xspace}
@@
 the Large Area Telescope (LAT), the primary science instrument on the
-{\em Fermi Gamma-ray Space Telescope (Fermi)}. 
-The source extension is an important input to correctly 
+{\em Fermi Gamma-ray Space Telescope} (FGST). 
+Spatial extension
+is an important input to correctly 
 associate LAT sources with their counterparts at other
-wavelengths. We provide
+wavelengths. We perform
 a series of Monte Carlo studies to validate this tool and calculate
-the LAT's detection threshold to spatially extended sources.  We then
+the LAT's detection threshold to detect the extension of 
+spatially extended sources.  We then
 apply this tool to test all sources in the two year source catalog for
-extension. We present on the detection of nine spatially extended sources
+extension. We report the detection of nine spatially extended sources
 in addition to the twelve spatially extended sources reported in the
@@
 The Large Area Telescope (LAT) is a pair conversion telescope on the Fermi
-Gamma-Ray Space Telescope (FGST). It has been surveying the $\gamma$-ray
-sky since June 2008.  Fermi has a broad energy coverage (20 \mev to $>300$
+Gamma-Ray Space Telescope (FGST) that been surveying the $\gamma$-ray
+sky since June 2008.  The LAT has a broad energy coverage (20 \mev to $>300$
 \gev), wide field of view ($\approx 2.4 \sr$), and large effective area
@@
 
-Using two years of all sky surveying data, the LAT Collaboration published
+Using two years of all-sky surveying data, the LAT Collaboration published
 a catalog of 1873 \gev sources \citep{second_cat}. Many of these can be
@@
 Galactic Nuclei (AGN), pulsars, galaxies, and supernova remnants (SNRs).
-While many of the LAT sources can be spatially resolved when observed
+While the counterparts of many LAT sources
+can be spatially resolved when observed
 at other frequencies, detection of an extension at \gev energies by
-the LAT is complicated by the rather large point-spread function (PSF)
+the LAT is complicated by the large point-spread function (PSF)
 of the instrument. The angular resolution for events converting in the
-front part of the detector, defined as the 68\% containment radius for
+thin conversion foils of the tracker system, defined as the 68\% containment radius for
 a point source, is approximately $3.5^{\circ}$ at 100 \mev, improving
@@
 However, a number of sources positionally coincident with LAT sources
-exhibit extension at other wavelengths which are larger or comparable to
-the LAT PSF.  In particular certain SNRs, pulsar wind nebulae (PWNe),
+exhibit extensions at other wavelengths which are comparable to or larger than 
+the LAT PSF.  In particular, certain SNRs, pulsar wind nebulae (PWNe),
 molecular clouds, normal galaxies, galaxy clusters or dark matter
-satellites can therefore be expected to be observed as spatially extended
-sources in the LAT.  The LAT collaboration has previously reported on the
-discovered of five spatially extended supernova remnants, IC443, W28, W44,
-W51C, and RX J1713.7-3946 \citep{ic443,w28,w44,w51c,rx_j1713_lat}. In
+satellites can therefore be expected to be detected as spatially extended
+sources by the LAT.  
+The LAT collaboration has previously reported five SNRs which are
+spatially extended beyond the LAT PSF at \gev energies 
+(IC443, W28, W44,
+W51C, and RX J1713.7-3946 \citep{ic443,w28,w44,w51c,rx_j1713_lat}). In
 addition, three extended PWNe were detected: MSH 15-52, Vela~X,
@@
 For each of these sources, the extension was determined based on
-dedicated analysis of the particular source or region of interest
+dedicated analysis of the particular source 
 instead of being the outcome of a systematic search of the LAT catalog.
-For the systematic scan of all LAT catalog sources presented here, we
+For the systematic scan of all LAT catalog sources presented in this work, we
 therefore expect to find additional spatially extended LAT sources, in
 particular since many extended sources in the Galactic plane have been
-detected at \tev energies using Air Cherenkov detectors and \tev and
+detected at \tev energies using air Cherenkov detectors and \tev and
 \gev emission often originates from the same population of high-energy
@@
 the Galactic plane using the High Energy Stereoscopic System (H.E.S.S)
-which presented 14 spatially extended sources
+which reported 14 spatially extended sources
  with extensions varying from
@@
 HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes}
-are amongst the few Galactic sources
-for which no significant extension was detected at \tev energies. Given
+have 
+no significant extension detected at \tev energies. Given
 these findings, it can be expected that if the source population at \gev
@@
 
-Being able to spatially resolve the \gev emission from a source is
-important for several reasons. Because of the large PSF and the large
-candidate source density in our Galaxy, source confusion is a severe
-problem for the identification of LAT sources.  Finding a coherent
+The capability to
+spatially resolve GeV $\gamma$-ray sources is
+important for several reasons. 
+First, multiple potential counterparts detected at other frequencies
+exist within the localization confidence region of a typical LAT source
+along the Galactic plane.
+Finding a coherent
 source extension across different energy bands allows a firm association
-of a LAT source to an otherwise confused counterpart.  Because of the
-strongly varying PSF of the LAT, the spatial and spectral information
-about a source do not simply decouple. A biased spatial model will bias
-the spectral model of the source. In particular, performing a spectral
+of a LAT source to an otherwise confused counterpart.  Also, due
+to the strong energy dependence of the LAT PSF,
+the spatial and spectral information
+about a source do not simply decouple. An inaccurate spatial model will bias
+the spectral model of the source. Specifically, performing a spectral
 analysis on a spatially extended source modeled as point-like will
@@
 systematic uncertainties in the Galactic diffuse emission.  The LAT's
-PSF is limited at lower energies by multiple scattering in the tracker
+PSF is limited at its lowest detectable energies by multiple scattering in the tracker
 and the 68\% containment radius of the PSF is approximately 5.1\deg
@@
 work to determine the optimal energy range to measure source extension
-(see below).
+(section \ref{extended_source_search_method}).
 
@@
 for studying spatially extended sources with the LAT. The tool
-provides a maximum likelihood analysis where the Poisson likelihood
+performs a maximum likelihood analysis in which the Poisson likelihood
 for observing the measured counts is maximized,
@@
 Fermi Science Support Center \citep{fssc}} because \gtlike can only 
-fit the spectral parameters of the model.
-
+fit the spectral parameters of the model unless a more sophisticated
+iterative procedure is used to also test various source morphologies.
 We note that \gtlike has been used in the past in several studies of
@@
 detection.  Furthermore since the \gtlike likelihood profile approach
-is computationally intensive, no large-scale Monte Carlo effort can be
+is computationally intensive, no large-scale Monte Carlo effort has been
 run to validate it.
@@
 The approach presented here is based on a second maximum likelihood
-fitting package developed in the LAT collaboration and called \pointlike
+fitting package developed in the LAT collaboration called \pointlike
 \citep{first_cat,matthew_kerr_thesis}.  We extended the code to allow
@@
 our catalog scan as well as the Monte Carlo validation of our method.
-Details on the \pointlike package can be found in \citep{matthew_kerr_thesis}.
+Details on the \pointlike package can be found in \cite{matthew_kerr_thesis}.
 
@@
 model of an extended source are separable, i.e. that the source
-model $M(l,b,E)=S(l,b)\times X(E)$.  To fit an extended source,
+model $M(l,b,E)=S(l,b)\times X(E)$ where $S(l,b)$ is the spatial
+distribution and $X(E)$ is the spectral distribution.  To fit an extended source,
 \pointlike convolves the extended source shape with the PSF (as a
@@
 section~\ref{monte_carlo_validation}, simultaneously fitting the position
-and extension is necessary to correctly calculate the statistical
+and extension is important to correctly calculate the statistical
 significance of the detection of extension.  For each position and
@@
 a model with a spatially extended source and a model
-with a point-like source and defined as
+with a point-like source and is defined as
 \begin{equation}
-  \tsext=2\log(\loglikelihood_\text{ext}/\loglikelihood_\text{ps}).
+  \tsext=2\log(\likelihood_\text{ext}/\likelihood_\text{ps}) = 2 (\loglikelihood_\text{ext}-\loglikelihood_\text{ps})
 \end{equation}
@@
 \citep{matthew_kerr_thesis}.  For radially symmetric extended sources,
-the angular part of the integral can be done analytically
+the angular part of the integral can be evaluated analytically
 \begin{align}
@@
 extended source due to numerical error in the convolution.  In most
-situations, this error would be insignificant.  But in particular for
+situations, this error is insignificant.  But in particular for
 very bright sources, this numerical error has the potential to bias the
-test statistic for the extension test. The source with an extended shape
-to the likelihood fitting it with its extension fixed to ${10^{-10}}\deg$.
-
-We estimate the errors on the extension
-by recalculating the likelihood for a set of extension values
-while keeping the position fixed.
+test statistic for the extension test. Therefore, when calculating
+\tsext, we compare the likelihood fitting the source with an extended
+spatial model to the likelihood when fixing its extension to ${10^{-10}}\deg$.
 
@@
 The localization error is calculated by fixing the extension and spectrum
-of the source and fitting a Gaussian to the likelihood as a function
+of the source and fitting to the likelihood function a Gaussian as a function
 of position.
@@
 
-\pointlike is important for LAT analysis that require many iterations
+\pointlike is important for LAT analyses that require many iterations
 such as source localization and extension fitting.  On the other hand,
@@
 analysis package, it has been more extensively validated for spectral
-analysis.  For that reason, in the following analysis  we use \pointlike
-to determinate the position and extension of a source and then determine
+analysis.  For those reasons, in the following analysis  we use \pointlike
+to determinate the position and extension of a source and subsequently determine
 the spectrum using \gtlike. Both \gtlike and \pointlike can be 
@@
 Unless explicitly mentioned, all \ts, \tsext, and spectral
-parameters were calculated using \gtlike using \pointlike's positions
-and extensions.
+parameters were calculated using \gtlike using the best-fit
+positions and extensiosn found with \pointlike.
 
@@
 extended if $\tsext>\tsinc$.
-Like extended sources described in section~\ref{gtlike_crosscheck},
+Similar to the case of extended sources described in section~\ref{gtlike_crosscheck},
 the spectrum of the two point sources can be refit using \gtlike.
@@
 \end{equation}
-Although these shapes are significantly different, the convolution
-of them with the PSF look similar.  Figure~\ref{compare_disk_gauss}
+Although these shapes are significantly different, their convolution
+with the PSF look similar.  Figure~\ref{compare_disk_gauss}
 demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
@@
 is defined in equation~\ref{gauss_pdf} and
-equation~\ref{disk_pdf} respectively.} This plot shows that we are
+equation~\ref{disk_pdf} respectively.} This plot shows that the LAT is 
 not very sensitive to probing the exact structure of an extended source.
@@
 
-\subsection{Significance of Extension}
 \label{monte_carlo_validation}
 
+We test the performance of \pointlike fitting the extension of
+point-like sources.
 \cite{mattox_egret} discuss that the test statistic distribution
@@
 in the test for source extension as the same conditions
-apply (with source flux $\Phi$ replaced by source radius $r$).
+apply (with the source flux $\Phi$ replaced by the source radius $r$ and
+$r<0$ being unphysical).
 To validate this claim, we performed a Monte Carlo
@@
 
-We simulated point sources of varying spectral models using
+We simulated point sources with various spectral forms using
 \gtobssim\footnote{\gtobssim is distributed by the Fermi Science Support
-Center \citep{fssc}.} and fit them them using \pointlike as both point
-and extended sources.  The point sources were simulated with a power-law
+Center \citep{fssc}.} and fit them with \pointlike using both point
+and extended source hypotheses.  The point sources were simulated with a power-law
 spectral model with integrated fluxes above 100 \mev ranging from $3\times
-10^{-9}$ to $10^{-6} \ph/\cm^2/\sec$ in six discrete steps and spectral
+10^{-9}$ to $10^{-6}$ \phflux in six discrete steps and spectral
 indices ranging from 1.5 to 3 in four discrete steps.  These values
-were picked to to represent typical source parameters in LAT-detected
+were picked to to represent typical source parameter of LAT-detected
 sources. The point sources were simulated on top of an isotropic
 background with an integrated flux above 100 \mev of $1.5\times10^{-5}$
+taken to be the same as the isotropic spectrum measured by EGRET
 \citep{sreekumar_isotropic}.  The Monte Carlo simulation was performed
@@
 using 1-100 \gev photons and the Pass 7\_V6 (P7\_V6) Source Instrument
-Response Function (IRFs).  For each point source, we used \pointlike
-to fit it as both a point and extended source and calculate \tsext and
-we only kept the sources which had a significant point source detection
-($\ts>25$).
-
-For most of the spectral models, ~30,000 statistically independent
+Response Function (IRFs, \cite{lat_on_orbit_psf}).  For each 
+significantly detected point source ($\ts>25$), we used \pointlike
+to fit it as an extended source and calculate \tsext.
+
+For each set of spectral parameters, $\approx30,000$ statistically independent
 simulations were performed. For the dimmer spectral models, many of the
@@
 be that \pointlike ignores energy dispersion which would change the
-PSF's shape as a function of energy. We emphasize that most of the
-time, our empirical curve lies to the left of the theoretical curve so
+PSF shape as a function of energy. We emphasize that many of
+the empirical distributions lies to the left of the theoretical curve so
 using the theoretical distribution would lead to an underestimate of the
@@
 
-\section{Extended Source Detection Threshold}\label{extension_sensitivity}
-
-We calculated the LAT's detection threshold to spatially extended
-sources. We define the detection threshold as the flux at which the value
-of $\tsext$ averaged over many statistical representations of a source
-is $\langle\tsext\rangle=16$ corresponding to a $4\sigma$ detection
+\section{Extended Source Detection Threshold}
+\label{extension_sensitivity}
+
+We calculated the LAT's detection threshold to resolve spatially extended
+sources as being extended. We define the detection threshold as the flux at which the value
+of $\tsext$ averaged over many statistical realizations of a source
+is $\langle\tsext\rangle=16$, corresponding to a $4\sigma$ detection
 (see section~\ref{monte_carlo_validation}).
@@
 brightness and
-instead over the actual two year time interval.  For each extension and
-spectral index, we picked a flux range which bracketed $\tsext=16$. We
-then picked ten flux points in this range and repeatedly simulated
-and then performed extension tests of the simulated extended source.
+simulated over the actual two year time interval of LAT observations.  
+For each extension and
+spectral index, we selected a flux range which bracketed $\tsext=16$
+and performed an extension test for $>100$ independent realizations of
+ten flux values in this range.
 We calculated $\langle\tsext\rangle=16$ by fitting a line to the flux
-and $\tsext$ values.
+and $\tsext$ values in this narrow range.
 
@@
 spectral indices from 1.5 to 3 and extension varying from $\sigma=0.1\deg$
-to $2.0\deg$.  The LAT's threshold for a significant detection
-of an extension of a LAT souce drops quickly with
+to $2.0\deg$.  The LAT's flux threshold for a significant detection
+of source extension drops quickly with
 increasing source size and reaches a minimum around 0.5\deg. 
@@
 and also using only 1-100\gev photons.
-Except for the hardest and largest sources, our detection threshold is
-almost unchanged when including photons with energies between 100 \mev and
+Except for very large ($>1\deg$) sources, our detection threshold is
+not substantially improved including photons with energies between 100 \mev and
 1 \gev.  This is also demonstrated in figure~\ref{four_plots_ic443}(b)
@@
 become increasingly important at low energy. For our extension search,
-we use therefore only photons with energies above 1 \gev.
-
-\begin{shaded}
-Figure~\ref{all_sensitivity} shows the flux threshold as a function of
-source extension for different background levels (1x, 10x, and 100x the
-nominal background), different spectral indices, and two different energy
-bands (1-100 \gev and 10-100 \gev).  The detection threshold is higher
-for sources in regions of higher background.  For a fixed 1-100 \gev or
-10-100 \gev flux, the LAT's detection threshold is only weakly depends
-upon the spectral index.  Overlaid on figure~\ref{all_sensitivity} are
-the LAT detected extended sources from table~\ref{known_extended_sources}
-and table~\ref{new_ext_srcs_table}.  This effect is most pronounced when
-using only photons with energies above 10 \gev. The extension thresholds
-are tabulated in table~\ref{all_sensitivity_table}.
+we therefore use only photons with energies above 1 \gev.
+
+\begin{shaded} Figure~\ref{all_sensitivity} shows the flux threshold
+as a function of source extension for different background levels (1x,
+10x, and 100x the nominal background), different spectral indices, and
+two different energy bands (1-100 \gev and 10-100 \gev).  The detection
+threshold is higher for sources in regions of higher background.  For a
+fixed 1-100 \gev or 10-100 \gev flux, the LAT's detection threshold
+is only weakly depends upon the spectral index.  This effect is most
+pronounced when using only photons with energies above 10 \gev.  Overlaid
+on figure~\ref{all_sensitivity} are the LAT detected extended sources
+that will be discussed in sections~\ref{validate_known}
+and \ref{new_ext_srcs_section}.  The extension thresholds are tabulated
+in table~\ref{all_sensitivity_table}.
 
@@
 the Galactic plane.  For small extended sources, our detection threshold
-improves better than $\sqrt{\text{t}}$ because at high energies, where we
+improves by a factor larger than the square root of time because at high energies, where we
 are most sensitive to extension, the background levels are in the Poisson
 instead of Gaussian regime.  For large extended sources, the relevant
-background is larger and the improvement is closer to $\sqrt{\text{t}}$.
+background is larger and the improvement is closer to the expected
+factor of the square root of time.
 \end{shaded}
@@
 
-We test all sources in the 2FGL catalog for spatial extendedness.
+We test all sources in the 
+second Fermi-LAT Catalog (2FGL) for spatial extendedness.
 2FGL is a catalog of 1873 sources detected by the LAT.  It included
@@
 
-As was shown, we gain little in sensitivity using photons with energies
+As was shown in section~\ref{extension_sensitivity}, we gain little in sensitivity using photons with energies
 below 1 \gev. On the other hand, the large PSF at low energy makes us
@@
 confusion becomes less of a problem since most LAT sources are not
-significant at energies above 10 \gev.  Using higher energies, we might
-expect to detect harder sources in more complicated regions. This is
-beneficial for regions near pulsars which cutoff before 10 \gev and was
+significantly detected at energies exclusively above 10 \gev. So we
+expect to be able to resolve harder sources in more complicated regions. The $>10$ \gev
+analysis is
+especially
+beneficial for regions near pulsars which are not significantly above 10 \gev and was
 successfully used in detecting HESS\,J1825-137 and MSH 15-52 with the LAT
@@
 \pointlike
-assuming the source had a uniform radially symmetric surface brightness.
+assuming the source had a uniform radially symmetric surface brightness
+and a power-law spectral model.
 We used a circular $10\deg$ region of interest centered on our source and
@@
 interest due to close-by background sources.
-We modeled each source with a power-law spectral model.
 
@@
 sources which were within 0.5\deg of the source of interest. This was
-done to avoid a concern that extended sources would end up in 2FGL as
-multiple point sources. These spurious sources would then distort the
+done to avoid a concern that extended sources are included in 2FGL as
+multiple point sources. These spurious sources could distort the
 extension fit.  Instead, when a source is found to be significantly
@@
 
-Based on size vs. distance considerations,
+Based on size vs. physical distance considerations,
 we expect most extended sources to be inside our Galaxy.  Unfortunately, the \gev emission
@@
 Cygnus Loop were
-first reported in \citep{ic443,w28,w44,w51c,cygnus_loop_lat}.  A
+first reported in \cite{ic443,w28,w44,w51c,cygnus_loop_lat}.  A
 detailed publication by the LAT
 collaboration about W30 is still in preparation.
-\gev emission from W30 was also studied in \citep{castro_and_slane_2010}.
+\gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
 Using 1-100 \gev photons, our analysis significantly detected the
@@
 % 3 PWN
-Three pulsar wind nebula Vela X, MSH 15-52, and HESS\,J1825-137 were
+Three PWNe Vela X, MSH 15-52, and HESS\,J1825-137 were
 included in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  Using photons
@@
 %   Flux = PowerLaw(norm=6.21e-14,index=2.22,e0=10000).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%        = 4.7804242225163421e-11 ergs/cm^2/s
-%   Luminosity =  Flux * 4*pi*r^2 = 4.78e-11 ergs/cm^2/s * 4*pi * (2.2 kpc )**2 in ergs/s
+%        = 4.7804242225163421e-11 ergs cm^-2 s-1
+%   Luminosity =  Flux * 4*pi*r^2 = 4.78e-11 ergs cm^-2 s^-1 * 4*pi * (2.2 kpc )**2 in ergs/s
 %              = 2.8e34 ergs/s from 1.0-100 gev
@@
 LAT sources to the 42 extended H.E.S.S. sources.  Because of the large
-field of view and all sky coverage, the LAT can more easily measure
+field of view and all-sky coverage, the LAT can more easily measure
 larger sources including the LMC and SMC.  On the other hand, the smaller
@@
 
-\tablenotetext{a}{Integral 1-100 \mev flux in units of $\ph/\cm^2/\sec$}
+\tablenotetext{a}{Integral 1-100 \mev flux in units of \phflux}
 
@@
       integral fluxes in the analyzed energy range (1-100 \gev or 10-100
-      \gev) in units of $10^{-10}\ph/\cm^2/\sec$.
+      \gev) in units of $10^{-10}\phflux$.
       }
@@
     \caption{
-    The LAT's projected detection theshold to extension after 10 years for a power-law
+    The LAT's projected detection threshold to extension after 10 years for a power-law
     source of spectral index 2 against 10 times the isotropic background
@@
   \caption{
-  A test statistic map generated for the region around supernova
-  remnant IC443 using 1-100 \gev photons.  (a) test statistic map after
+  A test statistic map generated for the region around the SNR 
+  IC443 using 1-100 \gev photons.  (a) test statistic map after
   subtracting IC443 modeled as a point source. (b) same as (a), but
@@
 integrated in the fit energy range (either 1-100 \gev or 10-100 \gev)
-in units of $10^{-9}\ph/\cm^2/\sec$.
+in units of $10^{-9}\phflux$.
 }

### 2011-08-16 extended_catalog/paper/extended_catalog.tex
lots of keiths changes

@@
 Based on size vs. physical distance considerations,
-we expect most extended sources to be inside our Galaxy.  Unfortunately, the \gev emission
+we expect most extended sources to be located inside our Galaxy
+adn thus to be concentrated along the Galactic plane.  Unfortunately, the \gev emission
 in the Galactic plane is dominated by extremely structured 
 diffuse emission from the interactions of cosmic rays with the
-intergalactic medium.  Finding sources on top of this emission is difficult
+interstellar medium.  Finding sources on top of this emission is difficult
 \citep{first_diffuse_paper} as has been discussed in 1FGL and 2FGL
@@
 likelihood when fitting its flux. \ts maps are useful to look for residual
-structure in the sky mode.  Figure~\ref{res_tsmaps} shows a residual \ts
-map for the extended source IC443.  We also generated plots of the sum of
+structure in the sky model.  Figure~\ref{res_tsmaps} shows a residual \ts
+map for the extended source IC443.  The residual \ts map indicates that
+the spatially extended model for IC443 is a significantly better description
+of the observed photons.
+We also generated plots of the sum of
 all counts within a given distance of the source and compared it to the
-model predictions of a point source.  The plots were binned uniformly
-in $\Delta \theta^2$ so that an isotropic background would be flat.
+model predictions of a point source.  
 An example radial integral plot is shown for the extended source IC443
@@
 
+\begin{figure}
+  \begin{center}
+  \includegraphics{ic443_plots/res_tsmap_ic443.pdf}
+  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1
+
+  \caption{
+  A test statistic map generated for the region around the SNR 
+  IC443 using 1-100 \gev photons.  (a) test statistic map after
+  subtracting IC443 modeled as a point source. (b) same as (a), but
+  IC443 modeled as extended source. Crosses represent sources included
+  in the model of the region.  Such maps were generated for all extended
+  source candidates.}
+  \label{res_tsmaps}
+  \end{center}
+\end{figure}
+
 \clearpage
@@
     \label{example_bad_fit}
-  \end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics{ic443_plots/res_tsmap_ic443.pdf}
-  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1
-
-  \caption{
-  A test statistic map generated for the region around the SNR 
-  IC443 using 1-100 \gev photons.  (a) test statistic map after
-  subtracting IC443 modeled as a point source. (b) same as (a), but
-  IC443 modeled as extended source. Crosses represent sources included
-  in the model of the region.  Such maps were generated for all extended
-  source candidates.}
-  \label{res_tsmaps}
   \end{center}

### 2011-08-16 extended_catalog/paper/extended_catalog.tex
done with keiths changes

@@
 in figure~\ref{four_plots_ic443}(c).  For each source, we also made
-Galactic and extragalactic diffuse emission subtracted smoothed counts
+diffuse-emission-subtracted smoothed counts
 maps. Figure~\ref{four_plots_ic443}(d) shows an example for IC443.
@@
 integral distributions to identify cases in which the extension fit
-is clearly biased by large-scale residuals in the diffuse emission
+is clearly influenced by large-scale residuals in the diffuse emission
 and hence the extension measurement unreliable.  An example of such a
 case is shown in figure~\ref{example_bad_fit}. It shows a Galactic and
-isotropic diffuse emission subtracted smoothed counts map of this source
+isotropic diffuse-emission-subtracted smoothed counts map of this source
 using 1-100 \gev photons.  In this region along the Galactic plane,
@@
 a result, 2FGL\,J1856.2+0450c fit to an extension of 1.83\deg and the
-result is statistically significant with \tsext=45.4.  By looking at
-the residuals, it is clear that this complicated region is not fit well
+result is statistically significant with \tsext=45.4. However, by looking at
+the residuals it is clear that this complicated region is not fit well
 even though the source's extension is statistically significant. We do
@@
 we took the spatial and spectral model found using \pointlike and
-redetermined the spectral 
+re-determined the spectral 
 parameters using
@@
 We estimate a systematic error on the extension of a source due to
-uncertainty in our knowledge of the angular resolution of the LAT.  Before
+uncertainty in our knowledge of the LAT PSF.  Before
 launch, the LAT PSF was determined by a detector simulation which was
-verified in accelerator tests \citep{atwood_LAT_mission}.  A discrepancy
-was found in flight data above a few \gev in the PSF compared to the
-shape of bright AGN.  A publication on this issue is in preparation
+verified in accelerator tests \citep{atwood_LAT_mission}. However,
+in-flight data revealed a discrepancy
+above a few \gev in the PSF compared to the
+photon angular distribution of bright AGN.  A publication on this issue is in preparation
 \citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit empirically to
@@
 of the PSF from bright AGN is substantially better than the Monte Carlo
-representation of the PSF so this systematic errors is conservative.
+representation of the PSF so this estimate of systematic errors is conservative.
 
@@
 due to uncertainty in the model of the Galactic diffuse emission by
-using an alternative diffuse model. The alternative model was based on
-the GALPROP\footnote{GALPROP is a software package for calculating the
+using an alternative diffuse model. An alternative model was based upon
+GALPROP\footnote{GALPROP is a software package for calculating the
 Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
 in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
-references} model used in the LAT analysis of the isotropic diffuse
+references} and used in the LAT analysis of the isotropic diffuse
 emission \citep{isotropic_lat}.  
-The intensities of various contributions to the galactic
+The intensities of various components to the galactic
 diffuse emission are then fitted individually using a spatial
@@
 It is not expected that this diffuse model is superior to the standard
-LAT model.  But adding degrees of freedom to the background model can
+LAT model that was obtained through an all-sky fit.  But adding degrees of freedom to the background model can
 remove likely spurious sources that correlate with features in the
@@
 
-\section{Analysis of Extended Sources in 2FGL}
+\section{Analysis of Extended Sources Identified in 2FGL}
 \label{validate_known}
@@
 
-Two nearby galaxies the Large Magalenic Cloud and the Small Magalenic
-Cloud were included in 2FGL \citep{lmc,smc}.  They were significantly
+Two nearby satellite galaxies of the Milky Way the Large Magalenic Cloud (LMC)
+and the Small Magalenic
+Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
 detected using 1-100 \gev photons. Our
 fit extension is comparable to the published result, but we note that
-previous publication used a more complicated two Gaussian surface
-brightness spatial model when fitting the LMC.
+previous LAT collaboration publication on LMC used a more complicated two Gaussian surface
+brightness spatial model when fitting it (\citep{lmc}).
 
@@
 Three PWNe Vela X, MSH 15-52, and HESS\,J1825-137 were
-included in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  Using photons
-with energy above 10 \gev, we significantly detected the extension of
-HESS\,J1825-137.  To improve the model of this source, we removed the
+already identified in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  
+HESS\,J1825-137 was significantly detected using 10-100 \gev photons.
+To improve the model of this source, we removed the
 nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
@@
 Our analysis was unable to resolve Vela X which would have required first
-removing the pulsed photons from the Vela pulsar. This is beyond the
+removing the pulsed photons from the Vela pulsar which is beyond the
 scope of this paper.  Our analysis also failed to detect a significant
@@
 of kpc-scale jets of distant galaxies.  Therefore AGN are not expected
-to be spatially resolvable and provide a good calibration source to
+to be spatially resolvable by the LAT and provide a good calibration source to
 demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
@@
 
-Following 1FGL, the LAT collaboration published a list called 1LAC
+Following 1FGL, the LAT collaboration published a list 
 of sources that
-had a high probability association with AGN \citep{first_agn_cat}.
+had a high probability association with AGN 
+called 1LAC \citep{first_agn_cat}.
 1FGL had 709 1FGL sources associated with 671 distinct AGN at high
 latitude ($|b|>10\deg$).  
-Using two years of data and 2FGL, the LAT collaboraiton
+Using two years of data and 2FGL, the LAT collaboration
 associated 1016 2FGL sources
-with AGN \citep{second_agn_cat}.
+with AGN called 2LAC \citep{second_agn_cat}.
 To avoid systematic problems with AGN classification, we
@@
 Of the 885 clean AGN, we select 783 of these 2FGL sources which
-are significant above 1 \gev and fit each of them for extension.
+are significantly-detected above 1 \gev and fit each of them for extension.
 A histogram of the \tsext values computed for these AGN is
@@
     \caption{
-    A Diffuse emission subtracted 1-100 \gev counts map of the region
+    A diffuse-emission-subtracted 1-100 \gev counts map of the region
     around 2FGL\,J1856.2+0450c smoothed by a 0.1\deg Gaussian kernel. The
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
-  \caption{A Diffuse emission subtracted 1-100
+  \caption{A diffuse-emission-subtracted 1-100
   \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
@@
   \caption{
-  A Diffuse emission subtracted 1-100 \gev counts
+  A diffuse-emission-subtracted 1-100 \gev counts
   map of (a) the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
@@
   \end{center}
-  \caption{A Diffuse emission subtracted 1-100 \gev
+  \caption{A diffuse-emission-subtracted 1-100 \gev
   counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
-  \caption{A Diffuse emission subtracted 10-100
+  \caption{A diffuse-emission-subtracted 10-100
   \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
@@
   \caption{
-    A Diffuse emission subtracted 10-100
+    A diffuse-emission-subtracted 10-100
     \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
-  \caption{A Diffuse emission subtracted 10-100
+  \caption{A diffuse-emission-subtracted 10-100
   \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
@@
   \caption{
-  A Diffuse emission subtracted 10-100 \gev counts map of
+  A diffuse-emission-subtracted 10-100 \gev counts map of
   (a)

### 2011-08-19 extended_catalog/paper/extended_catalog.tex
eps

@@
 \usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
-
-% for highlighting text
-\usepackage{framed}
-\colorlet{shadecolor}{yellow}
 
@@
 \newcommand{\cm}{\text{cm}\xspace}
-\renewcommand{\sec}{\text{s}\xspace}
+\newcommand{\km}{\text{km}\xspace}
 \newcommand{\phflux}{\ensuremath{\ph\ \cm^{-2}\s^{-1}}\xspace}
@@
 \newcommand{\xmmnewton}{\text{{\em XMM-Newton}}\xspace}
+\newcommand{\fermi}{\textit{Fermi}\xspace}
 
@@
 
-\renewcommand{\deg}{\ensuremath{^\circ}\xspace}
-
 % the program names
-\newcommand{\pointlike}{\text{\em pointlike}\xspace}
-\newcommand{\python}{\text{\em python}\xspace}
-\newcommand{\gtlike}{\text{\em gtlike}\xspace}
-\newcommand{\gtobssim}{\text{\em gtobssim}\xspace}
-\newcommand{\minuit}{\text{\em Minuit}\xspace}
-\renewcommand{\approx}{\sim\!\xspace}
-
+\newcommand{\gtlike}{\ensuremath{\mathtt{gtlike}}\xspace}
+\newcommand{\pointlike}{\ensuremath{\mathtt{pointlike}}\xspace}
+\newcommand{\gtobssim}{\ensuremath{\mathtt{gtobssim}}\xspace}
+\newcommand{\minuit}{\ensuremath{\mathtt{minuit}}\xspace}
+
+\newcommand{\hl}[1]{{\color{red}#1}}
+
+\begin{document}
+
+\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight
+Data}
 \shorttitle{Search for Extended LAT Sources}
 
-\begin{document}
-
-\title{Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight
-Data}
+\keywords{
+Catalogs;
+Fermi Gamma-ray Space Telescope; 
+Gamma rays: observations; 
+ISM: supernova remnants;
+Methods: statistical
+pulsar wind nebula
+}
 
@@
 the Large Area Telescope (LAT), the primary science instrument on the
-{\em Fermi Gamma-ray Space Telescope} (FGST). 
+{\em \fermi Gamma-ray Space Telescope} (\fermi). 
 Spatial extension
@@
 in addition to the twelve spatially extended sources reported in the
-second Fermi-LAT Catalog (2FGL).
+second \fermi-LAT Catalog (2FGL).
 \end{abstract}
 
-\listoftodos
-
 \section{Introduction}
 
-The Large Area Telescope (LAT) is a pair conversion telescope on the Fermi
-Gamma-Ray Space Telescope (FGST) that been surveying the $\gamma$-ray
-sky since June 2008.  The LAT has a broad energy coverage (20 \mev to $>300$
-\gev), wide field of view ($\approx 2.4 \sr$), and large effective area
-($\approx 8000 \cm^2$ at $>1 \gev$).
+The Large Area Telescope (LAT) is a pair conversion telescope on the {\em \fermi
+Gamma-Ray Space Telescope} (\fermi) that been surveying the $\gamma$-ray
+sky since 2008 June.  The LAT has a broad energy coverage (20 \mev to $>300$
+\gev), wide field of view ($\sim 2.4 \sr$), and large effective area
+($\sim 8000 \cm^2$ at $>1 \gev$).
 
@@
  with extensions varying from
-$~0.1\deg$ to $~0.25\deg$ \citep{hess_plane_survey}.
+$\sim0\fdg1$ to $\sim0\fdg25$ \citep{hess_plane_survey}.
 In fact, within
@@
 these findings, it can be expected that if the source population at \gev
-energies has similar properties, that at least some of the Fermi-LAT
+energies has similar properties, that at least some of the \fermi-LAT
 sources in our Galaxy should be spatially resolvable at \gev energies.
 
-\begin{shaded} 
+\hl{
 High energy $\gamma$-rays are produced by the decay of $\pi^0$s produced
@@
 Galactic plane are unidentified. Some of these sources could produce
-hadronic cosmic rays up to $\approx 10^{15}$ eV and subsequently radiate
+hadronic cosmic rays up to $\sim 10^{15}$ eV and subsequently radiate
 $\gamma$-rays through $\pi^0$ decay \citep{blandford_and_eichler_1987}.
@@
 determine the emission mechanisms of these high energy sources.
-\end{shaded}
+}
 
@@
 PSF is limited at its lowest detectable energies by multiple scattering in the tracker
-and the 68\% containment radius of the PSF is approximately 5.1\deg
+and the 68\% containment radius of the PSF is approximately $5\fdg1$
 at 100 \mev  when averaged over instrument acceptance and including
@@
 tracker. The PSF improves with energy and approaches a limit given
-by the granularity of the silicon strips and is 0.14\deg at 10 \gev
+by the granularity of the silicon strips and is $0\fdg14$ at 10 \gev
 \citep{on_orbit_calibration}.  However, since most high energy
@@
 of the source and varying the extension until the likelihood has fallen
-by $\tfrac{1}{2}$, corresponding to a $1\sigma$ error.  This method is
+by \onehalf, corresponding to a $1\sigma$ error.  This method is
 shown schematically in figure~\ref{four_plots_ic443}(a) which shows the
@@
 demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
-a radially symmetric uniform brightness and the Gaussian surface brightness of size 0.5\deg.\footnote{To
+a radially symmetric uniform brightness and the Gaussian surface brightness of size 0\fdg5.\footnote{To
 allow a valid comparison between Gaussian and disk shaped morphologies,
@@
 \begin{equation}\label{ts_ext_distribution}
-  P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
+  P(\ts)=\onehalf(\chi^2_1(\ts)+\delta(\ts)).
 \end{equation}
@@
 
-For each set of spectral parameters, $\approx30,000$ statistically independent
+For each set of spectral parameters, $\sim30,000$ statistically independent
 simulations were performed. For the dimmer spectral models, many of the
@@
 Figure~\ref{index_sensitivity} shows the threshold for sources of four
-spectral indices from 1.5 to 3 and extension varying from $\sigma=0.1\deg$
-to $2.0\deg$.  The LAT's flux threshold for a significant detection
+spectral indices from 1.5 to 3 and extension varying from $\sigma=0\fdg1$
+to $2\fdg0$.  The LAT's flux threshold for a significant detection
 of source extension drops quickly with
-increasing source size and reaches a minimum around 0.5\deg. 
+increasing source size and reaches a minimum around 0\fdg5. 
 Figure~\ref{index_sensitivity} shows
@@
 energy bins between 100 \mev and 100 \gev. For IC443, which has a
-spectral index $\approx2.4$, almost the entire increase in \ts comes
+spectral index $\sim2.4$, almost the entire increase in \ts comes
 from energies above 1 \gev.  On the other hand, other systematic errors
@@
 
-\begin{shaded} Figure~\ref{all_sensitivity} shows the flux threshold
+\hl{
+Figure~\ref{all_sensitivity} shows the flux threshold
 as a function of source extension for different background levels (1x,
@@
 factor of the square root of time.
-\end{shaded}
+}
 
@@
 We test all sources in the 
-second Fermi-LAT Catalog (2FGL) for spatial extendedness.
+second \fermi-LAT Catalog (2FGL) for spatial extendedness.
 2FGL is a catalog of 1873 sources detected by the LAT.  It included
@@
 Our analysis setup is closely related to the setup used for the
-derivation of the catalog We used the same two years of data from August
-4, 2008 to August 1, 2010 and we used the same Pass 7\_V6 (P7\_V6)
+derivation of the catalog We used the same two years of data from 
+2008 August 4
+to 2010 August 1 and we used the same Pass 7\_V6 (P7\_V6)
 Source class event selection and IRFs \citep{lat_on_orbit_psf}.  We used the same models to describe the
@@
 Finally, when analyzing the region, we automatically removed other 2FGL
-sources which were within 0.5\deg of the source of interest. This was
+sources which were within 0\fdg5 of the source of interest. This was
 done to avoid a concern that extended sources are included in 2FGL as
@@
 there appears to be large-scale residual in the diffuse emission. As
-a result, 2FGL\,J1856.2+0450c fit to an extension of 1.83\deg and the
+a result, 2FGL\,J1856.2+0450c fit to an extension of 1\fdg83 and the
 result is statistically significant with \tsext=45.4. However, by looking at
@@
 the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
-ROI with a pixel size of 0.03\deg.
+ROI with a pixel size of 0\fdg03.
 We obtained a second measure of \tsext from \gtlike for the extension
@@
 using 1-100 \gev photons to have an 
-extension of $0.37\deg\pm0.03\deg_\stat\pm0.02\deg_\sys$ 
+extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
 with an extension
 significance of $\tsext=46.3$.  The source was fit to a position of
-$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
-counts map of this source.  This source is coincident with the one year
+$(l,b)=(260\fdg32,-3\fdg28)$.  
+This source is coincident with the one year
 catalog source 1FGL\,J0823.3-4248.
+\hl{
+Figure~\ref{1FGL_J0823.3-4248} shows a
+counts map of this source
+and figure~\ref{snr_seds}(a) shows the LAT spectrum of it.
+}
 
@@
 
-\begin{shaded}
+\hl{1
 This extended source is spatially coincident with the middle-aged
@@
 Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
-which leads to a 1-100 \gev luminosity of $\approx 3\times 10^{34}$ ergs/\s.
+which leads to a 1-100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.
 
@@
 \citep{cygnus_loop_lat}.
-\end{shaded}
+}
 
@@
 The source 2FGL\,J1627.0-2425c was found using 1-100 \gev photons to
-have an extension of $0.41\deg\pm0.05\deg_\stat\pm0.02\deg_\sys$ with
+have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
 an extension significance of $\tsext=31.1$.  The best fit position is
-$(l,b)=(353.08\deg, 16.78\deg)$.  This source is coincident with the one
+$(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
 year catalog source 1FGL\,J1628.6-2419c.  A counts map showing this source
@@
 
-\begin{shaded}
+\hl{
 This source is in a region of remarkably complicated diffuse emission.
-Even though it is 16\deg from the Galactic plane, the source is on
+Even though it is $16\deg$ from the Galactic plane, the source is on
 top of the core of the Ophiuchus molecular cloud which contains massive
@@
 \citep{isabelle_dark_gass}. Embedded star-forming regions make it even
-more challenging to measure the column density of dust.  Infared and CO
-contours are overlaid on figure~\ref{1FGL_J1628.6-2419c} and there is good
-spatial correlation with the \gev emission \citep{iras_rho_ophiuci}.
-Therefore this source might represent an inadequacy in the diffuse
-$\gamma$-ray model
-\end{shaded}
+more challenging to measure the column density of dust.  Infared and 
+${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
+contours are overlaid on figure~\ref{1FGL_J1628.6-2419c}. There is good
+spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}
+so this source might represent an inadequacy in the diffuse
+$\gamma$-ray model.
+}
 
@@
 The source 2FGL\,J1712.4-3941 was found using 1-100 \gev
-photons to have an extension $0.56\deg\pm0.04\deg_\stat\pm0.02\deg_\sys$
+photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
 with an extension significance of $\tsext=39.6$.  This source was
-fit to a position of $(l,b)=(347.25\deg,-0.54\deg)$.  The source
+fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  The source
 is coincident with the one year catalog source 1FGL\,J1711.7-3944c.
@@
 using 10-100 \gev photons to have an
-extension of $1.13\deg\pm0.08\deg_\stat\pm0.05\deg_\sys$ 
+extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
 with an extension
 significance of $\tsext=87.2$.  The source was fit to a position of
-$(l,b)=(266.29\deg,-1.43\deg)$.  Figure~\ref{Vela_Jr} shows a counts
+$(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
 map of this source.
@@
 the position of the nearby catalog source 2FGL\,J0854.7-4501 to
-$(l,b)=(266.24\deg,0.49\deg)$ to better fit its position at high energies
+$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
 in the presence of of the extended source.  In addition, we removed the
@@
 The source 2FGL\,J1615.0-5051 was found using 10-100 \tev
-photons to have an extension of $0.33\deg\pm0.04\deg_\stat\pm0.01\deg_\sys$
+photons to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
 with an extension significance of \tsext=16.3.  The source
-was fit to a position of $(l,b)=(332.38\deg,-0.14\deg)$.
+was fit to a position of $(l,b)=(332\fdg38,-0\fdg14)$.
 This source is coincident with the one year catalog source
@@
 
-This source is less than 1\deg away from 2FGL\,J1615.2-5138 which is
+This source is less than $1\deg$ away from 2FGL\,J1615.2-5138 which is
 also spatially extended (see section~\ref{section_2FGL_J1615.2-5138}).
@@
 Gaussian surface brightness.  This size corresponds to a 68\% containment
-radius of $\rsixeight=0.21\deg\pm0.01\deg$. This size is comparable to the LAT
-size $\rsixeight=0.27\deg\pm0.03\deg$ (see section~\ref{compare_source_size}).
-Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
+radius of $\rsixeight=0\fdg21\pm0\fdg01$. This size is comparable to the LAT
+size $\rsixeight=0\fdg27\pm0\fdg03$ (see section~\ref{compare_source_size}).
+Figure~\ref{hess_seds}(a) shows that the LAT spectrum of 2FGL\,J1615.0-5051
 connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.
 
-\begin{shaded}
+\hl{
 HESS\,J1616-508 is located in the region of two SNRs, RCW103
@@
 pulsar could be responsible for the emission of HESS\,J1616-508.
-Because HESS\,J1616-508 is 9' away from PSR J1617-5055, this would
+Because HESS\,J1616-508 is $9\arcmin$ away from PSR J1617-5055, this would
 require an assymetric X-ray PWNe to power the \tev emission. However,
 \chandra ACIS observations revealed only an underluminous PWN of
-about $\approx1'$ size around the pulsar which was not oriented
+about $\sim1\arcmin$ size around the pulsar which was not oriented
 towards the \tev emission, rendering this association as uncertain
@@
 understand this region.
-\end{shaded}
+}
 
@@
 The source 2FGL\,J1615.2-5138 was found using 10-100 \gev
-photons to have an extension of $0.42\deg\pm0.03\deg_\stat\pm0.01_\sys$
+photons to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
 with an extension significance of \tsext=48.0.  The source was fit to a
-position of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
+position of $(l,b)=(331\fdg66,-0\fdg66)$.  This source is coincident
 with the one year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
@@
 on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian
-extension of $\sigma=0.23\deg\pm0.02\deg$ and $\sigma=0.15\pm0.02$
+extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0.15\pm0.02$
 in the semi-major and semi-minor axis. This size corresponds
-to a 68\% containment size of $\rsixeight=0.35\deg\pm0.03\deg$
+to a 68\% containment size of $\rsixeight=0\fdg35\pm0\fdg03$
 and $0.23\pm0.03$.  This elliptical size matches the LAT size
-$\rsixeight=0.35\deg\pm0.03\deg$.  Figure~\ref{hess_seds} shows
+$\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds}(b) shows
 that the LAT spectrum of 2FGL\,J1615.2-5138 connects smoothly to
@@
 
-\begin{shaded}
+\hl{
 There are five nearby pulsars, but none are luminous enough to
@@
 acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
-\end{shaded}
+}
 
@@
 using 10-100 \gev photons to
-have an extension of $0.44\deg\pm0.04\deg_\stat\pm0.03\deg_\sys$ 
+have an extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ 
 with an extension
 significance of \tsext=64.5.  The source was fit to a position of
-$(l,b)=(336.41\deg,0.22\deg)$.  This source is coincident with the one
+$(l,b)=(336\fdg41,0\fdg22)$.  This source is coincident with the one
 year catalog source 1FGL\,J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
@@
 We then iteratively relocalized the source 2FGL\,J1635.4-4717c
-to $(l,b)=(337.230\deg,0.346\deg)$ and 2FGL\,J1636.3-4740c to
-$(l,b)=(336.968\deg,-0.066\deg)$ while fitting the extension of
+to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3-4740c to
+$(l,b)=(336\fdg97,-0\fdg07)$ while fitting the extension of
 2FGL\,J1632.4-4753c.  In addition we removed from our model four
@@
 elliptical Gaussian surface brightness.  This corresponds to a 68\%
-containment size $\rsixeight=0.31\deg\pm0.08\deg$ and $0.09\pm0.06$
+containment size $\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$
 along the semi-major and semi-minor axis. This size is consistent with
-the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.  Figure~\ref{hess_seds}
+the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}(c)
 shows that the LAT spectrum of 2FGL\,J1635.4-4717c connects smoothly to
@@
 
-\begin{shaded}
+\hl{
 \cite{hess_plane_survey} argued that HESS\,J1632-478
@@
 extension disfavors the association.  Further observations by
-\xmmnewton reveal extended emission of size $\approx32''\times15''$
+\xmmnewton reveal extended emission of size $\sim32\arcsec\times15\arcsec$
 and inside point-like emission coincident with the peak
@@
 and \tev gamma rays.
-\end{shaded}
+}
 
@@
 The source 2FGL\,J1837.3-0700c was found with 10-100 \gev photons to
-have an extension of $0.35\deg\pm0.08\deg_\stat\pm0.03\deg_\sys$ with an
+have an extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an
 extension significance of $\tsext=18.8$.  The source was fit to a position
-of $(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
+of $(l,b)=(25\fdg08,0\fdg13)$.  This source is coincident with the one
 year catalog source 1FGL\,J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
@@
 2FGL\,J1839.3-0558c.  To get a good fit of 2FGL\,J1837.3-0700c, we
-relocalized 2FGL\,J1834.7-0705c to $(l,b)=(24.77\deg,0.50\deg)$,
-2FGL\,J1836.8-0623c to $(l,b)=(25.57\deg,0.32\deg)$, and
-2FGL\,J1839.3-0558c to $(l,b)=(26.08\deg,0.23\deg)$.  We removed the
+relocalized 2FGL\,J1834.7-0705c to $(l,b)=(24\fdg77,0\fdg50)$,
+2FGL\,J1836.8-0623c to $(l,b)=(25\fdg57,0\fdg32)$, and
+2FGL\,J1839.3-0558c to $(l,b)=(26\fdg08,0\fdg23)$.  We removed the
 nearby catalog source 2FGL\,J1835.5-0649 which is part of the extended
@@
 with an elliptical Gaussian surface brightness.  This corresponds
-to a 68\% containment radius of $\rsixeight=0.18\deg\pm0.03\deg$ and
-$0.08\deg\pm0.03\deg$ along the semi-major and semi-minor axis. The
+to a 68\% containment radius of $\rsixeight=0\fdg18\pm0\fdg03$ and
+$0\fdg08\pm0\fdg03$ along the semi-major and semi-minor axis. The
 size is comparable to LAT which fit a 68\% containment radius of
-$\rsixeight=0.29\deg\pm0.07\deg$.  the size difference is not significant
-(less than 2 sigma).  Figure~\ref{hess_seds} shows that the LAT spectrum
+$\rsixeight=0\fdg29\pm0\fdg07$.  the size difference is not significant
+(less than 2 sigma).  Figure~\ref{hess_seds}(d) shows that the LAT spectrum
 connects smoothly to the H.E.S.S spectrum of HESS\,J1837-069.
 
-\begin{shaded}
+\hl{
 HESS\,J1837-069 is coincident
@@
 resolved by \chandra to be a bright point source surrounded by
-a $\sim2'$ nebula \citep{pulsations_HESS_J1837-069} and so the
+a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069} and so the
 $\gamma$-ray emission may be powered by this pulsar.  A second
@@
 AX J1837.3-0652.
-\end{shaded}
+}
 
@@
 The source 2FGL\,J2021.5+4026 was found with 10-100 \gev
-photons to have an extension of $0.59\deg\pm0.03\deg_\stat\pm0.02\deg_\sys$
+photons to have an extension of $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
 with an extension significance of $\tsext=116.4$.  The source was
-fit to a position of $(l,b)=(78.18\deg,2.19\deg)$.  This source
+fit to a position of $(l,b)=(78\fdg18,2\fdg19)$.  This source
 is coincident with the one year catalog source 1FGL\,J2020.0+4049.
+\hl{
 Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source.
+and figure~\ref{snr_seds}(b) shows that the LAT spectrum of it.
+}
 
@@
 the two year catalog into our background model.  The new source is was
-localized to a position of $(l,b)=(78.85\deg,2.67\deg)$ and had $\ts=13.5$ .
+localized to a position of $(l,b)=(78\fdg85,2\fdg67)$ and had $\ts=13.5$ .
 Although the source is not very significant, not including it into the
@@
 
-This source is spatially coincident with the $\gamma$ Cygni SNR.  Contours of
-$\gamma$ Cygni at 408MHz from the Canadian Galactic Plane Survey are overlaid
-on figure~\ref{1FGL_J2020.0+4049} and there is good spatial agreement
-with the LAT emission \citep{canadian_galactic_plane_survey}.
-
-% Radio observations
-% ...
-
-% X-ray observations
-% ...
-
-% Age
-% ...
-
-% Distance
-%   1.5 kpc Landecker et al 1980 (from integral paper)
-
-% Optical (Mavromatakis 2003 (from integral paper)
-
-% EGRET observations
-%   3EG J2020+4027
-%   ...
-
+\hl{
+This extended sources is coincident with 2CG\,078+01 and
+3EG\,J2020+4017 detected by COS B and EGRET respectively
+\citep{second_cos_b_catalog,third_egret_catalog}.  This source is
+spatially coincident with the $\gamma$-Cygni SNR and has been speculated
+to be be the interaction of accelerated particles in the SNR interacting
+with dense molecular clouds \citep{pollock_1985,gaisser_1998}.  But this
+association was disfavored when the LAT \gev emission from this source
+was detected to be pulsed 
+(PSR J2021+4026,\cite{first_lat_pulsar_cat}).
+
+Milagro detected a $4.2\sigma$
+excess at energies $\sim 30 \tev$ from the location of
+this source in the previous LAT bright $\gamma$-ray source
+list. \cite{lat_bsl,milagro_bright_source_list}.  Veritas also detected
+an extended source VER\,J2019+407 coincident with the SNR above 200
+\gev and suggested the \tev emission could be a shock-cloud interaction
+in $\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10-100
+\gev photons to avoid PSR J2021+4026, we resolve an
+extended source whose inferred \gev size well matches the radio size of
+$\gamma$-Cygni, as can be seen in figure~\ref{1FGL_J2020.0+4049}
+which overlays contours of $\gamma$-Cygni at 408MHz from the Canadian
+Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
+}
+
+% Radio observations \dots
+% X-ray observations \dots
+% Age \ldots
+% Distance: 1.5 kpc Landecker et al 1980 (from integral paper)
+% Optical: (Mavromatakis 2003 (from integral paper)
+% EGRET observations: 3EG J2020+4027
 % LAT Pulsar detected
@@
 %      unidentified source 3EG J2020+4027, thought to be associated
-%      with SNR 78.2+2.1, a.k.a. the Gamma Cygni SNR.
+%      with SNR 78.2+2.1, a.k.a. the $\gamm$-Cygni SNR.
 %      Unfortunately, so far this pulsar lacks a radio counterpart, and
@@
 
-% Veritas observations of Gamma Cygni: 
+% Veritas observations of $\gamma$-Cygni: 
 %   http://arxiv.org/pdf/0912.4492v1
 %   extended: VER J019+407
-% 
 %     Veritas observations of $\gamm$-Cygni veritas_gamma_cygni,
-
-\begin{shaded}
-Interpreation...
-\end{shaded}
-
-\todo[inline]{Add some more information about $\gamma$ cygni.}
 
@@
 population of extended sources below our sensitivity limit (currently at
-about $\approx0.2\deg$).  Fermi has a five year nominal livetime with a
+about $\sim0\fdg2$).  \fermi has a five year nominal livetime with a
 goal of ten years of operation.  As figure~\ref{time_sensitivity} shows,
 our sensitivity to these smaller sources will improve by a factor greater
-than $\sqrt{t}$.  With increased exposure, the LAT will likely begin to
+than the square root of time.  With increased exposure, the LAT will likely begin to
 resolve these smaller \tev sources.
@@
   \begin{center}
-    \includegraphics{ic443_plots/four_plots_ic443.pdf}
+    \includegraphics{ic443_plots/four_plots_ic443.eps}
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
@@
   \begin{center}
-    \includegraphics{mc_plots/compare_disk_gauss.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
+    \includegraphics{mc_plots/compare_disk_gauss.eps}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/plot.py
     \end{center}
@@
     for a power-law source of spectral index 2. The dashed red line
-    is the brightness profile of a Gaussian with $\rsixeight=0.5\deg$.
+    is the brightness profile of a Gaussian with $\rsixeight=0\fdg5$.
     The dashed blue line is the brightness profile for a uniform disk
-    with $\rsixeight=0.5\deg$.  The solid red and blue lines show the
+    with $\rsixeight=0\fdg5$.  The solid red and blue lines show the
     convolution of the Gaussian and uniform disk brightness profiles
@@
 \colhead{Spectral Index}&
-\colhead{Flux\tablenotemark{a}}&
+\colhead{Flux\tablenotemark{(a)}}&
 \colhead{$N_\text{sims}$}&
-\colhead{$\langle\ts\rangle$}
+\colhead{$\langle\ts\rangle$}\\
+\colhead{}&
+\colhead{\phflux}&
+\colhead{}&
+\colhead{}\\
 }
@@
 
-\tablenotetext{a}{Integral 1-100 \mev flux in units of \phflux}
+\tablenotetext{(a)}{Integral 1-100 \mev flux.}
 
@@
   \begin{center}
-    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
+    \includegraphics{mc_plots/ts_ext_emin_1000.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
@@
   \begin{center}
-    \includegraphics{mc_plots/index_sensitivity.pdf}
+    \includegraphics{mc_plots/index_sensitivity.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
@@
   \begin{center}
-    \includegraphics{mc_plots/all_sensitivity.pdf}
+    \includegraphics{mc_plots/all_sensitivity.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
@@
 \begin{deluxetable}{rrrrrrrrrrrrrrrrrrrrrrr}
+\tablecolumns{22}
 \tabletypesize{\scriptsize}
@@
   \begin{center}
-    \includegraphics{mc_plots/time_sensitivity.pdf}
+    \includegraphics{mc_plots/time_sensitivity.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
@@
     \caption{
+    \hl{
     The LAT's projected detection threshold to extension after 10 years for a power-law
@@
     detection threshold assuming the sensitivity improves from the 2
-    year threshold by $\sqrt{\text{t}}$ (top edge) and linearly with
+    year threshold by the square root of time (top edge) and linearly with
     time (bottom edge).  The lower plot shows the factor increase in
     sensitivity.  For small extended sources, our detection threshold
-    improves by a factor better than $\sqrt{\text{t}}$. 
+    improves by a factor better than the square root of time. 
+    }
     }\label{time_sensitivity}
@@
   \begin{center}
-  \includegraphics{ic443_plots/res_tsmap_ic443.pdf}
+  \includegraphics{ic443_plots/res_tsmap_ic443.eps}
   % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1
@@
   \begin{center}
-    \includegraphics{source_plots/example_bad_fit.pdf}
+    \includegraphics{source_plots/example_bad_fit.eps}
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
@@
     A diffuse-emission-subtracted 1-100 \gev counts map of the region
-    around 2FGL\,J1856.2+0450c smoothed by a 0.1\deg Gaussian kernel. The
+    around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 Gaussian kernel. The
     red cross and circle are the center and size of the best fit radially
@@
 \begin{deluxetable}{lrrrrrrrr}
+\tablecolumns{9}
 \rotate
@@
 \colhead{Name}&
-\colhead{\glon\tablenotemark{a}}&
-\colhead{\glat\tablenotemark{a}}&
-\colhead{$\sigma$\tablenotemark{a}}&
+\colhead{\glon}&
+\colhead{\glat}&
+\colhead{$\sigma$}&
 \colhead{\ts}&
 \colhead{\tsext}&
-\colhead{Pos Err\tablenotemark{a}}&
-\colhead{Flux\tablenotemark{b}}&
-\colhead{Index}
+\colhead{Pos Err}&
+\colhead{Flux\tablenotemark{(a)}}&
+\colhead{Index}\\
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{}&
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{(\phflux)}&
+\colhead{}
 }
@@
 Vela X               &     263.34 &      -3.11 & $                         0.88$ &            &            &        &                       &                        \\
-Centarus A           &     309.52 &      19.42 &                     $\approx10$ &            &            &        &                       &                        \\
+Centarus A           &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
 W28                  &       6.50 &      -0.27 & $  0.43 \pm   0.02 \pm   0.03 $ &     1324.8 &      177.4 &   0.01 & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$  \\
@@
 
-\tablenotetext{a}{in degrees.}
-\tablenotetext{b}{
-integrated in the fit energy range (either 1-100 \gev or 10-100 \gev)
-in units of $10^{-9}\phflux$.
+\tablenotetext{(a)}{
+Integrated in the fit energy range (either 1-100 \gev or 10-100 \gev).
 }
@@
   \begin{center}
-    \includegraphics{source_plots/agn.pdf}
+    \includegraphics{source_plots/agn.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v2/agn.py
@@
 \begin{deluxetable}{lrrrrrrrrr}
+\tablecolumns{10}
 \tabletypesize{\small}
@@
 \colhead{Pos Err}&
-\colhead{Flux}&
+\colhead{Flux\tablenotemark{(a)}}&
 \colhead{Index}&
-\colhead{Counterpart}
+\colhead{Counterpart}\\
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{}&
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{(\phflux)}&
+\colhead{}&
+\colhead{}
 }
@@
 2FGL\,J1837.3-0700c  &      25.08 &       0.13 & $  0.35 \pm   0.08 \pm   0.03 $ &       46.2 &       18.8 &   0.07 & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
-2FGL\,J2021.5+4026   &      78.18 &       2.19 & $  0.59 \pm   0.03 \pm   0.02 $ &      222.2 &      116.4 &   0.04 & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &       $\gamma$ Cygni \\
+2FGL\,J2021.5+4026   &      78.18 &       2.19 & $  0.59 \pm   0.03 \pm   0.02 $ &      222.2 &      116.4 &   0.04 & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &       $\gamma$-Cygni \\
 \enddata
+
+\tablenotetext{(a)}{
+Integrated in the fit energy range (either 1-100 \gev or 10-100 \gev).
+}
 
@@
 \begin{deluxetable}{lrrrrrrrrrr}
+  \tablecolumns{11}
   \rotate
@@
   \colhead{$\tsext_\altdiff$}&
-  \colhead{$\sigma$\tablenotemark{a}}&
-  \colhead{$\sigma_\altdiff$\tablenotemark{a}}&
-  \colhead{$\sigma_\altpsf$\tablenotemark{a}}&
-  \colhead{$\tsinc$}
+  \colhead{$\sigma$}&
+  \colhead{$\sigma_\altdiff$}&
+  \colhead{$\sigma_\altpsf$}&
+  \colhead{$\tsinc$}\\
+  \colhead{}&
+  \colhead{}&
+  \colhead{}&
+  \colhead{}&
+  \colhead{}&
+  \colhead{}&
+  \colhead{}&
+  \colhead{(deg.)}&
+  \colhead{(deg.)}&
+  \colhead{(deg.)}&
+  \colhead{}
   }
@@
 
-\tablenotetext{a}{in degrees.}
-
 \tablecomments{
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J0823.3-4248}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v7/source_1FGL_J0823.3-4248.pdf
   \caption{A diffuse-emission-subtracted 1-100
   \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
-  by a 0.1\deg Gaussian kernel.  The red star is the catalog position
+  by a 0\fdg1 Gaussian kernel.  The red star is the 2FGL position
   of this source.  The red cross and circle are the best fit position
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1628.6-2419c}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1628.6-2419c}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v2/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v7/run.py
   \caption{
-  A diffuse-emission-subtracted 1-100 \gev counts
-  map of (a) the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
-  Gaussian kernel (b) also the emission from the background source 
-  2FGL\,J1625.7-2526 subtracted.  The red star is the catalog's
-  position of this source.  The red cross and circle are the best
-  position and extension of this source assuming a radially symmetric
-  uniform surface brightness.  The left contours correspond to the
-  100 micrometer image observed by IRAS \citep{iras_rho_ophiuci} and the right
-  contours correspond to CO emission \citep{co_rho_ophiuci}.
-  \todo[inline]{Rewrite CO contours based upon descritipon
-  of CO contours in Cygnus Loop paper
-  http://arxiv.org/pdf/1108.1833v2
+    \hl{
+  A diffuse-emission-subtracted 1-100 \gev counts map of (a) the region
+  around 2FGL\,J1627.0-2425 smoothed by a 0\fdg1 Gaussian kernel (b)
+  also the emission from the background source 2FGL\,J1625.7-2526
+  subtracted.  The red star is the 2FGL position of this source.
+  The red cross and circle are the best position and extension of this
+  source assuming a radially symmetric uniform surface brightness. The
+  contours in (a) correspond to the 100 micrometer image observed by
+  IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
+  ${}^{12}\text{CO}$ ($J=1\rightarrow 0$) emission integrated from -8 \km/\s
+  to 20 \km/\s.  They are from \cite{co_rho_ophiuci}, were cleaned using
+  the moment-masking technique \citep{masking_moment_2011}, and have
+  been smoothed by a 0\fdg25 Gaussian kernel.
     }
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_RX_J1713.7-3946}
     % this plot came from
@@
   counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
-  a 0.25\deg Gaussian kernel and (b) also the emission 
+  a 0\fdg25 Gaussian kernel and (b) also the emission 
   from the background sources subtracted.
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_Vela_Jr}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v7/run.py
   \caption{A diffuse-emission-subtracted 10-100
   \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
-  by a 0.25\deg Gaussian kernel. The red star is the catalog position of this source.  The red cross
+  by a 0\fdg25 Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
   and circle are the best fit position and extension of the source
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1613.6-5100c}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1613.6-5100c}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v7/run.py
   \caption{
@@
     \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
-    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0.1\deg
+    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0\fdg1
     Gaussian kernel.  The red stars are the catalog positions of these
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1632.9-4802c}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1632.9-4802c}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v7/run.py
   \caption{A diffuse-emission-subtracted 10-100
   \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
-  a 0.1\deg Gaussian kernel.  This source is in a crowded region.
-  The red star is the catalog position of this source.  The red
+  a 0\fdg1 Gaussian kernel.  This source is in a crowded region.
+  The red star is the 2FGL position of this source.  The red
   cross and circle are the best fit position and extension 2FGL\,J1632.4-4753c 
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1837.5-0659c}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1837.5-0659c}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v2/source_1FGL_J1837.5-0659c.pdf
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v7/run.py
   \caption{
@@
   (a)
-  the region around 2FGL\,J1837.3-0700c smoothed by a 0.1\deg Gaussian
+  the region around 2FGL\,J1837.3-0700c smoothed by a 0\fdg1 Gaussian
   kernel and (b) also the emission from the background 
   sources subtracted.  The red
-  star is the catalog position of this source. The red cross and circle
+  star is the 2FGL position of this source. The red cross and circle
   are the best fit position and extension  of 2FGL\,J1837.3-0700c 
@@
   \begin{center}
-    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Gamma_Cygni}
+    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_Gamma_Cygni}
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v2/source_Gamma_Cygni.pdf
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v7/run.py
   \caption{A Diffuse subtracted 10-100 \gev counts map of the region
-  around 2FGL\,J2021.5+4026 smoothed by a 0.1\deg Gaussian kernel. The
-  red star is the catalog position of 2FGL J2021.5+4026.  The red cross
+  around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 Gaussian kernel. The
+  red star is the 2FGL position of 2FGL J2021.5+4026.  The red cross
   and circle are the best fit position and extension 2FGL\,J2021.5+4026
@@
   \begin{center}
-    \includegraphics{summary_plots/hess_seds.pdf}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_seds.py
+    \includegraphics{summary_plots/snr_seds.eps}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_snr_seds.py
+    \end{center}
+    \caption{
+    \hl{
+    The spectral energy distribution of the extended sources 
+    Puppis A (2FGL\,J0823.0-4246) and $\gamma$-Cygni 
+    (2FGL\,J2021.5+4026) which are coincident with SNRs.
+    The red line is the best fit power-law spectral model.
+    The LAT spectral errors are statistical only.}
+    }
+    \label{snr_seds}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+  \begin{center}
+    \includegraphics{summary_plots/hess_seds.eps}
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_hess_seds.py
     \end{center}
@@
     2FGL\,J1837.3-0700c and HESS\,J1837-069. The H.E.S.S. data points
-    are from \citep{hess_plane_survey} The LAT upper limits are at the
-    95\% confidence level.  Both LAT and H.E.S.S. spectral errors are
-    systematic only.}
+    are from \citep{hess_plane_survey} Both LAT and H.E.S.S. spectral errors are
+    statistical only.}
     \label{hess_seds}
@@
   \begin{center}
-    \includegraphics{summary_plots/allsky_extended_sources.pdf}
+    \includegraphics{summary_plots/allsky_extended_sources.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v1/run.py
@@
   \begin{center}
-    \includegraphics{summary_plots/gev_vs_tev_plot.pdf}
+    \includegraphics{summary_plots/gev_vs_tev_plot.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v1/run.py
@@
   \begin{center}
-    \includegraphics{summary_plots/gev_vs_tev_histogram.pdf}
+    \includegraphics{summary_plots/gev_vs_tev_histogram.eps}
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v4/extension_histogram.py
@@
   \begin{center}
-    \includegraphics{summary_plots/compare_index_2FGL.pdf}
+    \includegraphics{summary_plots/compare_index_2FGL.eps}
     % plot taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_index_2fgl/v3/run.py

### 2011-08-21 extended_catalog/paper/extended_catalog.tex
eps
more plots

@@
 \documentclass[12pt,preprint]{aastex}
-%\documentclass[preprint]{aastex}
 
 \bibliographystyle{apj}
-\newcommand{\etal}{et al.}
-
-\usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
+
+\newif\ifcolorfigure
+%\colorfiguretrue
+\colorfigurefalse
 
@@
 
+\usepackage{color}
 \newcommand{\hl}[1]{{\color{red}#1}}
@@
 \begin{equation}
-  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r'^2 dr' d\phi'
+  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r' dr' d\phi'
 \end{equation}
@@
 \begin{align}
-  \text{PDF}(u) & = \int_0^\infty r'^2 dr'
+  \text{PDF}(u) & = \int_0^\infty r' dr'
   I_\text{src}(v) 
@@
 (\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
-The highest resolution image of the entire source was obtained
-by \rosat and contours corresponding to this
+Mosaic \rosat observations of Puppis A produced the highest
+resolution X-ray image of the source
+and contours corresponding to this
 image are overlaid on figure~\ref{1FGL_J0823.3-4248} and match the
@@
 \citep{co_eastern_puppis_a}.
-This is similar to the the LAT detected SNR the Cyngus Loop \citep{cygnus_loop_lat}.
+This is similar to the LAT detected SNR the Cyngus Loop \citep{cygnus_loop_lat}.
 The luminolsity of Puppis A is also smaller than that of 
@@
   \begin{center}
-    \includegraphics{ic443_plots/four_plots_ic443.eps}
+    \ifcolorfigure
+      \includegraphics{ic443_plots/four_plots_ic443_color.eps}
+    \else
+      \includegraphics{ic443_plots/four_plots_ic443_bw.eps}
+    \fi
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
@@
     Counts and test statistic profiles for the SNR IC443. (a) \ts
-    vs. extension of the source. (b) \tsext for individual energy bands. (c)
-    observed radial profile of counts in comparison to the expected profiles
-    for a point source (blue) and a spatially extended source (red) . (d)
-    smoothed count map after subtraction of the diffuse emission compared
-    to the LAT PSF (inset).  Plots (a), (c), and (d) use only 1-100 \gev photons. 
-    Plots (c) and (d)
-    use only photons which converted in the front
-    part of the detector and have an improved angular resolution.
+    vs. extension of the source. (b) \tsext for individual energy
+    bands. (c) observed radial profile of counts in comparison to the
+    expected profiles for a spatially extended source (solid and colored
+    red in the online version) and for a point source (dashed and colored
+    blue in the online version).  (d) smoothed count map after subtraction
+    of the diffuse emission compared to the LAT PSF (inset).  Plots (a),
+    (c), and (d) use only 1-100 \gev photons.  Plots (c) and (d) use
+    only photons which converted in the front part of the detector and
+    have an improved angular resolution.
     }
@@
   \begin{center}
-    \includegraphics{mc_plots/compare_disk_gauss.eps}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/plot.py
+    \ifcolorfigure
+      \includegraphics{mc_plots/compare_disk_gauss_color.eps}
+    \else
+      \includegraphics{mc_plots/compare_disk_gauss_bw.eps}
+    \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v3/plot.py
     \end{center}
     \caption{
-    A comparison of a Gaussian and disk like surface brightness profile
+    A comparison of a Gaussian and disk surface brightness profiles
     of extended sources before and after convolving with the PSF for two
-    energy ranges.  The black line is the PSF that would be observed
-    for a power-law source of spectral index 2. The dashed red line
-    is the brightness profile of a Gaussian with $\rsixeight=0\fdg5$.
-    The dashed blue line is the brightness profile for a uniform disk
-    with $\rsixeight=0\fdg5$.  The solid red and blue lines show the
-    convolution of the Gaussian and uniform disk brightness profiles
-    with the LAT PSF.
+    energy ranges.  The solid black line is the PSF that would be observed
+    for a power-law source of spectral index 2. The dashed line
+    and the dash-dot line are 
+    the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
+    and the convolution of this profile with the LAT PSF respectivly
+    (colored red in the online version)
+    The dash-dot-dot and the dot-dot line are the brightness profile of a uniform disk
+    with $\rsixeight=0\fdg5$ and the convolution 
+    of this profile with the LAT PSF respectivly (colored blue in the online version).
     }\label{compare_disk_gauss}
@@
 \colhead{}&
-\colhead{\phflux}&
+\colhead{(\phflux)}&
 \colhead{}&
@@
   \begin{center}
-    \includegraphics{mc_plots/ts_ext_emin_1000.eps}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
-    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
+    \ifcolorfigure
+    \includegraphics{mc_plots/ts_ext_emin_1000_color.eps}
+    \else
+    \includegraphics{mc_plots/ts_ext_emin_1000_bw.eps}
+    \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
     \end{center}
@@
     represent simulated point sources of different spectral indices and
-    the different colors represent point sources with different 100 \mev
-    to 100 \gev integral fluxes.  The dashed red line is the cumulative
+    the different lines (colored in the online version) 
+    represent point sources with different 100 \mev
+    to 100 \gev integral fluxes.  The dashed line (colored red in online version)
+    is the cumulative
     density function of equation~\ref{ts_ext_distribution}.
@@
   \begin{center}
-    \includegraphics{mc_plots/index_sensitivity.eps}
+    \ifcolorfigure
+    \includegraphics{mc_plots/index_sensitivity_color.eps}
+    \else
+    \includegraphics{mc_plots/index_sensitivity_bw.eps}
+    \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
@@
   \begin{center}
-    \includegraphics{mc_plots/all_sensitivity.eps}
+    \ifcolorfigure
+    \includegraphics{mc_plots/all_sensitivity_color.eps}
+    \else
+    \includegraphics{mc_plots/all_sensitivity_bw.eps}
+    \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
@@
     is integrated only in the selected energy range.  Overlaid on this
-    plot are the LAT detected extended sources placed by their nearby
-    Galactic diffuse emission and color coded by their spectral index.
-    The black point in plot (d) below the green line is MSH 15-52 which
-    was found by our analysis to have $\tsext=6.5$.  
+    plot are the LAT detected extended sources placed by the magnitude of
+    the nearby Galactic diffuse emission and the energy range they were
+    analyzed with.  The stars (colored red in the electronic version) are
+    sources with a spectral index closer to 1.5, the triangles (colored
+    blue) an index closer to 2, and the circles (colored green) an index
+    closer to 2.5 The circle in plot (d) below the sensitivity line is
+    MSH 15-52 which was found by our analysis to have $\tsext=6.5$.
     }\label{all_sensitivity} 
@@
   \begin{center}
-    \includegraphics{mc_plots/time_sensitivity.eps}
+    \ifcolorfigure
+      \includegraphics{mc_plots/time_sensitivity_color.eps}
+    \else
+      \includegraphics{mc_plots/time_sensitivity_bw.eps}
+    \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
@@
     source of spectral index 2 against 10 times the isotropic background
-    in the energy range from 1-100 \gev (solid red) and 10-100 \gev
-    (dashed blue). The solid gray region is the 
-    detection threshold assuming the sensitivity improves from the 2
-    year threshold by the square root of time (top edge) and linearly with
+    in the energy range from 1 \gev to 100 \gev (solid line colored red in the electronic
+    version) and 10 \gev to 100 \gev
+    (dashed line colored blue in the electronic version). The solid gray region is the 
+    detection threshold assuming the sensitivity improves from 2 to 10
+    years by the square root of time (top edge) and linearly with
     time (bottom edge).  The lower plot shows the factor increase in
     sensitivity.  For small extended sources, our detection threshold
-    improves by a factor better than the square root of time. 
+    to the extension of a source will improve by a factor better than the square root of time. 
     }
@@
   \begin{center}
-  \includegraphics{ic443_plots/res_tsmap_ic443.eps}
+  \ifcolorfigure
+    \includegraphics{ic443_plots/res_tsmap_ic443_color.eps}
+    \else
+    \includegraphics{ic443_plots/res_tsmap_ic443_bw.eps}
+    \fi
   % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1
@@
   \begin{center}
-    \includegraphics{source_plots/example_bad_fit.eps}
+    \ifcolorfigure
+    \includegraphics{source_plots/example_bad_fit_color.eps}
+    \else
+    \includegraphics{source_plots/example_bad_fit_bw.eps}
+    \fi
     % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
@@
     around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 Gaussian kernel. The
-    red cross and circle are the center and size of the best fit radially
-    symmetric source with a uniform intensity profile. The result is
-    statistically significant, but the extension encompasses many catalog
-    sources and the emission does not look to be uniform. Instead,
-    this source is probably fitting large-scale diffuse residual
-    features. Although the fit is statistically significant, it likely
-    corresponds to residual features of inaccurately modeled diffuse
-    emission picked up by the fit.  We manually discard candidates that
-    appear like this.
+    plus and circle (colored red in the online version) represent the
+    center and size of the best fit radially symmetric source with
+    a uniform intensity profile.  The black crosses represent the
+    position of background 2FGL sources.  The result is statistically
+    significant, but the extension encompasses many catalog sources and
+    the emission does not look to be uniform. Instead, this source is
+    probably fitting large-scale diffuse residual features. Although
+    the fit is statistically significant, it likely corresponds to
+    residual features of inaccurately modeled diffuse emission picked
+    up by the fit.  We manually discard candidates that appear like this.
     }
@@
   \begin{center}
-    \includegraphics{source_plots/agn.eps}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v2/agn.py
+    \ifcolorfigure
+      \includegraphics{source_plots/agn_color.eps}
+    \else
+      \includegraphics{source_plots/agn_bw.eps}
+    \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v6/agn.py
     \end{center}
     \caption{The cumulative density of \tsext for 783 of the clean
-    AGN in 2LAC which are significant above 1 \gev.  AGNs are too far
+    AGN in 2LAC which are significant above 1 \gev calculted with \pointlike (the dashed line
+    colored blue in the electronic version)
+    and with \gtlike (the solid line colored red in the electronic version).  AGNs are too far
     and too small to be resolved by the LAT. Therefore, the cumulative
     density of $\tsext$ is expected to follow a $\chi^2/2$ distribution
-    (equation~\ref{ts_ext_distribution}).     
+    (equation~\ref{ts_ext_distribution}) and is the dash-dotted line (colored
+    red in the electronic version).
     }\label{agn_ts_ext}
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J0823.3-4248}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_Puppis_A_color.eps}
+    \else
+      \includegraphics{source_plots/source_Puppis_A_bw.eps}
+    \fi
   \end{center}
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v7/source_1FGL_J0823.3-4248.pdf
-  \caption{A diffuse-emission-subtracted 1-100
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v7/run.py
+  \caption{A diffuse-emission-subtracted 1 \gev to 100
   \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
-  by a 0\fdg1 Gaussian kernel.  The red star is the 2FGL position
-  of this source.  The red cross and circle are the best fit position
+  by a 0\fdg1 Gaussian kernel.  
+  The triangle (colored red in the online version)
+  is the 2FGL position
+  of this source.  The cross and circle (colored red) are the best fit position
   and extension of this source assuming a radially symmetric uniform
-  surface brightness.  The two green stars are the positions of the
+  surface brightness.  The two stars (colored green) are the positions of the
   sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which were removed
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1628.6-2419c}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_Ophiuchus_color.eps}
+    \else
+      \includegraphics{source_plots/source_Ophiuchus_bw.eps}
+    \fi
   \end{center}
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_RX_J1713.7-3946}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_RX_J1713.7-3946_color.eps}
+    \else
+      \includegraphics{source_plots/source_RX_J1713.7-3946_bw.eps}
+    \fi
     % this plot came from
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_Vela_Jr}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_Vela_Jr_color.eps}
+    \else
+      \includegraphics{source_plots/source_Vela_Jr_bw.eps}
+    \fi
   \end{center}
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1613.6-5100c}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_HESS_J1614-518_color.eps}
+    \else
+      \includegraphics{source_plots/source_HESS_J1614-518_bw.eps}
+    \fi
   \end{center}
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1632.9-4802c}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_HESS_J1632-478_color.eps}
+    \else
+      \includegraphics{source_plots/source_HESS_J1632-478_bw.eps}
+    \fi
   \end{center}
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1837.5-0659c}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_HESS_J1837-069_color.eps}
+    \else
+      \includegraphics{source_plots/source_HESS_J1837-069_bw.eps}
+    \fi
   \end{center}
@@
   \begin{center}
-    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_Gamma_Cygni}
+    \ifcolorfigure
+      \includegraphics{source_plots/source_Gamma_Cygni_color.eps}
+    \else
+      \includegraphics{source_plots/source_Gamma_Cygni_bw.eps}
+    \fi
   \end{center}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v7/run.py
-  \caption{A Diffuse subtracted 10-100 \gev counts map of the region
+  \caption{A Diffuse subtracted 10 \gev to 100 \gev counts map of the region
   around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 Gaussian kernel. The
-  red star is the 2FGL position of 2FGL J2021.5+4026.  The red cross
-  and circle are the best fit position and extension 2FGL\,J2021.5+4026
-  assuming a radially symmetric uniform surface brightness.  The green
-  cross inside the extension is 2FGL\,J2019.1+4040 which was removed
-  because it is part of the extended source.  The farther away green
-  stars represent other catalog sources which were removed because
-  they were not significant above 10 \gev.  The gray cross is the
+  triangle (colored red in the online version)
+  represents the 2FGL position of 2FGL J2021.5+4026.  The plus
+  and circle (colored red) 
+  represent the best fit position and extension 2FGL\,J2021.5+4026
+  assuming a radially symmetric uniform surface brightness.  The 
+  star (clored green) 
+  inside the extension represents the position of 
+  2FGL\,J2019.1+4040 which was removed
+  because it is part of the extended source.  The diamont
+  (colored purple) is the
   position a source not in the two year catalog which was added to the
   region. 2FGL\,J2021.5+4026 is spatially coincident with the $\gamma$
-  Cygni SNR.  The light blue contours correspond to the 408MHz image of
+  Cygni SNR.  The contours (colored light blue)
+  correspond to the 408MHz image of
   $\gamma$ Cygni observed by the Canadian Galactic Plane Survey.
@@
   \begin{center}
-    \includegraphics{summary_plots/snr_seds.eps}
+    \ifcolorfigure
+      \includegraphics{summary_plots/snr_seds_color.eps}
+    \else
+      \includegraphics{summary_plots/snr_seds_bw.eps}
+    \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_snr_seds.py
@@
     Puppis A (2FGL\,J0823.0-4246) and $\gamma$-Cygni 
-    (2FGL\,J2021.5+4026) which are coincident with SNRs.
-    The red line is the best fit power-law spectral model.
+    (2FGL\,J2021.5+4026).
+    The lines (colored red in the online version)
+    are the best fit power-law spectral model of
+    these sources.
     The LAT spectral errors are statistical only.}
@@
   \begin{center}
-    \includegraphics{summary_plots/hess_seds.eps}
+    \ifcolorfigure
+      \includegraphics{summary_plots/hess_seds_color.eps}
+    \else
+      \includegraphics{summary_plots/hess_seds_bw.eps}
+    \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_hess_seds.py
@@
     The spectral energy distribution of four the extended sources
-    associated with extended \tev sources.  The black points with circular
-    markers are the LAT data points. The red points with dashed markers
-    are H.E.S.S points of associated sources.  Plot (a) shows the \gev
-    SED of 2FGL\,J1615.0-5051 together with the \tev SED of HESS\,J1616-508.
+    associated with extended \tev sources.  The black points with
+    circular markers are the LAT data points. The points with dashed
+    markers (colored red in the electronic version) are the H.E.S.S
+    points of the associated sources.  Plot (a) shows the \gev SED of
+    2FGL\,J1615.0-5051 together with the \tev SED of HESS\,J1616-508.
     Plot (b) shows 2FGL\,J1615.2-5138 and HESS\,J1614-518 Plot (c)
@@
     2FGL\,J1837.3-0700c and HESS\,J1837-069. The H.E.S.S. data points
-    are from \citep{hess_plane_survey} Both LAT and H.E.S.S. spectral errors are
-    statistical only.}
+    are from \citep{hess_plane_survey} Both LAT and H.E.S.S. spectral
+    errors are statistical only.}
     \label{hess_seds}
@@
 
-\clearpage
 {\rotate
 \begin{figure}
-  \begin{center}
-    \includegraphics{summary_plots/allsky_extended_sources.eps}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v1/run.py
-    \end{center}
+  %\begin{center}
+    \ifcolorfigure
+    \includegraphics{summary_plots/allsky_extended_sources_color.eps}
+    \else
+    \includegraphics{summary_plots/allsky_extended_sources_bw.eps}
+    \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v2/run.py
+    %\end{center}
     \caption{A plot of all \gev extended sources detected by the LAT
     with two years of data.  The twelve extended sources included in
-    2FGL are the red markers and the nine additional
-    extended sources analyzed in this paper are the orange markers. 
+    2FGL are indicated by the circular markers (colored 
+    red in the online version).
+    The nine 
+    new
+    extended sources analyzed in this paper are the triangular
+    markers (colored orange in the online version). 
     }\label{allsky_extended_sources}
@@
   \begin{center}
-    \includegraphics{summary_plots/gev_vs_tev_plot.eps}
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v1/run.py
+    \ifcolorfigure
+      \includegraphics{summary_plots/gev_vs_tev_plot_color.eps}
+    \else
+      \includegraphics{summary_plots/gev_vs_tev_plot_bw.eps}
+      \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v3/run.py
     \end{center}
@@
   \begin{center}
-    \includegraphics{summary_plots/gev_vs_tev_histogram.eps}
+    \ifcolorfigure
+      \includegraphics{summary_plots/gev_vs_tev_histogram_color.eps}
+    \else
+      \includegraphics{summary_plots/gev_vs_tev_histogram_bw.eps}
+    \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v4/extension_histogram.py
@@
     \caption{
-    A comparison of the size of detected LAT and H.E.S.S sources.
-    The extension of the 22 extended LAT sources comes from
+    The distribution of the \gev size of the 22 extended LAT 
+    sources (colored blue in the electronic version) and
+    the \tev size of the 42 extended H.E.S.S. sources
+    (colored red in the electronic version).
+    The extension of the LAT sources comes from
     table~\ref{known_extended_sources}, table~\ref{new_ext_srcs_table},
-    and the LAT extension of Vela X is taken from \citep{velax}. The
+    and from \cite{velax}. 
     The \tev extension of
@@
     Gaussian surface brightness model, the \gev and
-    \tev extensions are assuming a uniform surface brightness.
+    \tev extensions are included assuming a uniform surface brightness.
     }\label{gev_vs_tev_histogram}
@@
   \begin{center}
-    \includegraphics{summary_plots/compare_index_2FGL.eps}
+    \ifcolorfigure
+      \includegraphics{summary_plots/compare_index_2FGL_color.eps}
+    \else
+      \includegraphics{summary_plots/compare_index_2FGL_bw.eps}
+    \fi
     % plot taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_index_2fgl/v3/run.py
@@
     \caption{
-    The distribution of spectral indices of all 1873 2FGL sources in
-    red and all spatially extended sources in blue. The
+    The distribution of spectral indices of all 1873 2FGL sources 
+    (colored red in the electronic version)
+    and the spatially extended sources (colored blue in the electronic
+    version). The
     spectral indices of LAT extended sources are taken from

### 2011-08-22 extended_catalog/paper/extended_catalog.tex
more plots

@@
 \begin{abstract}
-We present a new method for analyzing 
+We present a new method for quantifying
 the spatial extension of sources with
@@
 Spatial extension
-is an important input to correctly 
-associate LAT sources with their counterparts at other
+is an important characteristic for correctly 
+associating LAT sources with their counterparts at other
 wavelengths. We perform
 a series of Monte Carlo studies to validate this tool and calculate
-the LAT's detection threshold to detect the extension of 
-spatially extended sources.  We then
-apply this tool to test all sources in the two year source catalog for
+the LAT's threshold for detecting the spatial extension of sources.  We then
+use this tool to test all sources in the two year source catalog for
 extension. We report the detection of nine spatially extended sources
@@
 The Large Area Telescope (LAT) is a pair conversion telescope on the {\em \fermi
-Gamma-Ray Space Telescope} (\fermi) that been surveying the $\gamma$-ray
-sky since 2008 June.  The LAT has a broad energy coverage (20 \mev to $>300$
+Gamma-ray Space Telescope} (\fermi) that been surveying the $\gamma$-ray
+sky since 2008 June.  The LAT has broad energy coverage (20 \mev to $>300$
 \gev), wide field of view ($\sim 2.4 \sr$), and large effective area
@@
 Using two years of all-sky surveying data, the LAT Collaboration published
-a catalog of 1873 \gev sources \citep{second_cat}. Many of these can be
+a catalog of 1873 \gev sources \citep{second_cat}. Many of these have been
 positionally associated with a variety of source classes including Active

### 2011-08-22 extended_catalog/paper/extended_catalog.tex
better plots

@@
 ISM: supernova remnants;
-Methods: statistical
+Methods: statistical;
 pulsar wind nebula
@@
 \author{
-J.~Lande\altaffilmark{3}, 
-\altaffiltext{3}{W.
+J.~Lande\altaffilmark{2},
+S.~Funk\altaffilmark{2},
+M.~Ackermann (???),
+A.~Allafort\altaffilmark{2},
+K.~Bechtol\altaffilmark{2},
+M.-H.~Grondin\altaffilmark{53},
+\ldots
+\altaffiltext{2}{W.
 W.
 Hansen Experimental Physics Laboratory, Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics and SLAC National Accelerator Laboratory, Stanford University, Stanford, CA 94305, USA}
+\altaffiltext{53}{Institut f\"ur Astronomie und Astrophysik, Universit\"at T\"ubingen, D 72076 T\"ubingen, Germany}
 }
@@
 \gev), wide field of view ($\sim 2.4 \sr$), and large effective area
-($\sim 8000 \cm^2$ at $>1 \gev$).
+($\sim 8000\ \cm^2$ at $>1 \gev$).
 
 Using two years of all-sky surveying data, the LAT Collaboration published
-a catalog of 1873 \gev sources \citep{second_cat}. Many of these have been
-positionally associated with a variety of source classes including Active
-Galactic Nuclei (AGN), pulsars, galaxies, and supernova remnants (SNRs).
-While the counterparts of many LAT sources
-can be spatially resolved when observed
-at other frequencies, detection of an extension at \gev energies by
-the LAT is complicated by the large point-spread function (PSF)
-of the instrument. The angular resolution for events converting in the
-thin conversion foils of the tracker system, defined as the 68\% containment radius for
-a point source, is approximately $3.5^{\circ}$ at 100 \mev, improving
-to about 0.1$^{\circ}$ at 10 \gev.
+a catalog of 1873 \gev sources \citep{second_cat}. Many of these have
+been positionally associated with a variety of source classes including
+Active Galactic Nuclei (AGN), pulsars, normal galaxies, and supernova
+remnants (SNRs).  While the counterparts of many LAT sources can be
+spatially resolved when observed at other frequencies, detection of
+spatial extension of these sources at \gev energies is difficult because
+the size of the point-spread function (PSF) of the LAT is comparable
+to the typical size of many of these sources.
 
@@
 molecular clouds, normal galaxies, galaxy clusters or dark matter
-satellites can therefore be expected to be detected as spatially extended
+satellites could be expected to be detected as spatially extended
 sources by the LAT.  
-The LAT collaboration has previously reported five SNRs which are
+The LAT Collaboration has previously reported on five SNRs which are
 spatially extended beyond the LAT PSF at \gev energies 
@@
 and HESS\,J1825-137 \citep{msh1552,velax,fermi_hess_j1825}, as well
-as two close-by galaxies, the Large Magellanic and Small Magalenic
+as two close-by galaxies, the Large and Small Magalenic
 Cloud \citep{lmc,smc}, and finally the radio galaxy Centarus A
 \citep{cen_a_lat}.
-
-For each of these sources, the extension was determined based on
-dedicated analysis of the particular source 
-instead of being the outcome of a systematic search of the LAT catalog.
-For the systematic scan of all LAT catalog sources presented in this work, we
-therefore expect to find additional spatially extended LAT sources, in
-particular since many extended sources in the Galactic plane have been
-detected at \tev energies using air Cherenkov detectors and \tev and
-\gev emission often originates from the same population of high-energy
-particles.  A variety of spatially extended sources have been detected
-in the Galactic plane at \tev energies. Most prominent was a survey of
+For each of these sources, the extension was determined from a dedicated
+analysis of the particular source and so a systematic
+scan of all LAT detected sources could uncover
+additonal spatially extended sources.
+
+\hl{
+Many extended sources in the Galactic plane have been detected at \tev
+energies using air Cherenkov detectors.  Most prominent was a survey of
 the Galactic plane using the High Energy Stereoscopic System (H.E.S.S)
-which reported 14 spatially extended sources
- with extensions varying from
-$\sim0\fdg1$ to $\sim0\fdg25$ \citep{hess_plane_survey}.
-In fact, within
+which reported 14 spatially extended sources with extensions varying from
+$\sim0\fdg1$ to $\sim0\fdg25$ \citep{hess_plane_survey}.  In fact, within
 our Galaxy only very few sources (most notably the $\gamma$-ray binaries
 LS\,5039 \citep{HESSLS5039}, LS I+61-303 \citep{MAGICLSI, VERITASLSI}
-HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes}
-have 
-no significant extension detected at \tev energies. Given
-these findings, it can be expected that if the source population at \gev
-energies has similar properties, that at least some of the \fermi-LAT
-sources in our Galaxy should be spatially resolvable at \gev energies.
-
-\hl{
-High energy $\gamma$-rays are produced by the decay of $\pi^0$s produced
-by hadronic interactions with interstellar matter and by relativistic
-electrons due to Inverse Compton (IC) scattering and Bremsstrahlung
-radiation.  Many of these spatially extended \tev sources in the
-Galactic plane are unidentified. Some of these sources could produce
-hadronic cosmic rays up to $\sim 10^{15}$ eV and subsequently radiate
-$\gamma$-rays through $\pi^0$ decay \citep{blandford_and_eichler_1987}.
-Studying the spectra of these \tev sources at \gev energies may help to
-determine the emission mechanisms of these high energy sources.
-}
-
-The capability to
-spatially resolve GeV $\gamma$-ray sources is
-important for several reasons. 
-First, multiple potential counterparts detected at other frequencies
-exist within the localization confidence region of a typical LAT source
-along the Galactic plane.
-Finding a coherent
-source extension across different energy bands allows a firm association
-of a LAT source to an otherwise confused counterpart.  Also, due
-to the strong energy dependence of the LAT PSF,
-the spatial and spectral information
-about a source do not simply decouple. An inaccurate spatial model will bias
-the spectral model of the source. Specifically, performing a spectral
-analysis on a spatially extended source modeled as point-like will
-systematically shift the spectral index to be softer.  Furthermore,
+HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
+have no significant extension detected at \tev energies.  High energy
+$\gamma$-rays from these sources are produced by the decay of $\pi^0$s
+produced by hadronic interactions with interstellar matter and by
+relativistic electrons due to Inverse Compton (IC) scattering and
+Bremsstrahlung radiation \citep{blandford_and_eichler_1987}.  It is likely
+that the \gev and \tev emission from these sources originates from the
+same population of high-energy particles and so at least some of these
+sources should be detected as extended sources at \gev energies. By
+studying the spectra of these \tev sources at \gev energies, we may help
+to determine the emission mechanisms of these high energy sources.
+}
+
+The capability to spatially resolve \gev $\gamma$-ray sources is important
+for several reasons.  First, multiple potential counterparts detected at
+other frequencies exist within the localization confidence region of a
+typical LAT source along the Galactic plane.  Finding a coherent source
+extension across different energy bands can help to associate a
+LAT source to an otherwise confused counterpart.  Also, due to the strong
+energy dependence of the LAT PSF, the spatial and spectral information
+about a source do not simply decouple. An inaccurate spatial model
+will bias the spectral model of the source. Specifically, 
+modeling a spatially extended source as point-like will systematically
+shift a spectral analysis to softer indices. Furthermore,
 correctly modeling a source's extension is important for improving
 the model of the sky and removing excess residuals, for example in the
-region around surrounding the Large Magellanic Cloud \citep{first_cat}.
-Additionally, such excess residuals potentially bias the significance
+region around surrounding the Large Magellanic Clouds \citep{first_cat}.
+Such excess residuals potentially bias the significance
 and measured spectrum of neighboring sources in the densely populated
@@
 
-Morphological studies of sources in the \gev energy range using the
-LAT are challenging because of the strongly energy-dependent PSF.
-Additional complications arise for sources along the Galactic plane due to
-systematic uncertainties in the Galactic diffuse emission.  The LAT's
-PSF is limited at its lowest detectable energies by multiple scattering in the tracker
-and the 68\% containment radius of the PSF is approximately $5\fdg1$
-at 100 \mev  when averaged over instrument acceptance and including
-photons which convert in either the thick or thin layers of the
-tracker. The PSF improves with energy and approaches a limit given
-by the granularity of the silicon strips and is $0\fdg14$ at 10 \gev
-\citep{on_orbit_calibration}.  However, since most high energy
-astrophysical sources have power-law spectra, the better resolution of the higher
-energy photons is offset by their low
-statistics. Therefore a detailed investigation has been performed in this
-work to determine the optimal energy range to measure source extension
-(section \ref{extended_source_search_method}).
+Morphological studies of sources using the LAT are challenging
+because of the strongly energy-dependent PSF that is comparable in
+size to the extension of many sources expected to be detected at
+\gev energies.  Additional complications arise for sources along
+the Galactic plane due to systematic uncertainties in the Galactic
+diffuse emission.  The LAT's PSF is limited at its lowest detectable
+energies by multiple scattering in the silicon strip tracking section
+of the detector and is several degrees at 100 \mev.  The PSF improves
+with energy approaching a 68\% containment radius of $\sim0\fdg2$ at
+the highest energies (when averaged over the acceptance of the LAT)
+and is limited by the granularity of the silicon strips in the tracker
+\citep{atwood_LAT_mission,on_orbit_calibration,lat_on_orbit_psf}.\footnote{More
+information about the performance of the LAT can be found at the Fermi
+Science Support Center (FSSC,\url{http://fermi.gsfc.nasa.gov}).} However,
+since most high energy astrophysical sources have spectra that decrease
+rapidly with increasing energy, the improved resolution of the higher
+energy photons is offset by their low statistics. Therefore sophisticated
+analysis techniques are required to maximize our sensitivity
+to these extended sources.
 
@@
 A new analysis tool has been developed to address the unique requirements
-for studying spatially extended sources with the LAT. The tool
-performs a maximum likelihood analysis in which the Poisson likelihood
-for observing the measured counts is maximized,
-given a parametrized spatial and spectral model of 
-the source and its surrounding region.
-The extension of a source can be modeled by a
-geometric shape (e.g. a disk or Gaussian) and the source's position,
-extension, and spectrum can be simultaneously fit.
-
-This analysis is not feasible using the standard LAT likelihood
+for studying spatially extended sources with the LAT. The tool performs
+a maximum likelihood analysis in which the Poisson likelihood for
+observing the measured counts is maximized, given a parametrized
+spatial and spectral model of the source and its surrounding region.
+The extension of a source can be modeled by a geometric shape (e.g. a
+disk or Gaussian) and the source's position, extension, and spectrum
+can be simultaneously fit.
+
+This type of analysis is not feasible using the standard LAT likelihood
 analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
-Fermi Science Support Center \citep{fssc}} because \gtlike can only 
+FSSC.} because \gtlike can only
 fit the spectral parameters of the model unless a more sophisticated
@@
 We note that \gtlike has been used in the past in several studies of
-source extension in the LAT collaboration \citep{lmc,smc,w28,w51c}.
+source extension in the LAT Collaboration \citep{lmc,smc,w28,w51c}.
 Based upon a set of \gtlike maximum likelihood fits at fixed extensions,
@@
 The approach presented here is based on a second maximum likelihood
-fitting package developed in the LAT collaboration called \pointlike
+fitting package developed in the LAT Collaboration called \pointlike
 \citep{first_cat,matthew_kerr_thesis}.  We extended the code to allow
@@
 
-The choice to base the spatial extension fitting on \pointlike
-rather than \gtlike was made on considerations of computing time.
-The \pointlike algorithm was optimized for speed to handle
-larger numbers of sources efficiently which is important for
-our catalog scan as well as the Monte Carlo validation of our method.
-Details on the \pointlike package can be found in \cite{matthew_kerr_thesis}.
+The choice to base the spatial extension fitting on \pointlike rather than
+\gtlike was made on considerations of computing time.  The \pointlike
+algorithm was optimized for speed to handle larger numbers of sources
+efficiently which is important for our catalog scan as well as the Monte
+Carlo validation of our method.  Details on the \pointlike package can
+be found in \cite{matthew_kerr_thesis}.
 
@@
 the source \citep{minuit_documentation}.  As will be described in
-section~\ref{monte_carlo_validation}, simultaneously fitting the position
+Section~\ref{monte_carlo_validation}, simultaneously fitting the position
 and extension is important to correctly calculate the statistical
@@
 of \tsext in terms of a statistical significance is discussed in
-section~\ref{monte_carlo_validation}.
+Section~\ref{monte_carlo_validation}.
 
@@
 by \onehalf, corresponding to a $1\sigma$ error.  This method is
-shown schematically in figure~\ref{four_plots_ic443}(a) which shows the
+shown schematically in Figure~\ref{four_plots_ic443}(a) which shows the
 change in \loglikelihood when varying the extension of the SNR IC443.
@@
 extended if $\tsext>\tsinc$.
-Similar to the case of extended sources described in section~\ref{gtlike_crosscheck},
+Similar to the case of extended sources described in Section~\ref{gtlike_crosscheck},
 the spectrum of the two point sources can be refit using \gtlike.
@@
 and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
-is defined in equation~\ref{gauss_pdf} and
-equation~\ref{disk_pdf} respectively.} This plot shows that the LAT is 
+is defined in Equation~\ref{gauss_pdf} and
+Equation~\ref{disk_pdf} respectively.} This plot shows that the LAT is 
 not very sensitive to probing the exact structure of an extended source.
@@
 \end{equation}
-The particular form of equation \ref{ts_ext_distribution} is
+The particular form of Equation \ref{ts_ext_distribution} is
 due to the null hypothesis (source flux $\Phi=0$) residing
@@
 study to calculate empirical distributions for $\tsext$ and
-compared them to equation~\ref{ts_ext_distribution}.
+compared them to Equation~\ref{ts_ext_distribution}.
 
 We simulated point sources with various spectral forms using
-\gtobssim\footnote{\gtobssim is distributed by the Fermi Science Support
-Center \citep{fssc}.} and fit them with \pointlike using both point
+\gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit them with \pointlike using both point
 and extended source hypotheses.  The point sources were simulated with a power-law
@@
 number of simulations.  The cumulative density of \tsext is plotted in
-figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution of
-equation~\ref{ts_ext_distribution} is overlaid for comparison.
+Figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution of
+Equation~\ref{ts_ext_distribution} is overlaid for comparison.
 
 Our Monte Carlo study shows broad agreement between simulations and
-equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is not
+Equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is not
 perfect.  It should be noted that the discrepancy seems to be worst for
@@
 becoming more apparent for sufficiently bright sources.  Other possible
-reasons for departure from equation~\ref{ts_ext_distribution} could
+reasons for departure from Equation~\ref{ts_ext_distribution} could
 be that \pointlike ignores energy dispersion which would change the
@@
 We used the simulation setup described in
-section~\ref{monte_carlo_validation}, but instead simulated extended
+Section~\ref{monte_carlo_validation}, but instead simulated extended
 sources with a radially symmetric uniform surface
@@
 not substantially improved including photons with energies between 100 \mev and
-1 \gev.  This is also demonstrated in figure~\ref{four_plots_ic443}(b)
+1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}(b)
 which shows \tsext for the SNR IC443 computed independently in twelve
@@
 pronounced when using only photons with energies above 10 \gev.  Overlaid
-on figure~\ref{all_sensitivity} are the LAT detected extended sources
-that will be discussed in sections~\ref{validate_known}
+on Figure~\ref{all_sensitivity} are the LAT detected extended sources
+that will be discussed in Sections~\ref{validate_known}
 and \ref{new_ext_srcs_section}.  The extension thresholds are tabulated
-in table~\ref{all_sensitivity_table}.
-
-Finally, figure~\ref{time_sensitivity} shows the LAT's projected detection
+in Table~\ref{all_sensitivity_table}.
+
+Finally, Figure~\ref{time_sensitivity} shows the LAT's projected detection
 threshold to extension after 10 years against 10 times the isotropic
@@
 
-As was shown in section~\ref{extension_sensitivity}, we gain little in sensitivity using photons with energies
+As was shown in Section~\ref{extension_sensitivity}, we gain little in sensitivity using photons with energies
 below 1 \gev. On the other hand, the large PSF at low energy makes us
@@
 extended (i.e. $\tsext>16$), we perform the dual localization procedure
-(described in section~\ref{dual_localization_method} to compare the
+(described in Section~\ref{dual_localization_method} to compare the
 extended source hypothesis to the hypothesis of two independent point
@@
 An example radial integral plot is shown for the extended source IC443
-in figure~\ref{four_plots_ic443}(c).  For each source, we also made
+in Figure~\ref{four_plots_ic443}(c).  For each source, we also made
 diffuse-emission-subtracted smoothed counts
@@
 and hence the extension measurement unreliable.  An example of such a
-case is shown in figure~\ref{example_bad_fit}. It shows a Galactic and
+case is shown in Figure~\ref{example_bad_fit}. It shows a Galactic and
 isotropic diffuse-emission-subtracted smoothed counts map of this source
@@
 detailed publication by the LAT
-collaboration about W30 is still in preparation.
+Collaboration about W30 is still in preparation.
 \gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
@@
 fit extension is comparable to the published result, but we note that
-previous LAT collaboration publication on LMC used a more complicated two Gaussian surface
+previous LAT Collaboration publication on LMC used a more complicated two Gaussian surface
 brightness spatial model when fitting it (\citep{lmc}).
@@
 Our analysis of these sources is summarized in
-table~\ref{known_extended_sources}.  This table includes the best fit
+Table~\ref{known_extended_sources}.  This table includes the best fit
 position and extension of these sources when fitting them as disk-shaped
@@
 
-Following 1FGL, the LAT collaboration published a list 
+Following 1FGL, the LAT Collaboration published a list 
 of sources that
@@
 latitude ($|b|>10\deg$).  
-Using two years of data and 2FGL, the LAT collaboration
+Using two years of data and 2FGL, the LAT Collaboration
 associated 1016 2FGL sources
@@
 A histogram of the \tsext values computed for these AGN is
-shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is the
-$\chi^2/2$ distribution of equation~\ref{ts_ext_distribution}.
+shown in Figure~\ref{agn_ts_ext}. Overlaid on the plot is the
+$\chi^2/2$ distribution of Equation~\ref{ts_ext_distribution}.
 The \tsext distribution for AGN shows good agreement with the
@@
 to incorrectly automatically removing a nearby catalog sources (see
-section~\ref{extended_source_search_method}) and the other was due to a
+Section~\ref{extended_source_search_method}) and the other was due to a
 failure of convergence of the point hypothesis.  This result demonstrates
@@
 empirically by fitting the observed shape of bright AGN (see
-section~\ref{systematic_errors_on_extension}). Finding that the AGN we
+Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
 test are not extended is not surprising.  This validation analysis is
@@
 found in our search using 10-100 \gev photons.  The fit properties of
-these nine sources is summarized in table~\ref{new_ext_srcs_table}.
+these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
 This table includes for each source the best fit position, extension,
@@
 measurement are presented in 
-table~\ref{alt_diff_model_results}.  It
+Table~\ref{alt_diff_model_results}.  It
 shows a comparison between the fit with a single extended source
@@
 results of the extension fit using variations of the PSF and the galactic
-diffuse model described in section~\ref{systematic_errors_on_extension}.
+diffuse model described in Section~\ref{systematic_errors_on_extension}.
 There is good agreement between \tsext and the fit size using
@@
 counts map of this source
-and figure~\ref{snr_seds}(a) shows the LAT spectrum of it.
+and Figure~\ref{snr_seds}(a) shows the LAT spectrum of it.
 }
@@
 we conclude that this is an extended source.  These modifications are
-shown in figure~\ref{1FGL_J0823.3-4248}.
+shown in Figure~\ref{1FGL_J0823.3-4248}.
 
@@
 and contours corresponding to this
-image are overlaid on figure~\ref{1FGL_J0823.3-4248} and match the
+image are overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the
 inferred \gev size \citep{rosat_puppis_a}.
@@
 year catalog source 1FGL\,J1628.6-2419c.  A counts map showing this source
-is seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
+is seen in Figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
 we also fit the source instead as two point sources. Since $\tsinc=20.0$
@@
 ${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
-contours are overlaid on figure~\ref{1FGL_J1628.6-2419c}. There is good
+contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c}. There is good
 spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}
@@
 2FGL\,J0851.7-4635 is spatially coincident with the SNR Vela Jr.
-Overlaid on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
+Overlaid on Figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
 \tev by H.E.S.S \citep{vela_jr_hess}.  The \gev and \tev morphology
-match well.  A detailed papers by the LAT collaboration on Vela Jr. is
+match well.  A detailed papers by the LAT Collaboration on Vela Jr. is
 in preparation.
@@
 This source is less than $1\deg$ away from 2FGL\,J1615.2-5138 which is
-also spatially extended (see section~\ref{section_2FGL_J1615.2-5138}).
+also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
 To get a good fit of both sources, we had to model both sources as
@@
 significant above 10 \gev.  These modifications are further described
-in the caption to figure~\ref{1FGL_J1613.6-5100c}.  After modifying
+in the caption to Figure~\ref{1FGL_J1613.6-5100c}.  After modifying
 the region, we found that \tsinc=11.9 which is less than \tsext so we
@@
 \tev source HESS\,J1616-508 \citep{hess_plane_survey}.  In
-figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
+Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
 on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured an
@@
 radius of $\rsixeight=0\fdg21\pm0\fdg01$. This size is comparable to the LAT
-size $\rsixeight=0\fdg27\pm0\fdg03$ (see section~\ref{compare_source_size}).
+size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
 Figure~\ref{hess_seds}(a) shows that the LAT spectrum of 2FGL\,J1615.0-5051
@@
 J1615.2-5138 is close to 2FGL\,J1615.0-5051, the same model described
-in section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
-sources. Both sources can be seen in figure~\ref{1FGL_J1613.6-5100c}.
+in Section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
+sources. Both sources can be seen in Figure~\ref{1FGL_J1613.6-5100c}.
 For 2FGL\,J1615.2-5138, \tsinc=37.0 which is less than \tsext so we
@@
 \tev source HESS\,J1614-518 \citep{hess_plane_survey}. In
-figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
+Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
 on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian
@@
 were not significant above 10 \gev.  These modifications are shown
-in figure~\ref{1FGL_J1632.9-4802c}.  To test for source confusion,
+in Figure~\ref{1FGL_J1632.9-4802c}.  To test for source confusion,
 we compared the likelihood fitting this region as one extended source
@@
 \tev source HESS\,J1632-478 \citep{hess_plane_survey}.
-In figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478
+In Figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478
 are overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a 
@@
 because it was not significant above 10 \gev. These modifications are
-shown in figure~\ref{1FGL_J1837.5-0659c}.  After modifying the region,
+shown in Figure~\ref{1FGL_J1837.5-0659c}.  After modifying the region,
 we found that \tsinc=12.6 which is less than \tsext, so we conclude that
@@
 This source is spatially coincident with the \tev source HESS\,J1837-069
-\citep{hess_plane_survey}.  In figure~\ref{1FGL_J1837.5-0659c}, contours
+\citep{hess_plane_survey}.  In Figure~\ref{1FGL_J1837.5-0659c}, contours
 of HESS\,J1837-069 are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured
@@
 Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source.
-and figure~\ref{snr_seds}(b) shows that the LAT spectrum of it.
+and Figure~\ref{snr_seds}(b) shows that the LAT spectrum of it.
 }
@@
 extended.  These modifications are further described in the caption to
-figure~\ref{1FGL_J2020.0+4049}.
+Figure~\ref{1FGL_J2020.0+4049}.
 
@@
 extended source whose inferred \gev size well matches the radio size of
-$\gamma$-Cygni, as can be seen in figure~\ref{1FGL_J2020.0+4049}
+$\gamma$-Cygni, as can be seen in Figure~\ref{1FGL_J2020.0+4049}
 which overlays contours of $\gamma$-Cygni at 408MHz from the Canadian
@@
 The position of the 21 extended LAT sources are close to the Galactic
-plane and plotted in figure~\ref{allsky_extended_sources}.  Most of the
+plane and plotted in Figure~\ref{allsky_extended_sources}.  Most of the
 extended sources are indeed expected to be of Galactic origin as the
@@
 of LAT detected extended sources and of all sources in 2FGL. This, and
-table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
+Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
 show that the LAT observes a population of hard (index $<2$)
@@
 For the LAT extended sources also seen in \tev,
-figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
+Figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
 a good correlation between the \gev and \tev sizes of the sources. Even
@@
 about $\sim0\fdg2$).  \fermi has a five year nominal livetime with a
-goal of ten years of operation.  As figure~\ref{time_sensitivity} shows,
+goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
 our sensitivity to these smaller sources will improve by a factor greater
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{ic443_plots/four_plots_ic443_color.eps}
+    \plotone{ic443_plots/four_plots_ic443_color.eps}
     \else
-      \includegraphics{ic443_plots/four_plots_ic443_bw.eps}
+    \plotone{ic443_plots/four_plots_ic443_bw.eps}
     \fi
@@
     (c), and (d) use only 1-100 \gev photons.  Plots (c) and (d) use
-    only photons which converted in the front part of the detector and
+    only photons which converted in the front part of the tracker and
     have an improved angular resolution.
@@
     \label{four_plots_ic443}
-  \end{center}
 \end{figure}
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{mc_plots/compare_disk_gauss_color.eps}
+      \plotone{mc_plots/compare_disk_gauss_color.eps}
     \else
-      \includegraphics{mc_plots/compare_disk_gauss_bw.eps}
+      \plotone{mc_plots/compare_disk_gauss_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v3/plot.py
-    \end{center}
     \caption{
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-    \includegraphics{mc_plots/ts_ext_emin_1000_color.eps}
+    \plotone{mc_plots/ts_ext_emin_1000_color.eps}
     \else
-    \includegraphics{mc_plots/ts_ext_emin_1000_bw.eps}
+    \plotone{mc_plots/ts_ext_emin_1000_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
-    \end{center}
     \caption{
@@
     is the cumulative
-    density function of equation~\ref{ts_ext_distribution}.
+    density function of Equation~\ref{ts_ext_distribution}.
     }\label{ts_ext_mc}
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-    \includegraphics{mc_plots/index_sensitivity_color.eps}
+    \plotone{mc_plots/index_sensitivity_color.eps}
     \else
-    \includegraphics{mc_plots/index_sensitivity_bw.eps}
+    \plotone{mc_plots/index_sensitivity_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
-    \end{center}
     \caption{
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-    \includegraphics{mc_plots/all_sensitivity_color.eps}
+    \plotone{mc_plots/all_sensitivity_color.eps}
     \else
-    \includegraphics{mc_plots/all_sensitivity_bw.eps}
+    \plotone{mc_plots/all_sensitivity_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
-    \end{center}
     \caption{the LAT detection threshold for four spectral indices and
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{mc_plots/time_sensitivity_color.eps}
+      \plotone{mc_plots/time_sensitivity_color.eps}
     \else
-      \includegraphics{mc_plots/time_sensitivity_bw.eps}
+      \plotone{mc_plots/time_sensitivity_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
-    \end{center}
     \caption{
@@
 \begin{figure}
-  \begin{center}
   \ifcolorfigure
-    \includegraphics{ic443_plots/res_tsmap_ic443_color.eps}
+    \plotone{ic443_plots/res_tsmap_ic443_color.eps}
     \else
-    \includegraphics{ic443_plots/res_tsmap_ic443_bw.eps}
+    \plotone{ic443_plots/res_tsmap_ic443_bw.eps}
     \fi
@@
   \label{res_tsmaps}
-  \end{center}
 \end{figure}
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-    \includegraphics{source_plots/example_bad_fit_color.eps}
+    \plotone{source_plots/example_bad_fit_color.eps}
     \else
-    \includegraphics{source_plots/example_bad_fit_bw.eps}
+    \plotone{source_plots/example_bad_fit_bw.eps}
     \fi
@@
     \label{example_bad_fit}
-  \end{center}
 \end{figure}
@@
 error on $\sigma$ is statistical and the second is systematic (see
-section~\ref{systematic_errors_on_extension}).  Pos Err is the error on
+Section~\ref{systematic_errors_on_extension}).  Pos Err is the error on
 the position of the source.  Vela X and the Centarus A Lobes were
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/agn_color.eps}
+      \plotone{source_plots/agn_color.eps}
     \else
-      \includegraphics{source_plots/agn_bw.eps}
+      \plotone{source_plots/agn_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v6/agn.py
-    \end{center}
     \caption{The cumulative density of \tsext for 783 of the clean
@@
     density of $\tsext$ is expected to follow a $\chi^2/2$ distribution
-    (equation~\ref{ts_ext_distribution}) and is the dash-dotted line (colored
+    (Equation~\ref{ts_ext_distribution}) and is the dash-dotted line (colored
     red in the electronic version).
@@
     The columns in this table
-    are equivalent to the columns in table~\ref{known_extended_sources}.
+    are equivalent to the columns in Table~\ref{known_extended_sources}.
 }
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_Puppis_A_color.eps}
+      \plotone{source_plots/source_Puppis_A_color.eps}
     \else
-      \includegraphics{source_plots/source_Puppis_A_bw.eps}
+      \plotone{source_plots/source_Puppis_A_bw.eps}
     \fi
-  \end{center}
   % this plot came from 
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_Ophiuchus_color.eps}
+      \plotone{source_plots/source_Ophiuchus_color.eps}
     \else
-      \includegraphics{source_plots/source_Ophiuchus_bw.eps}
+      \plotone{source_plots/source_Ophiuchus_bw.eps}
     \fi
-  \end{center}
   % this plot came from 
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_RX_J1713.7-3946_color.eps}
+      \plotone{source_plots/source_RX_J1713.7-3946_color.eps}
     \else
-      \includegraphics{source_plots/source_RX_J1713.7-3946_bw.eps}
+      \plotone{source_plots/source_RX_J1713.7-3946_bw.eps}
     \fi
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
-  \end{center}
   \caption{A diffuse-emission-subtracted 1-100 \gev
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_Vela_Jr_color.eps}
+      \plotone{source_plots/source_Vela_Jr_color.eps}
     \else
-      \includegraphics{source_plots/source_Vela_Jr_bw.eps}
+      \plotone{source_plots/source_Vela_Jr_bw.eps}
     \fi
-  \end{center}
   % this plot came from 
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_HESS_J1614-518_color.eps}
+      \plotone{source_plots/source_HESS_J1614-518_color.eps}
     \else
-      \includegraphics{source_plots/source_HESS_J1614-518_bw.eps}
+      \plotone{source_plots/source_HESS_J1614-518_bw.eps}
     \fi
-  \end{center}
   % this plot came from 
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_HESS_J1632-478_color.eps}
+      \plotone{source_plots/source_HESS_J1632-478_color.eps}
     \else
-      \includegraphics{source_plots/source_HESS_J1632-478_bw.eps}
+      \plotone{source_plots/source_HESS_J1632-478_bw.eps}
     \fi
-  \end{center}
   % this plot came from 
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_HESS_J1837-069_color.eps}
+      \plotone{source_plots/source_HESS_J1837-069_color.eps}
     \else
-      \includegraphics{source_plots/source_HESS_J1837-069_bw.eps}
+      \plotone{source_plots/source_HESS_J1837-069_bw.eps}
     \fi
-  \end{center}
   % this plot came from 
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{source_plots/source_Gamma_Cygni_color.eps}
+      \plotone{source_plots/source_Gamma_Cygni_color.eps}
     \else
-      \includegraphics{source_plots/source_Gamma_Cygni_bw.eps}
+      \plotone{source_plots/source_Gamma_Cygni_bw.eps}
     \fi
-  \end{center}
   % this plot came from 
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{summary_plots/snr_seds_color.eps}
+      \plotone{summary_plots/snr_seds_color.eps}
     \else
-      \includegraphics{summary_plots/snr_seds_bw.eps}
+      \plotone{summary_plots/snr_seds_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_snr_seds.py
-    \end{center}
     \caption{
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{summary_plots/hess_seds_color.eps}
+      \plotone{summary_plots/hess_seds_color.eps}
     \else
-      \includegraphics{summary_plots/hess_seds_bw.eps}
+      \plotone{summary_plots/hess_seds_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_hess_seds.py
-    \end{center}
     \caption{
@@
 \begin{figure}
-  %\begin{center}
     \ifcolorfigure
-    \includegraphics{summary_plots/allsky_extended_sources_color.eps}
+    \plotone{summary_plots/allsky_extended_sources_color.eps}
     \else
-    \includegraphics{summary_plots/allsky_extended_sources_bw.eps}
+    \plotone{summary_plots/allsky_extended_sources_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v2/run.py
-    %\end{center}
     \caption{A plot of all \gev extended sources detected by the LAT
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{summary_plots/gev_vs_tev_plot_color.eps}
+      \plotone{summary_plots/gev_vs_tev_plot_color.eps}
     \else
-      \includegraphics{summary_plots/gev_vs_tev_plot_bw.eps}
+      \plotone{summary_plots/gev_vs_tev_plot_bw.eps}
       \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v3/run.py
-    \end{center}
     \caption{
@@
     surface brightness so the plotted \gev and \tev extensions were first
-    converted to \rsixeight (see section~\ref{compare_source_size}).
+    converted to \rsixeight (see Section~\ref{compare_source_size}).
     Because of their large size, the shape of RX J1713.7-3946 and Vela Jr.
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{summary_plots/gev_vs_tev_histogram_color.eps}
+      \plotone{summary_plots/gev_vs_tev_histogram_color.eps}
     \else
-      \includegraphics{summary_plots/gev_vs_tev_histogram_bw.eps}
+      \plotone{summary_plots/gev_vs_tev_histogram_bw.eps}
     \fi
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v4/extension_histogram.py
-    \end{center}
     \caption{
@@
     The extension of the LAT sources comes from
-    table~\ref{known_extended_sources}, table~\ref{new_ext_srcs_table},
+    Table~\ref{known_extended_sources}, Table~\ref{new_ext_srcs_table},
     and from \cite{velax}. 
@@
     Catalog \citep{hesscat}.
+%   The \tev extension of
+%   the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
+%   Catalog\footnote{
+%   The H.E.S.S. source catalog can be found at \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
     Except for RX J1713.7-3946 and Vela Jr.,
@@
     so the LAT and H.E.S.S. sizes are first converted to \rsixeight.
-    (see section~\ref{compare_source_size}). Because the spatial
+    (see Section~\ref{compare_source_size}). Because the spatial
     morphology of RX J1713.7-3946 and Vela Jr. is poorly matched by a
@@
 \begin{figure}
-  \begin{center}
     \ifcolorfigure
-      \includegraphics{summary_plots/compare_index_2FGL_color.eps}
+      \plotone{summary_plots/compare_index_2FGL_color.eps}
     \else
-      \includegraphics{summary_plots/compare_index_2FGL_bw.eps}
+      \plotone{summary_plots/compare_index_2FGL_bw.eps}
     \fi
     % plot taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_index_2fgl/v3/run.py
-    \end{center}
     \caption{
@@
     spectral indices of LAT extended sources are taken from
-    table~\ref{known_extended_sources} table~\ref{new_ext_srcs_table}.
+    Table~\ref{known_extended_sources} and \ref{new_ext_srcs_table}.
     The index of Centarus A is taken to be 2.58 from 

### 2011-08-23 extended_catalog/paper/extended_catalog.tex
alexs changes

@@
 \newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{inc}}}\xspace}
-\newcommand{\loglikelihood}{\ensuremath{LL}\xspace}
-\newcommand{\likelihood}{\ensuremath{L}\xspace}
+
+\newcommand{\likelihood}{\ensuremath{\mathcal{L}}\xspace}
+
 \newcommand{\chandra}{\text{{\em Chandra}}\xspace}
@@
 \usepackage{color}
-\newcommand{\hl}[1]{{\color{red}#1}}
+
+%\newcommand{\hl}[1]{{\color{red}#1}}
+\newcommand{\hl}[1]{#1}
 
@@
 A.~Allafort\altaffilmark{2},
-K.~Bechtol\altaffilmark{2},
 M.-H.~Grondin\altaffilmark{53},
+% Keith Bechtol
+% Marshall Roth?
+% Marianne Lemoine-Goumard
+% Francesco Giordano
+% Toby Burnett
+% Jean Ballet
+% Matthew Kerr
 \ldots
@@
 \begin{abstract}
-We present a new method for quantifying
-the spatial extension of sources with
-the Large Area Telescope (LAT), the primary science instrument on the
-{\em \fermi Gamma-ray Space Telescope} (\fermi). 
-Spatial extension
-is an important characteristic for correctly 
-associating LAT sources with their counterparts at other
-wavelengths. We perform
-a series of Monte Carlo studies to validate this tool and calculate
-the LAT's threshold for detecting the spatial extension of sources.  We then
-use this tool to test all sources in the two year source catalog for
-extension. We report the detection of nine spatially extended sources
-in addition to the twelve spatially extended sources reported in the
-second \fermi-LAT Catalog (2FGL).
+We present a new method for quantifying the spatial extension of sources
+with the Large Area Telescope (LAT), the primary science instrument on
+the {\em \fermi Gamma-ray Space Telescope} (\fermi).  Spatial extension
+is an important characteristic for correctly associating LAT sources with
+their counterparts at other wavelengths. We perform a series of Monte
+Carlo simulations to validate this tool and calculate the LAT's threshold
+for detecting the spatial extension of sources.  We then use this tool
+to test all sources in the two-year source catalog for extension. We
+report the detection of nine spatially extended sources in addition to
+the twelve spatially extended sources reported in the second \fermi-LAT
+Catalog (2FGL).
 \end{abstract}
@@
 
-The Large Area Telescope (LAT) is a pair conversion telescope on the {\em \fermi
-Gamma-ray Space Telescope} (\fermi) that been surveying the $\gamma$-ray
-sky since 2008 June.  The LAT has broad energy coverage (20 \mev to $>300$
-\gev), wide field of view ($\sim 2.4 \sr$), and large effective area
-($\sim 8000\ \cm^2$ at $>1 \gev$).
-
-Using two years of all-sky surveying data, the LAT Collaboration published
-a catalog of 1873 \gev sources \citep{second_cat}. Many of these have
-been positionally associated with a variety of source classes including
-Active Galactic Nuclei (AGN), pulsars, normal galaxies, and supernova
-remnants (SNRs).  While the counterparts of many LAT sources can be
-spatially resolved when observed at other frequencies, detection of
-spatial extension of these sources at \gev energies is difficult because
-the size of the point-spread function (PSF) of the LAT is comparable
-to the typical size of many of these sources.
-
-However, a number of sources positionally coincident with LAT sources
-exhibit extensions at other wavelengths which are comparable to or larger than 
-the LAT PSF.  In particular, certain SNRs, pulsar wind nebulae (PWNe),
-molecular clouds, normal galaxies, galaxy clusters or dark matter
-satellites could be expected to be detected as spatially extended
-sources by the LAT.  
-The LAT Collaboration has previously reported on five SNRs which are
-spatially extended beyond the LAT PSF at \gev energies 
-(IC443, W28, W44,
-W51C, and RX J1713.7-3946 \citep{ic443,w28,w44,w51c,rx_j1713_lat}). In
-addition, three extended PWNe were detected: MSH 15-52, Vela~X,
-and HESS\,J1825-137 \citep{msh1552,velax,fermi_hess_j1825}, as well
-as two close-by galaxies, the Large and Small Magalenic
-Cloud \citep{lmc,smc}, and finally the radio galaxy Centarus A
-\citep{cen_a_lat}.
-For each of these sources, the extension was determined from a dedicated
-analysis of the particular source and so a systematic
-scan of all LAT detected sources could uncover
-additonal spatially extended sources.
-
 \hl{
-Many extended sources in the Galactic plane have been detected at \tev
-energies using air Cherenkov detectors.  Most prominent was a survey of
-the Galactic plane using the High Energy Stereoscopic System (H.E.S.S)
-which reported 14 spatially extended sources with extensions varying from
-$\sim0\fdg1$ to $\sim0\fdg25$ \citep{hess_plane_survey}.  In fact, within
-our Galaxy only very few sources (most notably the $\gamma$-ray binaries
+
+A number of astrophysical sources classes including supernova remnant
+(SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
+galaxy clusters could be expected to spatially resolvable at \gev
+energies.  Dark matter satellites are also hypothesized to be seen
+as spatially extended at \gev energies.  The LAT Collaboration has
+previously reported on five SNRs which are spatially extended beyond
+the LAT PSF at \gev energies (IC443, W28, W44, W51C, and RX J1713.7-3946
+\citep{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended PWNe
+were detected as being extended: MSH 15-52, Vela~X, and HESS\,J1825-137
+\citep{msh1552,velax,fermi_hess_j1825}. Two close-by galaxies the Large
+and Small Magalenic Clouds and one radio galaxy Centarus A were spatially
+resolved at \gev energies \citep{lmc,smc,cen_a_lat}.  Furthermore,
+a number of other sources previously detected at \gev energies are
+positionally coincident with sources that exhibit extension at other
+wavelengths and could be expected to be spatially resolvable at \gev
+energies.
+
+At \tev energies many sources have been recently detected as
+begin spatially extended using air Cherenkov detectors.  Most
+prominent was a survey of the Galactic plane using the High Energy
+Stereoscopic System (H.E.S.S) which reported 14 spatially extended
+sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
+\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
+sources detected at \tev energies (most notably the $\gamma$-ray binaries
 LS\,5039 \citep{HESSLS5039}, LS I+61-303 \citep{MAGICLSI, VERITASLSI}
 HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
-have no significant extension detected at \tev energies.  High energy
-$\gamma$-rays from these sources are produced by the decay of $\pi^0$s
-produced by hadronic interactions with interstellar matter and by
-relativistic electrons due to Inverse Compton (IC) scattering and
-Bremsstrahlung radiation \citep{blandford_and_eichler_1987}.  It is likely
-that the \gev and \tev emission from these sources originates from the
-same population of high-energy particles and so at least some of these
-sources should be detected as extended sources at \gev energies. By
-studying the spectra of these \tev sources at \gev energies, we may help
-to determine the emission mechanisms of these high energy sources.
-}
-
-The capability to spatially resolve \gev $\gamma$-ray sources is important
-for several reasons.  First, multiple potential counterparts detected at
-other frequencies exist within the localization confidence region of a
-typical LAT source along the Galactic plane.  Finding a coherent source
-extension across different energy bands can help to associate a
-LAT source to an otherwise confused counterpart.  Also, due to the strong
-energy dependence of the LAT PSF, the spatial and spectral information
-about a source do not simply decouple. An inaccurate spatial model
-will bias the spectral model of the source. Specifically, 
+have no significant extension detected.  High energy $\gamma$-rays from
+these sources are produced by the decay of $\pi^0$s produced by hadronic
+interactions with interstellar matter and by relativistic electrons
+due to Inverse Compton (IC) scattering and Bremsstrahlung radiation
+\citep{blandford_and_eichler_1987}.  It is likely that the \gev and
+\tev emission from these sources originates from the same population of
+high-energy particles and so at least some of these sources should be
+detected as extended sources at \gev energies.  Studying 
+these \tev sources at \gev energies would help to
+determine the emission mechanisms producing these high energy photons.
+
+The Large Area Telescope (LAT) is a pair conversion telescope on the
+{\em \fermi Gamma-ray Space Telescope} (\fermi) that been surveying the
+$\gamma$-ray sky since 2008 June.  The LAT has broad energy coverage
+(20 \mev to $>300$ \gev), wide field of view ($\sim 2.4 \sr$), and large
+effective area ($\sim 8000\ \cm^2$ at $>1 \gev$).  Using two years of
+all-sky surveying data, the LAT Collaboration published a catalog of 1873
+sources detected at these \gev energies called 2FGL \citep{second_cat}.
+The counterparts of many of these sources can be spatially resolved
+when observed at other frequencies but detecting the spatial extension
+of these sources at \gev energies is difficult because the size of the
+point-spread function (PSF) of the LAT is comparable to the typical size
+of many of these sources.
+
+On the other hand, the capability to spatially resolve \gev $\gamma$-ray
+sources is important for several reasons.  First, multiple potential
+counterparts detected at other frequencies exist within the localization
+confidence region of a typical LAT source along the Galactic plane.
+Finding a coherent source extension across different energy bands can
+help to associate a LAT source to an otherwise confused counterpart.
+Furthermore, dark matter satellite in our galaxy have been predicted to be
+detected and spatially extended at \gev energies and could be discovered
+outside the galactic plane \citep{pre_luanch_dark_matter_fermi}.  Also,
+due to the strong energy dependence of the LAT PSF, the spatial and
+spectral information about a source do not simply decouple. An inaccurate
+spatial model will bias the spectral model of the source. Specifically,
 modeling a spatially extended source as point-like will systematically
-shift a spectral analysis to softer indices. Furthermore,
-correctly modeling a source's extension is important for improving
-the model of the sky and removing excess residuals, for example in the
-region around surrounding the Large Magellanic Clouds \citep{first_cat}.
-Such excess residuals potentially bias the significance
-and measured spectrum of neighboring sources in the densely populated
-Galactic plane.
+shift a spectral analysis to softer indices. Furthermore, correctly
+modeling a source's extension is important for improving the model of
+the sky and removing excess residuals, for example in the region around
+surrounding the Large Magellanic Clouds \citep{first_cat}.  Such excess
+residuals potentially bias the significance and measured spectrum of
+neighboring sources in the densely populated Galactic plane.
+
+Each of the previously detected extended LAT sources was spatially
+resolved by a dedicated analysis of the particular source so
+we expect that a systematic scan of all LAT detected sources
+could uncover additional spatially extended sources.  For these
+reasons, in Section~\ref{analysis_methods_section} we present
+a new method for analyzing spatially extended LAT sources. In
+Section~\ref{monte_carlo_validation} we demonstrate that this tool
+can be used for an unbiased statistical test of the extension of
+LAT sources and in Section~\ref{extension_sensitivity} we calculate
+the LAT's detection threshold to resolve the extension of a source.
+In Section~\ref{extended_source_search_method} we describe a search for
+new spatially extended LAT sources and in Section~\ref{validate_known}
+we reanalyzing the twelve previously detected extended sources
+included in 2FGL.  In Section~\ref{test_2lac_sources} we further
+validate our extension test by testing the extension of Active
+galactic nucleus (AGN) believed to be unresolvable. Finally, in
+Section~\ref{new_ext_srcs_section} we present the detection of the
+extension of nine spatially extended sources that were reported in 2FGL
+but not previously spatially resolved.
+
+}
 
 \section{Analysis Methods}
+\label{analysis_methods_section}
 
@@
 \citep{atwood_LAT_mission,on_orbit_calibration,lat_on_orbit_psf}.\footnote{More
-information about the performance of the LAT can be found at the Fermi
+information about the performance of the LAT can be found at the \fermi
 Science Support Center (FSSC,\url{http://fermi.gsfc.nasa.gov}).} However,
@@
 for studying spatially extended sources with the LAT. The tool performs
-a maximum likelihood analysis in which the Poisson likelihood for
-observing the measured counts is maximized, given a parametrized
-spatial and spectral model of the source and its surrounding region.
-The extension of a source can be modeled by a geometric shape (e.g. a
-disk or Gaussian) and the source's position, extension, and spectrum
-can be simultaneously fit.
+a maximum likelihood analysis in which the Poisson likelihood to find
+the observing counts is maximized given a parametrized spatial and
+spectral model of the source and its surrounding region.  The sky is
+divided into cubes in space and energy using the healpix representation
+of the sky \citep{healpix} and the likelihood is maximized over all bins
+in a region.  The extension of a source can be modeled by a geometric
+shape (e.g. a disk or a two-dimensional Gaussian) and the source's position, extension,
+and spectrum can be simultaneously fit.
 
@@
 analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
-FSSC.} because \gtlike can only
-fit the spectral parameters of the model unless a more sophisticated
-iterative procedure is used to also test various source morphologies.
-We note that \gtlike has been used in the past in several studies of
-source extension in the LAT Collaboration \citep{lmc,smc,w28,w51c}.
-Based upon a set of \gtlike maximum likelihood fits at fixed extensions,
-a profile of the likelihood as a function of the extension was calculated.
+FSSC.} because it can only fit the spectral parameters of the model
+unless a more sophisticated iterative procedure is used to also test
+various source morphologies.  We note that \gtlike has been used in the
+past in several studies of source extension in the LAT Collaboration
+\citep{lmc,smc,w28,w51c}.  In these studies, a profile based upon a
+set of \gtlike maximum likelihood fits at fixed extensions was used
+to build a profile of the likelihood as a function of extension.
 This approach is not optimal because the position, extension, and
 spectrum of the source must be simultaneously fit to find the best fit
-parameters and to correctly compute the statistical significance of the
-detection.  Furthermore since the \gtlike likelihood profile approach
-is computationally intensive, no large-scale Monte Carlo effort has been
-run to validate it.
+parameters and to correctly compute the statistical significance of
+a detection.  Furthermore since the \gtlike likelihood profile approach
+is computationally intensive, no large-scale Monte Carlo simulations
+have been run to validate it.
 
@@
 fitting package developed in the LAT Collaboration called \pointlike
-\citep{first_cat,matthew_kerr_thesis}.  We extended the code to allow
-a simultaneous fit of the source extension together with the position
-and the spectral parameters.
-
-The choice to base the spatial extension fitting on \pointlike rather than
-\gtlike was made on considerations of computing time.  The \pointlike
-algorithm was optimized for speed to handle larger numbers of sources
-efficiently which is important for our catalog scan as well as the Monte
-Carlo validation of our method.  Details on the \pointlike package can
-be found in \cite{matthew_kerr_thesis}.
+\citep{first_cat,matthew_kerr_thesis}.  The choice to base the
+spatial extension fitting on \pointlike rather than \gtlike was made
+on considerations of computing time.  The \pointlike algorithm was
+optimized for speed to handle larger numbers of sources efficiently
+which is important for our catalog scan and for being able
+to perform large-scale Monte Carlo simulations to validate the tool.
+Details on the \pointlike package can be
+found in \cite{matthew_kerr_thesis}.  We extended the code to allow a
+simultaneous fit of the source extension together with the position and
+the spectral parameters.
 
@@
 \pointlike convolves the extended source shape with the PSF (as a
-function of energy) and uses the \minuit library to maximize the
+function of energy) and uses the \minuit library 
+\citep{minuit_documentation}
+to maximize the
 likelihood by simultaneously varying the position and extension of
-the source \citep{minuit_documentation}.  As will be described in
+the source.  As will be described in
 Section~\ref{monte_carlo_validation}, simultaneously fitting the position
@@
 
-The significance of the extension of a source can be calculated
-from \tsext, which 
-is the test statistic of the likelihood ratio test of
-a model with a spatially extended source and a model
-with a point-like source and is defined as
+The significance of the extension of a source can be calculated from the
+likelihood ratio test of a model with a spatially extended source and
+a model with a point-like source. The test statistic for this procedure
+is defined as
 \begin{equation}
-  \tsext=2\log(\likelihood_\text{ext}/\likelihood_\text{ps}) = 2 (\loglikelihood_\text{ext}-\loglikelihood_\text{ps})
+  \tsext=2\log(\likelihood_\text{ext}/\likelihood_\text{ps}) 
 \end{equation}
-where \loglikelihood is the log of the Poisson likelihood.
+where \likelihood is the Poisson likelihood.
 \pointlike calculates \tsext by fitting a source first with a spatially
@@
 For extended sources with an assumed radially symmetric shape,
-we use a semi-analytic calculation to speed up the calculation of
-the expected photon distribution. The expected photon 
+we can optimize the calculation by performing one
+of the integrals analytically.
+The expected photon 
 distribution can be written as
@@
 \end{equation}
-For the LAT, the PSF can be parameterized by a {\em King function}
+For the LAT, the PSF can be parameterized by a King function \citep{king_function}:
 \begin{equation}
@@
 \tsext, we compare the likelihood fitting the source with an extended
-spatial model to the likelihood when fixing its extension to ${10^{-10}}\deg$.
-
-We estimate the error on the extension of a source by fixing the position
-of the source and varying the extension until the likelihood has fallen
-by \onehalf, corresponding to a $1\sigma$ error.  This method is
-shown schematically in Figure~\ref{four_plots_ic443}(a) which shows the
-change in \loglikelihood when varying the extension of the SNR IC443.
-The localization error is calculated by fixing the extension and spectrum
-of the source and fitting to the likelihood function a Gaussian as a function
+spatial model to the likelihood when fixing its extension to $10^{-10\,\circ}$.
+
+We estimate the error on the extension of a source by fixing
+the position of the source and varying the extension until the
+likelihood has fallen by \onehalf, corresponding to a $1\sigma$ error
+\citep{Statistical_methods_book}.  This method is shown schematically in
+Figure~\ref{four_plots_ic443} which shows the change in the log of the
+likelihood when varying the extension of the SNR IC443.  The localization
+error is calculated by fixing the extension and spectrum of the source
+and fitting to the likelihood function a 2D Gaussian as a function
 of position.
@@
 such as source localization and extension fitting.  On the other hand,
-because of the fewer approximations used in calculating the likelihood
-we expect the spectral parameters found with \gtlike to be slightly
-more precise.  Furthermore, because \gtlike is the standard likelihood
-analysis package, it has been more extensively validated for spectral
-analysis.  For those reasons, in the following analysis  we use \pointlike
-to determinate the position and extension of a source and subsequently determine
-the spectrum using \gtlike. Both \gtlike and \pointlike can be 
-used to estimate
-the statistical significance of the extension of a source and we require
-that both methods agree to claim a detection.
-
-We found good agreement between the two methods.  
-Unless explicitly mentioned, all \ts, \tsext, and spectral
-parameters were calculated using \gtlike using the best-fit
-positions and extensiosn found with \pointlike.
+because \gtlike makes fewer approximations in calculating the likelihood
+we expect the spectral parameters found with \gtlike to be slightly more
+precise.  Furthermore, because \gtlike is the standard likelihood analysis
+package, it has been more extensively validated for spectral analysis.
+For those reasons, in the following analysis we used \pointlike to
+determine the position and extension of a source and subsequently derived
+the spectrum using \gtlike. Both \gtlike and \pointlike can be used to
+estimate the statistical significance of the extension of a source and we
+required that both methods agree for a source to be considered extended.
+We found good agreement between the two methods.  Unless explicitly
+mentioned, all \ts, \tsext, and spectral parameters were calculated using
+\gtlike with the best-fit positions and extension found by \pointlike.
 
@@
 There is a degeneracy between a spatially extended source and multiple
-point sources that are separated by angular distances comparable or
-smaller than the size of the LAT PSF.  To assess the possibility of source
-confusion, we developed a function in \pointlike to simultaneously fit
-the position of two point sources.
-
-We define \tsinc as twice the increase in \loglikelihood fitting the
+point sources separated by angular distances comparable to or smaller than
+the size of the LAT PSF.  To assess the possibility of source confusion,
+we use \pointlike to simultaneously fit the position of two point sources
+in the region of extended source candidates.
+
+We define \tsinc as twice the increase in the log of the likelihood fitting the
 region as two point sources compared to fitting the region as one point
@@
 \begin{equation}
-  \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
+  \tsinc=2\log(\likelihood_\text{2pts}/\likelihood_\text{ps}).
 \end{equation} 
@@
 Similar to the case of extended sources described in Section~\ref{gtlike_crosscheck},
-the spectrum of the two point sources can be refit using \gtlike.
+the spectra of the two point sources can be refit using \gtlike.
 We quote the spectral values obtained from \gtlike using the best fit
@@
 We tested two different models for the
-surface brightness profile, either a two dimensional Gaussian
+surface brightness profile, either a 2D Gaussian
 \begin{equation}\label{gauss_pdf}
@@
 \end{equation}
-Although these shapes are significantly different, their convolution
-with the PSF look similar.  Figure~\ref{compare_disk_gauss}
-demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
-a radially symmetric uniform brightness and the Gaussian surface brightness of size 0\fdg5.\footnote{To
+Although these shapes are significantly different, when convolved
+with the PSF, their profiles are very similar.  
+This is demonstrated in 
+Figure~\ref{compare_disk_gauss}
+by showing $I_\text{src}$, the PSF, and the PDF for
+a radially symmetric uniform brightness and a Gaussian surface brightness of size 0\fdg5.\footnote{To
 allow a valid comparison between Gaussian and disk shaped morphologies,
@@
 is defined in Equation~\ref{gauss_pdf} and
-Equation~\ref{disk_pdf} respectively.} This plot shows that the LAT is 
-not very sensitive to probing the exact structure of an extended source.
-In the search for extended sources, we therefore use only a uniform
+Equation~\ref{disk_pdf} respectively.} This plot shows that the LAT 
+has little sensitivity to
+the exact structure of an extended source.
+Therefore, in our
+search for extended sources, we use only a uniform
 disk as our spatial extension shape. We then quote the radius of the
@@
 
-We test the performance of \pointlike fitting the extension of
+We test the false detection probability of \pointlike by fitting the extension of
 point-like sources.
@@
 expect a similar distribution of the test statistic
-in the test for source extension as the same conditions
+in the test for source extension since the same conditions
 apply (with the source flux $\Phi$ replaced by the source radius $r$ and
 $r<0$ being unphysical).
-To validate this claim, we performed a Monte Carlo
-study to calculate empirical distributions for $\tsext$ and
+To validate this claim, we performed Monte Carlo
+simulations
+to calculate empirical distributions for $\tsext$ and
 compared them to Equation~\ref{ts_ext_distribution}.
@@
 We simulated point sources with various spectral forms using
+the LAT on-orbit simulation tool, 
 \gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit them with \pointlike using both point
-and extended source hypotheses.  The point sources were simulated with a power-law
-spectral model with integrated fluxes above 100 \mev ranging from $3\times
-10^{-9}$ to $10^{-6}$ \phflux in six discrete steps and spectral
+and extended source hypotheses.  These point sources were simulated with a power-law
+spectral model with integrated fluxes above 100 \mev ranging from $3\times10^{-9}$ 
+to $1\times10^{-6}$ \phflux in six discrete steps and spectral
 indices ranging from 1.5 to 3 in four discrete steps.  These values
-were picked to to represent typical source parameter of LAT-detected
+were picked to to represent typical source parameters of LAT-detected
 sources. The point sources were simulated on top of an isotropic
-background with an integrated flux above 100 \mev of $1.5\times10^{-5}$
+background with an integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux
 taken to be the same as the isotropic spectrum measured by EGRET
 \citep{sreekumar_isotropic}.  The Monte Carlo simulation was performed
-over a one year observation period using a default rocking profile and a
+over a one-year observation period using a representative rocking profile and a
 representative livetime fraction of 0.8.  The reconstruction was performed
-using 1-100 \gev photons and the Pass 7\_V6 (P7\_V6) Source Instrument
+using 1 \gev to 100 \gev photons and the Pass~7\_V6 (P7\_V6) Source Instrument
 Response Function (IRFs, \cite{lat_on_orbit_psf}).  For each 
-significantly detected point source ($\ts>25$), we used \pointlike
+significantly detected point source ($\ts\ge25$), we used \pointlike
 to fit it as an extended source and calculate \tsext.
@@
 
-Our Monte Carlo study shows broad agreement between simulations and
+Our study shows broad agreement between simulations and
 Equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is not
 perfect.  It should be noted that the discrepancy seems to be worst for
-bright sources, a likely cause being numerical errors in the convolution
-becoming more apparent for sufficiently bright sources.  Other possible
-reasons for departure from Equation~\ref{ts_ext_distribution} could
-be that \pointlike ignores energy dispersion which would change the
+bright sources where numerical errors in the convolution
+are most apparent.  Another possible
+reason for the departure from Equation~\ref{ts_ext_distribution} 
+is that \pointlike ignores energy dispersion which will change the
 PSF shape as a function of energy. We emphasize that many of
-the empirical distributions lies to the left of the theoretical curve so
-using the theoretical distribution would lead to an underestimate of the
+the empirical distributions lie to the left of the theoretical curve so
+using the theoretical distribution will lead to an underestimate of the
 statistical significance of a detection. Therefore, we are confident that
@@
 
-We calculated the LAT's detection threshold to resolve spatially extended
-sources as being extended. We define the detection threshold as the flux at which the value
+We calculated the LAT's detection threshold to detect that a spatially extended
+sources is extended. We define the detection threshold as the flux at which the value
 of $\tsext$ averaged over many statistical realizations of a source
@@
 
-We used the simulation setup described in
-Section~\ref{monte_carlo_validation}, but instead simulated extended
+We used a simulation setup similar to that described in
+Section~\ref{monte_carlo_validation}, but instead of point sources
+we simulated extended
 sources with a radially symmetric uniform surface
-brightness and
-simulated over the actual two year time interval of LAT observations.  
-For each extension and
+brightness. Additionally, we
+simulated our sources over the two-year time range included
+in 2FGL.
+Each extension and
 spectral index, we selected a flux range which bracketed $\tsext=16$
@@
 the threshold using photons with energies between 100 \mev and 100 \gev
-and also using only 1-100\gev photons.
+and also using only 1 \gev to 100 \gev photons.
 Except for very large ($>1\deg$) sources, our detection threshold is
-not substantially improved including photons with energies between 100 \mev and
-1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}(b)
+not substantially improved by including photons with energies between 100 \mev and
+1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}
 which shows \tsext for the SNR IC443 computed independently in twelve
 energy bins between 100 \mev and 100 \gev. For IC443, which has a
-spectral index $\sim2.4$, almost the entire increase in \ts comes
+spectral index $\sim2.4$, almost the entire increase in likelihood
+modeling the source as being extended comes
 from energies above 1 \gev.  On the other hand, other systematic errors
@@
 10x, and 100x the nominal background), different spectral indices, and
-two different energy bands (1-100 \gev and 10-100 \gev).  The detection
+two different energy bands (1 \gev to 100 \gev and 10 \gev to 100 \gev).  The detection
 threshold is higher for sources in regions of higher background.  For a
-fixed 1-100 \gev or 10-100 \gev flux, the LAT's detection threshold
-is only weakly depends upon the spectral index.  This effect is most
+fixed 1 \gev to 100 \gev or 10 \gev to 100 \gev flux, the LAT's detection threshold
+only weakly depends upon the spectral index.  This effect is most
 pronounced when using only photons with energies above 10 \gev.  Overlaid
@@
 
-Finally, Figure~\ref{time_sensitivity} shows the LAT's projected detection
-threshold to extension after 10 years against 10 times the isotropic
-background. This background is representative of the background near
-the Galactic plane.  For small extended sources, our detection threshold
-improves by a factor larger than the square root of time because at high energies, where we
-are most sensitive to extension, the background levels are in the Poisson
-instead of Gaussian regime.  For large extended sources, the relevant
-background is larger and the improvement is closer to the expected
-factor of the square root of time.
+Finally, Figure~\ref{time_sensitivity} shows the LAT's projected
+detection threshold to extension after 10 years against 10 times
+the isotropic background. This background is representative of the
+background near the Galactic plane.  For small extended sources, our
+detection threshold improves by a factor larger than the square root
+of the exposure because at high energies, where we are most sensitive
+to extension, the background levels are in the Poisson instead of the
+Gaussian regime.  For large extended sources, the relevant background
+is over a larger spatial range and so the improvement is closer to the
+expected factor corresponding to the square root of the exposure.
 }
@@
 
-We test all sources in the 
-second \fermi-LAT Catalog (2FGL) for spatial extendedness.
-2FGL is a catalog of 1873 sources detected by the LAT.  It included
-twelve previously published spatially extended sources but did not
-attempt to fit the extension of these sources. Other than these sources,
+We test all sources in 2FGL for spatial extension.
+2FGL included
+twelve previously published spatially extended sources but not
+attempt was made to fit the extension of these sources. Other than these sources,
 all 2FGL sources were modeled as point sources and 2FGL did not attempt
@@
 
-Our analysis setup is closely related to the setup used for the
-derivation of the catalog We used the same two years of data from 
-2008 August 4
-to 2010 August 1 and we used the same Pass 7\_V6 (P7\_V6)
-Source class event selection and IRFs \citep{lat_on_orbit_psf}.  We used the same models to describe the
-background from Galactic diffuse, isotropic, and earth limb emission.
-The galactic diffuse emission was scaled by a power-law and the isotropic
-component's normalization was left free.
+Our analysis technique is closely related to that 
+of the 2FGL catalog. We used the same two-year dataset from 2008 August 4
+to 2010 August 1 and we used the same P7\_V6 Source class
+event selection and IRFs \citep{lat_on_orbit_psf}.  
+The same 
+models were used to describe the background from Galactic diffuse, isotropic, and
+Earth limb emission.  To account for possible residuals in the diffuse
+emission model, the galactic emission was scaled by a unitless power-law
+and the isotropic component's normalization was left free.
 
@@
 is more pronounced at lower energies due to its steep energy spectrum.
-For that reason, we performed our search using photons only between 1
-\gev and 100 \gev.
+For that reason, we performed our search using only photons with
+energies between 1 \gev and 100 \gev.
 
@@
 An example radial integral plot is shown for the extended source IC443
-in Figure~\ref{four_plots_ic443}(c).  For each source, we also made
+in Figure~\ref{four_plots_ic443}.  For each source, we also made
 diffuse-emission-subtracted smoothed counts
-maps. Figure~\ref{four_plots_ic443}(d) shows an example for IC443.
+maps. Figure~\ref{four_plots_ic443} also shows an example for IC443.
 
@@
 fit extension is comparable to the published result, but we note that
-previous LAT Collaboration publication on LMC used a more complicated two Gaussian surface
+previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
 brightness spatial model when fitting it (\citep{lmc}).
@@
 $(l,b)=(260\fdg32,-3\fdg28)$.  
-This source is coincident with the one year
+This source is coincident with the one-year
 catalog source 1FGL\,J0823.3-4248.
@@
 counts map of this source
-and Figure~\ref{snr_seds}(a) shows the LAT spectrum of it.
+and Figure~\ref{snr_seds} shows the LAT spectrum of it.
 }
@@
 
-No molecular clouds have been observed directly ajacent to Puppis A 
+No molecular clouds have been observed directly adjacent to Puppis A 
 \citep{co_eastern_puppis_a}.
 This is similar to the LAT detected SNR the Cyngus Loop \citep{cygnus_loop_lat}.
-The luminolsity of Puppis A is also smaller than that of 
+The luminosity of Puppis A is also smaller than that of 
 other SNRs believed to interact with molecular clouds
@@
 fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  The source
-is coincident with the one year catalog source 1FGL\,J1711.7-3944c.
+is coincident with the one-year catalog source 1FGL\,J1711.7-3944c.
 Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.
@@
 This source is spatially coincident with the SNR RX J1713.7-3946
-and was recently reported by \citep{rx_j1713_lat}.  Figure
-\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR RX
+and was recently reported by \citep{rx_j1713_lat}.  
+Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR RX
 J1713.7-3946 from \citep{rx_j1713_hess}.  To analyze this source,
@@
 was fit to a position of $(l,b)=(332\fdg38,-0\fdg14)$.
-This source is coincident with the one year catalog source
+This source is coincident with the one-year catalog source
 1FGL\,J1613.6-5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
@@
 extension $0.136\pm 0.008$ when fitting the source with an elliptical
-Gaussian surface brightness.  This size corresponds to a 68\% containment
+2D Gaussian surface brightness.  This size corresponds to a 68\% containment
 radius of $\rsixeight=0\fdg21\pm0\fdg01$. This size is comparable to the LAT
 size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
-Figure~\ref{hess_seds}(a) shows that the LAT spectrum of 2FGL\,J1615.0-5051
+Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
 connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.
@@
 HESS\,J1616-508 is located in the region of two SNRs, RCW103
-(G332.4-04) and Kes 32 (G332.4+0.1) but is not spatially coincident
+(G332.4-04) and Kes~32 (G332.4+0.1) but is not spatially coincident
 with either of them \citep{hess_plane_survey}.  HESS\,J1616-508 is near
@@
 \citep{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
-counterparts were observed in observations of x-ray and soft gamma-ray
+counterparts were observed in observations of X-ray and soft gamma-ray
 emission by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
@@
 position of $(l,b)=(331\fdg66,-0\fdg66)$.  This source is coincident
-with the one year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
+with the one-year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
 J1615.2-5138 is close to 2FGL\,J1615.0-5051, the same model described
@@
 Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
-on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a Gaussian
+on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a 2D Gaussian
 extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0.15\pm0.02$
@@
 and $0.23\pm0.03$.  This elliptical size matches the LAT size
-$\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds}(b) shows
+$\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds} shows
 that the LAT spectrum of 2FGL\,J1615.2-5138 connects smoothly to
@@
 \suzaku detected two
-promising x-ray candidates. Source A is an extended source consistent
+promising X-ray candidates. Source A is an extended source consistent
 with the peak of HESS\,J1614-518 and source B coincident with Pismis 22
@@
 2FGL\,J1632.4-4753c.  In addition we removed from our model four
-farther away two year catalog sources 2FGL\,J1638.0-4703c, 2FGL
+farther away two-year catalog sources 2FGL\,J1638.0-4703c, 2FGL
 J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL\,J1639.8-4921c because they
@@
 semi-major and semi-minor axes when fitting the source with an
-elliptical Gaussian surface brightness.  This corresponds to a 68\%
+elliptical 2D Gaussian surface brightness.  This corresponds to a 68\%
 containment size $\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$
 along the semi-major and semi-minor axis. This size is consistent with
-the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}(c)
+the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
 shows that the LAT spectrum of 2FGL\,J1635.4-4717c connects smoothly to
@@
 along the semi-major and semi-minor axis when fitting the source
-with an elliptical Gaussian surface brightness.  This corresponds
+with an elliptical 2D Gaussian surface brightness.  This corresponds
 to a 68\% containment radius of $\rsixeight=0\fdg18\pm0\fdg03$ and
@@
 $\rsixeight=0\fdg29\pm0\fdg07$.  the size difference is not significant
-(less than 2 sigma).  Figure~\ref{hess_seds}(d) shows that the LAT spectrum
+(less than 2 sigma).  Figure~\ref{hess_seds} shows that the LAT spectrum
 connects smoothly to the H.E.S.S spectrum of HESS\,J1837-069.
@@
 fit to a position of $(l,b)=(78\fdg18,2\fdg19)$.  This source
-is coincident with the one year catalog source 1FGL\,J2020.0+4049.
+is coincident with the one-year catalog source 1FGL\,J2020.0+4049.
 \hl{
 Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source.
-and Figure~\ref{snr_seds}(b) shows that the LAT spectrum of it.
+and Figure~\ref{snr_seds} shows that the LAT spectrum of it.
 }
@@
 Further, we found it necessary to add an additional point source not in
-the two year catalog into our background model.  The new source is was
+the two-year catalog into our background model.  The new source is was
 localized to a position of $(l,b)=(78\fdg85,2\fdg67)$ and had $\ts=13.5$ .
@@
 population of extended sources below our sensitivity limit (currently at
-about $\sim0\fdg2$).  \fermi has a five year nominal livetime with a
+about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with a
 goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
 our sensitivity to these smaller sources will improve by a factor greater
-than the square root of time.  With increased exposure, the LAT will likely begin to
+than the square root of the exposure.  With increased exposure, the LAT will likely begin to
 resolve these smaller \tev sources.
@@
     \caption{
-    A comparison of a Gaussian and disk surface brightness profiles
+    A comparison of a 2D Gaussian and disk surface brightness profiles
     of extended sources before and after convolving with the PSF for two
@@
     the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
-    and the convolution of this profile with the LAT PSF respectivly
+    and the convolution of this profile with the LAT PSF respectively
     (colored red in the online version)
@@
     with $\rsixeight=0\fdg5$ and the convolution 
-    of this profile with the LAT PSF respectivly (colored blue in the online version).
+    of this profile with the LAT PSF respectively (colored blue in the online version).
     }\label{compare_disk_gauss}
@@
 \tablecomments{
-    the spectral models used in the Monte Carlo validation of \pointlike.
+    the spectral models used in the Monte Carlo simulations used to
+    validate of \pointlike.
     For each model, the number of statistically independent simulations
@@
     detection threshold assuming the sensitivity improves from 2 to 10
-    years by the square root of time (top edge) and linearly with
-    time (bottom edge).  The lower plot shows the factor increase in
+    years by the square root of the exposure (top edge) and linearly with
+    exposure (bottom edge).  The lower plot shows the factor increase in
     sensitivity.  For small extended sources, our detection threshold
-    to the extension of a source will improve by a factor better than the square root of time. 
+    to the extension of a source will improve by a factor better than the square root of 
+    the exposure.
     }
@@
     A diffuse-emission-subtracted 1-100 \gev counts map of the region
-    around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 Gaussian kernel. The
+    around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian kernel. The
     plus and circle (colored red in the online version) represent the
@@
   \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
-  by a 0\fdg1 Gaussian kernel.  
+  by a 0\fdg1 2D Gaussian kernel.  
   The triangle (colored red in the online version)
@@
   is the model predicted emission from a point source with the same
-  spectrum as 2FGL\,J0823.4-4305 smoothed by the same Gaussian kernel.
+  spectrum as 2FGL\,J0823.4-4305 smoothed by the same kernel.
   This source is spatially coincident with the Puppis A SNR. The
@@
   A diffuse-emission-subtracted 1-100 \gev counts map of (a) the region
-  around 2FGL\,J1627.0-2425 smoothed by a 0\fdg1 Gaussian kernel (b)
+  around 2FGL\,J1627.0-2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
   also the emission from the background source 2FGL\,J1625.7-2526
@@
   the moment-masking technique \citep{masking_moment_2011}, and have
-  been smoothed by a 0\fdg25 Gaussian kernel.
+  been smoothed by a 0\fdg25 2D Gaussian kernel.
     }
@@
   counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
-  a 0\fdg25 Gaussian kernel and (b) also the emission 
+  a 0\fdg25 2D Gaussian kernel and (b) also the emission 
   from the background sources subtracted.
@@
   \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
-  by a 0\fdg25 Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
+  by a 0\fdg25 2D Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
   and circle are the best fit position and extension of the source
@@
     left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0\fdg1
-    Gaussian kernel.  The red stars are the catalog positions of these
+    2D Gaussian kernel.  The red stars are the catalog positions of these
     sources.  The red stars and circles are the best fit positions and
@@
   \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
-  a 0\fdg1 Gaussian kernel.  This source is in a crowded region.
+  a 0\fdg1 2D Gaussian kernel.  This source is in a crowded region.
   The red star is the 2FGL position of this source.  The red
@@
   (a)
-  the region around 2FGL\,J1837.3-0700c smoothed by a 0\fdg1 Gaussian
+  the region around 2FGL\,J1837.3-0700c smoothed by a 0\fdg1 2D Gaussian
   kernel and (b) also the emission from the background 
@@
   \caption{A Diffuse subtracted 10 \gev to 100 \gev counts map of the region
-  around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 Gaussian kernel. The
+  around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 2D Gaussian kernel. The
   triangle (colored red in the online version)
@@
   assuming a radially symmetric uniform surface brightness.  The 
-  star (clored green) 
+  star (colored green) 
   inside the extension represents the position of 
   2FGL\,J2019.1+4040 which was removed
-  because it is part of the extended source.  The diamont
+  because it is part of the extended source.  The diamond
   (colored purple) is the
-  position a source not in the two year catalog which was added to the
+  position a source not in the two-year catalog which was added to the
   region. 2FGL\,J2021.5+4026 is spatially coincident with the $\gamma$
@@
     The LAT extension of Vela X is from \citep{velax}.  Except for RX
-    J1713.7-3946 Vela Jr., the \tev sources were fit assuming a Gaussian
+    J1713.7-3946 Vela Jr., the \tev sources were fit assuming a 2D Gaussian
     surface brightness so the plotted \gev and \tev extensions were first
@@
     HESS\,J1632-478, and HESS\,J1837-069 have only been reported with
-    an elliptical Gaussian fit and so the plotted size is the average
+    an elliptical 2D Gaussian fit and so the plotted size is the average
     of semi-major and semi-minor axis.
@@
     Except for RX J1713.7-3946 and Vela Jr.,
-    the H.E.S.S. sources were fit with a Gaussian surface
+    the H.E.S.S. sources were fit with a 2D Gaussian surface
     brightness model and
@@
     morphology of RX J1713.7-3946 and Vela Jr. is poorly matched by a
-    Gaussian surface brightness model, the \gev and
+    2D Gaussian surface brightness model, the \gev and
     \tev extensions are included assuming a uniform surface brightness.

### 2011-08-23 extended_catalog/paper/extended_catalog.tex
additions

@@
 previously reported on five SNRs which are spatially extended beyond
-the LAT PSF at \gev energies (IC443, W28, W44, W51C, and RX J1713.7-3946
+the LAT PSF at \gev energies (IC443, W28, W44, W51C, and RX\,J1713.7$-$3946
 \citep{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended PWNe
-were detected as being extended: MSH 15-52, Vela~X, and HESS\,J1825-137
+were detected as being extended: MSH\,15$-$52, Vela~X, and HESS\,J1825$-$137
 \citep{msh1552,velax,fermi_hess_j1825}. Two close-by galaxies the Large
@@
 sources detected at \tev energies (most notably the $\gamma$-ray binaries
-LS\,5039 \citep{HESSLS5039}, LS I+61-303 \citep{MAGICLSI, VERITASLSI}
+LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI}
 HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
@@
 (20 \mev to $>300$ \gev), wide field of view ($\sim 2.4 \sr$), and large
-effective area ($\sim 8000\ \cm^2$ at $>1 \gev$).  Using two years of
-all-sky surveying data, the LAT Collaboration published a catalog of 1873
-sources detected at these \gev energies called 2FGL \citep{second_cat}.
+effective area ($\sim 8000\ \cm^2$ at $>1 \gev$).  
+Using one year of all-sky surveying data, the LAT Collaboration published
+a catalog of 1451 sources significantly detected at \gev energies called 1FGL \citep{first_cat}.
+Using two years of data, a second catalog called 2FGL reported on 1873
+sources \citep{second_cat}.
 The counterparts of many of these sources can be spatially resolved
@@
 
-On the other hand, the capability to spatially resolve \gev $\gamma$-ray
+The capability to spatially resolve \gev $\gamma$-ray
 sources is important for several reasons.  First, multiple potential
@@
 Earth limb emission.  To account for possible residuals in the diffuse
-emission model, the galactic emission was scaled by a unitless power-law
+emission model, the galactic emission was scaled by a power-law
 and the isotropic component's normalization was left free.
@@
 more susceptible to systematic errors arising from source confusion due
-to multiple point sources and susceptible to incorrect modeling of the
+to multiple point sources and modeling of the
 Galactic diffuse emission. In addition, the Galactic diffuse emission
-is more pronounced at lower energies due to its steep energy spectrum.
+is more pronounced at lower energies due to its steep energy spectrum
+\citep{intermediate_diffuse_lat}.
 For that reason, we performed our search using only photons with
@@
 
-We also performed a search for extended sources using only 10-100 \gev photons. 
-Even though we are testing the same
-sources, this approach is complimentary because the Galactic diffuse
+We also performed a search for extended sources using only 10 \gev to 100 \gev photons. 
+Even this approach tests the same
+sources, it is complimentary because the Galactic diffuse
 emission is even less dominant above 10 \gev. Furthermore, source
@@
 especially
-beneficial for regions near pulsars which are not significantly above 10 \gev and was
-successfully used in detecting HESS\,J1825-137 and MSH 15-52 with the LAT
+beneficial for regions near pulsars which are not significantly detected 
+above 10 \gev. A similar procedure was
+used to detect HESS\,J1825$-$137 and MSH\,15$-$52 with the LAT
 \citep{msh1552,fermi_hess_j1825}.
@@
 and a power-law spectral model.
-We used a circular $10\deg$ region of interest centered on our source and
+We used a circular $10\deg$ region of interest (ROI) centered on our source and
 included all catalog sources within $15\deg$ of the source of interest
@@
 
-Finally, when analyzing the region, we automatically removed other 2FGL
-sources which were within 0\fdg5 of the source of interest. This was
-done to avoid a concern that extended sources are included in 2FGL as
-multiple point sources. These spurious sources could distort the
-extension fit.  Instead, when a source is found to be significantly
-extended (i.e. $\tsext>16$), we perform the dual localization procedure
-(described in Section~\ref{dual_localization_method} to compare the
-extended source hypothesis to the hypothesis of two independent point
-sources. Only sources with $\tsext>\tsinc$ are considered as extended.
+Finally, when analyzing each region, we automatically removed from
+our background model other 2FGL sources which were within 0\fdg5 of
+the source of interest from the background model. This was done due
+to a concern that extended sources are included in 2FGL as multiple
+point sources. These spurious sources could distort the extension
+fit.  Instead, when a source is found to be significantly extended
+(i.e. $\tsext>16$), we perform the dual localization procedure (described
+in Section~\ref{dual_localization_method} to compare the extended source
+hypothesis to the hypothesis of two independent point sources. Only
+sources with $\tsext>\tsinc$ are considered as extended.
 
@@
 
-Based on size vs. physical distance considerations,
-we expect most extended sources to be located inside our Galaxy
-adn thus to be concentrated along the Galactic plane.  Unfortunately, the \gev emission
-in the Galactic plane is dominated by extremely structured 
-diffuse emission from the interactions of cosmic rays with the
-interstellar medium.  Finding sources on top of this emission is difficult
-\citep{first_diffuse_paper} as has been discussed in 1FGL and 2FGL
-\citep{first_cat,second_cat}.  Furthermore, the Galactic plane is crowded
-and it is often difficult to correctly model nearby sources.  Because of this,
-finding a source with $\tsext>16$ is not a sufficient
-criteria for resolving a source. For each extended source,
-we perform several analysis crosschecks.
+We expect most spatially resolvable extended sources to be located
+in our Galaxy and thus to be concentrated along the Galactic plane.
+Unfortunately, the \gev emission in the Galactic plane is dominated by
+extremely structured diffuse emission from the interactions of cosmic rays
+with the interstellar medium.  Finding sources on top of this emission
+is difficult \citep{first_diffuse_paper} as has been discussed in 1FGL
+and 2FGL \citep{first_cat,second_cat}.  Furthermore, the Galactic plane
+is crowded and it is often difficult to correctly model nearby sources.
+Because of this, finding a source with $\tsext>16$ is not a sufficient
+criteria alone for claiming a detection of source extension.  For each
+extended source, we perform several analysis crosschecks.
 
 For each candidate, we generated a map of residual \ts by adding a new
-source of spectral index 2 into the region and finding the increase in
-likelihood when fitting its flux. \ts maps are useful to look for residual
-structure in the sky model.  Figure~\ref{res_tsmaps} shows a residual \ts
-map for the extended source IC443.  The residual \ts map indicates that
-the spatially extended model for IC443 is a significantly better description
-of the observed photons.
-We also generated plots of the sum of
-all counts within a given distance of the source and compared it to the
-model predictions of a point source.  
-An example radial integral plot is shown for the extended source IC443
-in Figure~\ref{four_plots_ic443}.  For each source, we also made
-diffuse-emission-subtracted smoothed counts
-maps. Figure~\ref{four_plots_ic443} also shows an example for IC443.
+source of spectral index 2 into the region at each pixel and finding the
+increase in likelihood when fitting its flux. Residual \ts maps are useful
+to look for residual structure in the sky model.  Figure~\ref{res_tsmaps}
+shows a residual \ts map for the extended source IC443.  The residual
+\ts map indicates that the spatially extended model for IC443 is a
+significantly better description of the observed photons.  We also
+generated plots of the sum of all counts within a given distance of
+the source and compared it to the model predictions of a point source.
+An example radial integral plot is shown for the extended source
+IC443 in Figure~\ref{four_plots_ic443}.  For each source, we also made
+diffuse-emission-subtracted smoothed counts maps (show for IC443 in
+Figure~\ref{four_plots_ic443}).
 
 % 2FGL J1856.2+0450c = P72Y3047 for
-We then inspected the residual \ts, smoothed counts maps, and radial
-integral distributions to identify cases in which the extension fit
-is clearly influenced by large-scale residuals in the diffuse emission
-and hence the extension measurement unreliable.  An example of such a
-case is shown in Figure~\ref{example_bad_fit}. It shows a Galactic and
-isotropic diffuse-emission-subtracted smoothed counts map of this source
-using 1-100 \gev photons.  In this region along the Galactic plane,
-there appears to be large-scale residual in the diffuse emission. As
-a result, 2FGL\,J1856.2+0450c fit to an extension of 1\fdg83 and the
-result is statistically significant with \tsext=45.4. However, by looking at
-the residuals it is clear that this complicated region is not fit well
-even though the source's extension is statistically significant. We do
-not report sources as extended that fail this inspection.
+We then inspected each extended source candidate to identify cases in
+which the extension fit is clearly influenced by large-scale residuals in
+the diffuse emission and hence the extension measurement is unreliable.
+An example of such a case is shown in Figure~\ref{example_bad_fit}. It
+shows a Galactic and isotropic diffuse-emission-subtracted smoothed
+counts map of 2FGL\,J1856.2+0450c using 1 \gev to 100 \gev photons.
+In this region along the Galactic plane, there appears to be large-scale
+residual in the diffuse emission. As a result, 2FGL\,J1856.2+0450c is fit
+to an extension of 1\fdg83 and the result is statistically significant
+with \tsext=45.4. However, by looking at the residuals it is clear
+that this complicated region is not fit well even though the source's
+extension is statistically significant. We do not report sources that
+fail this inspection as extended.
 % information came from
@@
 
-For the remaining candidates, 
-we took the spatial and spectral model found using \pointlike and
-re-determined the spectral 
-parameters using
-\gtlike.  We used 
-the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
-ROI with a pixel size of 0\fdg03.
-We obtained a second measure of \tsext from \gtlike for the extension
-and position of the source as determined by \pointlike.
-We only considered a source to be significantly extended if $\tsext>16$ with
-both \pointlike and \gtlike.
-
-Because of the high source density in the Galactic plane, for promising
-candidates we often had to iteratively improve the model of our background
-sources to obtain a better fit of the sources.  Several catalog
-sources would often fill in the emission of the extended source and would
-have to be removed from the region.  Similarly, background sources
-were often insignificant in the fit energy range and had to be removed.
-The position of background sources would often have to be refit once the
-extended source was fit.  When the model of the extended source coupled
-strongly with nearby sources, we iteratively fit the extended source and
-all nearby sources until the fit converged.  For each extended source,
-we describe the modifications of the background model compared to the model
-used in the creation of the 2FGL catalog that were required.
+For the remaining candidates, we took the spatial and spectral model found
+using \pointlike and re-determined the spectral parameters using \gtlike.
+We used the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
+ROI with a pixel size of 0\fdg03.  We obtained a second measure of \tsext
+from \gtlike for the extension and position of the source as determined
+by \pointlike.  We only considered a source to be significantly extended
+if $\tsext>16$ with both \pointlike and \gtlike.
+
+Because of the high source density in the Galactic plane, we often had
+to iteratively improve the model of our background sources to obtain a
+better fit of the candidate source.  Several catalog sources would often
+fill in the emission of the extended source and had to be removed from
+the background model of the region.  Similarly, background sources were
+often insignificant in the fit energy range and had to be removed from
+the sky model.  The position of background sources would often have
+to be refit once the extended source was fit.  When the model of the
+extended source coupled strongly with nearby sources, we iteratively
+fit the extended source and all nearby sources until the fit converged.
+For each extended source, we describe the modifications of the background
+model compared to the model used in the creation of the 2FGL catalog
+that were required.
 
@@
 We estimate a systematic error on the extension of a source due to
-uncertainty in our knowledge of the LAT PSF.  Before
-launch, the LAT PSF was determined by a detector simulation which was
-verified in accelerator tests \citep{atwood_LAT_mission}. However,
-in-flight data revealed a discrepancy
-above a few \gev in the PSF compared to the
-photon angular distribution of bright AGN.  A publication on this issue is in preparation
-\citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit empirically to
-bright AGN and this empirical parameterization is the default PSF used
-in the P7\_V6 IRFs.  To account for this uncertainty in our knowledge of
-the PSF, we refit our extended source candidates using the Monte Carlo
-representation of the PSF and consider the difference in extension found
-using the two PSFs as a systematic error on the extension of a source.
-The same approach was used in
-\citep{ic443}.  At high energies, we believe that our parameterization
-of the PSF from bright AGN is substantially better than the Monte Carlo
-representation of the PSF so this estimate of systematic errors is conservative.
+uncertainty in our knowledge of the LAT PSF.  Before launch, the LAT
+PSF was determined by detector simulations which were verified in
+accelerator tests \citep{atwood_LAT_mission}. However, in-flight data
+revealed a discrepancy above a few \gev in the PSF compared to the 
+angular distribution of photons from bright AGN.  A publication on this issue is in
+preparation \citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit
+empirically to bright AGN and this empirical parameterization is the
+default PSF used in the P7\_V6 IRFs.  To account for this uncertainty in
+our knowledge of the PSF, we refit our extended source candidates using
+the pre-flight Monte Carlo representation of the PSF and consider the difference
+in extension found using the two PSFs as a systematic error on the
+extension of a source.  The same approach was used in \citep{ic443}.
+At high energies, we believe that our parameterization of the PSF from
+bright AGN is substantially better than the Monte Carlo representation
+of the PSF so this estimate of systematic errors is conservative.
 
@@
 due to uncertainty in the model of the Galactic diffuse emission by
-using an alternative diffuse model. An alternative model was based upon
-GALPROP\footnote{GALPROP is a software package for calculating the
+using an alternative diffuse model. An alternative model was based
+upon GALPROP\footnote{GALPROP is a software package for calculating the
 Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
-in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
-references} and used in the LAT analysis of the isotropic diffuse
-emission \citep{isotropic_lat}.  
-The intensities of various components to the galactic
-diffuse emission are then fitted individually using a spatial
-distribution of the intensities within the ROI 
-as predicted by the model.
-We distinguish contributions from CR interactions with
-the molecular hydrogen, the atomic+ionized hydrogen,
-residual gas traced by dust \citep{isabelle_dark_gass},
-and the interstellar radiation field. We further
-split the contributions from interactions with molecular
-and atomic hydrogen to the
-Galactic diffuse emission according
-to the distance from the Galactic center in
-which they are produced. Hence, we replace
-the standard diffuse emission model by 18
-individually fitted templates to describe individual
-components of the diffuse emission.
-A similar crosscheck was used in the
-LAT Collaboration's analysis of RX J1713.7-3946 \citep{rx_j1713_lat}.
+in the Galaxy. See \url{http://galprop.stanford.edu/} for details
+and references} and used in the LAT analysis of the isotropic diffuse
+emission \citep{isotropic_lat}.  The intensities of various components
+to the galactic diffuse emission were then fitted individually using a
+spatial distribution of the intensities within the ROI as predicted by
+the model.  We distinguish contributions from CR interactions with the
+molecular hydrogen, the atomic+ionized hydrogen, residual gas traced
+by dust \citep{isabelle_dark_gass}, and the interstellar radiation
+field. We further split the contributions from interactions with molecular
+and atomic hydrogen to the Galactic diffuse emission according to the
+distance from the Galactic center in which they are produced. Hence, we
+replace the standard diffuse emission model by 18 individually fitted
+templates to describe individual components of the diffuse emission.
+A similar crosscheck was used in the LAT Collaboration's analysis of 
+RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
 
 It is not expected that this diffuse model is superior to the standard
-LAT model that was obtained through an all-sky fit.  But adding degrees of freedom to the background model can
+LAT model obtained through an all-sky fit.  However, adding degrees of freedom to the background model can
 remove likely spurious sources that correlate with features in the
@@
 \citep{second_cat}.
-The six extended SNRs IC443, W28, W30, W44, W51C, and the
-Cygnus Loop were included in 2FGL.  IC443, W28, W44, W51C, and the
-Cygnus Loop were
-first reported in \cite{ic443,w28,w44,w51c,cygnus_loop_lat}.  A
+Six extended SNRs were included in 2FGL: IC443, W28, W30, W44, W51C, and the
+Cygnus Loop \citep{ic443,w28,w44,w51c,cygnus_loop_lat}.\footnote{A
 detailed publication by the LAT
-Collaboration about W30 is still in preparation.
+Collaboration about W30 is still in preparation.}
 \gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
-Using 1-100 \gev photons, our analysis significantly detected the
+Using 1 \gev to 100 \gev photons, our analysis significantly detected the
 extension of all six SNRs.
@@
 Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
-detected using 1-100 \gev photons. Our
+detected using 1 \gev to 100 \gev photons. Our
 fit extension is comparable to the published result, but we note that
@@
 % 3 PWN
-Three PWNe Vela X, MSH 15-52, and HESS\,J1825-137 were
-already identified in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  
-HESS\,J1825-137 was significantly detected using 10-100 \gev photons.
-To improve the model of this source, we removed the
-nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
-source.  To avoid confusion with the nearby bright pulsar PSR J1509-5850, MSH 15-52 must be
+Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137 were
+identified in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  
+HESS\,J1825$-$137 was significantly detected using 10 \gev to 100 \gev photons.
+To improve the model of this source, we removed from our background model the
+nearby catalog source 2FGL\,J1823.1$-$1338c which is part of the extended
+source.  To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 must be
 analyzed at high energies.  Using photons with energies above 10 \gev,
-we fit the extension of MSH 15-52 to be consistent with the published
+we fit the extension of MSH\,15$-$52 to be consistent with the published
 size with an extension significance of \tsext=6.5.
@@
 includes the best fit spectral parameters for each source.  The position
-and extension of Vela X and the Centaurus A Lobes are included in this
-list for completeness.
+and extension of Vela X and the Centaurus A Lobes are taken from
+\cite{velax,cen_a_lat} and are included in this list for completeness.
 
@@
 
-\subsection{2FGL\,J0823.0-4246}
+\subsection{2FGL\,J0823.0$-$4246}
 \label{section_2FGL_J0823.0-4246}
@@
 
-The source 2FGL\,J0823.0-4246 was found 
+The source 2FGL\,J0823.0$-$4246 was found 
 using 1-100 \gev photons to have an 
@@
 This source is coincident with the one-year
-catalog source 1FGL\,J0823.3-4248.
+catalog source 1FGL\,J0823.3$-$4248.
 \hl{
@@
 
-To get a good fit of the source, we had to remove the nearby catalog
-sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which are part of the
+To get a good fit of the source, we had to remove from our background
+model the nearby catalog
+sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which are part of the
 extended source.  We tested the source for source confusion by fitting
@@
 
-\subsection{2FGL\,J1627.0-2425c}
+\subsection{2FGL\,J1627.0$-$2425c}
 \label{section_2FGL_J1627.0-2425c}
@@
 
-The source 2FGL\,J1627.0-2425c was found using 1-100 \gev photons to
+The source 2FGL\,J1627.0$-$2425c was found using 1-100 \gev photons to
 have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
@@
 $(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
-year catalog source 1FGL\,J1628.6-2419c.  A counts map showing this source
+year catalog source 1FGL\,J1628.6$-$2419c.  A counts map showing this source
 is seen in Figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
@@
 
-\subsection{2FGL\,J1712.4-3941}
+\subsection{2FGL\,J1712.4$-$3941}
 \label{section_2FGL_J1712.4-3941}
@@
 
-The source 2FGL\,J1712.4-3941 was found using 1-100 \gev
+The source 2FGL\,J1712.4$-$3941 was found using 1-100 \gev
 photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
@@
 fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  The source
-is coincident with the one-year catalog source 1FGL\,J1711.7-3944c.
+is coincident with the one-year catalog source 1FGL\,J1711.7$-$3944c.
 Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.
 
-This source is spatially coincident with the SNR RX J1713.7-3946
+This source is spatially coincident with the SNR RX\,J1713.7$-$3946
 and was recently reported by \citep{rx_j1713_lat}.  
-Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR RX
-J1713.7-3946 from \citep{rx_j1713_hess}.  To analyze this source,
+Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR 
+RX\,J1713.7$-$3946 from \citep{rx_j1713_hess}.  To analyze this source,
 we used the same background model as the recent LAT publication.
-2FGL\,J1715.4-4024c is spatially coincident with Source A and was
+2FGL\,J1715.4$-$4024c is spatially coincident with Source A and was
 moved to $(\text{RA},\text{Dec})=(258.84,-40.46)$. Source B was added
@@
 
-\subsection{2FGL\,J0851.7-4635}
+\subsection{2FGL\,J0851.7$-$4635}
 \label{section_2FGL_J0851.7-4635}
@@
 
-The source 2FGL\,J0851.7-4635 was found 
+The source 2FGL\,J0851.7$-$4635 was found 
 using 10-100 \gev photons to have an
@@
 
-2FGL\,J0851.7-4635 is spatially coincident with the SNR Vela Jr.
+2FGL\,J0851.7$-$4635 is spatially coincident with the SNR Vela Jr.
 Overlaid on Figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
@@
 
-To get a good fit of the source, we had to remove thee nearby catalog
-sources 2FGL\,J0853.5-4711, 2FGL\,J0848.5-4535, and 2FGL\,J0855.4-4625
+To get a good fit of the source, we had to remove from
+our background model the nearby catalog
+sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
 which are part of the extended source.  In addition, we relocalized
-the position of the nearby catalog source 2FGL\,J0854.7-4501 to
+the position of the nearby catalog source 2FGL\,J0854.7$-$4501 to
 $(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
-in the presence of of the extended source.  In addition, we removed the
-further away catalog sources 2FGL\,J0858.0-4815 and 2FGL\,J0901.7-4655
+in the presence of of the extended source.  In addition, we removed from
+our model the
+further away catalog sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
 because they were not significant above 10 \gev.  After modifying
@@
 
-\subsection{2FGL\,J1615.0-5051}
+\subsection{2FGL\,J1615.0$-$5051}
 \label{section_2FGL_J1615.0-5051}
@@
 
-The source 2FGL\,J1615.0-5051 was found using 10-100 \tev
+The source 2FGL\,J1615.0$-$5051 was found using 10-100 \tev
 photons to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
@@
 This source is coincident with the one-year catalog source
-1FGL\,J1613.6-5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
+1FGL\,J1613.6$-$5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
 of this source.
 
-This source is less than $1\deg$ away from 2FGL\,J1615.2-5138 which is
+This source is less than $1\deg$ away from 2FGL\,J1615.2$-$5138 which is
 also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
@@
 of each source until obtaining a global best fit.  Before doing this,
-We removed from our model the source 2FGL\,J1614.9-5212 because it is
-part of 2FGL\,J1615.2-5138's. Furthermore, we removed the nearby catalog
-sources 2FGL\,J1619.7-5040c and 2FGL\,J1620.6-5111c because they were not
+We removed from our background model the source 2FGL\,J1614.9$-$5212 because it is
+part of 2FGL\,J1615.2$-$5138's. Furthermore, we removed from our model the nearby catalog
+sources 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
 significant above 10 \gev.  These modifications are further described
@@
 
-2FGL\,J1615.2-5138 is spatially coincident with the extended
-\tev source HESS\,J1616-508 \citep{hess_plane_survey}.  In
-Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
-on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured an
+2FGL\,J1615.2$-$5138 is spatially coincident with the extended
+\tev source HESS\,J1616$-$508 \citep{hess_plane_survey}.  In
+Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616$-$508 are overlaid
+on 2FGL\,J1615.0$-$5051.  The H.E.S.S. experiment measured an
 extension $0.136\pm 0.008$ when fitting the source with an elliptical
@@
 size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
-Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
-connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.
+Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0$-$5051
+connects smoothly to the H.E.S.S spectrum of HESS\,J1616$-$508.
 
 \hl{
-HESS\,J1616-508 is located in the region of two SNRs, RCW103
+HESS\,J1616$-$508 is located in the region of two SNRs, RCW103
 (G332.4-04) and Kes~32 (G332.4+0.1) but is not spatially coincident
-with either of them \citep{hess_plane_survey}.  HESS\,J1616-508 is near
-three pulsars PSR J1614-5048, PSR J1616-5109, and PSR J1617-5055
-but only PSR J1617-5055 is energetically favored as being the \tev
+with either of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near
+three pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055
+but only PSR\,J1617$-$5055 is energetically favored as being the \tev
 emitter \citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.
 \cite{hess_plane_survey} speculated that a PWN powered by this young
-pulsar could be responsible for the emission of HESS\,J1616-508.
-Because HESS\,J1616-508 is $9\arcmin$ away from PSR J1617-5055, this would
+pulsar could be responsible for the emission of HESS\,J1616$-$508.
+Because HESS\,J1616$-$508 is $9\arcmin$ away from PSR\,J1617$-$5055, this would
 require an assymetric X-ray PWNe to power the \tev emission. However,
@@
 Finally, \cite{discovery_of_pwn_for_PSR_J1617-5055} found diffuse
-emission towards the center of HESS\,J1616-508 using archival radio and
+emission towards the center of HESS\,J1616$-$508 using archival radio and
 infared observations.  Deeper observations will likely be necessary to
@@
 
-\subsection{2FGL\,J1615.2-5138}
+\subsection{2FGL\,J1615.2$-$5138}
 \label{section_2FGL_J1615.2-5138}
 
-The source 2FGL\,J1615.2-5138 was found using 10-100 \gev
+The source 2FGL\,J1615.2$-$5138 was found using 10-100 \gev
 photons to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
@@
 position of $(l,b)=(331\fdg66,-0\fdg66)$.  This source is coincident
-with the one-year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
-J1615.2-5138 is close to 2FGL\,J1615.0-5051, the same model described
+with the one-year catalog source 1FGL\,J1614.7$-$5138c.  Because 2FGL
+J1615.2$-$5138 is close to 2FGL\,J1615.0$-$5051, the same model described
 in Section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
 sources. Both sources can be seen in Figure~\ref{1FGL_J1613.6-5100c}.
-For 2FGL\,J1615.2-5138, \tsinc=37.0 which is less than \tsext so we
+For 2FGL\,J1615.2$-$5138, \tsinc=37.0 which is less than \tsext so we
 conclude that the source is extended.
@@
 This source is spatially coincident with the extended
-\tev source HESS\,J1614-518 \citep{hess_plane_survey}. In
-Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614-518 are overlaid
-on 2FGL\,J1615.2-5138.  The H.E.S.S. experiment measured a 2D Gaussian
+\tev source HESS\,J1614$-$518 \citep{hess_plane_survey}. In
+Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614$-$518 are overlaid
+on 2FGL\,J1615.2$-$5138.  The H.E.S.S. experiment measured a 2D Gaussian
 extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0.15\pm0.02$
@@
 $\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds} shows
-that the LAT spectrum of 2FGL\,J1615.2-5138 connects smoothly to
-the H.E.S.S spectrum of HESS\,J1614-518.  Further data collected by
+that the LAT spectrum of 2FGL\,J1615.2$-$5138 connects smoothly to
+the H.E.S.S spectrum of HESS\,J1614$-$518.  Further data collected by
 H.E.S.S. in 2007 helped to resolve a double peaked structure in the
@@
 provide the required energy output required to power the $\tev$ 
-emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614-518
+emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614$-$518
 is spatially coincident with a young open cluster Pismis 22
@@
 promising X-ray candidates. Source A is an extended source consistent
-with the peak of HESS\,J1614-518 and source B coincident with Pismis 22
-and towards the center but in a relatively dim region of HESS\,J1614-518
+with the peak of HESS\,J1614$-$518 and source B coincident with Pismis 22
+and towards the center but in a relatively dim region of HESS\,J1614$-$518
 \citep{suazku_hess_j1614_518}.  Three hypothesis have been presented to
@@
 
-\subsection{2FGL\,J1632.4-4753c}
+\subsection{2FGL\,J1632.4$-$4753c}
 \label{section_2FGL_J1632.4-4753c}
@@
 
-The source 2FGL\,J1632.4-4753c was found 
+The source 2FGL\,J1632.4$-$4753c was found 
 using 10-100 \gev photons to
@@
 $(l,b)=(336\fdg41,0\fdg22)$.  This source is coincident with the one
-year catalog source 1FGL\,J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
+year catalog source 1FGL\,J1632.9$-$4802c.  Figure~\ref{1FGL_J1632.9-4802c}
 shows a counts map of this source.
 
-To get a good fit of the source, we had to remove from our model
-three catalog sources 2FGL\,J1631.7-4720c, 2FGL\,J1630.2-4752,
-2FGL J1634.4-4743c.4-4820c that were part of the extended source..
-We then iteratively relocalized the source 2FGL\,J1635.4-4717c
-to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3-4740c to
+To get a good fit of the source, we had to remove from our background model
+three catalog sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
+2FGL J1634.4$-$4743c.4-4820c that were part of the extended source..
+We then iteratively relocalized the source 2FGL\,J1635.4$-$4717c
+to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3$-$4740c to
 $(l,b)=(336\fdg97,-0\fdg07)$ while fitting the extension of
-2FGL\,J1632.4-4753c.  In addition we removed from our model four
-farther away two-year catalog sources 2FGL\,J1638.0-4703c, 2FGL
-J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL\,J1639.8-4921c because they
+2FGL\,J1632.4$-$4753c.  In addition we removed from our model four
+farther away two-year catalog sources 2FGL\,J1638.0$-$4703c, 
+2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
 were not significant above 10 \gev.  These modifications are shown
@@
 This extended source is spatially coincident with the extended
-\tev source HESS\,J1632-478 \citep{hess_plane_survey}.
-In Figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478
-are overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a 
+\tev source HESS\,J1632$-$478 \citep{hess_plane_survey}.
+In Figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632$-$478
+are overlaid on 2FGL\,J1635.4$-$4717c.  H.E.S.S measured a 
 extension of $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the
@@
 the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
-shows that the LAT spectrum of 2FGL\,J1635.4-4717c connects smoothly to
-the H.E.S.S spectrum of HESS\,J1632-478.
+shows that the LAT spectrum of 2FGL\,J1635.4$-$4717c connects smoothly to
+the H.E.S.S spectrum of HESS\,J1632$-$478.
 
 \hl{
-\cite{hess_plane_survey} argued that HESS\,J1632-478
+\cite{hess_plane_survey} argued that HESS\,J1632$-$478
 is positionally coincident with the hard X-ray source
@@
 to the X-ray size has previously been observed in several aging PWNe
-including HESS\,J1825-137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
-HESS\,J1640-465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
+including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
+HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
 and Vela X \citep{vela_x_rosat,vela_x_hess}.  This can be explained by
@@
 
-\subsection{2FGL\,J1837.3-0700c}
+\subsection{2FGL\,J1837.3$-$0700c}
 \label{section_2FGL_J1837.3-0700c}
@@
 
-The source 2FGL\,J1837.3-0700c was found with 10-100 \gev photons to
+The source 2FGL\,J1837.3$-$0700c was found with 10-100 \gev photons to
 have an extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an
@@
 of $(l,b)=(25\fdg08,0\fdg13)$.  This source is coincident with the one
-year catalog source 1FGL\,J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
+year catalog source 1FGL\,J1837.5$-$0659c.  Figure~\ref{1FGL_J1837.5-0659c}
 shows a counts map of this source.
@@
 This source is in a complicated region. There are three nearby
-catalog sources 2FGL\,J1834.7-0705c, 2FGL\,J1836.8-0623c, and
-2FGL\,J1839.3-0558c.  To get a good fit of 2FGL\,J1837.3-0700c, we
-relocalized 2FGL\,J1834.7-0705c to $(l,b)=(24\fdg77,0\fdg50)$,
-2FGL\,J1836.8-0623c to $(l,b)=(25\fdg57,0\fdg32)$, and
-2FGL\,J1839.3-0558c to $(l,b)=(26\fdg08,0\fdg23)$.  We removed the
-nearby catalog source 2FGL\,J1835.5-0649 which is part of the extended
-source and also the farther away catalog source 2FGL\,J1839.0-0539
+catalog sources 2FGL\,J1834.7$-$0705c, 2FGL\,J1836.8$-$0623c, and
+2FGL\,J1839.3$-$0558c.  To get a good fit of 2FGL\,J1837.3$-$0700c, we
+relocalized 2FGL\,J1834.7$-$0705c to $(l,b)=(24\fdg77,0\fdg50)$,
+2FGL\,J1836.8$-$0623c to $(l,b)=(25\fdg57,0\fdg32)$, and
+2FGL\,J1839.3$-$0558c to $(l,b)=(26\fdg08,0\fdg23)$.  We removed from
+our background model the
+nearby catalog source 2FGL\,J1835.5$-$0649 which is part of the extended
+source and also the farther away catalog source 2FGL\,J1839.0$-$0539
 because it was not significant above 10 \gev. These modifications are
@@
 
-This source is spatially coincident with the \tev source HESS\,J1837-069
+This source is spatially coincident with the \tev source HESS\,J1837$-$069
 \citep{hess_plane_survey}.  In Figure~\ref{1FGL_J1837.5-0659c}, contours
-of HESS\,J1837-069 are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured
+of HESS\,J1837$-$069 are overlaid on 2FGL\,J1837.3$-$0700c. H.E.S.S. measured
 an extension of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$
@@
 (less than 2 sigma).  Figure~\ref{hess_seds} shows that the LAT spectrum
-connects smoothly to the H.E.S.S spectrum of HESS\,J1837-069.
+connects smoothly to the H.E.S.S spectrum of HESS\,J1837$-$069.
 
 \hl{
-HESS\,J1837-069 is coincident
-with the hard and steady X-ray source AX J1838.0-0655
+HESS\,J1837$-$069 is coincident
+with the hard and steady X-ray source AX\,J1838.0$-$0655
 \citep{einstein_galactic_plane_survey,hard_x-ray_asca,integral_AX_J1838.0-0655,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
 This source was discovery by RXTE to be a pulsar sufficiently
-luminous to power the \tev emission.  AX J1838.0-0655 was spatially
+luminous to power the \tev emission.  AX\,J1838.0$-$0655 was spatially
 resolved by \chandra to be a bright point source surrounded by
@@
 $\gamma$-ray emission may be powered by this pulsar.  A second
-X-ray point source AX J1837.3-0652 is in the region of HESS\,J1837-069
+X-ray point source AX\,J1837.3$-$0652 is in the region of HESS\,J1837$-$069
 \citep{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
@@
 although no pulsations have yet been detected from it
-\citep{pulsations_HESS_J1837-069}.  If AX J1838.0-0655 is a pulsar/PWN
-powering HESS\,J1837-069, some of the \tev emission may also come from
-AX J1837.3-0652.
+\citep{pulsations_HESS_J1837-069}.  If AX\,J1838.0$-$0655 is a pulsar/PWN
+powering HESS\,J1837$-$069, some of the \tev emission may also come from
+AX\,J1837.3$-$0652.
 }
@@
 
-To get a good fit of the source, we had to remove the nearby catalog
+To get a good fit of the source, we had to remove from our background
+model the nearby catalog
 source 2FGL\,J2019.1+4040 which were part of the extended source.
@@
 background model appeared visually to significantly throw off the fit
-of the region.  In addition, we removed the four further away catalog
+of the region.  In addition, we removed from our model the four further away catalog
 sources 2FGL\,J2022.8+3843c, 2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c,
@@
 was detected to be pulsed 
-(PSR J2021+4026,\cite{first_lat_pulsar_cat}).
+(PSR\,J2021+4026,\cite{first_lat_pulsar_cat}).
 
@@
 in $\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10-100
-\gev photons to avoid PSR J2021+4026, we resolve an
+\gev photons to avoid PSR\,J2021+4026, we resolve an
 extended source whose inferred \gev size well matches the radio size of
@@
 2FGL reported on the detection of twelve sources
-prviously known as extended. Using
+previously known as extended. Using
 two years of LAT data and a new analysis method, we present on 
@@
 extended sources.  The LAT energy spectrum connects smoothly to \tev.
-This is also true of HESS\,J1825-137 \citep{fermi_hess_j1825} and RX
-J1713.7-3946 \citep{rx_j1713_lat}.
+This is also true of HESS\,J1825$-$137 \citep{fermi_hess_j1825} and 
+RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
 
@@
 so, the size of PWNe are expected to vary across the \gev and \tev energy
-range and the size of HESS\,J1825-137 was seen by H.E.S.S. to vary
+range and the size of HESS\,J1825$-$137 was seen by H.E.S.S. to vary
 between 200 \gev and 20 \tev \citep{energy_dependent_hess_j1825}.
-HESS\,J1825-137 is significantly larger in \gev than \tev
+HESS\,J1825$-$137 is significantly larger in \gev than \tev
 \citep{fermi_hess_j1825}.  It is interesting to compare the \gev and
@@
     closer to 2.5 The circle in plot (d) below the sensitivity line is
-    MSH 15-52 which was found by our analysis to have $\tsext=6.5$.
+    MSH\,15$-$52 which was found by our analysis to have $\tsext=6.5$.
     }\label{all_sensitivity} 
@@
 \cutinhead{E$>$10 \gev}
-MSH 15-52            &     320.38 &      -1.22 & $  0.20 \pm   0.04 \pm   0.03 $ &       76.2 &        6.5 &   0.03 & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
-HESS J1825-137       &      17.56 &      -0.46 & $  0.65 \pm   0.03 \pm   0.01 $ &       83.6 &       55.9 &   0.05 & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
+MSH\,15$-$52         &     320.38 &      -1.22 & $  0.20 \pm   0.04 \pm   0.03 $ &       76.2 &        6.5 &   0.03 & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
+HESS\,J1825$-$137    &      17.56 &      -0.46 & $  0.65 \pm   0.03 \pm   0.01 $ &       83.6 &       55.9 &   0.05 & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
 \enddata
@@
     \caption{The cumulative density of \tsext for 783 of the clean
-    AGN in 2LAC which are significant above 1 \gev calculted with \pointlike (the dashed line
+    AGN in 2LAC which are significant above 1 \gev calculated with \pointlike (the dashed line
     colored blue in the electronic version)
@@
 \hline
-2FGL\,J0823.0-4246   &     260.32 &      -3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      320.9 &       46.3 &   0.02 & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
-2FGL\,J1627.0-2425c  &     353.08 &      16.78 & $  0.41 \pm   0.05 \pm   0.02 $ &      144.5 &       31.1 &   0.04 & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
-2FGL\,J1712.4-3941   &     347.25 &      -0.54 & $  0.56 \pm   0.04 \pm   0.01 $ &       75.0 &       39.6 &   0.05 & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
+2FGL\,J0823.0$-$4246   &     260.32 &      -3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      320.9 &       46.3 &   0.02 & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
+2FGL\,J1627.0$-$2425c  &     353.08 &      16.78 & $  0.41 \pm   0.05 \pm   0.02 $ &      144.5 &       31.1 &   0.04 & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
+2FGL\,J1712.4$-$3941   &     347.25 &      -0.54 & $  0.56 \pm   0.04 \pm   0.01 $ &       75.0 &       39.6 &   0.05 & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7$-$3946 \\
 \cutinhead{E$>$10 \gev}
-2FGL\,J0851.7-4635   &     266.29 &      -1.43 & $  1.13 \pm   0.08 \pm   0.05 $ &      116.1 &       87.2 &   0.07 & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr. \\
-2FGL\,J1615.0-5051   &     332.38 &      -0.14 & $  0.33 \pm   0.04 \pm   0.01 $ &       53.4 &       16.3 &   0.04 & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
-2FGL\,J1615.2-5138   &     331.66 &      -0.66 & $  0.42 \pm   0.03 \pm   0.01 $ &       76.6 &       48.0 &   0.05 & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
-2FGL\,J1632.4-4753c  &     336.41 &       0.22 & $  0.44 \pm   0.04 \pm   0.03 $ &      127.8 &       64.5 &   0.04 & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
-2FGL\,J1837.3-0700c  &      25.08 &       0.13 & $  0.35 \pm   0.08 \pm   0.03 $ &       46.2 &       18.8 &   0.07 & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
+2FGL\,J0851.7$-$4635   &     266.29 &      -1.43 & $  1.13 \pm   0.08 \pm   0.05 $ &      116.1 &       87.2 &   0.07 & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr. \\
+2FGL\,J1615.0$-$5051   &     332.38 &      -0.14 & $  0.33 \pm   0.04 \pm   0.01 $ &       53.4 &       16.3 &   0.04 & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616$-$508 \\
+2FGL\,J1615.2$-$5138   &     331.66 &      -0.66 & $  0.42 \pm   0.03 \pm   0.01 $ &       76.6 &       48.0 &   0.05 & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614$-$518 \\
+2FGL\,J1632.4$-$4753c  &     336.41 &       0.22 & $  0.44 \pm   0.04 \pm   0.03 $ &      127.8 &       64.5 &   0.04 & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632$-$478 \\
+2FGL\,J1837.3$-$0700c  &      25.08 &       0.13 & $  0.35 \pm   0.08 \pm   0.03 $ &       46.2 &       18.8 &   0.07 & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837$-$069 \\
 2FGL\,J2021.5+4026     &      78.18 &       2.19 & $  0.59 \pm   0.03 \pm   0.02 $ &      222.2 &      116.4 &   0.04 & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &       $\gamma$-Cygni \\
@@
   \hline
-  2FGL\,J0823.0-4246   &                350.9 &                320.9 &                352.5 &                 66.0 &                 46.3 &                 53.6 &                 0.37 &                 0.39 &                 0.38 &                 22.1 \\
-  2FGL\,J1627.0-2425c  &                170.2 &                144.5 &                112.6 &                 43.9 &                 31.1 &                 23.9 &                 0.41 &                 0.40 &                 0.39 &                 20.0 \\
-  2FGL\,J1712.4-3941   &                 80.9 &                 75.0 &                 43.4 &                 47.4 &                 39.6 &                 22.2 &                 0.56 &                 0.56 &                 0.54 &                  6.4 \\
+  2FGL\,J0823.0$-$4246   &                350.9 &                320.9 &                352.5 &                 66.0 &                 46.3 &                 53.6 &                 0.37 &                 0.39 &                 0.38 &                 22.1 \\
+  2FGL\,J1627.0$-$2425c  &                170.2 &                144.5 &                112.6 &                 43.9 &                 31.1 &                 23.9 &                 0.41 &                 0.40 &                 0.39 &                 20.0 \\
+  2FGL\,J1712.4$-$3941   &                 80.9 &                 75.0 &                 43.4 &                 47.4 &                 39.6 &                 22.2 &                 0.56 &                 0.56 &                 0.54 &                  6.4 \\
   \cutinhead{E$>$10 \gev}
-  2FGL\,J0851.7-4635   &                116.7 &                116.1 &                122.3 &                 87.1 &                 87.2 &                 90.4 &                 1.13 &                 1.16 &                 1.17 &                 16.1 \\
-  2FGL\,J1615.0-5051   &                 52.4 &                 53.4 &                 55.6 &                 17.5 &                 16.3 &                 17.4 &                 0.33 &                 0.32 &                 0.32 &                 11.9 \\
-  2FGL\,J1615.2-5138   &                 76.3 &                 76.6 &                 86.3 &                 44.0 &                 48.0 &                 52.6 &                 0.42 &                 0.43 &                 0.43 &                 37.0 \\
-  2FGL\,J1632.4-4753c  &                126.6 &                127.8 &                120.7 &                 63.9 &                 64.5 &                 64.1 &                 0.44 &                 0.44 &                 0.47 &                 40.6 \\
-  2FGL\,J1837.3-0700c  &                 45.4 &                 46.2 &                 39.0 &                 18.5 &                 18.8 &                 16.6 &                 0.35 &                 0.34 &                 0.38 &                 12.6 \\
+  2FGL\,J0851.7$-$4635   &                116.7 &                116.1 &                122.3 &                 87.1 &                 87.2 &                 90.4 &                 1.13 &                 1.16 &                 1.17 &                 16.1 \\
+  2FGL\,J1615.0$-$5051   &                 52.4 &                 53.4 &                 55.6 &                 17.5 &                 16.3 &                 17.4 &                 0.33 &                 0.32 &                 0.32 &                 11.9 \\
+  2FGL\,J1615.2$-$5138   &                 76.3 &                 76.6 &                 86.3 &                 44.0 &                 48.0 &                 52.6 &                 0.42 &                 0.43 &                 0.43 &                 37.0 \\
+  2FGL\,J1632.4$-$4753c  &                126.6 &                127.8 &                120.7 &                 63.9 &                 64.5 &                 64.1 &                 0.44 &                 0.44 &                 0.47 &                 40.6 \\
+  2FGL\,J1837.3$-$0700c  &                 45.4 &                 46.2 &                 39.0 &                 18.5 &                 18.8 &                 16.6 &                 0.35 &                 0.34 &                 0.38 &                 12.6 \\
   2FGL\,J2021.5+4026     &                234.3 &                222.2 &                235.6 &                135.9 &                116.4 &                121.4 &                 0.59 &                 0.60 &                 0.60 &                 24.3 \\
@@
   \caption{A diffuse-emission-subtracted 1 \gev to 100
-  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
+  \gev counts map of the region around 2FGL\,J0823.0$-$4246 smoothed
   by a 0\fdg1 2D Gaussian kernel.  
@@
   surface brightness.  The two stars (colored green) are the positions of the
-  sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which were removed
+  sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which were removed
+  from out background model
   because they are part of the extended source.  The lower right inset
   is the model predicted emission from a point source with the same
-  spectrum as 2FGL\,J0823.4-4305 smoothed by the same kernel.
+  spectrum as 2FGL\,J0823.4$-$4305 smoothed by the same kernel.
   This source is spatially coincident with the Puppis A SNR. The
@@
   A diffuse-emission-subtracted 1-100 \gev counts map of (a) the region
-  around 2FGL\,J1627.0-2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
-  also the emission from the background source 2FGL\,J1625.7-2526
+  around 2FGL\,J1627.0$-$2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
+  also the emission from the background source 2FGL\,J1625.7$-$2526
   subtracted.  The red star is the 2FGL position of this source.
@@
   \caption{A diffuse-emission-subtracted 1-100 \gev
-  counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
+  counts map of (a) the region around 2FGL\,J1712.4$-$3941 smoothed by
   a 0\fdg25 2D Gaussian kernel and (b) also the emission 
@@
   This source is spatially
-  coincident with RX J1713.7-3946 was was recently reported by
+  coincident with RX\,J1713.7$-$3946 was was recently reported by
   \citep{rx_j1713_lat}.  The light blue contours correspond to the \tev image
@@
   with the same background model as \citep{rx_j1713_lat}.  Source A (blue
-  cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
+  cross) is spatially coincident with 2FGL\,J1715.4$-$4024c (blue star).
   The gray crosses represent from left to right the position of source B
@@
   \caption{A diffuse-emission-subtracted 10-100
-  \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
+  \gev counts map of the region around 2FGL\,J0851.7$-$4635 smoothed
   by a 0\fdg25 2D Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
@@
   symmetric uniform surface brightness.  The inner three green stars
-  are (from left to right) 2FGL\,J0853.5-4711, 2FGL\,J0855.4-4625,
-  and 2FGL\,J0848.5-4535 which were removed because they are part of
+  are (from left to right) 2FGL\,J0853.5$-$4711, 2FGL\,J0855.4$-$4625,
+  and 2FGL\,J0848.5$-$4535 which were removed from our background model
+  because they are part of
   the extended source.  The farther away green stars are (from left to
-  right) 2FGL\,J0901.7-4655 and 2FGL\,J0858.0-4815 which were removed
+  right) 2FGL\,J0901.7$-$4655 and 2FGL\,J0858.0$-$4815 which were removed
+  from our model
   because they were not significant above 10 \gev.  The blue cross
-  is the relocalized position of 2FGL\,J0854.7-4501.  This extended
+  is the relocalized position of 2FGL\,J0854.7$-$4501.  This extended
   source is spatially coincident with the Vela Jr SNR.  The light
@@
     A diffuse-emission-subtracted 10-100
-    \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
-    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0\fdg1
+    \gev counts map of the region around 2FGL\,J1615.0$-$5051 (upper
+    left) and 2FGL\,J1615.2$-$5138 (lower right) smoothed by a 0\fdg1
     2D Gaussian kernel.  The red stars are the catalog positions of these
@@
     symmetric uniform surface brightness.
-    The green star inside the extension of 2FGL\,J1615.2-5138  is
-    2FGL\,J1614.9-5212 which was removed because it is part of the
-    extended source.  The green stars to the left are 2FGL\,J1619.7-5040c
-    and 2FGL\,J1620.6-5111c which were removed because they were
+    The green star inside the extension of 2FGL\,J1615.2$-$5138  is
+    2FGL\,J1614.9$-$5212 which was removed from our background model
+  because it is part of the
+    extended source.  The green stars to the left are 2FGL\,J1619.7$-$5040c
+    and 2FGL\,J1620.6$-$5111c which were removed from our model because they were
     not significant above 10\gev. These are shown as green stars.
@@
     of the extended sources
-    HESS\,J1616-508 (left) and the extended source HESS\,J1614-518
+    HESS\,J1616$-$508 (left) and the extended source HESS\,J1614$-$518
     (right)
@@
     \citep{hess_plane_survey}
-    2FGL\,J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
-    2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
+    2FGL\,J1615.0$-$5051 is spatially consistent with HESS\,J1616$-$508 and
+    2FGL\,J1615.2$-$5138 is spatially consistent with HESS\,J1614$-$518.
   }\label{1FGL_J1613.6-5100c}
@@
   \caption{A diffuse-emission-subtracted 10-100
-  \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
+  \gev counts map of the region around 2FGL\,J1632.4$-$4753c smoothed by
   a 0\fdg1 2D Gaussian kernel.  This source is in a crowded region.
   The red star is the 2FGL position of this source.  The red
-  cross and circle are the best fit position and extension 2FGL\,J1632.4-4753c 
+  cross and circle are the best fit position and extension 2FGL\,J1632.4$-$4753c 
   assuming a radially
@@
   The three
-  green crosses inside the extension are 2FGL
-  J1631.7-4720c, 2FGL\,J1630.2-4752, and 2FGL\,J1634.4-4743c.4-4820c
-  which were removed because they are part
+  green crosses inside the extension are 2FGL\,J1631.7$-$4720c, 
+  2FGL\,J1630.2$-$4752, and 2FGL\,J1634.4$-$4743c.4-4820c
+  which were removed from our background model because they are part
   of the extended source.  The blue stars and crosses are the catalog
   positions and the relocalized positions of (from left to right)
-  2FGL\,J1635.4-4717c and 2FGL\,J1636.3-4740c.  The farther away green
-  stars are other catalog sources which were removed because they are
+  2FGL\,J1635.4$-$4717c and 2FGL\,J1636.3$-$4740c.  The farther away green
+  stars are other catalog sources which were removed from our model because they are
   not significant above 10 \gev.  This extended source is spatially
@@
   (a)
-  the region around 2FGL\,J1837.3-0700c smoothed by a 0\fdg1 2D Gaussian
+  the region around 2FGL\,J1837.3$-$0700c smoothed by a 0\fdg1 2D Gaussian
   kernel and (b) also the emission from the background 
@@
   star is the 2FGL position of this source. The red cross and circle
-  are the best fit position and extension  of 2FGL\,J1837.3-0700c 
+  are the best fit position and extension  of 2FGL\,J1837.3$-$0700c 
   assuming a radially
@@
   catalog position and the relocalized position of (from left to right)
-  2FGL\,J1839.3-0558c, 2FGL\,J1836.8-0623c, and 2FGL\,J1834.7-0705c.
-  The green cross inside the extension is 2FGL\,J1835.5-0649 which
-  was removed because it is part of the extended source.  The farther
-  away green star is 2FGL J1839.0-0539 which was removed because
+  2FGL\,J1839.3$-$0558c, 2FGL\,J1836.8$-$0623c, and 2FGL\,J1834.7$-$0705c.
+  The green cross inside the extension is 2FGL\,J1835.5$-$0649 which
+  was removed from our background model because it is part of the extended source.  The farther
+  away green star is 2FGL J1839.0$-$0539 which was removed from
+  our model because
   it is not significant above 10 \gev.  This source is spatially
-  coincident with the \tev source HESS\,J1837-069.  The light blue
+  coincident with the \tev source HESS\,J1837$-$069.  The light blue
   contours correspond to the \tev image observed by H.E.S.S.
@@
   2FGL\,J2019.1+4040 which was removed
+from our background model 
   because it is part of the extended source.  The diamond
@@
     The spectral energy distribution of the extended sources 
-    Puppis A (2FGL\,J0823.0-4246) and $\gamma$-Cygni 
+    Puppis A (2FGL\,J0823.0$-$4246) and $\gamma$-Cygni 
     (2FGL\,J2021.5+4026).
@@
     points of the associated sources.  Plot (a) shows the \gev SED of
-    2FGL\,J1615.0-5051 together with the \tev SED of HESS\,J1616-508.
-    Plot (b) shows 2FGL\,J1615.2-5138 and HESS\,J1614-518 Plot (c)
-    shows 2FGL\,J1632.4-4753c and HESS\,J1632-478. Plot (d) shows
-    2FGL\,J1837.3-0700c and HESS\,J1837-069. The H.E.S.S. data points
+    2FGL\,J1615.0$-$5051 together with the \tev SED of HESS\,J1616$-$508.
+    Plot (b) shows 2FGL\,J1615.2$-$5138 and HESS\,J1614$-$518 Plot (c)
+    shows 2FGL\,J1632.4$-$4753c and HESS\,J1632$-$478. Plot (d) shows
+    2FGL\,J1837.3$-$0700c and HESS\,J1837$-$069. The H.E.S.S. data points
     are from \citep{hess_plane_survey} Both LAT and H.E.S.S. spectral
@@
 
-{\rotate
+\clearpage
   \begin{figure}
@@
       with two years of data.  The twelve extended sources included in
-    2FGL are indicated by the circular markers (colored 
-    red in the online version).
-    The nine 
-    new
-    extended sources analyzed in this paper are the triangular
-    markers (colored orange in the online version). 
-    }\label{allsky_extended_sources}
+      2FGL are indicated by the circular markers (colored red in the online
+      version).  The nine new extended sources analyzed in this paper are
+      the triangular markers (colored orange in the online version).}
+\label{allsky_extended_sources}
   \end{figure}
-  }
 
@@
     sources detected by \tev instruments.  The \tev extensions
-    of W30, 2FGL\,J1837.3-0700c, 2FGL\,J1632.4-4753c,
-    2FGL\,J1615.0-5051, and 2FGL\,J1615.2-5138 \citep{hess_plane_survey}.
-    The \tev extensions of MSH 15-52, HESS\,J1825-137, Vela X,
-    Vela Jr., RX J1713.7-3946 and W28 are from 
+    of W30, 2FGL\,J1837.3$-$0700c, 2FGL\,J1632.4$-$4753c,
+    2FGL\,J1615.0$-$5051, and 2FGL\,J1615.2$-$5138 \citep{hess_plane_survey}.
+    The \tev extensions of MSH\,15$-$52, HESS\,J1825$-$137, Vela X,
+    Vela Jr., RX\,J1713.7$-$3946 and W28 are from 
     \citep{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
@@
     and W51c is from \citep{w51c_with_magic_at_fermi_symposium}.
-    The LAT extension of Vela X is from \citep{velax}.  Except for RX
-    J1713.7-3946 Vela Jr., the \tev sources were fit assuming a 2D Gaussian
+    The LAT extension of Vela X is from \citep{velax}.  Except for 
+RX\,J1713.7$-$3946 Vela Jr., the \tev sources were fit assuming a 2D Gaussian
     surface brightness so the plotted \gev and \tev extensions were first
     converted to \rsixeight (see Section~\ref{compare_source_size}).
-    Because of their large size, the shape of RX J1713.7-3946 and Vela Jr.
+    Because of their large size, the shape of RX\,J1713.7$-$3946 and Vela Jr.
     were not directly fit in \tev. Here, we take their
@@
     do not converted it to \rsixeight. The LAT extension errors are
-    the statistical and systematic errors added in quadrature. The \tev size of MSH 15-52, HESS\,J1614-518,
-    HESS\,J1632-478, and HESS\,J1837-069 have only been reported with
+    the statistical and systematic errors added in quadrature. The \tev size of MSH\,15$-$52, HESS\,J1614$-$518,
+    HESS\,J1632$-$478, and HESS\,J1837$-$069 have only been reported with
     an elliptical 2D Gaussian fit and so the plotted size is the average
@@
 %   The H.E.S.S. source catalog can be found at \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
-    Except for RX J1713.7-3946 and Vela Jr.,
+    Except for RX\,J1713.7$-$3946 and Vela Jr.,
     the H.E.S.S. sources were fit with a 2D Gaussian surface
@@
     (see Section~\ref{compare_source_size}). Because the spatial
-    morphology of RX J1713.7-3946 and Vela Jr. is poorly matched by a
+    morphology of RX\,J1713.7$-$3946 and Vela Jr. is poorly matched by a
     2D Gaussian surface brightness model, the \gev and

### 2011-08-23 extended_catalog/paper/extended_catalog.tex
added alexs comments

@@
 Carlo simulations to validate this tool and calculate the LAT's threshold
-for detecting the spatial extension of sources.  We then use this tool
-to test all sources in the two-year source catalog for extension. We
+for detecting the spatial extension of sources.  We then 
+test all sources in the two-year source catalog for extension. We
 report the detection of nine spatially extended sources in addition to
@@
 included in 2FGL.  In Section~\ref{test_2lac_sources} we further
-validate our extension test by testing the extension of Active
+demonstrate that our detection method does not misidentify
+point sources as being extended 
+by testing the extension of Active
 galactic nucleus (AGN) believed to be unresolvable. Finally, in
@@
 To validate our method, we test LAT sources associated with AGN for
-extension.  \gev emission from AGN is believed to originate from the cores
-of kpc-scale jets of distant galaxies.  Therefore AGN are not expected
-to be spatially resolvable by the LAT and provide a good calibration source to
-demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
-halos around AGNs have been hypothesized \citep{pair_halo_paper} which
-could be resolved by the LAT However, no such halo has been discovered
-in the LAT data so far.
-
-Following 1FGL, the LAT Collaboration published a list 
-of sources that
-had a high probability association with AGN 
-called 1LAC \citep{first_agn_cat}.
-1FGL had 709 1FGL sources associated with 671 distinct AGN at high
-latitude ($|b|>10\deg$).  
-Using two years of data and 2FGL, the LAT Collaboration
-associated 1016 2FGL sources
-with AGN called 2LAC \citep{second_agn_cat}.
-To avoid systematic problems with AGN classification, we
-selected 885 out of the 1016 AGN which made it into the clean AGN sub-sample.  An AGN
-association is considered clean only if it has a high probability
-of association $P\ge 80\%$, if it is the only AGN associated with the
-catalog source, and if there are no flags on the source in 2FGL. These
-last two conditions are important for our analysis. Source
-confusion may look like a spatially extended source and flagged catalog
-sources may correlate with unmodeled structure in the diffuse emission.
+extension.  \gev emission from AGN is believed to originate from the
+cores of kiloparsec-scale jets of distant galaxies.  Therefore AGN are
+not expected to be spatially resolvable by the LAT and provide a good
+calibration source to demonstrate that our extension detection method
+does not misidentify point sources as being extended.  We note that
+megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
+\citep{pair_halo_paper} to be resolvable by the LAT. However, no such
+halo has been discovered in the LAT data so far.
+
+Following 1FGL, the LAT Collaboration published the First LAT AGN Catalog
+(1LAC), a list of sources that had a high probability association with
+AGN \citep{first_agn_cat}.  1FGL had 709 1FGL sources associated with 671
+distinct AGN at high latitude ($|b|>10\deg$).  Using two years of data
+and 2FGL, the Second LAT AGN Catalog (2LAC) associated 1016 2FGL sources
+with AGN \citep{second_agn_cat}.  To avoid systematic problems with AGN
+classification, we selected 885 out of the 1016 AGN which made it into
+the clean AGN sub-sample.  An AGN association is considered clean only
+if it has a high probability of association $P\ge 80\%$, if it is the
+only AGN associated with the catalog source, and if there are no flags
+on the source in 2FGL. These last two conditions are important for our
+analysis. Source confusion may look like a spatially extended source
+and flagged catalog sources may correlate with unmodeled structure in
+the diffuse emission.
 
@@
 theoretical distribution.  Two sources had $\tsext>10$.  One was due
-to incorrectly automatically removing a nearby catalog sources (see
+to the incorrect removal of a nearby catalog sources from
+the sky model (see
 Section~\ref{extended_source_search_method}) and the other was due to a
@@
 test are not extended is not surprising.  This validation analysis is
-not suitable to reject any hypotheses about the existence of mpc-scale
+not suitable to reject any hypotheses about the existence of megaparsec-scale
 halos around AGN.
@@
 Nine extended sources not included in 2FGL were found using this search.
-Three were found in our search using 1-100 \gev photons and six were
-found in our search using 10-100 \gev photons.  The fit properties of
+Three were found in our search using 1 \gev 100 \gev photons and six were
+found in our search using 10 \gev to 100 \gev photons.  The fit properties of
 these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
@@
 The source 2FGL\,J0823.0$-$4246 was found 
-using 1-100 \gev photons to have an 
+to have an 
 extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
 with an extension
-significance of $\tsext=46.3$.  The source was fit to a position of
+significance of $\tsext=46.3$
+using 1 \gev to 100 \gev photons.  This source was fit to a position of
 $(l,b)=(260\fdg32,-3\fdg28)$.  
@@
 }
-
-To get a good fit of the source, we had to remove from our background
+To get a good fit of this source, we removed from our background
 model the nearby catalog
 sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which are part of the
-extended source.  We tested the source for source confusion by fitting
-it as two point sources. Because $\tsinc=22.1$ is smaller then \tsext,
-we conclude that this is an extended source.  These modifications are
+extended source.  These modifications are
 shown in Figure~\ref{1FGL_J0823.3-4248}.
 
-\hl{1
+\hl{
 This extended source is spatially coincident with the middle-aged
@@
 Mosaic \rosat observations of Puppis A produced the highest
-resolution X-ray image of the source
+resolution X-ray image of this source
 and contours corresponding to this
@@
 Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
-which leads to a 1-100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.
+which leads to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.
 
@@
 
-The source 2FGL\,J1627.0$-$2425c was found using 1-100 \gev photons to
+The source 2FGL\,J1627.0$-$2425c was found  to
 have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
-an extension significance of $\tsext=31.1$.  The best fit position is
+an extension significance of $\tsext=31.1$
+using 1 \gev to 100 \gev photons.  The best fit position is
 $(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
 year catalog source 1FGL\,J1628.6$-$2419c.  A counts map showing this source
-is seen in Figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
-we also fit the source instead as two point sources. Since $\tsinc=20.0$
-is smaller than \tsext, we conclude that this is an extended source.
+is seen in Figure \ref{1FGL_J1628.6-2419c}.
 
@@
 This source is in a region of remarkably complicated diffuse emission.
-Even though it is $16\deg$ from the Galactic plane, the source is on
+Even though it is $16\deg$ from the Galactic plane, this source is on
 top of the core of the Ophiuchus molecular cloud which contains massive
@@
 abundant molecular and atomic gas traced by CO and HI but also plenty of
-dark gas, the kind that we find only by its association with dust emission
+dark gas found only by its association with dust emission
 \citep{isabelle_dark_gass}. Embedded star-forming regions make it even
@@
 
-The source 2FGL\,J1712.4$-$3941 was found using 1-100 \gev
+The source 2FGL\,J1712.4$-$3941 was found 
 photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
-with an extension significance of $\tsext=39.6$.  This source was
-fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  The source
+with an extension significance of $\tsext=39.6$
+using 1 \gev to 100 \gev.  This source was
+fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  this source
 is coincident with the one-year catalog source 1FGL\,J1711.7$-$3944c.
@@
 The source 2FGL\,J0851.7$-$4635 was found 
-using 10-100 \gev photons to have an
+to have an
 extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
 with an extension
-significance of $\tsext=87.2$.  The source was fit to a position of
+significance of $\tsext=87.2$
+using 10 \gev to 100 \gev photons.  This source was fit to a position of
 $(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
@@
 
-To get a good fit of the source, we had to remove from
+To get a good fit of this source, removed from
 our background model the nearby catalog
@@
 further away catalog sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
-because they were not significant above 10 \gev.  After modifying
-the region, we found that \tsinc=16.1 which is less than \tsext so we
-conclude that the source is extended.
+because they were not significant above 10 \gev.
 
@@
 
-The source 2FGL\,J1615.0$-$5051 was found using 10-100 \tev
+The source 2FGL\,J1615.0$-$5051 was found 
 photons to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
-with an extension significance of \tsext=16.3.  The source
+with an extension significance of \tsext=16.3
+using 10 \gev to 100 \gev.  This source
 was fit to a position of $(l,b)=(332\fdg38,-0\fdg14)$.
@@
 also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
-To get a good fit of both sources, we had to model both sources as
+To get a good fit of both sources, we modeled both sources as
 being spatially extended and iteratively fit the position and extension
@@
 significant above 10 \gev.  These modifications are further described
-in the caption to Figure~\ref{1FGL_J1613.6-5100c}.  After modifying
-the region, we found that \tsinc=11.9 which is less than \tsext so we
-conclude that the source is extended.
+in the caption to Figure~\ref{1FGL_J1613.6-5100c}.
 
@@
 on 2FGL\,J1615.0$-$5051.  The H.E.S.S. experiment measured an
-extension $0.136\pm 0.008$ when fitting the source with an elliptical
+extension $0.136\pm 0.008$ when fitting this source with an elliptical
 2D Gaussian surface brightness.  This size corresponds to a 68\% containment
@@
 
-The source 2FGL\,J1615.2$-$5138 was found using 10-100 \gev
+The source 2FGL\,J1615.2$-$5138 was found 
 photons to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
-with an extension significance of \tsext=48.0.  The source was fit to a
+with an extension significance of \tsext=48.0
+using 10 \gev to 100 \gev.  This source was fit to a
 position of $(l,b)=(331\fdg66,-0\fdg66)$.  This source is coincident
@@
 sources. Both sources can be seen in Figure~\ref{1FGL_J1613.6-5100c}.
-For 2FGL\,J1615.2$-$5138, \tsinc=37.0 which is less than \tsext so we
-conclude that the source is extended.
 
@@
 H.E.S.S. in 2007 helped to resolve a double peaked structure in the
-H.E.S.S. data but no spectral variation across the source, suggesting
+H.E.S.S. data but no spectral variation across this source, suggesting
 that the emission is not the confusion of physically separate sources
@@
 There are five nearby pulsars, but none are luminous enough to
-provide the required energy output required to power the $\tev$ 
+provide the energy output required to power the $\tev$ 
 emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614$-$518
@@
 The source 2FGL\,J1632.4$-$4753c was found 
-using 10-100 \gev photons to
+to
 have an extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ 
 with an extension
-significance of \tsext=64.5.  The source was fit to a position of
+significance of \tsext=64.5
+using 10 \gev to 100 \gev photons.  This source was fit to a position of
 $(l,b)=(336\fdg41,0\fdg22)$.  This source is coincident with the one
@@
 
-To get a good fit of the source, we had to remove from our background model
+To get a good fit of this source, we removed from our background model
 three catalog sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
@@
 were not significant above 10 \gev.  These modifications are shown
-in Figure~\ref{1FGL_J1632.9-4802c}.  To test for source confusion,
-we compared the likelihood fitting this region as one extended source
-to the likelihood fitting this region as two point sources. We found
-$\tsinc=40.6$ which is less than \tsext so we conclude
-that this is an extended source.
+in Figure~\ref{1FGL_J1632.9-4802c}.
 
@@
 extension of $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the
-semi-major and semi-minor axes when fitting the source with an
+semi-major and semi-minor axes when fitting this source with an
 elliptical 2D Gaussian surface brightness.  This corresponds to a 68\%
@@
 a different synchrotron cooling time for the electrons producing X-rays
-and \tev gamma rays.
+and \tev $\gamma$-rays.
 }
@@
 
-The source 2FGL\,J1837.3$-$0700c was found with 10-100 \gev photons to
+The source 2FGL\,J1837.3$-$0700c was found 
+to
 have an extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an
-extension significance of $\tsext=18.8$.  The source was fit to a position
+extension significance of $\tsext=18.8$
+using 10 \gev to 100 \gev photons.  This source was fit to a position
 of $(l,b)=(25\fdg08,0\fdg13)$.  This source is coincident with the one
@@
 because it was not significant above 10 \gev. These modifications are
-shown in Figure~\ref{1FGL_J1837.5-0659c}.  After modifying the region,
-we found that \tsinc=12.6 which is less than \tsext, so we conclude that
-the source is spatially extended.
+shown in Figure~\ref{1FGL_J1837.5-0659c}.
 
@@
 an extension of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$
-along the semi-major and semi-minor axis when fitting the source
+along the semi-major and semi-minor axis when fitting this source
 with an elliptical 2D Gaussian surface brightness.  This corresponds
@@
 
-The source 2FGL\,J2021.5+4026 was found with 10-100 \gev
-photons to have an extension of $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
-with an extension significance of $\tsext=116.4$.  The source was
+The source 2FGL\,J2021.5+4026 was found 
+to have an extension of $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
+with an extension significance of $\tsext=116.4$
+using 10 \gev to 100 \gev photons.  This source was
 fit to a position of $(l,b)=(78\fdg18,2\fdg19)$.  This source
@@
 
-To get a good fit of the source, we had to remove from our background
+To get a good fit of this source, we removed from our background
 model the nearby catalog
@@
 localized to a position of $(l,b)=(78\fdg85,2\fdg67)$ and had $\ts=13.5$ .
-Although the source is not very significant, not including it into the
-background model appeared visually to significantly throw off the fit
-of the region.  In addition, we removed from our model the four further away catalog
+Although this source is not very significant, not including it into the
+background model significantly biased the fit extension.
+In addition, we removed from our model the four further away catalog
 sources 2FGL\,J2022.8+3843c, 2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c,
 and 2FGL\,J2012.4+3955c from the region because they were not significant
-above 10 \gev.  After modifying the region, we found that \tsinc=24.3
-which is less than \tsext, so we believe that this source is spatially
-extended.  These modifications are further described in the caption to
+above 10 \gev.  These modifications are further described in the caption to
 Figure~\ref{1FGL_J2020.0+4049}.
@@
 \gev and suggested the \tev emission could be a shock-cloud interaction
-in $\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10-100
+in $\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10 \gev to 100
 \gev photons to avoid PSR\,J2021+4026, we resolve an
@@
 
-2FGL reported on the detection of twelve sources
-previously known as extended. Using
+2FGL reported the detection of twelve sources
+previously resolved by the LAT at \gev energies. Using
 two years of LAT data and a new analysis method, we present on 
@@
 
-The position of the 21 extended LAT sources are close to the Galactic
+The 21 extended LAT sources are located close to the Galactic
 plane and plotted in Figure~\ref{allsky_extended_sources}.  Most of the
@@
 distance of extragalactic sources (with exception of the local group
-Galaxies) is typically too large to resolve them in gamma rays.
+Galaxies) is typically too large to resolve them in $\gamma$-rays.
 
@@
 show that the LAT observes a population of hard (index $<2$)
-extended sources above 10 \gev which connects to \tev sources.
+extended sources at energies above 10 \gev which connects to \tev sources.
 Figure~\ref{hess_seds} shows the LAT energy spectrum of four of the
@@
 
-For the LAT extended sources also seen in \tev,
+For the LAT extended sources also seen in the \tev energy range,
 Figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
-a good correlation between the \gev and \tev sizes of the sources. Even
+a good correlation between the size of the sources in the \gev and \tev
+energy ranges. Even
 so, the size of PWNe are expected to vary across the \gev and \tev energy
@@
     of the diffuse emission compared to the LAT PSF (inset).  Plots (a),
-    (c), and (d) use only 1-100 \gev photons.  Plots (c) and (d) use
+    (c), and (d) use only 1 \gev to 100 \gev photons.  Plots (c) and (d) use
     only photons which converted in the front part of the tracker and
@@
     \caption{
-    A comparison of a 2D Gaussian and disk surface brightness profiles
+    A comparison of a 2D Gaussian and disk-like surface brightness profiles
     of extended sources before and after convolving with the PSF for two
@@
 
-\tablenotetext{(a)}{Integral 1-100 \mev flux.}
+\tablenotetext{(a)}{Integral 1 \gev to 100 \gev flux.}
 
 \tablecomments{
-    the spectral models used in the Monte Carlo simulations used to
-    validate of \pointlike.
-    For each model, the number of statistically independent simulations
-    and the average value of \ts is tabulated.  The models spans
-    representative spectral parameters.
+    A list of th spectral models of simulated point sources which were
+    tested for extension.  For each model, the number of statistically
+    independent simulations and the average value of \ts is also
+    tabulated.  The models spans representative spectral parameters.
 }
@@
     detection threshold using photons with energy between 100 \mev and 100
-    \gev while the dashed line is the threshold using 1-100 \gev photons.
+    \gev while the dashed line is the threshold using 1 \gev to 100 \gev photons.
     }\label{index_sensitivity}
@@
     spectrum) for a two-year exposure. The left plots are the detection
-    threshold when using 1-100 \gev photons and the right plots are
-    the detection threshold when using 10-100 \gev photons.  The flux
+    threshold when using 1 \gev to 100 \gev photons and the right plots are
+    the detection threshold when using 10 \gev 100 \gev photons.  The flux
     is integrated only in the selected energy range.  Overlaid on this
@@
       in degrees assuming a uniform surface brightness. The table quotes
-      integral fluxes in the analyzed energy range (1-100 \gev or 10-100
+      integral fluxes in the analyzed energy range (1 \gev to 100 \gev or 10 \gev 100
       \gev) in units of $10^{-10}\phflux$.
@@
   A test statistic map generated for the region around the SNR 
-  IC443 using 1-100 \gev photons.  (a) test statistic map after
+  IC443 using 1 \gev to 100 \gev photons.  (a) test statistic map after
   subtracting IC443 modeled as a point source. (b) same as (a), but
@@
     \caption{
-    A diffuse-emission-subtracted 1-100 \gev counts map of the region
+    A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of the region
     around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian kernel. The
@@
 \tablenotetext{(a)}{
-Integrated in the fit energy range (either 1-100 \gev or 10-100 \gev).
+Integrated in the fit energy range (either 1 \gev 100 \gev or 10 \gev 100 \gev).
 }
@@
 \tablenotetext{(a)}{
-Integrated in the fit energy range (either 1-100 \gev or 10-100 \gev).
+Integrated in the fit energy range (either 1 \gev to 100 \gev or 10 \gev 100 \gev).
 }
@@
     \hl{
-  A diffuse-emission-subtracted 1-100 \gev counts map of (a) the region
+  A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of (a) the region
   around 2FGL\,J1627.0$-$2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
-  \caption{A diffuse-emission-subtracted 1-100 \gev
-  counts map of (a) the region around 2FGL\,J1712.4$-$3941 smoothed by
-  a 0\fdg25 2D Gaussian kernel and (b) also the emission 
+  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev
+  counts map of the region around 2FGL\,J1712.4$-$3941 (a) smoothed by
+  a 0\fdg25 2D Gaussian kernel and (b) with the emission 
   from the background sources subtracted.
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v7/run.py
-  \caption{A diffuse-emission-subtracted 10-100
+  \caption{A diffuse-emission-subtracted 10 \gev 100
   \gev counts map of the region around 2FGL\,J0851.7$-$4635 smoothed
   by a 0\fdg25 2D Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
-  and circle are the best fit position and extension of the source
+  and circle are the best fit position and extension of this source
   assuming a radially
-  symmetric uniform surface brightness.  The inner three green stars
+  symmetric uniform surface brightness.  The three green stars
+  inside the extension circle 
   are (from left to right) 2FGL\,J0853.5$-$4711, 2FGL\,J0855.4$-$4625,
-  and 2FGL\,J0848.5$-$4535 which were removed from our background model
-  because they are part of
-  the extended source.  The farther away green stars are (from left to
+  and 2FGL\,J0848.5$-$4535 and were removed from our background model.
+  The farther away green stars are (from left to
   right) 2FGL\,J0901.7$-$4655 and 2FGL\,J0858.0$-$4815 which were removed
@@
   \caption{
-    A diffuse-emission-subtracted 10-100
+    A diffuse-emission-subtracted 10 \gev to 100
     \gev counts map of the region around 2FGL\,J1615.0$-$5051 (upper
@@
     2FGL\,J1614.9$-$5212 which was removed from our background model
-  because it is part of the
-    extended source.  The green stars to the left are 2FGL\,J1619.7$-$5040c
+    The green stars to the left are 2FGL\,J1619.7$-$5040c
     and 2FGL\,J1620.6$-$5111c which were removed from our model because they were
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v7/run.py
-  \caption{A diffuse-emission-subtracted 10-100
+  \caption{A diffuse-emission-subtracted 10 \gev to 100
   \gev counts map of the region around 2FGL\,J1632.4$-$4753c smoothed by
@@
   2FGL\,J1630.2$-$4752, and 2FGL\,J1634.4$-$4743c.4-4820c
-  which were removed from our background model because they are part
-  of the extended source.  The blue stars and crosses are the catalog
+  which were removed from our background model.
+  The blue stars and crosses are the catalog
   positions and the relocalized positions of (from left to right)
@@
   \caption{
-  A diffuse-emission-subtracted 10-100 \gev counts map of
-  (a)
-  the region around 2FGL\,J1837.3$-$0700c smoothed by a 0\fdg1 2D Gaussian
-  kernel and (b) also the emission from the background 
+  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
+  the region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg1 2D Gaussian
+  kernel and (b) with the emission from the background 
   sources subtracted.  The red
@@
   The green cross inside the extension is 2FGL\,J1835.5$-$0649 which
-  was removed from our background model because it is part of the extended source.  The farther
+  was removed from our background model. The farther
   away green star is 2FGL J1839.0$-$0539 which was removed from
@@
   2FGL\,J2019.1+4040 which was removed
-from our background model 
-  because it is part of the extended source.  The diamond
+from our background model. The diamond
   (colored purple) is the
@@
     \caption{
-    The spectral energy distribution of four the extended sources
+    The spectral energy distribution of the four extended sources
     associated with extended \tev sources.  The black points with
@@
     markers (colored red in the electronic version) are the H.E.S.S
-    points of the associated sources.  Plot (a) shows the \gev SED of
-    2FGL\,J1615.0$-$5051 together with the \tev SED of HESS\,J1616$-$508.
-    Plot (b) shows 2FGL\,J1615.2$-$5138 and HESS\,J1614$-$518 Plot (c)
+    points of the associated sources.  Plot (a) shows the LAT SED of
+    2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED of HESS\,J1616$-$508.
+    Plot (b) shows 2FGL\,J1615.2$-$5138 and HESS\,J1614$-$518. Plot (c)
     shows 2FGL\,J1632.4$-$4753c and HESS\,J1632$-$478. Plot (d) shows
@@
       % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v2/run.py
-      \caption{A plot of all \gev extended sources detected by the LAT
+      \caption{A plot of all spatially extended sources detected by the LAT
+      in the \gev energy range
       with two years of data.  The twelve extended sources included in
@@
     The \tev extension of
-    the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
+    the extended H.E.S.S. sources comes from the H.E.S.S. Source
     Catalog \citep{hesscat}.

### 2011-08-26 extended_catalog/paper/extended_catalog.tex
updated test(?)
alexs introduction changes

@@
 \newif\ifcolorfigure
-%\colorfiguretrue
-\colorfigurefalse
+\colorfiguretrue
+%\colorfigurefalse
 
@@
 \begin{abstract}
-We present a new method for quantifying the spatial extension of sources
-with the Large Area Telescope (LAT), the primary science instrument on
-the {\em \fermi Gamma-ray Space Telescope} (\fermi).  Spatial extension
-is an important characteristic for correctly associating LAT sources with
-their counterparts at other wavelengths. We perform a series of Monte
-Carlo simulations to validate this tool and calculate the LAT's threshold
-for detecting the spatial extension of sources.  We then 
-test all sources in the two-year source catalog for extension. We
-report the detection of nine spatially extended sources in addition to
-the twelve spatially extended sources reported in the second \fermi-LAT
-Catalog (2FGL).
+Spatial extension is an important characteristic for correctly
+associating LAT sources with their counterparts at other wavelengths
+and for obtaining an unbiased model of their spectra.  We present a new
+method for quantifying the spatial extension of sources with the Large
+Area Telescope (LAT), the primary science instrument on the {\em \fermi
+Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
+simulations to validate this tool and calculate the LAT's threshold for
+detecting the spatial extension of sources.  We then test all sources
+in the second \fermi-LAT catalog (2FGL) for extension. We report the
+detection of nine spatially extended sources in addition to the twelve
+spatially extended sources reported in 2FGL.
 \end{abstract}
@@
 
-A number of astrophysical sources classes including supernova remnant
+A number of astrophysical source classes including supernova remnants
 (SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
-galaxy clusters could be expected to spatially resolvable at \gev
-energies.  Dark matter satellites are also hypothesized to be seen
-as spatially extended at \gev energies.  The LAT Collaboration has
-previously reported on five SNRs which are spatially extended beyond
-the LAT PSF at \gev energies (IC443, W28, W44, W51C, and RX\,J1713.7$-$3946
-\citep{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended PWNe
-were detected as being extended: MSH\,15$-$52, Vela~X, and HESS\,J1825$-$137
-\citep{msh1552,velax,fermi_hess_j1825}. Two close-by galaxies the Large
-and Small Magalenic Clouds and one radio galaxy Centarus A were spatially
-resolved at \gev energies \citep{lmc,smc,cen_a_lat}.  Furthermore,
-a number of other sources previously detected at \gev energies are
-positionally coincident with sources that exhibit extension at other
-wavelengths and could be expected to be spatially resolvable at \gev
-energies.
-
-At \tev energies many sources have been recently detected as
-begin spatially extended using air Cherenkov detectors.  Most
+and galaxy clusters are expected to be spatially resolvable at
+\gev energies.  Dark matter satellites are also hypothesized to
+be spatially extended.  The Large Area Telescope
+(LAT) on the {\em \fermi Gamma-ray Space Telescope} (\fermi) has
+detected five SNRs which are significantly extended
+at \gev energies: IC443, W28, W44, W51C, and RX\,J1713.7$-$3946
+\citep{ic443,w28,w44,w51c,rx_j1713_lat}. In addition, three extended
+PWNe were detected as being extended: MSH\,15$-$52, Vela~X, and
+HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
+close-by galaxies, the Large and Small Magalenic Clouds, and one
+radio galaxy, Centarus A, were spatially resolved at \gev energies
+\citep{lmc,smc,cen_a_lat}.  A number of additional sources detected
+at \gev energies are positionally coincident with sources that exhibit
+extension at other wavelengths. These sources could be expected to be spatially
+resolvable by the LAT at \gev energies.
+
+The current generation of air Cherenkov detectors have
+made it apparent that many sources can be spatially resolved
+at even higher energies.
+Most
 prominent was a survey of the Galactic plane using the High Energy
@@
 HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
-have no significant extension detected.  High energy $\gamma$-rays from
+have no detectable extension.  High-energy $\gamma$-rays from
 these sources are produced by the decay of $\pi^0$s produced by hadronic
@@
 high-energy particles and so at least some of these sources should be
-detected as extended sources at \gev energies.  Studying 
+detected at \gev energies.  Studying 
 these \tev sources at \gev energies would help to
@@
 
-The Large Area Telescope (LAT) is a pair conversion telescope on the
-{\em \fermi Gamma-ray Space Telescope} (\fermi) that been surveying the
+The LAT is a pair conversion telescope that been surveying the
 $\gamma$-ray sky since 2008 June.  The LAT has broad energy coverage
@@
 The capability to spatially resolve \gev $\gamma$-ray
-sources is important for several reasons.  First, multiple potential
-counterparts detected at other frequencies exist within the localization
-confidence region of a typical LAT source along the Galactic plane.
+sources is important for several reasons.  
 Finding a coherent source extension across different energy bands can
 help to associate a LAT source to an otherwise confused counterpart.
-Furthermore, dark matter satellite in our galaxy have been predicted to be
-detected and spatially extended at \gev energies and could be discovered
-outside the galactic plane \citep{pre_luanch_dark_matter_fermi}.  Also,
+Furthermore, some of the dark matter substructure in our Galaxy 
+is predicted to be spatially extended at \gev energies \citep{pre_luanch_dark_matter_fermi}.  
+Characterization of spatial extension could help to identify this substructure.
+Also,
 due to the strong energy dependence of the LAT PSF, the spatial and
-spectral information about a source do not simply decouple. An inaccurate
-spatial model will bias the spectral model of the source. Specifically,
+spectral character of a source do not decouple. An inaccurate
+spatial model will bias the spectral model of the source and vice versa. Specifically,
 modeling a spatially extended source as point-like will systematically
 shift a spectral analysis to softer indices. Furthermore, correctly
-modeling a source's extension is important for improving the model of
-the sky and removing excess residuals, for example in the region around
-surrounding the Large Magellanic Clouds \citep{first_cat}.  Such excess
-residuals potentially bias the significance and measured spectrum of
+modeling a source's extension is important for 
+understanding an entire region of the sky. For example,
+an incorrect model of the spatially extended LMC introduced
+significant residuals in the surrounding region \citep{first_cat,second_cat}.
+Such residuals can bias the significance and measured spectrum of
 neighboring sources in the densely populated Galactic plane.
 
-Each of the previously detected extended LAT sources was spatially
-resolved by a dedicated analysis of the particular source so
-we expect that a systematic scan of all LAT detected sources
+Previous analysis of
+extended LAT sources were performed as dedicated studies
+of individual sources, so we expect
+that a systematic scan of all LAT detected sources
 could uncover additional spatially extended sources.  For these
 reasons, in Section~\ref{analysis_methods_section} we present
-a new method for analyzing spatially extended LAT sources. In
-Section~\ref{monte_carlo_validation} we demonstrate that this tool
-can be used for an unbiased statistical test of the extension of
-LAT sources and in Section~\ref{extension_sensitivity} we calculate
+a new systematic method for analyzing spatially extended LAT sources. In
+Section~\ref{monte_carlo_validation} we demonstrate that this method
+can be used to test the statistical significance of
+the extension of
+a LAT sources and in Section~\ref{extension_sensitivity} we calculate
 the LAT's detection threshold to resolve the extension of a source.
@@
 new spatially extended LAT sources and in Section~\ref{validate_known}
-we reanalyzing the twelve previously detected extended sources
+we reanalyze the twelve previously detected extended sources
 included in 2FGL.  In Section~\ref{test_2lac_sources} we further
@@
 point sources as being extended 
-by testing the extension of Active
-galactic nucleus (AGN) believed to be unresolvable. Finally, in
+by testing the extension of active
+galactic nuclei (AGN) believed to be unresolvable. Finally, in
 Section~\ref{new_ext_srcs_section} we present the detection of the

### 2011-08-27 extended_catalog/paper/extended_catalog.tex

@@
 \begin{abstract}
+\hl{
 Spatial extension is an important characteristic for correctly
@@
 spatially extended sources reported in 2FGL.
+}
 \end{abstract}
@@
 Figure~\ref{all_sensitivity} shows the flux threshold
-as a function of source extension for different background levels (1x,
-10x, and 100x the nominal background), different spectral indices, and
+as a function of source extension for different background levels 
+($1\times$,
+$10\times$, 
+and $100\times$ the nominal background), different spectral indices, and
 two different energy bands (1 \gev to 100 \gev and 10 \gev to 100 \gev).  The detection
@@
 image are overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the
-inferred \gev size \citep{rosat_puppis_a}.
+inferred size at \gev energies \citep{rosat_puppis_a}.
 Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
@@
 single synchrotron processes producing X-ray and \gev and \tev radiation,
-likely due to a PWNe.  The increased \gev and \tev size compared
-to the X-ray size has previously been observed in several aging PWNe
+likely due to a PWNe.  The increased size at \tev energies
+compared
+to X-ray energies has previously been observed in several aging PWNe
 including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
@@
 
-Milagro detected a $4.2\sigma$
-excess at energies $\sim 30 \tev$ from the location of
-this source in the previous LAT bright $\gamma$-ray source
+Milagro detected a $4.2\sigma$ excess at energies $\sim 30 \tev$ from the
+location of this source in the previous LAT bright $\gamma$-ray source
 list. \cite{lat_bsl,milagro_bright_source_list}.  Veritas also detected
-an extended source VER\,J2019+407 coincident with the SNR above 200
-\gev and suggested the \tev emission could be a shock-cloud interaction
-in $\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10 \gev to 100
-\gev photons to avoid PSR\,J2021+4026, we resolve an
-extended source whose inferred \gev size well matches the radio size of
-$\gamma$-Cygni, as can be seen in Figure~\ref{1FGL_J2020.0+4049}
-which overlays contours of $\gamma$-Cygni at 408MHz from the Canadian
-Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
+an extended source VER\,J2019+407 coincident with the SNR above 200 \gev
+and suggested the \tev emission could be a shock-cloud interaction in
+$\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10 \gev to 100
+\gev photons to avoid PSR\,J2021+4026, we resolve an extended source
+whose inferred size at \gev energies well matches the radio size of
+$\gamma$-Cygni, as can be seen in Figure~\ref{1FGL_J2020.0+4049} which
+overlays contours of $\gamma$-Cygni at 408MHz from the Canadian Galactic
+Plane Survey \citep{canadian_galactic_plane_survey}.
 }
@@
 
-2FGL reported the detection of twelve sources
-previously resolved by the LAT at \gev energies. Using
-two years of LAT data and a new analysis method, we present on 
-the detection of nine additional extended sources. We also reanalyze
-the spatial shape of the extended sources in 2FGL.  Finding a coherent
-source extension with different frequencies, especially at \tev energies,
-allows us to firmly associate the LAT source in many cases.
-
-The 21 extended LAT sources are located close to the Galactic
-plane and plotted in Figure~\ref{allsky_extended_sources}.  Most of the
-extended sources are indeed expected to be of Galactic origin as the
-distance of extragalactic sources (with exception of the local group
-Galaxies) is typically too large to resolve them in $\gamma$-rays.
-
-Figure~\ref{compare_index_2FGL} shows a comparison of the spectral index
-of LAT detected extended sources and of all sources in 2FGL. This, and
-Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
-show that the LAT observes a population of hard (index $<2$)
-extended sources at energies above 10 \gev which connects to \tev sources.
-Figure~\ref{hess_seds} shows the LAT energy spectrum of four of the
-extended sources which were first discovered in the H.E.S.S. Galactic
-plane survey \citep{hess_plane_survey} and have a matching size to LAT
-extended sources.  The LAT energy spectrum connects smoothly to \tev.
-This is also true of HESS\,J1825$-$137 \citep{fermi_hess_j1825} and 
-RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
+\hl{
+Twelve extended sources were included in 2FGL.  Using two years of
+LAT data and a new analysis method, we presented the detection of
+nine additional extended sources. We also reanalyze the spatial
+shape of the twelve extended sources in 2FGL.  The 21 extended
+LAT sources are located close to the Galactic plane and plotted in
+Figure~\ref{allsky_extended_sources}.  Most of the extended sources are
+indeed expected to be of Galactic origin as the distance of extragalactic
+sources (with the exception of the local group Galaxies) is typically too
+large to resolve them in $\gamma$-rays.
 
 For the LAT extended sources also seen in the \tev energy range,
-Figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
-a good correlation between the size of the sources in the \gev and \tev
-energy ranges. Even
-so, the size of PWNe are expected to vary across the \gev and \tev energy
-range and the size of HESS\,J1825$-$137 was seen by H.E.S.S. to vary
-between 200 \gev and 20 \tev \citep{energy_dependent_hess_j1825}.
-HESS\,J1825$-$137 is significantly larger in \gev than \tev
-\citep{fermi_hess_j1825}.  It is interesting to compare the \gev and
-\tev size of other PWN candidates, but definitively measuring this 
-would require a more in-depth analysis of the LAT data using the same 
-elliptical surface brightness model.
+Figure~\ref{gev_vs_tev_plot} shows that their is a good correlation
+between the size of the sources in the \gev and \tev energy ranges. Even
+so, the size of PWNe are expected to vary across the \gev and \tev
+energy range and the size of HESS\,J1825$-$137 is significantly larger at
+\gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting to
+compare the size at \gev and \tev energies
+of other PWN candidates, but definitively
+measuring this would require a more in-depth analysis of the LAT data
+using the same elliptical surface brightness model.
 
 Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
-LAT sources to the 42 extended H.E.S.S. sources.  Because of the large
+LAT sources to the 42 extended H.E.S.S. sources.\footnote{The 
+\tev extension of
+the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
+Catalog. The H.E.S.S. source catalog can be found at \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
+Because of the large
 field of view and all-sky coverage, the LAT can more easily measure
@@
 population of extended sources below our sensitivity limit (currently at
-about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with a
-goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
-our sensitivity to these smaller sources will improve by a factor greater
-than the square root of the exposure.  With increased exposure, the LAT will likely begin to
-resolve these smaller \tev sources.
+about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with
+a goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
+the LAT's low background at high energies will allow it's sensitivity to
+these smaller sources to improve by a factor greater than the square root
+of the exposure.  With increased exposure, the LAT will likely begin to
+detect and resolve many smaller \tev sources.
+
+Figure~\ref{compare_index_2FGL} compares the spectral index
+of LAT detected extended sources and of all sources in 2FGL. This,
+and Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
+show that the LAT observes a population of hard extended sources at
+energies above 10 \gev.  Figure~\ref{hess_seds} shows that the
+\gev spectral of
+four of these sources (2FGL\,J1615.0$-$5051, 2FGL\,J1615.2$-$5138,
+2FGL\,J1632.4$-$4753c, and 2FGL\,J1837.3$-$0700c)  
+connect smoothly to their \tev counterparts. This is also true of Vela
+Jr., HESS\,J1825$-$137 \citep{fermi_hess_j1825}, RX\,J1713.7$-$3946
+\citep{rx_j1713_lat}.  It is likely that the \gev and \tev emission
+from these sources originates from the same population of high-energy
+particles.
+
+Many of the \tev detected extended sources now seen at \gev energies are
+currently unidentified and further multi-wavelength follow-up observations
+will be necessary to understand these particle accelerators. But \gev
+observations of these \tev sources in many cases can help to constrain
+handronic and leptonic models of these sources and, especially if their
+spectra can be extended to lower energies, help to understand the emission
+mechanisms producing these high energy $\gamma$-rays.  
+}
 
@@
     \caption{
-    Counts and test statistic profiles for the SNR IC443. (a) \ts
+    Counts maps and test statistic profiles for the SNR IC443. (a) \ts
     vs. extension of the source. (b) \tsext for individual energy
@@
     blue in the online version).  (d) smoothed count map after subtraction
-    of the diffuse emission compared to the LAT PSF (inset).  Plots (a),
+    of the diffuse emission compared to the smoothed
+    LAT PSF (inset).  Plots (a),
     (c), and (d) use only 1 \gev to 100 \gev photons.  Plots (c) and (d) use
@@
     for a power-law source of spectral index 2. The dashed line
-    and the dash-dot line are 
+    and the dash-dotted line are 
     the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
     and the convolution of this profile with the LAT PSF respectively
-    (colored red in the online version)
-    The dash-dot-dot and the dot-dot line are the brightness profile of a uniform disk
-    with $\rsixeight=0\fdg5$ and the convolution 
+    (colored red in the online version).
+    The dash-dot-doted and the dot-doted line are the brightness profile
+    of a uniform disk with $\rsixeight=0\fdg5$ and the convolution
     of this profile with the LAT PSF respectively (colored blue in the online version).
@@
 \tablecomments{
-    A list of th spectral models of simulated point sources which were
-    tested for extension.  For each model, the number of statistically
-    independent simulations and the average value of \ts is also
-    tabulated.  The models spans representative spectral parameters.
+    A list of the spectral models of the simulated point sources
+    which were tested for extension.  For each model, the number of
+    statistically independent simulations and the average value of \ts is
+    also tabulated.  The models spans representative spectral parameters.
 }
@@
     \caption{
-    Distribution of the test statistic \tsext of a likelihood ratio
-    test when fitting the extension of a point source.  The four plots
+    Distribution of the test statistic for the extension test.
+    The four plots
     represent simulated point sources of different spectral indices and
@@
     represent point sources with different 100 \mev
-    to 100 \gev integral fluxes.  The dashed line (colored red in online version)
+    to 100 \gev integral fluxes.  The dashed line (colored red)
     is the cumulative
@@
     \caption{
-    The detection threshold ($\langle\tsext\rangle=16$) to resolve a
+    The detection threshold to resolve a
     uniform disk extended source for a two-year exposure.  All sources
@@
     to different simulated spectral indices.  The solid line is the
-    detection threshold using photons with energy between 100 \mev and 100
+    detection threshold using photons with energies between 100 \mev and 100
     \gev while the dashed line is the threshold using 1 \gev to 100 \gev photons.
@@
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
-    \caption{the LAT detection threshold for four spectral indices and
-    three background (1x, 10x, and 100x the Sreekumar-like isotropic
-    spectrum) for a two-year exposure. The left plots are the detection
-    threshold when using 1 \gev to 100 \gev photons and the right plots are
-    the detection threshold when using 10 \gev 100 \gev photons.  The flux
-    is integrated only in the selected energy range.  Overlaid on this
-    plot are the LAT detected extended sources placed by the magnitude of
-    the nearby Galactic diffuse emission and the energy range they were
-    analyzed with.  The stars (colored red in the electronic version) are
-    sources with a spectral index closer to 1.5, the triangles (colored
-    blue) an index closer to 2, and the circles (colored green) an index
-    closer to 2.5 The circle in plot (d) below the sensitivity line is
-    MSH\,15$-$52 which was found by our analysis to have $\tsext=6.5$.
+    \caption{the LAT detection threshold for four spectral indices
+    and three background ($1\times$, $10\times$, and $100\times$ the
+    Sreekumar-like isotropic spectrum) for a two-year exposure. The
+    left plots are the detection threshold when using 1 \gev to 100 \gev
+    photons and the right plots are the detection threshold when using
+    10 \gev to 100 \gev photons.  The flux is integrated only in the
+    selected energy range.  Overlaid on this plot are the LAT detected
+    extended sources placed by the magnitude of the nearby Galactic
+    diffuse emission and the energy range they were analyzed with.
+    The star shaped markers (colored red in the electronic version)
+    are sources with a spectral index closer to 1.5, the triangular
+    markers (colored blue) an index closer to 2, and the circular markers
+    (colored green) an index closer to 2.5.  The circular marker in plot
+    (d) below the sensitivity line is MSH\,15$-$52.
     }\label{all_sensitivity} 
@@
 \hline
-     1.5 &       x1 &      148.1 &       23.3 &       11.3 &        8.0 &        7.2 &        6.9 &        6.7 &        6.8 &        7.1 &        7.4 &        7.6 &        7.9 &        8.1 &        8.5 &        9.2 &        9.9 &        9.1 &        9.2 &        9.0 &       10.3 \\
-         &      x10 &      148.4 &       29.0 &       18.7 &       15.2 &       15.4 &       15.0 &       16.1 &       16.0 &       16.8 &       17.7 &       18.2 &       19.3 &       20.9 &       22.5 &       23.8 &       24.8 &       21.3 &       22.8 &       23.4 &       23.7 \\
-         &     x100 &      186.8 &       55.0 &       43.4 &       40.7 &       41.0 &       41.8 &       40.9 &       40.9 &       42.7 &       43.6 &       38.4 &       39.9 &       40.6 &       38.4 &       36.9 &       36.3 &       37.1 &       38.8 &       37.2 &       37.6 \\
-       2 &       x1 &      328.4 &       43.4 &       18.9 &       13.4 &       11.2 &       10.4 &       10.2 &       10.2 &       10.2 &       10.4 &       10.7 &       10.9 &       11.2 &       11.5 &       12.4 &       12.6 &       13.0 &       13.4 &       14.0 &       14.4 \\
-         &      x10 &      341.0 &       55.9 &       32.3 &       27.6 &       26.5 &       25.4 &       25.6 &       25.9 &       27.4 &       26.8 &       27.8 &       28.7 &       29.8 &       30.1 &       31.0 &       31.5 &       31.7 &       34.0 &       34.3 &       35.9 \\
-         &     x100 &      420.5 &      128.3 &       90.2 &       77.3 &       73.3 &       70.8 &       67.5 &       64.3 &       64.2 &       64.1 &       62.8 &       63.6 &       61.7 &       61.9 &       58.4 &       59.0 &       61.4 &       63.3 &       60.1 &       58.1 \\
-     2.5 &       x1 &      627.1 &       75.6 &       29.8 &       19.3 &       15.5 &       13.5 &       12.8 &       12.6 &       12.5 &       12.5 &       12.6 &       12.9 &       12.9 &       13.1 &       13.5 &       13.7 &       14.3 &       14.8 &       15.2 &       15.8 \\
-         &      x10 &      638.9 &       99.1 &       52.1 &       39.1 &       34.6 &       33.0 &       32.5 &       32.5 &       32.8 &       33.2 &       34.1 &       34.3 &       34.5 &       35.1 &       36.6 &       36.9 &       35.5 &       36.0 &       36.5 &       37.3 \\
-         &     x100 &      795.0 &      262.1 &      140.9 &      104.3 &       90.4 &       81.2 &       77.2 &       75.1 &       69.7 &       70.9 &       66.5 &       65.6 &       64.9 &       64.0 &       58.9 &       58.1 &       60.2 &       58.4 &       57.5 &       55.8 \\
-       3 &       x1 &      841.5 &      110.6 &       43.2 &       25.5 &       18.7 &       16.1 &       14.4 &       13.6 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.6 &       13.5 &       13.8 &       14.2 &       14.4 &       14.8 &       15.4 \\
-         &      x10 &      921.6 &      151.3 &       69.1 &       47.8 &       40.7 &       37.1 &       35.5 &       34.5 &       35.1 &       35.5 &       35.3 &       35.3 &       35.4 &       35.5 &       36.8 &       37.6 &       35.3 &       35.4 &       36.3 &       36.6 \\
-         &     x100 &     1124.1 &      282.9 &      181.1 &      119.8 &      100.7 &       91.1 &       84.3 &       77.9 &       73.3 &       71.8 &       67.6 &       66.4 &       65.5 &       63.9 &       59.0 &       58.6 &       58.8 &       57.5 &       55.4 &       54.4 \\
+     1.5 &      $1\times$ &      148.1 &       23.3 &       11.3 &        8.0 &        7.2 &        6.9 &        6.7 &        6.8 &        7.1 &        7.4 &        7.6 &        7.9 &        8.1 &        8.5 &        9.2 &        9.9 &        9.1 &        9.2 &        9.0 &       10.3 \\
+         &     $10\times$ &      148.4 &       29.0 &       18.7 &       15.2 &       15.4 &       15.0 &       16.1 &       16.0 &       16.8 &       17.7 &       18.2 &       19.3 &       20.9 &       22.5 &       23.8 &       24.8 &       21.3 &       22.8 &       23.4 &       23.7 \\
+         &    $100\times$ &      186.8 &       55.0 &       43.4 &       40.7 &       41.0 &       41.8 &       40.9 &       40.9 &       42.7 &       43.6 &       38.4 &       39.9 &       40.6 &       38.4 &       36.9 &       36.3 &       37.1 &       38.8 &       37.2 &       37.6 \\
+       2 &      $1\times$ &      328.4 &       43.4 &       18.9 &       13.4 &       11.2 &       10.4 &       10.2 &       10.2 &       10.2 &       10.4 &       10.7 &       10.9 &       11.2 &       11.5 &       12.4 &       12.6 &       13.0 &       13.4 &       14.0 &       14.4 \\
+         &     $10\times$ &      341.0 &       55.9 &       32.3 &       27.6 &       26.5 &       25.4 &       25.6 &       25.9 &       27.4 &       26.8 &       27.8 &       28.7 &       29.8 &       30.1 &       31.0 &       31.5 &       31.7 &       34.0 &       34.3 &       35.9 \\
+         &    $100\times$ &      420.5 &      128.3 &       90.2 &       77.3 &       73.3 &       70.8 &       67.5 &       64.3 &       64.2 &       64.1 &       62.8 &       63.6 &       61.7 &       61.9 &       58.4 &       59.0 &       61.4 &       63.3 &       60.1 &       58.1 \\
+     2.5 &      $1\times$ &      627.1 &       75.6 &       29.8 &       19.3 &       15.5 &       13.5 &       12.8 &       12.6 &       12.5 &       12.5 &       12.6 &       12.9 &       12.9 &       13.1 &       13.5 &       13.7 &       14.3 &       14.8 &       15.2 &       15.8 \\
+         &     $10\times$ &      638.9 &       99.1 &       52.1 &       39.1 &       34.6 &       33.0 &       32.5 &       32.5 &       32.8 &       33.2 &       34.1 &       34.3 &       34.5 &       35.1 &       36.6 &       36.9 &       35.5 &       36.0 &       36.5 &       37.3 \\
+         &    $100\times$ &      795.0 &      262.1 &      140.9 &      104.3 &       90.4 &       81.2 &       77.2 &       75.1 &       69.7 &       70.9 &       66.5 &       65.6 &       64.9 &       64.0 &       58.9 &       58.1 &       60.2 &       58.4 &       57.5 &       55.8 \\
+       3 &      $1\times$ &      841.5 &      110.6 &       43.2 &       25.5 &       18.7 &       16.1 &       14.4 &       13.6 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.6 &       13.5 &       13.8 &       14.2 &       14.4 &       14.8 &       15.4 \\
+         &     $10\times$ &      921.6 &      151.3 &       69.1 &       47.8 &       40.7 &       37.1 &       35.5 &       34.5 &       35.1 &       35.5 &       35.3 &       35.3 &       35.4 &       35.5 &       36.8 &       37.6 &       35.3 &       35.4 &       36.3 &       36.6 \\
+         &    $100\times$ &     1124.1 &      282.9 &      181.1 &      119.8 &      100.7 &       91.1 &       84.3 &       77.9 &       73.3 &       71.8 &       67.6 &       66.4 &       65.5 &       63.9 &       59.0 &       58.6 &       58.8 &       57.5 &       55.4 &       54.4 \\
 \cutinhead{E$>$10 \gev}
-     1.5 &       x1 &       44.6 &        8.0 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.5 &        2.5 &        2.6 &        2.7 &        2.8 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
-         &      x10 &       45.2 &        9.2 &        5.8 &        5.0 &        4.9 &        4.9 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.3 &        6.6 &        6.5 &        6.8 &        7.6 &        7.8 &        8.2 &        8.5 &        8.7 \\
-         &     x100 &       47.3 &       13.4 &       11.6 &       10.6 &       10.8 &       10.8 &       12.0 &       12.7 &       13.2 &       13.7 &       15.3 &       16.1 &       17.2 &       18.2 &       18.9 &       19.5 &       20.4 &       21.0 &       21.7 &       22.9 \\
-       2 &       x1 &       49.7 &        8.4 &        4.4 &        3.3 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
-         &      x10 &       48.6 &        9.5 &        6.0 &        5.2 &        5.0 &        5.2 &        5.2 &        5.3 &        5.4 &        5.8 &        6.4 &        6.6 &        7.0 &        7.1 &        7.5 &        8.0 &        8.3 &        8.6 &        9.0 &        9.2 \\
-         &     x100 &       51.8 &       14.7 &       11.8 &       11.5 &       11.5 &       11.9 &       13.2 &       14.0 &       14.3 &       15.3 &       16.2 &       16.9 &       18.4 &       19.2 &       19.8 &       21.0 &       22.0 &       22.8 &       23.2 &       24.3 \\
-     2.5 &       x1 &       53.1 &        9.1 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.8 &        2.9 &        3.1 &        3.2 &        3.3 &        3.5 &        3.6 \\
-         &      x10 &       53.7 &       10.5 &        6.3 &        5.4 &        5.1 &        5.1 &        5.3 &        5.4 &        5.7 &        6.0 &        6.3 &        6.6 &        6.8 &        6.9 &        7.5 &        8.1 &        8.3 &        8.6 &        8.9 &        9.2 \\
-         &     x100 &       57.0 &       15.6 &       12.7 &       11.9 &       11.8 &       12.2 &       13.1 &       14.3 &       14.6 &       15.2 &       16.3 &       17.0 &       18.8 &       19.2 &       19.9 &       21.0 &       21.9 &       22.3 &       23.3 &       23.7 \\
-       3 &       x1 &       55.5 &        9.4 &        4.8 &        3.4 &        2.9 &        2.7 &        2.6 &        2.5 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 \\
-         &      x10 &       56.0 &       10.5 &        6.2 &        5.3 &        5.1 &        5.1 &        5.1 &        5.3 &        5.5 &        5.7 &        5.9 &        6.4 &        6.4 &        6.6 &        7.0 &        7.8 &        8.0 &        8.3 &        8.6 &        8.9 \\
-         &     x100 &       60.3 &       16.2 &       12.7 &       11.7 &       11.8 &       12.2 &       12.6 &       13.8 &       14.2 &       14.6 &       15.8 &       16.5 &       17.6 &       18.5 &       19.4 &       19.8 &       20.7 &       21.0 &       21.8 &       22.5 \\
+     1.5 &      $1\times$ &       44.6 &        8.0 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.5 &        2.5 &        2.6 &        2.7 &        2.8 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
+         &     $10\times$ &       45.2 &        9.2 &        5.8 &        5.0 &        4.9 &        4.9 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.3 &        6.6 &        6.5 &        6.8 &        7.6 &        7.8 &        8.2 &        8.5 &        8.7 \\
+         &    $100\times$ &       47.3 &       13.4 &       11.6 &       10.6 &       10.8 &       10.8 &       12.0 &       12.7 &       13.2 &       13.7 &       15.3 &       16.1 &       17.2 &       18.2 &       18.9 &       19.5 &       20.4 &       21.0 &       21.7 &       22.9 \\
+       2 &      $1\times$ &       49.7 &        8.4 &        4.4 &        3.3 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
+         &     $10\times$ &       48.6 &        9.5 &        6.0 &        5.2 &        5.0 &        5.2 &        5.2 &        5.3 &        5.4 &        5.8 &        6.4 &        6.6 &        7.0 &        7.1 &        7.5 &        8.0 &        8.3 &        8.6 &        9.0 &        9.2 \\
+         &    $100\times$ &       51.8 &       14.7 &       11.8 &       11.5 &       11.5 &       11.9 &       13.2 &       14.0 &       14.3 &       15.3 &       16.2 &       16.9 &       18.4 &       19.2 &       19.8 &       21.0 &       22.0 &       22.8 &       23.2 &       24.3 \\
+     2.5 &      $1\times$ &       53.1 &        9.1 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.8 &        2.9 &        3.1 &        3.2 &        3.3 &        3.5 &        3.6 \\
+         &     $10\times$ &       53.7 &       10.5 &        6.3 &        5.4 &        5.1 &        5.1 &        5.3 &        5.4 &        5.7 &        6.0 &        6.3 &        6.6 &        6.8 &        6.9 &        7.5 &        8.1 &        8.3 &        8.6 &        8.9 &        9.2 \\
+         &    $100\times$ &       57.0 &       15.6 &       12.7 &       11.9 &       11.8 &       12.2 &       13.1 &       14.3 &       14.6 &       15.2 &       16.3 &       17.0 &       18.8 &       19.2 &       19.9 &       21.0 &       21.9 &       22.3 &       23.3 &       23.7 \\
+       3 &      $1\times$ &       55.5 &        9.4 &        4.8 &        3.4 &        2.9 &        2.7 &        2.6 &        2.5 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 \\
+         &     $10\times$ &       56.0 &       10.5 &        6.2 &        5.3 &        5.1 &        5.1 &        5.1 &        5.3 &        5.5 &        5.7 &        5.9 &        6.4 &        6.4 &        6.6 &        7.0 &        7.8 &        8.0 &        8.3 &        8.6 &        8.9 \\
+         &    $100\times$ &       60.3 &       16.2 &       12.7 &       11.7 &       11.8 &       12.2 &       12.6 &       13.8 &       14.2 &       14.6 &       15.8 &       16.5 &       17.6 &       18.5 &       19.4 &       19.8 &       20.7 &       21.0 &       21.8 &       22.5 \\
 \enddata
@@
       The detection threshold to resolve a uniform disk spatially extended
-      sources using two years of data for sources of varying energy
+      sources for a two-year exposure
+      for sources of varying energy
       ranges, spectral indices, and background levels.  The extended
@@
       and the second column is the factor that the simulated background
-      was scaled by. The remaining columns are varying sizes of the source
-      in degrees assuming a uniform surface brightness. The table quotes
+      was scaled by. The remaining columns are varying sizes of the source. 
+      The table quotes
       integral fluxes in the analyzed energy range (1 \gev to 100 \gev or 10 \gev 100
-      \gev) in units of $10^{-10}\phflux$.
+      \gev) in units of $10^{-10}$ \phflux.
       }
@@
     \hl{
-    The LAT's projected detection threshold to extension after 10 years for a power-law
+    The LAT's projected detection threshold to extension after a ten-year exposure
+    for a power-law
     source of spectral index 2 against 10 times the isotropic background
@@
     version) and 10 \gev to 100 \gev
-    (dashed line colored blue in the electronic version). The solid gray region is the 
+    (dashed line colored blue). The solid gray regions represent the
     detection threshold assuming the sensitivity improves from 2 to 10
@@
     sensitivity.  For small extended sources, our detection threshold
-    to the extension of a source will improve by a factor better than the square root of 
+    to the extension of a source will improve by a factor larger than the square root of 
     the exposure.
@@
   IC443 modeled as extended source. Crosses represent sources included
-  in the model of the region.  Such maps were generated for all extended
-  source candidates.}
+  in the model of the region.}
   \label{res_tsmaps}
@@
     \caption{
-    A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of the region
-    around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian kernel. The
-    plus and circle (colored red in the online version) represent the
-    center and size of the best fit radially symmetric source with
-    a uniform intensity profile.  The black crosses represent the
-    position of background 2FGL sources.  The result is statistically
-    significant, but the extension encompasses many catalog sources and
-    the emission does not look to be uniform. Instead, this source is
-    probably fitting large-scale diffuse residual features. Although
+    A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of the
+    region around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian
+    kernel. The plus-shaped marker and circle circle (colored red in
+    the online version) represent the center and size of the best fit
+    radially symmetric source with a uniform intensity profile.  The black
+    crosses represent the position of other 2FGL sources.  The extension
+    is statistically significant, but the extension encompasses many 2FGL
+    sources and the emission does not look to be uniform. This source
+    is probably fitting large-scale diffuse residual features. Although
     the fit is statistically significant, it likely corresponds to
@@
 \tablewidth{0pt}
-\tablecaption{Extension fit for the twelve extended sources included in 2FGL
+\tablecaption{Analysis of the twelve extended sources included in 2FGL
 \label{known_extended_sources}
@@
 the position of the source.  Vela X and the Centarus A Lobes were
-not fit by our analysis but are include for completeness.
+not fit in our analysis but are include for completeness.
 }
@@
     \caption{The cumulative density of \tsext for 783 of the clean
-    AGN in 2LAC which are significant above 1 \gev calculated with \pointlike (the dashed line
+    AGN in 2LAC which are significant above 1 \gev calculated with \pointlike (dashed line
     colored blue in the electronic version)
-    and with \gtlike (the solid line colored red in the electronic version).  AGNs are too far
+    and with \gtlike (solid line colored red).  AGN are too far
     and too small to be resolved by the LAT. Therefore, the cumulative
     density of $\tsext$ is expected to follow a $\chi^2/2$ distribution
-    (Equation~\ref{ts_ext_distribution}) and is the dash-dotted line (colored
-    red in the electronic version).
+    (Equation~\ref{ts_ext_distribution}, the dash-dotted line colored
+    red).
     }\label{agn_ts_ext}
@@
 \tablecomments{
-    The columns in this table
-    are equivalent to the columns in Table~\ref{known_extended_sources}.
+    The columns in this table have the same meaning as those in
+    Table~\ref{known_extended_sources}.
 }
@@
 \begin{deluxetable}{lrrrrrrrrrr}
+  \tabletypesize{\small}
   \tablecolumns{11}
@@
 $\ts_\pointlike$, $\ts_\gtlike$, and $\ts_\altdiff$ are the test
-statistic values from \pointlike, \gtlike, and with the alternate
+statistic values from \pointlike, \gtlike, and \gtlike with the alternate
 diffuse model respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$,
 and $\tsext_\altdiff$ are the test statistic values of the extension
-test from \pointlike, \gtlike, and with the alternate diffuse
+test from \pointlike, \gtlike, and \gtlike with the alternate diffuse
 model respectively.  $\sigma$, $\sigma_\altdiff$, and $\sigma_\altpsf$
-are the fit extension with the standard analysis,
-alternate diffuse model, and alternate PSF respectively.  \tsinc is
-the test statistic for the two point source test.
+are the fit extension with the standard analysis, the alternate diffuse
+model, and the alternate PSF respectively.  \tsinc is the test statistic
+for the two point source hypothesis test 
+(see Section~\ref{dual_localization_method}).
 }
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v7/run.py
-  \caption{A diffuse-emission-subtracted 1 \gev to 100
-  \gev counts map of the region around 2FGL\,J0823.0$-$4246 smoothed
-  by a 0\fdg1 2D Gaussian kernel.  
-  The triangle (colored red in the online version)
-  is the 2FGL position
-  of this source.  The cross and circle (colored red) are the best fit position
-  and extension of this source assuming a radially symmetric uniform
-  surface brightness.  The two stars (colored green) are the positions of the
-  sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which were removed
-  from out background model
-  because they are part of the extended source.  The lower right inset
-  is the model predicted emission from a point source with the same
-  spectrum as 2FGL\,J0823.4$-$4305 smoothed by the same kernel.
-  This source is spatially coincident with the Puppis A SNR. The
-  light blue contours correspond to the X-ray image of Puppis A observed by 
-  \rosat
-  \citep{rosat_puppis_a}. 
+  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
+  of the region around 2FGL\,J0823.0$-$4246 smoothed by a 0\fdg1 2D
+  Gaussian kernel.  The triangular marker 
+  (colored red in the online version)
+  represents the 2FGL position of this source.  The plus-shaped
+  marker and the circle (colored
+  red) represent 
+  the best fit position and extension of this source assuming a
+  radially symmetric uniform surface brightness.  The two 
+  star-shaped markers (colored
+  green) represent 2FGL sources that were
+  removed from the background model.
+  The lower right inset is the model predicted emission from a point
+  source with the same spectrum as 2FGL\,J0823.4$-$4305 smoothed by the
+  same kernel.  This source is spatially coincident with the Puppis A
+  SNR. The light blue contours correspond to the X-ray image of Puppis
+  A observed by \rosat \citep{rosat_puppis_a}.
   }\label{1FGL_J0823.3-4248}
@@
   also the emission from the background source 2FGL\,J1625.7$-$2526
-  subtracted.  The red star is the 2FGL position of this source.
-  The red cross and circle are the best position and extension of this
+  subtracted.  The triangular marker 
+  (colored red in the
+  online version) represents the 2FGL position of this source.
+  The plus-shaped marker and the circle (colored red) 
+  represent the best fit position and extension of this
   source assuming a radially symmetric uniform surface brightness. The
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
-  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev
-  counts map of the region around 2FGL\,J1712.4$-$3941 (a) smoothed by
-  a 0\fdg25 2D Gaussian kernel and (b) with the emission 
-  from the background sources subtracted.
-  This source is spatially
-  coincident with RX\,J1713.7$-$3946 was was recently reported by
-  \citep{rx_j1713_lat}.  The light blue contours correspond to the \tev image
-  observed by H.E.S.S. \citep{rx_j1713_hess}.  The region was analyzed
-  with the same background model as \citep{rx_j1713_lat}.  Source A (blue
-  cross) is spatially coincident with 2FGL\,J1715.4$-$4024c (blue star).
-  The gray crosses represent from left to right the position of source B
-  and C which were added to the background model. 
+  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
+  of the region around 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg25 2D
+  Gaussian kernel and (b) with the emission from the background sources
+  subtracted.  This source is spatially coincident with RX\,J1713.7$-$3946
+  and was recently reported by \cite{rx_j1713_lat}.  The triangular marker
+  (colored red in the online version) represents the 2FGL position of this
+  source.  The plus-shaped marker and 
+  the circle (colored red) are the best fit position
+  and extension of this source assuming a radially symmetric uniform
+  surface brightness.  The contours (colored light blue) correspond
+  to the \tev image \citep{rx_j1713_hess}.  The region was analyzed
+  with the same background model as \cite{rx_j1713_lat}. Source A is
+  coincident with 2FGL\,J1715.4$-$4024c and the circular and square-shaped
+  marker
+  (colored blue) represent the 2FGL and relocalized position of this
+  source respectively.  The diamond-shaped markers
+  (colored purple) represent
+  the position of source B and C that were added to the background model.
   }\label{2FGL_J1712.4-3941}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v7/run.py
-  \caption{A diffuse-emission-subtracted 10 \gev 100
-  \gev counts map of the region around 2FGL\,J0851.7$-$4635 smoothed
-  by a 0\fdg25 2D Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
-  and circle are the best fit position and extension of this source
-  assuming a radially
-  symmetric uniform surface brightness.  The three green stars
-  inside the extension circle 
-  are (from left to right) 2FGL\,J0853.5$-$4711, 2FGL\,J0855.4$-$4625,
-  and 2FGL\,J0848.5$-$4535 and were removed from our background model.
-  The farther away green stars are (from left to
-  right) 2FGL\,J0901.7$-$4655 and 2FGL\,J0858.0$-$4815 which were removed
-  from our model
-  because they were not significant above 10 \gev.  The blue cross
-  is the relocalized position of 2FGL\,J0854.7$-$4501.  This extended
-  source is spatially coincident with the Vela Jr SNR.  The light
-  blue contours correspond to the \tev image of Vela Jr. observed by H.E.S.S
+  \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
+  the region around 2FGL\,J0851.7$-$4635 smoothed by a 0\fdg25 2D Gaussian
+  kernel. The triangular marker (colored red in the electronic version)
+  represents the 2FGL position of this source.  The plus-shaped marker
+  and the circle (colored red) are the best fit position and extension of
+  this source assuming a radially symmetric uniform surface brightness.
+  The five star-shaped markers (colored green) represent 2FGL sources
+  that were removed from the background model.  The circular and square
+  marker (colored blue) represents the 2FGL and relocalized position of
+  2FGL\,J0854.7$-$4501 respectively.  This extended source is spatially
+  coincident with the Vela Jr. SNR.  The contours (colored light blue)
+  correspond to the \tev image of Vela Jr.
   \citep{vela_jr_hess}.
@@
   \caption{
-    A diffuse-emission-subtracted 10 \gev to 100
-    \gev counts map of the region around 2FGL\,J1615.0$-$5051 (upper
-    left) and 2FGL\,J1615.2$-$5138 (lower right) smoothed by a 0\fdg1
-    2D Gaussian kernel.  The red stars are the catalog positions of these
-    sources.  The red stars and circles are the best fit positions and
-    extensions of these sources 
-    assuming a radially
-    symmetric uniform surface brightness.
-    The green star inside the extension of 2FGL\,J1615.2$-$5138  is
-    2FGL\,J1614.9$-$5212 which was removed from our background model
-    The green stars to the left are 2FGL\,J1619.7$-$5040c
-    and 2FGL\,J1620.6$-$5111c which were removed from our model because they were
-    not significant above 10\gev. These are shown as green stars.
-    The light blue
-    contours correspond to the \tev image 
-    of the extended sources
-    HESS\,J1616$-$508 (left) and the extended source HESS\,J1614$-$518
-    (right)
-    observed by H.E.S.S
-    \citep{hess_plane_survey}
-    2FGL\,J1615.0$-$5051 is spatially consistent with HESS\,J1616$-$508 and
-    2FGL\,J1615.2$-$5138 is spatially consistent with HESS\,J1614$-$518.
+    A diffuse-emission-subtracted 10 \gev to 100 \gev counts
+    map of the region around 2FGL\,J1615.0$-$5051 (upper left)
+    and 2FGL\,J1615.2$-$5138 (lower right) smoothed by a 0\fdg1
+    2D Gaussian kernel.  The triangular markers (colored red in the
+    electronic version) represent the 2FGL positions of these sources.
+    The cross-shaped markers and the
+    circles (colored red) represent the best fit
+    positions and extensions of these sources assuming a radially
+    symmetric uniform surface brightness.  The three star-shaped
+    markers (colored
+    green) represent 2FGL sources that were removed from the background
+    model.  The contours (colored light blue) correspond to the \tev
+    image of HESS\,J1616$-$508 (left) and HESS\,J1614$-$518 (right)
+    \citep{hess_plane_survey}.   
     }\label{1FGL_J1613.6-5100c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v7/run.py
-  \caption{A diffuse-emission-subtracted 10 \gev to 100
-  \gev counts map of the region around 2FGL\,J1632.4$-$4753c smoothed by
-  a 0\fdg1 2D Gaussian kernel.  This source is in a crowded region.
-  The red star is the 2FGL position of this source.  The red
-  cross and circle are the best fit position and extension 2FGL\,J1632.4$-$4753c 
-  assuming a radially
-  symmetric uniform surface brightness.
-  The three
-  green crosses inside the extension are 2FGL\,J1631.7$-$4720c, 
-  2FGL\,J1630.2$-$4752, and 2FGL\,J1634.4$-$4743c.4-4820c
-  which were removed from our background model.
-  The blue stars and crosses are the catalog
-  positions and the relocalized positions of (from left to right)
-  2FGL\,J1635.4$-$4717c and 2FGL\,J1636.3$-$4740c.  The farther away green
-  stars are other catalog sources which were removed from our model because they are
-  not significant above 10 \gev.  This extended source is spatially
-  coincident with the extended H.E.S.S source HESS\,J1632-478.
-  The light blue contours correspond to the \tev image observed by H.E.S.S.
-  \citep{hess_plane_survey}.
+  \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
+  the region around 2FGL\,J1632.4$-$4753c smoothed by a 0\fdg1 2D Gaussian
+  kernel.  The triangular marker (colored red in the electronic version)
+  represents the 2FGL position of this source.  The plus-shaped marker
+  and the circle (colored red) are the best fit position and extension
+  2FGL\,J1632.4$-$4753c assuming a radially symmetric uniform surface
+  brightness.  The four star-shaped markers (colored red) represent 2FGL
+  sources that were removed from the background model.  The circular
+  and square markers (colored blue) represent the 2FGL and relocalized
+  positions respectively of (from left to right) 2FGL\,J1635.4$-$4717c
+  and 2FGL\,J1636.3$-$4740c.  
+  The contours (colored light blue) correspond to the \tev image of
+  HESS\,J1632-478 \citep{hess_plane_survey}.
   }\label{1FGL_J1632.9-4802c}
@@
   \caption{
-  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  the region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg1 2D Gaussian
-  kernel and (b) with the emission from the background 
-  sources subtracted.  The red
-  star is the 2FGL position of this source. The red cross and circle
-  are the best fit position and extension  of 2FGL\,J1837.3$-$0700c 
-  assuming a radially
-  symmetric uniform surface brightness. The blue stars and crosses are the
-  catalog position and the relocalized position of (from left to right)
-  2FGL\,J1839.3$-$0558c, 2FGL\,J1836.8$-$0623c, and 2FGL\,J1834.7$-$0705c.
-  The green cross inside the extension is 2FGL\,J1835.5$-$0649 which
-  was removed from our background model. The farther
-  away green star is 2FGL J1839.0$-$0539 which was removed from
-  our model because
-  it is not significant above 10 \gev.  This source is spatially
-  coincident with the \tev source HESS\,J1837$-$069.  The light blue
-  contours correspond to the \tev image observed by H.E.S.S.
+  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of the
+  region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg1 2D Gaussian
+  kernel and (b) with the emission from the background sources subtracted.
+  The triangular marker (colored red in the online version) represents
+  the 2FGL
+  position of this source. The plus-shaped marker and 
+  the circle (colored red) represent
+  the best fit position and extension of 2FGL\,J1837.3$-$0700c assuming a
+  radially symmetric uniform surface brightness. The circular
+  and square markers 
+  (colored blue) represent the 2FGL and the relocalized position of
+  (from left to right) 2FGL\,J1839.3$-$0558c, 2FGL\,J1836.8$-$0623c,
+  and 2FGL\,J1834.7$-$0705c.  The star-shaped marker 
+  (colored green) represent a
+  2FGL source that was removed from the background model.  
+  The contours (colored light blue) correspond to the \tev image of
+  HESS\,J1837$-$069
   \citep{hess_plane_survey}.}\label{1FGL_J1837.5-0659c}
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v7/run.py
-  \caption{A Diffuse subtracted 10 \gev to 100 \gev counts map of the region
-  around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 2D Gaussian kernel. The
-  triangle (colored red in the online version)
-  represents the 2FGL position of 2FGL J2021.5+4026.  The plus
-  and circle (colored red) 
-  represent the best fit position and extension 2FGL\,J2021.5+4026
-  assuming a radially symmetric uniform surface brightness.  The 
-  star (colored green) 
-  inside the extension represents the position of 
-  2FGL\,J2019.1+4040 which was removed
-from our background model. The diamond
-  (colored purple) is the
-  position a source not in the two-year catalog which was added to the
-  region. 2FGL\,J2021.5+4026 is spatially coincident with the $\gamma$
-  Cygni SNR.  The contours (colored light blue)
-  correspond to the 408MHz image of
-  $\gamma$ Cygni observed by the Canadian Galactic Plane Survey.
+  \caption{A Diffuse-emission-subtracted 
+  subtracted 10 \gev to 100 \gev counts map of the
+  region around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 2D Gaussian
+  kernel. The triangular marker (colored red in the online version)
+  represents the 2FGL position of this source.  The plus-shaped
+  marker and the circle (colored red) represent the best fit position
+  and extension of 2FGL\,J2021.5+4026 assuming a radially symmetric
+  uniform surface brightness.  The star-shaped markers (colored green)
+  represent 2FGL sources that were removed from the background model.
+  The diamond-shaped marker (colored purple) represents the position of
+  a
+  source not in 2FGL that was added to the region. 2FGL\,J2021.5+4026
+  is spatially coincident with the $\gamma$-Cygni SNR.  The contours
+  (colored light blue) correspond to the 408MHz image of $\gamma$-Cygni
+  observed by the Canadian Galactic Plane Survey.
   }\label{1FGL_J2020.0+4049}
@@
     \caption{
-    The spectral energy distribution of the four extended sources
-    associated with extended \tev sources.  The black points with
-    circular markers are the LAT data points. The points with dashed
-    markers (colored red in the electronic version) are the H.E.S.S
-    points of the associated sources.  Plot (a) shows the LAT SED of
-    2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED of HESS\,J1616$-$508.
-    Plot (b) shows 2FGL\,J1615.2$-$5138 and HESS\,J1614$-$518. Plot (c)
-    shows 2FGL\,J1632.4$-$4753c and HESS\,J1632$-$478. Plot (d) shows
-    2FGL\,J1837.3$-$0700c and HESS\,J1837$-$069. The H.E.S.S. data points
-    are from \citep{hess_plane_survey} Both LAT and H.E.S.S. spectral
-    errors are statistical only.}
+    The spectral energy distribution of four extended
+    sources associated with unidentified
+    extended \tev sources.  The black points
+    with circular markers are the LAT data points. The points with
+    dashed markers (colored red in the electronic version) are the
+    H.E.S.S points of the associated sources.  Plot (a) shows the
+    LAT SED of 2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED
+    of HESS\,J1616$-$508.  Plot (b) shows 2FGL\,J1615.2$-$5138
+    and HESS\,J1614$-$518. Plot (c) shows 2FGL\,J1632.4$-$4753c
+    and HESS\,J1632$-$478. Plot (d) shows 2FGL\,J1837.3$-$0700c
+    and HESS\,J1837$-$069. The H.E.S.S. data points are from
+    \citep{hess_plane_survey} Both LAT and H.E.S.S. spectral errors are
+    statistical only.}
     \label{hess_seds}
@@
       % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v2/run.py
-      \caption{A plot of all spatially extended sources detected by the LAT
+      \caption{A plot of the 21
+      spatially extended sources detected by the LAT
       in the \gev energy range
       with two years of data.  The twelve extended sources included in
-      2FGL are indicated by the circular markers (colored red in the online
-      version).  The nine new extended sources analyzed in this paper are
-      the triangular markers (colored orange in the online version).}
+      2FGL are represented by the circular markers (colored red in the online
+      version).  The nine new extended sources are represented by
+      the triangular markers (colored orange).}
 \label{allsky_extended_sources}
@@
     \caption{
-    A comparison of the \gev and \tev sizes of LAT extended
-    sources detected by \tev instruments.  The \tev extensions
-    of W30, 2FGL\,J1837.3$-$0700c, 2FGL\,J1632.4$-$4753c,
-    2FGL\,J1615.0$-$5051, and 2FGL\,J1615.2$-$5138 \citep{hess_plane_survey}.
-    The \tev extensions of MSH\,15$-$52, HESS\,J1825$-$137, Vela X,
-    Vela Jr., RX\,J1713.7$-$3946 and W28 are from 
-    \citep{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
-    The \tev extension of IC443 is from \citep{ic443_veritas}
-    and W51c is from \citep{w51c_with_magic_at_fermi_symposium}.
-    The LAT extension of Vela X is from \citep{velax}.  Except for 
-RX\,J1713.7$-$3946 Vela Jr., the \tev sources were fit assuming a 2D Gaussian
-    surface brightness so the plotted \gev and \tev extensions were first
-    converted to \rsixeight (see Section~\ref{compare_source_size}).
-    Because of their large size, the shape of RX\,J1713.7$-$3946 and Vela Jr.
-    were not directly fit in \tev. Here, we take their
-    sizes to be the same as the LAT size and 
-    do not converted it to \rsixeight. The LAT extension errors are
-    the statistical and systematic errors added in quadrature. The \tev size of MSH\,15$-$52, HESS\,J1614$-$518,
-    HESS\,J1632$-$478, and HESS\,J1837$-$069 have only been reported with
-    an elliptical 2D Gaussian fit and so the plotted size is the average
-    of semi-major and semi-minor axis.
+    A comparison of the size of extended sources detected at
+    both \gev and \tev energies.  The \tev extensions of W30,
+    2FGL\,J1837.3$-$0700c, 2FGL\,J1632.4$-$4753c, 2FGL\,J1615.0$-$5051,
+    and 2FGL\,J1615.2$-$5138 are from \cite{hess_plane_survey}.
+    The \tev extensions of MSH\,15$-$52, HESS\,J1825$-$137,
+    Vela X, Vela Jr., RX\,J1713.7$-$3946 and W28 are from
+    \cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
+    The \tev extension of IC443 is from \cite{ic443_veritas} and
+    W51c is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev
+    size of MSH\,15$-$52, HESS\,J1614$-$518, HESS\,J1632$-$478, and
+    HESS\,J1837$-$069 have only been reported with an elliptical 2D
+    Gaussian fit and so the assumed size is the average of the semi-major
+    and semi-minor axis.
+    The LAT extension of
+    Vela X is from \cite{velax}.  Except for RX\,J1713.7$-$3946 Vela Jr.,
+    the \tev sources were fit assuming a 2D Gaussian surface brightness
+    so the plotted \gev and \tev extensions were first converted to
+    \rsixeight (see Section~\ref{compare_source_size}).  Because of
+    their large size, the shape of RX\,J1713.7$-$3946 and Vela Jr.
+    were not directly fit in \tev energies. Here, we take their sizes to be the
+    same as the LAT size and do not converted them to \rsixeight. The LAT
+    extension errors are the statistical and systematic errors added
+    in quadrature. 
 }\label{gev_vs_tev_plot}
@@
     \caption{
-    The distribution of the \gev size of the 22 extended LAT 
-    sources (colored blue in the electronic version) and
-    the \tev size of the 42 extended H.E.S.S. sources
-    (colored red in the electronic version).
-    The extension of the LAT sources comes from
-    Table~\ref{known_extended_sources}, Table~\ref{new_ext_srcs_table},
-    and from \cite{velax}. 
-    The \tev extension of
-    the extended H.E.S.S. sources comes from the H.E.S.S. Source
-    Catalog \citep{hesscat}.
-%   The \tev extension of
-%   the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-%   Catalog\footnote{
-%   The H.E.S.S. source catalog can be found at \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
-    Except for RX\,J1713.7$-$3946 and Vela Jr.,
-    the H.E.S.S. sources were fit with a 2D Gaussian surface
-    brightness model and
-    so the LAT and H.E.S.S. sizes are first converted to \rsixeight.
-    (see Section~\ref{compare_source_size}). Because the spatial
-    morphology of RX\,J1713.7$-$3946 and Vela Jr. is poorly matched by a
-    2D Gaussian surface brightness model, the \gev and
-    \tev extensions are included assuming a uniform surface brightness.
+    The distribution of the size of the 22 extended LAT sources
+    at \gev energies
+    (colored blue in the electronic version) and the size of the
+    42 extended H.E.S.S. sources at \tev energies
+    (colored red).  The size of Vela X
+    is taken from \cite{velax}.  Except for RX\,J1713.7$-$3946 and
+    Vela Jr., the H.E.S.S. sources were fit with a 2D Gaussian surface
+    brightness model so the LAT and H.E.S.S. sizes are first converted
+    to \rsixeight.  (see Section~\ref{compare_source_size}). Because
+    the spatial morphology of RX\,J1713.7$-$3946 and Vela Jr. is poorly
+    matched by a 2D Gaussian surface brightness model, the \gev and \tev
+    extensions are included assuming a uniform surface brightness.
     }\label{gev_vs_tev_histogram}
@@
     \caption{
-    The distribution of spectral indices of all 1873 2FGL sources 
-    (colored red in the electronic version)
-    and the spatially extended sources (colored blue in the electronic
-    version). The
-    spectral indices of LAT extended sources are taken from
-    Table~\ref{known_extended_sources} and \ref{new_ext_srcs_table}.
-    The index of Centarus A is taken to be 2.58 from 
-    \cite{second_cat} and the index of Vela X is taken to be 2.41
-    from \cite{velax}. }\label{compare_index_2FGL}
+    The distribution of spectral indices of the 1873 2FGL sources
+    (colored red in the electronic version) and the 21 spatially extended
+    sources (colored blue).  The index of Centarus A is taken from
+    \cite{second_cat} and the index of Vela X is taken from \cite{velax}.
+    }\label{compare_index_2FGL}
   \end{figure}

### 2011-08-27 extended_catalog/code/followup.py

@@ -81,21 +81,19 @@ if datafiles.__dict__.has_key('cache_ft1_dir'):
     roi.cache_ft1(cachefile)
 print t
 
-roi.toRegion('results_%s_%s.reg' % (spatial,savename))
-
 # if two point sources, use first hypothesis
 which=name if spatial != 'TwoPoints' else '%s (first)' % name
 
 if (args.maps or args.all or args.pointlike) and \
         'Pseudo' not in spatial:
-    roi.plot_counts_map(filename='map_%s_%s.png' % (spatial,savename),
-                    countsfile='counts_%s_%s.fits' % (spatial,savename),
-                    modelfile='model_%s_%s.fits' % (spatial,savename))
-
-    roi.plot_significance(filename='significance_%s_%s.png' % (spatial,savename))
 
     if spatial not in ['Background']:
 
+        print t
+        roi.plot_sources(which=which,filename='sources_%s_%s.png' % (spatial,savename))
+        print t
+        roi.plot_source(which=which,filename='source_%s_%s.png' % (spatial,savename))
+        print t
         # make slice & radial integral front events only.
         roi.plot_slice(which=which,filename='slice_%s_%s_gal.png' % (spatial,savename),conv_type=0,galactic=True)
         print t
@@ -103,12 +101,15 @@ if (args.maps or args.all or args.pointlike) and \
         print t
         roi.plot_radial_integral(which=which,filename='radial_%s_%s.png' % (spatial,savename),conv_type=0)
         print t
-        roi.plot_source(which=which,filename='source_%s_%s.png' % (spatial,savename))
-        print t
-        roi.plot_sources(which=which,filename='sources_%s_%s.png' % (spatial,savename))
-        print t
         roi.plot_model(which=which,filename='model_%s_%s.png' % (spatial,savename))
-        print t
+
+    print t
+    roi.plot_counts_map(filename='map_%s_%s.png' % (spatial,savename),
+                    countsfile='counts_%s_%s.fits' % (spatial,savename),
+                    modelfile='model_%s_%s.fits' % (spatial,savename))
+
+    print t
+    roi.plot_significance(filename='significance_%s_%s.png' % (spatial,savename))
 
 if args.sed or args.all or args.pointlike:
     if spatial not in ['Background' ]:

### 2011-08-27 pointlike/lande_roi.py

@@ -111,58 +111,6 @@ def merge_dict(first,second):
     return ret
 
 
-class OldCatalog2FGL(FermiCatalog):
-    """ Quick hack to load in new 2FGL and get correct extended sources. """
-    def __init__(self,point_catalog,extended_archive,**kwargs):
- 
-        super(OldCatalog2FGL,self).__init__(point_catalog,**kwargs)
-
-        self.extended_cat = ExtendedSourceCatalog(extended_archive)
-
-        # kludge
-        if os.path.basename(point_catalog)=='24M7_uw40.fits' and \
-                os.path.basename(extended_archive) == 'Extended_archive_v06':
-            self.extended_cat.names[self.extended_cat.names=='HESS J1825-137']='HESSJ1825-137'
-
-        # This is an important sanity check to make sure that the extended
-        # archive is consistent with the catalog file.
-        if not set(self.extended_cat.names).issubset(set(self.names)):
-            difference=list(set(self.extended_cat.names).difference(set(self.names)))
-            print "Warning: Extended Sources %s found in extended catalog but not in catalog file" % difference
-
-
-    def get_sources(self,*args,**kwargs):
-        """ Returns a list with mixed point & extended sources. """
-
-        sources=super(OldCatalog2FGL,self).get_sources(*args,**kwargs)
-
-        for i,source in enumerate(sources):
-
-            if source.name in self.extended_cat.names:
-                index = np.where(self.extended_cat.names==source.name)[0][0]
-
-                sources[i] = ExtendedSource(name=source.name,
-                    model=source.model,
-                    spatial_model = self.extended_cat.spatial_models[index])
-
-        return sources
-
-    def merge_lists(self,*args,**kwargs):
-        """ Merge other sources with the catalog sources. Note that since get_sources
-            mixes the catalog point & extended sources, 
-            the return of merge_lists is also mixed but correctly prunes out extended
-            catalog sources which interfer with user sources. At the end of the function,
-            we must resort out the point & diffuse sources. """
-
-
-        point,diffuse = super(OldCatalog2FGL,self).merge_lists(*args,**kwargs)
-
-        sources = point + diffuse
-
-        point = [ i for i in sources if isinstance(i,PointSource)]
[…]

### 2011-08-28 extended_catalog/collaboration_meeting_presentation/collaboration_meeting_presentation.tex
collaboration meeting presentation

\documentclass[12pt]{beamer}
\usetheme[navbar=false, bkgimage=false, shadow=true]{Fermi}
\usepackage{amsmath}
\usepackage{xspace}

\newcommand{\fermi}{\textit{Fermi}\xspace}

\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight
Data}
%\subtitle{\ldots}

\author{Joshua Lande, Markus Ackermann, Stefan Funk}
\institute{SLAC/Stanford}
\email{joshualande@gmail.com}
\date{August 25, 2011}

\begin{document}

\fermititle

\begin{frame}{Overview}
  \begin{itemize}
    \item Category II Paper
    \item Contact Authors: J. Lande, 
    \item Full author list being finalized
    \item 
  \end{itemize}
\end{frame}

\end{document}

### 2011-08-28 extended_catalog/paper/extended_catalog.tex
collaboration meeting presentation

@@
 M.~Ackermann (???),
-A.~Allafort\altaffilmark{2},
-M.-H.~Grondin\altaffilmark{53},
+%A.~Allafort\altaffilmark{2},
+%M.-H.~Grondin\altaffilmark{53},
 % Keith Bechtol
@@
 (LAT) on the {\em \fermi Gamma-ray Space Telescope} (\fermi) has
-detected five SNRs which are significantly extended
-at \gev energies: IC443, W28, W44, W51C, and RX\,J1713.7$-$3946
-\citep{ic443,w28,w44,w51c,rx_j1713_lat}. In addition, three extended
+detected seven SNRs which are significantly extended
+at \gev energies: 
+W51C, W30, 
+IC443, W28, W44, RX\,J1713.7$-$3946,
+and the Cygnus Loop
+\citep{w51c,castro_and_slane_2010,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, three extended
 PWNe were detected as being extended: MSH\,15$-$52, Vela~X, and
@@
 at \gev energies are positionally coincident with sources that exhibit
-extension at other wavelengths. These sources could be expected to be spatially
+extension at other wavelengths, large enough to be spatially
 resolvable by the LAT at \gev energies.
@@
 
-The LAT is a pair conversion telescope that been surveying the
+The LAT is a pair conversion telescope that has been surveying the
 $\gamma$-ray sky since 2008 June.  The LAT has broad energy coverage
@@
 \hl{
-Figure~\ref{all_sensitivity} shows the flux threshold
-as a function of source extension for different background levels 
-($1\times$,
-$10\times$, 
-and $100\times$ the nominal background), different spectral indices, and
-two different energy bands (1 \gev to 100 \gev and 10 \gev to 100 \gev).  The detection
-threshold is higher for sources in regions of higher background.  For a
-fixed 1 \gev to 100 \gev or 10 \gev to 100 \gev flux, the LAT's detection threshold
-only weakly depends upon the spectral index.  This effect is most
-pronounced when using only photons with energies above 10 \gev.  Overlaid
-on Figure~\ref{all_sensitivity} are the LAT detected extended sources
-that will be discussed in Sections~\ref{validate_known}
-and \ref{new_ext_srcs_section}.  The extension thresholds are tabulated
-in Table~\ref{all_sensitivity_table}.
+Figure~\ref{all_sensitivity} shows the flux threshold as a function of
+source extension for different background levels ($1\times$, $10\times$,
+and $100\times$ the nominal background), different spectral indices,
+and two different energy bands (1 \gev to 100 \gev and 10 \gev to
+100 \gev).  The detection threshold is higher for sources in regions of
+higher background.  When studying sources only at energies above 1 \gev,
+the LAT's detection threshold (defined as the 1 \gev to 100 \gev flux at
+which $\langle\tsext\rangle=16$) depends less strongly on the source's
+spectral index. The index dependence of the detection threshold is
+even weaker when considering only photons with energies above 10 \gev.
+Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
+sources that will be discussed in Sections~\ref{validate_known} and
+\ref{new_ext_srcs_section}.  The extension thresholds are tabulated in
+Table~\ref{all_sensitivity_table}.
 
@@
 We first present on our analysis of the twelve extended sources
-included in 2FGL.
-\citep{second_cat}.
-Six extended SNRs were included in 2FGL: IC443, W28, W30, W44, W51C, and the
-Cygnus Loop \citep{ic443,w28,w44,w51c,cygnus_loop_lat}.\footnote{A
-detailed publication by the LAT
-Collaboration about W30 is still in preparation.}
+included in 2FGL.  \citep{second_cat}.  Six extended SNRs were
+included in 2FGL: W51C, IC443, W28, W30, W44, and the Cygnus Loop
+\citep{w51c,ic443,w28,w44,cygnus_loop_lat}.\footnote{A detailed
+publication by the LAT Collaboration about W30 is still in preparation.}
 \gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
-Using 1 \gev to 100 \gev photons, our analysis significantly detected the
-extension of all six SNRs.
+Using 1 \gev to 100 \gev photons, our analysis significantly detected
+the extension of all six SNRs.
 % 2 galaxies
@@
 counts map of this source
-and Figure~\ref{snr_seds} shows the LAT spectrum of it.
+and Figure~\ref{snr_seds} shows its spectrum.
 }
@@
 \hl{
-This extended source is spatially coincident with the middle-aged
-SNR Puppis A.  Puppis A has been studied in detail in radio
-(\cite{puppis_a_vla}, and references therein) and  X-ray 
-(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
-Mosaic \rosat observations of Puppis A produced the highest
-resolution X-ray image of this source
-and contours corresponding to this
-image are overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the
-inferred size at \gev energies \citep{rosat_puppis_a}.
-Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
-which leads to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.
-
+This extended source is spatially coincident with the
+middle-aged SNR Puppis A.  Puppis A has been studied in detail
+in radio (\cite{puppis_a_vla}, and references therein) and  X-ray
+(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein) Mosaic
+\rosat observations of Puppis A produced the highest resolution X-ray
+image of this source and contours corresponding to this image are
+overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the inferred
+size at \gev energies \citep{rosat_puppis_a}.  Puppis A's distance
+was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} which leads
+to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.
 No molecular clouds have been observed directly adjacent to Puppis A
-\citep{co_eastern_puppis_a}.
-This is similar to the LAT detected SNR the Cyngus Loop \citep{cygnus_loop_lat}.
-The luminosity of Puppis A is also smaller than that of 
-other SNRs believed to interact with molecular clouds
+\citep{co_eastern_puppis_a}.  This is similar to the LAT detected Cyngus
+Loop SNR \citep{cygnus_loop_lat}.  The luminosity of Puppis A is also
+smaller than that of other SNRs believed to interact with molecular clouds
 \citep{w51c,ic443,w44,w28,w49b_lat}.
-The \gev emission could therefore be explained by the interaction
-of accelerated particles by interstellar matter or fields, similar
-to the emission mechanism suggested for the Cygnus Loop SNR
 \citep{cygnus_loop_lat}.
@@
 spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}
-so this source might represent an inadequacy in the diffuse
-$\gamma$-ray model.
+so this source might 
+represent $\gamma$-ray emission from the interactions of cosmic rays with
+interstellar gas which has not been accounted for in the LAT diffuse
+emission model.
 }
@@
 size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
-Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0$-$5051
-connects smoothly to the H.E.S.S spectrum of HESS\,J1616$-$508.
+Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1615.0$-$5051
+at \gev energies
+connects smoothly to the spectrum of HESS\,J1616$-$508 at \tev
+energies.
 
@@
 $\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds} shows
-that the LAT spectrum of 2FGL\,J1615.2$-$5138 connects smoothly to
-the H.E.S.S spectrum of HESS\,J1614$-$518.  Further data collected by
+that the spectrum of 2FGL\,J1615.2$-$5138 at \gev energies
+connects smoothly to
+the spectrum of HESS\,J1614$-$518 at \tev energies.  Further data collected by
 H.E.S.S. in 2007 helped to resolve a double peaked structure in the
@@
 the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
-shows that the LAT spectrum of 2FGL\,J1635.4$-$4717c connects smoothly to
-the H.E.S.S spectrum of HESS\,J1632$-$478.
+shows that the spectrum of 2FGL\,J1635.4$-$4717c at \gev energies
+connects smoothly to
+the spectrum of HESS\,J1632$-$478 at \tev energies.
 
@@
 \citep{Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751,asca_plane_survey},
-but this source is suspected to be an galactic X-Ray Binary so the $\gamma$-ray
+but this source is suspected to be a galactic X-Ray Binary so the $\gamma$-ray
 extension disfavors the association.  Further observations by
@@
 \citep{most_survey_galactic_plane}.  The positional match argues for a
-single synchrotron processes producing X-ray and \gev and \tev radiation,
+single synchrotron process producing X-ray and \gev and \tev radiation,
 likely due to a PWNe.  The increased size at \tev energies
@@
 $\rsixeight=0\fdg29\pm0\fdg07$.  the size difference is not significant
-(less than 2 sigma).  Figure~\ref{hess_seds} shows that the LAT spectrum
-connects smoothly to the H.E.S.S spectrum of HESS\,J1837$-$069.
+(less than 2 sigma).  Figure~\ref{hess_seds} shows that the spectrum
+of 2FGL\,J1837.3$-$0700c at \gev energies
+connects smoothly to the spectrum of HESS\,J1837$-$069
+at \tev energies.
 
@@
 \citep{einstein_galactic_plane_survey,hard_x-ray_asca,integral_AX_J1838.0-0655,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
-This source was discovery by RXTE to be a pulsar sufficiently
+This source was discovered by RXTE to be a pulsar sufficiently
 luminous to power the \tev emission.  AX\,J1838.0$-$0655 was spatially
@@
 
-The source 2FGL\,J2021.5+4026 was found 
-to have an extension of $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
-with an extension significance of $\tsext=116.4$
-using 10 \gev to 100 \gev photons.  This source was
-fit to a position of $(l,b)=(78\fdg18,2\fdg19)$.  This source
-is coincident with the one-year catalog source 1FGL\,J2020.0+4049.
-\hl{
-Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source.
-and Figure~\ref{snr_seds} shows that the LAT spectrum of it.
+The source 2FGL\,J2021.5+4026 was found to have an extension of
+$0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
+of $\tsext=116.4$ using 10 \gev to 100 \gev photons.  This source
+was fit to a position of $(l,b)=(78\fdg18,2\fdg19)$.  This source is
+coincident with the one-year catalog source 1FGL\,J2020.0+4049. \hl{
+Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source
+and Figure~\ref{snr_seds} shows its spectrum.  
 }
@@
 spatially coincident with the $\gamma$-Cygni SNR and has been speculated
-to be be the interaction of accelerated particles in the SNR interacting
+to originate from 
+the interaction of accelerated particles in the SNR interacting
 with dense molecular clouds \citep{pollock_1985,gaisser_1998}.  But this
@@
 shape of the twelve extended sources in 2FGL.  The 21 extended
-LAT sources are located close to the Galactic plane and plotted in
+LAT sources are located close to the Galactic plane 
+and their localizations shown in
 Figure~\ref{allsky_extended_sources}.  Most of the extended sources are
@@
 field of view and all-sky coverage, the LAT can more easily measure
-larger sources including the LMC and SMC.  On the other hand, the smaller
+larger sources including the LMC and SMC.  On the other hand, the 
+better
 angular resolution of Air Cherenkov detectors allows them to measure a
@@
 energies above 10 \gev.  Figure~\ref{hess_seds} shows that the
-\gev spectral of
-four of these sources (2FGL\,J1615.0$-$5051, 2FGL\,J1615.2$-$5138,
+spectra of four of these sources (2FGL\,J1615.0$-$5051, 2FGL\,J1615.2$-$5138,
 2FGL\,J1632.4$-$4753c, and 2FGL\,J1837.3$-$0700c)  
-connect smoothly to their \tev counterparts. This is also true of Vela
+at \gev energies
+connect smoothly to their H.E.S.S. counterparts at \tev
+energies. This is also true of Vela
 Jr., HESS\,J1825$-$137 \citep{fermi_hess_j1825}, RX\,J1713.7$-$3946
@@
 currently unidentified and further multi-wavelength follow-up observations
-will be necessary to understand these particle accelerators. But \gev
-observations of these \tev sources in many cases can help to constrain
-handronic and leptonic models of these sources and, especially if their
-spectra can be extended to lower energies, help to understand the emission
-mechanisms producing these high energy $\gamma$-rays.  
+will be necessary to understand these particle accelerators.  But the
+extension of the spectrum of these \tev sources towards lower energies
+by LAT observations can help to determine the origin and nature of the
+high-energy emission seen from these sources.
 }
@@
     these sources.
-    The LAT spectral errors are statistical only.}
+    The spectral errors are statistical only.}
     }

### 2011-08-28 extended_catalog/lande_ext_collab_august_2011/collaboration_meeting_presentation.tex
renaming

\documentclass[12pt]{beamer}
\usetheme[navbar=false, bkgimage=false, shadow=true]{Fermi}

\usepackage{graphicx}

\usepackage{amsmath}
\usepackage{xspace}
\usepackage{deluxetable}

\newcommand{\gtlike}{\ensuremath{\mathtt{gtlike}}\xspace}
\newcommand{\pointlike}{\ensuremath{\mathtt{pointlike}}\xspace}
\newcommand{\gtobssim}{\ensuremath{\mathtt{gtobssim}}\xspace}
\newcommand{\fermi}{\textit{Fermi}\xspace}

\newcommand{\glon}{\text{GLON}\xspace}
\newcommand{\glat}{\text{GLAT}\xspace}
\newcommand{\ts}{\text{TS}\xspace}
\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
\newcommand{\phflux}{\ensuremath{\text{ph}\ \text{cm}^{-2}\,\text{s}^{-1}}\xspace}
\newcommand{\mev}{\text{MeV}\xspace}
\newcommand{\gev}{\text{GeV}\xspace}

\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight
Data}
%\subtitle{\ldots}

\author{Joshua Lande}
\institute{SLAC/Stanford}
\email{joshualande@gmail.com}
\date{August 25, 2011}

\begin{document}

\fermititle

\begin{frame}{Overview}
  \begin{itemize}
    \item Category II Paper
    \item Contact Authors: J. Lande, M. Ackermann, S. Funk
    \item Full author list being finalized
    \item Internal Referees: Marianne Lemoine-Goumard and Johann Cohen-Tanugi
    \item Target Journal: ApJ
    \item Status (something about being submitted to internal referees XXXX)
  \end{itemize}
\end{frame}

\begin{frame}{Paper Outline}
  \begin{itemize}
    \item Description/validation of a new method (\pointlike) for analyzing extended sources.
    \item  Calculation of the LAT's sensitivity to spatially extended sources
    \item  Presentation of a new search for spatially extended sources:
      \begin{itemize}
        \item reanalyzing the extension of the 12 extended sources in 2FGL
        \item testing AGN from 2LAC for extension to validate the analysis
        \item presenting on the discovery/interpretation of several new extended sources not in 2FGL.
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Fig. 1}
  \begin{center}
    \includegraphics[scale=0.5]{../paper/ic443_plots/four_plots_ic443_color.eps}
  \end{center}
\end{frame}

\begin{frame}{Fig. 2}
  \begin{center}
    \includegraphics[scale=0.5]{../paper/mc_plots/compare_disk_gauss_color.eps}
  \end{center}
\end{frame}

\begin{frame}{Fig. 3}
  \begin{center}
    \includegraphics[scale=0.5]{../paper/mc_plots/ts_ext_emin_1000_color.eps}
  \end{center}
\end{frame}

\begin{frame}{Fig. 4}
  \begin{center}
    \includegraphics[scale=0.5]{../paper/mc_plots/index_sensitivity_color.eps}
  \end{center}
\end{frame}

\begin{frame}{Fig. 5}
  \begin{center}
    \includegraphics[scale=0.5]{../paper/mc_plots/all_sensitivity_color.eps}
  \end{center}
\end{frame}

\begin{frame}{Fig. 6}
  \begin{center}
    \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
  \end{center}
\end{frame}

\begin{frame}{Fig. 6}
  \begin{center}
    \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
  \end{center}
\end{frame}

\begin{frame}
  \begin{center}
    \includegraphics[scale=0.5]{tables/table3.eps}
  \end{center}
\end{frame}

\begin{frame}
  \begin{center}
    \includegraphics[scale=0.5]{tables/table4.eps}
  \end{center}
\end{frame}

\begin{frame}
  \begin{center}
    \includegraphics[scale=0.5]{tables/table5.eps}
  \end{center}
\end{frame}

\end{document}

### 2011-08-28 extended_catalog/lande_ext_collab_august_2011/lande_cat_ext_collab_august_2011.tex
better makefile

--- 2011-08-28 extended_catalog/lande_ext_collab_august_2011/collaboration_meeting_presentation.tex
@@
 
-\newcommand{\glon}{\text{GLON}\xspace}
-\newcommand{\glat}{\text{GLAT}\xspace}
-\newcommand{\ts}{\text{TS}\xspace}
-\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
-\newcommand{\phflux}{\ensuremath{\text{ph}\ \text{cm}^{-2}\,\text{s}^{-1}}\xspace}
-\newcommand{\mev}{\text{MeV}\xspace}
-\newcommand{\gev}{\text{GeV}\xspace}
-
 \title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight
@@
 
-\fermititle
-
-\begin{frame}{Overview}
-  \begin{itemize}
-    \item Category II Paper
-    \item Contact Authors: J. Lande, M. Ackermann, S. Funk
-    \item Full author list being finalized
-    \item Internal Referees: Marianne Lemoine-Goumard and Johann Cohen-Tanugi
-    \item Target Journal: ApJ
-    \item Status (something about being submitted to internal referees XXXX)
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Paper Outline}
-  \begin{itemize}
-    \item Description/validation of a new method (\pointlike) for analyzing extended sources.
-    \item  Calculation of the LAT's sensitivity to spatially extended sources
-    \item  Presentation of a new search for spatially extended sources:
-      \begin{itemize}
-        \item reanalyzing the extension of the 12 extended sources in 2FGL
-        \item testing AGN from 2LAC for extension to validate the analysis
-        \item presenting on the discovery/interpretation of several new extended sources not in 2FGL.
-      \end{itemize}
-  \end{itemize}
-\end{frame}
+\include{introduction}
 

### 2011-08-28 extended_catalog/lande_ext_collab_august_2011/introduction.tex
better

--- 2011-08-28 extended_catalog/lande_ext_collab_august_2011/collaboration_meeting_presentation.tex
@@
-\documentclass[12pt]{beamer}
-\usetheme[navbar=false, bkgimage=false, shadow=true]{Fermi}
-
-\usepackage{graphicx}
-
-\usepackage{amsmath}
-\usepackage{xspace}
-\usepackage{deluxetable}
-
-\newcommand{\gtlike}{\ensuremath{\mathtt{gtlike}}\xspace}
-\newcommand{\pointlike}{\ensuremath{\mathtt{pointlike}}\xspace}
-\newcommand{\gtobssim}{\ensuremath{\mathtt{gtobssim}}\xspace}
-\newcommand{\fermi}{\textit{Fermi}\xspace}
-
-\newcommand{\glon}{\text{GLON}\xspace}
-\newcommand{\glat}{\text{GLAT}\xspace}
-\newcommand{\ts}{\text{TS}\xspace}
-\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
-\newcommand{\phflux}{\ensuremath{\text{ph}\ \text{cm}^{-2}\,\text{s}^{-1}}\xspace}
-\newcommand{\mev}{\text{MeV}\xspace}
-\newcommand{\gev}{\text{GeV}\xspace}
-
-\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight
-Data}
-%\subtitle{\ldots}
-
-\author{Joshua Lande}
-\institute{SLAC/Stanford}
-\email{joshualande@gmail.com}
-\date{August 25, 2011}
-
-\begin{document}
-
 \fermititle
@@
 \end{frame}
-
-\begin{frame}{Fig. 1}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/ic443_plots/four_plots_ic443_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 2}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/compare_disk_gauss_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 3}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/ts_ext_emin_1000_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 4}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/index_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 5}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/all_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 6}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 6}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}
-  \begin{center}
-    \includegraphics[scale=0.5]{tables/table3.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}
-  \begin{center}
-    \includegraphics[scale=0.5]{tables/table4.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}
-  \begin{center}
-    \includegraphics[scale=0.5]{tables/table5.eps}
-  \end{center}
-\end{frame}
-
-\end{document}

### 2011-08-28 extended_catalog/lande_ext_collab_august_2011/lande_gal_ext_collab_august_2011.tex
better

--- 2011-08-28 extended_catalog/lande_ext_collab_august_2011/lande_cat_ext_collab_august_2011.tex
@@
 
-\begin{frame}{Fig. 1}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/ic443_plots/four_plots_ic443_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 2}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/compare_disk_gauss_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 3}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/ts_ext_emin_1000_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 4}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/index_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 5}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/all_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 6}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Fig. 6}
-  \begin{center}
-    \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
-  \end{center}
-\end{frame}
-
 \begin{frame}
@@
 
-\begin{frame}
-  \begin{center}
-    \includegraphics[scale=0.5]{tables/table5.eps}
-  \end{center}
-\end{frame}
-
 \end{document}

### 2011-08-28 extended_catalog/paper/extended_catalog.tex
renaming
josh revisions

@@
 \newcommand{\tev}{\text{TeV}\xspace}
-\newcommand{\sr}{\text{sr}\xspace}
 \newcommand{\s}{\text{s}\xspace}
@@
 \newcommand{\km}{\text{km}\xspace}
-\newcommand{\phflux}{\ensuremath{\ph\ \cm^{-2}\s^{-1}}\xspace}
+\newcommand{\phflux}{\ensuremath{\text{ph}\ \text{cm}^{-2}\,\text{s}^{-1}}\xspace}
 \newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
@@
 \newcommand{\minuit}{\ensuremath{\mathtt{minuit}}\xspace}
+
+\newcommand{\degree}{^\circ\xspace}
 
@@
 sources detected at \tev energies (most notably the $\gamma$-ray binaries
-LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI}
+LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI},
 HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
 have no detectable extension.  High-energy $\gamma$-rays from
-these sources are produced by the decay of $\pi^0$s produced by hadronic
+these sources originate by the decay of $\pi^0$s produced by hadronic
 interactions with interstellar matter and by relativistic electrons
@@
 $\gamma$-ray sky since 2008 June.  The LAT has broad energy coverage
-(20 \mev to $>300$ \gev), wide field of view ($\sim 2.4 \sr$), and large
+(20 \mev to $>300$ \gev), wide field of view ($\sim 2.4$ sr), and large
 effective area ($\sim 8000\ \cm^2$ at $>1 \gev$).  
@@
 a new systematic method for analyzing spatially extended LAT sources. In
-Section~\ref{monte_carlo_validation} we demonstrate that this method
+Section~\ref{monte_carlo_validation}, we demonstrate that this method
 can be used to test the statistical significance of
@@
 the LAT's detection threshold to resolve the extension of a source.
-In Section~\ref{extended_source_search_method} we describe a search for
+In Section~\ref{extended_source_search_method}, we describe a search for
 new spatially extended LAT sources and in Section~\ref{validate_known}
@@
 demonstrate that our detection method does not misidentify
-point sources as being extended 
+point-like sources as being extended 
 by testing the extension of active
@@
 information about the performance of the LAT can be found at the \fermi
-Science Support Center (FSSC,\url{http://fermi.gsfc.nasa.gov}).} However,
+Science Support Center (FSSC, \url{http://fermi.gsfc.nasa.gov}).} However,
 since most high energy astrophysical sources have spectra that decrease
 rapidly with increasing energy, the improved resolution of the higher
-energy photons is offset by their low statistics. Therefore sophisticated
-analysis techniques are required to maximize our sensitivity
+energy photons is typically offset by their low statistics. Therefore sophisticated
+analysis techniques are required to maximize the LATs sensitivity
 to these extended sources.
@@
 A new analysis tool has been developed to address the unique requirements
-for studying spatially extended sources with the LAT. The tool performs
-a maximum likelihood analysis in which the Poisson likelihood to find
+for studying spatially extended sources with the LAT.
+The Poisson likelihood to find
 the observing counts is maximized given a parametrized spatial and
 spectral model of the source and its surrounding region.  The sky is
-divided into cubes in space and energy using the healpix representation
+divided into cubes of space and energy using the healpix representation
 of the sky \citep{healpix} and the likelihood is maximized over all bins
@@
 which is important for our catalog scan and for being able
-to perform large-scale Monte Carlo simulations to validate the tool.
+to perform large-scale Monte Carlo simulations to validate the analysis.
 Details on the \pointlike package can be
@@
 
-In \pointlike, it is assumed that the spatial and spectral
-model of an extended source are separable, i.e. that the source
-model $M(l,b,E)=S(l,b)\times X(E)$ where $S(l,b)$ is the spatial
-distribution and $X(E)$ is the spectral distribution.  To fit an extended source,
-\pointlike convolves the extended source shape with the PSF (as a
-function of energy) and uses the \minuit library 
-\citep{minuit_documentation}
-to maximize the
-likelihood by simultaneously varying the position and extension of
-the source.  As will be described in
-Section~\ref{monte_carlo_validation}, simultaneously fitting the position
-and extension is important to correctly calculate the statistical
-significance of the detection of extension.  For each position and
-extension, the spectral parameters of the sky model are refit.  To avoid
-projection effects, the fitted source position parameters are not the
-source's longitude and latitude but instead the source's displacement
-in a rotated reference frame.
+In \pointlike, it is assumed that the spatial and spectral model
+of an extended source are separable, i.e. that the source model
+$M(l,b,E)=S(l,b)\times X(E)$ where $S(l,b)$ is the spatial distribution
+and $X(E)$ is the spectral distribution.  To fit an extended source,
+\pointlike convolves the extended source shape with the PSF (as a function
+of energy) and uses the \minuit library \citep{minuit_documentation}
+to maximize the likelihood by simultaneously varying the position,
+extension, and spectrum of the source.  As will be described in
+Section~\ref{monte_carlo_validation}, simultaneously fitting the
+position, extension, and spectrum is important to correctly calculate
+the statistical significance of the detection of extension of a source.
+To avoid projection effects, the source's longitude and latitude are
+not directly fit but instead the source's displacement in a rotated
+reference frame.
 
 The significance of the extension of a source can be calculated from the
-likelihood ratio test of a model with a spatially extended source and
-a model with a point-like source. The test statistic for this procedure
+likelihood ratio test of a hypothesis with a spatially extended source and
+a hypothesis with a point-like source. The test statistic for this procedure
 is defined as
@@
 \pointlike calculates \tsext by fitting a source first with a spatially
-extended model and then as a point source.  The interpretation
+extended model and then as a point-like source.  The interpretation
 of \tsext in terms of a statistical significance is discussed in
@@
 For extended sources with an assumed radially symmetric shape,
-we can optimize the calculation by performing one
+we optimized the calculation by performing one
 of the integrals analytically.
@@
 There will always be a small numerical discrepancy between the expected
-photon distribution derived from a true point source and a very small
+photon distribution derived from a true point-like source and a very small
 extended source due to numerical error in the convolution.  In most
@@
 likelihood has fallen by \onehalf, corresponding to a $1\sigma$ error
-\citep{Statistical_methods_book}.  This method is shown schematically in
-Figure~\ref{four_plots_ic443} which shows the change in the log of the
+\citep{Statistical_methods_book}.  Figure~\ref{four_plots_ic443}
+demonstrates this method by showing the change in the log of the
 likelihood when varying the extension of the SNR IC443.  The localization
@@
 There is a degeneracy between a spatially extended source and multiple
-point sources separated by angular distances comparable to or smaller than
+point-like  sources separated by angular distances comparable to or smaller than
 the size of the LAT PSF.  To assess the possibility of source confusion,
-we use \pointlike to simultaneously fit the position of two point sources
+we use \pointlike to simultaneously fit the position of two point-like sources
 in the region of extended source candidates.
@@
 We define \tsinc as twice the increase in the log of the likelihood fitting the
-region as two point sources compared to fitting the region as one point
+region as two point-like sources compared to fitting the region as one point-like
 source: 
@@
 \tsinc is not a calibrated test, we find the cases $\tsinc \ll \tsext$
-or $\tsinc\gg\tsext$ suggestive and we only consider a source to be
+and $\tsinc\gg\tsext$ suggestive and we only consider a source to be
 extended if $\tsext>\tsinc$.
 Similar to the case of extended sources described in Section~\ref{gtlike_crosscheck},
-the spectra of the two point sources can be refit using \gtlike.
+the spectra of the two point-like sources can be refit using \gtlike.
 We quote the spectral values obtained from \gtlike using the best fit
@@
 \end{equation}
-or a uniform disk
+or a uniform surface brightness
 \begin{equation}\label{disk_pdf}
@@
     \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
-    0                      & x^2+y^2>\sigma^2
+    0                      & x^2+y^2>\sigma^2.
   \end{cases}
 \end{equation}
-Although these shapes are significantly different, when convolved
-with the PSF, their profiles are very similar.  
-This is demonstrated in 
-Figure~\ref{compare_disk_gauss}
-by showing $I_\text{src}$, the PSF, and the PDF for
-a radially symmetric uniform brightness and a Gaussian surface brightness of size 0\fdg5.\footnote{To
-allow a valid comparison between Gaussian and disk shaped morphologies,
-we define the source size for this test as the radius containing
+Although these shapes are significantly different, 
+Figure~\ref{compare_disk_gauss} shows the their PDF 
+are very similar for an example source of size
+0\fdg5.\footnote{To
+allow a valid comparison between the Gaussian and the uniform surface
+brightness morphologies,
+we define here the source size (0\fdg5) 
+as the radius containing
 68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
@@
 is defined in Equation~\ref{gauss_pdf} and
-Equation~\ref{disk_pdf} respectively.} This plot shows that the LAT 
-has little sensitivity to
-the exact structure of an extended source.
-Therefore, in our
-search for extended sources, we use only a uniform
-disk as our spatial extension shape. We then quote the radius of the
-disk edge as the size of the source.
+Equation~\ref{disk_pdf} respectively.} The LAT 
+has little sensitivity /thereto the exact structure of extended source.
+Therefore, in our search for extended sources we used only a uniform
+surface brightness as our spatial extension shape. We quote the radius
+of the edge ($\sigma$) as the size of the source.
 
@@
 
-We test the false detection probability of \pointlike by fitting the extension of
+We test the false detection probability of for the
+extended source test by fitting the extension of
 point-like sources.
@@
 on the edge of parameter space and the model hypothesis
-adding a single degree of freedom. It is plausible to
+adding a single degree of freedom
+and leads to the often quoted result that the square root
+of the test statistic is the number of $\sigma$ of
+the detection. It is plausible to
 expect a similar distribution of the test statistic
@@
 $r<0$ being unphysical).
-To validate this claim, we performed Monte Carlo
+We performed Monte Carlo
 simulations
 to calculate empirical distributions for $\tsext$ and
-compared them to Equation~\ref{ts_ext_distribution}.
-
-We simulated point sources with various spectral forms using
-the LAT on-orbit simulation tool, 
-\gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit them with \pointlike using both point
-and extended source hypotheses.  These point sources were simulated with a power-law
+we compared them to Equation~\ref{ts_ext_distribution}.
+
+We simulated point-like sources with various spectral forms using
+the LAT on-orbit simulation tool
+\gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit the sources
+with \pointlike using both point-like
+and extended source hypotheses.  These point-like sources were simulated with a power-law
 spectral model with integrated fluxes above 100 \mev ranging from $3\times10^{-9}$ 
@@
 indices ranging from 1.5 to 3 in four discrete steps.  These values
-were picked to to represent typical source parameters of LAT-detected
-sources. The point sources were simulated on top of an isotropic
+were picked to represent typical source parameters of LAT-detected
+sources. The point-like sources were simulated on top of an isotropic
 background with an integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux
@@
 representative livetime fraction of 0.8.  The reconstruction was performed
-using 1 \gev to 100 \gev photons and the Pass~7\_V6 (P7\_V6) Source Instrument
+using photons with energies between 1 \gev to 100 \gev 
+and the Pass~7\_V6 (P7\_V6) Source Instrument
 Response Function (IRFs, \cite{lat_on_orbit_psf}).  For each 
-significantly detected point source ($\ts\ge25$), we used \pointlike
-to fit it as an extended source and calculate \tsext.
+significantly detected point-like source ($\ts\ge25$), we used \pointlike
+to fit the source as an extended source and calculate \tsext.
 
 For each set of spectral parameters, $\sim30,000$ statistically independent
-simulations were performed. For the dimmer spectral models, many of the
+simulations were performed. For dimmer spectral models, many of the
 simulations left the source undetected ($\ts<25$)
@@
 shows the different spectral models used in our study as well as the
-number of simulations.  The cumulative density of \tsext is plotted in
-Figure~\ref{ts_ext_mc}. The $\chi^2_1/2$ distribution of
-Equation~\ref{ts_ext_distribution} is overlaid for comparison.
+number of simulations and the average point-like source
+significance.  The cumulative density of \tsext is plotted in
+Figure~\ref{ts_ext_mc} and compared to the $\chi^2_1/2$ distribution of
+Equation~\ref{ts_ext_distribution}.
 
@@
 the empirical distributions lie to the left of the theoretical curve so
-using the theoretical distribution will lead to an underestimate of the
+using the theoretical distribution will often lead to an underestimate of the
 statistical significance of a detection. Therefore, we are confident that
-$\sqrt{\tsext}$ can be used as a conservative measure of the statistical
-significance of a source's extension and use it in the following analysis.
+\tsext can be used as a conservative measure of the statistical
+significance of a source's extension and we used it in the following analysis.
 
@@
 
-We calculated the LAT's detection threshold to detect that a spatially extended
-sources is extended. We define the detection threshold as the flux at which the value
+We calculated the LAT's threshold to detect that a spatially extended
+source is extended. We define the detection threshold as the flux at which the value
 of $\tsext$ averaged over many statistical realizations of a source
-is $\langle\tsext\rangle=16$, corresponding to a $4\sigma$ detection
-(see section~\ref{monte_carlo_validation}).
+is $\langle\tsext\rangle=16$, corresponding to a $4\sigma$ detection.
 
 We used a simulation setup similar to that described in
-Section~\ref{monte_carlo_validation}, but instead of point sources
+Section~\ref{monte_carlo_validation}, but instead of point-like sources
 we simulated extended
@@
 in 2FGL.
-Each extension and
+For each extension and
 spectral index, we selected a flux range which bracketed $\tsext=16$
 and performed an extension test for $>100$ independent realizations of
-ten flux values in this range.
+ten fluxes in the range.
 We calculated $\langle\tsext\rangle=16$ by fitting a line to the flux
-and $\tsext$ values in this narrow range.
+and $\tsext$ values in the narrow range.
 
 Figure~\ref{index_sensitivity} shows the threshold for sources of four
-spectral indices from 1.5 to 3 and extension varying from $\sigma=0\fdg1$
+spectral indices from 1.5 to 3 and extensions varying from $\sigma=0\fdg1$
 to $2\fdg0$.  The LAT's flux threshold for a significant detection
@@
 and also using only 1 \gev to 100 \gev photons.
-Except for very large ($>1\deg$) sources, our detection threshold is
+Except for very large ($>1\degree$) sources, our detection threshold is
 not substantially improved by including photons with energies between 100 \mev and
@@
 become increasingly important at low energy. For our extension search,
-we therefore use only photons with energies above 1 \gev.
+we therefore used only photons with energies above 1 \gev.
 
@@
 and $100\times$ the nominal background), different spectral indices,
-and two different energy bands (1 \gev to 100 \gev and 10 \gev to
+and two different energy ranges (1 \gev to 100 \gev and 10 \gev to
 100 \gev).  The detection threshold is higher for sources in regions of
@@
 Finally, Figure~\ref{time_sensitivity} shows the LAT's projected
-detection threshold to extension after 10 years against 10 times
+detection threshold to extension with a 10 year
+exposure against 10 times
 the isotropic background. This background is representative of the
@@
 
-We test all sources in 2FGL for spatial extension.
+We tested all sources in 2FGL for spatial extension.
 2FGL included
@@
 attempt was made to fit the extension of these sources. Other than these sources,
-all 2FGL sources were modeled as point sources and 2FGL did not attempt
-to resolve the extension of new sources.
+all 2FGL sources were modeled as point-like and 2FGL did no attempt
+to resolve their extension.
 
@@
 more susceptible to systematic errors arising from source confusion due
-to multiple point sources and modeling of the
+to multiple point-like sources and modeling of the
 Galactic diffuse emission. In addition, the Galactic diffuse emission
@@
 We also performed a search for extended sources using only 10 \gev to 100 \gev photons. 
-Even this approach tests the same
+Although this approach tests the same
 sources, it is complimentary because the Galactic diffuse
@@
 significantly detected at energies exclusively above 10 \gev. So we
-expect to be able to resolve harder sources in more complicated regions. The $>10$ \gev
+expect to be able to resolve harder sources in more complicated regions
+by restricting our analysis to higher energies. The $>10$ \gev
 analysis is
@@
 and a power-law spectral model.
-We used a circular $10\deg$ region of interest (ROI) centered on our source and
-included all catalog sources within $15\deg$ of the source of interest
+We used a circular $10\degree$ region of interest (ROI) centered on our source and
+included all catalog sources within $15\degree$ of the source of interest
 in our background model.
-We refit the spectral parameters of sources within $2\deg$ of the source
+We refit the spectral parameters of sources within $2\degree$ of the source
 to avoid potential biases of the extension parameters of the source of
@@
 our background model other 2FGL sources which were within 0\fdg5 of
-the source of interest from the background model. This was done due
-to a concern that extended sources are included in 2FGL as multiple
-point sources. These spurious sources could distort the extension
-fit.  Instead, when a source is found to be significantly extended
-(i.e. $\tsext>16$), we perform the dual localization procedure (described
-in Section~\ref{dual_localization_method} to compare the extended source
-hypothesis to the hypothesis of two independent point sources. Only
-sources with $\tsext>\tsinc$ are considered as extended.
+the source of interest. This was done due
+to a concern that extended sources could be included in 2FGL as multiple
+point-like sources. These spurious sources could distort the extension
+fit.  Instead, when a source was found to be significantly extended
+(i.e. $\tsext>16$), we performed the dual localization procedure 
+to compare the extended source
+hypothesis to the hypothesis of two independent point-like sources
+(section~\ref{dual_localization_method}). Only
+sources with $\tsext>\tsinc$ were considered as extended.
 
@@
 with the interstellar medium.  Finding sources on top of this emission
-is difficult \citep{first_diffuse_paper} as has been discussed in 1FGL
+is difficult as was discussed in 1FGL
 and 2FGL \citep{first_cat,second_cat}.  Furthermore, the Galactic plane
@@
 Because of this, finding a source with $\tsext>16$ is not a sufficient
-criteria alone for claiming a detection of source extension.  For each
+criteria alone for claiming the detection of source extension.  For each
 extended source, we perform several analysis crosschecks.
@@
 source of spectral index 2 into the region at each pixel and finding the
-increase in likelihood when fitting its flux. Residual \ts maps are useful
-to look for residual structure in the sky model.  Figure~\ref{res_tsmaps}
+increase in likelihood when fitting its flux. Figure~\ref{res_tsmaps}
 shows a residual \ts map for the extended source IC443.  The residual
 \ts map indicates that the spatially extended model for IC443 is a
-significantly better description of the observed photons.  We also
-generated plots of the sum of all counts within a given distance of
-the source and compared it to the model predictions of a point source.
+significantly better description of the observed photons
+and that there is no significant residual in region after modeling
+the source as being spatially extended.  We also
+generated maps of the sum of all counts within a given distance of
+the source and compared it to the model predictions of a point-like source.
 An example radial integral plot is shown for the extended source
@@
 % 2FGL J1856.2+0450c = P72Y3047 for
-We then inspected each extended source candidate to identify cases in
-which the extension fit is clearly influenced by large-scale residuals in
-the diffuse emission and hence the extension measurement is unreliable.
-An example of such a case is shown in Figure~\ref{example_bad_fit}. It
-shows a Galactic and isotropic diffuse-emission-subtracted smoothed
-counts map of 2FGL\,J1856.2+0450c using 1 \gev to 100 \gev photons.
-In this region along the Galactic plane, there appears to be large-scale
-residual in the diffuse emission. As a result, 2FGL\,J1856.2+0450c is fit
-to an extension of 1\fdg83 and the result is statistically significant
+We inspected each extended source candidate to identify cases in
+which the fit was influenced by large-scale residuals in
+the diffuse emission and hence the extension measurement was unreliable.
+An example of such a case is 
+the source 2FGL\,J1856.2+0450c 
+shown in Figure~\ref{example_bad_fit}. The
+diffuse-emission-subtracted smoothed
+counts map shows that
+there appears to be large-scale
+residual in the diffuse emission
+in this region along the Galactic plane.
+As a result, 2FGL\,J1856.2+0450c is fit
+to an extension of $\sim2\degree$ and the result is statistically significant
 with \tsext=45.4. However, by looking at the residuals it is clear
-that this complicated region is not fit well even though the source's
-extension is statistically significant. We do not report sources that
-fail this inspection as extended.
+that this complicated region is not fit well.
+We did not report as extended sources that fail this inspection.
 % information came from
@@
 
-For the remaining candidates, we took the spatial and spectral model found
+For the remaining candidates, we took the extended source's
+spatial and spectral model found
 using \pointlike and re-determined the spectral parameters using \gtlike.
-We used the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
+We used the `binned likelihood' mode of \gtlike on a $14\degree\times14\degree$
 ROI with a pixel size of 0\fdg03.  We obtained a second measure of \tsext
-from \gtlike for the extension and position of the source as determined
+from \gtlike using the extension and position of the source as determined
 by \pointlike.  We only considered a source to be significantly extended
@@
 to iteratively improve the model of our background sources to obtain a
-better fit of the candidate source.  Several catalog sources would often
-fill in the emission of the extended source and had to be removed from
-the background model of the region.  Similarly, background sources were
-often insignificant in the fit energy range and had to be removed from
-the sky model.  The position of background sources would often have
-to be refit once the extended source was fit.  When the model of the
-extended source coupled strongly with nearby sources, we iteratively
-fit the extended source and all nearby sources until the fit converged.
-For each extended source, we describe the modifications of the background
-model compared to the model used in the creation of the 2FGL catalog
-that were required.
+better fit of the candidate source.  Several point-like 2FGL sources
+were often include in the catalog to fill in the emission of the extended
+source candidate and had to be removed from the background model of
+the region.  Similarly, background sources were often insignificant at
+higher energies and had to be removed from the sky model.  The position
+of background sources would often have to be refit once the extended
+source's extension was modeled.  When the model of the extended source
+coupled strongly with nearby sources, we iteratively fit the extended
+source and all nearby sources until the fit converged.  For each extended
+source, we describe any modifications required of the background model
+compared to 2FGL sky model.
 
@@
 
-We estimate a systematic error on the extension of a source due to
-uncertainty in our knowledge of the LAT PSF.  Before launch, the LAT
-PSF was determined by detector simulations which were verified in
-accelerator tests \citep{atwood_LAT_mission}. However, in-flight data
-revealed a discrepancy above a few \gev in the PSF compared to the 
-angular distribution of photons from bright AGN.  A publication on this issue is in
-preparation \citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit
-empirically to bright AGN and this empirical parameterization is the
-default PSF used in the P7\_V6 IRFs.  To account for this uncertainty in
-our knowledge of the PSF, we refit our extended source candidates using
-the pre-flight Monte Carlo representation of the PSF and consider the difference
-in extension found using the two PSFs as a systematic error on the
-extension of a source.  The same approach was used in \citep{ic443}.
-At high energies, we believe that our parameterization of the PSF from
-bright AGN is substantially better than the Monte Carlo representation
-of the PSF so this estimate of systematic errors is conservative.
+We estimated a systematic error on the extension of a source due to
+uncertainty in our knowledge of the LAT PSF.  Before launch, the LAT PSF
+was determined by detector simulations which were verified in accelerator
+tests \citep{atwood_LAT_mission}. However, in-flight data revealed
+a discrepancy above a few \gev in the PSF compared to the angular
+distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
+Subsequently, the PSF was fit empirically to bright AGN and this
+empirical parameterization is used in the P7\_V6 IRFs.  To account for
+our uncertainty in our knowledge of the PSF, we refit our extended source
+candidates using the pre-flight Monte Carlo representation of the PSF
+and consider the difference in extension found using the two PSFs as a
+systematic error on the extension of a source.  The same approach was used
+in \cite{ic443}.  At high energies, we believe that our parameterization
+of the PSF from bright AGN is substantially better than the Monte Carlo
+representation of the PSF so this systematic error is conservative.
 
@@
 We estimate a second systematic error on the extension of a source
-due to uncertainty in the model of the Galactic diffuse emission by
-using an alternative diffuse model. An alternative model was based
+due to uncertainty in out model of the Galactic diffuse emission by
+using an alternative diffuse model based
 upon GALPROP\footnote{GALPROP is a software package for calculating the
@@
 in the Galaxy. See \url{http://galprop.stanford.edu/} for details
-and references} and used in the LAT analysis of the isotropic diffuse
+and references.} and used in the LAT analysis of the isotropic diffuse
 emission \citep{isotropic_lat}.  The intensities of various components
-to the galactic diffuse emission were then fitted individually using a
+of the Galactic diffuse emission were fitted individually using a
 spatial distribution of the intensities within the ROI as predicted by
-the model.  We distinguish contributions from CR interactions with the
+the model.  We distinguished contributions from CR interactions with the
 molecular hydrogen, the atomic+ionized hydrogen, residual gas traced
@@
 distance from the Galactic center in which they are produced. Hence, we
-replace the standard diffuse emission model by 18 individually fitted
+replaced the standard diffuse emission model by 18 individually fitted
 templates to describe individual components of the diffuse emission.
@@
 It is not expected that this diffuse model is superior to the standard
-LAT model obtained through an all-sky fit.  However, adding degrees of freedom to the background model can
-remove likely spurious sources that correlate with features in the
-Galactic diffuse emission.  Therefore, this tests systematics that may
-be due to incorrect modeling of the diffuse emission in the region.
-
-We do not except the systematic error due to uncertainties in the PSF to
-be correlated to the systematic due to uncertainty in the Galactic diffuse
-emission so the total systematic error on the extension of a source so
-we obtain the total systematic error by adding them in quadrature.
+LAT model obtained through an all-sky fit.  However, adding degrees of
+freedom to the background model can remove likely spurious sources that
+correlate with features in the Galactic diffuse emission.  Therefore,
+this tests systematics that may be due to incorrect modeling of the
+diffuse emission in the region.  We do not except the systematic error
+due to uncertainties in the PSF to be correlated to the systematic
+error due to uncertainty in the Galactic diffuse emission. Therefore,
+the total systematic error on the extension of a source was obtained by
+adding the two errors in quadrature.
 
@@
 \citep{w51c,ic443,w28,w44,cygnus_loop_lat}.\footnote{A detailed
-publication by the LAT Collaboration about W30 is still in preparation.}
+publication by the LAT Collaboration about W30 is in preparation.
 \gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
-Using 1 \gev to 100 \gev photons, our analysis significantly detected
+}
+Using photons
+with energies between
+1 \gev and 100 \gev, our analysis significantly detected
 the extension of all six SNRs.
@@
 Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
-detected using 1 \gev to 100 \gev photons. Our
+detected using photons with energies between
+1 \gev and 100 \gev. Our
 fit extension is comparable to the published result, but we note that
-previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
+the previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
 brightness spatial model when fitting it (\citep{lmc}).
@@
 identified in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  
-HESS\,J1825$-$137 was significantly detected using 10 \gev to 100 \gev photons.
-To improve the model of this source, we removed from our background model the
-nearby catalog source 2FGL\,J1823.1$-$1338c which is part of the extended
-source.  To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 must be
+HESS\,J1825$-$137 was significantly detected using photons
+with energies between 10 \gev and 100 \gev.
+To improve our analysis of this source, we removed from our background model the
+nearby catalog source 2FGL\,J1823.1$-$1338c which appeared to
+represent part of the emission from the extended source.
+To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 had
+to be
 analyzed at high energies.  Using photons with energies above 10 \gev,
 we fit the extension of MSH\,15$-$52 to be consistent with the published
-size with an extension significance of \tsext=6.5.
+size but with an extension significance of \tsext=6.5.
 
@@
 Our analysis was unable to resolve Vela X which would have required first
-removing the pulsed photons from the Vela pulsar which is beyond the
+removing the pulsed photons from the Vela pulsar which was beyond the
 scope of this paper.  Our analysis also failed to detect a significant
-extension for the Centaurus A Lobes \citep{cen_a_lat}. This is because
+extension for the Centaurus A Lobes because
 the source's emission is significantly different from a uniform
-radially symmetric surface brightness.
+radially symmetric surface brightness \citep{cen_a_lat}.
 
@@
 Table~\ref{known_extended_sources}.  This table includes the best fit
-position and extension of these sources when fitting them as disk-shaped
-sources with a radially symmetric uniform surface brightness. It also
+position and extension of these sources when fitting them 
+with a radially symmetric uniform surface brightness spatial model. It also
 includes the best fit spectral parameters for each source.  The position
-and extension of Vela X and the Centaurus A Lobes are taken from
+and extension of Vela X and the Centaurus A Lobes were taken from
 \cite{velax,cen_a_lat} and are included in this list for completeness.
@@
 
-To validate our method, we test LAT sources associated with AGN for
+To validate our method, we tested LAT sources associated with AGN for
 extension.  \gev emission from AGN is believed to originate from the
@@
 calibration source to demonstrate that our extension detection method
-does not misidentify point sources as being extended.  We note that
+does not misidentify point-like sources as being extended.  We note that
 megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
-\citep{pair_halo_paper} to be resolvable by the LAT. However, no such
+to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
 halo has been discovered in the LAT data so far.
@@
 (1LAC), a list of sources that had a high probability association with
-AGN \citep{first_agn_cat}.  1FGL had 709 1FGL sources associated with 671
-distinct AGN at high latitude ($|b|>10\deg$).  Using two years of data
+AGN \citep{first_agn_cat}.  1LAC associated 709 1FGL sources with 671
+AGN at high latitude ($|b|>10\degree$).  Using two years of data
 and 2FGL, the Second LAT AGN Catalog (2LAC) associated 1016 2FGL sources
 with AGN \citep{second_agn_cat}.  To avoid systematic problems with AGN
-classification, we selected 885 out of the 1016 AGN which made it into
+classification, we selected only the 885 AGN which made it into
 the clean AGN sub-sample.  An AGN association is considered clean only
@@
 
-Of the 885 clean AGN, we select 783 of these 2FGL sources which
-are significantly-detected above 1 \gev and fit each of them for extension.
-A histogram of the \tsext values computed for these AGN is
-shown in Figure~\ref{agn_ts_ext}. Overlaid on the plot is the
-$\chi^2/2$ distribution of Equation~\ref{ts_ext_distribution}.
+Of the 885 clean AGN, we selected the 783 of these 2FGL sources which
+were significantly-detected above 1 \gev and fit each of them for extension.
+The cumulative density of \tsext for these AGN compared to the
+$\chi^2/2$ distribution of Equation~\ref{ts_ext_distribution}
+is
+shown in Figure~\ref{agn_ts_ext}. 
 The \tsext distribution for AGN shows good agreement with the
-theoretical distribution.  Two sources had $\tsext>10$.  One was due
+theoretical distribution, but two sources had $\tsext>10$.  One was due
 to the incorrect removal of a nearby catalog sources from
@@
 Section~\ref{extended_source_search_method}) and the other was due to a
-failure of convergence of the point hypothesis.  This result demonstrates
+failure of convergence of the point-like source hypothesis.  This result demonstrates
 that we can use \tsext as a measure of the statistical significance of
@@
 This source is in a region of remarkably complicated diffuse emission.
-Even though it is $16\deg$ from the Galactic plane, this source is on
+Even though it is $16\degree$ from the Galactic plane, this source is on
 top of the core of the Ophiuchus molecular cloud which contains massive
@@
 
-This source is less than $1\deg$ away from 2FGL\,J1615.2$-$5138 which is
+This source is less than $1\degree$ away from 2FGL\,J1615.2$-$5138 which is
 also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
@@
 luminous to power the \tev emission.  AX\,J1838.0$-$0655 was spatially
-resolved by \chandra to be a bright point source surrounded by
+resolved by \chandra to be a bright point-like source surrounded by
 a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069} and so the
 $\gamma$-ray emission may be powered by this pulsar.  A second
-X-ray point source AX\,J1837.3$-$0652 is in the region of HESS\,J1837$-$069
+X-ray point-like source AX\,J1837.3$-$0652 is in the region of HESS\,J1837$-$069
 \citep{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
@@
 source 2FGL\,J2019.1+4040 which were part of the extended source.
-Further, we found it necessary to add an additional point source not in
+Further, we found it necessary to add an additional point-like source not in
 the two-year catalog into our background model.  The new source is was
@@
     expected profiles for a spatially extended source (solid and colored
-    red in the online version) and for a point source (dashed and colored
+    red in the online version) and for a point-like source (dashed and colored
     blue in the online version).  (d) smoothed count map after subtraction
@@
 \tablecomments{
-    A list of the spectral models of the simulated point sources
+    A list of the spectral models of the simulated point-like sources
     which were tested for extension.  For each model, the number of
@@
     The four plots
-    represent simulated point sources of different spectral indices and
+    represent simulated point-like sources of different spectral indices and
     the different lines (colored in the online version) 
-    represent point sources with different 100 \mev
+    represent point-like sources with different 100 \mev
     to 100 \gev integral fluxes.  The dashed line (colored red)
@@
   IC443 using 1 \gev to 100 \gev photons.  (a) test statistic map after
-  subtracting IC443 modeled as a point source. (b) same as (a), but
+  subtracting IC443 modeled as a point-like source. (b) same as (a), but
   IC443 modeled as extended source. Crosses represent sources included
@@
 model, and the alternate PSF respectively.  \tsinc is the test statistic
-for the two point source hypothesis test 
+for the two point-like source hypothesis test 
 (see Section~\ref{dual_localization_method}).
@@
   removed from the background model.
-  The lower right inset is the model predicted emission from a point
+  The lower right inset is the model predicted emission from a point-like
   source with the same spectrum as 2FGL\,J0823.4$-$4305 smoothed by the

### 2011-08-29 extended_catalog/paper/extended_catalog.tex
improvements

@@
 \usepackage{color}
-
-%\newcommand{\hl}[1]{{\color{red}#1}}
-\newcommand{\hl}[1]{#1}
 
@@
 \begin{abstract}
-\hl{
 Spatial extension is an important characteristic for correctly
@@
 spatially extended sources reported in 2FGL.
-}
 \end{abstract}
@@
 \section{Introduction}
-
-\hl{
 
@@
 but not previously spatially resolved.
-
-}
 
@@
 required that both methods agree for a source to be considered extended.
-We found good agreement between the two methods.  Unless explicitly
+There was good agreement between the two methods.  Unless explicitly
 mentioned, all \ts, \tsext, and spectral parameters were calculated using
@@
 representative livetime fraction of 0.8.  The reconstruction was performed
-using photons with energies between 1 \gev to 100 \gev 
+using photons with energies between 1 \gev and 100 \gev 
 and the Pass~7\_V6 (P7\_V6) Source Instrument
@@
 the threshold using photons with energies between 100 \mev and 100 \gev
-and also using only 1 \gev to 100 \gev photons.
+and also using only photons with energies between 1 \gev and 100 \gev.
 Except for very large ($>1\degree$) sources, our detection threshold is
@@
 
-\hl{
 Figure~\ref{all_sensitivity} shows the flux threshold as a function of
@@
 expected factor corresponding to the square root of the exposure.
-}
 
@@
 
-As was shown in Section~\ref{extension_sensitivity}, we gain little in sensitivity using photons with energies
-below 1 \gev. On the other hand, the large PSF at low energy makes us
-more susceptible to systematic errors arising from source confusion due
-to multiple point-like sources and modeling of the
-Galactic diffuse emission. In addition, the Galactic diffuse emission
-is more pronounced at lower energies due to its steep energy spectrum
-\citep{intermediate_diffuse_lat}.
-For that reason, we performed our search using only photons with
-energies between 1 \gev and 100 \gev.
-
-We also performed a search for extended sources using only 10 \gev to 100 \gev photons. 
+As was shown in Section~\ref{extension_sensitivity}, we gain little in
+sensitivity using photons with energies below 1 \gev. On the other hand,
+the large PSF at low energy makes us more susceptible to systematic
+errors arising from source confusion due to multiple point-like sources
+and modeling of the Galactic diffuse emission. In addition, the Galactic
+diffuse emission is more pronounced at lower energies due to its steep
+energy spectrum \citep{intermediate_diffuse_lat}.  For that reason,
+we performed our search using only photons with energies between 1 \gev
+and 100 \gev.
+
+We also performed a search for extended sources using only photons with energies
+between 10 \gev and 100 \gev. 
 Although this approach tests the same
@@
 An example of such a case is 
-the source 2FGL\,J1856.2+0450c 
+2FGL\,J1856.2+0450c 
 shown in Figure~\ref{example_bad_fit}. The
@@
 with energies between 10 \gev and 100 \gev.
-To improve our analysis of this source, we removed from our background model the
-nearby catalog source 2FGL\,J1823.1$-$1338c which appeared to
-represent part of the emission from the extended source.
+To improve our analysis of this source, we had to remove
+from our background model 
+2FGL\,J1823.1$-$1338c which was included in 2FGL to
+represent part of the extended emission.
 To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 had
@@
 
-Nine extended sources not included in 2FGL were found using this search.
-Three were found in our search using 1 \gev 100 \gev photons and six were
-found in our search using 10 \gev to 100 \gev photons.  The fit properties of
+Nine extended sources not included in 2FGL were found by our 
+extended source search.
+Three were found when using photons with energies between 1 \gev
+and 100 \gev and six were found when using photons with energies
+between 10 \gev and 100 \gev.  The spectral and spatial properties of
 these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
-This table includes for each source the best fit position, extension,
-spectrum, source significance, and significance of extension.
-
-The results of our investigation of systematic uncertainties of this
-measurement are presented in 
-Table~\ref{alt_diff_model_results}.  It
-shows a comparison between the fit with a single extended source
-hypothesis and the fit assuming the emission originates from two
-independent sources and  the
-results of the extension fit using variations of the PSF and the galactic
-diffuse model described in Section~\ref{systematic_errors_on_extension}.
-There is good agreement between \tsext and the fit size using
-the standard analysis, the alternative diffuse models, and the alternative PSF.
-This suggests that the sources are robust against features in the diffuse
-model and uncertainties in the angular resolution.
+The results of our investigation of systematic errors 
+are presented in Table~\ref{alt_diff_model_results}.  it 
+compares the fit extension with an extended source hypothesis
+to the fit assuming the emission originates from two independent
+point-like sources. For these extended extended sources,
+$\tsext>\tsinc$ suggesting that the \gev emission does not originate
+from multiple physically distinct sources.
+Table~\ref{alt_diff_model_results}
+also includes the results of the extension fit
+using variations of the PSF and the galactic diffuse model described
+in Section~\ref{systematic_errors_on_extension}.  There is good
+agreement between \tsext and the fit size using the standard analysis,
+the alternative diffuse models, and the alternative PSF.  This suggests
+that the sources are robust against features in the diffuse emission
+model and uncertainties in the angular resolution of the LAT.
 
@@
 
-The source 2FGL\,J0823.0$-$4246 was found 
+2FGL\,J0823.0$-$4246 was found 
 to have an 
@@
 significance of $\tsext=46.3$
-using 1 \gev to 100 \gev photons.  This source was fit to a position of
-$(l,b)=(260\fdg32,-3\fdg28)$.  
-This source is coincident with the one-year
-catalog source 1FGL\,J0823.3$-$4248.
-\hl{
+using 
+ photons with energies between
+1 \gev and 100 \gev.  This source was fit to 
+$(l,b)=(260\fdg32,-3\fdg28)$ and
+is coincident with 1FGL\,J0823.3$-$4248.
 Figure~\ref{1FGL_J0823.3-4248} shows a
@@
 and Figure~\ref{snr_seds} shows its spectrum.
-}
-To get a good fit of this source, we removed from our background
-model the nearby catalog
-sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which are part of the
-extended source.  These modifications are
-shown in Figure~\ref{1FGL_J0823.3-4248}.
-
-\hl{
+To get a good fit of this source, we had to remove from our background
+model the nearby sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254
+which were included in 2FGL to represent part of the
+extended emission.
+
 This extended source is spatially coincident with the
@@
 size at \gev energies \citep{rosat_puppis_a}.  Puppis A's distance
-was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} which leads
-to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.
+was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads
+to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
 No molecular clouds have been observed directly adjacent to Puppis A
-\citep{co_eastern_puppis_a}.  This is similar to the LAT detected Cyngus
+\citep{co_eastern_puppis_a}, similar to the LAT detected Cyngus
 Loop SNR \citep{cygnus_loop_lat}.  The luminosity of Puppis A is also
@@
 \citep{w51c,ic443,w44,w28,w49b_lat}.
-\citep{cygnus_loop_lat}.
-}
 
@@
 
-The source 2FGL\,J1627.0$-$2425c was found  to
+2FGL\,J1627.0$-$2425c was found  to
 have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
 an extension significance of $\tsext=31.1$
-using 1 \gev to 100 \gev photons.  The best fit position is
-$(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
-year catalog source 1FGL\,J1628.6$-$2419c.  A counts map showing this source
-is seen in Figure \ref{1FGL_J1628.6-2419c}.
-
-\hl{
+using photons with energies between 1 \gev and 100 \gev.  The source
+was fit to
+$(l,b)=(353\fdg08, 16\fdg78)$ and is coincident with 
+1FGL\,J1628.6$-$2419c.  
+Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
+
 This source is in a region of remarkably complicated diffuse emission.
@@
 ${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
-contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c}. There is good
-spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}
-so this source might 
+contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
+spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
+This source might 
 represent $\gamma$-ray emission from the interactions of cosmic rays with
@@
 emission model.
-}
 
@@
 
-The source 2FGL\,J1712.4$-$3941 was found 
-photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
+2FGL\,J1712.4$-$3941 was found 
+to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
 with an extension significance of $\tsext=39.6$
-using 1 \gev to 100 \gev.  This source was
-fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  this source
-is coincident with the one-year catalog source 1FGL\,J1711.7$-$3944c.
-Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.
-
+using 
+photons with energies between
+1 \gev and 100 \gev.  This source was
+fit to $(l,b)=(347\fdg25,-0\fdg54)$ and is coincident
+with 1FGL\,J1711.7$-$3944c.
+Figure \ref{2FGL_J1712.4-3941} shows a counts map of this source.
 This source is spatially coincident with the SNR RX\,J1713.7$-$3946
-and was recently reported by \citep{rx_j1713_lat}.  
+and was recently reported by \cite{rx_j1713_lat}.  
 Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR 
-RX\,J1713.7$-$3946 from \citep{rx_j1713_hess}.  To analyze this source,
-we used the same background model as the recent LAT publication.
-2FGL\,J1715.4$-$4024c is spatially coincident with Source A and was
-moved to $(\text{RA},\text{Dec})=(258.84,-40.46)$. Source B was added
-at $(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
-$(\text{RA},\text{Dec})=(257.47,-39.75)$.
+RX\,J1713.7$-$3946 from \cite{rx_j1713_hess}.  To analyze this source,
+we used the same background source model as the recent LAT publication.
 
@@
 
-The source 2FGL\,J0851.7$-$4635 was found 
+2FGL\,J0851.7$-$4635 was found 
 to have an
@@
 significance of $\tsext=87.2$
-using 10 \gev to 100 \gev photons.  This source was fit to a position of
-$(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
-map of this source.
-
+using photons with energies between 10 \gev and 100 \gev.  
+This source was fit to 
+$(l,b)=(266\fdg29,-1\fdg43)$ and figure~\ref{Vela_Jr} shows a counts
+map of the source.
 2FGL\,J0851.7$-$4635 is spatially coincident with the SNR Vela Jr.
-Overlaid on Figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
-\tev by H.E.S.S \citep{vela_jr_hess}.  The \gev and \tev morphology
+Overlaid on Figure~\ref{Vela_Jr} are H.E.S.S. \tev contours of Vela Jr.
+\citep{vela_jr_hess}.  The \gev and \tev morphology
 match well.  A detailed papers by the LAT Collaboration on Vela Jr. is
@@
 
-To get a good fit of this source, removed from
-our background model the nearby catalog
-sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
-which are part of the extended source.  In addition, we relocalized
-the position of the nearby catalog source 2FGL\,J0854.7$-$4501 to
+To get a good fit of this source, we had to remove from
+our background model 
+2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
+which were included in 2FGL to account for part of the extended emission.  In addition, we relocalized
+2FGL\,J0854.7$-$4501 to
 $(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
-in the presence of of the extended source.  In addition, we removed from
-our model the
-further away catalog sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
+and we had to remove from our model 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
 because they were not significant above 10 \gev.
@@
 
-The source 2FGL\,J1615.0$-$5051 was found 
-photons to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
+2FGL\,J1615.0$-$5051 was found 
+to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
 with an extension significance of \tsext=16.3
-using 10 \gev to 100 \gev.  This source
-was fit to a position of $(l,b)=(332\fdg38,-0\fdg14)$.
-This source is coincident with the one-year catalog source
+using 
+photons with energies between
+10 \gev and 100 \gev.  This source
+was fit to $(l,b)=(332\fdg38,-0\fdg14)$ and
+is coincident with 
 1FGL\,J1613.6$-$5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
-of this source.
-
-This source is less than $1\degree$ away from 2FGL\,J1615.2$-$5138 which is
+of the source.
+It is less than $1\degree$ away from 2FGL\,J1615.2$-$5138 which is
 also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
-To get a good fit of both sources, we modeled both sources as
+To get a good fit of both sources, we modeled both of them as
 being spatially extended and iteratively fit the position and extension
-of each source until obtaining a global best fit.  Before doing this,
-We removed from our background model the source 2FGL\,J1614.9$-$5212 because it is
-part of 2FGL\,J1615.2$-$5138's. Furthermore, we removed from our model the nearby catalog
-sources 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
-significant above 10 \gev.  These modifications are further described
-in the caption to Figure~\ref{1FGL_J1613.6-5100c}.
+of each source. 
+We had to remove from our background model 2FGL\,J1614.9$-$5212 
+which was included in 2FGL to account for part of the extended emission.
+We also removed from our model 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
+significant above 10 \gev.
 
 2FGL\,J1615.2$-$5138 is spatially coincident with the extended
-\tev source HESS\,J1616$-$508 \citep{hess_plane_survey}.  In
-Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616$-$508 are overlaid
-on 2FGL\,J1615.0$-$5051.  The H.E.S.S. experiment measured an
-extension $0.136\pm 0.008$ when fitting this source with an elliptical
-2D Gaussian surface brightness.  This size corresponds to a 68\% containment
-radius of $\rsixeight=0\fdg21\pm0\fdg01$. This size is comparable to the LAT
-size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
+and \tev contours are 
+overlaid on Figure~\ref{1FGL_J1613.6-5100c} \citep{hess_plane_survey}.
+H.E.S.S. measured an
+extension $0\fdg136\pm0\fdg008$ when fitting this source with an elliptical
+2D Gaussian surface brightness.  This corresponds to a 68\% containment
+radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the LAT
+size $\rsixeight=0\fdg27\pm0\fdg03$.
 Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1615.0$-$5051
 at \gev energies
-connects smoothly to the spectrum of HESS\,J1616$-$508 at \tev
+also connects smoothly to the spectrum of HESS\,J1616$-$508 at \tev
 energies.
 
-\hl{
-HESS\,J1616$-$508 is located in the region of two SNRs, RCW103
+HESS\,J1616$-$508 is located in the region of two SNRs RCW103
 (G332.4-04) and Kes~32 (G332.4+0.1) but is not spatially coincident
 with either of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near
-three pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055
-but only PSR\,J1617$-$5055 is energetically favored as being the \tev
-emitter \citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.
-\cite{hess_plane_survey} speculated that a PWN powered by this young
-pulsar could be responsible for the emission of HESS\,J1616$-$508.
+three pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055.
+\citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.
+Only PSR\,J1617$-$5055 is energetically capable of powering the
+\tev emission
+and
+\cite{hess_plane_survey} speculated that 
+HESS\,J1616$-$508 could be 
+a PWN powered by this young
+pulsar.
 Because HESS\,J1616$-$508 is $9\arcmin$ away from PSR\,J1617$-$5055, this would
-require an assymetric X-ray PWNe to power the \tev emission. However,
-\chandra ACIS observations revealed only an underluminous PWN of
-about $\sim1\arcmin$ size around the pulsar which was not oriented
-towards the \tev emission, rendering this association as uncertain
+require an asymmetric X-ray PWNe to power the \tev emission. 
+\chandra ACIS observations revealed an underluminous PWN of
+size $\sim1\arcmin$ around the pulsar that was not oriented
+towards the \tev emission rendering this association uncertain
 \citep{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
-counterparts were observed in observations of X-ray and soft gamma-ray
-emission by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
+counterparts were observed at X-ray and soft gamma-ray energies
+by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
 IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
-Finally, \cite{discovery_of_pwn_for_PSR_J1617-5055} found diffuse
+\cite{discovery_of_pwn_for_PSR_J1617-5055} discovered some additional
+diffuse
 emission towards the center of HESS\,J1616$-$508 using archival radio and
 infared observations. Deeper observations will likely be necessary to
-understand this region.
-}
+understand this $\gamma$-ray source.
 
@@
 
-The source 2FGL\,J1615.2$-$5138 was found 
-photons to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
+2FGL\,J1615.2$-$5138 was found 
+ to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
 with an extension significance of \tsext=48.0
-using 10 \gev to 100 \gev.  This source was fit to a
-position of $(l,b)=(331\fdg66,-0\fdg66)$.  This source is coincident
-with the one-year catalog source 1FGL\,J1614.7$-$5138c.  Because 2FGL
+using 
+photons with energies between
+10 \gev and 100 \gev.  This source was fit to 
+$(l,b)=(331\fdg66,-0\fdg66)$ and is coincident with
+1FGL\,J1614.7$-$5138c.  Because 2FGL
 J1615.2$-$5138 is close to 2FGL\,J1615.0$-$5051, the same model described
@@
 This source is spatially coincident with the extended
-\tev source HESS\,J1614$-$518 \citep{hess_plane_survey}. In
-Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614$-$518 are overlaid
-on 2FGL\,J1615.2$-$5138.  The H.E.S.S. experiment measured a 2D Gaussian
-extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0.15\pm0.02$
-in the semi-major and semi-minor axis. This size corresponds
+\tev source HESS\,J1614$-$518 and \tev contours
+are ovlaid on
+Figure~\ref{1FGL_J1613.6-5100c}
+\citep{hess_plane_survey}. 
+H.E.S.S. measured a 2D Gaussian
+extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0\fdg15\pm0\fdg02$
+in the semi-major and semi-minor axis. This corresponds
 to a 68\% containment size of $\rsixeight=0\fdg35\pm0\fdg03$
-and $0.23\pm0.03$.  This elliptical size matches the LAT size
+and $0\fdg23\pm0\fdg03$,  consistent with the LAT size
 $\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds} shows
@@
 the spectrum of HESS\,J1614$-$518 at \tev energies.  Further data collected by
-H.E.S.S. in 2007 helped to resolve a double peaked structure in the
-H.E.S.S. data but no spectral variation across this source, suggesting
+H.E.S.S. in 2007 resolve a double peaked structure at \tev
+energies
+but no spectral variation across this source, suggesting
 that the emission is not the confusion of physically separate sources
@@
 
-\hl{
 There are five nearby pulsars, but none are luminous enough to
@@
 acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
-}
 
@@
 
-The source 2FGL\,J1632.4$-$4753c was found 
+2FGL\,J1632.4$-$4753c was found 
 to
@@
 significance of \tsext=64.5
-using 10 \gev to 100 \gev photons.  This source was fit to a position of
-$(l,b)=(336\fdg41,0\fdg22)$.  This source is coincident with the one
-year catalog source 1FGL\,J1632.9$-$4802c.  Figure~\ref{1FGL_J1632.9-4802c}
+using 
+photons with energies between
+10 \gev and 100 \gev.  This source was fit to 
+$(l,b)=(336\fdg41,0\fdg22)$ and is coincident with 
+1FGL\,J1632.9$-$4802c.  Figure~\ref{1FGL_J1632.9-4802c}
 shows a counts map of this source.
-
-To get a good fit of this source, we removed from our background model
-three catalog sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
-2FGL J1634.4$-$4743c.4-4820c that were part of the extended source..
-We then iteratively relocalized the source 2FGL\,J1635.4$-$4717c
+To get a good fit of this source, we had to remove from our background model
+three sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
+2FGL J1634.4$-$4743c.4-4820c which were included in 2FGL to account for
+part of the extended emission.
+We relocalized 2FGL\,J1635.4$-$4717c
 to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3$-$4740c to
-$(l,b)=(336\fdg97,-0\fdg07)$ while fitting the extension of
-2FGL\,J1632.4$-$4753c.  In addition we removed from our model four
-farther away two-year catalog sources 2FGL\,J1638.0$-$4703c, 
+$(l,b)=(336\fdg97,-0\fdg07)$
+and removed from our model four
+farther away sources 2FGL\,J1638.0$-$4703c, 
 2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
-were not significant above 10 \gev.  These modifications are shown
-in Figure~\ref{1FGL_J1632.9-4802c}.
+were not significant above 10 \gev.
 
 This extended source is spatially coincident with the extended
-\tev source HESS\,J1632$-$478 \citep{hess_plane_survey}.
-In Figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632$-$478
-are overlaid on 2FGL\,J1635.4$-$4717c.  H.E.S.S measured a 
-extension of $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the
+\tev source HESS\,J1632$-$478 
+and \tev contours are overlaid on 
+Figure~\ref{1FGL_J1632.9-4802c}
+\citep{hess_plane_survey}.
+H.E.S.S measured a 
+extension of $\sigma=0\fdg21\pm0\fdg05$ and $0\fdg06\pm0\fdg04$ along the
 semi-major and semi-minor axes when fitting this source with an
@@
 containment size $\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$
-along the semi-major and semi-minor axis. This size is consistent with
+along the semi-major and semi-minor axis, consistent with
 the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
@@
 
-\hl{
 \cite{hess_plane_survey} argued that HESS\,J1632$-$478
 is positionally coincident with the hard X-ray source
-IGR\,J1632-4751 observed by INTEGRAL, \xmmnewton, and \asca
-\citep{Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751,asca_plane_survey},
-but this source is suspected to be a galactic X-Ray Binary so the $\gamma$-ray
-extension disfavors the association.  Further observations by
-\xmmnewton reveal extended emission of size $\sim32\arcsec\times15\arcsec$
-and inside point-like emission coincident with the peak
-H.E.S.S. emission \citep{hess_j1632_478_xmm_newton}.  They found
-in archival MGPS-2 data a spatially coincident extended radio source
-\citep{most_survey_galactic_plane}.  The positional match argues for a
-single synchrotron process producing X-ray and \gev and \tev radiation,
-likely due to a PWNe.  The increased size at \tev energies
-compared
+IGR\,J1632-4751 observed by \asca, INTEGRAL, and \xmmnewton
+\citep{asca_plane_survey,Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751},
+but this source is suspected to be a galactic X-Ray Binary so the
+$\gamma$-ray extension disfavors the association.  Further observations
+by \xmmnewton discovered point-like emission coincident with the peak
+of the H.E.S.S. source surrounded by extended emission of size
+$\sim32\arcsec\times15\arcsec$ \citep{hess_j1632_478_xmm_newton}.
+They found in archival MGPS-2 data a spatially coincident extended
+radio source \citep{most_survey_galactic_plane} and argued for a single
+synchrotron process producing the radio, X-ray, and \tev emission,
+likely due to a PWNe.  The increased size at \tev energies compared
 to X-ray energies has previously been observed in several aging PWNe
@@
 HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
-and Vela X \citep{vela_x_rosat,vela_x_hess}.  This can be explained by
-a different synchrotron cooling time for the electrons producing X-rays
-and \tev $\gamma$-rays.
-}
+and Vela X \citep{vela_x_rosat,vela_x_hess} and can be explained by
+different synchrotron cooling times for the electrons that produce X-rays
+and $\gamma$-rays.
 
@@
 
-The source 2FGL\,J1837.3$-$0700c was found 
+2FGL\,J1837.3$-$0700c was found 
 to
@@
 extension significance of $\tsext=18.8$
-using 10 \gev to 100 \gev photons.  This source was fit to a position
-of $(l,b)=(25\fdg08,0\fdg13)$.  This source is coincident with the one
-year catalog source 1FGL\,J1837.5$-$0659c.  Figure~\ref{1FGL_J1837.5-0659c}
+using 
+ photons with energies between
+10 \gev and 100 \gev.  This source was fit to 
+$(l,b)=(25\fdg08,0\fdg13)$ and is coincident with 
+1FGL\,J1837.5$-$0659c.  Figure~\ref{1FGL_J1837.5-0659c}
 shows a counts map of this source.
-
-This source is in a complicated region. There are three nearby
-catalog sources 2FGL\,J1834.7$-$0705c, 2FGL\,J1836.8$-$0623c, and
+It is in a complicated region with three nearby
+sources 2FGL\,J1834.7$-$0705c, 2FGL\,J1836.8$-$0623c, and
 2FGL\,J1839.3$-$0558c.  To get a good fit of 2FGL\,J1837.3$-$0700c, we
@@
 2FGL\,J1836.8$-$0623c to $(l,b)=(25\fdg57,0\fdg32)$, and
-2FGL\,J1839.3$-$0558c to $(l,b)=(26\fdg08,0\fdg23)$.  We removed from
-our background model the
-nearby catalog source 2FGL\,J1835.5$-$0649 which is part of the extended
-source and also the farther away catalog source 2FGL\,J1839.0$-$0539
-because it was not significant above 10 \gev. These modifications are
-shown in Figure~\ref{1FGL_J1837.5-0659c}.
+2FGL\,J1839.3$-$0558c to $(l,b)=(26\fdg08,0\fdg23)$.  We had to remove from
+our background model 
+2FGL\,J1835.5$-$0649 which was included in 2FGL to account for
+part of the extended emission 
+and also 2FGL\,J1839.0$-$0539
+because it was not significant above 10 \gev.
 
 This source is spatially coincident with the \tev source HESS\,J1837$-$069
-\citep{hess_plane_survey}.  In Figure~\ref{1FGL_J1837.5-0659c}, contours
-of HESS\,J1837$-$069 are overlaid on 2FGL\,J1837.3$-$0700c. H.E.S.S. measured
-an extension of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$
+and \tev contours are overlaid on 
+Figure~\ref{1FGL_J1837.5-0659c} \citep{hess_plane_survey}.  
+H.E.S.S. measured
+an extension of $\sigma=0\fdg12\pm0\fdg02$ and $0\fdg05\pm0\fdg02$
 along the semi-major and semi-minor axis when fitting this source
@@
 $0\fdg08\pm0\fdg03$ along the semi-major and semi-minor axis. The
-size is comparable to LAT which fit a 68\% containment radius of
-$\rsixeight=0\fdg29\pm0\fdg07$.  the size difference is not significant
-(less than 2 sigma).  Figure~\ref{hess_seds} shows that the spectrum
+size is not significantly different from the LAT 68\% containment radius of
+$\rsixeight=0\fdg29\pm0\fdg07$ (less than $2\sigma$).  
+Figure~\ref{hess_seds} shows that the spectrum
 of 2FGL\,J1837.3$-$0700c at \gev energies
@@
 
-\hl{
 HESS\,J1837$-$069 is coincident
@@
 resolved by \chandra to be a bright point-like source surrounded by
-a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069} and so the
-$\gamma$-ray emission may be powered by this pulsar.  A second
-X-ray point-like source AX\,J1837.3$-$0652 is in the region of HESS\,J1837$-$069
+a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069}. The
+$\gamma$-ray emission may be powered by this pulsar.  A second X-ray
+point-like source AX\,J1837.3$-$0652 is near HESS\,J1837$-$069
 \citep{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
 It was also resolved into point-like and diffuse component
-although no pulsations have yet been detected from it
-\citep{pulsations_HESS_J1837-069}.  If AX\,J1838.0$-$0655 is a pulsar/PWN
-powering HESS\,J1837$-$069, some of the \tev emission may also come from
-AX\,J1837.3$-$0652.
-}
+although no pulsations have been detected from it
+\citep{pulsations_HESS_J1837-069}. Some of the $\gamma$-ray emission
+could also come from AX\,J1837.3$-$0652.
 
@@
 
-The source 2FGL\,J2021.5+4026 was found to have an extension of
+2FGL\,J2021.5+4026 was found to have an extension of
 $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=116.4$ using 10 \gev to 100 \gev photons.  This source
-was fit to a position of $(l,b)=(78\fdg18,2\fdg19)$.  This source is
-coincident with the one-year catalog source 1FGL\,J2020.0+4049. \hl{
+of $\tsext=116.4$ using 
+ photons with energies between
+10 \gev and 100 \gev.  This source
+was fit to $(l,b)=(78\fdg18,2\fdg19)$ and is
+coincident with 1FGL\,J2020.0+4049. 
 Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source
 and Figure~\ref{snr_seds} shows its spectrum.  
-}
-
-To get a good fit of this source, we removed from our background
-model the nearby catalog
-source 2FGL\,J2019.1+4040 which were part of the extended source.
-Further, we found it necessary to add an additional point-like source not in
-the two-year catalog into our background model.  The new source is was
-localized to a position of $(l,b)=(78\fdg85,2\fdg67)$ and had $\ts=13.5$ .
-Although this source is not very significant, not including it into the
+To get a good fit of this source, we had to remove from our background
+model 2FGL\,J2019.1+4040 which was included in 2FGL to account for
+part of the extended emission.
+Further, it was necessary to add to our region an additional point-like source 
+at
+$(l,b)=(78\fdg85,2\fdg67)$.
+Although this source is not very significant
+($\ts=13.5$), not including it in the
 background model significantly biased the fit extension.
-In addition, we removed from our model the four further away catalog
+In addition, we had to remove from our model the four 
 sources 2FGL\,J2022.8+3843c, 2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c,
-and 2FGL\,J2012.4+3955c from the region because they were not significant
-above 10 \gev.  These modifications are further described in the caption to
-Figure~\ref{1FGL_J2020.0+4049}.
-
-\hl{
+and 2FGL\,J2012.4+3955c because they were not significant
+above 10 \gev.
+
 This extended sources is coincident with 2CG\,078+01 and
-3EG\,J2020+4017 detected by COS B and EGRET respectively
-\citep{second_cos_b_catalog,third_egret_catalog}.  This source is
-spatially coincident with the $\gamma$-Cygni SNR and has been speculated
-to originate from 
-the interaction of accelerated particles in the SNR interacting
-with dense molecular clouds \citep{pollock_1985,gaisser_1998}.  But this
-association was disfavored when the LAT \gev emission from this source
-was detected to be pulsed 
-(PSR\,J2021+4026,\cite{first_lat_pulsar_cat}).
-
-Milagro detected a $4.2\sigma$ excess at energies $\sim 30 \tev$ from the
-location of this source in the previous LAT bright $\gamma$-ray source
-list. \cite{lat_bsl,milagro_bright_source_list}.  Veritas also detected
-an extended source VER\,J2019+407 coincident with the SNR above 200 \gev
-and suggested the \tev emission could be a shock-cloud interaction in
-$\gamma$-Cygni \citep{veritas_gamma_cygni}.  Using just 10 \gev to 100
-\gev photons to avoid PSR\,J2021+4026, we resolve an extended source
-whose inferred size at \gev energies well matches the radio size of
-$\gamma$-Cygni, as can be seen in Figure~\ref{1FGL_J2020.0+4049} which
-overlays contours of $\gamma$-Cygni at 408MHz from the Canadian Galactic
-Plane Survey \citep{canadian_galactic_plane_survey}.
-}
+3EG\,J2020+4017 \citep{second_cos_b_catalog,third_egret_catalog}
+and also with the $\gamma$-Cygni SNR. This $\gamma$-ray source has
+been speculated to originate from the interaction of accelerated
+particles in the SNR interacting with dense molecular clouds
+\citep{pollock_1985,gaisser_1998},  but this association was disfavored
+when the LAT \gev emission from this source was detected to be pulsed
+(PSR\,J2021+4026, \cite{first_lat_pulsar_cat}).
+
+Milagro detected a $4.2\sigma$ excess at energies $\sim 30$ \tev
+from this location \citep{lat_bsl,milagro_bright_source_list}.
+Veritas also detected an extended source VER\,J2019+407 coincident
+with the SNR above 200 \gev and suggested that the \tev emission could be a
+shock-cloud interaction in $\gamma$-Cygni \citep{veritas_gamma_cygni}.
+Using just photons with energies between 10 \gev to 100 \gev 
+where
+PSR\,J2021+4026 is not significant, we resolved an extended source whose inferred size at
+\gev energies well matches the radio size of $\gamma$-Cygni. This can
+be seen clearly in Figure~\ref{1FGL_J2020.0+4049} which overlays radio
+contours of $\gamma$-Cygni from the Canadian Galactic Plane Survey
+\citep{canadian_galactic_plane_survey}.
 
@@
 
-\hl{
 Twelve extended sources were included in 2FGL.  Using two years of
@@
 shape of the twelve extended sources in 2FGL.  The 21 extended
-LAT sources are located close to the Galactic plane 
-and their localizations shown in
-Figure~\ref{allsky_extended_sources}.  Most of the extended sources are
-indeed expected to be of Galactic origin as the distance of extragalactic
+LAT sources are primarily along the Galactic plane 
+and their locations are shown in
+Figure~\ref{allsky_extended_sources}.  Most of the LAT detected
+extended sources are
+expected to be of Galactic origin as the distance of extragalactic
 sources (with the exception of the local group Galaxies) is typically too
-large to resolve them in $\gamma$-rays.
-
-For the LAT extended sources also seen in the \tev energy range,
-Figure~\ref{gev_vs_tev_plot} shows that their is a good correlation
-between the size of the sources in the \gev and \tev energy ranges. Even
+large to be able to resolve them at $\gamma$-rays energies.
+
+For the LAT extended sources also seen at \tev energies,
+Figure~\ref{gev_vs_tev_plot} shows that there is a good correlation
+between the size of the sources at \gev and \tev energies. Even
 so, the size of PWNe are expected to vary across the \gev and \tev
@@
 \gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting to
-compare the size at \gev and \tev energies
-of other PWN candidates, but definitively
+compare the size of other PWN candidates at \gev and \tev energies, 
+but definitively
 measuring this would require a more in-depth analysis of the LAT data
@@
 field of view and all-sky coverage, the LAT can more easily measure
-larger sources including the LMC and SMC.  On the other hand, the 
+larger sources.  On the other hand, the 
 better
-angular resolution of Air Cherenkov detectors allows them to measure a
-population of extended sources below our sensitivity limit (currently at
+angular resolution of air Cherenkov detectors allows them to measure a
+population of extended sources below our detection threshold limit (currently 
 about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with
 a goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
-the LAT's low background at high energies will allow it's sensitivity to
+the LAT's low background at high energies allows its sensitivity 
+to
 these smaller sources to improve by a factor greater than the square root
-of the exposure.  With increased exposure, the LAT will likely begin to
-detect and resolve many smaller \tev sources.
+of the exposure.  With increasing exposure, the LAT will likely begin to
+detect and resolve some of these smaller \tev sources.
 
@@
 at \gev energies
-connect smoothly to their H.E.S.S. counterparts at \tev
+connects smoothly to the spectra of their H.E.S.S. counterparts at \tev
 energies. This is also true of Vela
-Jr., HESS\,J1825$-$137 \citep{fermi_hess_j1825}, RX\,J1713.7$-$3946
+Jr., HESS\,J1825$-$137 \citep{fermi_hess_j1825}, and RX\,J1713.7$-$3946
 \citep{rx_j1713_lat}.  It is likely that the \gev and \tev emission
@@
 high-energy emission seen from these sources.
-}
 
@@
     LAT PSF (inset).  Plots (a),
-    (c), and (d) use only 1 \gev to 100 \gev photons.  Plots (c) and (d) use
+    (c), and (d) use only 
+    photons with energies between
+    1 \gev and 100 \gev.  Plots (c) and (d) use
     only photons which converted in the front part of the tracker and
@@
     \caption{
-    A comparison of a 2D Gaussian and disk-like surface brightness profiles
+    A comparison of a 2D Gaussian and uniform surface brightness profiles
     of extended sources before and after convolving with the PSF for two
@@
     for a power-law source of spectral index 2. The dashed line
-    and the dash-dotted line are 
+    and the dash-dotted lines are 
     the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
@@
     (colored red in the online version).
-    The dash-dot-doted and the dot-doted line are the brightness profile
+    The dash-dot-doted and the dot-doted lines are the brightness profile
     of a uniform disk with $\rsixeight=0\fdg5$ and the convolution
@@
 \tabletypesize{\normalsize}
-\tablecaption{Monte Carlo Validation Parameters
+\tablecaption{Monte Carlo Spectral Parameters
 \label{ts_ext_num_sims}
@@
     statistically independent simulations and the average value of \ts is
-    also tabulated.  The models spans representative spectral parameters.
+    also tabulated.  The models span representative spectral parameters.
 }
@@
     The detection threshold to resolve a
-    uniform disk extended source for a two-year exposure.  All sources
+    uniform surface brightness extended source for a two-year exposure.  All sources
     have an assumed power-law spectrum and the different colors correspond
@@
     detection threshold using photons with energies between 100 \mev and 100
-    \gev while the dashed line is the threshold using 1 \gev to 100 \gev photons.
+    \gev while the dashed line is the threshold using 
+     photons with energies between 1 \gev and 100 \gev.
     }\label{index_sensitivity}
@@
     and three background ($1\times$, $10\times$, and $100\times$ the
-    Sreekumar-like isotropic spectrum) for a two-year exposure. The
-    left plots are the detection threshold when using 1 \gev to 100 \gev
-    photons and the right plots are the detection threshold when using
-    10 \gev to 100 \gev photons.  The flux is integrated only in the
+    Sreekumar-like isotropic background) for a two-year exposure. The
+    left plots are the detection threshold when using 
+    photons with energies between
+    1 \gev and 100 \gev
+    and the right plots are the detection threshold when using
+    photons with energies between
+    10 \gev and 100 \gev.  The flux is integrated only in the
     selected energy range.  Overlaid on this plot are the LAT detected
@@
     diffuse emission and the energy range they were analyzed with.
-    The star shaped markers (colored red in the electronic version)
+    The star-shaped markers (colored red in the electronic version)
     are sources with a spectral index closer to 1.5, the triangular
@@
 \tablecomments{
-      The detection threshold to resolve a uniform disk spatially extended
-      sources for a two-year exposure
-      for sources of varying energy
-      ranges, spectral indices, and background levels.  The extended
-      sources were simulated against a Sreekumar-like isotropic spectrum
+      The detection threshold to resolve spatially extended
+      sources with a uniform surface brightness for a two-year exposure
+      The threshold is calculated for
+      sources of varying energy
+      ranges, spectral indices, and background levels.  The sensitivity
+      was calculated against
+      a Sreekumar-like isotropic background
       and the second column is the factor that the simulated background
@@
     \caption{
-    \hl{
     The LAT's projected detection threshold to extension after a ten-year exposure
@@
     the exposure.
-    }
     }\label{time_sensitivity}
@@
   A test statistic map generated for the region around the SNR 
-  IC443 using 1 \gev to 100 \gev photons.  (a) test statistic map after
+  IC443 using 
+  photons with energies between
+  1 \gev and 100 \gev.  (a) test statistic map after
   subtracting IC443 modeled as a point-like source. (b) same as (a), but
@@
     region around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian
-    kernel. The plus-shaped marker and circle circle (colored red in
+    kernel. The plus-shaped marker and circle (colored red in
     the online version) represent the center and size of the best fit
@@
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v6/agn.py
-    \caption{The cumulative density of \tsext for 783 of the clean
-    AGN in 2LAC which are significant above 1 \gev calculated with \pointlike (dashed line
+    \caption{The cumulative density of \tsext for the 783 clean
+    AGN in 2LAC that were significant above 1 \gev calculated with \pointlike (dashed line
     colored blue in the electronic version)
@@
 \tablenotetext{(a)}{
-Integrated in the fit energy range (either 1 \gev to 100 \gev or 10 \gev 100 \gev).
-}
+Integrated in the fit energy range (either 1 \gev to 100 \gev or 10 \gev 100 \gev).  }
 
@@
   \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
-  of the region around 2FGL\,J0823.0$-$4246 smoothed by a 0\fdg1 2D
+  of 2FGL\,J0823.0$-$4246 smoothed by a 0\fdg1 2D
   Gaussian kernel.  The triangular marker 
@@
 
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+      \plotone{summary_plots/snr_seds_color.eps}
+    \else
+      \plotone{summary_plots/snr_seds_bw.eps}
+    \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_snr_seds.py
+    \caption{
+    The spectral energy distribution of the extended sources 
+    Puppis A (2FGL\,J0823.0$-$4246) and $\gamma$-Cygni 
+    (2FGL\,J2021.5+4026).
+    The lines (colored red in the online version)
+    are the best fit power-law spectral models of
+    these sources.
+    The spectral errors are statistical only.
+    }
+    \label{snr_seds}
+  \end{figure}
+
 \begin{figure}
@@
   \caption{
-    \hl{
   A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of (a) the region
   around 2FGL\,J1627.0$-$2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
-  also the emission from the background source 2FGL\,J1625.7$-$2526
+  also the emission from 2FGL\,J1625.7$-$2526
   subtracted.  The triangular marker 
@@
   been smoothed by a 0\fdg25 2D Gaussian kernel.
-  }
   }\label{1FGL_J1628.6-2419c}
@@
   \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
-  of the region around 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg25 2D
+  of 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg25 2D
   Gaussian kernel and (b) with the emission from the background sources
   subtracted.  This source is spatially coincident with RX\,J1713.7$-$3946
-  and was recently reported by \cite{rx_j1713_lat}.  The triangular marker
-  (colored red in the online version) represents the 2FGL position of this
-  source.  The plus-shaped marker and 
-  the circle (colored red) are the best fit position
-  and extension of this source assuming a radially symmetric uniform
-  surface brightness.  The contours (colored light blue) correspond
-  to the \tev image \citep{rx_j1713_hess}.  The region was analyzed
-  with the same background model as \cite{rx_j1713_lat}. Source A is
-  coincident with 2FGL\,J1715.4$-$4024c and the circular and square-shaped
-  marker
-  (colored blue) represent the 2FGL and relocalized position of this
-  source respectively.  The diamond-shaped markers
-  (colored purple) represent
-  the position of source B and C that were added to the background model.
+  and was recently studied in \cite{rx_j1713_lat}.  The triangular marker
+  (colored red in the online version) represents the 2FGL position of
+  this source.  The plus-shaped marker and the circle (colored red) are
+  the best fit position and extension of this source assuming a radially
+  symmetric uniform surface brightness.  The contours (colored light blue)
+  correspond to the \tev image \citep{rx_j1713_hess}.  The region was
+  analyzed with the same background model as \cite{rx_j1713_lat}. Source
+  A is coincident with 2FGL\,J1715.4$-$4024c and the circular and
+  square-shaped marker (colored blue) represent the 2FGL and relocalized
+  position of this source respectively.  The diamond-shaped markers
+  (colored purple) represent the position of source B and C that were
+  added to the background model.
   }\label{2FGL_J1712.4-3941}
@@
   \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  the region around 2FGL\,J0851.7$-$4635 smoothed by a 0\fdg25 2D Gaussian
+  2FGL\,J0851.7$-$4635 smoothed by a 0\fdg25 2D Gaussian
   kernel. The triangular marker (colored red in the electronic version)
@@
     A diffuse-emission-subtracted 10 \gev to 100 \gev counts
-    map of the region around 2FGL\,J1615.0$-$5051 (upper left)
+    map of 2FGL\,J1615.0$-$5051 (upper left)
     and 2FGL\,J1615.2$-$5138 (lower right) smoothed by a 0\fdg1
@@
   \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  the region around 2FGL\,J1632.4$-$4753c smoothed by a 0\fdg1 2D Gaussian
+  2FGL\,J1632.4$-$4753c smoothed by a 0\fdg1 2D Gaussian
   kernel.  The triangular marker (colored red in the electronic version)
   represents the 2FGL position of this source.  The plus-shaped marker
-  and the circle (colored red) are the best fit position and extension
+  and the circle (colored red) are the best fit position and extension of
   2FGL\,J1632.4$-$4753c assuming a radially symmetric uniform surface
-  brightness.  The four star-shaped markers (colored red) represent 2FGL
+  brightness.  The four star-shaped markers (colored green) represent 2FGL
   sources that were removed from the background model.  The circular
   and square markers (colored blue) represent the 2FGL and relocalized
-  positions respectively of (from left to right) 2FGL\,J1635.4$-$4717c
-  and 2FGL\,J1636.3$-$4740c.  
+  positions respectively of 2FGL\,J1635.4$-$4717c (left)
+  and 2FGL\,J1636.3$-$4740c (right).  
   The contours (colored light blue) correspond to the \tev image of
@@
   (colored blue) represent the 2FGL and the relocalized position of
-  (from left to right) 2FGL\,J1839.3$-$0558c, 2FGL\,J1836.8$-$0623c,
-  and 2FGL\,J1834.7$-$0705c.  The star-shaped marker 
+  2FGL\,J1839.3$-$0558c (left), 2FGL\,J1836.8$-$0623c (middle),
+  and 2FGL\,J1834.7$-$0705c (right).  The star-shaped marker 
   (colored green) represent a
@@
     \ifcolorfigure
-      \plotone{summary_plots/snr_seds_color.eps}
-    \else
-      \plotone{summary_plots/snr_seds_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_snr_seds.py
-    \caption{
-    \hl{
-    The spectral energy distribution of the extended sources 
-    Puppis A (2FGL\,J0823.0$-$4246) and $\gamma$-Cygni 
-    (2FGL\,J2021.5+4026).
-    The lines (colored red in the online version)
-    are the best fit power-law spectral model of
-    these sources.
-    The spectral errors are statistical only.}
-    }
-    \label{snr_seds}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
       \plotone{summary_plots/hess_seds_color.eps}
@@
     extended \tev sources.  The black points
-    with circular markers are the LAT data points. The points with
-    dashed markers (colored red in the electronic version) are the
-    H.E.S.S points of the associated sources.  Plot (a) shows the
+    with circular markers are obtained by the LAT. The points with
+    plus-shaped markers (colored red in the electronic version) are
+    for the associated H.E.S.S sources.  (a) the
     LAT SED of 2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED
-    of HESS\,J1616$-$508.  Plot (b) shows 2FGL\,J1615.2$-$5138
-    and HESS\,J1614$-$518. Plot (c) shows 2FGL\,J1632.4$-$4753c
-    and HESS\,J1632$-$478. Plot (d) shows 2FGL\,J1837.3$-$0700c
+    of HESS\,J1616$-$508. (b) 2FGL\,J1615.2$-$5138
+    and HESS\,J1614$-$518. (c) 2FGL\,J1632.4$-$4753c
+    and HESS\,J1632$-$478. (d) 2FGL\,J1837.3$-$0700c
     and HESS\,J1837$-$069. The H.E.S.S. data points are from
-    \citep{hess_plane_survey} Both LAT and H.E.S.S. spectral errors are
+    \citep{hess_plane_survey}. Both LAT and H.E.S.S. spectral errors are
     statistical only.}
@@
       % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v2/run.py
-      \caption{A plot of the 21
+      \caption{The 21
       spatially extended sources detected by the LAT
-      in the \gev energy range
+      at \gev energies 
       with two years of data.  The twelve extended sources included in
@@
     A comparison of the size of extended sources detected at
-    both \gev and \tev energies.  The \tev extensions of W30,
+    both \gev and \tev energies.  The \tev size of W30,
     2FGL\,J1837.3$-$0700c, 2FGL\,J1632.4$-$4753c, 2FGL\,J1615.0$-$5051,
     and 2FGL\,J1615.2$-$5138 are from \cite{hess_plane_survey}.
-    The \tev extensions of MSH\,15$-$52, HESS\,J1825$-$137,
+    The \tev size of MSH\,15$-$52, HESS\,J1825$-$137,
     Vela X, Vela Jr., RX\,J1713.7$-$3946 and W28 are from
     \cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
-    The \tev extension of IC443 is from \cite{ic443_veritas} and
+    The \tev size of IC443 is from \cite{ic443_veritas} and
     W51c is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev
@@
     The LAT extension of
-    Vela X is from \cite{velax}.  Except for RX\,J1713.7$-$3946 Vela Jr.,
+    Vela X is from \cite{velax}.  Except for RX\,J1713.7$-$3946 and Vela Jr.,
     the \tev sources were fit assuming a 2D Gaussian surface brightness
@@
     their large size, the shape of RX\,J1713.7$-$3946 and Vela Jr.
-    were not directly fit in \tev energies. Here, we take their sizes to be the
+    were not directly fit at \tev energies. Here, we take their sizes to be the
     same as the LAT size and do not converted them to \rsixeight. The LAT
@@
     brightness model so the LAT and H.E.S.S. sizes are first converted
-    to \rsixeight.  (see Section~\ref{compare_source_size}). Because
+    to \rsixeight. Because
     the spatial morphology of RX\,J1713.7$-$3946 and Vela Jr. is poorly
-    matched by a 2D Gaussian surface brightness model, the \gev and \tev
-    extensions are included assuming a uniform surface brightness.
+    described by a 2D Gaussian surface brightness model, the \gev and \tev
+    extensions are included assuming a uniform surface brightness model.
     }\label{gev_vs_tev_histogram}

### 2011-09-15 extended_catalog/paper/extended_catalog.tex
update draft
udpate code

@@
 \documentclass[12pt,preprint]{aastex}
+
+% Changes from v2.0 to v3.0
+
+% * Move section 'Dual Localization' to its own
+%   section after 'Extended Source Detection Threshold'
+%   and rename it 'Testing Against Source Confusion'
+%   -> Significantly expanded the section with a new
+%      monte carlo study fitting extended sources as
+%      two point sources, and vice versa
+%
+% * replace all occurances of ts_inc with ts_2pts
+%%%%%%%%
+% * Added acknowlegements section to end of the paper
+% * Move HESS SEDs to earlier in paper to fix order.
+% * Fix some occurances of chi^2 to correctly be chi^2_1
+% * Better description of how the alternate diffuse model
+%   is different from galprop
+% * Add galprop citation
+% * Add AGILE Gamma Cygni Pulsar citation.
 
@@
 \newcommand{\km}{\text{km}\xspace}
-\newcommand{\phflux}{\ensuremath{\text{ph}\ \text{cm}^{-2}\,\text{s}^{-1}}\xspace}
+\newcommand{\phflux}{\ensuremath{\text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}}\xspace}
 \newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
-\newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{inc}}}\xspace}
+\newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{2pts}}}\xspace}
 
@@
 \newcommand{\degree}{^\circ\xspace}
+
+%\newcommand{\newtext}[1]{{\textbf #1}}
+\newcommand{\newtext}[1]{{\bfseries \color{red}#1}}
 
@@
 
-\subsection{Dual Localization}
-\label{dual_localization_method}
-
-There is a degeneracy between a spatially extended source and multiple
-point-like  sources separated by angular distances comparable to or smaller than
-the size of the LAT PSF.  To assess the possibility of source confusion,
-we use \pointlike to simultaneously fit the position of two point-like sources
-in the region of extended source candidates.
-
-We define \tsinc as twice the increase in the log of the likelihood fitting the
-region as two point-like sources compared to fitting the region as one point-like
-source: 
-\begin{equation}
-  \tsinc=2\log(\likelihood_\text{2pts}/\likelihood_\text{ps}).
-\end{equation} 
-\tsinc can not be directly compared to \tsext to see which
-model is more significant because the models are not nested
-\citep{statistics_with_care}. Even though the comparison of \tsext with
-\tsinc is not a calibrated test, we find the cases $\tsinc \ll \tsext$
-and $\tsinc\gg\tsext$ suggestive and we only consider a source to be
-extended if $\tsext>\tsinc$.
-Similar to the case of extended sources described in Section~\ref{gtlike_crosscheck},
-the spectra of the two point-like sources can be refit using \gtlike.
-We quote the spectral values obtained from \gtlike using the best fit
-positions found using \pointlike.
-
 \subsection{Comparing Source Sizes}
@@
 
-We test the false detection probability of for the
-extended source test by fitting the extension of
-point-like sources.
-\cite{mattox_egret} discuss that the test statistic distribution
-for a likelihood ratio test on the existence of a source at
-a given position is 
+We tested the false detection probability for the extended source test
+by fitting the extension of point-like sources.  \cite{mattox_egret}
+discuss that the test statistic distribution for a likelihood ratio test
+on the existence of a source at a given position is
 \begin{equation}\label{ts_ext_distribution}
@@
 \end{equation}
-The particular form of Equation \ref{ts_ext_distribution} is
-due to the null hypothesis (source flux $\Phi=0$) residing
-on the edge of parameter space and the model hypothesis
-adding a single degree of freedom
-and leads to the often quoted result that the square root
-of the test statistic is the number of $\sigma$ of
-the detection. It is plausible to
-expect a similar distribution of the test statistic
-in the test for source extension since the same conditions
-apply (with the source flux $\Phi$ replaced by the source radius $r$ and
-$r<0$ being unphysical).
-We performed Monte Carlo
-simulations
-to calculate empirical distributions for $\tsext$ and
-we compared them to Equation~\ref{ts_ext_distribution}.
+The particular form of Equation \ref{ts_ext_distribution} is due to the
+null hypothesis (source flux $\Phi=0$) residing on the edge of parameter
+space and the model hypothesis adding a single degree of freedom and
+leads to the often quoted result that the square root of the test
+statistic is the number of $\sigma$ of the detection. It is plausible
+to expect a similar distribution of the test statistic in the test for
+source extension since the same conditions apply (with the source flux
+$\Phi$ replaced by the source radius $r$ and $r<0$ being unphysical).
+We performed Monte Carlo simulations to calculate empirical distributions
+for $\tsext$ and we compared them to Equation~\ref{ts_ext_distribution}.
 
@@
 Section~\ref{monte_carlo_validation}, but instead of point-like sources
-we simulated extended
-sources with a radially symmetric uniform surface
-brightness. Additionally, we
-simulated our sources over the two-year time range included
-in 2FGL.
-For each extension and
-spectral index, we selected a flux range which bracketed $\tsext=16$
-and performed an extension test for $>100$ independent realizations of
-ten fluxes in the range.
-We calculated $\langle\tsext\rangle=16$ by fitting a line to the flux
-and $\tsext$ values in the narrow range.
+we simulated extended sources with a radially symmetric uniform surface
+brightness. Additionally, we simulated our sources over the two-year
+time range included in 2FGL.  For each extension and spectral index,
+we selected a flux range which bracketed $\tsext=16$ and performed an
+extension test for $>100$ independent realizations of ten fluxes in
+the range.  We calculated $\langle\tsext\rangle=16$ by fitting a line
+to the flux and $\tsext$ values in the narrow range.
 
@@
 expected factor corresponding to the square root of the exposure.
+
+\section{Testing Against Source Confusion}
+\label{dual_localization_method}
+
+\newtext{
+It is impossible to discriminate with LAT data exclusively between a
+spatially extended source and multiple point-like sources separated by
+angular distances comparable to or smaller than the size of the LAT PSF.
+To assess the plausibility of source confusion, we used \pointlike to
+simultaneously fit the position and spectrum of two point-like sources
+in the region of extended source candidates.
+
+We define \tsinc as twice the increase in the log of the likelihood
+fitting the region as two point-like sources compared to fitting the
+region as one point-like source:
+\begin{equation}
+  \tsinc=2\log(\likelihood_\text{2pts}/\likelihood_\text{ps}).
+\end{equation} 
+\tsinc cannot be quantitatively compared to \tsext using a
+simple likelihood ratio test to evaluate which model provides the
+most significant improvement because the models are not nested
+\citep{statistics_with_care}.  Even though the comparison of \tsext
+with \tsinc is not a calibrated test, $\tsext>\tsinc$ indicates that
+the likelihood for the extended source hypothesis is higher than for
+two point-like sources and we only consider a source to be extended
+if $\tsext>\tsinc$.
+
+We assessed the power of the test comparing \tsinc to \tsext to correctly
+distinguish between source confusion and a spatially extended source using
+a Monte Carlo study.  We simulated two point sources and fit them as both
+an extended source and two point-like sources.  We then simulated two
+point sources and fit them with the same hypothesis. We could therefore
+compare \tsinc and \tsext for the case of there being actually two point
+sources and of there being extended source.  All sources were simulated
+using the same two-year time range included in 2FGL and all fit values
+were calculated using \pointlike.
+
+We did this study first in the energy range from 1 \gev to 100 \gev by
+simulating extended sources of flux $4\times10^{-9} \phflux$ in the 1
+\gev to 100 \gev energy range and with a power-law spectral model with
+spectral index 2.  This flux was picked to be representative of the
+new extended sourced that were discovered by our subsequent analysis
+looking at energies between 1 \gev and 100 \gev
+(see section~\ref{new_ext_srcs_section}).
+We simulated these sources using a uniform surface brightness spatial
+model with extensions varying
+up to $1\degree$.  Figure~\ref{confusion_plot}a shows 
+the distribution of \tsinc and \tsext as a
+function of the simulated extension of the source
+for 200 statistically independent simulations.
+
+Figure~\ref{confusion_plot}c shows the same analysis but when fitting
+simulations of two point-like sources each with power-law spectral models
+with a spectral index of 2.  Here, the two point-like sources are each given half
+of the flux of the extended source ($2\times10^{-9} \phflux$ integrated
+from 1 \gev to 100 \gev) to ensure that the two point-like sources predict
+the same number of photons but with a different spatial shape.
+Finally, figure~\ref{confusion_plot}e shows the same analysis but with
+one point source given a spectral index of 1.5 and the other point source
+given an index of 2.5, but with each point source still have an integral
+1 \gev to 100 \gev flux of $2\times10^{-9} \phflux$.
+
+The same three plots are shown in 
+figure~\ref{confusion_plot}b, figure~\ref{confusion_plot}d,
+and figure~\ref{confusion_plot}f but this time when analyzing
+a source of flux $10^{-9} \phflux$ (integrated from 10 \gev to 100 \gev) 
+analyzed only in the 10 \gev to 100 \gev energy range.
+This spectrum is typical 
+of the new extended sources discovered using only photons with energies
+between 1 \gev and 100 \gev (see section~\ref{new_ext_srcs_section}).
+
+Several interesting conclusions can be made from this Monte
+Carlo study. The overall behavior of these plots is what one would
+expect. \tsext is on average greater than \tsinc when fitting simulated
+extended sources whereas \tsinc is greater than \tsext when fitting two
+simulated point sources.  Furthermore, the distributions of \tsext and
+\tsinc separate better when the extended source is bigger and when the
+two point sources are farther apart.
+
+On the other hand, the plots show that for extended sources with typical
+sizes $\sim0\fdg5$, one can often obtain almost as good a likelihood
+increase when fitting a simulated extended source as two point sources and
+that \tsinc is often not much larger.  This makes sense because although
+two point-like sources represent an incorrect spatial model when fitting
+an extended sources, the two point-like sources have three more degrees
+of freedom than the one extended source and can therefore easy model
+statistical fluctuations in the counts distribution to create almost as
+good a fit.  This effect is most pronounced when using energies from 1
+\gev to 100 \gev where the PSF is even larger.  From this, we conclude
+that if we have an extended source candidate where \tsinc is smaller
+than but comparable to \tsext, this is not good evidence that we are
+most likely seeing instead source confusion.
+
+When testing the two simulated point-like sources for extension, our
+test did a better job at separating the distribution of \tsinc and
+\tsext, especially for larger separation distances.  This says that
+when there are two point-like sources instead of one extended source,
+we really are less likely to confuse the emission as looking more like
+a spatially extended source.
+
+Talk about how comparing the spectral index is often a
+difficult way to distinguish between two point sources
+and one extended source. Discuss figure \ref{index_difference}.
+
+From study, we see that \dots
+
+Conclusions from the MC study:
+* TSinc can be very large even for a true extended source.
+
+This shows that the LAT can not uniquiely determinte what featuers
+we see in the data. The 2FGL catalog's method of fitting all residuals
+as new point sources is incorrect as is assuming everything is an
+extended source an not source confusion. A more nuanced, but somewhat arbitrary,
+criterion must be used on a case by case basis using multiwavelenth
+information to decide whether we believe our best fit model is 
+composed of multiple separate sources or one spatially extended source.
+
+Even so, if the LAT detects a source as being extended, it could
+likely in the future be resolved into multiple point sources.
+This is actually almost inevitable because of the large density of
+sources in the galactic plane which could all be \gev emitters.
+
+Even though this dedicated monte carlo study was performed
+using \pointlike, for the analysis of LAT data we took the best
+fit positions of the two point-like sources and refit them using \gtlike.
+We quote the spectral values obtained from \gtlike using the best fit
+positions of the two point-like sources found using \pointlike.
+
+}
 
@@
 
-We estimate a second systematic error on the extension of a source
-due to uncertainty in out model of the Galactic diffuse emission by
-using an alternative diffuse model based
-upon GALPROP\footnote{GALPROP is a software package for calculating the
+\newtext{
+We estimated a second systematic error on the extension of a source
+due to uncertainty in our model of the Galactic diffuse emission by
+using an alternative model which takes as input templates
+calculated by
+GALPROP\footnote{GALPROP is a software package for calculating the
 Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
-in the Galaxy. See \url{http://galprop.stanford.edu/} for details
-and references.} and used in the LAT analysis of the isotropic diffuse
-emission \citep{isotropic_lat}.  The intensities of various components
+in the Galaxy \citep{galprop1998,galprop2011}. 
+See also \url{http://galprop.stanford.edu/} for details.} 
+but then fits each template locally in
+the surrounding region.
+The particular GALPROP model that was used as input is described in
+the LAT analysis of the isotropic diffuse
+emission \citep{isotropic_lat}.  
+}
+The intensities of various components
 of the Galactic diffuse emission were fitted individually using a
@@
 The cumulative density of \tsext for these AGN compared to the
-$\chi^2/2$ distribution of Equation~\ref{ts_ext_distribution}
+$\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
 is
@@
 (PSR\,J2021+4026, \cite{first_lat_pulsar_cat}). 
+\newtext{
+This
+pulsar was also observed by AGILE \citep{gamma_cygni_agile}.
+}
 
@@
 high-energy emission seen from these sources.
+
+\newtext{
+
+The \textit{Fermi} LAT Collaboration acknowledges generous ongoing support
+from a number of agencies and institutes that have supported both the
+development and the operation of the LAT as well as scientific data analysis.
+These include the National Aeronautics and Space Administration and the
+Department of Energy in the United States, the Commissariat \`a l'Energie Atomique
+and the Centre National de la Recherche Scientifique / Institut National de Physique
+Nucl\'eaire et de Physique des Particules in France, the Agenzia Spaziale Italiana
+and the Istituto Nazionale di Fisica Nucleare in Italy, the Ministry of Education,
+Culture, Sports, Science and Technology (MEXT), High Energy Accelerator Research
+Organization (KEK) and Japan Aerospace Exploration Agency (JAXA) in Japan, and
+the K.~A.~Wallenberg Foundation, the Swedish Research Council and the
+Swedish National Space Board in Sweden.
+
+Additional support for science analysis during the operations phase is gratefully
+acknowledged from the Istituto Nazionale di Astrofisica in Italy and the Centre National d'\'Etudes Spatiales in France.
+
+This research has made use of
+pywcsgrid2, an open-source plotting package for
+Python\footnote{http://leejjoon.github.com/pywcsgrid2/}. The authors acknowledge the
+use of HEALPix\footnote{http://healpix.jpl.nasa.gov/} \citep{healpix}.
+
+}
 
@@
 \clearpage
-
 \begin{figure}
@@
 
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{mc_plots/confusion_plot_color.eps}
+    \else
+    \plotone{mc_plots/confusion_plot_bw.eps}
+    \fi
+    % this plot came from 
+    \caption{Testing Confusion.
+    }\label{confusion_plot}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{mc_plots/index_difference_color.eps}
+    \else
+    \plotone{mc_plots/index_difference_bw.eps}
+    \fi
+    % this plot came from 
+    \caption{Index difference.
+    }\label{index_difference}
+  \end{figure}
+
 \begin{figure}
@@
     and too small to be resolved by the LAT. Therefore, the cumulative
-    density of $\tsext$ is expected to follow a $\chi^2/2$ distribution
+    density of $\tsext$ is expected to follow a $\chi^2_1/2$ distribution
     (Equation~\ref{ts_ext_distribution}, the dash-dotted line colored
@@
 
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+      \plotone{summary_plots/hess_seds_color.eps}
+    \else
+      \plotone{summary_plots/hess_seds_bw.eps}
+    \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_hess_seds.py
+    \caption{
+    The spectral energy distribution of four extended
+    sources associated with unidentified
+    extended \tev sources.  The black points
+    with circular markers are obtained by the LAT. The points with
+    plus-shaped markers (colored red in the electronic version) are
+    for the associated H.E.S.S sources.  (a) the
+    LAT SED of 2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED
+    of HESS\,J1616$-$508. (b) 2FGL\,J1615.2$-$5138
+    and HESS\,J1614$-$518. (c) 2FGL\,J1632.4$-$4753c
+    and HESS\,J1632$-$478. (d) 2FGL\,J1837.3$-$0700c
+    and HESS\,J1837$-$069. The H.E.S.S. data points are from
+    \citep{hess_plane_survey}. Both LAT and H.E.S.S. spectral errors are
+    statistical only.}
+    \label{hess_seds}
+  \end{figure}
+
 \begin{figure}
@@
   }\label{1FGL_J2020.0+4049}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/hess_seds_color.eps}
-    \else
-      \plotone{summary_plots/hess_seds_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_hess_seds.py
-    \caption{
-    The spectral energy distribution of four extended
-    sources associated with unidentified
-    extended \tev sources.  The black points
-    with circular markers are obtained by the LAT. The points with
-    plus-shaped markers (colored red in the electronic version) are
-    for the associated H.E.S.S sources.  (a) the
-    LAT SED of 2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED
-    of HESS\,J1616$-$508. (b) 2FGL\,J1615.2$-$5138
-    and HESS\,J1614$-$518. (c) 2FGL\,J1632.4$-$4753c
-    and HESS\,J1632$-$478. (d) 2FGL\,J1837.3$-$0700c
-    and HESS\,J1837$-$069. The H.E.S.S. data points are from
-    \citep{hess_plane_survey}. Both LAT and H.E.S.S. spectral errors are
-    statistical only.}
-    \label{hess_seds}
 \end{figure}

### 2011-09-15 extended_catalog/paper/extended_catalog.tex
draft

@@
 a source of flux $10^{-9} \phflux$ (integrated from 10 \gev to 100 \gev) 
-analyzed only in the 10 \gev to 100 \gev energy range.
+only in the 10 \gev to 100 \gev energy range.
 This spectrum is typical 
@@
 * TSinc can be very large even for a true extended source.
+* Say Something about how there could be multiple point sources,
+  but all of this is below our detector resolution.
 

### 2011-09-21 extended_catalog/paper/extended_catalog.tex
udpated draft

@@
 %   section after 'Extended Source Detection Threshold'
-%   and rename it 'Testing Against Source Confusion'
-%   -> Significantly expanded the section with a new
+%   and rename it 'Testing Against Source Confusion'.
+%   The section is significantly expanded with a new
 %   monte carlo study fitting extended sources as
-%      two point sources, and vice versa
+%   two point-like sources, and vice versa
 %
-% * replace all occurances of ts_inc with ts_2pts
-%%%%%%%%
+% * Major rewrite of ``Extended Source Search Method'' section.
+%   This section now more correctly explains how the
+%   analysis search was done as well as cautions the
+%   reader about what caveats may apply to the analysis.
+
+% * Major rewrite of the sections on the new extended sources
+%   to better describe why various point sources were removed
+%   and why some were kept using multiwavelenth information.
+
+% * Move AGN validation section earlier in the text
+%   so that it is the first section analyzing actual LAT 
+% * Move section on reanalyzing 2FGL sources
+%   to earlier in the paper to be right after the AGN
+%   validation.
+% * Move earlier section discussing systematic errors
+% * better description of how two of the 'new extended sources'
+%   already have dedicated publications
+
+% * Remake 2FGL J1632.4-4753c smoothed counts map plot to show
+%   before + after background subtraction
+%
+% * Reordered Gamma-Cygni section to first discuss the pulsar.
+%
+% * For HESS J1837, smooth image by a 0.15 degree Gaussain
+%   instead of a 0.1 degree gausian
+%   kernel to surpress some of the noise which is likely spurious.
+%   Also, add in some lower level contour from HESS data
+%   to better show how wide the HESS emission is.
+%
+% * Rewrote the 'preview of what's to come section
+%   in the introduction to have the right order.
+%
+% * Cleaned up the Comparing source size section.
+% * Better description of converting TSext into sigma.
+% * better warning about the limits of the alternate diffuse model.
+% * Fixed figure order.
+% * made tickmarks white in plots.
+% * replace all occurrences of ts_inc with ts_2pts
+% * changed zoom of IC443 res tsmap to be easier to view.
+% * Added LAT collaboration citation of W30.
+%
 % * Added acknowlegements section to end of the paper
@@
 % * Add galprop citation
-% * Add AGILE Gamma Cygni Pulsar citation.
+% * Add AGILE citation Gamma Cygni Pulsar citation.
 
@@
 Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
-simulations to validate this tool and calculate the LAT's threshold for
+simulations to validate this tool and calculate the LAT threshold for
 detecting the spatial extension of sources.  We then test all sources
-in the second \fermi-LAT catalog (2FGL) for extension. We report the
-detection of nine spatially extended sources in addition to the twelve
-spatially extended sources reported in 2FGL.
+in the second \fermi-LAT catalog (2FGL) for extension. 
+\newtext{
+We report the
+detection of seven spatially extended sources in addition to the twelve
+spatially extended sources reported in 2FGL and two other sources studied
+in dedicated publications.
+}
 \end{abstract}
@@
 and the Cygnus Loop
-\citep{w51c,castro_and_slane_2010,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, three extended
+\citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, three 
 PWNe were detected as being extended: MSH\,15$-$52, Vela~X, and
 HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
-close-by galaxies, the Large and Small Magalenic Clouds, and one
+close-by galaxies, the Large and Small Magellanic Clouds, and one
 radio galaxy, Centarus A, were spatially resolved at \gev energies
@@
 have no detectable extension.  High-energy $\gamma$-rays from
-these sources originate by the decay of $\pi^0$s produced by hadronic
+these sources are produced by the decay of $\pi^0$s produced by hadronic
 interactions with interstellar matter and by relativistic electrons
-due to Inverse Compton (IC) scattering and Bremsstrahlung radiation
-\citep{blandford_and_eichler_1987}.  It is likely that the \gev and
+due to Inverse Compton (IC) scattering and Bremsstrahlung radiation.  
+It is plausible that the \gev and
 \tev emission from these sources originates from the same population of
@@
 The LAT is a pair conversion telescope that has been surveying the
-$\gamma$-ray sky since 2008 June.  The LAT has broad energy coverage
+$\gamma$-ray sky since 2008 August.  The LAT has broad energy coverage
 (20 \mev to $>300$ \gev), wide field of view ($\sim 2.4$ sr), and large
-effective area ($\sim 8000\ \cm^2$ at $>1 \gev$).  
-Using one year of all-sky surveying data, the LAT Collaboration published
-a catalog of 1451 sources significantly detected at \gev energies called 1FGL \citep{first_cat}.
-Using two years of data, a second catalog called 2FGL reported on 1873
-sources \citep{second_cat}.
-The counterparts of many of these sources can be spatially resolved
+effective area ($\sim 8000\ \cm^2$ at $>1 \gev$) 
+Additional information about the performance of the LAT can be found in
+\cite{atwood_LAT_mission}.
+Using 2 years of all-sky surveying data, the LAT Collaboration published
+a catalog of 1873
+sources significantly detected at \gev energies called 2FGL \citep{second_cat}.
+The possible counterparts of many of these sources can be spatially resolved
 when observed at other frequencies but detecting the spatial extension
@@
 due to the strong energy dependence of the LAT PSF, the spatial and
-spectral character of a source do not decouple. An inaccurate
+spectral characterization of a source cannot be
+decoupled. An inaccurate
 spatial model will bias the spectral model of the source and vice versa. Specifically,
@@
 shift a spectral analysis to softer indices. Furthermore, correctly
-modeling a source's extension is important for 
+modeling source extension is important for 
 understanding an entire region of the sky. For example,
-an incorrect model of the spatially extended LMC introduced
+an imperfect model of the spatially extended LMC introduced
 significant residuals in the surrounding region \citep{first_cat,second_cat}.
@@
 
-Previous analysis of
-extended LAT sources were performed as dedicated studies
-of individual sources, so we expect
-that a systematic scan of all LAT detected sources
-could uncover additional spatially extended sources.  For these
-reasons, in Section~\ref{analysis_methods_section} we present
-a new systematic method for analyzing spatially extended LAT sources. In
-Section~\ref{monte_carlo_validation}, we demonstrate that this method
-can be used to test the statistical significance of
-the extension of
-a LAT sources and in Section~\ref{extension_sensitivity} we calculate
-the LAT's detection threshold to resolve the extension of a source.
-In Section~\ref{extended_source_search_method}, we describe a search for
-new spatially extended LAT sources and in Section~\ref{validate_known}
-we reanalyze the twelve previously detected extended sources
-included in 2FGL.  In Section~\ref{test_2lac_sources} we further
-demonstrate that our detection method does not misidentify
-point-like sources as being extended 
-by testing the extension of active
-galactic nuclei (AGN) believed to be unresolvable. Finally, in
-Section~\ref{new_ext_srcs_section} we present the detection of the
+\newtext{
+Previous analysis of extended LAT sources were performed as dedicated
+studies of individual sources, so we expect that a systematic scan of
+all LAT detected sources could uncover additional spatially extended
+sources.  For these reasons, in Section~\ref{analysis_methods_section}
+we present a new systematic method for analyzing spatially extended
+LAT sources.  In Section~\ref{monte_carlo_validation}, we demonstrate
+that this method can be used to test the statistical significance of the
+extension of a LAT source and in Section~\ref{extension_sensitivity}
+we calculate the LAT detection threshold to resolve the extension
+of a source.  In Section~\ref{dual_localization_method}, we
+study the ability of the LAT to distinguish between spatially
+extended sources and confusion of nearby point-like sources.
+In Section~\ref{test_2lac_sources} we further demonstrate that our
+detection method does not misidentify point-like sources as being
+extended by testing the extension of active galactic nuclei (AGN)
+believed to be unresolvable.  In Section~\ref{validate_known},
+we systematically reanalyze the twelve extended sources included
+in 2FGL and in Section~\ref{systematic_errors_on_extension}
+we describe a way to estimate systematic errors on the extension of a source.
+In Section~\ref{extended_source_search_method}, we
+describe a search for new spatially extended LAT sources. Finally,
+in Section~\ref{new_ext_srcs_section} we present the detection of the
 extension of nine spatially extended sources that were reported in 2FGL
-but not previously spatially resolved.
+but as being point-like.  Two of these have been previously analyzed in
+dedicated publications.
+}
 
@@
 the Galactic plane due to systematic uncertainties in the Galactic
-diffuse emission.  The LAT's PSF is limited at its lowest detectable
+diffuse emission.  The LAT PSF is limited at its lowest detectable
 energies by multiple scattering in the silicon strip tracking section
@@
 since most high energy astrophysical sources have spectra that decrease
-rapidly with increasing energy, the improved resolution of the higher
-energy photons is typically offset by their low statistics. Therefore sophisticated
+rapidly with increasing energy, there are typically fewer higher
+energy photons with improved angular resolution. Therefore sophisticated
 analysis techniques are required to maximize the LATs sensitivity
@@
 spectrum of the source must be simultaneously fit to find the best fit
-parameters and to correctly compute the statistical significance of
-a detection.  Furthermore since the \gtlike likelihood profile approach
+parameters and to maximize the statistical significance of
+the detection.  Furthermore since the \gtlike likelihood profile approach
 is computationally intensive, no large-scale Monte Carlo simulations
@@
 on considerations of computing time.  The \pointlike algorithm was
-optimized for speed to handle larger numbers of sources efficiently
+optimized for speed to handle larger numbers of sources efficiently,
 which is important for our catalog scan and for being able
@@
 Section~\ref{monte_carlo_validation}, simultaneously fitting the
-position, extension, and spectrum is important to correctly calculate
+position, extension, and spectrum is important to maximize
 the statistical significance of the detection of extension of a source.
@@
 
-For extended sources with an assumed radially symmetric shape,
+For extended sources with an assumed radially-symmetric shape,
 we optimized the calculation by performing one
@@
 \end{equation}
+where $I_\text{src}(\vec r')$ is the spatial distribution of the
+source.
 For the LAT, the PSF can be parameterized by a King function \citep{king_function}:
@@
 where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
-\citep{matthew_kerr_thesis}.  For radially symmetric extended sources,
+\citep{matthew_kerr_thesis}.  For radially-symmetric extended sources,
 the angular part of the integral can be evaluated analytically
@@
 \tsext, we compare the likelihood fitting the source with an extended
-spatial model to the likelihood when fixing its extension to $10^{-10\,\circ}$.
+spatial model to the likelihood when the extension is
+fixed to a very small value ($10^{-10}$ degrees in radius 
+for a uniform surface brightness spatial model).
 
@@
 error is calculated by fixing the extension and spectrum of the source
-and fitting to the likelihood function a 2D Gaussian as a function
-of position.
+to their best fit value and then
+fitting to the likelihood function a 2D Gaussian as a function
+of position. This localization error algorithm is further described in
+\cite{second_cat}.
 
@@
 
-We tested two different models for the
-surface brightness profile, either a 2D Gaussian
+\newtext{
+We considered two different models to use for the
+surface brightness profile for extended sources, either a 2D Gaussian
+profile
 \begin{equation}\label{gauss_pdf}
-  I(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
+  I_\text{Gaussian}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
 \end{equation}
-or a uniform surface brightness
+or a uniform surface brightness profile
 \begin{equation}\label{disk_pdf}
-  I(x,y)=
+  I_\text{disk}(x,y)=
   \begin{cases}
@@
 Figure~\ref{compare_disk_gauss} shows the their PDF 
-are very similar for an example source of size
-0\fdg5.\footnote{To
+are similar for a source that has a 
+0\fdg5
+radius
+typical of LAT detected extended sources.
+To
 allow a valid comparison between the Gaussian and the uniform surface
 brightness morphologies,
-we define here the source size (0\fdg5) 
+we defined here the source size (0\fdg5) 
 as the radius containing
@@
 is defined in Equation~\ref{gauss_pdf} and
-Equation~\ref{disk_pdf} respectively.} The LAT 
-has little sensitivity /thereto the exact structure of extended source.
-Therefore, in our search for extended sources we used only a uniform
-surface brightness as our spatial extension shape. We quote the radius
-of the edge ($\sigma$) as the size of the source.
+Equation~\ref{disk_pdf} respectively.
+For this example, where $\rsixeight=0\fdg5$, 
+$\sigma_\text{disk}=0.61\degree$ and 
+$\sigma_\text{Gaussian}=0.33\degree$.
+
+For smaller and fainter extended sources, the differences in the PDF
+for different spatial models are lost in the noise and the LAT is not
+sensitive to the detailed spatial structure of the sources.  Therefore,
+in our search for extended sources we use only a radially-symmetric
+uniform surface brightness as our spatial extension shape. We quote the
+radius of the edge ($\sigma$) as the size of the source.
+}
 
@@
 sources. The point-like sources were simulated on top of an isotropic
-background with an integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux
+background with a power-law spectral model with
+integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux
+and spectral index 2.1.
+This was
 taken to be the same as the isotropic spectrum measured by EGRET
@@
 
+\newtext{
 Our study shows broad agreement between simulations and
-Equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is not
-perfect.  It should be noted that the discrepancy seems to be worst for
-bright sources where numerical errors in the convolution
-are most apparent.  Another possible
-reason for the departure from Equation~\ref{ts_ext_distribution} 
-is that \pointlike ignores energy dispersion which will change the
-PSF shape as a function of energy. We emphasize that many of
-the empirical distributions lie to the left of the theoretical curve so
-using the theoretical distribution will often lead to an underestimate of the
-statistical significance of a detection. Therefore, we are confident that
-\tsext can be used as a conservative measure of the statistical
-significance of a source's extension and we used it in the following analysis.
+Equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is
+not perfect.  It should be noted that the discrepancy seems to be
+worst for softer sources where we are anyways less sensitive to
+the source's extension.  One possible reason for departures from
+Equation~\ref{ts_ext_distribution} is that \pointlike ignores energy
+dispersion which will change the PSF shape as a function of energy.
+Considering the distribution in Figure~\ref{ts_ext_mc},
+the choice of a threshold \text set to 16 (correspond to a $4\sigma$
+detection if Equation~\ref{ts_ext_distribution} strictly held) is
+reasonable despite the imperfections of the corresponding calibration.
+}
 
@@
 
-We calculated the LAT's threshold to detect that a spatially extended
-source is extended. We define the detection threshold as the flux at which the value
-of $\tsext$ averaged over many statistical realizations of a source
-is $\langle\tsext\rangle=16$, corresponding to a $4\sigma$ detection.
+We calculated the LAT flux threshold to detect that a spatially extended
+source is extended. We define the detection threshold as the flux at
+which the value of $\tsext$ averaged over many statistical realizations is
+$\langle\tsext\rangle=16$ for a source of a given flux and true extension.
 
@@
 Section~\ref{monte_carlo_validation}, but instead of point-like sources
-we simulated extended sources with a radially symmetric uniform surface
+we simulated extended sources with a radially-symmetric uniform surface
 brightness. Additionally, we simulated our sources over the two-year
@@
 spectral indices from 1.5 to 3 and extensions varying from $\sigma=0\fdg1$
-to $2\fdg0$.  The LAT's flux threshold for a significant detection
+to $2\fdg0$.  
+The LAT flux threshold for a significant detection
 of source extension drops quickly with
 increasing source size and reaches a minimum around 0\fdg5. 
-Figure~\ref{index_sensitivity} shows
+\newtext{
+The threshold is high for small extensions because the
+source becomes
+small compared to the PSF. The threshold increases
+for large extended sources because the source becomes
+increasingly diluted by the background.
+} Figure~\ref{index_sensitivity} shows
 the threshold using photons with energies between 100 \mev and 100 \gev
 and also using only photons with energies between 1 \gev and 100 \gev.
-Except for very large ($>1\degree$) sources, our detection threshold is
+Except for very large or very soft
+sources, our detection threshold is
 not substantially improved by including photons with energies between 100 \mev and
@@
 energy bins between 100 \mev and 100 \gev. For IC443, which has a
-spectral index $\sim2.4$, almost the entire increase in likelihood
+spectral index $\sim2.4$ and an extension $\sim0\fdg35$, 
+almost the entire increase in likelihood
 modeling the source as being extended comes
-from energies above 1 \gev.  On the other hand, other systematic errors
-become increasingly important at low energy. For our extension search,
+from energies above 1 \gev.  Furthermore, other systematic errors
+become increasingly important at low energy. For our extension search
+(Section~\ref{extended_source_search_method}),
 we therefore used only photons with energies above 1 \gev.
@@
 higher background.  When studying sources only at energies above 1 \gev,
-the LAT's detection threshold (defined as the 1 \gev to 100 \gev flux at
+the LAT detection threshold (defined as the 1 \gev to 100 \gev flux at
 which $\langle\tsext\rangle=16$) depends less strongly on the source's
-spectral index. The index dependence of the detection threshold is
-even weaker when considering only photons with energies above 10 \gev.
+spectral index. 
+\newtext{
+The index dependence of the detection threshold is
+even weaker when considering only photons with energies above 10 \gev
+because the PSF changes little from 10 \gev to 100 \gev.}
 Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
@@
 
-Finally, Figure~\ref{time_sensitivity} shows the LAT's projected
-detection threshold to extension with a 10 year
+Finally, Figure~\ref{time_sensitivity} shows the projected
+detection threshold of the LAT to extension with a 10 year
 exposure against 10 times
-the isotropic background. This background is representative of the
+the isotropic background measured by EGRET. This background is representative of the
 background near the Galactic plane.  For small extended sources, our
@@
 angular distances comparable to or smaller than the size of the LAT PSF.
-To assess the plausibility of source confusion, we used \pointlike to
-simultaneously fit the position and spectrum of two point-like sources
-in the region of extended source candidates.
-
-We define \tsinc as twice the increase in the log of the likelihood
+To assess the plausibility of source confusion for situations
+in which $\tsext>16$, we developed an algorithm in \pointlike to
+simultaneously fit the position and spectrum of two point-like sources.
+
+After simultaneously fitting the two positions and two spectra,
+we define \tsinc as twice the increase in the log of the likelihood
 fitting the region as two point-like sources compared to fitting the
@@
 \tsinc cannot be quantitatively compared to \tsext using a
-simple likelihood ratio test to evaluate which model provides the
-most significant improvement because the models are not nested
+simple likelihood ratio test to evaluate which model
+is 
+significantly better because the models are not nested
 \citep{statistics_with_care}.  Even though the comparison of \tsext
@@
 
-We assessed the power of the test comparing \tsinc to \tsext to correctly
-distinguish between source confusion and a spatially extended source using
-a Monte Carlo study.  We simulated two point sources and fit them as both
+We assessed the power of the $\tsext>\tsinc$ test using a Monte Carlo
+study.  We simulated one spatially extended sources and fit it as both
 an extended source and two point-like sources.  We then simulated two
-point sources and fit them with the same hypothesis. We could therefore
-compare \tsinc and \tsext for the case of there being actually two point
-sources and of there being extended source.  All sources were simulated
-using the same two-year time range included in 2FGL and all fit values
-were calculated using \pointlike.
+point-like sources and fit them with the same two hypothesis. By comparing
+the distribution of \tsinc and \tsext for the two cases, we evaluated
+how well comparing \tsext to \tsinc is at rejecting the possibility of
+source confusion as well as how likely it is to incorrectly reject an
+extended source as being extended.  All sources were simulated using
+the same two-year time range included in 2FGL and all fit values were
+calculated using \pointlike. The simulations were performed against
+an background 10 times the isotropic background measured by EGRET,
+representative of the background near the Galactic plane.
 
 We did this study first in the energy range from 1 \gev to 100 \gev by
-simulating extended sources of flux $4\times10^{-9} \phflux$ in the 1
-\gev to 100 \gev energy range and with a power-law spectral model with
+simulating extended sources of flux $4\times10^{-9} \phflux$ integrated
+from 1 \gev to 100 \gev and a power-law spectral model with
 spectral index 2.  This flux was picked to be representative of the
-new extended sourced that were discovered by our subsequent analysis
-looking at energies between 1 \gev and 100 \gev
-(see section~\ref{new_ext_srcs_section}).
+new extended sourced that were discovered in the following analysis
+when looking in the 1 \gev and 100 \gev energy range
+(see Section~\ref{new_ext_srcs_section}).
 We simulated these sources using a uniform surface brightness spatial
@@
 
-Figure~\ref{confusion_plot}c shows the same analysis but when fitting
-simulations of two point-like sources each with power-law spectral models
-with a spectral index of 2.  Here, the two point-like sources are each given half
-of the flux of the extended source ($2\times10^{-9} \phflux$ integrated
-from 1 \gev to 100 \gev) to ensure that the two point-like sources predict
-the same number of photons but with a different spatial shape.
-Finally, figure~\ref{confusion_plot}e shows the same analysis but with
-one point source given a spectral index of 1.5 and the other point source
-given an index of 2.5, but with each point source still have an integral
-1 \gev to 100 \gev flux of $2\times10^{-9} \phflux$.
-
-The same three plots are shown in 
-figure~\ref{confusion_plot}b, figure~\ref{confusion_plot}d,
-and figure~\ref{confusion_plot}f but this time when analyzing
-a source of flux $10^{-9} \phflux$ (integrated from 10 \gev to 100 \gev) 
-only in the 10 \gev to 100 \gev energy range.
-This spectrum is typical 
-of the new extended sources discovered using only photons with energies
-between 1 \gev and 100 \gev (see section~\ref{new_ext_srcs_section}).
-
-Several interesting conclusions can be made from this Monte
-Carlo study. The overall behavior of these plots is what one would
-expect. \tsext is on average greater than \tsinc when fitting simulated
-extended sources whereas \tsinc is greater than \tsext when fitting two
-simulated point sources.  Furthermore, the distributions of \tsext and
-\tsinc separate better when the extended source is bigger and when the
-two point sources are farther apart.
-
-On the other hand, the plots show that for extended sources with typical
-sizes $\sim0\fdg5$, one can often obtain almost as good a likelihood
-increase when fitting a simulated extended source as two point sources and
-that \tsinc is often not much larger.  This makes sense because although
-two point-like sources represent an incorrect spatial model when fitting
-an extended sources, the two point-like sources have three more degrees
-of freedom than the one extended source and can therefore easy model
-statistical fluctuations in the counts distribution to create almost as
-good a fit.  This effect is most pronounced when using energies from 1
-\gev to 100 \gev where the PSF is even larger.  From this, we conclude
-that if we have an extended source candidate where \tsinc is smaller
-than but comparable to \tsext, this is not good evidence that we are
-most likely seeing instead source confusion.
-
-When testing the two simulated point-like sources for extension, our
-test did a better job at separating the distribution of \tsinc and
-\tsext, especially for larger separation distances.  This says that
-when there are two point-like sources instead of one extended source,
-we really are less likely to confuse the emission as looking more like
-a spatially extended source.
-
-Talk about how comparing the spectral index is often a
-difficult way to distinguish between two point sources
-and one extended source. Discuss figure \ref{index_difference}.
-
-From study, we see that \dots
-
-Conclusions from the MC study:
-* TSinc can be very large even for a true extended source.
-* Say Something about how there could be multiple point sources,
-  but all of this is below our detector resolution.
-
-This shows that the LAT can not uniquiely determinte what featuers
-we see in the data. The 2FGL catalog's method of fitting all residuals
-as new point sources is incorrect as is assuming everything is an
-extended source an not source confusion. A more nuanced, but somewhat arbitrary,
-criterion must be used on a case by case basis using multiwavelenth
-information to decide whether we believe our best fit model is 
-composed of multiple separate sources or one spatially extended source.
-
-Even so, if the LAT detects a source as being extended, it could
-likely in the future be resolved into multiple point sources.
-This is actually almost inevitable because of the large density of
-sources in the galactic plane which could all be \gev emitters.
-
-Even though this dedicated monte carlo study was performed
-using \pointlike, for the analysis of LAT data we took the best
-fit positions of the two point-like sources and refit them using \gtlike.
-We quote the spectral values obtained from \gtlike using the best fit
-positions of the two point-like sources found using \pointlike.
-
-}
-
-\section{Extended Source Search Method}
-\label{extended_source_search_method}
-
-We tested all sources in 2FGL for spatial extension.
-2FGL included
-twelve previously published spatially extended sources but not
-attempt was made to fit the extension of these sources. Other than these sources,
-all 2FGL sources were modeled as point-like and 2FGL did no attempt
-to resolve their extension.
-
-Our analysis technique is closely related to that 
-of the 2FGL catalog. We used the same two-year dataset from 2008 August 4
-to 2010 August 1 and we used the same P7\_V6 Source class
+Figure~\ref{confusion_plot}c shows the same analysis but when
+fitting simulations of two point-like sources each with half of the
+flux of the spatially extended source but the same spectral index.
+Finally, figure~\ref{confusion_plot}e shows the same analysis with each
+point-like source having the same flux but different spectral indices.
+One point-like source had a spectral index of 1.5 and the other an index
+of 2.5.
+
+The same three plots are shown in figure~\ref{confusion_plot}b,
+figure~\ref{confusion_plot}d, and figure~\ref{confusion_plot}f but this
+time when analyzing a source of flux $10^{-9} \phflux$ (integrated from
+10 \gev to 100 \gev) only in the 10 \gev to 100 \gev energy range.
+This spectrum is typical of the new extended sources discovered
+using only photons with energies between 1 \gev and 100 \gev (see
+Section~\ref{new_ext_srcs_section}).
+
+Several interesting conclusions can be made from this study. The overall
+behavior of these plots is what one would expect. \tsext is on average
+greater than \tsinc when fitting simulated extended sources whereas
+\tsinc is greater than \tsext when fitting two simulated point-like sources.
+Furthermore, the distributions of \tsext and \tsinc separate better
+when the extended source is bigger or when the two point-like sources are
+farther apart.
+
+The distributions show that for simulated
+extended sources with typical
+sizes ($\sigma\sim0\fdg5$), one can often obtain almost as good an
+increase in likelihood
+when fitting the extended source as two point-like sources
+($\tsext\sim\tsinc$).
+This is because although
+two point-like sources represent an incorrect spatial model, 
+the two point-like sources have four additional degrees
+of freedom (two spatial and two spectral parameters)
+than the one extended source (one extension parameter)
+and can therefore easy model
+statistical fluctuations.
+This effect is most pronounced when using energies from 1
+\gev to 100 \gev where the PSF is even larger.  
+On the other hand,
+when testing the two simulated point-like sources for extension our test
+did a better job at separating the distribution of \tsinc and \tsext
+and found that \tsinc was typically much larger than \tsext.
+This is because the one additional extension degree of freedom does
+now as easily fit fit statistical fluctuations.
+
+From this, we conclude that the $\tsext>\tsinc$ test is reasonably
+powerful at discarding cases in which the true emission is derived
+from two point-like sources instead of from a spatially extended
+source. On the other hand, because of the large values of \tsinc
+in figure~\ref{confusion_plot}a and figure~\ref{confusion_plot}a when
+fitting spatially extended sources, we caution that even in the case of
+their being spatially extended emission the fit of two point-like sources
+can often seem (by comparing the likelihoods) to be almost as good.
+
+Finally, figure~\ref{index_difference} shows the absolute value of the
+difference of the fit spectral indices for the case of fitting simulated
+spatially extended sources as two point-like sources. The plot compares
+the fit in the 1 \gev to 100 \gev energy range and in the 10 \gev to
+100 \gev energy range. An error on the difference in spectral index is
+calculated by adding in quadrature the statistical error on the spectral
+index.  This plot shows that there can be a large difference in the
+spectral index of the two fit point-like sources which is often greater
+than the statistical errors on the difference in spectral index. This is
+because the fit values the errors on an incorrect model are not expected
+to be meaningful. Therefore, the difference in spectral index when fitting
+an extended source candidate as two point-like sources can not be easily
+used to help determine whether a source is actually spatially extended
+instead of the emission from two confused point-like sources.
+
+From this Monte Carlo study, we can see the limits of a LAT analysis of
+spatially extended sources.  Section~\ref{monte_carlo_validation} showed
+that we have a statistical test which can rigorously find sources for
+which the spatial emission is not well described by the PSF.  But for
+the extended sources we are searching for, this extension test does
+not uniquely prove that the emission originates from spatially extended
+emission instead of from multiple unresolved sources.  Demanding that
+$\tsext>\tsinc$ is a reasonably powerful test to avoid cases of simple
+confusion with two point-like sources. But it could always be the
+case that an extended source candidate is actually the superposition
+of multiple point-like or extended sources which could be resolved
+with deeper observations of the region.  Of course, there is nothing
+about this conclusion unique to LAT analysis.  Its just that the 
+larger PSF of the LAT and the density of sources expected to be \gev emitters in
+the galactic plane makes this issue more significant for LAT analysis.
+When possible, multiwavelength information should be used to help decide
+what is qualitatively the best sky model.
+
+Even though this dedicated monte carlo study was performed using
+\pointlike, for the analysis of LAT data we took the best fit positions
+of the two point-like sources and refit them using \gtlike.  We quote
+\tsinc calculated with \gtlike using the best fit positions of the two
+point-like sources found using \pointlike.
+}
+
+\section{Test of 2LAC Sources}
+\label{test_2lac_sources}
+
+\newtext{
+For all following LAT analysis, we used the same two-year dataset
+that was used in 2FGL spanning from 2008 August 4 to 2010 August 1. We
+applied the same acceptance cuts and we used the same P7\_V6 Source class
 event selection and IRFs \citep{lat_on_orbit_psf}.  
-The same 
-models were used to describe the background from Galactic diffuse, isotropic, and
-Earth limb emission.  To account for possible residuals in the diffuse
-emission model, the galactic emission was scaled by a power-law
-and the isotropic component's normalization was left free.
-
-As was shown in Section~\ref{extension_sensitivity}, we gain little in
-sensitivity using photons with energies below 1 \gev. On the other hand,
-the large PSF at low energy makes us more susceptible to systematic
-errors arising from source confusion due to multiple point-like sources
-and modeling of the Galactic diffuse emission. In addition, the Galactic
-diffuse emission is more pronounced at lower energies due to its steep
-energy spectrum \citep{intermediate_diffuse_lat}.  For that reason,
-we performed our search using only photons with energies between 1 \gev
-and 100 \gev.
-
-We also performed a search for extended sources using only photons with energies
-between 10 \gev and 100 \gev. 
-Although this approach tests the same
-sources, it is complimentary because the Galactic diffuse
-emission is even less dominant above 10 \gev. Furthermore, source
-confusion becomes less of a problem since most LAT sources are not
-significantly detected at energies exclusively above 10 \gev. So we
-expect to be able to resolve harder sources in more complicated regions
-by restricting our analysis to higher energies. The $>10$ \gev
-analysis is
-especially
-beneficial for regions near pulsars which are not significantly detected 
-above 10 \gev. A similar procedure was
-used to detect HESS\,J1825$-$137 and MSH\,15$-$52 with the LAT
-\citep{msh1552,fermi_hess_j1825}.
-
-We tested each source for extension using
-\pointlike
-assuming the source had a uniform radially symmetric surface brightness
-and a power-law spectral model.
-We used a circular $10\degree$ region of interest (ROI) centered on our source and
-included all catalog sources within $15\degree$ of the source of interest
-in our background model.
-We refit the spectral parameters of sources within $2\degree$ of the source
-to avoid potential biases of the extension parameters of the source of
-interest due to close-by background sources.
-
-Finally, when analyzing each region, we automatically removed from
-our background model other 2FGL sources which were within 0\fdg5 of
-the source of interest. This was done due
-to a concern that extended sources could be included in 2FGL as multiple
-point-like sources. These spurious sources could distort the extension
-fit.  Instead, when a source was found to be significantly extended
-(i.e. $\tsext>16$), we performed the dual localization procedure 
-to compare the extended source
-hypothesis to the hypothesis of two independent point-like sources
-(section~\ref{dual_localization_method}). Only
-sources with $\tsext>\tsinc$ were considered as extended.
-
-\subsection{Additional Analysis}
-
-We expect most spatially resolvable extended sources to be located
-in our Galaxy and thus to be concentrated along the Galactic plane.
-Unfortunately, the \gev emission in the Galactic plane is dominated by
-extremely structured diffuse emission from the interactions of cosmic rays
-with the interstellar medium.  Finding sources on top of this emission
-is difficult as was discussed in 1FGL
-and 2FGL \citep{first_cat,second_cat}.  Furthermore, the Galactic plane
-is crowded and it is often difficult to correctly model nearby sources.
-Because of this, finding a source with $\tsext>16$ is not a sufficient
-criteria alone for claiming the detection of source extension.  For each
-extended source, we perform several analysis crosschecks.
-
-For each candidate, we generated a map of residual \ts by adding a new
-source of spectral index 2 into the region at each pixel and finding the
-increase in likelihood when fitting its flux. Figure~\ref{res_tsmaps}
-shows a residual \ts map for the extended source IC443.  The residual
-\ts map indicates that the spatially extended model for IC443 is a
-significantly better description of the observed photons
-and that there is no significant residual in region after modeling
-the source as being spatially extended.  We also
-generated maps of the sum of all counts within a given distance of
-the source and compared it to the model predictions of a point-like source.
-An example radial integral plot is shown for the extended source
-IC443 in Figure~\ref{four_plots_ic443}.  For each source, we also made
-diffuse-emission-subtracted smoothed counts maps (show for IC443 in
-Figure~\ref{four_plots_ic443}).
-
-% 2FGL J1856.2+0450c = P72Y3047 for
-We inspected each extended source candidate to identify cases in
-which the fit was influenced by large-scale residuals in
-the diffuse emission and hence the extension measurement was unreliable.
-An example of such a case is 
-2FGL\,J1856.2+0450c 
-shown in Figure~\ref{example_bad_fit}. The
-diffuse-emission-subtracted smoothed
-counts map shows that
-there appears to be large-scale
-residual in the diffuse emission
-in this region along the Galactic plane.
-As a result, 2FGL\,J1856.2+0450c is fit
-to an extension of $\sim2\degree$ and the result is statistically significant
-with \tsext=45.4. However, by looking at the residuals it is clear
-that this complicated region is not fit well.
-We did not report as extended sources that fail this inspection.
-% information came from
-% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
-
-For the remaining candidates, we took the extended source's
-spatial and spectral model found
-using \pointlike and re-determined the spectral parameters using \gtlike.
-We used the `binned likelihood' mode of \gtlike on a $14\degree\times14\degree$
-ROI with a pixel size of 0\fdg03.  We obtained a second measure of \tsext
-from \gtlike using the extension and position of the source as determined
-by \pointlike.  We only considered a source to be significantly extended
-if $\tsext>16$ with both \pointlike and \gtlike.
-
-Because of the high source density in the Galactic plane, we often had
-to iteratively improve the model of our background sources to obtain a
-better fit of the candidate source.  Several point-like 2FGL sources
-were often include in the catalog to fill in the emission of the extended
-source candidate and had to be removed from the background model of
-the region.  Similarly, background sources were often insignificant at
-higher energies and had to be removed from the sky model.  The position
-of background sources would often have to be refit once the extended
-source's extension was modeled.  When the model of the extended source
-coupled strongly with nearby sources, we iteratively fit the extended
-source and all nearby sources until the fit converged.  For each extended
-source, we describe any modifications required of the background model
-compared to 2FGL sky model.
-
-\subsection{Systematic Errors on Extension}
-\label{systematic_errors_on_extension}
-
-% Alternative PSF
-
-We estimated a systematic error on the extension of a source due to
-uncertainty in our knowledge of the LAT PSF.  Before launch, the LAT PSF
-was determined by detector simulations which were verified in accelerator
-tests \citep{atwood_LAT_mission}. However, in-flight data revealed
-a discrepancy above a few \gev in the PSF compared to the angular
-distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
-Subsequently, the PSF was fit empirically to bright AGN and this
-empirical parameterization is used in the P7\_V6 IRFs.  To account for
-our uncertainty in our knowledge of the PSF, we refit our extended source
-candidates using the pre-flight Monte Carlo representation of the PSF
-and consider the difference in extension found using the two PSFs as a
-systematic error on the extension of a source.  The same approach was used
-in \cite{ic443}.  At high energies, we believe that our parameterization
-of the PSF from bright AGN is substantially better than the Monte Carlo
-representation of the PSF so this systematic error is conservative.
-
-% Alternate Diffuse
-
-\newtext{
-We estimated a second systematic error on the extension of a source
-due to uncertainty in our model of the Galactic diffuse emission by
-using an alternative model which takes as input templates
-calculated by
-GALPROP\footnote{GALPROP is a software package for calculating the
-Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
-in the Galaxy \citep{galprop1998,galprop2011}. 
-See also \url{http://galprop.stanford.edu/} for details.} 
-but then fits each template locally in
-the surrounding region.
-The particular GALPROP model that was used as input is described in
-the LAT analysis of the isotropic diffuse
-emission \citep{isotropic_lat}.  
-}
-The intensities of various components
-of the Galactic diffuse emission were fitted individually using a
-spatial distribution of the intensities within the ROI as predicted by
-the model.  We distinguished contributions from CR interactions with the
-molecular hydrogen, the atomic+ionized hydrogen, residual gas traced
-by dust \citep{isabelle_dark_gass}, and the interstellar radiation
-field. We further split the contributions from interactions with molecular
-and atomic hydrogen to the Galactic diffuse emission according to the
-distance from the Galactic center in which they are produced. Hence, we
-replaced the standard diffuse emission model by 18 individually fitted
-templates to describe individual components of the diffuse emission.
-A similar crosscheck was used in the LAT Collaboration's analysis of 
-RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
-
-It is not expected that this diffuse model is superior to the standard
-LAT model obtained through an all-sky fit.  However, adding degrees of
-freedom to the background model can remove likely spurious sources that
-correlate with features in the Galactic diffuse emission.  Therefore,
-this tests systematics that may be due to incorrect modeling of the
-diffuse emission in the region.  We do not except the systematic error
-due to uncertainties in the PSF to be correlated to the systematic
-error due to uncertainty in the Galactic diffuse emission. Therefore,
-the total systematic error on the extension of a source was obtained by
-adding the two errors in quadrature.
+When analyzing sources in \pointlike, we used a circular $10\degree$ region of
+interest (ROI) centered on our source.  
+When refitting the region in \gtlike using the best fit spatial and
+spectral models from \pointlike, we used the `binned likelihood' mode of
+\gtlike on a $14\degree\times14\degree$ ROI with a pixel size of 0\fdg03.
+
+Unless explicitly
+mentioned, we used the same background model as 2FGL to represent the
+Galactic diffuse, isotropic, and Earth limb emission.  To account for
+possible residuals in the diffuse emission model, the galactic emission
+was scaled by a power-law and the isotropic component's normalization
+was left free.  
+Unless explicitly mentioned,
+we used all 2FGL sources within $15\degree$ of our source as our list
+of background sources and we refit the spectral parameters of sources
+within $2\degree$ of the source.
+
+}
+
+To validate our method, we tested LAT sources associated with AGN for
+extension.  \gev emission from AGN is believed to originate from the
+cores of kiloparsec-scale jets of distant galaxies.  Therefore AGN are
+not expected to be spatially resolvable by the LAT and provide a good
+calibration source to demonstrate that our extension detection method
+does not misidentify point-like sources as being extended.  We note that
+megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
+to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
+halo has been discovered in the LAT data so far.
+
+Following 2FGL, the LAT Collaboration published the Second LAT AGN
+Catalog (2LAC), a list a list of high latitude ($|b|>10\degree$) sources
+that had a high probability association with AGN \citep{second_agn_cat}.
+2LAC associated 1016 2FGL sources with AGN.  To avoid systematic problems
+with AGN classification, we selected only the 885 AGN which made it into
+the clean AGN sub-sample.  An AGN association is considered clean only
+if it has a high probability of association $P\ge 80\%$, if it is the
+only AGN associated with the catalog source, and if there are no flags
+on the source in 2FGL. These last two conditions are important for our
+analysis. Source confusion may look like a spatially extended source
+and flagged catalog sources may correlate with unmodeled structure in
+the diffuse emission.
+
+Of the 885 clean AGN, we selected the 783 of these 2FGL sources which
+were significantly-detected above 1 \gev and fit each of them for extension.
+The cumulative density of \tsext for these AGN compared to the
+$\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
+is
+shown in Figure~\ref{agn_ts_ext}. 
+The \tsext distribution for AGN shows good agreement with the
+theoretical distribution, but two sources had $\tsext>10$.  One was due
+to the incorrect removal of a nearby catalog sources from
+the sky model (see
+Section~\ref{extended_source_search_method}) and the other was due to a
+failure of convergence of the point-like source hypothesis.  This result demonstrates
+that we can use \tsext as a measure of the statistical significance of
+the detection of the extension of a source.
+
+We should clarify that the LAT PSF used in this study was determined
+empirically by fitting the observed shape of bright AGN (see
+Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
+test are not extended is not surprising.  This validation analysis is
+not suitable to reject any hypotheses about the existence of megaparsec-scale
+halos around AGN.
 
@@
 
+\newtext{
+As further validation of our extended source method for studying
+spatially extended sources, we reanalyzed the twelve spatially extended
+sources which were included in 2FGL \citep{second_cat}.  Even though
+each of these sources required a dedicated analysis and these sources
+were fit with a variety of spatial models, it is valuable to show that
+these sources are significantly extended using our systematic extension
+method and consistently assuming a radially-symmetric uniform surface
+brightness for their spatial model.  On the other hand, for some of
+these sources a uniform disk spatial model does not well describe the
+observed extended emission and so the dedicated LAT publications give
+a qualitatively better model of the source.
+
+}
+
 % 6 SNRs
 
-We first present on our analysis of the twelve extended sources
-included in 2FGL.  \citep{second_cat}.  Six extended SNRs were
-included in 2FGL: W51C, IC443, W28, W30, W44, and the Cygnus Loop
-\citep{w51c,ic443,w28,w44,cygnus_loop_lat}.\footnote{A detailed
-publication by the LAT Collaboration about W30 is in preparation.
-\gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
-}
+Six extended SNRs were
+included in 2FGL: W51C, IC443, W28, W30, W44, the Cygnus Loop,
+and W30
+\citep{w51c,ic443,w28,w44,cygnus_loop_lat,w30_lat}.
 Using photons
@@
 1 \gev and 100 \gev, our analysis significantly detected
-the extension of all six SNRs.
+the extension of all six of these SNRs.
+
 % 2 galaxies
 
-Two nearby satellite galaxies of the Milky Way the Large Magalenic Cloud (LMC)
-and the Small Magalenic
+Two nearby satellite galaxies of the Milky Way the Large Magellanic Cloud (LMC)
+and the Small Magellanic
 Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
@@
 the source's emission is significantly different from a uniform
-radially symmetric surface brightness \citep{cen_a_lat}.
+radially-symmetric surface brightness \citep{cen_a_lat}.
 
@@
 position and extension of these sources when fitting them 
-with a radially symmetric uniform surface brightness spatial model. It also
+with a radially-symmetric uniform surface brightness spatial model. It also
 includes the best fit spectral parameters for each source.  The position
@@
 
-\section{Test of 2LAC Sources}
-\label{test_2lac_sources}
-
-To validate our method, we tested LAT sources associated with AGN for
-extension.  \gev emission from AGN is believed to originate from the
-cores of kiloparsec-scale jets of distant galaxies.  Therefore AGN are
-not expected to be spatially resolvable by the LAT and provide a good
-calibration source to demonstrate that our extension detection method
-does not misidentify point-like sources as being extended.  We note that
-megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
-to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
-halo has been discovered in the LAT data so far.
-
-Following 1FGL, the LAT Collaboration published the First LAT AGN Catalog
-(1LAC), a list of sources that had a high probability association with
-AGN \citep{first_agn_cat}.  1LAC associated 709 1FGL sources with 671
-AGN at high latitude ($|b|>10\degree$).  Using two years of data
-and 2FGL, the Second LAT AGN Catalog (2LAC) associated 1016 2FGL sources
-with AGN \citep{second_agn_cat}.  To avoid systematic problems with AGN
-classification, we selected only the 885 AGN which made it into
-the clean AGN sub-sample.  An AGN association is considered clean only
-if it has a high probability of association $P\ge 80\%$, if it is the
-only AGN associated with the catalog source, and if there are no flags
-on the source in 2FGL. These last two conditions are important for our
-analysis. Source confusion may look like a spatially extended source
-and flagged catalog sources may correlate with unmodeled structure in
-the diffuse emission.
-
-Of the 885 clean AGN, we selected the 783 of these 2FGL sources which
-were significantly-detected above 1 \gev and fit each of them for extension.
-The cumulative density of \tsext for these AGN compared to the
-$\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
-is
-shown in Figure~\ref{agn_ts_ext}. 
-The \tsext distribution for AGN shows good agreement with the
-theoretical distribution, but two sources had $\tsext>10$.  One was due
-to the incorrect removal of a nearby catalog sources from
-the sky model (see
-Section~\ref{extended_source_search_method}) and the other was due to a
-failure of convergence of the point-like source hypothesis.  This result demonstrates
-that we can use \tsext as a measure of the statistical significance of
-the detection of the extension of a source.
-
-We should clarify that the LAT PSF used in this study was determined
-empirically by fitting the observed shape of bright AGN (see
-Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
-test are not extended is not surprising.  This validation analysis is
-not suitable to reject any hypotheses about the existence of megaparsec-scale
-halos around AGN.
+\section{Systematic Errors on Extension}
+\label{systematic_errors_on_extension}
+
+% Alternative PSF
+
+\newtext{
+For the LAT detected extended sources presented in this paper,
+we developed two criteria for estimating the systematic error
+on the extension of the source.
+First, we estimated a systematic error due to
+uncertainty in our knowledge of the LAT PSF.  
+}
+Before launch, the LAT PSF
+was determined by detector simulations which were verified in accelerator
+tests \citep{atwood_LAT_mission}. However, in-flight data revealed
+a discrepancy above a few \gev in the PSF compared to the angular
+distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
+Subsequently, the PSF was fit empirically to bright AGN and this
+empirical parameterization is used in the P7\_V6 IRFs.  To account for
+our uncertainty in our knowledge of the PSF, we refit our extended source
+candidates using the pre-flight Monte Carlo representation of the PSF
+and consider the difference in extension found using the two PSFs as a
+systematic error on the extension of a source.  The same approach was used
+in \cite{ic443}.  At high energies, we believe that our parameterization
+of the PSF from bright AGN is substantially better than the Monte Carlo
+representation of the PSF so this systematic error is conservative.
+
+% Alternate Diffuse
+
+\newtext{
+We estimated a second systematic error on the extension of a source
+due to uncertainty in our model of the Galactic diffuse emission by
+using an alternative model which takes as input templates
+calculated by
+GALPROP\footnote{GALPROP is a software package for calculating the
+Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
+in the Galaxy \citep{galprop1998,galprop2011}. 
+See also \url{http://galprop.stanford.edu/} for details.} 
+but then fits each template locally in
+the surrounding region.
+The particular GALPROP model that was used as input is described in
+the LAT analysis of the isotropic diffuse
+emission \citep{isotropic_lat}.  
+}
+The intensities of various components
+of the Galactic diffuse emission were fitted individually using a
+spatial distribution of the intensities within the ROI as predicted by
+the model.  We distinguished contributions from CR interactions with the
+molecular hydrogen, the atomic+ionized hydrogen, residual gas traced
+by dust \citep{isabelle_dark_gass}, and the interstellar radiation
+field. We further split the contributions from interactions with molecular
+and atomic hydrogen to the Galactic diffuse emission according to the
+distance from the Galactic center in which they are produced. Hence, we
+replaced the standard diffuse emission model by 18 individually fitted
+templates to describe individual components of the diffuse emission.
+A similar crosscheck was used in the LAT Collaboration's analysis of 
+RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
+
+\newtext{
+It is not expected that this diffuse model is superior to the standard
+LAT model obtained through an all-sky fit.  However, adding degrees of
+freedom to the background model can remove likely spurious sources that
+correlate with features in the Galactic diffuse emission.  Therefore,
+this tests systematics that may be due to imperfect modeling of the
+diffuse emission in the region. Nevertheless, this alternative diffuse
+model does not test all systematics related to the diffuse emission model.
+In particular, because the alternate model uses the same underlying gas
+maps it is unable to asses systematics due to misidentified of local
+diffuse structure due to lack lack of resolution of the underlying maps.
+}
+
+We do not expect the systematic error
+due to uncertainties in the PSF to be correlated to the systematic
+error due to uncertainty in the Galactic diffuse emission. Therefore,
+the total systematic error on the extension of a source was obtained by
+adding the two errors in quadrature.
+
+\section{Extended Source Search Method}
+\label{extended_source_search_method}
+
+\newtext{
+
+Now that we have demonstrated that we can analyze sources
+previously known to be extended at \gev energies
+(Section~\ref{validate_known})
+and that we understand the statistical issues associated with
+this analysis (Section~\ref{monte_carlo_validation} and~\ref{test_2lac_sources}),
+we applied this method to search for new spatially extended \gev sources.
+
+Ideally, we would have applied a completely blind search where we simply
+fit the extension of each catalog source in the presence of all other 2FGL
+sources to find a complete list of all the sources that are spatially
+extended.  And as our test of AGN in Section~\ref{test_2lac_sources}
+showed, at high galactic latitude where the source density is not as
+great and the diffuse emission is less structured, this method works well.
+
+This method is infeasible in the galactic plane where we
+most likely expect to discover new spatially extended sources.  In the
+galactic plane, the analysis becomes challenged by our imperfect model of
+the diffuse emission and by issues related to source confusion.  
+Finding sources on top of this emission
+is difficult as was discussed in 1FGL
+and 2FGL \citep{first_cat,second_cat} and we expect that finding
+spatially extended sources be even more difficult.
+The Monte
+Carlo study on source confusion in Section~\ref{dual_localization_method}
+showed that the overall likelihood would greatly increase when fitting
+a spatially extended source as two point-like sources. So we expect that
+most spatially extended LAT sources that are
+currently modeled as point-like in 2FGL are surrounded by other 
+point-like sources that representing
+residual induced by not correctly modeling the sources' extension.
+Furthermore, the position of other nearby sources in the region near
+an extended source could be biased by not taking the extended
+sources' extension into account.  Furthermore, 2FGL produced a
+list of sources significant at energies above 100 \mev
+whereas we are most sensitive to spatial extension at higher energies.
+Therefore, we expect that when studying spatially extended sources
+at higher energies our analysis would be complicated
+by 2FGL sources not significant at higher energies and 2FGL sources
+whose position was biased by the diffuse emission at lower energies.
+
+To account for these issues,
+we first produces a large list of
+possibly extended sources employing a very liberal search criteria
+and then refined the analysis of the promising candidates on a case by case basis.
+Our strategy was to test all point-like 2FGL sources
+for extension by assuming that they have a uniform radially-symmetric
+uniform surface brightness
+and that they have a power-law spectral model.
+Although not all extended sources are
+expected to have a shape very similar to a uniform surface brightness,
+Section~\ref{compare_source_size} showed that for many spatially
+extended sources the wide PSF of the LAT and limited statistics allows
+for this to be a reasonable approximation.
+Additionally,
+our Monte Carlo studies (Section~\ref{monte_carlo_validation}
+and~\ref{test_2lac_sources}) demonstrate that we can use this shape for a
+statistically rigorous test. Because this spatial model only
+adds one additional degree of freedom, this
+test should be very sensitive to most spatially extended sources.
+On the other hand, this spatial model could bias us against
+finding extended sources which are not well described by uniform
+emission such as certain shell-type supernova remnants.
+
+Before testing for extension,
+we automatically removed from the background model all other 2FGL
+sources within 0\fdg5 of the source.  This value is somewhat arbitrary,
+but was picked in hopes of finding extended sources with sizes on the
+order of $\sim1\degree$ or smaller. On the other hand, by removing
+these nearby background sources we expect to also incorrectly flag 
+in our preliminary list point-like sources that are 
+confused with
+nearby sources.  To screen out obvious cases of source
+confusion, we performed the dual localization procedure described in
+Section~\ref{dual_localization_method} to compare the extended source
+hypothesis to the hypothesis of two independent point-like sources.
+
+As was shown in Section~\ref{extension_sensitivity}, we gain little in
+sensitivity using photons with energies below 1 \gev. On the other hand,
+the large PSF at low energy makes us more susceptible to systematic
+errors arising from source confusion due to nearby soft point-like sources
+and by uncertainties in our modeling of the Galactic diffuse emission. 
+\newtext{
+In addition, the Galactic
+diffuse emission is more pronounced at lower energies due to its steep
+energy spectrum compared to the typical spectrum of extended sources \citep{intermediate_diffuse_lat}.}
+For that reason,
+we performed our search using only photons with energies between 1 \gev
+and 100 \gev.
+
+We also performed a second search for extended sources using only photons with
+energies between 10 \gev and 100 \gev.  Although this approach tests the
+same sources, it is complementary because the Galactic diffuse emission is
+even less dominant above 10 \gev. Furthermore, source confusion becomes
+less of a problem since most LAT sources are not significantly detected
+at energies exclusively above 10 \gev. So we expected to be able to resolve
+harder sources in more complicated regions by restricting our analysis
+to higher energies. The $>10$ \gev analysis is especially beneficial
+for regions near pulsars which are not significantly detected above
+10 \gev. A similar procedure was used to detect HESS\,J1825$-$137 and
+MSH\,15$-$52 with the LAT \citep{msh1552,fermi_hess_j1825}.
+
+When we applied this test to the 1861 point-like sources in 2FGL, our
+search found 117 extended source candidates in the 1 \gev to 100 \gev
+energy range and 11 extended source candidates in the 10 \gev to 100
+\gev energy range. Most of the extended sources flagged above 10 \gev were
+also flagged above 1 \gev.  Many of these situations represent multiple
+point-like 2FGL sources all fitting the same emission region. For example,
+the sources 2FGL\,J1630.2-4752, 2FGL\,J1632.4-4753c 2FGL\,J1634.4-4743c,
+and 2FGL\,J1636.3-4740c were all found to be spatially extended in the
+10 \gev to 100 \gev energy range even though they all fit to similar
+positions and sizes.  For these situations, we manually discarded all
+but one of the 2FGL sources.
+
+Similarly, many of these sources were confused with nearby
+point-like sources or influence by large-scale residuals in the
+diffuse emission.  To help determine which of these fits represented
+truly extended sourced and in which of these fits the extension was
+influenced by source confusion and diffuse emission, we generated a
+series of diagnostic plots.  For each candidate, we generated a map
+of residual \ts by adding a new source of spectral index 2 into the
+region at each pixel and finding the increase in likelihood when fitting
+its flux. Figure~\ref{res_tsmaps} shows a residual \ts map around the
+most significantly extended source IC443 when it is modeled both as a
+point-like sources and an extended source.  The residual \ts map indicates
+that the spatially extended model for IC443 is a significantly better
+description of the observed photons and that there is no significant
+residual in region after modeling the source as being spatially extended.
+We also generated maps of the sum of all counts within a given distance of
+the source and compared it to the model predictions assuming the emission
+originated from a point-like source.  An example radial integral plot
+is shown for the extended source IC443 in Figure~\ref{four_plots_ic443}.
+For each source, we also made diffuse-emission-subtracted smoothed counts
+maps (show for IC443 in Figure~\ref{four_plots_ic443}).
+
+It was very clear by visually inspecting many of these plots that in many
+cases our analysis was strongly influence by large-scale residual in the
+diffuse emission and hence the extension measure was unreliable.  This was
+especially true in our analysis of sources in the 1 \gev to 100 \gev
+energy range.  An example of such a case is 2FGL\,J1856.2+0450c analyzed
+in the 1 \gev to 100 \gev energy range. Figure~\ref{example_bad_fit}
+shows a diffuse-emission-subtracted smoothed counts map with the best
+fit extension of the source overlaid. There appears to be large-scale
+residual in the diffuse emission in this region along the Galactic plane.
+As a result, 2FGL\,J1856.2+0450c is fit to an extension of $\sim2\degree$
+and the result is statistically significant with \tsext=45.4. However,
+by looking at the residuals it is clear that this complicated region is
+not well modeled. We manually discard sources like this.
+% information came from
+% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
+% (2FGL J1856.2+0450c = P72Y3047 for)
+
+Because of these systematic issues, we only to selected candidates in
+regions which seemed relatively simple or in regions where there was an
+obvious spatially extended multiwavelength counterpart. Furthermore,
+by assuming extended sources had a uniform spatial emission our
+search was biased towards finding sources with this certain type of
+morphology. Therefore, our search can not be expected to be complete
+and it is likely that there are other spatially extended sources that
+this method missed.
+
+For each candidate that was not biased by neighboring point-like
+sources or by large-scale residuals in the diffuse emission model, we
+improved the model of the region by decided on a case by case basis which
+background point-like sources should be kept.  We kept sources that we
+believed represented physically distinct sources and we removed from the
+model of the sky sources that we believed were included in 2FGL to account
+for residual induced by not taking the extension of the extended source
+into account and sources include in 2FGL to represent soft point-like
+sources that were not significant at higher energies.  When deciding
+which background sources to keep and which to remove, we used as much as possible
+multiwavelenth information about possibly extended source counterparts
+to help guild our choice. For each extended source presented in 
+Section~\ref{new_ext_srcs_section}, we will describe any modification from 2FGL
+of the background model that were required.
+
+The best fit position of nearby point-like sources can be influenced by
+the spatial model of a nearby extended source and vice versa.  Similarly,
+the best fit position of nearby point-like sources in 2FGL can be biased
+by systematic errors at lower energies.
+Therefore, after selecting the list of sources, we had to iteratively
+refit the position and spectrum of nearby background sources as well as
+the position, extension, and spectrum of the analyzed spatially extended
+sources until the overall fit had globally converged.  For each extended
+source, we will describe these modifications.
+
+After obtaining the overall best fit positions and extensions of all
+of the sources in the region using \pointlike, we refit the spectral
+parameters of the region using \gtlike.  Using \gtlike, we obtained a
+second measure of \tsext.  We only consider a source to be extended when
+both \pointlike and \gtlike agree that $\tsext>16$. 
+We required also that $\tsext>16$ using the alternate diffuse
+model presented in seciton~\ref{systematic_errors_on_extension}.
+we then replaced the spatially extended source with two point-like
+sources and refit their positions and spectrum and calculate \tsinc.
+We only consider a source to be spatially extended, instead of being
+the result of confusion of two point-like sources, if $\tsext>\tsinc$.
+As was show in Section~\ref{dual_localization_method}, this test is
+fairly powerful at removing situations in which the emission actually
+originates from two distinct point-like sources instead of one spatially
+extended source.  On the other hand, it is still possible that improved
+observations could resolve additional structure or new sources that we are
+currently not sensitive to. Considering the very complicated morphologies
+of extended sources observed at other wavelengths and the high density
+of possible sources that are expected to emit at \gev energies, it is
+likely that in some of these regions further observations will resolve
+that the emission is significantly more complicated than the simple
+radially-symmetric uniform surface brightness model.
+
+}
 
@@
 
+\newtext{
 Nine extended sources not included in 2FGL were found by our
-extended source search.
-Three were found when using photons with energies between 1 \gev
-and 100 \gev and six were found when using photons with energies
-between 10 \gev and 100 \gev.  The spectral and spatial properties of
-these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
-The results of our investigation of systematic errors 
-are presented in Table~\ref{alt_diff_model_results}.  it 
-compares the fit extension with an extended source hypothesis
-to the fit assuming the emission originates from two independent
-point-like sources. For these extended extended sources,
-$\tsext>\tsinc$ suggesting that the \gev emission does not originate
-from multiple physically distinct sources.
-Table~\ref{alt_diff_model_results}
-also includes the results of the extension fit
-using variations of the PSF and the galactic diffuse model described
-in Section~\ref{systematic_errors_on_extension}.  There is good
-agreement between \tsext and the fit size using the standard analysis,
-the alternative diffuse models, and the alternative PSF.  This suggests
-that the sources are robust against features in the diffuse emission
-model and uncertainties in the angular resolution of the LAT.
+extended source search. Two of these have been previously
+studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
+Jr. \citep{rx_j1713_lat,vela_jr_lat}
+Three of these sources were
+found when using photons with energies between 1 \gev and 100 \gev and six
+were found when using photons with energies between 10 \gev and 100 \gev.
+For the sources found at energies above 10 \gev, we restrict our
+analysis of these sources to higher energies because of the issues
+of source confusion and diffuse emission modeling described in
+section~\ref{extended_source_search_method}.
+The spectral and spatial properties of these nine sources is summarized
+in Table~\ref{new_ext_srcs_table}.  The results of our investigation of
+systematic errors are presented in Table~\ref{alt_diff_model_results}.
+This section compares the fit extension with an extended source hypothesis to the
+fit assuming the emission originates from two independent point-like
+sources. For these extended extended sources, $\tsext>\tsinc$ suggesting
+that the \gev emission does not originate from multiple physically
+distinct sources.  Table~\ref{alt_diff_model_results} also includes the
+results of the extension fit using variations of the PSF and the galactic
+diffuse model described in Section~\ref{systematic_errors_on_extension}.
+There is good agreement between \tsext and the fit size using the standard
+analysis, the alternative diffuse models, and the alternative PSF.
+This suggests that the sources are robust against features in the diffuse
+emission model and uncertainties in the angular resolution of the LAT.
+}
 
@@
 
-2FGL\,J0823.0$-$4246 was found 
-to have an 
-extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
-with an extension
-significance of $\tsext=46.3$
-using 
- photons with energies between
-1 \gev and 100 \gev.  This source was fit to 
-$(l,b)=(260\fdg32,-3\fdg28)$ and
-is coincident with 1FGL\,J0823.3$-$4248.
-Figure~\ref{1FGL_J0823.3-4248} shows a
-counts map of this source
-and Figure~\ref{snr_seds} shows its spectrum.
-To get a good fit of this source, we had to remove from our background
-model the nearby sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254
-which were included in 2FGL to represent part of the
-extended emission.
-
-This extended source is spatially coincident with the
-middle-aged SNR Puppis A.  Puppis A has been studied in detail
-in radio (\cite{puppis_a_vla}, and references therein) and  X-ray
-(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein) Mosaic
-\rosat observations of Puppis A produced the highest resolution X-ray
-image of this source and contours corresponding to this image are
-overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the inferred
-size at \gev energies \citep{rosat_puppis_a}.  Puppis A's distance
-was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads
-to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
+\newtext{
+2FGL\,J0823.0$-$4246 was found by our search to be an extended source
+candidate in the 10 \gev to 100 \gev energy range and is spatially
+coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
+a counts map of this source and overlays and \rosat X-ray contours of
+this source.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
+and 2FGL\,J0821.0$-$4254 which are also coincident with the SNR but that
+do not separate into multiple point-like components.  We concluded that
+these two sources were included in 2FGL to account for residual induced
+by not taking the extension of this extended source into account and
+remvoed them from our model of the sky.
+
+With this model, 2FGL\,J0823.0$-$4246 was found to have an extension of
+$0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
+of $\tsext=46.3$ using photons with energies between 1 \gev and 100 \gev.
+This source was fit to $(l,b)=(260\fdg32,-3\fdg28)$ and is also coincident
+with 1FGL\,J0823.3$-$4248.  Figure~\ref{snr_seds} shows the spectrum of
+this source.
+
+Puppis A has been studied in detail in radio (\cite{puppis_a_vla}, and
+references therein) and  X-ray (\cite{rosat_puppis_a,suzaku_puppis_a},
+and references therein).  The fit extension of 2FGL\,J0823.0$-$4246
+match well its inferred size at \gev energies.  Puppis A's distance was
+estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
+\gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
 No molecular clouds have been observed directly adjacent to Puppis A
-\citep{co_eastern_puppis_a}, similar to the LAT detected Cyngus
-Loop SNR \citep{cygnus_loop_lat}.  The luminosity of Puppis A is also
-smaller than that of other SNRs believed to interact with molecular clouds
+\citep{co_eastern_puppis_a}, similar to the LAT detected Cyngus Loop SNR
+\citep{cygnus_loop_lat}.  The luminosity of Puppis A is also smaller
+than that of other SNRs believed to interact with molecular clouds
 \citep{w51c,ic443,w44,w28,w49b_lat}.
+}
 
@@
 
-2FGL\,J1627.0$-$2425c was found  to
+2FGL\,J1627.0$-$2425c was found by our search to
 have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
@@
 was fit to
-$(l,b)=(353\fdg08, 16\fdg78)$ and is coincident with 
+$(l,b)=(353\fdg08, 16\fdg78)$ and is also coincident with 
 1FGL\,J1628.6$-$2419c.  
@@
 
-2FGL\,J1712.4$-$3941 was found 
-to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
-with an extension significance of $\tsext=39.6$
-using 
-photons with energies between
-1 \gev and 100 \gev.  This source was
-fit to $(l,b)=(347\fdg25,-0\fdg54)$ and is coincident
-with 1FGL\,J1711.7$-$3944c.
-Figure \ref{2FGL_J1712.4-3941} shows a counts map of this source.
-This source is spatially coincident with the SNR RX\,J1713.7$-$3946
-and was recently reported by \cite{rx_j1713_lat}.  
-Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR 
+\newtext{
+2FGL\,J1712.4$-$3941 was found by our search to be spatially extended using
+photons with energies between 1 \gev and 100 \gev.  It is
+spatially coincident with the SNR RX\,J1713.7$-$3946 and was
+recently studied by the LAT collaboration in \cite{rx_j1713_lat}.
+Figure~\ref{2FGL_J1712.4-3941}a shows a smoothed counts map of the source
+and overlays H.E.S.S. \tev contours of SNR
 RX\,J1713.7$-$3946 from \cite{rx_j1713_hess}.  To analyze this source,
 we used the same background source model as the recent LAT publication.
+Figure~\ref{2FGL_J1712.4-3941}b shows the source after subtracting
+these background sources.
+With this background, RX\,J1713.7$-$3946 fit to an extension of
+$0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with an extension significance
+of $\tsext=39.6$.  This source was fit to $(l,b)=(347\fdg25,-0\fdg54)$
+and is also coincident with 1FGL\,J1711.7$-$3944c.  Figure
+\ref{2FGL_J1712.4-3941} shows a counts map of this source.
+}
 
@@
 
-2FGL\,J0851.7$-$4635 was found 
-to have an
-extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
-with an extension
-significance of $\tsext=87.2$
-using photons with energies between 10 \gev and 100 \gev.  
-This source was fit to 
-$(l,b)=(266\fdg29,-1\fdg43)$ and figure~\ref{Vela_Jr} shows a counts
-map of the source.
-2FGL\,J0851.7$-$4635 is spatially coincident with the SNR Vela Jr.
-Overlaid on Figure~\ref{Vela_Jr} are H.E.S.S. \tev contours of Vela Jr.
-\citep{vela_jr_hess}.  The \gev and \tev morphology
-match well.  A detailed papers by the LAT Collaboration on Vela Jr. is
+\newtext{
+2FGL\,J0851.7$-$4635 was found by our search to be an extended source
+candidate in the 10 \gev to 100 \gev energy range and is spatially
+coincident with the SNR Vela Jr.  Figure~\ref{Vela_Jr} shows a counts
+map of the source.  Overlaid on Figure~\ref{Vela_Jr} are H.E.S.S. \tev
+contours of Vela Jr.  \citep{vela_jr_hess} and show that three
+point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
+and 2FGL\,J0855.4$-$4625 correlate with the multiwavelenth emission of
+this SNR are were most likely included in 2FGL to account for residual
+induced by not taking the extension of this extended source into account.
+These sources were removed from our model of the sky.  In addition,
+two further away sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
+were removed from our model of the sky because they were not significant
+above 10 \gev.
+
+With this model of the sky, 2FGL\,J0851.7$-$4635 was found to have an
+extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ with an extension
+significance of $\tsext=87.2$ using photons with energies between 10
+\gev and 100 \gev.  This source was fit to $(l,b)=(266\fdg29,-1\fdg43)$.
+While fitting the extension of 2FGL\,J0851.7$-$4635, we iteartively
+relocalized the position of the nearby point-like catalog source
+2FGL\,J0854.7$-$4501 to $(l,b)=(266\fdg24,0\fdg49)$ to better fit its
+position at high energies.  The LAT size matches well the \tev morphology
+of Vela Jr.  A detailed papers by the LAT Collaboration on this SNR is
 in preparation.
-
-To get a good fit of this source, we had to remove from
-our background model 
-2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
-which were included in 2FGL to account for part of the extended emission.  In addition, we relocalized
-2FGL\,J0854.7$-$4501 to
-$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
-and we had to remove from our model 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
-because they were not significant above 10 \gev.
+}
 
@@
 
-2FGL\,J1615.0$-$5051 was found 
-to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
-with an extension significance of \tsext=16.3
-using 
-photons with energies between
-10 \gev and 100 \gev.  This source
-was fit to $(l,b)=(332\fdg38,-0\fdg14)$ and
-is coincident with 
-1FGL\,J1613.6$-$5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
-of the source.
-It is less than $1\degree$ away from 2FGL\,J1615.2$-$5138 which is
-also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
-To get a good fit of both sources, we modeled both of them as
-being spatially extended and iteratively fit the position and extension
-of each source. 
-We had to remove from our background model 2FGL\,J1614.9$-$5212 
-which was included in 2FGL to account for part of the extended emission.
-We also removed from our model 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
-significant above 10 \gev.
-
-2FGL\,J1615.2$-$5138 is spatially coincident with the extended
-and \tev contours are 
-overlaid on Figure~\ref{1FGL_J1613.6-5100c} \citep{hess_plane_survey}.
-H.E.S.S. measured an
-extension $0\fdg136\pm0\fdg008$ when fitting this source with an elliptical
-2D Gaussian surface brightness.  This corresponds to a 68\% containment
-radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the LAT
-size $\rsixeight=0\fdg27\pm0\fdg03$.
-Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1615.0$-$5051
-at \gev energies
-also connects smoothly to the spectrum of HESS\,J1616$-$508 at \tev
-energies.
-
-HESS\,J1616$-$508 is located in the region of two SNRs RCW103
-(G332.4-04) and Kes~32 (G332.4+0.1) but is not spatially coincident
-with either of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near
-three pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055.
-\citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.
-Only PSR\,J1617$-$5055 is energetically capable of powering the
-\tev emission
-and
-\cite{hess_plane_survey} speculated that 
-HESS\,J1616$-$508 could be 
-a PWN powered by this young
-pulsar.
-Because HESS\,J1616$-$508 is $9\arcmin$ away from PSR\,J1617$-$5055, this would
-require an asymmetric X-ray PWNe to power the \tev emission. 
-\chandra ACIS observations revealed an underluminous PWN of
-size $\sim1\arcmin$ around the pulsar that was not oriented
-towards the \tev emission rendering this association uncertain
-\citep{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
-counterparts were observed at X-ray and soft gamma-ray energies
-by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
+\newtext{
+2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to
+be extended source candidates in the 10 \gev to 100 \gev energy
+range. They are less than $1\degree$ away from eachother and needed
+to be analyzed simultaneously.  2FGL\,J1615.0$-$5051 is spatially
+coincident with the extended \tev source HESS\,J1616$-$508 and
+2FGL\,J1615.2$-$5138 is coincident with the extended \tev source
+HESS\,J1614$-$518.  Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
+of the source and overlays the \tev contours of HESS\,J1616$-$508 and
+HESS\,J1614$-$518 \citep{hess_plane_survey}.  The figure shows that the
+source 2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and
+correlates with the extended \tev source.  Therefore, We concluded that
+these two sources were included in 2FGL to account for residual induced by
+not taking the extension of this extended source into account and remvoed
+them from our model of the sky.  There are two further away sources
+2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c that were removed from
+our model because they were not significant at energies above 10 \gev.
+
+With this model of the sky, we iterativly fit the extensions of
+2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138.
+2FGL\,J1615.0$-$5051 was found to have an extension of
+$0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$ with an extension significance
+of \tsext=16.3.  This source was fit to $(l,b)=(332\fdg38,-0\fdg14)$ and is coincident
+with 1FGL\,J1613.6$-$5100c.
+2FGL\,J1615.2$-$5138 was found
+ to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
+with an extension significance of \tsext=48.0.  This source
+was fit to $(l,b)=(331\fdg66,-0\fdg66)$ and is also coincident
+with 1FGL\,J1614.7$-$5138c. To test for the possibility that
+2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
+of two point-like sources (one of them represtend in 2FGL by
+2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
+sources.  Because $\tsinc=37.0$ is less than \tsext, we conclue that
+this emission does not originate from two nearby point-like sources.
+
+2FGL\,J1615.0$-$5051's \tev counterpart HESS\,J1616$-$508's was fit
+with a radially-symmetric Gaussian surface brightness profile to have an
+extension $0\fdg136\pm0\fdg008$.  This \tev size corresponds to a 68\%
+containment radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the
+LAT size $\rsixeight=0\fdg27\pm0\fdg03$.  Figure~\ref{hess_seds} shows
+that the spectrum of 2FGL\,J1615.0$-$5051 at \gev energies connects to
+the spectrum of HESS\,J1616$-$508 at \tev energies.
+
+HESS\,J1616$-$508 is located in the region of two SNRs RCW103 (G332.4-04)
+and Kes~32 (G332.4+0.1) but is not spatially coincident with either
+of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near three
+pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055.
+\citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.  Only
+PSR\,J1617$-$5055 is energetically capable of powering the \tev emission
+and \cite{hess_plane_survey} speculated that HESS\,J1616$-$508 could
+be a PWN powered by this young pulsar.  Because HESS\,J1616$-$508 is
+$9\arcmin$ away from PSR\,J1617$-$5055, this would require an asymmetric
+X-ray PWNe to power the \tev emission.  \chandra ACIS observations
+revealed an underluminous PWN of size $\sim1\arcmin$ around the
+pulsar that was not oriented towards the \tev emission rendering this
+association uncertain \citep{discovery_of_pwn_for_PSR_J1617-5055}.
+No other promising counterparts were observed at X-ray and soft
+gamma-ray energies by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
 IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
 \cite{discovery_of_pwn_for_PSR_J1617-5055} discovered some additional
-diffuse
-emission towards the center of HESS\,J1616$-$508 using archival radio and
-infared observations. Deeper observations will likely be necessary to
-understand this $\gamma$-ray source.
+diffuse emission towards the center of HESS\,J1616$-$508 using archival
+radio and infared observations. Deeper observations will likely be
+necessary to understand this $\gamma$-ray source.
+}
 
@@
 
-2FGL\,J1615.2$-$5138 was found 
- to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
-with an extension significance of \tsext=48.0
-using 
-photons with energies between
-10 \gev and 100 \gev.  This source was fit to 
-$(l,b)=(331\fdg66,-0\fdg66)$ and is coincident with
-1FGL\,J1614.7$-$5138c.  Because 2FGL
-J1615.2$-$5138 is close to 2FGL\,J1615.0$-$5051, the same model described
-in Section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
-sources. Both sources can be seen in Figure~\ref{1FGL_J1613.6-5100c}.
-
-This source is spatially coincident with the extended
-\tev source HESS\,J1614$-$518 and \tev contours
-are ovlaid on
-Figure~\ref{1FGL_J1613.6-5100c}
-\citep{hess_plane_survey}. 
-H.E.S.S. measured a 2D Gaussian
-extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0\fdg15\pm0\fdg02$
-in the semi-major and semi-minor axis. This corresponds
-to a 68\% containment size of $\rsixeight=0\fdg35\pm0\fdg03$
-and $0\fdg23\pm0\fdg03$,  consistent with the LAT size
-$\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds} shows
-that the spectrum of 2FGL\,J1615.2$-$5138 at \gev energies
-connects smoothly to
-the spectrum of HESS\,J1614$-$518 at \tev energies.  Further data collected by
-H.E.S.S. in 2007 resolve a double peaked structure at \tev
-energies
-but no spectral variation across this source, suggesting
+\newtext{
+2FGL\,J1615.2$-$5138 is spatialy coincident with 
+the extended \tev source HESS\,J1614$-$518.
+H.E.S.S. measured a 2D Gaussian extension of $\sigma=0\fdg23\pm0\fdg02$
+and $\sigma=0\fdg15\pm0\fdg02$ in the semi-major and
+semi-minor axis. This corresponds to a 68\% containment size of
+$\rsixeight=0\fdg35\pm0\fdg03$ and $0\fdg23\pm0\fdg03$,  consistent with
+the LAT size $\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds}
+shows that the spectrum of 2FGL\,J1615.2$-$5138 at \gev energies connects
+to the spectrum of HESS\,J1614$-$518 at \tev energies.  Further data
+collected by H.E.S.S. in 2007 resolve a double peaked structure at
+\tev energies but no spectral variation across this source, suggesting
 that the emission is not the confusion of physically separate sources
-\citep{closer_look_hess_j1614-518}.  The source was also detected by
+\citep{closer_look_hess_j1614-518}.  This double peaked structure is
+also hinted at in the LAT counts map in Figure~\ref{1FGL_J1613.6-5100c}
+but is not very significant.  The \tev source was also detected by
 CANGAROO-III \citep{cangaroo_j1614-518}.
@@
 There are five nearby pulsars, but none are luminous enough to
-provide the energy output required to power the $\tev$ 
+provide the energy output required to power the $\gamma$-ray
 emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614$-$518
 is spatially coincident with a young open cluster Pismis 22
-\citep{hess_1614_landi_atel,closer_look_hess_j1614-518}.
-\suzaku detected two
-promising X-ray candidates. Source A is an extended source consistent
+\citep{hess_1614_landi_atel,closer_look_hess_j1614-518}.  \suzaku detected
+two promising X-ray candidates. Source A is an extended source consistent
 with the peak of HESS\,J1614$-$518 and source B coincident with Pismis 22
@@
 acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
+}
 
@@
 
-2FGL\,J1632.4$-$4753c was found 
-to
-have an extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ 
-with an extension
-significance of \tsext=64.5
-using 
-photons with energies between
-10 \gev and 100 \gev.  This source was fit to 
-$(l,b)=(336\fdg41,0\fdg22)$ and is coincident with 
-1FGL\,J1632.9$-$4802c.  Figure~\ref{1FGL_J1632.9-4802c}
-shows a counts map of this source.
-To get a good fit of this source, we had to remove from our background model
-three sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
-2FGL J1634.4$-$4743c.4-4820c which were included in 2FGL to account for
-part of the extended emission.
-We relocalized 2FGL\,J1635.4$-$4717c
-to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3$-$4740c to
-$(l,b)=(336\fdg97,-0\fdg07)$
+\newtext{
+
+2FGL\,J1632.4$-$4753c was found by our search to be an extended source
+candidate in the 10 \gev to 100 \gev energy range but is in a crowded
+region of hte sky.  It is spatially coincident with the \tev source
+HESS\,J1632$-$478.  Figure~\ref{1FGL_J1632.9-4802c}a shows a counts
+map of this source and overlays \tev contours of HESS\,J1632$-$478
+\citep{hess_plane_survey}.  The figure shows that there are three nearby
+point-like 2FGL sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
+2FGL J1634.4$-$4743c.4-4820c that correlate with the extended \tev source
+but that do not separate from 2FGL\,J1632.4$-$4753c at \gev energies.
+we concluded that these sources were included in 2FGL to account for
+residual induced by not taking the extension of this extended source
+into account and removed them from our model of the sky.
 and removed from our model four
-farther away sources 2FGL\,J1638.0$-$4703c, 
+further away sources 2FGL\,J1638.0$-$4703c, 
 2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
 were not significant above 10 \gev.
+
+Our sky model therefore included three nearby sources 2FGL J1632.4-4820c,
+2FGL J1635.4-4717c, 2FGL J1636.3-4740c and which do not correlate with
+the extended \tev emission of HESS\,J1632$-$478 and that separate from
+the extended source candidate 2FGL\,J1632.4$-$4753c at \gev energies.
+Figure~\ref{1FGL_J1632.9-4802c}b shows the same region with these
+background sources subtracted.
+
+With this model of the sky, 2FGL\,J1632.4$-$4753c was found to have an
+extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ with an extension
+significance of \tsext=64.5.  This source was fit to 
+$(l,b)=(336\fdg41,0\fdg22)$ and is
+also coincident with 1FGL\,J1632.9$-$4802c.  While fitting the extension
+of 2FGL\,J1632.4$-$4753c, we iteratively relocalized 2FGL\,J1635.4$-$4717c
+to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3$-$4740c to
+$(l,b)=(336\fdg97,-0\fdg07)$.
 
@@
 the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
-shows that the spectrum of 2FGL\,J1635.4$-$4717c at \gev energies
-connects smoothly to
+shows that the spectrum of 
+2FGL\,J1632.4$-$4753c at \gev energies connects to
 the spectrum of HESS\,J1632$-$478 at \tev energies.
@@
 and $\gamma$-rays.
+}
 
@@
 
-2FGL\,J1837.3$-$0700c was found 
-to
-have an extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an
-extension significance of $\tsext=18.8$
-using 
+\newtext{
+2FGL\,J1837.3$-$0700c was found by our search to be an extended source
+candidate in the 10 \gev to 100 \gev energy range and is spatially
+coincident with the \tev source HESS\,J1837$-$069.  This source is
+in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
+smoothed counts map of the region in and overlays the \tev contours of
+HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
+point-like 2FGL sources 2FGL\,J1836.8$-$0623c, and 2FGL\,J1839.3$-$0558c
+that clearly represent distinct sources.  On the other hand, there
+is another source 2FGL\,J1835.5$-$0649 located between the three
+sources which appears to correlate with the \tev morphology of
+HESS\,J1837$-$069. Similarly, the emission from 2FGL\,J1835.5$-$0649
+and 2FGL\,J1837.3$-$0700c does appear to separate at \gev energies.
+Therefore, we concluded that this source was included in 2FGL to account
+for residual induced by not taking the extension of this extended source
+into account and removed them from our model of the sky.  We also removed
+from our model of the sky the further away point-like catlaog soruce
+2FGL\,J1839.0-0539 because it was not significant with energies above
+10 \gev.  Figure~\ref{1FGL_J1837.5-0659c}b shows a counts map of this
+region after subtracted the modeled background sources.
+
+With our improved model, 2FGL\,J1837.3$-$0700c was found to have an
+extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an extension
+significance of $\tsext=18.8$ using
  photons with energies between
-10 \gev and 100 \gev.  This source was fit to 
-$(l,b)=(25\fdg08,0\fdg13)$ and is coincident with 
-1FGL\,J1837.5$-$0659c.  Figure~\ref{1FGL_J1837.5-0659c}
-shows a counts map of this source.
-It is in a complicated region with three nearby
-sources 2FGL\,J1834.7$-$0705c, 2FGL\,J1836.8$-$0623c, and
-2FGL\,J1839.3$-$0558c.  To get a good fit of 2FGL\,J1837.3$-$0700c, we
-relocalized 2FGL\,J1834.7$-$0705c to $(l,b)=(24\fdg77,0\fdg50)$,
-2FGL\,J1836.8$-$0623c to $(l,b)=(25\fdg57,0\fdg32)$, and
-2FGL\,J1839.3$-$0558c to $(l,b)=(26\fdg08,0\fdg23)$.  We had to remove from
-our background model 
-2FGL\,J1835.5$-$0649 which was included in 2FGL to account for
-part of the extended emission 
-and also 2FGL\,J1839.0$-$0539
-because it was not significant above 10 \gev.
-
-This source is spatially coincident with the \tev source HESS\,J1837$-$069
-and \tev contours are overlaid on 
-Figure~\ref{1FGL_J1837.5-0659c} \citep{hess_plane_survey}.  
-H.E.S.S. measured
-an extension of $\sigma=0\fdg12\pm0\fdg02$ and $0\fdg05\pm0\fdg02$
+10 \gev and 100 \gev.  This source was fit to $(l,b)=(25\fdg08,0\fdg13)$
+and is also coincident with 1FGL\,J1837.5$-$0659c.  To get a good fit
+of 2FGL\,J1837.3$-$0700c, we iteratively relocalized the three nearby
+background sources along with the extension of 2FGL\,J1837.3$-$0700c but
+their positions did not significantly change.  2FGL\,J1834.7$-$0705c
+moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
+to $(l,b)=(25\fdg57,0\fdg32)$, and 2FGL\,J1839.3$-$0558c moved to
+$(l,b)=(26\fdg08,0\fdg23)$. With this best fit sky model, we tested for
+source confusion by fitting the source instead as two point sources.
+Because $\tsinc=12.6$ is less than \tsext, we conclue that this emission
+does not originate from two nearby point-like sources.
+
+H.E.S.S. measured an extension of
+$\sigma=0\fdg12\pm0\fdg02$ and $0\fdg05\pm0\fdg02$ 
+of the coincident \tev source HESS\,J1837$-$069 
 along the semi-major and semi-minor axis when fitting this source
@@
 $0\fdg08\pm0\fdg03$ along the semi-major and semi-minor axis. The
-size is not significantly different from the LAT 68\% containment radius of
-$\rsixeight=0\fdg29\pm0\fdg07$ (less than $2\sigma$).  
-Figure~\ref{hess_seds} shows that the spectrum
-of 2FGL\,J1837.3$-$0700c at \gev energies
-connects smoothly to the spectrum of HESS\,J1837$-$069
-at \tev energies.
-
-HESS\,J1837$-$069 is coincident
-with the hard and steady X-ray source AX\,J1838.0$-$0655
-\citep{einstein_galactic_plane_survey,hard_x-ray_asca,integral_AX_J1838.0-0655,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
-This source was discovered by RXTE to be a pulsar sufficiently
-luminous to power the \tev emission.  AX\,J1838.0$-$0655 was spatially
-resolved by \chandra to be a bright point-like source surrounded by
-a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069}. The
-$\gamma$-ray emission may be powered by this pulsar.  A second X-ray
-point-like source AX\,J1837.3$-$0652 is near HESS\,J1837$-$069
-\citep{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}.
-It was also resolved into point-like and diffuse component
-although no pulsations have been detected from it
-\citep{pulsations_HESS_J1837-069}. Some of the $\gamma$-ray emission
-could also come from AX\,J1837.3$-$0652.
+size is not significantly different from the LAT 68\% containment
+radius of $\rsixeight=0\fdg29\pm0\fdg07$ (less than $2\sigma$).
+Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1837.3$-$0700c
+at \gev energies connects to the spectrum of HESS\,J1837$-$069 at \tev
+energies.
+
+HESS\,J1837$-$069 is coincident with the hard and steady X-ray source
+AX\,J1838.0$-$0655 \citep{hard_x-ray_asca}.  This source was discovered
+by RXTE to be a pulsar sufficiently luminous to power the \tev emission
+and was resolved by \chandra to be a bright point-like source surrounded
+by a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069}. The
+$\gamma$-ray emission may be powered by this pulsar.  
+2FGL\,J1837.3$-$0700c's hard spectral index and spatial extension
+disfavor a pulsar origin of the LAT emission and suggest instead
+that the \gev and \tev emission both originate from the pulsar's wind.
+There is another
+X-ray point-like source AX\,J1837.3$-$0652 near HESS\,J1837$-$069
+\citep{hard_x-ray_asca} that was also resolved into a point-like
+and diffuse component \citep{pulsations_HESS_J1837-069}.  Although no
+pulsations have been detected from it, it could also be a pulsar powering
+some of the $\gamma$-ray emission.
+}
 
@@
 
-2FGL\,J2021.5+4026 was found to have an extension of
+\newtext{
+The source 2FGL\,J2021.5+4026 is coincident
+with 2CG\,078+01, 3EG\,J2020+4017, and 1FGL\,J2020.0+4049
+\citep{second_cos_b_catalog,third_egret_catalog,first_cat} and also with
+the $\gamma$-Cygni SNR. This $\gamma$-ray source has been speculated
+to originate from the interaction of accelerated particles in the SNR
+with dense molecular clouds \citep{pollock_1985,gaisser_1998},
+but this association was disfavored when the LAT \gev emission
+from this source was detected to be pulsed (PSR\,J2021+4026,
+\cite{first_lat_pulsar_cat}).  This pulsar was also been observed by
+AGILE \citep{gamma_cygni_agile}.
+
+Looking at the same region at energies above 10 \gev, the pulsar
+is no longer significant but we instead 
+found in our search an extended source candidate.
+Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source and
+overlays radio contours of $\gamma$-Cygni from the Canadian Galactic
+Plane Survey \citep{canadian_galactic_plane_survey}.  There is good
+spatial overlap between the SNR and the \gev emission.
+
+There is
+a nearby source 2FGL\,J2019.1+4040 which correlates with the radio
+emission of $\gamma$-Cygni and does not appear to represent a physically
+distinct source.  We concluded that it was included in 2FGL to account for
+residual induced by not taking the extension of $\gamma$-Cygni into
+account and removed it from our model of the sky.  We also removed from
+our model of the sky the four further away sources 2FGL\,J2022.8+3843c,
+2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c, and 2FGL\,J2012.4+3955c because
+they were not significant when observed at energies above 10 \gev.
+Furthermore, we chose to add to our region an additional point-like
+source $(l,b)=(78\fdg85,2\fdg67)$.  Although this source is not very
+significant ($\ts=13.5$ in the 1 \gev to 100 \gev energy range), its
+location is outside the multiwavelenth contours of $\gamma$-Cygni and
+modeling it improved the connection of the best fit extension
+with the multiwavelenth size of $\gamma$-Cygni. Nevertheless,
+the overall spatial and spectral characteristics of the source were not
+significantly changed after including the source.
+
+Using this sky model, 2FGL\,J2021.5+4026 fit an extension of
 $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=116.4$ using 
- photons with energies between
-10 \gev and 100 \gev.  This source
-was fit to $(l,b)=(78\fdg18,2\fdg19)$ and is
-coincident with 1FGL\,J2020.0+4049. 
-Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source
-and Figure~\ref{snr_seds} shows its spectrum.  
-To get a good fit of this source, we had to remove from our background
-model 2FGL\,J2019.1+4040 which was included in 2FGL to account for
-part of the extended emission.
-Further, it was necessary to add to our region an additional point-like source 
-at
-$(l,b)=(78\fdg85,2\fdg67)$.
-Although this source is not very significant
-($\ts=13.5$), not including it in the
-background model significantly biased the fit extension.
-In addition, we had to remove from our model the four 
-sources 2FGL\,J2022.8+3843c, 2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c,
-and 2FGL\,J2012.4+3955c because they were not significant
-above 10 \gev.
-
-This extended sources is coincident with 2CG\,078+01 and
-3EG\,J2020+4017 \citep{second_cos_b_catalog,third_egret_catalog}
-and also with the $\gamma$-Cygni SNR. This $\gamma$-ray source has
-been speculated to originate from the interaction of accelerated
-particles in the SNR interacting with dense molecular clouds
-\citep{pollock_1985,gaisser_1998},  but this association was disfavored
-when the LAT \gev emission from this source was detected to be pulsed
-(PSR\,J2021+4026, \cite{first_lat_pulsar_cat}). 
-\newtext{
-This
-pulsar was also observed by AGILE \citep{gamma_cygni_agile}.
-}
-
+of $\tsext=116.4$.  This source was fit to $(l,b)=(78\fdg18,2\fdg19)$.
+Figure~\ref{snr_seds} shows its spectrum.  The inferred size of this
+source at \gev energies well matches the radio size of $\gamma$-Cygni,
+as can be seen in Figure~\ref{1FGL_J2020.0+4049}.
 Milagro detected a $4.2\sigma$ excess at energies $\sim 30$ \tev
@@
 shock-cloud interaction in $\gamma$-Cygni \citep{veritas_gamma_cygni}.
-Using just photons with energies between 10 \gev to 100 \gev 
-where
-PSR\,J2021+4026 is not significant, we resolved an extended source whose inferred size at
-\gev energies well matches the radio size of $\gamma$-Cygni. This can
-be seen clearly in Figure~\ref{1FGL_J2020.0+4049} which overlays radio
-contours of $\gamma$-Cygni from the Canadian Galactic Plane Survey
-\citep{canadian_galactic_plane_survey}.
 
@@
 %      unidentified source 3EG J2020+4027, thought to be associated
-%      with SNR 78.2+2.1, a.k.a. the $\gamm$-Cygni SNR.
+%      with SNR 78.2+2.1, a.k.a. the $\gamma$-Cygni SNR.
 %      Unfortunately, so far this pulsar lacks a radio counterpart, and
@@
 %   extended: VER J019+407
-%     Veritas observations of $\gamm$-Cygni veritas_gamma_cygni,
+%     Veritas observations of $\gamma$-Cygni veritas_gamma_cygni,
+
+}
 
@@
 
-Twelve extended sources were included in 2FGL.  Using two years of
+\newtext{
+Twelve extended sources were included in 2FGL and two additonal
+extended sources were studied in dedicated publications.  Using two years of
 LAT data and a new analysis method, we presented the detection of
-nine additional extended sources. We also reanalyze the spatial
-shape of the twelve extended sources in 2FGL.  The 21 extended
-LAT sources are primarily along the Galactic plane 
+seven additional extended sources. 
+}
+We also reanalyze the spatial
+shape of the twelve extended sources in 2FGL and the two additional
+sources.  The 21 extended
+LAT sources are located primarily along the Galactic plane 
 and their locations are shown in
@@
 Figure~\ref{gev_vs_tev_plot} shows that there is a good correlation
-between the size of the sources at \gev and \tev energies. Even
-so, the size of PWNe are expected to vary across the \gev and \tev
-energy range and the size of HESS\,J1825$-$137 is significantly larger at
-\gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting to
-compare the size of other PWN candidates at \gev and \tev energies, 
-but definitively
-measuring this would require a more in-depth analysis of the LAT data
-using the same elliptical surface brightness model.
+between the size of the sources at \gev and \tev energies. Even so,
+the size of PWNe are expected to vary across the \gev and \tev energy
+range and the size of HESS\,J1825$-$137 is significantly larger at
+\gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting
+to compare the size of other PWN candidates at \gev and \tev energies,
+but definitively measuring this would require a more in-depth analysis
+of the LAT data using the same elliptical surface brightness model.
 
@@
 a goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
-the LAT's low background at high energies allows its sensitivity 
+the low background of the LAT at high energies allows its sensitivity 
 to
@@
 
-Figure~\ref{compare_index_2FGL} compares the spectral index
-of LAT detected extended sources and of all sources in 2FGL. This,
-and Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
-show that the LAT observes a population of hard extended sources at
-energies above 10 \gev.  Figure~\ref{hess_seds} shows that the
-spectra of four of these sources (2FGL\,J1615.0$-$5051, 2FGL\,J1615.2$-$5138,
-2FGL\,J1632.4$-$4753c, and 2FGL\,J1837.3$-$0700c)  
-at \gev energies
-connects smoothly to the spectra of their H.E.S.S. counterparts at \tev
-energies. This is also true of Vela
-Jr., HESS\,J1825$-$137 \citep{fermi_hess_j1825}, and RX\,J1713.7$-$3946
-\citep{rx_j1713_lat}.  It is likely that the \gev and \tev emission
-from these sources originates from the same population of high-energy
-particles.
+Figure~\ref{compare_index_2FGL} compares the spectral index of LAT
+detected extended sources and of all sources in 2FGL. This, and
+Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
+show that the LAT observes a population of hard extended sources
+at energies above 10 \gev.  Figure~\ref{hess_seds} shows that
+the spectra of four of these sources (2FGL\,J1615.0$-$5051,
+2FGL\,J1615.2$-$5138, 2FGL\,J1632.4$-$4753c, and 2FGL\,J1837.3$-$0700c)
+at \gev energies connects to the spectra of their H.E.S.S. counterparts
+at \tev energies. This is also true of Vela Jr., HESS\,J1825$-$137
+\citep{fermi_hess_j1825}, and RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
+It is likely that the \gev and \tev emission from these sources originates
+from the same population of high-energy particles.
 
@@
     \fi
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v2/run.py
     \caption{
@@
     of the diffuse emission compared to the smoothed
-    LAT PSF (inset).  Plots (a),
+    LAT PSF (inset). Both were smoothed by a 0\fdg1 2D Gaussian kernel.
+    Plots (a),
     (c), and (d) use only 
@@
     \caption{
-    The detection threshold to resolve a
-    uniform surface brightness extended source for a two-year exposure.  All sources
-    have an assumed power-law spectrum and the different colors correspond
-    to different simulated spectral indices.  The solid line is the
-    detection threshold using photons with energies between 100 \mev and 100
-    \gev while the dashed line is the threshold using 
-     photons with energies between 1 \gev and 100 \gev.
+    \newtext{
+    The detection threshold to resolve a uniform surface brightness
+    extended source for a two-year exposure.  All sources have an
+    assumed power-law spectrum and the different line styles (colors in
+    the electronic version) correspond to different simulated spectral
+    indices.  The lines with no markers correspond to the detection
+    threshold using photons with energies between 100 \mev and 100 \gev
+    while the lines with star-shaped markers correspond to the threshold
+    using photons with energies between 1 \gev and 100 \gev.
+    }
     }\label{index_sensitivity}
@@
     \caption{
-    The LAT's projected detection threshold to extension after a ten-year exposure
+    The projected detection threshold of the LAT to extension after a ten-year exposure
     for a power-law
@@
     version) and 10 \gev to 100 \gev
-    (dashed line colored blue). The solid gray regions represent the
+    (dashed line colored blue). The shaded gray regions represent the
     detection threshold assuming the sensitivity improves from 2 to 10
@@
     % this plot came from 
-    \caption{Testing Confusion.
+    \caption{
+    \newtext{
+    The distribution of \tsext and \tsinc 
+    (a) and (b) when fitting simulated spatially extended sources
+    with radially-symmetric uniform intensity surface profiles and varying the
+    source's size and (c), (d), (e), and (f) when fitting
+    two simulated point-like sources and varying their separation distance.
+    (c), and (d) represent simulations of two point-like sources with the
+    same spectral index and (e), and (f) represent simulations of two
+    point-like sources with different spectral indices.  (a), (c), and (e)
+    fit the simulated sources in the 1 \gev to 100 \gev energy range and
+    (b), (d), and (f) when fitting the simulated sources in the
+    10 \gev to 100 \gev energy range.
+    }
     }\label{confusion_plot}
@@
     % this plot came from 
-    \caption{Index difference.
+    \caption{
+    \newtext{
+    The absolute value of the difference of the fit
+    spectral index when fitting the simulated extended sources from
+    figure~\ref{confusion_plot} as two point-like sources for the first 100
+    simulated extended sources.  The errors on the difference in spectral
+    index were obtained by adding in quadrature the error on each spectral
+    index.  (a) represents the difference in index when analyzing the
+    simulated extended sources in figure~\ref{confusion_plot}a in the 1
+    \gev to 100 \gev energy range whereas (b) represents the difference
+    for the sources in figure~\ref{confusion_plot}a in the 10 \gev to
+    100 \gev energy range.
+    }
     }\label{index_difference}
   \end{figure}
-
-\begin{figure}
-  \ifcolorfigure
-    \plotone{ic443_plots/res_tsmap_ic443_color.eps}
-    \else
-    \plotone{ic443_plots/res_tsmap_ic443_bw.eps}
-    \fi
-  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1
-
-  \caption{
-  A test statistic map generated for the region around the SNR 
-  IC443 using 
-  photons with energies between
-  1 \gev and 100 \gev.  (a) test statistic map after
-  subtracting IC443 modeled as a point-like source. (b) same as (a), but
-  IC443 modeled as extended source. Crosses represent sources included
-  in the model of the region.}
-  \label{res_tsmaps}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{source_plots/example_bad_fit_color.eps}
-    \else
-    \plotone{source_plots/example_bad_fit_bw.eps}
-    \fi
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
-    \caption{
-    A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of the
-    region around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian
-    kernel. The plus-shaped marker and circle (colored red in
-    the online version) represent the center and size of the best fit
-    radially symmetric source with a uniform intensity profile.  The black
-    crosses represent the position of other 2FGL sources.  The extension
-    is statistically significant, but the extension encompasses many 2FGL
-    sources and the emission does not look to be uniform. This source
-    is probably fitting large-scale diffuse residual features. Although
-    the fit is statistically significant, it likely corresponds to
-    residual features of inaccurately modeled diffuse emission picked
-    up by the fit.  We manually discard candidates that appear like this.
-    }
-    \label{example_bad_fit}
-\end{figure}
-
-\begin{deluxetable}{lrrrrrrrr}
-\tablecolumns{9}
-\rotate
-\tabletypesize{\footnotesize}
-\tablewidth{0pt}
-\tablecaption{Analysis of the twelve extended sources included in 2FGL
-\label{known_extended_sources}
-}
-\tablehead{
-\colhead{Name}&
-\colhead{\glon}&
-\colhead{\glat}&
-\colhead{$\sigma$}&
-\colhead{\ts}&
-\colhead{\tsext}&
-\colhead{Pos Err}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{Index}\\
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{(\phflux)}&
-\colhead{}
-}
-
-\startdata
-\multicolumn{9}{c}{E$>$1 \gev} \\
-\hline
-SMC                  &     302.68 &     -44.81 & $  1.75 \pm   0.07 \pm   0.02 $ &       94.8 &       67.4 &   0.12 & $    3.3 \pm     0.4$ & $   2.41 \pm    0.17$  \\
-LMC                  &     279.10 &     -32.61 & $  1.74 \pm   0.05 \pm   0.13 $ &     1101.3 &      860.5 &   0.05 & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$  \\
-IC443                &     189.05 &       3.04 & $  0.36 \pm   0.01 \pm   0.04 $ &    10719.8 &      510.4 &   0.01 & $   64.8 \pm     1.2$ & $   2.23 \pm    0.02$  \\
-Vela X               &     263.34 &      -3.11 & $                         0.88$ &            &            &        &                       &                        \\
-Centarus A           &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
-W28                  &       6.50 &      -0.27 & $  0.43 \pm   0.02 \pm   0.03 $ &     1324.8 &      177.4 &   0.01 & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$  \\
-W30                  &       8.61 &      -0.20 & $  0.36 \pm   0.02 \pm   0.02 $ &      465.4 &       73.3 &   0.02 & $   30.7 \pm     1.6$ & $   2.59 \pm    0.04$  \\
-W44                  &      34.69 &      -0.38 & $  0.36 \pm   0.01 \pm   0.02 $ &     1903.3 &      217.7 &   0.01 & $   73.6 \pm     1.8$ & $   2.68 \pm    0.02$  \\
-W51C                 &      49.13 &      -0.45 & $  0.28 \pm   0.02 \pm   0.05 $ &     1819.5 &      115.7 &   0.01 & $   39.3 \pm     1.3$ & $   2.35 \pm    0.03$  \\
-Cygnus Loop          &      74.22 &      -8.46 & $  1.72 \pm   0.05 \pm   0.07 $ &      356.5 &      356.5 &   0.06 & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$  \\
-\cutinhead{E$>$10 \gev}
-MSH\,15$-$52         &     320.38 &      -1.22 & $  0.20 \pm   0.04 \pm   0.03 $ &       76.2 &        6.5 &   0.03 & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
-HESS\,J1825$-$137    &      17.56 &      -0.46 & $  0.65 \pm   0.03 \pm   0.01 $ &       83.6 &       55.9 &   0.05 & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
-\enddata
-
-\tablenotetext{(a)}{
-Integrated in the fit energy range (either 1 \gev 100 \gev or 10 \gev 100 \gev).
-}
-
-\tablecomments{
-All sources were fit using a spatial model assuming a uniform radially
-symmetric intensity distribution. \glon and \glat are Galactic longitude
-and latitude of the best fit extended source respectively.  The first
-error on $\sigma$ is statistical and the second is systematic (see
-Section~\ref{systematic_errors_on_extension}).  Pos Err is the error on
-the position of the source.  Vela X and the Centarus A Lobes were
-not fit in our analysis but are include for completeness.
-}
-\end{deluxetable}
 
@@
 
+\begin{figure}
+  \ifcolorfigure
+    \plotone{ic443_plots/res_tsmap_ic443_color.eps}
+    \else
+    \plotone{ic443_plots/res_tsmap_ic443_bw.eps}
+    \fi
+  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v2
+
+  \caption{
+  \newtext{
+  A test statistic map generated for the region around the SNR 
+  IC443 using 
+  photons with energies between
+  1 \gev and 100 \gev.  (a) test statistic map after
+  subtracting IC443 modeled as a point-like source. (b) same as (a), but
+  IC443 modeled as an extended source. The cross represents the best
+  fit position of IC443.}
+  }
+  \label{res_tsmaps}
+\end{figure}
+
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{source_plots/example_bad_fit_color.eps}
+    \else
+    \plotone{source_plots/example_bad_fit_bw.eps}
+    \fi
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
+    \caption{
+    A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of the
+    region around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian
+    kernel. The plus-shaped marker and circle (colored red in
+    the online version) represent the center and size of the best fit
+    radially-symmetric source with a uniform intensity profile.  The black
+    crosses represent the position of other 2FGL sources.  The extension
+    is statistically significant, but the extension encompasses many 2FGL
+    sources and the emission does not look to be uniform. Although
+    the fit is statistically significant, it likely corresponds to
+    residual features of inaccurately modeled diffuse emission picked
+    up by the fit. 
+    }
+    \label{example_bad_fit}
+\end{figure}
+
+\begin{deluxetable}{lrrrrrrrr}
+\tablecolumns{9}
+\rotate
+\tabletypesize{\footnotesize}
+\tablewidth{0pt}
+\tablecaption{Analysis of the twelve extended sources included in 2FGL
+\label{known_extended_sources}
+}
+\tablehead{
+\colhead{Name}&
+\colhead{\glon}&
+\colhead{\glat}&
+\colhead{$\sigma$}&
+\colhead{\ts}&
+\colhead{\tsext}&
+\colhead{Pos Err}&
+\colhead{Flux\tablenotemark{(a)}}&
+\colhead{Index}\\
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{}&
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{}&
+\colhead{}
+}
+
+\startdata
+\multicolumn{9}{c}{E$>$1 \gev} \\
+\hline
+SMC                  &     302.68 &     -44.81 & $  1.75 \pm   0.07 \pm   0.02 $ &       94.8 &       67.4 &   0.12 & $    3.3 \pm     0.4$ & $   2.41 \pm    0.17$  \\
+LMC                  &     279.10 &     -32.61 & $  1.74 \pm   0.05 \pm   0.13 $ &     1101.3 &      860.5 &   0.05 & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$  \\
+IC443                &     189.05 &       3.04 & $  0.36 \pm   0.01 \pm   0.04 $ &    10719.8 &      510.4 &   0.01 & $   64.8 \pm     1.2$ & $   2.23 \pm    0.02$  \\
+Vela X               &     263.34 &      -3.11 & $                         0.88$ &            &            &        &                       &                        \\
+Centarus A           &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
+W28                  &       6.50 &      -0.27 & $  0.43 \pm   0.02 \pm   0.03 $ &     1324.8 &      177.4 &   0.01 & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$  \\
+W30                  &       8.61 &      -0.20 & $  0.36 \pm   0.02 \pm   0.02 $ &      465.4 &       73.3 &   0.02 & $   30.7 \pm     1.6$ & $   2.59 \pm    0.04$  \\
+W44                  &      34.69 &      -0.38 & $  0.36 \pm   0.01 \pm   0.02 $ &     1903.3 &      217.7 &   0.01 & $   73.6 \pm     1.8$ & $   2.68 \pm    0.02$  \\
+W51C                 &      49.13 &      -0.45 & $  0.28 \pm   0.02 \pm   0.05 $ &     1819.5 &      115.7 &   0.01 & $   39.3 \pm     1.3$ & $   2.35 \pm    0.03$  \\
+Cygnus Loop          &      74.22 &      -8.46 & $  1.72 \pm   0.05 \pm   0.07 $ &      356.5 &      356.5 &   0.06 & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$  \\
+\cutinhead{E$>$10 \gev}
+MSH\,15$-$52         &     320.38 &      -1.22 & $  0.20 \pm   0.04 \pm   0.03 $ &       76.2 &        6.5 &   0.03 & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
+HESS\,J1825$-$137    &      17.56 &      -0.46 & $  0.65 \pm   0.03 \pm   0.01 $ &       83.6 &       55.9 &   0.05 & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
+\enddata
+
+\tablenotetext{(a)}{
+Integral Flux is in units of $10^{-9}\phflux$ and integrated in the fit
+energy range (either 1 \gev 100 \gev or 10 \gev 100 \gev).
+}
+
+\tablecomments{
+All sources were fit using a spatial model assuming a uniform radially
+symmetric intensity distribution. \glon and \glat are Galactic longitude
+and latitude of the best fit extended source respectively.  The first
+error on $\sigma$ is statistical and the second is systematic (see
+Section~\ref{systematic_errors_on_extension}).  Pos Err is the error on
+the position of the source.  Vela X and the Centarus A Lobes were
+not fit in our analysis but are include for completeness.
+}
+\end{deluxetable}
+
   % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
@@
 \tablewidth{0pt}
-\tablecaption{Extension fit for the nine new extended sources
+\tablecaption{Extension fit for the nine additional extended sources
 \label{new_ext_srcs_table}
@@
 \colhead{(deg.)}&
-\colhead{(\phflux)}&
+\colhead{}&
 \colhead{}&
@@
 \tablenotetext{(a)}{
-Integrated in the fit energy range (either 1 \gev to 100 \gev or 10 \gev 100 \gev).  }
+Integral Flux is in units of $10^{-9}\phflux$ and integrated in the fit
+energy range (either 1 \gev 100 \gev or 10 \gev 100 \gev).
+}
 
@@
     Table~\ref{known_extended_sources}.
+    \newtext{
+    RX\,J1713.7$-$3946 and Vela Jr. were previously studied in dedicated publications \citep{rx_j1713_lat,vela_jr_lat}.
+    }
 }
@@
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v7/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v8/run.py
   \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
@@
   the best fit position and extension of this source assuming a
-  radially symmetric uniform surface brightness.  The two 
+  radially-symmetric uniform surface brightness.  The two 
   star-shaped markers (colored
@@
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v7/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v8/run.py
   \caption{
@@
   represent the best fit position and extension of this
-  source assuming a radially symmetric uniform surface brightness. The
+  source assuming a radially-symmetric uniform surface brightness. The
   contours in (a) correspond to the 100 micrometer image observed by
@@
     % this plot came from
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v8/run.py
   \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
@@
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v7/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v8/run.py
   \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
@@
   and the circle (colored red) are the best fit position and extension of
-  this source assuming a radially symmetric uniform surface brightness.
+  this source assuming a radially-symmetric uniform surface brightness.
   The five star-shaped markers (colored green) represent 2FGL sources
@@
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v7/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v8/run.py
   \caption{
@@
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v7/run.py
-  \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  2FGL\,J1632.4$-$4753c smoothed by a 0\fdg1 2D Gaussian
-  kernel.  The triangular marker (colored red in the electronic version)
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v8/run.py
+  \caption{
+  \newtext{
+  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
+  2FGL\,J1632.4$-$4753c (a) smoothed by a 0\fdg1 2D Gaussian
+  kernel and (b) with the emission from the background sources subtracted.  
+  }
+  The triangular marker (colored red in the electronic version)
   represents the 2FGL position of this source.  The plus-shaped marker
   and the circle (colored red) are the best fit position and extension of
-  2FGL\,J1632.4$-$4753c assuming a radially symmetric uniform surface
+  2FGL\,J1632.4$-$4753c assuming a radially-symmetric uniform surface
   brightness.  The four star-shaped markers (colored green) represent 2FGL
@@
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v7/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v8/run.py
   \caption{
+  \newtext{
   A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of the
-  region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg1 2D Gaussian
+  region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg15 2D Gaussian
   kernel and (b) with the emission from the background sources subtracted.
+  }
   The triangular marker (colored red in the online version) represents
@@
   the best fit position and extension of 2FGL\,J1837.3$-$0700c assuming a
-  radially symmetric uniform surface brightness. The circular
+  radially-symmetric uniform surface brightness. The circular
   and square markers 
@@
   % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v7/run.py
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v8/run.py
   \caption{A Diffuse-emission-subtracted 
@@
   marker and the circle (colored red) represent the best fit position
-  and extension of 2FGL\,J2021.5+4026 assuming a radially symmetric
+  and extension of 2FGL\,J2021.5+4026 assuming a radially-symmetric
   uniform surface brightness.  The star-shaped markers (colored green)

### 2011-09-22 extended_catalog/paper/extended_catalog.tex
improving draft

@@
 
-% Changes from v2.0 to v3.0
-
-% * Move section 'Dual Localization' to its own
-%   section after 'Extended Source Detection Threshold'
-%   and rename it 'Testing Against Source Confusion'.
-%   The section is significantly expanded with a new
-%   monte carlo study fitting extended sources as
-%   two point-like sources, and vice versa
-%
-% * Major rewrite of ``Extended Source Search Method'' section.
-%   This section now more correctly explains how the
-%   analysis search was done as well as cautions the
-%   reader about what caveats may apply to the analysis.
-
-% * Major rewrite of the sections on the new extended sources
-%   to better describe why various point sources were removed
-%   and why some were kept using multiwavelenth information.
-
-% * Move AGN validation section earlier in the text
-%   so that it is the first section analyzing actual LAT 
-% * Move section on reanalyzing 2FGL sources
-%   to earlier in the paper to be right after the AGN
-%   validation.
-% * Move earlier section discussing systematic errors
-% * better description of how two of the 'new extended sources'
-%   already have dedicated publications
-
-% * Remake 2FGL J1632.4-4753c smoothed counts map plot to show
-%   before + after background subtraction
-%
-% * Reordered Gamma-Cygni section to first discuss the pulsar.
-%
-% * For HESS J1837, smooth image by a 0.15 degree Gaussain
-%   instead of a 0.1 degree gausian
-%   kernel to surpress some of the noise which is likely spurious.
-%   Also, add in some lower level contour from HESS data
-%   to better show how wide the HESS emission is.
-%
-% * Rewrote the 'preview of what's to come section
-%   in the introduction to have the right order.
-%
-% * Cleaned up the Comparing source size section.
-% * Better description of converting TSext into sigma.
-% * better warning about the limits of the alternate diffuse model.
-% * Fixed figure order.
-% * made tickmarks white in plots.
-% * replace all occurrences of ts_inc with ts_2pts
-% * changed zoom of IC443 res tsmap to be easier to view.
-% * Added LAT collaboration citation of W30.
-%
-% * Added acknowlegements section to end of the paper
-% * Move HESS SEDs to earlier in paper to fix order.
-% * Fix some occurances of chi^2 to correctly be chi^2_1
-% * Better description of how the alternate diffuse model
-%   is different from galprop
-% * Add galprop citation
-% * Add AGILE citation Gamma Cygni Pulsar citation.
-
 \bibliographystyle{apj}
@@
 \newif\ifcolorfigure
-\colorfiguretrue
-%\colorfigurefalse
+%\colorfiguretrue
+\colorfigurefalse
 
@@
 \author{
-J.~Lande\altaffilmark{2},
-S.~Funk\altaffilmark{2},
-M.~Ackermann (???),
+J.~Lande\altaffilmark{2,1}, 
+S.~Funk\altaffilmark{2,1}, 
+M.~Ackermann\altaffilmark{3,1}, 
 %A.~Allafort\altaffilmark{2},
@@
 \ldots
+\altaffiltext{1}{Corresponding authors: M.~Ackermann, markus.ackermann@desy.de; S.~Funk, funk@slac.stanford.edu; J.~Lande, joshualande@gmail.com.}
 \altaffiltext{2}{W.
@@
 Hansen Experimental Physics Laboratory, Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics and SLAC National Accelerator Laboratory, Stanford University, Stanford, CA 94305, USA}
-\altaffiltext{53}{Institut f\"ur Astronomie und Astrophysik, Universit\"at T\"ubingen, D 72076 T\"ubingen, Germany}
+\altaffiltext{3}{Deutsches Elektronen Synchrotron DESY, D-15738 Zeuthen, Germany}
 }
@@
 and for obtaining an unbiased model of their spectra.  We present a new
-method for quantifying the spatial extension of sources with the Large
+method for quantifying the spatial extension of sources detected by the Large
 Area Telescope (LAT), the primary science instrument on the {\em \fermi
@@
 detection of seven spatially extended sources in addition to the twelve
-spatially extended sources reported in 2FGL and two other sources studied
+spatially extended sources reported in 2FGL and two others studied
 in dedicated publications.
@@
 \newtext{
-Previous analysis of extended LAT sources were performed as dedicated
-studies of individual sources, so we expect that a systematic scan of
+Previous analysis of extended LAT sources was performed as dedicated
+studies of individual sources so we expect that a systematic scan of
 all LAT detected sources could uncover additional spatially extended
@@
 of a source.  In Section~\ref{dual_localization_method}, we
-study the ability of the LAT to distinguish between spatially
-extended sources and confusion of nearby point-like sources.
-In Section~\ref{test_2lac_sources} we further demonstrate that our
+study the ability of the LAT to distinguish between a spatially
+extended source and the confusion of nearby point-like sources.
+In Section~\ref{test_2lac_sources}, we further demonstrate that our
 detection method does not misidentify point-like sources as being
@@
 extension of nine spatially extended sources that were reported in 2FGL
-but as being point-like.  Two of these have been previously analyzed in
+but as being point-like.  Two of these sources have been previously analyzed in
 dedicated publications.
@@
 \newtext{
-We considered two different models to use for the
+We considered two different models that can be used to model the
 surface brightness profile for extended sources, either a 2D Gaussian
@@
 Although these shapes are significantly different, 
-Figure~\ref{compare_disk_gauss} shows the their PDF 
+Figure~\ref{compare_disk_gauss} shows that their PDF 
 are similar for a source that has a 
@@
 brightness morphologies,
-we defined here the source size (0\fdg5) 
+we define the source size 
 as the radius containing
@@
 Equation~\ref{disk_pdf} respectively.
-For this example, where $\rsixeight=0\fdg5$, 
+For this example, $\rsixeight=0\fdg5$ so
 $\sigma_\text{disk}=0.61\degree$ and 
@@
 
-For smaller and fainter extended sources, the differences in the PDF
-for different spatial models are lost in the noise and the LAT is not
-sensitive to the detailed spatial structure of the sources.  Therefore,
-in our search for extended sources we use only a radially-symmetric
-uniform surface brightness as our spatial extension shape. We quote the
-radius of the edge ($\sigma$) as the size of the source.
+For smaller and fainter extended sources, the differences in the PDF for
+different spatial models lost in the noise and the LAT is not sensitive
+to the detailed spatial structure of these sources.  Therefore, in our
+search for extended sources we use only a radially-symmetric uniform
+surface brightness as our spatial extension shape. Unless otherwise noted,
+we quote the radius of the edge ($\sigma$) as the size of the source.
 }
@@
 \newtext{
-The threshold is high for small extensions because the
-source becomes
-small compared to the PSF. The threshold increases
+The threshold is high for small extensions when the
+source is 
+small compared to the size of the PSF. The threshold increases
 for large extended sources because the source becomes
@@
 
-We assessed the power of the $\tsext>\tsinc$ test using a Monte Carlo
-study.  We simulated one spatially extended sources and fit it as both
-an extended source and two point-like sources.  We then simulated two
+We assessed the power of the $\tsext>\tsinc$ test with a Monte Carlo
+study.  We simulated one spatially extended source and fit it as both
+an extended source and as two point-like sources.  We then simulated two
 point-like sources and fit them with the same two hypothesis. By comparing
 the distribution of \tsinc and \tsext for the two cases, we evaluated
-how well comparing \tsext to \tsinc is at rejecting the possibility of
-source confusion as well as how likely it is to incorrectly reject an
-extended source as being extended.  All sources were simulated using
+how well the $\tsext>\tsinc$ test is at rejecting the possibility of
+source confusion as well as how likely it is to incorrectly reject 
+with this test that an extendd source is 
+spatially extended.  All sources were simulated using
 the same two-year time range included in 2FGL and all fit values were
@@
 simulating extended sources of flux $4\times10^{-9} \phflux$ integrated
-from 1 \gev to 100 \gev and a power-law spectral model with
+from 1 \gev to 100 \gev with a power-law spectral model with
 spectral index 2.  This flux was picked to be representative of the
 new extended sourced that were discovered in the following analysis
-when looking in the 1 \gev and 100 \gev energy range
+when looking in the 1 \gev to 100 \gev energy range
 (see Section~\ref{new_ext_srcs_section}).
@@
 fitting simulations of two point-like sources each with half of the
-flux of the spatially extended source but the same spectral index.
+flux of the spatially extended source and with the same spectral index
+as the extended source.
 Finally, figure~\ref{confusion_plot}e shows the same analysis with each
@@
 
-The distributions show that for simulated
+The distributions also shows that for simulated
 extended sources with typical
@@
 increase in likelihood
-when fitting the extended source as two point-like sources
-($\tsext\sim\tsinc$).
+when fitting the extended source as two point-like sources.
 This is because although
@@
 of freedom (two spatial and two spectral parameters)
-than the one extended source (one extension parameter)
+than one extended source (one extension parameter)
 and can therefore easy model
-statistical fluctuations.
-This effect is most pronounced when using energies from 1
-\gev to 100 \gev where the PSF is even larger.  
+the extended source and statistical fluctuations in the data.
+This effect is most pronounced when using photons with energies between 1
+\gev and 100 \gev where the PSF is even larger.  
 On the other hand,
@@
 and found that \tsinc was typically much larger than \tsext.
-This is because the one additional extension degree of freedom does
-now as easily fit fit statistical fluctuations.
-
-From this, we conclude that the $\tsext>\tsinc$ test is reasonably
+This is because the one additional extension parameter is less able to
+model the second source or statistical fluctuations.
+
+From this, we conclude that the $\tsext>\tsinc$ test is 
 powerful at discarding cases in which the true emission is derived
@@
 source. On the other hand, because of the large values of \tsinc
-in figure~\ref{confusion_plot}a and figure~\ref{confusion_plot}a when
+in figure~\ref{confusion_plot}a and figure~\ref{confusion_plot}b when
 fitting spatially extended sources, we caution that even in the case of
@@
 100 \gev energy range. An error on the difference in spectral index is
-calculated by adding in quadrature the statistical error on the spectral
-index.  This plot shows that there can be a large difference in the
+calculated by adding in quadrature the statistical errors on the spectral
+indices.  This plot shows that there can be a large difference in the
 spectral index of the two fit point-like sources which is often greater
@@
 used to help determine whether a source is actually spatially extended
-instead of the emission from two confused point-like sources.
+instead of being the emission of two nearby point-like sources.
 
@@
 spatially extended sources.  Section~\ref{monte_carlo_validation} showed
-that we have a statistical test which can rigorously find sources for
-which the spatial emission is not well described by the PSF.  But for
-the extended sources we are searching for, this extension test does
+that we have a statistical test that finds when a LAT source is
+not well described by the PSF. 
+But this test does
 not uniquely prove that the emission originates from spatially extended
 emission instead of from multiple unresolved sources.  Demanding that
-$\tsext>\tsinc$ is a reasonably powerful test to avoid cases of simple
-confusion with two point-like sources. But it could always be the
+$\tsext>\tsinc$ is a powerful second test to avoid cases of simple
+confusion of two point-like sources. But it could always be the
 case that an extended source candidate is actually the superposition
-of multiple point-like or extended sources which could be resolved
-with deeper observations of the region.  Of course, there is nothing
-about this conclusion unique to LAT analysis.  Its just that the 
+of multiple point-like or extended sources that could be resolved
+with deeper observations of the region.  There is nothing
+about this conclusion unique to LAT analysis, but the
 larger PSF of the LAT and the density of sources expected to be \gev emitters in
 the galactic plane makes this issue more significant for LAT analysis.
-When possible, multiwavelength information should be used to help decide
-what is qualitatively the best sky model.
+When possible, multiwavelength information should be used to help 
+select the best model of the sky.
 
@@
 candidate in the 10 \gev to 100 \gev energy range and is spatially
-coincident with the SNR Vela Jr.  Figure~\ref{Vela_Jr} shows a counts
+coincident with the SNR Vela Jr and was recently studied by the LAT
+collaboration in \cite{vel_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
 map of the source.  Overlaid on Figure~\ref{Vela_Jr} are H.E.S.S. \tev
@@
 this SNR are were most likely included in 2FGL to account for residual
-induced by not taking the extension of this extended source into account.
-These sources were removed from our model of the sky.  In addition,
-two further away sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
-were removed from our model of the sky because they were not significant
-above 10 \gev.
+induced by not taking the extension Vela Jr. into account.  We removed
+from our model of the sky these sources.  In addition, two further away
+sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655 were removed from
+our model of the sky because they were not significant above 10 \gev.
 
@@
 extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ with an extension
-significance of $\tsext=87.2$ using photons with energies between 10
-\gev and 100 \gev.  This source was fit to $(l,b)=(266\fdg29,-1\fdg43)$.
-While fitting the extension of 2FGL\,J0851.7$-$4635, we iteartively
+significance of $\tsext=87.2$.
+The LAT size matches well the \tev morphology
+of Vela Jr. This source was fit to $(l,b)=(266\fdg29,-1\fdg43)$.
+While fitting the extension of 2FGL\,J0851.7$-$4635, we iteratively 
 relocalized the position of the nearby point-like catalog source
 2FGL\,J0854.7$-$4501 to $(l,b)=(266\fdg24,0\fdg49)$ to better fit its
-position at high energies.  The LAT size matches well the \tev morphology
-of Vela Jr.  A detailed papers by the LAT Collaboration on this SNR is
-in preparation.
+position at high energies.  
 }
@@
 \tablenotetext{(a)}{
-Integral Flux is in units of $10^{-9}\phflux$ and integrated in the fit
+Integral Flux in units of $10^{-9}\phflux$ and integrated in the fit
 energy range (either 1 \gev 100 \gev or 10 \gev 100 \gev).
@@
       \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v3/run.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v4/run.py
     \caption{
@@
     The LAT extension of
-    Vela X is from \cite{velax}.  Except for RX\,J1713.7$-$3946 and Vela Jr.,
-    the \tev sources were fit assuming a 2D Gaussian surface brightness
+    Vela X is from \cite{velax}. 
+    The \tev sources were fit assuming a 2D Gaussian surface brightness
     so the plotted \gev and \tev extensions were first converted to
-    \rsixeight (see Section~\ref{compare_source_size}).  Because of
+    \rsixeight (see Section~\ref{compare_source_size}).  
+    \newtext{Because of
     their large size, the shape of RX\,J1713.7$-$3946 and Vela Jr.
-    were not directly fit at \tev energies. Here, we take their sizes to be the
-    same as the LAT size and do not converted them to \rsixeight. The LAT
+    were not directly fit at \tev energies and so are not included
+    in this comparison. On the other hand, dedicated LAT publications on
+    these sources showed that their morphologies are consistent
+    \citep{rx_j1713_lat,vela_jr_lat}.
+    }
+    The LAT
     extension errors are the statistical and systematic errors added
@@
     brightness model so the LAT and H.E.S.S. sizes are first converted
-    to \rsixeight. Because
-    the spatial morphology of RX\,J1713.7$-$3946 and Vela Jr. is poorly
-    described by a 2D Gaussian surface brightness model, the \gev and \tev
-    extensions are included assuming a uniform surface brightness model.
+    to \rsixeight. 
+    \newtext{
+    Because of their large size, the shape of RX\,J1713.7$-$3946 and
+    Vela Jr. were not directly fit at \tev energies. Their size at
+    \tev energies is taken from the HESS source catalog to be 0\fdg5
+    and $1\degree$ respectively.  Because the spatial morphology of
+    RX\,J1713.7$-$3946 and Vela Jr. is poorly described by a 2D Gaussian,
+    the \gev and \tev extensions of these sources was not converted
+    to \rsixeight.
+    }
     }\label{gev_vs_tev_histogram}

### 2011-09-22 extended_catalog/paper/extended_catalog.tex
improvements

@@
 fixed to a very small value ($10^{-10}$ degrees in radius 
-for a uniform surface brightness spatial model).
+for a uniform surface brightness profile).
 
@@
 search for extended sources we use only a radially-symmetric uniform
-surface brightness as our spatial extension shape. Unless otherwise noted,
+surface brightness profile as our spatial extension shape. Unless otherwise noted,
 we quote the radius of the edge ($\sigma$) as the size of the source.
@@
 we simulated extended sources with a radially-symmetric uniform surface
-brightness. Additionally, we simulated our sources over the two-year
+brightness profile. Additionally, we simulated our sources over the two-year
 time range included in 2FGL.  For each extension and spectral index,
@@
 (see Section~\ref{new_ext_srcs_section}).
-We simulated these sources using a uniform surface brightness spatial
-model with extensions varying
+We simulated these sources using a uniform surface brightness profile
+with extensions varying
 up to $1\degree$.  Figure~\ref{confusion_plot}a shows 
@@
 we used all 2FGL sources within $15\degree$ of our source as our list
-of background sources and we refit the spectral parameters of sources
+of background sources and we refit the spectral parameters of all sources
 within $2\degree$ of the source.
@@
 sources which were included in 2FGL \citep{second_cat}.  Even though
-each of these sources required a dedicated analysis and these sources
+each of these sources required a dedicated analysis and they
 were fit with a variety of spatial models, it is valuable to show that
 these sources are significantly extended using our systematic extension
-method and consistently assuming a radially-symmetric uniform surface
-brightness for their spatial model.  On the other hand, for some of
+method that assumed a radially-symmetric uniform surface
+brightness profile.  On the other hand, for some of
 these sources a uniform disk spatial model does not well describe the
-observed extended emission and so the dedicated LAT publications give
-a qualitatively better model of the source.
+observed extended emission and so the dedicated LAT publications provides
+a qualitatively better model these sources.
 
@@
 the previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
-brightness spatial model when fitting it (\citep{lmc}).
+brightness profile when fitting it (\citep{lmc}).
 
@@
 the source's emission is significantly different from a uniform
-radially-symmetric surface brightness \citep{cen_a_lat}.
+radially-symmetric surface brightness profile \citep{cen_a_lat}.
 
@@
 position and extension of these sources when fitting them 
-with a radially-symmetric uniform surface brightness spatial model. It also
+with a radially-symmetric uniform surface brightness profile. It also
 includes the best fit spectral parameters for each source.  The position
@@
 \newtext{
-For the LAT detected extended sources presented in this paper,
-we developed two criteria for estimating the systematic error
-on the extension of the source.
+For the extended sources presented in this paper,
+we developed two criteria for estimating systematic errors
+on the extension of the sources.
 First, we estimated a systematic error due to
@@
 In particular, because the alternate model uses the same underlying gas
-maps it is unable to asses systematics due to misidentified of local
+maps it is unable to asses systematics due to mischaracterization of local
 diffuse structure due to lack lack of resolution of the underlying maps.
@@
 We do not expect the systematic error
-due to uncertainties in the PSF to be correlated to the systematic
+due to uncertainties in the PSF to be correlated with the systematic
 error due to uncertainty in the Galactic diffuse emission. Therefore,
@@
 
-Now that we have demonstrated that we can analyze sources
-previously known to be extended at \gev energies
-(Section~\ref{validate_known})
-and that we understand the statistical issues associated with
-this analysis (Section~\ref{monte_carlo_validation} and~\ref{test_2lac_sources}),
-we applied this method to search for new spatially extended \gev sources.
-
-Ideally, we would have applied a completely blind search where we simply
-fit the extension of each catalog source in the presence of all other 2FGL
-sources to find a complete list of all the sources that are spatially
-extended.  And as our test of AGN in Section~\ref{test_2lac_sources}
-showed, at high galactic latitude where the source density is not as
-great and the diffuse emission is less structured, this method works well.
-
-This method is infeasible in the galactic plane where we
-most likely expect to discover new spatially extended sources.  In the
-galactic plane, the analysis becomes challenged by our imperfect model of
-the diffuse emission and by issues related to source confusion.  
-Finding sources on top of this emission
-is difficult as was discussed in 1FGL
-and 2FGL \citep{first_cat,second_cat} and we expect that finding
-spatially extended sources be even more difficult.
-The Monte
-Carlo study on source confusion in Section~\ref{dual_localization_method}
+Now that we have demonstrated that we understand the statistical
+issues associated with analyzing spatially extended sources
+(Section~\ref{monte_carlo_validation} and~\ref{test_2lac_sources}) and
+that our method can correctly analyze the extended sources included in
+2FGL (Section~\ref{validate_known}), we apply this method to search for
+new spatially extended \gev sources.
+
+Ideally, we would apply a completely blind and uniform search that
+tests the extension of each catalog source in the presence of all other
+2FGL sources to find a complete list of all spatially extended sources.
+As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
+galactic latitude where the source density is not as great and the
+diffuse emission is less structured, this method works well.
+
+But this is infeasible in the galactic plane where we most likely expect
+to discover new spatially extended sources.  In the galactic plane,
+this analysis is challenged by our imperfect model of the diffuse
+emission and by issues related to source confusion.  The Monte Carlo
+study in Section~\ref{dual_localization_method}
 showed that the overall likelihood would greatly increase when fitting
-a spatially extended source as two point-like sources. So we expect that
-most spatially extended LAT sources that are
-currently modeled as point-like in 2FGL are surrounded by other 
-point-like sources that representing
-residual induced by not correctly modeling the sources' extension.
-Furthermore, the position of other nearby sources in the region near
-an extended source could be biased by not taking the extended
-sources' extension into account.  Furthermore, 2FGL produced a
-list of sources significant at energies above 100 \mev
-whereas we are most sensitive to spatial extension at higher energies.
-Therefore, we expect that when studying spatially extended sources
-at higher energies our analysis would be complicated
-by 2FGL sources not significant at higher energies and 2FGL sources
-whose position was biased by the diffuse emission at lower energies.
-
-To account for these issues,
-we first produces a large list of
+a spatially extended source as two point-like sources so we expect
+that spatially extended LAT sources are modeled in 2FGL as
+multiple point-like sources. Furthermore, the position of other nearby sources
+in the region near an extended source could be biased by not correctly
+modeling the
+sources' extension.  Furthermore, 2FGL produced a
+list of sources significant at energies above 100 \mev whereas we are
+most sensitive to spatial extension at higher energies.  Therefore,
+we expect that at higher energies our analysis would be complicated
+by 2FGL sources no longer significant and by 2FGL
+sources whose position was biased by diffuse emission at lower energies.
+
+To account for these issues, we first produces a large list of
 possibly extended sources employing a very liberal search criteria
-and then refined the analysis of the promising candidates on a case by case basis.
-Our strategy was to test all point-like 2FGL sources
-for extension by assuming that they have a uniform radially-symmetric
-uniform surface brightness
-and that they have a power-law spectral model.
-Although not all extended sources are
-expected to have a shape very similar to a uniform surface brightness,
-Section~\ref{compare_source_size} showed that for many spatially
-extended sources the wide PSF of the LAT and limited statistics allows
-for this to be a reasonable approximation.
-Additionally,
-our Monte Carlo studies (Section~\ref{monte_carlo_validation}
-and~\ref{test_2lac_sources}) demonstrate that we can use this shape for a
-statistically rigorous test. Because this spatial model only
-adds one additional degree of freedom, this
-test should be very sensitive to most spatially extended sources.
-On the other hand, this spatial model could bias us against
-finding extended sources which are not well described by uniform
-emission such as certain shell-type supernova remnants.
+and then refined the analysis of the promising candidates on a case
+by case basis.  Our strategy tested all point-like 2FGL sources for
+extension assuming they had a uniform radially-symmetric uniform surface
+brightness profile and a power-law spectral model.  Although not all
+extended sources are expected to have a shape very similar to a uniform
+surface brightness profile, Section~\ref{compare_source_size} showed that
+for many spatially extended sources the wide PSF of the LAT and limited
+statistics makes this a reasonable approximation.  Additionally, our Monte
+Carlo study and AGN validation (Sections~\ref{monte_carlo_validation}
+and~\ref{test_2lac_sources}) demonstrate that we can use this shape
+for a statistically rigorous test. Because this spatial model only adds
+one additional degree of freedom, this test should be very sensitive.
+On the other hand, choosing this spatial model could bias us against
+finding extended sources that are not well described by uniform emission
+such as shell-type supernova remnants.
 
@@
 we automatically removed from the background model all other 2FGL
-sources within 0\fdg5 of the source.  This value is somewhat arbitrary,
+sources within 0\fdg5 of the source.  This distance is somewhat arbitrary,
 but was picked in hopes of finding extended sources with sizes on the
@@
 
-We also performed a second search for extended sources using only photons with
-energies between 10 \gev and 100 \gev.  Although this approach tests the
-same sources, it is complementary because the Galactic diffuse emission is
-even less dominant above 10 \gev. Furthermore, source confusion becomes
-less of a problem since most LAT sources are not significantly detected
-at energies exclusively above 10 \gev. So we expected to be able to resolve
-harder sources in more complicated regions by restricting our analysis
-to higher energies. The $>10$ \gev analysis is especially beneficial
-for regions near pulsars which are not significantly detected above
-10 \gev. A similar procedure was used to detect HESS\,J1825$-$137 and
-MSH\,15$-$52 with the LAT \citep{msh1552,fermi_hess_j1825}.
+We also performed a second search for extended sources using only photons
+with energies between 10 \gev and 100 \gev.  Although this approach
+tests the same sources, it is complementary because the Galactic
+diffuse emission is even less dominant above 10 \gev. Furthermore,
+source confusion is less of a problem since many LAT sources are not
+significantly detected at energies exclusively above 10 \gev. Therefore,
+we expected to be able to resolve harder sources in more complicated
+regions by restricting our analysis to higher energies.  The $>10$ \gev
+analysis is especially beneficial for regions near pulsars which are
+not significantly detected above 10 \gev. A similar procedure was used
+to detect the spatial extension of HESS\,J1825$-$137 and MSH\,15$-$52
+with the LAT \citep{msh1552,fermi_hess_j1825}.
 
@@
 series of diagnostic plots.  For each candidate, we generated a map
-of residual \ts by adding a new source of spectral index 2 into the
-region at each pixel and finding the increase in likelihood when fitting
-its flux. Figure~\ref{res_tsmaps} shows a residual \ts map around the
+of the residual test statistic by adding a new source of spectral index 2 into the
+region at each position and finding the increase in likelihood when fitting
+its flux. Figure~\ref{res_tsmaps} shows this map around the
 most significantly extended source IC443 when it is modeled both as a
-point-like sources and an extended source.  The residual \ts map indicates
+point-like sources and an extended source.  The residual test statistic
+map indicates
 that the spatially extended model for IC443 is a significantly better
-description of the observed photons and that there is no significant
+description of the observed photons and that there is not significant
 residual in region after modeling the source as being spatially extended.
@@
 
-It was very clear by visually inspecting many of these plots that in many
+It was very clear by visual inspection that in many
 cases our analysis was strongly influence by large-scale residual in the
@@
 in the 1 \gev to 100 \gev energy range. Figure~\ref{example_bad_fit}
-shows a diffuse-emission-subtracted smoothed counts map with the best
+shows a diffuse-emission-subtracted smoothed counts map around
+this source with the best
 fit extension of the source overlaid. There appears to be large-scale
@@
 
-Because of these systematic issues, we only to selected candidates in
-regions which seemed relatively simple or in regions where there was an
-obvious spatially extended multiwavelength counterpart. Furthermore,
-by assuming extended sources had a uniform spatial emission our
-search was biased towards finding sources with this certain type of
-morphology. Therefore, our search can not be expected to be complete
-and it is likely that there are other spatially extended sources that
-this method missed.
+Because of these systematic issues, we only selected extended source
+candidates in regions that did not appear dominated by these issues and
+in regions where there was an obvious spatially extended multiwavelength
+counterpart. Because of these systematic issues, this search can not be
+expected to be complete and it is likely that there are other spatially
+extended sources that this method missed.
 
@@
 model of the sky sources that we believed were included in 2FGL to account
-for residual induced by not taking the extension of the extended source
-into account and sources include in 2FGL to represent soft point-like
+for residual induced by not modeling the extension of the source
+and sources include in 2FGL to represent soft point-like
 sources that were not significant at higher energies.  When deciding
 which background sources to keep and which to remove, we used as much as possible
-multiwavelenth information about possibly extended source counterparts
+multiwavelength information about possibly extended source counterparts
 to help guild our choice. For each extended source presented in 
@@
 by systematic errors at lower energies.
-Therefore, after selecting the list of sources, we had to iteratively
+Therefore, after selecting the list of background sources, we iteratively
 refit the position and spectrum of nearby background sources as well as
-the position, extension, and spectrum of the analyzed spatially extended
-sources until the overall fit had globally converged.  For each extended
-source, we will describe these modifications.
+the position and extension of the analyzed spatially extended
+sources until the overall fit globally converged.  For each extended
+source, we will describe the position of any relocalized background
+sources.
 
@@
 both \pointlike and \gtlike agree that $\tsext>16$. 
-We required also that $\tsext>16$ using the alternate diffuse
-model presented in seciton~\ref{systematic_errors_on_extension}.
-we then replaced the spatially extended source with two point-like
-sources and refit their positions and spectrum and calculate \tsinc.
+We further required that $\tsext>16$ using the alternate diffuse
+model presented in section~\ref{systematic_errors_on_extension}.
+We then replaced the spatially extended source with two point-like
+sources and refit the position and spectrum of the
+two point-like sources to calculate \tsinc.
 We only consider a source to be spatially extended, instead of being
@@
 that the emission is significantly more complicated than the simple
-radially-symmetric uniform surface brightness model.
+radially-symmetric uniform surface brightness profile that we assume.
 
@@
 For the sources found at energies above 10 \gev, we restrict our
-analysis of these sources to higher energies because of the issues
+analysis to higher energies because of the issues
 of source confusion and diffuse emission modeling described in
@@
 The spectral and spatial properties of these nine sources is summarized
-in Table~\ref{new_ext_srcs_table}.  The results of our investigation of
+in Table~\ref{new_ext_srcs_table} and the results of our investigation of
 systematic errors are presented in Table~\ref{alt_diff_model_results}.
-This section compares the fit extension with an extended source hypothesis to the
-fit assuming the emission originates from two independent point-like
-sources. For these extended extended sources, $\tsext>\tsinc$ suggesting
-that the \gev emission does not originate from multiple physically
-distinct sources.  Table~\ref{alt_diff_model_results} also includes the
+Table~\ref{alt_diff_model_results}
+also
+compares the likelihood assuming the source is spatially
+extended to the likelihood assuming 
+that the emission originates from two independent point-like
+sources. For these new extended sources, $\tsext>\tsinc$ 
+so we conclude that 
+the \gev emission does not originate from two physically
+distinct point-like sources (see Section~\ref{dual_localization_method}).  
+Table~\ref{alt_diff_model_results} also includes the
 results of the extension fit using variations of the PSF and the galactic
@@
 a counts map of this source and overlays and \rosat X-ray contours of
-this source.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
-and 2FGL\,J0821.0$-$4254 which are also coincident with the SNR but that
-do not separate into multiple point-like components.  We concluded that
-these two sources were included in 2FGL to account for residual induced
-by not taking the extension of this extended source into account and
-remvoed them from our model of the sky.
-
-With this model, 2FGL\,J0823.0$-$4246 was found to have an extension of
+Puppis A.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
+and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
+do not appear as separate point-like components.  We concluded that
+these nearby point-like sources
+were included in 2FGL to account for residual induced
+by not modeling the extension of this source and
+removed them from our model of the sky.
+After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension of
 $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=46.3$ using photons with energies between 1 \gev and 100 \gev.
-This source was fit to $(l,b)=(260\fdg32,-3\fdg28)$ and is also coincident
-with 1FGL\,J0823.3$-$4248.  Figure~\ref{snr_seds} shows the spectrum of
+of $\tsext=46.3$.  Figure~\ref{snr_seds} shows the spectrum of
 this source.
@@
 and references therein).  The fit extension of 2FGL\,J0823.0$-$4246
-match well its inferred size at \gev energies.  Puppis A's distance was
+matches well its inferred size at \gev energies.  Puppis A's distance was
 estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
@@
 using photons with energies between 1 \gev and 100 \gev.  The source
-was fit to
-$(l,b)=(353\fdg08, 16\fdg78)$ and is also coincident with 
-1FGL\,J1628.6$-$2419c.  
 Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
@@
 2FGL\,J1712.4$-$3941 was found by our search to be spatially extended using
-photons with energies between 1 \gev and 100 \gev.  It is
+photons with energies between 1 \gev and 100 \gev.  This source is
 spatially coincident with the SNR RX\,J1713.7$-$3946 and was
@@
 Figure~\ref{2FGL_J1712.4-3941}a shows a smoothed counts map of the source
-and overlays H.E.S.S. \tev contours of SNR
-RX\,J1713.7$-$3946 from \cite{rx_j1713_hess}.  To analyze this source,
+and overlays \tev contours of the SNR \cite{rx_j1713_hess}.  To analyze this source,
 we used the same background source model as the recent LAT publication.
@@
 $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=39.6$.  This source was fit to $(l,b)=(347\fdg25,-0\fdg54)$
-and is also coincident with 1FGL\,J1711.7$-$3944c.  Figure
-\ref{2FGL_J1712.4-3941} shows a counts map of this source.
+of $\tsext=39.6$.  
 }
@@
 candidate in the 10 \gev to 100 \gev energy range and is spatially
-coincident with the SNR Vela Jr and was recently studied by the LAT
-collaboration in \cite{vel_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
-map of the source.  Overlaid on Figure~\ref{Vela_Jr} are H.E.S.S. \tev
-contours of Vela Jr.  \citep{vela_jr_hess} and show that three
+coincident with the SNR Vela Jr. This source was recently studied by the LAT
+collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
+map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
+contours of Vela Jr. \citep{vela_jr_hess}.
+There are three
 point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
-and 2FGL\,J0855.4$-$4625 correlate with the multiwavelenth emission of
-this SNR are were most likely included in 2FGL to account for residual
-induced by not taking the extension Vela Jr. into account.  We removed
+and 2FGL\,J0855.4$-$4625 which correlate with the 
+multiwavelength
+emission of
+this SNR and were most likely included in 2FGL to account for residual
+induced by not modeling the extension Vela Jr.  We removed
 from our model of the sky these sources.  In addition, two further away
@@
 
-With this model of the sky, 2FGL\,J0851.7$-$4635 was found to have an
+With this model of the background, 2FGL\,J0851.7$-$4635 was found to have an
 extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ with an extension
@@
 The LAT size matches well the \tev morphology
-of Vela Jr. This source was fit to $(l,b)=(266\fdg29,-1\fdg43)$.
+of Vela Jr. 
 While fitting the extension of 2FGL\,J0851.7$-$4635, we iteratively 
@@
 be extended source candidates in the 10 \gev to 100 \gev energy
-range. They are less than $1\degree$ away from eachother and needed
+range. They are less than $1\degree$ away from each other and needed
 to be analyzed simultaneously.  2FGL\,J1615.0$-$5051 is spatially
@@
 HESS\,J1614$-$518.  Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
-of the source and overlays the \tev contours of HESS\,J1616$-$508 and
+of these sources and overlays the \tev contours of HESS\,J1616$-$508 and
 HESS\,J1614$-$518 \citep{hess_plane_survey}.  The figure shows that the
-source 2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and
-correlates with the extended \tev source.  Therefore, We concluded that
-these two sources were included in 2FGL to account for residual induced by
-not taking the extension of this extended source into account and remvoed
-them from our model of the sky.  There are two further away sources
+2FGL source 2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and
+correlates with the same extended \tev source
+as 2FGL\,J1615.2$-$5138.  Therefore, We concluded that
+this source were included in 2FGL to account for residual induced by
+not modeling the extension of
+2FGL\,J1615.2$-$5138 and
+remove
+it from our model of the sky.  There are two further away sources
 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c that were removed from
@@
 $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$ with an extension significance
-of \tsext=16.3.  This source was fit to $(l,b)=(332\fdg38,-0\fdg14)$ and is coincident
-with 1FGL\,J1613.6$-$5100c.
+of \tsext=16.3.  
 2FGL\,J1615.2$-$5138 was found
  to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
-with an extension significance of \tsext=48.0.  This source
-was fit to $(l,b)=(331\fdg66,-0\fdg66)$ and is also coincident
-with 1FGL\,J1614.7$-$5138c. To test for the possibility that
+with an extension significance of \tsext=48.0.  
+To test for the possibility that
 2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
@@
 2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
-sources.  Because $\tsinc=37.0$ is less than \tsext, we conclue that
+sources.  Because \tsinc is less than \tsext, we conclue that
 this emission does not originate from two nearby point-like sources.
@@
 candidate in the 10 \gev to 100 \gev energy range but is in a crowded
-region of hte sky.  It is spatially coincident with the \tev source
+region of the sky.  It is spatially coincident with the \tev source
 HESS\,J1632$-$478.  Figure~\ref{1FGL_J1632.9-4802c}a shows a counts
@@
 point-like 2FGL sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
-2FGL J1634.4$-$4743c.4-4820c that correlate with the extended \tev source
+2FGL\,J1634.4$-$4743c that correlate with the extended \tev source
 but that do not separate from 2FGL\,J1632.4$-$4753c at \gev energies.
-we concluded that these sources were included in 2FGL to account for
-residual induced by not taking the extension of this extended source
-into account and removed them from our model of the sky.
-and removed from our model four
+we concluded that these point-like 
+sources were included in 2FGL to account for
+residual induced by not modeling the extension of 
+2FGL\,J1632.4$-$4753c
+and removed them from our model of the sky.
+We also removed four
 further away sources 2FGL\,J1638.0$-$4703c, 
@@
 2FGL J1635.4-4717c, 2FGL J1636.3-4740c and which do not correlate with
-the extended \tev emission of HESS\,J1632$-$478 and that separate from
-the extended source candidate 2FGL\,J1632.4$-$4753c at \gev energies.
+the extended \tev emission of HESS\,J1632$-$478 as well
+as 
+the extended source candidate 2FGL\,J1632.4$-$4753c.
 Figure~\ref{1FGL_J1632.9-4802c}b shows the same region with these
 background sources subtracted.
-
-With this model of the sky, 2FGL\,J1632.4$-$4753c was found to have an
+With this model, 2FGL\,J1632.4$-$4753c was found to have an
 extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ with an extension
-significance of \tsext=64.5.  This source was fit to 
-$(l,b)=(336\fdg41,0\fdg22)$ and is
-also coincident with 1FGL\,J1632.9$-$4802c.  While fitting the extension
+significance of \tsext=64.5.  While fitting the extension
 of 2FGL\,J1632.4$-$4753c, we iteratively relocalized 2FGL\,J1635.4$-$4717c
@@
 
-This extended source is spatially coincident with the extended
-\tev source HESS\,J1632$-$478 
-and \tev contours are overlaid on 
-Figure~\ref{1FGL_J1632.9-4802c}
-\citep{hess_plane_survey}.
 H.E.S.S measured a 
 extension of $\sigma=0\fdg21\pm0\fdg05$ and $0\fdg06\pm0\fdg04$ along the
-semi-major and semi-minor axes when fitting this source with an
-elliptical 2D Gaussian surface brightness.  This corresponds to a 68\%
+semi-major and semi-minor axes when fitting 
+HESS\,J1632$-$478 
+with an
+elliptical 2D Gaussian surface brightness profile.  This corresponds to a 68\%
 containment size $\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$
@@
 in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
-smoothed counts map of the region in and overlays the \tev contours of
+smoothed counts map of the region and overlays the \tev contours of
 HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
@@
 is another source 2FGL\,J1835.5$-$0649 located between the three
-sources which appears to correlate with the \tev morphology of
-HESS\,J1837$-$069. Similarly, the emission from 2FGL\,J1835.5$-$0649
-and 2FGL\,J1837.3$-$0700c does appear to separate at \gev energies.
-Therefore, we concluded that this source was included in 2FGL to account
-for residual induced by not taking the extension of this extended source
-into account and removed them from our model of the sky.  We also removed
-from our model of the sky the further away point-like catlaog soruce
+sources that appears to correlate with the \tev morphology of
+HESS\,J1837$-$069 and does not separate from the emission 
+of 2FGL\,J1837.3$-$0700c.
+We concluded that this source was included in 2FGL to account
+for residual induced by not modeling the extension of this source
+and removed it from our model of the sky.  We also removed
+from our model of the sky the further away point-like 2FGL source
 2FGL\,J1839.0-0539 because it was not significant with energies above
 10 \gev.  Figure~\ref{1FGL_J1837.5-0659c}b shows a counts map of this
-region after subtracted the modeled background sources.
-
-With our improved model, 2FGL\,J1837.3$-$0700c was found to have an
+region after subtracted these background sources.
+
+With this model, 2FGL\,J1837.3$-$0700c was found to have an
 extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an extension
-significance of $\tsext=18.8$ using
- photons with energies between
-10 \gev and 100 \gev.  This source was fit to $(l,b)=(25\fdg08,0\fdg13)$
-and is also coincident with 1FGL\,J1837.5$-$0659c.  To get a good fit
-of 2FGL\,J1837.3$-$0700c, we iteratively relocalized the three nearby
+significance of $\tsext=18.8$. 
+While fitting the extension of 2FGL\,J1837.3$-$0700c,
+we iteratively relocalized the three nearby
 background sources along with the extension of 2FGL\,J1837.3$-$0700c but
@@
 $(l,b)=(26\fdg08,0\fdg23)$. With this best fit sky model, we tested for
-source confusion by fitting the source instead as two point sources.
-Because $\tsinc=12.6$ is less than \tsext, we conclue that this emission
+source confusion by fitting the source instead as two point-like sources.
+Because \tsinc is less than \tsext, we concluded that this emission
 does not originate from two nearby point-like sources.
@@
 along the semi-major and semi-minor axis when fitting this source
-with an elliptical 2D Gaussian surface brightness.  This corresponds
+with an elliptical 2D Gaussian surface brightness profile.  This corresponds
 to a 68\% containment radius of $\rsixeight=0\fdg18\pm0\fdg03$ and
@@
 The source 2FGL\,J2021.5+4026 is coincident
-with 2CG\,078+01, 3EG\,J2020+4017, and 1FGL\,J2020.0+4049
-\citep{second_cos_b_catalog,third_egret_catalog,first_cat} and also with
+with 2CG\,078+01 and 3EG\,J2020+4017
+\citep{second_cos_b_catalog,third_egret_catalog} and also with
 the $\gamma$-Cygni SNR. This $\gamma$-ray source has been speculated
@@
 There is
-a nearby source 2FGL\,J2019.1+4040 which correlates with the radio
+a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
 emission of $\gamma$-Cygni and does not appear to represent a physically
 distinct source.  We concluded that it was included in 2FGL to account for
-residual induced by not taking the extension of $\gamma$-Cygni into
-account and removed it from our model of the sky.  We also removed from
+residual induced by not modeling the extension of $\gamma$-Cygni 
+and removed it from our model of the sky.  We also removed from
 our model of the sky the four further away sources 2FGL\,J2022.8+3843c,
@@
 they were not significant when observed at energies above 10 \gev.
-Furthermore, we chose to add to our region an additional point-like
-source $(l,b)=(78\fdg85,2\fdg67)$.  Although this source is not very
-significant ($\ts=13.5$ in the 1 \gev to 100 \gev energy range), its
-location is outside the multiwavelenth contours of $\gamma$-Cygni and
+Furthermore, we decided to add to our region an additional point-like
+source at $(l,b)=(78\fdg85,2\fdg67)$.  Although this source is not very
+significant ($\ts=13.5$ in the 10 \gev to 100 \gev energy range), its
+location is outside the 
+multiwavelength
+contours of $\gamma$-Cygni and
 modeling it improved the connection of the best fit extension
-with the multiwavelenth size of $\gamma$-Cygni. Nevertheless,
+with the 
+multiwavelength
+contours of $\gamma$-Cygni. Nevertheless,
 the overall spatial and spectral characteristics of the source were not
-significantly changed after including the source.
-
-Using this sky model, 2FGL\,J2021.5+4026 fit an extension of
+significantly changed by the presence of this source.
+
+With this model, 2FGL\,J2021.5+4026 was found to have an extension of
 $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=116.4$.  This source was fit to $(l,b)=(78\fdg18,2\fdg19)$.
+of $\tsext=116.4$.  
 Figure~\ref{snr_seds} shows its spectrum.  The inferred size of this
-source at \gev energies well matches the radio size of $\gamma$-Cygni,
-as can be seen in Figure~\ref{1FGL_J2020.0+4049}.
+source at \gev energies well matches the radio size of $\gamma$-Cygni.
 Milagro detected a $4.2\sigma$ excess at energies $\sim 30$ \tev
@@
 but definitively measuring this would require a more in-depth analysis
-of the LAT data using the same elliptical surface brightness model.
+of the LAT data using the same elliptical surface brightness profile.
 
@@
 Many of the \tev detected extended sources now seen at \gev energies are
-currently unidentified and further multi-wavelength follow-up observations
+currently unidentified and further multiwavelength follow-up observations
 will be necessary to understand these particle accelerators.  But the
@@
     \newtext{
-    The detection threshold to resolve a uniform surface brightness
+    The detection threshold to resolve a uniform surface brightness profile
     extended source for a two-year exposure.  All sources have an
@@
       The detection threshold to resolve spatially extended
-      sources with a uniform surface brightness for a two-year exposure
+      sources with a uniform surface brightness profile for a two-year exposure
       The threshold is calculated for
@@
   the best fit position and extension of this source assuming a
-  radially-symmetric uniform surface brightness.  The two 
+  radially-symmetric uniform surface brightness profile.  The two 
   star-shaped markers (colored
@@
   represent the best fit position and extension of this
-  source assuming a radially-symmetric uniform surface brightness. The
+  source assuming a radially-symmetric uniform surface brightness profile. The
   contours in (a) correspond to the 100 micrometer image observed by
@@
   the best fit position and extension of this source assuming a radially
-  symmetric uniform surface brightness.  The contours (colored light blue)
+  symmetric uniform surface brightness profile.  The contours (colored light blue)
   correspond to the \tev image \citep{rx_j1713_hess}.  The region was
@@
   and the circle (colored red) are the best fit position and extension of
-  this source assuming a radially-symmetric uniform surface brightness.
+  this source assuming a radially-symmetric uniform surface brightness profile.
   The five star-shaped markers (colored green) represent 2FGL sources
@@
     positions and extensions of these sources assuming a radially
-    symmetric uniform surface brightness.  The three star-shaped
+    symmetric uniform surface brightness profile.  The three star-shaped
     markers (colored
@@
   2FGL\,J1632.4$-$4753c assuming a radially-symmetric uniform surface
-  brightness.  The four star-shaped markers (colored green) represent 2FGL
+  brightness profile.  The four star-shaped markers (colored green) represent 2FGL
   sources that were removed from the background model.  The circular
@@
   the best fit position and extension of 2FGL\,J1837.3$-$0700c assuming a
-  radially-symmetric uniform surface brightness. The circular
+  radially-symmetric uniform surface brightness profile. The circular
   and square markers 
@@
   and extension of 2FGL\,J2021.5+4026 assuming a radially-symmetric
-  uniform surface brightness.  The star-shaped markers (colored green)
+  uniform surface brightness profile.  The star-shaped markers (colored green)
   represent 2FGL sources that were removed from the background model.
@@
     Vela X is from \cite{velax}. 
-    The \tev sources were fit assuming a 2D Gaussian surface brightness
+    The \tev sources were fit assuming a 2D Gaussian surface brightness profile
     so the plotted \gev and \tev extensions were first converted to
@@
     Vela Jr., the H.E.S.S. sources were fit with a 2D Gaussian surface
-    brightness model so the LAT and H.E.S.S. sizes are first converted
+    brightness profile so the LAT and H.E.S.S. sizes are first converted
     to \rsixeight. 

### 2011-09-22 extended_catalog/paper/extended_catalog.tex
ading new draft

@@
 and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
-do not appear as separate point-like components.  We concluded that
+do not appear to represent physically distinct sources.
+We concluded that
 these nearby point-like sources
@@
 emission of
-this SNR and were most likely included in 2FGL to account for residual
-induced by not modeling the extension Vela Jr.  We removed
-from our model of the sky these sources.  In addition, two further away
+this SNR but do not appear to be physically distinct sources.
+They were most likely included in 2FGL to account for residual
+induced by not modeling the extension Vela Jr. and were removed
+from our model of the sky.  In addition, two further away
 sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655 were removed from
@@
 \newtext{
-2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to
-be extended source candidates in the 10 \gev to 100 \gev energy
-range. They are less than $1\degree$ away from each other and needed
-to be analyzed simultaneously.  2FGL\,J1615.0$-$5051 is spatially
-coincident with the extended \tev source HESS\,J1616$-$508 and
-2FGL\,J1615.2$-$5138 is coincident with the extended \tev source
-HESS\,J1614$-$518.  Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
-of these sources and overlays the \tev contours of HESS\,J1616$-$508 and
-HESS\,J1614$-$518 \citep{hess_plane_survey}.  The figure shows that the
-2FGL source 2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and
-correlates with the same extended \tev source
-as 2FGL\,J1615.2$-$5138.  Therefore, We concluded that
-this source were included in 2FGL to account for residual induced by
-not modeling the extension of
-2FGL\,J1615.2$-$5138 and
-remove
+2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to be
+extended source candidates in the 10 \gev to 100 \gev energy range. They
+are less than $1\degree$ away from each other and needed to be analyzed
+simultaneously.  2FGL\,J1615.0$-$5051 is spatially coincident with
+the extended \tev source HESS\,J1616$-$508 and 2FGL\,J1615.2$-$5138
+is coincident with the extended \tev source HESS\,J1614$-$518.
+Figure~\ref{1FGL_J1613.6-5100c} shows a counts map of these sources and
+overlays the \tev contours of HESS\,J1616$-$508 and HESS\,J1614$-$518
+\citep{hess_plane_survey}.  The figure shows that the 2FGL source
+2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and correlates
+with the same extended \tev source as 2FGL\,J1615.2$-$5138.  We concluded
+that this source was included in 2FGL to account for residual induced
+by not modeling the extension of 2FGL\,J1615.2$-$5138 and removed
 it from our model of the sky.  There are two further away sources
@@
 2FGL\,J1634.4$-$4743c that correlate with the extended \tev source
-but that do not separate from 2FGL\,J1632.4$-$4753c at \gev energies.
-we concluded that these point-like 
-sources were included in 2FGL to account for
+but that do appear to be physically distinct sources.
+We concluded that they
+were included in 2FGL to account for
 residual induced by not modeling the extension of 
@@
 We also removed four
-further away sources 2FGL\,J1638.0$-$4703c, 
+farther away sources 2FGL\,J1638.0$-$4703c, 
 2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
@@
 point-like 2FGL sources 2FGL\,J1836.8$-$0623c, and 2FGL\,J1839.3$-$0558c
-that clearly represent distinct sources.  On the other hand, there
-is another source 2FGL\,J1835.5$-$0649 located between the three
-sources that appears to correlate with the \tev morphology of
-HESS\,J1837$-$069 and does not separate from the emission 
-of 2FGL\,J1837.3$-$0700c.
-We concluded that this source was included in 2FGL to account
-for residual induced by not modeling the extension of this source
-and removed it from our model of the sky.  We also removed
-from our model of the sky the further away point-like 2FGL source
-2FGL\,J1839.0-0539 because it was not significant with energies above
-10 \gev.  Figure~\ref{1FGL_J1837.5-0659c}b shows a counts map of this
-region after subtracted these background sources.
+that clearly represent distinct sources.  On the other hand, there is
+another source 2FGL\,J1835.5$-$0649 located between the three sources that
+appears to correlate with the \tev morphology of HESS\,J1837$-$069 but
+does not appear to represent a physically distinct source.  We concluded
+that this source was included in 2FGL to account for residual induced by
+not modeling the extension of this source and removed it from our model
+of the sky.  We also removed from our model of the sky the farther away
+point-like 2FGL source 2FGL\,J1839.0-0539 because it was not significant
+with energies above 10 \gev.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
+counts map of this region after subtracted these background sources.
 
@@
 While fitting the extension of 2FGL\,J1837.3$-$0700c,
-we iteratively relocalized the three nearby
+we iteratively relocalized the three nearest
 background sources along with the extension of 2FGL\,J1837.3$-$0700c but
@@
 and removed it from our model of the sky.  We also removed from
-our model of the sky the four further away sources 2FGL\,J2022.8+3843c,
+our model of the sky the four farther away sources 2FGL\,J2022.8+3843c,
 2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c, and 2FGL\,J2012.4+3955c because

### 2011-09-27 extended_catalog/paper/extended_catalog.tex
francesco suggestion

@@
 \documentclass[12pt,preprint]{aastex}
+
+% New text (from v3.0 to v?.?):
+%  * Better clarification about previous gtlike validation of extended source analysis.
 
@@
 in the second \fermi-LAT catalog (2FGL) for extension. 
-\newtext{
 We report the
@@
 in dedicated publications.
-}
 \end{abstract}
@@
 
-\newtext{
 Previous analysis of extended LAT sources was performed as dedicated
@@
 dedicated publications.
-}
 
@@
 to build a profile of the likelihood as a function of extension.
-This approach is not optimal because the position, extension, and
-spectrum of the source must be simultaneously fit to find the best fit
-parameters and to maximize the statistical significance of
-the detection.  Furthermore since the \gtlike likelihood profile approach
-is computationally intensive, no large-scale Monte Carlo simulations
-have been run to validate it.
+\newtext{
+The gtlike likelihood profile approach has been show to correctly
+reproduce the extension of simulated extended sources assuming that the
+true position is known \citep{francesco_2011}.  But it is not optimal
+because the position, extension, and spectrum of the source must be
+simultaneously fit to find the best fit parameters and to maximize the
+statistical significance of the detection.  Furthermore, because the \gtlike
+approach is computationally intensive no large-scale Monte Carlo
+simulations have been run to calculate its false detection rate.
+}
 
@@
 
-\newtext{
 We considered two different models that can be used to model the
@@
 we quote the radius of the edge ($\sigma$) as the size of the source.
-}
 
@@
 
-\newtext{
 Our study shows broad agreement between simulations and
@@
 reasonable despite the imperfections of the corresponding calibration.
-}
 
@@
 increasing source size and reaches a minimum around 0\fdg5. 
-\newtext{
 The threshold is high for small extensions when the
@@
 increasingly diluted by the background.
-} Figure~\ref{index_sensitivity} shows
+Figure~\ref{index_sensitivity} shows
 the threshold using photons with energies between 100 \mev and 100 \gev
@@
 spectral index. 
-\newtext{
 The index dependence of the detection threshold is
 even weaker when considering only photons with energies above 10 \gev
-because the PSF changes little from 10 \gev to 100 \gev.}
+because the PSF changes little from 10 \gev to 100 \gev.
 Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
@@
 
-\newtext{
 It is impossible to discriminate with LAT data exclusively between a
@@
 point-like sources found using \pointlike.
-}
 
@@
 
-\newtext{
 For all following LAT analysis, we used the same two-year dataset
@@
 within $2\degree$ of the source.
-
-}
 
@@
 
-\newtext{
 As further validation of our extended source method for studying
@@
 a qualitatively better model these sources.
-
-}
 
@@
 
-\newtext{
 For the extended sources presented in this paper,
@@
 uncertainty in our knowledge of the LAT PSF.  
-}
 Before launch, the LAT PSF
@@
 
-\newtext{
 We estimated a second systematic error on the extension of a source
@@
 emission \citep{isotropic_lat}.  
-}
 The intensities of various components
@@
 
-\newtext{
 It is not expected that this diffuse model is superior to the standard
@@
 diffuse structure due to lack lack of resolution of the underlying maps.
-}
 
@@
 \label{extended_source_search_method}
-
-\newtext{
 
@@
 and by uncertainties in our modeling of the Galactic diffuse emission. 
-\newtext{
 In addition, the Galactic
 diffuse emission is more pronounced at lower energies due to its steep
-energy spectrum compared to the typical spectrum of extended sources \citep{intermediate_diffuse_lat}.}
+energy spectrum compared to the typical spectrum of extended sources \citep{intermediate_diffuse_lat}.
 For that reason,
@@
 
-}
-
 \section{New Extended Sources}
@@
 
-\newtext{
 Nine extended sources not included in 2FGL were found by our
@@
 emission model and uncertainties in the angular resolution of the LAT.
-}
 
@@
 
-\newtext{
 2FGL\,J0823.0$-$4246 was found by our search to be an extended source
@@
 \citep{w51c,ic443,w44,w28,w49b_lat}.
-}
 
@@
 
-\newtext{
 2FGL\,J1712.4$-$3941 was found by our search to be spatially extended using
@@
 of $\tsext=39.6$.
-}
 
@@
 
-\newtext{
 2FGL\,J0851.7$-$4635 was found by our search to be an extended source
@@
 position at high energies.
-}
 
@@
 
-\newtext{
 2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to be
@@
 necessary to understand this $\gamma$-ray source.
-}
 
@@
 
-\newtext{
 2FGL\,J1615.2$-$5138 is spatialy coincident with 
@@
 %              (initial Position  - SkyDir(336.9639,-0.236)
-
-\newtext{
 
@@
 and $\gamma$-rays.
-}
 
@@
 
-\newtext{
 2FGL\,J1837.3$-$0700c was found by our search to be an extended source
@@
 some of the $\gamma$-ray emission.
-}
 
@@
 
-\newtext{
 The source 2FGL\,J2021.5+4026 is coincident
@@
 
-}
-
 \section{Discussion}
 
-\newtext{
 Twelve extended sources were included in 2FGL and two additonal
@@
 seven additional extended sources. 
-}
 We also reanalyze the spatial
@@
 
-\newtext{
-
 The \textit{Fermi} LAT Collaboration acknowledges generous ongoing support
@@
 use of HEALPix\footnote{http://healpix.jpl.nasa.gov/} \citep{healpix}.
-
-}
 
@@
     \caption{
-    \newtext{
     The detection threshold to resolve a uniform surface brightness profile
@@
     using photons with energies between 1 \gev and 100 \gev.
-    }
     }\label{index_sensitivity}
@@
     \caption{
-    \newtext{
     The distribution of \tsext and \tsinc 
@@
     10 \gev to 100 \gev energy range.
-    }
     }\label{confusion_plot}
@@
     \caption{
-    \newtext{
     The absolute value of the difference of the fit
@@
     100 \gev energy range.
-    }
     }\label{index_difference}
@@
   \caption{
-  \newtext{
   A test statistic map generated for the region around the SNR 
@@
   IC443 modeled as an extended source. The cross represents the best
-  fit position of IC443.}
   }
@@
     Table~\ref{known_extended_sources}.
-    \newtext{
     RX\,J1713.7$-$3946 and Vela Jr. were previously studied in dedicated publications \citep{rx_j1713_lat,vela_jr_lat}.
-    }
 }
@@
   \caption{
-  \newtext{
   A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
@@
   kernel and (b) with the emission from the background sources subtracted.  
-  }
   The triangular marker (colored red in the electronic version)
@@
   \caption{
-  \newtext{
   A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of the
@@
   kernel and (b) with the emission from the background sources subtracted.
-  }
   The triangular marker (colored red in the online version) represents
@@
     \rsixeight (see Section~\ref{compare_source_size}).  
-    \newtext{Because of
+    Because of
     their large size, the shape of RX\,J1713.7$-$3946 and Vela Jr.
@@
     \citep{rx_j1713_lat,vela_jr_lat}.
-    }
     The LAT
@@
     to \rsixeight. 
-    \newtext{
     Because of their large size, the shape of RX\,J1713.7$-$3946 and
@@
     to \rsixeight.
-    }
     }\label{gev_vs_tev_histogram}

### 2011-10-02 extended_catalog/lande_ext_collab_august_2011/lande_gal_ext_collab_august_2011.tex
update presentation
reogranize

@@
 
-\begin{frame}
+\begin{frame}{Fig. 3: Monte Carlo Study of false detection rate}
+  \begin{columns}
+    \column{.6\textwidth} 
+    \includegraphics[scale=0.45]{../paper/mc_plots/ts_ext_emin_1000_color.eps}
+    \column{.4\textwidth} 
+    \begin{itemize}
+      \item Test simulated point sources for extension
+      \item Lots of spectral parameters
+      \item Good agreement with Wilks' Theorem
+      \item $\sqrt{\text{TS}_\text{ext}} \rightarrow \# \sigma$
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 5: Threshold vs background}
+  \begin{columns}
+    \column{.6\textwidth} 
+    \includegraphics[scale=0.5]{../paper/mc_plots/all_sensitivity_color.eps}
+    \column{.4\textwidth} 
+    \begin{itemize}
+      \item Large Monte Carlo study
+      \item Calculate detection threshold
+        to spatially extended sources
+      \item Overlay LAT extended sources
+      \item For future extended sources, can compare to
+        threshold
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Table. 3: Reanalyze 12 sources in 2FGL}
+    \includegraphics[scale=0.5]{tables/table3.eps}
+  \begin{itemize}
+    \item Test 12 2FGL sources for extension
+    \item But always assume radially symmetric disk spatial model
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Table. 4: New Extended Sources}
+  \includegraphics[scale=0.45]{tables/table4.eps}
+  \begin{itemize}
+    \item 9 Extended Sources Not in 2FGL
+    \item Skip in this talk
+      \begin{itemize}
+        \item Vela Jr. - Dedicated Publication
+        \item RX\,J1713.7$-$3946 - Dedicated Publication
+        \item Ophiuchus - Most likely diffuse emission
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Table. 5: Extension Errors}
+    \includegraphics[scale=0.5]{tables/table5.eps}
+    \begin{itemize}
+      \item Two Methods to estimate systematic error on extension
+    \begin{itemize}
+      \item Alternate diffuse model (add degrees of freedom)
+      \item MC representation of the PSF
+    \end{itemize}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{2FGL\,J0823.0$-$4246 - Puppis A}
+  \begin{columns}
+    \column{.55\textwidth} 
+    \includegraphics[scale=0.5]{../paper/source_plots/source_Puppis_A_color.eps}
+    \column{.45\textwidth} 
+    \begin{itemize}
+      \item 1 GeV to 100 GeV
+      \item Middle-age SNR Puppis A
+      \item ROSAT X-ray contours (Petre+1996)
+      \item SNR not observed to interact with molecular clouds 
+        (Paron+2008)
+      \item Similar to Cygnus Loop SNR
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{2FGL\,J2021.5+4026 - $\gamma$-Cygni}
+  \begin{columns}
+    \column{.55\textwidth} 
+    \includegraphics[scale=0.5]{../paper/source_plots/source_Gamma_Cygni_color.eps}
+    \column{.45\textwidth} 
+    \begin{itemize}
+      \item 10 GeV to 100 GeV
+      \item PSR\,J2021+4026 at lower energies
+      \item Radio contours (Taylor+2003)
+      \item SNR interacting with Molecular cloud
+      \item Milagro: $4.2\sigma$ excess at $\sim 30$ TeV (Abdo+2009)
+      \item 
+        VER\,J2019+407 
+        detected by Veritas at 200 GeV (Weinstein 2009)
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Puppis A + $\gamma$-Cygni}
   \begin{center}
-    \includegraphics[scale=0.5]{tables/table3.eps}
+    \includegraphics[scale=0.5]{../paper/summary_plots/snr_seds_color.eps}
   \end{center}
@@
 
-\begin{frame}
+\begin{frame}{HESS\,J1614$-$518 \& HESS\,J1616$-$508}
+  \begin{columns}
+    \column{.6\textwidth} 
+    \includegraphics[scale=0.5]{../paper/source_plots/source_HESS_J1614-518_color.eps}
+    \column{.4\textwidth} 
+    \begin{itemize}
+      \item 10 GeV to 100 GeV
+      \item Two nearby LAT extended sources 
+      \item both
+        coincident with extended TeV sources.
+    \end{itemize}
+  \end{columns}
+
+  \begin{itemize}
+    \item (left): 
+      2FGL\,J1615.0$-$5051 $\rightarrow$ HESS\,J1616$-$508
+    \item (right):
+      2FGL\,J1615.2$-$5138 $\rightarrow$ HESS\,J1614$-$518
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{2FGL\,J1615.0$-$5051 $\rightarrow$ HESS\,J1616$-$508}
+  \begin{columns}
+    \column{.4\textwidth} 
+    % from http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/som/2007/01/
+  \includegraphics[scale=0.45]{plots/Som_1_07_p1.eps}
+    \column{.7\textwidth} 
+  \begin{itemize}
+    \item 2 nearby SNRs: RCW103 and Kes~32 - not spatially coincident (Aharonian+2006) 
+    \item 3 Nearby Pulsars: only 
+      PSR\,J1617$-$5055 energetically powerful enough
+      \begin{itemize}
+        \item 9' away $\rightarrow$ offset PWN?
+        \item {\em Chandra} detected $\sim 1'$ PWN 
+        \item not oriented towards HESS\,J1616$-$508
+        \end{itemize}
+      \item Other diffuse emission in region (Kargaltsev+2009)
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{2FGL\,J1615.2$-$5138 $\rightarrow$ HESS\,J1614$-$518}
+
+  \begin{columns}
+    \column{.4\textwidth} 
+    \includegraphics[scale=0.3]{plots/Som_9_08_p1.eps}
+    \column{.7\textwidth} 
+    \begin{itemize}
+      \item 5 nearby pulsars, but none powerful enough (Rowell+2008)
+      \item Open cluster Pisim 22 
+      \item Suzaku: 2 X-ray sources, one towards peak 
+        of HESS\,J1614$-$518 and one coincident with Pisim 22
+        (Matsumoto+2008)
+      \item SNR? PWN? Acceleration in Stellar Winds of Pisim 22?
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{2FGL\,J1632.4$-$4753c - HESS\,J1632-478}
+  \begin{columns}
+    \column{.55\textwidth} 
+    \includegraphics[scale=0.5]{../paper/source_plots/source_HESS_J1632-478_color.eps}
+    \column{.45\textwidth} 
+    \begin{itemize}
+      \item 10 GeV to 100 GeV
+      \item  {\em XMM-Newton} point-like + extended emission
+        ($32''\times15''$)
+        towards center of H.E.S.S source (Balbo+2010)
+      \item Extended radio source in archival MGPS-2 data
+      \item PWN? No pulsations (yet) in point-like X-ray source
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{2FGL\,J1837.3$-$0700c - HESS\,J1837-069}
+  \begin{columns}
+    \column{.55\textwidth} 
+    \includegraphics[scale=0.45]{../paper/source_plots/source_HESS_J1837-069_color.eps}
+    \column{.45\textwidth} 
+    \begin{itemize}
+      \item 10 GeV to 100 GeV
+      \item Coincident with X-ray source
+        AX\,J1838$-$0655 (Hertz \& Grindlay 1988)
+      \item X-ray Pulsations: PSR\,J1838$-$0655 
+    \end{itemize}
+  \end{columns}
+    \begin{itemize}
+      \item also: X-ray PWN $\sim 2'$ 
+        (Gotthelf \& Halpern 2008)
+      \item $\gamma$-rays from PWN?
+      \item Second X-ray source
+        AX\,J1837.3$-$0652 resolved into
+        point + extended component (no pulsations yet)
+      \item $\gamma$-rays from multiple PWN
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{LAT + H.E.S.S. SEDs}
+  \begin{columns}
+    \column{.65\textwidth} 
+    \includegraphics[scale=0.5]{../paper/summary_plots/hess_seds_color.eps}
+    \column{.35\textwidth} 
+\begin{itemize}
+    \item GeV + TeV spectrum connect for
+    these souces
+  \item (Statistical Errors Only)
+  \item
+ Future work: take SEDs to lower
+    energies
+\end{itemize}
+
+  \end{columns}
+\end{frame}
+
+\begin{frame}{LAT Detected Extended Sources}
   \begin{center}
-    \includegraphics[scale=0.5]{tables/table4.eps}
+    \includegraphics[scale=0.65]{../paper/summary_plots/allsky_extended_sources_color.eps}
   \end{center}
@@
 
+\begin{frame}{Spectral Index of extended sources}
+  \begin{columns}
+    \column{.6\textwidth} 
+    \includegraphics[scale=0.5]{../paper/summary_plots/compare_index_2FGL_color.eps}
+    \column{.4\textwidth} 
+    \begin{itemize}
+      \item Compare Index to 2FGL 
+      \item Seems like there is roughly a
+        divide between softer SNRs and harder PWN
+      \item Have not quantified
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{LAT + H.E.S.S. Sizes}
+  \begin{columns}
+    \column{.5\textwidth} 
+    \includegraphics[scale=0.4]{../paper/summary_plots/gev_vs_tev_plot_color.eps}
+    \column{.5\textwidth} 
+    \begin{itemize}
+      \item Compare GeV and TeV sizes
+      \item Generally, good agreement
+      \item HESS\,J1825$-$137 significantly
+        larger at GeV than TeV
+      \item Other PWN expected to be larger at
+        GeV than TeV energies, but
+      \item Would require improving systematics on the
+        analysis (source confusion, elliptical spatial models, etc)
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{LAT + H.E.S.S. Distributions}
+  \begin{columns}
+    \column{.6\textwidth} 
+    \includegraphics[scale=0.5]{../paper/summary_plots/gev_vs_tev_histogram_color.eps}
+    \column{.4\textwidth} 
+    \begin{itemize}
+      \item Compare GeV and TeV sizes
+      \item LAT detectes larger sources
+      \item H.E.S.S. detects smaller sources
+      \item Population of small TeV
+        extended sources we can't resolve
+      \item Presumably, currently outside our
+        detectability
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Sensitivity after 10 years}
+  \begin{columns}
+    \column{.6\textwidth} 
+  \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
+    \column{.4\textwidth} 
+    \begin{itemize}
+      \item Calculate extension threshold with 10 year simulation
+      \item Also, project from 2 year threshold by $\sqrt{time}$ and time
+      \item Sensitivity $>\sqrt{time}$ for small sources
+      \item Many future discoveries!
+      \item Think about putting in senior review
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
 \end{document}

### 2011-10-02 compare_flight_mc_psf/v1/plot.py

@@ -1,61 +1,0 @@
-import h5py
-import pylab as P
-import numpy as np
-from scipy.stats import chi2
-
-
-file=h5py.File('/nfs/slac/g/ki/ki03/lande/compare_flight_mc_psf/v1/merged.hdf5')
-
-flux=np.asarray(file['flux_mc'])
-ts_ext_P7SOURCE_V4=np.asarray(file['ts_ext_P7SOURCE_V4'])
-ts_ext_P7SOURCE_V6=np.asarray(file['ts_ext_P7SOURCE_V6'])
-ts=np.asarray(file['ts_P7SOURCE_V6'])
-index=np.asarray(file['index_mc'])
-
-
-index_mc=2
-#for flux_mc in [ 1e-9, 3e-9, 1e-8, 3e-8, 1e-7, 3e-7, 1e-6, 3e-6 ]:
-for flux_mc,kwargs in [ [3e-8, dict() ] ]:
-
-    select = np.where((flux==flux_mc) & (index==index_mc) & (ts>25))
-
-    for irf,ts_ext in [['P7SOURCE_V4',ts_ext_P7SOURCE_V4],
-                       ['P7SOURCE_V6',ts_ext_P7SOURCE_V6]]:
-        
-        ts_ext = ts_ext[select]
-
-        print irf, ts_ext
-        ts_ext[ts_ext<0] = 0
-        print irf, ts_ext
-
-
-        max_ts=25
-        bins=np.linspace(0,max_ts,1e3)
-        bin_center=bins[:-1] + (bins[1]-bins[0])/2
-
-        binned=np.histogram(ts_ext,bins=bins)[0]
-
-        if any(ts_ext>max_ts):
-            print 'v4: ',ts_ext[np.where(ts_ext>max_ts)]
-            print 'v6: ',ts_ext[np.where(ts_ext>max_ts)]
-
-        cdf=np.cumsum(binned[::-1])[::-1]
-        cdf=cdf.astype(float)/cdf[0] # normalize
-
-        #cdf[cdf==0]=min_cdf
-
-        #def format(x):
-        #    a,b=x.split('e-0')
-        #    return (r'$%s\times'%a if a !='1' else r'$')+'10^{-%s}\ \mathrm{ph}\ \mathrm{cm}^{-2}\mathrm{s}^{-1}$' % b
-        #grid[i].semilogy(bin_center,cdf,color,linewidth=1,label=format(flux_mc))
-
[…]

### 2011-10-02 fermi/compare_flight_mc_psf/v1/monte_carlo.py

@@ -77,7 +77,10 @@ results_dict=[]
 
 index_mc=2
 
-for flux_mc in [ 1e-9, 3e-9, 1e-8, 3e-8, 1e-7, 3e-7, 1e-6, 3e-6 ]:
+for flux_mc in [1e-9, 3e-6,
+                3e-9, 1e-6,
+                1e-8, 3e-7,
+                3e-8, 1e-7]:
 
     source_str="%g_%g_%s" % (flux_mc,index_mc,istr)
 
@@ -200,6 +203,9 @@ for flux_mc in [ 1e-9, 3e-9, 1e-8, 3e-8, 1e-7, 3e-7, 1e-6, 3e-6 ]:
         results_dict[-1]['ts_%s' % fit_irf] = ts
         results_dict[-1]['ts_ext_%s' % fit_irf] = ts_ext
         results_dict[-1]['sigma_%s' % fit_irf] = sigma
+
+        del roi
+
 
     results_dict = toolbag.tolist(results_dict)
 

### 2011-10-02 fermi/compare_flight_mc_psf/v1/plot.py

@@ -1,0 +1,82 @@
+import h5py
+import pylab as P
+import numpy as np
+from scipy.stats import chi2
+
+
+file=h5py.File('/nfs/slac/g/ki/ki03/lande/compare_flight_mc_psf/v1/merged.hdf5')
+
+flux=np.asarray(file['flux_mc'])
+ts_ext_P7SOURCE_V4=np.asarray(file['ts_ext_P7SOURCE_V4'])
+ts_ext_P7SOURCE_V6=np.asarray(file['ts_ext_P7SOURCE_V6'])
+ts=np.asarray(file['ts_P7SOURCE_V6'])
+ts_point = ts - ts_ext_P7SOURCE_V6
+index=np.asarray(file['index_mc'])
+
+fig=P.figure(figsize=(6.5,4))
+from mpl_toolkits.axes_grid.axes_grid import Grid
+
+grid = Grid(fig, 111, nrows_ncols = (1, 2), axes_pad=0.0)
+
+
+min_cdf = 1e-4
+
+for i,(irf,all_ts_ext) in enumerate([
+    ['P7SOURCE_V6',ts_ext_P7SOURCE_V6],
+    ['P7SOURCE_V4',ts_ext_P7SOURCE_V4]
+]):
+
+    max_ts=max(all_ts_ext) + 1
+
+    axes = grid[i]
+
+    index_mc=2
+    for flux_mc in [ 1e-9, 3e-9, 1e-8, 3e-8, 1e-7, 3e-7, 1e-6, 3e-6 ]:
+        kwargs=dict()
+
+        select = (flux==flux_mc) & (index==index_mc) & (ts_point>25)
+
+        print 'index=%s, flux=%s, num=%s' % (index_mc,flux_mc,np.sum(select))
+
+        if np.sum(select) < 100:
+            continue
+
+        print irf, flux_mc, select
+        
+        ts_ext = all_ts_ext[select]
+
+        ts_ext[ts_ext<0] = 0
+
+
+        bins=np.linspace(0,max_ts,1e3)
+        bin_center=bins[:-1] + (bins[1]-bins[0])/2
+
+        binned=np.histogram(ts_ext,bins=bins)[0]
+
+        if any(ts_ext>max_ts):
+            print '> max: ',irf,ts_ext[np.where(ts_ext>max_ts)]
+
+        cdf=np.cumsum(binned[::-1])[::-1]
+
+        cdf=cdf.astype(float)/cdf[0] # normalize
[…]

### 2011-10-02 green_catalog/2FGL/v2/analyze_v1.py

@@ -20,7 +20,8 @@ from argparse import ArgumentParser
 import yaml
 import os
 
-def plot_extra_stuff(axes,header, roi):
+
+def overlay_on_plot(axes,header, roi):
     """ Overlay:
         * Deleted 2FGL sources
         * the SNR + best fit extension. 
@@ -30,10 +31,9 @@ def plot_extra_stuff(axes,header, roi):
         axes['gal'].plot([source.skydir.l()],[source.skydir.b()], marker='*', color='green', 
                          markeredgecolor='white', markersize=12)
 
-
     source = roi.get_source(name)
 
-    # plot the SNR in blue
+    # plot the best fit SNR position/center in blue
     ROISmoothedSource.overlay_source(source, axes, color='blue', zorder=10)
 
     if isinstance(source,ExtendedSource):
@@ -53,7 +53,7 @@ def plot_extra_stuff(axes,header, roi):
         levels = eval(contour['levels'])
         axes[hdu.header].contour(hdu.data, levels, colors='lightblue')
 
-def plots(when):
+def plots(hypothesis):
     """ make a smoothed counts map + tsmap. 
 
     here, plot again the region before + after background subtraction
@@ -67,49 +67,131 @@ def plots(when):
         for function,title_base,filename_base in [[roi.plot_sources,'Diffuse Subtracted','sources'],[roi.plot_source,'BG Source Subtracted','source']]:
             smooth=function(which = name,
                             size = plot_size, 
-                            show_extensions = True if when == 'postlocalize' else False,
-                            kernel_rad=kernel_rad, label_psf=False,
+                            kernel_rad=kernel_rad, 
                             colorbar_radius = max(snrsize, 1),
                             title=r'%s %s ($\sigma_\mathrm{smooth}=%g^\circ$)' % (title_base,name,kernel_rad))
-            plot_extra_stuff(smooth.axes, smooth.header, roi)
-            P.savefig('%s_%s_kernel_%g_%s.png' % (filename_base,when,kernel_rad,name))
+            overlay_on_plot(smooth.axes, smooth.header, roi)
+            P.savefig('%s_%s_kernel_%g_%s.png' % (filename_base,hypothesis,kernel_rad,name))
 
 
     # Residual TS Map
     tsmap=roi.plot_tsmap(size = plot_size, pixelsize = 1./8, title='Residual TS Map %s' % name)
[…]

### 2011-10-02 green_catalog/2FGL/v2/make_website.py

@@ -40,7 +40,48 @@ def t2t(lines,name):
         
     os.system('txt2tags --target html --style color.css --css-sugar %s' % filename)
 
-def format_table(only_significant=False):
+class Results(object):
+    """ Simple object to load in the yaml file and slice/dice it. """
+    def __init__(self,snr):
+        self.results = results = all_results[snr]
+
+        extended = results['extended']['gtlike']
+        point=results['point']['gtlike']
+        radio=results['radio_template']['gtlike']
+
+        self.ts=point['ts']
+        if self.ts < 0: self.ts=0
+
+        self.significant = self.ts >= 25
+        self.candidate = self.ts >= 9 and self.ts < 25
+
+        self.ts_ext = extended['ts_ext']
+        if self.ts_ext < 0: self.ts_ext = 0
+
+        self.nickname=snrdata[snr]['nickname']
+
+        if self.ts_ext > 16:
+            self.flux = extended['flux']
+            self.flux_err = extended['flux_err']
+
+            self.index=-1*extended['Index']
+        else:
+            self.flux=point['flux']
+            self.flux_err=point['flux_err']
+
+            self.index=-1*point['Index']
+
+        self.ul=radio['upper_limit']
+
+        if self.ts > 25 and self.ts_ext > 16:
+            self.category = 'extended'
+        elif self.ts > 25:
+            self.category = 'point'
+        else:
+            self.category = 'radio_template'
+
+
+def format_table(only_significant=False, only_candidates=False):
     index_t2t.append('')
 
     table=defaultdict(list)
@@ -48,42 +89,32 @@ def format_table(only_significant=False):
     format = '| %30s | %30s | %30s | %30s | %30s | %30s |' 
 
     index_t2t.append(
-        format % ('Name','TS','TS_ext','Flux','Index','Nickname')
+        format % ('Name','TS_point','TS_ext','Flux','Index','Nickname')
         )
 
     for snr in snrs:
         if all_results.has_key(snr):
-            results=all_results[snr]
 
-            ts=results['postlocalize_gtlike']['ts']
-            if ts < 0: ts=0
+            r = Results(snr)
+            
+            if only_significant and not r.significant: continue
+            if only_candidates and not r.candidate: continue
 
-            significant = results['status'] != 'insignificant'
-
[…]

### 2011-10-02 green_catalog/2FGL/v2/setup_snr.py

@@ -3,7 +3,7 @@ import yaml
 from os.path import expandvars as e
 
 from uw.like.pointspec import DataSpecification, SpectralAnalysis
-from uw.like.pointspec_helpers import get_default_diffuse
+from uw.like.pointspec_helpers import get_default_diffuse, PointSource
 from uw.like.roi_catalogs import Catalog2FGL
 from uw.like.roi_extended import ExtendedSource
 from uw.like.Models import PowerLaw
@@ -58,17 +58,25 @@ def setup_roi(name, snrdata, free_radius=2, fit_emin=1e4, fit_emax=1e5):
 
     return roi
 
-def get_snr(name, snrdata):
+def get_snr(name, snrdata, point_like=False):
 
     snr=yaml.load(open(snrdata))[name]
     skydir=SkyDir(*snr['cel'])
     radius=snr['radius']
+    model=PowerLaw(index=2)
 
-    return ExtendedSource(
-        name=name,
-        model=PowerLaw(index=2),
-        spatial_model=Disk(
-            sigma=radius,
-            center=skydir
-        )
-    )
+    if point_like:
+        return PointSource(
+            name=name,
+            model=model,
+            skydir=skydir
+            )
+    else:
+        return ExtendedSource(
+            name=name,
+            model=model,
+            spatial_model=Disk(
+                sigma=radius,
+                center=skydir
+                )
+            )

### 2011-10-02 pointlike/lande_roi.py

@@ -11,7 +11,8 @@
 import numpy as np
 #np.seterr(divide='ignore', invalid='ignore', over='ignore', under='ignore')
 
-from toolbag import *
+from . toolbag import *
+from . lande_localize import *
 
 # import stuff generally useful
 from uw.like.Models import *
@@ -30,8 +31,8 @@ from uw.utilities.minuit import Minuit
 from uw.utilities import keyword_options
 from skymaps import *
 from os.path import *
-from roi_gtlike import *
-from lande_plotting import *
+from . roi_gtlike import *
+from . lande_plotting import *
 
 from uw.like import sed_plotter
 import pylab as P
@@ -361,7 +362,6 @@ class LandeROI(ROIAnalysis):
         for name in names:
             self.localize(which=name,*args,**kwargs)
 
-
     def plot_all_seds(self,filename='all_seds.png',num_cols=4,**kwargs):
         """ Create an SED of all sources in the ROI. 
             It is important to make sure you are modeling
@@ -401,26 +401,6 @@ class LandeROI(ROIAnalysis):
         src_info = gtlike.get_gtlike_info_dict(which)
         return src_info
     
-    def sum_tsmap(self,*args,**kwargs):
-        if not self.quiet: print 'Creating sum tsmap'
-        tscalc = TSCalc(self)
-        mask = np.ones(len(self.psm.models),dtype=bool)
-        temp=TSCalcPySkyFunction(tscalc,source_mask=mask)
-        self._save_map(temp,*args,**kwargs)
-
-    def res_tsmap(self,*args,**kwargs):
-        if not self.quiet: print 'Creating residual tsmap'
-        tscalc = TSCalc(self)
-        temp=TSCalcPySkyFunction(tscalc)
-        self._save_map(temp,*args,**kwargs)
-
-    def _save_map(self,temp,center=None,filename=None,pixelsize=0.125,fov=10,projection='AIT', galactic=True):
-        skyfun=temp.get_pyskyfun()
-        center = self.roi_dir if center is None else center
-        skyimage = SkyImage(center,filename, pixelsize,fov,1,projection, galactic, False)
-        skyimage.fill(skyfun)
-        del(skyimage)
-
     def get_info_dict(self,which):
         """ Return a dictionary of everything Joshua finds
             interesting about the source. """
@@ -938,245 +918,4 @@ def random_point_near(skydir,distance):
[…]

### 2011-10-02 pointlike/toolbag.py

@@ -1,3 +1,4 @@
+""" This file contains various function which I have found useful. """
 import numpy as np
 import pyfits as pf
 
@@ -28,6 +29,7 @@ def sourcedict(like_or_roi, name, extra='', emin=100, emax=100000):
     from BinnedAnalysis import BinnedAnalysis
     from pyLikelihood import ParameterVector
     from uw.like.roi_analysis import ROIAnalysis
+    from uw.like.roi_extended import ExtendedSource
 
     d={}
 
@@ -37,6 +39,7 @@ def sourcedict(like_or_roi, name, extra='', emin=100, emax=100000):
         d['ts' + extra] = like.Ts(name,reoptimize=True)
         d['flux' + extra]=like.flux(name,emin=emin,emax=emax)
         d['flux_err' + extra]=like.fluxError(name,emin=emin,emax=emax)
+        d['logLikelihood']=like.logLike.value()
 
         spectralparameters=ParameterVector()
         like.model[name]['Spectrum'].getParams(spectralparameters)
@@ -48,18 +51,43 @@ def sourcedict(like_or_roi, name, extra='', emin=100, emax=100000):
         roi=like_or_roi
 
         source=roi.get_source(name)
+
         model=source.model
 
+        old_quiet = roi.quiet; roi.quiet=True
         d['ts' + extra] = roi.TS(name,quick=False)
+        roi.quiet = old_quiet
+
+        d['logLikelihood']=-roi.logLikelihood(roi.parameters())
+
         d['flux' + extra],d['flux_err' + extra]=model.i_flux(emin=emin,emax=emax,error=True)
         for param in model.param_names:
-            d[param + extra]=model['index']
-            d[param + '_err' + extra]=model.error('index')
+            d[param + extra]=model[param]
+            d[param + '_err' + extra]=model.error(param)
+
+        # Source position
+        d['gal'] = [source.skydir.l(),source.skydir.b()]
+        d['equ'] = [source.skydir.ra(),source.skydir.dec()]
+
+        if isinstance(source,ExtendedSource):
+            # Extended Source parameters
+            spatial_model = source.spatial_model
+            for param in spatial_model.param_names:
+                d[param + extra]=spatial_model[param]
+                d[param + '_err' + extra]=spatial_model.error(param)
+
+        # add elliptical error, if they exist.
+        # N.B. If no localization performed, this will return
+        # an empty dictionary.
[…]

### 2011-10-02 pwncatalog/1FGL_reanalysis/v3/loop_pwn.py

@@ -70,7 +70,7 @@ queue_jobs,err=p.communicate()
 
 for name in glob.iglob("*"):
     if isdir(name):
-        results="%s/results_*_%s.yaml" % (name,name)
+        results="%s/results*%s.yaml" % (name,name)
         log="%s/log_%s.txt" % (name,name)
         run='$PWD/%s/run_%s.sh' % (name,name)
 

### 2011-10-06 resume/v1/lande_resume.tex
adding resume to svn

% Resume taken from: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,12pt,line]{resume}

\begin{document}
\name{\Large Joshua Lande - Curriculum Vitae}

\begin{resume}

    \section{Contact\\Information}

    Kavli Institute for Particle Astrophysics and Cosmology \hfill (650) 427-0102       \\
    Stanford Linear Accelerator Center                      \hfill jlande@stanford.edu  \\
    2575 Sand Hill Road, Menlo Park, CA-94025, US                                       \\

    \section{Education}

    \textbf{Stanford University}, Stanford, CA \\
    \textsl{Doctor of Philosophy} \hfill \textbf{ September, 2008 -- present}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{itemize}
        \item Expected graduation date: May, 2012
        \item Advisors:  Dr. Stefan Funk
    \end{itemize}

    \textsl{Marlboro College, BS in Physics} \hfill \textbf{September, 2004 -- May, 2008}\vspace{-3mm}\\\vspace{-1mm}%

  \section{Talks and Posters}

      Lande, J., ``Search for Spatially Extended Sources Using Two Years of Flight Data,'' 
      \textsl{2011 Fermi Symposium}, \hfill \textbf{May 2011.}

      Lande, J., ``Analysis of the spatial extent of sources in the Fermi-LAT 1 year catalog,'' 
      \textsl{2009 Fermi Symposium}, \hfill \textbf{December 2009.}

￼￼Lande, J., ``Analysis of Spatially Extended Sources with the Fermi-LAT,''
      \textsl{TeV Particle Astrophysics 2009}, \hfill \textbf{June 2009.}

    \section{Distinctions}

    The Buck Turner Prize, \textsl{Marlboro College}                  \hfill \textbf{2008} \\
    The Ernest Coleman Award for Scholarship and Citizenship, \textsl{SULI Internship} \hfill \textbf{2007} \\

    \section{Professional\\Experience}

    \textbf{Stanford University}, Stanford, CA \\

    \textsl{Teaching Assistant}, Physics 110 \hfill \textbf{2011}\\
    Teaching assistant for undergraduate course in classical mechanics.

    \textsl{Teaching Assistant}, Physics 113 \hfill \textbf{2010}\\
    Teaching assistant for undergraduate course in computational
    methods in physics using MATLAB.

    \textsl{Teaching Assistant}, Physics 23 \hfill \textbf{2009}\\
    Teaching assistant for undergraduate course in introductory
    physics.

    \textsl{SULI Internship at SLAC}, Menlo Park, CA, \hfill \textbf{Summer, 2007}\\
      SULI Internship studying x-ray powder diffraction. 
      Adviser: Dr. Samuel Webb.

    \textsl{REU Internship at UC Davis} Davis, CA, \hfill \textbf{Summer, 2006}\\
        Physics REU studying gravitational lensing. Adviser: Dr. Tony Tyson.

    \textsl{SEAP Internship at Analytic Services} Arlington, VA, \hfill \textbf{Summer, 2004 \& 2005}\\
        George Washington University Science \& Engineering
        Apprentice Program studying space weather.
        Adviser: Dr. Ronald Turner.

\end{resume}
\end{document}

### 2011-10-14 presentations/lande_ext_collab_august_2011/lande_cat_ext_collab_august_2011.tex
Adding folder for presentations

\documentclass[12pt]{beamer}
\usetheme[navbar=false, bkgimage=false, shadow=true]{Fermi}

\usepackage{graphicx}

\usepackage{amsmath}
\usepackage{xspace}
\usepackage{deluxetable}

\title{Search for Spatially Extended \textit{fermi}-LAT Sources Using Two Years of Flight
Data}
%\subtitle{\ldots}

\author{Joshua Lande}
\institute{SLAC/Stanford}
\email{joshualande@gmail.com}
\date{August 25, 2011}

\begin{document}

\include{introduction}

\begin{frame}{Topics relevant to catalog}
  \begin{itemize}
        \item Monte Carlo study of false detection rate 
        \item LAT's detection threshold to extension
        \item Reanalysis of extended sources in 2FGL
        \item Testing AGN for extension
        \item (See presentation at Galactic splinter for rest of paper)
  \end{itemize}
\end{frame}

\begin{frame}{Fig. 3: Monte Carlo Study of false detection rate}
  \begin{columns}
    \column{.5\textwidth} 
    \includegraphics[scale=0.4]{../paper/mc_plots/ts_ext_emin_1000_color.eps}
    \column{.5\textwidth} 
    \begin{itemize}
      \item Simulate point sources
      \item One year simulation
      \item Against EGRET isotropic BG
      \item Vary flux, spectral index
      \item $\sim$30,000 sims per spectral model
      \item Test for extension
      \item Compare CDF of $\text{TS}_\text{ext}$ to $\chi^2_1/2$
      \item Good agreement with Wilks' Theorem
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 4: Detection Threshold}
  \begin{columns}
    \column{.6\textwidth} 
    \includegraphics[scale=0.5]{../paper/mc_plots/index_sensitivity_color.eps}
    \column{.4\textwidth} 
    \begin{itemize}
      \item Detetion threshold to extension
      \item 2 years + isotropic bg
      \item Definition: $\langle\text{TS}_\text{ext}\rangle=16$
      \item Little sensitivity to small+soft sources
      \item Little improvement using 100 MeV to 1 GeV photons
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 5: Threshold vs background}
  \begin{columns}
    \column{.6\textwidth} 
    \includegraphics[scale=0.5]{../paper/mc_plots/all_sensitivity_color.eps}
    \column{.4\textwidth} 
    \begin{itemize}
      \item Vary 
        \begin{itemize}
          \item spectral index, 
          \item diffuse normalization
          \item energy range
        \end{itemize}
      \item Overlay extended sources
      \item Reference for future publications
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 6: Threshold vs time}
  \begin{columns}
    \column{.6\textwidth} 
    \includegraphics[scale=0.5]{../paper/mc_plots/time_sensitivity_color.eps}
    \column{.4\textwidth} 
    \begin{itemize}
      \item Calculate 10 year detection
        threshold
        \begin{itemize}
          \item With MC simulationn
          \item Projected from 2 years by $\sqrt{\text{time}}$ and 
            time
        \end{itemize}
      \item Sensitivity $>\sqrt{\text{time}}$ for
        small extended sources
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 6: $\text{TS}_\text{ext}$ for 2LAC AGN}

  \begin{columns}
    \column{.6\textwidth} 
    \includegraphics[scale=0.5]{../paper/source_plots/agn_color.eps}
    \column{.4\textwidth} 
    \begin{itemize}
      \item 885 clean AGN in 2LAC
        \item Test 783 of these (with $\text{TS}>25$)
        for extension
      \item Compare CDF of $\text{TS}_\text{ext}$ to $\chi^2_1/2$
      \item Don't find AGN to be extended
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Table. 3: Reanalyze 12 sources in 2FGL}
    \includegraphics[scale=0.5]{tables/table3.eps}
  \begin{itemize}
    \item Test 12 2FGL sources for extension
    \item Assume radially symmetric disk spatial model
    \item Improved models could be included in future catalog
  \end{itemize}
\end{frame}

\begin{frame}{Table. 4: 9 more extended sources}
    \includegraphics[scale=0.45]{tables/table4.eps}

    Extended sources could be included in future catalog
\end{frame}

\end{document}

### 2011-10-14 presentations/lande_ext_collab_august_2011/tables/fix.sh

@@ -1,0 +1,10 @@
+
+
+# acroread -toPostScript has best
+# performance with bounding boxes.
+for i in *pdf; do
+    base=`basename $i .pdf`
+    acroread -toPostScript $base.pdf 
+    ps2epsi $base.ps $base.eps
+    rm $base.ps
+done

### 2011-10-15 presentations/pwncat2/lande_2011_bari_f2f/lande_2011_bari_f2f.tex
adding presentation

\documentclass[12pt]{beamer}
\usetheme[navbar=false, bkgimage=false, shadow=true]{Fermi}

\usepackage{graphicx}

\usepackage{amsmath}

\title{A New Maximum Likelihood Method for Defining the pulsar off-peak}
%\subtitle{\ldots}

\author{Joshua Lande\\[1em]
With much help from Damien + Matthew}
\institute{SLAC/Stanford}
\email{joshualande@gmail.com}
\date{August 25, 2011}

\begin{document}

\fermititle

\begin{frame}{Motivation}
  \begin{itemize}
    \item Most People like to study where the pulsar is
    \item But many reason to want to know where (in phase) the pulsar is not
      \begin{itemize}
        \item Studying nearby sources which may be confused $\rightarrow$ $\gamma$-Cgygni SNR
        \item Off-peak emission (or lack therefo) is interesting for pulsar modeling  $\rightarrow$ CTA1
        \item Looking for DC emission from the pulsar's wind $\rightarrow$ PWNCAT2
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{What has been done before}

  lala

  \includegraphics[width=0.75\textwidth]{plots/off_pulse_pwncat1.pdf}

  PWNCat1 $\rightarrow$ Selected by eye using pulsar phaseogram.
\end{frame}

\begin{frame}{Another Method: CTA1-Paper II}
  lala

  \includegraphics[width=0.75\textwidth]{plots/cta1.pdf}

  2nd CTA1 Paper$\rightarrow$ Look for break in TS vs $\Delta \phi$

\end{frame}

\begin{frame}{Maximum likelihood pulsar fitting}
  \begin{itemize}
    \item New idea for how to define the off pulse, proposed by Matthew
Background
   \item \texttt{uw.pulsar} for maximum likelihood fitting of pulsar light curves
   \item Has to be done anyway for 2nd pulsar catalog (Damien + Matthew)
     do define the peak separations
   \item Idea, can we use the best fit light curve to define the off peak?
  \end{itemize}
\end{frame}

\begin{frame}{\texttt{uw.pulsar}, under the hood}
  \begin{itemize}
   \item Define the likelihood: $\mathcal{L} = \sum_\text{photons}\text{PDF}(\text{phase})$
   \item Here, $\text{PDF}=\text{PDF}(\text{model parameters})$, so you have to pick a pulsar light curve model!
   \item As usual, maximize the log of the Likelihood
  \end{itemize}

  Example:\footnote{From \url{https://confluence.slac.stanford.edu/x/2AIyAw}}
  \begin{columns}
    \column{0.5\textwidth}
    \center{2 Gaussian}

    \includegraphics[width=1\textwidth]{plots/template_example_gauss.png}

    \column{0.5\textwidth}
    \center{2 Lorenzians}
    \includegraphics[width=1\textwidth]{plots/template_example_lorentzian.png}
  \end{columns}
\end{frame}

\begin{frame}{A more complicated Exmaple}
  \begin{itemize}
    \item Vela:
  \end{itemize}

\end{frame}

\end{document}

### 2011-10-15 pwncatalog/1FGL_reanalysis/v4/lande_off_peak.py
off peak code

@@ -1,0 +1,161 @@
+from argparse import ArgumentParser
+import copy
+import numbers
+import pickle
+import yaml
+import numpy as np
+import pylab as P
+
+from setup_pwn import setup_pwn
+
+from uw.pulsar import lc_plotting_func
+from uw.pulsar import lcprimitives as lp
+from uw.pulsar.lcprimitives import * # for the eval
+from uw.pulsar.lc_off_peak import OffPeak
+from uw.pulsar.phase_range import PhaseRange
+from uw.pulsar import lcfitters as lf
+from uw.like.Models import ExpCutoff
+from toolbag import tolist
+
+
+def find_TSdc(name,pwndata):
+    print 'Calculating TSdc'
+    roi=setup_pwn(name,pwndata,phase=PhaseRange(0,1))
+
+    # start with a grid search, for convergence help
+    f=roi.get_model(name).i_flux(1e2,1e5)
+
+    best_ts = -np.inf
+    for index in [.01, .5, 1,1.5,2]:
+        for cutoff in [ 3e2, 1e3, 3e3, 1e4, 3e4]:
+            m=ExpCutoff(index=index,cutoff=cutoff)
+            m.set_flux(f,1e2,1e5)
+            roi.modify(which=name, model=m, keep_old_flux=False)
+            roi.fit(use_gradient=True, estimate_errors=False)
+            ts=roi.TS(which=name)
+            print cutoff,index,ts
+            if  ts > best_ts:
+                best_ts, best_index, best_cutoff = ts, index, cutoff
+
+    roi.print_summary()
+
+    TSdc = best_ts
+
+    roi.plot_sed(which=name, filename='sed_%s.pdf' % name)
+    roi.print_summary()
+
+
+    print 'TSdc=%.1f' % TSdc
+
+    return TSdc
+
+
+def find_offpeak(ft1,name,rad,peaks,pwncat1phase, TSdc):
+    """plot light curve using pointlike script in whixh is added a line to plot the edges of the offpulse region
+    a=minimum of the edge
+    b=maximum of the edge"""
+    
+    plc = lc_plotting_func.PulsarLightCurve(ft1, 
+                                           psrname=name, radius=rad,
+                                           emin=50, emax=300000)
+    plc.fill_phaseogram()
+
+    phases = plc.get_phases()
+    primitives = []
+    for peak in peaks:
+        if isinstance(peak,numbers.Real):
[…]

### 2011-10-15 presentations/pwncat2/lande_2011_bari_f2f/lande_2011_bari_f2f.tex
better presentation

@@
 \usetheme[navbar=false, bkgimage=false, shadow=true]{Fermi}
+
+%  \begin{columns}
+%    \column{0.5\textwidth}
+%    \column{0.5\textwidth}
+%  \end{columns}
 
@@
 
+% taken from http://da.vidr.cc/2008/09/29/creating-flowcharts-with-pgftikz-in-latex/
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows}
+\tikzstyle{decision} = [diamond, draw, text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
+\tikzstyle{block} = [rectangle, draw, text width=5em, text centered, rounded corners, minimum height=4em]
+
 \title{A New Maximum Likelihood Method for Defining the pulsar off-peak}
@@
 
-\author{Joshua Lande\\[1em]
-With much help from Damien + Matthew}
-\institute{SLAC/Stanford}
+\author{Joshua Lande}
+
+\institute{
+With much help from Damien + Matthew\\[1em]
+SLAC/Stanford}
 \email{joshualande@gmail.com}
@@
 
-  lala
-
   \includegraphics[width=0.75\textwidth]{plots/off_pulse_pwncat1.pdf}
 
-  PWNCat1 $\rightarrow$ Selected by eye using pulsar phaseogram.
+  \begin{itemize}
+    \item PWNCat1 $\rightarrow$ Selected by eye from pulsar phaseogram.
+    \item Method validated by large scale spectral analysis
+  \end{itemize}
 \end{frame}
@@
 \begin{frame}{Another Method: CTA1-Paper II}
-  lala
 
@@
   \begin{itemize}
-    \item New idea for how to define the off pulse, proposed by Matthew
-Background
+    \item Any New Idea's for defining the off-peak?
+    \item Matthe gave me a new idea:
+      \begin{itemize}
    \item \texttt{uw.pulsar} for maximum likelihood fitting of pulsar light curves
@@
      do define the peak separations
-   \item Idea, can we use the best fit light curve to define the off peak?
+   \item Can we use the best fit light curve to define the off peak?
+  \end{itemize}
   \end{itemize}
@@
   \begin{itemize}
-   \item Define the likelihood: $\mathcal{L} = \sum_\text{photons}\text{PDF}(\text{phase})$
+   \item Define the unbinned likelihood: $\mathcal{L} = \sum_\text{photons}\text{PDF}(\text{phase})$
    \item Here, $\text{PDF}=\text{PDF}(\text{model parameters})$, so you have to pick a pulsar light curve model!
@@
 
-\begin{frame}{A more complicated Exmaple}
+\begin{frame}{Does this work for more complicated pulsars?}
+    \includegraphics[width=.85\textwidth]{plots/vela.pdf}
   \begin{itemize}
-    \item Vela:
+    \item Assymetric 2$\times$Lorenzian + Gaussian $\rightarrow$ surprisingly good fit
+      to Vela!
+    \item A fairly simple model will hopefully be able to describe all pulsars(?)
+    \item This fitting will be done already by PSRCAT2
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Hard to define off peak}
+  % Plot from /u/gl/lande/work/fermi/pwncatalog/plots_for_bari_f2f/compare_faint_bright
+
+  \includegraphics[width=.85\textwidth]{plots/compare_faint_bright.pdf}
+
+  \begin{itemize}
+    \item PSRJ0248+6021: TS$_\text{DC}$ = 70 (18M data)
+    \item Vela: TS$_\text{DC}$ = 360,000 (18M data) 
+    \item Two very different looking phaseograms
+    \item How to define the off peak emission?
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{New method to define off pulse}
+\begin{columns}
+  \column{0.5\textwidth}
+   % taken from http://da.vidr.cc/2008/09/29/creating-flowcharts-with-pgftikz-in-latex/
+  \begin{tikzpicture}[node distance=3cm]
+   \node[block] (a)                {Spectral analysis};
+   \node[block] (b)  [right of=a]  {Weighted light curve};
+   \node[block] (c)  [below of=a]  {light curve model};
+   \node[block] (d)  [right of=c]  {off-peak from model};
+   \draw[->] (a) -- (b);
+   \draw[->] (b) -- (c);
+   \draw[->] (c) -- (d);
+  \end{tikzpicture}
+
+  \column{0.5\textwidth}
+
+ \begin{itemize}
+   \item Everything until ``off-peak from model'' already done by 2nd pulsar catalog (Damien) 
+   \item If we could get this to work, it would very nicely sync PSRCAT2 + PWNCAT2 and
+     save a lot of duplicate effort
+ \end{itemize}
+\end{columns}
+\end{frame}
+
+\begin{frame}{How does it work?}
+  % /u/gl/lande/work/fermi/pwncatalog/plots_for_bari_f2f/find_off_pulse/plot_find_off_pulse.py
+
+\begin{columns}
+  \column{0.6\textwidth}
+  \includegraphics[width=1\textwidth]{plots/find_off_pulse.pdf}
+  \column{0.4\textwidth}
+  \begin{itemize}
+    \item (a) Fit the model
+    \item (b) Subtract lowest valley
+    \item (c) Guess a center
+    \item (d) Integrate until fraction of total emission (say 1\%) is included.
+    \item (e) Try many centers $\rightarrow$ pick biggest range
+  \end{itemize}
+\end{columns}
+\end{frame}
+
+\begin{frame}{2 Previous Examples}
+  \includegraphics[width=.85\textwidth]{plots/compare_faint_bright2.pdf}
+
+  \begin{itemize}
+    \item Integrate out 1\%. 
+    \item Qualittivly, works very well
+    \item For bright pulsars, 1\% integrates too far (more on this later\dots)
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{What about Edge cases/Special cases:}
+
+   \begin{columns}
+     \column{0.5\textwidth}
+  \includegraphics[width=1\textwidth]{plots/edge_case.pdf}
+     \column{0.5\textwidth}
+
+  \begin{itemize}
+   \item Left Peak is not significant
+   \item So would not be included in a pulsar model
+   \item But for defining off pulse, should we keep it?
+   \item Probably not too important since if the peak is significant, woudl not much bias a PWN analysis
+  \end{itemize}
+   \end{columns}
+\end{frame}
+
+\begin{frame}{Benefits/downsides}
+  Benefits:
+  \begin{itemize}
+    \item Algorithm Fast to run + easy to explain
+    \item Algorithm performs what we anyway do by eye anyway
+    \item While other algorithms use the off pulse to define
+      the on pulse, this method uses the peaks to
+      define where there are not peaks
+    \item By fitting a physical model, natural way to
+      remove statistical flucluations
+  \end{itemize}
+  Downsides: 
+  \begin{itemize}
+    \item dependent upon a model of the phaseogram
   \end{itemize}
@@
 
+\begin{frame}{Determine a second off pulse?}
+  \begin{itemize}
+    \item For many pulsars (e.g. Vela), bridge emission between two peaks:
+    \item For others, could be good second off-peak region to include.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Look at high energy?}
+  \begin{itemize}
+    \item Is this conservative enough?
+    \item Could the peaks be wider at high energy?
+    \item Or new peacks at high energy?
+    \item As a cross check, should we refit + look for new peaks above 1GeV?
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{What about very bright pulsars:}
+
+   * 1% of Vela is a lot of source!
+   * Should the containment be a function of source brightness?
+   * Ideas for containment = 0.01 * (100/TSdc)
+      * For vela, TSdc=… so contai
+   * Show Vela integrates to 0.01, 0.01 percent, etc.
+   * Make a plot of these issues.
+   * What about linear decrease: containment.
+\end{frame}
+
+\begin{frame}{Conclusion}
+  \begin{itemize}
+  \item Real test will be how this performs on 108 pulsars + 30 months of data
+  \item All code is avalible in \texttt{uw.pulsar.lc\_off\_peak}
+  \end{itemize}
+\end{frame}
+
 \end{document}

### 2011-10-15 presentations/pwncat2/lande_2011_bari_f2f/lande_2011_bari_f2f.tex
better talk

@@
     \item Two very different looking phaseograms
-    \item How to define the off peak emission?
+    \item How to define the off peak consistently for all pulsars?
   \end{itemize}
@@
   \begin{tikzpicture}[node distance=3cm]
-   \node[block] (a)                {Spectral analysis};
-   \node[block] (b)  [right of=a]  {Weighted light curve};
-   \node[block] (c)  [below of=a]  {light curve model};
-   \node[block] (d)  [right of=c]  {off-peak from model};
+   \node[block] (a)               {Phase Ft1};
+   \node[block] (b)  [right of=a] {Spectral analysis};
+   \node[block] (c)  [below of=a]  {Weighted light curve};
+   \node[block] (d)  [right of=c]  {light curve model};
+   \node[block] (e)  [below of=c]  {off-peak from model};
+   \node[block] (f)  [right of=e]  {Science!};
    \draw[->] (a) -- (b);
@@
    \draw[->] (c) -- (d);
+   \draw[->] (d) -- (e);
+   \draw[->] (e) -- (f);
   \end{tikzpicture}
@@
     \item (c) Guess a center
-    \item (d) Integrate until fraction of total emission (say 1\%) is included.
+    \item (e) Integrate until fraction of total emission (say 1\%) is included.
     \item (e) Try many centers $\rightarrow$ pick biggest range
@@
    \item But for defining off pulse, should we keep it?
-   \item Probably not too important since if the peak is significant, woudl not much bias a PWN analysis
+   \item Probably not too important since if the peak is not significant, it would not much bias a PWN analysis
   \end{itemize}
@@
 
-\begin{frame}{Benefits/downsides}
-  Benefits:
+\begin{frame}{Benefits}
   \begin{itemize}
-    \item Algorithm Fast to run + easy to explain
-    \item Algorithm performs what we anyway do by eye anyway
     \item While other algorithms use the off pulse to define
@@
       define where there are not peaks
-    \item By fitting a physical model, natural way to
-      remove statistical flucluations
-  \end{itemize}
-  Downsides: 
-  \begin{itemize}
-    \item dependent upon a model of the phaseogram
+    \item Algorithm Fast to run + easy to explain
+    \item Algorithm performs what we anyway do by eye 
+    \item Algoirthm indepdnet of spectral or spatial assumption about background model 
+    \item Personally, I believe that pickign the off pulse
+      always requires subjectivly deciding where you think the peaks are.
+    \item By fitting a model, you make explicity what you are assuming.
   \end{itemize}
@@
 
+\begin{frame}{How Far to Integrate}
+
+\begin{columns}
+  \column{0.7\textwidth}
+
+  \includegraphics[width=1\textwidth]{plots/how_far_to_integrate.pdf}
+  \column{0.3\textwidth}
+  \begin{itemize}
+    \item   Top is Vela (TS$_\text{DC}$ = 360,000
+    \item Bottom is PSR J0742-2822 (TS$_\text{DC}$ = 27
+    \item 1\% of Vela is too much
+    \item 0.1\$ of PSR J0742-2822 is too little
+  \end{itemize}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Scale Contamination with energy?}
+
+  \begin{itemize}
+    \item Should the Contaminationbe a function of TS$_\text{DC}$?
+    \item Ideas:
+      \begin{equation}
+        \text{contamination} = 0.01 \times \left(\frac{\text{TS}_\text{DC}}{100}\right)^{-\tfrac{1}{4}}
+      \end{equation}
+    \item TS$_\text{DC}=100$ $\rightarrow$ Contamination = 1\%
+    \item TS$_\text{DC}=1\times 10^4$ $\rightarrow$ Contamination = 0.01\%
+    \item Preliminary testing looks good
+    \item Best formula requires more work\dots
+  \end{itemize}
+\end{frame}
+
 \begin{frame}{Determine a second off pulse?}
+  \begin{columns}
+    \column{0.6\textwidth}
+    \includegraphics[width=1\textwidth]{plots/second_off_pulse_a.pdf}
+    \column{0.4\textwidth}
     \begin{itemize}
       \item For many pulsars (e.g. Vela), bridge emission between two peaks:
-    \item For others, could be good second off-peak region to include.
+      \item For others, could be second off-peak region 
+      \item In PWNCAT1, only one had two ranges (PSRJ2032+4127)
+      \item General method to pick second range?
     \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Determine a second off pulse? (cont)}
+  \begin{columns}
+    \column{0.6\textwidth}
+    \includegraphics[width=1\textwidth]{plots/second_off_pulse_b.pdf}
+    \column{0.4\textwidth}
+    \begin{itemize}
+      \item Select second largest off peak region if:
+      \item Peak in second range $>$ first range/4
+      \item poisson likelihodo of getting second counts assuming first counts is > 5\%
+      \item works here, not in other cases
+      \item Method needs work
+    \end{itemize}
+  \end{columns}
 \end{frame}
@@
   \begin{itemize}
-    \item Is this conservative enough?
+    \item Is this method conservative enough?
     \item Could the peaks be wider at high energy?
-    \item Or new peacks at high energy?
+    \item Or new peaks that are hard and only significant at high energy?
     \item As a cross check, should we refit + look for new peaks above 1GeV?
+    \item This question is general to any method to find off peak
   \end{itemize}
-\end{frame}
-
-\begin{frame}{What about very bright pulsars:}
-
-   * 1% of Vela is a lot of source!
-   * Should the containment be a function of source brightness?
-   * Ideas for containment = 0.01 * (100/TSdc)
-      * For vela, TSdc=… so contai
-   * Show Vela integrates to 0.01, 0.01 percent, etc.
-   * Make a plot of these issues.
-   * What about linear decrease: containment.
 \end{frame}
@@
   \begin{itemize}
-  \item Real test will be how this performs on 108 pulsars + 30 months of data
+    \item Having a robust algorithm to define the off-peak will
+      be useful for a variety of science
+    \item New algorithm to define off peak using maximum likelihood
+      model fitting of the region
+    \item Preliminary testing of algoirhtm seems robust
+  \item Real test will be how this performs on 108 pulsars + 36 months of data
   \item All code is avalible in \texttt{uw.pulsar.lc\_off\_peak}

### 2011-10-29 extended_catalog/paper/extended_catalog.tex
improve MC simulations

@@
 %  * Better clarification about previous gtlike validation of extended source analysis.
+%  * Improve MC null distribution tests by using 8 bins per decade + perofrm new test with E>10GeV.
 
@@
 statistical significance of the detection.  Furthermore, because the \gtlike
-approach is computationally intensive no large-scale Monte Carlo
+approach is computationally intensive, no large-scale Monte Carlo
 simulations have been run to calculate its false detection rate.
@@
 representative livetime fraction of 0.8.  The reconstruction was performed
-using photons with energies between 1 \gev and 100 \gev 
-and the Pass~7\_V6 (P7\_V6) Source Instrument
+using the Pass~7\_V6 (P7\_V6) Source Instrument
 Response Function (IRFs, \cite{lat_on_orbit_psf}).  For each 
@@
 to fit the source as an extended source and calculate \tsext.
-
-For each set of spectral parameters, $\sim30,000$ statistically independent
+\newtext{
+This entire procedure was performed twice, once fitting in the 1 \gev
+to 100 \gev energy range and once fitting in the 10 \gev to 100 \gev
+energy range.
+
+For each set of spectral parameters, $\sim20,000$ statistically independent
 simulations were performed. For dimmer spectral models, many of the
-simulations left the source undetected ($\ts<25$)
+simulations left the source insignificant ($\ts<25$)
 and were discarded.  Table~\ref{ts_ext_num_sims}
@@
 significance.  The cumulative density of \tsext is plotted in
-Figure~\ref{ts_ext_mc} and compared to the $\chi^2_1/2$ distribution of
+Figure~\ref{ts_ext_mc_1000} and Figure~\ref{ts_ext_mc_10000} 
+and compared to the $\chi^2_1/2$ distribution of
 Equation~\ref{ts_ext_distribution}.
@@
 Our study shows broad agreement between simulations and
-Equation~\ref{ts_ext_distribution}. Nevertheless, the agreement is
-not perfect.  It should be noted that the discrepancy seems to be
-worst for softer sources where we are anyways less sensitive to
-the source's extension.  One possible reason for departures from
-Equation~\ref{ts_ext_distribution} is that \pointlike ignores energy
-dispersion which will change the PSF shape as a function of energy.
-Considering the distribution in Figure~\ref{ts_ext_mc},
-the choice of a threshold \text set to 16 (correspond to a $4\sigma$
-detection if Equation~\ref{ts_ext_distribution} strictly held) is
-reasonable despite the imperfections of the corresponding calibration.
+Equation~\ref{ts_ext_distribution}. To the extent that there is
+disagreement, the simulations tended to produce smaller than expected
+values of \tsext which would make the formal significance conservative.
+Considering the distribution in Figure~\ref{ts_ext_mc_1000} and
+Figure~\ref{ts_ext_mc_10000}, the choice of a threshold \tsext set to 16
+(correspond to a formal $4\sigma$ significance) is reasonable.
+}
 
@@
 source confusion as well as how likely it is to incorrectly reject 
-with this test that an extendd source is 
+with this test that an extended source is 
 spatially extended.  All sources were simulated using
@@
 pywcsgrid2, an open-source plotting package for
-Python\footnote{http://leejjoon.github.com/pywcsgrid2/}. The authors acknowledge the
-use of HEALPix\footnote{http://healpix.jpl.nasa.gov/} \citep{healpix}.
+Python\footnote{\url{http://leejjoon.github.com/pywcsgrid2/}}. The authors acknowledge the
+use of HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.
 
@@
 \clearpage
-\begin{deluxetable}{rrrr}
+\begin{deluxetable}{rrrrrr}
 \tabletypesize{\normalsize}
@@
 \tablehead{
-
 \colhead{Spectral Index}&
 \colhead{Flux\tablenotemark{(a)}}&
-\colhead{$N_\text{sims}$}&
-\colhead{$\langle\ts\rangle$}\\
+\colhead{$N_{1-100\gev}$}&
+\colhead{$\langle\ts\rangle_{1-100\gev}$}&
+\colhead{$N_{10-100\gev}$}&
+\colhead{$\langle\ts\rangle_{10-100\gev}$}\\
 \colhead{}&
@@
 \colhead{}&
-\colhead{}\\
+\colhead{}&
+\colhead{}&
+\colhead{}
 }
@@
 \startdata
-      1.5 &          $10^{-6}$ &           31952 &  92862 \\
-          &  $3\times 10^{-7}$ &           31962 &  22169 \\
-          &          $10^{-7}$ &           31977 &   5806 \\
-          &  $3\times 10^{-8}$ &           31991 &   1270 \\
-          &          $10^{-8}$ &           31940 &    301 \\
-          &  $3\times 10^{-9}$ &           30324 &     62 \\
+      1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
+          &          $10^{-7}$ &           19079 &   5827    &     19079   &    2258     \\
+          &  $3\times 10^{-8}$ &           19303 &   1276    &     19303   &     541     \\
+          &          $10^{-8}$ &           19385 &    303    &     19381   &     142     \\
+          &  $3\times 10^{-9}$ &           18694 &     62    &     12442   &      43     \\
       \hline
-        2 &          $10^{-6}$ &           31872 &  22067 \\
-          &  $3\times 10^{-7}$ &           31890 &   4898 \\
-          &          $10^{-7}$ &           31858 &   1097 \\
-          &  $3\times 10^{-8}$ &           31632 &    236 \\
-          &          $10^{-8}$ &           27491 &    103 \\
+        2 &          $10^{-6}$ &           18760 &  22101    &     18760   &    3033     \\
+          &  $3\times 10^{-7}$ &           18775 &   4913    &     18775   &     730     \\
+          &          $10^{-7}$ &           18804 &   1170    &     18803   &     192     \\
+          &  $3\times 10^{-8}$ &           18836 &    224    &     15256   &      50     \\
+          &          $10^{-8}$ &           17060 &     50    &   \nodata   & \nodata     \\
       \hline
-      2.5 &          $10^{-6}$ &           31822 &   4706 \\
-          &  $3\times 10^{-7}$ &           31822 &    889 \\
-          &          $10^{-7}$ &           31169 &    176 \\
-          &  $3\times 10^{-8}$ &           21591 &     41 \\
+      2.5 &  $3\times 10^{-6}$ &           18597 &  19036    &     18597   &     786    \\
+          &          $10^{-6}$ &           18609 &   4738    &     18608   &     208    \\
+          &  $3\times 10^{-7}$ &           18613 &    954    &     15958   &      53    \\
+          &          $10^{-7}$ &           18658 &    203    &   \nodata   & \nodata    \\
+          &  $3\times 10^{-8}$ &           14072 &     41    &   \nodata   & \nodata    \\
       \hline                                                
-      3   &          $10^{-6}$ &           31763 &    929 \\
-          &  $3\times 10^{-7}$ &           31665 &    161 \\
-          &          $10^{-7}$ &           19271 &     40 \\
+        3 &          $10^{-5}$ &           18354 &  19466    &     18354   &     215    \\
+          &  $3\times 10^{-6}$ &           18381 &   4205    &     15973   &      54    \\
+          &          $10^{-6}$ &           18449 &    966    &   \nodata   & \nodata    \\
+          &  $3\times 10^{-7}$ &           18517 &    174    &   \nodata   & \nodata    \\
+          &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
 \enddata
 
-\tablenotetext{(a)}{Integral 1 \gev to 100 \gev flux.}
+\tablenotetext{(a)}{Integral 100 \mev to 100 \gev flux.}
 
 \tablecomments{
+\newtext{
     A list of the spectral models of the simulated point-like sources
@@
     also tabulated.  The models span representative spectral parameters.
+    }
 }
@@
     \caption{
-    Distribution of the test statistic for the extension test.
+    \newtext{
+    Distribution of the test statistic for the extension test when fitting
+    the sources in the 1 GeV to 100 GeV energy range.
     The four plots
@@
     density function of Equation~\ref{ts_ext_distribution}.
-    }\label{ts_ext_mc}
+    }
+    }\label{ts_ext_mc_1000}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{mc_plots/ts_ext_emin_10000_color.eps}
+    \else
+    \plotone{mc_plots/ts_ext_emin_10000_bw.eps}
+    \fi
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
+    \caption{
+    \newtext{
+    The same plot as Figure~\ref{ts_ext_mc_10000} but fitting in the 10 \gev to 100 \gev energy 
+    range.
+    }
+    }\label{ts_ext_mc_10000}
   \end{figure}

### 2011-11-02 extended_catalog/paper/extended_catalog.tex
updating text

@@
 
-% New text (from v3.0 to v?.?):
-%  * Better clarification about previous gtlike validation of extended source analysis.
-%  * Improve MC null distribution tests by using 8 bins per decade + perofrm new test with E>10GeV.
+% New text (from v3.0 to v4.0):
+%  * Improve MC null distribution tests by using 8 bins per decade.
+%  * New study of null hypothesis distribution fitting only above E>10GeV.
+%  * Regenerate source confusion plot to show TS_ext-TS2pts
+%  * Remove figure 8 from draft v3.0  (the one describing the spectral index difference of the two point 
+%    source fit of extended sources) since everybody asked me to.
+%  * Rerun of agn analysis to fix sources that failed to converge + using 8bins per decade + using 2FGL skymodel.
+%  * For new source anlaysis:
+%  ** use 8 insetad of 4 bins per decade
+%  ** Freeze instead of delete insignificant 2FGL sources. This should make the text clearer because sources are only
+%     deleted if they are part of the extended emission.
+%  ** Add two nearby point-like sources to analysis of HESS J1632-478.
+%  ** Redo analysis of RX J1713 to be E>10GeV to avoid issues of diffuse uncertainty at low energy.
+%  * Better clarification about previous gtlike validation of extended source analysis + Citation of Francesco's work.
 
@@
 
-\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight
-Data}
+\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data}
 \shorttitle{Search for Extended LAT Sources}
@@
 \author{
-J.~Lande\altaffilmark{2,1}, 
-S.~Funk\altaffilmark{2,1}, 
-M.~Ackermann\altaffilmark{3,1}, 
-%A.~Allafort\altaffilmark{2},
-%M.-H.~Grondin\altaffilmark{53},
-% Keith Bechtol
-% Marshall Roth?
-% Marianne Lemoine-Goumard
-% Francesco Giordano
-% Toby Burnett
-% Jean Ballet
-% Matthew Kerr
-\ldots
-\altaffiltext{1}{Corresponding authors: M.~Ackermann, markus.ackermann@desy.de; S.~Funk, funk@slac.stanford.edu; J.~Lande, joshualande@gmail.com.}
-\altaffiltext{2}{W.
+J.~Lande\altaffilmark{1,2}, 
+M.~Ackermann\altaffilmark{3,4}, 
+A.~Allafort\altaffilmark{1}, 
+K.~Bechtol\altaffilmark{1}, 
+T.~H.~Burnett\altaffilmark{5}, 
+A.~Drlica-Wagner\altaffilmark{1}, 
+S.~Funk\altaffilmark{1,6}, 
+F.~Giordano\altaffilmark{7,8}, 
+M.-H.~Grondin\altaffilmark{9,10}, 
+M.~Kerr\altaffilmark{1}, 
+M.~Lemoine-Goumard\altaffilmark{11,12}
+}
+\altaffiltext{1}{W.
 W.
 Hansen Experimental Physics Laboratory, Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics and SLAC National Accelerator Laboratory, Stanford University, Stanford, CA 94305, USA}
+\altaffiltext{2}{email: joshualande@gmail.com}
 \altaffiltext{3}{Deutsches Elektronen Synchrotron DESY, D-15738 Zeuthen, Germany}
-}
+\altaffiltext{4}{email: markus.ackermann@desy.de}
+\altaffiltext{5}{Department of Physics, University of Washington, Seattle, WA 98195-1560, USA}
+\altaffiltext{6}{email: funk@slac.stanford.edu}
+\altaffiltext{7}{Dipartimento di Fisica ``M. Merlin" dell'Universit\`a e del Politecnico di Bari, I-70126 Bari, Italy}
+\altaffiltext{8}{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70126 Bari, Italy}
+\altaffiltext{9}{Max-Planck-Institut f\"ur Kernphysik, D-69029 Heidelberg, Germany}
+\altaffiltext{10}{Landessternwarte, Universit\"at Heidelberg, K\"onigstuhl, D 69117 Heidelberg, Germany}
+\altaffiltext{11}{Universit\'e Bordeaux 1, CNRS/IN2p3, Centre d'\'Etudes Nucl\'eaires de Bordeaux Gradignan, 33175 Gradignan, France}
+\altaffiltext{12}{Funded by contract ERC-StG-259391 from the European Community}
 
@@
 and the Cygnus Loop
-\citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, three 
-PWNe were detected as being extended: MSH\,15$-$52, Vela~X, and
+\citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, 
+three extended PWN have been detected: MSH\,15$-$52, Vela~X, and
 HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
-close-by galaxies, the Large and Small Magellanic Clouds, and one
-radio galaxy, Centarus A, were spatially resolved at \gev energies
+nearby galaxies, the Large and Small Magellanic Clouds, and one
+radio galaxy, Centaurus A, were spatially resolved at \gev energies
 \citep{lmc,smc,cen_a_lat}.  A number of additional sources detected
@@
 \citep{hess_plane_survey}.  In fact, within our Galaxy only very few
-sources detected at \tev energies (most notably the $\gamma$-ray binaries
+sources detected at \tev energies, most notably the $\gamma$-ray binaries
 LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI},
-HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
+HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes},
 have no detectable extension.  High-energy $\gamma$-rays from
@@
 (20 \mev to $>300$ \gev), wide field of view ($\sim 2.4$ sr), and large
-effective area ($\sim 8000\ \cm^2$ at $>1 \gev$) 
+effective area ($\sim 8000\ \cm^2$ at $>1$ \gev) 
 Additional information about the performance of the LAT can be found in
@@
 
-\subsection{The \pointlike Package}
+\subsection{Modeling Extended Sources in the \pointlike Package}
 
@@
 in a region.  The extension of a source can be modeled by a geometric
-shape (e.g. a disk or a two-dimensional Gaussian) and the source's position, extension,
-and spectrum can be simultaneously fit.
+shape (e.g. a disk or a two-dimensional Gaussian) and the position, extension,
+and spectrum of the source
+can be simultaneously fit.
 
@@
 the statistical significance of the detection of extension of a source.
-To avoid projection effects, the source's longitude and latitude are
-not directly fit but instead the source's displacement in a rotated
+To avoid projection effects, the longitude and latitude 
+of the source are
+not directly fit but instead the displacement of the source in a rotated
 reference frame.
@@
 the LAT detection threshold (defined as the 1 \gev to 100 \gev flux at
-which $\langle\tsext\rangle=16$) depends less strongly on the source's
-spectral index. 
+which $\langle\tsext\rangle=16$) depends less strongly on the 
+spectral index of the source. 
 The index dependence of the detection threshold is
@@
 \end{equation} 
-\tsinc cannot be quantitatively compared to \tsext using a
-simple likelihood ratio test to evaluate which model
-is 
-significantly better because the models are not nested
-\citep{statistics_with_care}.  Even though the comparison of \tsext
-with \tsinc is not a calibrated test, $\tsext>\tsinc$ indicates that
-the likelihood for the extended source hypothesis is higher than for
-two point-like sources and we only consider a source to be extended
-if $\tsext>\tsinc$.
+\tsinc cannot be quantitatively compared to \tsext using a simple
+likelihood ratio test to evaluate which model is significantly better
+because the models are not nested \citep{statistics_with_care}.
+Even though the comparison of \tsext with \tsinc is not a calibrated
+test, $\tsext>\tsinc$ indicates that the likelihood for the extended
+source hypothesis is higher than for two point-like sources and we only
+consider a source to be extended if $\tsext>\tsinc$.
 
@@
 with extensions varying
-up to $1\degree$.  Figure~\ref{confusion_plot}a shows 
-the distribution of \tsinc and \tsext as a
+up to $1\degree$.  
+\newtext{
+Figure~\ref{confusion_plot}a shows 
+the distribution of $\tsext-\tsinc$ as a
 function of the simulated extension of the source
 for 200 statistically independent simulations.
-
-Figure~\ref{confusion_plot}c shows the same analysis but when
-fitting simulations of two point-like sources each with half of the
-flux of the spatially extended source and with the same spectral index
-as the extended source.
-Finally, figure~\ref{confusion_plot}e shows the same analysis with each
-point-like source having the same flux but different spectral indices.
-One point-like source had a spectral index of 1.5 and the other an index
-of 2.5.
+}
+
+Figure~\ref{confusion_plot}c shows the same plot but when fitting
+simulations of two point-like sources each with half of the flux of
+the spatially extended source and with the same spectral index as the
+extended source.  Finally, figure~\ref{confusion_plot}e shows the same
+plot with each point-like source having the same flux but different
+spectral indices.  One point-like source had a spectral index of 1.5
+and the other an index of 2.5.
 
@@
 increase in likelihood
-when fitting the extended source as two point-like sources.
+when fitting the extended source as two point-like sources ($\tsinc\sim\tsext$).
 This is because although
@@
 did a better job at separating the distribution of \tsinc and \tsext
-and found that \tsinc was typically much larger than \tsext.
+and found that \tsinc was larger than \tsext.
 This is because the one additional extension parameter is less able to
@@
 
-Finally, figure~\ref{index_difference} shows the absolute value of the
-difference of the fit spectral indices for the case of fitting simulated
-spatially extended sources as two point-like sources. The plot compares
-the fit in the 1 \gev to 100 \gev energy range and in the 10 \gev to
-100 \gev energy range. An error on the difference in spectral index is
-calculated by adding in quadrature the statistical errors on the spectral
-indices.  This plot shows that there can be a large difference in the
-spectral index of the two fit point-like sources which is often greater
-than the statistical errors on the difference in spectral index. This is
-because the fit values the errors on an incorrect model are not expected
-to be meaningful. Therefore, the difference in spectral index when fitting
-an extended source candidate as two point-like sources can not be easily
-used to help determine whether a source is actually spatially extended
-instead of being the emission of two nearby point-like sources.
-
-From this Monte Carlo study, we can see the limits of a LAT analysis of
-spatially extended sources.  Section~\ref{monte_carlo_validation} showed
-that we have a statistical test that finds when a LAT source is
-not well described by the PSF. 
-But this test does
-not uniquely prove that the emission originates from spatially extended
-emission instead of from multiple unresolved sources.  Demanding that
-$\tsext>\tsinc$ is a powerful second test to avoid cases of simple
-confusion of two point-like sources. But it could always be the
-case that an extended source candidate is actually the superposition
-of multiple point-like or extended sources that could be resolved
-with deeper observations of the region.  There is nothing
-about this conclusion unique to LAT analysis, but the
-larger PSF of the LAT and the density of sources expected to be \gev emitters in
-the galactic plane makes this issue more significant for LAT analysis.
-When possible, multiwavelength information should be used to help 
-select the best model of the sky.
+From this Monte Carlo study, we can see the limits of a LAT analysis
+of spatially extended sources.  Section~\ref{monte_carlo_validation}
+showed that we have a statistical test that finds when a LAT source is
+not well described by the PSF.  But this test does not uniquely prove
+that the emission originates from spatially extended emission instead
+of from multiple unresolved sources.  Demanding that $\tsext>\tsinc$
+is a powerful second test to avoid cases of simple confusion of two
+point-like sources. But it could always be the case that an extended
+source candidate is actually the superposition of multiple point-like or
+extended sources that could be resolved with deeper observations of the
+region.  There is nothing about this conclusion unique to LAT analysis,
+but the larger PSF of the LAT and the density of sources expected to be
+\gev emitters in the galactic plane makes this issue more significant
+for LAT analysis.  When possible, multiwavelength information should be
+used to help select the best model of the sky.
 
@@
 possible residuals in the diffuse emission model, the galactic emission
-was scaled by a power-law and the isotropic component's normalization
+was scaled by a power-law and the normalization
+of the isotropic component
 was left free.  
@@
 
-Of the 885 clean AGN, we selected the 783 of these 2FGL sources which
-were significantly-detected above 1 \gev and fit each of them for extension.
-The cumulative density of \tsext for these AGN compared to the
-$\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
-is
-shown in Figure~\ref{agn_ts_ext}. 
-The \tsext distribution for AGN shows good agreement with the
-theoretical distribution, but two sources had $\tsext>10$.  One was due
-to the incorrect removal of a nearby catalog sources from
-the sky model (see
-Section~\ref{extended_source_search_method}) and the other was due to a
-failure of convergence of the point-like source hypothesis.  This result demonstrates
-that we can use \tsext as a measure of the statistical significance of
-the detection of the extension of a source.
+\newtext{
+Of the 885 clean AGN, we selected the 733 of these 2FGL sources which
+were significantly detected above 1 \gev and fit each of them for
+extension.  The cumulative density of \tsext for these AGN is compared
+to the $\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
+and is shown in Figure~\ref{agn_ts_ext}.  The \tsext distribution
+for the AGN shows reasonable agreement with the theoretical
+distribution and no AGN was found to be significantly extended
+($\tsext>16$).  The observed discrepancy from the theoretical
+distribution is likely due to small systematics
+in our model of the LAT PSF and the Galactic diffuse emission (see
+Section~\ref{systematic_errors_on_extension}).  The discrepancy could
+also in a few cases be due to confusion with a nearby undetected source.
+The overall agreement with the expected distribution demonstrates that
+we can use \tsext as a measure of the statistical significance of the
+detection of the extension of a source.
+}
 
@@
 were fit with a variety of spatial models, it is valuable to show that
-these sources are significantly extended using our systematic extension
+these sources are significantly extended using our systematic 
 method that assumed a radially-symmetric uniform surface
@@
 observed extended emission and so the dedicated LAT publications provides
-a qualitatively better model these sources.
+a qualitatively better model of these sources.
 
@@
 we fit the extension of MSH\,15$-$52 to be consistent with the published
-size but with an extension significance of \tsext=6.5.
+size but with an extension significance of \tsext=6.6.
 
@@
 extension for the Centaurus A Lobes because
-the source's emission is significantly different from a uniform
+the shape of the source is significantly different from a uniform
 radially-symmetric surface brightness profile \citep{cen_a_lat}.
@@
 templates to describe individual components of the diffuse emission.
-A similar crosscheck was used in the LAT Collaboration's analysis of 
-RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
+A similar crosscheck was used in an analysis of RX\,J1713.7$-$3946 
+by the LAT Collaboration \citep{rx_j1713_lat}.
 
@@
 
-But this is infeasible in the galactic plane where we most likely expect
+But this is infeasible in the galactic plane where we are most likely expect
 to discover new spatially extended sources.  In the galactic plane,
@@
 
-To account for these issues, we first produces a large list of
+To account for these issues, we first produced a large list of
 possibly extended sources employing a very liberal search criteria
@@
 one additional degree of freedom, this test should be very sensitive.
-On the other hand, choosing this spatial model could bias us against
+On the other hand, choosing this spatial model biases us against
 finding extended sources that are not well described by uniform emission
@@
 \gev energy range. Most of the extended sources flagged above 10 \gev were
-also flagged above 1 \gev.  Many of these situations represent multiple
+also flagged above 1 \gev and many of these situations represent multiple
 point-like 2FGL sources all fitting the same emission region. For example,
@@
 point-like sources or influence by large-scale residuals in the
-diffuse emission.  To help determine which of these fits represented
-truly extended sourced and in which of these fits the extension was
+diffuse emission.  To help determine which of these fits found
+truly extended sourced and when the extension was
 influenced by source confusion and diffuse emission, we generated a
 series of diagnostic plots.  For each candidate, we generated a map
-of the residual test statistic by adding a new source of spectral index 2 into the
+of the residual test statistic by adding a new point-like source of spectral index 2 into the
 region at each position and finding the increase in likelihood when fitting
@@
 description of the observed photons and that there is not significant
-residual in region after modeling the source as being spatially extended.
+residual in the region after modeling the source as being spatially extended.
 We also generated maps of the sum of all counts within a given distance of
@@
 For each source, we also made diffuse-emission-subtracted smoothed counts
-maps (show for IC443 in Figure~\ref{four_plots_ic443}).
+maps (shown for IC443 in Figure~\ref{four_plots_ic443}).
 
@@
 in the 1 \gev to 100 \gev energy range. Figure~\ref{example_bad_fit}
-shows a diffuse-emission-subtracted smoothed counts map around
+shows a diffuse-emission-subtracted smoothed counts map for
 this source with the best
@@
 candidates in regions that did not appear dominated by these issues and
-in regions where there was an obvious spatially extended multiwavelength
+where there was a multiwavelength
 counterpart. Because of these systematic issues, this search can not be
@@
 improved the model of the region by decided on a case by case basis which
-background point-like sources should be kept.  We kept sources that we
-believed represented physically distinct sources and we removed from the
-model of the sky sources that we believed were included in 2FGL to account
-for residual induced by not modeling the extension of the source
-and sources include in 2FGL to represent soft point-like
-sources that were not significant at higher energies.  When deciding
+background point-like sources should be kept.  We kept in our model of the sky
+sources that we
+believed represented physically distinct sources and we removed 
+sources that we believed were included in 2FGL to account
+for residual induced by not modeling the extension of the source.
+\newtext{
+Soft nearby point-like 2FGL sources that were not significant at higher energies
+were frozen to the spectrum predicted by 2FGL.
+}
+When deciding
 which background sources to keep and which to remove, we used as much as possible
@@
 % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
 
@@
 % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
+% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
 % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
 % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
-% N/A                - P72Y1287         - 2FGL J0851.7-4635
+% N/A                - P72Y1287         - 2FGL J0851.7-4635 (Vela Jr)
 
@@
 Jr. \citep{rx_j1713_lat,vela_jr_lat}
-Three of these sources were
-found when using photons with energies between 1 \gev and 100 \gev and six
+Two of these sources were
+found when using photons with energies between 1 \gev and 100 \gev and seven
 were found when using photons with energies between 10 \gev and 100 \gev.
@@
 % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-% Deleted 
-%  * P72Y1214 - 2FGL J0823.4-4305
-%  * P72Y1210 - 2FGL J0821.0-4254
 
 2FGL\,J0823.0$-$4246 was found by our search to be an extended source
-candidate in the 10 \gev to 100 \gev energy range and is spatially
+candidate in the 1 \gev to 100 \gev energy range and is spatially
 coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
@@
 $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=46.3$.  Figure~\ref{snr_seds} shows the spectrum of
+of $\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
 this source.
@@
 and references therein).  The fit extension of 2FGL\,J0823.0$-$4246
-matches well its inferred size at \gev energies.  Puppis A's distance was
+matches well its inferred size at \gev energies.  The distance of Puppis A was
 estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
@@
 2FGL\,J1627.0$-$2425c was found by our search to
-have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
-an extension significance of $\tsext=31.1$
-using photons with energies between 1 \gev and 100 \gev.  The source
+have an extension of $0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
+an extension significance of $\tsext=32.4$
+using photons with energies between 1 \gev and 100 \gev.  
 Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
@@
 
-\subsection{2FGL\,J1712.4$-$3941}
-\label{section_2FGL_J1712.4-3941}
-
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
-% New Source:
-%  * SkyDir(346.85102135118683,0.24359779858357899,SkyDir.GALACTIC),
-% Delete:
-%  * P72Y2685 - Not in 2FGL
-%  * P72Y2680 - Not in 2FGL
-%  * P72Y2689 - Not in 2FGL
-
-2FGL\,J1712.4$-$3941 was found by our search to be spatially extended using
-photons with energies between 1 \gev and 100 \gev.  This source is
-spatially coincident with the SNR RX\,J1713.7$-$3946 and was
-recently studied by the LAT collaboration in \cite{rx_j1713_lat}.
-Figure~\ref{2FGL_J1712.4-3941}a shows a smoothed counts map of the source
-and overlays \tev contours of the SNR \cite{rx_j1713_hess}.  To analyze this source,
-we used the same background source model as the recent LAT publication.
-Figure~\ref{2FGL_J1712.4-3941}b shows the source after subtracting
-these background sources.
-With this background, RX\,J1713.7$-$3946 fit to an extension of
-$0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=39.6$.
-
 \subsection{2FGL\,J0851.7$-$4635}
@@
 % (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
-% Delete:
-% * P72Y1291 - 2FGL J0853.5-4711
-% * P72Y1296 - 2FGL J0855.4-4625
-% * P72Y1274 - 2FGL J0848.5-4535
-% * P72Y1259 - 2FGL J0842.9-4721
-% * P72Y1300 - 2FGL J0858.0-4815
-% * P72Y1310 - 2FGL J0901.7-4655 
-% Modify:
-% * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.235,0.493,SkyDir.GALACTIC))
-%              (initial Position - SkyDir(265.5705,-0.0099)
 
@@
 coincident with the SNR Vela Jr. This source was recently studied by the LAT
-collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
+Collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
 map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
@@
 induced by not modeling the extension Vela Jr. and were removed
-from our model of the sky.  In addition, two further away
-sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655 were removed from
-our model of the sky because they were not significant above 10 \gev.
-
-With this model of the background, 2FGL\,J0851.7$-$4635 was found to have an
-extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ with an extension
-significance of $\tsext=87.2$.
-The LAT size matches well the \tev morphology
-of Vela Jr. 
-While fitting the extension of 2FGL\,J0851.7$-$4635, we iteratively 
-relocalized the position of the nearby point-like catalog source
-2FGL\,J0854.7$-$4501 to $(l,b)=(266\fdg24,0\fdg49)$ to better fit its
-position at high energies.
+from our model of the sky.
+
+With this model of the background, 2FGL\,J0851.7$-$4635 was found to
+have an extension of $1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
+an extension significance of $\tsext=86.8$.  The LAT size matches
+well the \tev morphology of Vela Jr.  While fitting the extension
+of 2FGL\,J0851.7$-$4635, we iteratively relocalized the position
+of the nearby point-like catalog source 2FGL\,J0854.7$-$4501 to
+$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies.
 
@@
 %   * 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138 % extended source
-% Deleted
-%  *P72Y2490 - 2FGL J1620.6-5111c
-%  *P72Y2487 - 2FGL J1619.7-5040c
-%  *P72Y2496 - 2FGL J1622.8-5006
 
 2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to be
-extended source candidates in the 10 \gev to 100 \gev energy range. They
-are less than $1\degree$ away from each other and needed to be analyzed
+extended source candidates in the 10 \gev to 100 \gev energy range. Because
+they are less than $1\degree$ away from each other, they needed to be analyzed
 simultaneously.  2FGL\,J1615.0$-$5051 is spatially coincident with
@@
 by not modeling the extension of 2FGL\,J1615.2$-$5138 and removed
-it from our model of the sky.  There are two further away sources
-2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c that were removed from
-our model because they were not significant at energies above 10 \gev.
+it from our model of the sky.
 
@@
 2FGL\,J1615.0$-$5051 was found to have an extension of
-$0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$ with an extension significance
-of \tsext=16.3.  
+$0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ with an extension significance
+of \tsext=16.7.  
 2FGL\,J1615.2$-$5138 was found
- to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
-with an extension significance of \tsext=48.0.  
+ to have an extension of $0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
+with an extension significance of \tsext=46.5.
 To test for the possibility that
@@
 
-2FGL\,J1615.0$-$5051's \tev counterpart HESS\,J1616$-$508's was fit
+The \tev counterpart of 2FGL\,J1615.0$-$5051 was fit
 with a radially-symmetric Gaussian surface brightness profile to have an
@@
 containment radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the
-LAT size $\rsixeight=0\fdg27\pm0\fdg03$.  Figure~\ref{hess_seds} shows
+LAT size $\rsixeight=0\fdg26\pm0\fdg03$.  Figure~\ref{hess_seds} shows
 that the spectrum of 2FGL\,J1615.0$-$5051 at \gev energies connects to
@@
 $\rsixeight=0\fdg35\pm0\fdg03$ and $0\fdg23\pm0\fdg03$,  consistent with
-the LAT size $\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds}
+the LAT size $\rsixeight=0\fdg34\pm0\fdg03$.  Figure~\ref{hess_seds}
 shows that the spectrum of 2FGL\,J1615.2$-$5138 at \gev energies connects
@@
 % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-% Kept:
-% * P72Y2539 - 2FGL J1632.4-4820c
-% Deleted
-% * P72Y2535 - 2FGL J1631.7-4720c
-% * P72Y2556 - 2FGL J1638.0-4703c
-% * P72Y2528 - 2FGL J1630.2-4752
-% * P72Y2543 - 2FGL J1634.4-4743c
-% * P72Y2521 - 2FGL J1628.1-4857c
-% * P72Y2527 - 2FGL J1630.1-4615
-% * P72Y2562 - 2FGL J1639.8-4921c
-% Modify
-% * P72Y2547 - 2FGL J1635.4-4717c - SkyDir(337.230,0.346,SkyDir.GALACTIC)
-%              (initial Position  - SkyDir(337.1396,0.1433)
-% * P72Y2550 - 2FGL J1636.3-4740c - SkyDir(336.968,-0.066,SkyDir.GALACTIC))
-%              (initial Position  - SkyDir(336.9639,-0.236)
 
@@
 map of this source and overlays \tev contours of HESS\,J1632$-$478
-\citep{hess_plane_survey}.  The figure shows that there are three nearby
-point-like 2FGL sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
-2FGL\,J1634.4$-$4743c that correlate with the extended \tev source
-but that do appear to be physically distinct sources.
-We concluded that they
-were included in 2FGL to account for
-residual induced by not modeling the extension of 
-2FGL\,J1632.4$-$4753c
-and removed them from our model of the sky.
-We also removed four
-farther away sources 2FGL\,J1638.0$-$4703c, 
-2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
-were not significant above 10 \gev.
-
-Our sky model therefore included three nearby sources 2FGL J1632.4-4820c,
-2FGL J1635.4-4717c, 2FGL J1636.3-4740c and which do not correlate with
-the extended \tev emission of HESS\,J1632$-$478 as well
-as 
-the extended source candidate 2FGL\,J1632.4$-$4753c.
-Figure~\ref{1FGL_J1632.9-4802c}b shows the same region with these
-background sources subtracted.
-With this model, 2FGL\,J1632.4$-$4753c was found to have an
-extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ with an extension
-significance of \tsext=64.5.  While fitting the extension
-of 2FGL\,J1632.4$-$4753c, we iteratively relocalized 2FGL\,J1635.4$-$4717c
-to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3$-$4740c to
-$(l,b)=(336\fdg97,-0\fdg07)$.
-
-H.E.S.S measured a 
-extension of $\sigma=0\fdg21\pm0\fdg05$ and $0\fdg06\pm0\fdg04$ along the
-semi-major and semi-minor axes when fitting 
-HESS\,J1632$-$478 
-with an
-elliptical 2D Gaussian surface brightness profile.  This corresponds to a 68\%
-containment size $\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$
-along the semi-major and semi-minor axis, consistent with
-the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
-shows that the spectrum of 
-2FGL\,J1632.4$-$4753c at \gev energies connects to
-the spectrum of HESS\,J1632$-$478 at \tev energies.
+\citep{hess_plane_survey}.  There are five nearby point-like 2FGL
+sources that appear to  represent physically distinct sources: 2FGL
+J1630.2-4752, 2FGL J1631.7-4720c, 2FGL J1632.4-4820c, 2FGL J1635.4-4717c,
+2FGL J1636.3-4740c that were included in our background model.  On the
+other hand, one point-like 2FGL source 2FGL\,J1634.4$-$4743c  correlates
+with the extended \tev source and does not appear to be physically
+separate.  We therefore removed this source from our model of the
+background.  Figure~\ref{1FGL_J1632.9-4802c}b shows the same region with
+the background sources subtracted.  With this model, 2FGL\,J1632.4$-$4753c
+was found to have an extension of $0\fdg35\pm0\fdg04_\stat\pm0\fdg02_\sys$
+with an extension significance of \tsext=26.9.  While fitting the
+extension of 2FGL\,J1632.4$-$4753c, we iteratively relocalized
+2FGL\,J1635.4$-$4717c to $(l,b)=(337\fdg23,0\fdg35)$ and
+2FGL\,J1636.3$-$4740c to $(l,b)=(336\fdg97,-0\fdg07)$.
+
+H.E.S.S measured a extension of $\sigma=0\fdg21\pm0\fdg05$ and
+$0\fdg06\pm0\fdg04$ along the semi-major and semi-minor axes when
+fitting HESS\,J1632$-$478 with an elliptical 2D Gaussian surface
+brightness profile.  This corresponds to a 68\% containment size
+$\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$ along
+the semi-major and semi-minor axis, consistent with the LAT size
+$\rsixeight=0\fdg29\pm0\fdg04$.  Figure~\ref{hess_seds} shows that
+the spectrum of 2FGL\,J1632.4$-$4753c at \gev energies connects to the
+spectrum of HESS\,J1632$-$478 at \tev energies.
 
@@
 
+\subsection{2FGL\,J1712.4$-$3941}
+\label{section_2FGL_J1712.4-3941}
+
+% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
+
+2FGL\,J1712.4$-$3941 was found by our search to be spatially extended
+using photons with energies between 1 \gev and 100 \gev.  This source
+is spatially coincident with the SNR RX\,J1713.7$-$3946 and was
+recently studied by the LAT Collaboration in \cite{rx_j1713_lat}.
+To avoid issues related to uncertainties in the nearby Galactic
+diffuse emission at lower energy, we restricted our analysis only
+to energies above 10 \gev.  Figure~\ref{2FGL_J1712.4-3941} shows a
+smoothed counts map of the source. Above 10 \gev, the \gev emission
+nicely coorelates with the \tev contours of RX\,J1713.7$-$3946
+\cite{rx_j1713_hess} and 2FGL\,J1712.4$-$3941 fit to an extension of
+$0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with an extension significance
+of $\tsext=38.5$.
+
 \subsection{2FGL\,J1837.3$-$0700c}
@@
 % 1FGL J1837.5-0659c - P72Y2986 - 2FGL J1837.3-0700c
-
-% Delete:
-% * P72Y2982 - Not in 2FGL
-% * P72Y2979 - 2FGL J1835.5-0649 - SkyDir(25.0503,0.3894)
-% * P72Y2993 - 2FGL J1839.0-0539 - SkyDir(26.4904,0.1632)
-
-% Modify:
-% * P72Y2974 - 2FGL J1834.7-0705c - SkyDir(24.716,0.500,SkyDir.GALACTIC)
-%              (initial Position  - SkyDir(25.0953,-0.0887)
-% * P72Y2985 - 2FGL J1836.8-0623c - SkyDir(25.574,0.320,SkyDir.GALACTIC)
-%              (initial Position  - SkyDir(25.5925,0.3103)
-% * P72Y2994 - 2FGL J1839.3-0558c - SkyDir(26.080,0.229,SkyDir.GALACTIC)
-%              (initial Position  - SkyDir(26.2301,-0.0394)
 
@@
 not modeling the extension of this source and removed it from our model
-of the sky.  We also removed from our model of the sky the farther away
-point-like 2FGL source 2FGL\,J1839.0-0539 because it was not significant
-with energies above 10 \gev.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
+of the sky.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
 counts map of this region after subtracted these background sources.
@@
 With this model, 2FGL\,J1837.3$-$0700c was found to have an
-extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an extension
-significance of $\tsext=18.8$. 
+extension of $0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with an extension
+significance of $\tsext=18.5$. 
 While fitting the extension of 2FGL\,J1837.3$-$0700c,
-we iteratively relocalized the three nearest
+we iteratively relocalized the two closest
 background sources along with the extension of 2FGL\,J1837.3$-$0700c but
@@
 moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
-to $(l,b)=(25\fdg57,0\fdg32)$, and 2FGL\,J1839.3$-$0558c moved to
-$(l,b)=(26\fdg08,0\fdg23)$. With this best fit sky model, we tested for
+to $(l,b)=(25\fdg57,0\fdg32)$. With this best fit sky model, we tested for
 source confusion by fitting the source instead as two point-like sources.
@@
 size is not significantly different from the LAT 68\% containment
-radius of $\rsixeight=0\fdg29\pm0\fdg07$ (less than $2\sigma$).
+radius of $\rsixeight=0\fdg27\pm0\fdg07$ (less than $2\sigma$).
 Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1837.3$-$0700c
@@
 AX\,J1838.0$-$0655 \citep{hard_x-ray_asca}.  This source was discovered
-by RXTE to be a pulsar sufficiently luminous to power the \tev emission
+by RXTE to be a pulsar (PSR J1838-0655) 
+sufficiently luminous to power the \tev emission
 and was resolved by \chandra to be a bright point-like source surrounded
 by a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069}. The
-$\gamma$-ray emission may be powered by this pulsar.  
-2FGL\,J1837.3$-$0700c's hard spectral index and spatial extension
-disfavor a pulsar origin of the LAT emission and suggest instead
-that the \gev and \tev emission both originate from the pulsar's wind.
-There is another
+$\gamma$-ray emission may be powered by this pulsar.  The hard spectral
+index and spatial extension of 2FGL\,J1837.3$-$0700c disfavor a pulsar
+origin of the LAT emission and suggest instead that the \gev and \tev
+emission both originate from the pulsar's wind.  There is another
 X-ray point-like source AX\,J1837.3$-$0652 near HESS\,J1837$-$069
@@
 % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-% Delete:
-% * P72Y3282 - 2FGL J2019.1+4040
-% * P72Y3292 - 2FGL J2022.8+3843c
-% * P72Y3287 - 2FGL J2020.0+4159
-% * P72Y3262 - 2FGL J2013.8+4115c
-% * P72Y3260 - 2FGL J2012.4+3955c
-% New source
-%  * SkyDir(78.854,2.670,SkyDir.GALACTIC)
-
-The source 2FGL\,J2021.5+4026 is coincident
-with 2CG\,078+01 and 3EG\,J2020+4017
-\citep{second_cos_b_catalog,third_egret_catalog} and also with
-the $\gamma$-Cygni SNR. This $\gamma$-ray source has been speculated
+
+The source 2FGL\,J2021.5+4026 is coincident with 2CG\,078+01 and
+3EG\,J2020+4017 \citep{second_cos_b_catalog,third_egret_catalog} and also
+with the $\gamma$-Cygni SNR. This $\gamma$-ray source has been speculated
 to originate from the interaction of accelerated particles in the SNR
-with dense molecular clouds \citep{pollock_1985,gaisser_1998},
-but this association was disfavored when the LAT \gev emission
-from this source was detected to be pulsed (PSR\,J2021+4026,
-\cite{first_lat_pulsar_cat}).  This pulsar was also been observed by
-AGILE \citep{gamma_cygni_agile}.
-
-Looking at the same region at energies above 10 \gev, the pulsar
-is no longer significant but we instead 
-found in our search an extended source candidate.
-Figure~\ref{1FGL_J2020.0+4049} shows a counts map of this source and
-overlays radio contours of $\gamma$-Cygni from the Canadian Galactic
-Plane Survey \citep{canadian_galactic_plane_survey}.  There is good
-spatial overlap between the SNR and the \gev emission.
-
-There is
-a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
+with dense molecular clouds \citep{pollock_1985,gaisser_1998}, but this
+association was disfavored when the LAT \gev emission from this source
+was detected to be pulsed (PSR\,J2021+4026, \cite{first_lat_pulsar_cat}).
+This pulsar was also been observed by AGILE \citep{gamma_cygni_agile}.
+
+Looking at the same region at energies above 10 \gev, the pulsar is
+no longer significant but we instead found in our search an extended
+source candidate.  Figure~\ref{1FGL_J2020.0+4049} shows a counts map
+of this source and overlays radio contours of $\gamma$-Cygni from the
+Canadian Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
+There is good spatial overlap between the SNR and the \gev emission.
+
+There is a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
 emission of $\gamma$-Cygni and does not appear to represent a physically
-distinct source.  We concluded that it was included in 2FGL to account for
-residual induced by not modeling the extension of $\gamma$-Cygni 
-and removed it from our model of the sky.  We also removed from
-our model of the sky the four farther away sources 2FGL\,J2022.8+3843c,
-2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c, and 2FGL\,J2012.4+3955c because
-they were not significant when observed at energies above 10 \gev.
-Furthermore, we decided to add to our region an additional point-like
-source at $(l,b)=(78\fdg85,2\fdg67)$.  Although this source is not very
-significant ($\ts=13.5$ in the 10 \gev to 100 \gev energy range), its
-location is outside the 
-multiwavelength
-contours of $\gamma$-Cygni and
-modeling it improved the connection of the best fit extension
-with the 
-multiwavelength
-contours of $\gamma$-Cygni. Nevertheless,
-the overall spatial and spectral characteristics of the source were not
-significantly changed by the presence of this source.
-
-With this model, 2FGL\,J2021.5+4026 was found to have an extension of
-$0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=116.4$.  
-Figure~\ref{snr_seds} shows its spectrum.  The inferred size of this
-source at \gev energies well matches the radio size of $\gamma$-Cygni.
-Milagro detected a $4.2\sigma$ excess at energies $\sim 30$ \tev
-from this location \citep{lat_bsl,milagro_bright_source_list}.
-Veritas also detected an extended source VER\,J2019+407 coincident
-with the SNR above 200 \gev and suggested that the \tev emission could be a
-shock-cloud interaction in $\gamma$-Cygni \citep{veritas_gamma_cygni}.
+distinct source.  We concluded that it was included in 2FGL to account
+for residual induced by not modeling the extension of $\gamma$-Cygni and
+removed it from our model of the sky.  With this model, 2FGL\,J2021.5+4026
+was found to have an extension of $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
+with an extension significance of $\tsext=116.4$.  Figure~\ref{snr_seds}
+shows its spectrum.  The inferred size of this source at \gev energies
+well matches the radio size of $\gamma$-Cygni.  Milagro detected
+a $4.2\sigma$ excess at energies $\sim 30$ \tev from this location
+\citep{lat_bsl,milagro_bright_source_list}.  Veritas also detected an
+extended source VER\,J2019+407 coincident with the SNR above 200 \gev
+and suggested that the \tev emission could be a shock-cloud interaction
+in $\gamma$-Cygni \citep{veritas_gamma_cygni}.
 
@@
 
-Twelve extended sources were included in 2FGL and two additonal
-extended sources were studied in dedicated publications.  Using two years of
-LAT data and a new analysis method, we presented the detection of
-seven additional extended sources. 
-We also reanalyze the spatial
-shape of the twelve extended sources in 2FGL and the two additional
-sources.  The 21 extended
-LAT sources are located primarily along the Galactic plane 
-and their locations are shown in
-Figure~\ref{allsky_extended_sources}.  Most of the LAT detected
-extended sources are
-expected to be of Galactic origin as the distance of extragalactic
-sources (with the exception of the local group Galaxies) is typically too
-large to be able to resolve them at $\gamma$-rays energies.
+Twelve extended sources were included in 2FGL and two additonal extended
+sources were studied in dedicated publications.  Using two years of
+LAT data and a new analysis method, we presented the detection of seven
+additional extended sources.  We also reanalyze the spatial shape of the
+twelve extended sources in 2FGL and the two additional sources.  The 21
+extended LAT sources are located primarily along the Galactic plane
+and their locations are shown in Figure~\ref{allsky_extended_sources}.
+Most of the LAT detected extended sources are expected to be of Galactic
+origin as the distance of extragalactic sources (with the exception of
+the local group Galaxies) is typically too large to be able to resolve
+them at $\gamma$-rays energies.
 
@@
       The table quotes
-      integral fluxes in the analyzed energy range (1 \gev to 100 \gev or 10 \gev 100
+      integral fluxes in the analyzed energy range (1 \gev to 100 \gev or 10 \gev to 100
       \gev) in units of $10^{-10}$ \phflux.
@@
     \caption{
-    The distribution of \tsext and \tsinc 
-    (a) and (b) when fitting simulated spatially extended sources
-    with radially-symmetric uniform intensity surface profiles and varying the
-    source's size and (c), (d), (e), and (f) when fitting
-    two simulated point-like sources and varying their separation distance.
-    (c), and (d) represent simulations of two point-like sources with the
-    same spectral index and (e), and (f) represent simulations of two
-    point-like sources with different spectral indices.  (a), (c), and (e)
-    fit the simulated sources in the 1 \gev to 100 \gev energy range and
-    (b), (d), and (f) when fitting the simulated sources in the
-    10 \gev to 100 \gev energy range.
+    \newtext{
+    The distribution of $\tsext-\tsinc$ 
+    (a) and (b) when fitting simulated spatially extended sources with
+    radially-symmetric uniform intensity surface profiles and varying
+    the size of the source and (c), (d), (e), and (f) when fitting two
+    simulated point-like sources and varying their separation distance.
+    (c), and (d) represent simulations of two point-like sources with
+    the same spectral index and (e), and (f) represent simulations of
+    two point-like sources with different spectral indices.  (a), (c),
+    and (e) fit the simulated sources in the 1 \gev to 100 \gev energy
+    range and (b), (d), and (f) when fitting the simulated sources
+    in the 10 \gev to 100 \gev energy range. The plus-shaped markers
+    (colored red in the electronic version) are fits where $\tsext\ge16$
+    that would be flagged as extended.
+    }
     }\label{confusion_plot}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/index_difference_color.eps}
-    \else
-    \plotone{mc_plots/index_difference_bw.eps}
-    \fi
-    % this plot came from 
-    \caption{
-    The absolute value of the difference of the fit
-    spectral index when fitting the simulated extended sources from
-    figure~\ref{confusion_plot} as two point-like sources for the first 100
-    simulated extended sources.  The errors on the difference in spectral
-    index were obtained by adding in quadrature the error on each spectral
-    index.  (a) represents the difference in index when analyzing the
-    simulated extended sources in figure~\ref{confusion_plot}a in the 1
-    \gev to 100 \gev energy range whereas (b) represents the difference
-    for the sources in figure~\ref{confusion_plot}a in the 10 \gev to
-    100 \gev energy range.
-    }\label{index_difference}
   \end{figure}
@@
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v6/agn.py
-    \caption{The cumulative density of \tsext for the 783 clean
+    \caption{The cumulative density of \tsext for the 733 clean
     AGN in 2LAC that were significant above 1 \gev calculated with \pointlike (dashed line
@@
 \hline
-SMC                  &     302.68 &     -44.81 & $  1.75 \pm   0.07 \pm   0.02 $ &       94.8 &       67.4 &   0.12 & $    3.3 \pm     0.4$ & $   2.41 \pm    0.17$  \\
-LMC                  &     279.10 &     -32.61 & $  1.74 \pm   0.05 \pm   0.13 $ &     1101.3 &      860.5 &   0.05 & $   15.5 \pm     0.6$ & $   2.48 \pm    0.06$  \\
-IC443                &     189.05 &       3.04 & $  0.36 \pm   0.01 \pm   0.04 $ &    10719.8 &      510.4 &   0.01 & $   64.8 \pm     1.2$ & $   2.23 \pm    0.02$  \\
+SMC                       &     302.59 &     -44.42 & $  1.32 \pm   0.15 \pm   0.31 $ &       95.0 &       52.9 &   0.14 & $    2.7 \pm     0.3$ & $   2.48 \pm    0.19$  \\
+LMC                       &     279.26 &     -32.31 & $  1.37 \pm   0.04 \pm   0.11 $ &     1127.9 &      909.9 &   0.04 & $   13.6 \pm     0.6$ & $   2.43 \pm    0.06$  \\
+IC443                     &     189.05 &       3.04 & $  0.35 \pm   0.01 \pm   0.04 $ &    10692.9 &      554.4 &   0.01 & $   62.4 \pm     1.1$ & $   2.22 \pm    0.02$  \\
 Vela X                    &     263.34 &      -3.11 & $                         0.88$ &            &            &        &                       &                        \\
-Centarus A           &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
-W28                  &       6.50 &      -0.27 & $  0.43 \pm   0.02 \pm   0.03 $ &     1324.8 &      177.4 &   0.01 & $   58.0 \pm     1.8$ & $   2.63 \pm    0.03$  \\
-W30                  &       8.61 &      -0.20 & $  0.36 \pm   0.02 \pm   0.02 $ &      465.4 &       73.3 &   0.02 & $   30.7 \pm     1.6$ & $   2.59 \pm    0.04$  \\
-W44                  &      34.69 &      -0.38 & $  0.36 \pm   0.01 \pm   0.02 $ &     1903.3 &      217.7 &   0.01 & $   73.6 \pm     1.8$ & $   2.68 \pm    0.02$  \\
-W51C                 &      49.13 &      -0.45 & $  0.28 \pm   0.02 \pm   0.05 $ &     1819.5 &      115.7 &   0.01 & $   39.3 \pm     1.3$ & $   2.35 \pm    0.03$  \\
-Cygnus Loop          &      74.22 &      -8.46 & $  1.72 \pm   0.05 \pm   0.07 $ &      356.5 &      356.5 &   0.06 & $   11.1 \pm     0.7$ & $   2.53 \pm    0.11$  \\
+Centaurus A               &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
+W28                       &       6.50 &      -0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
+W30                       &       8.61 &      -0.20 & $  0.34 \pm   0.02 \pm  -1.00 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
+W44                       &      34.69 &      -0.39 & $  0.35 \pm   0.02 \pm  -1.00 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
+W51C                      &      49.12 &      -0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
+Cygnus Loop               &      74.21 &      -8.48 & $  1.71 \pm   0.05 \pm   0.06 $ &      357.9 &      246.0 &   0.06 & $   11.4 \pm     0.7$ & $   2.50 \pm    0.10$  \\
 \cutinhead{E$>$10 \gev}
-MSH\,15$-$52         &     320.38 &      -1.22 & $  0.20 \pm   0.04 \pm   0.03 $ &       76.2 &        6.5 &   0.03 & $    0.6 \pm     0.7$ & $   2.27 \pm    0.73$  \\
-HESS\,J1825$-$137    &      17.56 &      -0.46 & $  0.65 \pm   0.03 \pm   0.01 $ &       83.6 &       55.9 &   0.05 & $    1.8 \pm     0.2$ & $   1.74 \pm    0.19$  \\
+MSH\,15$-$52              &     320.39 &      -1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
+HESS\,J1825$-$137         &      17.57 &      -0.45 & $  0.65 \pm   0.04 \pm   0.02 $ &       82.9 &       44.9 &   0.05 & $    1.8 \pm     0.8$ & $   1.83 \pm    0.73$  \\
 \enddata
@@
 Integral Flux in units of $10^{-9}\phflux$ and integrated in the fit
-energy range (either 1 \gev 100 \gev or 10 \gev 100 \gev).
+energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
 }
@@
 Section~\ref{systematic_errors_on_extension}).  Pos Err is the error on
-the position of the source.  Vela X and the Centarus A Lobes were
+the position of the source.  Vela X and the Centaurus A Lobes were
 not fit in our analysis but are include for completeness.
@@
 \hline
-2FGL\,J0823.0$-$4246   &     260.32 &      -3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      320.9 &       46.3 &   0.02 & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
-2FGL\,J1627.0$-$2425c  &     353.08 &      16.78 & $  0.41 \pm   0.05 \pm   0.02 $ &      144.5 &       31.1 &   0.04 & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
-2FGL\,J1712.4$-$3941   &     347.25 &      -0.54 & $  0.56 \pm   0.04 \pm   0.01 $ &       75.0 &       39.6 &   0.05 & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7$-$3946 \\
+2FGL\,J0823.0$-$4246      &     260.32 &      -3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      322.2 &       48.0 &   0.02 & $    8.4 \pm     0.6$ & $   2.21 \pm    0.09$ &                  Puppis A \\
+2FGL\,J1627.0$-$2425c     &     353.07 &      16.80 & $  0.42 \pm   0.05 \pm   0.16 $ &      139.9 &       32.4 &   0.04 & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ &                 Ophiuchus \\
 \cutinhead{E$>$10 \gev}
-2FGL\,J0851.7$-$4635   &     266.29 &      -1.43 & $  1.13 \pm   0.08 \pm   0.05 $ &      116.1 &       87.2 &   0.07 & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr. \\
-2FGL\,J1615.0$-$5051   &     332.38 &      -0.14 & $  0.33 \pm   0.04 \pm   0.01 $ &       53.4 &       16.3 &   0.04 & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616$-$508 \\
-2FGL\,J1615.2$-$5138   &     331.66 &      -0.66 & $  0.42 \pm   0.03 \pm   0.01 $ &       76.6 &       48.0 &   0.05 & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614$-$518 \\
-2FGL\,J1632.4$-$4753c  &     336.41 &       0.22 & $  0.44 \pm   0.04 \pm   0.03 $ &      127.8 &       64.5 &   0.04 & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632$-$478 \\
-2FGL\,J1837.3$-$0700c  &      25.08 &       0.13 & $  0.35 \pm   0.08 \pm   0.03 $ &       46.2 &       18.8 &   0.07 & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837$-$069 \\
-2FGL\,J2021.5+4026     &      78.18 &       2.19 & $  0.59 \pm   0.03 \pm   0.02 $ &      222.2 &      116.4 &   0.04 & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &       $\gamma$-Cygni \\
+2FGL\,J0851.7$-$4635      &     266.31 &      -1.43 & $  1.15 \pm   0.08 \pm   0.02 $ &      116.6 &       86.8 &   0.07 & $    1.3 \pm     0.2$ & $   1.74 \pm    0.21$ &                  Vela Jr. \\
+2FGL\,J1615.0$-$5051      &     332.37 &      -0.13 & $  0.32 \pm   0.04 \pm   0.01 $ &       50.4 &       16.7 &   0.04 & $    1.0 \pm     0.2$ & $   2.19 \pm    0.28$ &         HESS\,J1616$-$508 \\
+2FGL\,J1615.2$-$5138      &     331.66 &      -0.66 & $  0.42 \pm   0.04 \pm   0.02 $ &       76.1 &       46.5 &   0.04 & $    1.1 \pm     0.2$ & $   1.79 \pm    0.26$ &         HESS\,J1614$-$518 \\
+2FGL\,J1632.4$-$4753c     &     336.52 &       0.12 & $  0.35 \pm   0.04 \pm   0.02 $ &       64.4 &       26.9 &   0.04 & $    1.4 \pm     0.2$ & $   2.66 \pm    0.30$ &         HESS\,J1632$-$478 \\
+2FGL\,J1712.4$-$3941      &     347.26 &      -0.53 & $  0.56 \pm   0.04 \pm   0.02 $ &       59.4 &       38.5 &   0.05 & $    1.2 \pm     0.2$ & $   1.87 \pm    0.22$ &        RX\,J1713.7$-$3946 \\
+2FGL\,J1837.3$-$0700c     &      25.08 &       0.13 & $  0.33 \pm   0.07 \pm   0.05 $ &       47.0 &       18.5 &   0.07 & $    1.0 \pm     0.2$ & $   1.65 \pm    0.29$ &         HESS\,J1837$-$069 \\
+2FGL\,J2021.5+4026        &      78.24 &       2.20 & $  0.63 \pm   0.05 \pm   0.04 $ &      237.2 &      128.9 &   0.05 & $    2.0 \pm     0.2$ & $   2.42 \pm    0.19$ &            $\gamma$-Cygni \\
 \enddata
@@
 \hline
-  2FGL\,J0823.0$-$4246   &                350.9 &                320.9 &                352.5 &                 66.0 &                 46.3 &                 53.6 &                 0.37 &                 0.39 &                 0.38 &                 22.1 \\
-  2FGL\,J1627.0$-$2425c  &                170.2 &                144.5 &                112.6 &                 43.9 &                 31.1 &                 23.9 &                 0.41 &                 0.40 &                 0.39 &                 20.0 \\
-  2FGL\,J1712.4$-$3941   &                 80.9 &                 75.0 &                 43.4 &                 47.4 &                 39.6 &                 22.2 &                 0.56 &                 0.56 &                 0.54 &                  6.4 \\
+2FGL\,J0823.0$-$4246      &                331.9 &                322.2 &                356.0 &                 60.0 &                 48.0 &                 56.0 &                 0.37 &                 0.39 &                 0.39 &                 23.0 \\
+2FGL\,J1627.0$-$2425c     &                154.8 &                139.9 &                105.7 &                 39.4 &                 32.4 &                 24.8 &                 0.42 &
+ 0.40 &                 0.58 &                 24.5 \\
 \cutinhead{E$>$10 \gev}
-  2FGL\,J0851.7$-$4635   &                116.7 &                116.1 &                122.3 &                 87.1 &                 87.2 &                 90.4 &                 1.13 &                 1.16 &                 1.17 &                 16.1 \\
-  2FGL\,J1615.0$-$5051   &                 52.4 &                 53.4 &                 55.6 &                 17.5 &                 16.3 &                 17.4 &                 0.33 &                 0.32 &                 0.32 &                 11.9 \\
-  2FGL\,J1615.2$-$5138   &                 76.3 &                 76.6 &                 86.3 &                 44.0 &                 48.0 &                 52.6 &                 0.42 &                 0.43 &                 0.43 &                 37.0 \\
-  2FGL\,J1632.4$-$4753c  &                126.6 &                127.8 &                120.7 &                 63.9 &                 64.5 &                 64.1 &                 0.44 &                 0.44 &                 0.47 &                 40.6 \\
-  2FGL\,J1837.3$-$0700c  &                 45.4 &                 46.2 &                 39.0 &                 18.5 &                 18.8 &                 16.6 &                 0.35 &                 0.34 &                 0.38 &                 12.6 \\
-  2FGL\,J2021.5+4026     &                234.3 &                222.2 &                235.6 &                135.9 &                116.4 &                121.4 &                 0.59 &                 0.60 &                 0.60 &                 24.3 \\
+2FGL\,J0851.7$-$4635      &                115.2 &                116.6 &                123.1 &                 83.9 &                 86.8 &                 89.8 &                 1.15 &                 1.16 &                 1.17 &                 15.5 \\
+2FGL\,J1615.0$-$5051      &                 48.2 &                 50.4 &                 56.6 &                 15.2 &                 16.7 &                 17.8 &                 0.32 &                 0.33 &                 0.32 &                 13.1 \\
+2FGL\,J1615.2$-$5138      &                 75.0 &                 76.1 &                 83.8 &                 42.9 &                 46.5 &                 54.1 &                 0.42 &                 0.43 &                 0.43 &                 35.1 \\
+2FGL\,J1632.4$-$4753c     &                 64.5 &                 64.4 &                 66.8 &                 23.0 &                 26.9 &                 25.5 &                 0.35 &                 0.36 &                 0.37 &                 10.9 \\
+2FGL\,J1712.4$-$3941      &                 59.8 &                 59.4 &                 39.9 &                 38.4 &                 38.5 &                 30.7 &                 0.56 &                 0.55 &                 0.53 &                  2.7 \\
+2FGL\,J1837.3$-$0700c     &                 44.5 &                 47.0 &                 39.2 &                 17.6 &                 18.5 &                 16.1 &                 0.33 &                 0.32 &                 0.38 &                 10.8 \\
+2FGL\,J2021.5+4026        &                239.1 &                237.2 &                255.8 &                139.1 &                128.9 &                138.0 &                 0.63 &                 0.65 &                 0.59 &                 37.3 \\
   \enddata
@@
   online version) represents the 2FGL position of this source.
+  \newtext{
   The plus-shaped marker and the circle (colored red) 
   represent the best fit position and extension of this
-  source assuming a radially-symmetric uniform surface brightness profile. The
+  source assuming a radially-symmetric uniform surface brightness profile
+  and the black cross represents a background 2FGL source. 
+  }
+  The
   contours in (a) correspond to the 100 micrometer image observed by
@@
   }\label{1FGL_J1628.6-2419c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_RX_J1713.7-3946_color.eps}
-    \else
-      \plotone{source_plots/source_RX_J1713.7-3946_bw.eps}
-    \fi
-    % this plot came from
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v8/run.py
-  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
-  of 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg25 2D
-  Gaussian kernel and (b) with the emission from the background sources
-  subtracted.  This source is spatially coincident with RX\,J1713.7$-$3946
-  and was recently studied in \cite{rx_j1713_lat}.  The triangular marker
-  (colored red in the online version) represents the 2FGL position of
-  this source.  The plus-shaped marker and the circle (colored red) are
-  the best fit position and extension of this source assuming a radially
-  symmetric uniform surface brightness profile.  The contours (colored light blue)
-  correspond to the \tev image \citep{rx_j1713_hess}.  The region was
-  analyzed with the same background model as \cite{rx_j1713_lat}. Source
-  A is coincident with 2FGL\,J1715.4$-$4024c and the circular and
-  square-shaped marker (colored blue) represent the 2FGL and relocalized
-  position of this source respectively.  The diamond-shaped markers
-  (colored purple) represent the position of source B and C that were
-  added to the background model.
-  }\label{2FGL_J1712.4-3941}
 \end{figure}
@@
   this source assuming a radially-symmetric uniform surface brightness profile.
-  The five star-shaped markers (colored green) represent 2FGL sources
-  that were removed from the background model.  The circular and square
-  marker (colored blue) represents the 2FGL and relocalized position of
-  2FGL\,J0854.7$-$4501 respectively.  This extended source is spatially
+  \newtext{
+  The three black crosses represent background 2FGL sources
+  and the three star-shaped markers (colored green) represent other 2FGL sources
+  that were removed from the background model 
+  The circular and square-shaped
+  marker (colored blue) represents the 2FGL and relocalized position of another 2FGL source.  
+  }
+  This extended source is spatially
   coincident with the Vela Jr. SNR.  The contours (colored light blue)
@@
     positions and extensions of these sources assuming a radially
-    symmetric uniform surface brightness profile.  The three star-shaped
-    markers (colored
-    green) represent 2FGL sources that were removed from the background
+    symmetric uniform surface brightness profile.  
+    \newtext{The two black crosses represent  background 2FGL sources and
+    the star-shaped
+    marker (colored green) represents another 2FGL source that was removed from the background
     model.  The contours (colored light blue) correspond to the \tev
     image of HESS\,J1616$-$508 (left) and HESS\,J1614$-$518 (right)
+    }
     \citep{hess_plane_survey}.   
@@
   2FGL\,J1632.4$-$4753c assuming a radially-symmetric uniform surface
-  brightness profile.  The four star-shaped markers (colored green) represent 2FGL
-  sources that were removed from the background model.  The circular
-  and square markers (colored blue) represent the 2FGL and relocalized
-  positions respectively of 2FGL\,J1635.4$-$4717c (left)
-  and 2FGL\,J1636.3$-$4740c (right).  
+  brightness profile.  
+  \newtext{
+  The four black crosses represent background 2FGL
+  sources subtracted in (b).  The 
+  circular and square-shaped markers (colored blue) represent 
+  the 2FGL and relocalized positions respectively of two
+  additional background 2FGL sources subtracted in (b).
+  The star-shaped marker (colored green) represent another 2FGL
+  source that was removed from the background model.  
+  }
   The contours (colored light blue) correspond to the \tev image of
@@
   }\label{1FGL_J1632.9-4802c}
+\end{figure}
+
+\begin{figure}
+    \ifcolorfigure
+      \plotone{source_plots/source_RX_J1713.7-3946_color.eps}
+    \else
+      \plotone{source_plots/source_RX_J1713.7-3946_bw.eps}
+    \fi
+    % this plot came from
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v8/run.py
+  \caption{
+  \newtext{
+  A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
+  of 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg15 2D
+  Gaussian kernel and (b) with the emission from the background sources
+  subtracted.  This source is spatially coincident with RX\,J1713.7$-$3946
+  and was recently studied in \cite{rx_j1713_lat}.  The triangular marker
+  (colored red in the online version) represents the 2FGL position of
+  this source.  The plus-shaped marker and the circle (colored red) are
+  the best fit position and extension of this source assuming a radially
+  symmetric uniform surface brightness profile.  
+  The two black crosses represent background 2FGL sources subtracted in (b).
+  The contours (colored light blue)
+  correspond to the \tev image \citep{rx_j1713_hess}.  
+  }
+  }\label{2FGL_J1712.4-3941}
 \end{figure}
@@
   the 2FGL
-  position of this source. The plus-shaped marker and 
-  the circle (colored red) represent
-  the best fit position and extension of 2FGL\,J1837.3$-$0700c assuming a
-  radially-symmetric uniform surface brightness profile. The circular
-  and square markers 
-  (colored blue) represent the 2FGL and the relocalized position of
-  2FGL\,J1839.3$-$0558c (left), 2FGL\,J1836.8$-$0623c (middle),
-  and 2FGL\,J1834.7$-$0705c (right).  The star-shaped marker 
-  (colored green) represent a
-  2FGL source that was removed from the background model.  
-  The contours (colored light blue) correspond to the \tev image of
-  HESS\,J1837$-$069
-  \citep{hess_plane_survey}.}\label{1FGL_J1837.5-0659c}
+  position of this source. 
+  \newtext{
+  The plus-shaped marker and 
+  the circle (colored red) represent the best fit position and extension
+  of 2FGL\,J1837.3$-$0700c assuming a radially-symmetric uniform surface
+  brightness profile. The circular and square-shaped markers (colored
+  blue) represent the 2FGL and the relocalized positions respectively of
+  two background 2FGL sources subtracted in (b).  The star-shaped marker
+  (colored green) represents a 2FGL source that was removed from the
+  background model.  The contours (colored light blue) correspond to
+  the \tev image of HESS\,J1837$-$069
+  \citep{hess_plane_survey}.
+  The diamond-shaped marker (colored orange) represents the position of PSR J1838-0655
+  and the hexagonal-shaped marker (colored purple) represents the position AX J1837.3-0652
+  \citep{pulsations_HESS_J1837-069}.
+  }
+  }\label{1FGL_J1837.5-0659c}
 \end{figure}
@@
   and extension of 2FGL\,J2021.5+4026 assuming a radially-symmetric
-  uniform surface brightness profile.  The star-shaped markers (colored green)
-  represent 2FGL sources that were removed from the background model.
-  The diamond-shaped marker (colored purple) represents the position of
-  a
-  source not in 2FGL that was added to the region. 2FGL\,J2021.5+4026
+  uniform surface brightness profile.  \newtext{
+  The star-shaped marker (colored green)
+  represents a 2FGL source that was removed from the background model.
+  }
+  2FGL\,J2021.5+4026
   is spatially coincident with the $\gamma$-Cygni SNR.  The contours
@@
     (colored red in the electronic version) and the 21 spatially extended
-    sources (colored blue).  The index of Centarus A is taken from
+    sources (colored blue).  The index of Centaurus A is taken from
     \cite{second_cat} and the index of Vela X is taken from \cite{velax}.

### 2011-11-08 extended_catalog/paper/extended_catalog.tex
updating text

@@
 %  * Better clarification about previous gtlike validation of extended source analysis + Citation of Francesco's work.
+%  * Removed from the GeV/TeV extension size plots RX J1713+Vela Jr becuase they were not directly fit at TeV energies.
 
@@
 \newtext{
-The gtlike likelihood profile approach has been show to correctly
+The \gtlike likelihood profile approach has been show to correctly
 reproduce the extension of simulated extended sources assuming that the
@@
 source.
-For the LAT, the PSF can be parameterized by a King function \citep{king_function}:
+\newtext{
+The LAT's PSF is currently parameterized 
+in the Pass~7\_V6 (P7\_V6) Source Instrument
+Response Function \citep[IRFs,][]{lat_on_orbit_psf} by a King function \citep{king_function}:
+}
 \begin{equation}
@@
 For smaller and fainter extended sources, the differences in the PDF for
-different spatial models lost in the noise and the LAT is not sensitive
+different spatial models are lost in the noise and the LAT is not sensitive
 to the detailed spatial structure of these sources.  Therefore, in our
@@
 representative livetime fraction of 0.8.  The reconstruction was performed
-using the Pass~7\_V6 (P7\_V6) Source Instrument
-Response Function (IRFs, \cite{lat_on_orbit_psf}).  For each 
+using the P7\_V6 Source class event selection and IRFs \citep{lat_on_orbit_psf}. For each 
 significantly detected point-like source ($\ts\ge25$), we used \pointlike
@@
 which the value of $\tsext$ averaged over many statistical realizations is
-$\langle\tsext\rangle=16$ for a source of a given flux and true extension.
+$\langle\tsext\rangle=16$ for a source of a given flux and true extension
+\newtext{
+(corresponding to a formal $4\sigma$ significance).
+}
 
@@
 to $2\fdg0$.  
-The LAT flux threshold for a significant detection
-of source extension drops quickly with
-increasing source size and reaches a minimum around 0\fdg5. 
 The threshold is high for small extensions when the
 source is 
-small compared to the size of the PSF. The threshold increases
+small compared to the size of the PSF. 
+It drops quickly with increasing source size and reaches
+a minimum around 0\fdg5. 
+The threshold increases
 for large extended sources because the source becomes
@@
 an extended source and as two point-like sources.  We then simulated two
-point-like sources and fit them with the same two hypothesis. By comparing
+point-like sources and fit them with the same two hypotheses. By comparing
 the distribution of \tsinc and \tsext for the two cases, we evaluated
-how well the $\tsext>\tsinc$ test is at rejecting the possibility of
+how good the $\tsext>\tsinc$ test is at rejecting the possibility of
 source confusion as well as how likely it is to incorrectly reject 
@@
 This spectrum is typical of the new extended sources discovered
-using only photons with energies between 1 \gev and 100 \gev (see
+using only photons with energies between 10 \gev and 100 \gev (see
 Section~\ref{new_ext_srcs_section}).
@@
 
-The distributions also shows that for simulated
+The distributions also show that for simulated
 extended sources with typical
-sizes ($\sigma\sim0\fdg5$), one can often obtain almost as good an
-increase in likelihood
-when fitting the extended source as two point-like sources ($\tsinc\sim\tsext$).
+sizes ($\sigma\sim0\fdg5$), one can often obtain almost as good 
+an increase in likelihood
+with two sources as with one extended source ($\tsinc\sim\tsext$).
 This is because although
@@
 region.  There is nothing about this conclusion unique to LAT analysis,
-but the larger PSF of the LAT and the density of sources expected to be
+but the broad PSF of the LAT and the density of sources expected to be
 \gev emitters in the galactic plane makes this issue more significant
@@
 the previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
-brightness profile when fitting it (\citep{lmc}).
+brightness profile when fitting it \citep{lmc}.
 
@@
 sensitivity using photons with energies below 1 \gev. On the other hand,
-the large PSF at low energy makes us more susceptible to systematic
+the broad PSF at low energy makes us more susceptible to systematic
 errors arising from source confusion due to nearby soft point-like sources
@@
 
-With this model of the sky, we iterativly fit the extensions of
+With this model of the sky, we iteratively fit the extensions of
 2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138.
@@
 2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
-of two point-like sources (one of them represtend in 2FGL by
+of two point-like sources (one of them represented in 2FGL by
 2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
-sources.  Because \tsinc is less than \tsext, we conclue that
+sources.  Because \tsinc is less than \tsext, we conclude that
 this emission does not originate from two nearby point-like sources.
@@
 association was disfavored when the LAT \gev emission from this source
-was detected to be pulsed (PSR\,J2021+4026, \cite{first_lat_pulsar_cat}).
+was detected to be pulsed \citep[PSR\,J2021+4026,][]{first_lat_pulsar_cat}.
 This pulsar was also been observed by AGILE \citep{gamma_cygni_agile}.
@@
 
-Twelve extended sources were included in 2FGL and two additonal extended
+Twelve extended sources were included in 2FGL and two additional extended
 sources were studied in dedicated publications.  Using two years of
@@
 W28                       &       6.50 &      -0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
-W30                       &       8.61 &      -0.20 & $  0.34 \pm   0.02 \pm  -1.00 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
-W44                       &      34.69 &      -0.39 & $  0.35 \pm   0.02 \pm  -1.00 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
+W30                       &       8.61 &      -0.20 & $  0.34 \pm   0.02 \pm   0.02 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
+W44                       &      34.69 &      -0.39 & $  0.35 \pm   0.02 \pm   0.02 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
 W51C                      &      49.12 &      -0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
@@
 \tablenotetext{(a)}{
-Integral Flux in units of $10^{-9}\phflux$ and integrated in the fit
+Integral Flux in units of $10^{-9}$ \phflux and integrated in the fit
 energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
@@
     \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v4/extension_histogram.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v5/extension_histogram.py
     \caption{
-    The distribution of the size of the 22 extended LAT sources
+    The distribution of the size of 18 extended LAT sources
     at \gev energies
     (colored blue in the electronic version) and the size of the
-    42 extended H.E.S.S. sources at \tev energies
-    (colored red).  The size of Vela X
-    is taken from \cite{velax}.  Except for RX\,J1713.7$-$3946 and
-    Vela Jr., the H.E.S.S. sources were fit with a 2D Gaussian surface
-    brightness profile so the LAT and H.E.S.S. sizes are first converted
+    40 extended H.E.S.S. sources at \tev energies
+    (colored red).  
+    The H.E.S.S. sources were fit with a 2D Gaussian surface
+    brightness profile so the LAT and H.E.S.S. sizes were first converted
     to \rsixeight. 
+    The \gev size of Vela X is taken from \cite{velax}.  
     Because of their large size, the shape of RX\,J1713.7$-$3946 and
-    Vela Jr. were not directly fit at \tev energies. Their size at
-    \tev energies is taken from the HESS source catalog to be 0\fdg5
-    and $1\degree$ respectively.  Because the spatial morphology of
-    RX\,J1713.7$-$3946 and Vela Jr. is poorly described by a 2D Gaussian,
-    the \gev and \tev extensions of these sources was not converted
-    to \rsixeight.
+    Vela Jr. were not directly fit at \tev energies
+    and are not included in this comparison.
+    Centaurus A is not included because of its large size.
     }\label{gev_vs_tev_histogram}

### 2011-11-08 pointlike/SED.py
cleanup

@@ -16,7 +16,7 @@ like=BinnedAnalysis(...)
 sed = SED(like,name)
 
 # by default, energy is quoted in MeV and
-# flux is quted in erg/cm^2/s:
+# flux is quted in MeV/cm^2/s:
 sed = SED(like,name)
 
 
@@ -59,7 +59,8 @@ class SED(object):
                  always_upper_limit=False,
                  ul_algorithm='bayesian',
                  powerlaw_index=-2,
-                 min_ts=4):
+                 min_ts=4,
+                 ul_confidence=.95):
         """ Parameters:
             * like - pyLikelihood object
             * name - source to make an SED for
@@ -71,7 +72,8 @@ class SED(object):
             * ul_algorithm - choices = 'frequentist', 'bayesian' 
             * powerlaw_index - fixed spectral index to assume when
                                computing SED.
-            * min_ts - minimum ts in which to quote a SED points instead of an upper limit. """
+            * min_ts - minimum ts in which to quote a SED points instead of an upper limit. 
+            * ul_confidence - confidence level for upper limit. """
         self.name               = name
         self.verbosity          = verbosity
         self.freeze_background  = freeze_background
@@ -79,6 +81,7 @@ class SED(object):
         self.ul_algorithm       = ul_algorithm
         self.powerlaw_index     = powerlaw_index
         self.min_ts             = min_ts
+        self.ul_confidence      = ul_confidence
 
         self.spectrum = like.logLike.getSource(self.name).spectrum()
 
@@ -89,7 +92,7 @@ class SED(object):
                     raise Exception("energy %.1f in bin_edges is not commensurate with the energy binning of pyLikelihood." % e)
             
             bin_edges = np.asarray(bin_edges)
-            self.energy = np.sqrt(self.bin_edges[1:]*self.bin_edges[:-1])
+            self.energy = np.sqrt(bin_edges[1:]*bin_edges[:-1])
         else:
             # These energies are always in MeV
             bin_edges = like.energies
@@ -120,27 +123,31 @@ class SED(object):
         self._calculate(like)
 
     @staticmethod
-    def frequentist_upper_limit(like,name,emin,emax,verbosity):
+    def frequentist_upper_limit(like,name,emin,emax,confidence,verbosity):
         """ Calculate a frequentist upper limit on the prefactor. 
             Returns the unscaled prefactor upper limit. """
[…]

### 2011-11-09 extended_catalog/paper/extended_catalog.tex
fixing text

@@
 energy bins between 100 \mev and 100 \gev. For IC443, which has a
-spectral index $\sim2.4$ and an extension $\sim0\fdg35$, 
+spectral index $\sim2.4$ and an extension $\sigma=\sim0\fdg35$, 
 almost the entire increase in likelihood
@@
 
-For the extended sources presented in this paper,
-we developed two criteria for estimating systematic errors
+We developed two criteria for estimating systematic errors
 on the extension of the sources.
@@
 
-Now that we have demonstrated that we understand the statistical
+Having demonstrated that we understand the statistical
 issues associated with analyzing spatially extended sources
@@
 that our method can correctly analyze the extended sources included in
-2FGL (Section~\ref{validate_known}), we apply this method to search for
+2FGL (Section~\ref{validate_known}), we applied this method to search for
 new spatially extended \gev sources.
@@
 this analysis is challenged by our imperfect model of the diffuse
-emission and by issues related to source confusion.  The Monte Carlo
+emission and by an imperfect model of nearby sources.  The Monte Carlo
 study in Section~\ref{dual_localization_method}
@@
 multiple point-like sources. Furthermore, the position of other nearby sources
-in the region near an extended source could be biased by not correctly
+in the region close to an extended source could be biased by not correctly
 modeling the
-sources' extension.  Furthermore, 2FGL produced a
+sources' extension.  Since 2FGL produced a
 list of sources significant at energies above 100 \mev whereas we are
-most sensitive to spatial extension at higher energies.  Therefore,
-we expect that at higher energies our analysis would be complicated
+most sensitive to spatial extension at higher energies,
+we also expect that at higher energies our analysis would be complicated
 by 2FGL sources no longer significant and by 2FGL
@@
 
-To account for these issues, we first produced a large list of
-possibly extended sources employing a very liberal search criteria
-and then refined the analysis of the promising candidates on a case
-by case basis.  Our strategy tested all point-like 2FGL sources for
-extension assuming they had a uniform radially-symmetric uniform surface
-brightness profile and a power-law spectral model.  Although not all
-extended sources are expected to have a shape very similar to a uniform
-surface brightness profile, Section~\ref{compare_source_size} showed that
-for many spatially extended sources the wide PSF of the LAT and limited
-statistics makes this a reasonable approximation.  Additionally, our Monte
-Carlo study and AGN validation (Sections~\ref{monte_carlo_validation}
-and~\ref{test_2lac_sources}) demonstrate that we can use this shape
-for a statistically rigorous test. Because this spatial model only adds
-one additional degree of freedom, this test should be very sensitive.
-On the other hand, choosing this spatial model biases us against
-finding extended sources that are not well described by uniform emission
-such as shell-type supernova remnants.
-
-Before testing for extension,
-we automatically removed from the background model all other 2FGL
-sources within 0\fdg5 of the source.  This distance is somewhat arbitrary,
-but was picked in hopes of finding extended sources with sizes on the
-order of $\sim1\degree$ or smaller. On the other hand, by removing
-these nearby background sources we expect to also incorrectly flag 
-in our preliminary list point-like sources that are 
-confused with
-nearby sources.  To screen out obvious cases of source
+To account for these issues, we first produced a large list of possibly
+extended sources employing a very liberal search criteria and then
+refined the analysis of the promising candidates on a case by case basis.
+Our strategy tested all point-like 2FGL sources for extension assuming
+they had a uniform radially-symmetric surface brightness profile
+and a power-law spectral model.  Although not all extended sources are
+expected to have a shape very similar to a uniform surface brightness
+profile, Section~\ref{compare_source_size} showed that for many spatially
+extended sources the wide PSF of the LAT and limited statistics makes
+this a reasonable approximation.  On the other hand, choosing this
+spatial model biases us against finding extended sources that are not
+well described by uniform emission such as shell-type supernova remnants.
+
+Before testing for extension, we automatically removed from the background
+model all other 2FGL sources within 0\fdg5 of the source.  This distance
+is somewhat arbitrary, but was picked in hopes of finding extended
+sources with sizes on the order of $\sim1\degree$ or smaller. On the
+other hand, by removing these nearby background sources we expect to
+also incorrectly add to our list of extended source candidates
+point-like sources that
+are confused with nearby sources.  To screen out obvious cases of source
 confusion, we performed the dual localization procedure described in
@@
 
-We also performed a second search for extended sources using only photons
-with energies between 10 \gev and 100 \gev.  Although this approach
-tests the same sources, it is complementary because the Galactic
-diffuse emission is even less dominant above 10 \gev. Furthermore,
-source confusion is less of a problem since many LAT sources are not
-significantly detected at energies exclusively above 10 \gev. Therefore,
-we expected to be able to resolve harder sources in more complicated
-regions by restricting our analysis to higher energies.  The $>10$ \gev
-analysis is especially beneficial for regions near pulsars which are
-not significantly detected above 10 \gev. A similar procedure was used
-to detect the spatial extension of HESS\,J1825$-$137 and MSH\,15$-$52
-with the LAT \citep{msh1552,fermi_hess_j1825}.
+\newtext{
+We also performed a second search for extended sources using only
+photons with energies between 10 \gev and 100 \gev.  Although this
+approach tests the same sources, it is complementary because the galactic
+diffuse emission is even less dominant above 10 \gev and because source
+confusion is less of an issue.  A similar procedure was used to detect
+the spatial extension of hess\,j1825$-$137 and msh\,15$-$52 with the
+lat \citep{msh1552,fermi_hess_j1825}.
+}
 
@@
 energy range and 11 extended source candidates in the 10 \gev to 100
-\gev energy range. Most of the extended sources flagged above 10 \gev were
-also flagged above 1 \gev and many of these situations represent multiple
-point-like 2FGL sources all fitting the same emission region. For example,
-the sources 2FGL\,J1630.2-4752, 2FGL\,J1632.4-4753c 2FGL\,J1634.4-4743c,
+\gev energy range. Most of the extended sources found above 10 \gev were
+also found above 1 \gev and in many cases multiple nearby point-like
+sources were found to be extended even though they fit the same emission region.
+For example, the sources 2FGL\,J1630.2-4752, 2FGL\,J1632.4-4753c 2FGL\,J1634.4-4743c,
 and 2FGL\,J1636.3-4740c were all found to be spatially extended in the
@@
 Similarly, many of these sources were confused with nearby
-point-like sources or influence by large-scale residuals in the
+point-like sources or influenced by large-scale residuals in the
 diffuse emission.  To help determine which of these fits found
@@
 that the spatially extended model for IC443 is a significantly better
-description of the observed photons and that there is not significant
+description of the observed photons and that there is no significant
 residual in the region after modeling the source as being spatially extended.
@@
 
-It was very clear by visual inspection that in many
-cases our analysis was strongly influence by large-scale residual in the
+We found by visual inspection that in many
+cases our analysis was strongly influenced by large-scale residuals in the
 diffuse emission and hence the extension measure was unreliable.  This was
@@
 sources or by large-scale residuals in the diffuse emission model, we
-improved the model of the region by decided on a case by case basis which
+improved the model of the region by deciding on a case by case basis which
 background point-like sources should be kept.  We kept in our model of the sky
@@
 multiwavelength information about possibly extended source counterparts
-to help guild our choice. For each extended source presented in 
+to help guide our choice. For each extended source presented in 
 Section~\ref{new_ext_srcs_section}, we will describe any modification from 2FGL
-of the background model that were required.
+of the background model that were performed.
 
@@
 coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
-a counts map of this source and overlays and \rosat X-ray contours of
-Puppis A.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
+a counts map of this source. There are two nearby catalog sources 2FGL\,J0823.4$-$4305
 and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
@@
 removed them from our model of the sky.
-After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension of
-$0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
+After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension 
+$\sigma=0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
 of $\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
@@
 
-Puppis A has been studied in detail in radio (\cite{puppis_a_vla}, and
-references therein) and  X-ray (\cite{rosat_puppis_a,suzaku_puppis_a},
-and references therein).  The fit extension of 2FGL\,J0823.0$-$4246
+Puppis A has been studied in detail in radio \citep{puppis_a_vla}, 
+and  X-ray \citep{rosat_puppis_a,suzaku_puppis_a}.
+The fit extension of 2FGL\,J0823.0$-$4246
 matches well its inferred size at \gev energies.  The distance of Puppis A was
@@
 No molecular clouds have been observed directly adjacent to Puppis A
-\citep{co_eastern_puppis_a}, similar to the LAT detected Cyngus Loop SNR
+\citep{co_eastern_puppis_a}, similar to the LAT detected Cygnus Loop SNR
 \citep{cygnus_loop_lat}.  The luminosity of Puppis A is also smaller
@@
 2FGL\,J1627.0$-$2425c was found by our search to
-have an extension of $0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
+have an extension $\sigma=0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
 an extension significance of $\tsext=32.4$
@@
 top of the core of the Ophiuchus molecular cloud which contains massive
-star-forming regions that are bright in the infrared.  The region also has
+star-forming regions that are bright in infrared.  The region also has
 abundant molecular and atomic gas traced by CO and HI but also plenty of
@@
 With this model of the background, 2FGL\,J0851.7$-$4635 was found to
-have an extension of $1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
+have an extension of $\sigma=1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
 an extension significance of $\tsext=86.8$.  The LAT size matches
@@
 2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138.
-2FGL\,J1615.0$-$5051 was found to have an extension of
-$0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ with an extension significance
+2FGL\,J1615.0$-$5051 was found to have an extension 
+$\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ with an extension significance
 of \tsext=16.7.  
 2FGL\,J1615.2$-$5138 was found
- to have an extension of $0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
+ to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
 with an extension significance of \tsext=46.5.
@@
 the background sources subtracted.  With this model, 2FGL\,J1632.4$-$4753c
-was found to have an extension of $0\fdg35\pm0\fdg04_\stat\pm0\fdg02_\sys$
+was found to have an extension $\sigma=0\fdg35\pm0\fdg04_\stat\pm0\fdg02_\sys$
 with an extension significance of \tsext=26.9.  While fitting the
@@
 smoothed counts map of the source. Above 10 \gev, the \gev emission
-nicely coorelates with the \tev contours of RX\,J1713.7$-$3946
-\cite{rx_j1713_hess} and 2FGL\,J1712.4$-$3941 fit to an extension of
-$0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with an extension significance
+nicely correlates with the \tev contours of RX\,J1713.7$-$3946
+\citep{rx_j1713_hess} and 2FGL\,J1712.4$-$3941 fit to an extension 
+$\sigma=0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with an extension significance
 of $\tsext=38.5$.
@@
 With this model, 2FGL\,J1837.3$-$0700c was found to have an
-extension of $0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with an extension
+extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with an extension
 significance of $\tsext=18.5$. 
@@
 removed it from our model of the sky.  With this model, 2FGL\,J2021.5+4026
-was found to have an extension of $0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
+was found to have an extension $\sigma=0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
 with an extension significance of $\tsext=116.4$.  Figure~\ref{snr_seds}
@@
     (colored red in the electronic version) are fits where $\tsext\ge16$
-    that would be flagged as extended.
+    that would be considered as extended.
     }
@@
     \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_snr_seds.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v4/plot_seds/plot_snr_seds.py
     \caption{
@@
     \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v3/plot_seds/plot_hess_seds.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v4/plot_seds/plot_hess_seds.py
     \caption{
@@
     The \tev size of IC443 is from \cite{ic443_veritas} and
-    W51c is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev
+    W51C is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev
     size of MSH\,15$-$52, HESS\,J1614$-$518, HESS\,J1632$-$478, and
     HESS\,J1837$-$069 have only been reported with an elliptical 2D
-    Gaussian fit and so the assumed size is the average of the semi-major
+    Gaussian fit and so the assumed size is the mean of the semi-major
     and semi-minor axis.

### 2011-11-09 extended_catalog/paper/extended_catalog.tex
updating text

@@
 \documentclass[12pt,preprint]{aastex}
-
-% New text (from v3.0 to v4.0):
-%  * Improve MC null distribution tests by using 8 bins per decade.
-%  * New study of null hypothesis distribution fitting only above E>10GeV.
-%  * Regenerate source confusion plot to show TS_ext-TS2pts
-%  * Remove figure 8 from draft v3.0  (the one describing the spectral index difference of the two point 
-%    source fit of extended sources) since everybody asked me to.
-%  * Rerun of agn analysis to fix sources that failed to converge + using 8bins per decade + using 2FGL skymodel.
-%  * For new source anlaysis:
-%  ** use 8 insetad of 4 bins per decade
-%  ** Freeze instead of delete insignificant 2FGL sources. This should make the text clearer because sources are only
-%     deleted if they are part of the extended emission.
-%  ** Add two nearby point-like sources to analysis of HESS J1632-478.
-%  ** Redo analysis of RX J1713 to be E>10GeV to avoid issues of diffuse uncertainty at low energy.
-%  * Better clarification about previous gtlike validation of extended source analysis + Citation of Francesco's work.
-%  * Removed from the GeV/TeV extension size plots RX J1713+Vela Jr becuase they were not directly fit at TeV energies.
 
@@
 \cite{atwood_LAT_mission}.
-Using 2 years of all-sky surveying data, the LAT Collaboration published
-a catalog of 1873
-sources significantly detected at \gev energies called 2FGL \citep{second_cat}.
+Using 2 years of all-sky survey data, the LAT Collaboration published
+the second Fermi Source Catalog \citep[2FGL][]{second_cat}.
 The possible counterparts of many of these sources can be spatially resolved
@@
 we expect the spectral parameters found with \gtlike to be slightly more
-precise.  Furthermore, because \gtlike is the standard likelihood analysis
+accurate.  Furthermore, because \gtlike is the standard likelihood analysis
 package, it has been more extensively validated for spectral analysis.
@@
 space and the model hypothesis adding a single degree of freedom and
-leads to the often quoted result that the square root of the test
-statistic is the number of $\sigma$ of the detection. It is plausible
+leads to the often quoted result $\sqrt{TS}=\sigma$. It is plausible
 to expect a similar distribution of the test statistic in the test for
@@
 $\Phi$ replaced by the source radius $r$ and $r<0$ being unphysical).
-We performed Monte Carlo simulations to calculate empirical distributions
-for $\tsext$ and we compared them to Equation~\ref{ts_ext_distribution}.
+To verify Equation~\ref{ts_ext_distribution}, we evaluated the
+empirical distribution function of \tsext computed from simulated sources.
 
@@
 \citep{sreekumar_isotropic}.  The Monte Carlo simulation was performed
-over a one-year observation period using a representative rocking profile and a
-representative livetime fraction of 0.8.  The reconstruction was performed
+over a one-year observation period using a representative 
+spacecraft orbit and livetime.
+The reconstruction was performed
 using the P7\_V6 Source class event selection and IRFs \citep{lat_on_orbit_psf}. For each 
@@
 exposure against 10 times
-the isotropic background measured by EGRET. This background is representative of the
-background near the Galactic plane.  For small extended sources, our
-detection threshold improves by a factor larger than the square root
-of the exposure because at high energies, where we are most sensitive
-to extension, the background levels are in the Poisson instead of the
-Gaussian regime.  For large extended sources, the relevant background
-is over a larger spatial range and so the improvement is closer to the
-expected factor corresponding to the square root of the exposure.
+the isotropic background measured by EGRET. This background is
+representative of the background near the Galactic plane.  For small
+extended sources, our detection threshold improves by a factor larger
+than the square root of the exposure because the LAT is signal-limited
+at high energies where we are most sensitive to extension. For large
+extended sources, the relevant background is over a larger spatial range
+and so the improvement is closer to the expected factor corresponding
+to the square root of the exposure.
 
@@
 \end{equation} 
+For the following analysis of LAT data, \tsinc was computed
+by fitting the spectra of the two point-like sources in \gtlike using the best fit positions
+of the sources found by \pointlike.
+
 \tsinc cannot be quantitatively compared to \tsext using a simple
@@
 study.  We simulated one spatially extended source and fit it as both
-an extended source and as two point-like sources.  We then simulated two
-point-like sources and fit them with the same two hypotheses. By comparing
-the distribution of \tsinc and \tsext for the two cases, we evaluated
-how good the $\tsext>\tsinc$ test is at rejecting the possibility of
-source confusion as well as how likely it is to incorrectly reject 
-with this test that an extended source is 
-spatially extended.  All sources were simulated using
-the same two-year time range included in 2FGL and all fit values were
-calculated using \pointlike. The simulations were performed against
-an background 10 times the isotropic background measured by EGRET,
-representative of the background near the Galactic plane.
+an extended source and as two point-like sources using \pointlike.
+We then simulated two point-like sources and fit them with the same two
+hypotheses. By comparing the distribution of \tsinc and \tsext computed by
+\pointlike for the two cases, we evaluated how good the $\tsext>\tsinc$
+test is at rejecting the possibility of source confusion as well as how
+likely it is to incorrectly reject that an extended source is spatially
+extended.  All sources were simulated using the same time range as in
+Section~\ref{extension_sensitivity} against a background 10 times the
+isotropic background measured by EGRET, representative of the background
+near the Galactic plane.
 
 We did this study first in the energy range from 1 \gev to 100 \gev by
-simulating extended sources of flux $4\times10^{-9} \phflux$ integrated
+simulating extended sources of flux $4\times10^{-9}$ \phflux integrated
 from 1 \gev to 100 \gev with a power-law spectral model with
 spectral index 2.  This flux was picked to be representative of the
-new extended sourced that were discovered in the following analysis
+new extended sources that were discovered in the following analysis
 when looking in the 1 \gev to 100 \gev energy range
@@
 of freedom (two spatial and two spectral parameters)
-than one extended source (one extension parameter)
 and can therefore easy model
@@
 when testing the two simulated point-like sources for extension our test
-did a better job at separating the distribution of \tsinc and \tsext
-and found that \tsinc was larger than \tsext.
+found that \tsinc was larger than \tsext.
 This is because the one additional extension parameter is less able to
 model the second source or statistical fluctuations.
-
 From this, we conclude that the $\tsext>\tsinc$ test is 
@@
 from two point-like sources instead of from a spatially extended
-source. On the other hand, because of the large values of \tsinc
-in figure~\ref{confusion_plot}a and figure~\ref{confusion_plot}b when
-fitting spatially extended sources, we caution that even in the case of
-their being spatially extended emission the fit of two point-like sources
-can often seem (by comparing the likelihoods) to be almost as good.
+source.
 
@@
 
-Even though this dedicated monte carlo study was performed using
-\pointlike, for the analysis of LAT data we took the best fit positions
-of the two point-like sources and refit them using \gtlike.  We quote
-\tsinc calculated with \gtlike using the best fit positions of the two
-point-like sources found using \pointlike.
-
 \section{Test of 2LAC Sources}
@@
 Following 2FGL, the LAT Collaboration published the Second LAT AGN
-Catalog (2LAC), a list a list of high latitude ($|b|>10\degree$) sources
+Catalog (2LAC), a list of high latitude ($|b|>10\degree$) sources
 that had a high probability association with AGN \citep{second_agn_cat}.
@@
 
-As further validation of our extended source method for studying
+As further validation of our method for studying
 spatially extended sources, we reanalyzed the twelve spatially extended
@@
 we fit the extension of MSH\,15$-$52 to be consistent with the published
-size but with an extension significance of \tsext=6.6.
+size but with \tsext=6.6.
 
@@
 In particular, because the alternate model uses the same underlying gas
-maps it is unable to asses systematics due to mischaracterization of local
-diffuse structure due to lack lack of resolution of the underlying maps.
+maps it is unable to assess systematics due to mischaracterization of local
+diffuse structure due to lack of resolution of the underlying maps.
 
@@
 As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
-galactic latitude where the source density is not as great and the
+galactic latitude where the source density is not as large and the
 diffuse emission is less structured, this method works well.
@@
 in the region close to an extended source could be biased by not correctly
-modeling the
-sources' extension.  Since 2FGL produced a
+modeling the extension of the source.  Since 2FGL produced a
 list of sources significant at energies above 100 \mev whereas we are
@@
 To account for these issues, we first produced a large list of possibly
-extended sources employing a very liberal search criteria and then
+extended sources employing very liberal search criteria and then
 refined the analysis of the promising candidates on a case by case basis.
@@
 and by uncertainties in our modeling of the Galactic diffuse emission. 
-In addition, the Galactic
-diffuse emission is more pronounced at lower energies due to its steep
-energy spectrum compared to the typical spectrum of extended sources \citep{intermediate_diffuse_lat}.
 For that reason,
@@
 most significantly extended source IC443 when it is modeled both as a
-point-like sources and an extended source.  The residual test statistic
+point-like source and an extended source.  The residual test statistic
 map indicates
@@
 residual in the region after modeling the source as being spatially extended.
-We also generated maps of the sum of all counts within a given distance of
+We also generated plots of the sum of all counts within a given distance of
 the source and compared it to the model predictions assuming the emission
@@
 to help guide our choice. For each extended source presented in 
-Section~\ref{new_ext_srcs_section}, we will describe any modification from 2FGL
+Section~\ref{new_ext_srcs_section}, we describe any modification from 2FGL
 of the background model that were performed.
@@
 The best fit position of nearby point-like sources can be influenced by
-the spatial model of a nearby extended source and vice versa.  Similarly,
+the extended source and vice versa.  Similarly,
 the best fit position of nearby point-like sources in 2FGL can be biased
@@
 the result of confusion of two point-like sources, if $\tsext>\tsinc$.
-As was show in Section~\ref{dual_localization_method}, this test is
+As was shown in Section~\ref{dual_localization_method}, this test is
 fairly powerful at removing situations in which the emission actually
@@
 section~\ref{extended_source_search_method}.
-The spectral and spatial properties of these nine sources is summarized
+The spectral and spatial properties of these nine sources are summarized
 in Table~\ref{new_ext_srcs_table} and the results of our investigation of
@@
 After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension 
-$\sigma=0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
+$\sigma=0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with 
+$\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
 this source.
@@
 The fit extension of 2FGL\,J0823.0$-$4246
-matches well its inferred size at \gev energies.  The distance of Puppis A was
+matches well the size of Puppis A in X-ray.  The distance of Puppis A was
 estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
@@
 have an extension $\sigma=0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
-an extension significance of $\tsext=32.4$
+$\tsext=32.4$
 using photons with energies between 1 \gev and 100 \gev.  
@@
 have an extension of $\sigma=1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
-an extension significance of $\tsext=86.8$.  The LAT size matches
+$\tsext=86.8$.  The LAT size matches
 well the \tev morphology of Vela Jr.  While fitting the extension
@@
 2FGL\,J1615.0$-$5051 was found to have an extension 
-$\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ with an extension significance
-of \tsext=16.7.  
+$\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ 
+\tsext=16.7.  
 2FGL\,J1615.2$-$5138 was found
  to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
-with an extension significance of \tsext=46.5.
+with $\tsext=46.5$.
 To test for the possibility that
@@
 IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
-\cite{discovery_of_pwn_for_PSR_J1617-5055} discovered some additional
+\cite{discovery_of_pwn_for_PSR_J1617-5055} discovered additional
 diffuse emission towards the center of HESS\,J1616$-$508 using archival
@@
 
-2FGL\,J1615.2$-$5138 is spatialy coincident with 
+2FGL\,J1615.2$-$5138 is spatially coincident with 
 the extended \tev source HESS\,J1614$-$518.
@@
 and towards the center but in a relatively dim region of HESS\,J1614$-$518
-\citep{suazku_hess_j1614_518}.  Three hypothesis have been presented to
-explain this emission; either source A is an SNR powering the $\gamma$-ray
-emission, source A is a PWN powered by an undiscovered pulsar in either
-source A or B, and finally that the emission may arise from hadronic
+\citep{suazku_hess_j1614_518}.  Three hypotheses have been presented to
+explain this emission: either source A is an SNR powering the $\gamma$-ray
+emission; source A is a PWN powered by an undiscovered pulsar in either
+source A or B; and finally that the emission may arise from hadronic
 acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
@@
 was found to have an extension $\sigma=0\fdg35\pm0\fdg04_\stat\pm0\fdg02_\sys$
-with an extension significance of \tsext=26.9.  While fitting the
+with $\tsext=26.9$.  While fitting the
 extension of 2FGL\,J1632.4$-$4753c, we iteratively relocalized
@@
 radio source \citep{most_survey_galactic_plane} and argued for a single
-synchrotron process producing the radio, X-ray, and \tev emission,
+synchrotron and inverse Compton process producing the radio, X-ray, and \tev emission,
 likely due to a PWNe.  The increased size at \tev energies compared
@@
 \citep{rx_j1713_hess} and 2FGL\,J1712.4$-$3941 fit to an extension 
-$\sigma=0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with an extension significance
-of $\tsext=38.5$.
+$\sigma=0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with $\tsext=38.5$.
 
@@
 HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
-point-like 2FGL sources 2FGL\,J1836.8$-$0623c, and 2FGL\,J1839.3$-$0558c
+point-like 2FGL sources, 2FGL\,J1836.8$-$0623c and 2FGL\,J1839.3$-$0558c,
 that clearly represent distinct sources.  On the other hand, there is
@@
 With this model, 2FGL\,J1837.3$-$0700c was found to have an
-extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with an extension
-significance of $\tsext=18.5$. 
+extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with 
+$\tsext=18.5$. 
 While fitting the extension of 2FGL\,J1837.3$-$0700c,
@@
 was found to have an extension $\sigma=0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
-with an extension significance of $\tsext=116.4$.  Figure~\ref{snr_seds}
+with $\tsext=116.4$.  Figure~\ref{snr_seds}
 shows its spectrum.  The inferred size of this source at \gev energies
@@
     \fi
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v2/run.py
+    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v3/run.py
     \caption{
@@
     \newtext{
-    Distribution of the test statistic for the extension test when fitting
+    Cumulative distribution of the test statistic for the extension test when fitting
     the sources in the 1 GeV to 100 GeV energy range.

### 2011-11-09 extended_catalog/paper/extended_catalog.tex
adding everybodys changes

@@
 Spatial extension is an important characteristic for correctly
-associating LAT sources with their counterparts at other wavelengths
+associating $\gamma$-ray-emitting sources with their counterparts at other wavelengths
 and for obtaining an unbiased model of their spectra.  We present a new
@@
 simulations to validate this tool and calculate the LAT threshold for
-detecting the spatial extension of sources.  We then test all sources
+detecting the spatial extension of sources.  
+\newtext{
+We then test all sources
 in the second \fermi-LAT catalog (2FGL) for extension. 
-We report the
-detection of seven spatially extended sources in addition to the twelve
-spatially extended sources reported in 2FGL and two others studied
-in dedicated publications.
+We report the detection of seven new spatially extended sources.
+}
 \end{abstract}
@@
 and galaxy clusters are expected to be spatially resolvable at
-\gev energies.  Dark matter satellites are also hypothesized to
+\gev energies.  Additionally, dark matter satellites are also hypothesized to
 be spatially extended.  The Large Area Telescope
@@
 at \gev energies are positionally coincident with sources that exhibit
-extension at other wavelengths, large enough to be spatially
+large enough extension at other wavelengths to be spatially
 resolvable by the LAT at \gev energies.
@@
 interactions with interstellar matter and by relativistic electrons
-due to Inverse Compton (IC) scattering and Bremsstrahlung radiation.  
+due to Inverse Compton (IC) scattering and bremsstrahlung radiation.  
 It is plausible that the \gev and
@@
 
-Previous analysis of extended LAT sources was performed as dedicated
+Previous analyses of extended LAT sources were performed as dedicated
 studies of individual sources so we expect that a systematic scan of
@@
 
-A new analysis tool has been developed to address the unique requirements
-for studying spatially extended sources with the LAT.
-The Poisson likelihood to find
-the observing counts is maximized given a parametrized spatial and
-spectral model of the source and its surrounding region.  The sky is
-divided into cubes of space and energy using the healpix representation
-of the sky \citep{healpix} and the likelihood is maximized over all bins
-in a region.  The extension of a source can be modeled by a geometric
-shape (e.g. a disk or a two-dimensional Gaussian) and the position, extension,
-and spectrum of the source
-can be simultaneously fit.
+\newtext{
+A new maximum-likelihood analysis tool has been developed to address the
+unique requirements for studying spatially extended sources with the LAT.
+It works by maximizing the Poisson likelihood to find the observing counts
+given a parametrized spatial and spectral model of the sky.  
+Space is
+divided into cubes of position and energy using the healpix representation of
+the sky \citep{healpix} and the likelihood is maximized over all bins in
+a region.
+}
+The extension of a source can be modeled by a geometric shape
+(e.g. a disk or a two-dimensional Gaussian) and the position, extension,
+and spectrum of the source can be simultaneously fit.
 
@@
 spatial extension fitting on \pointlike rather than \gtlike was made
-on considerations of computing time.  The \pointlike algorithm was
+due to considerations of computing time.  The \pointlike algorithm was
 optimized for speed to handle larger numbers of sources efficiently,
@@
 Although these shapes are significantly different,
-Figure~\ref{compare_disk_gauss} shows that their PDF 
-are similar for a source that has a 
-0\fdg5
-radius
-typical of LAT detected extended sources.
-To
-allow a valid comparison between the Gaussian and the uniform surface
-brightness morphologies,
-we define the source size 
-as the radius containing
-68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
-and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
-is defined in Equation~\ref{gauss_pdf} and
-Equation~\ref{disk_pdf} respectively.
-For this example, $\rsixeight=0\fdg5$ so
-$\sigma_\text{disk}=0.61\degree$ and 
-$\sigma_\text{Gaussian}=0.33\degree$.
+Figure~\ref{compare_disk_gauss} shows that, after convolution with the
+LAT PSF, their PDF are similar for a source that has a 0\fdg5 radius
+typical of LAT detected extended sources.  To allow a valid comparison
+between the Gaussian and the uniform surface brightness morphologies,
+we define the source size as the radius containing 68\% of the
+intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
+and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$ is defined
+in Equation~\ref{gauss_pdf} and Equation~\ref{disk_pdf} respectively.
+For this example, $\rsixeight=0\fdg5$ so $\sigma_\text{disk}=0.61\degree$
+and $\sigma_\text{Gaussian}=0.33\degree$.
 
@@
 
-It is impossible to discriminate with LAT data exclusively between a
+It is impossible to discriminate using only LAT data between a
 spatially extended source and multiple point-like sources separated by
@@
 we define \tsinc as twice the increase in the log of the likelihood
-fitting the region as two point-like sources compared to fitting the
-region as one point-like source:
+fitting the region with two point-like sources compared to fitting the
+region with one point-like source:
 \begin{equation}
@@
 hypotheses. By comparing the distribution of \tsinc and \tsext computed by
-\pointlike for the two cases, we evaluated how good the $\tsext>\tsinc$
-test is at rejecting the possibility of source confusion as well as how
+\pointlike for the two cases, we evaluated how effective the $\tsext>\tsinc$
+test is at rejecting cases of source confusion as well as how
 likely it is to incorrectly reject that an extended source is spatially
@@
 extended sources with typical
-sizes ($\sigma\sim0\fdg5$), one can often obtain almost as good 
+sizes ($\sigma\sim0\fdg5$), one can often obtain almost as large
 an increase in likelihood
@@
 This effect is most pronounced when using photons with energies between 1
-\gev and 100 \gev where the PSF is even larger.  
+\gev and 100 \gev where the PSF is larger.  
 On the other hand,
@@
 extension.  \gev emission from AGN is believed to originate from the
-cores of kiloparsec-scale jets of distant galaxies.  Therefore AGN are
+cores of kiloparsec-scale jets.  Therefore AGN are
 not expected to be spatially resolvable by the LAT and provide a good
@@
 
-We should clarify that the LAT PSF used in this study was determined
+We note that the LAT PSF used in this study was determined
 empirically by fitting the observed shape of bright AGN (see
@@
 was determined by detector simulations which were verified in accelerator
-tests \citep{atwood_LAT_mission}. However, in-flight data revealed
+beam tests \citep{atwood_LAT_mission}. However, in-flight data revealed
 a discrepancy above a few \gev in the PSF compared to the angular
@@
 spatial distribution of the intensities within the ROI as predicted by
-the model.  We distinguished contributions from CR interactions with the
-molecular hydrogen, the atomic+ionized hydrogen, residual gas traced
+the model.  We distinguished contributions from cosmic-ray interactions with the
+molecular hydrogen, the atomic and ionized hydrogen, residual gas traced
 by dust \citep{isabelle_dark_gass}, and the interstellar radiation
@@
 the position and extension of the analyzed spatially extended
-sources until the overall fit globally converged.  For each extended
+sources until the overall fit converged globally.  For each extended
 source, we will describe the position of any relocalized background
@@
 of the sources in the region using \pointlike, we refit the spectral
-parameters of the region using \gtlike.  Using \gtlike, we obtained a
+parameters of the region using \gtlike.  With \gtlike, we obtained a
 second measure of \tsext.  We only consider a source to be extended when
@@
 star-forming regions that are bright in infrared.  The region also has
-abundant molecular and atomic gas traced by CO and HI but also plenty of
+abundant molecular and atomic gas traced by CO and HI and significant 
 dark gas found only by its association with dust emission
@@
 
-Many of the \tev detected extended sources now seen at \gev energies are
-currently unidentified and further multiwavelength follow-up observations
-will be necessary to understand these particle accelerators.  But the
-extension of the spectrum of these \tev sources towards lower energies
-by LAT observations can help to determine the origin and nature of the
-high-energy emission seen from these sources.
+Many of the \tev detected extended sources now seen at \gev energies
+are currently unidentified and further multiwavelength follow-up
+observations will be necessary to understand these particle accelerators.
+But extending the spectra of these \tev sources towards lower energies
+with LAT observations may help to determine the origin and nature of
+the high-energy emission.
 

### 2011-11-10 extended_catalog/paper/extended_catalog.tex
updating draft

@@
 have no detectable extension.  High-energy $\gamma$-rays from
-these sources are produced by the decay of $\pi^0$s produced by hadronic
+\tev sources are produced by the decay of $\pi^0$s produced by hadronic
 interactions with interstellar matter and by relativistic electrons
@@
 high-energy particles and so at least some of these sources should be
-detected at \gev energies.  Studying 
+detectable at \gev energies.  Studying 
 these \tev sources at \gev energies would help to
@@
 Space is
-divided into cubes of position and energy using the healpix representation of
+divided into cubes of position and energy using the HEALPix representation of
 the sky \citep{healpix} and the likelihood is maximized over all bins in
@@
 FSSC.} because it can only fit the spectral parameters of the model
-unless a more sophisticated iterative procedure is used to also test
-various source morphologies.  We note that \gtlike has been used in the
+unless a more sophisticated iterative procedure is used.  
+We note that \gtlike has been used in the
 past in several studies of source extension in the LAT Collaboration
@@
 position, extension, and spectrum is important to maximize
-the statistical significance of the detection of extension of a source.
+the statistical significance of the detection of the extension of a source.
 To avoid projection effects, the longitude and latitude 
@@
 \newtext{
-The LAT's PSF is currently parameterized 
+The PSF of the LAT is currently parameterized 
 in the Pass~7\_V6 (P7\_V6) Source Instrument
@@
 surface brightness profile as our spatial extension shape. Unless otherwise noted,
-we quote the radius of the edge ($\sigma$) as the size of the source.
-
-\section{Validation of Analysis Method}
+we quote the radius to the edge ($\sigma$) as the size of the source.
+
+\section{Validation of the Analysis Method}
 
@@
 null hypothesis (source flux $\Phi=0$) residing on the edge of parameter
-space and the model hypothesis adding a single degree of freedom and
-leads to the often quoted result $\sqrt{TS}=\sigma$. It is plausible
-to expect a similar distribution of the test statistic in the test for
+space and the model hypothesis adding a single degree of freedom.
+It leads to the often quoted result $\sqrt{TS}=\sigma$. It is plausible
+to expect a similar distribution for the test statistic in the test for
 source extension since the same conditions apply (with the source flux
@@
 spectral model with integrated fluxes above 100 \mev ranging from $3\times10^{-9}$ 
-to $1\times10^{-6}$ \phflux in six discrete steps and spectral
-indices ranging from 1.5 to 3 in four discrete steps.  These values
-were picked to represent typical source parameters of LAT-detected
+to $1\times10^{-5}$ \phflux and spectral
+indices ranging from 1.5 to 3.  These values
+were picked to represent typical parameters of LAT-detected
 sources. The point-like sources were simulated on top of an isotropic
@@
 significance.  The cumulative density of \tsext is plotted in
-Figure~\ref{ts_ext_mc_1000} and Figure~\ref{ts_ext_mc_10000} 
+Figure~\ref{ts_ext_mc_1000} and \ref{ts_ext_mc_10000} 
 and compared to the $\chi^2_1/2$ distribution of
@@
 Equation~\ref{ts_ext_distribution}. To the extent that there is
-disagreement, the simulations tended to produce smaller than expected
+a discrepancy, the simulations tended to produce smaller than expected
 values of \tsext which would make the formal significance conservative.
@@
 which the value of $\tsext$ averaged over many statistical realizations is
-$\langle\tsext\rangle=16$ for a source of a given flux and true extension
+$\langle\tsext\rangle=16$ 
 \newtext{
-(corresponding to a formal $4\sigma$ significance).
+(corresponding to a formal $4\sigma$ significance)
+for a source of a given flux and extension.
 }
@@
 energy bins between 100 \mev and 100 \gev. For IC443, which has a
-spectral index $\sim2.4$ and an extension $\sigma=\sim0\fdg35$, 
+spectral index $\sim2.4$ and an extension $\sim0\fdg35$, 
 almost the entire increase in likelihood
@@
 from energies above 1 \gev.  Furthermore, other systematic errors
-become increasingly important at low energy. For our extension search
+become increasingly large at low energy. For our extension search
 (Section~\ref{extended_source_search_method}),
@@
 To assess the plausibility of source confusion for situations
-in which $\tsext>16$, we developed an algorithm in \pointlike to
+in which $\tsext\ge16$, we developed an algorithm in \pointlike to
 simultaneously fit the position and spectrum of two point-like sources.
@@
 \end{equation} 
+\newtext{
 For the following analysis of LAT data, \tsinc was computed
@@
 of the sources found by \pointlike.
+}
 
@@
 simulating extended sources of flux $4\times10^{-9}$ \phflux integrated
-from 1 \gev to 100 \gev with a power-law spectral model with
+from 1 \gev to 100 \gev and a power-law spectral model with
 spectral index 2.  This flux was picked to be representative of the
@@
 \newtext{
-Figure~\ref{confusion_plot}a shows 
+Figure~\ref{confusion_extended_plot}a shows the distribution
+of \tsext and \tsinc and 
+Figure~\ref{confusion_extended_plot}c shows 
 the distribution of $\tsext-\tsinc$ as a
@@
 for 200 statistically independent simulations.
-}
-
-Figure~\ref{confusion_plot}c shows the same plot but when fitting
-simulations of two point-like sources each with half of the flux of
+
+Figure~\ref{confusion_2pts_plot}a shows the same plot but when fitting
+two simulated point-like sources each with half of the flux of
 the spatially extended source and with the same spectral index as the
-extended source.  Finally, figure~\ref{confusion_plot}e shows the same
+extended source.  Finally, figure~\ref{confusion_2pts_plot}c shows the same
 plot with each point-like source having the same flux but different
@@
 
-The same three plots are shown in figure~\ref{confusion_plot}b,
-figure~\ref{confusion_plot}d, and figure~\ref{confusion_plot}f but this
-time when analyzing a source of flux $10^{-9} \phflux$ (integrated from
+The same four plots are shown in figure~\ref{confusion_extended_plot}b, \ref{confusion_extended_plot}d, 
+\ref{confusion_2pts_plot}b, and \ref{confusion_2pts_plot}d but this
+time when analyzing a source of flux $10^{-9}$ \phflux (integrated from
 10 \gev to 100 \gev) only in the 10 \gev to 100 \gev energy range.
@@
 Several interesting conclusions can be made from this study. The overall
-behavior of these plots is what one would expect. \tsext is on average
-greater than \tsinc when fitting simulated extended sources whereas
-\tsinc is greater than \tsext when fitting two simulated point-like sources.
-Furthermore, the distributions of \tsext and \tsinc separate better
-when the extended source is bigger or when the two point-like sources are
-farther apart.
-
-The distributions also show that for simulated
-extended sources with typical
-sizes ($\sigma\sim0\fdg5$), one can often obtain almost as large
-an increase in likelihood
-with two sources as with one extended source ($\tsinc\sim\tsext$).
-This is because although
-two point-like sources represent an incorrect spatial model, 
-the two point-like sources have four additional degrees
-of freedom (two spatial and two spectral parameters)
-and can therefore easy model
-the extended source and statistical fluctuations in the data.
-This effect is most pronounced when using photons with energies between 1
-\gev and 100 \gev where the PSF is larger.  
-On the other hand,
-when testing the two simulated point-like sources for extension our test
-found that \tsinc was larger than \tsext.
-This is because the one additional extension parameter is less able to
-model the second source or statistical fluctuations.
+behavior of these plots is what one would expect. $\tsext-\tsinc$
+is mostly positive when fitting the simulated extended sources in
+Figure~\ref{confusion_extended_plot} whereas $\tsext-\tsinc$ is
+mostly negative when fitting the two simulated point-like sources in
+Figure~\ref{confusion_2pts_plot}.  
+Furthermore, $\tsext-\tsinc$ becomes more positive when the extended
+soruce becomes larger and more negative when the two point-like sources
+are farther apart.
 From this, we conclude that the $\tsext>\tsinc$ test is
-powerful at discarding cases in which the true emission is derived
-from two point-like sources instead of from a spatially extended
-source.
+powerful at discarding cases in which the true emission comes from
+two point-like sources without frequently rejecting real extended sources.
+
+The other interesting feature in Figure~\ref{confusion_extended_plot}a
+and \ref{confusion_extended_plot}b is that for simulated extended
+sources with typical sizes ($\sigma\sim0\fdg5$), one can often obtain
+almost as large an increase in likelihood fitting the source as two
+point-like sources ($\tsinc\sim\tsext$).  This is because although the
+two point-like sources represent an incorrect spatial model, the second
+source has four additional degrees of freedom (two spatial and two
+spectral parameters) and can therefore easy model much of the extended
+source and statistical fluctuations in the data.  This effect is most
+pronounced when using photons with energies between 1 \gev and 100 \gev
+where the PSF is broader.
+}
 
@@
 point-like sources. But it could always be the case that an extended
-source candidate is actually the superposition of multiple point-like or
+source is actually the superposition of multiple point-like or
 extended sources that could be resolved with deeper observations of the
@@
 When analyzing sources in \pointlike, we used a circular $10\degree$ region of
-interest (ROI) centered on our source.  
+interest (ROI) centered on our source and eight energy bins per
+logarithmic decade in energy.
 When refitting the region in \gtlike using the best fit spatial and
@@
 these sources are significantly extended using our systematic 
-method that assumed a radially-symmetric uniform surface
+method assuming a radially-symmetric uniform surface
 brightness profile.  On the other hand, for some of
@@
 % 3 PWN
-Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137 were
+Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were
 identified in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  
@@
 with energies between 10 \gev and 100 \gev.
-To improve our analysis of this source, we had to remove
+To improve our analysis of this source, removed
 from our background model 
@@
 of the Galactic diffuse emission were fitted individually using a
-spatial distribution of the intensities within the ROI as predicted by
+spatial distribution predicted by
 the model.  We distinguished contributions from cosmic-ray interactions with the
@@
 
-But this is infeasible in the galactic plane where we are most likely expect
+But this is infeasible in the galactic plane where we most likely expect
 to discover new spatially extended sources.  In the galactic plane,
@@
 study in Section~\ref{dual_localization_method}
-showed that the overall likelihood would greatly increase when fitting
+showed that the overall likelihood would greatly increase by fitting
 a spatially extended source as two point-like sources so we expect
@@
 confusion is less of an issue.  A similar procedure was used to detect
-the spatial extension of hess\,j1825$-$137 and msh\,15$-$52 with the
-lat \citep{msh1552,fermi_hess_j1825}.
+the spatial extension of HESS\,j1825$-$137 and MSH\,15$-$52 with the
+LAT \citep{msh1552,fermi_hess_j1825}.
 }
@@
 most significantly extended source IC443 when it is modeled both as a
-point-like source and an extended source.  The residual test statistic
+point-like source and as an extended source.  The residual test statistic
 map indicates
@@
 the best fit position of nearby point-like sources in 2FGL can be biased
-by systematic errors at lower energies.
+by systematic issues at lower energies.
 Therefore, after selecting the list of background sources, we iteratively
@@
 studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
-Jr. \citep{rx_j1713_lat,vela_jr_lat}
+Jr. \citep{rx_j1713_lat,vela_jr_lat}.
 Two of these sources were
@@
 do not appear to represent physically distinct sources.
-We concluded that
+We conclude that
 these nearby point-like sources
@@
 2FGL\,J1615.0$-$5051 was found to have an extension 
-$\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ 
-\tsext=16.7.  
+$\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ and
+\tsext=16.7 and
 2FGL\,J1615.2$-$5138 was found
@@
 
+\newtext{
+
 2FGL\,J1632.4$-$4753c was found by our search to be an extended source
@@
 2FGL\,J1636.3$-$4740c to $(l,b)=(336\fdg97,-0\fdg07)$.
+}
 
@@
     statistically independent simulations and the average value of \ts is
-    also tabulated.  The models span representative spectral parameters.
+    also tabulated.  
     }
@@
     Cumulative distribution of the test statistic for the extension test when fitting
-    the sources in the 1 GeV to 100 GeV energy range.
+    simulated point-like sources in the 1 GeV to 100 GeV energy range.
     The four plots
-    represent simulated point-like sources of different spectral indices and
+    represent simulated sources of different spectral indices and
     the different lines (colored in the online version) 
@@
   \thispagestyle{empty}
-\begin{deluxetable}{rrrrrrrrrrrrrrrrrrrrrrr}
+\begin{deluxetable}{rr|rrrrrrrrrrrrrrrrrrrrr}
 \tablecolumns{22}
@@
     \caption{
-    The projected detection threshold of the LAT to extension after a ten-year exposure
+    The projected detection threshold of the LAT to extension after ten years
     for a power-law
@@
     \ifcolorfigure
-    \plotone{mc_plots/confusion_plot_color.eps}
+    \plotone{mc_plots/confusion_extended_plot_color.eps}
     \else
-    \plotone{mc_plots/confusion_plot_bw.eps}
+    \plotone{mc_plots/confusion_extended_plot_bw.eps}
     \fi
@@
     \newtext{
-    The distribution of $\tsext-\tsinc$ 
-    (a) and (b) when fitting simulated spatially extended sources with
-    radially-symmetric uniform intensity surface profiles and varying
-    the size of the source and (c), (d), (e), and (f) when fitting two
-    simulated point-like sources and varying their separation distance.
-    (c), and (d) represent simulations of two point-like sources with
-    the same spectral index and (e), and (f) represent simulations of
-    two point-like sources with different spectral indices.  (a), (c),
-    and (e) fit the simulated sources in the 1 \gev to 100 \gev energy
-    range and (b), (d), and (f) when fitting the simulated sources
-    in the 10 \gev to 100 \gev energy range. The plus-shaped markers
-    (colored red in the electronic version) are fits where $\tsext\ge16$
-    that would be considered as extended.
-    }
-    }\label{confusion_plot}
+    (a) and (b) are the distribution of \tsext and of \tsinc when
+    fitting simulated spatially extended sources of varying sizes as
+    both an extended source and as two point-like sources.  (c) and
+    (d) are the distribution of $\tsext-\tsinc$ for the same simualted sources.
+    (a) and (c) represent sources fit in the 1 \gev to 100 \gev energy
+    range and (b) and (d) represent sources fit in the 10 \gev to
+    100 \gev energy range.  In (c) and (d), the plus-shaped markers
+    (colored red in the electronic version) are fits where $\tsext\ge16$.
+    }
+    }\label{confusion_extended_plot}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{mc_plots/confusion_2pts_plot_color.eps}
+    \else
+    \plotone{mc_plots/confusion_2pts_plot_bw.eps}
+    \fi
+    % this plot came from 
+    \caption{
+    \newtext{
+    The distribution of $\tsext-\tsinc$ when fitting two simulated
+    point-like sources of varying separation distances as
+    both an extended source and as two point-like sources.  (a),
+    and (b) represent simulations of two point-like sources with the
+    same spectral index and (d) and (e) represent simulations of two
+    point-like sources with different spectral indices.  (a) and (c)
+    fit the simulated sources in the 1 \gev to 100 \gev energy range
+    and (b) and (d) fit in the 10 \gev to 100 \gev energy range.
+    The plus-shaped markers (colored red in the electronic version)
+    are fits where $\tsext\ge16$.
+    }
+    }\label{confusion_2pts_plot}
   \end{figure}
@@
   IC443 modeled as an extended source. The cross represents the best
+  fit position of IC443.
   }
@@
     The \gev size of Vela X is taken from \cite{velax}.  
+    \newtext{
     Because of their large size, the shape of RX\,J1713.7$-$3946 and
@@
     Centaurus A is not included because of its large size.
+    }
     }\label{gev_vs_tev_histogram}

### 2011-11-29 extended_catalog/paper/extended_catalog.tex
new version
updateing text

@@
 detecting the spatial extension of sources.  
-\newtext{
 We then test all sources
@@
 We report the detection of seven new spatially extended sources.
-}
 \end{abstract}
@@
 HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
-nearby galaxies, the Large and Small Magellanic Clouds, and one
+nearby galaxies, the Large and Small Magellanic Clouds, 
+and the lobes of one
 radio galaxy, Centaurus A, were spatially resolved at \gev energies
@@
 
-\newtext{
 A new maximum-likelihood analysis tool has been developed to address the
@@
 a region.
-}
 The extension of a source can be modeled by a geometric shape
@@
 to build a profile of the likelihood as a function of extension.
-\newtext{
-The \gtlike likelihood profile approach has been show to correctly
+The \gtlike likelihood profile approach has been shown to correctly
 reproduce the extension of simulated extended sources assuming that the
@@
 simulations have been run to calculate its false detection rate.
-}
 
@@
 
-In \pointlike, it is assumed that the spatial and spectral model
-of an extended source are separable, i.e. that the source model
-$M(l,b,E)=S(l,b)\times X(E)$ where $S(l,b)$ is the spatial distribution
+In \pointlike, one can fit the position and extension 
+of a source under the assumption that the source model
+can be factorized:
+$M(l,b,E)=S(l,b)\times X(E)$, where $S(l,b)$ is the spatial distribution
 and $X(E)$ is the spectral distribution.  To fit an extended source,
@@
 \end{equation}
-where $I_\text{src}(\vec r')$ is the spatial distribution of the
+where $\vec r$ represents the position in the sky and
+$I_\text{src}(\vec r)$ is the spatial distribution of the
 source.
-\newtext{
 The PSF of the LAT is currently parameterized 
@@
 Response Function \citep[IRFs,][]{lat_on_orbit_psf} by a King function \citep{king_function}:
-}
 \begin{equation}
@@
   \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
-  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
+  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right),
 \end{align}
@@
 the position of the source and varying the extension until the
-likelihood has fallen by \onehalf, corresponding to a $1\sigma$ error
+likelihood has fallen by 1/2, corresponding to a $1\sigma$ error
 \citep{Statistical_methods_book}.  Figure~\ref{four_plots_ic443}
@@
 background with a power-law spectral model with
-integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux
+integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux sr$^{-1}$
 and spectral index 2.1.
@@
 to fit the source as an extended source and calculate \tsext.
-\newtext{
 This entire procedure was performed twice, once fitting in the 1 \gev
@@
 (correspond to a formal $4\sigma$ significance) is reasonable.
-}
 
@@
 $\langle\tsext\rangle=16$ 
-\newtext{
 (corresponding to a formal $4\sigma$ significance)
-for a source of a given flux and extension.
-}
+for a source of a given extension.
 
@@
 \end{equation} 
-\newtext{
 For the following analysis of LAT data, \tsinc was computed
@@
 of the sources found by \pointlike.
-}
 
@@
 up to $1\degree$.  
-\newtext{
 Figure~\ref{confusion_extended_plot}a shows the distribution
@@
 Furthermore, $\tsext-\tsinc$ becomes more positive when the extended
-soruce becomes larger and more negative when the two point-like sources
+source becomes larger and more negative when the two point-like sources
 are farther apart.
@@
 source has four additional degrees of freedom (two spatial and two
-spectral parameters) and can therefore easy model much of the extended
+spectral parameters) and can therefore easily model much of the extended
 source and statistical fluctuations in the data.  This effect is most
@@
 where the PSF is broader.
-}
 
@@
 
-For all following LAT analysis, we used the same two-year dataset
+For all following LAT analyses, we used the same two-year dataset
 that was used in 2FGL spanning from 2008 August 4 to 2010 August 1. We
@@
 mentioned, we used the same background model as 2FGL to represent the
-Galactic diffuse, isotropic, and Earth limb emission.  To account for
+Galactic diffuse, isotropic, and Earth limb emission.  To compensate for
 possible residuals in the diffuse emission model, the galactic emission
@@
 
-\newtext{
 Of the 885 clean AGN, we selected the 733 of these 2FGL sources which
@@
 to the $\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
-and is shown in Figure~\ref{agn_ts_ext}.  The \tsext distribution
+in Figure~\ref{agn_ts_ext}.  The \tsext distribution
 for the AGN shows reasonable agreement with the theoretical
@@
 detection of the extension of a source.
-}
 
@@
 and the Small Magellanic
-Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
+Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  
+Their extension was significantly
 detected using photons with energies between
@@
 with energies between 10 \gev and 100 \gev.
-To improve our analysis of this source, removed
+To improve our analysis of this source, we removed
 from our background model 
@@
 empirical parameterization is used in the P7\_V6 IRFs.  To account for
-our uncertainty in our knowledge of the PSF, we refit our extended source
+the uncertainty in our knowledge of the PSF, we refit our extended source
 candidates using the pre-flight Monte Carlo representation of the PSF
@@
 
-% Alternate Diffuse
+% Alternative Diffuse Model
 
@@
 model does not test all systematics related to the diffuse emission model.
-In particular, because the alternate model uses the same underlying gas
+In particular, because the alternative model uses the same underlying gas
 maps it is unable to assess systematics due to mischaracterization of local
@@
 
-\newtext{
 We also performed a second search for extended sources using only
@@
 confusion is less of an issue.  A similar procedure was used to detect
-the spatial extension of HESS\,j1825$-$137 and MSH\,15$-$52 with the
-LAT \citep{msh1552,fermi_hess_j1825}.
-}
+the spatial extension of MSH\,15$-$52 and
+HESS\,J1825$-$137 with the LAT \citep{msh1552,fermi_hess_j1825}.
 
@@
 fit extension of the source overlaid. There appears to be large-scale
-residual in the diffuse emission in this region along the Galactic plane.
+residuals in the diffuse emission in this region along the Galactic plane.
 As a result, 2FGL\,J1856.2+0450c is fit to an extension of $\sim2\degree$
@@
 
-Because of these systematic issues, we only selected extended source
+We only selected extended source
 candidates in regions that did not appear dominated by these issues and
@@
 believed represented physically distinct sources and we removed 
-sources that we believed were included in 2FGL to account
-for residual induced by not modeling the extension of the source.
-\newtext{
+sources that we believed were included in 2FGL to compensate 
+for residuals induced by not modeling the extension of the source.
 Soft nearby point-like 2FGL sources that were not significant at higher energies
 were frozen to the spectrum predicted by 2FGL.
-}
 When deciding
@@
 both \pointlike and \gtlike agree that $\tsext>16$. 
-We further required that $\tsext>16$ using the alternate diffuse
-model presented in section~\ref{systematic_errors_on_extension}.
+We further required that $\tsext>16$ using the alternative diffuse
+model presented in Section~\ref{systematic_errors_on_extension}.
 We then replaced the spatially extended source with two point-like
@@
 these nearby point-like sources
-were included in 2FGL to account for residual induced
+were included in 2FGL to compensate for residuals induced
 by not modeling the extension of this source and
@@
 this SNR but do not appear to be physically distinct sources.
-They were most likely included in 2FGL to account for residual
+They were most likely included in 2FGL to compensate for residuals
 induced by not modeling the extension Vela Jr. and were removed
@@
 with the same extended \tev source as 2FGL\,J1615.2$-$5138.  We concluded
-that this source was included in 2FGL to account for residual induced
+that this source was included in 2FGL to compensate for residuals induced
 by not modeling the extension of 2FGL\,J1615.2$-$5138 and removed
@@
 The \tev counterpart of 2FGL\,J1615.0$-$5051 was fit
-with a radially-symmetric Gaussian surface brightness profile to have an
-extension $0\fdg136\pm0\fdg008$.  This \tev size corresponds to a 68\%
+with a radially-symmetric Gaussian surface brightness profile with
+$\sigma=0\fdg136\pm0\fdg008$.  This \tev size corresponds to a 68\%
 containment radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the
@@
 
-\newtext{
-
 2FGL\,J1632.4$-$4753c was found by our search to be an extended source
@@
 2FGL\,J1636.3$-$4740c to $(l,b)=(336\fdg97,-0\fdg07)$.
-}
-
-H.E.S.S measured a extension of $\sigma=0\fdg21\pm0\fdg05$ and
+
+H.E.S.S measured an extension of $\sigma=0\fdg21\pm0\fdg05$ and
 $0\fdg06\pm0\fdg04$ along the semi-major and semi-minor axes when
@@
 synchrotron and inverse Compton process producing the radio, X-ray, and \tev emission,
-likely due to a PWNe.  The increased size at \tev energies compared
+likely due to a PWN.  The increased size at \tev energies compared
 to X-ray energies has previously been observed in several aging PWNe
@@
 does not appear to represent a physically distinct source.  We concluded
-that this source was included in 2FGL to account for residual induced by
+that this source was included in 2FGL to compensate for residuals induced by
 not modeling the extension of this source and removed it from our model
@@
 was detected to be pulsed \citep[PSR\,J2021+4026,][]{first_lat_pulsar_cat}.
-This pulsar was also been observed by AGILE \citep{gamma_cygni_agile}.
+This pulsar was also observed by AGILE \citep{gamma_cygni_agile}.
 
@@
 emission of $\gamma$-Cygni and does not appear to represent a physically
-distinct source.  We concluded that it was included in 2FGL to account
-for residual induced by not modeling the extension of $\gamma$-Cygni and
+distinct source.  We concluded that it was included in 2FGL to compensate
+for residuals induced by not modeling the extension of $\gamma$-Cygni and
 removed it from our model of the sky.  With this model, 2FGL\,J2021.5+4026
-was found to have an extension $\sigma=0\fdg59\pm0\fdg03_\stat\pm0\fdg02_\sys$
-with $\tsext=116.4$.  Figure~\ref{snr_seds}
+was found to have an extension $\sigma=0\fdg63\pm0\fdg05_\stat\pm0\fdg04_\sys$
+with $\tsext=128.9$.  Figure~\ref{snr_seds}
 shows its spectrum.  The inferred size of this source at \gev energies
@@
     red in the online version) and for a point-like source (dashed and colored
-    blue in the online version).  (d) smoothed count map after subtraction
+    blue in the online version).  (d) smoothed counts map after subtraction
     of the diffuse emission compared to the smoothed
@@
 \tablecomments{
-\newtext{
     A list of the spectral models of the simulated point-like sources
@@
     also tabulated.  
-    }
 }
@@
     \caption{
-    \newtext{
     Cumulative distribution of the test statistic for the extension test when fitting
@@
     density function of Equation~\ref{ts_ext_distribution}.
-    }
     }\label{ts_ext_mc_1000}
@@
     \caption{
-    \newtext{
     The same plot as Figure~\ref{ts_ext_mc_10000} but fitting in the 10 \gev to 100 \gev energy 
     range.
-    }
     }\label{ts_ext_mc_10000}
@@
     \caption{
-    \newtext{
     (a) and (b) are the distribution of \tsext and of \tsinc when
@@
     (colored red in the electronic version) are fits where $\tsext\ge16$.
-    }
     }\label{confusion_extended_plot}
@@
     \caption{
-    \newtext{
     The distribution of $\tsext-\tsinc$ when fitting two simulated
@@
     are fits where $\tsext\ge16$.
-    }
     }\label{confusion_2pts_plot}
@@
 error on $\sigma$ is statistical and the second is systematic (see
-Section~\ref{systematic_errors_on_extension}).  Pos Err is the error on
+Section~\ref{systematic_errors_on_extension}).  
+The errors on the integral fluxes and the spectral indices
+are statistical only.
+Pos Err is the error on
 the position of the source.  Vela X and the Centaurus A Lobes were
@@
 $\ts_\pointlike$, $\ts_\gtlike$, and $\ts_\altdiff$ are the test
-statistic values from \pointlike, \gtlike, and \gtlike with the alternate
+statistic values from \pointlike, \gtlike, and \gtlike with the alternative
 diffuse model respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$,
 and $\tsext_\altdiff$ are the test statistic values of the extension
-test from \pointlike, \gtlike, and \gtlike with the alternate diffuse
+test from \pointlike, \gtlike, and \gtlike with the alternative diffuse
 model respectively.  $\sigma$, $\sigma_\altdiff$, and $\sigma_\altpsf$
-are the fit extension with the standard analysis, the alternate diffuse
-model, and the alternate PSF respectively.  \tsinc is the test statistic
+are the fit size assuming
+a uniform radially symmetric intensity distribution
+with the standard analysis, the alternative diffuse
+model, and the alternative PSF respectively.  \tsinc is the test statistic
 for the two point-like source hypothesis test 
@@
     The spectral errors are statistical only.
+    The upper limit is at the 95\% confidence level.
     }
@@
   online version) represents the 2FGL position of this source.
-  \newtext{
   The plus-shaped marker and the circle (colored red) 
@@
   and the black cross represents a background 2FGL source. 
-  }
   The
@@
   this source assuming a radially-symmetric uniform surface brightness profile.
-  \newtext{
   The three black crosses represent background 2FGL sources
@@
   marker (colored blue) represents the 2FGL and relocalized position of another 2FGL source.  
-  }
   This extended source is spatially
@@
     symmetric uniform surface brightness profile.  
-    \newtext{The two black crosses represent  background 2FGL sources and
+    The two black crosses represent  background 2FGL sources and
     the star-shaped
@@
     image of HESS\,J1616$-$508 (left) and HESS\,J1614$-$518 (right)
-    }
     \citep{hess_plane_survey}.   
@@
   brightness profile.  
-  \newtext{
   The four black crosses represent background 2FGL
@@
   additional background 2FGL sources subtracted in (b).
-  The star-shaped marker (colored green) represent another 2FGL
+  The star-shaped marker (colored green) represents another 2FGL
   source that was removed from the background model.  
-  }
   The contours (colored light blue) correspond to the \tev image of
@@
   \caption{
-  \newtext{
   A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
@@
   correspond to the \tev image \citep{rx_j1713_hess}.  
-  }
   }\label{2FGL_J1712.4-3941}
@@
   position of this source. 
-  \newtext{
   The plus-shaped marker and 
@@
   \citep{pulsations_HESS_J1837-069}.
-  }
   }\label{1FGL_J1837.5-0659c}
@@
   and extension of 2FGL\,J2021.5+4026 assuming a radially-symmetric
-  uniform surface brightness profile.  \newtext{
+  uniform surface brightness profile.  
   The star-shaped marker (colored green)
   represents a 2FGL source that was removed from the background model.
-  }
   2FGL\,J2021.5+4026
@@
       \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v4/run.py
+    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v5/run.py
     \caption{
@@
     HESS\,J1837$-$069 have only been reported with an elliptical 2D
-    Gaussian fit and so the assumed size is the mean of the semi-major
-    and semi-minor axis.
+    Gaussian fit and so the plotted size is the geometric 
+    mean of the semi-major and semi-minor axis.
     The LAT extension of
@@
     The \gev size of Vela X is taken from \cite{velax}.  
-    \newtext{
     Because of their large size, the shape of RX\,J1713.7$-$3946 and
@@
     Centaurus A is not included because of its large size.
-    }
     }\label{gev_vs_tev_histogram}

### 2011-12-06 presentations/extended_source_search/lande_ext_collab_august_2011/introduction.tex
moving

--- 2011-08-28 extended_catalog/lande_ext_collab_august_2011/introduction.tex
@@
     \item Contact Authors: J. Lande, M. Ackermann, S. Funk
-    \item Full author list being finalized
     \item Internal Referees: Marianne Lemoine-Goumard and Johann Cohen-Tanugi
     \item Target Journal: ApJ
-    \item Status (something about being submitted to internal referees XXXX)
+    \item Currently submitted to internal referees
+    \item Feedback welcome
   \end{itemize}
@@
   \begin{itemize}
-    \item Description/validation of a new method (\pointlike) for analyzing extended sources.
-    \item  Calculation of the LAT's sensitivity to spatially extended sources
+    \item Description of a new method (\texttt{pointlike}) for analyzing extended sources.
+    \item Monte Carlo calculation of false detection rate for extended sources.
+    \item Calculation of the LAT's detection threshold 
+      to spatially extended sources
     \item Presentation of a new search for spatially extended sources:
       \begin{itemize}
-        \item reanalyzing the extension of the 12 extended sources in 2FGL
-        \item testing AGN from 2LAC for extension to validate the analysis
-        \item presenting on the discovery/interpretation of several new extended sources not in 2FGL.
+        \item Reanalyzing extension of 12 extended sources in 2FGL
+        \item Test AGN from 2LAC for extension to validate the analysis
+        \item Present 9 extended sources not in 2FGL
       \end{itemize}

### 2011-12-07 extended_catalog/paper/extended_catalog.tex
2 new authors

@@
 A.~Allafort\altaffilmark{1}, 
+J.~Ballet\altaffilmark{5}, 
 K.~Bechtol\altaffilmark{1}, 
-T.~H.~Burnett\altaffilmark{5}, 
+T.~H.~Burnett\altaffilmark{6}, 
+J.~Cohen-Tanugi\altaffilmark{7}, 
 A.~Drlica-Wagner\altaffilmark{1}, 
-S.~Funk\altaffilmark{1,6}, 
-F.~Giordano\altaffilmark{7,8}, 
-M.-H.~Grondin\altaffilmark{9,10}, 
+S.~Funk\altaffilmark{1,8}, 
+F.~Giordano\altaffilmark{9,10}, 
+M.-H.~Grondin\altaffilmark{11,12}, 
 M.~Kerr\altaffilmark{1}, 
-M.~Lemoine-Goumard\altaffilmark{11,12}
+M.~Lemoine-Goumard\altaffilmark{13,14}
 }
@@
 \altaffiltext{4}{email: markus.ackermann@desy.de}
-\altaffiltext{5}{Department of Physics, University of Washington, Seattle, WA 98195-1560, USA}
-\altaffiltext{6}{email: funk@slac.stanford.edu}
-\altaffiltext{7}{Dipartimento di Fisica ``M. Merlin" dell'Universit\`a e del Politecnico di Bari, I-70126 Bari, Italy}
-\altaffiltext{8}{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70126 Bari, Italy}
-\altaffiltext{9}{Max-Planck-Institut f\"ur Kernphysik, D-69029 Heidelberg, Germany}
-\altaffiltext{10}{Landessternwarte, Universit\"at Heidelberg, K\"onigstuhl, D 69117 Heidelberg, Germany}
-\altaffiltext{11}{Universit\'e Bordeaux 1, CNRS/IN2p3, Centre d'\'Etudes Nucl\'eaires de Bordeaux Gradignan, 33175 Gradignan, France}
-\altaffiltext{12}{Funded by contract ERC-StG-259391 from the European Community}
+\altaffiltext{5}{Laboratoire AIM, CEA-IRFU/CNRS/Universit\'e Paris Diderot, Service d'Astrophysique, CEA Saclay, 91191 Gif sur Yvette, France}
+\altaffiltext{6}{Department of Physics, University of Washington, Seattle, WA 98195-1560, USA}
+\altaffiltext{7}{Laboratoire Univers et Particules de Montpellier, Universit\'e Montpellier 2, CNRS/IN2P3, Montpellier, France}
+\altaffiltext{8}{email: funk@slac.stanford.edu}
+\altaffiltext{9}{Dipartimento di Fisica ``M. Merlin" dell'Universit\`a e del Politecnico di Bari, I-70126 Bari, Italy}
+\altaffiltext{10}{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70126 Bari, Italy}
+\altaffiltext{11}{Max-Planck-Institut f\"ur Kernphysik, D-69029 Heidelberg, Germany}
+\altaffiltext{12}{Landessternwarte, Universit\"at Heidelberg, K\"onigstuhl, D 69117 Heidelberg, Germany}
+\altaffiltext{13}{Universit\'e Bordeaux 1, CNRS/IN2p3, Centre d'\'Etudes Nucl\'eaires de Bordeaux Gradignan, 33175 Gradignan, France}
+\altaffiltext{14}{Funded by contract ERC-StG-259391 from the European Community}
 
@@
 space and the model hypothesis adding a single degree of freedom.
-It leads to the often quoted result $\sqrt{TS}=\sigma$. It is plausible
+It leads to the often quoted result $\sqrt{TS}=\sigma$, where 
+$\sigma$ here refers to the significance of the detection. It is plausible
 to expect a similar distribution for the test statistic in the test for
@@
 
-Several interesting conclusions can be made from this study. The overall
-behavior of these plots is what one would expect. $\tsext-\tsinc$
-is mostly positive when fitting the simulated extended sources in
-Figure~\ref{confusion_extended_plot} whereas $\tsext-\tsinc$ is
-mostly negative when fitting the two simulated point-like sources in
-Figure~\ref{confusion_2pts_plot}.  
-Furthermore, $\tsext-\tsinc$ becomes more positive when the extended
-source becomes larger and more negative when the two point-like sources
-are farther apart.
-From this, we conclude that the $\tsext>\tsinc$ test is
-powerful at discarding cases in which the true emission comes from
-two point-like sources without frequently rejecting real extended sources.
+Several interesting conclusions can be made from this study.  As one would
+expect, $\tsext-\tsinc$ is mostly positive when fitting the simulated
+extended sources.  In the 1 \gev to 100 \gev analysis, only 11 of the
+200 simulated extended sources had $\tsext>16$ but were incorrectly
+reject due to \tsinc being greater than \tsext.  In the 10 \gev to 100 \gev
+analysis, only 7 of the 200 sources were incorrectly reject. From this,
+we conclude that this test is unlikely to incorrectly reject truly
+spatially extended sources.
+
+On the other hand, 
+it is often
+the case that $\tsext>16$ when testing the 
+two simulated point-like sources
+for extension.  This is especially the case
+when the two sources had the same spectral index. 40 out of 200 sources
+in the 1 \gev to 100 \gev energy range and 43 out of 200 sources in the
+10 \gev to 100 \gev energy range had $\tsext>16$.  But in these cases,
+we always found the single extended source fit to be worse than
+the two point-like source fit.  From this, we conclude that the $\tsext>\tsinc$
+test is powerful at discarding cases in which the true emission comes
+from two point-like sources.
 
@@
 
-We do not expect the systematic error
-due to uncertainties in the PSF to be correlated with the systematic
-error due to uncertainty in the Galactic diffuse emission. Therefore,
-the total systematic error on the extension of a source was obtained by
-adding the two errors in quadrature.
+We do not expect the systematic error due to uncertainties in the PSF
+to be correlated with the systematic error due to uncertainty in the
+Galactic diffuse emission. Therefore, the total systematic error on the
+extension of a source was obtained by adding the two errors in quadrature.
+
+There is another systematic error on the size of a source due to issues
+modeling nearby sources in crowded regions of the sky. It is beyond the
+scope of this paper to address this systematic error. Therefore, 
+for sources in crowded regions the systematic
+errors quoted in this paper may not be the full systematics of this
+analysis.
 
@@
 map of this source and overlays \tev contours of HESS\,J1632$-$478
-\citep{hess_plane_survey}.  There are five nearby point-like 2FGL
-sources that appear to  represent physically distinct sources: 2FGL
+\citep{hess_plane_survey}.  There are six nearby point-like 2FGL
+sources that appear to  represent physically distinct sources
+and were included in our background model: 2FGL
 J1630.2-4752, 2FGL J1631.7-4720c, 2FGL J1632.4-4820c, 2FGL J1635.4-4717c,
-2FGL J1636.3-4740c that were included in our background model.  On the
+2FGL J1636.3-4740c, and
+2FGL J1638.0-4703c. On the
 other hand, one point-like 2FGL source 2FGL\,J1634.4$-$4743c  correlates
-with the extended \tev source and does not appear to be physically
-separate.  We therefore removed this source from our model of the
+with the extended \tev source and at \gev energies does
+not appear physically separate. 
+We therefore removed this source from our model of the
 background.  Figure~\ref{1FGL_J1632.9-4802c}b shows the same region with
@@
 appears to correlate with the \tev morphology of HESS\,J1837$-$069 but
+at \gev energies
 does not appear to represent a physically distinct source.  We concluded
@@
 of the sky.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
-counts map of this region after subtracted these background sources.
+counts map of this region after subtracting these background sources.
+After removing 2FGL\,J1835.5$-$0649,
+we tested for
+source confusion by fitting 
+2FGL\,J1837.3$-$0700c
+instead as two point-like sources.
+Because \tsinc is less than \tsext, we conclude that this emission
+does not originate from two nearby point-like sources.
 
@@
 moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
-to $(l,b)=(25\fdg57,0\fdg32)$. With this best fit sky model, we tested for
-source confusion by fitting the source instead as two point-like sources.
-Because \tsinc is less than \tsext, we concluded that this emission
-does not originate from two nearby point-like sources.
+to $(l,b)=(25\fdg57,0\fdg32)$.
 
@@
 There is a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
-emission of $\gamma$-Cygni and does not appear to represent a physically
+emission of $\gamma$-Cygni and at \gev energies 
+does not appear to represent a physically
 distinct source.  We concluded that it was included in 2FGL to compensate
@@
     markers (colored blue) an index closer to 2, and the circular markers
-    (colored green) an index closer to 2.5.  The circular marker in plot
+    (colored green) an index closer to 2.5.  The triangular marker in plot
     (d) below the sensitivity line is MSH\,15$-$52.
@@
     both an extended source and as two point-like sources.  (c) and
-    (d) are the distribution of $\tsext-\tsinc$ for the same simualted sources.
+    (d) are the distribution of $\tsext-\tsinc$ for the same simulated sources.
     (a) and (c) represent sources fit in the 1 \gev to 100 \gev energy
@@
     and (b) represent simulations of two point-like sources with the
-    same spectral index and (d) and (e) represent simulations of two
+    same spectral index and (c) and (d) represent simulations of two
     point-like sources with different spectral indices.  (a) and (c)
@@
     colored blue in the electronic version)
-    and with \gtlike (solid line colored red).  AGN are too far
+    and with \gtlike (solid line colored black).  AGN are too far
     and too small to be resolved by the LAT. Therefore, the cumulative
@@
 2FGL\,J0851.7$-$4635      &                115.2 &                116.6 &                123.1 &                 83.9 &                 86.8 &                 89.8 &                 1.15 &                 1.16 &                 1.17 &                 15.5 \\
-2FGL\,J1615.0$-$5051      &                 48.2 &                 50.4 &                 56.6 &                 15.2 &                 16.7 &                 17.8 &                 0.32 &                 0.33 &                 0.32 &                 13.1 \\
+2FGL\,J1615.0$-$5051\tablenotemark{(a)} &                 48.2 &                 50.4 &                 56.6 &                 15.2 &                 16.7 &                 17.8 &                 0.32 &                 0.33 &                 0.32 &                 13.1 \\
 2FGL\,J1615.2$-$5138      &                 75.0 &                 76.1 &                 83.8 &                 42.9 &                 46.5 &                 54.1 &                 0.42 &                 0.43 &                 0.43 &                 35.1 \\
@@
   \enddata
+
+\tablenotetext{(a)}{
+% Fit from /u/gl/lande/work/fermi/extended_catalog/2FGL/individual_sources/HESS_J1616-508/v4/iteration_v2/r
+Using \pointlike, \tsext for 2FGL\,J1615.0$-$5051 was sligthly below
+16 when the source was fit in the 10 \gev to 100 \gev energy range. To
+confirm the extension measure, the extension was refit in \pointlike
+using a slightly lower energy.  In the 5.6 \gev to 100 \gev energy range,
+we obtained a consistent extension and \tsext=28.0.  In the rest of
+this paper, we quote the $E>10 \gev$ results for consistency with the
+other sources.
+}
 
@@
   \caption{
-  A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
+  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map
   of 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg15 2D
@@
   \caption{A Diffuse-emission-subtracted 
-  subtracted 10 \gev to 100 \gev counts map of the
+  10 \gev to 100 \gev counts map of the
   region around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 2D Gaussian

### 2011-12-08 extended_catalog/paper/extended_catalog.tex
update bibliography + update paper to v6

@@
 200 simulated extended sources had $\tsext>16$ but were incorrectly
-reject due to \tsinc being greater than \tsext.  In the 10 \gev to 100 \gev
+rejected due to \tsinc being greater than \tsext.  In the 10 \gev to 100 \gev
 analysis, only 7 of the 200 sources were incorrectly reject. From this,
@@
 % 3 PWN
-Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were
-identified in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  
-HESS\,J1825$-$137 was significantly detected using photons
-with energies between 10 \gev and 100 \gev.
-To improve our analysis of this source, we removed
-from our background model 
-2FGL\,J1823.1$-$1338c which was included in 2FGL to
-represent part of the extended emission.
-To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 had
-to be
-analyzed at high energies.  Using photons with energies above 10 \gev,
-we fit the extension of MSH\,15$-$52 to be consistent with the published
-size but with \tsext=6.6.
+Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were identified
+in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  HESS\,J1825$-$137
+was significantly detected using photons with energies between 10
+\gev and 100 \gev.  To avoid confusion with the nearby bright pulsar
+PSR\,J1509$-$5850, MSH\,15$-$52 had to be analyzed at high energies.
+Using photons with energies above 10 \gev, we fit the extension of
+MSH\,15$-$52 to be consistent with the published size but with \tsext=6.6.
 
@@
 new spatially extended \gev sources.
+The data and general analysis setting is as described in Section~\ref{test_2lac_sources}.
 
@@
 of source confusion and diffuse emission modeling described in
-section~\ref{extended_source_search_method}.
+Section~\ref{extended_source_search_method}.
 The spectral and spatial properties of these nine sources are summarized
@@
 $\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ and
-\tsext=16.7 and
-2FGL\,J1615.2$-$5138 was found
- to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
-with $\tsext=46.5$.
-To test for the possibility that
-2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
-of two point-like sources (one of them represented in 2FGL by
-2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
-sources.  Because \tsinc is less than \tsext, we conclude that
-this emission does not originate from two nearby point-like sources.
+\tsext=16.7.
 
@@
 \label{section_2FGL_J1615.2-5138}
+
+2FGL\,J1615.2$-$5138 was found
+ to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
+with $\tsext=46.5$.
+To test for the possibility that
+2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
+of two point-like sources (one of them represented in 2FGL by
+2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
+sources.  Because \tsinc is less than \tsext, we conclude that
+this emission does not originate from two nearby point-like sources.
 
@@
 \cutinhead{E$>$10 \gev}
-MSH\,15$-$52              &     320.39 &      -1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
-HESS\,J1825$-$137         &      17.57 &      -0.45 & $  0.65 \pm   0.04 \pm   0.02 $ &       82.9 &       44.9 &   0.05 & $    1.8 \pm     0.8$ & $   1.83 \pm    0.73$  \\
+MSH\,15$-$52\tablenotemark{(b)}      &     320.39 &      -1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
+HESS\,J1825$-$137\tablenotemark{(b)} &      17.56 &      -0.47 & $  0.65 \pm   0.04 \pm   0.02 $ &       59.7 &       33.8 &   0.05 & $    1.6 \pm     0.2$ & $   1.63 \pm    0.22$  \\
 \enddata
@@
 energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
+}
+\tablenotetext{(b)}{
+The discrepancy in the best fit spectra of MSH\,15$-$52 and HESS\,J1825$-$137
+compared to \cite{msh1552} and
+\cite{fermi_hess_j1825} is due to fitting over a different energy range.
 }
@@
 \cutinhead{E$>$10 \gev}
-2FGL\,J0851.7$-$4635      &     266.31 &      -1.43 & $  1.15 \pm   0.08 \pm   0.02 $ &      116.6 &       86.8 &   0.07 & $    1.3 \pm     0.2$ & $   1.74 \pm    0.21$ &                  Vela Jr. \\
+2FGL\,J0851.7$-$4635                       &     266.31 &      -1.43 & $  1.15 \pm   0.08 \pm   0.02 $ &      116.6 &       86.8 &   0.07 & $    1.3 \pm     0.2$ & $   1.74 \pm    0.21$ &                  Vela Jr.
+\\
 2FGL\,J1615.0$-$5051                       &     332.37 &      -0.13 & $  0.32 \pm   0.04 \pm   0.01 $ &       50.4 &       16.7 &   0.04 & $    1.0 \pm     0.2$ & $   2.19 \pm    0.28$ &         HESS\,J1616$-$508 \\
@@
 2FGL\,J1632.4$-$4753c                      &     336.52 &       0.12 & $  0.35 \pm   0.04 \pm   0.02 $ &       64.4 &       26.9 &   0.04 & $    1.4 \pm     0.2$ & $   2.66 \pm    0.30$ &         HESS\,J1632$-$478 \\
-2FGL\,J1712.4$-$3941      &     347.26 &      -0.53 & $  0.56 \pm   0.04 \pm   0.02 $ &       59.4 &       38.5 &   0.05 & $    1.2 \pm     0.2$ & $   1.87 \pm    0.22$ &        RX\,J1713.7$-$3946 \\
+2FGL\,J1712.4$-$3941\tablenotemark{(b)}    &     347.26 &      -0.53 & $  0.56 \pm   0.04 \pm   0.02 $ &       59.4 &       38.5 &   0.05 & $    1.2 \pm     0.2$ & $   1.87 \pm    0.22$ &        RX\,J1713.7$-$3946 \\
 2FGL\,J1837.3$-$0700c                      &      25.08 &       0.13 & $  0.33 \pm   0.07 \pm   0.05 $ &       47.0 &       18.5 &   0.07 & $    1.0 \pm     0.2$ & $   1.65 \pm    0.29$ &         HESS\,J1837$-$069 \\
@@
 energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
+}
+
+\tablenotetext{(b)}{
+The discrepancy in the best fit spectra of 2FGL\,J1712.4$-$3941 compared
+to \cite{rx_j1713_lat} is due to fitting over a different energy range.
 }

### 2011-12-09 presentations/extended_source_search/lande_ext_src_search_walthrough/lande_ext_src_search_walthrough.tex
new presnetation
update

--- 2011-08-28 extended_catalog/lande_ext_collab_august_2011/lande_gal_ext_collab_august_2011.tex
@@
 \usepackage{xspace}
-\usepackage{deluxetable}
 
@@
 
-\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight
-Data}
-%\subtitle{\ldots}
+\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data}
 
@@
 
-\include{introduction}
+\fermititle
 
-\begin{frame}
-  \begin{center}
-    \includegraphics[scale=0.5]{tables/table3.eps}
-  \end{center}
+\begin{frame}{paper}
+
+  \includegraphics[scale=0.45]{plots/title.png}
+
+  \begin{itemize}
+    \item Cat II paper
+    \item Target Journal: ApJ
+    \item Pub Board: \url{https://www-glast.stanford.edu/cgi-prot/pub_download?id=662}
+    \item Internal referees: Marianne Lemoine-Goumard + Johann Cohen-Tanugi (+ unofficially Jean Ballet)
+      \begin{itemize}
+        \item Thanks for all your help!
+      \end{itemize}
+    \item Ready for submission
+  \end{itemize}
 \end{frame}
 
-\begin{frame}
-  \begin{center}
-    \includegraphics[scale=0.5]{tables/table4.eps}
-  \end{center}
+\begin{frame}{Section 2.1. Modeling Extended Sources in the \texttt{pointlike} Package}
+  \begin{itemize}
+    \item Short Description of \texttt{pointlike}
+    \item Implementation of extended sources
+    \item Simultaneously Fit position + extension
+    \item optimization of likelihood computation
+    \item Cross check TS + spectral values using \texttt{gtlike}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Fig. 3+4: False-Detection Rate}
+  \begin{columns}
+    \column{.5\textwidth} 
+    \includegraphics[scale=0.4]{plots/ts_ext_emin_1000_color.pdf}
+    \column{.5\textwidth} 
+    \begin{itemize}
+      \item Simulate point-like sources
+      \item Test for extension
+      \item Good agreement with Wilk's Theorem
+      \item Proves that we can use $\sqrt{\mathrm{TS}_\mathrm{ext}}$
+        as a measure of significance
+      \item $\sim 20,000$ Simulations per spectral model!
+      \item Test in 1 GeV to 100 GeV + 10 GeV to 100 GeV
+        energy range
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 5+6+7: Detection Threshold}
+  \begin{columns}
+    \column{.6\textwidth}
+    \includegraphics[scale=0.5]{plots/all_sensitivity_color.pdf}
+    \column{.4\textwidth}
+    \begin{itemize}
+      \item Detetion threshold to extension
+      \item $\langle\text{TS}_\text{ext}\rangle=16$
+      \item Vary spectra, background, energy range
+      \item Overlay extended sources
+      \item Reference for future publications!
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 8+9: Effects of Source Confusion}
+  Non-nested model comparison
+  \begin{equation*}
+    \text{TS}_\text{2pts} = 2 \log(\mathcal{L}_\text{2pts}/\mathcal{L}_\text{ps})
+  \end{equation*}
+
+  \begin{columns}
+    \column{.6\textwidth}
+    \includegraphics[scale=0.30]{plots/confusion_2pts_plot_color.pdf}
+
+    Simulate extended sources. Fit as point-like sources.
+
+    \column{.4\textwidth}
+    \includegraphics[scale=0.30]{plots/confusion_extended_plot_color.pdf}
+
+    Simulate point-like sources. Fit for extension.
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 10: $\text{TS}_\text{ext}$ for 2LAC AGN}
+  \begin{columns}
+    \column{.6\textwidth}
+    \includegraphics[scale=0.4]{plots/agn_color.pdf}
+    \column{.4\textwidth}
+Use point-like AGN to validate extended source study
+    \begin{itemize}
+      \item Test clean 2LAC AGN for extension
+      \item Don't find AGN to be extended!
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Extended source systematics}
+  \begin{itemize}
+    \item \dots
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Reanalyze extended sources in 2FGL}
+  \begin{columns}
+    \column{.6\textwidth}
+    \includegraphics[scale=0.4]{plots/table_reanalysis.pdf}
+    \column{.4\textwidth}
+    \begin{itemize}
+      \item Test 12 extended 2FGL sources for extension
+      \item Systematic re-analytis using 2 years of data.
+      \item Assume uniform disk
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Extended Source Search}
+  \begin{itemize}
+    \item Run a dedicated search 
+    \item Find previously-unresolved
+      extended 2FGL sources
+    \item Search for $E>1$ and GeV $E>10$ GeV
+    \item Many difficulties in search, discussed at length in text\dots
+    \item Publish only good candidates
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{New extended Sources (not in 2FGL)}
+  \begin{columns}
+    \column{.65\textwidth}
+    \includegraphics[scale=0.30]{plots/new_extended.png}
+    \column{.35\textwidth}
+    \begin{itemize}
+      \item 7 new extended sources
+      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
+      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{2 Extended SNRs}
+  \begin{columns}
+    \column{.50\textwidth} 
+    Puppis A
+
+    \includegraphics[scale=0.40]{plots/source_Puppis_A_color.pdf}
+
+    \begin{itemize}
+      \item X-ray contours
+      \item Mid-aged SNR
+      \item Not observed to directly interact with molecular
+        clouds
+      \end{itemize}
+
+    \column{.50\textwidth} 
+    $\gamma$-Cygni
+
+    \includegraphics[scale=0.40]{plots/source_Gamma_Cygni_color.pdf}
+
+    \begin{itemize}
+      \item Radio contours
+      \item SNR interacting with molecular clouds?
+      \item Veritas + Milagro detections
+      \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Two Nearby LAT extended sources}
+
+  \begin{columns}
+    \column{.6\textwidth} 
+    \includegraphics[scale=0.5]{plots/source_HESS_J1614-518_color.pdf}
+    \column{.4\textwidth} 
+    \begin{itemize}
+    \item (left): 
+      2FGL\,J1615.0$-$5051
+    \item Coincident with HESS\,J1616$-$508
+    \item Coincident with X-ray pulsar
+PSR\,J1617$-$5055 + $\sim 1'$ PWN 
+    \item PWN Candidate
+    \end{itemize}
+  \end{columns}
+
+  \begin{itemize}
+    \item (right):
+      2FGL\,J1615.2$-$5138 $\rightarrow$ HESS\,J1614$-$518
+    \item No compelling counterpart
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{2 More PWN Candidate}
+
+  \begin{columns}
+    \column{.45\textwidth}
+
+2FGL\,J1632.4$-$4753c
+
+    \includegraphics[scale=0.3]{plots/source_HESS_J1632-478_color.pdf}
+
+    \begin{itemize}
+      \item Coincident with HESS\,J1632-478
+
+      \item  {\em XMM-Newton} point-like + extended emission
+      \item (but no pulsations)
+      \item PWN Candidate
+    \end{itemize}
+
+    \column{.60\textwidth}
+
+    2FGL\,J1837.3$-$0700c
+
+    \includegraphics[scale=0.3]{plots/source_HESS_J1837-069_color.pdf}
+
+    \begin{itemize}
+      \item Coincident with HESS\,J1837-069
+      \item + X-ray pulsar PSR\,J1838$-$0655 
+      \item + $\sim 2'$ X-ray PWN 
+      \item PWN candidate
+      \item Second X-ray PSR + PWN candidate in region
+        (but no pulsations)
+    \end{itemize}
+
+  \end{columns}
 \end{frame}

### 2011-12-17 extended_catalog/paper/extended_catalog.tex
new draft v6
better text

@@
 (SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
-and galaxy clusters are expected to be spatially resolvable at
-\gev energies.  Additionally, dark matter satellites are also hypothesized to
-be spatially extended.  The Large Area Telescope
-(LAT) on the {\em \fermi Gamma-ray Space Telescope} (\fermi) has
+and galaxy clusters are expected to be spatially resolvable 
+by the Large Area Telescope (LAT), the primary instrument on the {\em \fermi
+Gamma-ray Space Telescope} (\fermi).
+Additionally, dark matter satellites are also hypothesized to
+be spatially extended. See \cite{atwood_fermi} for pre-launch predictions.
+The LAT has
 detected seven SNRs which are significantly extended
@@
 \citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, 
-three extended PWN have been detected: MSH\,15$-$52, Vela~X, and
+three extended PWN have been detected by the LAT: MSH\,15$-$52, Vela~X, and
 HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
@@
 resolvable by the LAT at \gev energies.
+In particular, there are 59 \gev sources in the second Fermi Source Catalog (2FGL)
+that might be associated with extended SNRs \citep[2FGL][]{second_cat}.
+Previous analyses of extended LAT sources were performed as dedicated
+studies of individual sources so we expect that a systematic scan of
+all LAT detected sources could uncover additional spatially extended
+sources.
 
@@
 \cite{atwood_LAT_mission}.
+
 Using 2 years of all-sky survey data, the LAT Collaboration published
-the second Fermi Source Catalog \citep[2FGL][]{second_cat}.
+2FGL \citep[2FGL][]{second_cat}.
 The possible counterparts of many of these sources can be spatially resolved
@@
 help to associate a LAT source to an otherwise confused counterpart.
-Furthermore, some of the dark matter substructure in our Galaxy 
-is predicted to be spatially extended at \gev energies \citep{pre_luanch_dark_matter_fermi}.  
+Furthermore, $\gamma$-rays emission from dark matter
+annihilation has been predicted to be detectable by the LAT.
+Some of the dark matter substructure in our Galaxy 
+could be spatially resolvable by the LAT \citep{pre_luanch_dark_matter_fermi}.  
 Characterization of spatial extension could help to identify this substructure.
@@
 modeling a spatially extended source as point-like will systematically
-shift a spectral analysis to softer indices. Furthermore, correctly
+soften measured spectra. Furthermore, correctly
 modeling source extension is important for 
@@
 
-Previous analyses of extended LAT sources were performed as dedicated
-studies of individual sources so we expect that a systematic scan of
-all LAT detected sources could uncover additional spatially extended
-sources.  For these reasons, in Section~\ref{analysis_methods_section}
+ For these reasons, in Section~\ref{analysis_methods_section}
 we present a new systematic method for analyzing spatially extended
@@
 of a source.  In Section~\ref{dual_localization_method}, we
-study the ability of the LAT to distinguish between a spatially
-extended source and the confusion of nearby point-like sources.
+study the ability of the LAT to 
+distinguish between a single extended source and unresolved closely-spaced point sources
 In Section~\ref{test_2lac_sources}, we further demonstrate that our

### 2011-12-17 extended_catalog/paper/extended_catalog.tex
bugfixes

@@
 W51C, W30, 
-IC443, W28, W44, RX\,J1713.7$-$3946,
+IC~443, W28, W44, RX\,J1713.7$-$3946,
 and the Cygnus Loop
@@
 detection method does not misidentify point-like sources as being
-extended by testing the extension of active galactic nuclei (AGN)
+extended by testing the extension of active Galactic nuclei (AGN)
 believed to be unresolvable.  In Section~\ref{validate_known},
 we systematically reanalyze the twelve extended sources included
-in 2FGL and in Section~\ref{systematic_errors_on_extension}
-we describe a way to estimate systematic errors on the extension of a source.
+in the 2FGL catalog and in Section~\ref{systematic_errors_on_extension}
+we describe a way to estimate systematic errors on the measured extension of a source.
 In Section~\ref{extended_source_search_method}, we
@@
 in Section~\ref{new_ext_srcs_section} we present the detection of the
-extension of nine spatially extended sources that were reported in 2FGL
-but as being point-like.  Two of these sources have been previously analyzed in
+extension of nine spatially extended sources that were reported in the 2FGL catalog
+but treated as point-like in the analysis.  Two of these sources have been previously analyzed in
 dedicated publications.
@@
 \gev energies.  Additional complications arise for sources along
-the Galactic plane due to systematic uncertainties in the Galactic
-diffuse emission.  The LAT PSF is limited at its lowest detectable
-energies by multiple scattering in the silicon strip tracking section
+the Galactic plane due to systematic uncertainties in the model for
+Galactic diffuse emission.
+
+For energies below $\sim$300~\mev, the angular resolution is limited by
+multiple scattering in the silicon strip tracking section
 of the detector and is several degrees at 100 \mev.  The PSF improves
@@
 the highest energies (when averaged over the acceptance of the LAT)
-and is limited by the granularity of the silicon strips in the tracker
+and is limited by the strip pitch to the height of the tracker
 \citep{atwood_LAT_mission,on_orbit_calibration,lat_on_orbit_psf}.\footnote{More
@@
 energy photons with improved angular resolution. Therefore sophisticated
-analysis techniques are required to maximize the LATs sensitivity
-to these extended sources.
+analysis techniques are required to maximize the sensitivity of the LAT
+to extended sources.
 
@@
 unique requirements for studying spatially extended sources with the LAT.
-It works by maximizing the Poisson likelihood to find the observing counts
+It works by maximizing the Poisson 
+likelihood to detect the observed distributions of gamma rays (referred to as counts)
 given a parametrized spatial and spectral model of the sky.  
-Space is
-divided into cubes of position and energy using the HEALPix representation of
-the sky \citep{healpix} and the likelihood is maximized over all bins in
+The data are binned spatially, using HEALPix pixellization, and spectrally 
+\citep{healpix} and the likelihood is maximized over all bins in
 a region.
@@
 past in several studies of source extension in the LAT Collaboration
-\citep{lmc,smc,w28,w51c}.  In these studies, a profile based upon a
+\citep{lmc,smc,w28,w51c}.  In these studies, a 
 set of \gtlike maximum likelihood fits at fixed extensions was used
@@
 can be factorized:
-$M(l,b,E)=S(l,b)\times X(E)$, where $S(l,b)$ is the spatial distribution
+$M(x,y,E)=S(x,y)\times X(E)$, where $S(x,y)$ is the spatial distribution
 and $X(E)$ is the spectral distribution.  To fit an extended source,
@@
 of the source are
-not directly fit but instead the displacement of the source in a rotated
-reference frame.
+not directly fit but instead the displacement of the source 
+in a reference frame centered on the source.
 
@@
 the position of the source and varying the extension until the
-likelihood has fallen by 1/2, corresponding to a $1\sigma$ error
+log of the likelihood has decreased by 1/2, corresponding to a $1\sigma$ error
 \citep{Statistical_methods_book}.  Figure~\ref{four_plots_ic443}
 demonstrates this method by showing the change in the log of the
-likelihood when varying the extension of the SNR IC443.  The localization
+likelihood when 
+varying the modeled extension of the SNR IC~443.  The localization
 error is calculated by fixing the extension and spectrum of the source
-to their best fit value and then
-fitting to the likelihood function a 2D Gaussian as a function
+to their best fit values and then
+fitting the log of the likelihood to
+a 2D Gaussian as a function
 of position. This localization error algorithm is further described in
@@
 we expect the spectral parameters found with \gtlike to be slightly more
-accurate.  Furthermore, because \gtlike is the standard likelihood analysis
-package, it has been more extensively validated for spectral analysis.
+accurate.  Furthermore, because \gtlike is the 
+standard likelihood analysis package for LAT data, 
+it has been more extensively validated for spectral analysis.
 For those reasons, in the following analysis we used \pointlike to
@@
 
-We considered two different models that can be used to model the
-surface brightness profile for extended sources, either a 2D Gaussian
+We considered two models for the
+surface brightness profile for extended sources: a 2D Gaussian
 profile
@@
 Figure~\ref{compare_disk_gauss} shows that, after convolution with the
-LAT PSF, their PDF are similar for a source that has a 0\fdg5 radius
+LAT PSF, their PDFs are similar for a source that has a 0\fdg5 radius
 typical of LAT detected extended sources.  To allow a valid comparison
@@
 
-For smaller and fainter extended sources, the differences in the PDF for
+For sources that are comparable in size to the PSF,
+the differences in the PDF for
 different spatial models are lost in the noise and the LAT is not sensitive
@@
 \section{Validation of the Analysis Method}
-
 \label{monte_carlo_validation}
 
-We tested the false detection probability for the extended source test
-by fitting the extension of point-like sources.  \cite{mattox_egret}
+We evaluated the false detection probability for the measurement of source extent
+by fitting the extensions of point-like sources.  \cite{mattox_egret}
 discuss that the test statistic distribution for a likelihood ratio test
@@
 taken to be the same as the isotropic spectrum measured by EGRET
-\citep{sreekumar_isotropic}.  The Monte Carlo simulation was performed
+\citep{sreekumar_isotropic}.  This spectrum is comparable
+to the high-latitude background intensity seen by the LAT.
+The Monte Carlo simulation was performed
 over a one-year observation period using a representative 
@@
 significance.  The cumulative density of \tsext is plotted in
-Figure~\ref{ts_ext_mc_1000} and \ref{ts_ext_mc_10000} 
+Figures~\ref{ts_ext_mc_1000} and \ref{ts_ext_mc_10000} 
 and compared to the $\chi^2_1/2$ distribution of
@@
 values of \tsext which would make the formal significance conservative.
-Considering the distribution in Figure~\ref{ts_ext_mc_1000} and
-Figure~\ref{ts_ext_mc_10000}, the choice of a threshold \tsext set to 16
-(correspond to a formal $4\sigma$ significance) is reasonable.
+Considering the distribution in Figures~\ref{ts_ext_mc_1000} and
+\ref{ts_ext_mc_10000}, the choice of a threshold \tsext set to 16
+(corresponding to a formal $4\sigma$ significance) is reasonable.
 
@@
 
-We calculated the LAT flux threshold to detect that a spatially extended
-source is extended. We define the detection threshold as the flux at
+We calculated the LAT flux 
+threshold to detect spatial extent. We define the detection threshold as the flux at
 which the value of $\tsext$ averaged over many statistical realizations is
@@
 Section~\ref{monte_carlo_validation}, but instead of point-like sources
-we simulated extended sources with a radially-symmetric uniform surface
-brightness profile. Additionally, we simulated our sources over the two-year
-time range included in 2FGL.  For each extension and spectral index,
+we simulated extended sources with radially-symmetric uniform surface
+brightness profiles. Additionally, we simulated our sources over the two-year
+time range included in the 2FGL catalog.  For each extension and spectral index,
 we selected a flux range which bracketed $\tsext=16$ and performed an
@@
 Except for very large or very soft
-sources, our detection threshold is
+sources, the threshold is
 not substantially improved by including photons with energies between 100 \mev and
 1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}
-which shows \tsext for the SNR IC443 computed independently in twelve
-energy bins between 100 \mev and 100 \gev. For IC443, which has a
+which shows \tsext for the SNR IC~443 computed independently in twelve
+energy bins between 100 \mev and 100 \gev. For IC~443, which has a
 spectral index $\sim2.4$ and an extension $\sim0\fdg35$, 
-almost the entire increase in likelihood
-modeling the source as being extended comes
+almost the entire 
+increase in likelihood from optimizing the source extent in the model
+comes
 from energies above 1 \gev.  Furthermore, other systematic errors
@@
 representative of the background near the Galactic plane.  For small
-extended sources, our detection threshold improves by a factor larger
+extended sources, the threshold improves by a factor larger
 than the square root of the exposure because the LAT is signal-limited
@@
 extended sources, the relevant background is over a larger spatial range
-and so the improvement is closer to the expected factor corresponding
-to the square root of the exposure.
+and so the improvement is closer to a factor corresponding
+to the square root of the exposure and is caused by Poisson fluctuations in the background.
 
@@
 from 1 \gev to 100 \gev and a power-law spectral model with
-spectral index 2.  This flux was picked to be representative of the
+spectral index 2.  This spectrum was picked to be representative of the
 new extended sources that were discovered in the following analysis
@@
 the spatially extended source and with the same spectral index as the
-extended source.  Finally, figure~\ref{confusion_2pts_plot}c shows the same
+extended source.  Finally, Figure~\ref{confusion_2pts_plot}c shows the same
 plot with each point-like source having the same flux but different
@@
 and the other an index of 2.5.
-
-The same four plots are shown in figure~\ref{confusion_extended_plot}b, \ref{confusion_extended_plot}d, 
+These indices are representative of the range of indices of LAT-detected
+sources.
+
+The same four plots are shown in Figure~\ref{confusion_extended_plot}b, \ref{confusion_extended_plot}d, 
 \ref{confusion_2pts_plot}b, and \ref{confusion_2pts_plot}d but this
@@
 10 \gev to 100 \gev) only in the 10 \gev to 100 \gev energy range.
-This spectrum is typical of the new extended sources discovered
+This flux is typical of the new extended sources discovered
 using only photons with energies between 10 \gev and 100 \gev (see
@@
 rejected due to \tsinc being greater than \tsext.  In the 10 \gev to 100 \gev
-analysis, only 7 of the 200 sources were incorrectly reject. From this,
+analysis, only 7 of the 200 sources were incorrectly rejected. From this,
 we conclude that this test is unlikely to incorrectly reject truly
@@
 for extension.  This is especially the case
-when the two sources had the same spectral index. 40 out of 200 sources
+when the two sources had the same spectral index. Forty out of 200 sources
 in the 1 \gev to 100 \gev energy range and 43 out of 200 sources in the
@@
 but the broad PSF of the LAT and the density of sources expected to be
-\gev emitters in the galactic plane makes this issue more significant
+\gev emitters in the Galactic plane makes this issue more significant
 for LAT analysis.  When possible, multiwavelength information should be
@@
 For all following LAT analyses, we used the same two-year dataset
-that was used in 2FGL spanning from 2008 August 4 to 2010 August 1. We
+that was used in the 2FGL catalog spanning from 2008 August 4 to 2010 August 1. We
 applied the same acceptance cuts and we used the same P7\_V6 Source class
@@
 Galactic diffuse, isotropic, and Earth limb emission.  To compensate for
-possible residuals in the diffuse emission model, the galactic emission
+possible residuals in the diffuse emission model, the Galactic emission
 was scaled by a power-law and the normalization
@@
 To validate our method, we tested LAT sources associated with AGN for
-extension.  \gev emission from AGN is believed to originate from the
-cores of kiloparsec-scale jets.  Therefore AGN are
+extension.  \gev emission from AGN is believed to originate from collimated jets.  Therefore AGN are
 not expected to be spatially resolvable by the LAT and provide a good
@@
 to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
-halo has been discovered in the LAT data so far.
+halo has been discovered in the LAT data so far \citep{neronov_agn_halo}.
 
@@
 with AGN classification, we selected only the 885 AGN which made it into
-the clean AGN sub-sample.  An AGN association is considered clean only
+the clean AGN sub-sample defined in the 2LAC paper.  An AGN association is considered clean only
 if it has a high probability of association $P\ge 80\%$, if it is the
-only AGN associated with the catalog source, and if there are no flags
-on the source in 2FGL. These last two conditions are important for our
+only AGN associated with the catalog source, and if 
+no analysis flags have been set for the source
+in the 2FGL catalog. These last two conditions are important for our
 analysis. Source confusion may look like a spatially extended source
@@
 in our model of the LAT PSF and the Galactic diffuse emission (see
-Section~\ref{systematic_errors_on_extension}).  The discrepancy could
+Section~\ref{systematic_errors_on_extension}).  
+The discrepancy could
 also in a few cases be due to confusion with a nearby undetected source.
+We note that the Monte Carlo study
+of section~\ref{monte_carlo_validation} effectively used perfect
+IRFs and a perfect model of the sky.
 The overall agreement with the expected distribution demonstrates that
@@
 We note that the LAT PSF used in this study was determined
-empirically by fitting the observed shape of bright AGN (see
+empirically by fitting the distributions of gamma rays around bright AGN (see
 Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
@@
 
-\section{Analysis of Extended Sources Identified in 2FGL}
+\section{Analysis of Extended Sources Identified in the 2FGL Catalog}
 \label{validate_known}
@@
 spatially extended sources, we reanalyzed the twelve spatially extended
-sources which were included in 2FGL \citep{second_cat}.  Even though
+sources which were included in the 2FGL catalog \citep{second_cat}.  Even though
 each of these sources required a dedicated analysis and they
@@
 Six extended SNRs were
-included in 2FGL: W51C, IC443, W28, W30, W44, the Cygnus Loop,
+included in the 2FGL catalog: W51C, IC~443, W28, W30, W44, the Cygnus Loop,
 and W30
@@
 and the Small Magellanic
-Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  
+Cloud (SMC) were included in the 2FGL catalog as spatially extended sources \citep{lmc,smc}.  
 Their extension was significantly
@@
 Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were identified
-in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  HESS\,J1825$-$137
+in the 2FGL catalog \citep{msh1552,velax,fermi_hess_j1825}.  HESS\,J1825$-$137
 was significantly detected using photons with energies between 10
@@
 As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
-galactic latitude where the source density is not as large and the
+Galactic latitude where the source density is not as large and the
 diffuse emission is less structured, this method works well.
 
-But this is infeasible in the galactic plane where we most likely expect
-to discover new spatially extended sources.  In the galactic plane,
+But this is infeasible in the Galactic plane where we most likely expect
+to discover new spatially extended sources.  In the Galactic plane,
 this analysis is challenged by our imperfect model of the diffuse
@@
 a spatially extended source as two point-like sources so we expect
-that spatially extended LAT sources are modeled in 2FGL as
+that spatially extended LAT sources are modeled in the 2FGL catalog as
 multiple point-like sources. Furthermore, the position of other nearby sources
@@
 photons with energies between 10 \gev and 100 \gev.  Although this
-approach tests the same sources, it is complementary because the galactic
+approach tests the same sources, it is complementary because the Galactic
 diffuse emission is even less dominant above 10 \gev and because source
@@
 
-When we applied this test to the 1861 point-like sources in 2FGL, our
+When we applied this test to the 1861 point-like sources in the 2FGL catalog, our
 search found 117 extended source candidates in the 1 \gev to 100 \gev
@@
 sources were found to be extended even though they fit the same emission region.
-For example, the sources 2FGL\,J1630.2-4752, 2FGL\,J1632.4-4753c 2FGL\,J1634.4-4743c,
-and 2FGL\,J1636.3-4740c were all found to be spatially extended in the
+For example, the sources 2FGL\,J1630.2$-$4752, 2FGL\,J1632.4$-$4753c 2FGL\,J1634.4$-$4743c,
+and 2FGL\,J1636.3$-$4740c were all found to be spatially extended in the
 10 \gev to 100 \gev energy range even though they all fit to similar
@@
 its flux. Figure~\ref{res_tsmaps} shows this map around the
-most significantly extended source IC443 when it is modeled both as a
+most significantly extended source IC~443 when it is modeled both as a
 point-like source and as an extended source.  The residual test statistic
 map indicates
-that the spatially extended model for IC443 is a significantly better
+that the spatially extended model for IC~443 is a significantly better
 description of the observed photons and that there is no significant
@@
 originated from a point-like source.  An example radial integral plot
-is shown for the extended source IC443 in Figure~\ref{four_plots_ic443}.
+is shown for the extended source IC~443 in Figure~\ref{four_plots_ic443}.
 For each source, we also made diffuse-emission-subtracted smoothed counts
-maps (shown for IC443 in Figure~\ref{four_plots_ic443}).
+maps (shown for IC~443 in Figure~\ref{four_plots_ic443}).
 
@@
 believed represented physically distinct sources and we removed 
-sources that we believed were included in 2FGL to compensate
+sources that we believed were included in the 2FGL catalog to compensate
 for residuals induced by not modeling the extension of the source.
@@
 the extended source and vice versa.  Similarly,
-the best fit position of nearby point-like sources in 2FGL can be biased
+the best fit position of nearby point-like sources in the 2FGL catalog can be biased
 by systematic issues at lower energies.
@@
 
-Nine extended sources not included in 2FGL were found by our
+Nine extended sources not included in the 2FGL catalog were found by our
 extended source search. Two of these have been previously
@@
 Table~\ref{alt_diff_model_results} also includes the
-results of the extension fit using variations of the PSF and the galactic
+results of the extension fit using variations of the PSF and the Galactic
 diffuse model described in Section~\ref{systematic_errors_on_extension}.
@@
 these nearby point-like sources
-were included in 2FGL to compensate for residuals induced
+were included in the 2FGL catalog to compensate for residuals induced
 by not modeling the extension of this source and
@@
 %     L > 1 x 10^36 ergs/s (0.2-50GeV) - 
-%   IC443:
+%   IC~443:
 %     http://arxiv.org/pdf/1002.2198v1
@@
 this SNR but do not appear to be physically distinct sources.
-They were most likely included in 2FGL to compensate for residuals
+They were most likely included in the 2FGL catalog to compensate for residuals
 induced by not modeling the extension Vela Jr. and were removed
@@
 with the same extended \tev source as 2FGL\,J1615.2$-$5138.  We concluded
-that this source was included in 2FGL to compensate for residuals induced
+that this source was included in the 2FGL catalog to compensate for residuals induced
 by not modeling the extension of 2FGL\,J1615.2$-$5138 and removed
@@
 2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
-of two point-like sources (one of them represented in 2FGL by
+of two point-like sources (one of them represented in the 2FGL catalog by
 2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
@@
 sources that appear to  represent physically distinct sources
-and were included in our background model: 2FGL
-J1630.2-4752, 2FGL J1631.7-4720c, 2FGL J1632.4-4820c, 2FGL J1635.4-4717c,
-2FGL J1636.3-4740c, and
-2FGL J1638.0-4703c. On the
+and were included in our background model: 2FGL\,J1630.2$-$4752, 2FGL\,J1631.7$-$4720c, 2FGL\,J1632.4$-$4820c, 2FGL\,J1635.4$-$4717c,
+2FGL\,J1636.3$-$4740c, and
+2FGL\,J1638.0$-$4703c. On the
 other hand, one point-like 2FGL source 2FGL\,J1634.4$-$4743c  correlates
@@
 is positionally coincident with the hard X-ray source
-IGR\,J1632-4751 observed by \asca, INTEGRAL, and \xmmnewton
+IGR\,J1632$-$4751 observed by \asca, INTEGRAL, and \xmmnewton
 \citep{asca_plane_survey,Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751},
-but this source is suspected to be a galactic X-Ray Binary so the
+but this source is suspected to be a Galactic X-Ray Binary so the
 $\gamma$-ray extension disfavors the association.  Further observations
@@
 does not appear to represent a physically distinct source.  We concluded
-that this source was included in 2FGL to compensate for residuals induced by
+that this source was included in the 2FGL catalog to compensate for residuals induced by
 not modeling the extension of this source and removed it from our model
@@
 does not appear to represent a physically
-distinct source.  We concluded that it was included in 2FGL to compensate
+distinct source.  We concluded that it was included in the 2FGL catalog to compensate
 for residuals induced by not modeling the extension of $\gamma$-Cygni and
@@
 
-Twelve extended sources were included in 2FGL and two additional extended
+Twelve extended sources were included in the 2FGL catalog and two additional extended
 sources were studied in dedicated publications.  Using two years of
@@
 additional extended sources.  We also reanalyze the spatial shape of the
-twelve extended sources in 2FGL and the two additional sources.  The 21
+twelve extended sources in the 2FGL catalog and the two additional sources.  The 21
 extended LAT sources are located primarily along the Galactic plane
@@
 angular resolution of air Cherenkov detectors allows them to measure a
-population of extended sources below our detection threshold limit (currently 
+population of extended sources below the detection threshold limit of the LAT (currently 
 about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with
@@
 Figure~\ref{compare_index_2FGL} compares the spectral index of LAT
-detected extended sources and of all sources in 2FGL. This, and
+detected extended sources and of all sources in the 2FGL catalog. This, and
 Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
@@
     \caption{
-    Counts maps and test statistic profiles for the SNR IC443. (a) \ts
+    Counts maps and test statistic profiles for the SNR IC~443. (a) \ts
     vs. extension of the source. (b) \tsext for individual energy
@@
     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
-    \caption{the LAT detection threshold for four spectral indices
-    and three background ($1\times$, $10\times$, and $100\times$ the
+    \caption{The LAT detection threshold for four spectral indices
+    and three backgrounds ($1\times$, $10\times$, and $100\times$ the
     Sreekumar-like isotropic background) for a two-year exposure. The
-    left plots are the detection threshold when using 
+    left-hand plots are the detection threshold when using 
     photons with energies between
     1 \gev and 100 \gev
-    and the right plots are the detection threshold when using
+    and the right-hand plots are the detection threshold when using
     photons with energies between
@@
     exposure (bottom edge).  The lower plot shows the factor increase in
-    sensitivity.  For small extended sources, our detection threshold
+    sensitivity.  For small extended sources, the detection threshold of the LAT
     to the extension of a source will improve by a factor larger than the square root of 
@@
     The distribution of $\tsext-\tsinc$ when fitting two simulated
-    point-like sources of varying separation distances as
+    point-like sources of varying separations as
     both an extended source and as two point-like sources.  (a),
@@
   A test statistic map generated for the region around the SNR 
-  IC443 using 
+  IC~443 using 
   photons with energies between
   1 \gev and 100 \gev.  (a) test statistic map after
-  subtracting IC443 modeled as a point-like source. (b) same as (a), but
-  IC443 modeled as an extended source. The cross represents the best
-  fit position of IC443.
+  subtracting IC~443 modeled as a point-like source. (b) same as (a), but
+  IC~443 modeled as an extended source. The cross represents the best
+  fit position of IC~443.
   }
@@
     radially-symmetric source with a uniform intensity profile.  The black
-    crosses represent the position of other 2FGL sources.  The extension
+    crosses represent the positions of other 2FGL sources.  The extension
     is statistically significant, but the extension encompasses many 2FGL
@@
 \tablewidth{0pt}
-\tablecaption{Analysis of the twelve extended sources included in 2FGL
+\tablecaption{Analysis of the twelve extended sources included in the 2FGL catalog
 \label{known_extended_sources}
@@
 \hline
-SMC                                  &     302.59 &     -44.42 & $  1.32 \pm   0.15 \pm   0.31 $ &       95.0 &       52.9 &   0.14 & $    2.7 \pm     0.3$ & $   2.48 \pm    0.19$  \\
-LMC                                  &     279.26 &     -32.31 & $  1.37 \pm   0.04 \pm   0.11 $ &     1127.9 &      909.9 &   0.04 & $   13.6 \pm     0.6$ & $   2.43 \pm    0.06$  \\
-IC443                                &     189.05 &       3.04 & $  0.35 \pm   0.01 \pm   0.04 $ &    10692.9 &      554.4 &   0.01 & $   62.4 \pm     1.1$ & $   2.22 \pm    0.02$  \\
-Vela X                               &     263.34 &      -3.11 & $                         0.88$ &            &            &        &                       &                        \\
+SMC                                  &     302.59 &   $-$44.42 & $  1.32 \pm   0.15 \pm   0.31 $ &       95.0 &       52.9 &   0.14 & $    2.7 \pm     0.3$ & $   2.48 \pm    0.19$  \\
+LMC                                  &     279.26 &   $-$32.31 & $  1.37 \pm   0.04 \pm   0.11 $ &     1127.9 &      909.9 &   0.04 & $   13.6 \pm     0.6$ & $   2.43 \pm    0.06$  \\
+IC~443                               &     189.05 &       3.04 & $  0.35 \pm   0.01 \pm   0.04 $ &    10692.9 &      554.4 &   0.01 & $   62.4 \pm     1.1$ & $   2.22 \pm    0.02$  \\
+Vela X                               &     263.34 &    $-$3.11 & $                         0.88$ &            &            &        &                       &                        \\
 Centaurus A                          &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
-W28                                  &       6.50 &      -0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
-W30                                  &       8.61 &      -0.20 & $  0.34 \pm   0.02 \pm   0.02 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
-W44                                  &      34.69 &      -0.39 & $  0.35 \pm   0.02 \pm   0.02 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
-W51C                                 &      49.12 &      -0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
-Cygnus Loop                          &      74.21 &      -8.48 & $  1.71 \pm   0.05 \pm   0.06 $ &      357.9 &      246.0 &   0.06 & $   11.4 \pm     0.7$ & $   2.50 \pm    0.10$  \\
+W28                                  &       6.50 &    $-$0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
+W30                                  &       8.61 &    $-$0.20 & $  0.34 \pm   0.02 \pm   0.02 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
+W44                                  &      34.69 &    $-$0.39 & $  0.35 \pm   0.02 \pm   0.02 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
+W51C                                 &      49.12 &    $-$0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
+Cygnus Loop                          &      74.21 &    $-$8.48 & $  1.71 \pm   0.05 \pm   0.06 $ &      357.9 &      246.0 &   0.06 & $   11.4 \pm     0.7$ & $   2.50 \pm    0.10$  \\
 \cutinhead{E$>$10 \gev}
-MSH\,15$-$52\tablenotemark{(b)}      &     320.39 &      -1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
-HESS\,J1825$-$137\tablenotemark{(b)} &      17.56 &      -0.47 & $  0.65 \pm   0.04 \pm   0.02 $ &       59.7 &       33.8 &   0.05 & $    1.6 \pm     0.2$ & $   1.63 \pm    0.22$  \\
+MSH\,15$-$52\tablenotemark{(b)}      &     320.39 &    $-$1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
+HESS\,J1825$-$137\tablenotemark{(b)} &      17.56 &    $-$0.47 & $  0.65 \pm   0.04 \pm   0.02 $ &       59.7 &       33.8 &   0.05 & $    1.6 \pm     0.2$ & $   1.63 \pm    0.22$  \\
 \enddata
@@
 the position of the source.  Vela X and the Centaurus A Lobes were
-not fit in our analysis but are include for completeness.
+not fit in our analysis but are included for completeness.
 }
@@
 \thispagestyle{empty}
-\begin{deluxetable}{lrrrrrrrrr}
+\begin{deluxetable}{lrrrrrrrrl}
 \tablecolumns{10}
@@
 \hline
-2FGL\,J0823.0$-$4246                       &     260.32 &      -3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      322.2 &       48.0 &   0.02 & $    8.4 \pm     0.6$ & $   2.21 \pm    0.09$ &                  Puppis A \\
+2FGL\,J0823.0$-$4246                       &     260.32 &    $-$3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      322.2 &       48.0 &   0.02 & $    8.4 \pm     0.6$ & $   2.21 \pm    0.09$ &                  Puppis A \\
 2FGL\,J1627.0$-$2425c                      &     353.07 &      16.80 & $  0.42 \pm   0.05 \pm   0.16 $ &      139.9 &       32.4 &   0.04 & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ &                 Ophiuchus \\
 \cutinhead{E$>$10 \gev}
-2FGL\,J0851.7$-$4635                       &     266.31 &      -1.43 & $  1.15 \pm   0.08 \pm   0.02 $ &      116.6 &       86.8 &   0.07 & $    1.3 \pm     0.2$ & $   1.74 \pm    0.21$ &                  Vela Jr.
+2FGL\,J0851.7$-$4635                       &     266.31 &    $-$1.43 & $  1.15 \pm   0.08 \pm   0.02 $ &      116.6 &       86.8 &   0.07 & $    1.3 \pm     0.2$ & $   1.74 \pm    0.21$ &                  Vela Jr.
 \\
-2FGL\,J1615.0$-$5051                       &     332.37 &      -0.13 & $  0.32 \pm   0.04 \pm   0.01 $ &       50.4 &       16.7 &   0.04 & $    1.0 \pm     0.2$ & $   2.19 \pm    0.28$ &         HESS\,J1616$-$508 \\
-2FGL\,J1615.2$-$5138                       &     331.66 &      -0.66 & $  0.42 \pm   0.04 \pm   0.02 $ &       76.1 &       46.5 &   0.04 & $    1.1 \pm     0.2$ & $   1.79 \pm    0.26$ &         HESS\,J1614$-$518 \\
+2FGL\,J1615.0$-$5051                       &     332.37 &    $-$0.13 & $  0.32 \pm   0.04 \pm   0.01 $ &       50.4 &       16.7 &   0.04 & $    1.0 \pm     0.2$ & $   2.19 \pm    0.28$ &         HESS\,J1616$-$508 \\
+2FGL\,J1615.2$-$5138                       &     331.66 &    $-$0.66 & $  0.42 \pm   0.04 \pm   0.02 $ &       76.1 &       46.5 &   0.04 & $    1.1 \pm     0.2$ & $   1.79 \pm    0.26$ &         HESS\,J1614$-$518 \\
 2FGL\,J1632.4$-$4753c                      &     336.52 &       0.12 & $  0.35 \pm   0.04 \pm   0.02 $ &       64.4 &       26.9 &   0.04 & $    1.4 \pm     0.2$ & $   2.66 \pm    0.30$ &         HESS\,J1632$-$478 \\
-2FGL\,J1712.4$-$3941\tablenotemark{(b)}    &     347.26 &      -0.53 & $  0.56 \pm   0.04 \pm   0.02 $ &       59.4 &       38.5 &   0.05 & $    1.2 \pm     0.2$ & $   1.87 \pm    0.22$ &        RX\,J1713.7$-$3946 \\
+2FGL\,J1712.4$-$3941\tablenotemark{(b)}    &     347.26 &    $-$0.53 & $  0.56 \pm   0.04 \pm   0.02 $ &       59.4 &       38.5 &   0.05 & $    1.2 \pm     0.2$ & $   1.87 \pm    0.22$ &        RX\,J1713.7$-$3946 \\
 2FGL\,J1837.3$-$0700c                      &      25.08 &       0.13 & $  0.33 \pm   0.07 \pm   0.05 $ &       47.0 &       18.5 &   0.07 & $    1.0 \pm     0.2$ & $   1.65 \pm    0.29$ &         HESS\,J1837$-$069 \\
@@
   The
-  contours in (a) correspond to the 100 micrometer image observed by
+  contours in (a) correspond to the 100 $\mu$m image observed by
   IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
-  ${}^{12}\text{CO}$ ($J=1\rightarrow 0$) emission integrated from -8 \km/\s
-  to 20 \km/\s.  They are from \cite{co_rho_ophiuci}, were cleaned using
+  ${}^{12}\text{CO}$ ($J=1\rightarrow 0$) emission integrated from $-$8 $\km\,\s^{-1}$
+  to 20 $\km\,\s^{-1}$.  They are from \cite{co_rho_ophiuci}, were cleaned using
   the moment-masking technique \citep{masking_moment_2011}, and have
@@
   The contours (colored light blue) correspond to the \tev image of
-  HESS\,J1632-478 \citep{hess_plane_survey}.
+  HESS\,J1632$-$478 \citep{hess_plane_survey}.
   }\label{1FGL_J1632.9-4802c}
@@
   \citep{hess_plane_survey}.
-  The diamond-shaped marker (colored orange) represents the position of PSR J1838-0655
-  and the hexagonal-shaped marker (colored purple) represents the position AX J1837.3-0652
+  The diamond-shaped marker (colored orange) represents the position of PSR\,J1838$-$0655
+  and the hexagonal-shaped marker (colored purple) represents the position AX\,J1837.3$-$0652
   \citep{pulsations_HESS_J1837-069}.
@@
     \cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
-    The \tev size of IC443 is from \cite{ic443_veritas} and
+    The \tev size of IC~443 is from \cite{ic443_veritas} and
     W51C is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev

### 2011-12-18 extended_catalog/paper/extended_catalog.tex
improve text

@@
 fixed to a very small value ($10^{-10}$ degrees in radius 
-for a uniform surface brightness profile).
+for a uniform disk model).
 
@@
 We considered two models for the
-surface brightness profile for extended sources: a 2D Gaussian
-profile
+surface brightness profile for extended sources: a 2D Gaussian model
 \begin{equation}\label{gauss_pdf}
@@
 \end{equation}
-or a uniform surface brightness profile
+or a uniform disk model
 \begin{equation}\label{disk_pdf}
@@
 typical of LAT detected extended sources.  To allow a valid comparison
-between the Gaussian and the uniform surface brightness morphologies,
+between the Gaussian and the uniform disk models,
 we define the source size as the radius containing 68\% of the
@@
 search for extended sources we use only a radially-symmetric uniform
-surface brightness profile as our spatial extension shape. Unless otherwise noted,
+disk spatial model. Unless otherwise noted,
 we quote the radius to the edge ($\sigma$) as the size of the source.
@@
 Section~\ref{monte_carlo_validation}, but instead of point-like sources
-we simulated extended sources with radially-symmetric uniform surface
-brightness profiles. Additionally, we simulated our sources over the two-year
+we simulated extended sources with radially-symmetric uniform disk spatial 
+models. Additionally, we simulated our sources over the two-year
 time range included in the 2FGL catalog.  For each extension and spectral index,
@@
 (see Section~\ref{new_ext_srcs_section}).
-We simulated these sources using a uniform surface brightness profile
+We simulated these sources using uniform disk spatial models
 with extensions varying
@@
 spatially extended sources, we reanalyzed the twelve spatially extended
-sources which were included in the 2FGL catalog \citep{second_cat}.  Even though
-each of these sources required a dedicated analysis and they
-were fit with a variety of spatial models, it is valuable to show that
+sources which were included in the 2FGL catalog \citep{second_cat}.  
+Even though these sources had all been the subjects of dedicated
+analyses and separate publications, and had been fit with a variety
+of spatial models,
+it is valuable to show that
 these sources are significantly extended using our systematic 
-method assuming a radially-symmetric uniform surface
-brightness profile.  On the other hand, for some of
+method assuming radially-symmetric uniform disk spatial models.  On the other hand, for some of
 these sources a uniform disk spatial model does not well describe the
@@
 the shape of the source is significantly different from a uniform
-radially-symmetric surface brightness profile \citep{cen_a_lat}.
+radially-symmetric disk\citep{cen_a_lat}.
 
@@
 position and extension of these sources when fitting them 
-with a radially-symmetric uniform surface brightness profile. It also
+with a radially-symmetric uniform disk model. It also
 includes the best fit spectral parameters for each source.  The position
@@
 Our strategy tested all point-like 2FGL sources for extension assuming
-they had a uniform radially-symmetric surface brightness profile
+they had a uniform radially-symmetric disk spatial model
 and a power-law spectral model.  Although not all extended sources are
-expected to have a shape very similar to a uniform surface brightness
-profile, Section~\ref{compare_source_size} showed that for many spatially
+expected to have a shape very similar to a uniform disk, Section~\ref{compare_source_size} showed that for many spatially
 extended sources the wide PSF of the LAT and limited statistics makes
@@
 spatial model biases us against finding extended sources that are not
-well described by uniform emission such as shell-type supernova remnants.
+well described by a uniform disk model such as shell-type supernova remnants.
 
@@
 that the emission is significantly more complicated than the simple
-radially-symmetric uniform surface brightness profile that we assume.
+radially-symmetric uniform disk model that we assume.
 
@@
     \caption{
-    A comparison of a 2D Gaussian and uniform surface brightness profiles
+    A comparison of a 2D Gaussian and uniform disk spatial model
     of extended sources before and after convolving with the PSF for two
@@
     \caption{
-    The detection threshold to resolve a uniform surface brightness profile
-    extended source for a two-year exposure.  All sources have an
+    The detection threshold to resolve an
+    extended source with a uniform disk model for a two-year exposure.  All sources have an
     assumed power-law spectrum and the different line styles (colors in
@@
       The detection threshold to resolve spatially extended
-      sources with a uniform surface brightness profile for a two-year exposure
+      sources with a uniform disk spatial model for a two-year exposure
       The threshold is calculated for
@@
     kernel. The plus-shaped marker and circle (colored red in
-    the online version) represent the center and size of the best fit
-    radially-symmetric source with a uniform intensity profile.  The black
+    the online version) represent the center and size of the source
+    fit with a
+    radially-symmetric uniform disk spatial model.  The black
     crosses represent the positions of other 2FGL sources.  The extension
@@
 \tablecomments{
-All sources were fit using a spatial model assuming a uniform radially
-symmetric intensity distribution. \glon and \glat are Galactic longitude
+All sources were fit using a radially-symmetric uniform disk spatial model.
+\glon and \glat are Galactic longitude
 and latitude of the best fit extended source respectively.  The first
@@
 are the fit size assuming
-a uniform radially symmetric intensity distribution
+a radially-symmetric uniform disk model
 with the standard analysis, the alternative diffuse
@@
   the best fit position and extension of this source assuming a
-  radially-symmetric uniform surface brightness profile.  The two 
+  radially-symmetric uniform disk model.  The two 
   star-shaped markers (colored
@@
   represent the best fit position and extension of this
-  source assuming a radially-symmetric uniform surface brightness profile
+  source assuming a radially-symmetric uniform disk model
   and the black cross represents a background 2FGL source. 
@@
   and the circle (colored red) are the best fit position and extension of
-  this source assuming a radially-symmetric uniform surface brightness profile.
+  this source assuming a radially-symmetric uniform disk model.
   The three black crosses represent background 2FGL sources
@@
     positions and extensions of these sources assuming a radially
-    symmetric uniform surface brightness profile.  
+    symmetric uniform disk model.  
     The two black crosses represent  background 2FGL sources and
@@
   and the circle (colored red) are the best fit position and extension of
-  2FGL\,J1632.4$-$4753c assuming a radially-symmetric uniform surface
-  brightness profile.  
+  2FGL\,J1632.4$-$4753c assuming a radially-symmetric uniform disk model.  
   The four black crosses represent background 2FGL
@@
   the best fit position and extension of this source assuming a radially
-  symmetric uniform surface brightness profile.  
+  symmetric uniform disk model.  
   The two black crosses represent background 2FGL sources subtracted in (b).
@@
   the circle (colored red) represent the best fit position and extension
-  of 2FGL\,J1837.3$-$0700c assuming a radially-symmetric uniform surface
-  brightness profile. The circular and square-shaped markers (colored
+  of 2FGL\,J1837.3$-$0700c assuming a radially-symmetric uniform disk model. 
+  The circular and square-shaped markers (colored
   blue) represent the 2FGL and the relocalized positions respectively of
@@
   % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v8/run.py
-  \caption{A Diffuse-emission-subtracted 
+  \caption{A diffuse-emission-subtracted 
   10 \gev to 100 \gev counts map of the
@@
   and extension of 2FGL\,J2021.5+4026 assuming a radially-symmetric
-  uniform surface brightness profile.  
+  uniform disk model.  
   The star-shaped marker (colored green)
@@
   (colored light blue) correspond to the 408MHz image of $\gamma$-Cygni
-  observed by the Canadian Galactic Plane Survey.
+  observed by the Canadian Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
   }\label{1FGL_J2020.0+4049}
@@
       version).  The nine new extended sources are represented by
-      the triangular markers (colored orange).}
+      the triangular markers (colored orange).
+      The source positions are overlaid on a 100 \mev to 100 \gev 
+      Aitoff projection sky map of the LAT data in Galactic coordinates.
+}
 \label{allsky_extended_sources}
@@
     \caption{
-    A comparison of the size of extended sources detected at
+    A comparison of the sizes of extended sources detected at
     both \gev and \tev energies.  The \tev size of W30,
@@
     and 2FGL\,J1615.2$-$5138 are from \cite{hess_plane_survey}.
-    The \tev size of MSH\,15$-$52, HESS\,J1825$-$137,
+    The \tev sizes of MSH\,15$-$52, HESS\,J1825$-$137,
     Vela X, Vela Jr., RX\,J1713.7$-$3946 and W28 are from
@@
     Because of
-    their large size, the shape of RX\,J1713.7$-$3946 and Vela Jr.
+    their large sizes, the shape of RX\,J1713.7$-$3946 and Vela Jr.
     were not directly fit at \tev energies and so are not included
@@
     \caption{
-    The distribution of the size of 18 extended LAT sources
+    The distributions of the size of 18 extended LAT sources
     at \gev energies

### 2011-12-18 extended_catalog/paper/extended_catalog.tex
update

@@
 significant residuals in the surrounding region \citep{first_cat,second_cat}.
-Such residuals can bias the significance and measured spectrum of
+Such residuals can bias the significance and measured spectra of
 neighboring sources in the densely populated Galactic plane.
@@
 likelihood ratio test of a hypothesis with a spatially extended source and
-a hypothesis with a point-like source. The test statistic for this procedure
+a hypothesis with a point-like source. The test statistic (TS) for this procedure
 is defined as
@@
 very bright sources, this numerical error has the potential to bias the
-test statistic for the extension test. Therefore, when calculating
+TS for the extension test. Therefore, when calculating
 \tsext, we compare the likelihood fitting the source with an extended
@@
 by fitting the extensions of point-like sources.  \cite{mattox_egret}
-discuss that the test statistic distribution for a likelihood ratio test
+discuss that the TS distribution for a likelihood ratio test
 on the existence of a source at a given position is
@@
 $\sigma$ here refers to the significance of the detection. It is plausible
-to expect a similar distribution for the test statistic in the test for
+to expect a similar distribution for the TS in the test for
 source extension since the same conditions apply (with the source flux
@@
 extended sources, the threshold improves by a factor larger
-than the square root of the exposure because the LAT is signal-limited
-at high energies where we are most sensitive to extension. For large
+than the square root of the relative exposures because the LAT is signal-limited
+at high energies where the present analysis is most sensitive. For large
 extended sources, the relevant background is over a larger spatial range
 and so the improvement is closer to a factor corresponding
-to the square root of the exposure and is caused by Poisson fluctuations in the background.
+to the square root of the relative exposures and is caused by Poisson fluctuations in the background.
 
@@
 in which $\tsext\ge16$, we developed an algorithm in \pointlike to
-simultaneously fit the position and spectrum of two point-like sources.
+simultaneously fit the positions and spectra of two point-like sources.
 
@@
 these sources a uniform disk spatial model does not well describe the
-observed extended emission and so the dedicated LAT publications provides
-a qualitatively better model of these sources.
+observed extended emission and so the dedicated LAT 
+publications provide better models of these sources.
 
@@
 1 \gev and 100 \gev, our analysis significantly detected
-the extension of all six of these SNRs.
+that these six SNRs are spatially extended.
 
@@
 Cloud (SMC) were included in the 2FGL catalog as spatially extended sources \citep{lmc,smc}.  
-Their extension was significantly
+Their extensions were significantly
 detected using photons with energies between
 1 \gev and 100 \gev. Our
-fit extension is comparable to the published result, but we note that
-the previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
+fit extensions are comparable to the published result, but we note that
+the previous LAT Collaboration publication on the LMC used a more complicated two 2D Gaussian surface
 brightness profile when fitting it \citep{lmc}.
@@
 % 3 PWN
-Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were identified
-in the 2FGL catalog \citep{msh1552,velax,fermi_hess_j1825}.  HESS\,J1825$-$137
+Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were fit as
+extended sources in the 2FGL analysis \citep{msh1552,velax,fermi_hess_j1825}.  
+In the present analysis, HESS\,J1825$-$137
 was significantly detected using photons with energies between 10
@@
 Table~\ref{known_extended_sources}.  This table includes the best fit
-position and extension of these sources when fitting them 
+positions and extensions of these sources when fitting them 
 with a radially-symmetric uniform disk model. It also
-includes the best fit spectral parameters for each source.  The position
-and extension of Vela X and the Centaurus A Lobes were taken from
-\cite{velax,cen_a_lat} and are included in this list for completeness.
+includes the best fit spectral parameters for each source.  The positions
+and extensions of Vela X and the Centaurus A Lobes were taken from
+\cite{velax,cen_a_lat} and are included in this table for completeness.
 
@@
 We developed two criteria for estimating systematic errors
-on the extension of the sources.
+on the extensions of the sources.
 First, we estimated a systematic error due to
@@
 beam tests \citep{atwood_LAT_mission}. However, in-flight data revealed
-a discrepancy above a few \gev in the PSF compared to the angular
+a discrepancy above 3 \gev in the PSF compared to the angular
 distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
@@
 systematic error on the extension of a source.  The same approach was used
-in \cite{ic443}.  At high energies, we believe that our parameterization
+in \cite{ic443}.  we believe that our parameterization
 of the PSF from bright AGN is substantially better than the Monte Carlo
@@
 due to uncertainty in our model of the Galactic diffuse emission by
-using an alternative model which takes as input templates
+using an alternative 
+approach to modeling the diffuse emission
+which takes as input templates
 calculated by
@@
 Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
-in the Galaxy \citep{galprop1998,galprop2011}. 
+in the Galaxy and maps of the distributions of the 
+components of the interstellar medium \citep{galprop1998,galprop2011}. 
 See also \url{http://galprop.stanford.edu/} for details.} 
@@
 this tests systematics that may be due to imperfect modeling of the
-diffuse emission in the region. Nevertheless, this alternative diffuse
-model does not test all systematics related to the diffuse emission model.
-In particular, because the alternative model uses the same underlying gas
-maps it is unable to assess systematics due to mischaracterization of local
+diffuse emission in the region. Nevertheless, 
+this alternative approach to modeling the diffuse emission
+does not test all systematics related to the diffuse emission model.
+In particular, because the alternative approach uses the same underlying gas
+maps it is unable to be used to assess systematics due to mischaracterization of local
 diffuse structure due to lack of resolution of the underlying maps.
@@
 a spatially extended source as two point-like sources so we expect
-that spatially extended LAT sources are modeled in the 2FGL catalog as
-multiple point-like sources. Furthermore, the position of other nearby sources
+that spatially extended sources would be modeled in the 2FGL catalog as
+multiple point-like sources. Furthermore, the positions of other nearby sources
 in the region close to an extended source could be biased by not correctly
@@
 by 2FGL sources no longer significant and by 2FGL
-sources whose position was biased by diffuse emission at lower energies.
+sources whose positions were biased by diffuse emission at lower energies.
 
@@
 refined the analysis of the promising candidates on a case by case basis.
-Our strategy tested all point-like 2FGL sources for extension assuming
+Our strategy was to test all point-like 2FGL sources for extension assuming
 they had a uniform radially-symmetric disk spatial model
@@
 spatial model biases us against finding extended sources that are not
-well described by a uniform disk model such as shell-type supernova remnants.
+well described by a uniform disk model such as shell-type SNRs.
 
@@
 
-As was shown in Section~\ref{extension_sensitivity}, we gain little in
-sensitivity using photons with energies below 1 \gev. On the other hand,
-the broad PSF at low energy makes us more susceptible to systematic
+As was shown in Section~\ref{extension_sensitivity}, little sensitivity is gained by
+using photons with energies below 1 \gev. On the other hand,
+the broad PSF at low energy makes the analysis more susceptible to systematic
 errors arising from source confusion due to nearby soft point-like sources
@@
 confusion is less of an issue.  A similar procedure was used to detect
-the spatial extension of MSH\,15$-$52 and
+the spatial extensions of MSH\,15$-$52 and
 HESS\,J1825$-$137 with the LAT \citep{msh1552,fermi_hess_j1825}.
@@
 diffuse emission.  To help determine which of these fits found
-truly extended sourced and when the extension was
+truly extended sources and when the extension was
 influenced by source confusion and diffuse emission, we generated a
 series of diagnostic plots.  For each candidate, we generated a map
-of the residual test statistic by adding a new point-like source of spectral index 2 into the
+of the residual TS by adding a new point-like source of spectral index 2 into the
 region at each position and finding the increase in likelihood when fitting
@@
 most significantly extended source IC~443 when it is modeled both as a
-point-like source and as an extended source.  The residual test statistic
+point-like source and as an extended source.  The residual TS
 map indicates
@@
 We also generated plots of the sum of all counts within a given distance of
-the source and compared it to the model predictions assuming the emission
+the source and compared them to the model predictions assuming the emission
 originated from a point-like source.  An example radial integral plot
@@
 We found by visual inspection that in many
-cases our analysis was strongly influenced by large-scale residuals in the
+cases our results were strongly influenced by large-scale residuals in the
 diffuse emission and hence the extension measure was unreliable.  This was
@@
 this source with the best
-fit extension of the source overlaid. There appears to be large-scale
+fit extension of the source overlaid. There appear to be large-scale
 residuals in the diffuse emission in this region along the Galactic plane.
@@
 improved the model of the region by deciding on a case by case basis which
-background point-like sources should be kept.  We kept in our model of the sky
+background point-like sources should be kept.  We kept in our model the
 sources that we
@@
 Soft nearby point-like 2FGL sources that were not significant at higher energies
-were frozen to the spectrum predicted by 2FGL.
+were frozen to the spectras predicted by 2FGL.
 When deciding
@@
 to help guide our choice. For each extended source presented in 
-Section~\ref{new_ext_srcs_section}, we describe any modification from 2FGL
+Section~\ref{new_ext_srcs_section}, we describe any modifications from 2FGL
 of the background model that were performed.
 
-The best fit position of nearby point-like sources can be influenced by
+The best fit positions of nearby point-like sources can be influenced by
 the extended source and vice versa.  Similarly,
-the best fit position of nearby point-like sources in the 2FGL catalog can be biased
+the best fit positions of nearby point-like sources in the 2FGL catalog can be biased
 by systematic issues at lower energies.
 Therefore, after selecting the list of background sources, we iteratively
-refit the position and spectrum of nearby background sources as well as
-the position and extension of the analyzed spatially extended
+refit the positions and spectra of nearby background sources as well as
+the positions and extensions of the analyzed spatially extended
 sources until the overall fit converged globally.  For each extended
-source, we will describe the position of any relocalized background
+source, we will describe the positions of any relocalized background
 sources.
@@
 both \pointlike and \gtlike agree that $\tsext>16$. 
-We further required that $\tsext>16$ using the alternative diffuse
-model presented in Section~\ref{systematic_errors_on_extension}.
+We further required that $\tsext>16$ using the 
+alternative approach to modeling the diffuse emission
+presented in Section~\ref{systematic_errors_on_extension}.
 We then replaced the spatially extended source with two point-like
-sources and refit the position and spectrum of the
+sources and refit the positions and spectra of the
 two point-like sources to calculate \tsinc.
@@
 originates from two distinct point-like sources instead of one spatially
-extended source.  On the other hand, it is still possible that improved
-observations could resolve additional structure or new sources that we are
-currently not sensitive to. Considering the very complicated morphologies
+extended source.  On the other hand, it is still possible that longer
+observations could resolve additional structure or new sources 
+that the analysis cannot currently detect. 
+Considering the very complicated morphologies
 of extended sources observed at other wavelengths and the high density
 of possible sources that are expected to emit at \gev energies, it is
-likely that in some of these regions further observations will resolve
+likely that in some of these regions further observations will reveal
 that the emission is significantly more complicated than the simple
@@
 Table~\ref{alt_diff_model_results} also includes the
-results of the extension fit using variations of the PSF and the Galactic
+results of the extension fits using variations of the PSF and the Galactic
 diffuse model described in Section~\ref{systematic_errors_on_extension}.
 There is good agreement between \tsext and the fit size using the standard
-analysis, the alternative diffuse models, and the alternative PSF.
-This suggests that the sources are robust against features in the diffuse
-emission model and uncertainties in the angular resolution of the LAT.
+analysis, the alternative approach to modeling the diffuse emission, and the alternative PSF.
+This suggests that the sources are robust against mis-modeled features in the diffuse
+emission model and uncertainties in the PSF.
 
@@
 
-\subsection{2FGL\,J1627.0$-$2425c}
-\label{section_2FGL_J1627.0-2425c}
-
-% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-% No modifications to background were needed
-
-2FGL\,J1627.0$-$2425c was found by our search to
-have an extension $\sigma=0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
-$\tsext=32.4$
-using photons with energies between 1 \gev and 100 \gev.  
-Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
-
-This source is in a region of remarkably complicated diffuse emission.
-Even though it is $16\degree$ from the Galactic plane, this source is on
-top of the core of the Ophiuchus molecular cloud which contains massive
-star-forming regions that are bright in infrared.  The region also has
-abundant molecular and atomic gas traced by CO and HI and significant 
-dark gas found only by its association with dust emission
-\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
-more challenging to measure the column density of dust.  Infared and 
-${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
-contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
-spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
-This source might 
-represent $\gamma$-ray emission from the interactions of cosmic rays with
-interstellar gas which has not been accounted for in the LAT diffuse
-emission model.
-
 \subsection{2FGL\,J0851.7$-$4635}
@@
 They were most likely included in the 2FGL catalog to compensate for residuals
-induced by not modeling the extension Vela Jr. and were removed
+induced by not modeling the extension of Vela Jr. and were removed
 from our model of the sky.
@@
 well the \tev morphology of Vela Jr.  While fitting the extension
-of 2FGL\,J0851.7$-$4635, we iteratively relocalized the position
+of 2FGL\,J0851.7$-$4635, we iteratively relocalized the positions
 of the nearby point-like catalog source 2FGL\,J0854.7$-$4501 to
@@
 revealed an underluminous PWN of size $\sim1\arcmin$ around the
-pulsar that was not oriented towards the \tev emission rendering this
+pulsar that was not oriented towards the \tev emission, rendering this
 association uncertain \citep{discovery_of_pwn_for_PSR_J1617-5055}.
@@
 source A or B; and finally that the emission may arise from hadronic
-acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
+acceleration in the stellar winds of Pismis 22 \citep{cangaroo_j1614-518}.
+
+\subsection{2FGL\,J1627.0$-$2425c}
+\label{section_2FGL_J1627.0-2425c}
+
+% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
+% No modifications to background were needed
+
+2FGL\,J1627.0$-$2425c was found by our search to
+have an extension $\sigma=0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
+$\tsext=32.4$
+using photons with energies between 1 \gev and 100 \gev.  
+Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
+
+This source is in a region of remarkably complicated diffuse emission.
+Even though it is $16\degree$ from the Galactic plane, this source is on
+top of the core of the Ophiuchus molecular cloud which contains massive
+star-forming regions that are bright in infrared.  The region also has
+abundant molecular and atomic gas traced by CO and H~I and significant 
+dark gas found only by its association with dust emission
+\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
+more challenging to measure the column density of dust.  Infared and 
+CO ($J=1\rightarrow 0$)
+contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
+spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
+This source might 
+represent $\gamma$-ray emission from the interactions of cosmic rays with
+interstellar gas which has not been accounted for in the LAT diffuse
+emission model.
 
@@
 
-The source 2FGL\,J2021.5+4026 is coincident with 2CG\,078+01 and
-3EG\,J2020+4017 \citep{second_cos_b_catalog,third_egret_catalog} and also
-with the $\gamma$-Cygni SNR. This $\gamma$-ray source has been speculated
+The source 2FGL\,J2021.5+4026 is associated with the $\gamma$-Cygni SNR 
+and has been speculated
 to originate from the interaction of accelerated particles in the SNR
-with dense molecular clouds \citep{pollock_1985,gaisser_1998}, but this
-association was disfavored when the LAT \gev emission from this source
+with dense molecular clouds \citep{pollock_1985,gaisser_1998}. This
+association was disfavored when the \gev emission from this source
 was detected to be pulsed \citep[PSR\,J2021+4026,][]{first_lat_pulsar_cat}.
@@
 a $4.2\sigma$ excess at energies $\sim 30$ \tev from this location
-\citep{lat_bsl,milagro_bright_source_list}.  Veritas also detected an
+\citep{lat_bsl,milagro_bright_source_list}.  VERITAS also detected an
 extended source VER\,J2019+407 coincident with the SNR above 200 \gev
@@
 
-% Veritas observations of $\gamma$-Cygni: 
+% VERITAS observations of $\gamma$-Cygni: 
 %   http://arxiv.org/pdf/0912.4492v1
 %   extended: VER J019+407
-%     Veritas observations of $\gamma$-Cygni veritas_gamma_cygni,
+%     VERITAS observations of $\gamma$-Cygni veritas_gamma_cygni,
 
@@
 Twelve extended sources were included in the 2FGL catalog and two additional extended
-sources were studied in dedicated publications.  Using two years of
+sources were studied in dedicated publications.  Using 2 years of
 LAT data and a new analysis method, we presented the detection of seven
-additional extended sources.  We also reanalyze the spatial shape of the
+additional extended sources.  We also reanalyzed the spatial extents of the
 twelve extended sources in the 2FGL catalog and the two additional sources.  The 21
@@
 Most of the LAT detected extended sources are expected to be of Galactic
-origin as the distance of extragalactic sources (with the exception of
-the local group Galaxies) is typically too large to be able to resolve
-them at $\gamma$-rays energies.
+origin as the distances of extragalactic sources (with the exception of
+the local group Galaxies) are typically too large to be able to resolve
+them at $\gamma$-ray energies.
 
@@
 Figure~\ref{gev_vs_tev_plot} shows that there is a good correlation
-between the size of the sources at \gev and \tev energies. Even so,
-the size of PWNe are expected to vary across the \gev and \tev energy
+between the sizes of the sources at \gev and \tev energies. Even so,
+the sizes of PWNe are expected to vary across the \gev and \tev energy
 range and the size of HESS\,J1825$-$137 is significantly larger at
 \gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting
-to compare the size of other PWN candidates at \gev and \tev energies,
-but definitively measuring this would require a more in-depth analysis
-of the LAT data using the same elliptical surface brightness profile.
-
-Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
+to compare the sizes of other PWN candidates at \gev and \tev energies,
+but definitively measuring a difference in size would require a more in-depth analysis
+of the LAT data using the same elliptical Gaussian spatial model.
+
+Figure~\ref{gev_vs_tev_histogram} compares the sizes of the 21 extended
 LAT sources to the 42 extended H.E.S.S. sources.\footnote{The 
@@
 the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-Catalog. The H.E.S.S. source catalog can be found at \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
+Catalog \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
 Because of the large
@@
 angular resolution of air Cherenkov detectors allows them to measure a
-population of extended sources below the detection threshold limit of the LAT (currently 
-about $\sim0\fdg2$).  \fermi has a five year nominal mission lifetime with
-a goal of ten years of operation.  As Figure~\ref{time_sensitivity} shows,
+population of extended sources below the resolution limit of the LAT (currently 
+about $\sim0\fdg2$).  \fermi has a 5 year nominal mission lifetime with
+a goal of 10 years of operation.  As Figure~\ref{time_sensitivity} shows,
 the low background of the LAT at high energies allows its sensitivity 
@@
 these smaller sources to improve by a factor greater than the square root
-of the exposure.  With increasing exposure, the LAT will likely begin to
+of the relative exposures.  With increasing exposure, the LAT will likely begin to
 detect and resolve some of these smaller \tev sources.
 
-Figure~\ref{compare_index_2FGL} compares the spectral index of LAT
+Figure~\ref{compare_index_2FGL} compares the spectral indices of LAT
 detected extended sources and of all sources in the 2FGL catalog. This, and
-Table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
+Tables~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
 show that the LAT observes a population of hard extended sources
@@
     \caption{
-    Counts maps and test statistic profiles for the SNR IC~443. (a) \ts
+    Counts maps and TS profiles for the SNR IC~443. (a) \ts
     vs. extension of the source. (b) \tsext for individual energy
@@
     \caption{
-    Cumulative distribution of the test statistic for the extension test when fitting
+    Cumulative distribution of the TS for the extension test when fitting
     simulated point-like sources in the 1 GeV to 100 GeV energy range.
@@
     \caption{
-    The projected detection threshold of the LAT to extension after ten years
+    The projected detection threshold of the LAT to extension after 10 years
     for a power-law
@@
   \caption{
-  A test statistic map generated for the region around the SNR 
+  A TS map generated for the region around the SNR 
   IC~443 using 
   photons with energies between
-  1 \gev and 100 \gev.  (a) test statistic map after
+  1 \gev and 100 \gev.  (a) TS map after
   subtracting IC~443 modeled as a point-like source. (b) same as (a), but
@@
   \tablewidth{0pt}
-  \tablecaption{Dual localization, alternative PSF, and alternative diffuse results
+  \tablecaption{Dual localization, alternative PSF, and alternative approach to modeling the diffuse emission
   \label{alt_diff_model_results}
@@
 statistic values from \pointlike, \gtlike, and \gtlike with the alternative
-diffuse model respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$,
-and $\tsext_\altdiff$ are the test statistic values of the extension
-test from \pointlike, \gtlike, and \gtlike with the alternative diffuse
-model respectively.  $\sigma$, $\sigma_\altdiff$, and $\sigma_\altpsf$
-are the fit size assuming
+approach to modeling the diffuse emission respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$,
+and $\tsext_\altdiff$ are the TS values from \pointlike, \gtlike, and \gtlike with the alternative 
+approach to modeling the diffuse emission respectively.  $\sigma$, $\sigma_\altdiff$, and $\sigma_\altpsf$
+are the fit sizes assuming
 a radially-symmetric uniform disk model
-with the standard analysis, the alternative diffuse
-model, and the alternative PSF respectively.  \tsinc is the test statistic
-for the two point-like source hypothesis test 
-(see Section~\ref{dual_localization_method}).
+with the standard analysis, the alternative 
+approach to modeling the diffuse emission, and the alternative PSF respectively.  
 }
@@
   IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
-  ${}^{12}\text{CO}$ ($J=1\rightarrow 0$) emission integrated from $-$8 $\km\,\s^{-1}$
+  CO ($J=1\rightarrow 0$) emission integrated from $-$8 $\km\,\s^{-1}$
   to 20 $\km\,\s^{-1}$.  They are from \cite{co_rho_ophiuci}, were cleaned using
@@
       at \gev energies 
-      with two years of data.  The twelve extended sources included in
+      with 2 years of data.  The twelve extended sources included in
       2FGL are represented by the circular markers (colored red in the online
@@
     A comparison of the sizes of extended sources detected at
-    both \gev and \tev energies.  The \tev size of W30,
+    both \gev and \tev energies.  The \tev sizes of W30,
     2FGL\,J1837.3$-$0700c, 2FGL\,J1632.4$-$4753c, 2FGL\,J1615.0$-$5051,
@@
     W51C is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev
-    size of MSH\,15$-$52, HESS\,J1614$-$518, HESS\,J1632$-$478, and
+    sizes of MSH\,15$-$52, HESS\,J1614$-$518, HESS\,J1632$-$478, and
     HESS\,J1837$-$069 have only been reported with an elliptical 2D
-    Gaussian fit and so the plotted size is the geometric 
+    Gaussian fit and so the plotted sizes are the geometric 
     mean of the semi-major and semi-minor axis.
@@
     \caption{
-    The distributions of the size of 18 extended LAT sources
+    The distributions of the sizes of 18 extended LAT sources
     at \gev energies
-    (colored blue in the electronic version) and the size of the
+    (colored blue in the electronic version) and the sizes of the
     40 extended H.E.S.S. sources at \tev energies
@@
     The \gev size of Vela X is taken from \cite{velax}.  
-    Because of their large size, the shape of RX\,J1713.7$-$3946 and
+    Because of their large sizes, the shape of RX\,J1713.7$-$3946 and
     Vela Jr. were not directly fit at \tev energies

### 2011-12-18 extended_catalog/paper/extended_catalog.tex
imporve tex

@@
 study the ability of the LAT to 
-distinguish between a single extended source and unresolved closely-spaced point sources
+distinguish between a single extended source and unresolved closely-spaced point-like sources
 In Section~\ref{test_2lac_sources}, we further demonstrate that our
@@
 the highest energies (when averaged over the acceptance of the LAT)
-and is limited by the strip pitch to the height of the tracker
+and is limited by the ratio of the strip pitch to the height of the tracker
 \citep{atwood_LAT_mission,on_orbit_calibration,lat_on_orbit_psf}.\footnote{More
@@
 It works by maximizing the Poisson 
-likelihood to detect the observed distributions of gamma rays (referred to as counts)
+likelihood to detect the observed distributions of $\gamma$-rays (referred to as counts)
 given a parametrized spatial and spectral model of the sky.  
-The data are binned spatially, using HEALPix pixellization, and spectrally 
+The data are binned spatially, using a HEALPix pixellization, and spectrally 
 \citep{healpix} and the likelihood is maximized over all bins in
@@
 and so the improvement is closer to a factor corresponding
-to the square root of the relative exposures and is caused by Poisson fluctuations in the background.
+to the square root of the relative exposures that is caused by Poisson fluctuations in the background.
 

### 2011-12-20 extended_catalog/paper/extended_catalog.tex
neew draft v7
better description of diffuse sysetmatics

@@
 this tests systematics that may be due to imperfect modeling of the
-diffuse emission in the region. Nevertheless, 
-this alternative approach to modeling the diffuse emission
-does not test all systematics related to the diffuse emission model.
-In particular, because the alternative approach uses the same underlying gas
-maps it is unable to be used to assess systematics due to mischaracterization of local
-diffuse structure due to lack of resolution of the underlying maps.
+diffuse emission in the region. 
+Nevertheless, this alternative approach to modeling the diffuse emission
+does not test all systematics related to the diffuse emission model. In
+particular, because the alternative approach uses the same underlying gas
+maps, it is unable to be used to assess systematics due to insufficient
+resolution of the underlying maps. Structure in the diffuse emission that
+is not correlated with these maps will also not be assessed by this test.
 

### 2012-01-19 pwncatalog/PWNCAT2/v1/off_pulse/off_peak_bb.py
try with bayesian block analysis

@@ -1,0 +1,94 @@
+from argparse import ArgumentParser
+import copy
+import numbers
+import pickle
+import yaml
+import numpy as np
+import pylab as P
+
+from setup_pwn import setup_pwn
+
+from uw.pulsar import lc_plotting_func
+from uw.pulsar import lcprimitives as lp
+from uw.pulsar.lcprimitives import * # for the eval
+from uw.pulsar.lc_off_peak import OffPeak
+from uw.pulsar.phase_range import PhaseRange
+from uw.pulsar import lcfitters as lf
+from uw.like.Models import ExpCutoff
+from toolbag import tolist
+
+
+def off_peak_bb(phases,ncpPrior=3):
+
+    bb = BayesianBlocks.BayesianBlocks(phases)
+    xx, yy = bb.lightCurve(ncpPrior)
+
+    # min:
+    
+
+
+
+def find_offpeak(ft1,name,rad,peaks,pwncat1phase):
+    
+    plc = lc_plotting_func.PulsarLightCurve(ft1, 
+                                           psrname=name, radius=rad,
+                                           emin=50, emax=300000)
+    plc.fill_phaseogram()
+
+    phases = plc.get_phases()
+
+
+    off_peak.axvspan(label='lande', alpha=0.25, color='green')
+    pwncat1phase.axvspan(label='pwncat1', alpha=0.25, color='blue')
+
+    P.legend()
+
+    P.title(name)
+
+    P.savefig('results_%s.pdf' % name)
+    #P.savefig('phaseogram_%s.pdf' % name)
+
+    global results
+    results=tolist(
+            dict(
+                lande_phase = off_peak.tolist(),
+                pwncat1phase = pwncat1phase.tolist(),
+                )
+            )
+
+    yaml.dump(results,open('results_%s.yaml' % name,'w'))
+
+    results['lcf'] = lcf
+    results['init_template'] = init_template
+    results['final_template'] = lct
+
+    pickle.dump(results,open('results_%s.pickle' % name,'w'))
+
+
+if __name__ == '__main__':
+
+    parser = ArgumentParser()
+    parser.add_argument("--pwndata", required=True)
+    parser.add_argument("-n", "--name", required=True, help="Name of the pulsar")
+    parser.add_argument("--pwnphase", required=True)
+    parser.add_argument("--pwnpeaks", required=True)
[…]

### 2012-01-19 pwncatalog/PWNCAT2/paper/pwncat2.tex
new paper draft

--- 2011-12-18 extended_catalog/paper/extended_catalog.tex
@@
 
-% some units
-\newcommand{\kev}{\text{Kev}\xspace}
-\newcommand{\mev}{\text{MeV}\xspace}
-\newcommand{\gev}{\text{GeV}\xspace}
-\newcommand{\tev}{\text{TeV}\xspace}
-\newcommand{\s}{\text{s}\xspace}
-\newcommand{\ph}{\text{ph}\xspace}
-\newcommand{\cm}{\text{cm}\xspace}
-\newcommand{\km}{\text{km}\xspace}
-\newcommand{\phflux}{\ensuremath{\text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}}\xspace}
-\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
-\newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{2pts}}}\xspace}
-
-\newcommand{\likelihood}{\ensuremath{\mathcal{L}}\xspace}
-
-\newcommand{\chandra}{\text{{\em Chandra}}\xspace}
-\newcommand{\swiftxrt}{\text{{\em Swift}/XRT}\xspace}
-\newcommand{\rosat}{\text{{\em ROSAT}}\xspace}
-\newcommand{\suzaku}{\text{{\em Suzaku}}\xspace}
-\newcommand{\asca}{\text{{\em ASCA}}\xspace}
-\newcommand{\einstein}{\text{{\em Einstein}}\xspace}
-\newcommand{\xmmnewton}{\text{{\em XMM-Newton}}\xspace}
-\newcommand{\fermi}{\textit{Fermi}\xspace}
-
-\newcommand{\rsixeight}{{\ensuremath{\text{r}_{68}}}\xspace}
-
-\newcommand{\tsextpointlike}{\ensuremath{\tsext_{,\pointlike}}\xspace}
-\newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}\xspace}
-
-\newcommand{\ts}{\text{TS}\xspace}
-\newcommand{\glon}{\text{GLON}\xspace}
-\newcommand{\glat}{\text{GLAT}\xspace}
-\newcommand{\altdiff}{\text{alt,diff}\xspace}
-\newcommand{\altpsf}{\text{alt,psf}\xspace}
-\newcommand{\sys}{\text{sys}\xspace}
-\newcommand{\stat}{\text{stat}\xspace}
-
-% the program names
-\newcommand{\gtlike}{\ensuremath{\mathtt{gtlike}}\xspace}
-\newcommand{\pointlike}{\ensuremath{\mathtt{pointlike}}\xspace}
-\newcommand{\gtobssim}{\ensuremath{\mathtt{gtobssim}}\xspace}
-\newcommand{\minuit}{\ensuremath{\mathtt{minuit}}\xspace}
-
-\newcommand{\degree}{^\circ\xspace}
-
-%\newcommand{\newtext}[1]{{\textbf #1}}
-\newcommand{\newtext}[1]{{\bfseries \color{red}#1}}
-
 \usepackage{color}
@@
 
-\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data}
-\shorttitle{Search for Extended LAT Sources}
+\title{PWNCAT2}
+\shorttitle{PWNCAT2}
 
@@
 Gamma rays: observations; 
-ISM: supernova remnants;
-Methods: statistical;
 pulsar wind nebula
@@
 \author{
-J.~Lande\altaffilmark{1,2}, 
-M.~Ackermann\altaffilmark{3,4}, 
-A.~Allafort\altaffilmark{1}, 
-J.~Ballet\altaffilmark{5}, 
-K.~Bechtol\altaffilmark{1}, 
-T.~H.~Burnett\altaffilmark{6}, 
-J.~Cohen-Tanugi\altaffilmark{7}, 
-A.~Drlica-Wagner\altaffilmark{1}, 
-S.~Funk\altaffilmark{1,8}, 
-F.~Giordano\altaffilmark{9,10}, 
-M.-H.~Grondin\altaffilmark{11,12}, 
-M.~Kerr\altaffilmark{1}, 
-M.~Lemoine-Goumard\altaffilmark{13,14}
+Lots of peple\dots
 }
-\altaffiltext{1}{W.
-W.
-Hansen Experimental Physics Laboratory, Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics and SLAC National Accelerator Laboratory, Stanford University, Stanford, CA 94305, USA}
-\altaffiltext{2}{email: joshualande@gmail.com}
-\altaffiltext{3}{Deutsches Elektronen Synchrotron DESY, D-15738 Zeuthen, Germany}
-\altaffiltext{4}{email: markus.ackermann@desy.de}
-\altaffiltext{5}{Laboratoire AIM, CEA-IRFU/CNRS/Universit\'e Paris Diderot, Service d'Astrophysique, CEA Saclay, 91191 Gif sur Yvette, France}
-\altaffiltext{6}{Department of Physics, University of Washington, Seattle, WA 98195-1560, USA}
-\altaffiltext{7}{Laboratoire Univers et Particules de Montpellier, Universit\'e Montpellier 2, CNRS/IN2P3, Montpellier, France}
-\altaffiltext{8}{email: funk@slac.stanford.edu}
-\altaffiltext{9}{Dipartimento di Fisica ``M. Merlin" dell'Universit\`a e del Politecnico di Bari, I-70126 Bari, Italy}
-\altaffiltext{10}{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70126 Bari, Italy}
-\altaffiltext{11}{Max-Planck-Institut f\"ur Kernphysik, D-69029 Heidelberg, Germany}
-\altaffiltext{12}{Landessternwarte, Universit\"at Heidelberg, K\"onigstuhl, D 69117 Heidelberg, Germany}
-\altaffiltext{13}{Universit\'e Bordeaux 1, CNRS/IN2p3, Centre d'\'Etudes Nucl\'eaires de Bordeaux Gradignan, 33175 Gradignan, France}
-\altaffiltext{14}{Funded by contract ERC-StG-259391 from the European Community}
 
 \begin{abstract}
-Spatial extension is an important characteristic for correctly
-associating $\gamma$-ray-emitting sources with their counterparts at other wavelengths
-and for obtaining an unbiased model of their spectra.  We present a new
-method for quantifying the spatial extension of sources detected by the Large
-Area Telescope (LAT), the primary science instrument on the {\em \fermi
-Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
-simulations to validate this tool and calculate the LAT threshold for
-detecting the spatial extension of sources.  
-We then test all sources
-in the second \fermi-LAT catalog (2FGL) for extension. 
-We report the detection of seven new spatially extended sources.
+  Abstract
 \end{abstract}
@@
 
-A number of astrophysical source classes including supernova remnants
-(SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
-and galaxy clusters are expected to be spatially resolvable 
-by the Large Area Telescope (LAT), the primary instrument on the {\em \fermi
-Gamma-ray Space Telescope} (\fermi).
-Additionally, dark matter satellites are also hypothesized to
-be spatially extended. See \cite{atwood_fermi} for pre-launch predictions.
-The LAT has
-detected seven SNRs which are significantly extended
-at \gev energies: 
-W51C, W30, 
-IC~443, W28, W44, RX\,J1713.7$-$3946,
-and the Cygnus Loop
-\citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, 
-three extended PWN have been detected by the LAT: MSH\,15$-$52, Vela~X, and
-HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
-nearby galaxies, the Large and Small Magellanic Clouds, 
-and the lobes of one
-radio galaxy, Centaurus A, were spatially resolved at \gev energies
-\citep{lmc,smc,cen_a_lat}.  A number of additional sources detected
-at \gev energies are positionally coincident with sources that exhibit
-large enough extension at other wavelengths to be spatially
-resolvable by the LAT at \gev energies.
-In particular, there are 59 \gev sources in the second Fermi Source Catalog (2FGL)
-that might be associated with extended SNRs \citep[2FGL][]{second_cat}.
-Previous analyses of extended LAT sources were performed as dedicated
-studies of individual sources so we expect that a systematic scan of
-all LAT detected sources could uncover additional spatially extended
-sources.
-
-The current generation of air Cherenkov detectors have
-made it apparent that many sources can be spatially resolved
-at even higher energies.
-Most
-prominent was a survey of the Galactic plane using the High Energy
-Stereoscopic System (H.E.S.S) which reported 14 spatially extended
-sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
-\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
-sources detected at \tev energies, most notably the $\gamma$-ray binaries
-LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI},
-HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes},
-have no detectable extension.  High-energy $\gamma$-rays from
-\tev sources are produced by the decay of $\pi^0$s produced by hadronic
-interactions with interstellar matter and by relativistic electrons
-due to Inverse Compton (IC) scattering and bremsstrahlung radiation.  
-It is plausible that the \gev and
-\tev emission from these sources originates from the same population of
-high-energy particles and so at least some of these sources should be
-detectable at \gev energies.  Studying 
-these \tev sources at \gev energies would help to
-determine the emission mechanisms producing these high energy photons.
-
-The LAT is a pair conversion telescope that has been surveying the
-$\gamma$-ray sky since 2008 August.  The LAT has broad energy coverage
-(20 \mev to $>300$ \gev), wide field of view ($\sim 2.4$ sr), and large
-effective area ($\sim 8000\ \cm^2$ at $>1$ \gev) 
-Additional information about the performance of the LAT can be found in
-\cite{atwood_LAT_mission}.
-
-Using 2 years of all-sky survey data, the LAT Collaboration published
-2FGL \citep[2FGL][]{second_cat}.
-The possible counterparts of many of these sources can be spatially resolved
-when observed at other frequencies but detecting the spatial extension
-of these sources at \gev energies is difficult because the size of the
-point-spread function (PSF) of the LAT is comparable to the typical size
-of many of these sources.
-
-The capability to spatially resolve \gev $\gamma$-ray
-sources is important for several reasons.  
-Finding a coherent source extension across different energy bands can
-help to associate a LAT source to an otherwise confused counterpart.
-Furthermore, $\gamma$-rays emission from dark matter
-annihilation has been predicted to be detectable by the LAT.
-Some of the dark matter substructure in our Galaxy 
-could be spatially resolvable by the LAT \citep{pre_luanch_dark_matter_fermi}.  
-Characterization of spatial extension could help to identify this substructure.
-Also,
-due to the strong energy dependence of the LAT PSF, the spatial and
-spectral characterization of a source cannot be
-decoupled. An inaccurate
-spatial model will bias the spectral model of the source and vice versa. Specifically,
-modeling a spatially extended source as point-like will systematically
-soften measured spectra. Furthermore, correctly
-modeling source extension is important for 
-understanding an entire region of the sky. For example,
-an imperfect model of the spatially extended LMC introduced
-significant residuals in the surrounding region \citep{first_cat,second_cat}.
-Such residuals can bias the significance and measured spectra of
-neighboring sources in the densely populated Galactic plane.
-
- For these reasons, in Section~\ref{analysis_methods_section}
-we present a new systematic method for analyzing spatially extended
-LAT sources.  In Section~\ref{monte_carlo_validation}, we demonstrate
-that this method can be used to test the statistical significance of the
-extension of a LAT source and in Section~\ref{extension_sensitivity}
-we calculate the LAT detection threshold to resolve the extension
-of a source.  In Section~\ref{dual_localization_method}, we
-study the ability of the LAT to 
-distinguish between a single extended source and unresolved closely-spaced point sources
-In Section~\ref{test_2lac_sources}, we further demonstrate that our
-detection method does not misidentify point-like sources as being
-extended by testing the extension of active Galactic nuclei (AGN)
-believed to be unresolvable.  In Section~\ref{validate_known},
-we systematically reanalyze the twelve extended sources included
-in the 2FGL catalog and in Section~\ref{systematic_errors_on_extension}
-we describe a way to estimate systematic errors on the measured extension of a source.
-In Section~\ref{extended_source_search_method}, we
-describe a search for new spatially extended LAT sources. Finally,
-in Section~\ref{new_ext_srcs_section} we present the detection of the
-extension of nine spatially extended sources that were reported in the 2FGL catalog
-but treated as point-like in the analysis.  Two of these sources have been previously analyzed in
-dedicated publications.
+Introduction\dots
 
 \section{Analysis Methods}
-\label{analysis_methods_section}
-
-Morphological studies of sources using the LAT are challenging
-because of the strongly energy-dependent PSF that is comparable in
-size to the extension of many sources expected to be detected at
-\gev energies.  Additional complications arise for sources along
-the Galactic plane due to systematic uncertainties in the model for
-Galactic diffuse emission.
-
-For energies below $\sim$300~\mev, the angular resolution is limited by
-multiple scattering in the silicon strip tracking section
-of the detector and is several degrees at 100 \mev.  The PSF improves
-with energy approaching a 68\% containment radius of $\sim0\fdg2$ at
-the highest energies (when averaged over the acceptance of the LAT)
-and is limited by the strip pitch to the height of the tracker
-\citep{atwood_LAT_mission,on_orbit_calibration,lat_on_orbit_psf}.\footnote{More
-information about the performance of the LAT can be found at the \fermi
-Science Support Center (FSSC, \url{http://fermi.gsfc.nasa.gov}).} However,
-since most high energy astrophysical sources have spectra that decrease
-rapidly with increasing energy, there are typically fewer higher
-energy photons with improved angular resolution. Therefore sophisticated
-analysis techniques are required to maximize the sensitivity of the LAT
-to extended sources.
-
-\subsection{Modeling Extended Sources in the \pointlike Package}
-
-A new maximum-likelihood analysis tool has been developed to address the
-unique requirements for studying spatially extended sources with the LAT.
-It works by maximizing the Poisson 
-likelihood to detect the observed distributions of gamma rays (referred to as counts)
-given a parametrized spatial and spectral model of the sky.  
-The data are binned spatially, using HEALPix pixellization, and spectrally 
-\citep{healpix} and the likelihood is maximized over all bins in
-a region.
-The extension of a source can be modeled by a geometric shape
-(e.g. a disk or a two-dimensional Gaussian) and the position, extension,
-and spectrum of the source can be simultaneously fit.
-
-This type of analysis is not feasible using the standard LAT likelihood
-analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
-FSSC.} because it can only fit the spectral parameters of the model
-unless a more sophisticated iterative procedure is used.  
-We note that \gtlike has been used in the
-past in several studies of source extension in the LAT Collaboration
-\citep{lmc,smc,w28,w51c}.  In these studies, a 
-set of \gtlike maximum likelihood fits at fixed extensions was used
-to build a profile of the likelihood as a function of extension.
-The \gtlike likelihood profile approach has been shown to correctly
-reproduce the extension of simulated extended sources assuming that the
-true position is known \citep{francesco_2011}.  But it is not optimal
-because the position, extension, and spectrum of the source must be
-simultaneously fit to find the best fit parameters and to maximize the
-statistical significance of the detection.  Furthermore, because the \gtlike
-approach is computationally intensive, no large-scale Monte Carlo
-simulations have been run to calculate its false detection rate.
-
-The approach presented here is based on a second maximum likelihood
-fitting package developed in the LAT Collaboration called \pointlike
-\citep{first_cat,matthew_kerr_thesis}.  The choice to base the
-spatial extension fitting on \pointlike rather than \gtlike was made
-due to considerations of computing time.  The \pointlike algorithm was
-optimized for speed to handle larger numbers of sources efficiently,
-which is important for our catalog scan and for being able
-to perform large-scale Monte Carlo simulations to validate the analysis.
-Details on the \pointlike package can be
-found in \cite{matthew_kerr_thesis}.  We extended the code to allow a
-simultaneous fit of the source extension together with the position and
-the spectral parameters.
-
-\subsection{Extension Fitting}
-\label{extension_fitting}
-
-In \pointlike, one can fit the position and extension 
-of a source under the assumption that the source model
-can be factorized:
-$M(x,y,E)=S(x,y)\times X(E)$, where $S(x,y)$ is the spatial distribution
-and $X(E)$ is the spectral distribution.  To fit an extended source,
-\pointlike convolves the extended source shape with the PSF (as a function
-of energy) and uses the \minuit library \citep{minuit_documentation}
-to maximize the likelihood by simultaneously varying the position,
-extension, and spectrum of the source.  As will be described in
-Section~\ref{monte_carlo_validation}, simultaneously fitting the
-position, extension, and spectrum is important to maximize
-the statistical significance of the detection of the extension of a source.
-To avoid projection effects, the longitude and latitude 
-of the source are
-not directly fit but instead the displacement of the source 
-in a reference frame centered on the source.
-
-The significance of the extension of a source can be calculated from the
-likelihood ratio test of a hypothesis with a spatially extended source and
-a hypothesis with a point-like source. The test statistic (TS) for this procedure
-is defined as
-\begin{equation}
-  \tsext=2\log(\likelihood_\text{ext}/\likelihood_\text{ps}) 
-\end{equation}
-where \likelihood is the Poisson likelihood.
-\pointlike calculates \tsext by fitting a source first with a spatially
-extended model and then as a point-like source.  The interpretation
-of \tsext in terms of a statistical significance is discussed in
-Section~\ref{monte_carlo_validation}.
-
-For extended sources with an assumed radially-symmetric shape,
-we optimized the calculation by performing one
-of the integrals analytically.
-The expected photon 
-distribution can be written as
-\begin{equation}
-  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r' dr' d\phi'
-\end{equation}
-where $\vec r$ represents the position in the sky and
-$I_\text{src}(\vec r)$ is the spatial distribution of the
-source.
-The PSF of the LAT is currently parameterized 
-in the Pass~7\_V6 (P7\_V6) Source Instrument
-Response Function \citep[IRFs,][]{lat_on_orbit_psf} by a King function \citep{king_function}:
-\begin{equation}
-  \text{PSF}(r) = 
-  \frac{1}{2\pi\sigma^2}
-  \left(1-\frac{1}{\gamma}\right)
-  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
-\end{equation}
-where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
-\citep{matthew_kerr_thesis}.  For radially-symmetric extended sources,
-the angular part of the integral can be evaluated analytically
-\begin{align}
-  \text{PDF}(u) & = \int_0^\infty r' dr'
-  I_\text{src}(v) 
-  \int_0^{2\pi} d\phi' 
-  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
-  \\
-  & = \int_0^\infty dv
-  I_\text{src}(v) 
-  \left(\frac{\gamma-1}{\gamma}\right)
-  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
-  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right),
-\end{align}
-where $v=(r'/\sigma)^2/2$ and ${}_2F_1$ is the Gaussian hypergeometric
-function.  This convolution formula reduces the expected photon
-distribution to a single numerical integral.
-
-There will always be a small numerical discrepancy between the expected
-photon distribution derived from a true point-like source and a very small
-extended source due to numerical error in the convolution.  In most
-situations, this error is insignificant.  But in particular for
-very bright sources, this numerical error has the potential to bias the
-TS for the extension test. Therefore, when calculating
-\tsext, we compare the likelihood fitting the source with an extended
-spatial model to the likelihood when the extension is
-fixed to a very small value ($10^{-10}$ degrees in radius 
-for a uniform disk model).
-
-We estimate the error on the extension of a source by fixing
-the position of the source and varying the extension until the
-log of the likelihood has decreased by 1/2, corresponding to a $1\sigma$ error
-\citep{Statistical_methods_book}.  Figure~\ref{four_plots_ic443}
-demonstrates this method by showing the change in the log of the
-likelihood when 
-varying the modeled extension of the SNR IC~443.  The localization
-error is calculated by fixing the extension and spectrum of the source
-to their best fit values and then
-fitting the log of the likelihood to
-a 2D Gaussian as a function
-of position. This localization error algorithm is further described in
-\cite{second_cat}.
-
-\subsection{\gtlike Analysis Validation}
-\label{gtlike_crosscheck}
-
-\pointlike is important for LAT analyses that require many iterations
-such as source localization and extension fitting.  On the other hand,
-because \gtlike makes fewer approximations in calculating the likelihood
-we expect the spectral parameters found with \gtlike to be slightly more
-accurate.  Furthermore, because \gtlike is the 
-standard likelihood analysis package for LAT data, 
-it has been more extensively validated for spectral analysis.
-For those reasons, in the following analysis we used \pointlike to
-determine the position and extension of a source and subsequently derived
-the spectrum using \gtlike. Both \gtlike and \pointlike can be used to
-estimate the statistical significance of the extension of a source and we
-required that both methods agree for a source to be considered extended.
-There was good agreement between the two methods.  Unless explicitly
-mentioned, all \ts, \tsext, and spectral parameters were calculated using
-\gtlike with the best-fit positions and extension found by \pointlike.
-
-\subsection{Comparing Source Sizes}
-
-\label{compare_source_size}
-
-We considered two models for the
-surface brightness profile for extended sources: a 2D Gaussian model
-\begin{equation}\label{gauss_pdf}
-  I_\text{Gaussian}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
-\end{equation}
-or a uniform disk model
-\begin{equation}\label{disk_pdf}
-  I_\text{disk}(x,y)=
-  \begin{cases}
-    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
-    0                      & x^2+y^2>\sigma^2.
-  \end{cases}
-\end{equation}
-Although these shapes are significantly different,
-Figure~\ref{compare_disk_gauss} shows that, after convolution with the
-LAT PSF, their PDFs are similar for a source that has a 0\fdg5 radius
-typical of LAT detected extended sources.  To allow a valid comparison
-between the Gaussian and the uniform disk models,
-we define the source size as the radius containing 68\% of the
-intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
-and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$ is defined
-in Equation~\ref{gauss_pdf} and Equation~\ref{disk_pdf} respectively.
-For this example, $\rsixeight=0\fdg5$ so $\sigma_\text{disk}=0.61\degree$
-and $\sigma_\text{Gaussian}=0.33\degree$.
-
-For sources that are comparable in size to the PSF,
-the differences in the PDF for
-different spatial models are lost in the noise and the LAT is not sensitive
-to the detailed spatial structure of these sources.  Therefore, in our
-search for extended sources we use only a radially-symmetric uniform
-disk spatial model. Unless otherwise noted,
-we quote the radius to the edge ($\sigma$) as the size of the source.
-
-\section{Validation of the Analysis Method}
-\label{monte_carlo_validation}
-
-We evaluated the false detection probability for the measurement of source extent
-by fitting the extensions of point-like sources.  \cite{mattox_egret}
-discuss that the TS distribution for a likelihood ratio test
-on the existence of a source at a given position is
-\begin{equation}\label{ts_ext_distribution}
-  P(\ts)=\onehalf(\chi^2_1(\ts)+\delta(\ts)).
-\end{equation}
-The particular form of Equation \ref{ts_ext_distribution} is due to the
-null hypothesis (source flux $\Phi=0$) residing on the edge of parameter
-space and the model hypothesis adding a single degree of freedom.
-It leads to the often quoted result $\sqrt{TS}=\sigma$, where 
-$\sigma$ here refers to the significance of the detection. It is plausible
-to expect a similar distribution for the TS in the test for
-source extension since the same conditions apply (with the source flux
-$\Phi$ replaced by the source radius $r$ and $r<0$ being unphysical).
-To verify Equation~\ref{ts_ext_distribution}, we evaluated the
-empirical distribution function of \tsext computed from simulated sources.
-
-We simulated point-like sources with various spectral forms using
-the LAT on-orbit simulation tool
-\gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit the sources
-with \pointlike using both point-like
-and extended source hypotheses.  These point-like sources were simulated with a power-law
-spectral model with integrated fluxes above 100 \mev ranging from $3\times10^{-9}$ 
-to $1\times10^{-5}$ \phflux and spectral
-indices ranging from 1.5 to 3.  These values
-were picked to represent typical parameters of LAT-detected
-sources. The point-like sources were simulated on top of an isotropic
-background with a power-law spectral model with
-integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux sr$^{-1}$
-and spectral index 2.1.
-This was
-taken to be the same as the isotropic spectrum measured by EGRET
-\citep{sreekumar_isotropic}.  This spectrum is comparable
-to the high-latitude background intensity seen by the LAT.
-The Monte Carlo simulation was performed
-over a one-year observation period using a representative 
-spacecraft orbit and livetime.
-The reconstruction was performed
-using the P7\_V6 Source class event selection and IRFs \citep{lat_on_orbit_psf}. For each 
-significantly detected point-like source ($\ts\ge25$), we used \pointlike
-to fit the source as an extended source and calculate \tsext.
-This entire procedure was performed twice, once fitting in the 1 \gev
-to 100 \gev energy range and once fitting in the 10 \gev to 100 \gev
-energy range.
-
-For each set of spectral parameters, $\sim20,000$ statistically independent
-simulations were performed. For dimmer spectral models, many of the
-simulations left the source insignificant ($\ts<25$)
-and were discarded.  Table~\ref{ts_ext_num_sims}
-shows the different spectral models used in our study as well as the
-number of simulations and the average point-like source
-significance.  The cumulative density of \tsext is plotted in
-Figures~\ref{ts_ext_mc_1000} and \ref{ts_ext_mc_10000} 
-and compared to the $\chi^2_1/2$ distribution of
-Equation~\ref{ts_ext_distribution}.
-
-Our study shows broad agreement between simulations and
-Equation~\ref{ts_ext_distribution}. To the extent that there is
-a discrepancy, the simulations tended to produce smaller than expected
-values of \tsext which would make the formal significance conservative.
-Considering the distribution in Figures~\ref{ts_ext_mc_1000} and
-\ref{ts_ext_mc_10000}, the choice of a threshold \tsext set to 16
-(corresponding to a formal $4\sigma$ significance) is reasonable.
-
-\section{Extended Source Detection Threshold}
-\label{extension_sensitivity}
-
-We calculated the LAT flux 
-threshold to detect spatial extent. We define the detection threshold as the flux at
-which the value of $\tsext$ averaged over many statistical realizations is
-$\langle\tsext\rangle=16$ 
-(corresponding to a formal $4\sigma$ significance)
-for a source of a given extension.
-
-We used a simulation setup similar to that described in
-Section~\ref{monte_carlo_validation}, but instead of point-like sources
-we simulated extended sources with radially-symmetric uniform disk spatial 
-models. Additionally, we simulated our sources over the two-year
-time range included in the 2FGL catalog.  For each extension and spectral index,
-we selected a flux range which bracketed $\tsext=16$ and performed an
-extension test for $>100$ independent realizations of ten fluxes in
-the range.  We calculated $\langle\tsext\rangle=16$ by fitting a line
-to the flux and $\tsext$ values in the narrow range.
-
-Figure~\ref{index_sensitivity} shows the threshold for sources of four
-spectral indices from 1.5 to 3 and extensions varying from $\sigma=0\fdg1$
-to $2\fdg0$.  
-The threshold is high for small extensions when the
-source is 
-small compared to the size of the PSF. 
-It drops quickly with increasing source size and reaches
-a minimum around 0\fdg5. 
-The threshold increases
-for large extended sources because the source becomes
-increasingly diluted by the background.
-Figure~\ref{index_sensitivity} shows
-the threshold using photons with energies between 100 \mev and 100 \gev
-and also using only photons with energies between 1 \gev and 100 \gev.
-Except for very large or very soft
-sources, the threshold is
-not substantially improved by including photons with energies between 100 \mev and
-1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}
-which shows \tsext for the SNR IC~443 computed independently in twelve
-energy bins between 100 \mev and 100 \gev. For IC~443, which has a
-spectral index $\sim2.4$ and an extension $\sim0\fdg35$, 
-almost the entire 
-increase in likelihood from optimizing the source extent in the model
-comes
-from energies above 1 \gev.  Furthermore, other systematic errors
-become increasingly large at low energy. For our extension search
-(Section~\ref{extended_source_search_method}),
-we therefore used only photons with energies above 1 \gev.
-
-Figure~\ref{all_sensitivity} shows the flux threshold as a function of
-source extension for different background levels ($1\times$, $10\times$,
-and $100\times$ the nominal background), different spectral indices,
-and two different energy ranges (1 \gev to 100 \gev and 10 \gev to
-100 \gev).  The detection threshold is higher for sources in regions of
-higher background.  When studying sources only at energies above 1 \gev,
-the LAT detection threshold (defined as the 1 \gev to 100 \gev flux at
-which $\langle\tsext\rangle=16$) depends less strongly on the 
-spectral index of the source. 
-The index dependence of the detection threshold is
-even weaker when considering only photons with energies above 10 \gev
-because the PSF changes little from 10 \gev to 100 \gev.
-Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
-sources that will be discussed in Sections~\ref{validate_known} and
-\ref{new_ext_srcs_section}.  The extension thresholds are tabulated in
-Table~\ref{all_sensitivity_table}.
-
-Finally, Figure~\ref{time_sensitivity} shows the projected
-detection threshold of the LAT to extension with a 10 year
-exposure against 10 times
-the isotropic background measured by EGRET. This background is
-representative of the background near the Galactic plane.  For small
-extended sources, the threshold improves by a factor larger
-than the square root of the relative exposures because the LAT is signal-limited
-at high energies where the present analysis is most sensitive. For large
-extended sources, the relevant background is over a larger spatial range
-and so the improvement is closer to a factor corresponding
-to the square root of the relative exposures and is caused by Poisson fluctuations in the background.
-
-\section{Testing Against Source Confusion}
-\label{dual_localization_method}
-
-It is impossible to discriminate using only LAT data between a
-spatially extended source and multiple point-like sources separated by
-angular distances comparable to or smaller than the size of the LAT PSF.
-To assess the plausibility of source confusion for situations
-in which $\tsext\ge16$, we developed an algorithm in \pointlike to
-simultaneously fit the positions and spectra of two point-like sources.
-
-After simultaneously fitting the two positions and two spectra,
-we define \tsinc as twice the increase in the log of the likelihood
-fitting the region with two point-like sources compared to fitting the
-region with one point-like source:
-\begin{equation}
-  \tsinc=2\log(\likelihood_\text{2pts}/\likelihood_\text{ps}).
-\end{equation} 
-For the following analysis of LAT data, \tsinc was computed
-by fitting the spectra of the two point-like sources in \gtlike using the best fit positions
-of the sources found by \pointlike.
-
-\tsinc cannot be quantitatively compared to \tsext using a simple
-likelihood ratio test to evaluate which model is significantly better
-because the models are not nested \citep{statistics_with_care}.
-Even though the comparison of \tsext with \tsinc is not a calibrated
-test, $\tsext>\tsinc$ indicates that the likelihood for the extended
-source hypothesis is higher than for two point-like sources and we only
-consider a source to be extended if $\tsext>\tsinc$.
-
-We assessed the power of the $\tsext>\tsinc$ test with a Monte Carlo
-study.  We simulated one spatially extended source and fit it as both
-an extended source and as two point-like sources using \pointlike.
-We then simulated two point-like sources and fit them with the same two
-hypotheses. By comparing the distribution of \tsinc and \tsext computed by
-\pointlike for the two cases, we evaluated how effective the $\tsext>\tsinc$
-test is at rejecting cases of source confusion as well as how
-likely it is to incorrectly reject that an extended source is spatially
-extended.  All sources were simulated using the same time range as in
-Section~\ref{extension_sensitivity} against a background 10 times the
-isotropic background measured by EGRET, representative of the background
-near the Galactic plane.
-
-We did this study first in the energy range from 1 \gev to 100 \gev by
-simulating extended sources of flux $4\times10^{-9}$ \phflux integrated
-from 1 \gev to 100 \gev and a power-law spectral model with
-spectral index 2.  This spectrum was picked to be representative of the
-new extended sources that were discovered in the following analysis
-when looking in the 1 \gev to 100 \gev energy range
-(see Section~\ref{new_ext_srcs_section}).
-We simulated these sources using uniform disk spatial models
-with extensions varying
-up to $1\degree$.  
-Figure~\ref{confusion_extended_plot}a shows the distribution
-of \tsext and \tsinc and 
-Figure~\ref{confusion_extended_plot}c shows 
-the distribution of $\tsext-\tsinc$ as a
-function of the simulated extension of the source
-for 200 statistically independent simulations.
-
-Figure~\ref{confusion_2pts_plot}a shows the same plot but when fitting
-two simulated point-like sources each with half of the flux of
-the spatially extended source and with the same spectral index as the
-extended source.  Finally, Figure~\ref{confusion_2pts_plot}c shows the same
-plot with each point-like source having the same flux but different
-spectral indices.  One point-like source had a spectral index of 1.5
-and the other an index of 2.5.
-These indices are representative of the range of indices of LAT-detected
-sources.
-
-The same four plots are shown in Figure~\ref{confusion_extended_plot}b, \ref{confusion_extended_plot}d, 
-\ref{confusion_2pts_plot}b, and \ref{confusion_2pts_plot}d but this
-time when analyzing a source of flux $10^{-9}$ \phflux (integrated from
-10 \gev to 100 \gev) only in the 10 \gev to 100 \gev energy range.
-This flux is typical of the new extended sources discovered
-using only photons with energies between 10 \gev and 100 \gev (see
-Section~\ref{new_ext_srcs_section}).
-
-Several interesting conclusions can be made from this study.  As one would
-expect, $\tsext-\tsinc$ is mostly positive when fitting the simulated
-extended sources.  In the 1 \gev to 100 \gev analysis, only 11 of the
-200 simulated extended sources had $\tsext>16$ but were incorrectly
-rejected due to \tsinc being greater than \tsext.  In the 10 \gev to 100 \gev
-analysis, only 7 of the 200 sources were incorrectly rejected. From this,
-we conclude that this test is unlikely to incorrectly reject truly
-spatially extended sources.
-
-On the other hand, 
-it is often
-the case that $\tsext>16$ when testing the 
-two simulated point-like sources
-for extension.  This is especially the case
-when the two sources had the same spectral index. Forty out of 200 sources
-in the 1 \gev to 100 \gev energy range and 43 out of 200 sources in the
-10 \gev to 100 \gev energy range had $\tsext>16$.  But in these cases,
-we always found the single extended source fit to be worse than
-the two point-like source fit.  From this, we conclude that the $\tsext>\tsinc$
-test is powerful at discarding cases in which the true emission comes
-from two point-like sources.
-
-The other interesting feature in Figure~\ref{confusion_extended_plot}a
-and \ref{confusion_extended_plot}b is that for simulated extended
-sources with typical sizes ($\sigma\sim0\fdg5$), one can often obtain
-almost as large an increase in likelihood fitting the source as two
-point-like sources ($\tsinc\sim\tsext$).  This is because although the
-two point-like sources represent an incorrect spatial model, the second
-source has four additional degrees of freedom (two spatial and two
-spectral parameters) and can therefore easily model much of the extended
-source and statistical fluctuations in the data.  This effect is most
-pronounced when using photons with energies between 1 \gev and 100 \gev
-where the PSF is broader.
-
-From this Monte Carlo study, we can see the limits of a LAT analysis
-of spatially extended sources.  Section~\ref{monte_carlo_validation}
-showed that we have a statistical test that finds when a LAT source is
-not well described by the PSF.  But this test does not uniquely prove
-that the emission originates from spatially extended emission instead
-of from multiple unresolved sources.  Demanding that $\tsext>\tsinc$
-is a powerful second test to avoid cases of simple confusion of two
-point-like sources. But it could always be the case that an extended
-source is actually the superposition of multiple point-like or
-extended sources that could be resolved with deeper observations of the
-region.  There is nothing about this conclusion unique to LAT analysis,
-but the broad PSF of the LAT and the density of sources expected to be
-\gev emitters in the Galactic plane makes this issue more significant
-for LAT analysis.  When possible, multiwavelength information should be
-used to help select the best model of the sky.
-
-\section{Test of 2LAC Sources}
-\label{test_2lac_sources}
-
-For all following LAT analyses, we used the same two-year dataset
-that was used in the 2FGL catalog spanning from 2008 August 4 to 2010 August 1. We
-applied the same acceptance cuts and we used the same P7\_V6 Source class
-event selection and IRFs \citep{lat_on_orbit_psf}.  
-When analyzing sources in \pointlike, we used a circular $10\degree$ region of
-interest (ROI) centered on our source and eight energy bins per
-logarithmic decade in energy.
-When refitting the region in \gtlike using the best fit spatial and
-spectral models from \pointlike, we used the `binned likelihood' mode of
-\gtlike on a $14\degree\times14\degree$ ROI with a pixel size of 0\fdg03.
-
-Unless explicitly
-mentioned, we used the same background model as 2FGL to represent the
-Galactic diffuse, isotropic, and Earth limb emission.  To compensate for
-possible residuals in the diffuse emission model, the Galactic emission
-was scaled by a power-law and the normalization
-of the isotropic component
-was left free.  
-Unless explicitly mentioned,
-we used all 2FGL sources within $15\degree$ of our source as our list
-of background sources and we refit the spectral parameters of all sources
-within $2\degree$ of the source.
-
-To validate our method, we tested LAT sources associated with AGN for
-extension.  \gev emission from AGN is believed to originate from collimated jets.  Therefore AGN are
-not expected to be spatially resolvable by the LAT and provide a good
-calibration source to demonstrate that our extension detection method
-does not misidentify point-like sources as being extended.  We note that
-megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
-to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
-halo has been discovered in the LAT data so far \citep{neronov_agn_halo}.
-
-Following 2FGL, the LAT Collaboration published the Second LAT AGN
-Catalog (2LAC), a list of high latitude ($|b|>10\degree$) sources
-that had a high probability association with AGN \citep{second_agn_cat}.
-2LAC associated 1016 2FGL sources with AGN.  To avoid systematic problems
-with AGN classification, we selected only the 885 AGN which made it into
-the clean AGN sub-sample defined in the 2LAC paper.  An AGN association is considered clean only
-if it has a high probability of association $P\ge 80\%$, if it is the
-only AGN associated with the catalog source, and if 
-no analysis flags have been set for the source
-in the 2FGL catalog. These last two conditions are important for our
-analysis. Source confusion may look like a spatially extended source
-and flagged catalog sources may correlate with unmodeled structure in
-the diffuse emission.
-
-Of the 885 clean AGN, we selected the 733 of these 2FGL sources which
-were significantly detected above 1 \gev and fit each of them for
-extension.  The cumulative density of \tsext for these AGN is compared
-to the $\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
-in Figure~\ref{agn_ts_ext}.  The \tsext distribution
-for the AGN shows reasonable agreement with the theoretical
-distribution and no AGN was found to be significantly extended
-($\tsext>16$).  The observed discrepancy from the theoretical
-distribution is likely due to small systematics
-in our model of the LAT PSF and the Galactic diffuse emission (see
-Section~\ref{systematic_errors_on_extension}).  
-The discrepancy could
-also in a few cases be due to confusion with a nearby undetected source.
-We note that the Monte Carlo study
-of section~\ref{monte_carlo_validation} effectively used perfect
-IRFs and a perfect model of the sky.
-The overall agreement with the expected distribution demonstrates that
-we can use \tsext as a measure of the statistical significance of the
-detection of the extension of a source.
-
-We note that the LAT PSF used in this study was determined
-empirically by fitting the distributions of gamma rays around bright AGN (see
-Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
-test are not extended is not surprising.  This validation analysis is
-not suitable to reject any hypotheses about the existence of megaparsec-scale
-halos around AGN.
-
-\section{Analysis of Extended Sources Identified in the 2FGL Catalog}
-\label{validate_known}
-
-As further validation of our method for studying
-spatially extended sources, we reanalyzed the twelve spatially extended
-sources which were included in the 2FGL catalog \citep{second_cat}.  
-Even though these sources had all been the subjects of dedicated
-analyses and separate publications, and had been fit with a variety
-of spatial models,
-it is valuable to show that
-these sources are significantly extended using our systematic 
-method assuming radially-symmetric uniform disk spatial models.  On the other hand, for some of
-these sources a uniform disk spatial model does not well describe the
-observed extended emission and so the dedicated LAT 
-publications provide better models of these sources.
-
-% 6 SNRs
-
-Six extended SNRs were
-included in the 2FGL catalog: W51C, IC~443, W28, W30, W44, the Cygnus Loop,
-and W30
-\citep{w51c,ic443,w28,w44,cygnus_loop_lat,w30_lat}.
-Using photons
-with energies between
-1 \gev and 100 \gev, our analysis significantly detected
-that these six SNRs are spatially extended.
-
-% 2 galaxies
-
-Two nearby satellite galaxies of the Milky Way the Large Magellanic Cloud (LMC)
-and the Small Magellanic
-Cloud (SMC) were included in the 2FGL catalog as spatially extended sources \citep{lmc,smc}.  
-Their extensions were significantly
-detected using photons with energies between
-1 \gev and 100 \gev. Our
-fit extensions are comparable to the published result, but we note that
-the previous LAT Collaboration publication on the LMC used a more complicated two 2D Gaussian surface
-brightness profile when fitting it \citep{lmc}.
-
-% 3 PWN
-Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were fit as
-extended sources in the 2FGL analysis \citep{msh1552,velax,fermi_hess_j1825}.  
-In the present analysis, HESS\,J1825$-$137
-was significantly detected using photons with energies between 10
-\gev and 100 \gev.  To avoid confusion with the nearby bright pulsar
-PSR\,J1509$-$5850, MSH\,15$-$52 had to be analyzed at high energies.
-Using photons with energies above 10 \gev, we fit the extension of
-MSH\,15$-$52 to be consistent with the published size but with \tsext=6.6.
-
-% failed to detect vela x + cen a
-Our analysis was unable to resolve Vela X which would have required first
-removing the pulsed photons from the Vela pulsar which was beyond the
-scope of this paper.  Our analysis also failed to detect a significant
-extension for the Centaurus A Lobes because
-the shape of the source is significantly different from a uniform
-radially-symmetric disk\citep{cen_a_lat}.
-
-Our analysis of these sources is summarized in
-Table~\ref{known_extended_sources}.  This table includes the best fit
-positions and extensions of these sources when fitting them 
-with a radially-symmetric uniform disk model. It also
-includes the best fit spectral parameters for each source.  The positions
-and extensions of Vela X and the Centaurus A Lobes were taken from
-\cite{velax,cen_a_lat} and are included in this table for completeness.
-
-\section{Systematic Errors on Extension}
-\label{systematic_errors_on_extension}
-
-% Alternative PSF
-
-We developed two criteria for estimating systematic errors
-on the extensions of the sources.
-First, we estimated a systematic error due to
-uncertainty in our knowledge of the LAT PSF.  
-Before launch, the LAT PSF
-was determined by detector simulations which were verified in accelerator
-beam tests \citep{atwood_LAT_mission}. However, in-flight data revealed
-a discrepancy above 3 \gev in the PSF compared to the angular
-distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
-Subsequently, the PSF was fit empirically to bright AGN and this
-empirical parameterization is used in the P7\_V6 IRFs.  To account for
-the uncertainty in our knowledge of the PSF, we refit our extended source
-candidates using the pre-flight Monte Carlo representation of the PSF
-and consider the difference in extension found using the two PSFs as a
-systematic error on the extension of a source.  The same approach was used
-in \cite{ic443}.  we believe that our parameterization
-of the PSF from bright AGN is substantially better than the Monte Carlo
-representation of the PSF so this systematic error is conservative.
-
-% Alternative Diffuse Model
-
-We estimated a second systematic error on the extension of a source
-due to uncertainty in our model of the Galactic diffuse emission by
-using an alternative 
-approach to modeling the diffuse emission
-which takes as input templates
-calculated by
-GALPROP\footnote{GALPROP is a software package for calculating the
-Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
-in the Galaxy and maps of the distributions of the 
-components of the interstellar medium \citep{galprop1998,galprop2011}. 
-See also \url{http://galprop.stanford.edu/} for details.} 
-but then fits each template locally in
-the surrounding region.
-The particular GALPROP model that was used as input is described in
-the LAT analysis of the isotropic diffuse
-emission \citep{isotropic_lat}.  
-The intensities of various components
-of the Galactic diffuse emission were fitted individually using a
-spatial distribution predicted by
-the model.  We distinguished contributions from cosmic-ray interactions with the
-molecular hydrogen, the atomic and ionized hydrogen, residual gas traced
-by dust \citep{isabelle_dark_gass}, and the interstellar radiation
-field. We further split the contributions from interactions with molecular
-and atomic hydrogen to the Galactic diffuse emission according to the
-distance from the Galactic center in which they are produced. Hence, we
-replaced the standard diffuse emission model by 18 individually fitted
-templates to describe individual components of the diffuse emission.
-A similar crosscheck was used in an analysis of RX\,J1713.7$-$3946 
-by the LAT Collaboration \citep{rx_j1713_lat}.
-
-It is not expected that this diffuse model is superior to the standard
-LAT model obtained through an all-sky fit.  However, adding degrees of
-freedom to the background model can remove likely spurious sources that
-correlate with features in the Galactic diffuse emission.  Therefore,
-this tests systematics that may be due to imperfect modeling of the
-diffuse emission in the region. Nevertheless, 
-this alternative approach to modeling the diffuse emission
-does not test all systematics related to the diffuse emission model.
-In particular, because the alternative approach uses the same underlying gas
-maps it is unable to be used to assess systematics due to mischaracterization of local
-diffuse structure due to lack of resolution of the underlying maps.
-
-We do not expect the systematic error due to uncertainties in the PSF
-to be correlated with the systematic error due to uncertainty in the
-Galactic diffuse emission. Therefore, the total systematic error on the
-extension of a source was obtained by adding the two errors in quadrature.
-
-There is another systematic error on the size of a source due to issues
-modeling nearby sources in crowded regions of the sky. It is beyond the
-scope of this paper to address this systematic error. Therefore, 
-for sources in crowded regions the systematic
-errors quoted in this paper may not be the full systematics of this
-analysis.
-
-\section{Extended Source Search Method}
-\label{extended_source_search_method}
-
-Having demonstrated that we understand the statistical
-issues associated with analyzing spatially extended sources
-(Section~\ref{monte_carlo_validation} and~\ref{test_2lac_sources}) and
-that our method can correctly analyze the extended sources included in
-2FGL (Section~\ref{validate_known}), we applied this method to search for
-new spatially extended \gev sources.
-The data and general analysis setting is as described in Section~\ref{test_2lac_sources}.
-
-Ideally, we would apply a completely blind and uniform search that
-tests the extension of each catalog source in the presence of all other
-2FGL sources to find a complete list of all spatially extended sources.
-As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
-Galactic latitude where the source density is not as large and the
-diffuse emission is less structured, this method works well.
-
-But this is infeasible in the Galactic plane where we most likely expect
-to discover new spatially extended sources.  In the Galactic plane,
-this analysis is challenged by our imperfect model of the diffuse
-emission and by an imperfect model of nearby sources.  The Monte Carlo
-study in Section~\ref{dual_localization_method}
-showed that the overall likelihood would greatly increase by fitting
-a spatially extended source as two point-like sources so we expect
-that spatially extended sources would be modeled in the 2FGL catalog as
-multiple point-like sources. Furthermore, the positions of other nearby sources
-in the region close to an extended source could be biased by not correctly
-modeling the extension of the source.  Since 2FGL produced a
-list of sources significant at energies above 100 \mev whereas we are
-most sensitive to spatial extension at higher energies,
-we also expect that at higher energies our analysis would be complicated
-by 2FGL sources no longer significant and by 2FGL
-sources whose positions were biased by diffuse emission at lower energies.
-
-To account for these issues, we first produced a large list of possibly
-extended sources employing very liberal search criteria and then
-refined the analysis of the promising candidates on a case by case basis.
-Our strategy was to test all point-like 2FGL sources for extension assuming
-they had a uniform radially-symmetric disk spatial model
-and a power-law spectral model.  Although not all extended sources are
-expected to have a shape very similar to a uniform disk, Section~\ref{compare_source_size} showed that for many spatially
-extended sources the wide PSF of the LAT and limited statistics makes
-this a reasonable approximation.  On the other hand, choosing this
-spatial model biases us against finding extended sources that are not
-well described by a uniform disk model such as shell-type SNRs.
-
-Before testing for extension, we automatically removed from the background
-model all other 2FGL sources within 0\fdg5 of the source.  This distance
-is somewhat arbitrary, but was picked in hopes of finding extended
-sources with sizes on the order of $\sim1\degree$ or smaller. On the
-other hand, by removing these nearby background sources we expect to
-also incorrectly add to our list of extended source candidates
-point-like sources that
-are confused with nearby sources.  To screen out obvious cases of source
-confusion, we performed the dual localization procedure described in
-Section~\ref{dual_localization_method} to compare the extended source
-hypothesis to the hypothesis of two independent point-like sources.
-
-As was shown in Section~\ref{extension_sensitivity}, little sensitivity is gained by
-using photons with energies below 1 \gev. On the other hand,
-the broad PSF at low energy makes the analysis more susceptible to systematic
-errors arising from source confusion due to nearby soft point-like sources
-and by uncertainties in our modeling of the Galactic diffuse emission. 
-For that reason,
-we performed our search using only photons with energies between 1 \gev
-and 100 \gev.
-
-We also performed a second search for extended sources using only
-photons with energies between 10 \gev and 100 \gev.  Although this
-approach tests the same sources, it is complementary because the Galactic
-diffuse emission is even less dominant above 10 \gev and because source
-confusion is less of an issue.  A similar procedure was used to detect
-the spatial extensions of MSH\,15$-$52 and
-HESS\,J1825$-$137 with the LAT \citep{msh1552,fermi_hess_j1825}.
-
-When we applied this test to the 1861 point-like sources in the 2FGL catalog, our
-search found 117 extended source candidates in the 1 \gev to 100 \gev
-energy range and 11 extended source candidates in the 10 \gev to 100
-\gev energy range. Most of the extended sources found above 10 \gev were
-also found above 1 \gev and in many cases multiple nearby point-like
-sources were found to be extended even though they fit the same emission region.
-For example, the sources 2FGL\,J1630.2$-$4752, 2FGL\,J1632.4$-$4753c 2FGL\,J1634.4$-$4743c,
-and 2FGL\,J1636.3$-$4740c were all found to be spatially extended in the
-10 \gev to 100 \gev energy range even though they all fit to similar
-positions and sizes.  For these situations, we manually discarded all
-but one of the 2FGL sources.
-
-Similarly, many of these sources were confused with nearby
-point-like sources or influenced by large-scale residuals in the
-diffuse emission.  To help determine which of these fits found
-truly extended sources and when the extension was
-influenced by source confusion and diffuse emission, we generated a
-series of diagnostic plots.  For each candidate, we generated a map
-of the residual TS by adding a new point-like source of spectral index 2 into the
-region at each position and finding the increase in likelihood when fitting
-its flux. Figure~\ref{res_tsmaps} shows this map around the
-most significantly extended source IC~443 when it is modeled both as a
-point-like source and as an extended source.  The residual TS
-map indicates
-that the spatially extended model for IC~443 is a significantly better
-description of the observed photons and that there is no significant
-residual in the region after modeling the source as being spatially extended.
-We also generated plots of the sum of all counts within a given distance of
-the source and compared them to the model predictions assuming the emission
-originated from a point-like source.  An example radial integral plot
-is shown for the extended source IC~443 in Figure~\ref{four_plots_ic443}.
-For each source, we also made diffuse-emission-subtracted smoothed counts
-maps (shown for IC~443 in Figure~\ref{four_plots_ic443}).
-
-We found by visual inspection that in many
-cases our results were strongly influenced by large-scale residuals in the
-diffuse emission and hence the extension measure was unreliable.  This was
-especially true in our analysis of sources in the 1 \gev to 100 \gev
-energy range.  An example of such a case is 2FGL\,J1856.2+0450c analyzed
-in the 1 \gev to 100 \gev energy range. Figure~\ref{example_bad_fit}
-shows a diffuse-emission-subtracted smoothed counts map for
-this source with the best
-fit extension of the source overlaid. There appear to be large-scale
-residuals in the diffuse emission in this region along the Galactic plane.
-As a result, 2FGL\,J1856.2+0450c is fit to an extension of $\sim2\degree$
-and the result is statistically significant with \tsext=45.4. However,
-by looking at the residuals it is clear that this complicated region is
-not well modeled. We manually discard sources like this.
-% information came from
-% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
-% (2FGL J1856.2+0450c = P72Y3047 for)
-
-We only selected extended source
-candidates in regions that did not appear dominated by these issues and
-where there was a multiwavelength
-counterpart. Because of these systematic issues, this search can not be
-expected to be complete and it is likely that there are other spatially
-extended sources that this method missed.
-
-For each candidate that was not biased by neighboring point-like
-sources or by large-scale residuals in the diffuse emission model, we
-improved the model of the region by deciding on a case by case basis which
-background point-like sources should be kept.  We kept in our model the
-sources that we
-believed represented physically distinct sources and we removed 
-sources that we believed were included in the 2FGL catalog to compensate
-for residuals induced by not modeling the extension of the source.
-Soft nearby point-like 2FGL sources that were not significant at higher energies
-were frozen to the spectras predicted by 2FGL.
-When deciding
-which background sources to keep and which to remove, we used as much as possible
-multiwavelength information about possibly extended source counterparts
-to help guide our choice. For each extended source presented in 
-Section~\ref{new_ext_srcs_section}, we describe any modifications from 2FGL
-of the background model that were performed.
-
-The best fit positions of nearby point-like sources can be influenced by
-the extended source and vice versa.  Similarly,
-the best fit positions of nearby point-like sources in the 2FGL catalog can be biased
-by systematic issues at lower energies.
-Therefore, after selecting the list of background sources, we iteratively
-refit the positions and spectra of nearby background sources as well as
-the positions and extensions of the analyzed spatially extended
-sources until the overall fit converged globally.  For each extended
-source, we will describe the positions of any relocalized background
-sources.
-
-After obtaining the overall best fit positions and extensions of all
-of the sources in the region using \pointlike, we refit the spectral
-parameters of the region using \gtlike.  With \gtlike, we obtained a
-second measure of \tsext.  We only consider a source to be extended when
-both \pointlike and \gtlike agree that $\tsext>16$. 
-We further required that $\tsext>16$ using the 
-alternative approach to modeling the diffuse emission
-presented in Section~\ref{systematic_errors_on_extension}.
-We then replaced the spatially extended source with two point-like
-sources and refit the positions and spectra of the
-two point-like sources to calculate \tsinc.
-We only consider a source to be spatially extended, instead of being
-the result of confusion of two point-like sources, if $\tsext>\tsinc$.
-As was shown in Section~\ref{dual_localization_method}, this test is
-fairly powerful at removing situations in which the emission actually
-originates from two distinct point-like sources instead of one spatially
-extended source.  On the other hand, it is still possible that longer
-observations could resolve additional structure or new sources 
-that the analysis cannot currently detect. 
-Considering the very complicated morphologies
-of extended sources observed at other wavelengths and the high density
-of possible sources that are expected to emit at \gev energies, it is
-likely that in some of these regions further observations will reveal
-that the emission is significantly more complicated than the simple
-radially-symmetric uniform disk model that we assume.
-
-\section{New Extended Sources}
-\label{new_ext_srcs_section}
-
-% Notes about extended Catalog sources
-% Catalog used for analysis is P72Y_uw23.fits
-% Compare to final catalog gll_psc_v04.fit
-%          1FGL Name - Preliminary 2FGL - 2FGL Name
-% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-
-% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 
-% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
-% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
-% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
-% N/A                - P72Y1287         - 2FGL J0851.7-4635 (Vela Jr)
-
-Nine extended sources not included in the 2FGL catalog were found by our
-extended source search. Two of these have been previously
-studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
-Jr. \citep{rx_j1713_lat,vela_jr_lat}.
-Two of these sources were
-found when using photons with energies between 1 \gev and 100 \gev and seven
-were found when using photons with energies between 10 \gev and 100 \gev.
-For the sources found at energies above 10 \gev, we restrict our
-analysis to higher energies because of the issues
-of source confusion and diffuse emission modeling described in
-Section~\ref{extended_source_search_method}.
-The spectral and spatial properties of these nine sources are summarized
-in Table~\ref{new_ext_srcs_table} and the results of our investigation of
-systematic errors are presented in Table~\ref{alt_diff_model_results}.
-Table~\ref{alt_diff_model_results}
-also
-compares the likelihood assuming the source is spatially
-extended to the likelihood assuming 
-that the emission originates from two independent point-like
-sources. For these new extended sources, $\tsext>\tsinc$ 
-so we conclude that 
-the \gev emission does not originate from two physically
-distinct point-like sources (see Section~\ref{dual_localization_method}).  
-Table~\ref{alt_diff_model_results} also includes the
-results of the extension fits using variations of the PSF and the Galactic
-diffuse model described in Section~\ref{systematic_errors_on_extension}.
-There is good agreement between \tsext and the fit size using the standard
-analysis, the alternative approach to modeling the diffuse emission, and the alternative PSF.
-This suggests that the sources are robust against mis-modeled features in the diffuse
-emission model and uncertainties in the PSF.
-
-\subsection{2FGL\,J0823.0$-$4246}
-\label{section_2FGL_J0823.0-4246}
-
-% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-
-2FGL\,J0823.0$-$4246 was found by our search to be an extended source
-candidate in the 1 \gev to 100 \gev energy range and is spatially
-coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
-a counts map of this source. There are two nearby catalog sources 2FGL\,J0823.4$-$4305
-and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
-do not appear to represent physically distinct sources.
-We conclude that
-these nearby point-like sources
-were included in the 2FGL catalog to compensate for residuals induced
-by not modeling the extension of this source and
-removed them from our model of the sky.
-After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension 
-$\sigma=0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with 
-$\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
-this source.
-
-Puppis A has been studied in detail in radio \citep{puppis_a_vla}, 
-and  X-ray \citep{rosat_puppis_a,suzaku_puppis_a}.
-The fit extension of 2FGL\,J0823.0$-$4246
-matches well the size of Puppis A in X-ray.  The distance of Puppis A was
-estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
-\gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
-No molecular clouds have been observed directly adjacent to Puppis A
-\citep{co_eastern_puppis_a}, similar to the LAT detected Cygnus Loop SNR
-\citep{cygnus_loop_lat}.  The luminosity of Puppis A is also smaller
-than that of other SNRs believed to interact with molecular clouds
-\citep{w51c,ic443,w44,w28,w49b_lat}.
-
-% Puppis A:
-%   Flux = PowerLaw(norm=6.21e-14,index=2.22,e0=10000).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%        = 4.7804242225163421e-11 ergs cm^-2 s-1
-%   Luminosity =  Flux * 4*pi*r^2 = 4.78e-11 ergs cm^-2 s^-1 * 4*pi * (2.2 kpc )**2 in ergs/s
-%              = 2.8e34 ergs/s from 1.0-100 gev
-%              = 5.6e34 ergs/s from 0.1-100 gev
-%   Luminosities
-%   Cygnus Loop:
-%     L = 10^33 ergs/s between 1-100 \gev
-%   W51C : 
-%     http://arxiv.org/pdf/0910.0908
-%     L > 1 x 10^36 ergs/s (0.2-50GeV) - 
-%   IC~443:
-%     http://arxiv.org/pdf/1002.2198v1
-%     L = 1.2e35 ergs/s (from 0.2-50 gev)
-%     d = 1.5 kpc
-%     From my (possibly incorrect) powerlaw analysis 
-%       In [30]: PowerLaw(norm=4.69e-13,index=2.21,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%       Out[30]: 3.5968626651391638e-10 ergs/cm^2/s
-%       L = 3.5968626651391638e-10/cm^2 * 4*pi*(1.5kpc)**2 = 1e35 (1-100gev)
-%   W44:
-%     http://www.sciencemag.org/content/327/5969/1103.full.pdf
-%     From my (possibly incorrect) powerlaw analysis 
-%       PowerLaw(norm=2.7e-13,index=2.63,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%       Out[27]: 2.7681360351439016e-10 ergs/cm^2/s
-%     Distance = 3kpc
-%     L = 3e35 ergs/s (1-100 gev)
-%   W28
-%     http://iopscience.iop.org/0004-637X/718/1/348/
-%     From my (possibly incorrect) powerlaw analysis 
-%       In [28]: PowerLaw(norm=2.23e-13,index=2.6,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%       Out[28]: 2.221059203350944e-10 ergs/cm^2/s
-%     Distance = 2kpc
-%     L = 1e35 ergs/s (1-100 gev)
-%   W49B
-%     http://iopscience.iop.org/0004-637X/722/2/1303
-%     L = 10^36 erg/s (0.2 - 200 gev)
-%
-
-\subsection{2FGL\,J0851.7$-$4635}
-\label{section_2FGL_J0851.7-4635}
-
-% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
-
-2FGL\,J0851.7$-$4635 was found by our search to be an extended source
-candidate in the 10 \gev to 100 \gev energy range and is spatially
-coincident with the SNR Vela Jr. This source was recently studied by the LAT
-Collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
-map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
-contours of Vela Jr. \citep{vela_jr_hess}.
-There are three
-point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
-and 2FGL\,J0855.4$-$4625 which correlate with the 
-multiwavelength
-emission of
-this SNR but do not appear to be physically distinct sources.
-They were most likely included in the 2FGL catalog to compensate for residuals
-induced by not modeling the extension of Vela Jr. and were removed
-from our model of the sky.
-
-With this model of the background, 2FGL\,J0851.7$-$4635 was found to
-have an extension of $\sigma=1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
-$\tsext=86.8$.  The LAT size matches
-well the \tev morphology of Vela Jr.  While fitting the extension
-of 2FGL\,J0851.7$-$4635, we iteratively relocalized the positions
-of the nearby point-like catalog source 2FGL\,J0854.7$-$4501 to
-$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies.
-
-\subsection{2FGL\,J1615.0$-$5051}
-\label{section_2FGL_J1615.0-5051}
-
-% For both 2FGL J1615.0-5051 and 2FGL J1615.2-5138 
-% Extended Sources:
-%   * 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 % extended source
-%   * 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138 % extended source
-
-2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to be
-extended source candidates in the 10 \gev to 100 \gev energy range. Because
-they are less than $1\degree$ away from each other, they needed to be analyzed
-simultaneously.  2FGL\,J1615.0$-$5051 is spatially coincident with
-the extended \tev source HESS\,J1616$-$508 and 2FGL\,J1615.2$-$5138
-is coincident with the extended \tev source HESS\,J1614$-$518.
-Figure~\ref{1FGL_J1613.6-5100c} shows a counts map of these sources and
-overlays the \tev contours of HESS\,J1616$-$508 and HESS\,J1614$-$518
-\citep{hess_plane_survey}.  The figure shows that the 2FGL source
-2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and correlates
-with the same extended \tev source as 2FGL\,J1615.2$-$5138.  We concluded
-that this source was included in the 2FGL catalog to compensate for residuals induced
-by not modeling the extension of 2FGL\,J1615.2$-$5138 and removed
-it from our model of the sky.
-
-With this model of the sky, we iteratively fit the extensions of
-2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138.
-2FGL\,J1615.0$-$5051 was found to have an extension 
-$\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ and
-\tsext=16.7.
-
-The \tev counterpart of 2FGL\,J1615.0$-$5051 was fit
-with a radially-symmetric Gaussian surface brightness profile with
-$\sigma=0\fdg136\pm0\fdg008$.  This \tev size corresponds to a 68\%
-containment radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the
-LAT size $\rsixeight=0\fdg26\pm0\fdg03$.  Figure~\ref{hess_seds} shows
-that the spectrum of 2FGL\,J1615.0$-$5051 at \gev energies connects to
-the spectrum of HESS\,J1616$-$508 at \tev energies.
-
-HESS\,J1616$-$508 is located in the region of two SNRs RCW103 (G332.4-04)
-and Kes~32 (G332.4+0.1) but is not spatially coincident with either
-of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near three
-pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055.
-\citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.  Only
-PSR\,J1617$-$5055 is energetically capable of powering the \tev emission
-and \cite{hess_plane_survey} speculated that HESS\,J1616$-$508 could
-be a PWN powered by this young pulsar.  Because HESS\,J1616$-$508 is
-$9\arcmin$ away from PSR\,J1617$-$5055, this would require an asymmetric
-X-ray PWNe to power the \tev emission.  \chandra ACIS observations
-revealed an underluminous PWN of size $\sim1\arcmin$ around the
-pulsar that was not oriented towards the \tev emission, rendering this
-association uncertain \citep{discovery_of_pwn_for_PSR_J1617-5055}.
-No other promising counterparts were observed at X-ray and soft
-gamma-ray energies by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
-IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
-\cite{discovery_of_pwn_for_PSR_J1617-5055} discovered additional
-diffuse emission towards the center of HESS\,J1616$-$508 using archival
-radio and infared observations. Deeper observations will likely be
-necessary to understand this $\gamma$-ray source.
-
-\subsection{2FGL\,J1615.2$-$5138}
-\label{section_2FGL_J1615.2-5138}
-
-2FGL\,J1615.2$-$5138 was found
- to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
-with $\tsext=46.5$.
-To test for the possibility that
-2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
-of two point-like sources (one of them represented in the 2FGL catalog by
-2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
-sources.  Because \tsinc is less than \tsext, we conclude that
-this emission does not originate from two nearby point-like sources.
-
-2FGL\,J1615.2$-$5138 is spatially coincident with 
-the extended \tev source HESS\,J1614$-$518.
-H.E.S.S. measured a 2D Gaussian extension of $\sigma=0\fdg23\pm0\fdg02$
-and $\sigma=0\fdg15\pm0\fdg02$ in the semi-major and
-semi-minor axis. This corresponds to a 68\% containment size of
-$\rsixeight=0\fdg35\pm0\fdg03$ and $0\fdg23\pm0\fdg03$,  consistent with
-the LAT size $\rsixeight=0\fdg34\pm0\fdg03$.  Figure~\ref{hess_seds}
-shows that the spectrum of 2FGL\,J1615.2$-$5138 at \gev energies connects
-to the spectrum of HESS\,J1614$-$518 at \tev energies.  Further data
-collected by H.E.S.S. in 2007 resolve a double peaked structure at
-\tev energies but no spectral variation across this source, suggesting
-that the emission is not the confusion of physically separate sources
-\citep{closer_look_hess_j1614-518}.  This double peaked structure is
-also hinted at in the LAT counts map in Figure~\ref{1FGL_J1613.6-5100c}
-but is not very significant.  The \tev source was also detected by
-CANGAROO-III \citep{cangaroo_j1614-518}.
-
-There are five nearby pulsars, but none are luminous enough to
-provide the energy output required to power the $\gamma$-ray
-emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614$-$518
-is spatially coincident with a young open cluster Pismis 22
-\citep{hess_1614_landi_atel,closer_look_hess_j1614-518}.  \suzaku detected
-two promising X-ray candidates. Source A is an extended source consistent
-with the peak of HESS\,J1614$-$518 and source B coincident with Pismis 22
-and towards the center but in a relatively dim region of HESS\,J1614$-$518
-\citep{suazku_hess_j1614_518}.  Three hypotheses have been presented to
-explain this emission: either source A is an SNR powering the $\gamma$-ray
-emission; source A is a PWN powered by an undiscovered pulsar in either
-source A or B; and finally that the emission may arise from hadronic
-acceleration in the stellar winds of Pismis 22 \citep{cangaroo_j1614-518}.
-
-\subsection{2FGL\,J1627.0$-$2425c}
-\label{section_2FGL_J1627.0-2425c}
-
-% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-% No modifications to background were needed
-
-2FGL\,J1627.0$-$2425c was found by our search to
-have an extension $\sigma=0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
-$\tsext=32.4$
-using photons with energies between 1 \gev and 100 \gev.  
-Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
-
-This source is in a region of remarkably complicated diffuse emission.
-Even though it is $16\degree$ from the Galactic plane, this source is on
-top of the core of the Ophiuchus molecular cloud which contains massive
-star-forming regions that are bright in infrared.  The region also has
-abundant molecular and atomic gas traced by CO and H~I and significant 
-dark gas found only by its association with dust emission
-\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
-more challenging to measure the column density of dust.  Infared and 
-CO ($J=1\rightarrow 0$)
-contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
-spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
-This source might 
-represent $\gamma$-ray emission from the interactions of cosmic rays with
-interstellar gas which has not been accounted for in the LAT diffuse
-emission model.
-
-\subsection{2FGL\,J1632.4$-$4753c}
-\label{section_2FGL_J1632.4-4753c}
-
-% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-
-2FGL\,J1632.4$-$4753c was found by our search to be an extended source
-candidate in the 10 \gev to 100 \gev energy range but is in a crowded
-region of the sky.  It is spatially coincident with the \tev source
-HESS\,J1632$-$478.  Figure~\ref{1FGL_J1632.9-4802c}a shows a counts
-map of this source and overlays \tev contours of HESS\,J1632$-$478
-\citep{hess_plane_survey}.  There are six nearby point-like 2FGL
-sources that appear to  represent physically distinct sources
-and were included in our background model: 2FGL\,J1630.2$-$4752, 2FGL\,J1631.7$-$4720c, 2FGL\,J1632.4$-$4820c, 2FGL\,J1635.4$-$4717c,
-2FGL\,J1636.3$-$4740c, and
-2FGL\,J1638.0$-$4703c. On the
-other hand, one point-like 2FGL source 2FGL\,J1634.4$-$4743c  correlates
-with the extended \tev source and at \gev energies does
-not appear physically separate. 
-We therefore removed this source from our model of the
-background.  Figure~\ref{1FGL_J1632.9-4802c}b shows the same region with
-the background sources subtracted.  With this model, 2FGL\,J1632.4$-$4753c
-was found to have an extension $\sigma=0\fdg35\pm0\fdg04_\stat\pm0\fdg02_\sys$
-with $\tsext=26.9$.  While fitting the
-extension of 2FGL\,J1632.4$-$4753c, we iteratively relocalized
-2FGL\,J1635.4$-$4717c to $(l,b)=(337\fdg23,0\fdg35)$ and
-2FGL\,J1636.3$-$4740c to $(l,b)=(336\fdg97,-0\fdg07)$.
-
-H.E.S.S measured an extension of $\sigma=0\fdg21\pm0\fdg05$ and
-$0\fdg06\pm0\fdg04$ along the semi-major and semi-minor axes when
-fitting HESS\,J1632$-$478 with an elliptical 2D Gaussian surface
-brightness profile.  This corresponds to a 68\% containment size
-$\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$ along
-the semi-major and semi-minor axis, consistent with the LAT size
-$\rsixeight=0\fdg29\pm0\fdg04$.  Figure~\ref{hess_seds} shows that
-the spectrum of 2FGL\,J1632.4$-$4753c at \gev energies connects to the
-spectrum of HESS\,J1632$-$478 at \tev energies.
-
-\cite{hess_plane_survey} argued that HESS\,J1632$-$478
-is positionally coincident with the hard X-ray source
-IGR\,J1632$-$4751 observed by \asca, INTEGRAL, and \xmmnewton
-\citep{asca_plane_survey,Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751},
-but this source is suspected to be a Galactic X-Ray Binary so the
-$\gamma$-ray extension disfavors the association.  Further observations
-by \xmmnewton discovered point-like emission coincident with the peak
-of the H.E.S.S. source surrounded by extended emission of size
-$\sim32\arcsec\times15\arcsec$ \citep{hess_j1632_478_xmm_newton}.
-They found in archival MGPS-2 data a spatially coincident extended
-radio source \citep{most_survey_galactic_plane} and argued for a single
-synchrotron and inverse Compton process producing the radio, X-ray, and \tev emission,
-likely due to a PWN.  The increased size at \tev energies compared
-to X-ray energies has previously been observed in several aging PWNe
-including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
-HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
-and Vela X \citep{vela_x_rosat,vela_x_hess} and can be explained by
-different synchrotron cooling times for the electrons that produce X-rays
-and $\gamma$-rays.
-
-\subsection{2FGL\,J1712.4$-$3941}
-\label{section_2FGL_J1712.4-3941}
-
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
-
-2FGL\,J1712.4$-$3941 was found by our search to be spatially extended
-using photons with energies between 1 \gev and 100 \gev.  This source
-is spatially coincident with the SNR RX\,J1713.7$-$3946 and was
-recently studied by the LAT Collaboration in \cite{rx_j1713_lat}.
-To avoid issues related to uncertainties in the nearby Galactic
-diffuse emission at lower energy, we restricted our analysis only
-to energies above 10 \gev.  Figure~\ref{2FGL_J1712.4-3941} shows a
-smoothed counts map of the source. Above 10 \gev, the \gev emission
-nicely correlates with the \tev contours of RX\,J1713.7$-$3946
-\citep{rx_j1713_hess} and 2FGL\,J1712.4$-$3941 fit to an extension 
-$\sigma=0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with $\tsext=38.5$.
-
-\subsection{2FGL\,J1837.3$-$0700c}
-\label{section_2FGL_J1837.3-0700c}
-
-% 1FGL J1837.5-0659c - P72Y2986 - 2FGL J1837.3-0700c
-
-2FGL\,J1837.3$-$0700c was found by our search to be an extended source
-candidate in the 10 \gev to 100 \gev energy range and is spatially
-coincident with the \tev source HESS\,J1837$-$069.  This source is
-in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
-smoothed counts map of the region and overlays the \tev contours of
-HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
-point-like 2FGL sources, 2FGL\,J1836.8$-$0623c and 2FGL\,J1839.3$-$0558c,
-that clearly represent distinct sources.  On the other hand, there is
-another source 2FGL\,J1835.5$-$0649 located between the three sources that
-appears to correlate with the \tev morphology of HESS\,J1837$-$069 but
-at \gev energies
-does not appear to represent a physically distinct source.  We concluded
-that this source was included in the 2FGL catalog to compensate for residuals induced by
-not modeling the extension of this source and removed it from our model
-of the sky.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
-counts map of this region after subtracting these background sources.
-After removing 2FGL\,J1835.5$-$0649,
-we tested for
-source confusion by fitting 
-2FGL\,J1837.3$-$0700c
-instead as two point-like sources.
-Because \tsinc is less than \tsext, we conclude that this emission
-does not originate from two nearby point-like sources.
-
-With this model, 2FGL\,J1837.3$-$0700c was found to have an
-extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with 
-$\tsext=18.5$. 
-While fitting the extension of 2FGL\,J1837.3$-$0700c,
-we iteratively relocalized the two closest
-background sources along with the extension of 2FGL\,J1837.3$-$0700c but
-their positions did not significantly change.  2FGL\,J1834.7$-$0705c
-moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
-to $(l,b)=(25\fdg57,0\fdg32)$.
-
-H.E.S.S. measured an extension of
-$\sigma=0\fdg12\pm0\fdg02$ and $0\fdg05\pm0\fdg02$ 
-of the coincident \tev source HESS\,J1837$-$069 
-along the semi-major and semi-minor axis when fitting this source
-with an elliptical 2D Gaussian surface brightness profile.  This corresponds
-to a 68\% containment radius of $\rsixeight=0\fdg18\pm0\fdg03$ and
-$0\fdg08\pm0\fdg03$ along the semi-major and semi-minor axis. The
-size is not significantly different from the LAT 68\% containment
-radius of $\rsixeight=0\fdg27\pm0\fdg07$ (less than $2\sigma$).
-Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1837.3$-$0700c
-at \gev energies connects to the spectrum of HESS\,J1837$-$069 at \tev
-energies.
-
-HESS\,J1837$-$069 is coincident with the hard and steady X-ray source
-AX\,J1838.0$-$0655 \citep{hard_x-ray_asca}.  This source was discovered
-by RXTE to be a pulsar (PSR J1838-0655) 
-sufficiently luminous to power the \tev emission
-and was resolved by \chandra to be a bright point-like source surrounded
-by a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069}. The
-$\gamma$-ray emission may be powered by this pulsar.  The hard spectral
-index and spatial extension of 2FGL\,J1837.3$-$0700c disfavor a pulsar
-origin of the LAT emission and suggest instead that the \gev and \tev
-emission both originate from the pulsar's wind.  There is another
-X-ray point-like source AX\,J1837.3$-$0652 near HESS\,J1837$-$069
-\citep{hard_x-ray_asca} that was also resolved into a point-like
-and diffuse component \citep{pulsations_HESS_J1837-069}.  Although no
-pulsations have been detected from it, it could also be a pulsar powering
-some of the $\gamma$-ray emission.
-
-\subsection{2FGL\,J2021.5+4026}
-\label{section_2FGL J2021.5+4026}
-
-% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-
-The source 2FGL\,J2021.5+4026 is associated with the $\gamma$-Cygni SNR 
-and has been speculated
-to originate from the interaction of accelerated particles in the SNR
-with dense molecular clouds \citep{pollock_1985,gaisser_1998}. This
-association was disfavored when the \gev emission from this source
-was detected to be pulsed \citep[PSR\,J2021+4026,][]{first_lat_pulsar_cat}.
-This pulsar was also observed by AGILE \citep{gamma_cygni_agile}.
-
-Looking at the same region at energies above 10 \gev, the pulsar is
-no longer significant but we instead found in our search an extended
-source candidate.  Figure~\ref{1FGL_J2020.0+4049} shows a counts map
-of this source and overlays radio contours of $\gamma$-Cygni from the
-Canadian Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
-There is good spatial overlap between the SNR and the \gev emission.
-
-There is a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
-emission of $\gamma$-Cygni and at \gev energies 
-does not appear to represent a physically
-distinct source.  We concluded that it was included in the 2FGL catalog to compensate
-for residuals induced by not modeling the extension of $\gamma$-Cygni and
-removed it from our model of the sky.  With this model, 2FGL\,J2021.5+4026
-was found to have an extension $\sigma=0\fdg63\pm0\fdg05_\stat\pm0\fdg04_\sys$
-with $\tsext=128.9$.  Figure~\ref{snr_seds}
-shows its spectrum.  The inferred size of this source at \gev energies
-well matches the radio size of $\gamma$-Cygni.  Milagro detected
-a $4.2\sigma$ excess at energies $\sim 30$ \tev from this location
-\citep{lat_bsl,milagro_bright_source_list}.  VERITAS also detected an
-extended source VER\,J2019+407 coincident with the SNR above 200 \gev
-and suggested that the \tev emission could be a shock-cloud interaction
-in $\gamma$-Cygni \citep{veritas_gamma_cygni}.
-
-% Radio observations \dots
-% X-ray observations \dots
-% Age \ldots
-% Distance: 1.5 kpc Landecker et al 1980 (from integral paper)
-% Optical: (Mavromatakis 2003 (from integral paper)
-% EGRET observations: 3EG J2020+4027
-% LAT Pulsar detected
-%   PSR J2021+4026
-%   Prestended at scineghe2010.
-%     http://scineghe2010.ts.infn.it/allegati/talks/ThursdaySept9/13_Razzano.pdf
-%   Presented at Fermi Symposium 2011:
-%     https://confluence.slac.stanford.edu/download/attachments/98831433/2011_3FermiSymp_CygPsr_ver2.pdf
-%     "PSR J2021+4026 is a 265 ms pulsar found by Fermi LAT using"
-%     "This discovery help to better clarify the nature of the
-%      unidentified source 3EG J2020+4027, thought to be associated
-%      with SNR 78.2+2.1, a.k.a. the $\gamma$-Cygni SNR.
-%      Unfortunately, so far this pulsar lacks a radio counterpart, and
-%      observations with Chandra and XMM show a potential X-ray
-%      counterpart [8,9,15], but no pulsations have been detected so
-%      far."
-
-% Milagro analysis
-% http://arxiv.org/abs/astro-ph/0611691
-% Milagro $4.2\sigma$ excess.
-
-% VERITAS observations of $\gamma$-Cygni: 
-%   http://arxiv.org/pdf/0912.4492v1
-%   extended: VER J019+407
-%     VERITAS observations of $\gamma$-Cygni veritas_gamma_cygni,
 
@@
 
-Twelve extended sources were included in the 2FGL catalog and two additional extended
-sources were studied in dedicated publications.  Using 2 years of
-LAT data and a new analysis method, we presented the detection of seven
-additional extended sources.  We also reanalyzed the spatial extents of the
-twelve extended sources in the 2FGL catalog and the two additional sources.  The 21
-extended LAT sources are located primarily along the Galactic plane
-and their locations are shown in Figure~\ref{allsky_extended_sources}.
-Most of the LAT detected extended sources are expected to be of Galactic
-origin as the distances of extragalactic sources (with the exception of
-the local group Galaxies) are typically too large to be able to resolve
-them at $\gamma$-ray energies.
-
-For the LAT extended sources also seen at \tev energies,
-Figure~\ref{gev_vs_tev_plot} shows that there is a good correlation
-between the sizes of the sources at \gev and \tev energies. Even so,
-the sizes of PWNe are expected to vary across the \gev and \tev energy
-range and the size of HESS\,J1825$-$137 is significantly larger at
-\gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting
-to compare the sizes of other PWN candidates at \gev and \tev energies,
-but definitively measuring a difference in size would require a more in-depth analysis
-of the LAT data using the same elliptical Gaussian spatial model.
-
-Figure~\ref{gev_vs_tev_histogram} compares the sizes of the 21 extended
-LAT sources to the 42 extended H.E.S.S. sources.\footnote{The 
-\tev extension of
-the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-Catalog \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
-Because of the large
-field of view and all-sky coverage, the LAT can more easily measure
-larger sources.  On the other hand, the 
-better
-angular resolution of air Cherenkov detectors allows them to measure a
-population of extended sources below the resolution limit of the LAT (currently 
-about $\sim0\fdg2$).  \fermi has a 5 year nominal mission lifetime with
-a goal of 10 years of operation.  As Figure~\ref{time_sensitivity} shows,
-the low background of the LAT at high energies allows its sensitivity 
-to
-these smaller sources to improve by a factor greater than the square root
-of the relative exposures.  With increasing exposure, the LAT will likely begin to
-detect and resolve some of these smaller \tev sources.
-
-Figure~\ref{compare_index_2FGL} compares the spectral indices of LAT
-detected extended sources and of all sources in the 2FGL catalog. This, and
-Tables~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
-show that the LAT observes a population of hard extended sources
-at energies above 10 \gev.  Figure~\ref{hess_seds} shows that
-the spectra of four of these sources (2FGL\,J1615.0$-$5051,
-2FGL\,J1615.2$-$5138, 2FGL\,J1632.4$-$4753c, and 2FGL\,J1837.3$-$0700c)
-at \gev energies connects to the spectra of their H.E.S.S. counterparts
-at \tev energies. This is also true of Vela Jr., HESS\,J1825$-$137
-\citep{fermi_hess_j1825}, and RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
-It is likely that the \gev and \tev emission from these sources originates
-from the same population of high-energy particles.
-
-Many of the \tev detected extended sources now seen at \gev energies
-are currently unidentified and further multiwavelength follow-up
-observations will be necessary to understand these particle accelerators.
-But extending the spectra of these \tev sources towards lower energies
-with LAT observations may help to determine the origin and nature of
-the high-energy emission.
+Discussion
 
@@
 
-Additional support for science analysis during the operations phase is gratefully
-acknowledged from the Istituto Nazionale di Astrofisica in Italy and the Centre National d'\'Etudes Spatiales in France.
+Additional support for science analysis during the operations phase is
+gratefully acknowledged from the Istituto Nazionale di Astrofisica in
+Italy and the Centre National d'\'Etudes Spatiales in France.
 
-This research has made use of
-pywcsgrid2, an open-source plotting package for
-Python\footnote{\url{http://leejjoon.github.com/pywcsgrid2/}}. The authors acknowledge the
-use of HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.
+The authors acknowledge the use of
+HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.
 
-\bibliography{extended_catalog}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{ic443_plots/four_plots_ic443_color.eps}
-    \else
-    \plotone{ic443_plots/four_plots_ic443_bw.eps}
-    \fi
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v3/run.py
-    \caption{
-    Counts maps and TS profiles for the SNR IC~443. (a) \ts
-    vs. extension of the source. (b) \tsext for individual energy
-    bands. (c) observed radial profile of counts in comparison to the
-    expected profiles for a spatially extended source (solid and colored
-    red in the online version) and for a point-like source (dashed and colored
-    blue in the online version).  (d) smoothed counts map after subtraction
-    of the diffuse emission compared to the smoothed
-    LAT PSF (inset). Both were smoothed by a 0\fdg1 2D Gaussian kernel.
-    Plots (a),
-    (c), and (d) use only 
-    photons with energies between
-    1 \gev and 100 \gev.  Plots (c) and (d) use
-    only photons which converted in the front part of the tracker and
-    have an improved angular resolution.
-    }
-    \label{four_plots_ic443}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{mc_plots/compare_disk_gauss_color.eps}
-    \else
-      \plotone{mc_plots/compare_disk_gauss_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v3/plot.py
-    \caption{
-    A comparison of a 2D Gaussian and uniform disk spatial model
-    of extended sources before and after convolving with the PSF for two
-    energy ranges.  The solid black line is the PSF that would be observed
-    for a power-law source of spectral index 2. The dashed line
-    and the dash-dotted lines are 
-    the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
-    and the convolution of this profile with the LAT PSF respectively
-    (colored red in the online version).
-    The dash-dot-doted and the dot-doted lines are the brightness profile
-    of a uniform disk with $\rsixeight=0\fdg5$ and the convolution
-    of this profile with the LAT PSF respectively (colored blue in the online version).
-    }\label{compare_disk_gauss}
-  \end{figure}
-
-\clearpage
-\begin{deluxetable}{rrrrrr}
-\tabletypesize{\normalsize}
-\tablecaption{Monte Carlo Spectral Parameters
-\label{ts_ext_num_sims}
-}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Spectral Index}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{$N_{1-100\gev}$}&
-\colhead{$\langle\ts\rangle_{1-100\gev}$}&
-\colhead{$N_{10-100\gev}$}&
-\colhead{$\langle\ts\rangle_{10-100\gev}$}\\
-\colhead{}&
-\colhead{(\phflux)}&
-\colhead{}&
-\colhead{}&
-\colhead{}&
-\colhead{}
-}
-
-\startdata
-      1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
-          &          $10^{-7}$ &           19079 &   5827    &     19079   &    2258     \\
-          &  $3\times 10^{-8}$ &           19303 &   1276    &     19303   &     541     \\
-          &          $10^{-8}$ &           19385 &    303    &     19381   &     142     \\
-          &  $3\times 10^{-9}$ &           18694 &     62    &     12442   &      43     \\
-      \hline
-        2 &          $10^{-6}$ &           18760 &  22101    &     18760   &    3033     \\
-          &  $3\times 10^{-7}$ &           18775 &   4913    &     18775   &     730     \\
-          &          $10^{-7}$ &           18804 &   1170    &     18803   &     192     \\
-          &  $3\times 10^{-8}$ &           18836 &    224    &     15256   &      50     \\
-          &          $10^{-8}$ &           17060 &     50    &   \nodata   & \nodata     \\
-      \hline
-      2.5 &  $3\times 10^{-6}$ &           18597 &  19036    &     18597   &     786    \\
-          &          $10^{-6}$ &           18609 &   4738    &     18608   &     208    \\
-          &  $3\times 10^{-7}$ &           18613 &    954    &     15958   &      53    \\
-          &          $10^{-7}$ &           18658 &    203    &   \nodata   & \nodata    \\
-          &  $3\times 10^{-8}$ &           14072 &     41    &   \nodata   & \nodata    \\
-      \hline                                                
-        3 &          $10^{-5}$ &           18354 &  19466    &     18354   &     215    \\
-          &  $3\times 10^{-6}$ &           18381 &   4205    &     15973   &      54    \\
-          &          $10^{-6}$ &           18449 &    966    &   \nodata   & \nodata    \\
-          &  $3\times 10^{-7}$ &           18517 &    174    &   \nodata   & \nodata    \\
-          &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
-\enddata
-
-\tablenotetext{(a)}{Integral 100 \mev to 100 \gev flux.}
-
-\tablecomments{
-    A list of the spectral models of the simulated point-like sources
-    which were tested for extension.  For each model, the number of
-    statistically independent simulations and the average value of \ts is
-    also tabulated.  
-}
-\end{deluxetable}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/ts_ext_emin_1000_color.eps}
-    \else
-    \plotone{mc_plots/ts_ext_emin_1000_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
-    \caption{
-    Cumulative distribution of the TS for the extension test when fitting
-    simulated point-like sources in the 1 GeV to 100 GeV energy range.
-    The four plots
-    represent simulated sources of different spectral indices and
-    the different lines (colored in the online version) 
-    represent point-like sources with different 100 \mev
-    to 100 \gev integral fluxes.  The dashed line (colored red)
-    is the cumulative
-    density function of Equation~\ref{ts_ext_distribution}.
-    }\label{ts_ext_mc_1000}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/ts_ext_emin_10000_color.eps}
-    \else
-    \plotone{mc_plots/ts_ext_emin_10000_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
-    \caption{
-    The same plot as Figure~\ref{ts_ext_mc_10000} but fitting in the 10 \gev to 100 \gev energy 
-    range.
-    }\label{ts_ext_mc_10000}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/index_sensitivity_color.eps}
-    \else
-    \plotone{mc_plots/index_sensitivity_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
-    \caption{
-    The detection threshold to resolve an
-    extended source with a uniform disk model for a two-year exposure.  All sources have an
-    assumed power-law spectrum and the different line styles (colors in
-    the electronic version) correspond to different simulated spectral
-    indices.  The lines with no markers correspond to the detection
-    threshold using photons with energies between 100 \mev and 100 \gev
-    while the lines with star-shaped markers correspond to the threshold
-    using photons with energies between 1 \gev and 100 \gev.
-    }\label{index_sensitivity}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/all_sensitivity_color.eps}
-    \else
-    \plotone{mc_plots/all_sensitivity_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
-    \caption{The LAT detection threshold for four spectral indices
-    and three backgrounds ($1\times$, $10\times$, and $100\times$ the
-    Sreekumar-like isotropic background) for a two-year exposure. The
-    left-hand plots are the detection threshold when using 
-    photons with energies between
-    1 \gev and 100 \gev
-    and the right-hand plots are the detection threshold when using
-    photons with energies between
-    10 \gev and 100 \gev.  The flux is integrated only in the
-    selected energy range.  Overlaid on this plot are the LAT detected
-    extended sources placed by the magnitude of the nearby Galactic
-    diffuse emission and the energy range they were analyzed with.
-    The star-shaped markers (colored red in the electronic version)
-    are sources with a spectral index closer to 1.5, the triangular
-    markers (colored blue) an index closer to 2, and the circular markers
-    (colored green) an index closer to 2.5.  The triangular marker in plot
-    (d) below the sensitivity line is MSH\,15$-$52.
-    }\label{all_sensitivity} 
-  \end{figure}
-
-  \clearpage
-  \thispagestyle{empty}
-\begin{deluxetable}{rr|rrrrrrrrrrrrrrrrrrrrr}
-\tablecolumns{22}
-\tabletypesize{\scriptsize}
-\rotate
-\tablewidth{0pt}
-\tablecaption{Extension Detection Threshold
-\label{all_sensitivity_table}
-}
-\tablehead{
-\colhead{$\gamma$}&       
-\colhead{BG}&
-\colhead{$0.1$}&
-\colhead{$0.2$}&
-\colhead{$0.3$}&
-\colhead{$0.4$}&
-\colhead{$0.5$}&
-\colhead{$0.6$}&
-\colhead{$0.7$}&
-\colhead{$0.8$}&
-\colhead{$0.9$}&
-\colhead{$1.0$}&
-\colhead{$1.1$}&
-\colhead{$1.2$}&
-\colhead{$1.3$}&
-\colhead{$1.4$}&
-\colhead{$1.5$}&
-\colhead{$1.6$}&
-\colhead{$1.7$}&
-\colhead{$1.8$}&
-\colhead{$1.9$}&
-\colhead{$2.0$}
-}
-\startdata
-\multicolumn{22}{c}{E$>$1 \gev} \\
-\hline
-     1.5 &      $1\times$ &      148.1 &       23.3 &       11.3 &        8.0 &        7.2 &        6.9 &        6.7 &        6.8 &        7.1 &        7.4 &        7.6 &        7.9 &        8.1 &        8.5 &        9.2 &        9.9 &        9.1 &        9.2 &        9.0 &       10.3 \\
-         &     $10\times$ &      148.4 &       29.0 &       18.7 &       15.2 &       15.4 &       15.0 &       16.1 &       16.0 &       16.8 &       17.7 &       18.2 &       19.3 &       20.9 &       22.5 &       23.8 &       24.8 &       21.3 &       22.8 &       23.4 &       23.7 \\
-         &    $100\times$ &      186.8 &       55.0 &       43.4 &       40.7 &       41.0 &       41.8 &       40.9 &       40.9 &       42.7 &       43.6 &       38.4 &       39.9 &       40.6 &       38.4 &       36.9 &       36.3 &       37.1 &       38.8 &       37.2 &       37.6 \\
-       2 &      $1\times$ &      328.4 &       43.4 &       18.9 &       13.4 &       11.2 &       10.4 &       10.2 &       10.2 &       10.2 &       10.4 &       10.7 &       10.9 &       11.2 &       11.5 &       12.4 &       12.6 &       13.0 &       13.4 &       14.0 &       14.4 \\
-         &     $10\times$ &      341.0 &       55.9 &       32.3 &       27.6 &       26.5 &       25.4 &       25.6 &       25.9 &       27.4 &       26.8 &       27.8 &       28.7 &       29.8 &       30.1 &       31.0 &       31.5 &       31.7 &       34.0 &       34.3 &       35.9 \\
-         &    $100\times$ &      420.5 &      128.3 &       90.2 &       77.3 &       73.3 &       70.8 &       67.5 &       64.3 &       64.2 &       64.1 &       62.8 &       63.6 &       61.7 &       61.9 &       58.4 &       59.0 &       61.4 &       63.3 &       60.1 &       58.1 \\
-     2.5 &      $1\times$ &      627.1 &       75.6 &       29.8 &       19.3 &       15.5 &       13.5 &       12.8 &       12.6 &       12.5 &       12.5 &       12.6 &       12.9 &       12.9 &       13.1 &       13.5 &       13.7 &       14.3 &       14.8 &       15.2 &       15.8 \\
-         &     $10\times$ &      638.9 &       99.1 &       52.1 &       39.1 &       34.6 &       33.0 &       32.5 &       32.5 &       32.8 &       33.2 &       34.1 &       34.3 &       34.5 &       35.1 &       36.6 &       36.9 &       35.5 &       36.0 &       36.5 &       37.3 \\
-         &    $100\times$ &      795.0 &      262.1 &      140.9 &      104.3 &       90.4 &       81.2 &       77.2 &       75.1 &       69.7 &       70.9 &       66.5 &       65.6 &       64.9 &       64.0 &       58.9 &       58.1 &       60.2 &       58.4 &       57.5 &       55.8 \\
-       3 &      $1\times$ &      841.5 &      110.6 &       43.2 &       25.5 &       18.7 &       16.1 &       14.4 &       13.6 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.6 &       13.5 &       13.8 &       14.2 &       14.4 &       14.8 &       15.4 \\
-         &     $10\times$ &      921.6 &      151.3 &       69.1 &       47.8 &       40.7 &       37.1 &       35.5 &       34.5 &       35.1 &       35.5 &       35.3 &       35.3 &       35.4 &       35.5 &       36.8 &       37.6 &       35.3 &       35.4 &       36.3 &       36.6 \\
-         &    $100\times$ &     1124.1 &      282.9 &      181.1 &      119.8 &      100.7 &       91.1 &       84.3 &       77.9 &       73.3 &       71.8 &       67.6 &       66.4 &       65.5 &       63.9 &       59.0 &       58.6 &       58.8 &       57.5 &       55.4 &       54.4 \\
-\cutinhead{E$>$10 \gev}
-     1.5 &      $1\times$ &       44.6 &        8.0 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.5 &        2.5 &        2.6 &        2.7 &        2.8 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
-         &     $10\times$ &       45.2 &        9.2 &        5.8 &        5.0 &        4.9 &        4.9 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.3 &        6.6 &        6.5 &        6.8 &        7.6 &        7.8 &        8.2 &        8.5 &        8.7 \\
-         &    $100\times$ &       47.3 &       13.4 &       11.6 &       10.6 &       10.8 &       10.8 &       12.0 &       12.7 &       13.2 &       13.7 &       15.3 &       16.1 &       17.2 &       18.2 &       18.9 &       19.5 &       20.4 &       21.0 &       21.7 &       22.9 \\
-       2 &      $1\times$ &       49.7 &        8.4 &        4.4 &        3.3 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
-         &     $10\times$ &       48.6 &        9.5 &        6.0 &        5.2 &        5.0 &        5.2 &        5.2 &        5.3 &        5.4 &        5.8 &        6.4 &        6.6 &        7.0 &        7.1 &        7.5 &        8.0 &        8.3 &        8.6 &        9.0 &        9.2 \\
-         &    $100\times$ &       51.8 &       14.7 &       11.8 &       11.5 &       11.5 &       11.9 &       13.2 &       14.0 &       14.3 &       15.3 &       16.2 &       16.9 &       18.4 &       19.2 &       19.8 &       21.0 &       22.0 &       22.8 &       23.2 &       24.3 \\
-     2.5 &      $1\times$ &       53.1 &        9.1 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.8 &        2.9 &        3.1 &        3.2 &        3.3 &        3.5 &        3.6 \\
-         &     $10\times$ &       53.7 &       10.5 &        6.3 &        5.4 &        5.1 &        5.1 &        5.3 &        5.4 &        5.7 &        6.0 &        6.3 &        6.6 &        6.8 &        6.9 &        7.5 &        8.1 &        8.3 &        8.6 &        8.9 &        9.2 \\
-         &    $100\times$ &       57.0 &       15.6 &       12.7 &       11.9 &       11.8 &       12.2 &       13.1 &       14.3 &       14.6 &       15.2 &       16.3 &       17.0 &       18.8 &       19.2 &       19.9 &       21.0 &       21.9 &       22.3 &       23.3 &       23.7 \\
-       3 &      $1\times$ &       55.5 &        9.4 &        4.8 &        3.4 &        2.9 &        2.7 &        2.6 &        2.5 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 \\
-         &     $10\times$ &       56.0 &       10.5 &        6.2 &        5.3 &        5.1 &        5.1 &        5.1 &        5.3 &        5.5 &        5.7 &        5.9 &        6.4 &        6.4 &        6.6 &        7.0 &        7.8 &        8.0 &        8.3 &        8.6 &        8.9 \\
-         &    $100\times$ &       60.3 &       16.2 &       12.7 &       11.7 &       11.8 &       12.2 &       12.6 &       13.8 &       14.2 &       14.6 &       15.8 &       16.5 &       17.6 &       18.5 &       19.4 &       19.8 &       20.7 &       21.0 &       21.8 &       22.5 \\
-\enddata
-\tablecomments{
-      The detection threshold to resolve spatially extended
-      sources with a uniform disk spatial model for a two-year exposure
-      The threshold is calculated for
-      sources of varying energy
-      ranges, spectral indices, and background levels.  The sensitivity
-      was calculated against
-      a Sreekumar-like isotropic background
-      and the second column is the factor that the simulated background
-      was scaled by. The remaining columns are varying sizes of the source. 
-      The table quotes
-      integral fluxes in the analyzed energy range (1 \gev to 100 \gev or 10 \gev to 100
-      \gev) in units of $10^{-10}$ \phflux.
-      }
-\end{deluxetable}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{mc_plots/time_sensitivity_color.eps}
-    \else
-      \plotone{mc_plots/time_sensitivity_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
-    \caption{
-    The projected detection threshold of the LAT to extension after 10 years
-    for a power-law
-    source of spectral index 2 against 10 times the isotropic background
-    in the energy range from 1 \gev to 100 \gev (solid line colored red in the electronic
-    version) and 10 \gev to 100 \gev
-    (dashed line colored blue). The shaded gray regions represent the
-    detection threshold assuming the sensitivity improves from 2 to 10
-    years by the square root of the exposure (top edge) and linearly with
-    exposure (bottom edge).  The lower plot shows the factor increase in
-    sensitivity.  For small extended sources, the detection threshold of the LAT
-    to the extension of a source will improve by a factor larger than the square root of 
-    the exposure.
-    }\label{time_sensitivity}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/confusion_extended_plot_color.eps}
-    \else
-    \plotone{mc_plots/confusion_extended_plot_bw.eps}
-    \fi
-    % this plot came from 
-    \caption{
-    (a) and (b) are the distribution of \tsext and of \tsinc when
-    fitting simulated spatially extended sources of varying sizes as
-    both an extended source and as two point-like sources.  (c) and
-    (d) are the distribution of $\tsext-\tsinc$ for the same simulated sources.
-    (a) and (c) represent sources fit in the 1 \gev to 100 \gev energy
-    range and (b) and (d) represent sources fit in the 10 \gev to
-    100 \gev energy range.  In (c) and (d), the plus-shaped markers
-    (colored red in the electronic version) are fits where $\tsext\ge16$.
-    }\label{confusion_extended_plot}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/confusion_2pts_plot_color.eps}
-    \else
-    \plotone{mc_plots/confusion_2pts_plot_bw.eps}
-    \fi
-    % this plot came from 
-    \caption{
-    The distribution of $\tsext-\tsinc$ when fitting two simulated
-    point-like sources of varying separations as
-    both an extended source and as two point-like sources.  (a),
-    and (b) represent simulations of two point-like sources with the
-    same spectral index and (c) and (d) represent simulations of two
-    point-like sources with different spectral indices.  (a) and (c)
-    fit the simulated sources in the 1 \gev to 100 \gev energy range
-    and (b) and (d) fit in the 10 \gev to 100 \gev energy range.
-    The plus-shaped markers (colored red in the electronic version)
-    are fits where $\tsext\ge16$.
-    }\label{confusion_2pts_plot}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/agn_color.eps}
-    \else
-      \plotone{source_plots/agn_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v6/agn.py
-    \caption{The cumulative density of \tsext for the 733 clean
-    AGN in 2LAC that were significant above 1 \gev calculated with \pointlike (dashed line
-    colored blue in the electronic version)
-    and with \gtlike (solid line colored black).  AGN are too far
-    and too small to be resolved by the LAT. Therefore, the cumulative
-    density of $\tsext$ is expected to follow a $\chi^2_1/2$ distribution
-    (Equation~\ref{ts_ext_distribution}, the dash-dotted line colored
-    red).
-    }\label{agn_ts_ext}
-  \end{figure}
-
-\begin{figure}
-  \ifcolorfigure
-    \plotone{ic443_plots/res_tsmap_ic443_color.eps}
-    \else
-    \plotone{ic443_plots/res_tsmap_ic443_bw.eps}
-    \fi
-  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v2
-
-  \caption{
-  A TS map generated for the region around the SNR 
-  IC~443 using 
-  photons with energies between
-  1 \gev and 100 \gev.  (a) TS map after
-  subtracting IC~443 modeled as a point-like source. (b) same as (a), but
-  IC~443 modeled as an extended source. The cross represents the best
-  fit position of IC~443.
-  }
-  \label{res_tsmaps}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{source_plots/example_bad_fit_color.eps}
-    \else
-    \plotone{source_plots/example_bad_fit_bw.eps}
-    \fi
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
-    \caption{
-    A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of the
-    region around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian
-    kernel. The plus-shaped marker and circle (colored red in
-    the online version) represent the center and size of the source
-    fit with a
-    radially-symmetric uniform disk spatial model.  The black
-    crosses represent the positions of other 2FGL sources.  The extension
-    is statistically significant, but the extension encompasses many 2FGL
-    sources and the emission does not look to be uniform. Although
-    the fit is statistically significant, it likely corresponds to
-    residual features of inaccurately modeled diffuse emission picked
-    up by the fit. 
-    }
-    \label{example_bad_fit}
-\end{figure}
-
-\begin{deluxetable}{lrrrrrrrr}
-\tablecolumns{9}
-\rotate
-\tabletypesize{\footnotesize}
-\tablewidth{0pt}
-\tablecaption{Analysis of the twelve extended sources included in the 2FGL catalog
-\label{known_extended_sources}
-}
-\tablehead{
-\colhead{Name}&
-\colhead{\glon}&
-\colhead{\glat}&
-\colhead{$\sigma$}&
-\colhead{\ts}&
-\colhead{\tsext}&
-\colhead{Pos Err}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{Index}\\
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}
-}
-
-\startdata
-\multicolumn{9}{c}{E$>$1 \gev} \\
-\hline
-SMC                                  &     302.59 &   $-$44.42 & $  1.32 \pm   0.15 \pm   0.31 $ &       95.0 &       52.9 &   0.14 & $    2.7 \pm     0.3$ & $   2.48 \pm    0.19$  \\
-LMC                                  &     279.26 &   $-$32.31 & $  1.37 \pm   0.04 \pm   0.11 $ &     1127.9 &      909.9 &   0.04 & $   13.6 \pm     0.6$ & $   2.43 \pm    0.06$  \\
-IC~443                               &     189.05 &       3.04 & $  0.35 \pm   0.01 \pm   0.04 $ &    10692.9 &      554.4 &   0.01 & $   62.4 \pm     1.1$ & $   2.22 \pm    0.02$  \\
-Vela X                               &     263.34 &    $-$3.11 & $                         0.88$ &            &            &        &                       &                        \\
-Centaurus A                          &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
-W28                                  &       6.50 &    $-$0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
-W30                                  &       8.61 &    $-$0.20 & $  0.34 \pm   0.02 \pm   0.02 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
-W44                                  &      34.69 &    $-$0.39 & $  0.35 \pm   0.02 \pm   0.02 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
-W51C                                 &      49.12 &    $-$0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
-Cygnus Loop                          &      74.21 &    $-$8.48 & $  1.71 \pm   0.05 \pm   0.06 $ &      357.9 &      246.0 &   0.06 & $   11.4 \pm     0.7$ & $   2.50 \pm    0.10$  \\
-\cutinhead{E$>$10 \gev}
-MSH\,15$-$52\tablenotemark{(b)}      &     320.39 &    $-$1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
-HESS\,J1825$-$137\tablenotemark{(b)} &      17.56 &    $-$0.47 & $  0.65 \pm   0.04 \pm   0.02 $ &       59.7 &       33.8 &   0.05 & $    1.6 \pm     0.2$ & $   1.63 \pm    0.22$  \\
-\enddata
-
-\tablenotetext{(a)}{
-Integral Flux in units of $10^{-9}$ \phflux and integrated in the fit
-energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
-}
-\tablenotetext{(b)}{
-The discrepancy in the best fit spectra of MSH\,15$-$52 and HESS\,J1825$-$137
-compared to \cite{msh1552} and
-\cite{fermi_hess_j1825} is due to fitting over a different energy range.
-}
-
-\tablecomments{
-All sources were fit using a radially-symmetric uniform disk spatial model.
-\glon and \glat are Galactic longitude
-and latitude of the best fit extended source respectively.  The first
-error on $\sigma$ is statistical and the second is systematic (see
-Section~\ref{systematic_errors_on_extension}).  
-The errors on the integral fluxes and the spectral indices
-are statistical only.
-Pos Err is the error on
-the position of the source.  Vela X and the Centaurus A Lobes were
-not fit in our analysis but are included for completeness.
-}
-\end{deluxetable}
-
-  % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-  % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-  % 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
-  % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
-  % N/A                - P72Y1287         - 2FGL J0851.7-4635
-
-\clearpage
-\thispagestyle{empty}
-\begin{deluxetable}{lrrrrrrrrl}
-\tablecolumns{10}
-\tabletypesize{\small}
-\rotate
-\tablewidth{0pt}
-\tablecaption{Extension fit for the nine additional extended sources
-\label{new_ext_srcs_table}
-}
-\tablehead{
-\colhead{Name}&
-\colhead{\glon}&
-\colhead{\glat}&
-\colhead{$\sigma$}&
-\colhead{\ts}&
-\colhead{\tsext}&
-\colhead{Pos Err}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{Index}&
-\colhead{Counterpart}\\
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{}
-}
-
-\startdata
-\multicolumn{10}{c}{E$>$1 \gev} \\
-\hline
-2FGL\,J0823.0$-$4246                       &     260.32 &    $-$3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      322.2 &       48.0 &   0.02 & $    8.4 \pm     0.6$ & $   2.21 \pm    0.09$ &                  Puppis A \\
-2FGL\,J1627.0$-$2425c                      &     353.07 &      16.80 & $  0.42 \pm   0.05 \pm   0.16 $ &      139.9 &       32.4 &   0.04 & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ &                 Ophiuchus \\
-\cutinhead{E$>$10 \gev}
-2FGL\,J0851.7$-$4635                       &     266.31 &    $-$1.43 & $  1.15 \pm   0.08 \pm   0.02 $ &      116.6 &       86.8 &   0.07 & $    1.3 \pm     0.2$ & $   1.74 \pm    0.21$ &                  Vela Jr.
-\\
-2FGL\,J1615.0$-$5051                       &     332.37 &    $-$0.13 & $  0.32 \pm   0.04 \pm   0.01 $ &       50.4 &       16.7 &   0.04 & $    1.0 \pm     0.2$ & $   2.19 \pm    0.28$ &         HESS\,J1616$-$508 \\
-2FGL\,J1615.2$-$5138                       &     331.66 &    $-$0.66 & $  0.42 \pm   0.04 \pm   0.02 $ &       76.1 &       46.5 &   0.04 & $    1.1 \pm     0.2$ & $   1.79 \pm    0.26$ &         HESS\,J1614$-$518 \\
-2FGL\,J1632.4$-$4753c                      &     336.52 &       0.12 & $  0.35 \pm   0.04 \pm   0.02 $ &       64.4 &       26.9 &   0.04 & $    1.4 \pm     0.2$ & $   2.66 \pm    0.30$ &         HESS\,J1632$-$478 \\
-2FGL\,J1712.4$-$3941\tablenotemark{(b)}    &     347.26 &    $-$0.53 & $  0.56 \pm   0.04 \pm   0.02 $ &       59.4 &       38.5 &   0.05 & $    1.2 \pm     0.2$ & $   1.87 \pm    0.22$ &        RX\,J1713.7$-$3946 \\
-2FGL\,J1837.3$-$0700c                      &      25.08 &       0.13 & $  0.33 \pm   0.07 \pm   0.05 $ &       47.0 &       18.5 &   0.07 & $    1.0 \pm     0.2$ & $   1.65 \pm    0.29$ &         HESS\,J1837$-$069 \\
-2FGL\,J2021.5+4026                         &      78.24 &       2.20 & $  0.63 \pm   0.05 \pm   0.04 $ &      237.2 &      128.9 &   0.05 & $    2.0 \pm     0.2$ & $   2.42 \pm    0.19$ &            $\gamma$-Cygni \\
-\enddata
-
-\tablenotetext{(a)}{
-Integral Flux in units of $10^{-9}$ \phflux and integrated in the fit
-energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
-}
-
-\tablenotetext{(b)}{
-The discrepancy in the best fit spectra of 2FGL\,J1712.4$-$3941 compared
-to \cite{rx_j1713_lat} is due to fitting over a different energy range.
-}
-
-\tablecomments{
-    The columns in this table have the same meaning as those in
-    Table~\ref{known_extended_sources}.
-    RX\,J1713.7$-$3946 and Vela Jr. were previously studied in dedicated publications \citep{rx_j1713_lat,vela_jr_lat}.
-}
-\end{deluxetable}
-
-\clearpage
-\thispagestyle{empty}
-\begin{deluxetable}{lrrrrrrrrrr}
-  \tabletypesize{\small}
-  \tablecolumns{11}
-  \rotate
-  \tablewidth{0pt}
-  \tablecaption{Dual localization, alternative PSF, and alternative approach to modeling the diffuse emission
-  \label{alt_diff_model_results}
-  }
-  \tablehead{
-  \colhead{Name}&
-  \colhead{$\ts_\pointlike$}&
-  \colhead{$\ts_\gtlike$}&
-  \colhead{$\ts_\altdiff$}&
-  \colhead{$\tsext_\pointlike$}&
-  \colhead{$\tsext_\gtlike$}&
-  \colhead{$\tsext_\altdiff$}&
-  \colhead{$\sigma$}&
-  \colhead{$\sigma_\altdiff$}&
-  \colhead{$\sigma_\altpsf$}&
-  \colhead{$\tsinc$}\\
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{(deg.)}&
-  \colhead{(deg.)}&
-  \colhead{(deg.)}&
-  \colhead{}
-  }
-  \startdata
-\multicolumn{11}{c}{E$>$1 \gev} \\
-\hline
-2FGL\,J0823.0$-$4246      &                331.9 &                322.2 &                356.0 &                 60.0 &                 48.0 &                 56.0 &                 0.37 &                 0.39 &                 0.39 &                 23.0 \\
-2FGL\,J1627.0$-$2425c     &                154.8 &                139.9 &                105.7 &                 39.4 &                 32.4 &                 24.8 &                 0.42 &
- 0.40 &                 0.58 &                 24.5 \\
-\cutinhead{E$>$10 \gev}
-2FGL\,J0851.7$-$4635      &                115.2 &                116.6 &                123.1 &                 83.9 &                 86.8 &                 89.8 &                 1.15 &                 1.16 &                 1.17 &                 15.5 \\
-2FGL\,J1615.0$-$5051\tablenotemark{(a)} &                 48.2 &                 50.4 &                 56.6 &                 15.2 &                 16.7 &                 17.8 &                 0.32 &                 0.33 &                 0.32 &                 13.1 \\
-2FGL\,J1615.2$-$5138      &                 75.0 &                 76.1 &                 83.8 &                 42.9 &                 46.5 &                 54.1 &                 0.42 &                 0.43 &                 0.43 &                 35.1 \\
-2FGL\,J1632.4$-$4753c     &                 64.5 &                 64.4 &                 66.8 &                 23.0 &                 26.9 &                 25.5 &                 0.35 &                 0.36 &                 0.37 &                 10.9 \\
-2FGL\,J1712.4$-$3941      &                 59.8 &                 59.4 &                 39.9 &                 38.4 &                 38.5 &                 30.7 &                 0.56 &                 0.55 &                 0.53 &                  2.7 \\
-2FGL\,J1837.3$-$0700c     &                 44.5 &                 47.0 &                 39.2 &                 17.6 &                 18.5 &                 16.1 &                 0.33 &                 0.32 &                 0.38 &                 10.8 \\
-2FGL\,J2021.5+4026        &                239.1 &                237.2 &                255.8 &                139.1 &                128.9 &                138.0 &                 0.63 &                 0.65 &                 0.59 &                 37.3 \\
-  \enddata
-
-\tablenotetext{(a)}{
-% Fit from /u/gl/lande/work/fermi/extended_catalog/2FGL/individual_sources/HESS_J1616-508/v4/iteration_v2/r
-Using \pointlike, \tsext for 2FGL\,J1615.0$-$5051 was sligthly below
-16 when the source was fit in the 10 \gev to 100 \gev energy range. To
-confirm the extension measure, the extension was refit in \pointlike
-using a slightly lower energy.  In the 5.6 \gev to 100 \gev energy range,
-we obtained a consistent extension and \tsext=28.0.  In the rest of
-this paper, we quote the $E>10 \gev$ results for consistency with the
-other sources.
-}
-
-\tablecomments{
-$\ts_\pointlike$, $\ts_\gtlike$, and $\ts_\altdiff$ are the test
-statistic values from \pointlike, \gtlike, and \gtlike with the alternative
-approach to modeling the diffuse emission respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$,
-and $\tsext_\altdiff$ are the TS values from \pointlike, \gtlike, and \gtlike with the alternative 
-approach to modeling the diffuse emission respectively.  $\sigma$, $\sigma_\altdiff$, and $\sigma_\altpsf$
-are the fit sizes assuming
-a radially-symmetric uniform disk model
-with the standard analysis, the alternative 
-approach to modeling the diffuse emission, and the alternative PSF respectively.  
-}
-\end{deluxetable}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Puppis_A_color.eps}
-    \else
-      \plotone{source_plots/source_Puppis_A_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v8/run.py
-  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
-  of 2FGL\,J0823.0$-$4246 smoothed by a 0\fdg1 2D
-  Gaussian kernel.  The triangular marker 
-  (colored red in the online version)
-  represents the 2FGL position of this source.  The plus-shaped
-  marker and the circle (colored
-  red) represent 
-  the best fit position and extension of this source assuming a
-  radially-symmetric uniform disk model.  The two 
-  star-shaped markers (colored
-  green) represent 2FGL sources that were
-  removed from the background model.
-  The lower right inset is the model predicted emission from a point-like
-  source with the same spectrum as 2FGL\,J0823.4$-$4305 smoothed by the
-  same kernel.  This source is spatially coincident with the Puppis A
-  SNR. The light blue contours correspond to the X-ray image of Puppis
-  A observed by \rosat \citep{rosat_puppis_a}.
-  }\label{1FGL_J0823.3-4248}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/snr_seds_color.eps}
-    \else
-      \plotone{summary_plots/snr_seds_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v4/plot_seds/plot_snr_seds.py
-    \caption{
-    The spectral energy distribution of the extended sources 
-    Puppis A (2FGL\,J0823.0$-$4246) and $\gamma$-Cygni 
-    (2FGL\,J2021.5+4026).
-    The lines (colored red in the online version)
-    are the best fit power-law spectral models of
-    these sources.
-    The spectral errors are statistical only.
-    The upper limit is at the 95\% confidence level.
-    }
-    \label{snr_seds}
-  \end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Ophiuchus_color.eps}
-    \else
-      \plotone{source_plots/source_Ophiuchus_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of (a) the region
-  around 2FGL\,J1627.0$-$2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
-  also the emission from 2FGL\,J1625.7$-$2526
-  subtracted.  The triangular marker 
-  (colored red in the
-  online version) represents the 2FGL position of this source.
-  The plus-shaped marker and the circle (colored red) 
-  represent the best fit position and extension of this
-  source assuming a radially-symmetric uniform disk model
-  and the black cross represents a background 2FGL source. 
-  The
-  contours in (a) correspond to the 100 $\mu$m image observed by
-  IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
-  CO ($J=1\rightarrow 0$) emission integrated from $-$8 $\km\,\s^{-1}$
-  to 20 $\km\,\s^{-1}$.  They are from \cite{co_rho_ophiuci}, were cleaned using
-  the moment-masking technique \citep{masking_moment_2011}, and have
-  been smoothed by a 0\fdg25 2D Gaussian kernel.
-  }\label{1FGL_J1628.6-2419c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Vela_Jr_color.eps}
-    \else
-      \plotone{source_plots/source_Vela_Jr_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v8/run.py
-  \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  2FGL\,J0851.7$-$4635 smoothed by a 0\fdg25 2D Gaussian
-  kernel. The triangular marker (colored red in the electronic version)
-  represents the 2FGL position of this source.  The plus-shaped marker
-  and the circle (colored red) are the best fit position and extension of
-  this source assuming a radially-symmetric uniform disk model.
-  The three black crosses represent background 2FGL sources
-  and the three star-shaped markers (colored green) represent other 2FGL sources
-  that were removed from the background model 
-  The circular and square-shaped
-  marker (colored blue) represents the 2FGL and relocalized position of another 2FGL source.  
-  This extended source is spatially
-  coincident with the Vela Jr. SNR.  The contours (colored light blue)
-  correspond to the \tev image of Vela Jr.
-  \citep{vela_jr_hess}.
-  }\label{Vela_Jr}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_HESS_J1614-518_color.eps}
-    \else
-      \plotone{source_plots/source_HESS_J1614-518_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v8/run.py
-  \caption{
-    A diffuse-emission-subtracted 10 \gev to 100 \gev counts
-    map of 2FGL\,J1615.0$-$5051 (upper left)
-    and 2FGL\,J1615.2$-$5138 (lower right) smoothed by a 0\fdg1
-    2D Gaussian kernel.  The triangular markers (colored red in the
-    electronic version) represent the 2FGL positions of these sources.
-    The cross-shaped markers and the
-    circles (colored red) represent the best fit
-    positions and extensions of these sources assuming a radially
-    symmetric uniform disk model.  
-    The two black crosses represent  background 2FGL sources and
-    the star-shaped
-    marker (colored green) represents another 2FGL source that was removed from the background
-    model.  The contours (colored light blue) correspond to the \tev
-    image of HESS\,J1616$-$508 (left) and HESS\,J1614$-$518 (right)
-    \citep{hess_plane_survey}.   
-    }\label{1FGL_J1613.6-5100c}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/hess_seds_color.eps}
-    \else
-      \plotone{summary_plots/hess_seds_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v4/plot_seds/plot_hess_seds.py
-    \caption{
-    The spectral energy distribution of four extended
-    sources associated with unidentified
-    extended \tev sources.  The black points
-    with circular markers are obtained by the LAT. The points with
-    plus-shaped markers (colored red in the electronic version) are
-    for the associated H.E.S.S sources.  (a) the
-    LAT SED of 2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED
-    of HESS\,J1616$-$508. (b) 2FGL\,J1615.2$-$5138
-    and HESS\,J1614$-$518. (c) 2FGL\,J1632.4$-$4753c
-    and HESS\,J1632$-$478. (d) 2FGL\,J1837.3$-$0700c
-    and HESS\,J1837$-$069. The H.E.S.S. data points are from
-    \citep{hess_plane_survey}. Both LAT and H.E.S.S. spectral errors are
-    statistical only.}
-    \label{hess_seds}
-  \end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_HESS_J1632-478_color.eps}
-    \else
-      \plotone{source_plots/source_HESS_J1632-478_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  2FGL\,J1632.4$-$4753c (a) smoothed by a 0\fdg1 2D Gaussian
-  kernel and (b) with the emission from the background sources subtracted.  
-  The triangular marker (colored red in the electronic version)
-  represents the 2FGL position of this source.  The plus-shaped marker
-  and the circle (colored red) are the best fit position and extension of
-  2FGL\,J1632.4$-$4753c assuming a radially-symmetric uniform disk model.  
-  The four black crosses represent background 2FGL
-  sources subtracted in (b).  The 
-  circular and square-shaped markers (colored blue) represent 
-  the 2FGL and relocalized positions respectively of two
-  additional background 2FGL sources subtracted in (b).
-  The star-shaped marker (colored green) represents another 2FGL
-  source that was removed from the background model.  
-  The contours (colored light blue) correspond to the \tev image of
-  HESS\,J1632$-$478 \citep{hess_plane_survey}.
-  }\label{1FGL_J1632.9-4802c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_RX_J1713.7-3946_color.eps}
-    \else
-      \plotone{source_plots/source_RX_J1713.7-3946_bw.eps}
-    \fi
-    % this plot came from
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map
-  of 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg15 2D
-  Gaussian kernel and (b) with the emission from the background sources
-  subtracted.  This source is spatially coincident with RX\,J1713.7$-$3946
-  and was recently studied in \cite{rx_j1713_lat}.  The triangular marker
-  (colored red in the online version) represents the 2FGL position of
-  this source.  The plus-shaped marker and the circle (colored red) are
-  the best fit position and extension of this source assuming a radially
-  symmetric uniform disk model.  
-  The two black crosses represent background 2FGL sources subtracted in (b).
-  The contours (colored light blue)
-  correspond to the \tev image \citep{rx_j1713_hess}.  
-  }\label{2FGL_J1712.4-3941}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_HESS_J1837-069_color.eps}
-    \else
-      \plotone{source_plots/source_HESS_J1837-069_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of the
-  region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg15 2D Gaussian
-  kernel and (b) with the emission from the background sources subtracted.
-  The triangular marker (colored red in the online version) represents
-  the 2FGL
-  position of this source. 
-  The plus-shaped marker and 
-  the circle (colored red) represent the best fit position and extension
-  of 2FGL\,J1837.3$-$0700c assuming a radially-symmetric uniform disk model. 
-  The circular and square-shaped markers (colored
-  blue) represent the 2FGL and the relocalized positions respectively of
-  two background 2FGL sources subtracted in (b).  The star-shaped marker
-  (colored green) represents a 2FGL source that was removed from the
-  background model.  The contours (colored light blue) correspond to
-  the \tev image of HESS\,J1837$-$069
-  \citep{hess_plane_survey}.
-  The diamond-shaped marker (colored orange) represents the position of PSR\,J1838$-$0655
-  and the hexagonal-shaped marker (colored purple) represents the position AX\,J1837.3$-$0652
-  \citep{pulsations_HESS_J1837-069}.
-  }\label{1FGL_J1837.5-0659c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Gamma_Cygni_color.eps}
-    \else
-      \plotone{source_plots/source_Gamma_Cygni_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v8/run.py
-  \caption{A diffuse-emission-subtracted 
-  10 \gev to 100 \gev counts map of the
-  region around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 2D Gaussian
-  kernel. The triangular marker (colored red in the online version)
-  represents the 2FGL position of this source.  The plus-shaped
-  marker and the circle (colored red) represent the best fit position
-  and extension of 2FGL\,J2021.5+4026 assuming a radially-symmetric
-  uniform disk model.  
-  The star-shaped marker (colored green)
-  represents a 2FGL source that was removed from the background model.
-  2FGL\,J2021.5+4026
-  is spatially coincident with the $\gamma$-Cygni SNR.  The contours
-  (colored light blue) correspond to the 408MHz image of $\gamma$-Cygni
-  observed by the Canadian Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
-  }\label{1FGL_J2020.0+4049}
-\end{figure}
-
-\clearpage
-  \begin{figure}
-      \ifcolorfigure
-      \plotone{summary_plots/allsky_extended_sources_color.eps}
-      \else
-      \plotone{summary_plots/allsky_extended_sources_bw.eps}
-      \fi
-      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v2/run.py
-      \caption{The 21
-      spatially extended sources detected by the LAT
-      at \gev energies 
-      with 2 years of data.  The twelve extended sources included in
-      2FGL are represented by the circular markers (colored red in the online
-      version).  The nine new extended sources are represented by
-      the triangular markers (colored orange).
-      The source positions are overlaid on a 100 \mev to 100 \gev 
-      Aitoff projection sky map of the LAT data in Galactic coordinates.
-}
-\label{allsky_extended_sources}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/gev_vs_tev_plot_color.eps}
-    \else
-      \plotone{summary_plots/gev_vs_tev_plot_bw.eps}
-      \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v5/run.py
-    \caption{
-    A comparison of the sizes of extended sources detected at
-    both \gev and \tev energies.  The \tev sizes of W30,
-    2FGL\,J1837.3$-$0700c, 2FGL\,J1632.4$-$4753c, 2FGL\,J1615.0$-$5051,
-    and 2FGL\,J1615.2$-$5138 are from \cite{hess_plane_survey}.
-    The \tev sizes of MSH\,15$-$52, HESS\,J1825$-$137,
-    Vela X, Vela Jr., RX\,J1713.7$-$3946 and W28 are from
-    \cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
-    The \tev size of IC~443 is from \cite{ic443_veritas} and
-    W51C is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev
-    sizes of MSH\,15$-$52, HESS\,J1614$-$518, HESS\,J1632$-$478, and
-    HESS\,J1837$-$069 have only been reported with an elliptical 2D
-    Gaussian fit and so the plotted sizes are the geometric 
-    mean of the semi-major and semi-minor axis.
-    The LAT extension of
-    Vela X is from \cite{velax}. 
-    The \tev sources were fit assuming a 2D Gaussian surface brightness profile
-    so the plotted \gev and \tev extensions were first converted to
-    \rsixeight (see Section~\ref{compare_source_size}).  
-    Because of
-    their large sizes, the shape of RX\,J1713.7$-$3946 and Vela Jr.
-    were not directly fit at \tev energies and so are not included
-    in this comparison. On the other hand, dedicated LAT publications on
-    these sources showed that their morphologies are consistent
-    \citep{rx_j1713_lat,vela_jr_lat}.
-    The LAT
-    extension errors are the statistical and systematic errors added
-    in quadrature. 
-}\label{gev_vs_tev_plot}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/gev_vs_tev_histogram_color.eps}
-    \else
-      \plotone{summary_plots/gev_vs_tev_histogram_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v5/extension_histogram.py
-    \caption{
-    The distributions of the sizes of 18 extended LAT sources
-    at \gev energies
-    (colored blue in the electronic version) and the sizes of the
-    40 extended H.E.S.S. sources at \tev energies
-    (colored red).  
-    The H.E.S.S. sources were fit with a 2D Gaussian surface
-    brightness profile so the LAT and H.E.S.S. sizes were first converted
-    to \rsixeight. 
-    The \gev size of Vela X is taken from \cite{velax}.  
-    Because of their large sizes, the shape of RX\,J1713.7$-$3946 and
-    Vela Jr. were not directly fit at \tev energies
-    and are not included in this comparison.
-    Centaurus A is not included because of its large size.
-    }\label{gev_vs_tev_histogram}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/compare_index_2FGL_color.eps}
-    \else
-      \plotone{summary_plots/compare_index_2FGL_bw.eps}
-    \fi
-    % plot taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_index_2fgl/v3/run.py
-    \caption{
-    The distribution of spectral indices of the 1873 2FGL sources
-    (colored red in the electronic version) and the 21 spatially extended
-    sources (colored blue).  The index of Centaurus A is taken from
-    \cite{second_cat} and the index of Vela X is taken from \cite{velax}.
-    }\label{compare_index_2FGL}
-  \end{figure}
+\bibliography{pwncat2}
 

### 2012-01-19 pwncatalog/PWNCAT2/paper/pwncat2.tex
updating
organization

@@
 
-\author{
-Lots of peple\dots
-}
+\input{authors.tex}
 
 \begin{abstract}
-  Abstract
+  \input{abstract.tex}
 \end{abstract}
@@
 
-Discussion
+\section{sections/discussion.tex}
 
-The \textit{Fermi} LAT Collaboration acknowledges generous ongoing support
-from a number of agencies and institutes that have supported both the
-development and the operation of the LAT as well as scientific data analysis.
-These include the National Aeronautics and Space Administration and the
-Department of Energy in the United States, the Commissariat \`a l'Energie Atomique
-and the Centre National de la Recherche Scientifique / Institut National de Physique
-Nucl\'eaire et de Physique des Particules in France, the Agenzia Spaziale Italiana
-and the Istituto Nazionale di Fisica Nucleare in Italy, the Ministry of Education,
-Culture, Sports, Science and Technology (MEXT), High Energy Accelerator Research
-Organization (KEK) and Japan Aerospace Exploration Agency (JAXA) in Japan, and
-the K.~A.~Wallenberg Foundation, the Swedish Research Council and the
-Swedish National Space Board in Sweden.
-
-Additional support for science analysis during the operations phase is
-gratefully acknowledged from the Istituto Nazionale di Astrofisica in
-Italy and the Centre National d'\'Etudes Spatiales in France.
-
-The authors acknowledge the use of
-HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.
+\section{sections/acknowledgements.tex}
 

### 2012-01-19 pwncatalog/PWNCAT2/paper/sections/acknowledgements.tex
organization

--- 2011-12-18 extended_catalog/paper/extended_catalog.tex
@@
-\documentclass[12pt,preprint]{aastex}
-
-\bibliographystyle{apj}
-
-\newif\ifcolorfigure
-%\colorfiguretrue
-\colorfigurefalse
-
-%#For adding line numbers:
-\usepackage{lineno}
-\linenumbers
-
-%\usepackage{rotating}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{xspace}
-\usepackage{url}
-
-% Note, hyperref has to come after other packages!
-\usepackage{hyperref}
-
-% some units
-\newcommand{\kev}{\text{Kev}\xspace}
-\newcommand{\mev}{\text{MeV}\xspace}
-\newcommand{\gev}{\text{GeV}\xspace}
-\newcommand{\tev}{\text{TeV}\xspace}
-\newcommand{\s}{\text{s}\xspace}
-\newcommand{\ph}{\text{ph}\xspace}
-\newcommand{\cm}{\text{cm}\xspace}
-\newcommand{\km}{\text{km}\xspace}
-\newcommand{\phflux}{\ensuremath{\text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}}\xspace}
-\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
-\newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{2pts}}}\xspace}
-
-\newcommand{\likelihood}{\ensuremath{\mathcal{L}}\xspace}
-
-\newcommand{\chandra}{\text{{\em Chandra}}\xspace}
-\newcommand{\swiftxrt}{\text{{\em Swift}/XRT}\xspace}
-\newcommand{\rosat}{\text{{\em ROSAT}}\xspace}
-\newcommand{\suzaku}{\text{{\em Suzaku}}\xspace}
-\newcommand{\asca}{\text{{\em ASCA}}\xspace}
-\newcommand{\einstein}{\text{{\em Einstein}}\xspace}
-\newcommand{\xmmnewton}{\text{{\em XMM-Newton}}\xspace}
-\newcommand{\fermi}{\textit{Fermi}\xspace}
-
-\newcommand{\rsixeight}{{\ensuremath{\text{r}_{68}}}\xspace}
-
-\newcommand{\tsextpointlike}{\ensuremath{\tsext_{,\pointlike}}\xspace}
-\newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}\xspace}
-
-\newcommand{\ts}{\text{TS}\xspace}
-\newcommand{\glon}{\text{GLON}\xspace}
-\newcommand{\glat}{\text{GLAT}\xspace}
-\newcommand{\altdiff}{\text{alt,diff}\xspace}
-\newcommand{\altpsf}{\text{alt,psf}\xspace}
-\newcommand{\sys}{\text{sys}\xspace}
-\newcommand{\stat}{\text{stat}\xspace}
-
-% the program names
-\newcommand{\gtlike}{\ensuremath{\mathtt{gtlike}}\xspace}
-\newcommand{\pointlike}{\ensuremath{\mathtt{pointlike}}\xspace}
-\newcommand{\gtobssim}{\ensuremath{\mathtt{gtobssim}}\xspace}
-\newcommand{\minuit}{\ensuremath{\mathtt{minuit}}\xspace}
-
-\newcommand{\degree}{^\circ\xspace}
-
-%\newcommand{\newtext}[1]{{\textbf #1}}
-\newcommand{\newtext}[1]{{\bfseries \color{red}#1}}
-
-\usepackage{color}
-
-\begin{document}
-
-\title{Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data}
-\shorttitle{Search for Extended LAT Sources}
-
-\keywords{
-Catalogs;
-Fermi Gamma-ray Space Telescope; 
-Gamma rays: observations; 
-ISM: supernova remnants;
-Methods: statistical;
-pulsar wind nebula
-}
-
-\author{
-J.~Lande\altaffilmark{1,2}, 
-M.~Ackermann\altaffilmark{3,4}, 
-A.~Allafort\altaffilmark{1}, 
-J.~Ballet\altaffilmark{5}, 
-K.~Bechtol\altaffilmark{1}, 
-T.~H.~Burnett\altaffilmark{6}, 
-J.~Cohen-Tanugi\altaffilmark{7}, 
-A.~Drlica-Wagner\altaffilmark{1}, 
-S.~Funk\altaffilmark{1,8}, 
-F.~Giordano\altaffilmark{9,10}, 
-M.-H.~Grondin\altaffilmark{11,12}, 
-M.~Kerr\altaffilmark{1}, 
-M.~Lemoine-Goumard\altaffilmark{13,14}
-}
-\altaffiltext{1}{W.
-W.
-Hansen Experimental Physics Laboratory, Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics and SLAC National Accelerator Laboratory, Stanford University, Stanford, CA 94305, USA}
-\altaffiltext{2}{email: joshualande@gmail.com}
-\altaffiltext{3}{Deutsches Elektronen Synchrotron DESY, D-15738 Zeuthen, Germany}
-\altaffiltext{4}{email: markus.ackermann@desy.de}
-\altaffiltext{5}{Laboratoire AIM, CEA-IRFU/CNRS/Universit\'e Paris Diderot, Service d'Astrophysique, CEA Saclay, 91191 Gif sur Yvette, France}
-\altaffiltext{6}{Department of Physics, University of Washington, Seattle, WA 98195-1560, USA}
-\altaffiltext{7}{Laboratoire Univers et Particules de Montpellier, Universit\'e Montpellier 2, CNRS/IN2P3, Montpellier, France}
-\altaffiltext{8}{email: funk@slac.stanford.edu}
-\altaffiltext{9}{Dipartimento di Fisica ``M. Merlin" dell'Universit\`a e del Politecnico di Bari, I-70126 Bari, Italy}
-\altaffiltext{10}{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70126 Bari, Italy}
-\altaffiltext{11}{Max-Planck-Institut f\"ur Kernphysik, D-69029 Heidelberg, Germany}
-\altaffiltext{12}{Landessternwarte, Universit\"at Heidelberg, K\"onigstuhl, D 69117 Heidelberg, Germany}
-\altaffiltext{13}{Universit\'e Bordeaux 1, CNRS/IN2p3, Centre d'\'Etudes Nucl\'eaires de Bordeaux Gradignan, 33175 Gradignan, France}
-\altaffiltext{14}{Funded by contract ERC-StG-259391 from the European Community}
-
-\begin{abstract}
-Spatial extension is an important characteristic for correctly
-associating $\gamma$-ray-emitting sources with their counterparts at other wavelengths
-and for obtaining an unbiased model of their spectra.  We present a new
-method for quantifying the spatial extension of sources detected by the Large
-Area Telescope (LAT), the primary science instrument on the {\em \fermi
-Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
-simulations to validate this tool and calculate the LAT threshold for
-detecting the spatial extension of sources.  
-We then test all sources
-in the second \fermi-LAT catalog (2FGL) for extension. 
-We report the detection of seven new spatially extended sources.
-\end{abstract}
-
-\section{Introduction}
-
-A number of astrophysical source classes including supernova remnants
-(SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
-and galaxy clusters are expected to be spatially resolvable 
-by the Large Area Telescope (LAT), the primary instrument on the {\em \fermi
-Gamma-ray Space Telescope} (\fermi).
-Additionally, dark matter satellites are also hypothesized to
-be spatially extended. See \cite{atwood_fermi} for pre-launch predictions.
-The LAT has
-detected seven SNRs which are significantly extended
-at \gev energies: 
-W51C, W30, 
-IC~443, W28, W44, RX\,J1713.7$-$3946,
-and the Cygnus Loop
-\citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, 
-three extended PWN have been detected by the LAT: MSH\,15$-$52, Vela~X, and
-HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
-nearby galaxies, the Large and Small Magellanic Clouds, 
-and the lobes of one
-radio galaxy, Centaurus A, were spatially resolved at \gev energies
-\citep{lmc,smc,cen_a_lat}.  A number of additional sources detected
-at \gev energies are positionally coincident with sources that exhibit
-large enough extension at other wavelengths to be spatially
-resolvable by the LAT at \gev energies.
-In particular, there are 59 \gev sources in the second Fermi Source Catalog (2FGL)
-that might be associated with extended SNRs \citep[2FGL][]{second_cat}.
-Previous analyses of extended LAT sources were performed as dedicated
-studies of individual sources so we expect that a systematic scan of
-all LAT detected sources could uncover additional spatially extended
-sources.
-
-The current generation of air Cherenkov detectors have
-made it apparent that many sources can be spatially resolved
-at even higher energies.
-Most
-prominent was a survey of the Galactic plane using the High Energy
-Stereoscopic System (H.E.S.S) which reported 14 spatially extended
-sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
-\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
-sources detected at \tev energies, most notably the $\gamma$-ray binaries
-LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI},
-HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes},
-have no detectable extension.  High-energy $\gamma$-rays from
-\tev sources are produced by the decay of $\pi^0$s produced by hadronic
-interactions with interstellar matter and by relativistic electrons
-due to Inverse Compton (IC) scattering and bremsstrahlung radiation.  
-It is plausible that the \gev and
-\tev emission from these sources originates from the same population of
-high-energy particles and so at least some of these sources should be
-detectable at \gev energies.  Studying 
-these \tev sources at \gev energies would help to
-determine the emission mechanisms producing these high energy photons.
-
-The LAT is a pair conversion telescope that has been surveying the
-$\gamma$-ray sky since 2008 August.  The LAT has broad energy coverage
-(20 \mev to $>300$ \gev), wide field of view ($\sim 2.4$ sr), and large
-effective area ($\sim 8000\ \cm^2$ at $>1$ \gev) 
-Additional information about the performance of the LAT can be found in
-\cite{atwood_LAT_mission}.
-
-Using 2 years of all-sky survey data, the LAT Collaboration published
-2FGL \citep[2FGL][]{second_cat}.
-The possible counterparts of many of these sources can be spatially resolved
-when observed at other frequencies but detecting the spatial extension
-of these sources at \gev energies is difficult because the size of the
-point-spread function (PSF) of the LAT is comparable to the typical size
-of many of these sources.
-
-The capability to spatially resolve \gev $\gamma$-ray
-sources is important for several reasons.  
-Finding a coherent source extension across different energy bands can
-help to associate a LAT source to an otherwise confused counterpart.
-Furthermore, $\gamma$-rays emission from dark matter
-annihilation has been predicted to be detectable by the LAT.
-Some of the dark matter substructure in our Galaxy 
-could be spatially resolvable by the LAT \citep{pre_luanch_dark_matter_fermi}.  
-Characterization of spatial extension could help to identify this substructure.
-Also,
-due to the strong energy dependence of the LAT PSF, the spatial and
-spectral characterization of a source cannot be
-decoupled. An inaccurate
-spatial model will bias the spectral model of the source and vice versa. Specifically,
-modeling a spatially extended source as point-like will systematically
-soften measured spectra. Furthermore, correctly
-modeling source extension is important for 
-understanding an entire region of the sky. For example,
-an imperfect model of the spatially extended LMC introduced
-significant residuals in the surrounding region \citep{first_cat,second_cat}.
-Such residuals can bias the significance and measured spectra of
-neighboring sources in the densely populated Galactic plane.
-
- For these reasons, in Section~\ref{analysis_methods_section}
-we present a new systematic method for analyzing spatially extended
-LAT sources.  In Section~\ref{monte_carlo_validation}, we demonstrate
-that this method can be used to test the statistical significance of the
-extension of a LAT source and in Section~\ref{extension_sensitivity}
-we calculate the LAT detection threshold to resolve the extension
-of a source.  In Section~\ref{dual_localization_method}, we
-study the ability of the LAT to 
-distinguish between a single extended source and unresolved closely-spaced point sources
-In Section~\ref{test_2lac_sources}, we further demonstrate that our
-detection method does not misidentify point-like sources as being
-extended by testing the extension of active Galactic nuclei (AGN)
-believed to be unresolvable.  In Section~\ref{validate_known},
-we systematically reanalyze the twelve extended sources included
-in the 2FGL catalog and in Section~\ref{systematic_errors_on_extension}
-we describe a way to estimate systematic errors on the measured extension of a source.
-In Section~\ref{extended_source_search_method}, we
-describe a search for new spatially extended LAT sources. Finally,
-in Section~\ref{new_ext_srcs_section} we present the detection of the
-extension of nine spatially extended sources that were reported in the 2FGL catalog
-but treated as point-like in the analysis.  Two of these sources have been previously analyzed in
-dedicated publications.
-
-\section{Analysis Methods}
-\label{analysis_methods_section}
-
-Morphological studies of sources using the LAT are challenging
-because of the strongly energy-dependent PSF that is comparable in
-size to the extension of many sources expected to be detected at
-\gev energies.  Additional complications arise for sources along
-the Galactic plane due to systematic uncertainties in the model for
-Galactic diffuse emission.
-
-For energies below $\sim$300~\mev, the angular resolution is limited by
-multiple scattering in the silicon strip tracking section
-of the detector and is several degrees at 100 \mev.  The PSF improves
-with energy approaching a 68\% containment radius of $\sim0\fdg2$ at
-the highest energies (when averaged over the acceptance of the LAT)
-and is limited by the strip pitch to the height of the tracker
-\citep{atwood_LAT_mission,on_orbit_calibration,lat_on_orbit_psf}.\footnote{More
-information about the performance of the LAT can be found at the \fermi
-Science Support Center (FSSC, \url{http://fermi.gsfc.nasa.gov}).} However,
-since most high energy astrophysical sources have spectra that decrease
-rapidly with increasing energy, there are typically fewer higher
-energy photons with improved angular resolution. Therefore sophisticated
-analysis techniques are required to maximize the sensitivity of the LAT
-to extended sources.
-
-\subsection{Modeling Extended Sources in the \pointlike Package}
-
-A new maximum-likelihood analysis tool has been developed to address the
-unique requirements for studying spatially extended sources with the LAT.
-It works by maximizing the Poisson 
-likelihood to detect the observed distributions of gamma rays (referred to as counts)
-given a parametrized spatial and spectral model of the sky.  
-The data are binned spatially, using HEALPix pixellization, and spectrally 
-\citep{healpix} and the likelihood is maximized over all bins in
-a region.
-The extension of a source can be modeled by a geometric shape
-(e.g. a disk or a two-dimensional Gaussian) and the position, extension,
-and spectrum of the source can be simultaneously fit.
-
-This type of analysis is not feasible using the standard LAT likelihood
-analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
-FSSC.} because it can only fit the spectral parameters of the model
-unless a more sophisticated iterative procedure is used.  
-We note that \gtlike has been used in the
-past in several studies of source extension in the LAT Collaboration
-\citep{lmc,smc,w28,w51c}.  In these studies, a 
-set of \gtlike maximum likelihood fits at fixed extensions was used
-to build a profile of the likelihood as a function of extension.
-The \gtlike likelihood profile approach has been shown to correctly
-reproduce the extension of simulated extended sources assuming that the
-true position is known \citep{francesco_2011}.  But it is not optimal
-because the position, extension, and spectrum of the source must be
-simultaneously fit to find the best fit parameters and to maximize the
-statistical significance of the detection.  Furthermore, because the \gtlike
-approach is computationally intensive, no large-scale Monte Carlo
-simulations have been run to calculate its false detection rate.
-
-The approach presented here is based on a second maximum likelihood
-fitting package developed in the LAT Collaboration called \pointlike
-\citep{first_cat,matthew_kerr_thesis}.  The choice to base the
-spatial extension fitting on \pointlike rather than \gtlike was made
-due to considerations of computing time.  The \pointlike algorithm was
-optimized for speed to handle larger numbers of sources efficiently,
-which is important for our catalog scan and for being able
-to perform large-scale Monte Carlo simulations to validate the analysis.
-Details on the \pointlike package can be
-found in \cite{matthew_kerr_thesis}.  We extended the code to allow a
-simultaneous fit of the source extension together with the position and
-the spectral parameters.
-
-\subsection{Extension Fitting}
-\label{extension_fitting}
-
-In \pointlike, one can fit the position and extension 
-of a source under the assumption that the source model
-can be factorized:
-$M(x,y,E)=S(x,y)\times X(E)$, where $S(x,y)$ is the spatial distribution
-and $X(E)$ is the spectral distribution.  To fit an extended source,
-\pointlike convolves the extended source shape with the PSF (as a function
-of energy) and uses the \minuit library \citep{minuit_documentation}
-to maximize the likelihood by simultaneously varying the position,
-extension, and spectrum of the source.  As will be described in
-Section~\ref{monte_carlo_validation}, simultaneously fitting the
-position, extension, and spectrum is important to maximize
-the statistical significance of the detection of the extension of a source.
-To avoid projection effects, the longitude and latitude 
-of the source are
-not directly fit but instead the displacement of the source 
-in a reference frame centered on the source.
-
-The significance of the extension of a source can be calculated from the
-likelihood ratio test of a hypothesis with a spatially extended source and
-a hypothesis with a point-like source. The test statistic (TS) for this procedure
-is defined as
-\begin{equation}
-  \tsext=2\log(\likelihood_\text{ext}/\likelihood_\text{ps}) 
-\end{equation}
-where \likelihood is the Poisson likelihood.
-\pointlike calculates \tsext by fitting a source first with a spatially
-extended model and then as a point-like source.  The interpretation
-of \tsext in terms of a statistical significance is discussed in
-Section~\ref{monte_carlo_validation}.
-
-For extended sources with an assumed radially-symmetric shape,
-we optimized the calculation by performing one
-of the integrals analytically.
-The expected photon 
-distribution can be written as
-\begin{equation}
-  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r' dr' d\phi'
-\end{equation}
-where $\vec r$ represents the position in the sky and
-$I_\text{src}(\vec r)$ is the spatial distribution of the
-source.
-The PSF of the LAT is currently parameterized 
-in the Pass~7\_V6 (P7\_V6) Source Instrument
-Response Function \citep[IRFs,][]{lat_on_orbit_psf} by a King function \citep{king_function}:
-\begin{equation}
-  \text{PSF}(r) = 
-  \frac{1}{2\pi\sigma^2}
-  \left(1-\frac{1}{\gamma}\right)
-  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
-\end{equation}
-where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
-\citep{matthew_kerr_thesis}.  For radially-symmetric extended sources,
-the angular part of the integral can be evaluated analytically
-\begin{align}
-  \text{PDF}(u) & = \int_0^\infty r' dr'
-  I_\text{src}(v) 
-  \int_0^{2\pi} d\phi' 
-  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
-  \\
-  & = \int_0^\infty dv
-  I_\text{src}(v) 
-  \left(\frac{\gamma-1}{\gamma}\right)
-  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
-  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right),
-\end{align}
-where $v=(r'/\sigma)^2/2$ and ${}_2F_1$ is the Gaussian hypergeometric
-function.  This convolution formula reduces the expected photon
-distribution to a single numerical integral.
-
-There will always be a small numerical discrepancy between the expected
-photon distribution derived from a true point-like source and a very small
-extended source due to numerical error in the convolution.  In most
-situations, this error is insignificant.  But in particular for
-very bright sources, this numerical error has the potential to bias the
-TS for the extension test. Therefore, when calculating
-\tsext, we compare the likelihood fitting the source with an extended
-spatial model to the likelihood when the extension is
-fixed to a very small value ($10^{-10}$ degrees in radius 
-for a uniform disk model).
-
-We estimate the error on the extension of a source by fixing
-the position of the source and varying the extension until the
-log of the likelihood has decreased by 1/2, corresponding to a $1\sigma$ error
-\citep{Statistical_methods_book}.  Figure~\ref{four_plots_ic443}
-demonstrates this method by showing the change in the log of the
-likelihood when 
-varying the modeled extension of the SNR IC~443.  The localization
-error is calculated by fixing the extension and spectrum of the source
-to their best fit values and then
-fitting the log of the likelihood to
-a 2D Gaussian as a function
-of position. This localization error algorithm is further described in
-\cite{second_cat}.
-
-\subsection{\gtlike Analysis Validation}
-\label{gtlike_crosscheck}
-
-\pointlike is important for LAT analyses that require many iterations
-such as source localization and extension fitting.  On the other hand,
-because \gtlike makes fewer approximations in calculating the likelihood
-we expect the spectral parameters found with \gtlike to be slightly more
-accurate.  Furthermore, because \gtlike is the 
-standard likelihood analysis package for LAT data, 
-it has been more extensively validated for spectral analysis.
-For those reasons, in the following analysis we used \pointlike to
-determine the position and extension of a source and subsequently derived
-the spectrum using \gtlike. Both \gtlike and \pointlike can be used to
-estimate the statistical significance of the extension of a source and we
-required that both methods agree for a source to be considered extended.
-There was good agreement between the two methods.  Unless explicitly
-mentioned, all \ts, \tsext, and spectral parameters were calculated using
-\gtlike with the best-fit positions and extension found by \pointlike.
-
-\subsection{Comparing Source Sizes}
-
-\label{compare_source_size}
-
-We considered two models for the
-surface brightness profile for extended sources: a 2D Gaussian model
-\begin{equation}\label{gauss_pdf}
-  I_\text{Gaussian}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
-\end{equation}
-or a uniform disk model
-\begin{equation}\label{disk_pdf}
-  I_\text{disk}(x,y)=
-  \begin{cases}
-    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
-    0                      & x^2+y^2>\sigma^2.
-  \end{cases}
-\end{equation}
-Although these shapes are significantly different,
-Figure~\ref{compare_disk_gauss} shows that, after convolution with the
-LAT PSF, their PDFs are similar for a source that has a 0\fdg5 radius
-typical of LAT detected extended sources.  To allow a valid comparison
-between the Gaussian and the uniform disk models,
-we define the source size as the radius containing 68\% of the
-intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
-and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$ is defined
-in Equation~\ref{gauss_pdf} and Equation~\ref{disk_pdf} respectively.
-For this example, $\rsixeight=0\fdg5$ so $\sigma_\text{disk}=0.61\degree$
-and $\sigma_\text{Gaussian}=0.33\degree$.
-
-For sources that are comparable in size to the PSF,
-the differences in the PDF for
-different spatial models are lost in the noise and the LAT is not sensitive
-to the detailed spatial structure of these sources.  Therefore, in our
-search for extended sources we use only a radially-symmetric uniform
-disk spatial model. Unless otherwise noted,
-we quote the radius to the edge ($\sigma$) as the size of the source.
-
-\section{Validation of the Analysis Method}
-\label{monte_carlo_validation}
-
-We evaluated the false detection probability for the measurement of source extent
-by fitting the extensions of point-like sources.  \cite{mattox_egret}
-discuss that the TS distribution for a likelihood ratio test
-on the existence of a source at a given position is
-\begin{equation}\label{ts_ext_distribution}
-  P(\ts)=\onehalf(\chi^2_1(\ts)+\delta(\ts)).
-\end{equation}
-The particular form of Equation \ref{ts_ext_distribution} is due to the
-null hypothesis (source flux $\Phi=0$) residing on the edge of parameter
-space and the model hypothesis adding a single degree of freedom.
-It leads to the often quoted result $\sqrt{TS}=\sigma$, where 
-$\sigma$ here refers to the significance of the detection. It is plausible
-to expect a similar distribution for the TS in the test for
-source extension since the same conditions apply (with the source flux
-$\Phi$ replaced by the source radius $r$ and $r<0$ being unphysical).
-To verify Equation~\ref{ts_ext_distribution}, we evaluated the
-empirical distribution function of \tsext computed from simulated sources.
-
-We simulated point-like sources with various spectral forms using
-the LAT on-orbit simulation tool
-\gtobssim\footnote{\gtobssim is distributed publicly by the FSSC.} and fit the sources
-with \pointlike using both point-like
-and extended source hypotheses.  These point-like sources were simulated with a power-law
-spectral model with integrated fluxes above 100 \mev ranging from $3\times10^{-9}$ 
-to $1\times10^{-5}$ \phflux and spectral
-indices ranging from 1.5 to 3.  These values
-were picked to represent typical parameters of LAT-detected
-sources. The point-like sources were simulated on top of an isotropic
-background with a power-law spectral model with
-integrated flux above 100 \mev of $1.5\times10^{-5}$ \phflux sr$^{-1}$
-and spectral index 2.1.
-This was
-taken to be the same as the isotropic spectrum measured by EGRET
-\citep{sreekumar_isotropic}.  This spectrum is comparable
-to the high-latitude background intensity seen by the LAT.
-The Monte Carlo simulation was performed
-over a one-year observation period using a representative 
-spacecraft orbit and livetime.
-The reconstruction was performed
-using the P7\_V6 Source class event selection and IRFs \citep{lat_on_orbit_psf}. For each 
-significantly detected point-like source ($\ts\ge25$), we used \pointlike
-to fit the source as an extended source and calculate \tsext.
-This entire procedure was performed twice, once fitting in the 1 \gev
-to 100 \gev energy range and once fitting in the 10 \gev to 100 \gev
-energy range.
-
-For each set of spectral parameters, $\sim20,000$ statistically independent
-simulations were performed. For dimmer spectral models, many of the
-simulations left the source insignificant ($\ts<25$)
-and were discarded.  Table~\ref{ts_ext_num_sims}
-shows the different spectral models used in our study as well as the
-number of simulations and the average point-like source
-significance.  The cumulative density of \tsext is plotted in
-Figures~\ref{ts_ext_mc_1000} and \ref{ts_ext_mc_10000} 
-and compared to the $\chi^2_1/2$ distribution of
-Equation~\ref{ts_ext_distribution}.
-
-Our study shows broad agreement between simulations and
-Equation~\ref{ts_ext_distribution}. To the extent that there is
-a discrepancy, the simulations tended to produce smaller than expected
-values of \tsext which would make the formal significance conservative.
-Considering the distribution in Figures~\ref{ts_ext_mc_1000} and
-\ref{ts_ext_mc_10000}, the choice of a threshold \tsext set to 16
-(corresponding to a formal $4\sigma$ significance) is reasonable.
-
-\section{Extended Source Detection Threshold}
-\label{extension_sensitivity}
-
-We calculated the LAT flux 
-threshold to detect spatial extent. We define the detection threshold as the flux at
-which the value of $\tsext$ averaged over many statistical realizations is
-$\langle\tsext\rangle=16$ 
-(corresponding to a formal $4\sigma$ significance)
-for a source of a given extension.
-
-We used a simulation setup similar to that described in
-Section~\ref{monte_carlo_validation}, but instead of point-like sources
-we simulated extended sources with radially-symmetric uniform disk spatial 
-models. Additionally, we simulated our sources over the two-year
-time range included in the 2FGL catalog.  For each extension and spectral index,
-we selected a flux range which bracketed $\tsext=16$ and performed an
-extension test for $>100$ independent realizations of ten fluxes in
-the range.  We calculated $\langle\tsext\rangle=16$ by fitting a line
-to the flux and $\tsext$ values in the narrow range.
-
-Figure~\ref{index_sensitivity} shows the threshold for sources of four
-spectral indices from 1.5 to 3 and extensions varying from $\sigma=0\fdg1$
-to $2\fdg0$.  
-The threshold is high for small extensions when the
-source is 
-small compared to the size of the PSF. 
-It drops quickly with increasing source size and reaches
-a minimum around 0\fdg5. 
-The threshold increases
-for large extended sources because the source becomes
-increasingly diluted by the background.
-Figure~\ref{index_sensitivity} shows
-the threshold using photons with energies between 100 \mev and 100 \gev
-and also using only photons with energies between 1 \gev and 100 \gev.
-Except for very large or very soft
-sources, the threshold is
-not substantially improved by including photons with energies between 100 \mev and
-1 \gev.  This is also demonstrated in Figure~\ref{four_plots_ic443}
-which shows \tsext for the SNR IC~443 computed independently in twelve
-energy bins between 100 \mev and 100 \gev. For IC~443, which has a
-spectral index $\sim2.4$ and an extension $\sim0\fdg35$, 
-almost the entire 
-increase in likelihood from optimizing the source extent in the model
-comes
-from energies above 1 \gev.  Furthermore, other systematic errors
-become increasingly large at low energy. For our extension search
-(Section~\ref{extended_source_search_method}),
-we therefore used only photons with energies above 1 \gev.
-
-Figure~\ref{all_sensitivity} shows the flux threshold as a function of
-source extension for different background levels ($1\times$, $10\times$,
-and $100\times$ the nominal background), different spectral indices,
-and two different energy ranges (1 \gev to 100 \gev and 10 \gev to
-100 \gev).  The detection threshold is higher for sources in regions of
-higher background.  When studying sources only at energies above 1 \gev,
-the LAT detection threshold (defined as the 1 \gev to 100 \gev flux at
-which $\langle\tsext\rangle=16$) depends less strongly on the 
-spectral index of the source. 
-The index dependence of the detection threshold is
-even weaker when considering only photons with energies above 10 \gev
-because the PSF changes little from 10 \gev to 100 \gev.
-Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
-sources that will be discussed in Sections~\ref{validate_known} and
-\ref{new_ext_srcs_section}.  The extension thresholds are tabulated in
-Table~\ref{all_sensitivity_table}.
-
-Finally, Figure~\ref{time_sensitivity} shows the projected
-detection threshold of the LAT to extension with a 10 year
-exposure against 10 times
-the isotropic background measured by EGRET. This background is
-representative of the background near the Galactic plane.  For small
-extended sources, the threshold improves by a factor larger
-than the square root of the relative exposures because the LAT is signal-limited
-at high energies where the present analysis is most sensitive. For large
-extended sources, the relevant background is over a larger spatial range
-and so the improvement is closer to a factor corresponding
-to the square root of the relative exposures and is caused by Poisson fluctuations in the background.
-
-\section{Testing Against Source Confusion}
-\label{dual_localization_method}
-
-It is impossible to discriminate using only LAT data between a
-spatially extended source and multiple point-like sources separated by
-angular distances comparable to or smaller than the size of the LAT PSF.
-To assess the plausibility of source confusion for situations
-in which $\tsext\ge16$, we developed an algorithm in \pointlike to
-simultaneously fit the positions and spectra of two point-like sources.
-
-After simultaneously fitting the two positions and two spectra,
-we define \tsinc as twice the increase in the log of the likelihood
-fitting the region with two point-like sources compared to fitting the
-region with one point-like source:
-\begin{equation}
-  \tsinc=2\log(\likelihood_\text{2pts}/\likelihood_\text{ps}).
-\end{equation} 
-For the following analysis of LAT data, \tsinc was computed
-by fitting the spectra of the two point-like sources in \gtlike using the best fit positions
-of the sources found by \pointlike.
-
-\tsinc cannot be quantitatively compared to \tsext using a simple
-likelihood ratio test to evaluate which model is significantly better
-because the models are not nested \citep{statistics_with_care}.
-Even though the comparison of \tsext with \tsinc is not a calibrated
-test, $\tsext>\tsinc$ indicates that the likelihood for the extended
-source hypothesis is higher than for two point-like sources and we only
-consider a source to be extended if $\tsext>\tsinc$.
-
-We assessed the power of the $\tsext>\tsinc$ test with a Monte Carlo
-study.  We simulated one spatially extended source and fit it as both
-an extended source and as two point-like sources using \pointlike.
-We then simulated two point-like sources and fit them with the same two
-hypotheses. By comparing the distribution of \tsinc and \tsext computed by
-\pointlike for the two cases, we evaluated how effective the $\tsext>\tsinc$
-test is at rejecting cases of source confusion as well as how
-likely it is to incorrectly reject that an extended source is spatially
-extended.  All sources were simulated using the same time range as in
-Section~\ref{extension_sensitivity} against a background 10 times the
-isotropic background measured by EGRET, representative of the background
-near the Galactic plane.
-
-We did this study first in the energy range from 1 \gev to 100 \gev by
-simulating extended sources of flux $4\times10^{-9}$ \phflux integrated
-from 1 \gev to 100 \gev and a power-law spectral model with
-spectral index 2.  This spectrum was picked to be representative of the
-new extended sources that were discovered in the following analysis
-when looking in the 1 \gev to 100 \gev energy range
-(see Section~\ref{new_ext_srcs_section}).
-We simulated these sources using uniform disk spatial models
-with extensions varying
-up to $1\degree$.  
-Figure~\ref{confusion_extended_plot}a shows the distribution
-of \tsext and \tsinc and 
-Figure~\ref{confusion_extended_plot}c shows 
-the distribution of $\tsext-\tsinc$ as a
-function of the simulated extension of the source
-for 200 statistically independent simulations.
-
-Figure~\ref{confusion_2pts_plot}a shows the same plot but when fitting
-two simulated point-like sources each with half of the flux of
-the spatially extended source and with the same spectral index as the
-extended source.  Finally, Figure~\ref{confusion_2pts_plot}c shows the same
-plot with each point-like source having the same flux but different
-spectral indices.  One point-like source had a spectral index of 1.5
-and the other an index of 2.5.
-These indices are representative of the range of indices of LAT-detected
-sources.
-
-The same four plots are shown in Figure~\ref{confusion_extended_plot}b, \ref{confusion_extended_plot}d, 
-\ref{confusion_2pts_plot}b, and \ref{confusion_2pts_plot}d but this
-time when analyzing a source of flux $10^{-9}$ \phflux (integrated from
-10 \gev to 100 \gev) only in the 10 \gev to 100 \gev energy range.
-This flux is typical of the new extended sources discovered
-using only photons with energies between 10 \gev and 100 \gev (see
-Section~\ref{new_ext_srcs_section}).
-
-Several interesting conclusions can be made from this study.  As one would
-expect, $\tsext-\tsinc$ is mostly positive when fitting the simulated
-extended sources.  In the 1 \gev to 100 \gev analysis, only 11 of the
-200 simulated extended sources had $\tsext>16$ but were incorrectly
-rejected due to \tsinc being greater than \tsext.  In the 10 \gev to 100 \gev
-analysis, only 7 of the 200 sources were incorrectly rejected. From this,
-we conclude that this test is unlikely to incorrectly reject truly
-spatially extended sources.
-
-On the other hand, 
-it is often
-the case that $\tsext>16$ when testing the 
-two simulated point-like sources
-for extension.  This is especially the case
-when the two sources had the same spectral index. Forty out of 200 sources
-in the 1 \gev to 100 \gev energy range and 43 out of 200 sources in the
-10 \gev to 100 \gev energy range had $\tsext>16$.  But in these cases,
-we always found the single extended source fit to be worse than
-the two point-like source fit.  From this, we conclude that the $\tsext>\tsinc$
-test is powerful at discarding cases in which the true emission comes
-from two point-like sources.
-
-The other interesting feature in Figure~\ref{confusion_extended_plot}a
-and \ref{confusion_extended_plot}b is that for simulated extended
-sources with typical sizes ($\sigma\sim0\fdg5$), one can often obtain
-almost as large an increase in likelihood fitting the source as two
-point-like sources ($\tsinc\sim\tsext$).  This is because although the
-two point-like sources represent an incorrect spatial model, the second
-source has four additional degrees of freedom (two spatial and two
-spectral parameters) and can therefore easily model much of the extended
-source and statistical fluctuations in the data.  This effect is most
-pronounced when using photons with energies between 1 \gev and 100 \gev
-where the PSF is broader.
-
-From this Monte Carlo study, we can see the limits of a LAT analysis
-of spatially extended sources.  Section~\ref{monte_carlo_validation}
-showed that we have a statistical test that finds when a LAT source is
-not well described by the PSF.  But this test does not uniquely prove
-that the emission originates from spatially extended emission instead
-of from multiple unresolved sources.  Demanding that $\tsext>\tsinc$
-is a powerful second test to avoid cases of simple confusion of two
-point-like sources. But it could always be the case that an extended
-source is actually the superposition of multiple point-like or
-extended sources that could be resolved with deeper observations of the
-region.  There is nothing about this conclusion unique to LAT analysis,
-but the broad PSF of the LAT and the density of sources expected to be
-\gev emitters in the Galactic plane makes this issue more significant
-for LAT analysis.  When possible, multiwavelength information should be
-used to help select the best model of the sky.
-
-\section{Test of 2LAC Sources}
-\label{test_2lac_sources}
-
-For all following LAT analyses, we used the same two-year dataset
-that was used in the 2FGL catalog spanning from 2008 August 4 to 2010 August 1. We
-applied the same acceptance cuts and we used the same P7\_V6 Source class
-event selection and IRFs \citep{lat_on_orbit_psf}.  
-When analyzing sources in \pointlike, we used a circular $10\degree$ region of
-interest (ROI) centered on our source and eight energy bins per
-logarithmic decade in energy.
-When refitting the region in \gtlike using the best fit spatial and
-spectral models from \pointlike, we used the `binned likelihood' mode of
-\gtlike on a $14\degree\times14\degree$ ROI with a pixel size of 0\fdg03.
-
-Unless explicitly
-mentioned, we used the same background model as 2FGL to represent the
-Galactic diffuse, isotropic, and Earth limb emission.  To compensate for
-possible residuals in the diffuse emission model, the Galactic emission
-was scaled by a power-law and the normalization
-of the isotropic component
-was left free.  
-Unless explicitly mentioned,
-we used all 2FGL sources within $15\degree$ of our source as our list
-of background sources and we refit the spectral parameters of all sources
-within $2\degree$ of the source.
-
-To validate our method, we tested LAT sources associated with AGN for
-extension.  \gev emission from AGN is believed to originate from collimated jets.  Therefore AGN are
-not expected to be spatially resolvable by the LAT and provide a good
-calibration source to demonstrate that our extension detection method
-does not misidentify point-like sources as being extended.  We note that
-megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
-to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
-halo has been discovered in the LAT data so far \citep{neronov_agn_halo}.
-
-Following 2FGL, the LAT Collaboration published the Second LAT AGN
-Catalog (2LAC), a list of high latitude ($|b|>10\degree$) sources
-that had a high probability association with AGN \citep{second_agn_cat}.
-2LAC associated 1016 2FGL sources with AGN.  To avoid systematic problems
-with AGN classification, we selected only the 885 AGN which made it into
-the clean AGN sub-sample defined in the 2LAC paper.  An AGN association is considered clean only
-if it has a high probability of association $P\ge 80\%$, if it is the
-only AGN associated with the catalog source, and if 
-no analysis flags have been set for the source
-in the 2FGL catalog. These last two conditions are important for our
-analysis. Source confusion may look like a spatially extended source
-and flagged catalog sources may correlate with unmodeled structure in
-the diffuse emission.
-
-Of the 885 clean AGN, we selected the 733 of these 2FGL sources which
-were significantly detected above 1 \gev and fit each of them for
-extension.  The cumulative density of \tsext for these AGN is compared
-to the $\chi^2_1/2$ distribution of Equation~\ref{ts_ext_distribution}
-in Figure~\ref{agn_ts_ext}.  The \tsext distribution
-for the AGN shows reasonable agreement with the theoretical
-distribution and no AGN was found to be significantly extended
-($\tsext>16$).  The observed discrepancy from the theoretical
-distribution is likely due to small systematics
-in our model of the LAT PSF and the Galactic diffuse emission (see
-Section~\ref{systematic_errors_on_extension}).  
-The discrepancy could
-also in a few cases be due to confusion with a nearby undetected source.
-We note that the Monte Carlo study
-of section~\ref{monte_carlo_validation} effectively used perfect
-IRFs and a perfect model of the sky.
-The overall agreement with the expected distribution demonstrates that
-we can use \tsext as a measure of the statistical significance of the
-detection of the extension of a source.
-
-We note that the LAT PSF used in this study was determined
-empirically by fitting the distributions of gamma rays around bright AGN (see
-Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
-test are not extended is not surprising.  This validation analysis is
-not suitable to reject any hypotheses about the existence of megaparsec-scale
-halos around AGN.
-
-\section{Analysis of Extended Sources Identified in the 2FGL Catalog}
-\label{validate_known}
-
-As further validation of our method for studying
-spatially extended sources, we reanalyzed the twelve spatially extended
-sources which were included in the 2FGL catalog \citep{second_cat}.  
-Even though these sources had all been the subjects of dedicated
-analyses and separate publications, and had been fit with a variety
-of spatial models,
-it is valuable to show that
-these sources are significantly extended using our systematic 
-method assuming radially-symmetric uniform disk spatial models.  On the other hand, for some of
-these sources a uniform disk spatial model does not well describe the
-observed extended emission and so the dedicated LAT 
-publications provide better models of these sources.
-
-% 6 SNRs
-
-Six extended SNRs were
-included in the 2FGL catalog: W51C, IC~443, W28, W30, W44, the Cygnus Loop,
-and W30
-\citep{w51c,ic443,w28,w44,cygnus_loop_lat,w30_lat}.
-Using photons
-with energies between
-1 \gev and 100 \gev, our analysis significantly detected
-that these six SNRs are spatially extended.
-
-% 2 galaxies
-
-Two nearby satellite galaxies of the Milky Way the Large Magellanic Cloud (LMC)
-and the Small Magellanic
-Cloud (SMC) were included in the 2FGL catalog as spatially extended sources \citep{lmc,smc}.  
-Their extensions were significantly
-detected using photons with energies between
-1 \gev and 100 \gev. Our
-fit extensions are comparable to the published result, but we note that
-the previous LAT Collaboration publication on the LMC used a more complicated two 2D Gaussian surface
-brightness profile when fitting it \citep{lmc}.
-
-% 3 PWN
-Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137, were fit as
-extended sources in the 2FGL analysis \citep{msh1552,velax,fermi_hess_j1825}.  
-In the present analysis, HESS\,J1825$-$137
-was significantly detected using photons with energies between 10
-\gev and 100 \gev.  To avoid confusion with the nearby bright pulsar
-PSR\,J1509$-$5850, MSH\,15$-$52 had to be analyzed at high energies.
-Using photons with energies above 10 \gev, we fit the extension of
-MSH\,15$-$52 to be consistent with the published size but with \tsext=6.6.
-
-% failed to detect vela x + cen a
-Our analysis was unable to resolve Vela X which would have required first
-removing the pulsed photons from the Vela pulsar which was beyond the
-scope of this paper.  Our analysis also failed to detect a significant
-extension for the Centaurus A Lobes because
-the shape of the source is significantly different from a uniform
-radially-symmetric disk\citep{cen_a_lat}.
-
-Our analysis of these sources is summarized in
-Table~\ref{known_extended_sources}.  This table includes the best fit
-positions and extensions of these sources when fitting them 
-with a radially-symmetric uniform disk model. It also
-includes the best fit spectral parameters for each source.  The positions
-and extensions of Vela X and the Centaurus A Lobes were taken from
-\cite{velax,cen_a_lat} and are included in this table for completeness.
-
-\section{Systematic Errors on Extension}
-\label{systematic_errors_on_extension}
-
-% Alternative PSF
-
-We developed two criteria for estimating systematic errors
-on the extensions of the sources.
-First, we estimated a systematic error due to
-uncertainty in our knowledge of the LAT PSF.  
-Before launch, the LAT PSF
-was determined by detector simulations which were verified in accelerator
-beam tests \citep{atwood_LAT_mission}. However, in-flight data revealed
-a discrepancy above 3 \gev in the PSF compared to the angular
-distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
-Subsequently, the PSF was fit empirically to bright AGN and this
-empirical parameterization is used in the P7\_V6 IRFs.  To account for
-the uncertainty in our knowledge of the PSF, we refit our extended source
-candidates using the pre-flight Monte Carlo representation of the PSF
-and consider the difference in extension found using the two PSFs as a
-systematic error on the extension of a source.  The same approach was used
-in \cite{ic443}.  we believe that our parameterization
-of the PSF from bright AGN is substantially better than the Monte Carlo
-representation of the PSF so this systematic error is conservative.
-
-% Alternative Diffuse Model
-
-We estimated a second systematic error on the extension of a source
-due to uncertainty in our model of the Galactic diffuse emission by
-using an alternative 
-approach to modeling the diffuse emission
-which takes as input templates
-calculated by
-GALPROP\footnote{GALPROP is a software package for calculating the
-Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
-in the Galaxy and maps of the distributions of the 
-components of the interstellar medium \citep{galprop1998,galprop2011}. 
-See also \url{http://galprop.stanford.edu/} for details.} 
-but then fits each template locally in
-the surrounding region.
-The particular GALPROP model that was used as input is described in
-the LAT analysis of the isotropic diffuse
-emission \citep{isotropic_lat}.  
-The intensities of various components
-of the Galactic diffuse emission were fitted individually using a
-spatial distribution predicted by
-the model.  We distinguished contributions from cosmic-ray interactions with the
-molecular hydrogen, the atomic and ionized hydrogen, residual gas traced
-by dust \citep{isabelle_dark_gass}, and the interstellar radiation
-field. We further split the contributions from interactions with molecular
-and atomic hydrogen to the Galactic diffuse emission according to the
-distance from the Galactic center in which they are produced. Hence, we
-replaced the standard diffuse emission model by 18 individually fitted
-templates to describe individual components of the diffuse emission.
-A similar crosscheck was used in an analysis of RX\,J1713.7$-$3946 
-by the LAT Collaboration \citep{rx_j1713_lat}.
-
-It is not expected that this diffuse model is superior to the standard
-LAT model obtained through an all-sky fit.  However, adding degrees of
-freedom to the background model can remove likely spurious sources that
-correlate with features in the Galactic diffuse emission.  Therefore,
-this tests systematics that may be due to imperfect modeling of the
-diffuse emission in the region. Nevertheless, 
-this alternative approach to modeling the diffuse emission
-does not test all systematics related to the diffuse emission model.
-In particular, because the alternative approach uses the same underlying gas
-maps it is unable to be used to assess systematics due to mischaracterization of local
-diffuse structure due to lack of resolution of the underlying maps.
-
-We do not expect the systematic error due to uncertainties in the PSF
-to be correlated with the systematic error due to uncertainty in the
-Galactic diffuse emission. Therefore, the total systematic error on the
-extension of a source was obtained by adding the two errors in quadrature.
-
-There is another systematic error on the size of a source due to issues
-modeling nearby sources in crowded regions of the sky. It is beyond the
-scope of this paper to address this systematic error. Therefore, 
-for sources in crowded regions the systematic
-errors quoted in this paper may not be the full systematics of this
-analysis.
-
-\section{Extended Source Search Method}
-\label{extended_source_search_method}
-
-Having demonstrated that we understand the statistical
-issues associated with analyzing spatially extended sources
-(Section~\ref{monte_carlo_validation} and~\ref{test_2lac_sources}) and
-that our method can correctly analyze the extended sources included in
-2FGL (Section~\ref{validate_known}), we applied this method to search for
-new spatially extended \gev sources.
-The data and general analysis setting is as described in Section~\ref{test_2lac_sources}.
-
-Ideally, we would apply a completely blind and uniform search that
-tests the extension of each catalog source in the presence of all other
-2FGL sources to find a complete list of all spatially extended sources.
-As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
-Galactic latitude where the source density is not as large and the
-diffuse emission is less structured, this method works well.
-
-But this is infeasible in the Galactic plane where we most likely expect
-to discover new spatially extended sources.  In the Galactic plane,
-this analysis is challenged by our imperfect model of the diffuse
-emission and by an imperfect model of nearby sources.  The Monte Carlo
-study in Section~\ref{dual_localization_method}
-showed that the overall likelihood would greatly increase by fitting
-a spatially extended source as two point-like sources so we expect
-that spatially extended sources would be modeled in the 2FGL catalog as
-multiple point-like sources. Furthermore, the positions of other nearby sources
-in the region close to an extended source could be biased by not correctly
-modeling the extension of the source.  Since 2FGL produced a
-list of sources significant at energies above 100 \mev whereas we are
-most sensitive to spatial extension at higher energies,
-we also expect that at higher energies our analysis would be complicated
-by 2FGL sources no longer significant and by 2FGL
-sources whose positions were biased by diffuse emission at lower energies.
-
-To account for these issues, we first produced a large list of possibly
-extended sources employing very liberal search criteria and then
-refined the analysis of the promising candidates on a case by case basis.
-Our strategy was to test all point-like 2FGL sources for extension assuming
-they had a uniform radially-symmetric disk spatial model
-and a power-law spectral model.  Although not all extended sources are
-expected to have a shape very similar to a uniform disk, Section~\ref{compare_source_size} showed that for many spatially
-extended sources the wide PSF of the LAT and limited statistics makes
-this a reasonable approximation.  On the other hand, choosing this
-spatial model biases us against finding extended sources that are not
-well described by a uniform disk model such as shell-type SNRs.
-
-Before testing for extension, we automatically removed from the background
-model all other 2FGL sources within 0\fdg5 of the source.  This distance
-is somewhat arbitrary, but was picked in hopes of finding extended
-sources with sizes on the order of $\sim1\degree$ or smaller. On the
-other hand, by removing these nearby background sources we expect to
-also incorrectly add to our list of extended source candidates
-point-like sources that
-are confused with nearby sources.  To screen out obvious cases of source
-confusion, we performed the dual localization procedure described in
-Section~\ref{dual_localization_method} to compare the extended source
-hypothesis to the hypothesis of two independent point-like sources.
-
-As was shown in Section~\ref{extension_sensitivity}, little sensitivity is gained by
-using photons with energies below 1 \gev. On the other hand,
-the broad PSF at low energy makes the analysis more susceptible to systematic
-errors arising from source confusion due to nearby soft point-like sources
-and by uncertainties in our modeling of the Galactic diffuse emission. 
-For that reason,
-we performed our search using only photons with energies between 1 \gev
-and 100 \gev.
-
-We also performed a second search for extended sources using only
-photons with energies between 10 \gev and 100 \gev.  Although this
-approach tests the same sources, it is complementary because the Galactic
-diffuse emission is even less dominant above 10 \gev and because source
-confusion is less of an issue.  A similar procedure was used to detect
-the spatial extensions of MSH\,15$-$52 and
-HESS\,J1825$-$137 with the LAT \citep{msh1552,fermi_hess_j1825}.
-
-When we applied this test to the 1861 point-like sources in the 2FGL catalog, our
-search found 117 extended source candidates in the 1 \gev to 100 \gev
-energy range and 11 extended source candidates in the 10 \gev to 100
-\gev energy range. Most of the extended sources found above 10 \gev were
-also found above 1 \gev and in many cases multiple nearby point-like
-sources were found to be extended even though they fit the same emission region.
-For example, the sources 2FGL\,J1630.2$-$4752, 2FGL\,J1632.4$-$4753c 2FGL\,J1634.4$-$4743c,
-and 2FGL\,J1636.3$-$4740c were all found to be spatially extended in the
-10 \gev to 100 \gev energy range even though they all fit to similar
-positions and sizes.  For these situations, we manually discarded all
-but one of the 2FGL sources.
-
-Similarly, many of these sources were confused with nearby
-point-like sources or influenced by large-scale residuals in the
-diffuse emission.  To help determine which of these fits found
-truly extended sources and when the extension was
-influenced by source confusion and diffuse emission, we generated a
-series of diagnostic plots.  For each candidate, we generated a map
-of the residual TS by adding a new point-like source of spectral index 2 into the
-region at each position and finding the increase in likelihood when fitting
-its flux. Figure~\ref{res_tsmaps} shows this map around the
-most significantly extended source IC~443 when it is modeled both as a
-point-like source and as an extended source.  The residual TS
-map indicates
-that the spatially extended model for IC~443 is a significantly better
-description of the observed photons and that there is no significant
-residual in the region after modeling the source as being spatially extended.
-We also generated plots of the sum of all counts within a given distance of
-the source and compared them to the model predictions assuming the emission
-originated from a point-like source.  An example radial integral plot
-is shown for the extended source IC~443 in Figure~\ref{four_plots_ic443}.
-For each source, we also made diffuse-emission-subtracted smoothed counts
-maps (shown for IC~443 in Figure~\ref{four_plots_ic443}).
-
-We found by visual inspection that in many
-cases our results were strongly influenced by large-scale residuals in the
-diffuse emission and hence the extension measure was unreliable.  This was
-especially true in our analysis of sources in the 1 \gev to 100 \gev
-energy range.  An example of such a case is 2FGL\,J1856.2+0450c analyzed
-in the 1 \gev to 100 \gev energy range. Figure~\ref{example_bad_fit}
-shows a diffuse-emission-subtracted smoothed counts map for
-this source with the best
-fit extension of the source overlaid. There appear to be large-scale
-residuals in the diffuse emission in this region along the Galactic plane.
-As a result, 2FGL\,J1856.2+0450c is fit to an extension of $\sim2\degree$
-and the result is statistically significant with \tsext=45.4. However,
-by looking at the residuals it is clear that this complicated region is
-not well modeled. We manually discard sources like this.
-% information came from
-% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
-% (2FGL J1856.2+0450c = P72Y3047 for)
-
-We only selected extended source
-candidates in regions that did not appear dominated by these issues and
-where there was a multiwavelength
-counterpart. Because of these systematic issues, this search can not be
-expected to be complete and it is likely that there are other spatially
-extended sources that this method missed.
-
-For each candidate that was not biased by neighboring point-like
-sources or by large-scale residuals in the diffuse emission model, we
-improved the model of the region by deciding on a case by case basis which
-background point-like sources should be kept.  We kept in our model the
-sources that we
-believed represented physically distinct sources and we removed 
-sources that we believed were included in the 2FGL catalog to compensate
-for residuals induced by not modeling the extension of the source.
-Soft nearby point-like 2FGL sources that were not significant at higher energies
-were frozen to the spectras predicted by 2FGL.
-When deciding
-which background sources to keep and which to remove, we used as much as possible
-multiwavelength information about possibly extended source counterparts
-to help guide our choice. For each extended source presented in 
-Section~\ref{new_ext_srcs_section}, we describe any modifications from 2FGL
-of the background model that were performed.
-
-The best fit positions of nearby point-like sources can be influenced by
-the extended source and vice versa.  Similarly,
-the best fit positions of nearby point-like sources in the 2FGL catalog can be biased
-by systematic issues at lower energies.
-Therefore, after selecting the list of background sources, we iteratively
-refit the positions and spectra of nearby background sources as well as
-the positions and extensions of the analyzed spatially extended
-sources until the overall fit converged globally.  For each extended
-source, we will describe the positions of any relocalized background
-sources.
-
-After obtaining the overall best fit positions and extensions of all
-of the sources in the region using \pointlike, we refit the spectral
-parameters of the region using \gtlike.  With \gtlike, we obtained a
-second measure of \tsext.  We only consider a source to be extended when
-both \pointlike and \gtlike agree that $\tsext>16$. 
-We further required that $\tsext>16$ using the 
-alternative approach to modeling the diffuse emission
-presented in Section~\ref{systematic_errors_on_extension}.
-We then replaced the spatially extended source with two point-like
-sources and refit the positions and spectra of the
-two point-like sources to calculate \tsinc.
-We only consider a source to be spatially extended, instead of being
-the result of confusion of two point-like sources, if $\tsext>\tsinc$.
-As was shown in Section~\ref{dual_localization_method}, this test is
-fairly powerful at removing situations in which the emission actually
-originates from two distinct point-like sources instead of one spatially
-extended source.  On the other hand, it is still possible that longer
-observations could resolve additional structure or new sources 
-that the analysis cannot currently detect. 
-Considering the very complicated morphologies
-of extended sources observed at other wavelengths and the high density
-of possible sources that are expected to emit at \gev energies, it is
-likely that in some of these regions further observations will reveal
-that the emission is significantly more complicated than the simple
-radially-symmetric uniform disk model that we assume.
-
-\section{New Extended Sources}
-\label{new_ext_srcs_section}
-
-% Notes about extended Catalog sources
-% Catalog used for analysis is P72Y_uw23.fits
-% Compare to final catalog gll_psc_v04.fit
-%          1FGL Name - Preliminary 2FGL - 2FGL Name
-% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-
-% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 
-% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
-% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
-% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
-% N/A                - P72Y1287         - 2FGL J0851.7-4635 (Vela Jr)
-
-Nine extended sources not included in the 2FGL catalog were found by our
-extended source search. Two of these have been previously
-studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
-Jr. \citep{rx_j1713_lat,vela_jr_lat}.
-Two of these sources were
-found when using photons with energies between 1 \gev and 100 \gev and seven
-were found when using photons with energies between 10 \gev and 100 \gev.
-For the sources found at energies above 10 \gev, we restrict our
-analysis to higher energies because of the issues
-of source confusion and diffuse emission modeling described in
-Section~\ref{extended_source_search_method}.
-The spectral and spatial properties of these nine sources are summarized
-in Table~\ref{new_ext_srcs_table} and the results of our investigation of
-systematic errors are presented in Table~\ref{alt_diff_model_results}.
-Table~\ref{alt_diff_model_results}
-also
-compares the likelihood assuming the source is spatially
-extended to the likelihood assuming 
-that the emission originates from two independent point-like
-sources. For these new extended sources, $\tsext>\tsinc$ 
-so we conclude that 
-the \gev emission does not originate from two physically
-distinct point-like sources (see Section~\ref{dual_localization_method}).  
-Table~\ref{alt_diff_model_results} also includes the
-results of the extension fits using variations of the PSF and the Galactic
-diffuse model described in Section~\ref{systematic_errors_on_extension}.
-There is good agreement between \tsext and the fit size using the standard
-analysis, the alternative approach to modeling the diffuse emission, and the alternative PSF.
-This suggests that the sources are robust against mis-modeled features in the diffuse
-emission model and uncertainties in the PSF.
-
-\subsection{2FGL\,J0823.0$-$4246}
-\label{section_2FGL_J0823.0-4246}
-
-% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-
-2FGL\,J0823.0$-$4246 was found by our search to be an extended source
-candidate in the 1 \gev to 100 \gev energy range and is spatially
-coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
-a counts map of this source. There are two nearby catalog sources 2FGL\,J0823.4$-$4305
-and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
-do not appear to represent physically distinct sources.
-We conclude that
-these nearby point-like sources
-were included in the 2FGL catalog to compensate for residuals induced
-by not modeling the extension of this source and
-removed them from our model of the sky.
-After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension 
-$\sigma=0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with 
-$\tsext=48.0$.  Figure~\ref{snr_seds} shows the spectrum of
-this source.
-
-Puppis A has been studied in detail in radio \citep{puppis_a_vla}, 
-and  X-ray \citep{rosat_puppis_a,suzaku_puppis_a}.
-The fit extension of 2FGL\,J0823.0$-$4246
-matches well the size of Puppis A in X-ray.  The distance of Puppis A was
-estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
-\gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
-No molecular clouds have been observed directly adjacent to Puppis A
-\citep{co_eastern_puppis_a}, similar to the LAT detected Cygnus Loop SNR
-\citep{cygnus_loop_lat}.  The luminosity of Puppis A is also smaller
-than that of other SNRs believed to interact with molecular clouds
-\citep{w51c,ic443,w44,w28,w49b_lat}.
-
-% Puppis A:
-%   Flux = PowerLaw(norm=6.21e-14,index=2.22,e0=10000).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%        = 4.7804242225163421e-11 ergs cm^-2 s-1
-%   Luminosity =  Flux * 4*pi*r^2 = 4.78e-11 ergs cm^-2 s^-1 * 4*pi * (2.2 kpc )**2 in ergs/s
-%              = 2.8e34 ergs/s from 1.0-100 gev
-%              = 5.6e34 ergs/s from 0.1-100 gev
-%   Luminosities
-%   Cygnus Loop:
-%     L = 10^33 ergs/s between 1-100 \gev
-%   W51C : 
-%     http://arxiv.org/pdf/0910.0908
-%     L > 1 x 10^36 ergs/s (0.2-50GeV) - 
-%   IC~443:
-%     http://arxiv.org/pdf/1002.2198v1
-%     L = 1.2e35 ergs/s (from 0.2-50 gev)
-%     d = 1.5 kpc
-%     From my (possibly incorrect) powerlaw analysis 
-%       In [30]: PowerLaw(norm=4.69e-13,index=2.21,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%       Out[30]: 3.5968626651391638e-10 ergs/cm^2/s
-%       L = 3.5968626651391638e-10/cm^2 * 4*pi*(1.5kpc)**2 = 1e35 (1-100gev)
-%   W44:
-%     http://www.sciencemag.org/content/327/5969/1103.full.pdf
-%     From my (possibly incorrect) powerlaw analysis 
-%       PowerLaw(norm=2.7e-13,index=2.63,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%       Out[27]: 2.7681360351439016e-10 ergs/cm^2/s
-%     Distance = 3kpc
-%     L = 3e35 ergs/s (1-100 gev)
-%   W28
-%     http://iopscience.iop.org/0004-637X/718/1/348/
-%     From my (possibly incorrect) powerlaw analysis 
-%       In [28]: PowerLaw(norm=2.23e-13,index=2.6,e0=1e4).i_flux(cgs=True,emin=1e3,emax=1e5,e_weight=1)
-%       Out[28]: 2.221059203350944e-10 ergs/cm^2/s
-%     Distance = 2kpc
-%     L = 1e35 ergs/s (1-100 gev)
-%   W49B
-%     http://iopscience.iop.org/0004-637X/722/2/1303
-%     L = 10^36 erg/s (0.2 - 200 gev)
-%
-
-\subsection{2FGL\,J0851.7$-$4635}
-\label{section_2FGL_J0851.7-4635}
-
-% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635
-
-2FGL\,J0851.7$-$4635 was found by our search to be an extended source
-candidate in the 10 \gev to 100 \gev energy range and is spatially
-coincident with the SNR Vela Jr. This source was recently studied by the LAT
-Collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
-map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
-contours of Vela Jr. \citep{vela_jr_hess}.
-There are three
-point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
-and 2FGL\,J0855.4$-$4625 which correlate with the 
-multiwavelength
-emission of
-this SNR but do not appear to be physically distinct sources.
-They were most likely included in the 2FGL catalog to compensate for residuals
-induced by not modeling the extension of Vela Jr. and were removed
-from our model of the sky.
-
-With this model of the background, 2FGL\,J0851.7$-$4635 was found to
-have an extension of $\sigma=1\fdg15\pm0\fdg08_\stat\pm0\fdg02_\sys$ with
-$\tsext=86.8$.  The LAT size matches
-well the \tev morphology of Vela Jr.  While fitting the extension
-of 2FGL\,J0851.7$-$4635, we iteratively relocalized the positions
-of the nearby point-like catalog source 2FGL\,J0854.7$-$4501 to
-$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies.
-
-\subsection{2FGL\,J1615.0$-$5051}
-\label{section_2FGL_J1615.0-5051}
-
-% For both 2FGL J1615.0-5051 and 2FGL J1615.2-5138 
-% Extended Sources:
-%   * 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 % extended source
-%   * 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138 % extended source
-
-2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to be
-extended source candidates in the 10 \gev to 100 \gev energy range. Because
-they are less than $1\degree$ away from each other, they needed to be analyzed
-simultaneously.  2FGL\,J1615.0$-$5051 is spatially coincident with
-the extended \tev source HESS\,J1616$-$508 and 2FGL\,J1615.2$-$5138
-is coincident with the extended \tev source HESS\,J1614$-$518.
-Figure~\ref{1FGL_J1613.6-5100c} shows a counts map of these sources and
-overlays the \tev contours of HESS\,J1616$-$508 and HESS\,J1614$-$518
-\citep{hess_plane_survey}.  The figure shows that the 2FGL source
-2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and correlates
-with the same extended \tev source as 2FGL\,J1615.2$-$5138.  We concluded
-that this source was included in the 2FGL catalog to compensate for residuals induced
-by not modeling the extension of 2FGL\,J1615.2$-$5138 and removed
-it from our model of the sky.
-
-With this model of the sky, we iteratively fit the extensions of
-2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138.
-2FGL\,J1615.0$-$5051 was found to have an extension 
-$\sigma=0\fdg32\pm0\fdg04_\stat\pm0\fdg01_\sys$ and
-\tsext=16.7.
-
-The \tev counterpart of 2FGL\,J1615.0$-$5051 was fit
-with a radially-symmetric Gaussian surface brightness profile with
-$\sigma=0\fdg136\pm0\fdg008$.  This \tev size corresponds to a 68\%
-containment radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the
-LAT size $\rsixeight=0\fdg26\pm0\fdg03$.  Figure~\ref{hess_seds} shows
-that the spectrum of 2FGL\,J1615.0$-$5051 at \gev energies connects to
-the spectrum of HESS\,J1616$-$508 at \tev energies.
-
-HESS\,J1616$-$508 is located in the region of two SNRs RCW103 (G332.4-04)
-and Kes~32 (G332.4+0.1) but is not spatially coincident with either
-of them \citep{hess_plane_survey}.  HESS\,J1616$-$508 is near three
-pulsars PSR\,J1614$-$5048, PSR\,J1616$-$5109, and PSR\,J1617$-$5055.
-\citep{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}.  Only
-PSR\,J1617$-$5055 is energetically capable of powering the \tev emission
-and \cite{hess_plane_survey} speculated that HESS\,J1616$-$508 could
-be a PWN powered by this young pulsar.  Because HESS\,J1616$-$508 is
-$9\arcmin$ away from PSR\,J1617$-$5055, this would require an asymmetric
-X-ray PWNe to power the \tev emission.  \chandra ACIS observations
-revealed an underluminous PWN of size $\sim1\arcmin$ around the
-pulsar that was not oriented towards the \tev emission, rendering this
-association uncertain \citep{discovery_of_pwn_for_PSR_J1617-5055}.
-No other promising counterparts were observed at X-ray and soft
-gamma-ray energies by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
-IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
-\cite{discovery_of_pwn_for_PSR_J1617-5055} discovered additional
-diffuse emission towards the center of HESS\,J1616$-$508 using archival
-radio and infared observations. Deeper observations will likely be
-necessary to understand this $\gamma$-ray source.
-
-\subsection{2FGL\,J1615.2$-$5138}
-\label{section_2FGL_J1615.2-5138}
-
-2FGL\,J1615.2$-$5138 was found
- to have an extension $\sigma=0\fdg42\pm0\fdg04_\stat\pm0.02_\sys$
-with $\tsext=46.5$.
-To test for the possibility that
-2FGL\,J1615.2$-$5138 is not spatially extended but instead composed
-of two point-like sources (one of them represented in the 2FGL catalog by
-2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
-sources.  Because \tsinc is less than \tsext, we conclude that
-this emission does not originate from two nearby point-like sources.
-
-2FGL\,J1615.2$-$5138 is spatially coincident with 
-the extended \tev source HESS\,J1614$-$518.
-H.E.S.S. measured a 2D Gaussian extension of $\sigma=0\fdg23\pm0\fdg02$
-and $\sigma=0\fdg15\pm0\fdg02$ in the semi-major and
-semi-minor axis. This corresponds to a 68\% containment size of
-$\rsixeight=0\fdg35\pm0\fdg03$ and $0\fdg23\pm0\fdg03$,  consistent with
-the LAT size $\rsixeight=0\fdg34\pm0\fdg03$.  Figure~\ref{hess_seds}
-shows that the spectrum of 2FGL\,J1615.2$-$5138 at \gev energies connects
-to the spectrum of HESS\,J1614$-$518 at \tev energies.  Further data
-collected by H.E.S.S. in 2007 resolve a double peaked structure at
-\tev energies but no spectral variation across this source, suggesting
-that the emission is not the confusion of physically separate sources
-\citep{closer_look_hess_j1614-518}.  This double peaked structure is
-also hinted at in the LAT counts map in Figure~\ref{1FGL_J1613.6-5100c}
-but is not very significant.  The \tev source was also detected by
-CANGAROO-III \citep{cangaroo_j1614-518}.
-
-There are five nearby pulsars, but none are luminous enough to
-provide the energy output required to power the $\gamma$-ray
-emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614$-$518
-is spatially coincident with a young open cluster Pismis 22
-\citep{hess_1614_landi_atel,closer_look_hess_j1614-518}.  \suzaku detected
-two promising X-ray candidates. Source A is an extended source consistent
-with the peak of HESS\,J1614$-$518 and source B coincident with Pismis 22
-and towards the center but in a relatively dim region of HESS\,J1614$-$518
-\citep{suazku_hess_j1614_518}.  Three hypotheses have been presented to
-explain this emission: either source A is an SNR powering the $\gamma$-ray
-emission; source A is a PWN powered by an undiscovered pulsar in either
-source A or B; and finally that the emission may arise from hadronic
-acceleration in the stellar winds of Pismis 22 \citep{cangaroo_j1614-518}.
-
-\subsection{2FGL\,J1627.0$-$2425c}
-\label{section_2FGL_J1627.0-2425c}
-
-% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-% No modifications to background were needed
-
-2FGL\,J1627.0$-$2425c was found by our search to
-have an extension $\sigma=0\fdg42\pm0\fdg05_\stat\pm0\fdg16_\sys$ with
-$\tsext=32.4$
-using photons with energies between 1 \gev and 100 \gev.  
-Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
-
-This source is in a region of remarkably complicated diffuse emission.
-Even though it is $16\degree$ from the Galactic plane, this source is on
-top of the core of the Ophiuchus molecular cloud which contains massive
-star-forming regions that are bright in infrared.  The region also has
-abundant molecular and atomic gas traced by CO and H~I and significant 
-dark gas found only by its association with dust emission
-\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
-more challenging to measure the column density of dust.  Infared and 
-CO ($J=1\rightarrow 0$)
-contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
-spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
-This source might 
-represent $\gamma$-ray emission from the interactions of cosmic rays with
-interstellar gas which has not been accounted for in the LAT diffuse
-emission model.
-
-\subsection{2FGL\,J1632.4$-$4753c}
-\label{section_2FGL_J1632.4-4753c}
-
-% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-
-2FGL\,J1632.4$-$4753c was found by our search to be an extended source
-candidate in the 10 \gev to 100 \gev energy range but is in a crowded
-region of the sky.  It is spatially coincident with the \tev source
-HESS\,J1632$-$478.  Figure~\ref{1FGL_J1632.9-4802c}a shows a counts
-map of this source and overlays \tev contours of HESS\,J1632$-$478
-\citep{hess_plane_survey}.  There are six nearby point-like 2FGL
-sources that appear to  represent physically distinct sources
-and were included in our background model: 2FGL\,J1630.2$-$4752, 2FGL\,J1631.7$-$4720c, 2FGL\,J1632.4$-$4820c, 2FGL\,J1635.4$-$4717c,
-2FGL\,J1636.3$-$4740c, and
-2FGL\,J1638.0$-$4703c. On the
-other hand, one point-like 2FGL source 2FGL\,J1634.4$-$4743c  correlates
-with the extended \tev source and at \gev energies does
-not appear physically separate. 
-We therefore removed this source from our model of the
-background.  Figure~\ref{1FGL_J1632.9-4802c}b shows the same region with
-the background sources subtracted.  With this model, 2FGL\,J1632.4$-$4753c
-was found to have an extension $\sigma=0\fdg35\pm0\fdg04_\stat\pm0\fdg02_\sys$
-with $\tsext=26.9$.  While fitting the
-extension of 2FGL\,J1632.4$-$4753c, we iteratively relocalized
-2FGL\,J1635.4$-$4717c to $(l,b)=(337\fdg23,0\fdg35)$ and
-2FGL\,J1636.3$-$4740c to $(l,b)=(336\fdg97,-0\fdg07)$.
-
-H.E.S.S measured an extension of $\sigma=0\fdg21\pm0\fdg05$ and
-$0\fdg06\pm0\fdg04$ along the semi-major and semi-minor axes when
-fitting HESS\,J1632$-$478 with an elliptical 2D Gaussian surface
-brightness profile.  This corresponds to a 68\% containment size
-$\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$ along
-the semi-major and semi-minor axis, consistent with the LAT size
-$\rsixeight=0\fdg29\pm0\fdg04$.  Figure~\ref{hess_seds} shows that
-the spectrum of 2FGL\,J1632.4$-$4753c at \gev energies connects to the
-spectrum of HESS\,J1632$-$478 at \tev energies.
-
-\cite{hess_plane_survey} argued that HESS\,J1632$-$478
-is positionally coincident with the hard X-ray source
-IGR\,J1632$-$4751 observed by \asca, INTEGRAL, and \xmmnewton
-\citep{asca_plane_survey,Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751},
-but this source is suspected to be a Galactic X-Ray Binary so the
-$\gamma$-ray extension disfavors the association.  Further observations
-by \xmmnewton discovered point-like emission coincident with the peak
-of the H.E.S.S. source surrounded by extended emission of size
-$\sim32\arcsec\times15\arcsec$ \citep{hess_j1632_478_xmm_newton}.
-They found in archival MGPS-2 data a spatially coincident extended
-radio source \citep{most_survey_galactic_plane} and argued for a single
-synchrotron and inverse Compton process producing the radio, X-ray, and \tev emission,
-likely due to a PWN.  The increased size at \tev energies compared
-to X-ray energies has previously been observed in several aging PWNe
-including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
-HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
-and Vela X \citep{vela_x_rosat,vela_x_hess} and can be explained by
-different synchrotron cooling times for the electrons that produce X-rays
-and $\gamma$-rays.
-
-\subsection{2FGL\,J1712.4$-$3941}
-\label{section_2FGL_J1712.4-3941}
-
-% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
-
-2FGL\,J1712.4$-$3941 was found by our search to be spatially extended
-using photons with energies between 1 \gev and 100 \gev.  This source
-is spatially coincident with the SNR RX\,J1713.7$-$3946 and was
-recently studied by the LAT Collaboration in \cite{rx_j1713_lat}.
-To avoid issues related to uncertainties in the nearby Galactic
-diffuse emission at lower energy, we restricted our analysis only
-to energies above 10 \gev.  Figure~\ref{2FGL_J1712.4-3941} shows a
-smoothed counts map of the source. Above 10 \gev, the \gev emission
-nicely correlates with the \tev contours of RX\,J1713.7$-$3946
-\citep{rx_j1713_hess} and 2FGL\,J1712.4$-$3941 fit to an extension 
-$\sigma=0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$ with $\tsext=38.5$.
-
-\subsection{2FGL\,J1837.3$-$0700c}
-\label{section_2FGL_J1837.3-0700c}
-
-% 1FGL J1837.5-0659c - P72Y2986 - 2FGL J1837.3-0700c
-
-2FGL\,J1837.3$-$0700c was found by our search to be an extended source
-candidate in the 10 \gev to 100 \gev energy range and is spatially
-coincident with the \tev source HESS\,J1837$-$069.  This source is
-in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
-smoothed counts map of the region and overlays the \tev contours of
-HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
-point-like 2FGL sources, 2FGL\,J1836.8$-$0623c and 2FGL\,J1839.3$-$0558c,
-that clearly represent distinct sources.  On the other hand, there is
-another source 2FGL\,J1835.5$-$0649 located between the three sources that
-appears to correlate with the \tev morphology of HESS\,J1837$-$069 but
-at \gev energies
-does not appear to represent a physically distinct source.  We concluded
-that this source was included in the 2FGL catalog to compensate for residuals induced by
-not modeling the extension of this source and removed it from our model
-of the sky.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
-counts map of this region after subtracting these background sources.
-After removing 2FGL\,J1835.5$-$0649,
-we tested for
-source confusion by fitting 
-2FGL\,J1837.3$-$0700c
-instead as two point-like sources.
-Because \tsinc is less than \tsext, we conclude that this emission
-does not originate from two nearby point-like sources.
-
-With this model, 2FGL\,J1837.3$-$0700c was found to have an
-extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with 
-$\tsext=18.5$. 
-While fitting the extension of 2FGL\,J1837.3$-$0700c,
-we iteratively relocalized the two closest
-background sources along with the extension of 2FGL\,J1837.3$-$0700c but
-their positions did not significantly change.  2FGL\,J1834.7$-$0705c
-moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
-to $(l,b)=(25\fdg57,0\fdg32)$.
-
-H.E.S.S. measured an extension of
-$\sigma=0\fdg12\pm0\fdg02$ and $0\fdg05\pm0\fdg02$ 
-of the coincident \tev source HESS\,J1837$-$069 
-along the semi-major and semi-minor axis when fitting this source
-with an elliptical 2D Gaussian surface brightness profile.  This corresponds
-to a 68\% containment radius of $\rsixeight=0\fdg18\pm0\fdg03$ and
-$0\fdg08\pm0\fdg03$ along the semi-major and semi-minor axis. The
-size is not significantly different from the LAT 68\% containment
-radius of $\rsixeight=0\fdg27\pm0\fdg07$ (less than $2\sigma$).
-Figure~\ref{hess_seds} shows that the spectrum of 2FGL\,J1837.3$-$0700c
-at \gev energies connects to the spectrum of HESS\,J1837$-$069 at \tev
-energies.
-
-HESS\,J1837$-$069 is coincident with the hard and steady X-ray source
-AX\,J1838.0$-$0655 \citep{hard_x-ray_asca}.  This source was discovered
-by RXTE to be a pulsar (PSR J1838-0655) 
-sufficiently luminous to power the \tev emission
-and was resolved by \chandra to be a bright point-like source surrounded
-by a $\sim2\arcmin$ nebula \citep{pulsations_HESS_J1837-069}. The
-$\gamma$-ray emission may be powered by this pulsar.  The hard spectral
-index and spatial extension of 2FGL\,J1837.3$-$0700c disfavor a pulsar
-origin of the LAT emission and suggest instead that the \gev and \tev
-emission both originate from the pulsar's wind.  There is another
-X-ray point-like source AX\,J1837.3$-$0652 near HESS\,J1837$-$069
-\citep{hard_x-ray_asca} that was also resolved into a point-like
-and diffuse component \citep{pulsations_HESS_J1837-069}.  Although no
-pulsations have been detected from it, it could also be a pulsar powering
-some of the $\gamma$-ray emission.
-
-\subsection{2FGL\,J2021.5+4026}
-\label{section_2FGL J2021.5+4026}
-
-% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-
-The source 2FGL\,J2021.5+4026 is associated with the $\gamma$-Cygni SNR 
-and has been speculated
-to originate from the interaction of accelerated particles in the SNR
-with dense molecular clouds \citep{pollock_1985,gaisser_1998}. This
-association was disfavored when the \gev emission from this source
-was detected to be pulsed \citep[PSR\,J2021+4026,][]{first_lat_pulsar_cat}.
-This pulsar was also observed by AGILE \citep{gamma_cygni_agile}.
-
-Looking at the same region at energies above 10 \gev, the pulsar is
-no longer significant but we instead found in our search an extended
-source candidate.  Figure~\ref{1FGL_J2020.0+4049} shows a counts map
-of this source and overlays radio contours of $\gamma$-Cygni from the
-Canadian Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
-There is good spatial overlap between the SNR and the \gev emission.
-
-There is a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
-emission of $\gamma$-Cygni and at \gev energies 
-does not appear to represent a physically
-distinct source.  We concluded that it was included in the 2FGL catalog to compensate
-for residuals induced by not modeling the extension of $\gamma$-Cygni and
-removed it from our model of the sky.  With this model, 2FGL\,J2021.5+4026
-was found to have an extension $\sigma=0\fdg63\pm0\fdg05_\stat\pm0\fdg04_\sys$
-with $\tsext=128.9$.  Figure~\ref{snr_seds}
-shows its spectrum.  The inferred size of this source at \gev energies
-well matches the radio size of $\gamma$-Cygni.  Milagro detected
-a $4.2\sigma$ excess at energies $\sim 30$ \tev from this location
-\citep{lat_bsl,milagro_bright_source_list}.  VERITAS also detected an
-extended source VER\,J2019+407 coincident with the SNR above 200 \gev
-and suggested that the \tev emission could be a shock-cloud interaction
-in $\gamma$-Cygni \citep{veritas_gamma_cygni}.
-
-% Radio observations \dots
-% X-ray observations \dots
-% Age \ldots
-% Distance: 1.5 kpc Landecker et al 1980 (from integral paper)
-% Optical: (Mavromatakis 2003 (from integral paper)
-% EGRET observations: 3EG J2020+4027
-% LAT Pulsar detected
-%   PSR J2021+4026
-%   Prestended at scineghe2010.
-%     http://scineghe2010.ts.infn.it/allegati/talks/ThursdaySept9/13_Razzano.pdf
-%   Presented at Fermi Symposium 2011:
-%     https://confluence.slac.stanford.edu/download/attachments/98831433/2011_3FermiSymp_CygPsr_ver2.pdf
-%     "PSR J2021+4026 is a 265 ms pulsar found by Fermi LAT using"
-%     "This discovery help to better clarify the nature of the
-%      unidentified source 3EG J2020+4027, thought to be associated
-%      with SNR 78.2+2.1, a.k.a. the $\gamma$-Cygni SNR.
-%      Unfortunately, so far this pulsar lacks a radio counterpart, and
-%      observations with Chandra and XMM show a potential X-ray
-%      counterpart [8,9,15], but no pulsations have been detected so
-%      far."
-
-% Milagro analysis
-% http://arxiv.org/abs/astro-ph/0611691
-% Milagro $4.2\sigma$ excess.
-
-% VERITAS observations of $\gamma$-Cygni: 
-%   http://arxiv.org/pdf/0912.4492v1
-%   extended: VER J019+407
-%     VERITAS observations of $\gamma$-Cygni veritas_gamma_cygni,
-
-\section{Discussion}
-
-Twelve extended sources were included in the 2FGL catalog and two additional extended
-sources were studied in dedicated publications.  Using 2 years of
-LAT data and a new analysis method, we presented the detection of seven
-additional extended sources.  We also reanalyzed the spatial extents of the
-twelve extended sources in the 2FGL catalog and the two additional sources.  The 21
-extended LAT sources are located primarily along the Galactic plane
-and their locations are shown in Figure~\ref{allsky_extended_sources}.
-Most of the LAT detected extended sources are expected to be of Galactic
-origin as the distances of extragalactic sources (with the exception of
-the local group Galaxies) are typically too large to be able to resolve
-them at $\gamma$-ray energies.
-
-For the LAT extended sources also seen at \tev energies,
-Figure~\ref{gev_vs_tev_plot} shows that there is a good correlation
-between the sizes of the sources at \gev and \tev energies. Even so,
-the sizes of PWNe are expected to vary across the \gev and \tev energy
-range and the size of HESS\,J1825$-$137 is significantly larger at
-\gev than \tev energies \citep{fermi_hess_j1825}.  It is interesting
-to compare the sizes of other PWN candidates at \gev and \tev energies,
-but definitively measuring a difference in size would require a more in-depth analysis
-of the LAT data using the same elliptical Gaussian spatial model.
-
-Figure~\ref{gev_vs_tev_histogram} compares the sizes of the 21 extended
-LAT sources to the 42 extended H.E.S.S. sources.\footnote{The 
-\tev extension of
-the 42 extended H.E.S.S. sources comes from the H.E.S.S. Source
-Catalog \url{http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/sources/}.}
-Because of the large
-field of view and all-sky coverage, the LAT can more easily measure
-larger sources.  On the other hand, the 
-better
-angular resolution of air Cherenkov detectors allows them to measure a
-population of extended sources below the resolution limit of the LAT (currently 
-about $\sim0\fdg2$).  \fermi has a 5 year nominal mission lifetime with
-a goal of 10 years of operation.  As Figure~\ref{time_sensitivity} shows,
-the low background of the LAT at high energies allows its sensitivity 
-to
-these smaller sources to improve by a factor greater than the square root
-of the relative exposures.  With increasing exposure, the LAT will likely begin to
-detect and resolve some of these smaller \tev sources.
-
-Figure~\ref{compare_index_2FGL} compares the spectral indices of LAT
-detected extended sources and of all sources in the 2FGL catalog. This, and
-Tables~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
-show that the LAT observes a population of hard extended sources
-at energies above 10 \gev.  Figure~\ref{hess_seds} shows that
-the spectra of four of these sources (2FGL\,J1615.0$-$5051,
-2FGL\,J1615.2$-$5138, 2FGL\,J1632.4$-$4753c, and 2FGL\,J1837.3$-$0700c)
-at \gev energies connects to the spectra of their H.E.S.S. counterparts
-at \tev energies. This is also true of Vela Jr., HESS\,J1825$-$137
-\citep{fermi_hess_j1825}, and RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.
-It is likely that the \gev and \tev emission from these sources originates
-from the same population of high-energy particles.
-
-Many of the \tev detected extended sources now seen at \gev energies
-are currently unidentified and further multiwavelength follow-up
-observations will be necessary to understand these particle accelerators.
-But extending the spectra of these \tev sources towards lower energies
-with LAT observations may help to determine the origin and nature of
-the high-energy emission.
-
 The \textit{Fermi} LAT Collaboration acknowledges generous ongoing support
@@
 
-Additional support for science analysis during the operations phase is gratefully
-acknowledged from the Istituto Nazionale di Astrofisica in Italy and the Centre National d'\'Etudes Spatiales in France.
+Additional support for science analysis during the operations phase is
+gratefully acknowledged from the Istituto Nazionale di Astrofisica in
+Italy and the Centre National d'\'Etudes Spatiales in France.
 
-This research has made use of
-pywcsgrid2, an open-source plotting package for
-Python\footnote{\url{http://leejjoon.github.com/pywcsgrid2/}}. The authors acknowledge the
-use of HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.
-
-\bibliography{extended_catalog}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{ic443_plots/four_plots_ic443_color.eps}
-    \else
-    \plotone{ic443_plots/four_plots_ic443_bw.eps}
-    \fi
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v3/run.py
-    \caption{
-    Counts maps and TS profiles for the SNR IC~443. (a) \ts
-    vs. extension of the source. (b) \tsext for individual energy
-    bands. (c) observed radial profile of counts in comparison to the
-    expected profiles for a spatially extended source (solid and colored
-    red in the online version) and for a point-like source (dashed and colored
-    blue in the online version).  (d) smoothed counts map after subtraction
-    of the diffuse emission compared to the smoothed
-    LAT PSF (inset). Both were smoothed by a 0\fdg1 2D Gaussian kernel.
-    Plots (a),
-    (c), and (d) use only 
-    photons with energies between
-    1 \gev and 100 \gev.  Plots (c) and (d) use
-    only photons which converted in the front part of the tracker and
-    have an improved angular resolution.
-    }
-    \label{four_plots_ic443}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{mc_plots/compare_disk_gauss_color.eps}
-    \else
-      \plotone{mc_plots/compare_disk_gauss_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v3/plot.py
-    \caption{
-    A comparison of a 2D Gaussian and uniform disk spatial model
-    of extended sources before and after convolving with the PSF for two
-    energy ranges.  The solid black line is the PSF that would be observed
-    for a power-law source of spectral index 2. The dashed line
-    and the dash-dotted lines are 
-    the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
-    and the convolution of this profile with the LAT PSF respectively
-    (colored red in the online version).
-    The dash-dot-doted and the dot-doted lines are the brightness profile
-    of a uniform disk with $\rsixeight=0\fdg5$ and the convolution
-    of this profile with the LAT PSF respectively (colored blue in the online version).
-    }\label{compare_disk_gauss}
-  \end{figure}
-
-\clearpage
-\begin{deluxetable}{rrrrrr}
-\tabletypesize{\normalsize}
-\tablecaption{Monte Carlo Spectral Parameters
-\label{ts_ext_num_sims}
-}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Spectral Index}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{$N_{1-100\gev}$}&
-\colhead{$\langle\ts\rangle_{1-100\gev}$}&
-\colhead{$N_{10-100\gev}$}&
-\colhead{$\langle\ts\rangle_{10-100\gev}$}\\
-\colhead{}&
-\colhead{(\phflux)}&
-\colhead{}&
-\colhead{}&
-\colhead{}&
-\colhead{}
-}
-
-\startdata
-      1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
-          &          $10^{-7}$ &           19079 &   5827    &     19079   &    2258     \\
-          &  $3\times 10^{-8}$ &           19303 &   1276    &     19303   &     541     \\
-          &          $10^{-8}$ &           19385 &    303    &     19381   &     142     \\
-          &  $3\times 10^{-9}$ &           18694 &     62    &     12442   &      43     \\
-      \hline
-        2 &          $10^{-6}$ &           18760 &  22101    &     18760   &    3033     \\
-          &  $3\times 10^{-7}$ &           18775 &   4913    &     18775   &     730     \\
-          &          $10^{-7}$ &           18804 &   1170    &     18803   &     192     \\
-          &  $3\times 10^{-8}$ &           18836 &    224    &     15256   &      50     \\
-          &          $10^{-8}$ &           17060 &     50    &   \nodata   & \nodata     \\
-      \hline
-      2.5 &  $3\times 10^{-6}$ &           18597 &  19036    &     18597   &     786    \\
-          &          $10^{-6}$ &           18609 &   4738    &     18608   &     208    \\
-          &  $3\times 10^{-7}$ &           18613 &    954    &     15958   &      53    \\
-          &          $10^{-7}$ &           18658 &    203    &   \nodata   & \nodata    \\
-          &  $3\times 10^{-8}$ &           14072 &     41    &   \nodata   & \nodata    \\
-      \hline                                                
-        3 &          $10^{-5}$ &           18354 &  19466    &     18354   &     215    \\
-          &  $3\times 10^{-6}$ &           18381 &   4205    &     15973   &      54    \\
-          &          $10^{-6}$ &           18449 &    966    &   \nodata   & \nodata    \\
-          &  $3\times 10^{-7}$ &           18517 &    174    &   \nodata   & \nodata    \\
-          &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
-\enddata
-
-\tablenotetext{(a)}{Integral 100 \mev to 100 \gev flux.}
-
-\tablecomments{
-    A list of the spectral models of the simulated point-like sources
-    which were tested for extension.  For each model, the number of
-    statistically independent simulations and the average value of \ts is
-    also tabulated.  
-}
-\end{deluxetable}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/ts_ext_emin_1000_color.eps}
-    \else
-    \plotone{mc_plots/ts_ext_emin_1000_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
-    \caption{
-    Cumulative distribution of the TS for the extension test when fitting
-    simulated point-like sources in the 1 GeV to 100 GeV energy range.
-    The four plots
-    represent simulated sources of different spectral indices and
-    the different lines (colored in the online version) 
-    represent point-like sources with different 100 \mev
-    to 100 \gev integral fluxes.  The dashed line (colored red)
-    is the cumulative
-    density function of Equation~\ref{ts_ext_distribution}.
-    }\label{ts_ext_mc_1000}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/ts_ext_emin_10000_color.eps}
-    \else
-    \plotone{mc_plots/ts_ext_emin_10000_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
-    \caption{
-    The same plot as Figure~\ref{ts_ext_mc_10000} but fitting in the 10 \gev to 100 \gev energy 
-    range.
-    }\label{ts_ext_mc_10000}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/index_sensitivity_color.eps}
-    \else
-    \plotone{mc_plots/index_sensitivity_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
-    \caption{
-    The detection threshold to resolve an
-    extended source with a uniform disk model for a two-year exposure.  All sources have an
-    assumed power-law spectrum and the different line styles (colors in
-    the electronic version) correspond to different simulated spectral
-    indices.  The lines with no markers correspond to the detection
-    threshold using photons with energies between 100 \mev and 100 \gev
-    while the lines with star-shaped markers correspond to the threshold
-    using photons with energies between 1 \gev and 100 \gev.
-    }\label{index_sensitivity}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/all_sensitivity_color.eps}
-    \else
-    \plotone{mc_plots/all_sensitivity_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
-    \caption{The LAT detection threshold for four spectral indices
-    and three backgrounds ($1\times$, $10\times$, and $100\times$ the
-    Sreekumar-like isotropic background) for a two-year exposure. The
-    left-hand plots are the detection threshold when using 
-    photons with energies between
-    1 \gev and 100 \gev
-    and the right-hand plots are the detection threshold when using
-    photons with energies between
-    10 \gev and 100 \gev.  The flux is integrated only in the
-    selected energy range.  Overlaid on this plot are the LAT detected
-    extended sources placed by the magnitude of the nearby Galactic
-    diffuse emission and the energy range they were analyzed with.
-    The star-shaped markers (colored red in the electronic version)
-    are sources with a spectral index closer to 1.5, the triangular
-    markers (colored blue) an index closer to 2, and the circular markers
-    (colored green) an index closer to 2.5.  The triangular marker in plot
-    (d) below the sensitivity line is MSH\,15$-$52.
-    }\label{all_sensitivity} 
-  \end{figure}
-
-  \clearpage
-  \thispagestyle{empty}
-\begin{deluxetable}{rr|rrrrrrrrrrrrrrrrrrrrr}
-\tablecolumns{22}
-\tabletypesize{\scriptsize}
-\rotate
-\tablewidth{0pt}
-\tablecaption{Extension Detection Threshold
-\label{all_sensitivity_table}
-}
-\tablehead{
-\colhead{$\gamma$}&       
-\colhead{BG}&
-\colhead{$0.1$}&
-\colhead{$0.2$}&
-\colhead{$0.3$}&
-\colhead{$0.4$}&
-\colhead{$0.5$}&
-\colhead{$0.6$}&
-\colhead{$0.7$}&
-\colhead{$0.8$}&
-\colhead{$0.9$}&
-\colhead{$1.0$}&
-\colhead{$1.1$}&
-\colhead{$1.2$}&
-\colhead{$1.3$}&
-\colhead{$1.4$}&
-\colhead{$1.5$}&
-\colhead{$1.6$}&
-\colhead{$1.7$}&
-\colhead{$1.8$}&
-\colhead{$1.9$}&
-\colhead{$2.0$}
-}
-\startdata
-\multicolumn{22}{c}{E$>$1 \gev} \\
-\hline
-     1.5 &      $1\times$ &      148.1 &       23.3 &       11.3 &        8.0 &        7.2 &        6.9 &        6.7 &        6.8 &        7.1 &        7.4 &        7.6 &        7.9 &        8.1 &        8.5 &        9.2 &        9.9 &        9.1 &        9.2 &        9.0 &       10.3 \\
-         &     $10\times$ &      148.4 &       29.0 &       18.7 &       15.2 &       15.4 &       15.0 &       16.1 &       16.0 &       16.8 &       17.7 &       18.2 &       19.3 &       20.9 &       22.5 &       23.8 &       24.8 &       21.3 &       22.8 &       23.4 &       23.7 \\
-         &    $100\times$ &      186.8 &       55.0 &       43.4 &       40.7 &       41.0 &       41.8 &       40.9 &       40.9 &       42.7 &       43.6 &       38.4 &       39.9 &       40.6 &       38.4 &       36.9 &       36.3 &       37.1 &       38.8 &       37.2 &       37.6 \\
-       2 &      $1\times$ &      328.4 &       43.4 &       18.9 &       13.4 &       11.2 &       10.4 &       10.2 &       10.2 &       10.2 &       10.4 &       10.7 &       10.9 &       11.2 &       11.5 &       12.4 &       12.6 &       13.0 &       13.4 &       14.0 &       14.4 \\
-         &     $10\times$ &      341.0 &       55.9 &       32.3 &       27.6 &       26.5 &       25.4 &       25.6 &       25.9 &       27.4 &       26.8 &       27.8 &       28.7 &       29.8 &       30.1 &       31.0 &       31.5 &       31.7 &       34.0 &       34.3 &       35.9 \\
-         &    $100\times$ &      420.5 &      128.3 &       90.2 &       77.3 &       73.3 &       70.8 &       67.5 &       64.3 &       64.2 &       64.1 &       62.8 &       63.6 &       61.7 &       61.9 &       58.4 &       59.0 &       61.4 &       63.3 &       60.1 &       58.1 \\
-     2.5 &      $1\times$ &      627.1 &       75.6 &       29.8 &       19.3 &       15.5 &       13.5 &       12.8 &       12.6 &       12.5 &       12.5 &       12.6 &       12.9 &       12.9 &       13.1 &       13.5 &       13.7 &       14.3 &       14.8 &       15.2 &       15.8 \\
-         &     $10\times$ &      638.9 &       99.1 &       52.1 &       39.1 &       34.6 &       33.0 &       32.5 &       32.5 &       32.8 &       33.2 &       34.1 &       34.3 &       34.5 &       35.1 &       36.6 &       36.9 &       35.5 &       36.0 &       36.5 &       37.3 \\
-         &    $100\times$ &      795.0 &      262.1 &      140.9 &      104.3 &       90.4 &       81.2 &       77.2 &       75.1 &       69.7 &       70.9 &       66.5 &       65.6 &       64.9 &       64.0 &       58.9 &       58.1 &       60.2 &       58.4 &       57.5 &       55.8 \\
-       3 &      $1\times$ &      841.5 &      110.6 &       43.2 &       25.5 &       18.7 &       16.1 &       14.4 &       13.6 &       13.3 &       13.2 &       13.1 &       13.1 &       13.4 &       13.6 &       13.5 &       13.8 &       14.2 &       14.4 &       14.8 &       15.4 \\
-         &     $10\times$ &      921.6 &      151.3 &       69.1 &       47.8 &       40.7 &       37.1 &       35.5 &       34.5 &       35.1 &       35.5 &       35.3 &       35.3 &       35.4 &       35.5 &       36.8 &       37.6 &       35.3 &       35.4 &       36.3 &       36.6 \\
-         &    $100\times$ &     1124.1 &      282.9 &      181.1 &      119.8 &      100.7 &       91.1 &       84.3 &       77.9 &       73.3 &       71.8 &       67.6 &       66.4 &       65.5 &       63.9 &       59.0 &       58.6 &       58.8 &       57.5 &       55.4 &       54.4 \\
-\cutinhead{E$>$10 \gev}
-     1.5 &      $1\times$ &       44.6 &        8.0 &        4.3 &        3.2 &        2.7 &        2.6 &        2.5 &        2.5 &        2.4 &        2.5 &        2.5 &        2.6 &        2.7 &        2.8 &        2.9 &        2.9 &        3.1 &        3.2 &        3.3 &        3.4 \\
-         &     $10\times$ &       45.2 &        9.2 &        5.8 &        5.0 &        4.9 &        4.9 &        5.0 &        5.2 &        5.3 &        5.7 &        5.9 &        6.3 &        6.6 &        6.5 &        6.8 &        7.6 &        7.8 &        8.2 &        8.5 &        8.7 \\
-         &    $100\times$ &       47.3 &       13.4 &       11.6 &       10.6 &       10.8 &       10.8 &       12.0 &       12.7 &       13.2 &       13.7 &       15.3 &       16.1 &       17.2 &       18.2 &       18.9 &       19.5 &       20.4 &       21.0 &       21.7 &       22.9 \\
-       2 &      $1\times$ &       49.7 &        8.4 &        4.4 &        3.3 &        2.8 &        2.6 &        2.6 &        2.6 &        2.6 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.2 &        3.2 &        3.4 &        3.5 &        3.5 \\
-         &     $10\times$ &       48.6 &        9.5 &        6.0 &        5.2 &        5.0 &        5.2 &        5.2 &        5.3 &        5.4 &        5.8 &        6.4 &        6.6 &        7.0 &        7.1 &        7.5 &        8.0 &        8.3 &        8.6 &        9.0 &        9.2 \\
-         &    $100\times$ &       51.8 &       14.7 &       11.8 &       11.5 &       11.5 &       11.9 &       13.2 &       14.0 &       14.3 &       15.3 &       16.2 &       16.9 &       18.4 &       19.2 &       19.8 &       21.0 &       22.0 &       22.8 &       23.2 &       24.3 \\
-     2.5 &      $1\times$ &       53.1 &        9.1 &        4.5 &        3.3 &        2.8 &        2.7 &        2.6 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.8 &        2.9 &        3.1 &        3.2 &        3.3 &        3.5 &        3.6 \\
-         &     $10\times$ &       53.7 &       10.5 &        6.3 &        5.4 &        5.1 &        5.1 &        5.3 &        5.4 &        5.7 &        6.0 &        6.3 &        6.6 &        6.8 &        6.9 &        7.5 &        8.1 &        8.3 &        8.6 &        8.9 &        9.2 \\
-         &    $100\times$ &       57.0 &       15.6 &       12.7 &       11.9 &       11.8 &       12.2 &       13.1 &       14.3 &       14.6 &       15.2 &       16.3 &       17.0 &       18.8 &       19.2 &       19.9 &       21.0 &       21.9 &       22.3 &       23.3 &       23.7 \\
-       3 &      $1\times$ &       55.5 &        9.4 &        4.8 &        3.4 &        2.9 &        2.7 &        2.6 &        2.5 &        2.5 &        2.5 &        2.6 &        2.7 &        2.7 &        2.8 &        2.9 &        3.0 &        3.1 &        3.2 &        3.4 &        3.4 \\
-         &     $10\times$ &       56.0 &       10.5 &        6.2 &        5.3 &        5.1 &        5.1 &        5.1 &        5.3 &        5.5 &        5.7 &        5.9 &        6.4 &        6.4 &        6.6 &        7.0 &        7.8 &        8.0 &        8.3 &        8.6 &        8.9 \\
-         &    $100\times$ &       60.3 &       16.2 &       12.7 &       11.7 &       11.8 &       12.2 &       12.6 &       13.8 &       14.2 &       14.6 &       15.8 &       16.5 &       17.6 &       18.5 &       19.4 &       19.8 &       20.7 &       21.0 &       21.8 &       22.5 \\
-\enddata
-\tablecomments{
-      The detection threshold to resolve spatially extended
-      sources with a uniform disk spatial model for a two-year exposure
-      The threshold is calculated for
-      sources of varying energy
-      ranges, spectral indices, and background levels.  The sensitivity
-      was calculated against
-      a Sreekumar-like isotropic background
-      and the second column is the factor that the simulated background
-      was scaled by. The remaining columns are varying sizes of the source. 
-      The table quotes
-      integral fluxes in the analyzed energy range (1 \gev to 100 \gev or 10 \gev to 100
-      \gev) in units of $10^{-10}$ \phflux.
-      }
-\end{deluxetable}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{mc_plots/time_sensitivity_color.eps}
-    \else
-      \plotone{mc_plots/time_sensitivity_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
-    \caption{
-    The projected detection threshold of the LAT to extension after 10 years
-    for a power-law
-    source of spectral index 2 against 10 times the isotropic background
-    in the energy range from 1 \gev to 100 \gev (solid line colored red in the electronic
-    version) and 10 \gev to 100 \gev
-    (dashed line colored blue). The shaded gray regions represent the
-    detection threshold assuming the sensitivity improves from 2 to 10
-    years by the square root of the exposure (top edge) and linearly with
-    exposure (bottom edge).  The lower plot shows the factor increase in
-    sensitivity.  For small extended sources, the detection threshold of the LAT
-    to the extension of a source will improve by a factor larger than the square root of 
-    the exposure.
-    }\label{time_sensitivity}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/confusion_extended_plot_color.eps}
-    \else
-    \plotone{mc_plots/confusion_extended_plot_bw.eps}
-    \fi
-    % this plot came from 
-    \caption{
-    (a) and (b) are the distribution of \tsext and of \tsinc when
-    fitting simulated spatially extended sources of varying sizes as
-    both an extended source and as two point-like sources.  (c) and
-    (d) are the distribution of $\tsext-\tsinc$ for the same simulated sources.
-    (a) and (c) represent sources fit in the 1 \gev to 100 \gev energy
-    range and (b) and (d) represent sources fit in the 10 \gev to
-    100 \gev energy range.  In (c) and (d), the plus-shaped markers
-    (colored red in the electronic version) are fits where $\tsext\ge16$.
-    }\label{confusion_extended_plot}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{mc_plots/confusion_2pts_plot_color.eps}
-    \else
-    \plotone{mc_plots/confusion_2pts_plot_bw.eps}
-    \fi
-    % this plot came from 
-    \caption{
-    The distribution of $\tsext-\tsinc$ when fitting two simulated
-    point-like sources of varying separations as
-    both an extended source and as two point-like sources.  (a),
-    and (b) represent simulations of two point-like sources with the
-    same spectral index and (c) and (d) represent simulations of two
-    point-like sources with different spectral indices.  (a) and (c)
-    fit the simulated sources in the 1 \gev to 100 \gev energy range
-    and (b) and (d) fit in the 10 \gev to 100 \gev energy range.
-    The plus-shaped markers (colored red in the electronic version)
-    are fits where $\tsext\ge16$.
-    }\label{confusion_2pts_plot}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/agn_color.eps}
-    \else
-      \plotone{source_plots/agn_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v6/agn.py
-    \caption{The cumulative density of \tsext for the 733 clean
-    AGN in 2LAC that were significant above 1 \gev calculated with \pointlike (dashed line
-    colored blue in the electronic version)
-    and with \gtlike (solid line colored black).  AGN are too far
-    and too small to be resolved by the LAT. Therefore, the cumulative
-    density of $\tsext$ is expected to follow a $\chi^2_1/2$ distribution
-    (Equation~\ref{ts_ext_distribution}, the dash-dotted line colored
-    red).
-    }\label{agn_ts_ext}
-  \end{figure}
-
-\begin{figure}
-  \ifcolorfigure
-    \plotone{ic443_plots/res_tsmap_ic443_color.eps}
-    \else
-    \plotone{ic443_plots/res_tsmap_ic443_bw.eps}
-    \fi
-  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v2
-
-  \caption{
-  A TS map generated for the region around the SNR 
-  IC~443 using 
-  photons with energies between
-  1 \gev and 100 \gev.  (a) TS map after
-  subtracting IC~443 modeled as a point-like source. (b) same as (a), but
-  IC~443 modeled as an extended source. The cross represents the best
-  fit position of IC~443.
-  }
-  \label{res_tsmaps}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-    \plotone{source_plots/example_bad_fit_color.eps}
-    \else
-    \plotone{source_plots/example_bad_fit_bw.eps}
-    \fi
-    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
-    \caption{
-    A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of the
-    region around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 2D Gaussian
-    kernel. The plus-shaped marker and circle (colored red in
-    the online version) represent the center and size of the source
-    fit with a
-    radially-symmetric uniform disk spatial model.  The black
-    crosses represent the positions of other 2FGL sources.  The extension
-    is statistically significant, but the extension encompasses many 2FGL
-    sources and the emission does not look to be uniform. Although
-    the fit is statistically significant, it likely corresponds to
-    residual features of inaccurately modeled diffuse emission picked
-    up by the fit. 
-    }
-    \label{example_bad_fit}
-\end{figure}
-
-\begin{deluxetable}{lrrrrrrrr}
-\tablecolumns{9}
-\rotate
-\tabletypesize{\footnotesize}
-\tablewidth{0pt}
-\tablecaption{Analysis of the twelve extended sources included in the 2FGL catalog
-\label{known_extended_sources}
-}
-\tablehead{
-\colhead{Name}&
-\colhead{\glon}&
-\colhead{\glat}&
-\colhead{$\sigma$}&
-\colhead{\ts}&
-\colhead{\tsext}&
-\colhead{Pos Err}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{Index}\\
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}
-}
-
-\startdata
-\multicolumn{9}{c}{E$>$1 \gev} \\
-\hline
-SMC                                  &     302.59 &   $-$44.42 & $  1.32 \pm   0.15 \pm   0.31 $ &       95.0 &       52.9 &   0.14 & $    2.7 \pm     0.3$ & $   2.48 \pm    0.19$  \\
-LMC                                  &     279.26 &   $-$32.31 & $  1.37 \pm   0.04 \pm   0.11 $ &     1127.9 &      909.9 &   0.04 & $   13.6 \pm     0.6$ & $   2.43 \pm    0.06$  \\
-IC~443                               &     189.05 &       3.04 & $  0.35 \pm   0.01 \pm   0.04 $ &    10692.9 &      554.4 &   0.01 & $   62.4 \pm     1.1$ & $   2.22 \pm    0.02$  \\
-Vela X                               &     263.34 &    $-$3.11 & $                         0.88$ &            &            &        &                       &                        \\
-Centaurus A                          &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
-W28                                  &       6.50 &    $-$0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
-W30                                  &       8.61 &    $-$0.20 & $  0.34 \pm   0.02 \pm   0.02 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
-W44                                  &      34.69 &    $-$0.39 & $  0.35 \pm   0.02 \pm   0.02 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
-W51C                                 &      49.12 &    $-$0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
-Cygnus Loop                          &      74.21 &    $-$8.48 & $  1.71 \pm   0.05 \pm   0.06 $ &      357.9 &      246.0 &   0.06 & $   11.4 \pm     0.7$ & $   2.50 \pm    0.10$  \\
-\cutinhead{E$>$10 \gev}
-MSH\,15$-$52\tablenotemark{(b)}      &     320.39 &    $-$1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
-HESS\,J1825$-$137\tablenotemark{(b)} &      17.56 &    $-$0.47 & $  0.65 \pm   0.04 \pm   0.02 $ &       59.7 &       33.8 &   0.05 & $    1.6 \pm     0.2$ & $   1.63 \pm    0.22$  \\
-\enddata
-
-\tablenotetext{(a)}{
-Integral Flux in units of $10^{-9}$ \phflux and integrated in the fit
-energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
-}
-\tablenotetext{(b)}{
-The discrepancy in the best fit spectra of MSH\,15$-$52 and HESS\,J1825$-$137
-compared to \cite{msh1552} and
-\cite{fermi_hess_j1825} is due to fitting over a different energy range.
-}
-
-\tablecomments{
-All sources were fit using a radially-symmetric uniform disk spatial model.
-\glon and \glat are Galactic longitude
-and latitude of the best fit extended source respectively.  The first
-error on $\sigma$ is statistical and the second is systematic (see
-Section~\ref{systematic_errors_on_extension}).  
-The errors on the integral fluxes and the spectral indices
-are statistical only.
-Pos Err is the error on
-the position of the source.  Vela X and the Centaurus A Lobes were
-not fit in our analysis but are included for completeness.
-}
-\end{deluxetable}
-
-  % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-  % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-  % 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
-  % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
-  % N/A                - P72Y1287         - 2FGL J0851.7-4635
-
-\clearpage
-\thispagestyle{empty}
-\begin{deluxetable}{lrrrrrrrrl}
-\tablecolumns{10}
-\tabletypesize{\small}
-\rotate
-\tablewidth{0pt}
-\tablecaption{Extension fit for the nine additional extended sources
-\label{new_ext_srcs_table}
-}
-\tablehead{
-\colhead{Name}&
-\colhead{\glon}&
-\colhead{\glat}&
-\colhead{$\sigma$}&
-\colhead{\ts}&
-\colhead{\tsext}&
-\colhead{Pos Err}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{Index}&
-\colhead{Counterpart}\\
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{}
-}
-
-\startdata
-\multicolumn{10}{c}{E$>$1 \gev} \\
-\hline
-2FGL\,J0823.0$-$4246                       &     260.32 &    $-$3.28 & $  0.37 \pm   0.03 \pm   0.02 $ &      322.2 &       48.0 &   0.02 & $    8.4 \pm     0.6$ & $   2.21 \pm    0.09$ &                  Puppis A \\
-2FGL\,J1627.0$-$2425c                      &     353.07 &      16.80 & $  0.42 \pm   0.05 \pm   0.16 $ &      139.9 &       32.4 &   0.04 & $    6.3 \pm     0.6$ & $   2.50 \pm    0.14$ &                 Ophiuchus \\
-\cutinhead{E$>$10 \gev}
-2FGL\,J0851.7$-$4635                       &     266.31 &    $-$1.43 & $  1.15 \pm   0.08 \pm   0.02 $ &      116.6 &       86.8 &   0.07 & $    1.3 \pm     0.2$ & $   1.74 \pm    0.21$ &                  Vela Jr.
-\\
-2FGL\,J1615.0$-$5051                       &     332.37 &    $-$0.13 & $  0.32 \pm   0.04 \pm   0.01 $ &       50.4 &       16.7 &   0.04 & $    1.0 \pm     0.2$ & $   2.19 \pm    0.28$ &         HESS\,J1616$-$508 \\
-2FGL\,J1615.2$-$5138                       &     331.66 &    $-$0.66 & $  0.42 \pm   0.04 \pm   0.02 $ &       76.1 &       46.5 &   0.04 & $    1.1 \pm     0.2$ & $   1.79 \pm    0.26$ &         HESS\,J1614$-$518 \\
-2FGL\,J1632.4$-$4753c                      &     336.52 &       0.12 & $  0.35 \pm   0.04 \pm   0.02 $ &       64.4 &       26.9 &   0.04 & $    1.4 \pm     0.2$ & $   2.66 \pm    0.30$ &         HESS\,J1632$-$478 \\
-2FGL\,J1712.4$-$3941\tablenotemark{(b)}    &     347.26 &    $-$0.53 & $  0.56 \pm   0.04 \pm   0.02 $ &       59.4 &       38.5 &   0.05 & $    1.2 \pm     0.2$ & $   1.87 \pm    0.22$ &        RX\,J1713.7$-$3946 \\
-2FGL\,J1837.3$-$0700c                      &      25.08 &       0.13 & $  0.33 \pm   0.07 \pm   0.05 $ &       47.0 &       18.5 &   0.07 & $    1.0 \pm     0.2$ & $   1.65 \pm    0.29$ &         HESS\,J1837$-$069 \\
-2FGL\,J2021.5+4026                         &      78.24 &       2.20 & $  0.63 \pm   0.05 \pm   0.04 $ &      237.2 &      128.9 &   0.05 & $    2.0 \pm     0.2$ & $   2.42 \pm    0.19$ &            $\gamma$-Cygni \\
-\enddata
-
-\tablenotetext{(a)}{
-Integral Flux in units of $10^{-9}$ \phflux and integrated in the fit
-energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
-}
-
-\tablenotetext{(b)}{
-The discrepancy in the best fit spectra of 2FGL\,J1712.4$-$3941 compared
-to \cite{rx_j1713_lat} is due to fitting over a different energy range.
-}
-
-\tablecomments{
-    The columns in this table have the same meaning as those in
-    Table~\ref{known_extended_sources}.
-    RX\,J1713.7$-$3946 and Vela Jr. were previously studied in dedicated publications \citep{rx_j1713_lat,vela_jr_lat}.
-}
-\end{deluxetable}
-
-\clearpage
-\thispagestyle{empty}
-\begin{deluxetable}{lrrrrrrrrrr}
-  \tabletypesize{\small}
-  \tablecolumns{11}
-  \rotate
-  \tablewidth{0pt}
-  \tablecaption{Dual localization, alternative PSF, and alternative approach to modeling the diffuse emission
-  \label{alt_diff_model_results}
-  }
-  \tablehead{
-  \colhead{Name}&
-  \colhead{$\ts_\pointlike$}&
-  \colhead{$\ts_\gtlike$}&
-  \colhead{$\ts_\altdiff$}&
-  \colhead{$\tsext_\pointlike$}&
-  \colhead{$\tsext_\gtlike$}&
-  \colhead{$\tsext_\altdiff$}&
-  \colhead{$\sigma$}&
-  \colhead{$\sigma_\altdiff$}&
-  \colhead{$\sigma_\altpsf$}&
-  \colhead{$\tsinc$}\\
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{}&
-  \colhead{(deg.)}&
-  \colhead{(deg.)}&
-  \colhead{(deg.)}&
-  \colhead{}
-  }
-  \startdata
-\multicolumn{11}{c}{E$>$1 \gev} \\
-\hline
-2FGL\,J0823.0$-$4246      &                331.9 &                322.2 &                356.0 &                 60.0 &                 48.0 &                 56.0 &                 0.37 &                 0.39 &                 0.39 &                 23.0 \\
-2FGL\,J1627.0$-$2425c     &                154.8 &                139.9 &                105.7 &                 39.4 &                 32.4 &                 24.8 &                 0.42 &
- 0.40 &                 0.58 &                 24.5 \\
-\cutinhead{E$>$10 \gev}
-2FGL\,J0851.7$-$4635      &                115.2 &                116.6 &                123.1 &                 83.9 &                 86.8 &                 89.8 &                 1.15 &                 1.16 &                 1.17 &                 15.5 \\
-2FGL\,J1615.0$-$5051\tablenotemark{(a)} &                 48.2 &                 50.4 &                 56.6 &                 15.2 &                 16.7 &                 17.8 &                 0.32 &                 0.33 &                 0.32 &                 13.1 \\
-2FGL\,J1615.2$-$5138      &                 75.0 &                 76.1 &                 83.8 &                 42.9 &                 46.5 &                 54.1 &                 0.42 &                 0.43 &                 0.43 &                 35.1 \\
-2FGL\,J1632.4$-$4753c     &                 64.5 &                 64.4 &                 66.8 &                 23.0 &                 26.9 &                 25.5 &                 0.35 &                 0.36 &                 0.37 &                 10.9 \\
-2FGL\,J1712.4$-$3941      &                 59.8 &                 59.4 &                 39.9 &                 38.4 &                 38.5 &                 30.7 &                 0.56 &                 0.55 &                 0.53 &                  2.7 \\
-2FGL\,J1837.3$-$0700c     &                 44.5 &                 47.0 &                 39.2 &                 17.6 &                 18.5 &                 16.1 &                 0.33 &                 0.32 &                 0.38 &                 10.8 \\
-2FGL\,J2021.5+4026        &                239.1 &                237.2 &                255.8 &                139.1 &                128.9 &                138.0 &                 0.63 &                 0.65 &                 0.59 &                 37.3 \\
-  \enddata
-
-\tablenotetext{(a)}{
-% Fit from /u/gl/lande/work/fermi/extended_catalog/2FGL/individual_sources/HESS_J1616-508/v4/iteration_v2/r
-Using \pointlike, \tsext for 2FGL\,J1615.0$-$5051 was sligthly below
-16 when the source was fit in the 10 \gev to 100 \gev energy range. To
-confirm the extension measure, the extension was refit in \pointlike
-using a slightly lower energy.  In the 5.6 \gev to 100 \gev energy range,
-we obtained a consistent extension and \tsext=28.0.  In the rest of
-this paper, we quote the $E>10 \gev$ results for consistency with the
-other sources.
-}
-
-\tablecomments{
-$\ts_\pointlike$, $\ts_\gtlike$, and $\ts_\altdiff$ are the test
-statistic values from \pointlike, \gtlike, and \gtlike with the alternative
-approach to modeling the diffuse emission respectively.  $\tsext_\pointlike$, $\tsext_\gtlike$,
-and $\tsext_\altdiff$ are the TS values from \pointlike, \gtlike, and \gtlike with the alternative 
-approach to modeling the diffuse emission respectively.  $\sigma$, $\sigma_\altdiff$, and $\sigma_\altpsf$
-are the fit sizes assuming
-a radially-symmetric uniform disk model
-with the standard analysis, the alternative 
-approach to modeling the diffuse emission, and the alternative PSF respectively.  
-}
-\end{deluxetable}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Puppis_A_color.eps}
-    \else
-      \plotone{source_plots/source_Puppis_A_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v8/run.py
-  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
-  of 2FGL\,J0823.0$-$4246 smoothed by a 0\fdg1 2D
-  Gaussian kernel.  The triangular marker 
-  (colored red in the online version)
-  represents the 2FGL position of this source.  The plus-shaped
-  marker and the circle (colored
-  red) represent 
-  the best fit position and extension of this source assuming a
-  radially-symmetric uniform disk model.  The two 
-  star-shaped markers (colored
-  green) represent 2FGL sources that were
-  removed from the background model.
-  The lower right inset is the model predicted emission from a point-like
-  source with the same spectrum as 2FGL\,J0823.4$-$4305 smoothed by the
-  same kernel.  This source is spatially coincident with the Puppis A
-  SNR. The light blue contours correspond to the X-ray image of Puppis
-  A observed by \rosat \citep{rosat_puppis_a}.
-  }\label{1FGL_J0823.3-4248}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/snr_seds_color.eps}
-    \else
-      \plotone{summary_plots/snr_seds_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v4/plot_seds/plot_snr_seds.py
-    \caption{
-    The spectral energy distribution of the extended sources 
-    Puppis A (2FGL\,J0823.0$-$4246) and $\gamma$-Cygni 
-    (2FGL\,J2021.5+4026).
-    The lines (colored red in the online version)
-    are the best fit power-law spectral models of
-    these sources.
-    The spectral errors are statistical only.
-    The upper limit is at the 95\% confidence level.
-    }
-    \label{snr_seds}
-  \end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Ophiuchus_color.eps}
-    \else
-      \plotone{source_plots/source_Ophiuchus_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of (a) the region
-  around 2FGL\,J1627.0$-$2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
-  also the emission from 2FGL\,J1625.7$-$2526
-  subtracted.  The triangular marker 
-  (colored red in the
-  online version) represents the 2FGL position of this source.
-  The plus-shaped marker and the circle (colored red) 
-  represent the best fit position and extension of this
-  source assuming a radially-symmetric uniform disk model
-  and the black cross represents a background 2FGL source. 
-  The
-  contours in (a) correspond to the 100 $\mu$m image observed by
-  IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
-  CO ($J=1\rightarrow 0$) emission integrated from $-$8 $\km\,\s^{-1}$
-  to 20 $\km\,\s^{-1}$.  They are from \cite{co_rho_ophiuci}, were cleaned using
-  the moment-masking technique \citep{masking_moment_2011}, and have
-  been smoothed by a 0\fdg25 2D Gaussian kernel.
-  }\label{1FGL_J1628.6-2419c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Vela_Jr_color.eps}
-    \else
-      \plotone{source_plots/source_Vela_Jr_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v8/run.py
-  \caption{A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  2FGL\,J0851.7$-$4635 smoothed by a 0\fdg25 2D Gaussian
-  kernel. The triangular marker (colored red in the electronic version)
-  represents the 2FGL position of this source.  The plus-shaped marker
-  and the circle (colored red) are the best fit position and extension of
-  this source assuming a radially-symmetric uniform disk model.
-  The three black crosses represent background 2FGL sources
-  and the three star-shaped markers (colored green) represent other 2FGL sources
-  that were removed from the background model 
-  The circular and square-shaped
-  marker (colored blue) represents the 2FGL and relocalized position of another 2FGL source.  
-  This extended source is spatially
-  coincident with the Vela Jr. SNR.  The contours (colored light blue)
-  correspond to the \tev image of Vela Jr.
-  \citep{vela_jr_hess}.
-  }\label{Vela_Jr}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_HESS_J1614-518_color.eps}
-    \else
-      \plotone{source_plots/source_HESS_J1614-518_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v8/run.py
-  \caption{
-    A diffuse-emission-subtracted 10 \gev to 100 \gev counts
-    map of 2FGL\,J1615.0$-$5051 (upper left)
-    and 2FGL\,J1615.2$-$5138 (lower right) smoothed by a 0\fdg1
-    2D Gaussian kernel.  The triangular markers (colored red in the
-    electronic version) represent the 2FGL positions of these sources.
-    The cross-shaped markers and the
-    circles (colored red) represent the best fit
-    positions and extensions of these sources assuming a radially
-    symmetric uniform disk model.  
-    The two black crosses represent  background 2FGL sources and
-    the star-shaped
-    marker (colored green) represents another 2FGL source that was removed from the background
-    model.  The contours (colored light blue) correspond to the \tev
-    image of HESS\,J1616$-$508 (left) and HESS\,J1614$-$518 (right)
-    \citep{hess_plane_survey}.   
-    }\label{1FGL_J1613.6-5100c}
-\end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/hess_seds_color.eps}
-    \else
-      \plotone{summary_plots/hess_seds_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v4/plot_seds/plot_hess_seds.py
-    \caption{
-    The spectral energy distribution of four extended
-    sources associated with unidentified
-    extended \tev sources.  The black points
-    with circular markers are obtained by the LAT. The points with
-    plus-shaped markers (colored red in the electronic version) are
-    for the associated H.E.S.S sources.  (a) the
-    LAT SED of 2FGL\,J1615.0$-$5051 together with the H.E.S.S. SED
-    of HESS\,J1616$-$508. (b) 2FGL\,J1615.2$-$5138
-    and HESS\,J1614$-$518. (c) 2FGL\,J1632.4$-$4753c
-    and HESS\,J1632$-$478. (d) 2FGL\,J1837.3$-$0700c
-    and HESS\,J1837$-$069. The H.E.S.S. data points are from
-    \citep{hess_plane_survey}. Both LAT and H.E.S.S. spectral errors are
-    statistical only.}
-    \label{hess_seds}
-  \end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_HESS_J1632-478_color.eps}
-    \else
-      \plotone{source_plots/source_HESS_J1632-478_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of
-  2FGL\,J1632.4$-$4753c (a) smoothed by a 0\fdg1 2D Gaussian
-  kernel and (b) with the emission from the background sources subtracted.  
-  The triangular marker (colored red in the electronic version)
-  represents the 2FGL position of this source.  The plus-shaped marker
-  and the circle (colored red) are the best fit position and extension of
-  2FGL\,J1632.4$-$4753c assuming a radially-symmetric uniform disk model.  
-  The four black crosses represent background 2FGL
-  sources subtracted in (b).  The 
-  circular and square-shaped markers (colored blue) represent 
-  the 2FGL and relocalized positions respectively of two
-  additional background 2FGL sources subtracted in (b).
-  The star-shaped marker (colored green) represents another 2FGL
-  source that was removed from the background model.  
-  The contours (colored light blue) correspond to the \tev image of
-  HESS\,J1632$-$478 \citep{hess_plane_survey}.
-  }\label{1FGL_J1632.9-4802c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_RX_J1713.7-3946_color.eps}
-    \else
-      \plotone{source_plots/source_RX_J1713.7-3946_bw.eps}
-    \fi
-    % this plot came from
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map
-  of 2FGL\,J1712.4$-$3941 (a) smoothed by a 0\fdg15 2D
-  Gaussian kernel and (b) with the emission from the background sources
-  subtracted.  This source is spatially coincident with RX\,J1713.7$-$3946
-  and was recently studied in \cite{rx_j1713_lat}.  The triangular marker
-  (colored red in the online version) represents the 2FGL position of
-  this source.  The plus-shaped marker and the circle (colored red) are
-  the best fit position and extension of this source assuming a radially
-  symmetric uniform disk model.  
-  The two black crosses represent background 2FGL sources subtracted in (b).
-  The contours (colored light blue)
-  correspond to the \tev image \citep{rx_j1713_hess}.  
-  }\label{2FGL_J1712.4-3941}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_HESS_J1837-069_color.eps}
-    \else
-      \plotone{source_plots/source_HESS_J1837-069_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of the
-  region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg15 2D Gaussian
-  kernel and (b) with the emission from the background sources subtracted.
-  The triangular marker (colored red in the online version) represents
-  the 2FGL
-  position of this source. 
-  The plus-shaped marker and 
-  the circle (colored red) represent the best fit position and extension
-  of 2FGL\,J1837.3$-$0700c assuming a radially-symmetric uniform disk model. 
-  The circular and square-shaped markers (colored
-  blue) represent the 2FGL and the relocalized positions respectively of
-  two background 2FGL sources subtracted in (b).  The star-shaped marker
-  (colored green) represents a 2FGL source that was removed from the
-  background model.  The contours (colored light blue) correspond to
-  the \tev image of HESS\,J1837$-$069
-  \citep{hess_plane_survey}.
-  The diamond-shaped marker (colored orange) represents the position of PSR\,J1838$-$0655
-  and the hexagonal-shaped marker (colored purple) represents the position AX\,J1837.3$-$0652
-  \citep{pulsations_HESS_J1837-069}.
-  }\label{1FGL_J1837.5-0659c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
-      \plotone{source_plots/source_Gamma_Cygni_color.eps}
-    \else
-      \plotone{source_plots/source_Gamma_Cygni_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Gamma_Cygni/v8/run.py
-  \caption{A diffuse-emission-subtracted 
-  10 \gev to 100 \gev counts map of the
-  region around 2FGL\,J2021.5+4026 smoothed by a 0\fdg1 2D Gaussian
-  kernel. The triangular marker (colored red in the online version)
-  represents the 2FGL position of this source.  The plus-shaped
-  marker and the circle (colored red) represent the best fit position
-  and extension of 2FGL\,J2021.5+4026 assuming a radially-symmetric
-  uniform disk model.  
-  The star-shaped marker (colored green)
-  represents a 2FGL source that was removed from the background model.
-  2FGL\,J2021.5+4026
-  is spatially coincident with the $\gamma$-Cygni SNR.  The contours
-  (colored light blue) correspond to the 408MHz image of $\gamma$-Cygni
-  observed by the Canadian Galactic Plane Survey \citep{canadian_galactic_plane_survey}.
-  }\label{1FGL_J2020.0+4049}
-\end{figure}
-
-\clearpage
-  \begin{figure}
-      \ifcolorfigure
-      \plotone{summary_plots/allsky_extended_sources_color.eps}
-      \else
-      \plotone{summary_plots/allsky_extended_sources_bw.eps}
-      \fi
-      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/allsky/v2/run.py
-      \caption{The 21
-      spatially extended sources detected by the LAT
-      at \gev energies 
-      with 2 years of data.  The twelve extended sources included in
-      2FGL are represented by the circular markers (colored red in the online
-      version).  The nine new extended sources are represented by
-      the triangular markers (colored orange).
-      The source positions are overlaid on a 100 \mev to 100 \gev 
-      Aitoff projection sky map of the LAT data in Galactic coordinates.
-}
-\label{allsky_extended_sources}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/gev_vs_tev_plot_color.eps}
-    \else
-      \plotone{summary_plots/gev_vs_tev_plot_bw.eps}
-      \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_tev_gev_sizes/v5/run.py
-    \caption{
-    A comparison of the sizes of extended sources detected at
-    both \gev and \tev energies.  The \tev sizes of W30,
-    2FGL\,J1837.3$-$0700c, 2FGL\,J1632.4$-$4753c, 2FGL\,J1615.0$-$5051,
-    and 2FGL\,J1615.2$-$5138 are from \cite{hess_plane_survey}.
-    The \tev sizes of MSH\,15$-$52, HESS\,J1825$-$137,
-    Vela X, Vela Jr., RX\,J1713.7$-$3946 and W28 are from
-    \cite{msh_15_52_hess,hess_j1825_hess,vela_x_hess,vela_jr_hess,rx_j1713_hess,w28_hess}.
-    The \tev size of IC~443 is from \cite{ic443_veritas} and
-    W51C is from \cite{w51c_with_magic_at_fermi_symposium}.  The \tev
-    sizes of MSH\,15$-$52, HESS\,J1614$-$518, HESS\,J1632$-$478, and
-    HESS\,J1837$-$069 have only been reported with an elliptical 2D
-    Gaussian fit and so the plotted sizes are the geometric 
-    mean of the semi-major and semi-minor axis.
-    The LAT extension of
-    Vela X is from \cite{velax}. 
-    The \tev sources were fit assuming a 2D Gaussian surface brightness profile
-    so the plotted \gev and \tev extensions were first converted to
-    \rsixeight (see Section~\ref{compare_source_size}).  
-    Because of
-    their large sizes, the shape of RX\,J1713.7$-$3946 and Vela Jr.
-    were not directly fit at \tev energies and so are not included
-    in this comparison. On the other hand, dedicated LAT publications on
-    these sources showed that their morphologies are consistent
-    \citep{rx_j1713_lat,vela_jr_lat}.
-    The LAT
-    extension errors are the statistical and systematic errors added
-    in quadrature. 
-}\label{gev_vs_tev_plot}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/gev_vs_tev_histogram_color.eps}
-    \else
-      \plotone{summary_plots/gev_vs_tev_histogram_bw.eps}
-    \fi
-    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/extension_histogram/v5/extension_histogram.py
-    \caption{
-    The distributions of the sizes of 18 extended LAT sources
-    at \gev energies
-    (colored blue in the electronic version) and the sizes of the
-    40 extended H.E.S.S. sources at \tev energies
-    (colored red).  
-    The H.E.S.S. sources were fit with a 2D Gaussian surface
-    brightness profile so the LAT and H.E.S.S. sizes were first converted
-    to \rsixeight. 
-    The \gev size of Vela X is taken from \cite{velax}.  
-    Because of their large sizes, the shape of RX\,J1713.7$-$3946 and
-    Vela Jr. were not directly fit at \tev energies
-    and are not included in this comparison.
-    Centaurus A is not included because of its large size.
-    }\label{gev_vs_tev_histogram}
-  \end{figure}
-
-\clearpage
-\begin{figure}
-    \ifcolorfigure
-      \plotone{summary_plots/compare_index_2FGL_color.eps}
-    \else
-      \plotone{summary_plots/compare_index_2FGL_bw.eps}
-    \fi
-    % plot taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_index_2fgl/v3/run.py
-    \caption{
-    The distribution of spectral indices of the 1873 2FGL sources
-    (colored red in the electronic version) and the 21 spatially extended
-    sources (colored blue).  The index of Centaurus A is taken from
-    \cite{second_cat} and the index of Vela X is taken from \cite{velax}.
-    }\label{compare_index_2FGL}
-  \end{figure}
-
-\end{document}
+The authors acknowledge the use of
+HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.

### 2012-01-19 pwncatalog/PWNCAT2/paper/sections/analysis_of_the_fermi_lat_data.tex
update

\section{Analysis of the \fermi-LAT data}

Analysis goes here\ldots

### 2012-01-19 pwncatalog/PWNCAT2/paper/sections/off_peak_phase_selection.tex
update

\section{Off-peak Phase Selection}

Off-peak goes here\ldots

### 2012-01-21 pwncatalog/PWNCAT2/paper/sections/results.tex
new tables

\section{Results}

Results goes here\ldots

\input{tables/off_pulse_all_energy.tex}

\input{tables/off_pulse_each_energy.tex}

\input{tables/off_pulse_cutoff_test.tex}

### 2012-01-21 pwncatalog/PWNCAT2/code/summarize/lande_table.py
better table code

@@ -1,17 +1,23 @@
 from os.path import join as j
 import StringIO
+from textwrap import dedent
 import shutil
-from toolbag import OrderedDefaultdict
+from lande_toolbag import OrderedDefaultdict
 import os.path
 import tempfile
 
 import yaml
 import asciitable
 
-fitdir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT1/fits/analyze_v45/analysis/'
-savedir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT1/fits/analyze_v45/'
+#fitdir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT1/fits/analyze_v45/analysis/'
+#savedir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT1/fits/analyze_v45/'
 
-def write_latex(table, filename, **kwargs):
+fitdir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT2/analyze_psr/v4/analysis_no_plots/'
+savedir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT2/analyze_psr/v4/tables'
+
+if not os.path.exists(savedir): os.makedirs(savedir)
+
+def write_latex(table, filebase, **kwargs):
 
     outtable=StringIO.StringIO()
 
@@ -22,26 +28,19 @@ def write_latex(table, filename, **kwargs):
                     )
     t=outtable.getvalue()
 
-    print t
-    file=r"""
-    \documentclass{aastex}
-    \usepackage{amsmath}
-    \begin{document}
-    %s
-    \end{document}
-    """ % t
+    os.chdir(savedir)
 
-    cwd=os.getcwd()
-    tempdir=tempfile.mkdtemp()
-    os.chdir(tempdir)
-    open('table.tex','w').write(file)
+    open('%s.tex' % filebase,'w').write(t)
 
-    os.system('pdflatex table.tex')
+    open('temp.tex','w').write(dedent(r"""
+        \documentclass{aastex}
+        \usepackage{amsmath}
+        \begin{document}
+        \include{%s}
+        \end{document}""" % filebase))
 
-    os.chdir(cwd)
-    shutil.copy('%s/table.pdf' % tempdir,
-                filename)
-
+    os.system('pdflatex temp.tex')
+    shutil.move('temp.pdf','%s.pdf' % filebase)
 
[…]

### 2012-01-21 pwncatalog/PWNCAT2/code/summarize/lande_table.py
better table code

@@ -9,13 +9,15 @@ import tempfile
 import yaml
 import asciitable
 
-#fitdir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT1/fits/analyze_v45/analysis/'
-#savedir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT1/fits/analyze_v45/'
-
 fitdir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT2/analyze_psr/v4/analysis_no_plots/'
 savedir='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT2/analyze_psr/v4/tables'
 
 if not os.path.exists(savedir): os.makedirs(savedir)
+
+def table_name(pwn):
+    pwn = pwn.replace('PSR','')
+    pwn = pwn.replace('-','$-$')
+    return pwn
 
 def write_latex(table, filebase, **kwargs):
 
@@ -28,6 +30,16 @@ def write_latex(table, filebase, **kwargs):
                     )
     t=outtable.getvalue()
 
+    lines = t.split('\n')
+    if lines[-1] == '': 
+        lines=lines[0:-1]
+
+    header = lines[0]
+    footer= lines[-1]
+
+    t = '\n'.join(lines[1:-1])
+
+
     os.chdir(savedir)
 
     open('%s.tex' % filebase,'w').write(t)
@@ -36,8 +48,10 @@ def write_latex(table, filebase, **kwargs):
         \documentclass{aastex}
         \usepackage{amsmath}
         \begin{document}
-        \include{%s}
-        \end{document}""" % filebase))
+        %s
+        \input{%s}
+        %s
+        \end{document}""" % (header,filebase,footer)))
 
     os.system('pdflatex temp.tex')
     shutil.move('temp.pdf','%s.pdf' % filebase)
@@ -61,42 +75,49 @@ def all_energy_table(pwnlist):
     table = OrderedDefaultdict(list)
 
     flux_name=r'$F_{0.1-316}$'
+    ts_name='TS'
     gamma_name=r'$\Gamma$'
 
     for pwn in pwnlist:
         print pwn,j(fitdir,pwn,'results_%s.yaml' % pwn)
 
+        table['PSR'].append(table_name(pwn))
+
         results = get_results(pwn)
-        if results is None: continue
 
-        pl=results['at_pulsar']['pointlike']
-        gt=results['at_pulsar']['gtlike']
[…]

### 2012-01-21 pwncatalog/PWNCAT2/paper/sections/results.tex
fixing tables
new appendix

@@
 
+\tabref{off_pulse_all_energy} shows the results of the all energy analysis of the off-peak emission for each pulsar.
+
+\tabref{off_pulse_each_energy} shows the results of the analysis in separate energy bins of each pulsar.
+
+\tabref{off_pulse_cutoff_test} shows the results of the cutoff test for pulsars with significant low-energy emission.
+
+\begin{deluxetable}{cccc}
+\tabletypesize{\scriptsize}
+\tablecaption{All Energy spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
+\label{tab:off_pulse_all_energy}
+}
 \input{tables/off_pulse_all_energy.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}
 
+\begin{deluxetable}{ccccccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Energy bin spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
+\label{tab:off_pulse_each_energy}
+}
 \input{tables/off_pulse_each_energy.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}
 
+\begin{deluxetable}{lrrrr}
+\tabletypesize{\scriptsize}
+\tablecaption{Spectral fitting of pulsar wind nebula candidates with low energy component
+\label{tab:off_pulse_cutoff_test}
+}
 \input{tables/off_pulse_cutoff_test.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/summarize/table/all_energy_table.py
update

@@ -1,56 +1,0 @@
-from table_helper import get_pwnlist,get_results,table_name,write_latex
-from lande_toolbag import OrderedDefaultdict
-
-def all_energy_table(pwnlist):
-
-    table = OrderedDefaultdict(list)
-
-    flux_name=r'$F_{0.1-316}$'
-    ts_name='TS'
-    gamma_name=r'$\Gamma$'
-
-    for pwn in pwnlist:
-        table['PSR'].append(table_name(pwn))
-
-        results = get_results(pwn)
-
-        if results is None: 
-            table[ts_name].append('None')
-            table[flux_name].append('None')
-            table[gamma_name].append('None')
-        else:
-
-            pl=results['at_pulsar']['pointlike']
-            gt=results['at_pulsar']['gtlike']
-
-            ts=max(gt['TS'],0)
-            table[ts_name].append('%.1f' % ts)
-
-            if ts > 25:
-                flux=gt['flux']['flux']
-                flux_err=gt['flux']['flux_err']
-                table[flux_name].append('$%.2f \pm %.2f$' % (flux/1e-9,flux_err/1e-9) )
-            else:
-                if gt['upper_limit'] != -1:
-                    ul=gt['upper_limit']['flux']
-                    table[flux_name].append(r'$<%.2f$' % (ul/1e-9))
-                else:
-                    table[flux_name].append('None')
-
-
-            index=-1*gt['model']['Index']
-            index_err=-1*gt['model']['Index_err']
-
-            table[gamma_name].append('$%.2f \pm %.2f$' % (index,index_err) if ts > 25 else r'\nodata')
-
-    write_latex(table,
-                filebase='off_pulse_all_energy',
-                latexdict = dict(#caption=r'All Energy spectral fit for the %s LAT-detected Pulsars'  % len(pwnlist),
-                                 #preamble=r'\tabletypesize{\scriptsize}',
-                                 units={
-                                     flux_name:r'($10^{-9} \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',
-                                 }))
-
-
-pwnlist=get_pwnlist()
-all_energy_table(pwnlist)

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/summarize/table/cutoff_table.py

@@ -1,61 +1,0 @@
-from table_helper import get_pwnlist,get_results,table_name,write_latex
-from lande_toolbag import OrderedDefaultdict
-
-def cutoff_table(pwnlist,looppwn):
-
-    table = OrderedDefaultdict(list)
-
-    flux_name = r'$G_{0.1-316}$'
-    index_name = r'$\Gamma$'
-    cutoff_name = r'$E_\text{cutoff}$'
-    ts_cutoff_name = r'$\text{TS}_\text{cutoff}$'
-
-    for pwn in looppwn:
-        results = get_results(pwn)
-        if results is None: continue
-
-        table['PSR'].append(table_name(pwn))
-
-        cutoff=results['at_pulsar']['gtlike']['test_cutoff']
-
-        if cutoff != -1:
-
-            flux=cutoff['flux_1']['eflux']
-            flux_err=cutoff['flux_1']['eflux_err']
-            table[flux_name].append('$%.2f \pm %.2f$' % (flux/1e-12,flux_err/1e-12))
-            index=-1*cutoff['model_1']['Index1']
-            index_err=cutoff['model_1']['Index1_err']
-            table[index_name].append('$%.2f \pm %.2f$' % (index,index_err))
-            cutoff_energy=cutoff['model_1']['Cutoff']
-            cutoff_energy_err=cutoff['model_1']['Cutoff_err']
-            table[cutoff_name].append('$%.2f \pm %.2f$' % (cutoff_energy/1000,cutoff_energy_err/1000))
-            ts_cutoff = max(cutoff['TS_cutoff'],0)
-            table[ts_cutoff_name].append('%.1f' % ts_cutoff)
-        else:
-            table[flux_name].append('None')
-            table[index_name].append('None')
-            table[cutoff_name].append('None')
-            table[ts_cutoff_name].append('None')
-
-    write_latex(table,
-                filebase='off_pulse_cutoff_test',
-                latexdict = dict(#caption=r'Spectral fitting of pulsar wind nebula candidates with low energy component.',
-                                 #col_align=r'lrrrr',
-                                 #preamble=r'\tabletypesize{\scriptsize}',
-                                 units={
-                                     flux_name:r'($10^{-12}$\,erg\,cm$^{-2}$\,s$^{-1}$)',
-                                     cutoff_name:r'(GeV)',
-                                 }))
-
-
-cutoff_candidates = ['PSRJ0034-0534', 
[…]

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/summarize/table/each_energy_table.py

@@ -1,60 +1,0 @@
-from table_helper import get_pwnlist,get_results,table_name,get_sed,write_latex
-from lande_toolbag import OrderedDefaultdict
-
-def each_energy_table(pwnlist):
-
-    table = OrderedDefaultdict(list)
-
-    TS1_name = '$TS_{0.1-1}$'
-    TS2_name = '$TS_{1-10}$'
-    TS3_name = '$TS_{10-316}$'
-
-    flux1_name = '$F_{0.1-1}$'
-    flux2_name = '$F_{1-10}$'
-    flux3_name = '$F_{10-316}$'
-
-    for pwn in pwnlist:
-
-        results = get_results(pwn)
-        table['PSR'].append(table_name(pwn))
-
-        if results is None or get_sed(pwn,'1bpd','at_pulsar') == {}: 
-            table[TS1_name].append('None')
-            table[flux1_name].append('None')
-
-            table[TS2_name].append('None')
-            table[flux2_name].append('None')
-
-            table[TS3_name].append('None')
-            table[flux3_name].append('None')
-        else:
-
-            sed = get_sed(pwn,'1bpd','at_pulsar')
-            ts = sed['Test_Statistic']
-            flux = sed['Ph_Flux']['Value']
-            flux_err = sed['Ph_Flux']['Error']
-            ul = sed['Ph_Flux']['Upper_Limit']
-
-            ts = [i if i > 0 else 0 for i in ts]
-
-            table[TS1_name].append('%.1f' % ts[0])
-            table[flux1_name].append('$%.2f \pm %.2f$' % (flux[0]/1e-9,flux_err[0]/1e-9) if ts[0] > 25 else '$<%.2f$' % (ul[0]/1e-9))
-
-            table[TS2_name].append('%.1f' % ts[1])
-            table[flux2_name].append('$%.2f \pm %.2f$' % (flux[1]/1e-9,flux_err[1]/1e-9) if ts[1] > 25 else r'$<%.2f$' % (ul[1]/1e-9))
-
-            table[TS3_name].append('%.1f' % ts[2])
-            table[flux3_name].append('$%.2f \pm %.2f$' % (flux[2]/1e-9,flux_err[2]/1e-9) if ts[2] > 25 else r'$<%.2f$' % (ul[2]/1e-9))
-
-    write_latex(table,
-                filebase='off_pulse_each_energy',
-                latexdict = dict(#caption=r'Energy bin spectral fit for the %s LAT-detected Pulsars'  % len(pwnlist),
[…]

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/summarize/table/phase_table.py

@@ -1,31 +1,0 @@
-from table_helper import get_pwnlist,get_results,table_name,write_latex
-from lande_toolbag import OrderedDefaultdict
-
-from os.path import join as j
-def get_phase(pwn):
-    folder='$pwndata/off_peak/off_peak_bb/pwncat2/v1/'
-    file=j(folder,pwn,'v1','results_%s.yaml' % pwn)
-    r=yaml.load(file)
-    phase=r['bayesian_blocks']['off_peak']
-    return phase
-
-def all_energy_table(pwnlist):
-
-    table = OrderedDefaultdict(list)
-    phase_name='PHASE'
-
-    for pwn in pwnlist:
-        table['PSR'].append(table_name(pwn))
-
-        phase=get_pase(pwn)
-        table[phase_name]=str(phase)
-
-    write_latex(table,
-                filebase='off_peak_phase_range',
-                latexdict = dict(units={
-                                     #flux_name:r'($10^{-9} \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',
-                                 }))
-
-
-pwnlist=get_pwnlist()
-all_energy_table(pwnlist)

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/summarize/table/table_helper.py

@@ -1,76 +1,0 @@
-from os.path import join as j
-from os.path import expandvars
-import StringIO
-from textwrap import dedent
-import shutil
-import os.path
-
-import yaml
-import asciitable
-
-base='$pwndata/analyze_psr/v7/'
-
-fitdir=j(base,'analysis_no_plots/')
-savedir=j(base,'tables')
-
-if not os.path.exists(savedir): os.makedirs(savedir)
-
-def table_name(pwn):
-    pwn = pwn.replace('PSR','')
-    pwn = pwn.replace('-','$-$')
-    return pwn
-
-def write_latex(table, filebase, **kwargs):
-
-    outtable=StringIO.StringIO()
-
-    asciitable.write(table, outtable, 
-                     Writer=asciitable.AASTex,
-                     names=table.keys(),
-                     **kwargs
-                    )
-    t=outtable.getvalue()
-
-    lines = t.split('\n')
-    if lines[-1] == '': 
-        lines=lines[0:-1]
-
-    header = lines[0]
-    footer= lines[-1]
-
-    t = '\n'.join(lines[1:-1])
-
-
-    os.chdir(savedir)
-
-    open('%s.tex' % filebase,'w').write(t)
-
-    open('temp.tex','w').write(dedent(r"""
-        \documentclass{aastex}
-        \usepackage{amsmath}
-        \begin{document}
-        %s
-        \input{%s}
-        %s
-        \end{document}""" % (header,filebase,footer)))
-
-    os.system('pdflatex temp.tex')
-    shutil.move('temp.pdf','%s.pdf' % filebase)
-
-def get_results(pwn):
-    f = j(fitdir,pwn,'results_%s.yaml' % pwn)
-    if not os.path.exists(f): return None
-    results = yaml.load(open(f))
-
-    if not results.has_key('at_pulsar') or not results['at_pulsar'].has_key('gtlike'):
-        return None
-    return results
-
-def get_sed(pwn,binning,hypothesis):
-    filename=j(fitdir,pwn,'seds','sed_gtlike_%s_%s_%s.yaml' % (binning, hypothesis, pwn))
-    return yaml.load(open(filename))
-
-def get_pwnlist():
-    pwnlist=sorted(yaml.load(open(expandvars('$pwncode/pwndata/pwncat2_data_lande.yaml'))).keys())
-    return pwnlist
-

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/publication_plots/off_pulse_selection/plot_off_pulse_select.py
update

@@ -43,7 +43,7 @@ fig=P.figure(None,figsize=(6,6))
 
 fig.subplots_adjust(hspace=.25,wspace=.25, left=0.15, right=0.9, top=0.9, bottom=0.1)
 
-pwndata=yaml.load(open(expandvars('$pwn/pwndata/pwncat2_data_lande.yaml')))
+pwndata=yaml.load(open(expandvars('$pwncode/pwndata/pwncat2_data_lande.yaml')))
 
 
 off_peak_selection='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT2/off_peak/off_peak_bb/pwncat2/v1'
@@ -110,15 +110,15 @@ for i,pwn in enumerate(pwnlist):
     def add_text(text,loc,i):
         letter = chr(i+97)
 
-        _text = '(%s) %s' % (letter, text.replace('PSR',''))
+        _text = '(%s) %s' % (letter, text.replace('PSR','').replace('-','$-$'))
 
         at = AnchoredText(_text, loc=loc, frameon=False)
         axes.add_artist(at)
         at.txt._text.set_path_effects([withStroke(foreground="w",linewidth=3)])
     add_text(pwn,2,i)
 
-    bb_phase.axvspan(axes=axes, phase_offsets=[0,1], fill=True, edgecolor='0.5', 
-                     linewidth=linewidth, facecolor='0.75', linestyle='dashed')
+    bb_phase.axvspan(axes=axes, phase_offsets=[0,1], fill=True, edgecolor='none', 
+                     linewidth=linewidth, facecolor='0.75')
 
 
 # if there are not plots alow all of the bottom, overlay
@@ -130,9 +130,10 @@ while i < nrows*ncols:
     i+=1
 
 
+base='off_pulse_select'
 if args.bw:
-    P.savefig('off_pulse_select_bw.pdf')
-    P.savefig('off_pulse_select_bw.eps')
+    P.savefig('%s_bw.pdf' % base)
+    P.savefig('%s_bw.eps' % base)
 else:
-    P.savefig('off_pulse_select_color.pdf')
-    P.savefig('off_pulse_select_color.eps')
+    P.savefig('%s_color.pdf' % base)
+    P.savefig('%s_color.eps' % base)

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/off_peak/off_peak_bb.py
update

@@ -162,8 +162,7 @@ class OptimizePhases(object):
 
 
 
-def find_offpeak(ft1,name,cel,pwncat1phase, emax=300000):
-    skydir = SkyDir(*cel)
+def find_offpeak(ft1,name,skydir,pwncat1phase, emax=300000):
 
     # First, find energy and radius that maximize H test.
 
@@ -215,7 +214,6 @@ def find_offpeak(ft1,name,cel,pwncat1phase, emax=300000):
             emin = opt.optimal_emin,
             emax = emax,
             rad = opt.optimal_rad,
-            cel = cel
             )
         )
 
@@ -244,5 +242,5 @@ if __name__ == '__main__':
     else:
         pwncat1phase=None
 
-    cel = d['cel']
-    find_offpeak(ft1,name,cel,pwncat1phase=pwncat1phase)
+    skydir = SkyDir(*d['cel'])
+    find_offpeak(ft1,name,skydir,pwncat1phase=pwncat1phase)

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/table/all_energy_table.py
update

@@ -1,0 +1,56 @@
+from table_helper import get_pwnlist,get_results,table_name,write_latex
+from lande_toolbag import OrderedDefaultdict
+
+def all_energy_table(pwnlist):
+
+    table = OrderedDefaultdict(list)
+
+    flux_name=r'$F_{0.1-316}$'
+    ts_name='TS'
+    gamma_name=r'$\Gamma$'
+
+    for pwn in pwnlist:
+        table['PSR'].append(table_name(pwn))
+
+        results = get_results(pwn)
+
+        if results is None: 
+            table[ts_name].append('None')
+            table[flux_name].append('None')
+            table[gamma_name].append('None')
+        else:
+
+            pl=results['at_pulsar']['pointlike']
+            gt=results['at_pulsar']['gtlike']
+
+            ts=max(gt['TS'],0)
+            table[ts_name].append('%.1f' % ts)
+
+            if ts > 25:
+                flux=gt['flux']['flux']
+                flux_err=gt['flux']['flux_err']
+                table[flux_name].append('$%.2f \pm %.2f$' % (flux/1e-9,flux_err/1e-9) )
+            else:
+                if gt['upper_limit'] != -1:
+                    ul=gt['upper_limit']['flux']
+                    table[flux_name].append(r'$<%.2f$' % (ul/1e-9))
+                else:
+                    table[flux_name].append('None')
+
+
+            index=-1*gt['model']['Index']
+            index_err=-1*gt['model']['Index_err']
+
+            table[gamma_name].append('$%.2f \pm %.2f$' % (index,index_err) if ts > 25 else r'\nodata')
+
+    write_latex(table,
+                filebase='off_peak_all_energy',
+                latexdict = dict(#caption=r'All Energy spectral fit for the %s LAT-detected Pulsars'  % len(pwnlist),
+                                 #preamble=r'\tabletypesize{\scriptsize}',
+                                 units={
+                                     flux_name:r'($10^{-9} \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',
+                                 }))
+
+
+pwnlist=get_pwnlist()
+all_energy_table(pwnlist)

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/table/cutoff_table.py

@@ -1,0 +1,61 @@
+from table_helper import get_pwnlist,get_results,table_name,write_latex
+from lande_toolbag import OrderedDefaultdict
+
+def cutoff_table(pwnlist,looppwn):
+
+    table = OrderedDefaultdict(list)
+
+    flux_name = r'$G_{0.1-316}$'
+    index_name = r'$\Gamma$'
+    cutoff_name = r'$E_\text{cutoff}$'
+    ts_cutoff_name = r'$\text{TS}_\text{cutoff}$'
+
+    for pwn in looppwn:
+        results = get_results(pwn)
+        if results is None: continue
+
+        table['PSR'].append(table_name(pwn))
+
+        cutoff=results['at_pulsar']['gtlike']['test_cutoff']
+
+        if cutoff != -1:
+
+            flux=cutoff['flux_1']['eflux']
+            flux_err=cutoff['flux_1']['eflux_err']
+            table[flux_name].append('$%.2f \pm %.2f$' % (flux/1e-12,flux_err/1e-12))
+            index=-1*cutoff['model_1']['Index1']
+            index_err=cutoff['model_1']['Index1_err']
+            table[index_name].append('$%.2f \pm %.2f$' % (index,index_err))
+            cutoff_energy=cutoff['model_1']['Cutoff']
+            cutoff_energy_err=cutoff['model_1']['Cutoff_err']
+            table[cutoff_name].append('$%.2f \pm %.2f$' % (cutoff_energy/1000,cutoff_energy_err/1000))
+            ts_cutoff = max(cutoff['TS_cutoff'],0)
+            table[ts_cutoff_name].append('%.1f' % ts_cutoff)
+        else:
+            table[flux_name].append('None')
+            table[index_name].append('None')
+            table[cutoff_name].append('None')
+            table[ts_cutoff_name].append('None')
+
+    write_latex(table,
+                filebase='off_peak_cutoff_test',
+                latexdict = dict(#caption=r'Spectral fitting of pulsar wind nebula candidates with low energy component.',
+                                 #col_align=r'lrrrr',
+                                 #preamble=r'\tabletypesize{\scriptsize}',
+                                 units={
+                                     flux_name:r'($10^{-12}$\,erg\,cm$^{-2}$\,s$^{-1}$)',
+                                     cutoff_name:r'(GeV)',
+                                 }))
+
+
+cutoff_candidates = ['PSRJ0034-0534', 
[…]

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/table/each_energy_table.py

@@ -1,0 +1,60 @@
+from table_helper import get_pwnlist,get_results,table_name,get_sed,write_latex
+from lande_toolbag import OrderedDefaultdict
+
+def each_energy_table(pwnlist):
+
+    table = OrderedDefaultdict(list)
+
+    TS1_name = '$TS_{0.1-1}$'
+    TS2_name = '$TS_{1-10}$'
+    TS3_name = '$TS_{10-316}$'
+
+    flux1_name = '$F_{0.1-1}$'
+    flux2_name = '$F_{1-10}$'
+    flux3_name = '$F_{10-316}$'
+
+    for pwn in pwnlist:
+
+        results = get_results(pwn)
+        table['PSR'].append(table_name(pwn))
+
+        if results is None or get_sed(pwn,'1bpd','at_pulsar') == {}: 
+            table[TS1_name].append('None')
+            table[flux1_name].append('None')
+
+            table[TS2_name].append('None')
+            table[flux2_name].append('None')
+
+            table[TS3_name].append('None')
+            table[flux3_name].append('None')
+        else:
+
+            sed = get_sed(pwn,'1bpd','at_pulsar')
+            ts = sed['Test_Statistic']
+            flux = sed['Ph_Flux']['Value']
+            flux_err = sed['Ph_Flux']['Error']
+            ul = sed['Ph_Flux']['Upper_Limit']
+
+            ts = [i if i > 0 else 0 for i in ts]
+
+            table[TS1_name].append('%.1f' % ts[0])
+            table[flux1_name].append('$%.2f \pm %.2f$' % (flux[0]/1e-9,flux_err[0]/1e-9) if ts[0] > 25 else '$<%.2f$' % (ul[0]/1e-9))
+
+            table[TS2_name].append('%.1f' % ts[1])
+            table[flux2_name].append('$%.2f \pm %.2f$' % (flux[1]/1e-9,flux_err[1]/1e-9) if ts[1] > 25 else r'$<%.2f$' % (ul[1]/1e-9))
+
+            table[TS3_name].append('%.1f' % ts[2])
+            table[flux3_name].append('$%.2f \pm %.2f$' % (flux[2]/1e-9,flux_err[2]/1e-9) if ts[2] > 25 else r'$<%.2f$' % (ul[2]/1e-9))
+
+    write_latex(table,
+                filebase='off_peak_each_energy',
+                latexdict = dict(#caption=r'Energy bin spectral fit for the %s LAT-detected Pulsars'  % len(pwnlist),
[…]

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/table/phase_table.py

@@ -1,0 +1,28 @@
+from table_helper import get_pwnlist,get_results,table_name,write_latex
+from lande_toolbag import OrderedDefaultdict
+
+import yaml
+from os.path import join as j,expandvars
+
+def get_phase(pwn):
+    phase = yaml.load('$pwncode/pwndata/pwncat2_phase_lande.yaml')[pwn]['phase']
+def all_energy_table(pwnlist):
+
+    table = OrderedDefaultdict(list)
+    phase_name='PHASE'
+
+    for pwn in pwnlist:
+        table['PSR'].append(table_name(pwn))
+
+        phase=get_phase(pwn)
+        table[phase_name]=str(phase)
+
+    write_latex(table,
+                filebase='off_peak_phase_range',
+                latexdict = dict(units={
+                                     #flux_name:r'($10^{-9} \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',
+                                 }))
+
+
+pwnlist=get_pwnlist()
+all_energy_table(pwnlist)

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/table/table_helper.py

@@ -1,0 +1,77 @@
+from os.path import join as j
+from os.path import expandvars
+import StringIO
+from textwrap import dedent
+import shutil
+import os.path
+
+import yaml
+import asciitable
+
+base='$pwndata/analyze_psr/v7/'
+
+fitdir=expandvars(j(base,'analysis_no_plots/'))
+savedir=expandvars(j(base,'tables'))
+
+if not os.path.exists(savedir): os.makedirs(savedir)
+
+def table_name(pwn):
+    pwn = pwn.replace('PSR','')
+    pwn = pwn.replace('-','$-$')
+    return pwn
+
+def write_latex(table, filebase, **kwargs):
+
+    outtable=StringIO.StringIO()
+
+    asciitable.write(table, outtable, 
+                     Writer=asciitable.AASTex,
+                     names=table.keys(),
+                     **kwargs
+                    )
+    t=outtable.getvalue()
+
+    lines = t.split('\n')
+    if lines[-1] == '': 
+        lines=lines[0:-1]
+
+    header = lines[0]
+    footer= lines[-1]
+
+    t = '\n'.join(lines[1:-1])
+
+
+    os.chdir(savedir)
+
+    open('%s.tex' % filebase,'w').write(t)
+
+    open('temp.tex','w').write(dedent(r"""
+        \documentclass{aastex}
+        \usepackage{amsmath}
+        \begin{document}
+        %s
+        \input{%s}
+        %s
+        \end{document}""" % (header,filebase,footer)))
+
+    os.system('pdflatex temp.tex')
+    shutil.move('temp.pdf','%s.pdf' % filebase)
+    os.remove('temp.tex')
+
+def get_results(pwn):
+    f = j(fitdir,pwn,'results_%s.yaml' % pwn)
+    if not os.path.exists(f): return None
+    results = yaml.load(open(f))
+
+    if not results.has_key('at_pulsar') or not results['at_pulsar'].has_key('gtlike'):
+        return None
+    return results
+
+def get_sed(pwn,binning,hypothesis):
+    filename=j(fitdir,pwn,'seds','sed_gtlike_%s_%s_%s.yaml' % (binning, hypothesis, pwn))
+    return yaml.load(open(filename))
+
+def get_pwnlist():
+    pwnlist=sorted(yaml.load(open(expandvars('$pwncode/pwndata/pwncat2_data_lande.yaml'))).keys())
+    return pwnlist
+

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/summarize/website/lande_website.py
update

@@ -1,243 +1,0 @@
-import sys
-from glob import glob
-import yaml
-from StringIO import StringIO
-import re
-import os
-from os.path import join,exists
-from os.path import join as j
-from collections import defaultdict
-
-import asciitable
-
-from lande_toolbag import OrderedDefaultdict
-
-base='/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT2/analyze_psr/v6/'; at_pulsar='at_pulsar'
-
-analysis='analysis_plots'
-#analysis='analysis'
-pwnlist=sorted([os.path.basename(i) for i in glob(j(base,analysis,'*')) if os.path.isdir(i)])
-
-website=join(base,'website')
-
-if not os.path.exists(website): os.makedirs(website)
-
-
-
-def get_results(pwn):
-    f = j(base,analysis.replace('plots','no_plots'),pwn,'results_%s.yaml' % pwn)
-    #f = j(base,analysis,pwn,'results_%s.yaml' % pwn)
-
-    if not os.path.exists(f): return None
-    results = yaml.load(open(f))
-
-    #for hypothesis in [at_pulsar, 'point', 'extended']:
-    for hypothesis in [at_pulsar]:
-        h=results[hypothesis]
-        if not results.has_key(hypothesis):
-            results[hypothesis]=defaultdict(lambda:-1),
-        for t in ['gtlike','pointlike']:
-            if not h.has_key(t):
-                h[t]=defaultdict(lambda:-1)
-            for i in ['model', 'upper_limit', 'flux']:
-                if not h[t].has_key(i):
-                    h[t][i]=defaultdict(lambda:-1)
-    return results
-
-def get_sed(pwn,binning,hypothesis):
-    filename=j(base,analysis.replace('plots','no_plots'),pwn,'seds','sed_gtlike_%s_%s_%s.yaml' % (binning, hypothesis, pwn))
-    if os.path.exists(filename) and yaml.load(open(filename)) != {}:
-        return yaml.load(open(filename))
-    elif binning == '1bpd':
-        d=defaultdict(lambda: defaultdict(lambda:[-1,-1,-1]))
-        d['Test_Statistic']=[-1,-1,-1]
-        return d
-    else:
-        raise Exception("...")
-
-def get_t2t_table(table, **kwargs):
-
[…]

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/table/phase_table.py
update

@@ -5,23 +5,41 @@ import yaml
 from os.path import join as j,expandvars
 
 def get_phase(pwn):
-    phase = yaml.load('$pwncode/pwndata/pwncat2_phase_lande.yaml')[pwn]['phase']
+    phase = yaml.load(open(expandvars('$pwncode/pwndata/pwncat2_phase_lande.yaml')))
+    return phase[pwn]['phase']
+
 def all_energy_table(pwnlist):
 
     table = OrderedDefaultdict(list)
+
+    psr_name='PSR'
     phase_name='PHASE'
 
+    obs_id = 'ObsID'
+    distance = 'Distance'
+    rejected = 'Observation period rejected (MJD)'
+
     for pwn in pwnlist:
-        table['PSR'].append(table_name(pwn))
+        print pwn
+        table[psr_name].append(table_name(pwn))
 
         phase=get_phase(pwn)
-        table[phase_name]=str(phase)
+        table[obs_id].append(r'\nodata')
+        table[phase_name].append('%.2f-%.2f' % tuple(phase))
 
+        table[distance].append(r'\nodata')
+        table[rejected].append(r'\nodata')
+
+    print table
     write_latex(table,
                 filebase='off_peak_phase_range',
-                latexdict = dict(units={
-                                     #flux_name:r'($10^{-9} \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',
-                                 }))
+                latexdict = dict(
+                    units=dict(
+                        distance='kpc'
+                        #flux_name:r'($10^{-9} \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',
+                        )
+                    )
+               )
 
 
 pwnlist=get_pwnlist()

### 2012-01-26 pwncatalog/PWNCAT2/code/lande/table/table_helper.py

@@ -56,7 +56,8 @@ def write_latex(table, filebase, **kwargs):
 
     os.system('pdflatex temp.tex')
     shutil.move('temp.pdf','%s.pdf' % filebase)
-    os.remove('temp.tex')
+    for i in ['temp.tex','temp.aux','temp.log']:
+        os.remove(i)
 
 def get_results(pwn):
     f = j(fitdir,pwn,'results_%s.yaml' % pwn)

### 2012-01-26 pwncatalog/PWNCAT2/paper/sections/off_peak_phase_selection.tex
update tables + new figure
updated text

@@
 Off-peak goes here\ldots
+
+\figref{off_peak_select} shows the off peak selection for some pulsars\dots
+
+\begin{figure}
+  \ifdefined\bwfigures
+  \plotone{off_peak_select_bw.eps}
+  \else
+  \plotone{off_peak_select_color.eps}
+  \fi
+  \caption{Off peak selection for some pulsars\dots}
+  \label{fig:off_peak_select}
+\end{figure}
+
+THe off peak phase range is defined in \tabref{off_peak_phase_range}.
+
+\begin{deluxetable}{lcccc}
+  \tabletypesize{\scriptsize}
+  \tablecaption{Observatories, off-pulse definitions and distances of the \todo[inline]{How many pulsars?} \lat-detected pulsars
+  \label{tab:off_peak_phase_range}
+  }
+  \input{tables/off_peak_phase_range}
+  \tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}

### 2012-01-26 pwncatalog/PWNCAT2/paper/sections/results.tex
update tables + new figure
updated text

--- 2012-01-21 pwncatalog/PWNCAT2/paper/sections/results.tex
@@
 
-\input{tables/off_pulse_all_energy.tex}
+\tabref{off_peak_all_energy} shows the results of the all energy analysis of the off-peak emission for each pulsar.
 
-\input{tables/off_pulse_each_energy.tex}
+\tabref{off_peak_each_energy} shows the results of the analysis in separate energy bins of each pulsar.
 
-\input{tables/off_pulse_cutoff_test.tex}
+\tabref{off_peak_cutoff_test} shows the results of the cutoff test for pulsars with significant low-energy emission.
+
+\begin{deluxetable}{lccc}
+\tabletypesize{\scriptsize}
+\tablecaption{All Energy spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
+\label{tab:off_peak_all_energy}
+}
+\input{tables/off_peak_all_energy.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}
+
+\begin{deluxetable}{lcccccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Energy bin spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
+\label{tab:off_peak_each_energy}
+}
+\input{tables/off_peak_each_energy.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}
+
+\begin{deluxetable}{lcccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Spectral fitting of pulsar wind nebula candidates with low energy component
+\label{tab:off_peak_cutoff_test}
+}
+\input{tables/off_peak_cutoff_test.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}
+
+\todo[inline]{Add table on PWN Variability}
+
+\figref{cutoff_test} shows the cutoff test\ldots
+
+\begin{figure}
+  \ifdefined\bwfigures
+  \plotone{cutoff_test_bw.eps}
+  \else
+  \plotone{cutoff_test_color.eps}
+  \fi
+  \caption{Cutoff test for some pulsars\dots}
+  \label{fig:cutoff_test}
+\end{figure}

### 2012-01-27 pwncatalog/PWNCAT2/paper/sections/analysis_of_the_fermi_lat_data.tex
update indent

@@
 
-Analysis goes here\ldots
+Methods for data analysis
+\begin{itemize}
+\item Cut on pulsar phase
+\item Perform localization or extension fitting using \gtlike using energies from 1 \gev to 316 \gev.
+\item Perform spectral analysis using \gtlike for energies above 100 \mev to 316 \gev.
+\item There is a detection if  $\ts>25$ in the point-like source hypothesis after fitting the position of the point-like source. 
+\item Consider the source to be extended if $\tsext>16$. Similar to extended source search paper \todo{cite extended source search paper}.
+\item Calculate \tscut for all energies.
+\end{itemize}
+
+When to consider the source a pulsar or PWN.
+\begin{itemize}
+  \item If extended, then it is a PWN (cannot be a pulsar)
+  \item If it is significiant for E>10 \gev, it is a PWN (too hard to be a pulsar)
+  \item Otherwise, if it has a cutoff, it is a Pulsar candidate
+  \item For point-like emission that is not significantly cutoff, the emission  mechanism is uncertain.
+\end{itemize}

### 2012-01-27 pwncatalog/PWNCAT2/paper/sections/off_peak_phase_selection.tex
update indent

@@
 \section{Off-peak Phase Selection}
-
-Off-peak goes here\ldots
 
@@
 
+To study the off-peak emission of \lat-detected pulsars, we first
+developed a new method for defining the off-peak emission.
+The primary constraint for this method was that it was systematic,
+computationally efficient and model independent, and that it correctly
+removed the pulsed emission for already studied pulsars.
+
+The method we developed required first representing the
+
 THe off peak phase range is defined in \tabref{off_peak_phase_range}.
@@
   \tabletypesize{\scriptsize}
-  \tablecaption{Observatories, off-pulse definitions and distances of the \todo[inline]{How many pulsars?} \lat-detected pulsars
+  \tablecaption{Timing Observatories, definition of the off-peak region, and pulsar distances.
   \label{tab:off_peak_phase_range}

### 2012-01-28 pwncatalog/PWNCAT2/paper/sections/off_peak_phase_selection.tex
updating text

@@
 
-\figref{off_peak_select} shows the off peak selection for some pulsars\dots
+To study the off-peak emission of \lat-detected pulsars, we first
+developed a new method for defining the off-peak emission.
+The primary constraint for this method was that it was systematic,
+computationally efficient and model independent, and that it correctly
+removed the pulsed emission for already studied pulsars.
+
+The method we developed is
+\begin{itemize}
+  \item First, deconstruct the pulsar phaseogram 
+    using a Bayseian blocks representation of the data.
+    \begin{itemize}
+      \item \figref{off_peak_select} shows the off peak selection for some pulsars\dots
+      \item Set the ncpPrior parameter to 5
+    \end{itemize}
+  \item Before beinning the data, first rotate the maximum phase range to 0
+    so that the off-peak region will not overlap the phase edge.
+  \item 
+\end{itemize}
+  required first representing the
 
@@
 
-To study the off-peak emission of \lat-detected pulsars, we first
-developed a new method for defining the off-peak emission.
-The primary constraint for this method was that it was systematic,
-computationally efficient and model independent, and that it correctly
-removed the pulsed emission for already studied pulsars.
-
-The method we developed required first representing the
-
 THe off peak phase range is defined in \tabref{off_peak_phase_range}.

### 2012-01-28 pwncatalog/PWNCAT2/paper/tables/off_peak_localization.tex
updating text

\tablehead{\colhead{PSR} & \colhead{$\ts_\text{point}$} & \colhead{GLON} & \colhead{GLAT} & \colhead{Pos Err} & \colhead{Offset} & \colhead{\tsext} & \colhead{Extension}\\ \colhead{ } & \colhead{ } & \colhead{(deg)} & \colhead{(deg)} & \colhead{ } & \colhead{(deg)} & \colhead{ } & \colhead{(deg)}}
\startdata
J0007+7303 & 82.8 & 119.66 & 10.46 & None & 0.00 & 10.6 & $<2.62$ \\
J0034$-$0534 & 42.4 & 111.53 & -68.03 & 0.06 & 0.04 & 0.0 & $<0.12$ \\
J0218+4232 & 34.7 & 139.56 & -17.53 & 0.08 & 0.05 & 0.0 & $<0.15$ \\
J0340+4130 & 25.1 & 153.81 & -11.00 & 0.06 & 0.04 & 0.0 & $<0.13$ \\
J0534+2200 & 4959.1 & 184.55 & -5.79 & 0.01 & 0.01 & 0.0 & $<0.02$ \\
J0633+1746 & 2842.4 & 195.12 & 4.22 & 0.02 & 0.05 & 3.3 & $<0.09$ \\
J0835$-$4510 & 304.7 & 263.46 & -3.15 & 0.08 & 0.37 & 295.3 & $0.73 \pm 0.06$ \\
\enddata

### 2012-02-05 pwncatalog/PWNCAT2/paper/sections/results.tex
update indent
updating text
new extension ul code

@@
 
-\tabref{off_peak_all_energy} shows the results of the all energy analysis of the off-peak emission for each pulsar.
+\tabref{all_energy} shows the results of the all energy analysis of the off-peak emission for each pulsar.
 
-\tabref{off_peak_each_energy} shows the results of the analysis in separate energy bins of each pulsar.
+\tabref{each_energy} shows the results of the analysis in separate energy bins of each pulsar.
 
-\tabref{off_peak_cutoff_test} shows the results of the cutoff test for pulsars with significant low-energy emission.
+\tabref{cutoff_test} shows the results of the cutoff test for pulsars with significant low-energy emission.
 
-\begin{deluxetable}{lccc}
+\begin{deluxetable}{l*{5}c}
 \tabletypesize{\scriptsize}
 \tablecaption{All Energy spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
-\label{tab:off_peak_all_energy}
+\label{tab:all_energy}
 }
-\input{tables/off_peak_all_energy.tex}
+\input{tables/all_energy.tex}
 \tablecomments{\todo[inline]{Put table comments}}
@@
 
-\begin{deluxetable}{lcccccc}
+\clearpage
+\begin{deluxetable}{l*{9}c}
+%\tabletypesize{\tiny}
+\setlength{\tabcolsep}{0.04in}
 \tabletypesize{\scriptsize}
+\tablewidth{0pt}
+\rotate
 \tablecaption{Energy bin spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
-\label{tab:off_peak_each_energy}
+\label{tab:each_energy}
 }
-\input{tables/off_peak_each_energy.tex}
+\input{tables/each_energy.tex}
 \tablecomments{\todo[inline]{Put table comments}}
@@
 
-\begin{deluxetable}{lcccc}
+\begin{deluxetable}{l*{6}c}
 \tabletypesize{\scriptsize}
 \tablecaption{Spectral fitting of pulsar wind nebula candidates with low energy component
-\label{tab:off_peak_cutoff_test}
+\label{tab:cutoff_test}
 }
-\input{tables/off_peak_cutoff_test.tex}
+\input{tables/cutoff_test.tex}
 \tablecomments{\todo[inline]{Put table comments}}
@@
 
-\todo[inline]{Add table on PWN Variability}
+The localization results are in \tabref{localization}
+
+\begin{deluxetable}{l*{7}c}
+\tabletypesize{\scriptsize}
+\tablecaption{Localization and extension fitting results
+\label{tab:localization}
+}
+\input{tables/localization.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}
 
@@
 \end{figure}
+
+\figref{variability} shows the cutoff test\ldots
+
+\begin{deluxetable}{l*{2}c}
+\tabletypesize{\scriptsize}
+\tablecaption{Variability test
+\label{tab:variability}
+}
+\input{tables/variability.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/submit.sh

@@ -354,16 +354,59 @@ echo python $pwncode/loop_pwn.py -c $pwncode/analyze_psr.py \
 
 # ----------------------------------------------------------------------------------------------------
 
-echo python $pwncode/loop_pwn.py -c $pwncode/analyze_psr.py \
+echo python $pwncode/loop_pwn.py \
+        -c $pwncode/analyze_psr.py \
         --pwndata $pwncode/pwndata/pwncat2_data_lande.yaml \
         --pwnphase $pwncode/pwndata/pwncat2_phase_lande.yaml  \
         --modify $pwncode/modify/modify_psr_lande.py \
         -o $pwndata/spectral/v9/analysis_no_plots --no-plots --max-free 5
 
-echo python $pwncode/loop_pwn.py -c $pwncode/analyze_psr.py \
+echo python $pwncode/loop_pwn.py \
+        -c $pwncode/analyze_psr.py \
         --pwndata $pwncode/pwndata/pwncat2_data_lande.yaml \
         --pwnphase $pwncode/pwndata/pwncat2_phase_lande.yaml  \
         --modify $pwncode/modify/modify_psr_lande.py \
         -o $pwndata/spectral/v9/analysis_plots --max-free 5
 
 # ----------------------------------------------------------------------------------------------------
+
+echo python $pwncode/loop_pwn.py \
+        --pwndata $pwncode/pwndata/pwncat2_data_lande.yaml \
+        -c $pwncode/lande/variability/test_variability.py \
+        --analysis-dir $pwndata/spectral/v9/analysis_no_plots \
+        -o $pwndata/spectral/v9/variability/v2
+
+# ----------------------------------------------------------------------------------------------------
+
+echo python $pwncode/loop_pwn.py \
+        --pwndata $pwncode/pwndata/pwncat2_data_lande.yaml \
+        -c $pwncode/lande/variability/test_variability.py \
+        --analysis-dir $pwndata/spectral/v9/analysis_no_plots \
+        -o $pwndata/spectral/v9/variability/v3
+
+# ----------------------------------------------------------------------------------------------------
+
+echo python $pwncode/loop_pwn.py \
+        --pwndata $pwncode/pwndata/pwncat2_data_lande.yaml \
+        -c $pwncode/lande/variability/test_variability.py \
+        --analysis-dir $pwndata/spectral/v9/analysis_no_plots \
+        -o $pwndata/spectral/v9/variability/v4
+
[…]

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/tables/all_energy_table.py

@@ -5,6 +5,7 @@ def all_energy_table(pwnlist):
 
     table = OrderedDefaultdict(list)
 
+    psr_name='PSR'
     flux_name=r'$F_{0.1-316}$'
     energy_flux_name=r'$G_{0.1-316}$'
     ts_name=r'\ts'
@@ -13,7 +14,7 @@ def all_energy_table(pwnlist):
     luminosity_name = r'Luminosity'
 
     for pwn in pwnlist:
-        table['PSR'].append(table_name(pwn))
+        table[psr_name].append(table_name(pwn))
 
         results = get_results(pwn)
 
@@ -64,7 +65,7 @@ def all_energy_table(pwnlist):
                     table[luminosity_name].append(r'None')
 
     write_latex(table,
-                filebase='off_peak_all_energy',
+                filebase='all_energy',
                 latexdict = dict(#caption=r'All Energy spectral fit for the %s LAT-detected Pulsars'  % len(pwnlist),
                                  #preamble=r'\tabletypesize{\scriptsize}',
                                  units={

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/tables/cutoff_table.py

@@ -5,7 +5,9 @@ def cutoff_table(pwnlist):
 
     table = OrderedDefaultdict(list)
 
-    flux_name = r'$G_{0.1-316}$'
+    psr_name='PSR'
+    flux_name = r'$F_{0.1-316}$'
+    eflux_name = r'$G_{0.1-316}$'
     index_name = r'$\Gamma$'
     cutoff_name = r'$E_\text{cutoff}$'
     ts_point_name = r'$\ts_\text{point}$'
@@ -23,7 +25,7 @@ def cutoff_table(pwnlist):
         if ts < 25:
             continue
 
-        table['PSR'].append(table_name(pwn))
+        table[psr_name].append(table_name(pwn))
 
         cutoff=results['point']['gtlike']['test_cutoff']
 
@@ -39,33 +41,40 @@ def cutoff_table(pwnlist):
 
             if ts_cutoff >= 16:
 
-                flux=cutoff['flux_1']['eflux']
-                flux_err=cutoff['flux_1']['eflux_err']
+                flux=cutoff['flux_1']['flux']
+                flux_err=cutoff['flux_1']['flux_err']
+
+                eflux=cutoff['flux_1']['eflux']
+                eflux_err=cutoff['flux_1']['eflux_err']
                 index=-1*cutoff['model_1']['Index1']
                 index_err=cutoff['model_1']['Index1_err']
                 cutoff_energy=cutoff['model_1']['Cutoff']
                 cutoff_energy_err=cutoff['model_1']['Cutoff_err']
 
-                table[flux_name].append('$%.2f \pm %.2f$' % (flux/1e-12,flux_err/1e-12))
+                table[flux_name].append('$%.2f \pm %.2f$' % (flux/1e-9,flux_err/1e-9))
+                table[eflux_name].append('$%.2f \pm %.2f$' % (eflux/1e-12,eflux_err/1e-12))
                 table[index_name].append('$%.2f \pm %.2f$' % (index,index_err))
                 table[cutoff_name].append('$%.2f \pm %.2f$' % (cutoff_energy/1000,cutoff_energy_err/1000))
             else:
                 table[flux_name].append(r'\nodata')
+                table[eflux_name].append(r'\nodata')
                 table[index_name].append(r'\nodata')
                 table[cutoff_name].append(r'\nodata')
         else:
             table[flux_name].append('None')
+            table[eflux_name].append('None')
             table[index_name].append('None')
             table[cutoff_name].append('None')
[…]

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/tables/each_energy_table.py

@@ -1,10 +1,12 @@
 from table_helper import get_pwnlist,get_results,table_name,write_latex, BestHypothesis
 from lande_toolbag import OrderedDefaultdict
+from numpy import asarray as a
 
 def each_energy_table(pwnlist):
 
     table = OrderedDefaultdict(list)
 
+    psr_name='PSR'
     TS1_name = r'$\ts_{0.1-1}$'
     TS2_name = r'$\ts_{1-10}$'
     TS3_name = r'$\ts_{10-316}$'
@@ -20,7 +22,7 @@ def each_energy_table(pwnlist):
     for pwn in pwnlist:
 
         results = get_results(pwn)
-        table['PSR'].append(table_name(pwn))
+        table[psr_name].append(table_name(pwn))
 
         if results is None: 
             table[TS1_name].append('None')
@@ -35,48 +37,51 @@ def each_energy_table(pwnlist):
             table[flux3_name].append('None')
             table[index3_name].append('None')
         else:
-            at_pulsar_gtlike = results['at_pulsar']['gtlike']
-            at_pulsar_pointlike = results['at_pulsar']['pointlike']
-            
-
-            point_gtlike = results['point']['gtlike']
-            point_pointlike = results['point']['pointlike']
-            
-            extended_gtlike = results['extended']['gtlike']
-            extended_pointlike = results['extended']['pointlike']
-
-            ts_point = point_gtlike['TS']
-            ts_ext = max(extended_gtlike['ts_ext'],0)
+            print 'name',pwn
 
             b = BestHypothesis(results)
             gtlike = b.gtlike
             pointlike = b.pointlike
             type = b.type
+            print type
 
             ts = gtlike['bands']['TS']
-
-            f = gtlike['bands']['flux']
-            flux = f['value']
-            flux_err = f['error']
-            ul = f['upper_limit']
+            flux = gtlike['bands']['flux']['value']
+            flux_err = gtlike['bands']['flux']['error']
+            ul = gtlike['bands']['flux']['upper_limit']
+            index = -a(gtlike['bands']['index']['value'])
+            index_err = -a(gtlike['bands']['index']['error'])
 
             ts = [i if i > 0 else 0 for i in ts]
 
             table[TS1_name].append('%.1f' % ts[0])
[…]

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/tables/localization_table.py

@@ -47,7 +47,7 @@ def localization_table(pwnlist):
         pointlike = b.pointlike
         type = b.type
 
-        if b.type != 'ul':
+        if b.type != 'upper_limit':
 
             l,b=pointlike['gal']
 
@@ -79,7 +79,7 @@ def localization_table(pwnlist):
             
     deg = '(deg)'
     write_latex(table,
-                filebase='off_peak_localization',
+                filebase='localization',
                 latexdict = dict(#caption=r'All Energy spectral fit for the %s LAT-detected Pulsars'  % len(pwnlist),
                                  #preamble=r'\tabletypesize{\scriptsize}',
                                  units={

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/tables/phase_table.py

@@ -25,14 +25,14 @@ def all_energy_table(pwnlist):
 
         phase=get_phase(pwn)
         table[obs_id].append(r'\nodata')
-        table[phase_name].append('%.2f-%.2f' % tuple(phase))
+        table[phase_name].append('%.2f - %.2f' % tuple(phase))
 
         table[distance].append(r'\nodata')
         table[rejected].append(r'\nodata')
 
     print table
     write_latex(table,
-                filebase='off_peak_phase_range',
+                filebase='phase_range',
                 latexdict = dict(
                     units=dict(
                         distance='kpc'

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/variability/test_variability.py

@@ -1,25 +1,35 @@
+import yaml
+import numpy as np
+np.seterr(all='ignore')
 
+from argparse import ArgumentParser
+
+import lande_variability
+
+from uw.like.roi_save import load
 
 parser = ArgumentParser()
 parser.add_argument("--pwndata", required=True)
-group=parser.add_mutually_exclusive_group(required=True)
-group.add_argument("-p", "--pwnphase")
+parser.add_argument("-n", "--name", required=True)
+parser.add_argument("--analysis-dir", required=True)
+args=parser.parse_args()
 
 
-
-
-name='PSRJ0534+2200'
-roi = load('$pwndata/spectral/v9/analysis_no_plots/%s/roi_at_pulsar_%s.dat' % (name,name))
+name=args.name
+roi = load('%s/%s/roi_at_pulsar_%s.dat' % (args.analysis_dir,name,name))
 
 roi.print_summary()
 roi.fit(use_gradient=False)
 roi.print_summary()
 
-import lande_variability
-reload(lande_variability);v = lande_variability.VariabilityTester(roi,name,nbins=36, always_upper_limit=True, savedir='savedir')
+v = lande_variability.VariabilityTester(roi,name,
+                                        nbins=36)
 
-print v
 print v.todict()
 
-open('results_%s.yaml' % name,'w').write(yaml.dump(v.todict()))
+d=v.todict()
+open('results_%s.yaml' % name,'w').write(
+    yaml.dump(d)
+)
 
+v.plot(filename='variability_%s.pdf' % name)

### 2012-02-05 pwncatalog/PWNCAT2/code/lande/website/lande_website.py

@@ -13,7 +13,7 @@ import asciitable
 
 from lande_toolbag import OrderedDefaultdict
 
-base=expandvars('$pwndata/spectral/v8')
+base=expandvars('$pwndata/spectral/v9')
 #base=expandvars('$pwndata/spectral/temp')
 
 
@@ -92,7 +92,6 @@ class TableFormatter(object):
 
             if results.has_key('point') and results['point'].has_key('pointlike') and results['point'].has_key('gtlike'):
                 point_finished = True
-
 
                 gt_point=results['point']['gtlike']
                 pt_point=results['point']['pointlike']
@@ -181,25 +180,25 @@ class TableFormatter(object):
             if gt.has_key('bands'):
 
                 bands=gt['bands']
-                if not np.allclose(bands['Energy']['Lower'], [1e2, 1e3, 1e4]) or \
-                   not np.allclose(bands['Energy']['Upper'], [1e3, 1e4, 10**5.5]):
+                if not np.allclose(bands['energy']['lower'], [1e2, 1e3, 1e4]) or \
+                   not np.allclose(bands['energy']['upper'], [1e3, 1e4, 10**5.5]):
                     raise Exception("...")
 
-                ts1,ts2,ts3=bands['Test_Statistic']
-                index1,index2,index3=bands['Index']['Value']
-                index_err1,index_err2,index_err3=bands['Index']['Error']
+                ts1,ts2,ts3=bands['TS']
+                index1,index2,index3=bands['index']['value']
+                index_err1,index_err2,index_err3=bands['index']['error']
 
-                flux1,flux2,flux3=bands['Ph_Flux']['Value']
-                flux_err1,flux_err2,flux_err3=bands['Ph_Flux']['Error']
+                flux1,flux2,flux3=bands['flux']['value']
+                flux_err1,flux_err2,flux_err3=bands['flux']['error']
 
-                ul1,ul2,ul3=bands['Ph_Flux']['Upper_Limit']
+                ul1,ul2,ul3=bands['flux']['upper_limit']
 
                 table['TS(.1-1)'].append('%.1f' % ts1)
                 if ts1>25:
[…]

### 2012-02-05 pwncatalog/PWNCAT2/code/modify/modify_psr_lande.py

@@ -3,6 +3,10 @@ folder = os.path.dirname(__file__)
 sys.path.append(folder)
 import modify_psr_base
 
+from skymaps import SkyDir
+from uw.like.pointspec_helpers import PointSource
+from uw.like.Models import PowerLaw
+
 def modify_roi(name,roi):
     modify_psr_base.modify_roi(name,roi)
 
@@ -16,10 +20,10 @@ def modify_roi(name,roi):
         modify_psr_base.set_flux_index(roi,name,5.637887384602554e-08,2.869750880323576)
 
 
-    if name == 'PSRJ1023-5746'
+    if name == 'PSRJ1023-5746':
 
         # In previous analysis 
-        # $pwndata/spectral/v9/analysis_no_plots/PSRJ1023-5746/log_PSRJ1023-5746.txt
+        # $pwndata/spectral/v9/analysis_no_plots/PSRJ1023-5746/results_PSRJ1023-5746.yaml
         # I foudn that this source had large residual surrounding it. So always fit it
         roi.modify(which='2FGL J1044.5-5737', free=True)
 
@@ -51,10 +55,59 @@ def modify_roi(name,roi):
         # $pwndata/spectral/v8/analysis_no_plots/PSRJ1620-4927/results_PSRJ1620-4927.yaml
         modify_psr_base.set_flux_index(roi,name,4.605558542777753e-08,2.0941239204631703)
 
+    if name == 'PSRJ1709-4429':
+
+        # Not sure, but this nearby source was fitting to a very unphysical
+        # log-parabola bump in the v9 analysis of PSR J1709
+        # $pwndata/spectral/v9/analysis_no_plots/PSRJ1709-4429/results_PSRJ1709-4429.yaml
+        # so turn it into a more well behaved PowerLaw
+        roi.modify(which='2FGL J1704.9-4618',
+                   keep_old_flux=False,
+                   model=PowerLaw(
+                       norm=2.6400767608080404e-12,
+                       index=2.6814468574367032,
+                       e0=1000.0))
+
+
+    if name == 'PSRJ1744-1134':
+
+        # Parameters taken from gtlike at_pulsar analysis in
+        # $pwndata/spectral/v9/analysis_no_plots/PSRJ1744-1134/results_PSRJ1744-1134.yaml
+        modify_psr_base.set_flux_index(roi,name,4.7112402016117437e-08,2.3441611339006334)
+
+    if name == 'PSRJ1746-3239':
+
+        # In previous analysis 
[…]

### 2012-02-05 pwncatalog/PWNCAT2/extul/extul.py

@@ -1,0 +1,134 @@
+from os.path import join
+import yaml
+
+import numpy as np
+
+from skymaps import SkyDir
+from skymaps import IsotropicPowerLaw
+
+from uw.like.roi_diffuse import DiffuseSource
+from uw.like.roi_extended import ExtendedSource
+from uw.like.Models import PowerLaw
+from uw.like.SpatialModels import Disk
+from uw.like.roi_monte_carlo import MonteCarlo
+from uw.like.pointspec import DataSpecification, SpectralAnalysis
+from uw.like.pointspec_helpers import PointSource
+
+from tempfile import mkdtemp
+from shutil import rmtree
+
+from lande_toobag import todict
+
+
+i=0
+
+emin=1e2
+emax=10**5.5
+#emax=10**3
+irf="P7SOURCE_V6"
+
+skydir_mc = SkyDir()
+
+
+
+bg = DiffuseSource(
+    IsotropicPowerLaw(1.5e-5,2.1),
+    PowerLaw(p=[1,1],index_offset=1),
+    'Isotropic Diffuse x1'
+)
+
+catalog_basedir = "/afs/slac/g/glast/groups/catalog/P7_V4_SOURCE/"
+ft2    = join(catalog_basedir,"ft2_2years.fits")
+ltcube = join(catalog_basedir,"ltcube_24m_pass7.4_source_z100_t90_cl0.fits")
+
+
+
+results = []
+
+extensions = np.linspace(0.1,2.0,20)
+
+for extension in extensions[0:1]:
+
+    tempdir = mkdtemp()
+
+    model = PowerLaw(gamma=2)
+    model.set_flux(1e-8, 1e2, 10**5.5)
+
+    spatial_model = Disk(sigma=extension, center=skydir_mc)
+
+    ext = ExtendedSource(
+        name='extended',
+        model=model,
+        spatial_model=spatial_model,
+    )
+
+    ft1 = join(tempdir,'ft1.fits')
+    binfile = join(tempdir, 'binned.fits')
+
+    ft2 = join(tempdir, 'ft2.fits')
+    mc=MonteCarlo(
+        diffuse_sources=[bg.copy(), ext.copy()],
+        seed=i,
+        irf=irf,
+        ft1=ft1,
+        ft2=ft2,
+        roi_dir=skydir_mc,
+        maxROI=15,
+        emin=emin,
+        emax=emax,
+
+        tstart=0,   
+        tstop=604800,
+        )
+
[…]

### 2012-02-07 pwncatalog/PWNCAT2/paper/sections/results.tex
update

@@
 
-Results goes here\ldots
+First, we tested the sources to see if they
+were spatially extended. The localization results are in \tabref{localization}.
 
-\tabref{all_energy} shows the results of the all energy analysis of the off-peak emission for each pulsar.
+\begin{deluxetable}{l*{7}c}
+\tabletypesize{\scriptsize}
+\tablecaption{Localization and extension fitting results
+\label{tab:localization}
+}
+\input{tables/localization.tex}
+\tablecomments{\todo[inline]{Put table comments}}
+\end{deluxetable}
 
-\tabref{each_energy} shows the results of the analysis in separate energy bins of each pulsar.
+Next, we performed a spectral analysis over all energy using the best
+fit morphology. \tabref{all_energy} shows the results of the all energy
+analysis of the off-peak emission for each pulsar.
 
-\tabref{cutoff_test} shows the results of the cutoff test for pulsars with significant low-energy emission.
+Next, we fit a powerlaw independently in each energy
+bin. \tabref{each_energy} shows the results of the analysis in separate
+energy bins of each pulsar.
+
+Finally, we tested sources to see which were
+variable. \tabref{cutoff_test} shows the results of the cutoff test for
+pulsars with significant low-energy emission.
 
@@
 
-The localization results are in \tabref{localization}
-
-\begin{deluxetable}{l*{7}c}
-\tabletypesize{\scriptsize}
-\tablecaption{Localization and extension fitting results
-\label{tab:localization}
-}
-\input{tables/localization.tex}
-\tablecomments{\todo[inline]{Put table comments}}
-\end{deluxetable}
-
 \figref{cutoff_test} shows the cutoff test\ldots

### 2012-02-15 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
rename

--- 2011-12-09 presentations/extended_source_search/lande_ext_src_search_walthrough/lande_ext_src_search_walthrough.tex
@@
 
-\author{Joshua Lande}
-\institute{SLAC/Stanford}
-\email{joshualande@gmail.com}
+\author{Joshua Lande,\\
+Stefan Funk,\\
+Markus Ackermann}
 \date{August 25, 2011}
@@
 \begin{frame}{Section 2.1. Modeling Extended Sources in the \texttt{pointlike} Package}
+  New method to study spatially-extended {\em Fermi}-LAT sources
   \begin{itemize}
-    \item Short Description of \texttt{pointlike}
+    \item Description of \texttt{pointlike}
     \item Implementation of extended sources
     \item Simultaneously Fit position + extension
-    \item optimization of likelihood computation
+    \item speed up likelihood computation
     \item Cross check TS + spectral values using \texttt{gtlike}
@@
       \item Good agreement with Wilk's Theorem
-      \item Proves that we can use $\sqrt{\mathrm{TS}_\mathrm{ext}}$
+      \item Use $\sqrt{\mathrm{TS}_\mathrm{ext}}$
         as a measure of significance
@@
     \column{.6\textwidth}
-    \includegraphics[scale=0.4]{plots/agn_color.pdf}
+    \includegraphics[scale=0.45]{plots/agn_color.pdf}
     \column{.4\textwidth}
-Use point-like AGN to validate extended source study
     \begin{itemize}
+      \item Use point-like AGN to validate extended source analysis
       \item Test clean 2LAC AGN for extension
@@
 
-\begin{frame}{Extended source systematics}
-  \begin{itemize}
-    \item \dots
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Reanalyze extended sources in 2FGL}
+\begin{frame}{Section 7: extended sources in 2FGL}
   \begin{columns}
@@
       \item Test 12 extended 2FGL sources for extension
-      \item Systematic re-analytis using 2 years of data.
+      \item Systematic reanalysis using 2 years of data.
       \item Assume uniform disk
+      \item Extended sources are extended!
     \end{itemize}
@@
 
-\begin{frame}{Extended Source Search}
+\begin{frame}{Section 8: Extension Systematics}
+  Test systematics due to not knowing PSF
+  \begin{itemize}
+    \item Compare best fit extension to 
+      MC based PSF
+    \item Use difference as systematic
+    \item Small effect on extension, large effect on statistical 
+      significance
+    \item Probably too conservative\dots
+  \end{itemize}
+  Test systematics due to not knowing PSF
+  \begin{itemize}
+    \item Break up GALPROP diffuse model into multiple components 
+    \item Fit each component locally
+    \item Tests systematics due to imperfect diffuse modeling
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Section 9: Extended Source Search}
   \begin{itemize}
@@
       extended 2FGL sources
-    \item Search for $E>1$ and GeV $E>10$ GeV
+    \item Search for $E>1$ GeV and $E>10$ GeV
     \item Many difficulties in search, discussed at length in text\dots
@@
 
-\begin{frame}{New extended Sources (not in 2FGL)}
+\begin{frame}{Section 10: New extended Sources}
   \begin{columns}
@@
     \begin{itemize}
-      \item 7 new extended sources
+      \item 6 new extended sources
       \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
@@
     \item Coincident with HESS\,J1616$-$508
-    \item Coincident with X-ray pulsar
+    \item + X-ray pulsar
 PSR\,J1617$-$5055 + $\sim 1'$ PWN 
@@
     \item (right):
-      2FGL\,J1615.2$-$5138 $\rightarrow$ HESS\,J1614$-$518
-    \item No compelling counterpart
+      2FGL\,J1615.2$-$5138 
+    \item Coincident with HESS\,J1614$-$518
+    \item No other compelling multiwavelenth counterpart
   \end{itemize}
@@
     \end{itemize}
-
   \end{columns}
@@
 
+\begin{frame}{Thank you}
+  See text for more details:
+  \begin{itemize}
+    \item
+  \url{https://www-glast.stanford.edu/cgi-prot/pub_download?id=662}
+  \end{itemize}
+
+\end{frame}
+
 \end{document}

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
update
new

@@
 Markus Ackermann}
-\date{August 25, 2011}
+\date{February 15, 2012}
 
@@
 
-  \includegraphics[scale=0.45]{plots/title.png}
+  \includegraphics[scale=0.65]{plots/title.pdf}
 
@@
     \item Cat II paper
-    \item Target Journal: ApJ
-    \item Pub Board: \url{https://www-glast.stanford.edu/cgi-prot/pub_download?id=662}
     \item Internal referees: Marianne Lemoine-Goumard + Johann Cohen-Tanugi (+ unofficially Jean Ballet)
-      \begin{itemize}
-        \item Thanks for all your help!
-      \end{itemize}
-    \item Ready for submission
+    \item Submitted to ApJ
   \end{itemize}
@@
 
-\begin{frame}{Fig. 3+4: False-Detection Rate}
+\begin{frame}{Fig. 2: LAT PSF}
+    \includegraphics[scale=0.5]{plots/compare_disk_gauss_color.pdf}
+\end{frame}
+
+\begin{frame}{Table 1: False-Detection Rate}
   \begin{columns}
     \column{.5\textwidth} 
-    \includegraphics[scale=0.4]{plots/ts_ext_emin_1000_color.pdf}
+    \includegraphics[scale=0.35]{plots/table_1.pdf}
     \column{.5\textwidth} 
@@
 
-\begin{frame}{Fig. 5+6+7: Detection Threshold}
+\begin{frame}{Fig. 3+4: False-Detection Rate (cont)}
+  \begin{columns}
+    \column{.5\textwidth} 
+    \includegraphics[scale=0.35]{plots/ts_ext_emin_1000_color.pdf}
+    \column{.5\textwidth} 
+    \includegraphics[scale=0.35]{plots/ts_ext_emin_10000_color.pdf}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 5: Detection Threshold}
   \begin{columns}
     \column{.6\textwidth}
-    \includegraphics[scale=0.5]{plots/all_sensitivity_color.pdf}
+    \includegraphics[scale=0.5]{plots/index_sensitivity_color.pdf}
     \column{.4\textwidth}
@@
 
-\begin{frame}{Fig. 8+9: Effects of Source Confusion}
-  Non-nested model comparison
-  \begin{equation*}
-    \text{TS}_\text{2pts} = 2 \log(\mathcal{L}_\text{2pts}/\mathcal{L}_\text{ps})
-  \end{equation*}
+\begin{frame}{Fig. 6: Detection Threshold (cont)}
+  \begin{columns}
+    \column{.6\textwidth}
+    \includegraphics[scale=0.5]{plots/all_sensitivity_color.pdf}
+    \column{.4\textwidth}
+    \begin{itemize}
+      \item Compute sensitivty for different background levels, energy ranges.
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 7: Detection Threshold (cont)}
+  \begin{columns}
+    \column{.6\textwidth}
+    \includegraphics[scale=0.5]{plots/time_sensitivity_color.pdf}
+    \column{.4\textwidth}
+    \begin{itemize}
+      \item Compute sensitivty after 10 years.
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 8: Effects of Source Confusion}
+  \begin{columns}
+    \column{.6\textwidth}
+    \includegraphics[scale=0.50]{plots/confusion_extended_plot_color.pdf}
+    \column{.4\textwidth}
+    \begin{enumerate}
+      \item Non-nested model comparison
+        \begin{multline*}
+          \text{TS}_\text{2pts} =  \\
+          2 \log(\mathcal{L}_\text{2pts}/\mathcal{L}_\text{ps})
+        \end{multline*}
+      \item Simulate extended sources. 
+      \item Fit as point-like sources.
+    \end{enumerate}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 9: Effects of Source Confusion (cont)}
 
   \begin{columns}
+
     \column{.6\textwidth}
-    \includegraphics[scale=0.30]{plots/confusion_2pts_plot_color.pdf}
-
-    Simulate extended sources. Fit as point-like sources.
-
+    \includegraphics[scale=0.50]{plots/confusion_2pts_plot_color.pdf}
     \column{.4\textwidth}
-    \includegraphics[scale=0.30]{plots/confusion_extended_plot_color.pdf}
-
-    Simulate point-like sources. Fit for extension.
+    \begin{enumerate}
+      \item Simulate point-like sources. 
+      \item Fit for extension.
+    \end{enumerate}
   \end{columns}
@@
 
+\begin{frame}{Fig. 1: IC~443}
+    \includegraphics[scale=0.5]{plots/four_plots_ic443_color.pdf}
+\end{frame}
+
+\begin{frame}{Fig. 11: Residual TS Map}
+  \includegraphics[scale=0.5]{plots/res_tsmap_ic443_color.pdf}
+\end{frame}
+
 \begin{frame}{Section 7: extended sources in 2FGL}
@@
   \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 12: Systematics in the plane}
+  \includegraphics[scale=0.5]{plots/example_bad_fit_color.pdf}
 \end{frame}

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
improve
update

@@
 
+\begin{frame}{Table 2: Detection Threshold (cont)}
+  \includegraphics[scale=0.5]{plots/threshold_table.pdf}
+\end{frame}
+
 \begin{frame}{Fig. 7: Detection Threshold (cont)}
@@
 
-\begin{frame}{Section 7: extended sources in 2FGL}
+\begin{frame}{Table 3: extended sources in 2FGL}
   \begin{columns}
@@
 
+\begin{frame}{Section 9: Extended Source Search}
+  \begin{itemize}
+    \item Run a dedicated search 
+    \item Find previously-unresolved
+      extended 2FGL sources
+    \item Search for $E>1$ GeV and $E>10$ GeV
+    \item Many difficulties in search, discussed at length in text\dots
+    \item Publish only good candidates
+  \end{itemize}
+\end{frame}
+
 \begin{frame}{Fig. 12: Systematics in the plane}
   \includegraphics[scale=0.5]{plots/example_bad_fit_color.pdf}
+\end{frame}
+
+\begin{frame}{Table 4: New extended Sources}
+  \begin{columns}
+    \column{.65\textwidth}
+    \includegraphics[scale=0.30]{plots/new_extended.pdf}
+    \column{.35\textwidth}
+    \begin{itemize}
+      \item 6 new extended sources
+      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
+      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
+    \end{itemize}
+  \end{columns}
 \end{frame}
@@
 
-\begin{frame}{Section 9: Extended Source Search}
-  \begin{itemize}
-    \item Run a dedicated search 
-    \item Find previously-unresolved
-      extended 2FGL sources
-    \item Search for $E>1$ GeV and $E>10$ GeV
-    \item Many difficulties in search, discussed at length in text\dots
-    \item Publish only good candidates
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Section 10: New extended Sources}
-  \begin{columns}
-    \column{.65\textwidth}
-    \includegraphics[scale=0.30]{plots/new_extended.png}
-    \column{.35\textwidth}
-    \begin{itemize}
-      \item 6 new extended sources
-      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
-      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
-    \end{itemize}
-  \end{columns}
+\begin{frame}{Table 5: Dual Localization, alternative PSF, alternative Diffuse}
+  \includegraphics[scale=0.40]{plots/alt_diff.pdf}
 \end{frame}
@@
   \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 14: SED of SNRs}
+  \includegraphics[scale=0.5]{plots/snr_seds_color.pdf}
 \end{frame}
@@
 
+\begin{frame}{Fig. 18: SED of HESS Sources}
+  \includegraphics[scale=0.5]{plots/hess_seds_color.pdf}
+\end{frame}
+
+\begin{frame}{Fig. 20: SED of RX J1713.7$-$3946}
+  \includegraphics[scale=0.5]{plots/source_RX_J1713_7-3946_color.pdf}
+\end{frame}
+
 \begin{frame}{Thank you}

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
add
update

@@
 
-\begin{frame}{Fig. 1: IC~443}
-    \includegraphics[scale=0.5]{plots/four_plots_ic443_color.pdf}
-\end{frame}
-
-\begin{frame}{Fig. 11: Residual TS Map}
-  \includegraphics[scale=0.5]{plots/res_tsmap_ic443_color.pdf}
+\begin{frame}{Fig. 1 + 11: IC~443}
+  Most significantly extended source
+  \begin{columns}
+    \column{.5\textwidth}
+    \includegraphics[scale=0.35]{plots/four_plots_ic443_color.pdf}
+    \column{.5\textwidth}
+  \includegraphics[scale=0.35]{plots/res_tsmap_ic443_color.pdf}
+  \end{columns}
 \end{frame}
@@
   \includegraphics[scale=0.5]{plots/example_bad_fit_color.pdf}
-\end{frame}
-
-\begin{frame}{Table 4: New extended Sources}
-  \begin{columns}
-    \column{.65\textwidth}
-    \includegraphics[scale=0.30]{plots/new_extended.pdf}
-    \column{.35\textwidth}
-    \begin{itemize}
-      \item 6 new extended sources
-      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
-      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
-    \end{itemize}
-  \end{columns}
-\end{frame}
-
-\begin{frame}{Section 8: Extension Systematics}
-  Test systematics due to not knowing PSF
-  \begin{itemize}
-    \item Compare best fit extension to 
-      MC based PSF
-    \item Use difference as systematic
-    \item Small effect on extension, large effect on statistical 
-      significance
-    \item Probably too conservative\dots
-  \end{itemize}
-  Test systematics due to not knowing PSF
-  \begin{itemize}
-    \item Break up GALPROP diffuse model into multiple components 
-    \item Fit each component locally
-    \item Tests systematics due to imperfect diffuse modeling
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Table 5: Dual Localization, alternative PSF, alternative Diffuse}
-  \includegraphics[scale=0.40]{plots/alt_diff.pdf}
 \end{frame}
@@
 
-\begin{frame}{Fig. 20: SED of RX J1713.7$-$3946}
+\begin{frame}{Fig. 20: RX J1713.7$-$3946}
   \includegraphics[scale=0.5]{plots/source_RX_J1713_7-3946_color.pdf}
+\end{frame}
+
+\begin{frame}{Table 4: New extended Sources}
+  \begin{columns}
+    \column{.65\textwidth}
+    \includegraphics[scale=0.30]{plots/new_extended.pdf}
+    \column{.35\textwidth}
+    \begin{itemize}
+      \item 6 new extended sources
+      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
+      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Section 8: Extension Systematics}
+  Test systematics due to not knowing PSF
+  \begin{itemize}
+    \item Compare best fit extension to 
+      MC based PSF
+    \item Use difference as systematic
+    \item Small effect on extension, large effect on statistical 
+      significance
+    \item Probably too conservative\dots
+  \end{itemize}
+  Test systematics due to not knowing PSF
+  \begin{itemize}
+    \item Break up GALPROP diffuse model into multiple components 
+    \item Fit each component locally
+    \item Tests systematics due to imperfect diffuse modeling
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Table 5: Dual Localization, alternative PSF, alternative Diffuse}
+  \includegraphics[scale=0.40]{plots/alt_diff.pdf}
+\end{frame}
+
+\begin{frame}{Fig 23: Sky Map of Extended Sources}
+\includegraphics[scale=0.50]{plots/allsky_extended_sources_color.pdf}
+\end{frame}
+
+\begin{frame}{Fig 24: Compare GeV and TeV Sizes}
+  \includegraphics[scale=0.50]{plots/gev_vs_tev_plot_color.pdf}
+\end{frame}
+
+\begin{frame}{Fig 25: GeV and TeV Sizes (cont)}
+  \includegraphics[scale=0.40]{plots/gev_vs_tev_histogram_color.pdf}
+\end{frame}
+
+\begin{frame}{Fig 26: Distribution of Spectral Indices}
+  \includegraphics[scale=0.40]{plots/compare_index_2FGL_color.pdf}
 \end{frame}

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
improve

@@
 
-\begin{frame}{2 Extended SNRs}
+\begin{frame}{Fig 13: Puppis A}
+
   \begin{columns}
     \column{.50\textwidth} 
-    Puppis A
+    \includegraphics[scale=0.50]{plots/source_Puppis_A_color.pdf}
 
-    \includegraphics[scale=0.40]{plots/source_Puppis_A_color.pdf}
-
+    \column{.50\textwidth} 
     \begin{itemize}
@@
       \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Fig 22: $\gamma$-Cygni}
+  \begin{columns}
 
     \column{.50\textwidth} 
-    $\gamma$-Cygni
+    \includegraphics[scale=0.50]{plots/source_Gamma_Cygni_color.pdf}
 
-    \includegraphics[scale=0.40]{plots/source_Gamma_Cygni_color.pdf}
+    \column{.50\textwidth}
 
@@
 \begin{frame}{Fig. 14: SED of SNRs}
-  \includegraphics[scale=0.5]{plots/snr_seds_color.pdf}
+  \includegraphics[scale=0.65]{plots/snr_seds_color.pdf}
 \end{frame}
@@
 
-\begin{frame}{2 More PWN Candidate}
-
+\begin{frame}{Fig 19: 2FGL\,J1632.4$-$4753c }
   \begin{columns}
-    \column{.45\textwidth}
-
-2FGL\,J1632.4$-$4753c
-
-    \includegraphics[scale=0.3]{plots/source_HESS_J1632-478_color.pdf}
-
+    \column{.6\textwidth} 
+    \includegraphics[scale=0.5]{plots/source_HESS_J1632-478_color.pdf}
+    \column{.4\textwidth}
     \begin{itemize}
@@
     \end{itemize}
+    \end{columns}
+    \end{frame}
 
+    \begin{frame}{Fig 21: 2FGL\,J1837.3$-$0700c}
+    \begin{columns}
     \column{.60\textwidth} 
-
-    2FGL\,J1837.3$-$0700c
-
-    \includegraphics[scale=0.3]{plots/source_HESS_J1837-069_color.pdf}
-
+    \includegraphics[scale=0.5]{plots/source_HESS_J1837-069_color.pdf}
+    \column{.40\textwidth} 
     \begin{itemize}
@@
 \begin{frame}{Fig. 20: RX J1713.7$-$3946}
-  \includegraphics[scale=0.5]{plots/source_RX_J1713_7-3946_color.pdf}
+  \includegraphics[scale=0.65]{plots/source_RX_J1713_7-3946_color.pdf}
+
+  Beautiful GeV Image for E$>$10 GeV!
 \end{frame}

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
update

@@
 
-\begin{frame}{Section 2.1. Modeling Extended Sources in the \texttt{pointlike} Package}
-  New method to study spatially-extended {\em Fermi}-LAT sources
+\begin{frame}{Sec. 2: Extended Sources in \texttt{pointlike}}
   \begin{itemize}
-    \item Description of \texttt{pointlike}
-    \item Implementation of extended sources
-    \item Simultaneously Fit position + extension
-    \item speed up likelihood computation
+    \item Pointlike designed for speed
+    \begin{itemize}
+    \item Scale pixel size with energy
+    \item Sparse Matricies
+    \item Other optimizations in evaluating likelihood
+    \end{itemize}
+    \item Implementation of extended sources in pointlike
+    \begin{itemize}
+      \item Semi-Analytic Convolution to speed up calculation
+    \end{itemize}
+    \item Simultaneously Fit position + extension with MINUIT
     \item Cross check TS + spectral values using \texttt{gtlike}
@@
 \begin{frame}{Fig. 2: LAT PSF}
-    \includegraphics[scale=0.5]{plots/compare_disk_gauss_color.pdf}
+  \begin{columns}
+    \column{.55\textwidth} 
+    \includegraphics[scale=0.50]{plots/compare_disk_gauss_color.pdf}
+    \column{.45\textwidth} 
+    \begin{itemize}
+      \item Compare Disk, Gauss, and their convolutions with 
+      the PSF
+      \item For smaller extended sources, little sensitivity
+      to spatial shape
+    \end{itemize}
+  \end{columns}
 \end{frame}
@@
     \includegraphics[scale=0.35]{plots/ts_ext_emin_1000_color.pdf}
+
+    Fig 3: 1 GeV to 100 GeV
     \column{.5\textwidth} 
     \includegraphics[scale=0.35]{plots/ts_ext_emin_10000_color.pdf}
+
+    Fig 4: 10 GeV to 100 GeV
   \end{columns}
@@
       \item Vary spectra, background, energy range
-      \item Overlay extended sources
-      \item Reference for future publications!
+      \item More sensitive to Harder sources
+      \item Not sensitive to very small extended sources
     \end{itemize}
@@
   \begin{columns}
-    \column{.6\textwidth}
-    \includegraphics[scale=0.5]{plots/all_sensitivity_color.pdf}
-    \column{.4\textwidth}
+    \column{.60\textwidth}
+    \includegraphics[scale=0.45]{plots/all_sensitivity_color.pdf}
+    \column{.40\textwidth}
     \begin{itemize}
-      \item Compute sensitivty for different background levels, energy ranges.
+      \item Compute sensitivty for 
+    \begin{itemize}
+      \item different background levels
+      \item energy ranges.
+      \item Spectral Indices
+    \end{itemize}
+    \item Little index dependence to sensitivity 
+      for hard or larger sources
+      \item Overlay extended sources 
+      $\rightarrow$ Good we are sensitive to them
     \end{itemize}
@@
     \column{.6\textwidth}
-    \includegraphics[scale=0.5]{plots/time_sensitivity_color.pdf}
+    \includegraphics[scale=0.50]{plots/time_sensitivity_color.pdf}
     \column{.4\textwidth}
@@
       \item Compute sensitivty after 10 years.
+      \item Improvement better than $\sqrt{n}$ for
+      small sources
+      \item True becasue sensitivity dominated by
+      high energy $\rightarrow$ not background limited
     \end{itemize}
@@
 \begin{frame}{Fig. 8: Effects of Source Confusion}
+
+Is it an extended source or two point sources?
+
+        \begin{equation*}
+          \text{TS}_\text{2pts} =  
+          2 \log(\mathcal{L}_\text{2pts}/\mathcal{L}_\text{ps})
+        \end{equation*}
+
   \begin{columns}
-    \column{.6\textwidth}
-    \includegraphics[scale=0.50]{plots/confusion_extended_plot_color.pdf}
-    \column{.4\textwidth}
+    \column{.60\textwidth}
+    \includegraphics[scale=0.40]{plots/confusion_extended_plot_color.pdf}
+    \column{.40\textwidth}
     \begin{enumerate}
       \item Non-nested model comparison
-        \begin{multline*}
-          \text{TS}_\text{2pts} =  \\
-          2 \log(\mathcal{L}_\text{2pts}/\mathcal{L}_\text{ps})
-        \end{multline*}
       \item Simulate extended sources. 
       \item Fit as point-like sources.
+      \item Can easily fit an extended
+      source as two point-like sources
     \end{enumerate}
@@
 
-    \column{.6\textwidth}
-    \includegraphics[scale=0.50]{plots/confusion_2pts_plot_color.pdf}
-    \column{.4\textwidth}
+    \column{.65\textwidth}
+    \includegraphics[scale=0.45]{plots/confusion_2pts_plot_color.pdf}
+    \column{.35\textwidth}
     \begin{enumerate}
@@
       \item Fit for extension.
+      \item Not likely to confuse two point-like sources
+      as an extended source
     \end{enumerate}
@@
 \begin{frame}{Fig. 1 + 11: IC~443}
-  Most significantly extended source
+\begin{itemize}
+\item IC443 is the Most significantly extended source
+\item Below are diagnostic plots
+\end{itemize}
   \begin{columns}
@@
       \includegraphics[scale=0.35]{plots/four_plots_ic443_color.pdf}
+
     \column{.5\textwidth}
       \includegraphics[scale=0.35]{plots/res_tsmap_ic443_color.pdf}
+
+      Residual TS Map 
+      \begin{itemize}
+      \item (a) IC443 a point source 
+      \item (b) IC443 extended
+      \end{itemize}
   \end{columns}
@@
     \item Run a dedicated search 
-    \item Find previously-unresolved
+    \item Try to find previously-unresolved
       extended 2FGL sources
@@
   \begin{columns}
-    \column{.50\textwidth} 
+    \column{.60\textwidth} 
     \includegraphics[scale=0.50]{plots/source_Puppis_A_color.pdf}
 
-    \column{.50\textwidth} 
+    \column{.40\textwidth} 
     \begin{itemize}
-      \item X-ray contours
-      \item Mid-aged SNR
-      \item Not observed to directly interact with molecular
-        clouds
+    \item 1 GeV to 100 GeV
+      \item Middle-aged SNR
+      \item ROSAT X-ray contours (Petre+1996)
+      \item SNR not observed to interact with
+      molecular clouds (Paron+2008)
+      \item Similar to Cygnus Loop
       \end{itemize}
@@
 
-    \column{.50\textwidth} 
+    \column{.55\textwidth} 
     \includegraphics[scale=0.50]{plots/source_Gamma_Cygni_color.pdf}
 
-    \column{.50\textwidth}
+    \column{.45\textwidth}
 
     \begin{itemize}
-      \item Radio contours
-      \item SNR interacting with molecular clouds?
-      \item Veritas + Milagro detections
+      \item 10 GeV to 100 GeV
+      \item PSR\,J2021+4026 at lower energies
+      \item Radio contours (Taylor+2003)
+      \item SNR interacting with Molecular cloud
+      \item Milagro: $4.2\sigma$ excess at $\sim 30$ TeV (Abdo+2009)
+      \item 
+        VER\,J2019+407 
+        detected by Veritas at 200 GeV (Weinstein 2009)
       \end{itemize}
@@
 
-\begin{frame}{Two Nearby LAT extended sources}
-
+\begin{frame}{Fig 17. HESS\,J1614$-$518 \& HESS\,J1616$-$508}
   \begin{columns}
@@
     \begin{itemize}
-    \item (left): 
-      2FGL\,J1615.0$-$5051
-    \item Coincident with HESS\,J1616$-$508
-    \item + X-ray pulsar
-PSR\,J1617$-$5055 + $\sim 1'$ PWN 
-    \item PWN Candidate
+      \item 10 GeV to 100 GeV
+      \item Two nearby LAT extended sources 
+      \item both
+        coincident with extended TeV sources.
     \end{itemize}
@@
   \begin{itemize}
+    \item (left): 
+      2FGL\,J1615.0$-$5051 $\rightarrow$ HESS\,J1616$-$508
     \item (right):
-      2FGL\,J1615.2$-$5138 
-    \item Coincident with HESS\,J1614$-$518
-    \item No other compelling multiwavelenth counterpart
+      2FGL\,J1615.2$-$5138 $\rightarrow$ HESS\,J1614$-$518
   \end{itemize}
+
 \end{frame}
 
-\begin{frame}{Fig 19: 2FGL\,J1632.4$-$4753c }
+\begin{frame}{2FGL\,J1615.0$-$5051 $\rightarrow$ HESS\,J1616$-$508}
   \begin{columns}
-    \column{.6\textwidth} 
-    \includegraphics[scale=0.5]{plots/source_HESS_J1632-478_color.pdf}
     \column{.4\textwidth} 
+    % from http://www.mpi-hd.mpg.de/hfm/HESS/pages/home/som/2007/01/
+  \includegraphics[scale=0.45]{plots/Som_1_07_p1.jpg}
+    \column{.7\textwidth} 
   \begin{itemize}
-      \item Coincident with HESS\,J1632-478
-
-      \item  {\em XMM-Newton} point-like + extended emission
-      \item (but no pulsations)
-      \item PWN Candidate
+    \item 2 nearby SNRs: RCW103 and Kes~32 - not spatially coincident (Aharonian+2006) 
+    \item 3 Nearby Pulsars: only 
+      PSR\,J1617$-$5055 energetically powerful enough
+      \begin{itemize}
+        \item 9' away $\rightarrow$ offset PWN?
+        \item {\em Chandra} detected $\sim 1'$ PWN 
+        \item not oriented towards HESS\,J1616$-$508
+        \end{itemize}
+      \item Other diffuse emission in region (Kargaltsev+2009)
     \end{itemize}
@@
 
-    \begin{frame}{Fig 21: 2FGL\,J1837.3$-$0700c}
+\begin{frame}{2FGL\,J1615.2$-$5138 $\rightarrow$ HESS\,J1614$-$518}
+
   \begin{columns}
-    \column{.60\textwidth} 
-    \includegraphics[scale=0.5]{plots/source_HESS_J1837-069_color.pdf}
-    \column{.40\textwidth} 
+    \column{.4\textwidth} 
+    \includegraphics[scale=0.3]{plots/Som_9_08_p1.jpg}
+    \column{.7\textwidth} 
     \begin{itemize}
-      \item Coincident with HESS\,J1837-069
-      \item + X-ray pulsar PSR\,J1838$-$0655 
-      \item + $\sim 2'$ X-ray PWN 
-      \item PWN candidate
-      \item Second X-ray PSR + PWN candidate in region
-        (but no pulsations)
+      \item 5 nearby pulsars, but none powerful enough (Rowell+2008)
+      \item Open cluster Pisim 22 
+      \item Suzaku: 2 X-ray sources, one towards peak 
+        of HESS\,J1614$-$518 and one coincident with Pisim 22
+        (Matsumoto+2008)
+      \item SNR? PWN? Acceleration in Stellar Winds of Pisim 22?
     \end{itemize}
   \end{columns}
+\end{frame}
+
+\begin{frame}{Fig. 19: HESS\,J1632-478}
+  \begin{columns}
+    \column{.65\textwidth} 
+    \includegraphics[scale=0.5]{plots/source_HESS_J1632-478_color.pdf}
+    \column{.35\textwidth} 
+    \begin{itemize}
+      \item 10 GeV to 100 GeV
+      \item  {\em XMM-Newton} point-like + extended emission
+        ($32''\times15''$)
+    \end{itemize}
+  \end{columns}
+
+  \begin{itemize}
+      \item PWN? No pulsations (yet) in point-like X-ray source
+        towards center of H.E.S.S source (Balbo+2010)
+      \item Extended radio source in archival MGPS-2 data
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Fig. 21: HESS\,J1837-069}
+  \begin{columns}
+    \column{.55\textwidth} 
+    \includegraphics[scale=0.45]{plots/source_HESS_J1837-069_color.pdf}
+    \column{.45\textwidth} 
+    \begin{itemize}
+      \item 10 GeV to 100 GeV
+      \item Coincident with X-ray source
+        AX\,J1838$-$0655 (Hertz \& Grindlay 1988)
+      \item X-ray Pulsations: PSR\,J1838$-$0655 
+    \end{itemize}
+  \end{columns}
+    \begin{itemize}
+      \item also: X-ray PWN $\sim 2'$ 
+        (Gotthelf \& Halpern 2008)
+      \item $\gamma$-rays from PWN?
+      \item Second X-ray source
+        AX\,J1837.3$-$0652 resolved into
+        point + extended component (no pulsations yet)
+      \item $\gamma$-rays from multiple PWN
+    \end{itemize}
 \end{frame}
@@
   \includegraphics[scale=0.65]{plots/source_RX_J1713_7-3946_color.pdf}
-
-  Beautiful GeV Image for E$>$10 GeV!
+  \begin{itemize}
+  \item Beautiful GeV Image for E$>$10 GeV!
+  \end{itemize}
 \end{frame}
@@
 \begin{frame}{Table 4: New extended Sources}
-  \begin{columns}
-    \column{.65\textwidth}
-    \includegraphics[scale=0.30]{plots/new_extended.pdf}
-    \column{.35\textwidth}
-    \begin{itemize}
-      \item 6 new extended sources
-      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
-      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
-    \end{itemize}
-  \end{columns}
+    \includegraphics[scale=0.50]{plots/new_extended.pdf}
 \end{frame}
@@
 
-\begin{frame}{Table 5: Dual Localization, alternative PSF, alternative Diffuse}
-  \includegraphics[scale=0.40]{plots/alt_diff.pdf}
+\begin{frame}{Table 5: Dual Localization, alternate PSF, alternate Diffuse}
+  \includegraphics[scale=0.45]{plots/alt_diff.pdf}
 \end{frame}
 
-\begin{frame}{Fig 23: Sky Map of Extended Sources}
-\includegraphics[scale=0.50]{plots/allsky_extended_sources_color.pdf}
+\begin{frame}{Fig 23: Skymap of Extended Sources}
+\includegraphics[scale=0.60]{plots/allsky_extended_sources_color.pdf}
 \end{frame}
@@
 \begin{frame}{Fig 24: Compare GeV and TeV Sizes}
-  \includegraphics[scale=0.50]{plots/gev_vs_tev_plot_color.pdf}
+  \includegraphics[scale=0.60]{plots/gev_vs_tev_plot_color.pdf}
 \end{frame}
@@
 \begin{frame}{Fig 25: GeV and TeV Sizes (cont)}
-  \includegraphics[scale=0.40]{plots/gev_vs_tev_histogram_color.pdf}
+  \includegraphics[scale=0.60]{plots/gev_vs_tev_histogram_color.pdf}
 \end{frame}
@@
 \begin{frame}{Fig 26: Distribution of Spectral Indices}
-  \includegraphics[scale=0.40]{plots/compare_index_2FGL_color.pdf}
+  \includegraphics[scale=0.60]{plots/compare_index_2FGL_color.pdf}
 \end{frame}
@@
   \end{itemize}
-
 \end{frame}

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
update

@@
   \begin{itemize}
-    \item Run a dedicated search 
-    \item Try to find previously-unresolved
+    \item Run a dedicated search for new
     extended 2FGL sources
+    \item Test for extension using pointlike, crosscheck with gtlike
     \item Search for $E>1$ GeV and $E>10$ GeV
@@
 \begin{frame}{Fig. 12: Systematics in the plane}
+  \begin{columns}
+    \column{.60\textwidth} 
   \includegraphics[scale=0.5]{plots/example_bad_fit_color.pdf}
+    \column{.40\textwidth} 
+    \begin{itemize}
+    \item Easy to find ``Significantly'' extended sources
+    in the galactic plane
+    \item Caused by residuals due to
+    \begin{itemize}
+    \item Diffuse residuals
+    \item Unmodeled or incorrectly modeled sources
+    \end{itemize}
+    \item No easy solution, in the text we discared these sources
+      \end{itemize}
+  \end{columns}
 \end{frame}

### 2012-02-22 pwncatalog/PWNCAT2/code/lande/publication_plots/extul/plot_extul.py
update

@@ -12,89 +12,88 @@ import numpy as np
 
 from uw.like.roi_plotting import DegreesFormatter
 
-from lande_plotting import fix_axesgrid
+from lande_plotting import label_axesgrid
 
 bw=plot_helper.get_bw()
 
-fig = P.figure(None,(6,6))
+for type in ['dim','bright']:
 
-grid = Grid(fig, 111, 
-            nrows_ncols = (5, 1),
-            share_all=False,
-            axes_pad=0.2)
+    fig = P.figure(None,(6,6))
 
-from uw.utilities.makerec import fitsrec
-r = fitsrec('cached.fits')
-print r
+    grid = Grid(fig, 111, 
+                nrows_ncols = (4, 1),
+                share_all=False,
+                axes_pad=0.2)
 
-extension_mc = r['extension_mc']
-extension_ul = r['extension_ul']
-index_mc = r['index_mc']
-ts_point = r['ts_point']
-ts_ext = r['ts_ext']
-flux_mc = r['flux_mc']
-type = np.char.strip(r['type'])
+    from uw.utilities.makerec import fitsrec
 
-for index, plot_kwargs in [
-                           [1.5, dict(label=r'$\gamma=1.5$', color='blue' )],
-                           [2,   dict(label=r'$\gamma=2$',   color='red'  )],
-                           [2.5, dict(label=r'$\gamma=2.5$', color='green')],
-                           [3,   dict(label=r'$\gamma=3$',   color='black')]
-                          ]:
+    r = fitsrec('/nfs/slac/g/ki/ki03/lande/pwncatalog/PWNCAT2/analyze_psr/monte_carlo/extul/v9/cached.fits')
+    print r
 
-    cut = (index_mc == index) & (type=='dim')
-    #cut = (index_mc == index) & (type=='bright')
+    extension_mc = r['extension_mc']
+    extension_ul = r['extension_ul']
+    index_mc = r['index_mc']
+    ts_point = r['ts_point']
+    ts_ext = r['ts_ext']
+    flux_mc = r['flux_mc']
+    type_array = np.char.strip(r['type'])
 
-    extlist = np.sort(np.unique(extension_mc[cut]))
+    for index, plot_kwargs in [
+                               [1.5, dict(label=r'$\gamma=1.5$', color='blue' )],
[…]

### 2012-02-22 pwncatalog/PWNCAT2/paper/sections/analysis_of_the_fermi_lat_data.tex
new extension ul code
improve discussion of extension upper limits

@@
 \item Perform localization or extension fitting using \gtlike using energies from 1 \gev to 316 \gev.
+\item If it is point-like, perform an extension upper limit analysis 
 \item Perform spectral analysis using \gtlike for energies above 100 \mev to 316 \gev.
@@
 
-When to consider the source a pulsar or PWN.
+\subsection{Variability}
+
+\subsection{When to consider the source a pulsar or PWN.}
 \begin{itemize}
   \item If extended, then it is a PWN (cannot be a pulsar)
-  \item If it is significiant for E>10 \gev, it is a PWN (too hard to be a pulsar)
+  \item If it is significiant for $E>10$ \gev, it is a PWN (too hard to be a pulsar)
   \item Otherwise, if it has a cutoff, it is a Pulsar candidate

### 2012-02-22 pwncatalog/PWNCAT2/paper/sections/extension_upper_limits.tex
improve discussion of extension upper limits

\section{Validation of Extension Upper Limits}

For sources that are significantly detected but that do not have a
significantly-detectable extension, it can often interesting to derive an
upper limit on any possible extension for the source.  Here, we present
an algorithm for obtaining an upper limit on the extension
of a currently unresolved source using a a Bayesian method proposed by Helene \citep{Helene1983}.
The same algorithm has been used by the \fermi-LAT collaboration to
obtain upper limits on the flux of point-like sources not significantly
detected at \gev energies. See for example \cite{first_cat}.

In this method, we assume a particular spatial shape for
the currently-unresolved source (for example a uniform disk
spatial distribution) and we profile over the extension of the
currently-unresolved source. For simplicty, we assume this spatial shape
is defined by a single extension parameter $\sigma$.

For a given extension, the spectral parameters
of the source as well as other nearby sources and diffuse backgrounds
are maximized to obtain the likelihood as a function of extension $\likelihood(\sigma)$.
The 95\% confidence upper limits $\sigma_{ul}$ on the extension of a source
is obtained by finding the extension $\sigma$ such that
\begin{equation}
  \int_0^{\sigma_{ul}} \likelihood(\sigma) = 0.95
\end{equation}
assuming that the likelihood is normalized such that
\begin{equation}
  \int_0^{\infty} \likelihood(\sigma) = 1
\end{equation}

For compulational efficienciy, this upper limit algorithm was implemented in \pointlike 
which introduces negligible approximations what make this alogirhtm compultationally 
tractable \citep{extended_source_search}.
Something about how this is biased by not marginalizing over the position of the extended source,
but that this is not a huge effect

To validate this method, we performed a monte carlo study of the coverage
of the extension upper limits.  Because the method is Bayesian, it has
to overcover for arbitrarily small extensions.  On the other hand, it
is reasonable to expect the method to correctly cover for larger sources.

For simplicity, In our simulation we used the same time range and background model described in section 
4 of \cite{extended_source_serach}. In particular, our simulations were performed assuming the 2FGL
pointing history against an isotropic background consistent with the 
isotropic background measured by EGRET.

We were interseted in verying the extension upper limits in two distincy energy ranges, first
for sources just on the edge of detectability (as pointlike) which could potentially be extended.
We picked for spectral indices varying from 1.5 to 4 and extensions varying from 0\fdg0 to 2\fdg0.
We selected fluxes so that $\ts_\text{point} \sim 35$ for a given flux and extension.
\figref{extul_dim} shows this monte carlo study.

The second simulation concerns sources that are very significant, comparable in brightness to, for example,
the Crab Nebula but that cannot be spatially resolved.
\figref{extul_bright} shows this monte carlo study.

\begin{figure}
  \ifdefined\bwfigures
  \plotone{extul_dim_bw.eps}
  \else
  \plotone{extul_dim_color.eps}
  \fi
  \caption{Monte carlo study.}
\label{fig:extul_dim}
\end{figure}

\begin{figure}
  \ifdefined\bwfigures
  \plotone{extul_bright_bw.eps}
  \else
  \plotone{extul_bright_color.eps}
  \fi
  \caption{Extension upper limit stuff.}
\label{fig:extul_bright}
\end{figure}

### 2012-04-23 extended_catalog/paper/extended_search.tex
reorganize
updated draft

--- 2011-12-20 extended_catalog/paper/extended_catalog.tex
@@
 we present a new systematic method for analyzing spatially extended
-LAT sources.  In Section~\ref{monte_carlo_validation}, we demonstrate
+LAT sources.  
+\newtext{
+In Section~\ref{monte_carlo_validation}, we demonstrate
 that this method can be used to test the statistical significance of the
-extension of a LAT source and in Section~\ref{extension_sensitivity}
+extension of a LAT source and in Section~\ref{bias_wrong_spatial_model}
+we asses the bias that is is introduced by using an incorrect spatial model.
+In Section~\ref{extension_sensitivity}
 we calculate the LAT detection threshold to resolve the extension
-of a source.  In Section~\ref{dual_localization_method}, we
+of a source.}
+In Section~\ref{dual_localization_method}, we
 study the ability of the LAT to 
@@
 different spatial models are lost in the noise and the LAT is not sensitive
-to the detailed spatial structure of these sources.  Therefore, in our
+to the detailed spatial structure of these sources.  
+\newtext{In section XXX, we perform a dedicated monte carlo simulation
+to asses possible bias due to incorrectly modeling the spatial structure
+of an extended source.}
+Therefore, in our
 search for extended sources we use only a radially-symmetric uniform
@@
 \section{Validation of the Analysis Method}
+
+\subsection{\newtext{Statistical Significance Testing}}
+
 \label{monte_carlo_validation}
@@
 (corresponding to a formal $4\sigma$ significance) is reasonable.
+
+\newtext{
+These previous simulations were preformed assuming an isotropic backgorund.
+We performed a second test only
+
+The flux of the source was scaled as
+\begin{equation}
+  F(\vec{x}) = F(GC) \times \left(\frac{B(\vec{x})}{B(GC)
+\end{equation}
+
+.
+The benifitted from probing a large range of fluxes and spectral indices
+and by testing two energy ranges.
+But were unable to assess any possible systematics that may be due to
+structured diffuse emission.
+
+Assessing possible difficulties due to having
+an incorrect
+
+We performed an additional Monte Carlo test with sources
+
+Figure~\ref{tsext_plane_plot}
+
+We note that this study does not asses issues due to incorrectly modeling the 
+galactic diffuse background which are much more difficult to assess. But
+this test does show the power of our tools when the model is good (or something).
+
+}
+
+\subsection{\newtext{Assessing the Bias Due to Incorrect Spatial Models}}
+\label{bias_wrong_spatial_model}
+
+\newtext{
+We performed a Monte Carlo study to asses the biases introudced by incorreclty
+modeling the spatial structure of an extended source. This is important because any assumed spatial
+model is just an approximation to the true photon distribution of the source.
+
+To assess this systematic, we simulated the spatially extended ring-type SNR W44.
+W44 was slelected because it is the most signfiicant extended source detected by the LAT 
+that has been reported as having a non-radially symmetric photon-distribution \cite{w44}.
+
+W44 was simulated with a power-law spectral model. The flux and spectral index of this source
+were taken from our re-analysis in this paper which is described in Section~\ref{validate_known}
+and summarized in Table~\label{known_extended_sources}. In particualr W44 was simulated
+with a flux of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100 \gev with a spectral
+index of 2.66.
+
+W44 was simulated with an elliptical ring spatial model described in
+\cite{w44}.  Because that publication does not provide the numbers describing
+the parameters of the ellipse, we summarize them here for completeness. The elliptical
+spatial model has a major axis of 0\fdg3 and a minor axis of 0\fdg19. The
+ellipse predicts emission only for the outer 0.75\% of the ellipse and
+the ellipse has an angle of $147\degree$ measured east of celestial north.
+
+We used a simulation setup similar to that described in
+Section~\ref{monte_carlo_validation}, but the souce was simulated on
+top of the standard galactic and isotropic diffuse background model used
+in 2FGL.  This simulation was in the 1 \gev to 100 \gev energy range and
+the sources were simulated over the two-year time range included in the
+2FGL catalog. We performed 985 identical simulations with different seeds to
+see the statistical spread in the fit values.
+
+After simulating the ring-like source, we fit the spectral and spatial parametesr of 
+the ring-like extended source with successivly more complicated spatial models.
+We obtained the best fit spatial parameters using \pointlike and, using 
+these best fit spatial paramters, obtained the best fit spectral paramters 
+using \gtlike. In total, we performed the fit using a point-like spatial model,
+using a radially-symmetric uniform Gaussian and disk spatial model, 
+an Elliptical disk spatial model, and finally the Monte Carlo true Elliptical
+ring spatial model.
+
+Figure~\ref{ts_comparison_w44sim} shows the the distribution of TS values for 
+each of the simluations when fitting the simulated sources 
+with the different spatial models. 
+Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
+fitting the simulated Elliptical ring extended source as as a point-like source.
+the source is very significant as a point source ($\ts\sim3500$).
+Figure~\ref{ts_comparison_w44sim}b shows the distirbution of \tsext values
+when fitting the source as a radially-symmetric uniform disk or Gaussian source.
+The source is very significiantly extended ($\tsext\sim250$). 
+On average \tsext is slightly larger when
+fitting the source with the Disk spatial model compared to the Gaussian spatial model.
+Considering that the simulated source's true spatial model has a sharp edge, it
+makes sense that the Disk would provide a better fit.
+
+Figure~\ref{ts_comparison_w44sim}c then shows the change in \ts (or
+twice the improvement in log likelihood) when fitting the simulated source as
+an elliptical disk compared to fitting the source as a disk. Since the change
+in \ts is $\sim30$, we see that our simulated source is significantly better
+described with an ellpitical spatial model. Finally, 
+Figure~\ref{ts_comparison_w44sim}d shows the change in \ts when fitting
+the source as an elliptical ring compared to fitting it as an elliptical disk.
+Since the change is $\sim9$, we see that the source is somewhat better described
+by the true spatial model, but not at a high statistical significance.
+
+Figure~\ref{bias_w44sim} shows the distirbution of best fit parameters
+for these simulations. Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
+show the distribututions of best fit flux and spectral indices.
+They show that when fitting this simulated extended source with a point-like
+spatial model, there is a $\sim$10\% bias in the fit flux and
+$\sim5\%$ bias in the fit index. But when fitting the sources with any of
+the extended spatial models, there is no bias in the best fit spectral parameters
+(within the precision of this Monte Carlo study. The reason for this is
+because within the finite angular precision and limited statsitics of the LAT, 
+all of the extended spatial models can be ajusted to look almost the same.
+For brighter or larger sources, this could potentially be a larger effect.
+
+Figure~\ref{bias_w44sim}c plots the best fit 68\% contaiment radius
+(\rsixeight).  For the elliptical ring spatial model, as expected
+there is no significant bias in the best fit size. What is surprising
+is that for none of the tested spatial models was the bias greater
+than $\sim10\%$. This shows that for whatever spatial model is used,
+the best fit \rsixeight is a reasonable measure of the true 68\%
+containment radius.
+
+For completeness, for the elliptical disk and ring spatial models,
+Figure~\ref{bias_w44sim}c plots the distribution of best fit eccentricity
+of the ellipse. It is defined as $\sqrt{1-b^2/a^2}$ where $a$ is the
+length of the semi-major axis and $b$ is the length of the semi-minor
+axis.  Figure~\ref{bias_w44sim}c plots the distribution of best fit
+orientation angle of the ellipse. For the elliptical spatial models,
+there is no systematic bias in the eccentricities or orentiation angles.
+For the true sptial model, there is less spread in the distributions of
+the fit parameters.  Finally, for completeness Figure~\ref{bias_w44sim}d
+shows that the distirubtion of best fit ring fractions is unbiased when
+the source is fit with the for the elliptical ring spatial model.
+
+}
 
@@
 consider a source to be extended if $\tsext>\tsinc$.
+
+\newtext{In this paragraph, we describe how our test is really the same as the AIC test
+because \dots}
 
@@
 
-\bibliography{extended_catalog}
+\bibliography{extended_search}
 
@@
     }\label{ts_ext_mc_10000}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{mc_plots/plot_tsext_plane_color.eps}
+    \else
+    \plotone{mc_plots/plot_tsext_plane_bw.eps}
+    \fi
+    % this plot came from $tsext_plot_plane/tsext_plane_plot.py
+    \caption{
+    \newtext{
+    ts ext in gal plane
+    }
+    }\label{tsext_plane_plot}
+  \end{figure}
+
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{mc_plots/ts_comparison_w44sim_color.eps}
+    \else
+    \plotone{mc_plots/ts_comparison_w44sim_bw.eps}
+    \fi
+    % this plot came from $w44simplots/plot_ts_values.py
+    \caption{
+    \newtext{The distirbution of \ts values when fitting statistically
+    independent simulations of the
+    elliptical ring shaped SNR W44. (a) is the distribution of \ts values
+    when fitting W44 as a point-like source and (b) is the
+    distribution of \tsext when fitting the SNR with a Gaussian and uniform disk 
+    spatial model. (c) is the distribution of the change in TS when
+    fitting the source with an elliptical disk spatial model compared to
+    fitting it with a radially symmetric spatial model and (d) 
+    when fitting the source with a elliptical ring spatial model compared
+    to an elliptical disk spatial model.
+    }
+    }\label{ts_comparison_w44sim}
+\end{figure}
+
+\clearpage
+\begin{figure}
+    \ifcolorfigure
+    \plotone{mc_plots/bias_w44sim_color.eps}
+    \else
+    \plotone{mc_plots/bias_w44sim_bw.eps}
+    \fi
+    % this plot came from $w44simplots/plot_bias
+    \caption{
+    \newtext{the distribution of fit parameters
+    for the simulation of Monte Carlo simulations of W44.
+    The plots show the distribution of (a)
+    (a) best fit flux (b) spectral index (c) 68\% containment
+    radius (d) eccentricity (e) elliptical orientation angle
+    (f) inner ring fraction.
+    }
+    }\label{bias_w44sim}
 \end{figure}

### 2012-04-23 extended_catalog/paper/extended_search.tex
updated text

@@
 
-\newcommand{\degree}{^\circ\xspace}
+\newcommand{\degree}{\ensuremath{^\circ}\xspace}
 
@@
 to the detailed spatial structure of these sources.  
-\newtext{In section XXX, we perform a dedicated monte carlo simulation
+\newtext{In section \ref{bias_wrong_spatial_model}, we perform a dedicated Monte Carlo simulation
 to asses possible bias due to incorrectly modeling the spatial structure
@@
 \newtext{
-These previous simulations were preformed assuming an isotropic backgorund.
-We performed a second test only
-
-The flux of the source was scaled as
+These previous simulations spaned the range of detectable fluxes 
+over two different energy ranges, but only assuming an isotropic backgorund.
+We performed a second simulation to assess any effects that could
+be introduces by performing this test in the presence of a highly
+structured background.
+Our simulation setup was the same as above except that the sources
+were simulated on top of and analytized assuming the presence of
+the standard Galactic and isotropic diffuse background model used
+in 2FGL.
+
+In our simulation, we selected our sources to have a random position on the sky
+such that the absolute value of the galactic latitude of the source is
+less than 5\degree, probing the most structured areas of the galaxy.
+
+To limit the number of tests, we selected only one flux
+level for each of the four spectral indices and we perform
+this test only in the 1 \gev to 100 \gev energy range. 
+The source flux was selected so that $\ts\sim50$. This is around 
+the significane level for which on might
+exepcted to be able to spatially resolve the source. 
+We do not test brigher sources since the structured background
+should produce the most significant effect for very bright sources.
+
+Because the Galactic diffuse emission is highly structure, the point-source
+sensitivity can vary signficantly across the galactic plane.
+To account for this, we scaled the flux (for a given spectral index)
+by the overal background level according to this formula:
 \begin{equation}
-  F(\vec{x}) = F(GC) \times \left(\frac{B(\vec{x})}{B(GC)
+  \label{scale_flux_by_background}
+  F(\vec{x}) = F(\text{GC}) \times \left(
+  \frac{B(\text{GC})}{B(\vec{x})}\right)^{1/2}.
 \end{equation}
-
-.
-The benifitted from probing a large range of fluxes and spectral indices
-and by testing two energy ranges.
-But were unable to assess any possible systematics that may be due to
-structured diffuse emission.
-
-Assessing possible difficulties due to having
-an incorrect
-
-We performed an additional Monte Carlo test with sources
-
-Figure~\ref{tsext_plane_plot}
-
-We note that this study does not asses issues due to incorrectly modeling the 
-galactic diffuse background which are much more difficult to assess. But
-this test does show the power of our tools when the model is good (or something).
+Here, $\vec{x}$ is the position of the source, $F$ is the integral
+flux of the simulated source from 100 \mev to 100 \gev, $F(\text{GC})$
+is the same quantity if the source were at the galactic center, $B$
+is the integral of the Galactic diffuse and isotropic diffuse emission
+model from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quanitty
+if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
+tabulates $F(\text{GC})$ and the average \ts for the four spectral models.
+For each spectral index, we performed $\sim90,000$ simulations.
+
+Figure~\ref{tsext_plane_plot} shows the cumulative density
+of \tsext compared to the $\chi^2_1/2$ distribution of
+Equation~\ref{ts_ext_distribution}. For small values of \tsext,
+there is reasonable agreement between the Monte Carlo simulation and
+theory.  At the highest obtained values of \tsext, there is possibly
+some discrepancy.  But in this range there are only limited statistics
+because the curve is determined by only a few points.
 
@@
 were taken from our re-analysis in this paper which is described in Section~\ref{validate_known}
-and summarized in Table~\label{known_extended_sources}. In particualr W44 was simulated
+and summarized in Table~\ref{known_extended_sources}. In particualr W44 was simulated
 with a flux of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100 \gev with a spectral
@@
 Section~\ref{monte_carlo_validation}, but the souce was simulated on
-top of the standard galactic and isotropic diffuse background model used
-in 2FGL.  This simulation was in the 1 \gev to 100 \gev energy range and
+top of and analyzed assuming the presence of the standard galactic and
+isotropic diffuse background model used in 2FGL.  This simulation was
+in the 1 \gev to 100 \gev energy range and
 the sources were simulated over the two-year time range included in the
@@
 \begin{deluxetable}{rrrrrr}
-\tabletypesize{\normalsize}
+\tabletypesize{\footnotesize}
 \tablecaption{Monte Carlo Spectral Parameters
@@
 }
+\tablecolumns{6}
 \tablewidth{0pt}
@@
 \startdata
+\multicolumn{6}{c}{Isotropic Background} \\
+\hline
       1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
@@
           &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
+\cutinhead{Galactic and Isotropic Diffuse Background\tablenotemark{(b)}}
+      1.5 &  $3\times 10^{-7}$ &           90741 &     63    &   \nodata   & \nodata     \\
+        2 &          $10^{-6}$ &           92161 &     60    &   \nodata   & \nodata     \\
+      2.5 &  $3\times 10^{-6}$ &           86226 &     47    &   \nodata   & \nodata    \\
+        3 &          $10^{-5}$ &           94412 &     61    &   \nodata   & \nodata    \\
 \enddata
@@
 \tablenotetext{(a)}{Integral 100 \mev to 100 \gev flux.}
+\tablenotetext{(b)}{
+\newtext{For the Galactic simulations, the quoted fluxes are
+if it was placed in the galactic center and is scaled by Equation~\ref{scale_flux_by_background}.}
+}
 
@@
     also tabulated.  
+    \newtext{The top rows are the sources simulated on top of an isotropic background and
+    the bottom rows are the simulations on top of the Galactic and isotropic
+    background.}
 }

### 2012-04-24 extended_catalog/paper/extended_search.tex
updated
update

@@
 \newcommand{\ts}{\text{TS}\xspace}
+\newcommand{\aic}{\text{AIC}\xspace}
 \newcommand{\glon}{\text{GLON}\xspace}
@@
 
-%\newcommand{\newtext}[1]{{\textbf #1}}
+% New text is included inside of the \newtext command
+% and is bold and red
 \newcommand{\newtext}[1]{{\bfseries \color{red}#1}}
+% To unformat the new text, comment out the above line
+% and include hte line below
+% \newcommand{\newtext}[1]{#1}
 
@@
 In particular, there are 59 \gev sources in the second Fermi Source Catalog (2FGL)
-that might be associated with extended SNRs \citep[2FGL][]{second_cat}.
+that might be associated with extended SNRs \citep[2FGL,][]{second_cat}.
 Previous analyses of extended LAT sources were performed as dedicated
@@
 Using 2 years of all-sky survey data, the LAT Collaboration published
-2FGL \citep[2FGL][]{second_cat}.
+2FGL \citep[2FGL,][]{second_cat}.
 The possible counterparts of many of these sources can be spatially resolved
@@
 we define the source size as the radius containing 68\% of the
-intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
-and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$ is defined
+intensity ($\rsixeight$). \newtext{
+By direct integration, we find
+\begin{align}
+\rsixeight_\text{,Gaussian}=&1.51\sigma, \\
+\rsixeight_\text{,disk}=&0.82\sigma, 
+\end{align}
+where $\sigma$ is defined
 in Equation~\ref{gauss_pdf} and Equation~\ref{disk_pdf} respectively.
-For this example, $\rsixeight=0\fdg5$ so $\sigma_\text{disk}=0.61\degree$
-and $\sigma_\text{Gaussian}=0.33\degree$.
+For the example above, $\rsixeight=0\fdg5$ so $\sigma_\text{disk}=0.61\degree$
+and $\sigma_\text{Gaussian}=0.33\degree$.}
 
@@
 \begin{equation}\label{ts_ext_distribution}
-  P(\ts)=\onehalf(\chi^2_1(\ts)+\delta(\ts)).
+  P(\ts)=\onehalf(\chi^2_1(\ts)+\delta(\ts)),
 \end{equation}
+\newtext{
+where $P(\ts)$ is the probability of getting a particular value of TS,
+$\chi^2_1$ is the chi-squared distribution with one degree of freedom, and
+$\delta$ is the Dirac delta function.
+}
 The particular form of Equation \ref{ts_ext_distribution} is due to the
@@
 
-\newtext{In this paragraph, we describe how our test is really the same as the AIC test
-because \dots}
+\newtext{
+It might be desirable to formulate a Bayesian test comparing an extended
+source to two point-like sources.
+We considered the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test}. 
+We found it difficult
+to apply to LAT data because it required a term including the number of data points
+and for LAT events, there are many photons included in the ROI that contribute only
+ marginally when considering different models.
+We also considered the Akaike information criterion \citep[\aic,][]{AIC_statistical_test}.
+The \aic is defines as
+\begin{equation}
+  \aic=2k-2\log\likelihood
+\end{equation}
+where $k$ is the number of parameters in the model. 
+The first term in the \aic penaize models with additonal parameters. 
+In this formulation, the best model is consided to be the one that minimzies the \aic.
+Because the two point-like source hypotheses has
+three more parameters compared to the one extended source hypothesis (two spatial
+parameters and two spectral parameters compared to one extnesion parameter),
+we note that the $\tsext>\tsinc$ is mathematically equivalent to the test that
+\begin{equation}
+  \aic_\text{ext} < \aic_\text{2pts} - 6,
+\end{equation}
+which gives our original test an equivalent Bayesian formulation by requring 
+$\aic_\text{ext}$ to be sufficently smaller than $\aic_\text{2pts}$.
+}
 
@@
 
+\newtext{
 Six extended SNRs were
-included in the 2FGL catalog: W51C, IC~443, W28, W30, W44, the Cygnus Loop,
+included in the 2FGL catalog: W51C, IC~443, W28, W44, the Cygnus Loop,
 and W30
-\citep{w51c,ic443,w28,w44,cygnus_loop_lat,w30_lat}.
+\citep{w51c,ic443,w28,w44,cygnus_loop_lat,w30_lat}.}
 Using photons
@@
 of the background model that were performed.
+\newtext{In Table~\ref{fake_2fgl_sources}, we will summarize the sources that were 
+included in 2FGL to account for residuals induced by not modeling the extension of
+a nearby source.}
 
@@
 emission model and uncertainties in the PSF.
+\newtext{Finally, in Table~\ref{fake_2fgl_sources} we 
+summarize the sources included in 2FGL to account for residuals induced
+by not modeling the extension of a nearby source.}
 
@@
 2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
-sources.  Because \tsinc is less than \tsext, we conclude that
-this emission does not originate from two nearby point-like sources.
+sources.  \newtext{Because $\tsinc=35.1$ is less than $\tsext=46.5$, we conclude that
+this emission does not originate from two nearby point-like sources.}
 
@@
 not appear physically separate. 
+\newtext{It is very close to the position of 2FGL\,J1632.4$-$4753c
+and does not show in the observed photon distribution separated emission.}
 We therefore removed this source from our model of the
@@
 instead as two point-like sources.
-Because \tsinc is less than \tsext, we conclude that this emission
+\newtext{Because $\tsinc=10.8$ is less than $\tsext=18.5$, we conclude that this emission
 does not originate from two nearby point-like sources.
@@
 With this model, 2FGL\,J1837.3$-$0700c was found to have an
-extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$ with 
-$\tsext=18.5$. 
+extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$.}
 While fitting the extension of 2FGL\,J1837.3$-$0700c,
@@
     \newtext{
-    ts ext in gal plane
+    The same plot as Figure~\ref{ts_ext_mc_1000}, but fitting sources
+    simulated on top of the Galactic diffuse and isotropic diffuse
+    emission.
     }
@@
 
+\clearpage
+\begin{deluxetable}{lr}
+\tablecolumns{2}
+\tablewidth{0pt}
+\tablecaption{Nearby Residual Sources
+\label{fake_2fgl_sources}
+}
+\tablehead{
+\colhead{Extended Source}&
+\colhead{Nearby Residual Sources}
+}
+\startdata
+\hline
+2FGL\,J0823.0$-$4246    & 2FGL\,J0823.4$-$4305, 2FGL\,J0821.0$-$4254 \\
+2FGL\,J1627.0$-$2425c   & \nodata \\
+2FGL\,J0851.7$-$4635    & 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, 2FGL\,J0855.4$-$4625 \\
+2FGL\,J1615.0$-$5051    & \nodata \\
+2FGL\,J1615.2$-$5138    & 2FGL\,J1614.9$-$5212  \\
+2FGL\,J1632.4$-$4753c   & 2FGL\,J1634.4$-$4743c \\
+2FGL\,J1712.4$-$3941    & \nodata \\
+2FGL\,J1837.3$-$0700c   & 2FGL\,J1835.5$-$0649 \\
+2FGL\,J2021.5+4026      & 2FGL\,J2019.1+4040 \\
+\enddata
+
+\tablecomments{
+\newtext{
+For each of the new extended sources, we list any catalog
+source that was included in 2FGL to account for residuals induced
+by not modeling the extension of a nearby source.
+These sources were removed from our model of the sky when studying
+the extended source.
+}
+}
+\end{deluxetable}
+
 \begin{figure}
@@
   removed from the background model.
+  \newtext{From left to right, these sources are, from left to right,
+  2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254.}
   The lower right inset is the model predicted emission from a point-like
@@
     are the best fit power-law spectral models of
-    these sources.
+    these sources. \newtext{Puppis A has a spectral index of
+    $2.21\pm0.09$ and $\gamma$-Cygni has a spectral
+    index of $2.42\pm0.19$.}
     The spectral errors are statistical only.
@@
   this source assuming a radially-symmetric uniform disk model.
-  The three black crosses represent background 2FGL sources
-  and the three star-shaped markers (colored green) represent other 2FGL sources
-  that were removed from the background model 
+  \newtext{The three black crosses represent background 2FGL sources.
+  The three star-shaped markers (colored green) represent other 2FGL sources
+  that were removed from the background model.
+  They are (from left to right) 2FGL\,J0853.5$-$4711, 2FGL\,J0855.4$-$4625, and 
+  2FGL\,J0848.5$-$4535.}
   The circular and square-shaped
@@
     symmetric uniform disk model.  
-    The two black crosses represent  background 2FGL sources and
+    \newtext{The two black crosses represent  background 2FGL sources and
     the star-shaped
-    marker (colored green) represents another 2FGL source that was removed from the background
-    model.  The contours (colored light blue) correspond to the \tev
+    marker (colored green) represents 2FGL J1614.9-5212, another 2FGL
+    source that was removed from the background
+    model.} The contours (colored light blue) correspond to the \tev
     image of HESS\,J1616$-$508 (left) and HESS\,J1614$-$518 (right)
@@
   additional background 2FGL sources subtracted in (b).
-  The star-shaped marker (colored green) represents another 2FGL
-  source that was removed from the background model.  
+  \newtext{The star-shaped marker (colored green) represents 
+  2FGL\,J1634.4$-$4743c, another 2FGL source that was removed from the background model.}
   The contours (colored light blue) correspond to the \tev image of
@@
   two background 2FGL sources subtracted in (b).  The star-shaped marker
-  (colored green) represents a 2FGL source that was removed from the
+  (colored green) represents 2FGL\,J1835.5$-$0649, another 2FGL source that was removed from the
   background model.  The contours (colored light blue) correspond to
@@
   uniform disk model.  
-  The star-shaped marker (colored green)
-  represents a 2FGL source that was removed from the background model.
+  \newtext{The star-shaped marker (colored green)
+  represents 2FGL\,J2019.1+4040,
+  a 2FGL source that was removed from the background model.}
   2FGL\,J2021.5+4026

### 2012-04-24 extended_catalog/paper/extended_search.tex
updated text

@@
 % To unformat the new text, comment out the above line
-% and include hte line below
+% and include the line below
 % \newcommand{\newtext}[1]{#1}
@@
 extension of a LAT source and in Section~\ref{bias_wrong_spatial_model}
-we asses the bias that is is introduced by using an incorrect spatial model.
+we asses the bias that is introduced by using an incorrect spatial model.
 In Section~\ref{extension_sensitivity}
@@
 to asses possible bias due to incorrectly modeling the spatial structure
-of an extended source.}
-Therefore, in our
-search for extended sources we use only a radially-symmetric uniform
+of an extended source.
+In our search for extended sources we use only a radially-symmetric uniform
 disk spatial model. Unless otherwise noted,
-we quote the radius to the edge ($\sigma$) as the size of the source.
+we quote the radius to the edge ($\sigma$) as the size of the source.}
 
@@
 \newtext{
-These previous simulations spaned the range of detectable fluxes 
-over two different energy ranges, but only assuming an isotropic backgorund.
+These simulations spanned the range of detectable fluxes 
+over two different energy ranges, but only assuming an isotropic background.
 We performed a second simulation to assess any effects that could
@@
 Our simulation setup was the same as above except that the sources
-were simulated on top of and analytized assuming the presence of
+were simulated on top of and analyzed assuming the presence of
 the standard Galactic and isotropic diffuse background model used
@@
 The source flux was selected so that $\ts\sim50$. This is around 
-the significane level for which on might
-exepcted to be able to spatially resolve the source. 
-We do not test brigher sources since the structured background
+the significance level for which on might
+expect to be able to spatially resolve the source. 
+We do not test brighter sources since the structured background
 should produce the most significant effect for very bright sources.
@@
 Because the Galactic diffuse emission is highly structure, the point-source
-sensitivity can vary signficantly across the galactic plane.
+sensitivity can vary significantly across the galactic plane.
 To account for this, we scaled the flux (for a given spectral index)
-by the overal background level according to this formula:
+so that the source always has approximatly the same signal-to-noise ratio:
 \begin{equation}
@@
   F(\vec{x}) = F(\text{GC}) \times \left(
-  \frac{B(\text{GC})}{B(\vec{x})}\right)^{1/2}.
+  \frac{B(\vec{x})}{B(\text{GC})}\right)^{1/2}.
 \end{equation}
@@
 is the integral of the Galactic diffuse and isotropic diffuse emission
-model from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quanitty
+model from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quantity
 if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
@@
 \newtext{
-We performed a Monte Carlo study to asses the biases introudced by incorreclty
+We performed a Monte Carlo study to asses the biases introduced by incorrectly
 modeling the spatial structure of an extended source. This is important because any assumed spatial
@@
 To assess this systematic, we simulated the spatially extended ring-type SNR W44.
-W44 was slelected because it is the most signfiicant extended source detected by the LAT 
+W44 was selected because it is the most significant extended source detected by the LAT 
 that has been reported as having a non-radially symmetric photon-distribution \cite{w44}.
@@
 were taken from our re-analysis in this paper which is described in Section~\ref{validate_known}
-and summarized in Table~\ref{known_extended_sources}. In particualr W44 was simulated
+and summarized in Table~\ref{known_extended_sources}. In particular W44 was simulated
 with a flux of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100 \gev with a spectral
@@
 We used a simulation setup similar to that described in
-Section~\ref{monte_carlo_validation}, but the souce was simulated on
+Section~\ref{monte_carlo_validation}, but the source was simulated on
 top of and analyzed assuming the presence of the standard galactic and
@@
 see the statistical spread in the fit values.
-
-After simulating the ring-like source, we fit the spectral and spatial parametesr of 
-the ring-like extended source with successivly more complicated spatial models.
+In the simulations of W44, we disabled the inherent energy dispersion of photons
+by the LAT. The bias caused by ignoring energy dispersion 
+will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.
+
+After simulating the ring-like source, we fit the spectral and spatial parameters of 
+the ring-like extended source with successively more complicated spatial models.
 We obtained the best fit spatial parameters using \pointlike and, using 
-these best fit spatial paramters, obtained the best fit spectral paramters 
+these best fit spatial parameters, obtained the best fit spectral parameters 
 using \gtlike. In total, we performed the fit using a point-like spatial model,
@@
 
-Figure~\ref{ts_comparison_w44sim} shows the the distribution of TS values for 
-each of the simluations when fitting the simulated sources 
+Figure~\ref{ts_comparison_w44sim} shows the distribution of TS values for 
+each of the simulations when fitting the simulated sources 
 with the different spatial models. 
@@
 (within the precision of this Monte Carlo study. The reason for this is
-because within the finite angular precision and limited statsitics of the LAT, 
-all of the extended spatial models can be ajusted to look almost the same.
+because within the finite angular precision and limited statistics of the LAT, 
+all of the extended spatial models can be adjusted to look almost the same.
 For brighter or larger sources, this could potentially be a larger effect.
 
-Figure~\ref{bias_w44sim}c plots the best fit 68\% contaiment radius
+Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius
 (\rsixeight).  For the elliptical ring spatial model, as expected
@@
 There are three
-point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
-and 2FGL\,J0855.4$-$4625 which correlate with the 
+point-like catalog sources 2FGL\,J0848.5$-$4535,
+2FGL\,J0853.5$-$4711, and
+2FGL\,J0855.4$-$4625
+which correlate with the 
 multiwavelength
@@
 \cutinhead{Galactic and Isotropic Diffuse Background\tablenotemark{(b)}}
-      1.5 &  $3\times 10^{-7}$ &           90741 &     63    &   \nodata   & \nodata     \\
-        2 &          $10^{-6}$ &           92161 &     60    &   \nodata   & \nodata     \\
-      2.5 &  $3\times 10^{-6}$ &           86226 &     47    &   \nodata   & \nodata    \\
-        3 &          $10^{-5}$ &           94412 &     61    &   \nodata   & \nodata    \\
+      1.5 &  $2.3\times 10^{-8}$ &           90741 &     63    &   \nodata   & \nodata     \\
+        2 &  $1.2\times 10^{-7}$ &           92161 &     60    &   \nodata   & \nodata     \\
+      2.5 &  $4.5\times 10^{-7}$ &           86226 &     47    &   \nodata   & \nodata    \\
+        3 &  $2.0\times 10^{-6}$ &           94412 &     61    &   \nodata   & \nodata    \\
 \enddata
@@
 \hline
-2FGL\,J0823.0$-$4246    & 2FGL\,J0823.4$-$4305, 2FGL\,J0821.0$-$4254 \\
+2FGL\,J0823.0$-$4246    & 2FGL\,J0821.0$-$4254, 2FGL\,J0823.4$-$4305 \\
 2FGL\,J1627.0$-$2425c   & \nodata \\
-2FGL\,J0851.7$-$4635    & 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, 2FGL\,J0855.4$-$4625 \\
+2FGL\,J0851.7$-$4635    & 2FGL\,J0848.5$-$4535, 2FGL\,J0853.5$-$4711, 2FGL\,J0855.4$-$4625 \\
 2FGL\,J1615.0$-$5051    & \nodata \\
@@
   removed from the background model.
-  \newtext{From left to right, these sources are, from left to right,
-  2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254.}
+  \newtext{From left to right, these sources are 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254.}
   The lower right inset is the model predicted emission from a point-like
@@
   blue) represent the 2FGL and the relocalized positions respectively of
-  two background 2FGL sources subtracted in (b).  The star-shaped marker
+  two background 2FGL sources subtracted in (b).  \newtext{The star-shaped marker
   (colored green) represents 2FGL\,J1835.5$-$0649, another 2FGL source that was removed from the
-  background model.  The contours (colored light blue) correspond to
+  background model.}  The contours (colored light blue) correspond to
   the \tev image of HESS\,J1837$-$069

### 2012-04-25 extended_catalog/paper/extended_search.tex
updated test

@@
 \newtext{
-These simulations spanned the range of detectable fluxes 
-over two different energy ranges, but only assuming an isotropic background.
+These simulations spanned a large range of fluxes 
+for two different energy ranges assuming an isotropic background.
 We performed a second simulation to assess any effects that could
@@
 structured background.
-Our simulation setup was the same as above except that the sources
-were simulated on top of and analyzed assuming the presence of
-the standard Galactic and isotropic diffuse background model used
-in 2FGL.
-
-In our simulation, we selected our sources to have a random position on the sky
-such that the absolute value of the galactic latitude of the source is
-less than 5\degree, probing the most structured areas of the galaxy.
+
+Our simulation setup was the same as above except that the sources were
+simulated on top of and analyzed assuming the presence of the standard
+Galactic diffuse and isotropic background models used in 2FGL.  In our
+simulations, we selected our sources to have a random position on the sky
+such that the absolute value of the galactic latitude of the source was
+less than 5\degree. This probes the most structured areas of the galaxy.
 
@@
 this test only in the 1 \gev to 100 \gev energy range. 
-The source flux was selected so that $\ts\sim50$. This is around 
+The fluxes were selected so that $\ts\sim50$ which is around 
 the significance level for which on might
 expect to be able to spatially resolve the source. 
-We do not test brighter sources since the structured background
-should produce the most significant effect for very bright sources.
+We only tested these relatively dim sources because they are most likely
+to be affected by the background.
 
@@
 To account for this, we scaled the flux (for a given spectral index)
-so that the source always has approximatly the same signal-to-noise ratio:
+so that the source always has approximately the same signal-to-noise ratio:
 \begin{equation}
@@
 \end{equation}
-Here, $\vec{x}$ is the position of the source, $F$ is the integral
-flux of the simulated source from 100 \mev to 100 \gev, $F(\text{GC})$
+Here, $\vec{x}$ is the position of the simulated source, $F$ is the integral
+flux of the source from 100 \mev to 100 \gev, $F(\text{GC})$
 is the same quantity if the source were at the galactic center, $B$
-is the integral of the Galactic diffuse and isotropic diffuse emission
-model from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quantity
+is the integral of the Galactic diffuse and isotropic emission
+from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quantity
 if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
-tabulates $F(\text{GC})$ and the average \ts for the four spectral models.
-For each spectral index, we performed $\sim90,000$ simulations.
+contains $F(\text{GC})$ and the average value of \ts for the four spectral models.
+For each spectrum, we performed $\sim90,000$ simulations.
 
@@
 Equation~\ref{ts_ext_distribution}. For small values of \tsext,
-there is reasonable agreement between the Monte Carlo simulation and
-theory.  At the highest obtained values of \tsext, there is possibly
-some discrepancy.  But in this range there are only limited statistics
-because the curve is determined by only a few points.
-
-}
-
-\subsection{\newtext{Assessing the Bias Due to Incorrect Spatial Models}}
+there is good agreement between the simulations and
+theory.  For the highest values of \tsext, there is possibly
+a small discrepancy, but limited statistics makes this hard to quantify.
+}
+
+\subsection{Assessing the Bias Due to Incorrect Spatial Models}
 \label{bias_wrong_spatial_model}
@@
 \newtext{
-We performed a Monte Carlo study to asses the biases introduced by incorrectly
-modeling the spatial structure of an extended source. This is important because any assumed spatial
-model is just an approximation to the true photon distribution of the source.
+We performed a Monte Carlo study to asses the bias that is introduced by
+incorrectly modeling the spatial structure of an extended source. This
+is important because any assumed spatial model is just an approximation
+to the true shape of a source.
 
 To assess this systematic, we simulated the spatially extended ring-type SNR W44.
-W44 was selected because it is the most significant extended source detected by the LAT 
-that has been reported as having a non-radially symmetric photon-distribution \cite{w44}.
-
-W44 was simulated with a power-law spectral model. The flux and spectral index of this source
-were taken from our re-analysis in this paper which is described in Section~\ref{validate_known}
-and summarized in Table~\ref{known_extended_sources}. In particular W44 was simulated
-with a flux of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100 \gev with a spectral
-index of 2.66.
-
-W44 was simulated with an elliptical ring spatial model described in
+We selected W44 because it is the most significant extended source detected by the LAT 
+that has a non-radially symmetric photon-distribution \citep{w44}.
+
+W44 was simulated with a power-law spectral model with an integral flux
+of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100
+\gev and a spectral index of 2.66.
+The flux and spectral index of this source
+were taken from our analysis of W44 which is described in Section~\ref{validate_known}.
+
+W44 was simulated with the elliptical ring spatial model described in
 \cite{w44}.  Because that publication does not provide the numbers describing
-the parameters of the ellipse, we summarize them here for completeness. The elliptical
-spatial model has a major axis of 0\fdg3 and a minor axis of 0\fdg19. The
-ellipse predicts emission only for the outer 0.75\% of the ellipse and
-the ellipse has an angle of $147\degree$ measured east of celestial north.
+the parameters of the ellipse, we summarize them here for completeness. The 
+ellipse has a semi-major axis of 0\fdg3 and a semi-minor axis of 0\fdg19. The
+ellipse predicts emission only for the outer 0.75\% of the shape and
+the has a position angle of $147\degree$ measured east of celestial north.
 
@@
 Section~\ref{monte_carlo_validation}, but the source was simulated on
-top of and analyzed assuming the presence of the standard galactic and
-isotropic diffuse background model used in 2FGL.  This simulation was
+top of and analyzed assuming the presence of the standard Galactic diffuse and
+isotropic background model used in 2FGL.  This simulation was
 in the 1 \gev to 100 \gev energy range and
-the sources were simulated over the two-year time range included in the
-2FGL catalog. We performed 985 identical simulations with different seeds to
-see the statistical spread in the fit values.
-In the simulations of W44, we disabled the inherent energy dispersion of photons
+W44 was simulated over the two-year time range included in the
+2FGL catalog. 
+In the simulations, we disabled the inherent energy dispersion of photons
 by the LAT. The bias caused by ignoring energy dispersion 
 will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.
-
-After simulating the ring-like source, we fit the spectral and spatial parameters of 
-the ring-like extended source with successively more complicated spatial models.
+In total, we performed 985 identical simulations.
+
+The simulated sources were fit using a point-like spatial model,
+a radially-symmetric uniform Gaussian and disk spatial model, 
+an Elliptical disk spatial model, and finally with an Elliptical
+ring spatial model.
 We obtained the best fit spatial parameters using \pointlike and, using 
 these best fit spatial parameters, obtained the best fit spectral parameters 
-using \gtlike. In total, we performed the fit using a point-like spatial model,
-using a radially-symmetric uniform Gaussian and disk spatial model, 
-an Elliptical disk spatial model, and finally the Monte Carlo true Elliptical
+using \gtlike.
+
+Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
+fitting the simulations of W44 as as a point-like source.
+The sources are very significant ($\ts\sim3500$).
+Figure~\ref{ts_comparison_w44sim}b shows the distribution of \tsext values
+when fitting the source as a radially-symmetric uniform disk and Gaussian source.
+The sources are very significantly extended ($\tsext\sim250$). 
+On average \tsext is slightly larger when
+fitting the source with the disk spatial model compared to the Gaussian spatial model,
+consistent with the fact that the simulated source's true spatial model has a sharp edge.
+Figure~\ref{ts_comparison_w44sim}c then shows the change in \ts 
+when fitting the simulated source as
+an elliptical disk compared to fitting the source as a disk. Since the changes
+in \ts are on average $\sim30$, we see that our simulated source is significantly better
+described with an elliptical spatial model. Finally, 
+Figure~\ref{ts_comparison_w44sim}d shows the changes in \ts when fitting
+the sources with an elliptical ring spatial model compared to fitting them
+with elliptical disk spatial models.
+Since the changes are on average $\sim9$, the simulated sources are only somewhat better described
+by the true spatial model.
+
+Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
+show the distributions of best fit flux and spectral indices when fitting
+the simulated sources.
+When fitting the sources with a point-like
+spatial model, there is a $\sim$10\% bias in the fit flux and
+a $\sim5\%$ bias in the fit index. When fitting the sources assuming any
+of the extended spatial models, there is no bias in the best fit spectral parameters
+(within the precision of the Monte Carlo study). The reason is that
+within the finite angular precision and limited statistics of the LAT, 
+all of the extended spatial models can be adjusted to look very similar.
+
+Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius.  
+For the elliptical ring spatial model, there is no significant bias in the best fit size. 
+None of the other spectral models induced a bias greater
+than $\sim10\%$. From this, we see that \rsixeight is a reasonable measure of the true 68\%
+containment radius for a reasonable spatial models.
+
+For completeness, Figure~\ref{bias_w44sim}d plots the distribution of best
+fit elliptical eccentricities and Figure~\ref{bias_w444im}e plots the
+distribution of orientation angles
+when the sources were fit with elliptical
+disk and elliptical ring spatial models.  
+The eccentricity is defined as
+$\sqrt{1-b^2/a^2}$, where $a$ is the length of the semi-major axis and
+$b$ is the length of the semi-minor axis.  
+There is no systematic bias in the eccentricities or orientation angles.
+Finally, Figure~\ref{bias_w44sim}f shows that the distribution of best fit
+ring fractions is unbiased when the sources are fit with the elliptical
 ring spatial model.
-
-Figure~\ref{ts_comparison_w44sim} shows the distribution of TS values for 
-each of the simulations when fitting the simulated sources 
-with the different spatial models. 
-Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
-fitting the simulated Elliptical ring extended source as as a point-like source.
-the source is very significant as a point source ($\ts\sim3500$).
-Figure~\ref{ts_comparison_w44sim}b shows the distirbution of \tsext values
-when fitting the source as a radially-symmetric uniform disk or Gaussian source.
-The source is very significiantly extended ($\tsext\sim250$). 
-On average \tsext is slightly larger when
-fitting the source with the Disk spatial model compared to the Gaussian spatial model.
-Considering that the simulated source's true spatial model has a sharp edge, it
-makes sense that the Disk would provide a better fit.
-
-Figure~\ref{ts_comparison_w44sim}c then shows the change in \ts (or
-twice the improvement in log likelihood) when fitting the simulated source as
-an elliptical disk compared to fitting the source as a disk. Since the change
-in \ts is $\sim30$, we see that our simulated source is significantly better
-described with an ellpitical spatial model. Finally, 
-Figure~\ref{ts_comparison_w44sim}d shows the change in \ts when fitting
-the source as an elliptical ring compared to fitting it as an elliptical disk.
-Since the change is $\sim9$, we see that the source is somewhat better described
-by the true spatial model, but not at a high statistical significance.
-
-Figure~\ref{bias_w44sim} shows the distirbution of best fit parameters
-for these simulations. Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
-show the distribututions of best fit flux and spectral indices.
-They show that when fitting this simulated extended source with a point-like
-spatial model, there is a $\sim$10\% bias in the fit flux and
-$\sim5\%$ bias in the fit index. But when fitting the sources with any of
-the extended spatial models, there is no bias in the best fit spectral parameters
-(within the precision of this Monte Carlo study. The reason for this is
-because within the finite angular precision and limited statistics of the LAT, 
-all of the extended spatial models can be adjusted to look almost the same.
-For brighter or larger sources, this could potentially be a larger effect.
-
-Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius
-(\rsixeight).  For the elliptical ring spatial model, as expected
-there is no significant bias in the best fit size. What is surprising
-is that for none of the tested spatial models was the bias greater
-than $\sim10\%$. This shows that for whatever spatial model is used,
-the best fit \rsixeight is a reasonable measure of the true 68\%
-containment radius.
-
-For completeness, for the elliptical disk and ring spatial models,
-Figure~\ref{bias_w44sim}c plots the distribution of best fit eccentricity
-of the ellipse. It is defined as $\sqrt{1-b^2/a^2}$ where $a$ is the
-length of the semi-major axis and $b$ is the length of the semi-minor
-axis.  Figure~\ref{bias_w44sim}c plots the distribution of best fit
-orientation angle of the ellipse. For the elliptical spatial models,
-there is no systematic bias in the eccentricities or orentiation angles.
-For the true sptial model, there is less spread in the distributions of
-the fit parameters.  Finally, for completeness Figure~\ref{bias_w44sim}d
-shows that the distirubtion of best fit ring fractions is unbiased when
-the source is fit with the for the elliptical ring spatial model.
-
 }
@@
 \newtext{
-It might be desirable to formulate a Bayesian test comparing an extended
-source to two point-like sources.
-We considered the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test}. 
-We found it difficult
+We considered an alternate Bayesian formulation of this test.
+We considered the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test},
+but found it difficult
 to apply to LAT data because it required a term including the number of data points
-and for LAT events, there are many photons included in the ROI that contribute only
- marginally when considering different models.
-We also considered the Akaike information criterion \citep[\aic,][]{AIC_statistical_test}.
-The \aic is defines as
+and for LAT events. Because there are many photons included in an analysis that contribute only
+ marginally to the analysis of a source, it is unclear how this test could be applied.
+We also considered the Akaike information criterion test \citep[\aic,][]{AIC_statistical_test}.
+The \aic is defined as
 \begin{equation}
-  \aic=2k-2\log\likelihood
+  \aic=2k-2\log\likelihood,
 \end{equation}
 where $k$ is the number of parameters in the model. 
-The first term in the \aic penaize models with additonal parameters. 
-In this formulation, the best model is consided to be the one that minimzies the \aic.
+In this formulation, the best model is considered to be the one that minimizes the \aic.
+The first term penalizes models with additional parameters.
+
 Because the two point-like source hypotheses has
-three more parameters compared to the one extended source hypothesis (two spatial
-parameters and two spectral parameters compared to one extnesion parameter),
-we note that the $\tsext>\tsinc$ is mathematically equivalent to the test that
+three more parameters than the single extended source hypothesis (two spatial
+parameters and two spectral parameters compared to one extension parameter),
+we note that the $\tsext>\tsinc$ is mathematically equivalent to the test:
 \begin{equation}
-  \aic_\text{ext} < \aic_\text{2pts} - 6,
+  \aic_\text{ext} < \aic_\text{2pts} - 6.
 \end{equation}
-which gives our original test an equivalent Bayesian formulation by requring 
-$\aic_\text{ext}$ to be sufficently smaller than $\aic_\text{2pts}$.
+Therefore, our original test has an 
+equivalent Bayesian formulation requiring that $\aic_\text{ext}$ 
+be sufficiently smaller than $\aic_\text{2pts}$.
 }
@@
 included in 2FGL to account for residuals induced by not modeling the extension of
-a nearby source.}
+nearby extended sources.}
 
@@
 summarize the sources included in 2FGL to account for residuals induced
-by not modeling the extension of a nearby source.}
+by not modeling the extension of nearby extended sources.}
 
@@
 \newtext{Because $\tsinc=10.8$ is less than $\tsext=18.5$, we conclude that this emission
-does not originate from two nearby point-like sources.
-
-With this model, 2FGL\,J1837.3$-$0700c was found to have an
+does not originate from two nearby point-like sources.}
+
+\newtext{With this model, 2FGL\,J1837.3$-$0700c was found to have an
 extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$.}
@@
 \startdata
-\multicolumn{6}{c}{Isotropic Background} \\
+\multicolumn{6}{c}{\newtext{Isotropic Background}} \\
 \hline
@@
           &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
-\cutinhead{Galactic and Isotropic Diffuse Background\tablenotemark{(b)}}
+\cutinhead{\newtext{Galactic Diffuse and Isotropic Background\tablenotemark{(b)}}}
       1.5 &  $2.3\times 10^{-8}$ &           90741 &     63    &   \nodata   & \nodata     \\
@@
 \newtext{For the Galactic simulations, the quoted fluxes are
-if it was placed in the galactic center and is scaled by Equation~\ref{scale_flux_by_background}.}
+if the sources were placed in the Galactic center and the actual
+flux is scaled by Equation~\ref{scale_flux_by_background}.}
 }
@@
     \newtext{The top rows are the sources simulated on top of an isotropic background and
-    the bottom rows are the simulations on top of the Galactic and isotropic
+    the bottom rows are the simulations on top of the Galactic diffuse and isotropic
     background.}
@@
     The same plot as Figure~\ref{ts_ext_mc_1000}, but fitting sources
-    simulated on top of the Galactic diffuse and isotropic diffuse
-    emission.
+    simulated on top of the Galactic diffuse and isotropic background.
     }
@@
     \caption{
-    \newtext{The distirbution of \ts values when fitting statistically
+    \newtext{The distribution of \ts values when fitting statistically
     independent simulations of the

### 2012-04-25 extended_catalog/paper/extended_search.tex
update

@@
     \newtext{The distribution of \ts values when fitting statistically
-    independent simulations of the
-    elliptical ring shaped SNR W44. (a) is the distribution of \ts values
+    independent simulations of W44. (a) is the distribution of \ts values
     when fitting W44 as a point-like source and (b) is the
-    distribution of \tsext when fitting the SNR with a Gaussian and uniform disk 
+    distribution of \tsext when fitting the source with a Gaussian and uniform disk 
     spatial model. (c) is the distribution of the change in TS when
     fitting the source with an elliptical disk spatial model compared to
-    fitting it with a radially symmetric spatial model and (d) 
+    fitting it with a radially-symmetric disk spatial model and (d) 
     when fitting the source with a elliptical ring spatial model compared
@@
     for the simulation of Monte Carlo simulations of W44.
-    The plots show the distribution of (a)
+    The plots show the distribution of 
     (a) best fit flux (b) spectral index (c) 68\% containment
@@
 \newtext{
-For each of the new extended sources, we list any catalog
-source that was included in 2FGL to account for residuals induced
-by not modeling the extension of a nearby source.
-These sources were removed from our model of the sky when studying
-the extended source.
+For each new extended sources, we list nearby catalog
+sources that were included in 2FGL to account for residuals induced
+by not modeling the extension of the nearby extended source.
 }

### 2012-04-25 extended_catalog/external_review_reply/replies_to_review_comments.tex
update

\documentclass{article}

\usepackage{url}
\usepackage{color}

\newenvironment{referee}
{\begin{quote}\color{red}}
  {\end{quote}}

\newenvironment{reply}
  {}
  {}

\title{Reply to Referee Report}

\begin{document}

\maketitle

\begin{reply}
Thank you for your careful review of the text. We discuss below the
changes we have made incorporating your feedback. To make the changes more visible,
in the new draft we have bolded and colored red the parts that are new or have changed.
\end{reply}

\begin{referee}
Major issues :

The authors use a uniform disk model for fitting the extended sources.
However many sources show a complex morphology (for example, not radial symmetric)
They should quantify how the results they are presenting depend on the actual shape of the sources.
\end{referee}

\begin{reply}
In the new draft, Section 3 (Validation of Analysis Method) has been
divided into two sections. The original section is now section 3.1
(now called Statistical Significance Testing).

There is a new section 3.2 called ``Assessing the Bias Due to Incorrect
Spatial Models''. In this section, we address your question by performing
a dedicated Monte Carlo study of W44 simulated with a ring-type spatial
model. By fitting the source with different spatial models, we asses
this bias and find it to be very small.

This new section requires two new figures (Figure 6 and Figure 7). Also,
in section 2.4 (Comparing Source Size) we add a line of text referring
to this new section. Finally, there is a new sentance in the introduction
of the paper which references the new text.
\end{reply}

\begin{referee}
Most of the new extended sources found in this work lie on the galactic
plane at very low latitudes. Why the simulations used to validate the
analysis (par. 3) do not include the diffuse Galactic background? Can
the structures of this diffuse background affect the analysis results?
\end{referee}

\begin{reply}
In section 3.1 (which was previously just section 3 and is called
Statistical Significance Testing), we have added new text describing a
follow up Monte Carlo study performed in the presence of the galactic
plane. In addition, this new text required updating Table 1 (Monte Carlo
Spectral Parameters) to include the new simulation parameters. There is also
a new figure (Figure 5) which shows the distribution of TSext for these
new simulations.
\end{reply}

\begin{referee}
An important result of this work is that some 2FGL sources could be fake due to the residuals induced by modeling the extended sources as point-like. It may be worth having a table that lists the sources that are not longer needed in the modeling of the sky (alternatively this information could be included in table 4). They must also be mentioned in the captions of figures 16, 17, 19, 21 and 22.
\end{referee}

\begin{reply}
We have added a new table (Table 6 in the current draft) which contains
this information. There are paragraphs in section 9 (Extended Source
Search Method) and Section 10 (New Extended Sources) which refer to this
table. We have also updated the specified captions to list names of 2FGL
sources that were removed.
\end{reply}

\begin{referee}
Minor issues :

Par. 3, eq 8 : The authors should explain the symbols used
\end{referee}

\begin{reply}
The symbols are now described after the equation.
\end{reply}

\begin{referee}
Par. 7, row 386 : W30 is cited 2 times
\end{referee}

\begin{reply}
Fixed
\end{reply}

\begin{referee}
  Par. 10.3, rows 650-651 : The authors should explain the relation between $r_{68}$ and $\sigma$
\end{referee}

\begin{reply}
  The relation between $r_{68}$ and $\sigma$ was already included in the text
in section 2.4 (Comparing Source Sizes). But we restructured the
text in that section to bring to prominence the relevant equations.
\end{reply}

\begin{referee}
Par. 10.4, row 674 : The authors should quantify the statistical
improvement using one single extended source instead of 2 pointlike
\end{referee}

\begin{reply}
The numbers are now included in the text
\end{reply}

\begin{referee}
Par. 10.6, row 720 : The authors should explain better how you distinguish
if a source is ``physically separate'' or not
\end{referee}

\begin{reply}
The text has been clarified
\end{reply}

\begin{referee}
Par. 10.8, row 768 : The authors should quantify the statistical
improvement using one single extended source instead of 2 pointlike
\end{referee}

\begin{reply}
The numbers are included in the text
\end{reply}

\begin{referee}
Fig. 2 : Is the y axis logarithmic ? Please clarify.
\end{referee}

\begin{reply}
The legend now says ``log(PDF) [Arbitrary Units]''
\end{reply}

\begin{referee}
Fig. 14 : The authors should specify the spectral index of the two plotted power-laws (or else remove them).
\end{referee}

\begin{reply}
The spectral indices have been added to the caption.
\end{reply}

\begin{referee}
++++++++++++++++
Report on statistical methodology

Search for Spatially Extended Fermi-LAT Sources Using Two Years of Data

J. Lande et al. (ApJ86244)

a) line 98 states: In the pointlike package, ``The data are binned
spatially, using a HEALPix pixelization, and spectrally (G ́orski et
al. 2005) and the likelihood is maximized over all bins in a region.'' Why
is any binning used? Maximum likelihood estimation (MLE) is best used
on exact photon positions, and binning is not required (as it is with
older chi-square-minimiization techniques). Binning is ill-advised as
it results in a loss of information, and sometimes in a bias. As this
assumption is built into pointlike, perhaps it cannot be changed by the
authors for their analysis.
\end{referee}

\begin{reply}
The Fermi LAT analysis package gtlike has an unbinned likelihood mode
which is indeed slightly more precise. But running an unbinned analysis
is very slow because Fermi collects a large number of photons, many of
which do not contribute very much to the detection of a source. gtlike
in binned mode is much faster and is therefore the most common tool
for LAT analysis. Because the LAT collaboration has extensively tested
binned gtlike for spectral analysis, we do not expect it to introduce
any large bias in our spectral analysis result.

But even binned gtlike is prohibitively slow for the extended source
spatial fitting described in this paper. That is why we developed this
new functionality inside of pointlike. The validations of pointlike
presented in this paper allow us to be confident in our spatial analysis results.
\end{reply}

\begin{referee}
b) The likelihood ratio test (LRT, eqns 1 \& 9) is a classic technique of
MLE that has been largely replaced by statisticians (since the 1980s) by
closely related measures that take into account the complexity of models
and size of the dataset. The LRT has serious deficiencies: it tends
to accept the more complex model as sample size (i.e., source counts)
increases (or equivalently, it assesses only bias and not variability),
and it is inapplicable when parameters (e.g. source sizes) are near zero
(discussed in the ApJ by Protassov et al. 2002). I also am not confident
that the chi-squared approximation in eqn 8 is correct (please refer to
a statistics book not an old ApJ article, or consult a statistician).

Model selection today is instead guided by `penalized' measures,
and the most widely used is the Bayesian Information Criterion
(BIC,\url{http://en.wikipedia.org/wiki/Bayesian_information_criterion}). It
is very easy to compute, essentially an offset from the LRT scaled to
the log of the counts involved. The issues are discussed in detail in
the volume ``Model Selection and Multi-Model Inference'' (K.P. Burnham
\& D. Anderson, 2nd ed, 2002); see also lectures (especially \#14) at
\url{http://myweb.uiowa.edu/cavaaugh/ms_seminar.html}.

I guess you could argue that your Monte Carlo experiments (Figs 3-4) take
the flux and degrees of freedom into account for the LRT statistic. But
if you want your method to be widely used, it should not rest on a weak
and obsolete statistical foundation. Altogether, I recommend moving to
the BIC. Your approach of Monte Carlo testing of the significance of
LRT values should also work for BIC values.
\end{referee}

\begin{reply}
Concerning the extension significance test, we extensively validated it
against Monte Carlo simulations. Furthermore, the high energy astrophysics
community has a lot of experience with the test statistic (TS) applied to
nested models. So we are very confident that we can apply it to the actual
data.

Concerning the test comparing two point-like sources to one extended
source, we find the desire for a Bayesian test more compelling since the
models are not nested. We considered the BIC test but found that it would
not work well for Fermi LAT. We alternately considered the AIC test and
found that it is equivalent to the test we actually performed. We have
added a new paragraph to Section 5 (Testing Against Source Confusion)
that describes the Bayesian interoperation of the test we performed.
\end{reply}

\begin{referee}
Finally, I can suggest that the lead author discuss the issue with experts
at his institution, as Stanford's Dept. of Statistics is universally
recognized as the best in the nation. They might provide a balanced
judgment whether the BIC is substantially better than the LRT in the
situation under study.
\end{referee}

\begin{reply}
Thanks for the suggestion.  In addition to the above changes, we have
fixed the bibliographical information on the LAT publication of Vela Jr.
\end{reply}

\end{document}

### 2012-04-25 extended_catalog/paper/extended_search.tex
updated draft

@@
 we asses the bias that is introduced by using an incorrect spatial model.
-In Section~\ref{extension_sensitivity}
+In Section~\ref{extension_sensitivity},
 we calculate the LAT detection threshold to resolve the extension
@@
 of an extended source.
-In our search for extended sources we use only a radially-symmetric uniform
+In our search for extended sources, we use only a radially-symmetric uniform
 disk spatial model. Unless otherwise noted,
@@
 \newtext{
-where $P(\ts)$ is the probability of getting a particular value of TS,
+where $P(\ts)$ is the probability density to get a particular value of TS,
 $\chi^2_1$ is the chi-squared distribution with one degree of freedom, and
@@
 \newtext{
-These simulations spanned a large range of fluxes 
-for two different energy ranges assuming an isotropic background.
 We performed a second simulation to assess any effects that could
@@
 structured background.
-
 Our simulation setup was the same as above except that the sources were
@@
 such that the absolute value of the galactic latitude of the source was
-less than 5\degree. This probes the most structured areas of the galaxy.
+less than 5\degree. This probes the most structured areas of the 
+Galactic background.
 
@@
 this test only in the 1 \gev to 100 \gev energy range. 
-The fluxes were selected so that $\ts\sim50$ which is around 
-the significance level for which on might
-expect to be able to spatially resolve the source. 
-We only tested these relatively dim sources because they are most likely
-to be affected by the background.
+The fluxes were selected so that $\ts\sim50$. We do not
+expect to be able to spatially resolve sources much dimmer than this
+and sources much brigher are not likely to be affected by the background.
 
@@
 is the integral of the Galactic diffuse and isotropic emission
-from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quantity
-if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
+from 1 \gev to 100 \gev, and $B(\text{GC})$ is the same quantity
+if the source was at the galactic center.  Table~\ref{ts_ext_num_sims}
 contains $F(\text{GC})$ and the average value of \ts for the four spectral models.
+
 For each spectrum, we performed $\sim90,000$ simulations.
-
 Figure~\ref{tsext_plane_plot} shows the cumulative density
-of \tsext compared to the $\chi^2_1/2$ distribution of
-Equation~\ref{ts_ext_distribution}. For small values of \tsext,
+of \tsext. For small values of \tsext,
 there is good agreement between the simulations and
@@
 \newtext{
-We performed a Monte Carlo study to asses the bias that is introduced by
-incorrectly modeling the spatial structure of an extended source. This
-is important because any assumed spatial model is just an approximation
-to the true shape of a source.
-
+We performed a Monte Carlo study to quantify the bias that is introduced by
+incorrectly modeling the spatial structure of an extended source. 
 To assess this systematic, we simulated the spatially extended ring-type SNR W44.
@@
 \gev and a spectral index of 2.66.
-The flux and spectral index of this source
+The simulated flux and spectral index of this source
 were taken from our analysis of W44 which is described in Section~\ref{validate_known}.
@@
 W44 was simulated with the elliptical ring spatial model described in
-\cite{w44}.  Because that publication does not provide the numbers describing
-the parameters of the ellipse, we summarize them here for completeness. The 
-ellipse has a semi-major axis of 0\fdg3 and a semi-minor axis of 0\fdg19. The
-ellipse predicts emission only for the outer 0.75\% of the shape and
-the has a position angle of $147\degree$ measured east of celestial north.
+\cite{w44}. For reference, the ellipse has a semi-major axis of 0\fdg3,
+a semi-minor axis of 0\fdg19, has a position angle of $147\degree$
+measured east of celestial north, and predicts emission only for the
+outer 0.75\% of the shape.
 
@@
 top of and analyzed assuming the presence of the standard Galactic diffuse and
-isotropic background model used in 2FGL.  This simulation was
+isotropic background model used in 2FGL.  The simulations were
 in the 1 \gev to 100 \gev energy range and
-W44 was simulated over the two-year time range included in the
-2FGL catalog. 
+W44 was simulated over the two-year time range used in 2FGL. 
 In the simulations, we disabled the inherent energy dispersion of photons
@@
 
-Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
-fitting the simulations of W44 as as a point-like source.
-The sources are very significant ($\ts\sim3500$).
-Figure~\ref{ts_comparison_w44sim}b shows the distribution of \tsext values
-when fitting the source as a radially-symmetric uniform disk and Gaussian source.
-The sources are very significantly extended ($\tsext\sim250$). 
-On average \tsext is slightly larger when
-fitting the source with the disk spatial model compared to the Gaussian spatial model,
-consistent with the fact that the simulated source's true spatial model has a sharp edge.
-Figure~\ref{ts_comparison_w44sim}c then shows the change in \ts 
-when fitting the simulated source as
-an elliptical disk compared to fitting the source as a disk. Since the changes
-in \ts are on average $\sim30$, we see that our simulated source is significantly better
-described with an elliptical spatial model. Finally, 
-Figure~\ref{ts_comparison_w44sim}d shows the changes in \ts when fitting
-the sources with an elliptical ring spatial model compared to fitting them
-with elliptical disk spatial models.
-Since the changes are on average $\sim9$, the simulated sources are only somewhat better described
-by the true spatial model.
+Figure~\ref{ts_comparison_w44sim}a shows that the simulations of
+W44 when fit as point-like sources are very significant ($\ts\sim3500$).
+Figure~\ref{ts_comparison_w44sim}b shows that the simulations when
+fit with a radially-symmetric uniform disk or Gaussian spatial
+model are highly extended ($\tsext\sim250$).  On average \tsext is
+slightly larger when fitting the sources with a uniform disk spatial
+model compared to a Gaussian spatial model, consistent with the
+fact that the simulated source's true spatial model has a sharp edge.
+Figure~\ref{ts_comparison_w44sim}c shows that the sources fit better
+when assuming an elliptical disk spatial model compared to a uniform disk
+spatial model ($\ts_\text{elliptical\ disk}-\ts_\text{disk}\sim30$).
+Finally, Figure~\ref{ts_comparison_w44sim}d shows that the sources
+are only fit slightly better assuming an elliptical ring spatial model
+compared to an elliptical disk spatial model ($\ts_\text{elliptical\
+ring}-\ts_\text{elliptical\ disk}\sim9$).
 
 Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
-show the distributions of best fit flux and spectral indices when fitting
+show the distributions of best fit fluxes and spectral indices when fitting
 the simulated sources.
@@
 of the extended spatial models, there is no bias in the best fit spectral parameters
-(within the precision of the Monte Carlo study). The reason is that
-within the finite angular precision and limited statistics of the LAT, 
+(within the precision of the Monte Carlo study). This is because,
+within the finite angular resolution and limited statistics of the LAT, 
 all of the extended spatial models can be adjusted to look very similar.
 
-Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius.  
-For the elliptical ring spatial model, there is no significant bias in the best fit size. 
-None of the other spectral models induced a bias greater
-than $\sim10\%$. From this, we see that \rsixeight is a reasonable measure of the true 68\%
-containment radius for a reasonable spatial models.
-
-For completeness, Figure~\ref{bias_w44sim}d plots the distribution of best
-fit elliptical eccentricities and Figure~\ref{bias_w444im}e plots the
-distribution of orientation angles
+Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius when
+the sources are fit with the extended spatial models.  When assuming
+the elliptical ring spatial model, there is no significant bias in the
+best fit size.  Becasue none of the other spectral models induced a
+bias greater than $\sim10\%$, we see that \rsixeight for any of the
+spatial models can be used as a reasonable measure of the true 68\%
+containment radius for the source.
+
+For completeness, Figure~\ref{bias_w44sim}d and Figure~\ref{bias_w44sim}e 
+shows that there are 
+no systematic biases in the
+distribution of best
+fit elliptical eccentricities and orientation angles
 when the sources were fit with elliptical
-disk and elliptical ring spatial models.  
+spatial models.  
 The eccentricity is defined as
@@
 $b$ is the length of the semi-minor axis.  
-There is no systematic bias in the eccentricities or orientation angles.
 Finally, Figure~\ref{bias_w44sim}f shows that the distribution of best fit
-ring fractions is unbiased when the sources are fit with the elliptical
+inner ring fractions is unbiased when the sources are fit with the elliptical
 ring spatial model.
@@
 \newtext{
-We considered an alternate Bayesian formulation of this test.
-We considered the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test},
-but found it difficult
-to apply to LAT data because it required a term including the number of data points
-and for LAT events. Because there are many photons included in an analysis that contribute only
- marginally to the analysis of a source, it is unclear how this test could be applied.
-We also considered the Akaike information criterion test \citep[\aic,][]{AIC_statistical_test}.
+We considered using 
+the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test} as
+an alternate Bayesian formulation of this test. But it is difficult to apply
+to LAT data because it contains a term including the number of data points. But for LAT data,
+there are many photons included in an analysis that contribute only
+ marginally to the analysis of a source
+As an alternative, we considered the Akaike information criterion test \citep[\aic,][]{AIC_statistical_test}.
 The \aic is defined as
@@
 parameters and two spectral parameters compared to one extension parameter),
-we note that the $\tsext>\tsinc$ is mathematically equivalent to the test:
+we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing 
 \begin{equation}
@@
 \end{equation}
-Therefore, our original test has an 
+Therefore, our test has an 
 equivalent Bayesian formulation requiring that $\aic_\text{ext}$ 
@@
 \newtext{It is very close to the position of 2FGL\,J1632.4$-$4753c
-and does not show in the observed photon distribution separated emission.}
+and does not show separated emission in the observed photon distribution.}
 We therefore removed this source from our model of the
@@
 \newtext{For the Galactic simulations, the quoted fluxes are
-if the sources were placed in the Galactic center and the actual
-flux is scaled by Equation~\ref{scale_flux_by_background}.}
+the flux for sources placed 
+in the Galactic center. The actual flux is scaled by Equation~\ref{scale_flux_by_background}.}
 }
@@
     also tabulated.  
-    \newtext{The top rows are the sources simulated on top of an isotropic background and
+    \newtext{The top rows are the simulations on top of an isotropic background and
     the bottom rows are the simulations on top of the Galactic diffuse and isotropic
@@
     when fitting W44 as a point-like source and (b) is the
-    distribution of \tsext when fitting the source with a Gaussian and uniform disk 
+    distribution of \tsext when fitting the source with a uniform disk and Gaussian
     spatial model. (c) is the distribution of the change in TS when
@@
     fitting it with a radially-symmetric disk spatial model and (d) 
-    when fitting the source with a elliptical ring spatial model compared
+    when fitting the source with an elliptical ring spatial model compared
     to an elliptical disk spatial model.
@@
     \newtext{the distribution of fit parameters
-    for the simulation of Monte Carlo simulations of W44.
+    for the Monte Carlo simulations of W44.
     The plots show the distribution of 
-    (a) best fit flux (b) spectral index (c) 68\% containment
+    best fit (a) flux (b) spectral index (c) 68\% containment
     radius (d) eccentricity (e) elliptical orientation angle
-    (f) inner ring fraction.
+    and (f) inner ring fraction.
     }
@@
 \tablewidth{0pt}
-\tablecaption{Nearby Residual Sources
+\tablecaption{Nearby Residual-induced Sources
 \label{fake_2fgl_sources}
@@
 \colhead{Extended Source}&
-\colhead{Nearby Residual Sources}
+\colhead{Residual-induced Sources}
 }

### 2012-04-25 extended_catalog/paper/extended_search.tex
update

@@
 extension of a LAT source and in Section~\ref{bias_wrong_spatial_model}
-we asses the bias that is introduced by using an incorrect spatial model.
+we asses the bias that is introduced by assuming an incorrect spatial model.
 In Section~\ref{extension_sensitivity},
@@
 \newtext{In section \ref{bias_wrong_spatial_model}, we perform a dedicated Monte Carlo simulation
-to asses possible bias due to incorrectly modeling the spatial structure
+that shows there is little bias due to incorrectly modeling the spatial structure
 of an extended source.
-In our search for extended sources, we use only a radially-symmetric uniform
+Therefore, in our search for extended sources we use only a radially-symmetric uniform
 disk spatial model. Unless otherwise noted,
@@
 \newtext{
-We performed a second simulation to assess any effects that could
-be introduces by performing this test in the presence of a highly
+We performed a second simulation to assess any bias that could
+be introduces by performing the extension test in the presence of a highly
 structured background.
@@
 expect to be able to spatially resolve sources much dimmer than this
-and sources much brigher are not likely to be affected by the background.
+and sources much brighter are less likely to be affected by the background.
 
@@
 flux of the source from 100 \mev to 100 \gev, $F(\text{GC})$
-is the same quantity if the source were at the galactic center, $B$
+is the same quantity if the source was at the galactic center, $B$
 is the integral of the Galactic diffuse and isotropic emission
-from 1 \gev to 100 \gev, and $B(\text{GC})$ is the same quantity
-if the source was at the galactic center.  Table~\ref{ts_ext_num_sims}
-contains $F(\text{GC})$ and the average value of \ts for the four spectral models.
+from 1 \gev to 100 \gev at the position of the source, and $B(\text{GC})$ is the same quantity
+if the source was at the galactic center.  For the four spectral models,
+Table~\ref{ts_ext_num_sims} lists $F(\text{GC})$ and the average value of \ts.
 
@@
 Figure~\ref{tsext_plane_plot} shows the cumulative density
-of \tsext. For small values of \tsext,
+of \tsext for each spectrum. For small values of \tsext,
 there is good agreement between the simulations and
@@
 \gev and a spectral index of 2.66.
-The simulated flux and spectral index of this source
-were taken from our analysis of W44 which is described in Section~\ref{validate_known}.
+The flux and spectral index of this source
+was taken from our analysis of W44 which will be described in Section~\ref{validate_known}.
 
@@
 \cite{w44}. For reference, the ellipse has a semi-major axis of 0\fdg3,
-a semi-minor axis of 0\fdg19, has a position angle of $147\degree$
+a semi-minor axis of 0\fdg19, a position angle of $147\degree$
 measured east of celestial north, and predicts emission only for the
@@
 We used a simulation setup similar to that described in
-Section~\ref{monte_carlo_validation}, but the source was simulated on
+Section~\ref{monte_carlo_validation}, but the sources were simulated on
 top of and analyzed assuming the presence of the standard Galactic diffuse and
@@
 will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.
-In total, we performed 985 identical simulations.
+In total, we performed 985 statistically independent simulations.
 
@@
 a radially-symmetric uniform Gaussian and disk spatial model, 
-an Elliptical disk spatial model, and finally with an Elliptical
+an elliptical disk spatial model, and finally with an elliptical
 ring spatial model.
-We obtained the best fit spatial parameters using \pointlike and, using 
-these best fit spatial parameters, obtained the best fit spectral parameters 
+We obtained the best fit spatial parameters using \pointlike and, 
+with these parameters, obtained the best fit spectral parameters 
 using \gtlike.
@@
 Figure~\ref{ts_comparison_w44sim}a shows that the simulations of
-W44 when fit as point-like sources are very significant ($\ts\sim3500$).
-Figure~\ref{ts_comparison_w44sim}b shows that the simulations when
-fit with a radially-symmetric uniform disk or Gaussian spatial
-model are highly extended ($\tsext\sim250$).  On average \tsext is
+W44 are very significant ($\ts\sim3500$) when fit as point-like sources.
+Figure~\ref{ts_comparison_w44sim}b shows that the simulations 
+are highly extended ($\tsext\sim250$)
+when fit with a radially-symmetric uniform disk or Gaussian spatial
+model.
+On average \tsext is
 slightly larger when fitting the sources with a uniform disk spatial
@@
 fact that the simulated source's true spatial model has a sharp edge.
-Figure~\ref{ts_comparison_w44sim}c shows that the sources fit better
+Figure~\ref{ts_comparison_w44sim}c shows that the sources were fit better
 when assuming an elliptical disk spatial model compared to a uniform disk
@@
 Finally, Figure~\ref{ts_comparison_w44sim}d shows that the sources
-are only fit slightly better assuming an elliptical ring spatial model
+were fit somewhat better assuming an elliptical ring spatial model
 compared to an elliptical disk spatial model ($\ts_\text{elliptical\
@@
 Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius when
-the sources are fit with the extended spatial models.  When assuming
-the elliptical ring spatial model, there is no significant bias in the
-best fit size.  Becasue none of the other spectral models induced a
+the sources were fit with extended spatial models.  When assuming
+the elliptical ring spatial model, there is no significant bias in 
+\rsixeight.  Because none of the other spatial models induced a
 bias greater than $\sim10\%$, we see that \rsixeight for any of the
@@
 Finally, Figure~\ref{bias_w44sim}f shows that the distribution of best fit
-inner ring fractions is unbiased when the sources are fit with the elliptical
+inner ring fractions is unbiased when the sources were fit with the elliptical
 ring spatial model.
@@
 the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test} as
-an alternate Bayesian formulation of this test. But it is difficult to apply
-to LAT data because it contains a term including the number of data points. But for LAT data,
-there are many photons included in an analysis that contribute only
- marginally to the analysis of a source
+an alternative Bayesian formulation of this test, but it is difficult to apply
+to LAT data because it contains a term including the number of data points. For LAT data,
+this is not a clear concept because there are many photons included in an analysis that contribute only
+ marginally to the analysis of a source.
+
 As an alternative, we considered the Akaike information criterion test \citep[\aic,][]{AIC_statistical_test}.
@@
 parameters and two spectral parameters compared to one extension parameter),
-we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing 
+we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing that
 \begin{equation}
@@
 \newtext{In Table~\ref{fake_2fgl_sources}, we will summarize the sources that were 
-included in 2FGL to account for residuals induced by not modeling the extension of
+included in 2FGL to account for residuals induced by not modeling the extensions of
 nearby extended sources.}
@@
 summarize the sources included in 2FGL to account for residuals induced
-by not modeling the extension of nearby extended sources.}
+by not modeling the extensions of nearby extended sources.}
 
@@
 \newtext{It is very close to the position of 2FGL\,J1632.4$-$4753c
-and does not show separated emission in the observed photon distribution.}
+and does not show spatially separated emission in the observed photon distribution.}
 We therefore removed this source from our model of the
@@
 \begin{deluxetable}{rrrrrr}
-\tabletypesize{\footnotesize}
+\tabletypesize{\scriptsize}
 \tablecaption{Monte Carlo Spectral Parameters
@@
 \newtext{For the Galactic simulations, the quoted fluxes are
-the flux for sources placed 
-in the Galactic center. The actual flux is scaled by Equation~\ref{scale_flux_by_background}.}
+the fluxes for sources placed 
+in the Galactic center. The actual fluxes are scaled by Equation~\ref{scale_flux_by_background}.}
 }
@@
     \caption{
-    \newtext{the distribution of fit parameters
+    \newtext{The distribution of fit parameters
     for the Monte Carlo simulations of W44.
@@
     these sources. \newtext{Puppis A has a spectral index of
-    $2.21\pm0.09$ and $\gamma$-Cygni has a spectral
+    $2.21\pm0.09$ and $\gamma$-Cygni has an
     index of $2.42\pm0.19$.}

### 2012-04-25 extended_catalog/external_review_reply/replies_to_review_comments.tex
update

@@
 \usepackage{color}
+\usepackage{fullpage}
 
@@
 
-There is a new section 3.2 called ``Assessing the Bias Due to Incorrect
-Spatial Models''. In this section, we address your question by performing
+There is a new section 3.2 (Assessing the Bias Due to Incorrect
+Spatial Models). In this section, we address your question by performing
 a dedicated Monte Carlo study of W44 simulated with a ring-type spatial
@@
 \begin{reply}
-In section 3.1 (which was previously just section 3 and is called
+In section 3.1 (which was previously just section 3 and is now called
 Statistical Significance Testing), we have added new text describing a
@@
 \begin{reply}
-We have added a new table (Table 6 in the current draft) which contains
+We have added a new table (Table 6 in the current draft, named Nearby Residual-induced Sources) which contains
 this information. There are paragraphs in section 9 (Extended Source
 Search Method) and Section 10 (New Extended Sources) which refer to this
-table. We have also updated the specified captions to list names of 2FGL
+table. We have also updated the requested captions to list names of 2FGL
 sources that were removed.
@@
 models are not nested. We considered the BIC test but found that it would
-not work well for Fermi LAT. We alternately considered the AIC test and
+not work well for LAT data. We alternately considered the AIC test and
 found that it is equivalent to the test we actually performed. We have
 added a new paragraph to Section 5 (Testing Against Source Confusion)
-that describes the Bayesian interoperation of the test we performed.
+that describes the Bayesian interpretation of the test we actually performed.
 \end{reply}

### 2012-05-08 extended_catalog/external_review_reply/replies_to_review_comments.tex
update

@@
 \begin{reply}
-Thank you for your careful review of the text. We discuss below the
+  We thank the referee for the careful review of the text. We discuss below the
 changes we have made incorporating your feedback. To make the changes more visible,
-in the new draft we have bolded and colored red the parts that are new or have changed.
+in the new draft we have made bold and colored red the parts that are new or have changed.
 \end{reply}
@@
 \begin{reply}
-In the new draft, Section 3 (Validation of Analysis Method) has been
-divided into two sections. The original section is now section 3.1
-(now called Statistical Significance Testing).
+In the new draft, Section 2 has new text defining TS.
+Section 3 has been renamed (Validation of the TS Distribution) and has been
+divided into three sections. The original section is now section 3.1
+(now called Point-like Source Simulations Over a Uniform Background).
+I will describe section 3.2 in reply to the next question.
 
-There is a new section 3.2 (Assessing the Bias Due to Incorrect
-Spatial Models). In this section, we address your question by performing
+There is also a new section 3.3 (Extended Source Simulations Over a 244 Structured Background). 
+In this section, we address your question by performing
 a dedicated Monte Carlo study of W44 simulated with a ring-type spatial
-model. By fitting the source with different spatial models, we asses
+model. By fitting the source with different spatial models, we assess
 this bias and find it to be very small.
@@
 in section 2.4 (Comparing Source Size) we add a line of text referring
-to this new section. Finally, there is a new sentance in the introduction
+to this new section. Finally, there is a new sentence in the introduction
 of the paper which references the new text.
@@
 \begin{reply}
-In section 3.1 (which was previously just section 3 and is now called
-Statistical Significance Testing), we have added new text describing a
+In section 3.2 (Point-like Source Simulations Over a Structured Background), we have added new text describing a
 follow up Monte Carlo study performed in the presence of the galactic
@@
 Spectral Parameters) to include the new simulation parameters. There is also
-a new figure (Figure 5) which shows the distribution of TSext for these
+a new figure (Figure 5) which shows the distribution of $\mathrm{TS}_\mathrm{ext}$
+for these
 new simulations.
@@
 We have added a new table (Table 6 in the current draft, named Nearby Residual-induced Sources) which contains
-this information. There are paragraphs in section 9 (Extended Source
-Search Method) and Section 10 (New Extended Sources) which refer to this
+this information. There is also new text in section 9 (Extended Source
+Search Method) which refer to this
 table. We have also updated the requested captions to list names of 2FGL
@@
 on exact photon positions, and binning is not required (as it is with
-older chi-square-minimiization techniques). Binning is ill-advised as
+older chi-square-minimization techniques). Binning is ill-advised as
 it results in a loss of information, and sometimes in a bias. As this
@@
 spatial fitting described in this paper. That is why we developed this
-new functionality inside of pointlike. The validations of pointlike
-presented in this paper allow us to be confident in our spatial analysis results.
+new functionality inside of pointlike. 
+Even though pointlike performs a fully binned analysis, it used the
+healpix hierarchy for spatial bins and scales the spatial bin size with
+energy. This ensures that the spatial binning is always smaller than the
+inherent spatial resolution of the instrument.
+The validations of this method
+presented in this paper allow us to be confident in our results.
 \end{reply}
@@
 \begin{reply}
-Concerning the extension significance test, we extensively validated it
+Concerning the extension significance test, it actually relies not exactly
+on Wilk's theorem (which does not hold for the extension test)
+but on Chernoff's theorem (see ``On the Distribution of the Likelihood 
+Ratio'', \url{http://www.jstor.org/stable/10.2307/2236839}).
+we also extensively validated it
 against Monte Carlo simulations. Furthermore, the high energy astrophysics
-community has a lot of experience with the test statistic (TS) applied to
+community has a lot of experience with the likelihood ratio test applied to
 nested models. So we are very confident that we can apply it to the actual
@@
 models are not nested. We considered the BIC test but found that it would
-not work well for LAT data. We alternately considered the AIC test and
-found that it is equivalent to the test we actually performed. We have
+not work well for LAT data. The reason for this is described in the text.
+We alternatively considered the AIC test and
+found that it is mathematically equivalent to the test we actually performed,
+putting the test on firmer ground. We have
 added a new paragraph to Section 5 (Testing Against Source Confusion)
-that describes the Bayesian interpretation of the test we actually performed.
+that describes this.
 \end{reply}
@@
 Thanks for the suggestion.  In addition to the above changes, we have
-fixed the bibliographical information on the LAT publication of Vela Jr.
+fixed a few bibliographical entries.
 \end{reply}

### 2012-05-08 extended_catalog/paper/extended_search.tex
update
done w/ draft v10 of ext src paper

@@
 extension of a LAT source and in Section~\ref{bias_wrong_spatial_model}
-we asses the bias that is introduced by assuming an incorrect spatial model.
+we assess the expected level of bias 
+introduced by assuming an incorrect spatial model.
 In Section~\ref{extension_sensitivity},
@@
 
+\newtext{
 The significance of the extension of a source can be calculated from the
-likelihood ratio test of a hypothesis with a spatially extended source and
-a hypothesis with a point-like source. The test statistic (TS) for this procedure
-is defined as
+likelihood-ratio test. The likelihood ratio defines the
+test statistic (TS) by comparing the likelihood of a simpler hypothesis to
+a more complicated one:
 \begin{equation}
-  \tsext=2\log(\likelihood_\text{ext}/\likelihood_\text{ps}) 
+  \ts=2\log(\likelihood(H_1)/\likelihood(H_0)),
 \end{equation}
-where \likelihood is the Poisson likelihood.
+where $H_1$ is the more complicated hypothesis and $H_0$ the simpler one.
+For the case of the extension test, we compare the likelihood
+when assuming the source has either a point-like or spatially extended spatial model:}
+\begin{equation}
+  \tsext=2\log(\likelihood_\text{ext}/\likelihood_\text{ps}).
+\end{equation}
 \pointlike calculates \tsext by fitting a source first with a spatially
@@
 
-\section{Validation of the Analysis Method}
-
-\subsection{\newtext{Statistical Significance Testing}}
+\newtext{
+\section{Validation of the \ts Distribution}
+
+\subsection{Point-like Source Simulations Over a Uniform Background}
+
+}
 
@@
 
-We evaluated the false detection probability for the measurement of source extent
-by fitting the extensions of point-like sources.  \cite{mattox_egret}
-discuss that the TS distribution for a likelihood ratio test
+\newtext{
+We tested the theoretical distribution for \tsext
+to evaluate the false detection probability for measuring source extension.
+To do so, we tested simulated point-like sources for extension.} 
+\cite{mattox_egret}
+discuss that the \ts distribution for a likelihood-ratio test
 on the existence of a source at a given position is
@@
 $\delta$ is the Dirac delta function.
-}
 The particular form of Equation \ref{ts_ext_distribution} is due to the
 null hypothesis (source flux $\Phi=0$) residing on the edge of parameter
-space and the model hypothesis adding a single degree of freedom.
+space and the model hypothesis adding a single degree of freedom (the source extension).}
 It leads to the often quoted result $\sqrt{TS}=\sigma$, where 
@@
 \newtext{
-We performed a second simulation to assess any bias that could
-be introduces by performing the extension test in the presence of a highly
-structured background.
+
+\subsection{\newtext{Point-like Source Simulations Over a Structured Background}}
+
+We performed a second simulation to show that the theoretical distribution
+for \tsext is still preserved when the point-like sources are present over
+a highly-structured diffuse background.
 Our simulation setup was the same as above except that the sources were
@@
 To limit the number of tests, we selected only one flux
-level for each of the four spectral indices and we perform
+level for each of the four spectral indices and we performed
 this test only in the 1 \gev to 100 \gev energy range. 
@@
 expect to be able to spatially resolve sources much dimmer than this
-and sources much brighter are less likely to be affected by the background.
+and sources much brighter are less likely to be affected by the 
+structured background.
 
@@
 a small discrepancy, but limited statistics makes this hard to quantify.
-}
-
-\subsection{Assessing the Bias Due to Incorrect Spatial Models}
+Therefore, we are confident we can used \tsext as a robust measure of
+statistical significance when testing LAT-detected sources for extension.
+
+\subsection{Extended Source Simulations Over a Structured Background}
 \label{bias_wrong_spatial_model}
 
-\newtext{
-We performed a Monte Carlo study to quantify the bias that is introduced by
-incorrectly modeling the spatial structure of an extended source. 
-To assess this systematic, we simulated the spatially extended ring-type SNR W44.
+We also performed a Monte Carlo study to show that incorrectly modeling the
+spatial extension of an extended source does not substantially bias
+the spectral fit of the source, although it does alter the value of the \ts.
+To assess this, we simulated the spatially extended ring-type SNR W44.
 We selected W44 because it is the most significant extended source detected by the LAT 
@@
 a semi-minor axis of 0\fdg19, a position angle of $147\degree$
-measured east of celestial north, and predicts emission only for the
-outer 0.75\% of the shape.
+measured east of celestial north, and the ring's inner radius is 0.75 times
+the outer radius.
 
@@
 In the simulations, we disabled the inherent energy dispersion of photons
-by the LAT. The bias caused by ignoring energy dispersion 
+by the LAT to isolate the effects due to changing the assumed spatial model. 
+The bias caused by ignoring energy dispersion 
 will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.
@@
 
-Figure~\ref{ts_comparison_w44sim}a shows that the simulations of
-W44 are very significant ($\ts\sim3500$) when fit as point-like sources.
-Figure~\ref{ts_comparison_w44sim}b shows that the simulations 
-are highly extended ($\tsext\sim250$)
-when fit with a radially-symmetric uniform disk or Gaussian spatial
-model.
-On average \tsext is
-slightly larger when fitting the sources with a uniform disk spatial
-model compared to a Gaussian spatial model, consistent with the
-fact that the simulated source's true spatial model has a sharp edge.
-Figure~\ref{ts_comparison_w44sim}c shows that the sources were fit better
-when assuming an elliptical disk spatial model compared to a uniform disk
-spatial model ($\ts_\text{elliptical\ disk}-\ts_\text{disk}\sim30$).
-Finally, Figure~\ref{ts_comparison_w44sim}d shows that the sources
-were fit somewhat better assuming an elliptical ring spatial model
+Figure~\ref{ts_comparison_w44sim}a shows that the simulations of W44
+are very significant ($\ts\sim3500$) when fit as point-like sources.
+Figure~\ref{ts_comparison_w44sim}b shows that the simulations are
+highly extended ($\tsext\sim250$) when fit with any of the extended
+spatial models.  On average \tsext is somewhat larger when fitting
+the sources with more accurate spatial models.  This shows that
+assuming an incorrect spatial model will cause the source's
+significance to be underestimated.  Figure~\ref{ts_comparison_w44sim}c
+shows that the sources were fit better when assuming an elliptical
+disk spatial model compared to a uniform disk spatial model
+($\ts_\text{elliptical\ disk}-\ts_\text{disk}\sim30$).  Finally,
+Figure~\ref{ts_comparison_w44sim}d shows that the sources were
+fit somewhat better assuming an elliptical ring spatial model
 compared to an elliptical disk spatial model ($\ts_\text{elliptical\
-ring}-\ts_\text{elliptical\ disk}\sim9$).
-
-Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
-show the distributions of best fit fluxes and spectral indices when fitting
-the simulated sources.
-When fitting the sources with a point-like
-spatial model, there is a $\sim$10\% bias in the fit flux and
-a $\sim5\%$ bias in the fit index. When fitting the sources assuming any
-of the extended spatial models, there is no bias in the best fit spectral parameters
-(within the precision of the Monte Carlo study). This is because,
-within the finite angular resolution and limited statistics of the LAT, 
-all of the extended spatial models can be adjusted to look very similar.
-
-Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius when
-the sources were fit with extended spatial models.  When assuming
-the elliptical ring spatial model, there is no significant bias in 
-\rsixeight.  Because none of the other spatial models induced a
-bias greater than $\sim10\%$, we see that \rsixeight for any of the
-spatial models can be used as a reasonable measure of the true 68\%
-containment radius for the source.
+ring}-\ts_\text{elliptical\ disk}\sim9$). This shows that the LAT has
+some additional power to resolve substructure in bright extended sources.
+
+Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b clearly show that
+no significant bias is introduced by modeling the source as extended
+but with an inaccurate spatial model, while a point-like source modeling
+results in a $\sim10\%$ and $\sim5\%$ bias in the fit flux and index,
+respectively.  
+Furthermore, Figure~\ref{bias_w44sim}c shows that the \rsixeight estimate of
+the extension size is very mildly biased ($\sim10\%$) toward higher values
+when inaccurate spatial models are used, and thus represent a reasonable
+measurement of the true 68\% containment radius for the source.
 
@@
 \tsinc cannot be quantitatively compared to \tsext using a simple
-likelihood ratio test to evaluate which model is significantly better
+likelihood-ratio test to evaluate which model is significantly better
 because the models are not nested \citep{statistics_with_care}.
@@
 the Bayesian information criterion \citep[BIC,][]{BIC_statistical_test} as
-an alternative Bayesian formulation of this test, but it is difficult to apply
+an alternative Bayesian formulation for this test, but it is difficult to apply
 to LAT data because it contains a term including the number of data points. For LAT data,
 this is not a clear concept because there are many photons included in an analysis that contribute only
- marginally to the analysis of a source.
+ marginally to the analysis of a given source.
 
@@
 where $k$ is the number of parameters in the model. 
-In this formulation, the best model is considered to be the one that minimizes the \aic.
+In this formulation, the best hypothesis is considered to be the one that minimizes the \aic.
 The first term penalizes models with additional parameters.
@@
 of the background model that were performed.
-\newtext{In Table~\ref{fake_2fgl_sources}, we will summarize the sources that were 
+\newtext{In Table~\ref{fake_2fgl_sources}, we summarize the sources that were 
 included in 2FGL to account for residuals induced by not modeling the extensions of
@@
 emission model and uncertainties in the PSF.
-\newtext{Finally, in Table~\ref{fake_2fgl_sources} we 
-summarize the sources included in 2FGL to account for residuals induced
-by not modeling the extensions of nearby extended sources.}
 
@@
     radius (d) eccentricity (e) elliptical orientation angle
-    and (f) inner ring fraction.
+    and (f) inner ring fraction. The dashed vertical lines represent
+    the simulated values of the parameters.
     }
@@
 \newtext{
-For each new extended sources, we list nearby catalog
+For each new extended source, we list nearby catalog
 sources that were included in 2FGL to account for residuals induced
-by not modeling the extension of the nearby extended source.
+by not modeling the extension of the extended source.
 }

### 2012-05-08 extended_catalog/monte_carlo/w44sim/plots/plot_ts_values.py
update figs

@@ -47,11 +47,11 @@ axes=fig.add_subplot(222)
 histogram(axes, 
           data=[2*(ll_gaussian-ll_point),
                 2*(ll_disk-ll_point)],
-          color=['red' if not bw else '0.5','black'])
+          color=['red' if not bw else '0.6','black'])
 axes.set_xlabel(r'$\mathrm{TS}_\mathrm{ext}$')
 prop = matplotlib.font_manager.FontProperties(size=10)
 axes.set_ylim(0,100)
-axes.legend([Line2D([0],[0],color='black'),Line2D([0],[0],color='red')],
+axes.legend([Line2D([0],[0],color='black'),Line2D([0],[0],color='red' if not bw else '0.6')],
             ['disk','Gaussian'],
             prop=prop)
 

### 2012-05-10 extended_catalog/paper/extended_search.tex
update

@@
 \end{equation}
-Therefore, our test has an 
-equivalent Bayesian formulation requiring that $\aic_\text{ext}$ 
-be sufficiently smaller than $\aic_\text{2pts}$.
+This equation requires that the extended source hypothesis be considerably preferred
+over the hypothesis of two point-like sources.
+Therefore, our original test is mathematically equivalent to one with a Bayesian interpretation.
+
 }

### 2012-05-10 extended_catalog/paper/extended_search.tex
updated draft

--- 2012-05-08 extended_catalog/paper/extended_search.tex
@@
 to LAT data because it contains a term including the number of data points. For LAT data,
-this is not a clear concept because there are many photons included in an analysis that contribute only
+this is not a clear concept because there are many pixels included in an analysis that contribute only
  marginally to the analysis of a given source.
@@
 As an alternative, we considered the Akaike information criterion test \citep[\aic,][]{AIC_statistical_test}.
-The \aic is defined as
-\begin{equation}
-  \aic=2k-2\log\likelihood,
-\end{equation}
-where $k$ is the number of parameters in the model. 
+The \aic is defined as $\aic=2k-2\log\likelihood$, where $k$ is the number of parameters in the model. 
 In this formulation, the best hypothesis is considered to be the one that minimizes the \aic.
@@
 we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing that
-\begin{equation}
-  \aic_\text{ext} < \aic_\text{2pts} - 6.
-\end{equation}
-Therefore, our test has an 
-equivalent Bayesian formulation requiring that $\aic_\text{ext}$ 
-be sufficiently smaller than $\aic_\text{2pts}$.
+$\aic_\text{ext} < \aic_\text{2pts} - 6$.
+Thus our criterion based on the \ts value is equivalent to requesting
+that the \aic-based empirical support for the two-point-like-source model be
+``considerably less'' than for the extended source model, following the
+classification by \cite{aic_stats_book}.
 }

### 2012-05-15 pwncatalog/PWNCAT2/code/analyze_helper.py
update code

@@ -169,14 +169,14 @@ def plots(roi, name, hypothesis,
     roi.toRegion('%s/region_%s_%s.reg'%(datadir,hypothesis, name))
 
 def pointlike_analysis(roi, name, hypothesis, localization_emin=None,
-                       seddir='seds', datadir='data', plotdir='plots',
+                       seddir='seds', datadir='data', 
                        upper_limit=False, localize=False,
                        fit_extension=False, extension_upper_limit=False,
                        cutoff=False, seds=False):
     """ emin + emax used for computing upper limits. """
     print 'Performing Pointlike analysis for %s' % hypothesis
 
-    for dir in [seddir, datadir, plotdir]: 
+    for dir in [seddir, datadir]: 
         if not os.path.exists(dir): os.makedirs(dir)
 
     print_summary = lambda: roi.print_summary(galactic=True)
@@ -346,9 +346,12 @@ def gtlike_analysis(roi, name, hypothesis,
 
     return r
     
-def save_results(results, name): 
-    open('results_%s.yaml' % name,'w').write(
-        yaml.dump(tolist(results)))
+def save_results(results, name, hypothesis=None, followup=None): 
+    if hypothesis is None and followup is None:
+        filename='results_%s.yaml' % name
+    else:
+        filename='results_%s_%s_%s.yaml' % (name,hypothesis,followup)
+    open(filename,'w').write(yaml.dump(tolist(results)))
 
 def import_module(filename):
     """ import a python module from a pathname. """

### 2012-05-15 pwncatalog/PWNCAT2/code/analyze_psr.py

@@ -21,128 +21,98 @@ from collections import defaultdict
 import numpy as np
 np.seterr(all='ignore')
 
-parser = ArgumentParser()
-parser.add_argument("--pwndata", required=True)
-group=parser.add_mutually_exclusive_group(required=True)
-group.add_argument("-p", "--pwnphase")
-group.add_argument("--no-phase-cut", default=False, action="store_true")
-parser.add_argument("-n", "--name", required=True, help="Name of the pulsar")
-parser.add_argument("--emin", default=1e2, type=float)
-parser.add_argument("--binsperdec", default=4, type=int)
-parser.add_argument("--localization-emin", default=1e3, type=float)
-parser.add_argument("--emax", default=10**5.5, type=float)
-parser.add_argument("--use-gradient", default=False, action="store_true")
-parser.add_argument("--no-at-pulsar", default=False, action="store_true")
-parser.add_argument("--no-point", default=False, action="store_true")
-parser.add_argument("--no-extended", default=False, action="store_true")
-parser.add_argument("--no-gtlike", default=False, action="store_true")
-parser.add_argument("--no-plots", default=False, action="store_true")
-parser.add_argument("--no-cutoff", default=False, action="store_true")
-parser.add_argument("--no-upper-limits", default=False, action="store_true")
-parser.add_argument("--no-seds", default=False, action="store_true")
-parser.add_argument("--no-extension-upper-limits", default=False, action="store_true")
-parser.add_argument("--no-savedir", default=False, action="store_true")
-parser.add_argument("--max-free", default=10, type=float)
-parser.add_argument("--modify", required=True)
-args=parser.parse_args()
+def get_args():
 
-do_at_pulsar = not args.no_at_pulsar
-do_point = not args.no_point
-do_extended = not args.no_extended
-do_gtlike = not args.no_gtlike
-do_plots = not args.no_plots
-do_cutoff = not args.no_cutoff
-do_upper_limits = not args.no_upper_limits
-do_extension_upper_limits = not args.no_extension_upper_limits
-do_seds = not args.no_seds
+    parser = ArgumentParser()
+    parser.add_argument("--pwndata", required=True)
+    group=parser.add_mutually_exclusive_group(required=True)
+    group.add_argument("-p", "--pwnphase")
[…]

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/off_peak/merge.py

@@ -4,10 +4,15 @@ from os.path import join, expandvars, exists
 from os import makedirs
 import yaml
 
+from lande.utilities.lists import recursive_map
+
+
+#version = 'v4'
+version = 'v3'
 
 pwndata=yaml.load(open(expandvars('$pwncode/pwndata/pwncat2_data_lande.yaml')))
 
-r='$pwndata/off_peak/off_peak_bb/pwncat2/v4'
+r='$pwndata/off_peak/off_peak_bb/pwncat2/%s'  % version
 
 pwnlist = sorted(pwndata.keys())
 
@@ -26,6 +31,7 @@ for i,pwn in enumerate(pwnlist):
     optimal_radius=results['optimal_radius']
 
     f = PhaseRange(off_peak_phase).tolist(dense=True)
+    f = recursive_map(lambda i: '%.2f' % i, f)
     d[pwn] = dict(
         phase = f,
         optimal_emin=optimal_emin,

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/off_peak/website.py

@@ -5,8 +5,10 @@ from os.path import join,expandvars,exists,basename
 
 from lande.utilities.website import t2t
 
-website_path=expandvars('$pwndata/off_peak/off_peak_bb/pwncat2/v4/website')
-analysis_path=expandvars('$pwndata/off_peak/off_peak_bb/pwncat2/v4/analysis')
+#version='v4'
+version='v3'
+website_path=expandvars('$pwndata/off_peak/off_peak_bb/pwncat2/%s/website' % version)
+analysis_path=expandvars('$pwndata/off_peak/off_peak_bb/pwncat2/%s/analysis' % version)
 
 
 if not exists(website_path): os.makedirs(website_path)

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/submit.sh

@@ -627,3 +627,87 @@ echo python $common_kwargs \
 echo python $common_kwargs \
         -o $pwndata/spectral/$version/analysis_fast2 \
         --no-gtlike --no-cutoff --no-extension-upper-limits --no-upper-limits --no-plots
+
+
+
+
+
+
+
+# ----------------------------------------------------------------------------------------------------
+
+# major changes: ??? rerun
+version=test_v2
+common_kwargs="\$pwncode/loop_pwn.py \
+        -c \\\$pwncode/analyze_psr.py \
+        --pwndata \\\$pwncode/pwndata/pwncat2_data_lande.yaml \
+        --pwnphase \\\$pwncode/pwndata/pwncat2_phase_lande.yaml  \
+        --modify \\\$pwncode/modify/modify_psr_lande.py \
+        --max-free 5 --localization-emin=1e4 --no-savedir --emin=1e4 --emax=1e5 --binsperdec=2"
+
+echo python $common_kwargs \
+    -o $pwndata/spectral/$version/analysis_no_plots \
+    $common_kwargs \
+    --no-plots 
+
+echo python $common_kwargs \
+        -o $pwndata/spectral/$version/analysis_plots \
+        --no-gtlike --no-cutoff --no-extension-upper-limits --no-upper-limits
+
+echo python $common_kwargs \
+        -o $pwndata/spectral/$version/analysis_fast \
+        --no-gtlike --no-cutoff --no-extension-upper-limits --no-upper-limits --no-plots
+
+
+
+
+# ----------------------------------------------------------------------------------------------------
+
+# major changes: ??? rerun
+version=v18
+common_kwargs="\$pwncode/loop_pwn.py \
+        -c \\\$pwncode/analyze_psr.py \
+        --pwndata \\\$pwncode/pwndata/pwncat2_data_lande.yaml \
+        --pwnphase \\\$pwncode/pwndata/pwncat2_phase_lande.yaml  \
+        --modify \\\$pwncode/modify/modify_psr_lande.py \
+        --max-free 5 --localization-emin=1e2 --no-savedir --emax=1e5"
+
+echo python $common_kwargs \
+    -o $pwndata/spectral/$version/analysis_no_plots \
+    --no-plots 
+
+echo python $common_kwargs \
+        -o $pwndata/spectral/$version/analysis_plots \
+        --no-gtlike --no-cutoff --no-extension-upper-limits --no-upper-limits
+
[…]

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/tables/all_energy_table.py

@@ -1,8 +1,9 @@
 from table_helper import get_pwnlist,get_results,write_latex,write_confluence,BestHypothesis
 from table_helper import PWNFormatter
 from lande.utilities.tools import OrderedDefaultDict
+from lande.utilities.table import get_confluence
 
-confluence=True
+confluence=get_confluence()
 
 format=PWNFormatter(confluence=confluence, precision=2)
 

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/tables/cutoff_table.py

@@ -1,8 +1,9 @@
 from table_helper import get_pwnlist,get_results,write_confluence,write_latex
 from table_helper import PWNFormatter
 from lande.utilities.tools import OrderedDefaultDict
+from lande.utilities.table import get_confluence
 
-confluence=True
+confluence=get_confluence()
 
 format=PWNFormatter(confluence=confluence, precision=2)
 
@@ -86,12 +87,13 @@ def cutoff_table(pwnlist):
           })
     else:
         write_latex(table,
-          filebase=filebase,
-          units={
-              flux_name:r'($10^{-9}$\ erg\,cm$^{-2}$\,s$^{-1}$)',
-              eflux_name:r'($10^{-12}$\ erg\,cm$^{-2}$\,s$^{-1}$)',
-              cutoff_name:r'(GeV)',
-          })
+                    filebase=filebase,
+                    preamble=r'\tabletypesize{\tiny}',
+                    units={
+                        flux_name:r'($10^{-9}$\ erg\,cm$^{-2}$\,s$^{-1}$)',
+                        eflux_name:r'($10^{-12}$\ erg\,cm$^{-2}$\,s$^{-1}$)',
+                        cutoff_name:r'(GeV)',
+                    })
 
 
 pwnlist=get_pwnlist()

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/tables/each_energy_table.py

@@ -2,8 +2,9 @@ from table_helper import get_pwnlist,get_results,write_latex, write_confluence, 
 from table_helper import PWNFormatter
 from lande.utilities.tools import OrderedDefaultDict
 from numpy import asarray as a
+from lande.utilities.table import get_confluence
 
-confluence=True
+confluence=get_confluence()
 
 format=PWNFormatter(confluence=confluence, precision=2)
 
@@ -95,6 +96,7 @@ def each_energy_table(pwnlist):
     else:
         write_latex(table,
                     filebase=filebase,
+                    preamble=r'\tabletypesize{\scriptsize}',
                     units={
                         flux1_name:r'($10^{-9}\ \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',
                         flux2_name:r'($10^{-9}\ \text{ph}\,\text{cm}^{-2}\,\text{s}^{-1}$)',

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/tables/localization_table.py

@@ -4,8 +4,9 @@ from table_helper import PWNFormatter
 from lande.utilities.tools import OrderedDefaultDict
 import numpy as np
 from skymaps import SkyDir
+from lande.utilities.table import get_confluence
 
-confluence=True
+confluence=get_confluence()
 
 format=PWNFormatter(confluence=confluence, precision=2)
 
@@ -63,7 +64,7 @@ def localization_table(pwnlist):
             l,b=pointlike['position']['gal']
 
             try:
-                poserr='%.2f' % pointlike['spatial_model']['lsigma']
+                poserr='%.2f' % pointlike['spatial_model']['ellipse']['lsigma']
             except:
                 poserr='None'
 

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/tables/phase_table.py

@@ -1,10 +1,19 @@
-from table_helper import get_pwnlist,get_results,table_name,write_latex,write_confluence
-from lande.utilities.tools import OrderedDefaultDict
-
 import yaml
 from os.path import join as j,expandvars
+import numbers
 
-confluence=True
+from uw.pulsar.phase_range import PhaseRange
+
+from lande.utilities.tools import OrderedDefaultDict
+from lande.utilities.table import get_confluence
+
+from table_helper import get_pwnlist,get_results,write_latex,write_confluence
+from table_helper import PWNFormatter
+
+
+confluence=get_confluence()
+
+format=PWNFormatter(confluence=confluence, precision=2)
 
 def all_energy_table(pwnlist):
 
@@ -19,13 +28,13 @@ def all_energy_table(pwnlist):
 
     for pwn in pwnlist:
         print pwn
-        table[psr_name].append(table_name(pwn,confluence))
+        table[psr_name].append(format.pwn(pwn))
 
-        phase=data[pwn]['phase']
+        phase=PhaseRange(data[pwn]['phase'])
         optimal_emin=data[pwn]['optimal_emin']
         optimal_radius=data[pwn]['optimal_radius']
 
-        table[phase_name].append('%.2f - %.2f' % tuple(phase))
+        table[phase_name].append(phase.pretty_format())
         table[optimal_emin_name].append('%.2f' % optimal_emin)
         table[optimal_radius_name].append('%.2f' % optimal_radius)
 

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/tables/table_helper.py

@@ -10,7 +10,7 @@ import asciitable
 
 from lande.utilities.table import latex_table,confluence_table,TableFormatter
 
-base='$pwndata/spectral/v12/'
+base='$pwndata/spectral/v18/'
 
 fitdir=expandvars(j(base,'analysis_no_plots/'))
 savedir=expandvars(j(base,'tables'))
@@ -33,7 +33,7 @@ def write_confluence(table, filebase, **kwargs):
     open('%s.confluence' % filebase,'w').write(t)
 
 
-def write_latex(table, filebase, **kwargs):
+def write_latex(table, filebase, preamble='',**kwargs):
 
     t = latex_table(table, **kwargs)
 
@@ -58,9 +58,10 @@ def write_latex(table, filebase, **kwargs):
 
         \begin{document}
         %s
+        %s
         \input{%s}
         %s
-        \end{document}""" % (header,filebase,footer)))
+        \end{document}""" % (header,preamble,filebase,footer)))
 
     os.system('pdflatex temp.tex')
     shutil.move('temp.pdf','%s.pdf' % filebase)
@@ -70,10 +71,12 @@ def write_latex(table, filebase, **kwargs):
 def get_results(pwn):
     f = j(fitdir,pwn,'results_%s.yaml' % pwn)
     if not os.path.exists(f): return None
+    print f
     results = yaml.load(open(f))
 
-    if not results.has_key('at_pulsar') or not results['at_pulsar'].has_key('gtlike'):
-        return None
+    for h in 'at_pulsar', 'point', 'extended':
+        if not results.has_key(h) or not results[h].has_key('gtlike'):
+            return None
     return results
 
 def get_sed(pwn,binning,hypothesis):

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/tables/variability_table.py

@@ -1,10 +1,13 @@
-from table_helper import get_pwnlist,get_results,write_latex,write_confluence
-from table_helper import PWNFormatter
-from lande.utilities.tools import OrderedDefaultDict
 from os.path import join,exists,expandvars
 import yaml
 
-confluence=True
+from table_helper import get_pwnlist,get_results,write_latex,write_confluence
+from table_helper import PWNFormatter
+
+from lande.utilities.tools import OrderedDefaultDict
+from lande.utilities.table import get_confluence
+
+confluence=get_confluence()
 
 format=PWNFormatter(confluence=confluence, precision=2)
 

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/variability/test_variability.py

@@ -4,9 +4,11 @@ np.seterr(all='ignore')
 
 from argparse import ArgumentParser
 
-import lande.fermi.likelihood.variability import VariabilityTester
+from lande.fermi.likelihood.variability import VariabilityTester
 
 from uw.like.roi_save import load
+
+from setup_pwn import load_pwn
 
 parser = ArgumentParser()
 parser.add_argument("--pwndata", required=True)
@@ -16,14 +18,13 @@ args=parser.parse_args()
 
 
 name=args.name
-roi = load('%s/%s/roi_point_%s.dat' % (args.analysis_dir,name,name))
+roi = load_pwn('%s/%s/roi_point_%s.dat' % (args.analysis_dir,name,name))
 
 roi.print_summary()
 roi.fit(use_gradient=False)
 roi.print_summary()
 
-v = VariabilityTester(roi,name,
-                                        nbins=36)
+v = VariabilityTester(roi,name, nbins=36)
 
 print v.todict()
 

### 2012-05-15 pwncatalog/PWNCAT2/code/lande/website/lande_website.py

@@ -13,6 +13,8 @@ import asciitable
 
 from table_helper import BestHypothesis
 
+from lande.utilities.website import t2t
+
 """
 var_version='v10/variability/v3/'
 spec_version='v12'
@@ -26,7 +28,7 @@ gtlike=False
 """
 
 var_version='none'
-spec_version='v17'
+spec_version='v18'
 gtlike=True
 
 variability_unix=expandvars('$pwndata/spectral/%s' % var_version)
@@ -78,20 +80,6 @@ def get_variability(pwn):
     f = join(variability_unix, pwn, 'results_%s.yaml' % pwn)
     if not os.path.exists(f): return None
     return yaml.load(open(f))
-
-
-
-
-def t2t(lines,name): 
-    """ create the HTML for a given t2t file. """
-    filename = join(website_unix,'%s.t2t' % name)
-    
-    temp=open(filename,'w')
-    temp.write(
-        '\n'.join(lines))
-    temp.close()
-        
-    os.system('txt2tags --target html --style color.css --css-sugar %s' % filename)
 
 
 class TableFormatter(object):
@@ -340,7 +328,7 @@ def build_each_page(pwn):
     title('gtlike SED (1bpd')
     get_sed_table(*['seds/sed_gtlike_1bpd_%s_%s.png' % (i,pwn) for i in all])
 
-    get_img_table(
+    get_sed_table(
         'plots/test_cutoff_%s_%s.png' % (hypothesis,pwn))
 
     # Add variability plot
@@ -382,7 +370,7 @@ def build_each_page(pwn):
 %s
 ```""" % yaml.dump(var))
 
-    t2t(index_t2t, pwn)
+    t2t(index_t2t, join(website_unix,'%s.t2t' % pwn))
 
 def build_all_pages():
     for pwn in pwnlist: build_each_page(pwn)

### 2012-05-15 pwncatalog/PWNCAT2/code/loop_pwn.py

@@ -14,48 +14,61 @@ python loop_pwn.py -c analyze.py \
 
 """
 import yaml
-from os.path import expandvars
-from os.path import join
+from os.path import expandvars, join, exists
 import os
 from textwrap import dedent
 from argparse import ArgumentParser
 
 parser = ArgumentParser()
-parser.add_argument("-c", "--command", required=True)
-group=parser.add_mutually_exclusive_group(required=True)
-group.add_argument("--pwndata")
-group.add_argument("--tevsources")
+parser.add_argument("--pwndata", required=True)
 parser.add_argument("-o", "--outdir", required=True)
+parser.add_argument("--clobber", default=False, action='store_true')
 args,remaining_args = parser.parse_known_args()
 
 outdir=args.outdir
 
-if args.pwndata is not None:
-    sources=yaml.load(open(expandvars(args.pwndata)))
-    flags = '--pwndata %s' % args.pwndata
-else:
-    sources=yaml.load(open(expandvars(args.tevsources)))
-    flags = '--tevsources %s' % args.tevsources
+sources=yaml.load(open(expandvars(args.pwndata)))
+flags = '--pwndata %s' % args.pwndata
 
-if os.path.exists(outdir):
-    raise Exception("outdir %s already exists" % outdir)
-os.makedirs(outdir)
+if exists(outdir): 
+    if not args.clobber:
+        raise Exception("outdir %s already exists" % outdir)
+    pass
+else:
+    os.makedirs(outdir)
 
 for name in sources.keys():
     print name
 
     folder=join(outdir,name)
-    os.makedirs(folder)
+
+    if not exists(folder): os.makedirs(folder)
 
     file=join(folder,'run_%s.sh' % name)
-
     temp=open(file,'w')
     temp.write(dedent("""\
-        python %s \\
+        python $pwncode/analyze_psr.py \\
             -n %s \\
             %s \\
-            %s""" % (args.command,name, flags,' '.join(remaining_args))))
+            %s""" % (name, flags,' '.join(remaining_args))))
+
+    for hypothesis in ['at_pulsar', 'point', 'extended']:
+        for followup in ['plots','gtlike','variability']:
+            if hypothesis != 'point' and followup == 'variability':
+                continue
+
+            file=join(folder,'followup_%s_%s_%s.sh' % (name,hypothesis,followup))
+            temp=open(file,'w')
+            temp.write(dedent("""\
[…]

### 2012-05-15 pwncatalog/PWNCAT2/code/followup_psr.py
update

@@ -1,0 +1,65 @@
+#!/usr/bin/env python
+
+from analyze_psr import get_args()
+from setup_pwn import load_pwn
+
+
+parser = ArgumentParser()
+parser.add_argument("--hypothesis", required=True, choice=['at_pulsar', 'point', 'extended'])
+parser.add_argument("--followup", required=True, choice=['plots', 'gtlike', 'variability'])
+group=parser.parse_known_args(required=True)
+
+hypothesis = args.hypothesis
+followup = args.followup
+
+args = get_args()
+do_upper_limits = not args.no_upper_limits
+do_cutoff = not args.no_cutoff
+
+name = args.name
+
+gtlike_kwargs = dict(name=name, seds = do_seds)
+
+roi = load_pwn('roi_%s_%s.dat' % (hypothesis,name))
+
+
+if followup == 'gtlike':
+    results = dict(hypothesis=dict())
+    ul = (hypothesis == 'at_pulsar') and do_upper_limits
+    r[hypothesis]['gtlike']=gtlike_analysis(roi, hypothesis=hypothesis, upper_limit=ul, cutoff=do_cutoff, **gtlike_kwargs)
+
+    save_results(results,name, hypothesis=hypothesis, followup=followup)
+
+elif followup == 'plots':
+
+    if not os.path.exists('plots'): os.makedirs('plots')
+
+    pwndata=yaml.load(open(args.pwndata))[name]
+    ft1 = pwndata['ft1']
+    pulsar_position = SkyDir(*pwndata['cel'])
+
+    print 'Making phaseogram'
+
+    plot_kwargs = dict(ft1=ft1, skydir=pulsar_position, phase_range=phase, 
+                       emin=pwnphase['optimal_emin'], emax=pwnphase['emax'], radius=pwnphase['optimal_radius'])
+    plot_phaseogram(title='Phaseogram for %s' % name, filename='plots/phaseogram_%s.png' % name, **plot_kwargs)
+    plot_phase_vs_time(title='Phase vs Time for %s' % name, filename='plots/phase_vs_time_%s.png' % name, **plot_kwargs)
+
+
+    new_sources = roi.extra['new_sources']
+    overlay_kwargs = dict(pulsar_position=pulsar_position, new_sources=new_sources)
+    if do_plots: plots(roi, name, hypothesis, **overlay_kwargs)
+
+elif followup == 'variability':
+
+    roi.print_summary()
+    roi.fit(use_gradient=False)
[…]

### 2012-05-15 pwncatalog/PWNCAT2/code/merge_psr.py

@@ -1,0 +1,2 @@
+pass
+# soon, code will exist to merge results files...

### 2012-05-15 pwncatalog/PWNCAT2/mc/extul/extul.py
update

@@ -22,7 +22,7 @@ from uw.like.pointspec_helpers import PointSource
 
 from lande.utilities.tools import savedict
 from lande.fermi.likelihood.diffuse import get_sreekumar
-from lande.fermi.likelihood.catalogs import get_2fgl
+from lande.fermi.data.catalogs import dict2fgl
 from lande.fermi.likelihood.tools import force_gradient
 from lande.fermi.likelihood.save import sourcedict, spectrum_to_dict, pointlike_model_to_flux
 
@@ -65,9 +65,8 @@ skydir_mc = SkyDir()
 
 bg = get_sreekumar()
 
-cat = get_2fgl()
-ft2 = cat['ft2']
-ltcube = cat['ltcube']
+ft2 = dict2fgl['ft2']
+ltcube = dict2fgl['ltcube']
 
 results = []
 
@@ -148,6 +147,7 @@ for extension_mc in extensions:
         binfile  = binfile)
 
     sa=SpectralAnalysis(ds,
+        binsperdec  = 8,
         irf         = irf,
         roi_dir     = skydir_mc,
         maxROI      = 10,
@@ -175,6 +175,8 @@ for extension_mc in extensions:
 
     roi.fit()
     roi.print_summary()
+
+    r['bin_edges'] = roi.bin_edges
 
     r['point'] = sourcedict(roi,point)
 

### 2012-05-15 pwncatalog/PWNCAT2/mc/extul/loop.py

@@ -63,10 +63,12 @@ random.seed(0)
 #      [  3,  2.8e-7,  2.8e-7, 0, 0.5,   'bright'],
 #                                       ]:
 
-# v10 & v11 & v12
+# v10 & v11 & & v12 & v13
 #basedir =  expandvars('$pwndata/monte_carlo/extul/v10/')
 #basedir =  expandvars('$pwndata/monte_carlo/extul/v11/')
-basedir =  expandvars('$extuldata/v12/')
+#basedir =  expandvars('$extuldata/v12/')
+#  - note primiary difference in v12: 8bins per decade instead of 4
+basedir =  expandvars('$extuldata/v13/')
 num=1000
 for index_mc,min_flux,max_flux,min_extension, max_extension, type in \
      [[1.5,   1e-9,  1.8e-8, 0, 2.0,  'dim'], 

### 2012-05-15 extended_catalog/external_review_reply/replies_to_review_comments.tex
new draft

@@
 
-There is also a new section 3.3 (Extended Source Simulations Over a 244 Structured Background). 
+There is also a new section 3.3 (Extended Source Simulations Over a Structured Background). 
 In this section, we address your question by performing
@@
 Thanks for the suggestion.  In addition to the above changes, we have
-fixed a few bibliographical entries.
+replaced a few references to ``catalog sources'' with ``2FGL sources''
+for clarification. We have also fixed a few bibliographical entries. 
 \end{reply}

### 2012-05-15 extended_catalog/paper/extended_search.tex
new draft

@@
 
-We performed a second simulation to show that the theoretical distribution
+We performed a second set of simulation to show that the theoretical distribution
 for \tsext is still preserved when the point-like sources are present over
@@
 Galactic diffuse and isotropic background models used in 2FGL.  In our
-simulations, we selected our sources to have a random position on the sky
-such that the absolute value of the galactic latitude of the source was
-less than 5\degree. This probes the most structured areas of the 
-Galactic background.
+simulations, we selected our sources to have random positions on the sky
+such that they were within 5\degree of the Galactic plane. This probes the 
+brightest and most strongly contrasting areas of the Galactic background.
 
@@
 this test only in the 1 \gev to 100 \gev energy range. 
-The fluxes were selected so that $\ts\sim50$. We do not
+As described below, The fluxes were selected so that $\ts\sim50$. We do not
 expect to be able to spatially resolve sources much dimmer than this
-and sources much brighter are less likely to be affected by the 
+and the results for sources much brighter are less likely to be affected by the 
 structured background.
 
-Because the Galactic diffuse emission is highly structure, the point-source
-sensitivity can vary significantly across the galactic plane.
+Because the Galactic diffuse emission is highly structure with
+strong gradients, the point-source
+sensitivity can vary significantly across the Galactic plane.
 To account for this, we scaled the flux (for a given spectral index)
@@
 flux of the source from 100 \mev to 100 \gev, $F(\text{GC})$
-is the same quantity if the source was at the galactic center, $B$
+is the same quantity if the source was at the Galactic center, $B$
 is the integral of the Galactic diffuse and isotropic emission
 from 1 \gev to 100 \gev at the position of the source, and $B(\text{GC})$ is the same quantity
-if the source was at the galactic center.  For the four spectral models,
+if the source was at the Galactic center.  For the four spectral models,
 Table~\ref{ts_ext_num_sims} lists $F(\text{GC})$ and the average value of \ts.
@@
 theory.  For the highest values of \tsext, there is possibly
-a small discrepancy, but limited statistics makes this hard to quantify.
-Therefore, we are confident we can used \tsext as a robust measure of
+a small discrepancy, but the discrepancy is not statistically significant.
+Therefore, we are confident we can use \tsext as a robust measure of
 statistical significance when testing LAT-detected sources for extension.
@@
 
-We also performed a Monte Carlo study to show that incorrectly modeling the
-spatial extension of an extended source does not substantially bias
-the spectral fit of the source, although it does alter the value of the \ts.
+We also performed a Monte Carlo study that (a) shows that we obtain
+an unbiased fit of an extended source with a complicated spatial shape so long as
+the source is correctly modeled and (b) quantifies the biases 
+introduced by incorrectly modeling its spatial structure.
 To assess this, we simulated the spatially extended ring-type SNR W44.
 We selected W44 because it is the most significant extended source detected by the LAT 
-that has a non-radially symmetric photon-distribution \citep{w44}.
+that has a non-radially symmetric photon distribution \citep{w44}.
 
@@
 of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100
-\gev and a spectral index of 2.66.
-The flux and spectral index of this source
-was taken from our analysis of W44 which will be described in Section~\ref{validate_known}.
+\gev and a spectral index of 2.66 (see Section~\ref{validate_known}).
 
@@
 a semi-minor axis of 0\fdg19, a position angle of $147\degree$
-measured east of celestial north, and the ring's inner radius is 0.75 times
+measured East of celestial North, and the ring's inner radius is 75\% of
 the outer radius.
@@
 top of and analyzed assuming the presence of the standard Galactic diffuse and
-isotropic background model used in 2FGL.  The simulations were
-in the 1 \gev to 100 \gev energy range and
-W44 was simulated over the two-year time range used in 2FGL. 
-In the simulations, we disabled the inherent energy dispersion of photons
-by the LAT to isolate the effects due to changing the assumed spatial model. 
-The bias caused by ignoring energy dispersion 
-will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.
-In total, we performed 985 statistically independent simulations.
+isotropic background model used in 2FGL.  
+We simulated the gamma-ray emission in the 1 \gev to 100 \gev
+energy range for the 2-year interval of the 2FGL catalog.
+In the simulations, 
+we did not include the finite energy resolution of the LAT
+to isolate any effects due to changing the assumed spatial model. 
+The fitting code we use also ignores this energy dispersion and the
+potential bias introduced by this will be discussed in an upcoming paper
+by the LAT collaboration \citep{lat_on_orbit_psf}.
+In total, we performed 985 independent simulations.
 
 The simulated sources were fit using a point-like spatial model,
-a radially-symmetric uniform Gaussian and disk spatial model, 
+a radially-symmetric Gaussian spatial model, a uniform disk spatial model, 
 an elliptical disk spatial model, and finally with an elliptical
@@
 
-Figure~\ref{ts_comparison_w44sim}a shows that the simulations of W44
-are very significant ($\ts\sim3500$) when fit as point-like sources.
-Figure~\ref{ts_comparison_w44sim}b shows that the simulations are
-highly extended ($\tsext\sim250$) when fit with any of the extended
-spatial models.  On average \tsext is somewhat larger when fitting
+Figure~\ref{ts_comparison_w44sim}a 
+shows that
+the significance of W44 in the simulations is very great ($\ts\sim3500$) 
+for a model with a point-like source hypothesis.
+Figure~\ref{ts_comparison_w44sim}b shows that 
+the significance of the spatial extension is also very great
+($\tsext\sim250$).  
+On average \tsext is somewhat larger when fitting
 the sources with more accurate spatial models.  This shows that
@@
 
-Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b clearly show that
-no significant bias is introduced by modeling the source as extended
-but with an inaccurate spatial model, while a point-like source modeling
-results in a $\sim10\%$ and $\sim5\%$ bias in the fit flux and index,
+Figure~\ref{bias_w44sim} shows that there are no systematic biases in the
+distribution of best fit (a) flux (b) spectral index (c) \rsixeight
+(d) elliptical eccentricity (e) elliptical orientation angle and (f) inner
+ring fraction when the simulated extended sources were fit with the
+elliptical ring spatial model. For the elliptical spatial models, \rsixeight
+is computed by numeric integration.
+Figures~\ref{bias_w44sim}a and~\ref{bias_w44sim}b show that
+no significant bias is introduced by modeling the source with the 
+other extended spatial models, while modeling the source as point-like
+results in $\sim10\%$ and $\sim5\%$ biases in the fit flux and index,
 respectively.  
 Furthermore, Figure~\ref{bias_w44sim}c shows that the \rsixeight estimate of
-the extension size is very mildly biased ($\sim10\%$) toward higher values
-when inaccurate spatial models are used, and thus represent a reasonable
-measurement of the true 68\% containment radius for the source.
-
-For completeness, Figure~\ref{bias_w44sim}d and Figure~\ref{bias_w44sim}e 
-shows that there are 
-no systematic biases in the
-distribution of best
-fit elliptical eccentricities and orientation angles
-when the sources were fit with elliptical
-spatial models.  
-The eccentricity is defined as
-$\sqrt{1-b^2/a^2}$, where $a$ is the length of the semi-major axis and
-$b$ is the length of the semi-minor axis.  
-Finally, Figure~\ref{bias_w44sim}f shows that the distribution of best fit
-inner ring fractions is unbiased when the sources were fit with the elliptical
-ring spatial model.
+the extension is very mildly biased ($\sim10\%$) toward higher values
+when inaccurate spatial models are used, and thus \rsixeight for any of
+these spatial models can be used as a reasonable measurement of the true
+68\% containment radius for the source.
 }
@@
 an alternative Bayesian formulation for this test, but it is difficult to apply
-to LAT data because it contains a term including the number of data points. For LAT data,
-this is not a clear concept because there are many pixels included in an analysis that contribute only
- marginally to the analysis of a given source.
+to LAT data because it contains a term including the number of data points. 
+For studying gamma-ray sources in LAT data, we analyze relatively large
+regions of the sky to better define the contributions from diffuse
+backgrounds and nearby point sources. This is important for accurately
+evaluating source locations and fluxes but the fraction of data directly
+relevant to the evaluation of the parameters for the source of interest
+is relatively small.
 
@@
 
-Because the two point-like source hypotheses has
+Because the two point-like source hypothesis has
 three more parameters than the single extended source hypothesis (two spatial
@@
 if it has a high probability of association $P\ge 80\%$, if it is the
-only AGN associated with the catalog source, and if 
+only AGN associated with the 2FGL source, and if 
 no analysis flags have been set for the source
@@
 analysis. Source confusion may look like a spatially extended source
-and flagged catalog sources may correlate with unmodeled structure in
+and flagged 2FGL sources may correlate with unmodeled structure in
 the diffuse emission.
@@
 Ideally, we would apply a completely blind and uniform search that
-tests the extension of each catalog source in the presence of all other
+tests the extension of each 2FGL source in the presence of all other
 2FGL sources to find a complete list of all spatially extended sources.
@@
 of the background model that were performed.
-\newtext{In Table~\ref{fake_2fgl_sources}, we summarize the sources that were 
-included in 2FGL to account for residuals induced by not modeling the extensions of
-nearby extended sources.}
+\newtext{In Table~\ref{fake_2fgl_sources}, we summarize the sources in
+the 2FGL catalog that we have concluded here correspond to residuals
+induced by not modeling the extensions of nearby extended sources.}
 
@@
 coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
-a counts map of this source. There are two nearby catalog sources 2FGL\,J0823.4$-$4305
+a counts map of this source. There are two nearby 2FGL sources 2FGL\,J0823.4$-$4305
 and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
@@
 There are three
-point-like catalog sources 2FGL\,J0848.5$-$4535,
+point-like 2FGL sources 2FGL\,J0848.5$-$4535,
 2FGL\,J0853.5$-$4711, and
@@
 of 2FGL\,J0851.7$-$4635, we iteratively relocalized the positions
-of the nearby point-like catalog source 2FGL\,J0854.7$-$4501 to
+of the nearby point-like 2FGL source 2FGL\,J0854.7$-$4501 to
 $(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies.
@@
 sources.  \newtext{Because $\tsinc=35.1$ is less than $\tsext=46.5$, we conclude that
-this emission does not originate from two nearby point-like sources.}
+this emission does not originate from two closely-spaced point-like sources.}
 
@@
     when fitting W44 as a point-like source and (b) is the
-    distribution of \tsext when fitting the source with a uniform disk and Gaussian
+    distribution of \tsext when fitting the source with a uniform disk or a 
+    radially-symmetric Gaussian
     spatial model. (c) is the distribution of the change in TS when
@@
 \tablecomments{
-\newtext{
-For each new extended source, we list nearby catalog
-sources that were included in 2FGL to account for residuals induced
-by not modeling the extension of the extended source.
-}
+\newtext{For each new extended source, we list nearby 2FGL
+soruces that we have concluded here correspond to residuals induced by not
+modeling the extensions of nearby extended sources.}
 }

### 2012-05-17 extended_catalog/paper/extended_search.tex
new draft v12.0

@@
 
-We also performed a Monte Carlo study that (a) shows that we obtain
-an unbiased fit of an extended source with a complicated spatial shape so long as
-the source is correctly modeled and (b) quantifies the biases 
-introduced by incorrectly modeling its spatial structure.
+We also performed a Monte Carlo study to show that incorrectly modeling the
+spatial extension of an extended source does not substantially bias
+the spectral fit of the source, although it does alter the value of the \ts.
 To assess this, we simulated the spatially extended ring-type SNR W44.
@@
 
-Figure~\ref{bias_w44sim} shows that there are no systematic biases in the
-distribution of best fit (a) flux (b) spectral index (c) \rsixeight
-(d) elliptical eccentricity (e) elliptical orientation angle and (f) inner
-ring fraction when the simulated extended sources were fit with the
-elliptical ring spatial model. For the elliptical spatial models, \rsixeight
-is computed by numeric integration.
-Figures~\ref{bias_w44sim}a and~\ref{bias_w44sim}b show that
-no significant bias is introduced by modeling the source with the 
-other extended spatial models, while modeling the source as point-like
-results in $\sim10\%$ and $\sim5\%$ biases in the fit flux and index,
+Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b clearly show that
+no significant bias is introduced by modeling the source as extended
+but with an inaccurate spatial model, while a point-like source modeling
+results in a $\sim10\%$ and $\sim5\%$ bias in the fit flux and index,
 respectively.  
 Furthermore, Figure~\ref{bias_w44sim}c shows that the \rsixeight estimate of
-the extension is very mildly biased ($\sim10\%$) toward higher values
-when inaccurate spatial models are used, and thus \rsixeight for any of
-these spatial models can be used as a reasonable measurement of the true
-68\% containment radius for the source.
+the extension size is very mildly biased ($\sim10\%$) toward higher values
+when inaccurate spatial models are used, and thus represent a reasonable
+measurement of the true 68\% containment radius for the source.
+For the elliptical spatial models, \rsixeight is computed by numeric integration.
+
 }
@@
 
-Because the two point-like source hypothesis has
-three more parameters than the single extended source hypothesis (two spatial
-parameters and two spectral parameters compared to one extension parameter),
-we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing that
-$\aic_\text{ext} < \aic_\text{2pts} - 6$.
-Thus our criterion based on the \ts value is equivalent to requesting
-that the \aic-based empirical support for the two-point-like-source model be
-``considerably less'' than for the extended source model, following the
-classification by \cite{aic_stats_book}.
+The two point-like sources hypothesis has three more parameters than
+the single extended source hypothesis (two more spatial parameters and
+two more spectral parameters compared to one extension parameter), so the
+comparison $\aic_\text{ext} < \aic_\text{2pts}$  is formally equivalent to
+$\tsext + 6 > \tsinc$.  Our criterion for accepting extension ($\tsext > \tsinc$) 
+is thus equivalent to requesting that the AIC-based empirical
+support for the two point-like sources model be ``considerably less''
+than for the extended source model, following the classification by
+\cite{aic_stats_book}.
 }
@@
     The plots show the distribution of 
-    best fit (a) flux (b) spectral index (c) 68\% containment
-    radius (d) eccentricity (e) elliptical orientation angle
-    and (f) inner ring fraction. The dashed vertical lines represent
+    best fit (a) flux (b) spectral index and (c) 68\% containment
+    radius. The dashed vertical lines represent
     the simulated values of the parameters.

### 2012-05-17 extended_catalog/paper/extended_search.tex
upew draft v13

@@
 \subsection{Point-like Source Simulations Over a Uniform Background}
-
-}
-
 \label{monte_carlo_validation}
+
+}
 
@@
 \subsection{\newtext{Point-like Source Simulations Over a Structured Background}}
-
-We performed a second set of simulation to show that the theoretical distribution
+\label{validation_over_plane}
+
+We performed a second set of simulations to show that the theoretical distribution
 for \tsext is still preserved when the point-like sources are present over
@@
 this test only in the 1 \gev to 100 \gev energy range. 
-As described below, The fluxes were selected so that $\ts\sim50$. We do not
+As described below, the fluxes were selected so that $\ts\sim50$. We do not
 expect to be able to spatially resolve sources much dimmer than this
@@
 
-Because the Galactic diffuse emission is highly structure with
+Because the Galactic diffuse emission is highly structured with
 strong gradients, the point-source
@@
 We used a simulation setup similar to that described in
-Section~\ref{monte_carlo_validation}, but the sources were simulated on
-top of and analyzed assuming the presence of the standard Galactic diffuse and
-isotropic background model used in 2FGL.  
-We simulated the gamma-ray emission in the 1 \gev to 100 \gev
-energy range for the 2-year interval of the 2FGL catalog.
+Section~\ref{validation_over_plane}, but the simulations
+were over the 2-year interval of the 2FGL catalog.
 In the simulations, 
@@
 shows that
-the significance of W44 in the simulations is very great ($\ts\sim3500$) 
+the significance of W44 in the simulations is very large ($\ts\sim3500$) 
 for a model with a point-like source hypothesis.
 Figure~\ref{ts_comparison_w44sim}b shows that 
-the significance of the spatial extension is also very great
+the significance of the spatial extension is also large
 ($\tsext\sim250$).  
@@
 but with an inaccurate spatial model, while a point-like source modeling
-results in a $\sim10\%$ and $\sim5\%$ bias in the fit flux and index,
+results in a $\sim10\%$ and $\sim0.125$ bias in the fit flux and index,
 respectively.  
@@
 the extension size is very mildly biased ($\sim10\%$) toward higher values
-when inaccurate spatial models are used, and thus represent a reasonable
+when inaccurate spatial models are used, and thus represents a reasonable
 measurement of the true 68\% containment radius for the source.

### 2012-05-17 extended_catalog/monte_carlo/w44sim/plots/plot_bias.py

@@ -14,7 +14,6 @@ from lande.utilities.plotting import label_axes
 set_latex_defaults()
 bw=get_bw()
 
-#savedir = expandvars(join('$w44simdata/','v7', 'merged.hdf5'))
 savedir = expandvars(join('$w44simdata/','v33', 'merged.hdf5'))
 results = h5py.File(savedir, 'r')
 
@@ -66,39 +65,43 @@ def plot(axes, quantity, scale=1):
     axes.set_ylabel('Number')
     axes.set_ylim(ymin=0)
 
+#fig=P.figure(None, figsize=(6,6))
 fig=P.figure(None, figsize=(6,6))
 
 
-axes=fig.add_subplot(321)
+#axes=fig.add_subplot(321)
+axes=fig.add_subplot(221)
 plot(axes, 'flux', scale=1e-8)
 axes.set_xlabel(r'Flux ($10^{-8}$ ph$\;$cm$^{-1}$s$^{-1}$)')
 
-axes=fig.add_subplot(322)
+#axes=fig.add_subplot(322)
+axes=fig.add_subplot(222)
 plot(axes, 'index')
 axes.set_xlabel('Spectral Index')
 
-axes=fig.add_subplot(323)
+#axes=fig.add_subplot(323)
+axes=fig.add_subplot(223)
 plot(axes,'r68')
 axes.set_xlabel('r68 (deg)')
 
-axes=fig.add_subplot(324)
-plot(axes,'eccentricity')
-axes.set_xlabel('Eccentricity')
+#axes=fig.add_subplot(324)
+#plot(axes,'eccentricity')
+#axes.set_xlabel('Eccentricity')
 
 
-axes=fig.add_subplot(325)
-plot(axes,'angle')
-axes.set_xlabel('Ellipse Angle (deg)')
+#axes=fig.add_subplot(325)
+#plot(axes,'angle')
+#axes.set_xlabel('Ellipse Angle (deg)')
 
 
-axes=fig.add_subplot(326)
-plot(axes,'fraction')
-axes.set_xlabel('Ring Fraction')
+#axes=fig.add_subplot(326)
+#plot(axes,'fraction')
+#axes.set_xlabel('Ring Fraction')
 
 
-prop = matplotlib.font_manager.FontProperties(size=8)
+prop = matplotlib.font_manager.FontProperties(size=6)
 plots=[Line2D([0],[0],color=i) for i in all_colors]
[…]

### 2012-05-22 extended_catalog/paper/extended_search.tex
new draft v15

@@
 studies of individual sources so we expect that a systematic scan of
-all LAT detected sources could uncover additional spatially extended
+all LAT-detected sources could uncover additional spatially extended
 sources.
@@
 sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
-\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
+\citep{hess_plane_survey}.  Within our Galaxy very few
 sources detected at \tev energies, most notably the $\gamma$-ray binaries
@@
 The possible counterparts of many of these sources can be spatially resolved
-when observed at other frequencies but detecting the spatial extension
+when observed at other frequencies. But detecting the spatial extension
 of these sources at \gev energies is difficult because the size of the
@@
 help to associate a LAT source to an otherwise confused counterpart.
-Furthermore, $\gamma$-rays emission from dark matter
+Furthermore, $\gamma$-ray emission from dark matter
 annihilation has been predicted to be detectable by the LAT.
@@
 \newtext{
-In Section~\ref{monte_carlo_validation}, we demonstrate
+In Section~\ref{validate_ts}, we demonstrate
 that this method can be used to test the statistical significance of the
-extension of a LAT source and in Section~\ref{bias_wrong_spatial_model}
-we assess the expected level of bias 
+extension of a LAT source and we assess the expected level of bias 
 introduced by assuming an incorrect spatial model.
@@
 
-This type of analysis is not feasible using the standard LAT likelihood
+This type of analysis is unwieldy using the standard LAT likelihood
 analysis tool \gtlike\footnote{\gtlike is distributed publicly by the
@@
 
-\pointlike is important for LAT analyses that require many iterations
+\pointlike is important for analyses of LAT data that require many iterations
 such as source localization and extension fitting.  On the other hand,
@@
 LAT PSF, their PDFs are similar for a source that has a 0\fdg5 radius
-typical of LAT detected extended sources.  To allow a valid comparison
+typical of LAT-detected extended sources.  To allow a valid comparison
 between the Gaussian and the uniform disk models,
@@
 \section{Validation of the \ts Distribution}
+\label{validate_ts}
 
@@
 For each set of spectral parameters, $\sim20,000$ statistically independent
-simulations were performed. For dimmer spectral models, many of the
+simulations were performed. For lower-flux spectral models, many of the
 simulations left the source insignificant ($\ts<25$)
@@
 As described below, the fluxes were selected so that $\ts\sim50$. We do not
-expect to be able to spatially resolve sources much dimmer than this
-and the results for sources much brighter are less likely to be affected by the 
+expect to be able to spatially resolve sources 
+at lower fluxes than these, and the results for much brighter sources
+are less likely to be affected by the 
 structured background.
@@
 because the PSF changes little from 10 \gev to 100 \gev.
-Overlaid on Figure~\ref{all_sensitivity} are the LAT detected extended
+Overlaid on Figure~\ref{all_sensitivity} are the LAT-detected extended
 sources that will be discussed in Sections~\ref{validate_known} and
@@
 angular distances comparable to or smaller than the size of the LAT PSF. 
-To assess the plausibility of source confusion for situations
-in which $\tsext\ge16$, we developed an algorithm in \pointlike to
-simultaneously fit the positions and spectra of two point-like sources.
+\newtext{ To assess the plausibility of source confusion for sources with
+$\tsext\ge16$, we developed an algorithm to test if a region contains
+two point-like sources.  The algorithm works by simultaneously fitting
+in \pointlike the positions and spectra of the two point-like sources.
+To help with convergence, it begins by dividing the source into two
+spatially coincident point-like sources and then fitting the sum and
+difference of the positions of the two sources without any limitations
+on the fit parameters.}
 
@@
 to LAT data because it contains a term including the number of data points. 
-For studying gamma-ray sources in LAT data, we analyze relatively large
+For studying $\gamma$-ray sources in LAT data, we analyze relatively large
 regions of the sky to better define the contributions from diffuse
@@
 
-From this Monte Carlo study, we can see the limits of a LAT analysis
-of spatially extended sources.  Section~\ref{monte_carlo_validation}
+From this Monte Carlo study, we can see the limits of an analysis with
+LAT data of spatially extended sources.  Section~\ref{monte_carlo_validation}
 showed that we have a statistical test that finds when a LAT source is
@@
 extended sources that could be resolved with deeper observations of the
-region.  There is nothing about this conclusion unique to LAT analysis,
+region.  There is nothing about this conclusion unique to analyzing LAT data,
 but the broad PSF of the LAT and the density of sources expected to be
 \gev emitters in the Galactic plane makes this issue more significant
-for LAT analysis.  When possible, multiwavelength information should be
+for analyses of LAT data.  When possible, multiwavelength information should be
 used to help select the best model of the sky.
@@
 
-For all following LAT analyses, we used the same two-year dataset
+For all following analyses of LAT data, we used the same two-year dataset
 that was used in the 2FGL catalog spanning from 2008 August 4 to 2010 August 1. We
@@
 these sources a uniform disk spatial model does not well describe the
-observed extended emission and so the dedicated LAT 
-publications provide better models of these sources.
+observed extended emission and so the dedicated 
+publications by the LAT collaboration provide better models of these sources.
 
@@
 systematic error on the extension of a source.  The same approach was used
-in \cite{ic443}.  we believe that our parameterization
+in \cite{ic443}.  We believe that our parameterization
 of the PSF from bright AGN is substantially better than the Monte Carlo
@@
 The particular GALPROP model that was used as input is described in
-the LAT analysis of the isotropic diffuse
-emission \citep{isotropic_lat}.  
+the analysis of the isotropic diffuse
+emission with LAT data \citep{isotropic_lat}.  
 The intensities of various components
@@
 spatial distribution predicted by
-the model.  We distinguished contributions from cosmic-ray interactions with the
+the model.  
+We considered separate contributions from
+cosmic-ray interactions with the
 molecular hydrogen, the atomic and ionized hydrogen, residual gas traced
@@
 for sources in crowded regions the systematic
-errors quoted in this paper may not be the full systematics of this
-analysis.
+errors quoted in this paper 
+may not represent the full set of systematic errors associated with this analysis.
 
@@
 
-But this is infeasible in the Galactic plane where we most likely expect
-to discover new spatially extended sources.  In the Galactic plane,
+But this is infeasible in the Galactic plane where we 
+are most likely to discover new spatially extended sources.  In the Galactic plane,
 this analysis is challenged by our imperfect model of the diffuse
@@
 in the region close to an extended source could be biased by not correctly
-modeling the extension of the source.  Since 2FGL produced a
+modeling the extension of the source.  The 2FGL catalog contains a
 list of sources significant at energies above 100 \mev whereas we are
-most sensitive to spatial extension at higher energies,
-we also expect that at higher energies our analysis would be complicated
+most sensitive to spatial extension at higher energies.
+We therefore expect that at higher energies our analysis would be complicated
 by 2FGL sources no longer significant and by 2FGL
@@
 As was shown in Section~\ref{extension_sensitivity}, little sensitivity is gained by
-using photons with energies below 1 \gev. On the other hand,
+using photons with energies below 1 \gev. In addition,
 the broad PSF at low energy makes the analysis more susceptible to systematic
@@
 and by uncertainties in our modeling of the Galactic diffuse emission. 
-For that reason,
+For these reasons,
 we performed our search using only photons with energies between 1 \gev
@@
 that the spatially extended model for IC~443 is a significantly better
-description of the observed photons and that there is no significant
+description of the observed photons and that there is no $\ts>25$
 residual in the region after modeling the source as being spatially extended.
@@
 When deciding
-which background sources to keep and which to remove, we used as much as possible
+which background sources to keep and which to remove, we used 
 multiwavelength information about possibly extended source counterparts
@@
 second measure of \tsext.  We only consider a source to be extended when
-both \pointlike and \gtlike agree that $\tsext>16$. 
-We further required that $\tsext>16$ using the 
+both \pointlike and \gtlike agree that $\tsext\ge16$. 
+We further required that $\tsext\ge16$ using the 
 alternative approach to modeling the diffuse emission
@@
 No molecular clouds have been observed directly adjacent to Puppis A
-\citep{co_eastern_puppis_a}, similar to the LAT detected Cygnus Loop SNR
+\citep{co_eastern_puppis_a}, similar to the LAT-detected Cygnus Loop SNR
 \citep{cygnus_loop_lat}.  The luminosity of Puppis A is also smaller
@@
 well the \tev morphology of Vela Jr.  While fitting the extension
-of 2FGL\,J0851.7$-$4635, we iteratively relocalized the positions
+of 2FGL\,J0851.7$-$4635, we iteratively relocalized the position
 of the nearby point-like 2FGL source 2FGL\,J0854.7$-$4501 to
@@
 with a radially-symmetric Gaussian surface brightness profile with
-$\sigma=0\fdg136\pm0\fdg008$.  This \tev size corresponds to a 68\%
+$\sigma=0\fdg136\pm0\fdg008$ \citep{hess_plane_survey}. This \tev size corresponds to a 68\%
 containment radius of $\rsixeight=0\fdg21\pm0\fdg01$, comparable to the
@@
 No other promising counterparts were observed at X-ray and soft
-gamma-ray energies by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
+$\gamma$-ray energies by \suzaku \citep{suzakzu_HESS_J1616-508}, \swiftxrt,
 IBIS/ISGRBI, BeppoSAX and \xmmnewton \citep{integral_HESS_J1616-508}.
@@
 and their locations are shown in Figure~\ref{allsky_extended_sources}.
-Most of the LAT detected extended sources are expected to be of Galactic
+Most of the LAT-detected extended sources are expected to be of Galactic
 origin as the distances of extragalactic sources (with the exception of
@@
 
-Many of the \tev detected extended sources now seen at \gev energies
+Many of the \tev-detected extended sources now seen at \gev energies
 are currently unidentified and further multiwavelength follow-up
 observations will be necessary to understand these particle accelerators.
-But extending the spectra of these \tev sources towards lower energies
+Extending the spectra of these \tev sources towards lower energies
 with LAT observations may help to determine the origin and nature of
@@
     photons with energies between
-    1 \gev and 100 \gev.  Plots (c) and (d) use
+    1 \gev and 100 \gev.  Plots (c) and (d) include
     only photons which converted in the front part of the tracker and
-    have an improved angular resolution.
+    have an improved angular resolution \citep{atwood_fermi}.
     }
@@
     (colored red in the online version).
-    The dash-dot-doted and the dot-doted lines are the brightness profile
+    The dash-dot-dotted and the dot-dotted lines are the brightness profile
     of a uniform disk with $\rsixeight=0\fdg5$ and the convolution
@@
     \caption{
-    The same plot as Figure~\ref{ts_ext_mc_10000} but fitting in the 10 \gev to 100 \gev energy 
+    The same plot as Figure~\ref{ts_ext_mc_1000} but fitting in the 10 \gev to 100 \gev energy 
     range.
@@
     \newtext{
-    The same plot as Figure~\ref{ts_ext_mc_1000}, but fitting sources
-    simulated on top of the Galactic diffuse and isotropic background.
+    Cumulative distribution of \tsext
+    for sources simulated on top of the Galactic diffuse and isotropic background.
     }
@@
     \caption{
-    \newtext{The distribution of \ts values when fitting statistically
+    \newtext{The distribution of \ts values when fitting 985 statistically
     independent simulations of W44. (a) is the distribution of \ts values
@@
     indices.  The lines with no markers correspond to the detection
-    threshold using photons with energies between 100 \mev and 100 \gev
+    threshold using photons with energies between 100 \mev and 100 \gev,
     while the lines with star-shaped markers correspond to the threshold
@@
     10 \gev and 100 \gev.  The flux is integrated only in the
-    selected energy range.  Overlaid on this plot are the LAT detected
+    selected energy range.  Overlaid on this plot are the LAT-detected
     extended sources placed by the magnitude of the nearby Galactic
@@
 
+\begin{deluxetable}{lrrrrrrrr}
+\tablecolumns{9}
+\rotate
+\tabletypesize{\footnotesize}
+\tablewidth{0pt}
+\tablecaption{Analysis of the twelve extended sources included in the 2FGL catalog
+\label{known_extended_sources}
+}
+\tablehead{
+\colhead{Name}&
+\colhead{\glon}&
+\colhead{\glat}&
+\colhead{$\sigma$}&
+\colhead{\ts}&
+\colhead{\tsext}&
+\colhead{Pos Err}&
+\colhead{Flux\tablenotemark{(a)}}&
+\colhead{Index}\\
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{(deg.)}&
+\colhead{}&
+\colhead{}&
+\colhead{(deg.)}&
+\colhead{}&
+\colhead{}
+}
+
+\startdata
+\multicolumn{9}{c}{E$>$1 \gev} \\
+\hline
+SMC                                  &     302.59 &   $-$44.42 & $  1.32 \pm   0.15 \pm   0.31 $ &       95.0 &       52.9 &   0.14 & $    2.7 \pm     0.3$ & $   2.48 \pm    0.19$  \\
+LMC                                  &     279.26 &   $-$32.31 & $  1.37 \pm   0.04 \pm   0.11 $ &     1127.9 &      909.9 &   0.04 & $   13.6 \pm     0.6$ & $   2.43 \pm    0.06$  \\
+IC~443                               &     189.05 &       3.04 & $  0.35 \pm   0.01 \pm   0.04 $ &    10692.9 &      554.4 &   0.01 & $   62.4 \pm     1.1$ & $   2.22 \pm    0.02$  \\
+Vela X                               &     263.34 &    $-$3.11 & $                         0.88$ &            &            &        &                       &                        \\
+Centaurus A                          &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
+W28                                  &       6.50 &    $-$0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
+W30                                  &       8.61 &    $-$0.20 & $  0.34 \pm   0.02 \pm   0.02 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
+W44                                  &      34.69 &    $-$0.39 & $  0.35 \pm   0.02 \pm   0.02 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
+W51C                                 &      49.12 &    $-$0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
+Cygnus Loop                          &      74.21 &    $-$8.48 & $  1.71 \pm   0.05 \pm   0.06 $ &      357.9 &      246.0 &   0.06 & $   11.4 \pm     0.7$ & $   2.50 \pm    0.10$  \\
+\cutinhead{E$>$10 \gev}
+MSH\,15$-$52\tablenotemark{(b)}      &     320.39 &    $-$1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
+HESS\,J1825$-$137\tablenotemark{(b)} &      17.56 &    $-$0.47 & $  0.65 \pm   0.04 \pm   0.02 $ &       59.7 &       33.8 &   0.05 & $    1.6 \pm     0.2$ & $   1.63 \pm    0.22$  \\
+\enddata
+
+\tablenotetext{(a)}{
+Integral Flux in units of $10^{-9}$ \phflux and integrated in the fit
+energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
+}
+\tablenotetext{(b)}{
+The discrepancy in the best fit spectra of MSH\,15$-$52 and HESS\,J1825$-$137
+compared to \cite{msh1552} and
+\cite{fermi_hess_j1825} is due to fitting over a different energy range.
+}
+
+\tablecomments{
+All sources were fit using a radially-symmetric uniform disk spatial model.
+\glon and \glat are Galactic longitude
+and latitude of the best fit extended source respectively.  The first
+error on $\sigma$ is statistical and the second is systematic (see
+Section~\ref{systematic_errors_on_extension}).  
+The errors on the integral fluxes and the spectral indices
+are statistical only.
+Pos Err is the error on
+the position of the source.  Vela X and the Centaurus A Lobes were
+not fit in our analysis but are included for completeness.
+}
+\end{deluxetable}
+
 \begin{figure}
@@
 \end{figure}
-
-\begin{deluxetable}{lrrrrrrrr}
-\tablecolumns{9}
-\rotate
-\tabletypesize{\footnotesize}
-\tablewidth{0pt}
-\tablecaption{Analysis of the twelve extended sources included in the 2FGL catalog
-\label{known_extended_sources}
-}
-\tablehead{
-\colhead{Name}&
-\colhead{\glon}&
-\colhead{\glat}&
-\colhead{$\sigma$}&
-\colhead{\ts}&
-\colhead{\tsext}&
-\colhead{Pos Err}&
-\colhead{Flux\tablenotemark{(a)}}&
-\colhead{Index}\\
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}&
-\colhead{(deg.)}&
-\colhead{}&
-\colhead{}
-}
-
-\startdata
-\multicolumn{9}{c}{E$>$1 \gev} \\
-\hline
-SMC                                  &     302.59 &   $-$44.42 & $  1.32 \pm   0.15 \pm   0.31 $ &       95.0 &       52.9 &   0.14 & $    2.7 \pm     0.3$ & $   2.48 \pm    0.19$  \\
-LMC                                  &     279.26 &   $-$32.31 & $  1.37 \pm   0.04 \pm   0.11 $ &     1127.9 &      909.9 &   0.04 & $   13.6 \pm     0.6$ & $   2.43 \pm    0.06$  \\
-IC~443                               &     189.05 &       3.04 & $  0.35 \pm   0.01 \pm   0.04 $ &    10692.9 &      554.4 &   0.01 & $   62.4 \pm     1.1$ & $   2.22 \pm    0.02$  \\
-Vela X                               &     263.34 &    $-$3.11 & $                         0.88$ &            &            &        &                       &                        \\
-Centaurus A                          &     309.52 &      19.42 &                        $\sim10$ &            &            &        &                       &                        \\
-W28                                  &       6.50 &    $-$0.27 & $  0.42 \pm   0.02 \pm   0.05 $ &     1330.8 &      163.8 &   0.01 & $   56.5 \pm     1.8$ & $   2.60 \pm    0.03$  \\
-W30                                  &       8.61 &    $-$0.20 & $  0.34 \pm   0.02 \pm   0.02 $ &      464.8 &       76.0 &   0.02 & $   29.1 \pm     1.5$ & $   2.56 \pm    0.05$  \\
-W44                                  &      34.69 &    $-$0.39 & $  0.35 \pm   0.02 \pm   0.02 $ &     1917.0 &      224.8 &   0.01 & $   71.2 \pm     0.5$ & $   2.66 \pm    0.00$  \\
-W51C                                 &      49.12 &    $-$0.45 & $  0.27 \pm   0.02 \pm   0.04 $ &     1823.4 &      118.9 &   0.01 & $   37.2 \pm     1.3$ & $   2.34 \pm    0.03$  \\
-Cygnus Loop                          &      74.21 &    $-$8.48 & $  1.71 \pm   0.05 \pm   0.06 $ &      357.9 &      246.0 &   0.06 & $   11.4 \pm     0.7$ & $   2.50 \pm    0.10$  \\
-\cutinhead{E$>$10 \gev}
-MSH\,15$-$52\tablenotemark{(b)}      &     320.39 &    $-$1.22 & $  0.21 \pm   0.04 \pm   0.04 $ &       76.3 &        6.6 &   0.03 & $    0.6 \pm     0.1$ & $   2.20 \pm    0.22$  \\
-HESS\,J1825$-$137\tablenotemark{(b)} &      17.56 &    $-$0.47 & $  0.65 \pm   0.04 \pm   0.02 $ &       59.7 &       33.8 &   0.05 & $    1.6 \pm     0.2$ & $   1.63 \pm    0.22$  \\
-\enddata
-
-\tablenotetext{(a)}{
-Integral Flux in units of $10^{-9}$ \phflux and integrated in the fit
-energy range (either 1 \gev to 100 \gev or 10 \gev to 100 \gev).
-}
-\tablenotetext{(b)}{
-The discrepancy in the best fit spectra of MSH\,15$-$52 and HESS\,J1825$-$137
-compared to \cite{msh1552} and
-\cite{fermi_hess_j1825} is due to fitting over a different energy range.
-}
-
-\tablecomments{
-All sources were fit using a radially-symmetric uniform disk spatial model.
-\glon and \glat are Galactic longitude
-and latitude of the best fit extended source respectively.  The first
-error on $\sigma$ is statistical and the second is systematic (see
-Section~\ref{systematic_errors_on_extension}).  
-The errors on the integral fluxes and the spectral indices
-are statistical only.
-Pos Err is the error on
-the position of the source.  Vela X and the Centaurus A Lobes were
-not fit in our analysis but are included for completeness.
-}
-\end{deluxetable}
-
-  % 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
-  % 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
-  % 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
-  % 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
-  % 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
-  % 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
-  % N/A                - P72Y1287         - 2FGL J0851.7-4635
 
@@
     \ifcolorfigure
-      \plotone{source_plots/source_Ophiuchus_color.eps}
-    \else
-      \plotone{source_plots/source_Ophiuchus_bw.eps}
-    \fi
-  % this plot came from 
-  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v8/run.py
-  \caption{
-  A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of (a) the region
-  around 2FGL\,J1627.0$-$2425 smoothed by a 0\fdg1 2D Gaussian kernel (b)
-  also the emission from 2FGL\,J1625.7$-$2526
-  subtracted.  The triangular marker 
-  (colored red in the
-  online version) represents the 2FGL position of this source.
-  The plus-shaped marker and the circle (colored red) 
-  represent the best fit position and extension of this
-  source assuming a radially-symmetric uniform disk model
-  and the black cross represents a background 2FGL source. 
-  The
-  contours in (a) correspond to the 100 $\mu$m image observed by
-  IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
-  CO ($J=1\rightarrow 0$) emission integrated from $-$8 $\km\,\s^{-1}$
-  to 20 $\km\,\s^{-1}$.  They are from \cite{co_rho_ophiuci}, were cleaned using
-  the moment-masking technique \citep{masking_moment_2011}, and have
-  been smoothed by a 0\fdg25 2D Gaussian kernel.
-  }\label{1FGL_J1628.6-2419c}
-\end{figure}
-
-\begin{figure}
-    \ifcolorfigure
       \plotone{source_plots/source_Vela_Jr_color.eps}
@@
     \label{hess_seds}
+  \end{figure}
+
+\begin{figure}
+    \ifcolorfigure
+      \plotone{source_plots/source_Ophiuchus_color.eps}
+    \else
+      \plotone{source_plots/source_Ophiuchus_bw.eps}
+    \fi
+  % this plot came from 
+  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v8/run.py
+  \caption{
+  A diffuse-emission-subtracted 1 \gev to 100 \gev counts map of (a) the region
+  around 2FGL\,J1627.0$-$2425 smoothed by a 0\fdg1 2D Gaussian kernel and (b)
+  with the emission from 2FGL\,J1625.7$-$2526
+  subtracted.  The triangular marker 
+  (colored red in the
+  online version) represents the 2FGL position of this source.
+  The plus-shaped marker and the circle (colored red) 
+  represent the best fit position and extension of this
+  source assuming a radially-symmetric uniform disk model
+  and the black cross represents a background 2FGL source. 
+  The
+  contours in (a) correspond to the 100 $\mu$m image observed by
+  IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
+  CO ($J=1\rightarrow 0$) emission integrated from $-$8 $\km\,\s^{-1}$
+  to 20 $\km\,\s^{-1}$.  They are from \cite{co_rho_ophiuci}, were cleaned using
+  the moment-masking technique \citep{masking_moment_2011}, and have
+  been smoothed by a 0\fdg25 2D Gaussian kernel.
+  }\label{1FGL_J1628.6-2419c}
 \end{figure}
@@
     were not directly fit at \tev energies and so are not included
-    in this comparison. On the other hand, dedicated LAT publications on
+    in this comparison. On the other hand, dedicated publications by the 
+    LAT collaboration on
     these sources showed that their morphologies are consistent

### 2012-05-22 extended_catalog/external_review_reply/replies_to_review_comments.tex
new draft v15

@@
 Thanks for the suggestion.  In addition to the above changes, we have
-replaced a few references to ``catalog sources'' with ``2FGL sources''
-for clarification. We have also fixed a few bibliographical entries. 
+improved the discussion on the algorithm for fitting two point-like
+sources at the same time.  For clarification, we have added a few minor
+grammatical or stylistic improvements to the text.  We have also
+fixed a few bibliographical entries.
 \end{reply}

### 2012-05-22 extended_catalog/paper/extended_search.tex
new draft v15

@@
 null hypothesis (source flux $\Phi=0$) residing on the edge of parameter
-space and the model hypothesis adding a single degree of freedom (the source extension).}
+space and the model hypothesis adding a single degree of freedom (the source flux).}
 It leads to the often quoted result $\sqrt{TS}=\sigma$, where 

### 2012-06-06 pwncatalog/PWNCAT2/paper/subsections/analysis_of_the_fermi_lat_data.tex
update
udpated draft

--- 2012-01-19 pwncatalog/PWNCAT2/paper/sections/analysis_of_the_fermi_lat_data.tex
@@
-\section{Analysis of the \fermi-LAT data}
+\subsection{Analysis of the \fermi-LAT data}
 
-Analysis goes here\ldots
+We develope a procedure for characterizing any emission found
+in off-peak phase internals for the pulsars in this catalog.  
+This proceure used both the spectral and spatial characteristics
+of any observed emission to determine the physical origin of the emission.
+
+Pulsar wind nebula are expected in many cases to be spatially
+extended. For example, \velax and HESS\;J1825-137 are PWN
+that have been observed by the \lat to be spatially extended
+\citep{LAT_collaboration_Vela_X_2010,LAT_collaboration_HESS_J1825_2011}.
+On the other hand, not all pulsar wind nebula are expected to be
+significantly spatially resolved at \gev energies due to the finite
+instrument resolution of the LAT. For example, the Crab nebula appears
+as a point-like source in the LAT but is distinuished in the off-peak
+from the Crab pulsar by its hard spectrum for E$\gtrsim$1 \gev.
+\citep{LAT_collaboration_crab_2010}.
+
+On the other hand, a previous analysis by the Fermi LAT collaboration
+found seven off-peak regions to have significant emission which is
+point-like in nature that is characterized by a pulsar-like cutoff
+spectrum \citep{LAT_collaboration_PWNCAT_2011}.  We can thefore use
+either spatial extension or significant emission at high energy to
+distinguish the PWN scenario and point-like emission with a cutoff
+spectrum to distingiugh the pulsar scenario.
+
+To perform this test, we used the likelihood fitting pacakge \pointlike to study
+the spatial character of emission in the off-peak regions and \gtlike to
+study the spectral character of the emission. These tools provide complementary
+features and this method is very similar to the approach used in the
+second \lat catalog \citep{LAT_Collaboration_2FGL_2012}
+and a followup search for spatially extended sources 
+\citep{LAT_collaboration_extended_search_2012}.
+
+First, we assumed the potential emission to have a point-like spatial model
+and we used \pointlike to fit the position of 
+the off-peak region. The localization procedure is described in \cite{LAT_Collaboration_2FGL_2012}. 
+Following the position fit, we used the best fit positions
+obtained through \pointlike and performed a spectral analysis using \gtlike.
+
+\todo[inline]{Describe assumed spectral model}
+
+After fitting the position of a source, we use \gtlike to perform a likelihood ratio test for
+the detection of the source. Here, \ts is defiend as
+\begin{equation}
+  \ts = 2 \log(\likelihood_\text{pt}/\likelihood_\text{bg})
+\end{equation}
+where $\likelihood_\text{pt}$ is the poission likelihood for a model including the source and $\likelihood_\text{bg}$
+the likliehood for a model not including the source.
+We set the threshold for detection of signfiicant emission at $\ts>25$, 
+corresponding to a significance just over $4\sigma$ \citep{LAT_Collaboration_1FGL_2010}.
+
+We then used \pointlike to test wheter the observed emisssion was spatially extended, assuming
+a radially-symmetric Gaussian spatial model. 
+\pointlike canb e used simulatenously fits the position and the extension of the assumed Gaussian source, following
+the description in \citep{LAT_collaboration_extended_search_2012}. 
+After the extension fit, we refit the spectrum of the spatially extended source using \gtlike
+and performed a likelihood ratio for the significance of the extenstion of a source.
+\begin{equation}
+  \tsext = 2 \log(\likelihood_\text{ext}/\likelihood_\text{pt})
+\end{equation}
+We set the thresholt for detecting the significance of a spatially extended
+soruce at $\tsext>16$, corresponding to a $4\sigma$ detection \citep{LAT_collaboration_extended_search_2012}.
+
+\citep{LAT_collaboration_extended_search_2012}.
+
+From \gtlike, we obtained  
+\begin{equation}
+  \tscut= 2 \log(\likelihood_\text{expcut}/\likelihood_\text{pt})
+\end{equation}
+
+%for this analysis, 
+%we then attempted to fit the position of the region using \pointlike.
+%for the regions that contained significant emission, we then
+%
+%extended source search will be referneced: \cite{extended_source_search}.
+%
+%methods for data analysis
+%\begin{itemize}
+%\item cut on pulsar phase
+%\item perform localization or extension fitting using \gtlike using energies from 1 \gev to 316 \gev.
+%\item if it is point-like, perform an extension upper limit analysis 
+%\item perform spectral analysis using \gtlike for energies above 100 \mev to 316 \gev.
+%\item there is a detection if  $\ts>25$ in the point-like source hypothesis after fitting the position of the point-like source. 
+%\item consider the source to be extended if $\tsext>16$. similar to extended source search paper \todo{cite extended source search paper}.
+%\item calculate \tscut for all energies.
+%\item compute \tsvar
+%\end{itemize}
+%
+%
+%when to consider the source a pulsar or pwn:
+%\begin{itemize}
+%  \item if extended, then it is a pwn (cannot be a pulsar)
+%  \item if it is significiant for $e>10$ \gev, it is a pwn (too hard to be a pulsar)
+%  \item otherwise, if it has a cutoff, it is a pulsar candidate
+%  \item for point-like emission that is not significantly cutoff, the emission  mechanism is uncertain.
+%\end{itemize}

### 2012-06-06 pwncatalog/PWNCAT2/paper/subsections/off_peak_phase_selection.tex
new
update
udpated draft

--- 2012-01-26 pwncatalog/PWNCAT2/paper/sections/off_peak_phase_selection.tex
@@
-\section{Off-peak Phase Selection}
+\subsection{Off-peak Phase Selection}
+\label{subsec:off_peak_defintion}
 
-Off-peak goes here\ldots
+To study the off-peak emission of \lat-detected pulsars, we first
+developed a new method for defining the off-peak emission.
+The primary constraint for this method was that it was systematic,
+computationally efficient, and model independent.
+
+The method we developed procedes by deconstructing a pulsar phaseogram
+into a Baysian blocks using the implementation described in \cite{Jackson_Bayesian_Blocks_2003}.
+
+Set the ncpPrior parameter to 5?
 
 \figref{off_peak_select} shows the off peak selection for some pulsars\dots
+
+How to implement Baysian blocks on periodic data.
 
@@
 \end{figure}
-
-THe off peak phase range is defined in \tabref{off_peak_phase_range}.
-
-\begin{deluxetable}{lcccc}
-  \tabletypesize{\scriptsize}
-  \tablecaption{Observatories, off-pulse definitions and distances of the \todo[inline]{How many pulsars?} \lat-detected pulsars
-  \label{tab:off_peak_phase_range}
-  }
-  \input{tables/off_peak_phase_range}
-  \tablecomments{\todo[inline]{Put table comments}}
-\end{deluxetable}

### 2012-06-06 pwncatalog/PWNCAT2/paper/subsections/offpeak_introduction.tex
udpated draft

In this section, we will search for emission in the phase range between
the peaks of the pulsar's light curve. This potential DC emission could originate
in the pulsar's winds, from inside the pulsar's magnetosphere, or 
the emission could be spatially coincidental but physically
unrealted to the pulsar.

The \gev emission in the off-peak from LAT-detected pulsars has been studied in several previous 
publications. In particular, the spatially-extended \velax pulsar wind nebula has
been detected by the LAT in the off-peak phase region of the Vela pulsar \citep{LAT_collaboration_Vela_X_2010}
and the Crab nebula has been detected by the LAT \citep{LAT_collaboration_crab_2010}.
Surprisingly, this \gev emission from the Crab nebula was found to be variable
in time \citep{LAT_Collaboration_Crab_Flare_2011}.

Most prominently, a dedicated analysis was performed using LAT data of
the off-peak emission of 54 LAT-detected pulsars using 16 months of survey observations
\citep{LAT_collaboration_PWNCAT_2011}. 
The search discovered ten pulsars wich significant off-peak emission.
Along with \velax and the Crab nebula, the 
search discovered a source coincident with the TeV source HESS\;J1023-575
in the off-peak window of PSR\;J1023-5746. In addtion, four of hte other
regions showed a significantly cutoff pulsar-like spectrum and are
suspected to be be of magnetospheric origin.

We expand upon this previous work by searching in the off-peak region
of all 107 pulsars presented in this catalog. In addition to the larger
list of pulsars, in this earch we use an expanded data set, a larger energy range,
and an improved analysis method.

### 2012-06-06 pwncatalog/PWNCAT2/paper/subsections/results.tex
new
update
udpated draft

--- 2012-02-07 pwncatalog/PWNCAT2/paper/sections/results.tex
@@
-\section{Results}
+\subsection{Results}
 
 First, we tested the sources to see if they
-were spatially extended. The localization results are in \tabref{localization}.
+were spatially extended. The localization results are in \tabref{offpeak}.
 
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Localization and extension fitting results
-\label{tab:localization}
+\tablecaption{Off-Peak Spatial and Spectral Results
+\label{tab:offpeak}
 }
-\input{tables/localization.tex}
+\input{tables/off_peak_spatial_spectral.tex}
 \tablecomments{\todo[inline]{Put table comments}}
@@
 Next, we performed a spectral analysis over all energy using the best
-fit morphology. \tabref{all_energy} shows the results of the all energy
+fit morphology. XXX shows the results of the all energy
 analysis of the off-peak emission for each pulsar.
@@
 Next, we fit a powerlaw independently in each energy
-bin. \tabref{each_energy} shows the results of the analysis in separate
+bin. XXX shows the results of the analysis in separate
 energy bins of each pulsar.
@@
 Finally, we tested sources to see which were
-variable. \tabref{cutoff_test} shows the results of the cutoff test for
+variable. XXX shows the results of the cutoff test for
 pulsars with significant low-energy emission.
-
-\begin{deluxetable}{l*{5}c}
-\tabletypesize{\scriptsize}
-\tablecaption{All Energy spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
-\label{tab:all_energy}
-}
-\input{tables/all_energy.tex}
-\tablecomments{\todo[inline]{Put table comments}}
-\end{deluxetable}
-
-\clearpage
-\begin{deluxetable}{l*{9}c}
-%\tabletypesize{\tiny}
-\setlength{\tabcolsep}{0.04in}
-\tabletypesize{\scriptsize}
-\tablewidth{0pt}
-\rotate
-\tablecaption{Energy bin spectral fit for the \todo[inline]{How many pulsars?} \lat-detected Pulsars
-\label{tab:each_energy}
-}
-\input{tables/each_energy.tex}
-\tablecomments{\todo[inline]{Put table comments}}
-\end{deluxetable}
-
-\begin{deluxetable}{l*{6}c}
-\tabletypesize{\scriptsize}
-\tablecaption{Spectral fitting of pulsar wind nebula candidates with low energy component
-\label{tab:cutoff_test}
-}
-\input{tables/cutoff_test.tex}
-\tablecomments{\todo[inline]{Put table comments}}
-\end{deluxetable}
 
@@
 
-\figref{variability} shows the cutoff test\ldots
+We tested all sources for variability.
 
-\begin{deluxetable}{l*{2}c}
-\tabletypesize{\scriptsize}
-\tablecaption{Variability test
-\label{tab:variability}
-}
-\input{tables/variability.tex}
-\tablecomments{\todo[inline]{Put table comments}}
-\end{deluxetable}
+Special cases:
+\begin{itemize}
+  \item Crab has a funny spectrum, we have (so far) fixed it to
+  \item \velax
+\end{itemize}

### 2012-06-07 pwncatalog/PWNCAT2/paper/subsections/off_peak_phase_selection.tex
update

@@
 
-Set the ncpPrior parameter to 5?
+\todo[inline]{This is just a placeholder. Hopefully Andrea can fill this section
+in with the real details.}
+
+\todo[inline]{How to implement Baysian blocks on periodic data.}
 
 \figref{off_peak_select} shows the off peak selection for some pulsars\dots
-
-How to implement Baysian blocks on periodic data.
 
@@
   \fi
-  \caption{Off peak selection for some pulsars\dots}
+  \caption{Off peak selection for some pulsars. 
+  \todo[inline]{This is just a placeholder figure. 
+  Hopefull Andrea or somebody can update the plot
+  once the real algorithm is finished.}}
   \label{fig:off_peak_select}

### 2012-06-08 fermi/monte_carlo/snrsim/code/fit.py
update

@@ -13,6 +13,7 @@ parser = ArgumentParser()
 parser.add_argument("i", type=int)
 parser.add_argument("--source", required=True, choices=['W44', 'IC443'])
 parser.add_argument("--spectrum", required=True, choices=['PowerLaw', 'SmoothBrokenPowerLaw'])
+parser.add_argument("--normalization", choices=['standard','same_flux','same_prefactor'])
 parser.add_argument("--simdir", required=True)
 parser.add_argument("--debug", default=False, action='store_true')
 args= parser.parse_args()
@@ -21,8 +22,9 @@ i = args.i
 istr = '%05d' % i
 source = which = args.source
 spectrum = args.spectrum
+normalization = args.normalization
 
-simdir = join(args.simdir,"job_source_%s_spectrum_%s" % (source,spectrum),istr)
+simdir = join(args.simdir,"job_spectrum_%s_normalization_%s_source_%s" % (spectrum,normalization,source),istr)
 
 if source == 'W44':
     roi_dir = SkyDir(284.005,1.345)
@@ -32,10 +34,6 @@ elif source == 'IC443':
     roi_dir = SkyDir(94.310,22.580)
     name = 'IC443'
     ltcube = "/u/gl/funk/data/GLAST/ExtendedSources/NewAnalysis/gtlike/IC443/ltcube_239557414_334152002.fits"
-
-# TEMPORARY
-ltcube = 'ltcube.fits'
-# TEMPORARY
 
 data_specification = DataSpecification(
     ft1files = join(simdir,"simulated_ft1.fits"),

### 2012-06-08 fermi/monte_carlo/snrsim/code/loop.py

@@ -2,65 +2,56 @@ from os.path import join
 
 from lande.utilities.jobtools import JobBuilder
 
-#params=dict(spectrum=[ 'SmoothBrokenPowerLaw', 'SmoothDoubleBrokenPowerLaw'])
-#j = JobBuilder(savedir='$stefan_w44_data/v1',
-#               code='$stefan_w44_code/simulate.py',
-#               num=10,
+#params=dict(source=['W44','IC443'])
+#params['spectrum','normalization']=[['PowerLaw','same_prefactor'],
+#                                    ['PowerLaw','same_flux'],
+#                                    ['SmoothBrokenPowerLaw','standard'],
+#                                   ]
+#
+#j = JobBuilder(savedir='$snrsim_sims/v1',
+#               code='$snrsim_code/simulate.py',
+#               num=5,
 #               params=params)
 #j.build()
 
 
-
-#params=dict(source=['W44','IC443'], 
-#            spectrum=[ 'PowerLaw', 'SmoothBrokenPowerLaw'])
-#j = JobBuilder(savedir='$stefan_w44_sims/v2',
-#               code='$stefan_w44_code/simulate.py',
-#               num=10,
+#params=dict(source=['W44','IC443'])
+#params['spectrum','normalization']=[['PowerLaw','same_prefactor'],
+#                                    ['PowerLaw','same_flux'],
+#                                    ['SmoothBrokenPowerLaw','standard'],
+#                                   ]
+#
+#j = JobBuilder(savedir='$snrsim_sims/v2',
+#               code='$snrsim_code/simulate.py',
+#               num=5,
 #               params=params)
 #j.build()
 
 
-#params=dict(source=['W44','IC443'], 
-#            spectrum=[ 'PowerLaw', 'SmoothBrokenPowerLaw'])
-#            simdir=join("$stefan_w44_sims","v2"),
-#j = JobBuilder(savedir='$stefan_w44_fits/v1',
-#               code='$stefan_w44_code/fit.py',
-#               num=10,
-#               params=params)
-#j.build()
-
-
-# ------------------------------------------------------------------------------------------------------------------------
-
-#params=dict(source=['W44','IC443'], 
-#            debug=True,
-#            spectrum=[ 'PowerLaw', 'SmoothBrokenPowerLaw'])
-#j = JobBuilder(savedir='$stefan_w44_sims/temp1',
-#               code='$stefan_w44_code/simulate.py',
-#               num=10,
+#params=dict(source=['W44','IC443'])
[…]

### 2012-06-08 fermi/monte_carlo/snrsim/code/simulate.py

@@ -6,7 +6,7 @@ from argparse import ArgumentParser
 import numpy as np
 from skymaps import SkyDir
 from uw.utilities.xml_parsers import parse_sources, write_sources
-from uw.like.Models import PowerLaw, SmoothBrokenPowerLaw
+from uw.like.Models import PowerLaw, SmoothBrokenPowerLaw, FileFunction
 from uw.like.roi_catalogs import Catalog2FGL
 from uw.like.pointspec_helpers import get_default_diffuse
 from uw.like.roi_monte_carlo import MonteCarlo
@@ -17,6 +17,7 @@ parser.add_argument("i", type=int)
 parser.add_argument("--source", required=True, choices=['W44', 'IC443'])
 parser.add_argument("--spectrum", required=True, choices=['PowerLaw', 'SmoothBrokenPowerLaw'])
 parser.add_argument("--debug", default=False, action='store_true')
+parser.add_argument("--normalization", choices=['standard','same_flux','same_prefactor'])
 args= parser.parse_args()
 
 i = args.i
@@ -42,9 +43,11 @@ elif source == 'IC443':
 
 
 ds = get_default_diffuse(
-    diffdir="/afs/slac/g/glast/groups/diffuse/rings/2year/",
-    gfile="ring_2year_P76_v0.fits",
-    ifile="isotrop_2year_P76_source_v0.txt")
+    diffdir="/nfs/slac/g/ki/ki03/lande/fermi/diffuse/",
+    gfile="gal_2yearp7v6_v0.fits",
+    ifile="iso_p7v6source.txt")
+
+ds[1].smodel = FileFunction(file='/nfs/slac/g/ki/ki03/lande/fermi/diffuse/iso_p7v6source_extrapolated.txt')
 
 ps,ds = catalog.merge_lists(skydir, radius=15, user_diffuse_list=ds)
 
@@ -66,7 +69,7 @@ if source == 'W44':
     """
     smooth = SmoothBrokenPowerLaw(
         Norm=14.56863965e-10,
-        Index_1=1.504042874,
+        Index_1=-1.504042874,
         Index_2=1.891184873,
         E_break=204.3216401,
         beta=0.1,
@@ -74,10 +77,19 @@ if source == 'W44':
 
     if spectrum == 'PowerLaw':
         W44.model = PowerLaw(index=1.891184873, e0=200)
+
+        if args.normalization == 'same_flux':
+            W44.model.set_flux(smooth.i_flux(emin=60, emax=2000), emin=60, emax=2000)
[…]

### 2012-06-08 pwncatalog/PWNCAT2/paper/subsections/offpeak_results.tex
rename

--- 2012-06-06 pwncatalog/PWNCAT2/paper/subsections/results.tex
@@
 
+Following the procedure described in \subsecref{off_peak_analysis},
+we performed an analysis of the off-peak emission for all 107
+pulsars in this catalog. In this paper, we will present
+a condensed summary of the results. We will also
+describe a supplemental \fits-format table which will contain
+the full spectral and spatial results for each region.
+
+Table 
 First, we tested the sources to see if they
@@
 
+\todo[inline]{Finally, a description of the acompanying fits table}
+
 \figref{cutoff_test} shows the cutoff test\ldots
@@
 
-We tested all sources for variability.
+\todo[inline]{We tested all sources for variability.}
+
+\todo[inline]{Describe upper limits}
 
@@
   \item Crab has a funny spectrum, we have (so far) fixed it to
-  \item \velax
+  \item \velax Spatialmodel
 \end{itemize}
+
+Results:
+\begin{itemize}
+  \item List of all XXX detections detected
+  \item For each pulsar, is it a 
+    \begin{itemize}
+      \item Magnetospheric emission
+      \item PWN emission
+      \item Region where the fit shows trouble for some reason.
+    \end{itemize}
+\end{itemize}

### 2012-06-27 presentations/lande_roi_monte_carlo_simulation_wg_june_27_2012/lande_roi_monte_carlo_simulation_wg_june_27_2012.tex
update

\documentclass[12pt]{beamer}
\usetheme[navbar=false, bkgimage=false, shadow=true]{Fermi}

\usepackage{graphicx}

\usepackage{amsmath}
\usepackage{xspace}
\usepackage{listings}
\lstset{basicstyle=\scriptsize,frame=single,showstringspaces=false}

\newcommand{\python}{\ensuremath{\mathtt{python}}\xspace}
\newcommand{\gtlike}{\ensuremath{\mathtt{gtlike}}\xspace}
\newcommand{\pointlike}{\ensuremath{\mathtt{pointlike}}\xspace}
\newcommand{\gtobssim}{\ensuremath{\mathtt{gtobssim}}\xspace}
\newcommand{\gtmktime}{\ensuremath{\mathtt{gtmktime}}\xspace}
\newcommand{\fermi}{\textit{Fermi}\xspace}
\newcommand{\roimc}{\texttt{roi\_monte\_carlo}\xspace}
\newcommand{\FileSpectrumMap}{\texttt{FileSpectrumMap}\xspace}
\newcommand{\mapcube}{\texttt{MapCube}\xspace}
\newcommand{\ftone}{\texttt{ft1}\xspace}

\title{\pointlike's MC Simulation Package}

\author{Joshua Lande}
\date{June 27, 2012}

\begin{document}

\fermititle

\begin{frame}{Motivation (Ext. Srs. Search paper)}
\begin{columns}
  \column{.4\textwidth} 
  \includegraphics[scale=0.4]{plots/ext_src_table.pdf}
  \column{.6\textwidth} 
  \includegraphics[scale=0.45]{plots/ext_src_plot.pdf}

  $\sim90,000$ simulations/model!
\end{columns}
\end{frame}

\begin{frame}{\gtobssim Overview}
  \begin{itemize}
    \item Input to \gtobssim:
      \begin{itemize}
        \item XML File
        \item Ft2 file/source list
        \item templates for certain spectral and spatial models (more soon\dots)
      \end{itemize}
    \item After running \gtobssim
      \begin{itemize}
        \item Remove bad time intervals from simulated data
        \item Apply zenith angle cut to simulated data
      \end{itemize}
    \item \em{Building the \gtobssim XML file can be error prone}
    \item \em{Cutting simulated data can be error prone}
  \end{itemize}
\end{frame}

\begin{frame}{\pointlike's MC Simulation package}
  \begin{itemize}
    \item I developed a wrapper around \gtobssim to automate
      otherwise time consuming, tedious, or error-prone tasks
    \item Built around \pointlike, an alternate maximum
      likelihood package written in \python
      \begin{itemize}
      \item Uses as input a list of \pointlike objects
        \item Builds the XML file for \gtobssim
        \item Converts unsupported models into required templates.
        \item Automatically removes bad time intervals + \texttt{zmax} cut
      \end{itemize}
    \item Code is in \pointlike package: \texttt{uw.like.roi\_monte\_carlo.py}.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Point Sources}

  \begin{lstlisting}[language=XML]
<source name="source" flux="0.03">
  <spectrum escale="MeV">
    <particle name="gamma">
      <power_law emin="20" emax="1000000" gamma="1.9"/>
    </particle>
    <celestial_dir ra="193.98" dec="-5.82"/>
  </spectrum>
</source>
  \end{lstlisting}

  \begin{itemize}
    \item Supported Spectral Models
  \begin{itemize}
    \item power law, (dark matter) line, broken powerlaw, and file function
    \item \url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/other_sources.html}
  \end{itemize}
\item Problematic for all other spectral models!
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Point Sources (cont)}
  \begin{itemize}
    \item Any spectrum can be simulated using \texttt{FileSpectrum}:
  \end{itemize}

  \begin{lstlisting}[language=XML]
<source name="FileSpectrum">
   <spectrum escale="MeV" >
      <SpectrumClass name="FileSpectrum" params="flux=0.,
      specFile=$(FERMI_DIR)/spectrum.dat"/>
      <celestial_dir ra="194.04" dec="-5.789"/>
   </spectrum>
</source>
  \end{lstlisting}

  \begin{itemize}
    \item \roimc will automatically build a \texttt{FileSpectrum} for any otherwise-unsupported
      model
    \item \gtobssim Requires integral of spectral model (done automatically by \roimc)
    \item WARNING! \texttt{FileSpectrum} objects cannot contain 0 pixels (stripped out by \roimc)
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Diffuse Sources Sources}
  \begin{itemize}
  \item \mapcube model to simulate diffuse background:
  \end{itemize}
\begin{lstlisting}[language=XML]
<source name="map_cube_source">
   <spectrum escale="MeV">
      <SpectrumClass name="MapCube" params="1., 
        $(FERMI_DIR)/mapcube.fits "/>
      <use_spectrum frame="galaxy"/>
   </spectrum>
</source>
\end{lstlisting}
  \begin{itemize}
    \item Requires 3D integral of fits file
    \item Integration automatic by \roimc
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Building the XML file (Isotropic DIffuse Sources)}
\begin{itemize}
\item \FileSpectrumMap for simulation the isotropic diffuse:
\end{itemize}

\begin{lstlisting}[language=XML]
<source name="isotropic">
   <spectrum escale="GeV" flux="1.">
      <SpectrumClass name="FileSpectrumMap" 
      params="flux=17,fitsFile=$(FERMI_DIR)/iso_spatial.fits,
specFile=$(FERMI_DIR)/iso_spectral.dat,emin=100.,emax=1100"/>
      <use_spectrum frame="galaxy"/>
   </spectrum>
</source>
\end{lstlisting}

\begin{itemize}
  \item Must integrate isotropic spectrum
  \item Must generate allsky spatial \texttt{fits} file predicting 1 
  \item Must add energy range from isotropic file
  \item All done automatically by \roimc
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Extended Sources}
\begin{lstlisting}[language=XML]
<source name="gaussian_source">
   <spectrum escale="MeV">
      <SpectrumClass name="GaussianSource" 
        params="0.1,2.1,45,30,3,0.5,45,30,2e5"/>
      <use_spectrum frame="galaxy"/>
   </spectrum>
</source>
\end{lstlisting}
  \begin{itemize}
    \item \gtobssim only natively supports an Elliptical Gaussian spatial model with a power law spectral model.
    \item WARNING, the ellipse angle is defined west of celestial north)!
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Extended Sources (cont)}

  \begin{itemize}
    \item Any extended source can be represented by a \FileSpectrumMap
  \end{itemize}
\begin{lstlisting}[language=XML]
<source name="filespectrummap_test">
   <spectrum escale="GeV" flux="1.">
      <SpectrumClass name="FileSpectrumMap" params="
        flux=17,
        fitsFile=$(FERMI_DIR)/spatial.fits,
        specFile=$(FERMI_DIR)/spectral.dat,
        emin=100, emax=1100"/>
      <use_spectrum frame="galaxy"/>
   </spectrum>
</source>
\end{lstlisting}
  \begin{itemize}
    \item Have to:
    \begin{itemize}
    \item Build fits template for spatial model
    \item Build text file for spectral model
    \item Integrate spectral model
    \end{itemize}
  \item Process automatic by \roimc for any of \pointlike's extended
    sources (disk, Gauss, NFW, SpatialMap, \dots).
  \end{itemize}
\end{frame}

\begin{frame}{Common Gotcha's (Energy Dispersion)}
  \begin{itemize}
        \item Energy dispersion means photons with energies outside simulation range can
          disperse into energy range
        \item All spectral models must be simulated for energies well outside of simulation range
        \item Handled automatically by \roimc. 
        \item Parameter \texttt{roi\_pad} (default=2) will pad a given
          amount to energy of all spectral models.
        \item \texttt{acutal\_emin} = \texttt{simulation\_emin}/\texttt{roi\_pad}
        \item \texttt{acutal\_emax} = \texttt{simulation\_emax}*\texttt{roi\_pad}
      \end{itemize}
\end{frame}

\begin{frame}{Common Gotcha's (\ftone cuts)}
  \begin{itemize}
    \item Must remove bad time intervals
      \begin{itemize}
        \item \gtobssim takes as input an FT2 file (does not store GTIs)
        \item But \gtlike analysis uses \texttt{ltcube} only over good time intervals
        \item No ScienceTool for applying \texttt{gtmktime} unless you know exact filter applied to \ftone file
          which generated ltcube
        \item \roimc uses a compbiation of \texttt{pyfits} and \texttt{gtmktime} to apply exact GTIs
          from an \ftone or ltcube file.
      \end{itemize}
    \item zenith angle cut must be consistent with zmax flag in \texttt{gtltcube}
      \begin{itemize}
        \item Flag in \roimc to automatically apply \texttt{zmax} after simulation.
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{All sky vs region simulations}
  \begin{itemize}
    \item \gtobssim will simulate over all sky for allsky \mapcube files.
    \item \texttt{use\_ac} parameter is applied AFTER the simulation!
    \item This is very inefficient when simulating only a particular region in the sky
    \item As far as I can tell, non-allsky mapcubes will cause strange projection effects
    \item lonMin and lonMax parameters for spatial models does not work correct.
  \end{itemize}
\end{frame}

\begin{frame}{\mapcube Cutting}
  \includegraphics[scale=0.4]{plots/allsky_cubes.png}
  \begin{itemize}
    \item My solution for simulation small regions of the sky is to set to 0 pixels
      far away from ROI
    \item Done automaticlly by \roimc
    \item Dramatic speedup for simulations of small regions
    \item Also, cut out energy bins in \mapcube far away from simulation energy range.
    \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{\roimc Usage}
  \begin{itemize}
    \item First, build a list of pointlike soruces
    \item Most easily, you can use \pointlike's XML parser:
\begin{lstlisting}[language=Python]
from uw.utilities.xml_parsers import parse_sources
ps,ds=parse_sources(xmlfile)
sources=ps+ds
\end{lstlisting}
\item You can also build source programatically with \pointlike:
\begin{lstlisting}[language=Python]
  from uw.like.pointspec_helpers import PointSource
  from uw.like.Models import PowerLaw
  skydir = SkyDir(34,-100, SkyDir.EQUATORIAL)
  model = PowerLaw(norm=1e-10, index=2)
  ps=PointSource(name='ps', model=model, skydir=skydir)
\end{lstlisting}
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Run the Simulation}

\begin{lstlisting}[language=Python]
from skymaps import SkyDir
roi_dir = SkyDir(30, 0.5, SkyDir.GALACTIC)

from uw.like.roi_monte_carlo import MonteCarlo
mc = MonteCarlo(
    sources=sources,
    seed=0,
    emin=1e3,
    emax=1e4,
    roi_dir=roi_dir,
    maxROI=10,
    irf='P7SOURCE_V6',
    ft1='ft1.fits',
    ft2='ft2.fits',
    gtifile='ltcube.fits',
    zmax=100,
)
mc.simulate()
\end{lstlisting}

\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item \roimc part of \pointlike
    \item Automatically distributed with the ScienceTools
    \item \roimc documented on Confluence:
      \url{https://confluence.slac.stanford.edu/x/MIAcBw}
    \item The code has been successfully used by several people (see work by Stephan Zimmer)
  \end{itemize}
\end{frame}

\end{document}

### 2012-06-27 presentations/lande_roi_monte_carlo_simulation_wg_june_27_2012/lande_roi_monte_carlo_simulation_wg_june_27_2012.tex
udpate talk

@@
     \item Code is in \pointlike package: \texttt{uw.like.roi\_monte\_carlo.py}.
+    \item \url{http://www-glast.stanford.edu/cgi-bin/viewcvs/pointlike/python/uw/like/roi_monte_carlo.py}
   \end{itemize}
@@
   \frametitle{Point Sources}
+  \begin{itemize}
+    \item power law point sources are easy:
+  \end{itemize}
 
@@
   \begin{itemize}
-    \item Supported Spectral Models
+    \item \gtobssim supports power law, (dark matter) line, broken powerlaw
   \begin{itemize}
-    \item power law, (dark matter) line, broken powerlaw, and file function
     \item \url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/other_sources.html}
   \end{itemize}
-\item Problematic for all other spectral models!
   \end{itemize}
@@
   \begin{itemize}
-    \item \roimc will automatically build a \texttt{FileSpectrum} for any otherwise-unsupported
-      model
+    \item Requires generating a 2D data file of spectral model
+    \item \roimc will use \pointlike automatically build the \texttt{FileSpectrum} 
     \item \gtobssim Requires integral of spectral model (done automatically by \roimc)
@@
 \begin{frame}[fragile]
-  \frametitle{Building the XML file (Isotropic DIffuse Sources)}
+  \frametitle{Isotropic Diffuse}
 \begin{itemize}
@@
       <SpectrumClass name="FileSpectrumMap" 
-      params="flux=17,fitsFile=$(FERMI_DIR)/iso_spatial.fits,
-specFile=$(FERMI_DIR)/iso_spectral.dat,emin=100.,emax=1100"/>
+      params="flux=17,
+        fitsFile=$(FERMI_DIR)/iso_spatial.fits,
+        specFile=$(FERMI_DIR)/iso_spectral.dat,
+        emin=100,emax=1e5"/>
       <use_spectrum frame="galaxy"/>
@@
 \begin{itemize}
-  \item Must integrate isotropic spectrum
+  \item Must compute flux for isotropic spectrum
   \item Must generate allsky spatial \texttt{fits} file predicting 1 
-  \item Must add energy range from isotropic file
+  \item Must include energy range from isotropic file
   \item All done automatically by \roimc
@@
   \begin{itemize}
-    \item \gtobssim only natively supports an Elliptical Gaussian spatial model with a power law spectral model.
+    \item \gtobssim only natively supports an elliptical Gaussian spatial model with a power law spectral model.
     \item WARNING, the ellipse angle is defined west of celestial north)!
@@
   \begin{itemize}
-    \item Any extended source can be represented by a \FileSpectrumMap
+    \item Any extended source can be represented by a \FileSpectrumMap:
   \end{itemize}
@@
         specFile=$(FERMI_DIR)/spectral.dat,
-        emin=100, emax=1100"/>
+        emin=100, emax=1e5"/>
       <use_spectrum frame="galaxy"/>
@@
         \item Build text file for spectral model
-    \item Integrate spectral model
+        \item Calculate flux of spectral model
       \end{itemize}
-  \item Process automatic by \roimc for any of \pointlike's extended
+    \item XML built automatically by \roimc for any of \pointlike's extended
       sources (disk, Gauss, NFW, SpatialMap, \dots).
@@
 
-\begin{frame}{Common Gotcha's (Energy Dispersion)}
+\begin{frame}[fragile]
+  \frametitle{Common Gotcha's (Energy Dispersion)}
   \begin{itemize}
         \item Energy dispersion means photons with energies outside simulation range can
-          disperse into energy range
-        \item All spectral models must be simulated for energies well outside of simulation range
+          disperse into simulation
+          \begin{itemize}
+            \item All spectral models must be simulated for energies well outside simulation range!
+          \end{itemize}
         \item Handled automatically by \roimc. 
+          \begin{itemize}
             \item Parameter \texttt{roi\_pad} (default=2) will pad a given
-          amount to energy of all spectral models.
-        \item \texttt{acutal\_emin} = \texttt{simulation\_emin}/\texttt{roi\_pad}
-        \item \texttt{acutal\_emax} = \texttt{simulation\_emax}*\texttt{roi\_pad}
+              amount to energy to every spectral models.
           \end{itemize}
+      \end{itemize}
+\begin{lstlisting}[language=Python]
+actual_emin = simulation_emin/roi_pad
+actual_emax = simulation_emax*roi_pad
+\end{lstlisting}
 \end{frame}
 
-\begin{frame}{Common Gotcha's (\ftone cuts)}
+\begin{frame}{More Common Gotcha's}
   \begin{itemize}
+    \item All fluxes be in ph$\;$m$^{-2}$s$^{-1}$
     \item Must remove bad time intervals
       \begin{itemize}
-        \item \gtobssim takes as input an FT2 file (does not store GTIs)
-        \item But \gtlike analysis uses \texttt{ltcube} only over good time intervals
-        \item No ScienceTool for applying \texttt{gtmktime} unless you know exact filter applied to \ftone file
-          which generated ltcube
-        \item \roimc uses a compbiation of \texttt{pyfits} and \texttt{gtmktime} to apply exact GTIs
-          from an \ftone or ltcube file.
+        \item \gtobssim takes as input an FT2 file (no info on GTIs)
+        \item \gtlike analysis uses \texttt{ltcube} sumed over GTIs
+        \item Can only use \gtmktime if you know exact cuts applied to data (problematic)
+        \item No Science Tool for applying GTIs from another file
+        \item \roimc uses a combination of \texttt{pyfits} and \gtmktime to apply exact GTIs
+          from an \ftone or \texttt{ltcube} file.
       \end{itemize}
-    \item zenith angle cut must be consistent with zmax flag in \texttt{gtltcube}
+    \item zenith angle cut must be consistent with \texttt{zmax} used when generating \texttt{ltcube}
       \begin{itemize}
@@
   \begin{itemize}
-    \item \gtobssim will simulate over all sky for allsky \mapcube files.
-    \item \texttt{use\_ac} parameter is applied AFTER the simulation!
-    \item This is very inefficient when simulating only a particular region in the sky
-    \item As far as I can tell, non-allsky mapcubes will cause strange projection effects
-    \item lonMin and lonMax parameters for spatial models does not work correct.
+    \item \gtobssim will simulate over all sky for allsky \mapcube files
+    \item \gtobssim's \texttt{use\_ac} parameter is applied AFTER the simulation!
+    \item This is very inefficient when simulating a particular region in the sky
+    \item As far as I can tell, non-allsky \mapcube fits files will cause strange projection effects
+    \item \texttt{lonMin} and \texttt{lonMax} parameters for spatial models does not work correct.
   \end{itemize}
@@
       far away from ROI
-    \item Done automaticlly by \roimc
+    \item Done automatically by \roimc
     \item Dramatic speedup for simulations of small regions
@@
   \begin{itemize}
-    \item First, build a list of pointlike soruces
-    \item Most easily, you can use \pointlike's XML parser:
+    \item First, build a list of \pointlike sources
+    \item Most easily, use \pointlike's XML parser:
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-\item You can also build source programatically with \pointlike:
+\item Also build source programmatically with \pointlike:
 \begin{lstlisting}[language=Python]
@@
 
+  \begin{itemize}
+    \item (optional) \texttt{roi\_dir} + \texttt{maxROI} for \mapcube cutting
+  \end{itemize}
+
 \end{frame}
@@
   \begin{itemize}
-    \item \roimc part of \pointlike
-    \item Automatically distributed with the ScienceTools
-    \item \roimc documented on Confluence:
+    \item \roimc avoids otherwise time consuming, tedious, or error-prone tasks
+    \item \roimc part of \pointlike and automatically distributed with the Science Tools
+    \item Documented on Confluence:
       \url{https://confluence.slac.stanford.edu/x/MIAcBw}
-    \item The code has been successfully used by several people (see work by Stephan Zimmer)
+    \item Python module can be easily built on top of:
+      \begin{itemize}
+        \item For example, this package is the basis of MakeSkyModelsFromCatalog (see work by Stephan Zimmer)
+      \end{itemize}
   \end{itemize}

### 2012-06-27 presentations/lande_roi_monte_carlo_simulation_wg_june_27_2012/lande_roi_monte_carlo_simulation_wg_june_27_2012.tex
update talk

@@
 \begin{frame}{Motivation (Ext. Srs. Search paper)}
+\begin{columns}
+  \column{.5\textwidth} 
+  \includegraphics[scale=0.35]{plots/bias_w44sim_color.pdf}
+
+  \begin{itemize}
+    \item Simulation of W44 + Galactic \& Isotropic Diffuse $\sim 1,000$ times
+  \end{itemize}
+
+  \column{.5\textwidth} 
+  \includegraphics[scale=0.35]{plots/ts_comparison_w44sim_color.pdf}
+
+  \begin{itemize}
+    \item Look at distribution of TS values fitting with different spatial models
+  \end{itemize}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Ext. Srs. Search paper (cont)}
 \begin{columns}
@@
       \begin{itemize}
-      \item Uses as input a list of \pointlike objects
+      \item Uses as input a list of \pointlike sources
         \item Builds the XML file for \gtobssim
@@
   \end{itemize}
+\item No LogParabola, ExpCutoff\dots
   \end{itemize}
@@
   \begin{itemize}
-    \item Requires generating a 2D data file of spectral model
-    \item \roimc will use \pointlike automatically build the \texttt{FileSpectrum} 
-    \item \gtobssim Requires integral of spectral model (done automatically by \roimc)
+    \item Requires generating a 1D data file of spectral model
+    \item \roimc uses \pointlike to automatically build the \texttt{FileSpectrum} 
+    \item \gtobssim requires integral of spectral model (done automatically by \roimc)
     \item WARNING! \texttt{FileSpectrum} objects cannot contain 0 pixels (stripped out by \roimc)
@@
           \end{itemize}
-        \item Handled automatically by \roimc. 
+        \item Handled automatically by \roimc
           \begin{itemize}
             \item Parameter \texttt{roi\_pad} (default=2) will pad a given
-              amount to energy to every spectral models.
+              amount to energy to every spectral model:
           \end{itemize}

### 2012-06-29 extended_catalog/paper/extended_search.tex
final verison

@@
 \newcommand{\degree}{\ensuremath{^\circ}\xspace}
-
-% New text is included inside of the \newtext command
-% and is bold and red
-\newcommand{\newtext}[1]{{\bfseries \color{red}#1}}
-% To unformat the new text, comment out the above line
-% and include the line below
-% \newcommand{\newtext}[1]{#1}
 
@@
 LAT sources.  
-\newtext{
 In Section~\ref{validate_ts}, we demonstrate
@@
 we calculate the LAT detection threshold to resolve the extension
-of a source.}
+of a source.
 In Section~\ref{dual_localization_method}, we
@@
 
-\newtext{
 The significance of the extension of a source can be calculated from the
@@
 For the case of the extension test, we compare the likelihood
-when assuming the source has either a point-like or spatially extended spatial model:}
+when assuming the source has either a point-like or spatially extended spatial model:
 \begin{equation}
@@
 we define the source size as the radius containing 68\% of the
-intensity ($\rsixeight$). \newtext{
+intensity ($\rsixeight$). 
 By direct integration, we find
@@
 For the example above, $\rsixeight=0\fdg5$ so $\sigma_\text{disk}=0.61\degree$
-and $\sigma_\text{Gaussian}=0.33\degree$.}
+and $\sigma_\text{Gaussian}=0.33\degree$.
 
@@
 to the detailed spatial structure of these sources.  
-\newtext{In section \ref{bias_wrong_spatial_model}, we perform a dedicated Monte Carlo simulation
+In section \ref{bias_wrong_spatial_model}, we perform a dedicated Monte Carlo simulation
 that shows there is little bias due to incorrectly modeling the spatial structure
@@
 disk spatial model. Unless otherwise noted,
-we quote the radius to the edge ($\sigma$) as the size of the source.}
-
-\newtext{
+we quote the radius to the edge ($\sigma$) as the size of the source.
+
 \section{Validation of the \ts Distribution}
@@
 
-}
-
-\newtext{
 We tested the theoretical distribution for \tsext
 to evaluate the false detection probability for measuring source extension.
-To do so, we tested simulated point-like sources for extension.} 
+To do so, we tested simulated point-like sources for extension. 
 \cite{mattox_egret}
@@
 \end{equation}
-\newtext{
 where $P(\ts)$ is the probability density to get a particular value of TS,
@@
 null hypothesis (source flux $\Phi=0$) residing on the edge of parameter
-space and the model hypothesis adding a single degree of freedom (the source flux).}
+space and the model hypothesis adding a single degree of freedom (the source flux).
 It leads to the often quoted result $\sqrt{TS}=\sigma$, where 
@@
 
-\newtext{
-
-\subsection{\newtext{Point-like Source Simulations Over a Structured Background}}
+\subsection{Point-like Source Simulations Over a Structured Background}
 \label{validation_over_plane}
@@
 For the elliptical spatial models, \rsixeight is computed by numeric integration.
-
-}
 
@@
 angular distances comparable to or smaller than the size of the LAT PSF. 
-\newtext{ To assess the plausibility of source confusion for sources with
+To assess the plausibility of source confusion for sources with
 $\tsext\ge16$, we developed an algorithm to test if a region contains
@@
 difference of the positions of the two sources without any limitations
-on the fit parameters.}
+on the fit parameters.
 
@@
 
-\newtext{
 We considered using 
@@
 \cite{aic_stats_book}.
-}
 
@@
 
-\newtext{
 Six extended SNRs were
@@
 and W30
-\citep{w51c,ic443,w28,w44,cygnus_loop_lat,w30_lat}.}
+\citep{w51c,ic443,w28,w44,cygnus_loop_lat,w30_lat}.
 Using photons
@@
 of the background model that were performed.
-\newtext{In Table~\ref{fake_2fgl_sources}, we summarize the sources in
+In Table~\ref{fake_2fgl_sources}, we summarize the sources in
 the 2FGL catalog that we have concluded here correspond to residuals
-induced by not modeling the extensions of nearby extended sources.}
+induced by not modeling the extensions of nearby extended sources.
 
@@
 2FGL\,J1614.9$-$5212), we refit 2FGL\,J1615.2$-$5138 as two point-like
-sources.  \newtext{Because $\tsinc=35.1$ is less than $\tsext=46.5$, we conclude that
-this emission does not originate from two closely-spaced point-like sources.}
+sources.  Because $\tsinc=35.1$ is less than $\tsext=46.5$, we conclude that
+this emission does not originate from two closely-spaced point-like sources.
 
@@
 not appear physically separate. 
-\newtext{It is very close to the position of 2FGL\,J1632.4$-$4753c
-and does not show spatially separated emission in the observed photon distribution.}
+It is very close to the position of 2FGL\,J1632.4$-$4753c
+and does not show spatially separated emission in the observed photon distribution.
 We therefore removed this source from our model of the
@@
 instead as two point-like sources.
-\newtext{Because $\tsinc=10.8$ is less than $\tsext=18.5$, we conclude that this emission
-does not originate from two nearby point-like sources.}
-
-\newtext{With this model, 2FGL\,J1837.3$-$0700c was found to have an
-extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$.}
+Because $\tsinc=10.8$ is less than $\tsext=18.5$, we conclude that this emission
+does not originate from two nearby point-like sources.
+
+With this model, 2FGL\,J1837.3$-$0700c was found to have an
+extension $\sigma=0\fdg33\pm0\fdg07_\stat\pm0\fdg05_\sys$.
 While fitting the extension of 2FGL\,J1837.3$-$0700c,
@@
 \startdata
-\multicolumn{6}{c}{\newtext{Isotropic Background}} \\
+\multicolumn{6}{c}{Isotropic Background} \\
 \hline
@@
           &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
-\cutinhead{\newtext{Galactic Diffuse and Isotropic Background\tablenotemark{(b)}}}
+\cutinhead{Galactic Diffuse and Isotropic Background\tablenotemark{(b)}}
       1.5 &  $2.3\times 10^{-8}$ &           90741 &     63    &   \nodata   & \nodata     \\
@@
 \tablenotetext{(b)}{
-\newtext{For the Galactic simulations, the quoted fluxes are
+For the Galactic simulations, the quoted fluxes are
 the fluxes for sources placed 
-in the Galactic center. The actual fluxes are scaled by Equation~\ref{scale_flux_by_background}.}
+in the Galactic center. The actual fluxes are scaled by Equation~\ref{scale_flux_by_background}.
 }
@@
     also tabulated.  
-    \newtext{The top rows are the simulations on top of an isotropic background and
+    The top rows are the simulations on top of an isotropic background and
     the bottom rows are the simulations on top of the Galactic diffuse and isotropic
-    background.}
+    background.
 }
@@
     \caption{
-    \newtext{
     Cumulative distribution of \tsext
     for sources simulated on top of the Galactic diffuse and isotropic background.
-    }
     }\label{tsext_plane_plot}
@@
     \caption{
-    \newtext{The distribution of \ts values when fitting 985 statistically
+    The distribution of \ts values when fitting 985 statistically
     independent simulations of W44. (a) is the distribution of \ts values
@@
     to an elliptical disk spatial model.
-    }
     }\label{ts_comparison_w44sim}
@@
     \caption{
-    \newtext{The distribution of fit parameters
+    The distribution of fit parameters
     for the Monte Carlo simulations of W44.
@@
     the simulated values of the parameters.
-    }
     }\label{bias_w44sim}
@@
 \tablecomments{
-\newtext{For each new extended source, we list nearby 2FGL
+For each new extended source, we list nearby 2FGL
 soruces that we have concluded here correspond to residuals induced by not
-modeling the extensions of nearby extended sources.}
+modeling the extensions of nearby extended sources.
 }
@@
   removed from the background model.
-  \newtext{From left to right, these sources are 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254.}
+  From left to right, these sources are 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254.
   The lower right inset is the model predicted emission from a point-like
@@
     are the best fit power-law spectral models of
-    these sources. \newtext{Puppis A has a spectral index of
+    these sources. Puppis A has a spectral index of
     $2.21\pm0.09$ and $\gamma$-Cygni has an
-    index of $2.42\pm0.19$.}
+    index of $2.42\pm0.19$.
     The spectral errors are statistical only.
@@
   this source assuming a radially-symmetric uniform disk model.
-  \newtext{The three black crosses represent background 2FGL sources.
+  The three black crosses represent background 2FGL sources.
   The three star-shaped markers (colored green) represent other 2FGL sources
@@
   They are (from left to right) 2FGL\,J0853.5$-$4711, 2FGL\,J0855.4$-$4625, and 
-  2FGL\,J0848.5$-$4535.}
+  2FGL\,J0848.5$-$4535.
   The circular and square-shaped
@@
     symmetric uniform disk model.  
-    \newtext{The two black crosses represent  background 2FGL sources and
+    The two black crosses represent  background 2FGL sources and
     the star-shaped
@@
     source that was removed from the background
-    model.} The contours (colored light blue) correspond to the \tev
+    model. The contours (colored light blue) correspond to the \tev
     image of HESS\,J1616$-$508 (left) and HESS\,J1614$-$518 (right)
@@
   additional background 2FGL sources subtracted in (b).
-  \newtext{The star-shaped marker (colored green) represents 
-  2FGL\,J1634.4$-$4743c, another 2FGL source that was removed from the background model.}
+  The star-shaped marker (colored green) represents 
+  2FGL\,J1634.4$-$4743c, another 2FGL source that was removed from the background model.
   The contours (colored light blue) correspond to the \tev image of
@@
   blue) represent the 2FGL and the relocalized positions respectively of
-  two background 2FGL sources subtracted in (b).  \newtext{The star-shaped marker
+  two background 2FGL sources subtracted in (b).  The star-shaped marker
   (colored green) represents 2FGL\,J1835.5$-$0649, another 2FGL source that was removed from the
-  background model.}  The contours (colored light blue) correspond to
+  background model.  The contours (colored light blue) correspond to
   the \tev image of HESS\,J1837$-$069
@@
   uniform disk model.  
-  \newtext{The star-shaped marker (colored green)
+  The star-shaped marker (colored green)
   represents 2FGL\,J2019.1+4040,
-  a 2FGL source that was removed from the background model.}
+  a 2FGL source that was removed from the background model.
   2FGL\,J2021.5+4026

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_analysis_method.tex
update

\subsection{Off-peak Analysis Method}
\label{subsec:off_peak_analysis}

We develope a procedure for characterizing any emission found
in off-peak phase internals for the pulsars in this catalog.  
This proceure used both the spectral and spatial characteristics
of any observed emission to determine the physical origin of the emission.

Pulsar wind nebula are expected in many cases to be spatially
extended. For example, \velax and HESS\;J1825-137 are PWN
that have been observed by the \lat to be spatially extended
\citep{LAT_collaboration_Vela_X_2010,LAT_collaboration_HESS_J1825_2011}.
On the other hand, not all pulsar wind nebula are expected to be
significantly spatially resolved at \gev energies due to the finite
instrument resolution of the LAT. For example, the Crab nebula appears
as a point-like source in the LAT but is distinuished in the off-peak
from the Crab pulsar by its hard spectrum for E$\gtrsim$1 \gev.
\citep{LAT_collaboration_crab_2010}.

On the other hand, a previous analysis by the Fermi LAT collaboration
found seven off-peak regions to have significant emission which is
point-like in nature that is characterized by a pulsar-like cutoff
spectrum \citep{LAT_collaboration_PWNCAT_2011}.  We can thefore use
either spatial extension or significant emission at high energy to
distinguish the PWN scenario and point-like emission with a cutoff
spectrum to distingiugh the pulsar scenario.

To perform this test, we used the likelihood fitting pacakge \pointlike
to study the spatial character of emission in the off-peak regions
and \gtlike in binned model to study the spectral character of
the emission. These tools provide complementary features and this
method is very similar to the approach used in the second \lat catalog
\citep{LAT_Collaboration_2FGL_2012} and a followup search for spatially
extended sources \citep{LAT_collaboration_extended_search_2012}.

For this analysis, we build a model of the sky consistent with the
second \lat catalog. We included as background sources all
nearby sources from the second 
and used the same background model as the catalog \citep{LAT_Collaboration_2FGL_2012}.
Our analysis energy range varied from 100 \mev to 316 \gev.
For this analysis, we removed all of the on-peak photons before binning the data
and scaled the exposure to fit the all-phase flux assuming 
constant emission with phase.

With this model of the sky, we used fit an assumed source in the off-peak
emission.  First, we assumed the potential emission to have a point-like
spatial model and (unless otherwise noted) a power-law spectral model.
We used \pointlike to fit the position of the off-peak region following
the procedure described in \cite{LAT_Collaboration_2FGL_2012}.  We used
the best fit positions obtained through \pointlike and performed a
spectral analysis using \gtlike.

After fitting the position of a source, we use \gtlike to perform a likelihood-ratio test for
the detection of the source. Here, \ts is defined as
\begin{equation}
  \ts = 2 \log(\likelihood_\text{pt}/\likelihood_\text{bg})
\end{equation}
where $\likelihood_\text{pt}$ is the Poission likelihood for a model including the source and $\likelihood_\text{bg}$
the likelihood for a model not including the source.
We set the threshold for detection of signfiicant emission at $\ts>25$, 
corresponding to a significance just over $4\sigma$ \citep{LAT_Collaboration_1FGL_2010}.

For the significantly-detected source, after fitting the position of the source
we test to see if the spectrum of the source is significantly 
cutoff following the description in 
\cite{LAT_collaboration_PWNCAT_2011}. After fitting the source using \gtlike
with both a power-law and exponentially-cutoff spectral model, we
define the likelihood ratio test for the cutoff test as
From \gtlike, we obtained  
\begin{equation}
  \tscut= 2 \log(\likelihood_\text{cutoff}/\likelihood_\text{pt})
\end{equation}
where $\likelihood_\text{cutoff}$ is the poisson likelihood for a model including the source
with a cutoff spectral model.
We set the threshold for detecting a significant cutoff at 
$\tscut>16$, corresponding to a $4\sigma$ detection \citep{LAT_collaboration_PWNCAT_2011} .

We used \pointlike to test whether the observed emisssion was
spatially extended, assuming a radially-symmetric Gaussian spatial
model.  \pointlike can simulatenously fit the position and the
extension of the assumed Gaussian source, following the description in
\citep{LAT_collaboration_extended_search_2012}.  After the extension fit,
we refit the spectrum of the spatially extended source using \gtlike
and performed a likelihood ratio for the significance of the extenstion
of a source.  Following \cite{LAT_collaboration_extended_search_2012},
we define
\begin{equation}
  \tsext = 2 \log(\likelihood_\text{ext}/\likelihood_\text{pt})
\end{equation}
where $\likelihood_\text{ext}$ is the Poisson likelihood assuming the
source is spatially extended. We set the threshold for detecting the
significance of a spatially extended source at $\tsext>16$, corresponding
to a $4\sigma$ detection \citep{LAT_collaboration_extended_search_2012}.

For sources that are not significantly deteced over the energy range,
we compute flux upper limits for the region assuming a fixed spectral
index of 2.0.  We also computed a pulsed upper limit assuming a canonical
pulsar spectrum with an index of -1.7 and a cutoff energy of 3 \gev.

To better assess the spectral charter of any emission in the off-peak
region, we performed a spectral analsyis in three smaller energy bins
(100 \mev to 1 \gev, 1 \gev to 10 \gev, and 10 \gev to 316 \gev). In each
energy bin, we fit the flux and the spectral index of the source. For
sources not singificantly detected, we compute a flux upper limit
(assuming a fixed spectral index of 2) in the energy bin.

Following the discovery of variable emission from the Crab nebula
by the LAT, it is interesting to search for other variable PWN
\citep{LAT_Collaboration_Crab_Flare_2011}.  Therefore, we testing all the
off-peak regions for variable emission.  We divided the 3 year time range
into 36 month-long intervals and fit the flux of the source indepnedently
in each time range. We compute this significance of the variability
using \tsvar following the same procedure as the second LAT catalog
\citep{LAT_Collaboration_2FGL_2012}.  Since we have 36 months of data,
the null distribution (assuming no variability) should follow $\chi^2$
distribution with 35 degrees of freedom, and we set the detection critera
for significant variability at $\tsvar>91.7$, corresponding to a $4\sigma$
significance detection threshold.

In many situations, this algorithm would fail due to not modeling the
position of nearby sources. We expect to be more sensitive to nearby
sources than the second \lat catalog both because of our expanded data
set (three years of observations instead of two) and also because, for
very bright pulsars, we are more sensitivite to other sources once the
pulsar has been removed.

Unfortuantly, in many situations, this algorithm failed due to
systematics associated with the modeling nearby sources. The large and
energy depdended point-spread function of the \lat causes the analysis
of any one source to be sensitively affected by the modeling of nearby
sources. Therefore, we had to, in many situations, iteratively improve
the model of a region by including new sources. This procedure 
involved generating maps of residual test statistic assuming the
presence of a new source (of a fixed spectral index of 2) and looking
for regions with $\ts\ge25$.  For these positions, we would include a
new source into our model, fit the position and spectrum of this source,
and iterate until there was no remaining $\ts\ge25$ emission.

Even so, there are still some linering regions which have significant
emission but which remain particular difficult to model and understand
the origion of the emission for.  These issues are most likely due to
systematics associated with the model of the galactic diffuse emission
in the region and issues associated with modeling nearby sources. We
will flag these problematic regions in our analysis.

\todo[inline]{Describe special case of Crab spectrum}

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_introduction.tex
update

@@
 the peaks of the pulsar's light curve. This potential DC emission could originate
-in the pulsar's winds, from inside the pulsar's magnetosphere, or 
-the emission could be spatially coincidental but physically
-unrealted to the pulsar.
+in the pulsar winds, from inside a pulsar's magnetosphere, or 
+the emission could be physically unrealted to the pulsar.
 
-The \gev emission in the off-peak from LAT-detected pulsars has been studied in several previous 
-publications. In particular, the spatially-extended \velax pulsar wind nebula has
-been detected by the LAT in the off-peak phase region of the Vela pulsar \citep{LAT_collaboration_Vela_X_2010}
-and the Crab nebula has been detected by the LAT \citep{LAT_collaboration_crab_2010}.
-Surprisingly, this \gev emission from the Crab nebula was found to be variable
-in time \citep{LAT_Collaboration_Crab_Flare_2011}.
+\gev emission in the off-peak regions around LAT-detected
+pulsars has been studied in several previous publications. In
+particular, the spatially-extended \velax pulsar wind nebula has
+been detected by the LAT in the off-peak region of the Vela pulsar
+\citep{LAT_collaboration_Vela_X_2010} and the Crab nebula has been
+detected by the LAT \citep{LAT_collaboration_crab_2010}.  Surprisingly,
+this \gev emission from the Crab nebula was found to be variable in
+time \citep{LAT_Collaboration_Crab_Flare_2011}.
 
 Most prominently, a dedicated analysis was performed using LAT data of
-the off-peak emission of 54 LAT-detected pulsars using 16 months of survey observations
-\citep{LAT_collaboration_PWNCAT_2011}. 
-The search discovered ten pulsars wich significant off-peak emission.
-Along with \velax and the Crab nebula, the 
-search discovered a source coincident with the TeV source HESS\;J1023-575
-in the off-peak window of PSR\;J1023-5746. In addtion, four of hte other
-regions showed a significantly cutoff pulsar-like spectrum and are
-suspected to be be of magnetospheric origin.
+the off-peak emission of 54 LAT-detected pulsars using 16 months of survey
+observations \citep{LAT_collaboration_PWNCAT_2011}.  The search discovered
+ten pulsars with significant off-peak emission.  Along with \velax and the
+Crab nebula, the search discovered a source coincident with the TeV source
+HESS\;J1023-575 in the off-peak window of PSR\;J1023-5746. In addtion,
+four of the other regions showed a significantly cutoff pulsar-like
+spectrum and are suspected to be of magnetospheric origin.
 
 We expand upon this previous work by searching in the off-peak region
-of all 107 pulsars presented in this catalog. In addition to the larger
-list of pulsars, in this earch we use an expanded data set, a larger energy range,
+of all 117 pulsars in this catalog. In addition to the larger list of
+pulsars, we use an expanded observation time, a larger energy range,
 and an improved analysis method.

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_phase_selection.tex
update

\subsection{Off-peak Phase Selection}
\label{subsec:off_peak_defintion}

To study the off-peak emission of \lat-detected pulsars, we first
developed a systematic method to define the off-peak region of a pulsar.
The primary constraint for this method was for it to be systematic,
model independent, and computationally efficient.

The method we developed proceeds by deconstructing the pulsar's
phaseogram into simple Bayesian Blocks using the 
algorithm described in \cite{Jackson_Bayesian_Blocks_2003}.
To produce Bayesian Blocks on a periodic phaseogram, we applied the blocks
three sets of the data from a phase of -1 to 2 and selected the blocks from a
phase of 0 to 1.

TO improve the off-peak region definition,
we first optimized the pulsar phaseogram
by varying the minimum energy and radius of the included photons to optimize
the H-test. We then selected the lowest block to be the off-peak
region, but removed 10\% of the emission from either side of the block
to avoid potential contamination.

There is one free parameter in the Baysian Block algorithm called
$\text{ncp}_\text{prior}$ which modifies the probability that the
algorithm will divide a block into smaller intervals. For our situation,
we found that setting $\text{ncp}_\text{prior}=8$ protected against
the Bayesian Block decomposition containing unphysically small blocks.
For a few very marginally-detected pulsars, the algorithm failed
decomposed the phaseogram into multiple blocks
and in these situations we decreased $\text{ncp}_\text{prior}$ until the
algorithm succeeded.

In some situations, there can be two well defined off-peak regions between two
pulsed peaks. The method we used to select a second phase range was
to take the second lowest Bayesian block
but only when the emission in this block is consistent with the emission in
the lowest block (at the 99\% confidence level) and when the
second block contained at least half as much phase as the first block.

Figure \figref{off_peak_select} shows the energy-and-radius optimized
light curve and the off-peak selection for a representative sample of pulsars.
The off-peak definition for all pulsars is contained in the auxiliary material.

\begin{figure}
  \ifdefined\bwfigures
   % plots from $pwndata/off_peak/off_peak_bb/pwncat2/v6/plots/
  \plotone{off_peak_select_bw.eps}
  \else
  \plotone{off_peak_select_color.eps}
  \fi
  \caption{The phaseogram and off-peak selection for 
  (a) PSRJ0007+7303, (b) PSRJ0534+2200, (c) PSRJ0633+1746, (d) PSRJ0835-4510,
  (e) PSRJ1702-4128, (f) PSRJ1747-4036, (g) PSRJ1801-2451, and (h) PSRJ2021+4026.
  The black histogram represents the energy-and-radius optimized phaseogram.
  The gray lines (colored red in the electronic version)
  represent the Bayesian block decomposition of the pulsar light curves.
  The hatched areas represent the off-peak regions selected by this method.}
  \label{fig:off_peak_select}
\end{figure}

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_results.tex
update

--- 2012-06-06 pwncatalog/PWNCAT2/paper/subsections/results.tex
@@
 
-First, we tested the sources to see if they
-were spatially extended. The localization results are in \tabref{offpeak}.
+After analyzing the off-peak emission using the pipeline described
+in \subsecref{off_peak_analysis}, we consider any emission in the
+off-peak region to be magnetospheric in nature if the emsision is
+not significantly-extended and has a significantly-cutoff spectrum.
+We consider the emission to originate in the pulsar wind if it is
+spatially extended or had a hard spectral index.
+If the source is point-like and had a soft spectrum, or if it 
+is spatially extended but the extension is biased by modeling
+of the background, we are unable to determine the origin of the emission.
+
+A summay of the reuslts of the pipepline can be found in \tabref{offpeak}.
+It includes off off-peak phase ranges selected using the method described
+in \subsecref{off_peak_defintion}.
+This table includes \ts, \tsext, and \tscut
+for the significantly detected pulsars (with $\ts>25$).
+This table also includes the best fit flux and spectral index for these pulsars assuming
+the best hypothesis (either point-like, spatially-extended, or expontentially cutoff).
+For the sources that are significantly cutoff, the spectral index refers to the index
+from the fit of a cutoff spectral model and the final column includes the cutoff energy derived from the fit.
 
@@
 \end{deluxetable}
-
-Next, we performed a spectral analysis over all energy using the best
-fit morphology. XXX shows the results of the all energy
-analysis of the off-peak emission for each pulsar.
-
-Next, we fit a powerlaw independently in each energy
-bin. XXX shows the results of the analysis in separate
-energy bins of each pulsar.
-
-Finally, we tested sources to see which were
-variable. XXX shows the results of the cutoff test for
-pulsars with significant low-energy emission.
 
@@
 
-We tested all sources for variability.
+Consistent with \citep{LAT_Collaboration_Crab_Flare_2011}, we found
+the Crab nebula to be highly variable with \tsvar=XXXX.  Besides that,
+we found no significantly variable off-peak emission.  The results of
+the variability test are contained in the auxiliary information.
 
-Special cases:
+The results of the spectral analysis in smaller energy bands described
+in section \secref{peak_analysis} are included in the auxiliary
+information. In addition, upper limits computed assuming a powerlaw
+spectral model and a canonical pulsar spectrum are included in the
+auxiliary information.
+
+Results:
 \begin{itemize}
-  \item Crab has a funny spectrum, we have (so far) fixed it to
-  \item \velax
+  \item List of all XXX detections
+  \item For each pulsar, is it a 
+    \begin{itemize}
+      \item Magnetospheric emission
+      \item PWN emission
+      \item Region where the fit shows trouble for some reason.
     \end{itemize}
+\end{itemize}
+
+In our analysis, we detected the the Vela X PWN (associated with PSRJ0835$-$4510), the Crab Nebula (associated
+with PSRJ0534+2200), and MSH 15$-$52 (associated with PSRJ1513-5908).
+
+What to say about PSRJ1023-5746
+
+Sources we detect as clearly magnetospheric
+
+Special cases/problem cases:
+\begin{itemize}
+  \item PSRJ0101-6422: Very weird spectrum
+  \item PSRJ1112-6103: Very close to MSH 11~62 (arXiv:1202.3371v1). Nearby source is 2FGL J1112.1-6040. Significant extension.
+  \item When fitting PSRJ1119-6127, description of adding nearby point
+  source to represent emission residual from o represent residual from
+  PSRJ1112-6103 looking spatially
+    extended.
+  \item PSRJ1418-6058 and PSRJ1420-6048, very difficult to analyze because both very near eachother.
+  \item Something about the complciated Gamma Cygni PSR: PSRJ2021+4026
+  \item PSRJ1105-6107: something about adding source to background model that is very nearby. \todo{See what OZLEM is doing}.
+  \item PSRJ1648-4611 (what to do about nearby 2FGL soruce and other residual emission. Is this paper relevant: http://arxiv.org/pdf/1111.2043.pdf???)?
+  \item What to do about emission from PSR J1023 at low energy???
+  \item PSRJ0908-4913: waht to say about far localization?
+\end{itemize}
+
+\todo[inline]{Describe how we present the point-like hypothesis for signifciant extended soures if the extension fails for some reason}

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_analysis_method.tex
update

@@
 
-We develope a procedure for characterizing any emission found
-in off-peak phase internals for the pulsars in this catalog.  
-This proceure used both the spectral and spatial characteristics
+We developed a procedure for characterizing emission found
+in off-peak phase region for all pulsars in this catalog.  
+This procedure used both the spectral and spatial characteristics
 of any observed emission to determine the physical origin of the emission.
 
-Pulsar wind nebula are expected in many cases to be spatially
-extended. For example, \velax and HESS\;J1825-137 are PWN
-that have been observed by the \lat to be spatially extended
+PWNe are often expected to be spatially
+resolvable at GeV energies. For example, \velax and HESS\;J1825-137 are PWN
+that have been spatially resolved by the \lat 
 \citep{LAT_collaboration_Vela_X_2010,LAT_collaboration_HESS_J1825_2011}.
-On the other hand, not all pulsar wind nebula are expected to be
-significantly spatially resolved at \gev energies due to the finite
+On the other hand, not all PWN are expected to be
+significantly spatially resolved due to the finite
 instrument resolution of the LAT. For example, the Crab nebula appears
-as a point-like source in the LAT but is distinuished in the off-peak
-from the Crab pulsar by its hard spectrum for E$\gtrsim$1 \gev.
+as a point-like source in the LAT but is distinguished from the Crab
+pulsar in the off-peak region by its hard spectrum for E$\gtrsim$1 \gev.
 \citep{LAT_collaboration_crab_2010}.
 
-On the other hand, a previous analysis by the Fermi LAT collaboration
-found seven off-peak regions to have significant emission which is
-point-like in nature that is characterized by a pulsar-like cutoff
-spectrum \citep{LAT_collaboration_PWNCAT_2011}.  We can thefore use
-either spatial extension or significant emission at high energy to
-distinguish the PWN scenario and point-like emission with a cutoff
-spectrum to distingiugh the pulsar scenario.
+On the other hand, pulsars can have DC emission in the off-peak region
+due to the geometry of the pulsar's magnetosphere.  A previous analysis
+by the LAT collaboration found five off-peak regions to have significant
+emission which is point-like in nature that is characterized by a
+pulsar-like cutoff spectrum \citep{LAT_collaboration_PWNCAT_2011}.
+We can therefore use either spatial extension or a hard spectrum to
+distinguish a PWN scenario and point-like emission with a cutoff spectrum
+to distinguish the pulsar scenario.
 
-To perform this test, we used the likelihood fitting pacakge \pointlike
+To perform this test, we used the likelihood fitting package \pointlike
 to study the spatial character of emission in the off-peak regions
@@
 method is very similar to the approach used in the second \lat catalog
-\citep{LAT_Collaboration_2FGL_2012} and a followup search for spatially
+\citep{LAT_Collaboration_2FGL_2012} and a follow up search for spatially
 extended sources \citep{LAT_collaboration_extended_search_2012}.
@@
 For this analysis, we build a model of the sky consistent with the
-second \lat catalog. We included as background sources all
-nearby sources from the second 
-and used the same background model as the catalog \citep{LAT_Collaboration_2FGL_2012}.
-Our analysis energy range varied from 100 \mev to 316 \gev.
-For this analysis, we removed all of the on-peak photons before binning the data
-and scaled the exposure to fit the all-phase flux assuming 
-constant emission with phase.
+second \lat catalog. We included as background sources all nearby
+sources from the second and used the same background model as the catalog
+\citep{LAT_Collaboration_2FGL_2012}.  Our analysis energy range varied
+from 100 \mev to 316 \gev.  For this analysis, we removed all of the
+on-peak photons before binning the data and scaled the exposure to fit
+the all-phase flux assuming constant emission with phase.
 
@@
 
-After fitting the position of a source, we use \gtlike to perform a likelihood-ratio test for
-the detection of the source. Here, \ts is defined as
+After fitting the position of a source, we use \gtlike to perform a
+likelihood-ratio test for the detection of the source. Here, \ts is
+defined as
 \begin{equation}
@@
 \end{equation}
-where $\likelihood_\text{pt}$ is the Poission likelihood for a model including the source and $\likelihood_\text{bg}$
-the likelihood for a model not including the source.
-We set the threshold for detection of signfiicant emission at $\ts>25$, 
-corresponding to a significance just over $4\sigma$ \citep{LAT_Collaboration_1FGL_2010}.
+where $\likelihood_\text{pt}$ is the Poisson likelihood for a model
+including the source and $\likelihood_\text{bg}$ the likelihood for a
+model not including the source.  We set the threshold for detection of
+significant emission at $\ts>25$, corresponding to a significance just
+over $4\sigma$ \citep{LAT_Collaboration_1FGL_2010}.
 
-For the significantly-detected source, after fitting the position of the source
-we test to see if the spectrum of the source is significantly 
-cutoff following the description in 
-\cite{LAT_collaboration_PWNCAT_2011}. After fitting the source using \gtlike
-with both a power-law and exponentially-cutoff spectral model, we
-define the likelihood ratio test for the cutoff test as
-From \gtlike, we obtained  
+For the significantly-detected source, after fitting the
+position of the source we test to see if the spectrum of the
+source is significantly cutoff following the description in
+\cite{LAT_collaboration_PWNCAT_2011}. After fitting the source using
+\gtlike with both a power-law and exponentially-cutoff spectral model,
+we define the likelihood ratio test for the cutoff test as From \gtlike,
+we obtained
 \begin{equation}
@@
 \end{equation}
-where $\likelihood_\text{cutoff}$ is the poisson likelihood for a model including the source
-with a cutoff spectral model.
-We set the threshold for detecting a significant cutoff at 
-$\tscut>16$, corresponding to a $4\sigma$ detection \citep{LAT_collaboration_PWNCAT_2011} .
+where $\likelihood_\text{cutoff}$ is the poisson likelihood for a model
+including the source with a cutoff spectral model.  We set the threshold
+for detecting a significant cutoff at $\tscut>16$, corresponding to a
+$4\sigma$ detection \citep{LAT_collaboration_PWNCAT_2011} .
 
@@
 sources. Therefore, we had to, in many situations, iteratively improve
-the model of a region by including new sources. This procedure 
-involved generating maps of residual test statistic assuming the
-presence of a new source (of a fixed spectral index of 2) and looking
-for regions with $\ts\ge25$.  For these positions, we would include a
-new source into our model, fit the position and spectrum of this source,
-and iterate until there was no remaining $\ts\ge25$ emission.
+the model of a region by including new sources. This procedure involved
+generating maps of residual test statistic assuming the presence of a
+new source (of a fixed spectral index of 2) and looking for regions with
+$\ts\ge25$.  For these positions, we would include a new source into our
+model, fit the position and spectrum of this source, and iterate until
+there was no remaining $\ts\ge25$ emission.
 

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_analysis_method.tex
udpate

@@
 This procedure used both the spectral and spatial characteristics
-of any observed emission to determine the physical origin of the emission.
+of any observed emission to determine its physical origin.
 
@@
 significantly spatially resolved due to the finite
-instrument resolution of the LAT. For example, the Crab nebula appears
-as a point-like source in the LAT but is distinguished from the Crab
+instrument resolution of the LAT. For example, the Crab nebula 
+cannot be resolved by that LAT LAT but is distinguished from the Crab
 pulsar in the off-peak region by its hard spectrum for E$\gtrsim$1 \gev.
@@
 On the other hand, pulsars can have DC emission in the off-peak region
-due to the geometry of the pulsar's magnetosphere.  A previous analysis
+due to the geometry of the pulsar magnetospheres.  A previous analysis
 by the LAT collaboration found five off-peak regions to have significant
-emission which is point-like in nature that is characterized by a
+emission which is point-like in nature and characterized by a
 pulsar-like cutoff spectrum \citep{LAT_collaboration_PWNCAT_2011}.
 We can therefore use either spatial extension or a hard spectrum to
-distinguish a PWN scenario and point-like emission with a cutoff spectrum
-to distinguish the pulsar scenario.
+distinguish PWN emission and point-like emission with a cutoff spectrum
+to distinguish magnetospheric emission.
 
-To perform this test, we used the likelihood fitting package \pointlike
+To perform this analysis, we used the likelihood fitting package \pointlike
 to study the spatial character of emission in the off-peak regions
@@
 second \lat catalog. We included as background sources all nearby
-sources from the second and used the same background model as the catalog
-\citep{LAT_Collaboration_2FGL_2012}.  Our analysis energy range varied
-from 100 \mev to 316 \gev.  For this analysis, we removed all of the
-on-peak photons before binning the data and scaled the exposure to fit
-the all-phase flux assuming constant emission with phase.
+sources from the second catalog and we also used the same background models 
+\citep{LAT_Collaboration_2FGL_2012}.  For out analysis, we used
+an energy range from 100 \mev to 316 \gev ($10^{5.5}$ \mev).  For this analysis, 
+we removed all photons from the on-peak emission and scaled the exposure so as to fit
+the all-phase flux assuming the emission was constant with phase.
 
-With this model of the sky, we used fit an assumed source in the off-peak
-emission.  First, we assumed the potential emission to have a point-like
+First, we assumed any potential emission in the off-peak region 
+to have a point-like
 spatial model and (unless otherwise noted) a power-law spectral model.
@@
 the procedure described in \cite{LAT_Collaboration_2FGL_2012}.  We used
-the best fit positions obtained through \pointlike and performed a
+the best fit positions obtained by \pointlike and performed a
 spectral analysis using \gtlike.
 
-After fitting the position of a source, we use \gtlike to perform a
-likelihood-ratio test for the detection of the source. Here, \ts is
-defined as
+With the best-fit position, we used \gtlike to 
+test the significance of the detection of the source.
+We define the 
+likelihood-ratio test for the detection of the source as
 \begin{equation}
@@
 
-For the significantly-detected source, after fitting the
-position of the source we test to see if the spectrum of the
-source is significantly cutoff following the description in
-\cite{LAT_collaboration_PWNCAT_2011}. After fitting the source using
-\gtlike with both a power-law and exponentially-cutoff spectral model,
-we define the likelihood ratio test for the cutoff test as From \gtlike,
-we obtained
+For the significantly-detected source, we tested to see if the spectrum of the
+source is significantly cutoff following the prescription in
+\cite{LAT_collaboration_PWNCAT_2011}. 
+We fit the source in \gtlike 
+with both a power-law and exponentially-cutoff spectral model
+and define the likelihood-ratio test for a cutoff spectrum as
 \begin{equation}
@@
 \end{equation}
-where $\likelihood_\text{cutoff}$ is the poisson likelihood for a model
-including the source with a cutoff spectral model.  We set the threshold
+where $\likelihood_\text{cutoff}$ is the Poisson likelihood for a model
+including the cutoff spectrum.  We set the threshold
 for detecting a significant cutoff at $\tscut>16$, corresponding to a
@@
 
-We used \pointlike to test whether the observed emisssion was
-spatially extended, assuming a radially-symmetric Gaussian spatial
-model.  \pointlike can simulatenously fit the position and the
-extension of the assumed Gaussian source, following the description in
-\citep{LAT_collaboration_extended_search_2012}.  After the extension fit,
+We used \pointlike to simultaneously fit the position and the
+extension of the assumed radially-symmetric Gaussian source, following the description in
+\citep{LAT_collaboration_extended_search_2012}.  
+After the extension fit,
 we refit the spectrum of the spatially extended source using \gtlike
-and performed a likelihood ratio for the significance of the extenstion
-of a source.  Following \cite{LAT_collaboration_extended_search_2012},
-we define
+We tested the significance of the spatial extension
+and computed the likelihood-ratio test for the significance of the extension:
 \begin{equation}
-  \tsext = 2 \log(\likelihood_\text{ext}/\likelihood_\text{pt})
+  \tsext = 2 \log(\likelihood_\text{ext}/\likelihood_\text{pt}).
 \end{equation}
-where $\likelihood_\text{ext}$ is the Poisson likelihood assuming the
+Here, $\likelihood_\text{ext}$ is the Poisson likelihood assuming the
 source is spatially extended. We set the threshold for detecting the
@@
 
-For sources that are not significantly deteced over the energy range,
-we compute flux upper limits for the region assuming a fixed spectral
-index of 2.0.  We also computed a pulsed upper limit assuming a canonical
-pulsar spectrum with an index of -1.7 and a cutoff energy of 3 \gev.
+The spectrum of the Crab nebula was uniquely challenging because the
+GeV spectrum contains both a falling synchrotron spectrum and an
+inverse component component \citep{LAT_collaboration_crab_2010}.
+To avoid unnecessary complications in our pipeline, for this
+particular source we used the best fit two-component spectral model from
+\cite{LAT_collaboration_crab_2012} and fit only the overall normalization
+of the source.
+
+For sources that are not significantly detected, we compute flux upper
+limits assuming a point-like spatial model and a fixed spectral index
+of 2.0.  We also compute pulsed upper limit assuming a canonical pulsar
+spectrum with an index of -1.7 and a cutoff energy of 3 \gev.
 
 To better assess the spectral charter of any emission in the off-peak
-region, we performed a spectral analsyis in three smaller energy bins
+region, we performed a spectral analysis in three independent energy bins
 (100 \mev to 1 \gev, 1 \gev to 10 \gev, and 10 \gev to 316 \gev). In each
-energy bin, we fit the flux and the spectral index of the source. For
-sources not singificantly detected, we compute a flux upper limit
-(assuming a fixed spectral index of 2) in the energy bin.
+bin, we independently fit the flux and the spectral index of the source.
+We also computed flux upper limit assuming a fixed spectral index of 2
+when the source was not significantly detected in the energy range.
 
-Following the discovery of variable emission from the Crab nebula
+Following the discovery of time-variable emission from the Crab nebula
 by the LAT, it is interesting to search for other variable PWN
-\citep{LAT_Collaboration_Crab_Flare_2011}.  Therefore, we testing all the
-off-peak regions for variable emission.  We divided the 3 year time range
-into 36 month-long intervals and fit the flux of the source indepnedently
-in each time range. We compute this significance of the variability
-using \tsvar following the same procedure as the second LAT catalog
-\citep{LAT_Collaboration_2FGL_2012}.  Since we have 36 months of data,
-the null distribution (assuming no variability) should follow $\chi^2$
-distribution with 35 degrees of freedom, and we set the detection critera
+\citep{LAT_Collaboration_Crab_Flare_2011}.  Therefore, we tested all 
+off-peak regions for variability.  We divided the 3-year time range
+into 36 month-long intervals and fit the flux of the source independently
+in each time range. We computed the significance of variability
+with a likelihood-ratio test by computing \tsvar following the procedure of 2FGL
+\citep{LAT_Collaboration_2FGL_2012}.  Since we divided our time range into 
+36 months-long bins, the null distribution for $\tsvar$ follows a $\chi^2$
+distribution with 35 degrees of freedom. We set the detection criteria
 for significant variability at $\tsvar>91.7$, corresponding to a $4\sigma$
@@
 
-In many situations, this algorithm would fail due to not modeling the
-position of nearby sources. We expect to be more sensitive to nearby
+In many situations, our pipeline was significantly biased due to systematic
+errors associated with not modeling nearby sources.
+We are more sensitive to nearby
 sources than the second \lat catalog both because of our expanded data
-set (three years of observations instead of two) and also because, for
-very bright pulsars, we are more sensitivite to other sources once the
-pulsar has been removed.
+set (3 years of observations instead of 2) and also because, for
+very bright pulsars, we are more sensitive to nearby sources once
+the strong contribution from the pulsar has been removed.
 
-Unfortuantly, in many situations, this algorithm failed due to
-systematics associated with the modeling nearby sources. The large and
-energy depdended point-spread function of the \lat causes the analysis
+The large and energy dependent point-spread function of the \lat causes the analysis
 of any one source to be sensitively affected by the modeling of nearby
 sources. Therefore, we had to, in many situations, iteratively improve
-the model of a region by including new sources. This procedure involved
+the model of a region by including new background sources. 
+We modeled these sources by
 generating maps of residual test statistic assuming the presence of a
-new source (of a fixed spectral index of 2) and looking for regions with
-$\ts\ge25$.  For these positions, we would include a new source into our
+new source (of a fixed spectral index of 2) and looking for residuals with
+$\ts\ge25$. In these situations, we would include a new source into our
 model, fit the position and spectrum of this source, and iterate until
-there was no remaining $\ts\ge25$ emission.
+there was no remaining significant residual.
 
-Even so, there are still some linering regions which have significant
-emission but which remain particular difficult to model and understand
-the origion of the emission for.  These issues are most likely due to
-systematics associated with the model of the galactic diffuse emission
-in the region and issues associated with modeling nearby sources. We
-will flag these problematic regions in our analysis.
-
-\todo[inline]{Describe special case of Crab spectrum}
+Even so, there are still some lingering regions for where we were unable
+to obtain an unbiased fit.  the emission for.  These issues are most
+likely due to systematics associated with the model of the galactic
+diffuse emission and issues associated with modeling nearby sources.
+The most common symptom of a failed fit is a diverging localization
+or an unphysically large extension which causes the source model
+to incorporate multiple background sources. Systematics associated
+with modeling extended sources are discussed more thoroughly in
+\citep{LAT_collaboration_extended_search_2012}.  For the currently
+analysis, we flagged these problematic regions 
+and do not attempt a complete understanding of the region.

### 2012-08-30 fermi/snrlim/code/loop.py
remove tevcat

@@ -1,0 +1,17 @@
+from lande.utilities.save import loaddict
+from lande.utilities.jobtools import JobBuilder
+
+superfile='$superfile/snrdata.yaml'
+
+snrs=loaddict(superfile).keys()
+params=dict(name=snrs,
+            snrdata='$superfile/snrdata.yaml',
+            latdata='$snrlimcode/snrlatdata.yaml')
+
+
+b = JobBuilder(
+    savedir='$snrlimdata/v1',
+    params=params,
+    code='$snrlimcode/run.py',
+    short_folder_names=True)
+b.build()

### 2012-08-30 papers/tevcat/draft_v0/figures.tex
first version of draft

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/Plan_gal.eps}
\caption{Residual counts map of the Galactic Plane above 10 GeV. The galactic and isotropic diffuse emission are subtracted using the files described in section 4.2 with a normalization of 1. All sources associated to Blazars are subtracted using the spectral parameters listed in the hard source list(+ citer Hard source list). Excesses visible in this map are due to Galactic sources emitting above 10 GeV observed by the LAT. The counts map is smoothed with a Gaussian of 0.27$\degr$.
\label{fig:PlanGal}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[]{figures/HESSJ1303m631.eps}
\caption{Counts map of the region of HESS~J1303--631. We subtracted the Galactic and isotropic diffuse emission. The counts map is smoothed by a 0.27$\degr$ gaussian corresponding to the PSF above 10 GeV. The green star show the position of the SNR Kes 17, the blue square represent the position of PSR~J1301--6305. The small and big circles respectively show the extension of TeV gaussian proposed by \cite{2005AA...439.1013A} and the extension of the disk derived in this work.
\label{1303}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/out_errorbar_best_fit.eps}
\caption{Integrated flux of the detected sources as a function of the power-law index between 10 and 316 GeV. The green circles show the sources associated to pulsar detected by the LAT while the red squares represents the sources without pulsar detected in GeV energy ranges. The error bar shows the statistical and systematic uncertainties added in quadrature.  
\label{fig:fluxvssize}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/index_vs_size.eps}
\caption{Index of the sources as a function of the extension found for each detected source. The green circles show the sources associated to pulsar detected by the LAT while the red squares represents the sources without pulsar detected in GeV energy ranges. The error bar shows the statistical and systematic uncertainties added in quadrature. 
\label{fig:indexvssize}}
\end{figure}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=0.5\textwidth]{figures/0FGLJ1958.12848.eps}
%\caption{SED of MGRO J1958$+$2848. The red and blue points show respectively the \emph{Fermi}-LAT and ... points. The black error bars show the statistical and   systematic uncertainties added in quadrature. The black line corresponds to the best fit obtained using the LAT data. The dashed line correspond to the model of PSR J... taken from \cite{2012ApJS..199...31N}.
%\label{fig:1}}
%\end{figure}

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1708.eps}
\label{fig:hess1708}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ0632.eps}
\label{fig:mgroj0632}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ1908.eps}
\label{fig:mgro1908}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ201937.eps}
\label{fig:mgro2019}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ2228.eps}
\label{fig:mgroj2228}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/VERJ0006.eps}
\label{fig:verj0006}
}
\caption{\label{fig:sedsourcespuls}SED of the sources better described by a point--like source and with a pulsar within 0.5$\degr$. The blue points show the TeV points taken from \textbf{Add the papers}. The red circles and the magenta squares show respectively the SED without the pulsar included in the model and with the pulsar included in the model. The black error bars show the statistical and   systematic uncertainties added in quadrature. The dashed line correspond to the model of the associated pulsars sumarized in \ref{tab:pulsarfit} taken from \cite{2012ApJS..199...31N}. In the case of MGRO J1908+06, the red SED was derived assuming a point-like source as determined in tab. \ref{tab:GeVmorph} while the magenta SED was derived assuming the TeV shape.}
\end{figure}

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1018.eps}
\label{fig:hessj1018}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1023.eps}
\label{fig:hessj1023}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1418.eps}
\label{fig:hessj1418}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1458.eps}
\label{fig:hessj1458}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1718.eps}
\label{fig:hessj1718}
}
\caption{\label{fig:sedsourcespuls2}SED of the sources better described by the TeV shape and with a pulsar within 0.5$\degr$. The blue points show the TeV points taken from \textbf{rajouter tous les papiers}. The red circles and the magenta squares show respectively the SED without the pulsar included in the model and with the pulsar included in the model. The black error bars show the statistical and   systematic uncertainties added in quadrature. The dashed line correspond to the model of the associated pulsars sumarized in \ref{tab:pulsarfit} taken from \cite{2012ApJS..199...31N}.}
\end{figure}

\begin{figure}[h!]
\centering

\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1804.eps}
\label{fig:hessj1804}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1833.eps}
\label{fig:hess1833}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ0631.eps}
\label{fig:mgroj0631}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ1958.eps}
\label{fig:mgroj1958}
}

\caption{\label{fig:sedsourcespuls3}SED of the sources better described by the TeV shape and with a pulsar within 0.5$\degr$. The blue points show the TeV points taken from \textbf{rajouter tous les papiers}. The red circles and the magenta squares show respectively the SED without the pulsar included in the model and with the pulsar included in the model. The black error bars show the statistical and   systematic uncertainties added in quadrature. The dashed line correspond to the model of the associated pulsars sumarized in \ref{tab:pulsarfit} taken from \cite{2012ApJS..199...31N}.}
\end{figure}

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/HESSJ1420.eps}
\label{fig:hessj1420}}
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/HESSJ1420.eps}
\label{fig:hessj1420hadro}}
\caption{SED of . Top : Leptonic scenario. Bottom : Hadronic scenario. 
}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1356.eps}
\caption{SED of
\label{fig:hess1356}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1119.eps}
\caption{SED of 
\label{fig:hessj1119}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1303631leptdalton.eps}
\caption{SED of 
\label{fig:hessj1303}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1841055.eps}
\caption{SED of HESS~J1841-055
\label{fig:1841}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1848.eps}
\caption{SED of HESS~J1848
\label{fig:1848}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1026.eps}
\caption{SED of HESS~J1026 With SED model
\label{fig:1026}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1458.eps}
\caption{SED of HESS~J1458 With SED model
\label{fig:1458}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1626.eps}
\caption{SED of HESS~J1626 With SED model
\label{fig:1626}}
\end{figure}

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/HESSJ1813178SNRhadron.eps}
\label{fig:hessj1813}}
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/HESSJ1813178PWNlepton.eps}
\label{fig:hessj1813hadro}}
\caption{SED of . Top : Leptonic scenario. Bottom : Hadronic scenario. 
}

\end{figure}

### 2012-08-30 papers/tevcat/draft_v0/sections/abstract.tex
first version of draft

Since its launch, the \emph{Fermi} satellite has firmly identified 7 pulsar wind nebulae (PWNe) plus a large number of candidates, all powered by young and energetic pulsars. Furthermore, PWNe are the most populous class in the TeV energy range followed by the unidentified sources (UNID). Using 45 months of Fermi--LAT data, we looked around the position of 56 TeV sources to bring new constraints on the models and new clues on the nature of sources without counterparts. For each of them we derived a $\gamma$--ray flux or an upper limit (when the TeV source is not detected at GeV energies by the \emph{Fermi}--LAT) above 10~GeV.

The wealth of multi-wavelength data available and the new results provided by \emph{Fermi}--LAT is an extraordinary opportunity to constrain the origin of the gamma-ray emission of the large sample of UNID and the radiative processes taking place in known PWNe.

### 2012-08-30 papers/tevcat/draft_v0/sections/build_the_candidate_list.tex
first version of draft

\section{List of candidates}
As a starting point, we used the catalog of TeV sources provided by the university of Chicago\footnotemark[1] to build our list of candidates. This catalog summarizes the information of all sources detected by the TeV experiments. Looking for PWNe candidates which are galactic sources, we selected the sources located within $\pm$5$\degr$ in latitude.

The Galactic center being a complex region to study with \emph{Fermi}--LAT data, due to contamination by the large density of sources and by the diffuse emission, we removed all sources within 5$\degr$ of the Galactic center. Thus, we did not include to our list the three sources HESS~J1745-303, HESS~J1741-302 and G~0.9+0.1 \textbf{citer Lola + autre papier venant sur les SNRs}.

TeV sources associated to SNRs will not be discussed in this analysis. These sources will be included in a forthcoming paper which aims at bringing constraints on all known SNRs using the \emph{Fermi}--LAT data \textbf{(cite the SNR cat)}.

Finally we removed from this analysis the Crab Nebula and Vela-X. Both were already studied in details (\cite{2010ApJ...708.1254A}, \cite{2012ApJ...749...26B}), and the second is the object of a new analysis \textbf{Grondin et al., Forthcoming}.

The final list of 56 sources studied in this analysis is summarized in Table~\ref{tab:TeV_sources_nom_exp} together with their morphology as seen in TeV.

### 2012-08-30 papers/tevcat/draft_v0/sections/introduction.tex
first version of draft

\section{Introduction}

Since 2003, the continuous observation of the Galactic Plane by $\breve{C}$erenkov telescopes have yielded the detection of more than 80 Galactic sources. Among them, pulsar wind nebulae (PWNe) is the dominant class with more than 30 firm identifications. However, a similar number of Galactic sources cannot be associated to a counterpart in any other wavelength. They are ranked in the unidentified (UNID) class.

Multi-wavelength observations are essential to constrain the emission mechanisms occurring in these sources and identify their nature. The Large Area Telescope (LAT) aboard the \emph{Fermi} Gamma-Ray Space Telescope (\emph{Fermi}) is especially useful in this context. Covering the energy range from $\sim$ 100 MeV to more than 300 GeV, the LAT provides a precise view of the $\gamma$-ray sky. With 2 years of observations, the \emph{Fermi}--LAT Second Catalog \citep{2012ApJS..199...31N} already contains 1873 sources, 1397 being identified and 576 without counterparts.

Two different scenarii are proposed to explain the observed $\gamma$-ray radiation : the accelerated particles are either electrons (leptonic scenario) or protons (hadronic scenario). In the hadronic scenario, $\gamma$-ray photons are created by $\pi^0$ decay from the interaction of accelerated hadrons with nuclei of the interstellar medium. In the leptonic scenario, $\gamma$-ray photons are created by inverse Compton (IC) scattering of the accelerated leptons on the ambient photon fields (CMB, Stellar Radiation, IR, ...).

Leptonic sources such as relic PWNe \citep{2009ASSL..357..451D,2009arXiv0906.2644D} and hadronic sources such as old supernova remnants interacting with molecular clouds \citep{2011arXiv1104.1197U} have been proposed to explain the population of unidentified sources.

The distinction between these two scenarii is done by studying the link between the TeV and the GeV energy range. \cite{2010ApJ...720..266S,2011ApJ...738...42G,Rousseau1857} have demonstrated the potential that can be provided by the use of LAT observations to study PWNe candidates. Up to now, except Vela--X \citep{2010ApJ...713..146A}, the 7 PWNe firmly identified by Fermi are all associated to a TeV counterpart and show a hard spectrum consistent with an IC peak above 100 GeV (\cite{2010ApJ...708.1254A},\cite{2011ApJ...738...42G}).

The motivation of this work is to bring new constraints on already known PWNe and to look for new candidates among the unidentified TeV sources.  A search for gamma-ray emission in the off-pulse window of the $\gamma$-ray detected pulsars, updating the method proposed in \cite{2011ApJ...726...35A}, will be presented in \textbf{cite 2PC}. The strategy presented in our work (this paper) is closer to \cite{2010AA...518A...8T} in the sense that we analyzed the \emph{Fermi}-LAT data around already known potential PWNe.

The sources included in our search were detected by H.E.S.S., VERITAS, MAGIC and MILAGRO. H.E.S.S. \citep{2006AA...457..899A} is composed of four telescopes observing the very high energy (VHE) sky from 0.1 to 100 TeV with a mean point spread function (PSF) of $\sim$0.1$\degr$ for a point--source sensitivity around 1$\%$ of the Crab flux above 200 GeV for 25 hours of observations. The four telescopes of VERITAS \citep{2002APh....17..221W} detect the $\sim$ 0.1 to 30 TeV $\gamma$-rays with a sensitivity of 1$\%$ of the Crab in less than 30 hours and an angular resolution lower than 0.1$\degr$ at 1 TeV. MAGIC \citep{2012APh....35..435A} consists of two telescopes observing from $\sim$ 50 GeV to several tens of TeV with a sensitivity of $\sim$ 0.8$\%$ of the Crab nebula flux above 300 GeV with a $\sim$ 0.1$\degr$ PSF. MILAGRO \citep{2007ApJ...658L..33A} is a water $\breve{C}$erenkov detector with a large field of view (FoV) of $\sim$2sr and a $\sim$ 0.45$\degr$ angular resolution observing $\gamma$-rays from $\sim$ 1 to 100 TeV. 
%{\bf {\color{red} Manque les references}}

%references utiles :
%HESS
%http://arxiv.org/pdf/1203.3215v2.pdf
%Sensitivity : http://arxiv.org/pdf/1204.5690v1.pdf
%VERITAS
%http://arxiv.org/pdf/1205.5287v1.pdf
%sensitivity : http://veritas.sao.arizona.edu/about-veritas-mainmenu-81/veritas-specifications-mainmenu-111
%MAGIC
%http://arxiv.org/pdf/1201.4074v2.pdf
%PSF : http://magic.mppmu.mpg.de/magic/factsheet/
%MGRO
%http://scipp.ucsc.edu/milagro/papers/lansdell1205.pdf
%

Starting from the TeV catalog website \footnote{http://tevcat.uchicago.edu/}, which summarizes all sources detected at TeV energies, we established a list of sources possibly associated to PWNe (Section 3), that we studied using the method and the tools described in Section 4. The spatial and spectral results (Section 5) will be presented in the context of a population study (Section 6) before discussing the case one by one (Section 7). \textbf{a remoduler une fois le reste fait.}

### 2012-08-30 papers/tevcat/draft_v0/sections/results.tex
first version of draft

\section{Results}
\label{res}

Using the procedure described above, we detected 30 sources among the 56 PWNe candidates selected. For each of these detected sources, as explained in Section~\ref{signi}, we determined the best morphology by comparing the likelihood of our fit obtained under three different hypotheses: TeV shape, point-like source and extended source. The results of the spatial analysis are shown in Table~\ref{tab:Morphology_results}, the last column summarizing the best shape found for each source. Once the best morphology found, we performed a spectral analysis whose results are reported in Tables~\ref{tab:det_sources} and \ref{tab:det_sources2}, while upper limits on non-detections are presented in Tables~\ref{tab:nondet_sources} and \ref{tab:nondet_sources2}.

\subsection{Extended sources detected above 10~GeV}
\label{morph_res}

Most sources are better described using the TeV morphology as a template. This is partly due to the 2 (3 for an extended source) additional degrees of freedom to take into account but also to the low statistics above 10~GeV. Indeed, these sources have on average a low TS value or, are at the limit of our extension threshold, such as HESS J1514-591.

Interestingly, 11 sources are better described using the morphology obtained at GeV energies using the LAT data, 5 of them being extended. Table \ref{tab:GeVmorph} summarizes the spatial fits in such a case. The results presented here are consistent with Tables 3 and 4 of \cite{2012arXiv1207.0027L}. One can note that the agreement for HESS~J1632$-$478 is not excellent. The difference in extension (0.35 $\pm 0.06$ vs 0.45 $\pm$ 0.04 in our analysis) certainly comes from the 3 additional 2FGL sources (2FGL~J1631.7$-$4720c, 2FGL~J1630.2$-$4752 and 2FGL~J1632.4$-$4820c) in the model used by \cite{2012arXiv1207.0027L}. These sources were below our $\text{TS}>$25 threshold to add a source, and being unidentified, we found no physical reason to add them as we did in the case of PSR~J1838-0536.

HESS~J1303$-$631 is a new extended source detected at GeV energies. However, Figure~\ref{1303} shows that the \emph{Fermi}-LAT excess observed for this source is likely due to 2 point-like sources (one associated with HESS~J1303$-$631 and one associated with Kes 17 \citep{2011ApJ...740L..12W}) but the limited statistics at high energy does not allow us to separate them. When the region is fitted assuming the TeV morphology for HESS~J1303$-$631 and a separate source for Kes 17, the latter hardly reaches $\text{TS}>$ 20 and is thus too faint to be added to our model. Nevertheless, the difference between the true spectrum and the spectrum derived in this work will be included in the systematics on the flux taking into account the fact that we do not know the true morphology of the source.

\subsection{Pulsars detected above 10~GeV}
\label{pulsarsect}
Only six sources are better described by a point-source model above 10 GeV than with a uniform disk or by the TeV template reported in Table~\ref{tab:TeV_sources}: HESS~J1708$-$443, MGRO J0632+17, MGRO J1908$+$06, MGRO J2019$+$37, MGRO J2228+61 and VER J0006+727. It is not a surprise to see in Figure~\ref{fig:indexvssize} and Table~\ref{tab:det_sources} that these sources have a rather soft spectrum in comparison to the average index of TeV detected sources and that they are all coincident with bright gamma-ray pulsars. As can be seen on Figures \ref{fig:sedsourcespuls}, the spectrum obtained above 10 GeV for these sources is in good agreement with the spectrum derived in the 2FGL Catalog released by the Fermi collaboration \citep{2012ApJS..199...31N}. The $\gamma$-ray emission detected by the LAT above 10 GeV is therefore very likely due to the pulsar itself than to its associated PWN.

Three other sources are coincident with bright Fermi pulsars and present a very soft spectrum in agreement with the 2FGL Catalog as well: HESS J1418-609, MGRO J1958$+$2848 and MGRO~J2031+41. Again, the gamma-ray signal is very likely due to magnetospheric emission and the fact that these sources are rather faint above 10 GeV can explain why the improvement obtained using a point-source model is not significant in comparison to the simple TeV morphology.

To study the contamination of these pulsars to our sources of interest, we used the procedure described in Section 4 but including the pulsars in our models of the regions. The spectra of \emph{Fermi}-LAT pulsars are well characterized by exponentially cutoff power laws with photon indices near 1.5 and cutoff energies between 0.5 and 6 GeV~\textbf{cite 2PC}. As we selected the data above 10 GeV, we cannot fit the spectral parameters of theses pulsars. Thus we included them in our model assuming the fixed photon index, cutoff energy and normalization extracted from the 2FGL Catalog. It should be noted that some pulsars may deviate from the simple exponential cutoff power law above 10 GeV. This has been proposed for instance for the famous case of the Crab pulsar (citer les papiers Veritas et Magic). In such cases, our fit could still be contaminated by the pulsar, especially in the first energy interval (between 10 and 31.6 GeV).

Table \ref{tab:pulsarfit} and Figures \ref{fig:sedsourcespuls}, \ref{fig:sedsourcespuls2} \& \ref{fig:sedsourcespuls3} show the results of this new fit using the conventions presented in Table \ref{tab:pulsars}. As expected for the six point-like sources presented in Figure~\ref{fig:sedsourcespuls}, the low energy part of the spectrum tends to disappear confirming that we only detected a pulsar emission. In the case of MGRO J1908+06, the detection is not significant anymore. To present conservative results, we derived the upper limits assuming the TeV shape of the source.

Figures \ref{fig:sedsourcespuls2} \& \ref{fig:sedsourcespuls3} show the same behavior for HESS~J1418-609 confirming that the signal observed was dominated by the pulsar emission. In the case of HESS~J1420-607 and HESS~J1119-614, the spectra are now slightly harder but still in very good agreement with the previous ones, which is a good indication that we are seeing the  emission from the PWNe and not from their associated pulsars.

\subsection{Detections of PWNe candidates}
%{\bf {\color{red} My own choice looking at your previous results: Kooka, HESSJ1303, HESS J1356, G292.2, HESSJ1841 and HESSJ1848. Do a quick subsection for each of them (and modeling if needed) like in the PWN Cat paper}}

In this section we will describe the new PWNe candidates found in this analysis. We chose them by looking for signal connecting to the TeV spectrum and showing an hard spectrum. HESS~J1420-607, HESS~J1303-631, HESS~J1356-645 \& HESS~J1119-614 were already proposed as PWNe by analyses at other wave-length. The detection of these sources by the \emph{Fermi}-LAT tends to confirm this hypothesis.

HESS~J1848-018, is classified as UNID. The detection presented in Table \ref{tab:det_sources} show a faint source with a soft spectrum. We will discuss this source in a PWN scenario.

\subsubsection*{HESS J1420$-$607}

The complex of compact and extended radio/X-ray sources, called Kookaburra~\citep{1999ApJ...515..712R}, spans over about one square degree along the Galactic plane. It has been extensively studied to explain the EGRET source: 3EG J1420$-$6038/GeV J1417$-$6100 \citep{1999ApJS..123...79H}. Within the North-East excess of this complex, labeled 'K3',  was discovered the pulsar PSR J1420$-$6048, a young and energetic pulsar with period 68 ms, characteristic of 13 kyr, and spin down energy of $10^{37}$ erg s$^{-1}$ \citep{2001ApJ...552L..45D}. Following X-ray observations by ASCA and later by \emph{Chandra} and \emph{XMM-Newton} revealed an extended X-ray emission around this pulsar identified as a potential PWN \citep{2001ApJ...561L.187R,2005ApJ...627..904N}. In the South-West side of the large Kookaburra complex lies a bright nebula exhibiting an extended hard X-ray emission, G313.1+0.1, called the 'Rabbit'~\citep{1999ApJ...515..712R}. This X-ray excess was also proposed as a plausible PWN contributing also to the gamma-ray emission detected by EGRET.

In the TeV energy range, the survey of the Galactic plane by H.E.S.S. revealed two very high energy sources in this region: HESS J1420$-$607 and HESS J1418$-$609 \citep{2006AA...456..245A}. HESS J1420-607 is centered North of PSR~J1420$-$6048 (nearby the K3 nebula), while HESS J1418-609 is coincident with the Rabbit nebula. More recently, \emph{Fermi}-LAT detected  pulsed gamma-ray emission from PSR J1420$-$6048 and PSR J1418$-$6058, a new gamma-ray pulsar found through blind frequency searches. This new pulsar is coincident with an X-ray source in the Rabbit PWN and has a spin-down power high enough to power the TeV PWN candidate HESS J1418$-$609.

In our analysis, HESS J1420$-$607 is detected with a TS of 41 which corresponds to a significance of $\sim$ 6$\sigma$. With a TS of 41.2, the point source hypothesis does not significantly improve the likelihood of our fit in comparison to the TeV morphology (Gaussian of 0.06$\degr$) presented in \citep{2006AA...456..245A}. Thus assuming the TeV shape, we found an integrated flux F(10-316 GeV)=$(3.2 \pm 0.9_{stat} \pm 1.2_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, a spectral index of $\Gamma = 1.91 \pm 0.27_{stat} \pm 0.30_{syst}$ and an energy flux of E(10-316 GeV) = $(23.1 \pm 6.7_{stat} \pm 9.5_{syst}) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$.

In a second step, following the procedure presented in Section~\ref{pulsarsect}, we refitted the spectrum of HESS J1420$-$607 including PSR J1420$-$6048 in our model and fixing its spectral parameters found in the 2FGL Catalog. The fit of HESS~J1420-607 leads to a lower significance of $~5.6 \sigma$ (TS=35.8, 2 d.o.f) with an integrated flux of F(10-316 GeV)= $(3.4 \pm 0.9_{stat} \pm xx_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$ and an index of $\Gamma = 1.80 \pm 0.29_{stat} \pm xx_{syst}$.

The connection between the GeV flux as observed by Fermi and the TeV flux as seen by H.E.S.S., visible in Figure \ref{fig:hessj1420}, supports a common origin for the gamma-ray emission. The two black curves present the leptonic and hadronic models proposed by \cite{2010ApJ...711.1168V}. As said above, the lower energy part of our analysis could still be contaminated by the pulsar even when the 2FGL source associated with the pulsar is added. Therefore, the first energy bin should be taken as an upper limit. This implies that, with the current statistics, all models reproduce reasonably well the GeV and TeV data. A future \emph{Fermi}-LAT off-pulse analysis of this pulsar performed with more statistics could help discriminate between both models.

\subsubsection*{HESS J1356$-$645}

HESS~J1356$-$645 is a source detected in the TeV energy range by H.E.S.S. during the continuation of the Galactic Plane Survey~\citep{2011AA...533A.103H}. This extended source lies close to the pulsar PSR~J1357$-$6429 which was discovered during the Parkes multibeam survey of the Galactic Plane \citep{2004ApJ...611L..25C}. Its high spin-down power of $\dot{E} = 3.1 \times 10^{36}$ erg s$^{-1}$ makes it a good candidate to power a PWN. Archival radio and analysis of X-ray data from \emph{ROSAT/PSPC} and \emph{XMM/Newton} have revealed a faint extended structure coincident with the VHE emission~\citep{2011AA...533A.103H} thus providing another argument in favor of the PWN scenario. In parallel, \cite{2011AA...533A.102L} announced the detection of a pulsed signal from PSR~J1357$-$6429 in the $\gamma$-ray and X-ray energy ranges using \emph{Fermi}-LAT and \emph{XMM-Newton} data. However, using 29 months of LAT data between 0.1 and 100 GeV, no counterpart to the TeV emission was found in the off pulse window of the pulsar.

The 16 additional months of observations by \emph{Fermi}-LAT between 10 and 316 GeV included in our dataset now enables the detection of a faint counterpart to the TeV emission with a TS = 25.8 (4.7 $\sigma$ assuming 2 d.o.f.). Since the best GeV morphology does not improve the fit significantly, we used the TeV Gaussian of 0.17$\degr$ \citep{2011AA...533A.103H} for the spectral analysis and derived an integrated flux of F(10-316 GeV)=$(1.2 \pm 0.5_{stat} \pm 0.7_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, an energy flux of E(10-316 GeV)=$(16.8 \pm 6.9 \pm 8.1) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$ and a hard spectral index of $\Gamma = 1.01 \pm 0.38 \pm 0.25$.

It should also be noted that, with its low energy cutoff at around 800 MeV in the \emph{Fermi}-LAT energy range \citep{2011AA...533A.102L}, PSR~J1357$-$6429 is not significant anymore in the 10 to 316 GeV energy range. Therefore, we do not expect to see any changes in the spectral parameters when adding PSR~J1357$-$6429 to the model of the region. This is verified in Table~\ref{tab:pulsarfit} as well as in Figure \ref{fig:hess1356}.

The combined GeV-TeV data as seen in Figure \ref{fig:hess1356} provide new constraints concerning the spectral shape of the gamma-ray emission. It is clearly visible in this Figure that the \emph{Fermi}-LAT spectral points nicely match the H.E.S.S. ones, proving that the GeV and the TeV emission have a common origin. Assuming that the gamma-ray signal is coming from the PWN powered by PSR~J1357$-$6429, \cite{2011AA...533A.103H} proposed a leptonic scenario (black curve) which provides an excellent fit of the new multi-wavelength data. This model assumes a rather low magnetic field of $\sim 3 \mu$G similar to the value observed in other relic PWNe.

\subsubsection*{HESS~J1119$-$614}

During the Parkes multibeam pulsar survey, \cite{2000ApJ...541..367C} discovered PSR~J1119$-$6127, a young ($\tau = 1.6$ kyr) pulsar with a high $\dot{E} = 2.3 \times 10^{36}$ erg s$^{-1}$ within the supernova remnant G292.2$-$0.5. Using \emph{Chandra} observations, \cite{2003ApJ...591L.143G} and \cite{2008ApJ...684..532S} revealed the presence of a faint and compact PWN close to this pulsar. More recently, a TeV gamma-ray source coincident with PSR J1119$-$6127 and G292.2$-$0.5 was announced\footnote{http://cxc.harvard.edu/cdo/snr09/pres/DjannatiAtai\_Arache\_v2.pdf}.

Using the method described above, a faint signal consistent with the location of the composite SNR G292.2$-$0.5 is detected with a TS of 27.3 (4.9 $\sigma$ with 2 d.o.f.). Since the best GeV morphology does not improve the fit significantly, we used the TeV Gaussian of 0.05$\degr$ for the spectral analysis and derived an integrated flux of F(10 - 316 GeV) = $(2.1 \pm 0.6_{stat} \pm 1.1_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, an energy flux of E(10-316 GeV) = $(10.4 \pm 3.9_{stat} \pm 4.9_{syst}) \times 10^{-10}$ erg cm$^{-2}$ s$^{-1}$ and a soft index of $\Gamma = 2.15 \pm 0.35_{stat} \pm 0.20_{syst}$.

Nevertheless, as can be seen on Figure \ref{fig:hessj1119} and in Table \ref{tab:pulsarfit}, these parameters are contaminated by a low energy component associated to PSR~J1119$-$6127. Once the source 2FGL~J1118.8$-$6128, associated with PSR~J1119$-$6127, included in our model of the region, this contamination decreases and the significance of our GeV source is now just above the detection threshold that we fixed in Section XX, with TS = 16 (3.6 $\sigma$ with 2 d.o.f.). As can be seen in Figure \ref{fig:hessj1119}, the low energy point of the SED is now an upper limit. The best fit parameters in this hypothesis are an integrated flux of F(10-316 GeV) = $(1.5 \pm 0.6_{stat} \pm XX_{syst})\times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$ and an harder index of $\Gamma = 1.80 \pm 0.48_{stat} \pm XX_{syst}$. To be conservative, we used this fit to derive the physical properties of HESS~J1119$-$614.

\textbf{TO BE DONE}

\subsubsection*{HESS J1303$-$631}

HESS J1303$-$631 was serendipitously discovered in 2004 \citep{2005AA...439.1013A} during an observation campaign for the pulsar binary system PSR B1259$-$63. It was originally classified as a "dark" accelerator due to the lack of detected counterparts in radio and X-rays with \emph{Chandra} \citep{2005ApJ...629.1017M}. At this time, a search in the field of view only yielded one plausible counterpart located in the North-Western edge of HESS J1303$-$631, the high spin-down power pulsar PSR J1301$-$6305 ($\dot{E} = 1.70 \times 10^36$ erg s$^{-1}$). The recent detection of a very weak X-ray PWN using \emph{XMM-Newton} observations now allows the solid identification of this source as a VHE PWN associated to the pulsar PSR J1301$-$6305, leading \cite{2011arXiv1104.1680D} to classify the TeV excess as an older PWN with a complex morphology and an important offset between the pulsar and nebula.

Figures 1 \& 3 obtained by \cite{2011ApJ...740L..12W} show no significant emission coming from the location of HESS~J1303$-$631 using XX months of \emph{Fermi}-LAT data between 1 and 20 GeV. With 16 months of additional data and a higher energy threshold, our analysis now provides a first detection of GeV emission coincident with the TeV source. Nevertheless as discussed in Section \ref{morph_res}, Figure \ref{1303} shows that the detected emission might be contaminated by the source associated to Kes 17. When added to the model as an independent source, Kes 17 hardly reaches a TS of 20 which is lower than our threshold of 25 to add a source. Furthermore, Kes 17 is not included in the Hard Source List. Since we cannot separate these two sources with the current statistics, we decided to take into account this effect of source confusion in our systematics on HESS J1303$-$631.

Assuming our best GeV morphology represented by a Disk shape of 0.5$\degr$ (see Table \ref{tab:Morphology_results}), we obtained an integrated flux of F(10-316 GeV)=$(5.9 \pm 1.1_{stat} \pm 2.8_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, an energy flux of E(10-316 GeV)= $(43.5 \pm 10.0_{stat} \pm 14.2_{syst}) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$ and an index of $\Gamma = 1.71 \pm 0.19_{stat} \pm 0.28_{syst}$. This hard index is in the range of values obtained for PWNe as seen with \emph{Fermi} and is inconsistent with the spectral index of $\sim 2.4$ derived by \cite{2011ApJ...740L..12W} for Kes 17. This is a good evidence that the GeV emission is dominated by the PWN candidate. As can be seen in Fig XX (\textbf{modeling}), even though the connection between the GeV and the TeV energy range is not perfect, there is little to doubt that we have detected a counterpart to the TeV signal. A future analysis with more statistics would greatly help to separate the different components and conclude on the exact spectrum of HESS~J1303$-$631.

\subsubsection*{HESS J1841$-$055}

HESS~J1841$-$055 was discovered during the H.E.S.S. Galactic Plane Survey \citep{2008AA...477..353A} and remained an UNID source since then. The emission is highly extended and show possibly three peaks suggesting that the TeV emission is composed of more than one source. Using \emph{INTEGRAL} data, \cite{2009ApJ...697.1194S} proposed the  high-mass X-ray binary HMXB system AX J1841.0$-$0536 as a potential counterpart, at least for a part of the emission. \cite{2011ICRC....6..197T} proposed the association of HESS~J1841$-$055 to an ancient PWN powered by PSR~J1841$-$0524, PSR~J1838$-$0549 or both as each pulsar taken independently would need an efficiency greater than 100\% to power a potential PWN associated to the TeV source. More recently, the blind search detection of the new gamma-ray pulsar PSR~J1838$-$0537 with \emph{Fermi}-LAT provided another good counterpart of the TeV source. Indeed, assuming a distance of 2 kpc, \cite{2012ApJ...755L..20P} estimated that PSR J1838$-$0537 is sufficiently energetic to power the whole TeV source with a conversion efficiency of 0.5\%, similar to other suggested pulsar/PWN associations \citep{2008ApJ...682L..41H}.

HESS~J1841$-$055 is detected as a significantly extended source with our analysis (TS$_{ext}$= 38.3) at a position consistent with the TeV source but with a slightly larger extension (0.57 $\degr$ with respect to 0.41 $\degr$ $\times$ 0.25 $\degr$ for the TeV source). However, the GeV best morphology does not significantly improve the fit compared to the TeV morphology (TS$_{GeV/TeV}$= 13.0, 2.8$\sigma$ with 3 d.o.f.). Thus assuming the TeV shape, our best fit yielded an integrated flux of F(10-316 GeV) = $(9.3 \pm 1.9_{stat} \pm 3.9_{syst}) \times 10^{-10}$ for an energy flux of G(10-316 GeV) = $(79.6 \pm 16.0_{stat} \pm 19.1_{syst}) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$ and a hard index of $\Gamma = 1.56 \pm 0.20_{stat} \pm 0.32_{syst}$ consistent with the average value for PWNe detected by the \emph{Fermi}-LAT.

As can be seen in Figure \ref{fig:1841}, the \emph{Fermi}-LAT spectral points nicely match the H.E.S.S. ones, suggesting a common origin. The hard \emph{Fermi}-LAT spectrum detected imply that a curvature must arise between the TeV energy range and the GeV energy range. This is typical of most PWNe detected by \emph{Fermi} and HESS which present an inverse-Compton emission peaking at few hundreds of GeV and would favor the PWN scenario. However, as said above, this source is extremely extended in both wavelengths and could be composed of several gamma-ray sources. Follow-up observations with HESS and \emph{Fermi} would be needed to unveil the real nature of HESS J1841$-$055.

\subsubsection*{HESS J1848-018}

HESS~J1848-018 \emph{(WR121a,W43,TeV J1848-017)}.

\subsection{Constraints obtained from non-detections}
%{\bf {\color{red} My own choice looking at your previous results: HESSJ1026, HESSJ1458, HESSJ1626-490, HESSJ1813 and so on. Do a quick subsection for each of them (and modeling if needed) like in the PWN Cat paper}}

This section will present the sources for which the emission was not significant but for which the upper limit show an interesting behavior to bring new constraints on the models.

\subsubsection*{HESS J1026$-$582}

HESS~J1026$-$582 was discovered during a new analysis of the region of HESS~J1023$-$577 \citep{2011AA...525A..46H}. The presence of PSR~J1028$-$5819, detected by the Parkes Radio telescope \cite{2008MNRAS.389.1881K}, close to the TeV emission suggested a PWN scenario to explain this VHE source. This hypothesis is consolidated by the spin-down power energy of PSR~J1028$-$5819, $\dot{E} = 8.43 \times 10^{35}$ erg s$^{-1}$ \citep{2009ApJ...695L..72A}, which is high enough to power a PWN.

No significant GeV emission coming from the location of the TeV excess was detected in our analysis. The very low TS value derived (see Tables \ref{tab:nondet_sources} \& \ref{tab:nondet_sources2}) give few hope for a future detection of this source in this energy range on a short time scale. The upper limits presented on Figure \ref show that a curvature is needed between the TeV and the GeV energy range. This suggests an inverse-Compton peak consistent with a PWN hypothesis.

\subsubsection*{HESS J1458$-$608}

PSR~J1459$-$60 \citep{2010ApJS..187..460A} is an energetic pulsar with an $\dot{E} = 9.2 \times 10^{35}$ erg s$^{-1}$ sufficient to power a PWN. A potential PWN, HESS~J1458$-$608, was discovered 9.6$\prime$ from PSR~J1459$-$60 using H.E.S.S. data after a dedicated observation \cite{2012arXiv1205.0719D} based on a marginal detection in the 2004 Galactic Plane Survey.

The source was not significantly detected in our analysis above 10 GeV (TS = 12.3). It can also be noted from Table \ref{tab:nondet_sources2} that the marginal emission detected comes from the low energy range studied and is more likely associated to PSR~J1459$-$60. Figure \ref{fig:hessj1458} shows that even taking into account the pulsar in our model of the region, the SED is still contaminated at low energy. Nevertheless, the upper limits of the two high energy bins show that a change in the slope of the spectrum is needed between the TeV and the GeV component.

\textbf{TO BE DONE}

\subsubsection*{HESS J1626$-$490}

HESS~J1626$-$490 is another unidentified source detected during the H.E.S.S. Galactic Plane Survey \citep{2008AA...477..353A}. \cite{2011ICRC....7...44E} found no X-Ray source fulfilling the energetic requirement to explain the TeV emission using \emph{XMM-Newton} observations. However, the author suggested that a hadronic scenario based on the interaction of the SNR~G335.2+00.1 with a $^{12}$CO molecular cloud could explain the TeV emission.

Figure XX shows that the upper limits derived following the procedure described in Section 4 require a change in the slope of the spectrum, consistent with the model presented in Figure 4 of \cite{2011ICRC....7...44E}.

\subsubsection*{HESS J1813$-$178}

HESS J1813-178 was discovered during the H.E.S.S. Survey of the Inner Galaxy \citep{2005Sci...307.1938A}. It remained unidentified until the discovery of the SNR G12.8-0.0 \cite{2005ApJ...629L.105B}. X-ray studies resolved the emission into a point-like source and an extended nebula \cite{2007AA...470..249F}. The discovery of PSR J1813$-$1749 \cite{2009ApJ...700L.158G} confirmed a PWN/SNR scenario. With its $\dot{E} = 5.6 \times 10^{37}$ erg s$^{-1}$ \citep{2012ApJ...753L..14H}, this pulsar is the third most energetic pulsar of the Galaxy. Thus it could produce a PWN observable in TeV/GeV range.

\cite{2007AA...470..249F} \& \cite{2010ApJ...718..467F} preferred a leptonic scenario to explain the GeV/TeV emission to a potential hadronic scenario. The upper limits derived using the procedure described in sect. 4. show that the spectrum of HESS~J1813$-$178 cannot be flat between the TeV and the GeV energy ranges and suggest peak with an energy cutoff located between the two energy ranges. Therefore, this suggests a PWN scenario as determined in previous works.

\textbf{TO BE DONE}

\subsection{Conclusion}
To be done later....

### 2012-08-30 papers/tevcat/draft_v0/tables.tex
first version of draft

\begin{deluxetable}{l*{5}l}
\tabletypesize{\scriptsize}
\tablecaption{List of TeV sources analyzed
\label{tab:TeV_sources}}
\input{tables/TeV_sources_nom_exp.tex}

\tablecomments{ The first two columns are TeV source names and types as defined in the TeV catalog provided by the university of Chicago: PWN for Pulsar Wind Nebula, PSR for Pulsars, UNID for Unidentified sources, Massive Star Cluster and Star Forming Regions. The 3$^{rd}$ column reports the Galactic coordinates for each source. The 4$^{th}$ column presents the shape that best describes the source at TeV energies, together with a reference in the  5$^{th}$ column.}

\end{deluxetable}

\clearpage
\begin{deluxetable}{llllc}
\tabletypesize{\scriptsize}
\tablecaption{List of sources with a pulsar within 0.5$\degr$
\label{tab:pulsars}}
\input{tables/pulsars.tex}\\
\begin{flushleft}
a- The distance between the pulsar and the source is lower than 0.27$\degr$.\\
b- The pulsar is located inside the edge of the TeV shape.\\
c- The pulsar shown no significant excess.\\
\end{flushleft}
\tablecomments{ $_{ }$List of sources having a known $\gamma$-ray pulsar within 0.5$\degr$. The two first column shows the TeV source and the pulsar name. The third column show the distance between the TeV source and the GeV pulsar. The pulsar position comes from \textbf{Citer 2PC}. In the fourth colum Y means that we added the pulsar to the model and N that we didn't added it.}

\end{deluxetable}

\clearpage
\tabletypesize{\scriptsize}
\begin{deluxetable}{l*{5}l}
\tablewidth{0pt}
\tablecaption{Locations and spectral parameters of additional background sources above 10 GeV 
\label{tab:newsources}}
\input{tables/newsources.tex}

\tablecomments{The first two columns describe the source names and their corresponding Galactic coordinates. The test statistic (TS) for the source significance is provided in the 3$^{rd}$ column. The spectral results are presented in columns 4 and 5 for a power-law model (Equation~\ref{PL}) with a scale parameter $E_0 = 56234$ MeV which corresponds to the middle of the 10--316 GeV interval in log scale. PSR~J1838$-$0536 has been added to help the morphology fit of HESS~J1841$-$055 which is a diffuse source. The spectral fit is consistent with the pulsar component (index of$\sim$ 5).}

\end{deluxetable}
\normalsize
\noindent

\clearpage
\tabletypesize{\scriptsize}
\begin{deluxetable}{l*{7}l}
\tablewidth{0pt}
\tablecaption{Morphological results for LAT-detected TeV sources above 10 GeV
\label{tab:Morphology_results}}
\input{tables/Morphology_results.tex}

\tablecomments{Results of the morphological analysis for all LAT-detected TeV sources. The fits assumed either the TeV template defined in Table~\ref{tab:TeV_sources}, a point-source model or a uniform disk model (see Equation~\ref{eq:Disk}). The definition of $\text{TS}_{TeV}$, $\text{TS}_{GeV}$, $\text{TS}_{ext}$ and $\text{TS}_{GeV/TeV}$ is reported in Section~\ref{signi}.
The significance of the extension is measured using the $\text{TS}_{ext}$ criterium defined in Section~\ref{signi}.}

\end{deluxetable}
\normalsize
\noindent

\clearpage
\tabletypesize{\scriptsize}
\begin{deluxetable}{l*{5}l}
\tablewidth{0pt}
\tablecaption{Morphological results for LAT-detected TeV sources for which $\text{TS}_{GeV}$ is significantly better than $\text{TS}_{TeV}$ above 10 GeV
\label{tab:GeVmorph}}
\input{tables/GeV_morph_sources.tex}

\tablecomments{Results of the morphological analysis for LAT-detected TeV sources better described using the shape fitted at GeV energies. The fits assumed either a point-source model or a uniform disk model (see Equation~\ref{eq:Disk}) whose centroid and extension are provided in columns 4 and 5 respectively. The significance of the extension is measured using the $\text{TS}_{ext}$ criterium defined in Section~\ref{signi}.}

\end{deluxetable}
\normalsize
\noindent

\clearpage
\tabletypesize{\scriptsize}
\begin{deluxetable}{l*{5}l}
\tablewidth{0pt}
\tablecaption{Spectral fitting results for LAT-detected TeV sources above 10 GeV 
\label{tab:det_sources}}
\input{tables/detected_sources.tex}

\tablecomments{Results of the maximum likelihood spectral fits  
for LAT-detected TeV sources. The test statistic (TS) for the source significance is provided in column 2. 
Columns 3 and 4 list the photon flux F(10--316 GeV) and the 
energy flux G(10--316~GeV). The fits used the best morphology reported in Table~\ref{tab:GeVmorph} and a power-law spectral model (see Equation~\ref{PL}) with photon index $\Gamma$ given in column 5. 
The uncertainties on F(10--316 GeV), G(10--316~GeV), and $\Gamma$ correspond respectively to the statistical and systematics uncertainties (see Section~\ref{syst}).}

\end{deluxetable}
\normalsize
\noindent

\clearpage
\begin{landscape}
\begin{deluxetable}{l*{7}l}
\tabletypesize{\scriptsize}
\tablecaption{Spectral fitting results for LAT-detected TeV sources in three energy bands logarithmically-spaced
\label{tab:det_sources2}}
\tablewidth{0pt}
\input{tables/each_energy.tex}

\tablecomments{Results of the maximum likelihood spectral fits  
for LAT-detected TeV sources in three different energy bands: 10--31 GeV, 31--100 GeV, 100--316 GeV using the same convention as in Table~\ref{tab:det_sources}. A 99\% c.l. upper limit is computed when the TS in the band is lower than 10. }

\end{deluxetable}
\normalsize
\noindent
\end{landscape}

\clearpage
\tabletypesize{\scriptsize}
\begin{deluxetable}{lccc}
\tablewidth{0pt}
\tablecaption{Upper limits for non-detected TeV sources above 10 GeV
\tabletypesize{\small}
\label{tab:nondet_sources}}
\input{tables/un_detected_sources.tex}

\tablecomments{ Results of the maximum likelihood spectral fits  
for non-detected TeV sources. The test statistic (TS) for the source significance is provided in column 2. 
Columns 3 and 4 list the 99\% c.l. upper limits on the photon flux F(10--316 GeV) and on the 
energy flux G(10--316~GeV). The fits used the TeV template defined in Table~\ref{tab:TeV_sources} and a power-law spectral model (see Equation~\ref{PL}) with photon index fixed at 2. }

\end{deluxetable}
\normalsize
\noindent

\clearpage
\begin{landscape}
\begin{deluxetable}{lcccccc}
\tabletypesize{\scriptsize}
\tablecaption{Upper limits for non-detected TeV sources in three energy bands logarithmically-spaced between 10 and 316 GeV
\tabletypesize{\scriptsize}
\label{tab:nondet_sources2}}
\tablewidth{0pt}
\input{tables/undetected_energy_bin.tex}

\tablecomments{Results of the maximum likelihood spectral fits  
for non-detected TeV sources in three different energy bands: 10--31 GeV, 31--100 GeV, 100--316 GeV using the same convention as in Table~\ref{tab:nondet_sources}. A 99\% c.l. upper limit is computed when the TS in the band is lower than 10.}

\end{deluxetable}
\normalsize
\noindent
\end{landscape}

%\begin{deluxetable}{lccc}
%\tabletypesize{\scriptsize}
%\tablecaption{Spectral results for sources with a $\gamma$-ray detected pulsar within 0.5$\degr$. 
%\tabletypesize{\scriptsize}
%\label{tab:pulsarfit}}
%\tablewidth{0pt}
%\input{tables/pulsar_tev_shape.tex}

%\tablecomments{{\bf {\color{red} Results of the maximum likelihood spectral fits  
%for sources with a known $\gamma$-ray pulsar within 0.5 $\degr$. The pulsar is included in the model with the spectral parameters derived in the 2FGL catalog \cite{2012ApJS..199...31N}. The source of interest (column 1) is fitted assuming the TeV morphology. A 99\% c.l. upper limit is computed when the TS is lower than 16.}}}

%\end{deluxetable}
%\normalsize
%\noindent

\begin{deluxetable}{lcccccc}
\tabletypesize{\scriptsize}
\tablecaption{Spectral results for sources with a $\gamma$-ray detected pulsar within 0.5$\degr$ with the pulsar included in the model
\tabletypesize{\scriptsize}
\label{tab:pulsarfit}}
\tablewidth{0pt}
\input{tables/pulsar_comparison.tex}

\tablecomments{Results of the maximum likelihood spectral fits  
for sources with a known $\gamma$-ray pulsar within 0.5 $\degr$. The pulsar is included in the model with the spectral parameters derived in the 2FGL catalog \cite{2012ApJS..199...31N}. A 99\% c.l. upper limit is computed when the TS is lower than 16. As PSR~J1028-5819 is already included and fitted in our model of the region of HESS J1026-5819 we did not report it in this table. PSR J1513-5908 and PSR J1702-4128 were detected after the 2FGL catalog analysis \citep{2012ApJS..199...31N}. Thus no spectral parameters were available.}

\end{deluxetable}
\normalsize
\noindent

### 2012-08-30 papers/tevcat/sections/lat_description_and_observations.tex
removed folder draft_v0

\section{LAT Description and Observations}

The LAT is a $\gamma$-ray telescope that detects photons by conversion into electron-positron pairs and operates in the energy range between 20 MeV and more than 300 GeV. Details of the instrument and data processing are given in \cite{2009ApJ...697.1071A}. The on-orbit calibration is described in \cite{2009ApJ...696.1084A}.

The following analysis was performed using 45 months of data collected from August 4, 2008 to Mai 18, 2012 (MET : 239557440--356439741) within a $7$\degr $\times 7\degr$ square (see section 4) around the position of the TeV source aligned with Galactic coordinates. We excluded $\gamma$-rays coming from a zenith angle larger than 100$\degr$ because of possible contamination from secondary $\gamma$-rays from the Earth's atmosphere \citep{2009PhRvD..80l2004A}. We used the Pass 7 clean event class that has a substantial reduction in instrumental background above 10 GeV with only a small loss in effective area (compared to the standard event class).

This energy of 10 GeV is a good compromise between photon statistics, angular resolution necessary to study the shape of the TeV sources and proximity to the energy range covered by the $\breve{C}$erenkov telescopes. This also greatly reduces the contribution of the Galactic diffuse background.

The counts map in Figure~\ref{fig:PlanGal} summarizes the regions of the Galactic Plane analyzed here. The bright pulsars Vela and Geminga clearly stand out, as well as the SNR IC443. In addition to these famous objects, a large number of sources clearly appears along the Galactic Plane, several of them being coincident with TeV detected sources, such as HESS~J1614$-$518 and HESS~J1616$-$508. They will be discussed in Section~\ref{res}. The large number of sources visible in this counts map highlight perfectly the capabilities now offered at high energy by the LAT.

%Source shape analysis requires the best possible angular resolution. Since the sources are expected to have an hard spectrum we made a compromise between statistics and resolution by selecting photons in the 10--300~GeV. This drastically reduces the contribution of the Galactic diffuse background and improve the single-photon angular resolution.

### 2012-08-30 papers/tevcat/sections/method.tex
removed folder draft_v0

%[18:21:24] Joshua Lande mathcal{L}
%[18:21:28] Joshua Lande texttt{gtlike}
%[18:21:32] Joshua Lande text{TS}
%\newcommand{\gtlike}{\ensuremath{\mathtt{gtlike}}\xspace}

\section{Conventions and methods}

\subsection{Modeling of the regions of interest}

Two different tools were used to perform the spatial and spectral analysis: \gtlike \citep{1996ApJ...461..396M} and \pointlike \citep{2011arXiv1101.6072K, 2012arXiv1207.0027L}. These tools fit a source model to the data along with models for the instrumental, extragalactic and Galactic components of the background. We used the version 09--28--00 of the \emph{Fermi} Science Tools.

\pointlike and \gtlike using two different shapes for the region of interest, we used all events contained in a disk of 5$\degr$ centered on the location of the TeV source when fitting the region with \pointlike and we used a $7\degr \times 7\degr$ square included in the previous disk when fitting the region using \gtlike. We tried to keep the two methods as close as possible by using the same conventions (same spatial binning : $\sim 0.06\degr/$bin, same energy binning : 8 energy bins per decade between 10~GeV and 316~GeV, same optimizer : MINUIT \citep{JamesRoos1975}).

In the following analysis, the Galactic diffuse emission was modeled by the standard LAT diffuse emission ring$-$hybrid model \emph{ring\_2yearp7v6\_v0.fits} for all sources. The residual cosmic-ray background and extragalactic radiation are described by a single isotropic component with a spectral shape described by the file \emph{isotrop\_2year\_P76\_clean\_v0.txt}. The models have been released and described by the \emph{Fermi}-LAT Collaboration through the FSSC\footnote{http://fermi.gsfc.nasa.gov/ssc/data/access/lat/BackgroundModels.html}. In the following, we fixed the isotropic diffuse normalization to limit the number of free parameters and reduce the uncertainties on the fitted parameters.

Sources within 10$\degr$ around each source of interest and listed in the hard source list \textbf{(cite the hard source list paper)} were included in our spatial-spectral model. We replaced potential TeV counterparts by a source with the TeV morphology summarized in Table \ref{tab:TeV_sources}. The spectral parameters of sources closer than 2$\degr$ to the source of interest were left free, while the parameters of all other sources were fixed at the hard source list (1FHL) catalog values.

Table \ref{tab:pulsars} summarizes the sources of our list located close to a pulsar detected by the \emph{Fermi}-LAT \textbf{cite 2PC}. The proximity of the pulsar can lead either to the non detection of a faint source hidden by the pulsed emission or to a contamination at low energy if the pulsar is not included. We decided to include in our analysis all the pulsars if they were outside of the TeV template or if they were more than 0.27$\degr$ away from the source of interest. Section \ref{puls_cont} will show the results for the sources close to the pulsars in the case were we added the pulsar in the model and fitted the TeV source.

Due to the longer integration time of our analysis with respect to the 1FHL catalog (45 vs 36 months in the 1FHL), the appearance of additional sources is expected. To prevent contamination from these sources, we looked over all our regions and added to the model all excesses with a significance above 4.0 $\sigma$ which corresponds to a $\text{TS} >$ 25 with 4 degrees of freedom (2 spatial and 2 spectral, see Section~\ref{signi}). The location and spectral parameters of theses sources are described in Table~\ref{tab:newsources}. We fitted their spectra assuming a pure power--law above 10 GeV.

%Thus, we added the sources summarized in Tab. \ref{tab:newsources} to take these excesses into account. We fitted their spectra assuming a pure power--law above 10~GeV.

%In the regions of \emph{TeV~J2019+407, $\gamma$--Cygnii, MGRO~J2031+41, TeV~J2032+4130} the Galactic diffuse emission is taken into account using the models derived in \citet{Cygnus_loop} in which has been performed a precise study of interstellar emission dedicated for this region. We used the files adapted for the P7 V6 IRFs.

\subsection{Analysis of the shape}

Estimation of the position and extension of each PWNe candidates was performed using \pointlike. \pointlike is an alternate binned likelihood technique, optimized for characterizing the extension of a source (unlike \gtlike), that was extensively tested against \gtlike \citep{2011arXiv1101.6072K, 2012arXiv1207.0027L}. To fit an extended source, \pointlike convolves the extended source shape with the PSF (as a function of energy) and uses the MINUIT library \citep{JamesRoos1975} to maximize the likelihood by simultaneously varying the position, extension, and spectrum of the source. \cite{2012arXiv1207.0027L} present more details on the method used and its validation.

As previously done in \cite{2012arXiv1207.0027L}, we only used radially-symmetric uniform disk shape (defined in Equation \ref{eq:Disk}) to fit the extension of the GeV emission. In the following, we quote the radius to the edge ($\sigma$) as the size of the source.

\begin{equation}\label{eq:Disk}
I_\text{disk}(x,y)=
\begin{cases}
\frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
0                      & x^2+y^2>\sigma^2.
\end{cases}
\end{equation}

\subsection{Spectral analysis}

We performed the spectral analysis of each TeV candidate using \pointlike and \gtlike, the standard likelihood analysis package for LAT data implemented in the Science Tools and distributed by the FSSC. It is a binned maximum-likelihood method \citep{1996ApJ...461..396M} that was extensively validated for spectral analysis and makes fewer approximations in calculating the likelihood than \pointlike. Both methods provided results in agreement with each other, but all spectral parameters quoted in the following were obtained using \gtlike. The spectrum of each source was determined using the best morphological model provided by \pointlike. Due to the narrow energy range which prevents the detection of curved spectra, we fitted all sources assuming a pure power-law of differential flux K and index $\Gamma$ presented in Equation \ref{PL}.

\begin{equation}
\label{PL}
\frac{dN}{dE}=K \times \left( \frac{E}{E_0} \right)^{\Gamma}
\end{equation}

To minimize the covariance between K and $\Gamma$, we ran the whole analysis twice. In the first iteration, we fitted the source assuming a power-law model depending on the integral flux N and $\Gamma$ shown in Equation \ref{PLFlux}.

\begin{equation}
\label{PLFlux}
\frac{dN}{dE}=\frac{N\times(\Gamma +1)\times E^{\Gamma}}{E_{max}^{\Gamma+1}-E_{min}^{\Gamma+1}}
\end{equation}

Using the covariance matrix between the parameters of the fit, we derived the pivot energy $E_p$ computed as the energy at which the relative uncertainty on the differential flux K was minimal \citep{2012ApJS..199...31N}. Then, we refitted the spectrum of the source assuming a power-law spectral model (Equation \ref{PL}) with the scale parameter $E_0$ fixed at $E_p$.

Once the morphological and spectral fit was determined, we derived the photon flux F(10--316~GeV) in photons cm$^{-2}$ s$^{-1}$ and the energy flux G(10--316~GeV) in erg cm$^{-2}$ s$^{-1}$ defined as:

\begin{eqnarray}
F(10-316 \, \rm GeV) = \int_{10 GeV}^{316 GeV} \frac{dN}{dE} dE\\
G(10-316 \, \rm GeV) = \int_{10 GeV}^{316 GeV} E \frac{dN}{dE} dE
\end{eqnarray}

\subsection{Source significance and extension}
\label{signi}

We measured the source significance using a test statistic (\text{TS}) defined as Equation \ref{eq:TS} , where $\mathcal{L}_1$ corresponds to the likelihood obtained by fitting a model of the source of interest and the background model and $\mathcal{L}_0$ corresponds to the likelihood obtained by fitting the background model only.

\begin{equation}
\label{eq:TS}
\text{TS}=2\times\log (\mathcal{L}_1/\mathcal{L}_0)
\end{equation}

In the following, all \text{TS} values were calculated using \gtlike and the corresponding significance was evaluated from the $\chi^2$ distribution with the corresponding number of degrees of freedom (d.o.f.).

We applied two criteria to decide if a source was significantly detected or not. We selected sources with a $\text{TS}$ above 16 (3.6 $\sigma$ with 2 d.o.f) when assuming the TeV morphology. Then, we applied a second filter on this list of sources by requiring $\text{TS}>16$ at the best GeV shape as well.

To test the extension of each source, following \cite{2012arXiv1207.0027L}, we defined $\text{TS}_{ext}$ as  Equation \ref{eq:Tsext} where $\mathcal{L}_{ext}$ represents the likelihood under an extended source hypothesis (5 d.o.f.) and $\mathcal{L}_{ps}$ represents the likelihood assuming a point source (4 d.o.f.). The condition for a source to be extended is $\text{TS}_{ext} > 16$.

\begin{equation}
\text{TS}_{ext}=2 \times \log({\mathcal{L}_{ext}}/{\mathcal{L}_{ps}})
\label{eq:Tsext}
\end{equation}

We also compared the GeV morphology to the TeV shape. The TeV shape was fixed and we fitted only the spectra as a power-law. To assess the significance of the GeV morphology compared to the TeV shape, we computed $\text{TS}_{GeV/TeV}$ as Equation \ref{eq:Tstevgev} where $\mathcal{L}_{TeV}$ corresponds to the likelihood obtained by fitting the source assuming the TeV shape and $\mathcal{L}_{GeV}$ to the likelihood obtained by fitting the source using the best shape derived using \emph{Fermi}-LAT data.

\begin{equation}
\text{TS}_{GeV/TeV}=2 \times \log({\mathcal{L}_{GeV}}/{\mathcal{L}_{TeV}})
\label{eq:Tstevgev}
\end{equation}

The correspondence between $\text{TS}_{GeV/TeV}$ and the significance is evaluated from a $\chi^2$ distribution with 2 supplementary d.o.f if the best GeV source is a point-like source and 3 supplementary d.o.f if the best GeV source is an extended source. We considered the GeV morphology to be significantly better than the TeV morphology when the likelihood of the fit is better at more than 3$\sigma$ level, which means $\text{TS}_{GeV/TeV} > 12$ for a point-like source in GeV, or $\text{TS}_{GeV/TeV} > 14$ for an extended source (uniform disk) in GeV. All values of $\text{TS}$, $\text{TS}_{ext}$ and $\text{TS}_{GeV/TeV}$ quoted in the following are obtained using \gtlike.

\subsection{Procedure followed}

The 56 regions summarized in Table~\ref{tab:TeV_sources} were all analyzed using the same procedure with both \gtlike and \pointlike:

\begin{enumerate}
\item{We fitted each source assuming its TeV shape summarized in Table~\ref{tab:TeV_sources}. Here, we fixed the position and morphology and fit the spectrum assuming a pure power-law leading the $\text{TS}$ to follow a $\chi^2$ distribution with only 2 d.o.f. 
\begin{itemize}
\item{For sources with significance above 3.6 $\sigma$ ($\text{TS}>$16 with 2 d.o.f.) we applied steps 2 and 3.} 
\item{For sources with $\text{TS}<$ 16 we derived a 99 \% upper limit on the flux assuming the TeV morphology and a power--law index of 2.}
\end{itemize}}
\item{We fitted the source assuming a point source localized with \pointlike as well as the neighbouring sources within 2$\degr$.}
\item{We fitted the source assuming a disk shape derived using \pointlike and compared this hypothesis to the point source hypothesis.}
\end{enumerate}

To take into account the modifications lead by our analysis and have a consistent analysis between all the regions studied, we performed a third iteration where we fixed the shape of the sources further than 2$\degr$ of the source of interest but included in our region to the best morphology found in this analysis (see section \ref{morph_res}). 
%Je n'arrive pas à être clair ici. Peut-etre ai-je fait une erreur. Pour que l'analyse soit cohérente et ne pas avoir une source modélisée d'une sorte dans une région et d'une autre sorte dans une autre région, j'ai retourné l'analyse en fixant les sources voisines non pas aux morphologies du 1FHL mais aux morphologies que j'ai trouvé. Par exemple la région de 1632 1634 a été tournée une première fois en ayant 1640 et 1616 aux morphologies inclues dans le 1FHL. Puis j'ai fait retourner la région avec 1640 et 1616 modélisé par les templates TeV).

For the significant sources ($\text{TS}_{TeV}>$16 and $\text{TS}_{GeV}>$16) we derived both the photon and energy fluxes inferred by the fit with the 1 sigma statistical errors, assuming the best morphology. When the source was not significant ($\text{TS}_{TeV}<$16 or $\text{TS}_{GeV}<$16), we derived a 99 \% Confidence Level (C.L.) Bayesian upper limit on the flux using a pure power-law model with an index fixed at 2, assuming the TeV shape.

\emph{Fermi}-LAT spectral points were obtained by splitting the 10--316 GeV range into 3 logarithmically spaced energy bins. A 99 \% C.L. upper limit is computed when $\text{TS}<$10 using the approach used by \cite{2012ApJS..199...31N}. The errors on the spectral points represent the statistical errors.

%This algorithm was used two times. During the first iteration we used the data selected in a $8\degr\times 8\degr$ square around the TeV position of the source of interest aligned with galactic coordinates. These region are extended enough to allow a reliable fit of the galactic diffuse template normalization \emph{ring\_2yearp7v6\_v0.fits}. In a second iteration we reduced the square to $4\degr\times4\degr$ and we fixed the galactic diffuse normalization to the value derived during the first iteration.\textbf{Develop}

%We launched a second iteration of this analysis with a smaller roi (4$\degr\times$4$\degr$) fixing the spectrum of the galactic background

\subsection{Systematics on the extension}
\label{systext}

Two main systematic uncertainties can affect the extension fit of the sources: uncertainties in our model of the galactic diffuse emission and uncertainties on our knowledge of the LAT PSF.

To estimate the systematics due to the uncertainty in our knowledge of the PSF, we used the pre-flight Monte Carlo representation of the PSF. Indeed, before launch, the LAT PSF was determined by detector simulations which we verified in accelerator beam tests \citep{2009ApJ...697.1071A}. However, in-flight data revealed a discrepancy above 3 GeV in the PSF compared to the angular distribution of photons. To account for this uncertainty, we refit our extended source candidates using the pre-flight  PSF and consider the difference in extension found using the two PSFs as a systematic error on the extension of a source. This procedure was already used by \cite{2012arXiv1207.0027L}.

To estimate the uncertainties on the galactic diffuse emission, we used a GALPROP-based model and considered the various components of the diffuse emission model separately. We then individually fit the normalizations of each of them in our likelihood analysis. These various components are gamma-rays produced by IC emission, gamma-rays produced by interactions of CRs with atomic and ionized interstellar gas, and gamma-rays produced in the interactions of CRs with molecular gas. The model component describing the gamma-ray intensity from interactions with molecular gas is further subdivided into seven ranges of Galactocentric distance. It is not expected that this diffuse model is superior to the standard LAT model obtained through an all-sky fit. However, adding degrees of freedom to the background model can remove likely spurious sources that correlate with features in the Galactic diffuse emission. Therefore, this tests systematics that may be due to imperfect modeling of the diffuse emission in the region. This procedure was also used by \cite{2012arXiv1207.0027L}.

The total systematic error on the extension of a source was obtained by adding the two errors in quadrature.

\subsection{Systematics on the spectral parameters}
\label{syst}

Three main systematic uncertainties can affect the LAT flux estimate for an extended source: uncertainties in the Galactic diffuse background, uncertainties on the effective area and uncertainties on the shape of the source.

The dominant uncertainty comes from the Galactic diffuse emission and was estimated by using the GALPROP-based model described in Section~\ref{systext}.

The second systematic was determined by using modified IRFs whose effective areas bracket the nominal ones. These bracketing IRFs are defined by envelopes above and below the nominal energy dependence of the effective area by linearly connecting differences of (10\%, 5\%, 20\%) at log10(E/MeV) of (2, 2.75, 4), respectively.

The imperfect knowledge of the true $\gamma$-ray morphology introduces a last source of error. We derived an estimate of the uncertainty on the shape of the source by using the best model obtained by TeV experiments and compared it to the best extension value obtained in this analysis. We did not compute this component for the sources where the GeV emission is clearly associated to a contamination by the pulsar.

We combined these various errors in quadrature to obtain our best estimate of the total systematic uncertainty at each energy and propagated through to the fit model parameters.

### 2012-09-02 pwncatalog/PWNCAT2/code/analyze_helper.py
move

@@ -1,388 +1,0 @@
-# Not entirely sure why, but pyLikelihood
-# will get a swig::stop_iteraiton error
-# unless it is imported first.
-from lande.fermi.likelihood.roi_gtlike import Gtlike
-
-import traceback
-import sys
-import os
-import pylab as P
-import numpy as np
-
-import yaml
-
-from uw.like.roi_state import PointlikeState
-from uw.pulsar.phase_range import PhaseRange
-from uw.like.SpatialModels import Gaussian
-
-from lande.utilities.tools import tolist
-
-from lande.fermi.spectra.plotting import plot_all_seds
-from lande.fermi.likelihood.fit import paranoid_gtlike_fit, fit_prefactor, fit_only_source, freeze_insignificant_to_catalog, freeze_bad_index_to_catalog
-from lande.fermi.likelihood.save import sourcedict, get_full_energy_range
-from lande.fermi.likelihood.limits import powerlaw_upper_limit, cutoff_upper_limit
-from lande.fermi.likelihood.localize import GridLocalize, paranoid_localize
-from lande.fermi.likelihood.cutoff import plot_gtlike_cutoff_test, test_cutoff, fix_bad_cutoffs
-from lande.fermi.likelihood.bandfitter import BandFitter
-from lande.fermi.likelihood.printing import summary
-from lande.fermi.pulsar.plotting import plot_phaseogram,plot_phase_vs_time
-from lande.fermi.spectra.sed import GtlikeSED
-from lande.fermi.data.plotting import ROITSMapBandPlotter, ROISourceBandPlotter, ROISourcesBandPlotter
-from lande.fermi.likelihood.free import freeze_far_away, unfreeze_far_away
-
-from setup_pwn import PWNRegion
-
-close=lambda x,y: np.allclose(x,y, rtol=0, atol=1)
-all_energy=lambda emin,emax: close([emin,emax],[1e2,10**5.5]) or close([emin,emax],[1e2,1e5])
-high_energy=lambda emin,emax: close([emin,emax],[10**4,10**5.5])
-higher_energy=lambda emin,emax: close([emin,emax],[10**4.5,10**5.5])
-
-def one_bin_per_dec(emin,emax):
-    assert close(emin,1e2) and (close(emax,1e5) or close(emax,10**5.5))
-    if close(emax,1e5):
-        return np.logspace(2,5,4)
-    elif close(emax,10**5.5):
[…]

### 2012-09-02 pwncatalog/PWNCAT2/code/analyze_psr.py

@@ -1,114 +1,0 @@
-#!/usr/bin/env python
-
-# This import has to come first
-from analyze_helper import pointlike_analysis,gtlike_analysis,save_results,\
-        plot_phaseogram,plot_phase_vs_time,all_energy,import_module
-from uw.pulsar.phase_range import PhaseRange
-from lande.fermi.likelihood.tools import force_gradient
-from skymaps import SkyDir
-
-from uw.like.SpatialModels import Gaussian
-
-import os
-from os.path import join
-from glob import glob
-
-from lande.fermi.likelihood.parlimits import all_params_limited
-
-from setup_pwn import PWNRegion
-from argparse import ArgumentParser
-import yaml
-
-from collections import defaultdict
-import numpy as np
-np.seterr(all='ignore')
-
-
-def get_args():
-
-    parser = ArgumentParser()
-    parser.add_argument("--pwndata", required=True)
-    parser.add_argument("-p", "--pwnphase")
-    parser.add_argument("--no-phase-cut", default=False, action="store_true")
-    parser.add_argument("-n", "--name", required=True, help="Name of the pulsar")
-    parser.add_argument("--emin", default=1e2, type=float)
-    parser.add_argument("--binsperdec", default=4, type=int)
-    parser.add_argument("--emax", default=10**5.5, type=float)
-    parser.add_argument("--use-gradient", default=False, action="store_true")
-    parser.add_argument("--no-at-pulsar", default=False, action="store_true")
-    parser.add_argument("--no-point", default=False, action="store_true")
-    parser.add_argument("--no-extended", default=False, action="store_true")
-    parser.add_argument("--no-cutoff", default=False, action="store_true")
-    parser.add_argument("--no-savedir", default=False, action="store_true")
-    parser.add_argument("--max-free", default=5, type=float)
-    parser.add_argument("--modify", required=True)
-    args=parser.parse_args()
-    return args
-
-
-if __name__ == '__main__':
-    args = get_args()
-
-    do_at_pulsar = not args.no_at_pulsar
-    do_point = not args.no_point
-    do_extended = not args.no_extended
-    do_cutoff = not args.no_cutoff
-
-    force_gradient(use_gradient=args.use_gradient)
-
-    name=args.name
-    emin=args.emin
-    emax=args.emax
-
-    pwnphase=yaml.load(open(args.pwnphase))[name]
-    if args.no_phase_cut:
-        phase = PhaseRange(0,1)
-    else:
[…]

### 2012-09-02 pwncatalog/PWNCAT2/code/merge_psr.py

@@ -1,33 +1,0 @@
-import os
-from os.path import join,exists
-from glob import glob
-
-import yaml
-import numpy as np
-
-from lande.utilities.tools import merge_dict,tolist
-
-for psr in glob('PSR*'):
-
-    os.chdir(psr)
-
-    pointlike_results = 'results_%s_pointlike.yaml' % psr
-    gtlike_results = [ 'results_%s_gtlike_%s.yaml' % (psr,i) for i in ['at_pulsar', 'point', 'extended']]
-    extul_results = 'results_%s_extul_point.yaml' % psr
-
-    all_results = [pointlike_results,extul_results]+gtlike_results
-    if np.all(map(exists,all_results)):
-        print 'Merging Pulsar %s' % psr
-
-        all_dicts = [yaml.load(open(i)) for i in all_results]
-        results = tolist(merge_dict(all_dicts))
-
-        for which in ['pointlike','gtlike']:
-            results['extended'][which]['ts_ext'] = \
-                    2*(results['extended'][which]['logLikelihood'] - results['point'][which]['logLikelihood'])
-
-        open('results_%s.yaml' % psr,'w').write(yaml.dump(results))
-    else:
-        print 'Skippign Pulsar %s (not all jobs complete)' % psr
-
-    os.chdir('..')

### 2012-09-02 pwncatalog/PWNCAT2/code/lande/interp/auto_classify.py
update

@@ -1,0 +1,9 @@
+from lande.utilities.save import savedict
+from lande.fermi.pipeline.pwncat2.interp.classify import auto_classify
+
+classifications=auto_classify(pwndata='$pwncode/data/pwncat2_data_lande.yaml', 
+                              fitdir='$pwndata/spectral/v29/analysis/')
+
+savedict('$pwndata/spectral/v29/classify/automatic_classifications.yaml',
+         classifications,
+         yaml_kwargs=dict(default_flow_style=False))

### 2012-09-02 pwncatalog/PWNCAT2/code/lande/tables/auxiliary_table.py

@@ -1,0 +1,8 @@
+from lande.pipeline.pwncat2.table.auxiliary import auxiliary_table
+
+auxiliary_table(
+    pwndata='$pwncode/data/pwncat2_data_lande.yaml',
+    fitdir='$pwndata/spectral/v29/analysis',
+    filename='$pwndata/spectral/v29/tables/auxiliary_table.fits',
+    pwn_classification='$pwndata/spectral/v29/classify/automatic_classifications.yaml',
+)

### 2012-09-02 pwncatalog/PWNCAT2/draft_text/subsections/off_peak_results.tex
move

\subsection{Results}

After analyzing the off-peak emission using the pipeline described
in \subsecref{off_peak_analysis}, we consider any emission in the
off-peak region to be magnetospheric in nature if the emission is
not significantly-extended and has a significantly-cutoff spectrum.
We consider the emission to originate in the pulsar wind if it is
spatially extended or had a hard spectral index.  If the source is
point-like and had a soft spectrum, or if it is formally spatially
extended but if the best-fit extension is biased by nearby point-like
sources, we flag the source as confused and do not speculate on the
origin of the emission.  For these confused regions, we include in our
results the best fit spectrum at the position of the pulsar assuming a
point-like spectral model.

A condensed summary of the results of the pipeline can be found in
\tabref{off_peak_table}. This table includes the significance of the source,
extension, and cutoff as well as the spectrum of the source.
In addition, \figref{off_peak_seds} shows the best fit spectral
models for a selection of the significantly-detected sources.

\begin{deluxetable}{l*{7}c}
\tabletypesize{\scriptsize}
\tablecaption{Off-Peak Spatial and Spectral Results
\label{tab:off_peak_table}
}
\input{tables/off_peak_spatial_spectral.tex}
\tablecomments{A condensed version of the spectral analysis of
sources detected significantly in the off-peak regions.
This table includes the significance of the source, extension, and 
spectral cutoff (\ts, \tsext, \tscut).  The table also includes
the best fit spectrum for these sources. For sources that are
significantly cutoff, the spectral index and cutoff energy are from the
fit of a cutoff spectrum.
}
\end{deluxetable}

\begin{figure}
  \ifdefined\bwfigures
  \plotone{off_peak_seds_bw.eps}
  \else
  \plotone{off_peak_seds_color.eps}
  \fi
  \caption{SEDs for several sources significantly-detected in the off-peak region.}
  \label{fig:seds_test}
\end{figure}

Consistent with \citep{LAT_Collaboration_Crab_Flare_2011}, we found
the Crab nebula to be highly variable with \tsvar=XXXXXX.  Besides that,
we found no significantly variable off-peak emission.  The results of
the variability test are contained in the auxiliary information.

The results of the spectral analysis in smaller energy bands described
in section \subsecref{peak_analysis} are included in the auxiliary
information. In addition, upper limits computed assuming a power law
spectral model and a canonical pulsar spectrum are included in the
auxiliary information.

In our pipeline, we found XXXXX off-peak regions to show significant PWNe.
We detected the Vela X PWN (associated with PSRJ0835$-$4510), the Crab Nebula (associated
with PSRJ0534+2200), and MSH 15$-$52 (associated with PSRJ1513-5908).
\begin{itemize}
  \item What to say about PSRJ1023-5746, which was a PWN in PWNCAT1, but here shows a complicated spectrum???
\end{itemize}

We detected XXXXX of the regions to show clear magnetopsheric pulsar emission.
These pulsars are ...

And Finally, we found XXXXX regions which where the analysis could not decisively determine the nature of the emission.
\begin{itemize}
  \item PSRJ0101-6422 was fit to have an unphysically soft spectrum. We suspect that source is an artifact of
  problems modeling the nearby diffuse emission.
  \item PSRJ1112-6103: Very close to MSH 11~62 (arXiv:1202.3371v1). Nearby source is 2FGL J1112.1-6040. Significant extension.
  \item When fitting PSRJ1119-6127, description of adding nearby point
  source to represent emission residual from o represent residual from
  PSRJ1112-6103 looking spatially
    extended.
  \item PSRJ1418-6058 and PSRJ1420-6048, very difficult to analyze because both very near each other.
  \item Something about the complicated Gamma Cygni PSR: PSRJ2021+4026
  \item PSRJ1105-6107: something about adding source to background model that is very nearby.
  \item PSRJ1648-4611 (what to do about nearby 2FGL source and other residual emission. Is this paper relevant: http://arxiv.org/pdf/1111.2043.pdf???)?
  \item What to do about emission from PSR J1023 at low energy???
  \item PSRJ0908-4913: what to say about far localization?
\end{itemize}

### 2012-09-02 general/bash/general_settings.sh
update

@@ -1,6 +1,6 @@
 # These are my bash
 
-function terminal_tweaks {
+function setup_terminal_tweaks {
     [ -z "$PS1" ] && return
     export TERM=xterm-color
 
@@ -23,7 +23,6 @@ function terminal_tweaks {
 }
 
 
-terminal_tweaks
 
 
 function get_known_hosts {
@@ -32,7 +31,7 @@ function get_known_hosts {
     echo curl ftp://ftp.slac.stanford.edu/admin/known_hosts  > ~/.ssh/known_hosts
 }
 
-function alias_general {
+function setup_alias_general {
 
     alias clean="rm -f *~;rm -f .*~;rm -f '#'*;rm -rf .*.swp;rm -rf .'#'*"
     alias screen='screen -RD'
@@ -72,19 +71,25 @@ function alias_general {
     # http://svn.haxx.se/users/archive-2004-12/0809.shtml
     bind 'set match-hidden-files off' 
 }
-alias_general
 
-function python_general {
+function setup_python_general {
 export PYTHONUNBUFFERED=True
 }
-python_general
 
 
-function lande_svn_setup {
+function setup_svn_lande {
     # Best to put my SVN in the same place on all machine so
     # aliases are the same
     export svn=$HOME/svn/lande/trunk
     export presentations=$svn/presentations/
     export lande=/u/gl/lande/svn/lande/trunk/code/lande
 }
-lande_svn_setup
+
+
+function setup_default_general {
+    setup_terminal_tweaks
+    setup_alias_general
+    setup_python_general
+    setup_svn_lande
+}
+setup_default_general

### 2012-09-02 general/bash/slac_settings.sh

@@ -59,11 +59,10 @@ function kipacsetup {
 
 function fix_matplotlib {
     # This says to use file .matplotlib/matplotlibrc for my configuration
-    export MATPLOTLIBRC=~/.matplotlib/
+    export MATPLOTLIBRC=~/.matplotlib
     # whereas this says to use as a temp folder random scratch space.
-    export MPLCONFIGDIR=/scratch/
+    export MPLCONFIGDIR=/scratch
 }
-fix_matplotlib
 
 
 function set_bldtype {
@@ -92,12 +91,13 @@ function set_bldtype {
 
 function _stockscons {
     export SCTOOLS=$1
+    export optflag=$2
 
     set_bldtype
     export GLAST_EXT=/afs/slac/g/glast/ground/GLAST_EXT/${BLDTYPE}
     export BUILDS=/nfs/farm/g/glast/u35/ReleaseManagerBuild
-    export INST_DIR=${BUILDS}/${BLDTYPE}/Optimized/ScienceTools/$SCTOOLS
-    source ${INST_DIR}/bin/${BLDTYPE}-Optimized/_setup.sh
+    export INST_DIR=${BUILDS}/${BLDTYPE}/$optflag/ScienceTools/$SCTOOLS
+    source ${INST_DIR}/bin/${BLDTYPE}-$optflag/_setup.sh
 
     #export PATH=$GLAST_EXT/python/2.7.1/gcc41/bin:$PATH
     #export PATH=$GLAST_EXT/python/2.6.5/gcc41/bin:$PATH
@@ -106,18 +106,44 @@ function _stockscons {
     export CUSTOM_IRF_DIR=$FERMI/irfs
     export CUSTOM_IRF_NAMES=P7SOURCE_V4PSF,P7SOURCE_V4
 
+
+    # get my version of ipython        
+    export PATH=~/bin:$PATH
+
     export setup="${setup} stockscons"
 }
 
 function stockscons {
-    _stockscons 09-27-01
+#    _stockscons 09-25-00
+#    _stockscons 09-27-01 Optimized
+#    _stockscons HEAD-1-972 Debug
+#    _stockscons 09-28-00 Optimized
+#    _stockscons HEAD-1-981 Debug
+
+    # This version has my variability bug fixed in skymaps
+    #_stockscons HEAD-1-985 Debug
+    #_stockscons HEAD-1-980 Debug
+    _stockscons 09-29-00 Optimized
+}
+
+function testsconcs {
+    # for testing stuff
[…]

### 2012-09-02 fermi/snrlim/code/run.py
add

@@ -1,0 +1,11 @@
+from argparse import ArgumentParser
+
+from lande.fermi.pipeline.snrlim.main import run
+
+parser = ArgumentParser()
+parser.add_argument("-n", "--name", required=True, help="Name of the pulsar")
+parser.add_argument("--snrdata", required=True)
+parser.add_argument("--latdata", required=True)
+args=parser.parse_args()
+
+run(name=args.name, snrdata=args.snrdata, latdata=args.latdata)

### 2012-09-02 green_catalog/SNRCAT1/pipeline/lande_pipeline.py
udpate

@@ -89,7 +89,7 @@ if do_plots: plots(roi, hypothesis='point', **plot_kwargs)
 print '\n\nAnalyze SNR as extended source\n\n'
 
 roi.del_source(which=name)
-roi.add_source(get_snr(name, superfile))
+roi.add_source(get_snr(name, superfile, point_like=False))
 
 results['extended'] = {}
 results['extended']['pointlike']=pointlike_analysis(roi, hypothesis='extended', 

### 2012-10-16 papers/tevcat/sections/acknowledgements.tex
removed folder draft_v0
16/10/2012 : latest version with discussion and conclusion

--- 2012-01-19 pwncatalog/PWNCAT2/paper/sections/acknowledgements.tex
@@
 
-The authors acknowledge the use of
-HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.
+This research has made use of pywcsgrid2, an open-source plotting package for Python6\footnote{http://leejjoon.github.com/pywcsgrid2/}.
+The authors acknowledge the use of HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{2005ApJ...622..759G}.
+
+The authors acknowledge the use of the TeV catalog website\footnote{http://tevcat.uchicago.edu/} provided by the university of Chicago.
+
+The authors acknowledge the use of the \emph{Australia Telescope National Facility} pulsar catalog\footnote{http://www.atnf.csiro.au/people/pulsar/psrcat/}.

### 2012-10-16 papers/tevcat/sections/build_the_candidate_list.tex
16/10/2012 : latest version with discussion and conclusion

\section{List of candidates}
As a starting point, we used the catalog of TeV sources provided by the university of Chicago\footnotemark[1] to build our list of candidates. This catalog summarizes the information of all sources detected by the TeV experiments. Looking for PWNe candidates which are Galactic sources, we selected the sources located within $\pm$5$\degr$ in latitude.

The Galactic center being a complex region to study with \emph{Fermi}-LAT, due to the contamination by the large density of sources and by the diffuse emission, we removed all sources within 5$\degr$ of the Galactic center. Therefore, we did not include to our list the three sources HESS~J1745-303, HESS~J1741-302 and G~0.9+0.1 \citep{Mouse, Mouse2}.

TeV sources associated to SNRs will not be discussed in this analysis. These sources will be included in a forthcoming paper which aims at bringing constraints on all known SNRs using the \emph{Fermi}--LAT data \cite{SNRcat}.

Finally we removed from this analysis the Crab Nebula and Vela-X. Both were already studied in details (\cite{2010ApJ...708.1254A}, \cite{2012ApJ...749...26B}), and the second is the object of a new analysis \cite{VelaX}.

The final list of 58 sources studied in this analysis is summarized in Table~\ref{tab:TeV_sources} together with their morphology as seen in TeV.

### 2012-10-16 papers/tevcat/sections/method.tex
16/10/2012 : latest version with discussion and conclusion

@@
 
-\pointlike and \gtlike using two different shapes for the region of interest, we used all events contained in a disk of 5$\degr$ centered on the location of the TeV source when fitting the region with \pointlike and we used a $7\degr \times 7\degr$ square included in the previous disk when fitting the region using \gtlike.
+\pointlike and \gtlike using two different shapes for the region of interest, we used all events contained in a disk of radius 5$\degr$ centered on the location of the TeV source when fitting the region with \pointlike and we used a $7\degr \times 7\degr$ square included in the previous disk when fitting the region using \gtlike.
 We tried to keep the two methods as close as possible by using the same conventions (same spatial binning : $\sim 0.06\degr/$bin, same energy binning : 8 energy bins per decade between 10~GeV and 316~GeV, same optimizer : MINUIT \citep{JamesRoos1975}).
@@
 
-Sources within 10$\degr$ around each source of interest and listed in the hard source list \textbf{(cite the hard source list paper)} were included in our spatial-spectral model.
+Sources within 10$\degr$ around each source of interest and listed in the hard source list \citep{1FHL} were included in our spatial-spectral model.
 We replaced potential TeV counterparts by a source with the TeV morphology summarized in Table \ref{tab:TeV_sources}.
-The spectral parameters of sources closer than 2$\degr$ to the source of interest were left free, while the parameters of all other sources were fixed at the hard source list (1FHL) catalog values.
+The spectral parameters of sources closer than 2$\degr$ to the source of interest were left free, while the parameters of all other sources were fixed at the hard source list (1FHL) catalog values \citep{1FHL}.
 
-Table \ref{tab:pulsars} summarizes the sources of our list located close to a pulsar detected by the \emph{Fermi}-LAT \textbf{cite 2PC}.
+Table \ref{tab:pulsars} summarizes the sources of our list located close to a pulsar detected by the \emph{Fermi}-LAT \citep{2PC}.
 The proximity of the pulsar can lead either to the non detection of a faint source hidden by the pulsed emission or to a contamination at low energy if the pulsar is not included.
-We decided to include in our analysis all the pulsars if they were outside of the TeV template or if they were more than 0.27$\degr$ away from the source of interest.
-Section \ref{puls_cont} will show the results for the sources close to the pulsars in the case were we added the pulsar in the model and fitted the TeV source.
+We decided to include in our analysis all pulsars located outside of the TeV template or more than 0.27$\degr$ away from the source of interest, corresponding to the average PSF above 10 GeV.
+Section \ref{pulsarsect} will show the results for the sources close to the pulsars in the case where we added the pulsar in the model and fitted the TeV source.
 
@@
 
-%Thus, we added the sources summarized in Tab. \ref{tab:newsources} to take these excesses into account. We fitted their spectra assuming a pure power--law above 10~GeV.
+%Therefore, we added the sources summarized in Table \ref{tab:newsources} to take these excesses into account. We fitted their spectra assuming a pure power--law above 10~GeV.
 
@@
 \subsection{Analysis of the shape}
+\label{spatanalysis}
 
@@
 
-As previously done in \cite{2012arXiv1207.0027L}, we only used radially-symmetric uniform disk shape (defined in Equation \ref{eq:Disk}) to fit the extension of the GeV emission.
+As previously done in \cite{2012arXiv1207.0027L}, we only used a radially-symmetric uniform disk shape (defined in Equation \ref{eq:Disk}) to fit the extension of the GeV emission.
 In the following, we quote the radius to the edge ($\sigma$) as the size of the source.
@@
 \begin{eqnarray}
-F(10-316 \, \rm GeV) = \int_{10 GeV}^{316 GeV} \frac{dN}{dE} dE\\
-G(10-316 \, \rm GeV) = \int_{10 GeV}^{316 GeV} E \frac{dN}{dE} dE
+F(10-316\text{ GeV}) = \int_{\text{10 GeV}}^{\text{316 GeV}} \frac{dN}{dE} dE\\
+G(10-316\text{ GeV}) = \int_{\text{10 GeV}}^{\text{316 GeV}} E \frac{dN}{dE} dE
+\label{energy_flux}
 \end{eqnarray}
@@
 
-We measured the source significance using a test statistic (\text{TS}) defined as Equation \ref{eq:TS} , where $\mathcal{L}_1$ corresponds to the likelihood obtained by fitting a model of the source of interest and the background model and $\mathcal{L}_0$ corresponds to the likelihood obtained by fitting the background model only.
+We measured the source significance using a test statistic (\text{TS}) defined as Equation \ref{eq:TS}, where $\mathcal{L}_1$ corresponds to the likelihood obtained by fitting a model of the source of interest and the background model and $\mathcal{L}_0$ corresponds to the likelihood obtained by fitting the background model only.
 
@@
 
-We applied two criteria to decide if a source was significantly detected or not.
+To decide if a source was significantly detected or not, we selected sources with a $\text{TS}$ above 16 (3.6 $\sigma$ with 2 d.o.f) when assuming the TeV morphology.
+
+%We applied two criteria to decide if a source was significantly detected or not.
 We selected sources with a $\text{TS}$ above 16 (3.6 $\sigma$ with 2 d.o.f) when assuming the TeV morphology.
@@
 
-The 56 regions summarized in Table~\ref{tab:TeV_sources} were all analyzed using the same procedure with both \gtlike and \pointlike:
+The 58 regions summarized in Table~\ref{tab:TeV_sources} were all analyzed using the same procedure with both \gtlike and \pointlike:
 
@@
 
-To take into account the modifications lead by our analysis and have a consistent analysis between all the regions studied, we performed a third iteration where we fixed the shape of the sources further than 2$\degr$ of the source of interest but included in our region to the best morphology found in this analysis (see section \ref{morph_res}).
+To have a self consistent analysis between all regions studied, we performed a third iteration where we used the best shape found in our pipeline for all sources located in the region of interest.
+
+%To take into account the modifications lead by our analysis and have a consistent analysis between all the regions studied, we performed a third iteration where we fixed the shape of the sources further than 2$\degr$ of the source of interest but included in our region to the best morphology found in this analysis (see section \ref{morph_res}).
+
 %Je n'arrive pas à être clair ici.
@@
 
-For the significant sources ($\text{TS}_{TeV}>$16 and $\text{TS}_{GeV}>$16) we derived both the photon and energy fluxes inferred by the fit with the 1 sigma statistical errors, assuming the best morphology.
-When the source was not significant ($\text{TS}_{TeV}<$16 or $\text{TS}_{GeV}<$16), we derived a 99 \% Confidence Level (C.L.) Bayesian upper limit on the flux using a pure power-law model with an index fixed at 2, assuming the TeV shape.
+For the significant sources ($\text{TS}_{TeV}>$16) we derived both the photon and energy fluxes inferred by the fit with the 1 sigma statistical errors, assuming the best morphology.
+When the source was not significant ($\text{TS}_{TeV}<$16), we derived a 99 \% Confidence Level (C.L.) Bayesian upper limit on the flux using a pure power-law model with an index fixed at 2, assuming the TeV shape.
 
@@
 upper limit is computed when $\text{TS}<$10 using the approach used by \cite{2012ApJS..199...31N}.
-The errors on the spectral points represent the statistical errors.
+The errors on the spectral points represent the statistic and systematic uncertainties as discussed below.
 
 %This algorithm was used two times.
-During the first iteration we used the data selected in a $8\degr\times 8\degr$ square around the TeV position of the source of interest aligned with galactic coordinates.
-These region are extended enough to allow a reliable fit of the galactic diffuse template normalization \emph{ring\_2yearp7v6\_v0.fits}.
-In a second iteration we reduced the square to $4\degr\times4\degr$ and we fixed the galactic diffuse normalization to the value derived during the first iteration.\textbf{Develop}
+During the first iteration we used the data selected in a $8\degr\times 8\degr$ square around the TeV position of the source of interest aligned with Galactic coordinates.
+These region are extended enough to allow a reliable fit of the Galactic diffuse template normalization \emph{ring\_2yearp7v6\_v0.fits}.
+In a second iteration we reduced the square to $4\degr\times4\degr$ and we fixed the Galactic diffuse normalization to the value derived during the first iteration.\textbf{Develop}
 
-%We launched a second iteration of this analysis with a smaller roi (4$\degr\times$4$\degr$) fixing the spectrum of the galactic background
+%We launched a second iteration of this analysis with a smaller roi (4$\degr\times$4$\degr$) fixing the spectrum of the Galactic background
 
@@
 
-Two main systematic uncertainties can affect the extension fit of the sources: uncertainties in our model of the galactic diffuse emission and uncertainties on our knowledge of the LAT PSF.
+Two main systematic uncertainties can affect the extension fit of the sources: uncertainties in our model of the Galactic diffuse emission and uncertainties on our knowledge of the LAT PSF.
 
@@
 
-To estimate the uncertainties on the galactic diffuse emission, we used a GALPROP-based model and considered the various components of the diffuse emission model separately.
+To estimate the uncertainties on the Galactic diffuse emission, we used a GALPROP-based model and considered the various components of the diffuse emission model separately.
 We then individually fit the normalizations of each of them in our likelihood analysis.
-These various components are gamma-rays produced by IC emission, gamma-rays produced by interactions of CRs with atomic and ionized interstellar gas, and gamma-rays produced in the interactions of CRs with molecular gas.
-The model component describing the gamma-ray intensity from interactions with molecular gas is further subdivided into seven ranges of Galactocentric distance.
+These various components are $\gamma$-rays produced by IC emission, $\gamma$-rays produced by interactions of CRs with atomic and ionized interstellar gas, and $\gamma$-rays produced in the interactions of CRs with molecular gas.
+The model component describing the $\gamma$-ray intensity from interactions with molecular gas is further subdivided into seven ranges of Galactocentric distance.
 It is not expected that this diffuse model is superior to the standard LAT model obtained through an all-sky fit.

### 2012-10-16 papers/tevcat/tables.tex
16/10/2012 : latest version with discussion and conclusion

--- 2012-08-30 papers/tevcat/draft_v0/tables.tex
@@
 
-\tablecomments{ The first two columns are TeV source names and types as defined in the TeV catalog provided by the university of Chicago: PWN for Pulsar Wind Nebula, PSR for Pulsars, UNID for Unidentified sources, Massive Star Cluster and Star Forming Regions.
+\tablecomments{The first two columns list the TeV source names and types as defined in the TeV catalog provided by the university of Chicago: PWN for Pulsar Wind Nebula, PSR for Pulsars, UNID for Unidentified sources, Massive Star Cluster and Star Forming Regions.
 The 3$^{rd}$ column reports the Galactic coordinates for each source.
@@
 b- The pulsar is located inside the edge of the TeV shape.\\
-c- The pulsar shown no significant excess.\\
+c- No significant excess above 10 GeV at the position of the pulsar.\\
 \end{flushleft}
 \tablecomments{ $_{ }$List of sources having a known $\gamma$-ray pulsar within 0.5$\degr$.
-The two first column shows the TeV source and the pulsar name.
-The third column show the distance between the TeV source and the GeV pulsar.
-The pulsar position comes from \textbf{Citer 2PC}.
+The two first columns list the TeV source and the pulsar name.
+The third column gives the distance between the TeV source and the GeV pulsar.
+The pulsar position comes from \cite{2PC}.
 In the fourth colum Y means that we added the pulsar to the model and N that we didn't added it.}
@@
 \tablecomments{Results of the maximum likelihood spectral fits  
-for LAT-detected TeV sources. The test statistic (TS) for the source significance is provided in column 2. 
-Columns 3 and 4 list the photon flux F(10--316 GeV) and the 
+for LAT-detected TeV sources. The test statistic (TS) for the source significance is provided in column 2. Columns 3 and 4 list the photon flux F(10--316 GeV) and the 
 energy flux G(10--316~GeV). The fits used the best morphology reported in Table~\ref{tab:GeVmorph} and a power-law spectral model (see Equation~\ref{PL}) with photon index $\Gamma$ given in column 5. 
@@
 
-\tablecomments{Results of the maximum likelihood spectral fits  
-for LAT-detected TeV sources in three different energy bands: 10--31 GeV, 31--100 GeV, 100--316 GeV using the same convention as in Table~\ref{tab:det_sources}.
+\tablecomments{Results of the maximum likelihood spectral fits for LAT-detected TeV sources in three different energy bands: 10--31 GeV, 31--100 GeV, 100--316 GeV using the same convention as in Table~\ref{tab:det_sources}.
 A 99\% c.l.
@@
 \tablecomments{ Results of the maximum likelihood spectral fits  
-for non-detected TeV sources. The test statistic (TS) for the source significance is provided in column 2. 
-Columns 3 and 4 list the 99\% c.l. upper limits on the photon flux F(10--316 GeV) and on the 
+for non-detected TeV sources. The test statistic (TS) for the source significance is provided in column 2. Columns 3 and 4 list the 99\% c.l. upper limits on the photon flux F(10--316 GeV) and on the 
 energy flux G(10--316~GeV). The fits used the TeV template defined in Table~\ref{tab:TeV_sources} and a power-law spectral model (see Equation~\ref{PL}) with photon index fixed at 2. }
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Upper limits for non-detected TeV sources in three energy bands logarithmically-spaced between 10 and 316 GeV
+\tablecaption{Upper limits for non-detected sources in 3 logarithmically-spaced energy bands
 \tabletypesize{\scriptsize}
@@
 
-\tablecomments{Results of the maximum likelihood spectral fits  
-for sources with a known $\gamma$-ray pulsar within 0.5 $\degr$.
+\tablecomments{Results of the maximum likelihood spectral fits for sources with a known $\gamma$-ray pulsar within 0.5$\degr$.
 The pulsar is included in the model with the spectral parameters derived in the 2FGL catalog \cite{2012ApJS..199...31N}.
@@
 PSR J1513-5908 and PSR J1702-4128 were detected after the 2FGL catalog analysis \citep{2012ApJS..199...31N}.
-Thus no spectral parameters were available.}
+Therefore no spectral parameters were available for these 2 pulsars.}
 
@@
 \noindent
+\clearpage
+
+\begin{deluxetable}{llcccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Pulsars characteristics.
+\tabletypesize{\scriptsize}
+\label{tab:table_luminosity}}
+\tablewidth{0pt}
+\input{tables/table_luminosity.tex}\\
+
+\tablecomments{This table summarizes the pulsars properties taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}.
+Column 3 shows the pulsar spin-down power as found in the litterature, column 4 and 5 present the characteristic age of the pulsar and its distance.\\References: (1) \cite{1973PASP...85..579T}, (2) \cite{2008MNRAS.389.1881K}, (3) \cite{2004MNRAS.352.1405C}, (4) \cite{dalton1303}, (5) \cite{2005yCat.7245....0M}, (6) \cite{2006MNRAS.372..777L}, (7) \cite{1997ApJ...476..347Y}, (8) \cite{2012ApJ...750..162K}, (9) \cite{2009ApJ...694...12M}, (10) \cite{1996ApJ...471..887S}, (11) \cite{1999ApJ...511..274S}, (12) \cite{2007ApJ...662..517F}, (13) \cite{2003MNRAS.342.1299K}, (14) \cite{1995A&A...293..795J},  (15) \cite{2001MNRAS.328...17M}, (16) \cite{2011ICRC....7..247H}, (17) \cite{2006ApJ...637..456C}, (18) \cite{2012ApJ...755L..20P}, (19) \cite{2008AIPC.1085..372C}, (20) \cite{2011ApJ...729L..16G}, (21) \cite{2010ApJ...708.1426W}, (22) \cite{2012ApJ...755...39V}, (23) \cite{1997ApJ...476..347Y}, (24) \cite{2004ApJ...612..389H}, (25) \cite{2009ApJ...706.1331A}, (26) \cite{2001ApJ...560..236K}, (27) \cite{1993AJ....105.1060P}, (28) \cite{2008AJ....136.1477L}, (29) \cite{2003ApJ...596.1137D}, (30) \cite{2010ApJ...725..571S}, (31) \cite{2009ApJ...691..895T}, (32) \cite{2010A&A...520A.111B}.}
+
+\end{deluxetable}
+\normalsize
+\noindent
+
+\normalsize
+\noindent
+\clearpage
+
+\begin{deluxetable}{llccccc}
+\tabletypesize{\scriptsize}
+\tablecaption{PWNe properties.
+\tabletypesize{\scriptsize}
+\label{tab:table_luminosity2}}
+\tablewidth{0pt}
+\input{tables/table_luminosity_2.tex}\\
+
+\tablecomments{This table summarizes the PWNe properties and the fluxes taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}.
+Column 2,3 and 4 summarize the fluxes found in the GeV (10-316 GeV) , TeV (1-30 TeV) and X-ray (2-10 keV) energy ranges.
+Column 5 shows the luminosity found using the energy flux in column 2 and the distance in Table \ref{tab:table_luminosity}.
+\\References : (1) \cite{2009ApJ...694...12M} and references therein, (2) \cite{2011AA...525A..46H}, (3) \cite{Mayerdiploma}, (4) \cite{2011AA...533A.103H}, (5) \cite{2012arXiv1205.0719D}, (6) \cite{2010A&A...520A.111B}, (7) \cite{2006ApJ...636..777A}, (8) \cite{2011arXiv1112.2901H}, (9) \cite{2008AA...477..353A}, (10) \cite{2008AIPC.1085..372C}, (11) \cite{2008AIPC.1085..312T}, (12) \cite{dalton1303}, (13) \cite{2012ApJ...750..162K}, (14) \cite{2009ApJ...691..895T}.}
+
+\end{deluxetable}
+\normalsize
+\noindent
+\clearpage
+
+\begin{deluxetable}{lcccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Results of the fit of the IC peak.
+\tabletypesize{\scriptsize}
+\label{tab:Epeak}}
+\tablewidth{0pt}
+\input{tables/Epeak.tex}\\
+\tablecomments{}
+\end{deluxetable}
+\normalsize
+\noindent

### 2012-10-16 papers/tevcat/tables.tex
fixed the bibtex

@@
 \tablecomments{This table summarizes the pulsars properties taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}.
-Column 3 shows the pulsar spin-down power as found in the litterature, column 4 and 5 present the characteristic age of the pulsar and its distance.\\References: (1) \cite{1973PASP...85..579T}, (2) \cite{2008MNRAS.389.1881K}, (3) \cite{2004MNRAS.352.1405C}, (4) \cite{dalton1303}, (5) \cite{2005yCat.7245....0M}, (6) \cite{2006MNRAS.372..777L}, (7) \cite{1997ApJ...476..347Y}, (8) \cite{2012ApJ...750..162K}, (9) \cite{2009ApJ...694...12M}, (10) \cite{1996ApJ...471..887S}, (11) \cite{1999ApJ...511..274S}, (12) \cite{2007ApJ...662..517F}, (13) \cite{2003MNRAS.342.1299K}, (14) \cite{1995A&A...293..795J},  (15) \cite{2001MNRAS.328...17M}, (16) \cite{2011ICRC....7..247H}, (17) \cite{2006ApJ...637..456C}, (18) \cite{2012ApJ...755L..20P}, (19) \cite{2008AIPC.1085..372C}, (20) \cite{2011ApJ...729L..16G}, (21) \cite{2010ApJ...708.1426W}, (22) \cite{2012ApJ...755...39V}, (23) \cite{1997ApJ...476..347Y}, (24) \cite{2004ApJ...612..389H}, (25) \cite{2009ApJ...706.1331A}, (26) \cite{2001ApJ...560..236K}, (27) \cite{1993AJ....105.1060P}, (28) \cite{2008AJ....136.1477L}, (29) \cite{2003ApJ...596.1137D}, (30) \cite{2010ApJ...725..571S}, (31) \cite{2009ApJ...691..895T}, (32) \cite{2010A&A...520A.111B}.}
+Column 3 shows the pulsar spin-down power as found in the litterature, column 4 and 5 present the characteristic age of the pulsar and its distance.\\References: (1) \cite{1973PASP...85..579T}, (2) \cite{2008MNRAS.389.1881K}, (3) \cite{2004MNRAS.352.1405C}, (4) \cite{dalton1303}, (5) \cite{2005yCat.7245....0M}, (6) \cite{2006MNRAS.372..777L}, (7) \cite{1997ApJ...476..347Y}, (8) \cite{2012ApJ...750..162K}, (9) \cite{2009ApJ...694...12M}, (10) \cite{1996ApJ...471..887S}, (11) \cite{1999ApJ...511..274S}, (12) \cite{2007ApJ...662..517F}, (13) \cite{2003MNRAS.342.1299K}, (14) \cite{1995AA...293..795J},  (15) \cite{2001MNRAS.328...17M}, (16) \cite{2011ICRC....7..247H}, (17) \cite{2006ApJ...637..456C}, (18) \cite{2012ApJ...755L..20P}, (19) \cite{2008AIPC.1085..372C}, (20) \cite{2011ApJ...729L..16G}, (21) \cite{2010ApJ...708.1426W}, (22) \cite{2012ApJ...755...39V}, (23) \cite{1997ApJ...476..347Y}, (24) \cite{2004ApJ...612..389H}, (25) \cite{2009ApJ...706.1331A}, (26) \cite{2001ApJ...560..236K}, (27) \cite{1993AJ....105.1060P}, (28) \cite{2008AJ....136.1477L}, (29) \cite{2003ApJ...596.1137D}, (30) \cite{2010ApJ...725..571S}, (31) \cite{2009ApJ...691..895T}, (32) \cite{2010AA...520A.111B}.}
 
@@
 Column 5 shows the luminosity found using the energy flux in column 2 and the distance in Table \ref{tab:table_luminosity}.
-\\References : (1) \cite{2009ApJ...694...12M} and references therein, (2) \cite{2011AA...525A..46H}, (3) \cite{Mayerdiploma}, (4) \cite{2011AA...533A.103H}, (5) \cite{2012arXiv1205.0719D}, (6) \cite{2010A&A...520A.111B}, (7) \cite{2006ApJ...636..777A}, (8) \cite{2011arXiv1112.2901H}, (9) \cite{2008AA...477..353A}, (10) \cite{2008AIPC.1085..372C}, (11) \cite{2008AIPC.1085..312T}, (12) \cite{dalton1303}, (13) \cite{2012ApJ...750..162K}, (14) \cite{2009ApJ...691..895T}.}
+\\References : (1) \cite{2009ApJ...694...12M} and references therein, (2) \cite{2011AA...525A..46H}, (3) \cite{Mayerdiploma}, (4) \cite{2011AA...533A.103H}, (5) \cite{2012arXiv1205.0719D}, (6) \cite{2010AA...520A.111B}, (7) \cite{2006ApJ...636..777A}, (8) \cite{2011arXiv1112.2901H}, (9) \cite{2008AA...477..353A}, (10) \cite{2008AIPC.1085..372C}, (11) \cite{2008AIPC.1085..312T}, (12) \cite{dalton1303}, (13) \cite{2012ApJ...750..162K}, (14) \cite{2009ApJ...691..895T}.}
 

### 2012-10-16 fermi/tevcat/paper/figures.tex
update

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/Plan_gal.eps}
\caption{Residual counts map of the Galactic Plane above 10 GeV. The Galactic and isotropic diffuse emission are subtracted using the files described in section 4.2 with a normalization of 1. All sources associated to Blazars are subtracted using the spectral parameters listed in the hard source list \citep{1FHL}. Excesses visible in this map are due either to Galactic sources or to Blazars not yet associated, emitting above 10 GeV observed by the LAT. The counts map is smoothed with a Gaussian of 0.27$\degr$.
\label{fig:PlanGal}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[]{figures/HESSJ1303m631.eps}
\caption{Counts map of the region of HESS~J1303--631. We subtracted the Galactic and isotropic diffuse emission. The counts map is smoothed by a Gaussian of 0.27$\degr$ corresponding to the PSF above 10 GeV. The green star indicates the position of the SNR Kes 17, the blue square represents the position of PSR~J1301--6305. The small and big circles respectively show the extension of the TeV Gaussian proposed by \cite{2005AA...439.1013A} and the extension of the disk derived in this work.
\label{1303}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/out_errorbar_best_fit.eps}
\caption{Integrated flux of the detected sources as a function of the power-law index between 10 and 316 GeV (see Table \ref{tab:det_sources}). The green circles show the sources within 0.5$\degr$ of a pulsar detected by the LAT while the red squares represent the sources with no pulsar detected in the GeV energy range within 0.5$\degr$. The error bars show the statistical and systematic uncertainties added in quadrature.  
\label{fig:fluxvssize}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/index_vs_size.eps}
\caption{Spectral index as a function of the GeV or TeV extension for each detected source. The GeV morphology is obtained by fitting the position and extension of the sources as explained in Section \ref{spatanalysis} \& \ref{signi}. The green markers show the sources within 0.5$\degr$ of a pulsar detected by the LAT while the red markers represent the sources with no pulsar detected in the GeV energy range within 0.5$\degr$. The error bars show the statistical and systematic uncertainties added in quadrature. The 11 circles represent the sources for which the GeV morphology significantly improved the fit compared to the TeV morphology (Table \ref{tab:GeVmorph}), while the stars represent the sources modeled assuming their TeV morphology. For sources modelled assuming their TeV morphology, we reported the uncertainties found in the associated reference in Table \ref{tab:TeV_sources}. For asymmetric sources we represented the mean extension with an error bar corresponding to the maximum uncertainty.
\label{fig:indexvssize}}
\end{figure}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=0.5\textwidth]{figures/0FGLJ1958.12848.eps}
%\caption{SED of MGRO J1958$+$2848. The red and blue points show respectively the \emph{Fermi}-LAT and ... points. The black error bars show the statistical and   systematic uncertainties added in quadrature. The black line corresponds to the best fit obtained using the LAT data. The dashed line correspond to the model of PSR J... taken from \cite{2012ApJS..199...31N}.
%\label{fig:1}}
%\end{figure}

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1708.eps}
\label{fig:hess1708}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ0632.eps}
\label{fig:mgroj0632}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ1908.eps}
\label{fig:mgro1908}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ201937.eps}
\label{fig:mgro2019}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ2228.eps}
\label{fig:mgroj2228}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/VERJ0006.eps}
\label{fig:verj0006}
}
\caption{\label{fig:sedsourcespuls}SED of sources better described by a point-like source and with a pulsar within 0.5$\degr$. The blue points show the TeV points taken from \cite{2011AA...528A.143H, 2009ApJ...700L.127A, 2009AA...499..723A, 2007ApJ...664L..91A, 2009ApJ...700L.127A, 2011arXiv1111.2591M}. The red circles and the magenta squares show respectively the SED without the pulsar included in the model and with the pulsar included in the model. The black error bars show the statistical and   systematic uncertainties added in quadrature. The dashed line corresponds to the model of the associated pulsars sumarized in Table \ref{tab:pulsarfit}. In the case of MGRO J1908+06, the red SED was derived assuming a point-like source as determined in Table \ref{tab:GeVmorph} while the magenta SED was derived assuming the TeV shape since it is not significant anymore when the pulsar is included in the model.}
\end{figure}

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1018.eps}
\label{fig:hessj1018}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1023.eps}
\label{fig:hessj1023}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1418.eps}
\label{fig:hessj1418}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1718.eps}
\label{fig:hessj1718}
}
\caption{\label{fig:sedsourcespuls2}SED of sources better described by the TeV shape and with a pulsar within 0.5$\degr$. The blue points show the TeV points taken from the associated paper in Table \ref{tab:TeV_sources}. The red circles and the magenta squares show respectively the SED without the pulsar included in the model and with the pulsar included in the model. The black error bars show the statistical and   systematic uncertainties added in quadrature. The dashed line corresponds to the model of the associated pulsars sumarized in Table \ref{tab:pulsarfit}.}
\end{figure}

\begin{figure}[h!]
\centering

\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1804.eps}
\label{fig:hessj1804}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/HESSJ1833.eps}
\label{fig:hess1833}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ0631.eps}
\label{fig:mgroj0631}
}
\subfigure{
\includegraphics[width=0.45\textwidth]{figures/MGROJ1958.eps}
\label{fig:mgroj1958}
}

\caption{\label{fig:sedsourcespuls3}SED of sources better described by the TeV shape and with a pulsar within 0.5$\degr$. The blue points show the TeV points taken from the associated paper in Table \ref{tab:TeV_sources}. The red circles and the magenta squares show respectively the SED without the pulsar included in the model and with the pulsar included in the model. The black error bars show the statistical and   systematic uncertainties added in quadrature. The dashed line corresponds to the model of the associated pulsars summarized in Table. \ref{tab:pulsarfit}.}
\end{figure}

\clearpage

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/K310GeV.eps}}
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/K330GeV.eps}}
\caption{Smoothed counts map of the region of the Kookaburra complex observed by Fermi above 10 GeV (Top) and
30 GeV (Bottom). The Galactic diffuse emission is subtracted. The circle and right ellipse show the best fit obtained in TeV respectively for the K3 nebula and the Rabbit nebula.
\label{fig:K3countsmap}}
\end{figure}

\clearpage

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1420.eps}
\caption{SED of HESS J1420-607. The blue, green and magenta points respectively show the spectral points obtained by HESS \citep{2006AA...456..245A}, by Suzaku \citep{2010ApJ...711.1168V} and the upper limits derived in radio. The red points and the magenta squares show the spectral points obtained in this work without and with the pulsar included in the model. In the LAT energy range the black error bars show the statistical and systematic uncertainties added in quadrature. The red dashed line corresponds to the 2FGL spectrum of the PSR J1420-607. The three black lines show the results of SED modeling for the broad extended nebula emission presented in previous works. The solid and dot dashed lines respectively shows to the hadronic plus leptonic and leptonic models proposed by \cite{2010ApJ...711.1168V}. The dotted line corresponds to the leptonic model proposed by \cite{2012ApJ...750..162K} assuming an ambient magnetic field of 3$\mu$G.
\label{fig:hessj1420}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1356.eps}
\caption{SED of HESS J1356-645. The blue, green and magenta points represents the results obtained by HESS \citep{2011AA...533A.103H}, the X-ray data \citep{2011AA...533A.102L} and the radio data \citep{2007MNRAS.382..382M, 1995MNRAS.277...36D, 1993AJ....105.1666G}. The red and magenta points between 10 and 316 GeV show the points obtained in this work without and with PSR J1357-6429 included in the model. In the LAT energy range the red and black error bars respectively show the statistical and systematic uncertainties added in quadrature. The solid line presents the one-zone leptonic model proposed by \cite{2011AA...533A.103H}.
\label{fig:hess1356}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1119.eps}
\caption{SED of HESS J1119$-$614. The blue points represent the HESS data \citep{Mayerdiploma}. The red and magenta points between 10 and 316 GeV show the points obtained in this work without and with PSR J1119$-$6127 included in the model. In the LAT energy range the red and black error bars respectively show the statistical and systematic uncertainties added in quadrature. The solid line shows the model proposed by \cite{Mayerdiploma}. The red dashed line corresponds to the model of PSR~J1119$-$6127 \citep{2012ApJS..199...31N}.
\label{fig:hessj1119}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1303631.eps}
\caption{SED of HESS J1303-631. The blue, green and magenta points represents HESS results, the radio data and \emph{Chandra} results \citep{dalton1303}. In the LAT energy range the red and black error bars respectively show the statistical and systematic uncertainties added in quadrature. The solid line shows the leptonic model proposed by \cite{dalton1303}.
\label{fig:hessj1303}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1841055.eps}
\caption{SED of HESS~J1841$-$055. We reported the spectral points obtained using H.E.S.S. data in blues as well as the \emph{Fermi}-LAT spectral points in red. The red and black error bars respectively show the statistical and systematic uncertainties added in quadrature.
\label{fig:1841}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1848018.eps}
\caption{SED of HESS~J1848$-$018. H.E.S.S. pectral points from \cite{chavesthesis} are presented in blue while the radio points corresponding to the W43 central cluster from \cite{2011AA...532A..92L} are indicated in magenta. Red points represent \emph{Fermi}-LAT data. The red and black error bars respectiveley show the statistical uncertainties and statistical plus systematic uncertainties added in quadrature. The red dashed line corresponds to the SED derived in \cite{2011MmSAI..82..739L} using \emph{Fermi}-LAT data and assuming a Gaussian shape of 0.3$\degr$.
\label{fig:1848}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1026.eps}
\caption{SED of HESS~J1026$-$582. H.E.S.S. spectral points are reported in blue while \emph{Fermi}-LAT upper limits are indicated in red. 
\label{fig:1026}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1458.eps}
\caption{SED of HESS~J1458$-$608. H.E.S.S. spectral points are reported in blue while \emph{Fermi}-LAT spectral points are represented int red. The magenta points show the \emph{Fermi}-LAT points obtained once PSR~J1459$-$60 added to the model. The black error bars show the statistical and systematic uncertainties added in quadrature.
\label{fig:1458}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/HESSJ1626.eps}
\caption{SED of HESS~J1626$-$490. H.E.S.S. spectral points are reported in blue while \emph{Fermi}-LAT upper-limits are indicated in red.
\label{fig:1626}}
\end{figure}

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/HESSJ1813178PWN.eps}}
\subfigure{
\includegraphics[width=0.60\textwidth]{figures/HESSJ1813178SNR.eps}}
\caption{SED of HESS J1813$-$178. The blue and red points show the H.E.S.S. \citep{2006ApJ...636..777A} and \emph{Fermi}-LAT spectral results. The radio data (magenta) are from VLA, Bonn, Parkes, and Nobeyama observatories \citep{2005ApJ...629L.105B}. The X-ray data are from XMM-Newton \citep{2007AA...470..249F}
and INTEGRAL \citep{2005ApJ...629L.109U}. These points were derived either for the shell of the SNR and for the core (PWN). The solid and dot dashed lines respectively correspond to the models proposed by \cite{2007AA...470..249F} and by \cite{2010ApJ...718..467F}. Top : Leptonic scenario in which the radiation is created by a PWN.  Bottom : Hadronic scenario in which the radiation is created by the SNR. 
\label{fig:hessj1813}}
\end{figure}

\clearpage

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{figures/Gamma_GeV_Gamma_TeV.eps}
\caption{TeV spectral index as a function of the GeV spectral index for sources detected in our analysis for which the informations on the pulsar are available. These sources are summarized in Table \ref{tab:table_luminosity}. Full markers represent sources with a clear PWN association at TeV energies while hollow markers correspond to sources for which the association between TeV emission and a PWN is less clear. The dashed line corresponds to the symmetry compared to an index of 2. Pulsars summarized in Table \ref{tab:pulsarfit} are included in the model.
\label{fig:gammagamma}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{figures/E_cut_vs_TeV.eps}
\caption{TeV spectral index as a function of the energy of the maximum of the IC peak for sources detected in our analysis for which the informations on the pulsar are available. These sources are summarized in Table \ref{tab:table_luminosity}. Full markers represent sources with a clear PWN association at TeV energies while hollow markers correspond to sources for which the association between TeV emission and a PWN is less clear. Pulsars summarized in Table \ref{tab:pulsarfit} are included in the model.
\label{fig:EpeakETeV}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{figures/E_cut_vs_age.eps}
\caption{Energy of the maximum of IC peak as a function of the characteristic age of the pulsar for sources detected in our analysis for which the informations on the pulsar are available. These sources are summarized in Table \ref{tab:table_luminosity}. Full markers represent sources with a clear PWN association at TeV energies while hollow markers correspond to sources for which the association between TeV emission and a PWN is less clear. Pulsars summarized in Table \ref{tab:pulsarfit} are included in the model.
\label{fig:Epeakage}}
\end{figure}

\clearpage

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{figures/rapport_TeV.eps}
\caption{Ratio of luminosity of the PWN in GeV over the luminosity in TeV as a function of the pulsar spin-down power (top) and the pulsar characteristic age (bottom). Full markers correspond to sources with a clear PWN association at TeV energies while hollow markers correspond to sources for which the association between the TeV emission and a PWN is less clear. The red squares (\protect\includegraphics[scale=0.25]{figures/carrerouge.eps}) represent the sources detected at GeV energies, the magenta circles (\protect\includegraphics[scale=0.25]{figures/rondmagenta.eps}) show the upper limits, the green pentagon (\protect\includegraphics[scale=0.25]{figures/pentagonevert.eps}) represent the sources showing a pulsar behaviour in the energy range and the blue stars (\protect\includegraphics[scale=0.25]{figures/etoilebleue.eps}) represent the Crab nebula and Vela-X not studied in this work. Pulsars summarized in Table \ref{tab:pulsarfit} are included in the model. The dashed line represent the mean ratio found between the GeV and the TeV flux due to the spectral shape of the IC peak.
\label{fig:rapportTeV}}
\end{figure}

\clearpage

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{figures/rapport_X.eps}
\caption{Ratio of luminosity of the PWN in GeV over the luminosity in X-rays as a function of the pulsar spin-down power (top) and the pulsar characteristic age (bottom). Full markers correspond to sources with a clear PWN association at TeV energies while hollow markers correspond to sources for which the association between the TeV emission and a PWN is less clear. The red squares (\protect\includegraphics[scale=0.25]{figures/carrerouge.eps}) represent the sources detected at GeV energies, the magenta circles (\protect\includegraphics[scale=0.25]{figures/rondmagenta.eps}) show the upper limits, the green pentagon (\protect\includegraphics[scale=0.25]{figures/pentagonevert.eps}) represent the sources showing a pulsar behaviour in the energy range and the blue stars (\protect\includegraphics[scale=0.25]{figures/etoilebleue.eps}) represent the Crab nebula and Vela-X not studied in this work. Pulsars summarized in Table \ref{tab:pulsarfit} are included in the model. The dashed and solid lines represent respectively the relations derived in \cite{2009ApJ...694...12M} multiplied by $\bar{R}$ for the whole sample of sources and for the sources clearly identify to PWNe.
\label{fig:rapportX}}
\end{figure}

\clearpage

\begin{figure}[h!]
\centering
\includegraphics[]{figures/dotelpwn.eps}
\caption{Luminosity of the PWN as a function of the pulsar spin-down power. Full markers correspond to sources with a clear PWN association at TeV energies while hollow markers correspond to sources for which the association between the TeV emission and a PWN is less clear. The red squares (\protect\includegraphics[scale=0.25]{figures/carrerouge.eps}) represent the sources detected at GeV energies, the magenta circles (\protect\includegraphics[scale=0.25]{figures/rondmagenta.eps}) show the upper limits, the green pentagon (\protect\includegraphics[scale=0.25]{figures/pentagonevert.eps}) represent the sources showing a pulsar behaviour in the energy range and the blue stars (\protect\includegraphics[scale=0.25]{figures/etoilebleue.eps}) represent the Crab nebula and Vela-X not studied in this work. Sources with two distances estimates have two markers connected with a dotted blue line. Pulsars summarized in Table \ref{tab:pulsarfit} are included in the model. 
\label{fig:dotelpwn}}
\end{figure}

\clearpage

### 2012-10-16 fermi/tevcat/paper/sections/abstract.tex
update

--- 2012-08-30 papers/tevcat/draft_v0/sections/abstract.tex
@@
 Furthermore, PWNe are the most populous class in the TeV energy range followed by the unidentified sources (UNID).
-Using 45 months of Fermi--LAT data, we looked around the position of 56 TeV sources to bring new constraints on the models and new clues on the nature of sources without counterparts.
+Using 45 months of Fermi--LAT data, we looked around the position of 58 TeV sources to bring new constraints on the models and new clues on the nature of sources without counterparts.
 For each of them we derived a $\gamma$--ray flux or an upper limit (when the TeV source is not detected at GeV energies by the \emph{Fermi}--LAT) above 10~GeV.
 
-The wealth of multi-wavelength data available and the new results provided by \emph{Fermi}--LAT is an extraordinary opportunity to constrain the origin of the gamma-ray emission of the large sample of UNID and the radiative processes taking place in known PWNe.
+The wealth of multi-wavelength data available and the new results provided by \emph{Fermi}--LAT is an extraordinary opportunity to constrain the origin of the $\gamma$-ray emission of the large sample of UNID and the radiative processes taking place in known PWNe.

### 2012-10-16 fermi/tevcat/paper/sections/discussion.tex
update

\section{Discussion}
\label{discussion}

%Since \cite{2011ApJ...726...35A} the number of PWNe detected by \emph{Fermi}-LAT increased to X (Crab Nebula, Vela-X, MSH 15-52, HESS J1640, HESS J1825-137, ). This number must be considered with the growing number of PWNe candidates (HESS J1023, HESS J1857, K3 nebula, HESS J1119, HESS J1356, HESS J1303, HESS J1841 and HESS J1848). Table \ref{tab:table_luminosity} shows that these detected sources are located close to young pulsars of characteristic age between 1 and 30 kyr and of spin-down power between $10^{36}$ and $10^{39}$.

%Assuming that the TeV sources were actually associated to the pulsars of Table \ref{tab:table_luminosity}, we used to the pulsars distances to represent on Figure \ref{fig:dotelpwn} the PWN luminosity as a function of the pulsar spin-down power.

%In this section, we will study the behaviour of the population with physical parameters of the system as the age or the pulsar spin-down power. This analysis follows the work of \cite{2009ApJ...694...12M} where the authors used TeV and X-ray informations.

In this section we investigate the correlations between the pulsar/PWN system parameters (age, spin-down power) and the flux in GeV, TeV and X-ray energy ranges. Tables \ref{tab:table_luminosity} \& \ref{tab:table_luminosity2} summarize the pulsar characteristics and the multi-wavelength informations on each source. To allow the comparison between \cite{2009ApJ...694...12M} and our work, we studied the expected differences between the TeV energy range and the GeV energy range. We assumed that the TeV and the GeV emission coming from these sources were the two sides of the IC emission produced by the same population of electrons and we studied the spectral shape of this IC peak.

Figure \ref{fig:gammagamma} shows the TeV spectral index as a function of the GeV spectral index. This figure perfectly show that sources having a hard index in the GeV energy range ($\Gamma < 2$) have a harder index in the TeV energy range as well, confirming that we may be detecting the two sides of the same $\gamma$-ray peak.

To quantify the expected differences seen in GeV and TeV, we estimated the average energy of the IC peak. For that, we assumed that the $\gamma$-ray energy spectra can be described by a log-normal representation (Equation \ref{logp}) as done in  \cite{2008ApJ...674.1037A}.

\begin{equation}
\label{logp}
\frac{dN}{dE}=N_0 \times \left(\frac{E}{E_0}\right)^{-\left[ \alpha + \beta \times \log\left(\frac{E}{E_b}\right) \right]} 
\end{equation}

We fixed $E_0$ at 300 GeV and $\beta$ at 0.2 and fitted the prefactor $N_0$, the index $\alpha$ and the energy break $E_b$ using our \emph{Fermi}-LAT results and the TeV spectra. Then, we defined the energy of the peak ($E_{peak}$) as the energy at which the energy flux of the modeled peak is maximal. This also corresponds to Equation \ref{pos_epeak}.

\begin{equation}
\label{pos_epeak}
\alpha + \beta \times \log\left(\frac{E}{E_b}\right) = 2.0
\end{equation}

The fit results as well as the peak position are presented in Table \ref{tab:Epeak}. Figure \ref{fig:EpeakETeV} presents the TeV spectral index as a function of the energy of the maximum of the IC peak. This figure highlights a correlation between the TeV spectral index and the peak energy. The TeV index increases with decreasing peak energy except for HESS J1632$-$472. This means that the closer the energy peak is from the GeV energy range, the softer the index will be in the TeV energy range, which is consistent with our log parabola model. The exception of HESS J1632$-$472 could be due to the uncertainties due to the presence of neighbouring sources. As discussed in Section \ref{morph_res}, three sources are detected at lower energies \citep{2012ApJS..199...31N}. These sources are not significantly detected above 10 GeV. It means that these sources can contaminate the low energy of the spectrum derived in this analysis and therefore artificially decrease the fitted energy of the maximum of the IC peak.

Figure \ref{fig:Epeakage} shows the peak energy as a function of the pulsar characteristic age. This Figure presents no obvious correlation between the energy of the peak and the pulsar characteristic age as it would be expected from evolution models and presented in \cite{2012arXiv1202.1455M}. However, it is important to note that this Figure suffers two main biases. First, the characteristic age may not be a good age estimator for the PWN. For instance, MSH 15$-$52 is a known case where two ages are proposed, either the characteristic age of the pulsar 1.7 kyr or an age between 20 and 40 kyr as suggested by the size and general appearance of the SNR \citep{2001AA...374..259G}. Second, our sample is relatively restricted to PWNe with a characteristic age close to 10 kyr, except for MSH 15$-$52 and HESS J1119$-$614. In this context it is not surprising that no correlation is found between $E_{peak}$ and the characteristic age.

From Table \ref{tab:Epeak} we derived the mean parameters corresponding to our sources of interest : $\bar{\alpha} = 2.1 \pm 0.2$ and $\log_{10}\left(\bar{E_{peak}}\right)= 5.7 \pm 0.6$. Using these parameters we computed the mean expected ratio between the GeV and the TeV fluxes : $\bar{R}=1.9 \pm xx$. Figure \ref{fig:rapportTeV} presents the ratio of the luminosity in the GeV energy range over the luminosity found in the TeV energy range summarized in Table \ref{tab:table_luminosity2}. We represented the mean ratio found between the GeV and TeV energy ranges as a dashed line. This figure shows that no sources are located at more than 2$\sigma$ from this mean ratio except HESS J1804$-$216. \cite{2012ApJ...744...80A} studied the link between the TeV and the GeV emission and concluded that a theory assuming the energy-dependent diffusion of particles accelerated in the SNR is more likely than a PWN scenario. Therefore, the emission is not clearly associated to an IC peak and could have an hadronic origin, which would explain why this source is an outlier.

As described in \cite{2009ApJ...694...12M}, the $\gamma$-ray and the X-ray luminosities are expected to decrease with time, but the evolution should be different following the age and the pulsar spin-down power. From Table \ref{tab:table_luminosity2} we represent the ratio of the $\gamma$-ray luminosity over the X-ray luminosity as a function of the age and as a function of the pulsar spin-down power. We also represented respectively in solid and dashed line the relations derived in \cite{2009ApJ...694...12M} multiplied by $\bar{R}$ for the whole sample of sources and for the sources clearly identify to PWNe.

This figure show two correlations : one between the fluxes ratio and the spin-down power and the other between the same flux ratio and the characteristic age. These correlations are expected since the magnetic field depends on these two parameters. However, for each correlation, a sample of four upper limits consistent with fluxes measured at TeV energies are well below the correlation relations derived by \cite{2009ApJ...694...12M}. The overall agreement with the relations proposed by \cite{2009ApJ...694...12M} is relatively good but it can already be predicted that the GeV points will have a larger dispersion once these sources will be detected.

It seems clear from these figures that \emph{Fermi}-LAT mainly detect young and middle-aged PWNe (1-30 kyr) around energetic pulsars with a spin-down power between 10$^{36}$ and 10$^{37}$ erg s$^{-1}$. Figure \ref{fig:dotelpwn} shows the $\gamma$-ray luminosity of the PWN as a function of the pulsar spin-down power assuming the distances summarized in Table \ref{tab:table_luminosity}. The solid, dashed and dot dashed lines respectively show the lines where the luminosity corresponds to 100\%, 10\% and 1\% of the spin-down power. Full and hollow markers respectively represent sources for which the TeV emission is clearly associated to a PWNe and sources for which the association is less clear. Sources with a pulsar-like spectrum are represented in green pentagons. For all sources in Table \ref{tab:pulsars} the pulsar are included in the models. Among the detected sources, eight show a $\gamma$-ray efficiency below 1\% and five are consistent within uncertainties with  an efficiency between 1 an 10 \%. HESS J1303$-$631 is also consistent with an efficiency of 100\% assuming a distance of 15 kpc. This can be due to the large uncertainty on the distance measured which can lead to a factor 3 between the estimated distance and the true distance and by the contamination by Kes 17 as discussed in Section \ref{morph_res}. Six upper limits on the luminosity of TeV sources clearly associated to PWNe are well below an efficiency of 1\%.

\section{Conclusion}

45 months of \emph{Fermi}-LAT observations have been used to look for counterparts to the TeV sources potentially associated to PWNe. Among the 58 sources studied, 31 have been detected. Among these 31, 23 were also detected in \cite{1FHL} and 15 in \cite{2012PhRvD..85h3008N}. Interestingly five new sources are detected in our analysis (HESS J1119$-$614, HESS J1303$-$631, HESS J1356$-$645, HESS J1841$-055$ and HESS J1848$-$018). We analyzed the morphology of the 31 sources detected and found that for 19 of them the GeV shape did not significantly improve the fit in comparison to the TeV shape. For five sources, we found a significant extension larger than the TeV morphology. Six sources are well fitted by a point-like source; all of them have a high index and are probably associated to pulsars emitting above 10 GeV.

Since \cite{2011ApJ...726...35A} the number of PWNe detected by \emph{Fermi}-LAT increased to 5 (Crab Nebula, Vela-X, MSH 15$-$52, HESS J1640$-$465, HESS J1825$-$137 ). This number must be considered with the growing number of PWNe candidates (HESS J1023$-$577, HESS J1119$-$614, HESS J1303$-$631, HESS J1356$-$645, HESS J1420$-$607, HESS J1841$-$055, HESS J1848$-$018 and HESS J1857+026). These PWNe and PWNe candidates are powered by young (between 1 and 30 kyr) and powerfull pulsars (spin down power between 10$^{36}$ and 10$^{39}$ erg s$^{-1}$ with an efficiency below 10\%.

### 2012-10-16 fermi/tevcat/paper/sections/introduction.tex
update

--- 2012-08-30 papers/tevcat/draft_v0/sections/introduction.tex
@@
 Multi-wavelength observations are essential to constrain the emission mechanisms occurring in these sources and identify their nature.
-The Large Area Telescope (LAT) aboard the \emph{Fermi} Gamma-Ray Space Telescope (\emph{Fermi}) is especially useful in this context.
+The Large Area Telescope (LAT) aboard the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi}) is especially useful in this context.
 Covering the energy range from $\sim$ 100 MeV to more than 300 GeV, the LAT provides a precise view of the $\gamma$-ray sky.
@@
 The motivation of this work is to bring new constraints on already known PWNe and to look for new candidates among the unidentified TeV sources.
-A search for gamma-ray emission in the off-pulse window of the $\gamma$-ray detected pulsars, updating the method proposed in \cite{2011ApJ...726...35A}, will be presented in \textbf{cite 2PC}.
+A search for $\gamma$-ray emission in the off-pulse window of the $\gamma$-ray detected pulsars, updating the method proposed in \cite{2011ApJ...726...35A}, will be presented in \cite{2PC}.
 The strategy presented in our work (this paper) is closer to \cite{2010AA...518A...8T} in the sense that we analyzed the \emph{Fermi}-LAT data around already known potential PWNe.
@@
 MAGIC \citep{2012APh....35..435A} consists of two telescopes observing from $\sim$ 50 GeV to several tens of TeV with a sensitivity of $\sim$ 0.8$\%$ of the Crab nebula flux above 300 GeV with a $\sim$ 0.1$\degr$ PSF.
-MILAGRO \citep{2007ApJ...658L..33A} is a water $\breve{C}$erenkov detector with a large field of view (FoV) of $\sim$2sr and a $\sim$ 0.45$\degr$ angular resolution observing $\gamma$-rays from $\sim$ 1 to 100 TeV.
+MILAGRO \citep{2004ApJ...608..680A} is a water $\breve{C}$erenkov detector with a large field of view (FoV) of $\sim$2sr and a $\sim$ 0.45$\degr$ angular resolution observing $\gamma$-rays from $\sim$ 1 to 100 TeV.
 %{\bf {\color{red} Manque les references}}
@@
 Starting from the TeV catalog website \footnote{http://tevcat.uchicago.edu/}, which summarizes all sources detected at TeV energies, we established a list of sources possibly associated to PWNe (Section 3), that we studied using the method and the tools described in Section 4.
-The spatial and spectral results (Section 5) will be presented in the context of a population study (Section 6) before discussing the case one by one (Section 7).
-\textbf{a remoduler une fois le reste fait.}
+The most interesting cases as well as the spatial and spectral results will be discussed (Section 5) before being presented in the context of a complete population study (Section \ref{discussion}).
+
+%will be presented in the context of a population study (Section 6) before discussing the case one by one (Section 7). \textbf{a remoduler une fois le reste fait.}

### 2012-10-16 fermi/tevcat/paper/sections/lat_description_and_observations.tex
update

--- 2012-08-30 papers/tevcat/sections/lat_description_and_observations.tex
@@
 
-The following analysis was performed using 45 months of data collected from August 4, 2008 to Mai 18, 2012 (MET : 239557440--356439741) within a $7$\degr $\times 7\degr$ square (see section 4) around the position of the TeV source aligned with Galactic coordinates.
+The following analysis was performed using 45 months of data collected from August 4, 2008 to April 18, 2012 (MET : 239557440--356439741) within a $7$\degr $\times 7\degr$ square (see section 4) around the position of the TeV source aligned with Galactic coordinates.
 We excluded $\gamma$-rays coming from a zenith angle larger than 100$\degr$ because of possible contamination from secondary $\gamma$-rays from the Earth's atmosphere \citep{2009PhRvD..80l2004A}.

### 2012-10-16 fermi/tevcat/paper/sections/results.tex
update

\section{Results}
\label{res}

Using the procedure described above, we detected 30 sources among the 58 PWNe candidates selected. For each of these detected sources, as explained in Section~\ref{signi}, we determined the best morphology by comparing the likelihood of our fit obtained under three different hypotheses: TeV shape, point-like source and extended source. The results of the spatial analysis are shown in Table~\ref{tab:Morphology_results}, the last column summarizing the best shape found for each source. Once the best morphology found, we performed a spectral analysis whose results are reported in Tables~\ref{tab:det_sources} \& \ref{tab:det_sources2}, while upper limits on non-detections are presented in Tables ~\ref{tab:nondet_sources} \& \ref{tab:nondet_sources2}.

\subsection{Extended sources detected above 10~GeV}
\label{morph_res}

Most sources are better described using the TeV morphology as a template. This is partly due to the 2 (3 for an extended source) additional degrees of freedom to take into account but also to the low statistics above 10~GeV. Indeed, these sources have on average a low TS value or are at the limit of our extension threshold, such as HESS J1514-591.

Interestingly, 11 sources are better described using the morphology obtained at GeV energies using the LAT data, 5 of them being extended. Table \ref{tab:GeVmorph} summarizes the spatial fits in such a case. The results presented here are consistent with Tables 3 and 4 of \cite{2012arXiv1207.0027L}. One can note that the agreement for HESS~J1632$-$478 is not excellent. The difference in extension (0.35 $\pm 0.06$ vs 0.45 $\pm$ 0.04 in our analysis) certainly comes from the 3 additional 2FGL sources (2FGL~J1631.7$-$4720c, 2FGL~J1630.2$-$4752 and 2FGL~J1632.4$-$4820c) in the model used by \cite{2012arXiv1207.0027L}. These sources were below our $\text{TS}>$25 threshold to add a source, and being unidentified, we found no physical reason to add them in our model.

HESS~J1303$-$631 is a new extended source detected at GeV energies. However, Figure~\ref{1303} shows that the \emph{Fermi}-LAT excess observed for this source is likely due to 2 point-like sources (one associated with HESS~J1303$-$631 and one associated with Kes 17 \citep{2011ApJ...740L..12W}) but the limited statistics at high energy does not allow us to separate them. When the region is fitted assuming the TeV morphology for HESS~J1303$-$631 and a separate source for Kes 17, the latter hardly reaches $\text{TS} \sim$ 20 and is therefore too faint to be added to our model. Nevertheless, the difference between the true spectrum and the spectrum derived in this work will be included in the systematics on the flux taking into account the fact that we do not know the true morphology of the source.

\subsection{Pulsars detected above 10~GeV}
\label{pulsarsect}
Only six sources are better described by a point-source model above 10 GeV than by a uniform disk or by the TeV template reported in Table~\ref{tab:TeV_sources}: HESS~J1708$-$443, MGRO J0632+17, MGRO J1908$+$06, MGRO J2019$+$37, MGRO J2228+61 and VER J0006+727. It is not a surprise to see in Figure~\ref{fig:indexvssize} and Table~\ref{tab:det_sources} that these sources have a rather soft spectrum in comparison to the average index of TeV detected sources and that they are all coincident with bright $\gamma$-ray pulsars. As can be seen on Figure \ref{fig:sedsourcespuls}, the spectrum obtained above 10 GeV for these sources is in good agreement with the spectrum derived in the 2FGL Catalog released by the Fermi collaboration \citep{2012ApJS..199...31N}. The $\gamma$-ray emission detected by the LAT above 10 GeV is therefore very likely due to the pulsar itself than to its associated PWN.

Three other sources are coincident with bright Fermi pulsars and present a very soft spectrum in agreement with the 2FGL Catalog as well: HESS J1418-609, MGRO J1958$+$2848 and MGRO~J2031+41. Again, the $\gamma$-ray signal is very likely due to magnetospheric emission. The faintness of these sources above 10 GeV and their almost point-like shape in the TeV energy range can explain why the improvement obtained using a point source model is not significant in comparison to the simple TeV morphology.

To study the contamination of these pulsars to our sources of interest, we used the procedure described in Section 4 but including the pulsars in our models of the regions. The spectra of \emph{Fermi}-LAT pulsars are well characterized by exponentially cutoff power laws with photon indices near 1.5 and cutoff energies between 0.5 and 6 GeV \citep{2PC}. As we selected the data above 10 GeV, we cannot fit the spectral parameters of theses pulsars. Therefore we included them in our model assuming the fixed photon index, cutoff energy and normalization extracted from the 2FGL Catalog. It should be noted that some pulsars may deviate from the simple exponential cutoff power law above 10 GeV. This has been proposed for instance for the famous case of the Crab pulsar \citep{2011Sci...334...69V, 2008Sci...322.1221A}. In such cases, our fit could still be contaminated by the pulsar, especially in the first energy interval (between 10 and 31.6 GeV).

Table~\ref{tab:pulsarfit} and Figures~\ref{fig:sedsourcespuls}, \ref{fig:sedsourcespuls2} \& \ref{fig:sedsourcespuls3} show the results of this new fit using the conventions presented in Table \ref{tab:pulsars}. As expected for the six point-like sources presented in Figure~\ref{fig:sedsourcespuls}, the low energy part of the spectrum tends to disappear confirming that we only detected a pulsar emission. In the case of MGRO J1908+06, the detection is not significant anymore. To present conservative results, we derived the upper limits assuming the TeV shape of this source.

Figures~\ref{fig:sedsourcespuls2} \& \ref{fig:sedsourcespuls3} show the same behaviour for HESS~J1418-609 confirming that the signal observed was dominated by the pulsar emission. In the case of HESS~J1420-607 and HESS~J1119-614, the spectra are now slightly harder but still in very good agreement with the previous ones, which is a good indication that we are mainly seeing the emission from the PWNe and not from their associated pulsars.

\subsection{Detections of PWNe candidates}
%{\bf {\color{red} My own choice looking at your previous results: Kooka, HESSJ1303, HESS J1356, G292.2, HESSJ1841 and HESSJ1848. Do a quick subsection for each of them (and modeling if needed) like in the PWN Cat paper}}

In this section we will describe the new PWNe candidates found in this analysis. We chose them by looking for signal connecting to the TeV spectrum and showing a hard spectrum. HESS~J1420-607, HESS~J1303-631, HESS~J1356-645 \& HESS~J1119-614 were already proposed as PWNe by analyses at other wavelength. The detection of these sources by the \emph{Fermi}-LAT tends to confirm this hypothesis.

HESS~J1848-018, is classified as UNID. The detection presented in Table~\ref{tab:det_sources} shows a faint source with a soft spectrum. We will discuss this source in a PWN scenario.

\subsubsection*{HESS J1420$-$607}

The complex of compact and extended radio/X-ray sources, called Kookaburra~\citep{1999ApJ...515..712R}, spans over about one square degree along the Galactic plane. It has been extensively studied to explain the EGRET source: 3EG J1420$-$6038/GeV J1417$-$6100 \citep{1999ApJS..123...79H}. Within the North-East excess of this complex, labeled 'K3',  was discovered the pulsar PSR J1420$-$6048, a young and energetic pulsar with period 68 ms, characteristic age of 13 kyr, and spin down energy of $10^{37}$ erg s$^{-1}$ \citep{2001ApJ...552L..45D}. Following X-ray observations by ASCA and later by \emph{Chandra} and \emph{XMM-Newton} revealed an extended X-ray emission around this pulsar identified as a potential PWN \citep{2001ApJ...561L.187R,2005ApJ...627..904N}. In the South-West side of the large Kookaburra complex lies a bright nebula exhibiting an extended hard X-ray emission, G313.1+0.1, called the 'Rabbit'~\citep{1999ApJ...515..712R}. This X-ray excess was also proposed as a plausible PWN contributing to the $\gamma$-ray emission detected by EGRET.

In the TeV energy range, the survey of the Galactic plane by H.E.S.S. revealed two very high energy sources in this region: HESS J1420$-$607 and HESS J1418$-$609 \citep{2006AA...456..245A}. HESS J1420-607 is centered North of PSR~J1420$-$6048 (nearby the K3 nebula), while HESS J1418-609 is coincident with the Rabbit nebula. More recently, \emph{Fermi}-LAT detected pulsed $\gamma$-ray emission from PSR J1420$-$6048 and PSR J1418$-$6058, the latter being a new $\gamma$-ray pulsar found through blind frequency searches \citep{2010ApJS..187..460A, 2009Sci...325..840A}. This new pulsar is coincident with an X-ray source in the Rabbit PWN and has a spin-down power high enough to power the TeV PWN candidate HESS J1418$-$609.

In our analysis, HESS J1420$-$607 is detected with a TS of 41 which corresponds to a significance of $\sim$ 6$\sigma$. Figure~\ref{fig:K3countsmap} shows two smoothed counts map centered on the location of the K3 nebula represented by the crossed circle. The Galactic and the isotropic diffuses emission were subtracted in order to show the excesses coming from HESS~J1420$-$607 (represented by the crossed circle) and HESS J1418$-$609 (represented by the crossed ellipse). The first counts map (Top) represents the excesses of the two sources above 10 GeV and the second (Bottom) represents the excesses above 30 GeV. One can see an apparent emission of the region of HESS~J1418$-$609 close to HESS~J1420$-$607 above 10 GeV. Therefore, above 10 GeV, the observed spectrum of HESS~J1420$-$607 is potentially contaminated by the residual emission from HESS J1418$-$607. However, on the counts map above 30 GeV, the residual emission from HESS J1418$-$609 disappears. This confirms the soft spectral index and the pulsar behaviour of the emission coming from the region of HESS~J1418$-$609.

With a TS of 41.2, the point source hypothesis does not significantly improve the likelihood of our fit in comparison to the TeV morphology (Gaussian of 0.06$\degr$) presented in \cite{2006AA...456..245A}. Therefore, assuming the TeV shape, we found an integrated flux F(10-316 GeV)=$(3.2 \pm 0.9_{stat} \pm 1.0_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, a spectral index of $\Gamma = 1.91 \pm 0.27_{stat} \pm 0.31_{syst}$ and an energy flux of G(10-316 GeV) = $(23.1 \pm 5.7_{stat} \pm 6.3_{syst}) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$. In a second step, following the procedure presented in Section~\ref{pulsarsect}, we refitted the spectrum of HESS J1420$-$607 including PSR J1420$-$6048 in our model and fixing its spectral parameters found in the 2FGL Catalog. The fit of HESS~J1420$-$607 leads a lower significance of $~5.6 \sigma$ (TS=35.8, 2 d.o.f) with an integrated flux of F(10-316 GeV)= $(3.4 \pm 0.9_{stat} \pm 1.0_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$ and an index of $\Gamma = 1.80 \pm 0.29_{stat} \pm 0.32_{syst}$.

%Due to the deviation from the simple exponential cut-off observed for several $\gamma$-ray pulsars, and specially for the Crab, the lower energy part of our analysis could still be contaminated by the pulsar even when the 2FGL source associated with the pulsar is added to the model. Therefore, the SED of HESS~J1420$-$607 is potentially contaminated by pulsar emission from PSR~J1420$-$6048 and PSR~J1418$-$6058 at low energy (10-30 GeV). However, it is unlikely contaminated by these components at high energy ($>$ 30 GeV) and the connection between the GeV flux as observed by \emph{Fermi}-LAT and the TeV flux as seen by H.E.S.S., visible in Figure \ref{fig:hessj1420}, supports a common origin for the $\gamma$-ray emission.

%As discussed in Section \ref{pulsarsect}, another contamination could come from PSR~J1420$-$6048 and PSR~J1418$-$6058 (respectively 0.05$\degr$ and 0.27$\degr$ from the centroid of HESS~J1420$-$607) both detected by the LAT. However, the spectrum derived in this analysis is unlikely contaminated by this component at high energy ($>$ 30 GeV) and the connection between the GeV flux as observed by \emph{Fermi}-LAT and the TeV flux as seen by H.E.S.S., visible in Figure \ref{fig:hessj1420}, supports a common origin for the $\gamma$-ray emission.

\cite{2010ApJ...711.1168V} used a two-zone time dependent numerical model with constant injection luminosity to investigate the physical properties of HESS J1420$-$607. The authors injected relativistic particles following a power-law spectrum into the inner nebula zone, they evolved this spectrum over time and injected the resultant spectrum into the outer nebula zone. On Figure \ref{fig:hessj1420} we reported in solid line the results obtained for a hadronic + leptonic model assuming a low density environment (n$\sim$1 cm$^{-3}$) and a magnetic field of $\sim$ 12$\mu$G and $\sim$ 9$\mu$G respectively in the inner and outer nebula. We also reported in dashed line the model proposed for a leptonic scenario assuming a magnetic field of $\sim$ 12$\mu$G and $\sim$ 8$\mu$G respectively in the inner and outer nebula. This magnetic field implied a lepton spectral break at $\sim$100 TeV after evolution in the inner nebula. More recently \cite{2012ApJ...750..162K} proposed a one-zone leptonic model assuming a power-law injection spectrum with an index of 2.3 with a cut-off around 40 TeV and a magnetic field around $\sim$ 3$\mu$G. We represented this model in dotted line on the same figure. All these models show a good agreement with the observed spectrum.

%Figure \ref{fig:hessj1420} shows the results obtained for a leptonic model in solid line and a leptonic + hadronic model in dashed line. We also reported in dotted line the leptonic model proposed by \cite{2012ApJ...750..162K} for a magnetic field of 3$\mu$G. All these models show a good agreement with the observed spectrum. 
However, as noted above, the low energy part of the $\emph{Fermi}$-LAT spectrum may be contaminated by the pulsed emission from PSR J1420$-$6048. This implies that, with the current statistics, all models reproduce reasonably well the GeV and TeV data. A future \emph{Fermi}-LAT off-pulse analysis of this pulsar performed with more statistics could help discriminate between the models.

\subsubsection*{HESS J1356$-$645}

HESS~J1356$-$645 is a source detected in the TeV energy range by H.E.S.S. during the Galactic Plane Survey~\citep{2011AA...533A.103H}. This extended source lies close to the pulsar PSR~J1357$-$6429 which was discovered during the Parkes multibeam survey of the Galactic Plane \citep{2004ApJ...611L..25C}. Its high spin-down power of $\dot{E} = 3.1 \times 10^{36}$ erg s$^{-1}$ makes it a good candidate to power a PWN. Archival radio and analysis of X-ray data from \emph{ROSAT/PSPC} and \emph{XMM/Newton} have revealed a faint extended structure coincident with the VHE emission~\citep{2011AA...533A.103H} providing another argument in favor of the PWN scenario. In parallel, \cite{2011AA...533A.102L} announced the detection of a pulsed signal from PSR~J1357$-$6429 in the $\gamma$-ray and X-ray energy ranges using \emph{Fermi}-LAT and \emph{XMM-Newton} data. However, using 29 months of LAT data between 0.1 and 100 GeV, no counterpart to the TeV emission was found in the off pulse window of the pulsar.

The 16 additional months of observations by \emph{Fermi}-LAT and the higher maximal energy used (316 GeV instead of 100 GeV) in our dataset now enables the detection of a faint counterpart to the TeV emission with a TS = 25.8 (4.7 $\sigma$ assuming 2 d.o.f.). Since the best GeV morphology does not improve the fit significantly, we used the TeV Gaussian of 0.17$\degr$ \citep{2011AA...533A.103H} for the spectral analysis and derived an integrated flux of F(10-316 GeV)=$(1.2 \pm 0.4_{stat} \pm 0.5_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, an energy flux of G(10-316 GeV)=$(16.8 \pm 6.9 \pm 6.8) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$ and a hard spectral index of $\Gamma = 0.99 \pm 0.39 \pm 0.40$.

It should also be noted that, with its low energy cutoff at around 800 MeV in the \emph{Fermi}-LAT energy range \citep{2011AA...533A.102L}, PSR~J1357$-$6429 is not significant anymore in the 10 to 316 GeV energy range. Therefore, we do not expect to see any changes in the spectral parameters when adding PSR~J1357$-$6429 to the model of the region. This is verified in Table~\ref{tab:pulsarfit} as well as in Figure \ref{fig:hess1356}.

The combined GeV-TeV data as seen in Figure \ref{fig:hess1356} provide new information concerning the spectral shape of the $\gamma$-ray emission. It is clearly visible in this figure that the \emph{Fermi}-LAT spectral points nicely match the H.E.S.S. ones, proving that the GeV and the TeV emission have a common origin. Assuming that the $\gamma$-ray signal is coming from the PWN powered by PSR~J1357$-$6429, \cite{2011AA...533A.103H} proposed a leptonic scenario (black curve) which provides an excellent fit of the new multi-wavelength data. This one-zone model is based on the evolution of an electron population injected following an exponentially cutoff power-law spectrum of index 2.5 and cut-off energy of 350 TeV. These electrons cool radiatively through of IC scattering on the Cosmic Microwave Background (CMB), Galactic infrared (T$\sim$ 35K and 350 K), optical (T$\sim$ 4600K) photons and through synchrotron emission in a magnetic field $\sim$ 3.5$\mu$G

%This one-zone model assumes a rather low magnetic field of $\sim 3.5 \mu$G similar to the value observed in other relic PWNe \citep{2008ApJ...689L.125D}. It comprises the Galactic infrared emission from dust at T $\sim$ 35K and 350 K) and optical emission from stars at T$\sim$ 4600 K. The electron spectrum was fitted as a simple exponentially cutoff power-law of index p=2.5 and E$_{cut}$= 350 TeV. These parameters remind the parameters found for others relic PWNe candidates as HESS J1857+026 \citep{Rousseau1857}.

The similarities between PSR J1357$-$6429 and the Vela pulsar and between their PWNe lead \cite{2011AA...533A.103H} to discuss a potential two leptonic-components emission. However, in the case of Vela-X, the "halo" is seen in the GeV and radio energy ranges and the "cocoon" in the TeV and X-ray energy ranges, while in the case of HESS J1356$-$645, a single lepton population explain the broad-band spectrum with reasonable parameters. However, unlike Vela-X, the current radio and X-ray data are very faint and do not provide any morphological constraints. Future multi-wavelength data are highly needed to better describe this source.

%For now, the faintness of the radio and X-ray emission prevent any clear association with the TeV emission and the poor informations on the morphology prevents one from distinguishing between shell-type and plerionic SNR as the origin of HESS~J1356-645 in these energy ranges. New radio and X-ray observations would be needed to confirm the association of the extended emission to HESS J1356-645 and better constrain the model.

%However, radio observations are needed to confirm the association of the extended emission to HESS J1356-645 and better constrain the model. Furthermore, future VHE observations will help constraining the IC spectrum leading to a better knowledge of the magnetic field strength. In conclusion, we classify here HESS J1356-645 as another potential  PWN and others observations are needed to constrains the PWN model.

\subsubsection*{HESS~J1119$-$614}

During the Parkes multibeam pulsar survey, \cite{2000ApJ...541..367C} discovered PSR~J1119$-$6127, a young ($\tau = 1.6$ kyr) pulsar with a high spin-down power $\dot{E} = 2.3 \times 10^{36}$ erg s$^{-1}$ within the supernova remnant G292.2$-$0.5. Using \emph{Chandra} observations, \cite{2003ApJ...591L.143G} and \cite{2008ApJ...684..532S} revealed the presence of a faint and compact PWN close to this pulsar. More recently, a TeV $\gamma$-ray source coincident with PSR J1119$-$6127 and G292.2$-$0.5 was announced\footnote{http://cxc.harvard.edu/cdo/snr09/pres/DjannatiAtai\_Arache\_v2.pdf}.

Using the method described above, a faint signal consistent with the location of the composite SNR G292.2$-$0.5 is detected with a TS of 27.3 (4.9 $\sigma$ with 2 d.o.f.). Since the best GeV morphology does not improve the fit significantly, we used the TeV Gaussian of 0.05$\degr$ for the spectral analysis and derived an integrated flux of F(10 - 316 GeV) = $(2.1 \pm 0.6_{stat} \pm 0.7_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, an energy flux of G(10-316 GeV) = $(10.4 \pm 3.9_{stat} \pm 4.0_{syst}) \times 10^{-10}$ erg cm$^{-2}$ s$^{-1}$ and a soft index of $\Gamma = 2.15 \pm 0.37_{stat} \pm 0.38_{syst}$.

Nevertheless, as can be seen on Figure \ref{fig:hessj1119} and in Table \ref{tab:pulsarfit}, these parameters are contaminated by a low energy component associated to PSR~J1119$-$6127. Once the source 2FGL~J1118.8$-$6128, associated with PSR~J1119$-$6127, included in our model of the region, this contamination decreases and the significance of our GeV source is now just above the detection threshold that we fixed in Section~\ref{signi}, with TS = 16 (3.6 $\sigma$ with 2 d.o.f.). As can be seen in Figure \ref{fig:hessj1119}, the low energy point of the SED is now an upper limit. The best fit parameters in this hypothesis are an integrated flux of F(10-316 GeV) = $(1.5 \pm 0.6_{stat} \pm 0.6_{syst})\times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$ and an harder index of $\Gamma = 1.80 \pm 0.48_{stat} \pm 0.50_{syst}$.

Figure \ref{fig:hessj1119} shows the multi-wavelength SED of HESS~J1119$-$614 along with the H.E.S.S. points from \cite{Mayerdiploma}. The leptonic model proposed by \cite{Mayerdiploma} (solid line) is a one-zone model where accelerated electrons cool radiatively by IC scattering on CMB photons, starlight photons radiated in the vicinity and photons radiated by dust and by synchrotron losses. It implies an initial period of the pulsar $P_0 =21.4$ ms, an initial magnetic field inside the PWN $B_0 = 406.1 \mu$G (leading to a current magnetic field of B$ \sim 32 \mu$G), a braking index of n=2.91 \citep{2000ApJ...541..367C} and a conversion efficiency of spin-down power into relativistic particles of $\eta = 0.3$. The model well matches the LAT and H.E.S.S. points.

The presence of PSR J1119-6127, the detection of a compact PWN in X-ray and the leptonic model proposed by \cite{Mayerdiploma} point toward the hypothesis in which the GeV-TeV emission comes from the PWN inside G292.2$-$0.5. Furthermore, the parameters derived in \cite{Mayerdiploma} and the presence of jets in the  X-ray data remind the case of MSH 15$-$52 \citep{2010ApJ...714..927A,1996PASJ...48L..33T}.

\subsubsection*{HESS J1303$-$631}

HESS J1303$-$631 was serendipitously discovered in 2004 \citep{2005AA...439.1013A} during an observation campaign of the pulsar binary system PSR B1259$-$63. It was originally classified as a "dark" accelerator due to the lack of detected counterparts in radio and X-rays with \emph{Chandra} \citep{2005ApJ...629.1017M}. \cite{dalton1303} found only one plausible counterpart in the vicinity of HESS~J1303-631 : PSR J1301$-$6305  with a spin-down power of $\dot{E} = 1.70 \times 10^{36}$ erg s$^{-1}$. The authors also presented the detection of a very weak X-ray PWN using \emph{XMM-Newton} observations and the energy dependent morphology at TeV energies leading to the conclusion that HESS J1303-631 is an old PWNe offset from the pulsar powering it.

%At this time, a search in the field of view only yielded one plausible counterpart located in the North-Western edge of HESS J1303$-$631, the high spin-down power pulsar PSR J1301$-$6305 ($\dot{E} = 1.70 \times 10^{36}$ erg s$^{-1}$). The recent detection of a very weak X-ray PWN using \emph{XMM-Newton} observations now allows the solid identification of this source as a VHE PWN associated to the pulsar PSR J1301$-$6305, leading \cite{2011arXiv1104.1680D} to classify the TeV excess as an older PWN with a complex morphology and an important offset between the pulsar and nebula. This conclusion is supported by the energy dependant morphology presented in \cite{dalton1303}.

Figures 1 \& 3 in \cite{2011ApJ...740L..12W} show no significant emission coming from the location of HESS~J1303$-$631 using 30 months of \emph{Fermi}-LAT data between 1 and 20 GeV. With 15 months of additional data and a higher energy threshold, our analysis now provides a first detection of GeV emission coincident with the TeV source. Nevertheless as discussed in Section \ref{morph_res}, Figure \ref{1303} shows that the detected emission might be contaminated by a source associated to Kes 17. Since we cannot separate these two sources using our strategy with the current statistics, we decided to take into account this effect of source confusion in our systematics on HESS J1303$-$631. Therefore, we ran the analysis again, adding a source spatially consistent with Kes 17 and we performed a second fit. The maximal variation is seen for the lower energy bin of the SED.

Assuming our best GeV morphology represented by a Disk shape of 0.5$\degr$ (see Table \ref{tab:Morphology_results}), we obtained an integrated flux of F(10-316 GeV)=$(5.9 \pm 1.1_{stat} \pm 4.0_{syst}) \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$, an energy flux of G(10-316 GeV)= $(43.5 \pm 10.0_{stat} \pm 23.4_{syst}) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$ and an index of $\Gamma = 1.71 \pm 0.19_{stat} \pm 0.39_{syst}$. This hard index is in the range of values obtained for PWNe as seen with \emph{Fermi}-LAT and is inconsistent with the spectral index of $\sim 2.4$ derived by \cite{2011ApJ...740L..12W} for Kes 17. This is a good evidence that the $\gamma$-ray emission above 10 GeV is dominated by the PWN candidate. As can be seen in Figure \ref{fig:hessj1303}, even though the connection between the GeV and the TeV energy range is not perfect, there is little doubt that we have detected a counterpart to the TeV signal.

Figure \ref{fig:hessj1303} shows the SED of HESS~J1303-631 together with the one-zone leptonic model proposed by \cite{dalton1303}. In this model, VHE $\gamma$-rays are created via IC scattering of electrons on the CMB photons, infrared and optical target photons being neglected. The model reproduces the radio, X-ray and TeV data with an electron spectral index of  $1.8^{+0.1}_{-0.1}$, a cut-off energy of $31^{+5}_{-4}$\,TeV, and an average magnetic field of $1.4^{+0.2}_{-0.2}\,\mu$G. However, the flux predicted in the GeV energy range is well below the flux detected by the \emph{Fermi}-LAT. This may be due to the absence of infrared and optical photon field or to contamination produced by Kes 17. A specific analysis is needed to conclude on the constraints that the \emph{Fermi}-LAT could bring on the $\gamma$-ray emission of this source.

\subsubsection*{HESS J1841$-$055}

HESS~J1841$-$055 was discovered during the H.E.S.S. Galactic Plane Survey \citep{2008AA...477..353A} and remained unidentified since then. The emission is highly extended and shows possibly three peaks suggesting that the TeV emission is composed of more than one source. Using \emph{INTEGRAL} data, \cite{2009ApJ...697.1194S} proposed the  high-mass X-ray binary HMXB system AX J1841.0$-$0536 as a potential counterpart, at least for a part of the emission. \cite{2011ICRC....6..197T} proposed the association of HESS~J1841$-$055 to an ancient PWN powered by PSR~J1841$-$0524, PSR~J1838$-$0549 or both as each pulsar taken independently would need an efficiency greater than 100\% to power alone a potential PWN associated to the TeV source. More recently, the blind search detection of the new $\gamma$-ray pulsar PSR~J1838$-$0537 with \emph{Fermi}-LAT provided another good counterpart of the TeV source. Indeed, assuming a distance of 2 kpc, \cite{2012ApJ...755L..20P} estimated that PSR J1838$-$0537 is sufficiently energetic to power the whole TeV source with a conversion efficiency of 0.5\%, similar to other suggested pulsar/PWN associations \citep{2008ApJ...682L..41H}.

In this work, HESS~J1841$-$055 is detected as a significantly extended source (TS$_{ext}$= 38.3) at a position consistent with the TeV source but with a larger extension (0.57 $\degr$ with respect to 0.41 $\degr$ $\times$ 0.25 $\degr$ for the TeV source). However, the GeV best morphology does not significantly improve the fit compared to the TeV morphology (TS$_{GeV/TeV}$= 13.0, 2.8$\sigma$ with 3 d.o.f.). Therefore assuming the TeV shape, our best fit yielded an integrated flux of F(10-316 GeV) = $(9.3 \pm 1.9_{stat} \pm 3.9_{syst}) \times 10^{-10}$ for an energy flux of G(10-316 GeV) = $(79.6 \pm 16.0_{stat} \pm 19.1_{syst}) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$ and a hard index of $\Gamma = 1.56 \pm 0.20_{stat} \pm 0.32_{syst}$ consistent with the average value for PWNe detected by the \emph{Fermi}-LAT.

As can be seen in Figure \ref{fig:1841}, the \emph{Fermi}-LAT spectral points nicely match the H.E.S.S. ones, suggesting a common origin. The hard \emph{Fermi}-LAT spectrum detected imply that a curvature must arise between the TeV energy range and the GeV energy range. This is typical of most PWNe detected by \emph{Fermi}-LAT and H.E.S.S. which present IC emission peaking at few hundreds of GeV and would favor the PWN scenario. However, this source is extremely extended in both wavelengths and could be composed of several $\gamma$-ray sources. Follow-up observations with IACTs and \emph{Fermi}-LAT would be needed to unveil the real nature of HESS J1841$-$055.

\subsubsection*{HESS J1848$-$018}

HESS~J1848$-$018 \emph{(TeV J1848$-$017)} was discovered during the extended H.E.S.S. Galactic Plane Survey \citep{chavesthesis}, in the direction of, but slightly offset from, the star forming region W43 (=G30.8-0.2). The TeV emission is characterized by a significant extension (0.32$\degr$) and a power-law spectrum of index $\sim 2.8$ and an integrated flux above 1 TeV $\sim 2 \times 10^{-12}$ cm$^{-2}$ s$^{-1}$. The absence of energetic pulsar or SNR within 0.5$\degr$ from HESS~J1848$-$018 favor an association with the star forming region W43. No obvious counterparts were found in radio and X-ray in the region of the TeV source except the Wolf-Rayet star WR 121a.

%The absence of pulsar or SNR able to explain the TeV emission favoured the association of HESS J1848-018 to the star forming region itself.

%In a first step, a search for a radio or X-Ray counterpart led to no obvious counterpart for the TeV emission. However, the \emph{VII$^{th}$ Catalogue of Galactic Wolf-Rayet Stars} \citep{2001yCat.3215....0V} provided a new candidate \emph{WR 121a} (\emph{W43\#1}).

Located 0.2$\degr$ from the centroid of HESS J1848$-$028, WR 121a is a WN7 subtype star, in a binary system \citep{2011AA...532A..92L}, associated with W43 and characterized by extreme mass loss rates. \cite{chavesthesis} also proposed an association with the molecular clouds contained in W43. These molecular clouds could lead to the production of high energy $\gamma$-rays from the $\pi^0$-meson decays following \emph{p-p} collisions in the ambient gas.

In the GeV energy ranges, \cite{2010AA...518A...8T} proposed an association with the spatially coincident source 0FGL J1848.6$-$0138. \cite{2011MmSAI..82..739L} analyzed the \emph{Fermi}-LAT data around HESS J1848$-$018 and found a 3.7$\sigma$ evidence for an extension ($\sigma \sim 0.3\degr$). This disfavours models in which the GeV emission would be produced by a pulsar alone. However, the statistic was not large enough to discriminate between one extended source and several point sources. Moreover, the spectrum was well described by a log-parabola and the SED was very similar to those otained for most pulsars detected by \emph{Fermi}-LAT. Therefore, the emission observed by the \emph{Fermi}-LAT could be an extended source contaminated by a radio-faint pulsar not yet detected.

%However, studying the GeV spectrum, \cite{2011MmSAI..82..739L} shown that the GeV emission is more likely due to a pulsar component, for which the pulsation is not yet detected, instead of a counterpart to the TeV emission. \cite{2011AA...532A..92L} excluded a spatial association between 0FGL J1848.6-0138 and W43 using the position of 1FGL J1848.1-0145c \citep{2010ApJS..188..405A}.

%Therefore, further analyses are needed to conclude on the association of HESS J1848-0138 either to W43/W121a or to 0FGL J1848.6-0138.

In our analysis, HESS~J1848$-$018 is detected as a faint source and the GeV best morphology does not significantly improve the fit in comparison to the TeV morphology. Therefore assuming the TeV shape, our best fit yielded an integrated flux of F(10-316 GeV) = $(7.4 \pm 1.9_{stat} \pm 3.2_{syst}) \times 10^{-10}$ cm$^{-2}$ s$^{-1}$ for an energy flux of G(10-316 GeV) = $(30.0 \pm 10.1_{stat} \pm 16.5_{syst}) \times 10^{-12}$ erg cm$^{-2}$ s$^{-1}$ and an index of $\Gamma = 2.46 \pm 0.80_{stat} \pm 0.52_{syst}$ consistent with the average value for PWNe detected by the \emph{Fermi}-LAT.

On Figure \ref{fig:1848}, we reported the H.E.S.S. spectral points from \cite{chavesthesis} and the radio points corresponding to the W43 central cluster from \cite{2011AA...532A..92L}. It is important to note that the point obtained in our analysis, is consistent with the red dashed curve which represent the spectrum derived by \cite{2011MmSAI..82..739L}. It is not absolutely clear from this Figure if the GeV and TeV spectra have a common or a distinct origin and future multi-wavelength data would be needed to discriminate between the Pulsar/PWN and massive star formation region and conclude on the nature of HESS J1848$-$018.

%This lead to the conclusion that the emission detected in this work is not linked to the TeV emission but is consistent with the pulsar-like emission observed in \cite{2011MmSAI..82..739L}. Therefore, the discrimination between the Pulsar/PWN scenario and the massive star formation region needs help of others wavelengths to conclude on the true nature of HESS J1848$-$018.

\subsection{Constraints obtained from non-detections}
%{\bf {\color{red} My own choice looking at your previous results: HESSJ1026, HESSJ1458, HESSJ1626-490, HESSJ1813 and so on. Do a quick subsection for each of them (and modeling if needed) like in the PWN Cat paper}}

This section will present the sources for which the emission was not significant but for which the upper limits show an interesting behaviour to bring new constraints on the models.

\subsubsection*{HESS J1026$-$582}

HESS~J1026$-$582 is a source discovered by H.E.S.S. during a new analysis of the region of HESS~J1023$-$577 \citep{2011AA...525A..46H}. \cite{2011AA...525A..46H} have shown that the emission coming from this region could be splitted into two independent sources. While HESS~J1023$-$577 is located close to PSR~J1022$-$5746, the authors proposed an association between HESS~J1026$-$582 and PSR~J1028$-$5819, a pulsar detected by the Parkes Radio telescope \cite{2008MNRAS.389.1881K}. The proximity of the pulsar suggested a PWN scenario to explain the VHE emission. This hypothesis is consolidated by the spin-down power energy of PSR~J1028$-$5819, $\dot{E} = 8.43 \times 10^{35}$ erg s$^{-1}$ \citep{2009ApJ...695L..72A}, which is high enough to power a PWN. \cite{2012AA...543A.130M} compared the X-ray marginal emission observed in Suzaku data to a PWN scenario and conclude on a possible future detection. However, follow-up observations with \emph{XMM-Newton} and \emph{Chandra} are needed to confirm this detection.

No significant GeV emission coming from the location of the TeV excess was detected in our analysis. The very low TS value of 1.0 with an integrated flux below $1.6\times10^{-10}$ ph cm$^{-2}$ s$^{-1}$ (see Tables \ref{tab:nondet_sources} \& \ref{tab:nondet_sources2}) give few hope for a future detection of this source by the LAT. The upper limits presented on Figure \ref{fig:1026} show that a curvature is needed between the TeV and the GeV energy range. This suggests an IC peak at energies higher than 100 GeV consistent with \emph{Fermi}-LAT observations of other PWNe. However, the lack of multi-wavelength data (especially in radio and X-ray), prevent any conclusion on this source.

\subsubsection*{HESS J1458$-$608}

PSR~J1459$-$60 \citep{2010ApJS..187..460A} is an energetic and old pulsar with a spin-down power of $\dot{E} = 9.2 \times 10^{35}$ erg s$^{-1}$, high enough to power a PWN, and a characteristic age of 64 kyr. X-ray observations with \emph{Swift} \citep{2011ApJS..194...17R} and \emph{Suzaku} \citep{Kanaiphd} yielded the discovery of an X-ray counterpart to PSR~J1459$-$60. HESS~J1458$-$608, was discovered 9.6$^{\prime}$ from PSR~J1459$-$60 using H.E.S.S. data after a dedicated observation \citep{2012arXiv1205.0719D} triggered by marginal detection in the 2004 Galactic Plane Survey. The proximity to the pulsar and the extension of HESS~J1458$-$608 suggested that both object could be related in a PSR/PWN scenario. In this case, the lack of observable radio and X-ray emission could be explained by the age of the system.

In our work HESS~J1458$-$608 was not significantly detected above 10 GeV (TS = 12.3) with an integrated flux below $2.5 \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$. Furthermore, Table \ref{tab:nondet_sources2} shows that the observed marginal emission comes from the energy bin between 10 and 31 GeV. This means that the emission is more likely due to the pulsar than linked to the TeV source. Figure \ref{fig:1458} shows that even taking into account the pulsar in our model of the region, the SED is still contaminated at low energy. Nevertheless, the upper limits computed in the energy bins between 31 and 316 GeV, where no pulsar emission is expected anymore, show that a change in the slope of the spectrum is needed between the TeV and the GeV component. This could be consistent with an IC peak above 100 GeV which is the range observed for the PWN observed with the \emph{Fermi}-LAT.

\subsubsection*{HESS J1626$-$490}

HESS~J1626$-$490 is another unidentified source detected during the H.E.S.S. Galactic Plane Survey \citep{2008AA...477..353A}. In their search for counterparts, \cite{2011ICRC....7...44E} found no X-ray source fulfilling the energetic requirement to explain the TeV emission using \emph{XMM-Newton} observations. However, the author suggested that a hadronic scenario based on the interaction of the SNR~G335.2+00.1 with a $^{12}$CO molecular cloud could explain the TeV emission. This hypothesis is supported by a density depression in H I which could be explained by a recent event such as a SNR.

With a TS of 1.5, HESS~J1626$-$490 is not significantly detected in our analysis. The model presented in \cite{2011ICRC....7...44E} and reported on Figure \ref{fig:1626} reproduces the H.E.S.S. SED and is clearly below the upper limits obtained using \emph{Fermi}-LAT data. Only a radio or/and X-ray detection of synchrotron emission from a PWN or the detection of a pulsar could call this model into question.

\subsubsection*{HESS J1813$-$178}

HESS J1813-178 was discovered during the H.E.S.S. Survey of the Inner Galaxy \citep{2005Sci...307.1938A} and remained unidentified until the discovery of the SNR G12.8-0.0 \citep{2005ApJ...629L.105B} in the radio band. Using \emph{XMM-Newton} observations, \cite{2007AA...470..249F} detected a complex morphology composed of a point-like source and an extended nebula. The morphological and spectral ressemblance of the central object with a PWN, lead \cite{2007AA...470..249F} to propose a PWN/SNR scenario to describe the X-ray sources. This hypothesis was strengthened by the discovery of PSR J1813$-$1749 \citep{2009ApJ...700L.158G}, one of the most energetics pulsar in our Galaxy with a spin-down power of $\dot{E} = 5.6 \times 10^{37}$ erg s$^{-1}$. However, the nature of the TeV emission remains unclear as both the SNR or the PWN could produce emission at these energies.

%Related to the two regions observed in radio and X-Ray, two hypotheses are competing to explain the TeV emission of HESS J1813$-$178 : either the emission comes from the SNR or it comes from the PWN. Figure \ref{fig:hessj1813} show the SED with the Radio and X-Ray spectral points derived using the PWN region. We overlayed

Our analysis yielded a TS of 2.5 with an upper limit on the integrated flux of $2.4 \times 10^{-10}$ ph cm$^{-2}$ s$^{-1}$ assuming the TeV morphology as spatial shape. Figure \ref{fig:hessj1813} shows the multi-wavelength SED of HESS J1813$-$178. The red and blue points corresponds to the \emph{Fermi}-LAT and H.E.S.S. spectral points. The green and magenta show respectively the X-ray and radio points derived using the PWN region in Figure \ref{fig:hessj1813} (Top) and the SNR region in Figure \ref{fig:hessj1813} (Bottom). The upper limits derived using the procedure described in Section 4 show that the spectrum of HESS~J1813$-$178 cannot be flat between the TeV and the GeV energy ranges and suggest a peak with an energy cutoff located between the two energy ranges.

\cite{2007AA...470..249F} and \cite{2010ApJ...718..467F} investigated a leptonic model, in which the core X-ray and VHE $\gamma$-ray emission are associated. Both take into account IC scattering on CMB, infrared and near infrared photon fields and synchrotron emission produced with a rather low magnetic field (B $\sim 7\,\mu$G). The main difference between these two models lies in the injected electron population which follows power-law spectrum with an index of 2.0 in \cite{2007AA...470..249F} and a maxwellian + power-law tail spectrum \citep{2008ApJ...682L...5S} with an index of 2.4 in \cite{2010ApJ...718..467F}.

%\cite{2007AA...470..249F} proposed a one-zone time dependent model with a constant injection power-law spectrum of index 2.0 reported in solid line on Figure \ref{fig:hessj1813} (Top). The authors considered the IC cooling of accelerated electrons over the CMB, infrared (1 eV cm$^{-3}) $ and near infrared (with a strong component $\sim$ 1000 eV cm$^{-3}$) photon fields, a magnetic field of 7.5 $\mu$G and electron maximum and minimum energies of 1MeV and 1.5 PeV. This maximum energy suggests that HESS J1813$–$178 is a highly effective accelerator. \cite{2010ApJ...718..467F} presented a leptonic model assuming a maxwellian + power-law tail injection spectrum proposed by \cite{2008ApJ...682L...5S} with an index of 2.4 represented as a dashed line on Figure \ref{fig:hessj1813} (Top). The interstellar soft photons scattered in the IC process contain the CMB, infrared (T= 35K, U=1.5 eV cm$^{-3}$) and starlight (T$_{st}$ = 3000 K, U$_{st}$ = 1.5 eV cm$^{-3}$). They considered a distance of 4kpc with a density of 1.4 cm$^{-3}$, an age of 1.2 kyr, an ambient magnetic field of 5 $\mu$G and a maximum electron energy of 1 PeV.

Both also investigated the possibility for the TeV energy to be created by the SNR shell. We overlaid in solid line on Figure \ref{fig:hessj1813} (Top) the model proposed by \cite{2007AA...470..249F} assuming a hadronic scenario. The main differences between these two models lies in the injected protons and electron populations which follows power-law spectrum with an index of 2.1 in \cite{2007AA...470..249F} and is computed in a semi-anytical nonlinear model in \cite{2010ApJ...718..467F}.

%a maxwellian + power-law tail spectrum \citep{2008ApJ...682L...5S} with an index of 2.4 in \cite{2010ApJ...718..467F}.

%The accelerated particles were injected assuming a power-law spectrum of index 2.1 with a minimum and maximum energy of 1GeV and 100 TeV. The authors assumed a ambient density of 1 cm$^{-3}$ while the model proposed by \cite{2010ApJ...718..467F} assumed a density of 2.8 cm$^{-3}$, a electron to proton ration of 4.5$\times 10^{-4}$ and the same parameters than those used for the leptonic model. However, even assuming a denser medium to enhance the p-p collision in the SNR shell, the IC scattering of electrons and positrons in the PWNe is found prominent enough to contribute significantly to the VHE emission.

The upper limits derived in our analysis rejected one of the two model proposed in each hypothesis. Therefore, no conclusion can be reached on the nature of the TeV emission, being a PWN or a SNR. However, at the light of the different model discussed on can exclude a model assuming a maxwellian + power-law tail injection spectrum with an index of 2.4 assuming the same parameters than those derived in \cite{2010ApJ...718..467F} in the case where the TeV emission comes from the PWN core. These upper limits also constrain the hadronic model by rejecting a power-law injection spectrum of 2.1 with the parameters proposed by \cite{2007AA...470..249F}. Therefore, whatever the origin of the $\gamma$-ray emission, the injected spectrum of the primary electron and protons need to be relatively hard to reproduce the \emph{Fermi}-LAT upper limits ($\Gamma \leq 2.1$).

%Therefore, the model matching the data show that VHE emission comes either from the PWN core of the system or from p-p collision in the SNR shell with a non negligible leptonic IC component due to the PWN core.

%Two models are represented on each plot. The solid line correspond to the model proposed by \cite{2007AA...470..249F} while the dashed line show the model proposed by \cite{2010ApJ...718..467F}. On Figure \ref{fig:hessj1813} (Top), both models are obtained for a leptonic scenario, while Figure \ref{fig:hessj1813} (Bottom) show the models obtained assuming an hadronic scenario.

%In a leptonic scenario, the upper limit we obtained are not consistent with the model proposed by \cite{2010ApJ...718..467F}, while one of the models proposed by \cite{2007AA...470..249F} for a PWN of 1 kyr and a magnetic field of 7.5 $\mu$G nicely  matches the spectral points.

%Assuming now that the TeV emission comes from the SNR shell, Figure \ref{fig:hessj1813} (Bottom) we overlayed to the hadronic model proposed by \cite{2007AA...470..249F} and \cite{2010ApJ...718..467F}. While the hadronic hypothesis proposed by \cite{2007AA...470..249F} predict a flux over the detection threshold of the LAT in the 10 to 31 GeV energy bin, the hadronic model proposed by \cite{2010ApJ...718..467F} for an ISM number sensity of n$_0$ = 2.8 cm$^{-3}$ and electron to proton ratio of K$_{ep} = 4.5 \times 10^{-4}$ matches the radio and X-ray points as well as the GeV-TeV SED. It is important to note that the model proposed by \cite{2007AA...470..249F} in which the GeV-TeV peak comes from the IC emission from the electron population responsible for the radio emission (the SNR Shell), also matches the GeV-TeV SED. To conclude on this source \textbf{I HAVE NO IDEA HOW TO END THIS SENTENCE}.

%\subsection{Conclusion}
%To be done later....

### 2012-10-16 general/bash/slac_settings.sh
update

@@ -123,7 +123,8 @@ function stockscons {
     #_stockscons HEAD-1-985 Debug
     #_stockscons HEAD-1-980 Debug
     
-    _stockscons 09-29-00 Optimized
+    #_stockscons 09-29-00 Optimized
+    _stockscons 09-30-01 Optimized
 }
 
 function testsconcs {
@@ -268,7 +269,7 @@ function setup_fermi_code {
     export diffuse=$fermi/diffuse
     export catalogs=$fermi/catalogs
     export extended_archives=$fermi/extended_archives
-    export GLOBALCAT=/afs/slac/g/glast/groups/catalog
+    export globalcat=/afs/slac/g/glast/groups/catalog
 }
 
 
@@ -394,6 +395,11 @@ function dm_satellite_setup {
 }
 
 
+function setup_tevcat {
+    export tevcat_paper=test
+}
+
+
 
 function setup_pwncat {
     export help_others=$HOME/work/fermi/help_others
@@ -406,10 +412,15 @@ function setup_pwncat {
     export pwndata=$svn/fermi/pwn/pwncat2/data
     export pwnmodify=$svn/fermi/pwn/pwncat2/modify
     export pwnpipeline=$nfs/fermi/pwn/pwncat2/pipeline
-    export pwn_off_peak_results=$nfs/fermi/pwn/pwncat2/off_peak/off_peak_bb/pwncat2
-    export pwn_off_peak_code=$svn/fermi/pwn/pwncat2/off_peak/
 
-    export pwnplots=~/svn/lande/trunk/pwncatalog/PWNCAT2/code/lande/publication_plots
+    export pwncat2_off_peak_results=$nfs/fermi/pwn/pwncat2/off_peak/off_peak_bb/pwncat2
+    export pwncat2_off_peak_code=$svn/fermi/pwn/pwncat2/off_peak/code
+    export pwncat2_off_peak_plots=$svn/fermi/pwn/pwncat2/off_peak/plots
+
+    export pwncat2_spectral_plots=$svn/fermi/pwn/pwncat2/plots
+    export pwncat2_spectral_website=$svn/fermi/pwn/pwncat2/website
+    export pwncat2_spectral_tables=$svn/fermi/pwn/pwncat2/tables
+
     export pwnpaper=~/svn/lande/trunk/pwncatalog/PWNCAT2/paper
     export pwnpersonal=/u/gl/lande/work/fermi/pwncatalog/PWNCAT2
[…]

### 2012-10-18 fermi/tevcat/paper/sections/abstract.tex
Josh's changes to the abstract

--- 2012-08-30 papers/tevcat/draft_v0/sections/abstract.tex
@@
-Since its launch, the \emph{Fermi} satellite has firmly identified 7 pulsar wind nebulae (PWNe) plus a large number of candidates, all powered by young and energetic pulsars.
-Furthermore, PWNe are the most populous class in the TeV energy range followed by the unidentified sources (UNID).
-Using 45 months of Fermi--LAT data, we looked around the position of 56 TeV sources to bring new constraints on the models and new clues on the nature of sources without counterparts.
-For each of them we derived a $\gamma$--ray flux or an upper limit (when the TeV source is not detected at GeV energies by the \emph{Fermi}--LAT) above 10~GeV.
+Since its launch, the \emph{Fermi} satellite has firmly identified seven pulsar wind nebulae (PWNe) and a large number of PWNe candidates, all powered by young and energetic pulsars.
+Furthermore, PWNe are the most populous class of sources detected at TeV energys followed by the unidentified sources (UNID).
+Using 45 months of \emph{Fermi}--LAT data, we studied the 10 \gev to 316 \gev $gamma$-ray emission around the position of 58 TeV sources that are either associated with PWNe or unidentified.
+For each source, we derived a $\gamma$--ray flux or a flux upper limit (when the TeV source is not detected at GeV energies by the \emph{Fermi}--LAT).
 
-The wealth of multi-wavelength data available and the new results provided by \emph{Fermi}--LAT is an extraordinary opportunity to constrain the origin of the gamma-ray emission of the large sample of UNID and the radiative processes taking place in known PWNe.
+The wealth of multi-wavelength data available and the new results provided by the \emph{Fermi}--LAT provide an extraordinary opportunity to constrain the origin of the $\gamma$-ray emission of the large sample of UNID and the radiative processes taking place in known PWNe.

### 2012-10-29 fermi/pwn/pwncat2/off_peak/plots/plot_off_peak_select.py
new project

@@ -19,7 +19,7 @@ from lande.utilities import pubplot
 
 pubplot.set_latex_defaults()
 
-base='$pwn_off_peak_results/v6'
+base='$pwncat2_off_peak_results/v6'
 
 outdir = join(base,'plots')
 

### 2012-10-29 fermi/pwn/pwncat2/plots/off_peak_edot_d2_vs_age/plot_off_peak_edot_d2_vs_age.py

@@ -9,7 +9,7 @@ pubplot.set_latex_defaults()
 bw = pubplot.get_bw()
 
 
-fig = P.figure(None,(6,6))
+fig = P.figure(None,(4,4))
 axes = fig.add_subplot(111)
 
 axes.set_xscale("log")
@@ -20,32 +20,46 @@ cat=PulsarCatalogLoader(
     off_peak_auxiliary_filename='$lat2pc/OffPeak/tables/off_peak_auxiliary_table.fits')
 bigfile_fits = cat.bigfile_fits
 
-psrlist=bigfile_fits.data['PSRJ']
-Edot=bigfile_fits.data['Edot'] # erg/s
-age=bigfile_fits.data['Age'] # years
 
-dist = bigfile_fits.data['DIST1'] # kpc
-#dist = bigfile_fits.data['DPSR_1'] # kpc
-#dist=np.asarray([float(i) if i != '' and i[0]!='<' else np.nan for i in dist],dtype=float)
+psrlist = cat.get_off_peak_psrlist()
 
-off_peak_psrlist=cat.get_off_peak_psrlist()
-classification = np.asarray([ cat.get_off_peak_classification(i) if i in off_peak_psrlist else 'Non_Detected' for i in psrlist])
+
+Edot=np.empty_like(psrlist,dtype=float)
+age=np.empty_like(psrlist,dtype=float)
+classification=np.empty_like(psrlist,dtype=object)
+has_distance=np.empty_like(psrlist,dtype=bool)
+distance=np.empty_like(psrlist,dtype=float)
+
+
+for i,psr in enumerate(psrlist):
+    Edot[i]=cat.get_edot(psr)
+    age[i]=cat.get_age(psr)
+    classification[i] = cat.get_off_peak_classification(psr)
+
+    d=cat.get_distance(psr)
+    if d[0] == '<':
+        has_distance[i] = False
+    else:
+        distance[i] = float(d)
+        has_distance[i] = True
+
 
 blue = 'blue' if not bw else 'grey'
 red = 'red' if not bw else 'grey'
 
 def plot(cut, **kwargs):
-    axes.plot(age[cut],Edot[cut]/dist[cut]**2,'.', **kwargs)
+    axes.plot(age[cut],Edot[cut]/distance[cut]**2,'.', **kwargs)
 
-plot(classification=='Non_Detected',color='lightgrey', markersize=10)
-plot((classification=='Upper_Limit')|(classification=='Confused'),color='black', markersize=10)
[…]

### 2012-10-29 fermi/pwn/pwncat2/plots/off_peak_luminosity_vs_edot/plot_off_peak_luminosity_vs_edot.py

@@ -17,7 +17,7 @@ cat=PulsarCatalogLoader(
 psrlist = cat.get_off_peak_psrlist()
 
 
-fig = P.figure(None,(6,6))
+fig = P.figure(None,(4,4))
 axes = fig.add_subplot(111)
 
 axes.set_xscale("log")
@@ -86,5 +86,7 @@ axes.set_ylim(1e31,1e37)
 
 axes.set_xlabel('$\dot E$ [erg s$^{-1}$]')
 axes.set_ylabel(r'$L_\mathrm{off\,peak}$ [erg s$^{-1}$]')
+
+fig.tight_layout()
 
 pubplot.save('off_peak_luminosity_vs_edot')

### 2012-10-30 fermi/radiopsrs/paper/sections/notes.tex
update

\section{notes}

Benefits:
\begin{enumerate}
\item Improved time range (XXX months vs XXX months in 2PC)
\item Improved uppper limit from likelihood test.
\item Better analysis method (search for extended sources, could be more sensitive?)
    Look for hard-index sources (unlike 2PC).
\item For example, Lande et al 2012 discovered Gamma-ray emission
    from HESS J1616-508 which is associated with PSR J1617-5055.
\item  Note: Table 3 and 4 get upper limits assuming cutoff spectrum, not suitable
for PWNe searches. For describing of 2PC flux upper limits, see 
\url{https://confluence.slac.stanford.edu/x/UwDNBw}
\end{enumerate}

Notes/questions:
\begin{enumerate}
  \item Should we used reprocessed data?
\end{enumerate}

### 2012-10-30 fermi/radiopsrs/pipeline/loop.py
update

@@ -1,0 +1,19 @@
+
+from lande.utilities.save import loaddict
+from lande.utilities.jobtools import JobBuilder
+
+radiopsr_data='$radiopsrs_data/radiopsrs_data.yaml'
+names=loaddict(radiopsr_data).keys()
+bigfile='$lat2pc/BigFile/Pulsars_BigFile_v20121002103223.fits'
+
+params=dict(name=names, 
+            bigfile=bigfile)
+params['radiopsr-data']=radiopsr_data
+b = JobBuilder(
+    savedir='$radiopsrs_analysis/v1',
+    code='$radiopsrs_pipeline/main.py',
+    params=params,
+    short_folder_names=True,
+    )
+b.build()
+

### 2012-10-30 fermi/radiopsrs/pipeline/main.py

@@ -1,0 +1,10 @@
+#!/usr/bin/env python
+
+from argparse import ArgumentParser
+
+from lande.fermi.pipeline.radiopsrs.analysis.pipeline import Pipeline
+
+kwargs = Pipeline.get_kwargs()
+
+pipeline=Pipeline(**kwargs)
+pipeline.main()

### 2012-10-30 fermi/gamma_quiet_psrs/paper/sections/introduction.tex
update

\section{Introduction}

\begin{itemize}
  \item Pulsar Physics
  \item PWNe (high energy IC emission)
  \item PWNe detected at GeV energies
  \begin{itemize}
    \item 2PC Off-peak PWNe search
    \item TeVCat PWNe search
  \end{itemize}
  \item $\gamma$-quiet pulsars
  \item Search for new pulsars. Put some kind of note about how LAT has uniform coverage of all sources, which is a benefit.
  \item Also put note about how we discovered a source HESS J1616 \& HESS J1825 at \gev energies using this method.
\end{itemize}

\citep{LAT_Collaboration_2FGL_2012}.

### 2012-11-08 general/bash/analysis_setups.sh
update

@@ -38,10 +38,6 @@ function setup_snrlim {
     export superfile=$HOME/svn/snrcat1/superfile/
 }
 
-function setup_radiopsrs {
-    export radiopsrsfits=$fermi/radiopsrs/fits
-    export radiopsrsdata=$fermi/radiopsrs/data
-}
 
 function setup_multiwavelength {
     export multiwavelength=$svn/fermi/multiwavelength/
@@ -63,12 +59,9 @@ function dm_satellite_setup {
     export SHERIDAN=~szalewsk
 }
 
-
 function setup_tevcat {
     export tevcat_paper=$svn/fermi/tevcat/paper
 }
-
-
 
 function setup_pwncat {
     export help_others=$HOME/work/fermi/help_others
@@ -108,10 +101,6 @@ function setup_pwncat {
     export PYTHONPATH=$pwncode/lande/tables:$PYTHONPATH
     export PYTHONPATH=$pwncode/lande/off_peak:$PYTHONPATH
 
-    export extuldata=$pwndata/monte_carlo/extul
-    export extulcode=$pwnmc/extul
-    export extulplots=$pwnplots/extul
-
     export PYTHONPATH=$PYTHONPATH:$HOME/svn/lande/trunk/pwncatalog/PWNCAT2/code
 
     export lat2pc=/u/gl/lande/svn/lat2pc/trunk
@@ -145,3 +134,38 @@ function snrcat1setup {
     export PYTHONPATH=~/svn/snrcat1/code:$PYTHONPATH
 }
 
+
+function gamma_quiet_psrs_setup {
+    export gamma_quiet_psrs_data=$svn/fermi/gamma_quiet_psrs/data
+    export gamma_quiet_psrs_pipeline=$svn/fermi/gamma_quiet_psrs/pipeline
+    export gamma_quiet_psrs_lat_data=$nfs/fermi/gamma_quiet_psrs/lat_data
+    export gamma_quiet_psrs_analysis=$nfs/fermi/gamma_quiet_psrs/analysis
+    export gamma_quiet_psrs_personal=$HOME/work/fermi/gamma_quiet_psrs
+    export gamma_quiet_psrs_paper=$svn/fermi/gamma_quiet_psrs/paper/
+    export gamma_quiet_psrs_code=$lande/fermi/pipeline/gamma_quiet_psrs
+    export gamma_quiet_psrs_website=$svn/fermi/gamma_quiet_psrs/website/
+
+
+}
+
+function extul_setup {
[…]

### 2012-11-08 general/bash/general_settings.sh

@@ -1,5 +1,3 @@
-# These are my bash
-
 function setup_terminal_tweaks {
     [ -z "$PS1" ] && return
     export TERM=xterm-color

### 2012-11-08 general/bash/slac_settings.sh

@@ -195,25 +195,12 @@ function tagCollector {
     echo python tagCollector.py ScienceTools --new=HEAD -r True
 }
 
-
-
-
 function setup_defaults_slac {
     setup_general_slac_alias
     setup_svn
-    setup_mc_testing
     setup_personal_code
     setup_lsf
     fix_matplotlib
-    setup_extended_catalog
-    setup_pwncat
-    setup_tevcat
-    setup_pysed
-    setup_snrsim
     setup_science_tools_development 
-    setup_snr_low_energy
-    setup_snrlim
-    setup_radiopsrs
-    setup_multiwavelength
 }
 setup_defaults_slac

### 2012-11-08 fermi/gamma_quiet_psrs/paper/sections/introduction.tex
update

@@
 \section{Introduction}
+
+The Large Area Telescope (LAT) on board the \fermi Gamma-ray Space Telescop has vastly improved
+the field of $\gamma$-ray pulsars.
+
+How many pulsars detected by the LAT.
+
+Most prominently, the LAT Collaboratino rece
 
@@
   \item Pulsar Physics
+  \item Pulsars causing a pulsar wind.
   \item PWNe (high energy IC emission)
@@
     \item TeVCat PWNe search
+    \item Why we see high Edot pulsars.
   \end{itemize}
-  \item $\gamma$-quiet pulsars
-  \item Search for new pulsars. Put some kind of note about how LAT has uniform coverage of all sources, which is a benefit.
-  \item Also put note about how we discovered a source HESS J1616 \& HESS J1825 at \gev energies using this method.
+  \item Pulsars not seen by the LAT ($\gamma$-quiet pulsars)
+  \item Search for new pulsars. Put some kind of note about how LAT has
+  uniform coverage of all sources, which is a benefit.
+  \item Also put note about how we discovered a source HESS J1616 \&
+  HESS J1825 at \gev energies using this method.
+\item Put note about how there are 17 pulsars with Edot>1e37 (table 3 in 2PC).
+  Of those, 8 has no gamma-ray pulsations. There are 46 with $10^{36}$ < Edot < $10^{37}$.
+  19 pulsars with no gamma-ray pulsations (table 4 in 2PC). 
+  In total, there are 27 pulsars with $E_dot>10^{36}$ with no pulsations
+  (despite thorough search). We search the LAT data for these 27 high Edot pulsars to find
+  new PWNe.
 \end{itemize}

### 2012-11-08 fermi/gamma_quiet_psrs/pipeline/loop.py

@@ -12,8 +12,6 @@ names=loaddict(radiopsr_data).keys()
 bigfile='$lat2pc/BigFile/Pulsars_BigFile_v20121002103223.fits'
 
 params=dict(name=names, 
-            fast=True,
-            savedata=True
             bigfile=bigfile)
 params['radiopsr-data']=radiopsr_data
 b = PipelineBuilder(

### 2012-12-03 fermi/gamma_quiet_psrs/paper/sections/method.tex
update

\section{Analysis Method}

\subsection{Pulsar Selection Criteria}

Our selection criteria for our PWN search was that to selected high $\dot E$
pulsars with no $\gamma$-ray pulsations.

We took Table 10 from 2PC [CITATION NEEDED],

We excluded J0537$-$6910 and J0540$-$6919. They are in the LMC region which has been detected.

Exclude 3 regiongs with dedicated publications:
\begin{enumerate}
  \item J1617$-$5055 (HESS J1616-508)
  \item J1838$-$0655 (HESS J1837-069)
  \item J1826$-$1334 (HESS J1825-137)
\end{enumerate}

Don't include pulsars which have LAT-detected pulsars since publication of 2FGL.
Presumably, need to redo analysis in off-peak
\begin{enumerate}
  \item J1824$-$2452A 
  \item J1055$-$6028
\end{enumerate}

Don't include sources in Romain's PWNe search:
\begin{enumerate}
  \item J1301-6305 -> HESS J1303-631
  \item J1813-1749 -> HESS J1813-178
\end{enumerate}

\subsection{LAT Data Preparation}

### 2012-12-04 fermi/gamma_quiet_psrs/paper/sections/method.tex
add

@@
 
-We excluded J0537$-$6910 and J0540$-$6919. They are in the LMC region which has been detected.
+We excluded PSR J0537$-$6910 and PSR J0540$-$6919. They are in the LMC region which has been detected.
 
@@
 \begin{enumerate}
-  \item J1617$-$5055 (HESS J1616-508)
-  \item J1838$-$0655 (HESS J1837-069)
-  \item J1826$-$1334 (HESS J1825-137)
+  \item PSR J1617$-$5055 (HESS J1616-508)
+  \item PSR J1838$-$0655 (HESS J1837-069)
+  \item PSR J1826$-$1334 (HESS J1825-137)
 \end{enumerate}
@@
 \begin{enumerate}
-  \item J1824$-$2452A 
-  \item J1055$-$6028
+  \item PSR J1824$-$2452A 
+  \item PSR J1055$-$6028
 \end{enumerate}
@@
 \begin{enumerate}
-  \item J1301-6305 -> HESS J1303-631
-  \item J1813-1749 -> HESS J1813-178
+  \item PSR J1301-6305 -> HESS J1303-631 (detected by Romain)
+  \item PSR J1813-1749 -> HESS J1813-178 (not detected by Romain)
+  \item PSR J1809-1917 -> HESS J1809-193 (not detected by Romain)
+  \item PSR J1849-0001 -> HESS J1849-000 (not detected by Romain)
+  \item PSR J1831-0952 -> HESS J1831-098 (not detected by Romain)
+  \item PSR J1913+1011 -> HESS J1912+101 (not detected by Romain)
+  \item PSR J1846-0258 -> HESS J1846-029 (not detected by Romain)
+  \item PSR J1856+0245 -> HESS J1857+026 (detected by Romain + his previous dedicated publication)
+  \item PSR J1803-2137 -> HESS J1804-216 (significantly detected-http://arxiv.org/pdf/1109.3017v2.pdf)
+  \item PSR J1930+1852 -> VERJ1930+188 (not detected by Romain)
+  \item PSR J1614-5048 is spatially coincident with HESS J1616-508 (detected in ext. src. search paper).
+    Note that this HESS source cannot be energetically powered by
+    PSR J1614-5048 (see discussion in ext. src. search paper), but
+    the region itself was already studied, so we discard this source.
+
 \end{enumerate}

### 2012-12-04 fermi/gamma_quiet_psrs/pipeline/followup.py

@@ -9,9 +9,11 @@ from lande.fermi.pipeline.gamma_quiet_psrs.analysis.pipeline import Pipeline
 parser = ArgumentParser()
 parser.add_argument("--hypothesis", required=True, choices=['at_pulsar', 'point', 'extended'])
 parser.add_argument("--followup", required=True, choices=['tsmaps','plots', 'gtlike'])
+parser.add_argument("--size")
 followup_args = parse_strip_known_args(parser)
 hypothesis = followup_args.hypothesis
 followup =followup_args.followup
+size = followup_args.size
 
 kwargs = Pipeline.get_kwargs()
 
@@ -21,7 +23,7 @@ if followup == 'gtlike':
     pipeline.gtlike_followup(hypothesis=hypothesis)
 elif followup == 'variability':
     pipeline.variability_followup(hypothesis=hypothesis)
-elif followup == 'tsmaps':
-    pipeline.tsmaps_followup(hypothesis=hypothesis)
-elif followup == 'plots':
-    pipeline.plots_followup(hypothesis=hypothesis)
+elif 'tsmaps' in followup:
+    pipeline.tsmaps_followup(hypothesis=hypothesis, size=size)
+elif 'plots' in followup:
+    pipeline.plots_followup(hypothesis=hypothesis, size=size)

### 2012-12-04 fermi/gamma_quiet_psrs/pipeline/loop.py

@@ -32,6 +32,7 @@ b.build_followup(
 
 ####################################################################################################
 
+"""
 radiopsr_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml'
 names=loaddict(radiopsr_data).keys()
 bigfile='$lat2pc/BigFile/Pulsars_BigFile_v20121127171828.fits'
@@ -53,3 +54,35 @@ b.build_followup(
     hypotheses=['at_pulsar'],
     followups=['gtlike','plots','tsmaps']
 )
+"""
+radiopsr_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml'
+
+####################################################################################################
+
+radiopsr_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml'
+names=loaddict(radiopsr_data).keys()
+bigfile='$lat2pc/BigFile/Pulsars_BigFile_v20121127171828.fits'
+modify='$gamma_quiet_psrs_modify/gamma_quiet_psrs_data.yaml'
+
+params=dict(name=names, 
+            bigfile=bigfile)
+params['radiopsr-data']=radiopsr_data
+b = PipelineBuilder(
+    savedir='$gamma_quiet_psrs_analysis/v4/fits',
+    code='$gamma_quiet_psrs_pipeline/main.py',
+    params=params,
+    short_folder_names=True,
+)
+b.build()
+b.build_followup(
+    code = '$gamma_quiet_psrs_pipeline/followup.py',
+    hypotheses=['at_pulsar','point','extended'],
+    followups=['gtlike']
+)
+for size in [5,10]:
+    b.build_followup(
+        code = '$gamma_quiet_psrs_pipeline/followup.py',
+        hypotheses=['at_pulsar','point','extended'],
+        followups=['plots_%s' % size,'tsmap_%s' % size],
+        extra='--size=%s' % size
+    )

### 2012-12-04 fermi/gamma_quiet_psrs/website/website.py

@@ -10,11 +10,19 @@ b.build_all_psrs()
 """
 
 
-b=WebsiteBuilder(
-    gamma_quiet_psrs_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml',
-    analysisdir='$gamma_quiet_psrs_analysis/v2',
-    webdir='$gamma_quiet_psrs_analysis/v2/website')
-#b.build_main()
-b.build_all_psrs()
+if True:
+    b=WebsiteBuilder(
+        gamma_quiet_psrs_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml',
+        analysisdir='$gamma_quiet_psrs_analysis/v2',
+        webdir='$gamma_quiet_psrs_analysis/v2/website')
+    b.build_main()
+    b.build_all_psrs()
 
-
+if True:
+#if False:
+    b=WebsiteBuilder(
+        gamma_quiet_psrs_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml',
+        analysisdir='$gamma_quiet_psrs_analysis/v3',
+        webdir='$gamma_quiet_psrs_analysis/v3/website')
+    b.build_main()
+    b.build_all_psrs()

### 2013-02-27 fermi/pwn/pwncat2/tables/auxiliary_table.py
update

@@ -12,7 +12,7 @@ auxiliary_table(
 auxiliary_table(
     pwndata='$pwndata/pwncat2_data_lande.yaml',
     phase_shift='/nfs/farm/g/glast/u55/pulsar/2ndPulsarcatalog/psue/General/josh_dicts.pickle',
-    fitdir='$pwnpipeline/v36/analysis',
-    filename='$pwnpipeline/v36/tables/off_peak_auxiliary_table.fits',
+    fitdir='$pwnpipeline/v37/analysis',
+    filename='$pwnpipeline/v37/tables/off_peak_auxiliary_table.fits',
     pwn_classification='$pwnclassify/manual_classifications.yaml'
 )

### 2013-02-27 fermi/pwn/pwncat2/tables/spatial_spectral.py

@@ -6,9 +6,9 @@ table_type=get_table_type()
 spatial_spectral_table(
     pwndata='$pwndata/pwncat2_data_lande.yaml',
     phase_shift='/nfs/farm/g/glast/u55/pulsar/2ndPulsarcatalog/psue/General/josh_dicts.pickle',
-    fitdir='$pwnpipeline/v36/analysis',
-    savedir='$pwnpipeline/v36/tables',
+    fitdir='$pwnpipeline/v37/analysis',
+    savedir='$pwnpipeline/v37/tables',
     filebase='off_peak_spatial_spectral',
     table_type=table_type,
     pwn_classification='$pwnclassify/manual_classifications.yaml',
-    bigfile_filename='$lat2pc/BigFile/Pulsars_BigFile_v20121127171828.fits')
+    bigfile_filename='$lat2pc/BigFile/Pulsars_BigFile_v20130117130325.fits')

### 2013-02-27 fermi/pwn/pwncat2/off_peak/plots/plot_off_peak_select.py
update

@@ -47,6 +47,8 @@ fig.subplots_adjust(hspace=.35,wspace=.35, left=0.15, right=0.9, top=0.9, bottom
 
 pwndata=yaml.load(open(expandvars('$pwndata/pwncat2_data_lande.yaml')))
 
+off_peak_results = yaml.load(open(expandvars('$pwndata/pwncat2_phase_lande.yaml')))
+
 
 for i,(pwn,nbins) in enumerate(pwnlist):
     results = expandvars(join(r,pwn,'results_%s.yaml' % pwn))
@@ -68,7 +70,8 @@ for i,(pwn,nbins) in enumerate(pwnlist):
     emax = results['emax']
     radius = results['optimal_radius']
     blocks = results['blocks']
-    off_peak_phase = results['off_peak_phase']
+
+    off_peak_phase = off_peak_results[pwn]['phase']
 
     import pickle
     jd = pickle.load(open('/nfs/farm/g/glast/u55/pulsar/2ndPulsarcatalog/psue/General/josh_dicts.pickle'))

### 2013-02-27 general/bash/analysis_setups.sh
update

@@ -144,6 +144,7 @@ function gamma_quiet_psrs_setup {
     export gamma_quiet_psrs_paper=$svn/fermi/gamma_quiet_psrs/paper/
     export gamma_quiet_psrs_code=$lande/fermi/pipeline/gamma_quiet_psrs
     export gamma_quiet_psrs_website=$svn/fermi/gamma_quiet_psrs/website/
+    export gamma_quiet_psrs_modify=$svn/fermi/gamma_quiet_psrs/modify
 
 
 }
@@ -152,6 +153,10 @@ function extul_setup {
     export extulresults=$nfs/fermi/extul
     export extulcode=$svn/fermi/extul/code
     export extulplots=$pwnplots/extul
+}
+
+function setup_thesis {
+    export thesis=$svn/thesis
 }
 
 function setup_defaults {
@@ -167,5 +172,6 @@ function setup_defaults {
     setup_pwncat
     gamma_quiet_psrs_setup
     extul_setup
+    setup_thesis
 }
 setup_defaults

### 2013-02-27 general/bash/kipac_setup.sh

@@ -3,11 +3,13 @@ function _kipac_base {
     export KIPACSOFT=/afs/slac/g/ki/software
 }
 
-function pythonkipac {
+function _pythonkipac {
     _kipac_base 
+    export python_version=$1
+
     #export PATH=$KIPACSOFT/python/2.6.2/amd64_linux26/bin:$PATH
-    export PATH=/afs/slac/g/ki/software/python/2.5.5/amd64_rhel50/bin/:$PATH
-    export PYTHONPATH=/afs/slac/g/ki/software/python/2.5.5/amd64_rhel50/lib/python2.5/:$PYTHONPATH
+    export PATH=/afs/slac/g/ki/software/python/$python_version/amd64_rhel50/bin/:$PATH
+    export PYTHONPATH=/afs/slac/g/ki/software/python/$python_version/amd64_rhel50/lib/python2.5/:$PYTHONPATH
 }
 
 function ds9kipac {

### 2013-02-27 general/bash/slac_settings.sh

@@ -25,22 +25,44 @@ function fix_matplotlib {
 }
 
 
-function stockscons {
+
+function tempsetup1 {
+    _stockscons 09-31-01 Optimized
+    export PYTHONPATH=/u/gl/lande/lib/python2.7/site-packages:$PYTHONPATH
+    export PATH=~/bin:$PATH
+    export setup=`echo $setup | sed 's/stockscons/tempsetup1/g'`
+}
+
+function tempsetup2 {
+    _stockscons 09-30-00 Optimized
+    export PYTHONPATH=/u/gl/lande/lib/python2.7/site-packages:$PYTHONPATH
+    export PATH=~/bin:$PATH
+    export setup=`echo $setup | sed 's/stockscons/tempsetup2/g'`
+}
+
+function tempsetup3 {
     _stockscons 09-30-01 Optimized
+    export PYTHONPATH=/u/gl/lande/lib/python2.7/site-packages:$PYTHONPATH
+    export PATH=~/bin:$PATH
+    export setup=`echo $setup | sed 's/stockscons/tempsetup3/g'`
+}
+
+function tempsetup4 {
+    _stockscons 09-31-00 Optimized
+    export PYTHONPATH=/u/gl/lande/lib/python2.7/site-packages:$PYTHONPATH
+    export PATH=~/bin:$PATH
+    export setup=`echo $setup | sed 's/stockscons/tempsetup4/g'`
+}
+
+function stockscons {
+    #_stockscons 09-30-01 Optimized
+    _stockscons 09-31-01 Optimized
     export PATH=~/bin:$PATH
 }
 
 function testsconcs {
     # for testing stuff
     _stockscons 09-27-01 Optimized
-}
-
-function tempscons {
-    _stockscons 09-28-00 Optimized
-    export head=/u/gl/lande/head
-    export PYTHONPATH=$head:$PYTHONPATH
-    export PYTHONPATH=/u/gl/lande/lib/python2.7/site-packages:$PYTHONPATH
-    export setup=`echo $setup | sed 's/stockscons/tempscons/g'`
 }
 
 function headscons {
@@ -66,10 +88,16 @@ function headscons {
     export setup=`echo $setup | sed 's/stockscons/headscons/g'`
 }
 
+function pythonkipac {
+    #_pythonkipac 2.5.5
+    _pythonkipac 2.7.3 # Note, Checking for Chris - JL Dec 6, 2012
+}
+
 function devscons {
     # path of scons code
     set_bldtype
[…]

### 2013-02-27 fermi/gamma_quiet_psrs/pipeline/followup.py
update

@@ -9,7 +9,7 @@ from lande.fermi.pipeline.gamma_quiet_psrs.analysis.pipeline import Pipeline
 parser = ArgumentParser()
 parser.add_argument("--hypothesis", required=True, choices=['at_pulsar', 'point', 'extended'])
 parser.add_argument("--followup", required=True, choices=['tsmaps','plots', 'gtlike'])
-parser.add_argument("--size")
+parser.add_argument("--size", type=float)
 followup_args = parse_strip_known_args(parser)
 hypothesis = followup_args.hypothesis
 followup =followup_args.followup
@@ -23,7 +23,7 @@ if followup == 'gtlike':
     pipeline.gtlike_followup(hypothesis=hypothesis)
 elif followup == 'variability':
     pipeline.variability_followup(hypothesis=hypothesis)
-elif 'tsmaps' in followup:
+elif followup == 'tsmaps':
     pipeline.tsmaps_followup(hypothesis=hypothesis, size=size)
-elif 'plots' in followup:
+elif followup == 'plots':
     pipeline.plots_followup(hypothesis=hypothesis, size=size)

### 2013-02-27 fermi/gamma_quiet_psrs/pipeline/loop.py

@@ -62,10 +62,11 @@ radiopsr_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml'
 radiopsr_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml'
 names=loaddict(radiopsr_data).keys()
 bigfile='$lat2pc/BigFile/Pulsars_BigFile_v20121127171828.fits'
-modify='$gamma_quiet_psrs_modify/gamma_quiet_psrs_data.yaml'
+modify='$gamma_quiet_psrs_modify/gamma_quiet_psrs_data.py'
 
 params=dict(name=names, 
-            bigfile=bigfile)
+            bigfile=bigfile,
+            modify=modify)
 params['radiopsr-data']=radiopsr_data
 b = PipelineBuilder(
     savedir='$gamma_quiet_psrs_analysis/v4/fits',
@@ -83,6 +84,7 @@ for size in [5,10]:
     b.build_followup(
         code = '$gamma_quiet_psrs_pipeline/followup.py',
         hypotheses=['at_pulsar','point','extended'],
-        followups=['plots_%s' % size,'tsmap_%s' % size],
+        followups=['plots','tsmaps'],
+        followup_filenames=['plots_%s' % size,'tsmaps_%s' % size],
         extra='--size=%s' % size
     )

### 2013-02-27 fermi/gamma_quiet_psrs/website/website.py

@@ -10,7 +10,8 @@ b.build_all_psrs()
 """
 
 
-if True:
+#if True:
+if False:
     b=WebsiteBuilder(
         gamma_quiet_psrs_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml',
         analysisdir='$gamma_quiet_psrs_analysis/v2',
@@ -18,11 +19,20 @@ if True:
     b.build_main()
     b.build_all_psrs()
 
-if True:
-#if False:
+#if True:
+if False:
     b=WebsiteBuilder(
         gamma_quiet_psrs_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml',
         analysisdir='$gamma_quiet_psrs_analysis/v3',
         webdir='$gamma_quiet_psrs_analysis/v3/website')
+    b.build_main()
+    b.build_all_psrs()
+
+if True:
+#if False:
+    b=WebsiteBuilder(
+        gamma_quiet_psrs_data='$gamma_quiet_psrs_data/gamma_quiet_psrs_data.yaml',
+        analysisdir='$gamma_quiet_psrs_analysis/v4',
+        webdir='$gamma_quiet_psrs_analysis/v4/website')
     b.build_main()
     b.build_all_psrs()

### 2013-02-27 fermi/gamma_quiet_psrs/modify/gamma_quiet_psrs_data.py
update

@@ -1,0 +1,62 @@
+
+
+def modify_roi(roi, name):
+
+    print 'Running modify_roi on source %s' % name
+
+    deleted_sources = []
+    new_sources = []
+    
+    def delete(name, *args, **kwargs):
+        print ' * Deleting from ROI source %s' % name
+        source = roi.del_source(name, *args, **kwargs)
+        deleted_sources.append(name)
+
+    def add(source, *args, **kwargs):
+        print ' * Adding to ROI source %s' % (source.name)
+        roi.add_source(source, *args, **kwargs)
+        new_sources.append(source.name)
+
+
+    if name == 'J0855-4644':
+        pass
+    
+    elif name == 'J1341-6220':
+        pass
+    
+    elif name == 'J1400-6325':
+        pass
+    
+    elif name == 'J1437-5959':
+        pass
+
+    elif name == 'J1524-5625':
+        pass
+        
+    elif name == 'J1747-2809':
+        pass
+        
+    elif name == 'J1811-1925':
+        pass
+        
+    elif name == 'J1828-1101':
+        pass
+    
+    elif name == 'J1837-0604':
+        pass
+    
+    elif name == 'J1928+1746':
+        delete('2FGL J1928.8+1740c')
+
+    elif name == 'J1936+2025':
+        pass
+        
+    elif name == 'J2022+3842':
+        delete('2FGL J2022.8+3843c')
+
+    else:
+        raise Exception("Unrecognized source %s" % name)
+
+    print 'Done running modify_roi on source %s' % name
+
+    return new_sources, deleted_sources
